### 2021-08-27 manuscript.Rmd
Initial commit of manuscript

---
title             : "Light Exposure Behavior Assessment"
shorttitle        : "Title"

author: 
  - name          : "Mushfiqul Anwar Siraji"
    affiliation   : "1"
    corresponding : no   
    address       : "Monash University, Malaysia"
    email         : "mushfiqul.anwarsiraji@monash.edu"
    role:         
      - Data Analysis
      - Writing - Original Draft Preparation
      - Data Visualization

  - name          : "Rafael Robert Lazar"
    affiliation   : "2"
    role:
      - Writing - Original Draft Preparation

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
library(readr)
library(readxl)
library(lavaan)
library(semPlot)
library(semTools)
library(hemp)
library(psych)
library(dlookr)
library(tidyverse)
library(qgraph)
library(kableExtra)
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```
# Methods

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.

# Results

# Confirmatory Factor Analysis

```{r CFA, }
LB.cfa <- read_excel("Processed Data/SpitschanSleepSurvey_DATA_2021-08-24_1819_redacted_199_CFA.xlsx")
LB.cfa$id <- NULL
summarize <- summary(LB.cfa)
Descriptives <- psych::describe(LB.cfa)
#Univariate Normality
normality <- normality(LB.cfa) 
#Multivariate Normality
mardia(LB.cfa, na.rm = T, plot =F)

# CFA with five factor (23 items)
LB.model.Cor <- "F1 =~ item31+ item33+ item1+ item37 + item 24
             F2 =~ item10 + item47 + item36 + item44 + item35 + item13
            F3 =~ item43 + item26 + item32
           F4 =~  item14 + item 7 + item11 + item42 + item12 + item16 
            F5 =~ item19 + item34 + item2" 
fit.Cor <- cfa(LB.model.Cor, data = LB.cfa, estimator = "MLR", mimic = "Mplus") 
## Summary of Model 
summary(fit.Cor, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
## Selected Fit measures 
fitmeasures (fit.Cor,c("gfi", "agfi", "nfi","rfi", 
                       "cfi.robust","tli.robust",
                       "rmsea.robust", 
                       "srmr","aic"))

semTools::reliability(fit.Cor)

```

Based on CFI, TLI, RMSEA and SRMR value the fitted five factor model is not acceptable.
As a result a close inspection  on items with low factor-loadings and low R-square value was conducted. two items were found to be problematic **item7, item 24** with vary low R-square 
value thus discarded from the model.

```{r CFA23}
#Five factor correlational Model without item24, item 7 [21 Items]
LB.model.Cor.2 <- "F1 =~ item31+ item33+ item1+ item37
             F2 =~ item10 + item47 + item36 +  item35 + item13 + item44
            F3 =~ item43 + item26 + item32
           F4 =~  item14 +  item42 + item12 + item11 + item16 
             F5 =~ item19 + item34 + item2" 
## Fit the model 
fit.Cor.2 <- cfa(LB.model.Cor.2, data = LB.cfa, estimator = "MLR", mimic = "Mplus") 
## Summary of Model 
summary(fit.Cor.2, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
## Selected Fit measures 
fit.2 <- fitmeasures (fit.Cor.2,c("gfi", "agfi", "nfi","rfi", 
                       "cfi.robust","tli.robust",
                       "rmsea.robust", 
                       "srmr","aic"))
rownames <-  ("fitIndices")
colnames <- c("gfi", "agfi", "nfi","rfi", 
                       "cfi.robust","tli.robust",
                       "rmsea.robust", 
                       "srmr","aic")
dimnames <- list(rownames, colnames)
fitmatrix <- matrix(fit.2, nrow = 1, ncol = 9, byrow = T, dimnames)
semTools::reliability(fit.Cor.2)
```

```{r CFA5Mod}
modfit.Cor <- modindices(fit.Cor.2, sort. = TRUE) 
modfit.Cor[modfit.Cor$mi>3.84,] 
```

```{r CFA5bestfit}
#21 items
LB.model.Cor.3 <- "F1 =~ item31+ item33+ item1+ item37
             F2 =~ item10 + item47 + item36 +  item35 + item13 + item44
            F3 =~ item43 + item26 + item32
           F4 =~  item14 +  item42 + item12 + item11 + item16 
             F5 =~ item19 + item34 + item2
                    item31 ~~ item33
                     item12 ~~ item11" 
## Fit the model 
fit.Cor.3 <- cfa(LB.model.Cor.3, data = LB.cfa, estimator = "MLR", mimic = "Mplus") 
## Summary of Model 
summary(fit.Cor.3, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
## Selected Fit measures 
fit.3 <- fitmeasures (fit.Cor.3,c("gfi", "agfi", "nfi","rfi", 
                       "cfi.robust","tli.robust",
                       "rmsea.robust", 
                       "srmr","aic"))
rownames <-  ("fitIndices")
colnames <- c("gfi", "agfi", "nfi","rfi", 
                       "cfi.robust","tli.robust",
                       "rmsea.robust", 
                       "srmr","aic")
dimnames <- list(rownames, colnames)
fitmatrix <- matrix(fit.3, nrow = 1, ncol = 9, byrow = T, dimnames)
reliability1 <- semTools::reliability(fit.Cor.3, return.total = T)
as.table(reliability1 )
```

```{r CFA6}
#24 items
LB.model.Cor.4 <- "F1 =~ item31+ item33+ item1+ item37
             F2 =~ item10 + item47 + item36 +  item35 + item13 + item44
            F3 =~ item43 + item26 + item32
           F4 =~  item14 +  item42 + item12 + item11 + item16 
             F5 =~ item19 + item34 + item2
             F6 =~ item38 + item28 + item45
                   item31 ~~ item33
                    item10 ~~ item13
                     item12 ~~ item11
                     item26 ~~ item19  "

## Fit the model 
fit.Cor.4 <- cfa(LB.model.Cor.4, data = LB.cfa, estimator = "MLR", mimic = "Mplus")

## Summary of Model 
summary(fit.Cor.4, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)

## Selected Fit measures 
fit.4 <- fitmeasures (fit.Cor.4,c("gfi", "agfi", "nfi","rfi", 
                       "cfi.robust","tli.robust",
                       "rmsea.robust", 
                       "srmr","aic"))
reliability <- semTools::reliability(fit.Cor.4, return.total = T)
as.table(reliability)
```

# Discussion

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2021-08-27 manuscript.Rmd
U[dates

@@
 ```{r CFA, }
-LB.cfa <- read_excel("Processed Data/SpitschanSleepSurvey_DATA_2021-08-24_1819_redacted_199_CFA.xlsx")
+LB.cfa <- read_excel("SpitschanSleepSurvey_DATA_2021-08-24_1819_redacted_199_CFA.xlsx")
 LB.cfa$id <- NULL

### 2021-08-27 manuscript.Rmd
Updates

@@
 ---
-title             : "Light Exposure Behavior Assessment"
+title             : "_Light Exposure Behavior Assessment (LEBA)_: Develop of a novel instrument to capture light exposure-related behaviours"
 shorttitle        : "Title"
@@
 ```{r setup, include = FALSE}
-library("papaja")
+library(papaja) # devtools::install_github("crsh/papaja")
 r_refs("r-references.bib")
@@
 library(semTools)
-library(hemp)
+library(hemp) # devtools::install_github("cddesja/hemp")
 library(psych)

### 2021-08-27 manuscript.tex
Updates

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Light Exposure Behavior Assessment (LEBA): Develop of a novel instrument to capture light exposure-related behaviours},
  pdfauthor={Mushfiqul Anwar Siraji1 \& Rafael Robert Lazar2},
  pdflang={en-EN},
  pdfkeywords={keywords},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Title}
\keywords{keywords\newline\indent Word count: X}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifXeTeX
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\title{\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours}
\author{Mushfiqul Anwar Siraji\textsuperscript{1} \& Rafael Robert Lazar\textsuperscript{2}}
\date{}

\authornote{

Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

Enter author note here.

The authors made the following contributions. Mushfiqul Anwar Siraji: Data Analysis, Writing - Original Draft Preparation, Data Visualization; Rafael Robert Lazar: Writing - Original Draft Preparation.

Correspondence concerning this article should be addressed to Mushfiqul Anwar Siraji, Monash University, Malaysia. E-mail: \href{mailto:mushfiqul.anwarsiraji@monash.edu}{\nolinkurl{mushfiqul.anwarsiraji@monash.edu}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Wilhelm-Wundt-University\\\textsuperscript{2} Konstanz Business School}

\abstract{
One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.

Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.

One sentence clearly stating the \textbf{general problem} being addressed by this particular study.

One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).

Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.

One or two sentences to put the results into a more \textbf{general context}.

Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
}

\begin{document}
\maketitle

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{participants}{%
\subsection{Participants}\label{participants}}

\hypertarget{material}{%
\subsection{Material}\label{material}}

\hypertarget{procedure}{%
\subsection{Procedure}\label{procedure}}

\hypertarget{data-analysis}{%
\subsection{Data analysis}\label{data-analysis}}

We used R {[}Version 4.0.3; R Core Team (2020){]} and the R-package \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]} for all our analyses.

\hypertarget{results}{%
\section{Results}\label{results}}

\hypertarget{confirmatory-factor-analysis}{%
\section{Confirmatory Factor Analysis}\label{confirmatory-factor-analysis}}

\begin{verbatim}
## Call: mardia(x = LB.cfa, na.rm = T, plot = F)
## 
## Mardia tests of multivariate skew and kurtosis
## Use describe(x) the to get univariate tests
## n.obs = 199   num.vars =  48 
## b1p =  761.72   skew =  25263.82  with probability  <=  8.8e-152
##  small sample skew =  25660.39  with probability <=  1.2e-171
## b2p =  2540.5   kurtosis =  14.3  with probability <=  0
\end{verbatim}

\begin{verbatim}
## lavaan 0.6-9 ended normally after 64 iterations
## 
##   Estimator                                         ML
##   Optimization method                           NLMINB
##   Number of model parameters                        79
##                                                       
##   Number of observations                           199
##   Number of missing patterns                         1
##                                                       
## Model Test User Model:
##                                                Standard      Robust
##   Test Statistic                                406.275     387.999
##   Degrees of freedom                                220         220
##   P-value (Chi-square)                            0.000       0.000
##   Scaling correction factor                                   1.047
##        Yuan-Bentler correction (Mplus variant)                     
## 
## Model Test Baseline Model:
## 
##   Test statistic                              1700.445    1368.235
##   Degrees of freedom                               253         253
##   P-value                                        0.000       0.000
##   Scaling correction factor                                  1.243
## 
## User Model versus Baseline Model:
## 
##   Comparative Fit Index (CFI)                    0.871       0.849
##   Tucker-Lewis Index (TLI)                       0.852       0.827
##                                                                   
##   Robust Comparative Fit Index (CFI)                         0.873
##   Robust Tucker-Lewis Index (TLI)                            0.854
## 
## Loglikelihood and Information Criteria:
## 
##   Loglikelihood user model (H0)              -6371.304   -6371.304
##   Scaling correction factor                                  1.877
##       for the MLR correction                                      
##   Loglikelihood unrestricted model (H1)      -6168.166   -6168.166
##   Scaling correction factor                                  1.266
##       for the MLR correction                                      
##                                                                   
##   Akaike (AIC)                               12900.607   12900.607
##   Bayesian (BIC)                             13160.778   13160.778
##   Sample-size adjusted Bayesian (BIC)        12910.502   12910.502
## 
## Root Mean Square Error of Approximation:
## 
##   RMSEA                                          0.065       0.062
##   90 Percent confidence interval - lower         0.055       0.052
##   90 Percent confidence interval - upper         0.075       0.072
##   P-value RMSEA <= 0.05                          0.007       0.026
##                                                                   
##   Robust RMSEA                                               0.063
##   90 Percent confidence interval - lower                     0.053
##   90 Percent confidence interval - upper                     0.074
## 
## Standardized Root Mean Square Residual:
## 
##   SRMR                                           0.075       0.075
## 
## Parameter Estimates:
## 
##   Standard errors                             Sandwich
##   Information bread                           Observed
##   Observed information based on                Hessian
## 
## Latent Variables:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   F1 =~                                                                 
##     item31            1.000                               0.397    0.873
##     item33            0.823    0.123    6.685    0.000    0.327    0.724
##     item1             0.990    0.158    6.246    0.000    0.393    0.644
##     item37            0.901    0.284    3.176    0.001    0.358    0.507
##     item24            0.437    0.265    1.647    0.100    0.173    0.175
##   F2 =~                                                                 
##     item10            1.000                               0.859    0.783
##     item47            0.856    0.111    7.729    0.000    0.736    0.808
##     item36            0.945    0.137    6.876    0.000    0.812    0.701
##     item44           -0.714    0.139   -5.131    0.000   -0.613   -0.490
##     item35            0.739    0.139    5.300    0.000    0.635    0.508
##     item13            0.472    0.113    4.163    0.000    0.406    0.373
##   F3 =~                                                                 
##     item43            1.000                               1.291    0.951
##     item26            0.918    0.056   16.313    0.000    1.186    0.843
##     item32            0.895    0.064   13.928    0.000    1.155    0.872
##   F4 =~                                                                 
##     item14            1.000                               0.493    0.263
##     item7             0.640    0.267    2.392    0.017    0.316    0.171
##     item11            1.850    0.684    2.706    0.007    0.912    0.708
##     item42            0.788    0.314    2.513    0.012    0.389    0.225
##     item12            1.953    0.779    2.509    0.012    0.963    0.845
##     item16            1.017    0.410    2.479    0.013    0.501    0.343
##   F5 =~                                                                 
##     item19            1.000                               0.875    0.683
##     item34            1.312    0.174    7.555    0.000    1.148    0.831
##     item2             0.974    0.143    6.827    0.000    0.852    0.606
## 
## Covariances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   F1 ~~                                                                 
##     F2                0.038    0.033    1.169    0.243    0.112    0.112
##     F3               -0.019    0.051   -0.372    0.710   -0.037   -0.037
##     F4                0.013    0.024    0.532    0.595    0.064    0.064
##     F5                0.027    0.034    0.795    0.427    0.078    0.078
##   F2 ~~                                                                 
##     F3               -0.076    0.076   -0.998    0.318   -0.069   -0.069
##     F4                0.077    0.054    1.443    0.149    0.182    0.182
##     F5               -0.259    0.088   -2.929    0.003   -0.344   -0.344
##   F3 ~~                                                                 
##     F4                0.032    0.065    0.501    0.616    0.051    0.051
##     F5               -0.035    0.103   -0.339    0.735   -0.031   -0.031
##   F4 ~~                                                                 
##     F5               -0.015    0.044   -0.350    0.726   -0.036   -0.036
## 
## Intercepts:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##    .item31            0.879    0.032   27.295    0.000    0.879    1.935
##    .item33            0.869    0.032   27.150    0.000    0.869    1.925
##    .item1             0.990    0.043   22.904    0.000    0.990    1.624
##    .item37            0.995    0.050   19.900    0.000    0.995    1.411
##    .item24            1.131    0.070   16.129    0.000    1.131    1.143
##    .item10            2.543    0.078   32.704    0.000    2.543    2.318
##    .item47            2.035    0.065   31.553    0.000    2.035    2.237
##    .item36            2.095    0.082   25.511    0.000    2.095    1.808
##    .item44            2.995    0.089   33.796    0.000    2.995    2.396
##    .item35            2.070    0.089   23.362    0.000    2.070    1.656
##    .item13            2.834    0.077   36.750    0.000    2.834    2.605
##    .item43            1.578    0.096   16.401    0.000    1.578    1.163
##    .item26            1.482    0.100   14.868    0.000    1.482    1.054
##    .item32            1.533    0.094   16.314    0.000    1.533    1.156
##    .item14            3.020    0.133   22.749    0.000    3.020    1.613
##    .item7             3.688    0.131   28.175    0.000    3.688    1.997
##    .item11            2.382    0.091   26.054    0.000    2.382    1.847
##    .item42            2.935    0.122   23.959    0.000    2.935    1.698
##    .item12            2.005    0.081   24.793    0.000    2.005    1.758
##    .item16            3.211    0.104   30.991    0.000    3.211    2.197
##    .item19            3.930    0.091   43.244    0.000    3.930    3.065
##    .item34            3.583    0.098   36.558    0.000    3.583    2.592
##    .item2             2.482    0.100   24.897    0.000    2.482    1.765
##     F1                0.000                               0.000    0.000
##     F2                0.000                               0.000    0.000
##     F3                0.000                               0.000    0.000
##     F4                0.000                               0.000    0.000
##     F5                0.000                               0.000    0.000
## 
## Variances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##    .item31            0.049    0.032    1.533    0.125    0.049    0.237
##    .item33            0.097    0.058    1.678    0.093    0.097    0.476
##    .item1             0.217    0.058    3.718    0.000    0.217    0.585
##    .item37            0.370    0.125    2.952    0.003    0.370    0.743
##    .item24            0.948    0.200    4.729    0.000    0.948    0.969
##    .item10            0.465    0.130    3.582    0.000    0.465    0.386
##    .item47            0.287    0.054    5.359    0.000    0.287    0.347
##    .item36            0.683    0.094    7.283    0.000    0.683    0.509
##    .item44            1.187    0.139    8.551    0.000    1.187    0.760
##    .item35            1.160    0.156    7.447    0.000    1.160    0.742
##    .item13            1.019    0.112    9.133    0.000    1.019    0.861
##    .item43            0.175    0.101    1.726    0.084    0.175    0.095
##    .item26            0.573    0.164    3.500    0.000    0.573    0.289
##    .item32            0.422    0.114    3.694    0.000    0.422    0.240
##    .item14            3.264    0.236   13.831    0.000    3.264    0.931
##    .item7             3.311    0.274   12.104    0.000    3.311    0.971
##    .item11            0.831    0.172    4.816    0.000    0.831    0.499
##    .item42            2.835    0.171   16.555    0.000    2.835    0.949
##    .item12            0.373    0.155    2.413    0.016    0.373    0.287
##    .item16            1.885    0.199    9.453    0.000    1.885    0.882
##    .item19            0.877    0.130    6.769    0.000    0.877    0.534
##    .item34            0.592    0.179    3.319    0.001    0.592    0.310
##    .item2             1.252    0.144    8.687    0.000    1.252    0.633
##     F1                0.158    0.033    4.750    0.000    1.000    1.000
##     F2                0.738    0.147    5.035    0.000    1.000    1.000
##     F3                1.667    0.246    6.764    0.000    1.000    1.000
##     F4                0.243    0.170    1.431    0.152    1.000    1.000
##     F5                0.766    0.164    4.669    0.000    1.000    1.000
## 
## R-Square:
##                    Estimate
##     item31            0.763
##     item33            0.524
##     item1             0.415
##     item37            0.257
##     item24            0.031
##     item10            0.614
##     item47            0.653
##     item36            0.491
##     item44            0.240
##     item35            0.258
##     item13            0.139
##     item43            0.905
##     item26            0.711
##     item32            0.760
##     item14            0.069
##     item7             0.029
##     item11            0.501
##     item42            0.051
##     item12            0.713
##     item16            0.118
##     item19            0.466
##     item34            0.690
##     item2             0.367
\end{verbatim}

\begin{verbatim}
##          gfi         agfi          nfi          rfi   cfi.robust   tli.robust 
##        0.974        0.965        0.761        0.725        0.873        0.854 
## rmsea.robust         srmr          aic 
##        0.063        0.075    12900.607
\end{verbatim}

\begin{verbatim}
##               F1        F2        F3        F4        F5
## alpha  0.6310368 0.4818562 0.9175522 0.5837683 0.7413266
## omega  0.6175478 0.6258140 0.9185279 0.5055608 0.7523535
## omega2 0.6175478 0.6258140 0.9185279 0.5055608 0.7523535
## omega3 0.5953438 0.6255108 0.9183889 0.4373745 0.7559532
## avevar 0.2554061 0.3750499 0.7902138 0.1670288 0.5080283
\end{verbatim}

Based on CFI, TLI, RMSEA and SRMR value the fitted five factor model is not acceptable.
As a result a close inspection on items with low factor-loadings and low R-square value was conducted. two items were found to be problematic \textbf{item7, item 24} with vary low R-square
value thus discarded from the model.

\begin{verbatim}
## lavaan 0.6-9 ended normally after 67 iterations
## 
##   Estimator                                         ML
##   Optimization method                           NLMINB
##   Number of model parameters                        73
##                                                       
##   Number of observations                           199
##   Number of missing patterns                         1
##                                                       
## Model Test User Model:
##                                                Standard      Robust
##   Test Statistic                                273.193     263.376
##   Degrees of freedom                                179         179
##   P-value (Chi-square)                            0.000       0.000
##   Scaling correction factor                                   1.037
##        Yuan-Bentler correction (Mplus variant)                     
## 
## Model Test Baseline Model:
## 
##   Test statistic                              1557.809    1230.314
##   Degrees of freedom                               210         210
##   P-value                                        0.000       0.000
##   Scaling correction factor                                  1.266
## 
## User Model versus Baseline Model:
## 
##   Comparative Fit Index (CFI)                    0.930       0.917
##   Tucker-Lewis Index (TLI)                       0.918       0.903
##                                                                   
##   Robust Comparative Fit Index (CFI)                         0.932
##   Robust Tucker-Lewis Index (TLI)                            0.921
## 
## Loglikelihood and Information Criteria:
## 
##   Loglikelihood user model (H0)              -5691.495   -5691.495
##   Scaling correction factor                                  1.890
##       for the MLR correction                                      
##   Loglikelihood unrestricted model (H1)      -5554.899   -5554.899
##   Scaling correction factor                                  1.284
##       for the MLR correction                                      
##                                                                   
##   Akaike (AIC)                               11528.990   11528.990
##   Bayesian (BIC)                             11769.401   11769.401
##   Sample-size adjusted Bayesian (BIC)        11538.134   11538.134
## 
## Root Mean Square Error of Approximation:
## 
##   RMSEA                                          0.051       0.049
##   90 Percent confidence interval - lower         0.039       0.036
##   90 Percent confidence interval - upper         0.063       0.061
##   P-value RMSEA <= 0.05                          0.412       0.559
##                                                                   
##   Robust RMSEA                                               0.050
##   90 Percent confidence interval - lower                     0.036
##   90 Percent confidence interval - upper                     0.062
## 
## Standardized Root Mean Square Residual:
## 
##   SRMR                                           0.068       0.068
## 
## Parameter Estimates:
## 
##   Standard errors                             Sandwich
##   Information bread                           Observed
##   Observed information based on                Hessian
## 
## Latent Variables:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   F1 =~                                                                 
##     item31            1.000                               0.397    0.873
##     item33            0.828    0.119    6.962    0.000    0.328    0.727
##     item1             0.992    0.153    6.503    0.000    0.394    0.645
##     item37            0.890    0.278    3.203    0.001    0.353    0.501
##   F2 =~                                                                 
##     item10            1.000                               0.859    0.783
##     item47            0.856    0.111    7.739    0.000    0.735    0.808
##     item36            0.946    0.138    6.876    0.000    0.812    0.701
##     item35            0.739    0.139    5.300    0.000    0.635    0.508
##     item13            0.472    0.113    4.162    0.000    0.405    0.373
##     item44           -0.714    0.139   -5.133    0.000   -0.613   -0.490
##   F3 =~                                                                 
##     item43            1.000                               1.291    0.951
##     item26            0.919    0.056   16.331    0.000    1.186    0.843
##     item32            0.895    0.064   13.941    0.000    1.155    0.872
##   F4 =~                                                                 
##     item14            1.000                               0.444    0.237
##     item42            0.867    0.332    2.614    0.009    0.385    0.223
##     item12            2.245    0.830    2.704    0.007    0.996    0.873
##     item11            2.009    0.720    2.791    0.005    0.891    0.691
##     item16            1.108    0.445    2.488    0.013    0.492    0.336
##   F5 =~                                                                 
##     item19            1.000                               0.875    0.683
##     item34            1.312    0.173    7.568    0.000    1.148    0.831
##     item2             0.974    0.143    6.828    0.000    0.852    0.606
## 
## Covariances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   F1 ~~                                                                 
##     F2                0.037    0.032    1.143    0.253    0.108    0.108
##     F3               -0.020    0.051   -0.400    0.689   -0.040   -0.040
##     F4                0.011    0.020    0.535    0.593    0.062    0.062
##     F5                0.029    0.034    0.843    0.399    0.083    0.083
##   F2 ~~                                                                 
##     F3               -0.076    0.076   -0.998    0.318   -0.069   -0.069
##     F4                0.069    0.048    1.434    0.152    0.181    0.181
##     F5               -0.259    0.088   -2.931    0.003   -0.344   -0.344
##   F3 ~~                                                                 
##     F4                0.025    0.056    0.449    0.654    0.044    0.044
##     F5               -0.035    0.103   -0.339    0.735   -0.031   -0.031
##   F4 ~~                                                                 
##     F5               -0.015    0.039   -0.376    0.707   -0.038   -0.038
## 
## Intercepts:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##    .item31            0.879    0.032   27.295    0.000    0.879    1.935
##    .item33            0.869    0.032   27.150    0.000    0.869    1.925
##    .item1             0.990    0.043   22.904    0.000    0.990    1.624
##    .item37            0.995    0.050   19.900    0.000    0.995    1.411
##    .item10            2.543    0.078   32.704    0.000    2.543    2.318
##    .item47            2.035    0.065   31.553    0.000    2.035    2.237
##    .item36            2.095    0.082   25.511    0.000    2.095    1.808
##    .item35            2.070    0.089   23.362    0.000    2.070    1.656
##    .item13            2.834    0.077   36.750    0.000    2.834    2.605
##    .item44            2.995    0.089   33.796    0.000    2.995    2.396
##    .item43            1.578    0.096   16.401    0.000    1.578    1.163
##    .item26            1.482    0.100   14.868    0.000    1.482    1.054
##    .item32            1.533    0.094   16.314    0.000    1.533    1.156
##    .item14            3.020    0.133   22.749    0.000    3.020    1.613
##    .item42            2.935    0.122   23.959    0.000    2.935    1.698
##    .item12            2.005    0.081   24.793    0.000    2.005    1.758
##    .item11            2.382    0.091   26.054    0.000    2.382    1.847
##    .item16            3.211    0.104   30.991    0.000    3.211    2.197
##    .item19            3.930    0.091   43.244    0.000    3.930    3.065
##    .item34            3.583    0.098   36.558    0.000    3.583    2.592
##    .item2             2.482    0.100   24.897    0.000    2.482    1.765
##     F1                0.000                               0.000    0.000
##     F2                0.000                               0.000    0.000
##     F3                0.000                               0.000    0.000
##     F4                0.000                               0.000    0.000
##     F5                0.000                               0.000    0.000
## 
## Variances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##    .item31            0.049    0.031    1.578    0.115    0.049    0.238
##    .item33            0.096    0.058    1.669    0.095    0.096    0.472
##    .item1             0.217    0.058    3.717    0.000    0.217    0.583
##    .item37            0.373    0.124    3.005    0.003    0.373    0.749
##    .item10            0.465    0.130    3.584    0.000    0.465    0.387
##    .item47            0.287    0.054    5.343    0.000    0.287    0.347
##    .item36            0.683    0.094    7.276    0.000    0.683    0.509
##    .item35            1.160    0.156    7.452    0.000    1.160    0.742
##    .item13            1.019    0.112    9.133    0.000    1.019    0.861
##    .item44            1.187    0.139    8.549    0.000    1.187    0.759
##    .item43            0.175    0.101    1.731    0.083    0.175    0.095
##    .item26            0.572    0.164    3.498    0.000    0.572    0.289
##    .item32            0.422    0.114    3.695    0.000    0.422    0.240
##    .item14            3.310    0.213   15.534    0.000    3.310    0.944
##    .item42            2.838    0.170   16.714    0.000    2.838    0.950
##    .item12            0.310    0.180    1.719    0.086    0.310    0.238
##    .item11            0.869    0.182    4.765    0.000    0.869    0.522
##    .item16            1.895    0.201    9.419    0.000    1.895    0.887
##    .item19            0.877    0.129    6.775    0.000    0.877    0.534
##    .item34            0.593    0.178    3.327    0.001    0.593    0.310
##    .item2             1.252    0.144    8.693    0.000    1.252    0.633
##     F1                0.157    0.032    4.874    0.000    1.000    1.000
##     F2                0.738    0.146    5.037    0.000    1.000    1.000
##     F3                1.667    0.246    6.765    0.000    1.000    1.000
##     F4                0.197    0.132    1.493    0.136    1.000    1.000
##     F5                0.766    0.164    4.669    0.000    1.000    1.000
## 
## R-Square:
##                    Estimate
##     item31            0.762
##     item33            0.528
##     item1             0.417
##     item37            0.251
##     item10            0.613
##     item47            0.653
##     item36            0.491
##     item35            0.258
##     item13            0.139
##     item44            0.241
##     item43            0.905
##     item26            0.711
##     item32            0.760
##     item14            0.056
##     item42            0.050
##     item12            0.762
##     item11            0.478
##     item16            0.113
##     item19            0.466
##     item34            0.690
##     item2             0.367
\end{verbatim}

\begin{verbatim}
##               F1        F2        F3        F4        F5
## alpha  0.7547222 0.4818562 0.9175522 0.5566040 0.7413266
## omega  0.7466444 0.6258291 0.9185357 0.5272886 0.7523499
## omega2 0.7466444 0.6258291 0.9185357 0.5272886 0.7523499
## omega3 0.7344825 0.6255092 0.9184124 0.4921277 0.7559546
## avevar 0.4256850 0.3750895 0.7902299 0.2046565 0.5080155
\end{verbatim}

\begin{verbatim}
##        lhs op    rhs     mi    epc sepc.lv sepc.all sepc.nox
## 168 item31 ~~ item33 17.975  0.090   0.090    1.313    1.313
## 136     F4 =~  item1 14.553  0.339   0.150    0.247    0.247
## 245 item10 ~~ item13 13.377  0.222   0.222    0.322    0.322
## 134     F4 =~ item31 11.467 -0.210  -0.093   -0.205   -0.205
## 359 item42 ~~ item16 11.094  0.562   0.562    0.242    0.242
## 207  item1 ~~ item37 10.910  0.078   0.078    0.274    0.274
## 104     F2 =~ item37 10.403  0.184   0.158    0.224    0.224
## 363 item12 ~~ item11  9.624  1.312   1.312    2.529    2.529
## 339 item26 ~~ item19  8.623  0.177   0.177    0.250    0.250
## 137     F4 =~ item37  7.959  0.316   0.140    0.199    0.199
## 101     F2 =~ item31  7.808 -0.089  -0.076   -0.167   -0.167
## 237 item37 ~~ item11  7.249  0.122   0.122    0.215    0.215
## 218  item1 ~~ item42  7.190  0.159   0.159    0.203    0.203
## 188 item33 ~~  item1  6.541 -0.046  -0.046   -0.318   -0.318
## 308 item13 ~~ item16  6.525  0.258   0.258    0.186    0.186
## 332 item43 ~~  item2  6.427  0.140   0.140    0.300    0.300
## 350 item14 ~~ item42  5.773  0.530   0.530    0.173    0.173
## 362 item42 ~~  item2  5.298  0.330   0.330    0.175    0.175
## 100     F1 =~  item2  5.261 -0.547  -0.217   -0.154   -0.154
## 233 item37 ~~ item32  5.251  0.074   0.074    0.186    0.186
## 173 item31 ~~ item36  5.150 -0.045  -0.045   -0.248   -0.248
## 330 item43 ~~ item19  5.106 -0.109  -0.109   -0.277   -0.277
## 192 item33 ~~ item36  4.870  0.048   0.048    0.187    0.187
## 167     F5 =~ item16  4.750  0.278   0.243    0.166    0.166
## 170 item31 ~~ item37  4.638 -0.042  -0.042   -0.313   -0.313
## 141     F4 =~ item35  4.630  0.435   0.193    0.154    0.154
## 258 item47 ~~ item36  4.608  0.121   0.121    0.273    0.273
## 358 item42 ~~ item11  4.551 -0.293  -0.293   -0.187   -0.187
## 115     F2 =~  item2  4.513 -0.260  -0.224   -0.159   -0.159
## 226 item37 ~~ item47  4.505  0.060   0.060    0.184    0.184
## 114     F2 =~ item34  4.482  0.276   0.237    0.172    0.172
## 219  item1 ~~ item12  4.328  0.064   0.064    0.247    0.247
## 206 item33 ~~  item2  4.291 -0.060  -0.060   -0.173   -0.173
## 96      F1 =~ item11  4.020 -0.412  -0.164   -0.127   -0.127
\end{verbatim}

\begin{verbatim}
## lavaan 0.6-9 ended normally after 67 iterations
## 
##   Estimator                                         ML
##   Optimization method                           NLMINB
##   Number of model parameters                        75
##                                                       
##   Number of observations                           199
##   Number of missing patterns                         1
##                                                       
## Model Test User Model:
##                                                Standard      Robust
##   Test Statistic                                233.643     228.963
##   Degrees of freedom                                177         177
##   P-value (Chi-square)                            0.003       0.005
##   Scaling correction factor                                   1.020
##        Yuan-Bentler correction (Mplus variant)                     
## 
## Model Test Baseline Model:
## 
##   Test statistic                              1557.809    1230.314
##   Degrees of freedom                               210         210
##   P-value                                        0.000       0.000
##   Scaling correction factor                                  1.266
## 
## User Model versus Baseline Model:
## 
##   Comparative Fit Index (CFI)                    0.958       0.949
##   Tucker-Lewis Index (TLI)                       0.950       0.940
##                                                                   
##   Robust Comparative Fit Index (CFI)                         0.959
##   Robust Tucker-Lewis Index (TLI)                            0.951
## 
## Loglikelihood and Information Criteria:
## 
##   Loglikelihood user model (H0)              -5671.720   -5671.720
##   Scaling correction factor                                  1.907
##       for the MLR correction                                      
##   Loglikelihood unrestricted model (H1)      -5554.899   -5554.899
##   Scaling correction factor                                  1.284
##       for the MLR correction                                      
##                                                                   
##   Akaike (AIC)                               11493.441   11493.441
##   Bayesian (BIC)                             11740.438   11740.438
##   Sample-size adjusted Bayesian (BIC)        11502.834   11502.834
## 
## Root Mean Square Error of Approximation:
## 
##   RMSEA                                          0.040       0.038
##   90 Percent confidence interval - lower         0.024       0.022
##   90 Percent confidence interval - upper         0.053       0.052
##   P-value RMSEA <= 0.05                          0.884       0.920
##                                                                   
##   Robust RMSEA                                               0.039
##   90 Percent confidence interval - lower                     0.022
##   90 Percent confidence interval - upper                     0.052
## 
## Standardized Root Mean Square Residual:
## 
##   SRMR                                           0.061       0.061
## 
## Parameter Estimates:
## 
##   Standard errors                             Sandwich
##   Information bread                           Observed
##   Observed information based on                Hessian
## 
## Latent Variables:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   F1 =~                                                                 
##     item31            1.000                               0.293    0.645
##     item33            0.755    0.145    5.204    0.000    0.221    0.490
##     item1             1.782    0.655    2.721    0.007    0.522    0.856
##     item37            1.345    0.379    3.548    0.000    0.394    0.559
##   F2 =~                                                                 
##     item10            1.000                               0.858    0.782
##     item47            0.859    0.109    7.846    0.000    0.736    0.809
##     item36            0.947    0.137    6.937    0.000    0.813    0.701
##     item35            0.740    0.139    5.318    0.000    0.634    0.507
##     item13            0.475    0.114    4.169    0.000    0.407    0.374
##     item44           -0.714    0.139   -5.146    0.000   -0.612   -0.490
##   F3 =~                                                                 
##     item43            1.000                               1.291    0.951
##     item26            0.918    0.056   16.327    0.000    1.185    0.843
##     item32            0.895    0.064   13.889    0.000    1.155    0.872
##   F4 =~                                                                 
##     item14            1.000                               0.658    0.351
##     item42            1.470    0.481    3.058    0.002    0.967    0.559
##     item12            0.797    0.266    2.995    0.003    0.524    0.459
##     item11            0.527    0.254    2.078    0.038    0.347    0.269
##     item16            0.993    0.429    2.313    0.021    0.653    0.447
##   F5 =~                                                                 
##     item19            1.000                               0.870    0.679
##     item34            1.313    0.167    7.871    0.000    1.142    0.826
##     item2             0.995    0.150    6.653    0.000    0.866    0.615
## 
## Covariances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##  .item31 ~~                                                             
##    .item33            0.070    0.027    2.632    0.008    0.070    0.513
##  .item12 ~~                                                             
##    .item11            0.716    0.139    5.135    0.000    0.716    0.569
##   F1 ~~                                                                 
##     F2                0.050    0.027    1.849    0.064    0.197    0.197
##     F3               -0.008    0.035   -0.239    0.811   -0.022   -0.022
##     F4                0.080    0.031    2.530    0.011    0.413    0.413
##     F5                0.010    0.026    0.395    0.693    0.040    0.040
##   F2 ~~                                                                 
##     F3               -0.076    0.076   -1.000    0.317   -0.069   -0.069
##     F4                0.119    0.083    1.424    0.154    0.210    0.210
##     F5               -0.259    0.087   -2.972    0.003   -0.347   -0.347
##   F3 ~~                                                                 
##     F4                0.073    0.102    0.716    0.474    0.086    0.086
##     F5               -0.034    0.102   -0.336    0.737   -0.031   -0.031
##   F4 ~~                                                                 
##     F5                0.089    0.076    1.171    0.242    0.155    0.155
## 
## Intercepts:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##    .item31            0.879    0.032   27.295    0.000    0.879    1.935
##    .item33            0.869    0.032   27.150    0.000    0.869    1.925
##    .item1             0.990    0.043   22.904    0.000    0.990    1.624
##    .item37            0.995    0.050   19.900    0.000    0.995    1.411
##    .item10            2.543    0.078   32.704    0.000    2.543    2.318
##    .item47            2.035    0.065   31.553    0.000    2.035    2.237
##    .item36            2.095    0.082   25.511    0.000    2.095    1.808
##    .item35            2.070    0.089   23.362    0.000    2.070    1.656
##    .item13            2.834    0.077   36.750    0.000    2.834    2.605
##    .item44            2.995    0.089   33.796    0.000    2.995    2.396
##    .item43            1.578    0.096   16.401    0.000    1.578    1.163
##    .item26            1.482    0.100   14.868    0.000    1.482    1.054
##    .item32            1.533    0.094   16.314    0.000    1.533    1.156
##    .item14            3.020    0.133   22.749    0.000    3.020    1.613
##    .item42            2.935    0.122   23.959    0.000    2.935    1.698
##    .item12            2.005    0.081   24.793    0.000    2.005    1.758
##    .item11            2.382    0.091   26.054    0.000    2.382    1.847
##    .item16            3.211    0.104   30.991    0.000    3.211    2.197
##    .item19            3.930    0.091   43.244    0.000    3.930    3.065
##    .item34            3.583    0.098   36.558    0.000    3.583    2.592
##    .item2             2.482    0.100   24.897    0.000    2.482    1.765
##     F1                0.000                               0.000    0.000
##     F2                0.000                               0.000    0.000
##     F3                0.000                               0.000    0.000
##     F4                0.000                               0.000    0.000
##     F5                0.000                               0.000    0.000
## 
## Variances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##    .item31            0.121    0.035    3.491    0.000    0.121    0.584
##    .item33            0.155    0.070    2.218    0.027    0.155    0.760
##    .item1             0.099    0.090    1.099    0.272    0.099    0.267
##    .item37            0.342    0.130    2.621    0.009    0.342    0.688
##    .item10            0.468    0.128    3.650    0.000    0.468    0.389
##    .item47            0.286    0.054    5.312    0.000    0.286    0.345
##    .item36            0.682    0.094    7.244    0.000    0.682    0.508
##    .item35            1.161    0.155    7.465    0.000    1.161    0.743
##    .item13            1.018    0.112    9.101    0.000    1.018    0.860
##    .item44            1.188    0.138    8.579    0.000    1.188    0.760
##    .item43            0.175    0.101    1.731    0.083    0.175    0.095
##    .item26            0.573    0.164    3.503    0.000    0.573    0.290
##    .item32            0.422    0.114    3.684    0.000    0.422    0.240
##    .item14            3.075    0.292   10.534    0.000    3.075    0.877
##    .item42            2.051    0.322    6.376    0.000    2.051    0.687
##    .item12            1.027    0.150    6.867    0.000    1.027    0.789
##    .item11            1.543    0.172    8.957    0.000    1.543    0.928
##    .item16            1.710    0.272    6.292    0.000    1.710    0.800
##    .item19            0.886    0.131    6.783    0.000    0.886    0.539
##    .item34            0.606    0.178    3.402    0.001    0.606    0.317
##    .item2             1.229    0.150    8.214    0.000    1.229    0.621
##     F1                0.086    0.036    2.376    0.017    1.000    1.000
##     F2                0.735    0.145    5.067    0.000    1.000    1.000
##     F3                1.667    0.246    6.771    0.000    1.000    1.000
##     F4                0.433    0.228    1.902    0.057    1.000    1.000
##     F5                0.757    0.162    4.668    0.000    1.000    1.000
## 
## R-Square:
##                    Estimate
##     item31            0.416
##     item33            0.240
##     item1             0.733
##     item37            0.312
##     item10            0.611
##     item47            0.655
##     item36            0.492
##     item35            0.257
##     item13            0.140
##     item44            0.240
##     item43            0.905
##     item26            0.710
##     item32            0.760
##     item14            0.123
##     item42            0.313
##     item12            0.211
##     item11            0.072
##     item16            0.200
##     item19            0.461
##     item34            0.683
##     item2             0.379
\end{verbatim}

\begin{verbatim}
##               F1        F2        F3        F4        F5     total
## alpha  0.7547222 0.4818562 0.9175522 0.5566040 0.7413266 0.5705737
## omega  0.7047603 0.6261744 0.9185244 0.4777356 0.7527269 0.7006145
## omega2 0.7047603 0.6261744 0.9185244 0.4777356 0.7527269 0.7006145
## omega3 0.6939390 0.6265598 0.9183878 0.4742914 0.7572671 0.6879404
## avevar 0.4397748 0.3749622 0.7902041 0.1887734 0.5081583 0.4058147
\end{verbatim}

\begin{verbatim}
## lavaan 0.6-9 ended normally after 86 iterations
## 
##   Estimator                                         ML
##   Optimization method                           NLMINB
##   Number of model parameters                        91
##                                                       
##   Number of observations                           199
##   Number of missing patterns                         1
##                                                       
## Model Test User Model:
##                                                Standard      Robust
##   Test Statistic                                312.650     319.502
##   Degrees of freedom                                233         233
##   P-value (Chi-square)                            0.000       0.000
##   Scaling correction factor                                   0.979
##        Yuan-Bentler correction (Mplus variant)                     
## 
## Model Test Baseline Model:
## 
##   Test statistic                              1718.830    1439.817
##   Degrees of freedom                               276         276
##   P-value                                        0.000       0.000
##   Scaling correction factor                                  1.194
## 
## User Model versus Baseline Model:
## 
##   Comparative Fit Index (CFI)                    0.945       0.926
##   Tucker-Lewis Index (TLI)                       0.935       0.912
##                                                                   
##   Robust Comparative Fit Index (CFI)                         0.939
##   Robust Tucker-Lewis Index (TLI)                            0.928
## 
## Loglikelihood and Information Criteria:
## 
##   Loglikelihood user model (H0)              -6703.605   -6703.605
##   Scaling correction factor                                  1.802
##       for the MLR correction                                      
##   Loglikelihood unrestricted model (H1)      -6547.280   -6547.280
##   Scaling correction factor                                  1.210
##       for the MLR correction                                      
##                                                                   
##   Akaike (AIC)                               13589.210   13589.210
##   Bayesian (BIC)                             13888.900   13888.900
##   Sample-size adjusted Bayesian (BIC)        13600.607   13600.607
## 
## Root Mean Square Error of Approximation:
## 
##   RMSEA                                          0.041       0.043
##   90 Percent confidence interval - lower         0.028       0.031
##   90 Percent confidence interval - upper         0.053       0.055
##   P-value RMSEA <= 0.05                          0.885       0.830
##                                                                   
##   Robust RMSEA                                               0.043
##   90 Percent confidence interval - lower                     0.030
##   90 Percent confidence interval - upper                     0.054
## 
## Standardized Root Mean Square Residual:
## 
##   SRMR                                           0.065       0.065
## 
## Parameter Estimates:
## 
##   Standard errors                             Sandwich
##   Information bread                           Observed
##   Observed information based on                Hessian
## 
## Latent Variables:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##   F1 =~                                                                 
##     item31            1.000                               0.294    0.646
##     item33            0.752    0.145    5.183    0.000    0.221    0.489
##     item1             1.776    0.638    2.781    0.005    0.521    0.855
##     item37            1.344    0.379    3.549    0.000    0.395    0.560
##   F2 =~                                                                 
##     item10            1.000                               0.830    0.757
##     item47            0.899    0.124    7.268    0.000    0.747    0.821
##     item36            0.997    0.151    6.609    0.000    0.828    0.714
##     item35            0.766    0.147    5.201    0.000    0.636    0.509
##     item13            0.398    0.119    3.347    0.001    0.330    0.303
##     item44           -0.751    0.146   -5.135    0.000   -0.624   -0.499
##   F3 =~                                                                 
##     item43            1.000                               1.297    0.956
##     item26            0.904    0.055   16.458    0.000    1.173    0.838
##     item32            0.887    0.063   14.039    0.000    1.150    0.868
##   F4 =~                                                                 
##     item14            1.000                               0.632    0.337
##     item42            1.476    0.486    3.039    0.002    0.932    0.540
##     item12            0.855    0.351    2.437    0.015    0.540    0.474
##     item11            0.595    0.375    1.586    0.113    0.376    0.292
##     item16            1.088    0.568    1.916    0.055    0.687    0.470
##   F5 =~                                                                 
##     item19            1.000                               0.889    0.689
##     item34            1.271    0.147    8.639    0.000    1.130    0.817
##     item2             0.990    0.147    6.759    0.000    0.880    0.626
##   F6 =~                                                                 
##     item38            1.000                               0.526    0.388
##     item28            2.058    3.153    0.653    0.514    1.083    0.737
##     item45            1.518    0.693    2.192    0.028    0.799    0.512
## 
## Covariances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##  .item31 ~~                                                             
##    .item33            0.070    0.026    2.680    0.007    0.070    0.513
##  .item10 ~~                                                             
##    .item13            0.218    0.098    2.213    0.027    0.218    0.293
##  .item12 ~~                                                             
##    .item11            0.694    0.153    4.549    0.000    0.694    0.560
##  .item26 ~~                                                             
##    .item19            0.179    0.072    2.487    0.013    0.179    0.250
##   F1 ~~                                                                 
##     F2                0.047    0.026    1.860    0.063    0.195    0.195
##     F3               -0.008    0.035   -0.238    0.812   -0.022   -0.022
##     F4                0.075    0.036    2.120    0.034    0.407    0.407
##     F5                0.011    0.027    0.403    0.687    0.041    0.041
##     F6                0.021    0.053    0.406    0.685    0.138    0.138
##   F2 ~~                                                                 
##     F3               -0.086    0.072   -1.181    0.237   -0.079   -0.079
##     F4                0.094    0.084    1.116    0.265    0.179    0.179
##     F5               -0.258    0.086   -3.002    0.003   -0.350   -0.350
##     F6               -0.035    0.146   -0.240    0.810   -0.080   -0.080
##   F3 ~~                                                                 
##     F4                0.079    0.098    0.804    0.421    0.096    0.096
##     F5               -0.039    0.105   -0.374    0.708   -0.034   -0.034
##     F6               -0.025    0.132   -0.187    0.851   -0.036   -0.036
##   F4 ~~                                                                 
##     F5                0.087    0.076    1.133    0.257    0.154    0.154
##     F6                0.081    0.054    1.488    0.137    0.243    0.243
##   F5 ~~                                                                 
##     F6                0.114    0.150    0.759    0.448    0.244    0.244
## 
## Intercepts:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##    .item31            0.879    0.032   27.295    0.000    0.879    1.935
##    .item33            0.869    0.032   27.150    0.000    0.869    1.925
##    .item1             0.990    0.043   22.904    0.000    0.990    1.624
##    .item37            0.995    0.050   19.900    0.000    0.995    1.411
##    .item10            2.543    0.078   32.704    0.000    2.543    2.318
##    .item47            2.035    0.065   31.553    0.000    2.035    2.237
##    .item36            2.095    0.082   25.511    0.000    2.095    1.808
##    .item35            2.070    0.089   23.362    0.000    2.070    1.656
##    .item13            2.834    0.077   36.750    0.000    2.834    2.605
##    .item44            2.995    0.089   33.796    0.000    2.995    2.396
##    .item43            1.578    0.096   16.401    0.000    1.578    1.163
##    .item26            1.482    0.100   14.868    0.000    1.482    1.060
##    .item32            1.533    0.094   16.314    0.000    1.533    1.156
##    .item14            3.020    0.133   22.749    0.000    3.020    1.613
##    .item42            2.935    0.122   23.959    0.000    2.935    1.698
##    .item12            2.005    0.081   24.793    0.000    2.005    1.758
##    .item11            2.382    0.091   26.054    0.000    2.382    1.847
##    .item16            3.211    0.104   30.991    0.000    3.211    2.197
##    .item19            3.930    0.091   43.244    0.000    3.930    3.043
##    .item34            3.583    0.098   36.558    0.000    3.583    2.592
##    .item2             2.482    0.100   24.897    0.000    2.482    1.765
##    .item38            2.201    0.096   22.896    0.000    2.201    1.623
##    .item28            2.111    0.104   20.264    0.000    2.111    1.437
##    .item45            2.432    0.111   21.981    0.000    2.432    1.558
##     F1                0.000                               0.000    0.000
##     F2                0.000                               0.000    0.000
##     F3                0.000                               0.000    0.000
##     F4                0.000                               0.000    0.000
##     F5                0.000                               0.000    0.000
##     F6                0.000                               0.000    0.000
## 
## Variances:
##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
##    .item31            0.120    0.034    3.520    0.000    0.120    0.583
##    .item33            0.155    0.070    2.220    0.026    0.155    0.761
##    .item1             0.100    0.087    1.155    0.248    0.100    0.269
##    .item37            0.342    0.129    2.641    0.008    0.342    0.687
##    .item10            0.513    0.131    3.925    0.000    0.513    0.427
##    .item47            0.270    0.057    4.734    0.000    0.270    0.327
##    .item36            0.657    0.096    6.878    0.000    0.657    0.490
##    .item35            1.158    0.157    7.382    0.000    1.158    0.741
##    .item13            1.075    0.103   10.395    0.000    1.075    0.908
##    .item44            1.174    0.137    8.550    0.000    1.174    0.751
##    .item43            0.160    0.091    1.757    0.079    0.160    0.087
##    .item26            0.582    0.166    3.505    0.000    0.582    0.297
##    .item32            0.434    0.114    3.813    0.000    0.434    0.247
##    .item14            3.108    0.316    9.836    0.000    3.108    0.886
##    .item42            2.116    0.334    6.345    0.000    2.116    0.709
##    .item12            1.009    0.148    6.804    0.000    1.009    0.776
##    .item11            1.522    0.190    8.005    0.000    1.522    0.915
##    .item16            1.664    0.316    5.267    0.000    1.664    0.779
##    .item19            0.877    0.132    6.664    0.000    0.877    0.526
##    .item34            0.634    0.162    3.905    0.000    0.634    0.332
##    .item2             1.203    0.151    7.993    0.000    1.203    0.608
##    .item38            1.562    0.478    3.270    0.001    1.562    0.849
##    .item28            0.985    1.584    0.622    0.534    0.985    0.456
##    .item45            1.798    0.670    2.681    0.007    1.798    0.738
##     F1                0.086    0.036    2.407    0.016    1.000    1.000
##     F2                0.690    0.150    4.608    0.000    1.000    1.000
##     F3                1.682    0.244    6.901    0.000    1.000    1.000
##     F4                0.399    0.251    1.588    0.112    1.000    1.000
##     F5                0.791    0.161    4.899    0.000    1.000    1.000
##     F6                0.277    0.473    0.586    0.558    1.000    1.000
## 
## R-Square:
##                    Estimate
##     item31            0.417
##     item33            0.239
##     item1             0.731
##     item37            0.313
##     item10            0.573
##     item47            0.673
##     item36            0.510
##     item35            0.259
##     item13            0.092
##     item44            0.249
##     item43            0.913
##     item26            0.703
##     item32            0.753
##     item14            0.114
##     item42            0.291
##     item12            0.224
##     item11            0.085
##     item16            0.221
##     item19            0.474
##     item34            0.668
##     item2             0.392
##     item38            0.151
##     item28            0.544
##     item45            0.262
\end{verbatim}

\begin{verbatim}
##               F1        F2        F3        F4        F5        F6     total
## alpha  0.7547222 0.4818562 0.9175522 0.5566040 0.7413266 0.5529540 0.5867087
## omega  0.7047233 0.5882585 0.9176537 0.4814294 0.7559836 0.5718535 0.6975681
## omega2 0.7047233 0.5882585 0.9176537 0.4814294 0.7559836 0.5718535 0.6975681
## omega3 0.6939357 0.5880241 0.9123335 0.4801057 0.7686670 0.5694246 0.6768555
## avevar 0.4396193 0.3689684 0.7883714 0.1875180 0.5116007 0.3247497 0.3906214
\end{verbatim}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}

\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
R Core Team. (2020). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}

\end{CSLReferences}

\endgroup

\end{document}

### 2021-08-27 manuscript.Rmd
Updates

@@
 library(papaja) # devtools::install_github("crsh/papaja")
-r_refs("r-references.bib")
 library(readr)
@@
 library(kableExtra)
+r_refs("r-references.bib")
 ```

### 2021-08-27 manuscript.tex
Updates

@@
 
-We used R {[}Version 4.0.3; R Core Team (2020){]} and the R-package \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]} for all our analyses.
+We used R {[}Version 4.0.3; R Core Team (2020){]} and the R-packages \emph{boot} {[}Version 1.3.28; Davison and Hinkley (1997){]}, \emph{dlookr} {[}Version 0.5.0; Ryu (2021){]}, \emph{dplyr} {[}Version 1.0.7; Wickham, François, Henry, and Müller (2021){]}, \emph{equate} {[}Version 2.0.7; Albano (2016){]}, \emph{forcats} {[}Version 0.5.1; Wickham (2021a){]}, \emph{ggplot2} {[}Version 3.3.3; Wickham (2016){]}, \emph{hemp} {[}Version 0.1.0; Bulut (2021){]}, \emph{kableExtra} {[}Version 1.3.4; Zhu (2021){]}, \emph{lattice} {[}Version 0.20.44; Sarkar (2008){]}, \emph{lavaan} {[}Version 0.6.9; Rosseel (2012){]}, \emph{lme4} {[}Version 1.1.27.1; Bates, Mächler, Bolker, and Walker (2015){]}, \emph{Matrix} {[}Version 1.3.3; Bates and Maechler (2021){]}, \emph{mirt} {[}Version 1.34; Chalmers (2012){]}, \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]}, \emph{psych} {[}Version 2.1.6; Revelle (2021){]}, \emph{purrr} {[}Version 0.3.4; Henry and Wickham (2020){]}, \emph{qgraph} {[}Version 1.6.9; Epskamp, Cramer, Waldorp, Schmittmann, and Borsboom (2012){]}, \emph{readr} {[}Version 1.4.0; Wickham and Hester (2020){]}, \emph{readxl} {[}Version 1.3.1; Wickham and Bryan (2019){]}, \emph{reshape2} {[}Version 1.4.4; Wickham (2007){]}, \emph{semPlot} {[}Version 1.1.2; Epskamp (2019){]}, \emph{semTools} {[}Version 0.5.5; Jorgensen, Pornprasertmanit, Schoemann, and Rosseel (2021){]}, \emph{stringr} {[}Version 1.4.0; Wickham (2019){]}, \emph{tibble} {[}Version 3.1.2; Müller and Wickham (2021){]}, \emph{tidyr} {[}Version 1.1.3; Wickham (2021b){]}, and \emph{tidyverse} {[}Version 1.3.1; Wickham et al.
+(2019){]} for all our analyses.
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-R-equate}{}}%
+Albano, A. D. (2016). {equate}: An {R} package for observed-score linking and equating. \emph{Journal of Statistical Software}, \emph{74}(8), 1--36. \url{https://doi.org/10.18637/jss.v074.i08}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-Matrix}{}}%
+Bates, D., \& Maechler, M. (2021). \emph{Matrix: Sparse and dense matrix classes and methods}. Retrieved from \url{https://CRAN.R-project.org/package=Matrix}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-lme4}{}}%
+Bates, D., Mächler, M., Bolker, B., \& Walker, S.
+(2015).
+Fitting linear mixed-effects models using {lme4}.
+\emph{Journal of Statistical Software}, \emph{67}(1), 1--48.
+\url{https://doi.org/10.18637/jss.v067.i01}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-hemp}{}}%
+Bulut, O. (2021). \emph{Hemp: Handbook of educational measurement and psychometrics using r companion package}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-mirt}{}}%
+Chalmers, R.
+P.
+(2012).
+{mirt}: A multidimensional item response theory package for the {R} environment.
+\emph{Journal of Statistical Software}, \emph{48}(6), 1--29.
+\url{https://doi.org/10.18637/jss.v048.i06}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-boot}{}}%
+Davison, A. C., \& Hinkley, D. V. (1997). \emph{Bootstrap methods and their applications}. Cambridge: Cambridge University Press. Retrieved from \url{http://statwww.epfl.ch/davison/BMA/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-semPlot}{}}%
+Epskamp, S. (2019). \emph{semPlot: Path diagrams and visual analysis of various SEM packages' output}. Retrieved from \url{https://CRAN.R-project.org/package=semPlot}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-qgraph}{}}%
+Epskamp, S., Cramer, A.
+O.
+J., Waldorp, L.
+J., Schmittmann, V.
+D., \& Borsboom, D.
+(2012).
+{qgraph}: Network visualizations of relationships in psychometric data.
+\emph{Journal of Statistical Software}, \emph{48}(4), 1--18.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-purrr}{}}%
+Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-semTools}{}}%
+Jorgensen, T.
+D., Pornprasertmanit, S., Schoemann, A.
+M., \& Rosseel, Y.
+(2021).
+\emph{\texttt{semTools}: {U}seful tools for structural equation modeling}.
+Retrieved from \url{https://CRAN.R-project.org/package=semTools}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tibble}{}}%
+Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-psych}{}}%
+Revelle, W.
+(2021).
+\emph{Psych: Procedures for psychological, psychometric, and personality research}.
+Evanston, Illinois: Northwestern University.
+Retrieved from \url{https://CRAN.R-project.org/package=psych}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-lavaan}{}}%
+Rosseel, Y. (2012). {lavaan}: An {R} package for structural equation modeling. \emph{Journal of Statistical Software}, \emph{48}(2), 1--36. Retrieved from \url{https://www.jstatsoft.org/v48/i02/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-dlookr}{}}%
+Ryu, C. (2021). \emph{Dlookr: Tools for data diagnosis, exploration, transformation}. Retrieved from \url{https://CRAN.R-project.org/package=dlookr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-lattice}{}}%
+Sarkar, D. (2008). \emph{Lattice: Multivariate data visualization with r}. New York: Springer. Retrieved from \url{http://lmdvr.r-forge.r-project.org}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-reshape2}{}}%
+Wickham, H. (2007). Reshaping data with the {reshape} package. \emph{Journal of Statistical Software}, \emph{21}(12), 1--20. Retrieved from \url{http://www.jstatsoft.org/v21/i12/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-ggplot2}{}}%
+Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-stringr}{}}%
+Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-forcats}{}}%
+Wickham, H. (2021a). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyr}{}}%
+Wickham, H. (2021b). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyverse}{}}%
+Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
+D., François, R., \ldots{} Yutani, H.
+(2019).
+Welcome to the {tidyverse}.
+\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
+\url{https://doi.org/10.21105/joss.01686}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-readxl}{}}%
+Wickham, H., \& Bryan, J. (2019). \emph{Readxl: Read excel files}. Retrieved from \url{https://CRAN.R-project.org/package=readxl}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-dplyr}{}}%
+Wickham, H., François, R., Henry, L., \& Müller, K. (2021). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-readr}{}}%
+Wickham, H., \& Hester, J. (2020). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-kableExtra}{}}%
+Zhu, H. (2021). \emph{kableExtra: Construct complex table with 'kable' and pipe syntax}. Retrieved from \url{https://CRAN.R-project.org/package=kableExtra}
+
 \end{CSLReferences}

### 2021-08-27 manuscript.Rmd
updated on August 27 10PM

@@
 # Confirmatory Factor Analysis
+# Confirmatory Factor Analysis
 
-```{r CFA, }
-LB.cfa <- read_excel("SpitschanSleepSurvey_DATA_2021-08-24_1819_redacted_199_CFA.xlsx")
-LB.cfa$id <- NULL
-summarize <- summary(LB.cfa)
-Descriptives <- psych::describe(LB.cfa)
-#Univariate Normality
-normality <- normality(LB.cfa) 
-#Multivariate Normality
-mardia(LB.cfa, na.rm = T, plot =F)
-
-# CFA with five factor (23 items)
-LB.model.Cor <- "F1 =~ item31+ item33+ item1+ item37 + item 24
+```{r CFA 23 items, include=FALSE}
+LB.cfa <- read_excel("recoded not reversed_CFA.xlsx")
+LB.model.Cor <- "F1 =~ item5 + item24 + item30 + item1 + item16 + item28
              F2 =~ item10 + item47 + item36 + item44 + item35 + item13
             F3 =~ item43 + item26 + item32
-           F4 =~  item14 + item 7 + item11 + item42 + item12 + item16 
+           F4 =~  item14 + item41+ item7 + item27 + item21
             F5 =~ item19 + item34 + item2"
+
 fit.Cor <- cfa(LB.model.Cor, data = LB.cfa, estimator = "MLR", mimic = "Mplus")
+
 ## Summary of Model 
 summary(fit.Cor, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
+
 ## Selected Fit measures 
-fitmeasures (fit.Cor,c("gfi", "agfi", "nfi","rfi", 
+fit.1 <- fitmeasures (fit.Cor,c("gfi", "agfi", "nfi","rfi", 
                        "cfi.robust","tli.robust",
@@
 
-Based on CFI, TLI, RMSEA and SRMR value the fitted five factor model is not acceptable.
-As a result a close inspection  on items with low factor-loadings and low R-square value was conducted. two items were found to be problematic **item7, item 24** with vary low R-square 
-value thus discarded from the model.
+```{r CFA23withMI, include=FALSE}
+LB.model.Cor.3 <- "F1 =~ item5 + item24 + item30 + item1 + item16 + item28
+             F2 =~ item10 + item47 + item36 + item44 + item35 + item13
+            F3 =~ item43 + item26 + item32
+           F4 =~  item14 + item41+ item7 + item27 + item21
+            F5 =~ item19 + item34 + item2
+item44 ~~ item13
+item14 ~~  item7
+item10 ~~ item13"
 
-```{r CFA23}
-#Five factor correlational Model without item24, item 7 [21 Items]
-LB.model.Cor.2 <- "F1 =~ item31+ item33+ item1+ item37
-             F2 =~ item10 + item47 + item36 +  item35 + item13 + item44
+## Fit the model 
+fit.Cor.3 <- cfa(LB.model.Cor.3, data = LB.cfa, estimator = "MLR", mimic = "Mplus")
+
+reliability <- semTools::reliability(fit.Cor.3, return.total = T)
+as.table(reliability)
+## Summary of Model 
+summary(fit.Cor.3, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
+
+## Selected Fit measures 
+fit.3 <- fitmeasures (fit.Cor.3,c("gfi", "agfi", "nfi","rfi", 
+                       "cfi.robust","tli.robust",
+                       "rmsea.robust", 
+                       "srmr","aic"))
+
+rownames <-  ("fitIndices")
+colnames <- c("gfi", "agfi", "nfi","rfi", 
+                       "cfi.robust","tli.robust",
+                       "rmsea.robust", 
+                       "srmr","aic")
+
+```
+
+```{r CFI18items, include=FALSE}
+LB.model.Cor.2 <- "F1 =~ item5 + item24 + item30 + item16 
+             F2 =~ item10 + item47 + item36 + item44 + item35 
             F3 =~ item43 + item26 + item32
-           F4 =~  item14 +  item42 + item12 + item11 + item16 
-             F5 =~ item19 + item34 + item2" 
+           F4 =~  item14 + item41+ item7 
+            F5 =~ item19 + item34 + item2
+item14 ~~  item7"
+
+#item 1 &28 discarded from F1;
+#item13 discarded from F2
+#item 27 & 21 discarded from F4
+
 ## Fit the model 
 fit.Cor.2 <- cfa(LB.model.Cor.2, data = LB.cfa, estimator = "MLR", mimic = "Mplus")
+
 ## Summary of Model 
 summary(fit.Cor.2, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
+
 ## Selected Fit measures 
@@
                        "srmr","aic"))
+
 rownames <-  ("fitIndices")
@@
                        "srmr","aic")
-dimnames <- list(rownames, colnames)
-fitmatrix <- matrix(fit.2, nrow = 1, ncol = 9, byrow = T, dimnames)
-semTools::reliability(fit.Cor.2)
-```
 
-```{r CFA5Mod}
-modfit.Cor <- modindices(fit.Cor.2, sort. = TRUE) 
-modfit.Cor[modfit.Cor$mi>3.84,] 
-```
-
-```{r CFA5bestfit}
-#21 items
-LB.model.Cor.3 <- "F1 =~ item31+ item33+ item1+ item37
-             F2 =~ item10 + item47 + item36 +  item35 + item13 + item44
-            F3 =~ item43 + item26 + item32
-           F4 =~  item14 +  item42 + item12 + item11 + item16 
-             F5 =~ item19 + item34 + item2
-                    item31 ~~ item33
-                     item12 ~~ item11" 
-## Fit the model 
-fit.Cor.3 <- cfa(LB.model.Cor.3, data = LB.cfa, estimator = "MLR", mimic = "Mplus") 
-## Summary of Model 
-summary(fit.Cor.3, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
-## Selected Fit measures 
-fit.3 <- fitmeasures (fit.Cor.3,c("gfi", "agfi", "nfi","rfi", 
-                       "cfi.robust","tli.robust",
-                       "rmsea.robust", 
-                       "srmr","aic"))
-rownames <-  ("fitIndices")
-colnames <- c("gfi", "agfi", "nfi","rfi", 
-                       "cfi.robust","tli.robust",
-                       "rmsea.robust", 
-                       "srmr","aic")
-dimnames <- list(rownames, colnames)
-fitmatrix <- matrix(fit.3, nrow = 1, ncol = 9, byrow = T, dimnames)
-reliability1 <- semTools::reliability(fit.Cor.3, return.total = T)
-as.table(reliability1 )
-```
-
-```{r CFA6}
-#24 items
-LB.model.Cor.4 <- "F1 =~ item31+ item33+ item1+ item37
-             F2 =~ item10 + item47 + item36 +  item35 + item13 + item44
-            F3 =~ item43 + item26 + item32
-           F4 =~  item14 +  item42 + item12 + item11 + item16 
-             F5 =~ item19 + item34 + item2
-             F6 =~ item38 + item28 + item45
-                   item31 ~~ item33
-                    item10 ~~ item13
-                     item12 ~~ item11
-                     item26 ~~ item19  "
-
-## Fit the model 
-fit.Cor.4 <- cfa(LB.model.Cor.4, data = LB.cfa, estimator = "MLR", mimic = "Mplus")
-
-## Summary of Model 
-summary(fit.Cor.4, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
-
-## Selected Fit measures 
-fit.4 <- fitmeasures (fit.Cor.4,c("gfi", "agfi", "nfi","rfi", 
-                       "cfi.robust","tli.robust",
-                       "rmsea.robust", 
-                       "srmr","aic"))
-reliability <- semTools::reliability(fit.Cor.4, return.total = T)
-as.table(reliability)
 ```
@@
 \newpage
-
 # References

### 2021-08-27 manuscript.Rmd
test the push
Just added a line to the rmd to test the push function
Manuscript updated

@@
             F5 =~ item19 + item34 + item2" 
+# all items
 

### 2021-08-31 manuscript.Rmd
Updates on 31 Auguts

--- 2021-08-27 manuscript.Rmd
@@
     role:
+      - Data Analysis
       - Writing - Original Draft Preparation
+      - Data Visualization
+  - name          : "Manuel Spitschan "
+    affiliation   : "3"
+    corresponding : yes   
+    address       : ""
+    email         : ""
+    role:         
+      - Data Analysis
+      - Writing - Original Draft Preparation
+      - Data Visualization
 
@@
   - id            : "1"
-    institution   : "Wilhelm-Wundt-University"
+    institution   : "Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Monash University, Malaysia"
   - id            : "2"
-    institution   : "Konstanz Business School"
+    institution   : "University of Basel"
 
@@
 ```
+# Introduction
+
 # Methods
@@
 ## Participants
+
+This line is just a test for pushing in the github repo.
 

### 2021-08-31 manuscript.Rmd
Flowchart

@@
 
+---
+nocite: |
+  `r cite_r("r-references.bib")`
+---
+
 ```{r analysis-preferences}
@@
 
+```{r flowchart }
+Flowchart1 <- grViz("digraph nicegraph{
+
+                    graph [layout = dot,fontsize = 14]
+
+                     node[shape = rectangle, margin = 0.2, width = 6.5, height = 1, fixedsize = true]
+
+                    A[label = '48 items were generataed by a robust expert panel'] 
+                    B[label = 'Exploratory Factor Analysis on 48 Items (N = 428)']
+
+                    node[shape = rectangle, margin = 0.2, width = 6.5, height = 2, fixedsize = true]
+                    C[label = 'Factor Identification
+                    Scree Plot: 6 Factors
+                    Parallel Analysis: 6 Factors
+                    Minimum Average Partial Method: 5 Factors
+                    Hull Method: 5 Factors']
+
+                     subgraph cluster_1 {
+                      graph[shape = rectangle]
+                      style = rounded
+                     node[ margin = 0.2,width = 6.5, height = 1, fixedsize = true ]
+
+                     1[label = '5 Factor Solution Retained 23 Items']
+                     2[label = 'Reliability Analysis on EFA Sample (N=428)
+                    Alpha F1 =.49; F2 = .71; F3 = .86; F4 =.62; F5 =.77']
+
+                     3[label = 'Confirmatory Factor Analysis on Modified Model
+                     on the Five Factor Model (21 Items; N=199)
+                      Acceptable Fit ( CFI = .92; TLI .91; RMSEA = .05, SRMR = .07)']
+
+                     4[label = 'Reliability Analysis on CFA (N=199) 
+                      Alpha F1=.47; F2=.67; F3 =.92; F4=.58; F5= .74']
+                    }
+                subgraph cluster_2 {
+                      graph[shape = rectangle]
+                      style = rounded
+                     node[ margin = 0.2,width = 6.5, height = 1, fixedsize = true ]
+                    5[label = '6-Factor  one factor with only two salient loadings']
+                    6[label = 'Rejected']
+                    }
+
+                     edge[color = black,arrowhead = vee, arrowsize = 1.25]
+                     A ->B
+                     B ->C
+                     C ->1
+                     1 ->2
+                     2 ->3
+                     3 ->4
+                     C ->5
+                     5 ->6
+
+}")
+
+export_svg(Flowchart1) %>%
+  charToRaw() %>%
+  rsvg() %>%
+  png::writePNG("Flowchart1.png")
+
+```
+
+```{r, out.height= "50%",  fig.align='center', fig.cap='ABC'}
+knitr::include_graphics('Flowchart1.png')
+```
+
 ## Procedure
+Our study had three objectives.
+First, to develop an instrument to assess individual's light exposure behavior .
+Second, to conduct an exploratory factor analysis to understand the latent structure.
+Third to gather validity evidences [@furrPsychometricsIntroduction2014].
 
 ## Data analysis
-We used `r cite_r("r-references.bib")` for all our analyses.
 

### 2021-08-31 manuscript.Rmd

@@
       - Data Visualization
+  - name          : "Manuel Spitschan "
+    affiliation   : "3"
+    corresponding : yes   
+    address       : ""
+    email         : ""
+    role:         
+      - Data Analysis
+      - Writing - Original Draft Preparation
+      - Data Visualization
+
   - name          : "Manuel Spitschan "
@@
 library(kableExtra)
+library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
+library(DiagrammeRsvg)
+library(rsvg)
 r_refs("r-references.bib")
@@
 # Results
+```{r Normality assumption EFA}
+LB <- read_excel("recoded not reversed_EFA.xlsx")
+LB$X1 <- NULL
+KMO <- KMO(LB)
 
+```
+Sampling adequacy was investigated by Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy .
+The overall KMO vale for 23 items was `r printnum(KMO$MSA)` which was above the cutoff value of .50 indicating a mediocre sample [@RN1179].
 # Confirmatory Factor Analysis

### 2021-08-31 manuscript.Rmd
Updates

@@
 ```
-Sampling adequacy was investigated by Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy .
-The overall KMO vale for 23 items was `r printnum(KMO$MSA)` which was above the cutoff value of .50 indicating a mediocre sample [@RN1179].
+Sampling adequacy was investigated by Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy[@kaiserIndexFactorialSimplicity1974] .
+The overall KMO vale for 23 items was `r printnum(KMO$MSA)` which was above the cutoff value of .50 indicating a mediocre sample [@hutchesonMultivariateSocialScientist1999].
 # Confirmatory Factor Analysis

### 2021-08-31 manuscript.Rmd
Update manuscript.Rmd

@@
 ## Procedure
-Our study had three objectives.
+Our study had four objectives.
 First, to develop an instrument to assess individual's light exposure behavior .
-Second, to conduct an exploratory factor analysis to understand the latent structure.
-Third to gather validity evidences [@furrPsychometricsIntroduction2014].
+Second, to conduct an exploratory factor analysis(EFA)  to understand the latent structure.
+Third to gather structural validity evidence for the latent structure obtained in EFA.
+[@furrPsychometricsIntroduction2014]. Lastly, we gathered item information using Item response theory (IRT)[@bakerBasicsItemResponse2017]
 
-## Data analysis
+## Analytic Strategies
+
+We used R (version 4.1.0), including several R-packages for our analyses.
+Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix were assessed.
+Our data violated both the univariate and multivariate normality assumptions.
+Due to these violations and the  ordinal nature of our response data we used polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA.
+We employed principal axis (pa) a factor extraction method with varimax rotation.
+PA is apparently robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020].
+The obtained latent structure was confirmed by weighted least squares (WLS) extraction method as well.
+We used a combination factor indentification method including scree plot[@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method[@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
+Additionally, to identify the simple structure we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018; @childEssentialsFactorAnalysis2006; @mulaikFoundationsFactorAnalysis2009; @watkinsStepbyStepGuideExploratory2020]
 
@@
 The overall KMO vale for 23 items was `r printnum(KMO$MSA)` which was above the cutoff value of .50 indicating a mediocre sample [@hutchesonMultivariateSocialScientist1999].
-# Confirmatory Factor Analysis
+
 # Confirmatory Factor Analysis

### 2021-08-31 manuscript.Rmd

@@
 library(semTools)
-library(hemp) # devtools::install_github("cddesja/hemp")
+library(MOTE)
 library(psych)
@@
 
+### Data Collection
+Timeline of data collection, ethical approval, mode of data collection, how consent was recorded.
+
+### Item generation and Content Validity: Expert Panel Review
+How we developed the 48 items?
+
 ## Analytic Strategies
@@
 LB$X1 <- NULL
+#KMO test
 KMO <- KMO(LB)
 
+# Test of correlation matrix
+bartlet <- cortest.bartlett(LB, n =428)
+
+# Univariante normality
+normality <- normality(LB)
+
+# Multivariate Normality
+mardia <- mardia(LB, na.rm = T, plot =F)
+
+# Descriptives
+Descriptives <- psych::describe(LB)
+alpha <- psych::alpha(LB)
+Item.total <- alpha$item.stats
+Item.total$r.cor
+Des.combined <- cbind(apa(Descriptives$mean,2,T), apa(Descriptives$sd,2,T), apa(Descriptives$skew,2,T),apa(Descriptives$kurtosis,2,T), apa(normality$statistic,2,T), apa(normality$p_value,2,F), apa(Item.total$r.cor,2,F))
+colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics", "p", "Item-Total Correlation")
+rownameprefix <- "Item"
+rownamesufix <- seq(1:48)
+my.names <- paste(rownameprefix,rownamesufix, sep = "" )
+rownames(Des.combined) = (my.names)
+
+#Polychoric Correlation matrix
+LB.factor <- sapply(LB, as.factor)
+correlations <- polychoric(LB.factor, correct = 0)
+
+BigR = sum(correlations$rho >= abs(.30) & correlations$rho < abs(1.0), na.rm =T)/2 
+totR = length(LB)*(length(LB)-1)/2
+A <- print (BigR/totR)*100
+
+# Item analysis
+Item_analysis <- psych::alpha(LB)
+Item_analysis$item.stats$r.cor
+R.cor.sum <- summary(Item_analysis$item.stats$r.cor)
+low.r.cor <- abs(R.cor.sum[1])
+high.r.cor <- R.cor.sum[6]
 ```
@@
 The overall KMO vale for 23 items was `r printnum(KMO$MSA)` which was above the cutoff value of .50 indicating a mediocre sample [@hutchesonMultivariateSocialScientist1999].
+
+```{r tabDes, results='asis'}
+apa_table(Des.combined, caption = "Descriptive Statistics")
+```
+
+Table\@ref(tab:tabDes) summarizes the univariate descriptive statistics for the 48 items.
+some of the items were skewed with high Kurtosis values.
+The Shapiro-Wilk test of normality [@shapiroAnalysisVarianceTest1965] indicated all the items violated normality assumptions.
+Multivariate normality assumptions were investigated by Marida's test [@mardiaMeasuresMultivariateSkewness1970].
+Multivariate skew = `r printnum(mardia$b1p)` (p <0.001) and multivariate kurtosis = `r printnum(mardia$b2p)` (p <0.001) indicated  multivariate normality assumptions violation.
+Due to these violations and ordinal nature of the response data  polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018].
+Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001] indicated the correlations between items are adequate for the EFA.
+However only `r apa(((BigR/totR)*100), 2,T)`% of the inter-item correlation coefficients were greater than .30 in the obtained matrix.
+The corrected item-total correlations ranged between `r apa(low.r.cor,2,F)` to `r apa(high.r.cor,2,F)`.
 

### 2021-08-31 manuscript.Rmd

@@
 Item.total <- alpha$item.stats
-Item.total$r.cor
+
 Des.combined <- cbind(apa(Descriptives$mean,2,T), apa(Descriptives$sd,2,T), apa(Descriptives$skew,2,T),apa(Descriptives$kurtosis,2,T), apa(normality$statistic,2,T), apa(normality$p_value,2,F), apa(Item.total$r.cor,2,F))
+
 colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics", "p", "Item-Total Correlation")
+
 rownameprefix <- "Item"
@@
 my.names <- paste(rownameprefix,rownamesufix, sep = "" )
+
 rownames(Des.combined) = (my.names)
@@
 correlations <- polychoric(LB.factor, correct = 0)
+upper <- correlations$rho[upper.tri(correlations$rho, diag = F)]
+
+as.data.frame(upper)
+min.cor <- abs(min(upper)) #minimum cor.coefficient of the matrix
+max.cor <- abs(max(upper)) # max. correlation coefficent of the matrix
+
+# Calulating the percentange of correlations higher than .30
 
@@
 R.cor.sum <- summary(Item_analysis$item.stats$r.cor)
-low.r.cor <- abs(R.cor.sum[1])
-high.r.cor <- R.cor.sum[6]
+low.r.corec <- abs(R.cor.sum[1])  #minimum item total correlation
+high.r.corec <- R.cor.sum[6]     # maximum item total correlation
 ```
+
 Sampling adequacy was investigated by Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy[@kaiserIndexFactorialSimplicity1974] .
@@
 apa_table(Des.combined, caption = "Descriptive Statistics")
+```
+
+```{r figCor,fig.cap= "Iter-correlation of the items",results='asis'}
+
+qgraph(correlations$rho, cut =.30, details =T, posCol = "green", negCol = "orangered3", 
+       labels = names(LB))
 ```
@@
 However only `r apa(((BigR/totR)*100), 2,T)`% of the inter-item correlation coefficients were greater than .30 in the obtained matrix.
-The corrected item-total correlations ranged between `r apa(low.r.cor,2,F)` to `r apa(high.r.cor,2,F)`.
+The inter item correlation ranged between `r apa(min.cor,2,F)` to `r apa(max.cor,2,F)`.
+The corrected item-total correlations ranged between `r apa(low.r.corec,2,F)` to `r apa(high.r.corec,2,F)`.
 

### 2021-08-31 manuscript.tex
Updates

--- 2021-08-27 manuscript.tex
@@
 \usepackage{lmodern}
-\usepackage{iftex}
-\ifPDFTeX
+\usepackage{ifxetex,ifluatex}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
   \usepackage[T1]{fontenc}
@@
   pdftitle={Light Exposure Behavior Assessment (LEBA): Develop of a novel instrument to capture light exposure-related behaviours},
-  pdfauthor={Mushfiqul Anwar Siraji1 \& Rafael Robert Lazar2},
+  pdfauthor={Mushfiqul Anwar Siraji1, Rafael Robert Lazar2, Manuel Spitschan3, \& Manuel Spitschan3},
   pdflang={en-EN},
@@
 
+% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
+% See https://github.com/crsh/papaja/issues/292
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
+
 % \usepackage{etoolbox}
@@
 \usepackage{csquotes}
-\ifXeTeX
+\ifxetex
   % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
@@
 \fi
-\ifLuaTeX
+\ifluatex
   \usepackage{selnolig}  % disable illegal ligatures
@@
 \title{\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours}
-\author{Mushfiqul Anwar Siraji\textsuperscript{1} \& Rafael Robert Lazar\textsuperscript{2}}
+\author{Mushfiqul Anwar Siraji\textsuperscript{1}, Rafael Robert Lazar\textsuperscript{2}, Manuel Spitschan\textsuperscript{3}, \& Manuel Spitschan\textsuperscript{3}}
 \date{}
@@
 The authors made the following contributions.
-Mushfiqul Anwar Siraji: Data Analysis, Writing - Original Draft Preparation, Data Visualization; Rafael Robert Lazar: Writing - Original Draft Preparation.
+Mushfiqul Anwar Siraji: Data Analysis, Writing - Original Draft Preparation, Data Visualization; Rafael Robert Lazar: Data Analysis, Writing - Original Draft Preparation, Data Visualization; Manuel Spitschan: Data Analysis, Writing - Original Draft Preparation, Data Visualization; Manuel Spitschan: Data Analysis, Writing - Original Draft Preparation, Data Visualization.
 
-Correspondence concerning this article should be addressed to Mushfiqul Anwar Siraji, Monash University, Malaysia.
-E-mail: \href{mailto:mushfiqul.anwarsiraji@monash.edu}{\nolinkurl{mushfiqul.anwarsiraji@monash.edu}}
+Correspondence concerning this article should be addressed to Manuel Spitschan, . E-mail:
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Wilhelm-Wundt-University\\\textsuperscript{2} Konstanz Business School}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Monash University, Malaysia\\\textsuperscript{2} University of Basel}
 
@@
 
+\hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
+
 \hypertarget{methods}{%
@@
 
+This line is just a test for pushing in the github repo.
+
 \hypertarget{material}{%
 \subsection{Material}\label{material}}
+
+\begin{figure}
+
+{\centering \includegraphics[width=4.17in,height=0.5\textheight]{Flowchart1}
+
+}
+
+\caption{ABC}\label{fig:unnamed-chunk-1}
+\end{figure}
 
@@
 
-\hypertarget{data-analysis}{%
-\subsection{Data analysis}\label{data-analysis}}
+Our study had four objectives.
+First, to develop an instrument to assess individual's light exposure behavior .
+Second, to conduct an exploratory factor analysis(EFA) to understand the latent structure.
+Third to gather structural validity evidence for the latent structure obtained in EFA (Furr, 2014).
+Lastly, we gathered item information using Item response theory (IRT)(Baker, 2017)
 
-We used R {[}Version 4.0.3; R Core Team (2020){]} and the R-package \emph{papaja} {[}Version 0.1.0.9997; Aust and Barth (2020){]} for all our analyses.
+\hypertarget{data-collection}{%
+\subsubsection{Data Collection}\label{data-collection}}
+
+Timeline of data collection, ethical approval, mode of data collection, how consent was recorded.
+
+\hypertarget{item-generation-and-content-validity-expert-panel-review}{%
+\subsubsection{Item generation and Content Validity: Expert Panel Review}\label{item-generation-and-content-validity-expert-panel-review}}
+
+How we developed the 48 items?
+
+\hypertarget{analytic-strategies}{%
+\subsection{Analytic Strategies}\label{analytic-strategies}}
+
+We used R (version 4.1.0), including several R-packages for our analyses.
+Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix were assessed.
+Our data violated both the univariate and multivariate normality assumptions.
+Due to these violations and the ordinal nature of our response data we used polychoric correlation matrix (Desjardins \& Bulut, 2018) for the EFA.
+We employed principal axis (pa) a factor extraction method with varimax rotation.
+PA is apparently robust to the normality assumption violations (Watkins, 2020).
+The obtained latent structure was confirmed by weighted least squares (WLS) extraction method as well.
+We used a combination factor indentification method including scree plot(Cattell, 1966), Horn's parallel analysis (Horn, 1965), minimum average partials method(Velicer, 1976), and hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) to identify factor numbers.
+Additionally, to identify the simple structure we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \textless0.3 (iii) no items with cross-loading greater than .3 across factors (Bandalos \& Finney, 2018; Child, 2006; Mulaik, 2009; Watkins, 2020)
 
@@
 
+Sampling adequacy was investigated by Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy(Kaiser, 1974) .
+The overall KMO vale for 23 items was 0.63 which was above the cutoff value of .50 indicating a mediocre sample (Hutcheson, 1999).
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:tabDes}Descriptive Statistics}
+
+\begin{tabular}{llllllll}
+\toprule
+ & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{p} & \multicolumn{1}{c}{Item-Total Correlation}\\
+\midrule
+Item1 & 1.12 & 0.49 & 5.02 & 27.80 & 0.25 & .00 & .16\\
+Item2 & 2.16 & 1.19 & 0.71 & -0.54 & 0.84 & .00 & .14\\
+Item3 & 4.14 & 0.99 & -1.23 & 1.14 & 0.79 & .00 & .19\\
+Item4 & 2.87 & 1.59 & 0.08 & -1.60 & 0.83 & .00 & .19\\
+Item5 & 1.76 & 1.23 & 1.35 & 0.44 & 0.66 & .00 & .38\\
+Item6 & 2.73 & 1.46 & 0.20 & -1.36 & 0.87 & .00 & .33\\
+Item7 & 3.86 & 1.67 & -0.99 & -0.85 & 0.65 & .00 & .23\\
+Item8 & 3.76 & 1.14 & -0.68 & -0.45 & 0.86 & .00 & .00\\
+Item9 & 3.42 & 1.83 & -0.45 & -1.69 & 0.69 & .00 & .33\\
+Item10 & 2.74 & 1.04 & 0.09 & -0.74 & 0.91 & .00 & .28\\
+Item11 & 2.60 & 1.25 & 0.29 & -0.86 & 0.89 & .00 & .35\\
+Item12 & 2.11 & 1.17 & 0.77 & -0.39 & 0.83 & .00 & .32\\
+Item13 & 2.94 & 1.03 & -0.12 & -0.40 & 0.91 & .00 & .10\\
+Item14 & 3.62 & 1.64 & -0.68 & -1.25 & 0.74 & .00 & .32\\
+Item15 & 1.64 & 1.18 & 1.79 & 2.02 & 0.60 & .00 & .15\\
+Item16 & 3.51 & 1.30 & -0.70 & -0.59 & 0.85 & .00 & .39\\
+Item17 & 1.96 & 0.98 & 1.02 & 0.69 & 0.82 & .00 & .05\\
+Item18 & 2.44 & 1.31 & 0.38 & -1.14 & 0.86 & .00 & .11\\
+Item19 & 3.80 & 1.29 & -0.87 & -0.42 & 0.82 & .00 & .17\\
+Item20 & 4.01 & 1.40 & -1.22 & 0.07 & 0.70 & .00 & .13\\
+Item21 & 1.33 & 0.91 & 3.03 & 8.43 & 0.41 & .00 & .01\\
+Item22 & 2.59 & 1.41 & 0.27 & -1.27 & 0.86 & .00 & .19\\
+Item23 & 1.31 & 0.81 & 2.75 & 6.92 & 0.43 & .00 & .21\\
+Item24 & 1.47 & 1.18 & 2.38 & 4.00 & 0.43 & .00 & .28\\
+Item25 & 2.56 & 1.27 & 0.33 & -1.00 & 0.89 & .00 & .11\\
+Item26 & 1.54 & 1.25 & 2.13 & 2.86 & 0.46 & .00 & .36\\
+Item27 & 4.30 & 1.08 & -1.79 & 2.53 & 0.67 & .00 & .22\\
+Item28 & 2.27 & 1.39 & 0.74 & -0.81 & 0.81 & .00 & .25\\
+Item29 & 3.26 & 1.09 & -0.26 & -0.45 & 0.91 & .00 & .14\\
+Item30 & 2.22 & 1.48 & 0.71 & -1.02 & 0.76 & .00 & .30\\
+Item31 & 1.05 & 0.36 & 7.23 & 52.98 & 0.13 & .00 & .18\\
+Item32 & 1.54 & 1.21 & 2.07 & 2.75 & 0.49 & .00 & .31\\
+Item33 & 1.04 & 0.33 & 8.99 & 85.28 & 0.10 & .00 & .16\\
+Item34 & 3.36 & 1.38 & -0.48 & -1.03 & 0.87 & .00 & .16\\
+Item35 & 2.26 & 1.25 & 0.70 & -0.60 & 0.85 & .00 & .19\\
+Item36 & 2.36 & 1.22 & 0.59 & -0.62 & 0.87 & .00 & .25\\
+Item37 & 1.14 & 0.59 & 4.79 & 24.05 & 0.25 & .00 & .16\\
+Item38 & 2.25 & 1.27 & 0.69 & -0.64 & 0.84 & .00 & .18\\
+Item39 & 3.93 & 1.48 & -1.06 & -0.44 & 0.71 & .00 & .18\\
+Item40 & 3.57 & 1.07 & -0.65 & -0.17 & 0.88 & .00 & .21\\
+Item41 & 3.55 & 1.65 & -0.60 & -1.34 & 0.76 & .00 & .43\\
+Item42 & 3.00 & 1.62 & -0.08 & -1.61 & 0.83 & .00 & .44\\
+Item43 & 1.56 & 1.23 & 2.00 & 2.45 & 0.50 & .00 & .32\\
+Item44 & 2.97 & 1.20 & -0.06 & -0.94 & 0.91 & .00 & -.10\\
+Item45 & 2.79 & 1.55 & 0.19 & -1.48 & 0.85 & .00 & .20\\
+Item46 & 2.14 & 1.31 & 0.77 & -0.78 & 0.80 & .00 & .26\\
+Item47 & 2.18 & 0.90 & 0.60 & 0.12 & 0.86 & .00 & .26\\
+Item48 & 1.48 & 1.11 & 2.18 & 3.35 & 0.48 & .00 & .24\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{figure}
+\includegraphics[width=0.5\linewidth]{manuscript_files/figure-latex/figCor-1} \caption{Iter-correlation of the items}\label{fig:figCor}
+\end{figure}
+
+Table\ref{tab:tabDes} summarizes the univariate descriptive statistics for the 48 items.
+some of the items were skewed with high Kurtosis values.
+The Shapiro-Wilk test of normality (Shapiro \& Wilk, 1965) indicated all the items violated normality assumptions.
+Multivariate normality assumptions were investigated by Marida's test (Mardia, 1970).
+Multivariate skew = 583.80 (p \textless0.001) and multivariate kurtosis = 2,749.15 (p \textless0.001) indicated multivariate normality assumptions violation.
+Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen (Desjardins \& Bulut, 2018).
+Bartlett's test of sphericity (Bartlett, 1954), \(\chi^2\) (1128) = 5042.86, p \textless{} .001{]} indicated the correlations between items are adequate for the EFA.
+However only 4.96\% of the inter-item correlation coefficients were greater than .30 in the obtained matrix.
+The inter item correlation ranged between .44 to .91.
+The corrected item-total correlations ranged between .10 to .44.
+
+Scree plot ( Fig@ref(fig:fac.id)) suggested a six-factor solution.Horn's parallel analysis (Horn, 1965), like the Monte Carlo study, draws several sets of random data with the same number of participants as the original data set and compares the mean eigenvalues among the simulated and original data sets to retain optimal factors.This extraction method also supported a five-factor model.
+In our data set parallel analysis with 500 iterations indicated six-factor solution.
+However, In MAP method (Velicer, 1976) and Hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) suggested a five-factor solution Parallel analysis is also more immune to the normality assumptions violation(\textbf{RN1263?}).
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{parallel} \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/fac.id-2} \includegraphics[width=0.5\linewidth,height=0.5\textheight]{HUll method}
+
+}
+
+\caption{Factor Identification (A) Parallel analysis (B) Scree Plot, (C) Hull method}(\#fig:fac.id)
+\end{figure}
+
 \hypertarget{confirmatory-factor-analysis}{%
 \section{Confirmatory Factor Analysis}\label{confirmatory-factor-analysis}}
-
-\begin{verbatim}
-## Call: mardia(x = LB.cfa, na.rm = T, plot = F)
-## 
-## Mardia tests of multivariate skew and kurtosis
-## Use describe(x) the to get univariate tests
-## n.obs = 199   num.vars =  48 
-## b1p =  761.72   skew =  25263.82  with probability  <=  8.8e-152
-##  small sample skew =  25660.39  with probability <=  1.2e-171
-## b2p =  2540.5   kurtosis =  14.3  with probability <=  0
-\end{verbatim}
-
-\begin{verbatim}
-## lavaan 0.6-9 ended normally after 64 iterations
-## 
-##   Estimator                                         ML
-##   Optimization method                           NLMINB
-##   Number of model parameters                        79
-##                                                       
-##   Number of observations                           199
-##   Number of missing patterns                         1
-##                                                       
-## Model Test User Model:
-##                                                Standard      Robust
-##   Test Statistic                                406.275     387.999
-##   Degrees of freedom                                220         220
-##   P-value (Chi-square)                            0.000       0.000
-##   Scaling correction factor                                   1.047
-##        Yuan-Bentler correction (Mplus variant)                     
-## 
-## Model Test Baseline Model:
-## 
-##   Test statistic                              1700.445    1368.235
-##   Degrees of freedom                               253         253
-##   P-value                                        0.000       0.000
-##   Scaling correction factor                                  1.243
-## 
-## User Model versus Baseline Model:
-## 
-##   Comparative Fit Index (CFI)                    0.871       0.849
-##   Tucker-Lewis Index (TLI)                       0.852       0.827
-##                                                                   
-##   Robust Comparative Fit Index (CFI)                         0.873
-##   Robust Tucker-Lewis Index (TLI)                            0.854
-## 
-## Loglikelihood and Information Criteria:
-## 
-##   Loglikelihood user model (H0)              -6371.304   -6371.304
-##   Scaling correction factor                                  1.877
-##       for the MLR correction                                      
-##   Loglikelihood unrestricted model (H1)      -6168.166   -6168.166
-##   Scaling correction factor                                  1.266
-##       for the MLR correction                                      
-##                                                                   
-##   Akaike (AIC)                               12900.607   12900.607
-##   Bayesian (BIC)                             13160.778   13160.778
-##   Sample-size adjusted Bayesian (BIC)        12910.502   12910.502
-## 
-## Root Mean Square Error of Approximation:
-## 
-##   RMSEA                                          0.065       0.062
-##   90 Percent confidence interval - lower         0.055       0.052
-##   90 Percent confidence interval - upper         0.075       0.072
-##   P-value RMSEA <= 0.05                          0.007       0.026
-##                                                                   
-##   Robust RMSEA                                               0.063
-##   90 Percent confidence interval - lower                     0.053
-##   90 Percent confidence interval - upper                     0.074
-## 
-## Standardized Root Mean Square Residual:
-## 
-##   SRMR                                           0.075       0.075
-## 
-## Parameter Estimates:
-## 
-##   Standard errors                             Sandwich
-##   Information bread                           Observed
-##   Observed information based on                Hessian
-## 
-## Latent Variables:
-##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
-##   F1 =~                                                                 
-##     item31            1.000                               0.397    0.873
-##     item33            0.823    0.123    6.685    0.000    0.327    0.724
-##     item1             0.990    0.158    6.246    0.000    0.393    0.644
-##     item37            0.901    0.284    3.176    0.001    0.358    0.507
-##     item24            0.437    0.265    1.647    0.100    0.173    0.175
-##   F2 =~                                                                 
-##     item10            1.000                               0.859    0.783
-##     item47            0.856    0.111    7.729    0.000    0.736    0.808
-##     item36            0.945    0.137    6.876    0.000    0.812    0.701
-##     item44           -0.714    0.139   -5.131    0.000   -0.613   -0.490
-##     item35            0.739    0.139    5.300    0.000    0.635    0.508
-##     item13            0.472    0.113    4.163    0.000    0.406    0.373
-##   F3 =~                                                                 
-##     item43            1.000                               1.291    0.951
-##     item26            0.918    0.056   16.313    0.000    1.186    0.843
-##     item32            0.895    0.064   13.928    0.000    1.155    0.872
-##   F4 =~                                                                 
-##     item14            1.000                               0.493    0.263
-##     item7             0.640    0.267    2.392    0.017    0.316    0.171
-##     item11            1.850    0.684    2.706    0.007    0.912    0.708
-##     item42            0.788    0.314    2.513    0.012    0.389    0.225
-##     item12            1.953    0.779    2.509    0.012    0.963    0.845
-##     item16            1.017    0.410    2.479    0.013    0.501    0.343
-##   F5 =~                                                                 
-##     item19            1.000                               0.875    0.683
-##     item34            1.312    0.174    7.555    0.000    1.148    0.831
-##     item2             0.974    0.143    6.827    0.000    0.852    0.606
-## 
-## Covariances:
-##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
-##   F1 ~~                                                                 
-##     F2                0.038    0.033    1.169    0.243    0.112    0.112
-##     F3               -0.019    0.051   -0.372    0.710   -0.037   -0.037
-##     F4                0.013    0.024    0.532    0.595    0.064    0.064
-##     F5                0.027    0.034    0.795    0.427    0.078    0.078
-##   F2 ~~                                                                 
-##     F3               -0.076    0.076   -0.998    0.318   -0.069   -0.069
-##     F4                0.077    0.054    1.443    0.149    0.182    0.182
-##     F5               -0.259    0.088   -2.929    0.003   -0.344   -0.344
-##   F3 ~~                                                                 
-##     F4                0.032    0.065    0.501    0.616    0.051    0.051
-##     F5               -0.035    0.103   -0.339    0.735   -0.031   -0.031
-##   F4 ~~                                                                 
-##     F5               -0.015    0.044   -0.350    0.726   -0.036   -0.036
-## 
-## Intercepts:
-##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
-##    .item31            0.879    0.032   27.295    0.000    0.879    1.935
-##    .item33            0.869    0.032   27.150    0.000    0.869    1.925
-##    .item1             0.990    0.043   22.904    0.000    0.990    1.624
-##    .item37            0.995    0.050   19.900    0.000    0.995    1.411
-##    .item24            1.131    0.070   16.129    0.000    1.131    1.143
-##    .item10            2.543    0.078   32.704    0.000    2.543    2.318
-##    .item47            2.035    0.065   31.553    0.000    2.035    2.237
-##    .item36            2.095    0.082   25.511    0.000    2.095    1.808
-##    .item44            2.995    0.089   33.796    0.000    2.995    2.396
-##    .item35            2.070    0.089   23.362    0.000    2.070    1.656
-##    .item13            2.834    0.077   36.750    0.000    2.834    2.605
-##    .item43            1.578    0.096   16.401    0.000    1.578    1.163
-##    .item26            1.482    0.100   14.868    0.000    1.482    1.054
-##    .item32            1.533    0.094   16.314    0.000    1.533    1.156
-##    .item14            3.020    0.133   22.749    0.000    3.020    1.613
-##    .item7             3.688    0.131   28.175    0.000    3.688    1.997
-##    .item11            2.382    0.091   26.054    0.000    2.382    1.847
-##    .item42            2.935    0.122   23.959    0.000    2.935    1.698
-##    .item12            2.005    0.081   24.793    0.000    2.005    1.758
-##    .item16            3.211    0.104   30.991    0.000    3.211    2.197
-##    .item19            3.930    0.091   43.244    0.000    3.930    3.065
-##    .item34            3.583    0.098   36.558    0.000    3.583    2.592
-##    .item2             2.482    0.100   24.897    0.000    2.482    1.765
-##     F1                0.000                               0.000    0.000
-##     F2                0.000                               0.000    0.000
-##     F3                0.000                               0.000    0.000
-##     F4                0.000                               0.000    0.000
-##     F5                0.000                               0.000    0.000
-## 
-## Variances:
-##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
-##    .item31            0.049    0.032    1.533    0.125    0.049    0.237
-##    .item33            0.097    0.058    1.678    0.093    0.097    0.476
-##    .item1             0.217    0.058    3.718    0.000    0.217    0.585
-##    .item37            0.370    0.125    2.952    0.003    0.370    0.743
-##    .item24            0.948    0.200    4.729    0.000    0.948    0.969
-##    .item10            0.465    0.130    3.582    0.000    0.465    0.386
-##    .item47            0.287    0.054    5.359    0.000    0.287    0.347
-##    .item36            0.683    0.094    7.283    0.000    0.683    0.509
-##    .item44            1.187    0.139    8.551    0.000    1.187    0.760
-##    .item35            1.160    0.156    7.447    0.000    1.160    0.742
-##    .item13            1.019    0.112    9.133    0.000    1.019    0.861
-##    .item43            0.175    0.101    1.726    0.084    0.175    0.095
-##    .item26            0.573    0.164    3.500    0.000    0.573    0.289
-##    .item32            0.422    0.114    3.694    0.000    0.422    0.240
-##    .item14            3.264    0.236   13.831    0.000    3.264    0.931
-##    .item7             3.311    0.274   12.104    0.000    3.311    0.971
-##    .item11            0.831    0.172    4.816    0.000    0.831    0.499
-##    .item42            2.835    0.171   16.555    0.000    2.835    0.949
-##    .item12            0.373    0.155    2.413    0.016    0.373    0.287
-##    .item16            1.885    0.199    9.453    0.000    1.885    0.882
-##    .item19            0.877    0.130    6.769    0.000    0.877    0.534
-##    .item34            0.592    0.179    3.319    0.001    0.592    0.310
-##    .item2             1.252    0.144    8.687    0.000    1.252    0.633
-##     F1                0.158    0.033    4.750    0.000    1.000    1.000
-##     F2                0.738    0.147    5.035    0.000    1.000    1.000
-##     F3                1.667    0.246    6.764    0.000    1.000    1.000
-##     F4                0.243    0.170    1.431    0.152    1.000    1.000
-##     F5                0.766    0.164    4.669    0.000    1.000    1.000
-## 
-## R-Square:
-##                    Estimate
-##     item31            0.763
-##     item33            0.524
-##     item1             0.415
-##     item37            0.257
-##     item24            0.031
-##     item10            0.614
-##     item47            0.653
-##     item36            0.491
-##     item44            0.240
-##     item35            0.258
-##     item13            0.139
-##     item43            0.905
-##     item26            0.711
-##     item32            0.760
-##     item14            0.069
-##     item7             0.029
-##     item11            0.501
-##     item42            0.051
-##     item12            0.713
-##     item16            0.118
-##     item19            0.466
-##     item34            0.690
-##     item2             0.367
-\end{verbatim}
-
-\begin{verbatim}
-##          gfi         agfi          nfi          rfi   cfi.robust   tli.robust 
-##        0.974        0.965        0.761        0.725        0.873        0.854 
-## rmsea.robust         srmr          aic 
-##        0.063        0.075    12900.607
-\end{verbatim}
-
-\begin{verbatim}
-##               F1        F2        F3        F4        F5
-## alpha  0.6310368 0.4818562 0.9175522 0.5837683 0.7413266
-## omega  0.6175478 0.6258140 0.9185279 0.5055608 0.7523535
-## omega2 0.6175478 0.6258140 0.9185279 0.5055608 0.7523535
-## omega3 0.5953438 0.6255108 0.9183889 0.4373745 0.7559532
-## avevar 0.2554061 0.3750499 0.7902138 0.1670288 0.5080283
-\end{verbatim}
-
-Based on CFI, TLI, RMSEA and SRMR value the fitted five factor model is not acceptable.
-As a result a close inspection on items with low factor-loadings and low R-square value was conducted. two items were found to be problematic \textbf{item7, item 24} with vary low R-square
-value thus discarded from the model.
-
-\begin{verbatim}
-## lavaan 0.6-9 ended normally after 67 iterations
-## 
-##   Estimator                                         ML
-##   Optimization method                           NLMINB
-##   Number of model parameters                        73
-##                                                       
-##   Number of observations                           199
-##   Number of missing patterns                         1
-##                                                       
-## Model Test User Model:
-##                                                Standard      Robust
-##   Test Statistic                                273.193     263.376
-##   Degrees of freedom                                179         179
-##   P-value (Chi-square)                            0.000       0.000
-##   Scaling correction factor                                   1.037
-##        Yuan-Bentler correction (Mplus variant)                     
-## 
-## Model Test Baseline Model:
-## 
-##   Test statistic                              1557.809    1230.314
-##   Degrees of freedom                               210         210
-##   P-value                                        0.000       0.000
-##   Scaling correction factor                                  1.266
-## 
-## User Model versus Baseline Model:
-## 
-##   Comparative Fit Index (CFI)                    0.930       0.917
-##   Tucker-Lewis Index (TLI)                       0.918       0.903
-##                                                                   
-##   Robust Comparative Fit Index (CFI)                         0.932
-##   Robust Tucker-Lewis Index (TLI)                            0.921
-## 
-## Loglikelihood and Information Criteria:
-## 
-##   Loglikelihood user model (H0)              -5691.495   -5691.495
-##   Scaling correction factor                                  1.890
-##       for the MLR correction                                      
-##   Loglikelihood unrestricted model (H1)      -5554.899   -5554.899
-##   Scaling correction factor                                  1.284
-##       for the MLR correction                                      
-##                                                                   
-##   Akaike (AIC)                               11528.990   11528.990
-##   Bayesian (BIC)                             11769.401   11769.401
-##   Sample-size adjusted Bayesian (BIC)        11538.134   11538.134
-## 
-## Root Mean Square Error of Approximation:
-## 
-##   RMSEA                                          0.051       0.049
-##   90 Percent confidence interval - lower         0.039       0.036
-##   90 Percent confidence interval - upper         0.063       0.061
-##   P-value RMSEA <= 0.05                          0.412       0.559
-##                                                                   
-##   Robust RMSEA                                               0.050
-##   90 Percent confidence interval - lower                     0.036
-##   90 Percent confidence interval - upper                     0.062
-## 
-## Standardized Root Mean Square Residual:
-## 
-##   SRMR                                           0.068       0.068
-## 
-## Parameter Estimates:
-## 
-##   Standard errors                             Sandwich
-##   Information bread                           Observed
-##   Observed information based on                Hessian
-## 
-## Latent Variables:
-##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
-##   F1 =~                                                                 
-##     item31            1.000                               0.397    0.873
-##     item33            0.828    0.119    6.962    0.000    0.328    0.727
-##     item1             0.992    0.153    6.503    0.000    0.394    0.645
-##     item37            0.890    0.278    3.203    0.001    0.353    0.501
-##   F2 =~                                                                 
-##     item10            1.000                               0.859    0.783
-##     item47            0.856    0.111    7.739    0.000    0.735    0.808
-##     item36            0.946    0.138    6.876    0.000    0.812    0.701
-##     item35            0.739    0.139    5.300    0.000    0.635    0.508
-##     item13            0.472    0.113    4.162    0.000    0.405    0.373
-##     item44           -0.714    0.139   -5.133    0.000   -0.613   -0.490
-##   F3 =~                                                                 
-##     item43            1.000                               1.291    0.951
-##     item26            0.919    0.056   16.331    0.000    1.186    0.843
-##     item32            0.895    0.064   13.941    0.000    1.155    0.872
-##   F4 =~                                                                 
-##     item14            1.000                               0.444    0.237
-##     item42            0.867    0.332    2.614    0.009    0.385    0.223
-##     item12            2.245    0.830    2.704    0.007    0.996    0.873
-##     item11            2.009    0.720    2.791    0.005    0.891    0.691
-##     item16            1.108    0.445    2.488    0.013    0.492    0.336
-##   F5 =~                                                                 
-##     item19            1.000                               0.875    0.683
-##     item34            1.312    0.173    7.568    0.000    1.148    0.831
-##     item2             0.974    0.143    6.828    0.000    0.852    0.606
-## 
-## Covariances:
-##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
-##   F1 ~~                                                                 
-##     F2                0.037    0.032    1.143    0.253    0.108    0.108
-##     F3               -0.020    0.051   -0.400    0.689   -0.040   -0.040
-##     F4                0.011    0.020    0.535    0.593    0.062    0.062
-##     F5                0.029    0.034    0.843    0.399    0.083    0.083
-##   F2 ~~                                                                 
-##     F3               -0.076    0.076   -0.998    0.318   -0.069   -0.069
-##     F4                0.069    0.048    1.434    0.152    0.181    0.181
-##     F5               -0.259    0.088   -2.931    0.003   -0.344   -0.344
-##   F3 ~~                                                                 
-##     F4                0.025    0.056    0.449    0.654    0.044    0.044
-##     F5               -0.035    0.103   -0.339    0.735   -0.031   -0.031
-##   F4 ~~                                                                 
-##     F5               -0.015    0.039   -0.376    0.707   -0.038   -0.038
-## 
-## Intercepts:
-##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
-##    .item31            0.879    0.032   27.295    0.000    0.879    1.935
-##    .item33            0.869    0.032   27.150    0.000    0.869    1.925
-##    .item1             0.990    0.043   22.904    0.000    0.990    1.624
-##    .item37            0.995    0.050   19.900    0.000    0.995    1.411
-##    .item10            2.543    0.078   32.704    0.000    2.543    2.318
-##    .item47            2.035    0.065   31.553    0.000    2.035    2.237
-##    .item36            2.095    0.082   25.511    0.000    2.095    1.808
-##    .item35            2.070    0.089   23.362    0.000    2.070    1.656
-##    .item13            2.834    0.077   36.750    0.000    2.834    2.605
-##    .item44            2.995    0.089   33.796    0.000    2.995    2.396
-##    .item43            1.578    0.096   16.401    0.000    1.578    1.163
-##    .item26            1.482    0.100   14.868    0.000    1.482    1.054
-##    .item32            1.533    0.094   16.314    0.000    1.533    1.156
-##    .item14            3.020    0.133   22.749    0.000    3.020    1.613
-##    .item42            2.935    0.122   23.959    0.000    2.935    1.698
-##    .item12            2.005    0.081   24.793    0.000    2.005    1.758
-##    .item11            2.382    0.091   26.054    0.000    2.382    1.847
-##    .item16            3.211    0.104   30.991    0.000    3.211    2.197
-##    .item19            3.930    0.091   43.244    0.000    3.930    3.065
-##    .item34            3.583    0.098   36.558    0.000    3.583    2.592
-##    .item2             2.482    0.100   24.897    0.000    2.482    1.765
-##     F1                0.000                               0.000    0.000
-##     F2                0.000                               0.000    0.000
-##     F3                0.000                               0.000    0.000
-##     F4                0.000                               0.000    0.000
-##     F5                0.000                               0.000    0.000
-## 
-## Variances:
-##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
-##    .item31            0.049    0.031    1.578    0.115    0.049    0.238
-##    .item33            0.096    0.058    1.669    0.095    0.096    0.472
-##    .item1             0.217    0.058    3.717    0.000    0.217    0.583
-##    .item37            0.373    0.124    3.005    0.003    0.373    0.749
-##    .item10            0.465    0.130    3.584    0.000    0.465    0.387
-##    .item47            0.287    0.054    5.343    0.000    0.287    0.347
-##    .item36            0.683    0.094    7.276    0.000    0.683    0.509
-##    .item35            1.160    0.156    7.452    0.000    1.160    0.742
-##    .item13            1.019    0.112    9.133    0.000    1.019    0.861
-##    .item44            1.187    0.139    8.549    0.000    1.187    0.759
-##    .item43            0.175    0.101    1.731    0.083    0.175    0.095
-##    .item26            0.572    0.164    3.498    0.000    0.572    0.289
-##    .item32            0.422    0.114    3.695    0.000    0.422    0.240
-##    .item14            3.310    0.213   15.534    0.000    3.310    0.944
-##    .item42            2.838    0.170   16.714    0.000    2.838    0.950
-##    .item12            0.310    0.180    1.719    0.086    0.310    0.238
-##    .item11            0.869    0.182    4.765    0.000    0.869    0.522
-##    .item16            1.895    0.201    9.419    0.000    1.895    0.887
-##    .item19            0.877    0.129    6.775    0.000    0.877    0.534
-##    .item34            0.593    0.178    3.327    0.001    0.593    0.310
-##    .item2             1.252    0.144    8.693    0.000    1.252    0.633
-##     F1                0.157    0.032    4.874    0.000    1.000    1.000
-##     F2                0.738    0.146    5.037    0.000    1.000    1.000
-##     F3                1.667    0.246    6.765    0.000    1.000    1.000
-##     F4                0.197    0.132    1.493    0.136    1.000    1.000
-##     F5                0.766    0.164    4.669    0.000    1.000    1.000
-## 
-## R-Square:
-##                    Estimate
-##     item31            0.762
-##     item33            0.528
-##     item1             0.417
-##     item37            0.251
-##     item10            0.613
-##     item47            0.653
-##     item36            0.491
-##     item35            0.258
-##     item13            0.139
-##     item44            0.241
-##     item43            0.905
-##     item26            0.711
-##     item32            0.760
-##     item14            0.056
-##     item42            0.050
-##     item12            0.762
-##     item11            0.478
-##     item16            0.113
-##     item19            0.466
-##     item34            0.690
-##     item2             0.367
-\end{verbatim}
-
-\begin{verbatim}
-##               F1        F2        F3        F4        F5
-## alpha  0.7547222 0.4818562 0.9175522 0.5566040 0.7413266
-## omega  0.7466444 0.6258291 0.9185357 0.5272886 0.7523499
-## omega2 0.7466444 0.6258291 0.9185357 0.5272886 0.7523499
-## omega3 0.7344825 0.6255092 0.9184124 0.4921277 0.7559546
-## avevar 0.4256850 0.3750895 0.7902299 0.2046565 0.5080155
-\end{verbatim}
-
-\begin{verbatim}
-##        lhs op    rhs     mi    epc sepc.lv sepc.all sepc.nox
-## 168 item31 ~~ item33 17.975  0.090   0.090    1.313    1.313
-## 136     F4 =~  item1 14.553  0.339   0.150    0.247    0.247
-## 245 item10 ~~ item13 13.377  0.222   0.222    0.322    0.322
-## 134     F4 =~ item31 11.467 -0.210  -0.093   -0.205   -0.205
-## 359 item42 ~~ item16 11.094  0.562   0.562    0.242    0.242
-## 207  item1 ~~ item37 10.910  0.078   0.078    0.274    0.274
-## 104     F2 =~ item37 10.403  0.184   0.158    0.224    0.224
-## 363 item12 ~~ item11  9.624  1.312   1.312    2.529    2.529
-## 339 item26 ~~ item19  8.623  0.177   0.177    0.250    0.250
-## 137     F4 =~ item37  7.959  0.316   0.140    0.199    0.199
-## 101     F2 =~ item31  7.808 -0.089  -0.076   -0.167   -0.167
-## 237 item37 ~~ item11  7.249  0.122   0.122    0.215    0.215
-## 218  item1 ~~ item42  7.190  0.159   0.159    0.203    0.203
-## 188 item33 ~~  item1  6.541 -0.046  -0.046   -0.318   -0.318
-## 308 item13 ~~ item16  6.525  0.258   0.258    0.186    0.186
-## 332 item43 ~~  item2  6.427  0.140   0.140    0.300    0.300
-## 350 item14 ~~ item42  5.773  0.530   0.530    0.173    0.173
-## 362 item42 ~~  item2  5.298  0.330   0.330    0.175    0.175
-## 100     F1 =~  item2  5.261 -0.547  -0.217   -0.154   -0.154
-## 233 item37 ~~ item32  5.251  0.074   0.074    0.186    0.186
-## 173 item31 ~~ item36  5.150 -0.045  -0.045   -0.248   -0.248
-## 330 item43 ~~ item19  5.106 -0.109  -0.109   -0.277   -0.277
-## 192 item33 ~~ item36  4.870  0.048   0.048    0.187    0.187
-## 167     F5 =~ item16  4.750  0.278   0.243    0.166    0.166
-## 170 item31 ~~ item37  4.638 -0.042  -0.042   -0.313   -0.313
-## 141     F4 =~ item35  4.630  0.435   0.193    0.154    0.154
-## 258 item47 ~~ item36  4.608  0.121   0.121    0.273    0.273
-## 358 item42 ~~ item11  4.551 -0.293  -0.293   -0.187   -0.187
-## 115     F2 =~  item2  4.513 -0.260  -0.224   -0.159   -0.159
-## 226 item37 ~~ item47  4.505  0.060   0.060    0.184    0.184
-## 114     F2 =~ item34  4.482  0.276   0.237    0.172    0.172
-## 219  item1 ~~ item12  4.328  0.064   0.064    0.247    0.247
-## 206 item33 ~~  item2  4.291 -0.060  -0.060   -0.173   -0.173
-## 96      F1 =~ item11  4.020 -0.412  -0.164   -0.127   -0.127
-\end{verbatim}
-
-\begin{verbatim}
-## lavaan 0.6-9 ended normally after 67 iterations
-## 
-##   Estimator                                         ML
-##   Optimization method                           NLMINB
-##   Number of model parameters                        75
-##                                                       
-##   Number of observations                           199
-##   Number of missing patterns                         1
-##                                                       
-## Model Test User Model:
-##                                                Standard      Robust
-##   Test Statistic                                233.643     228.963
-##   Degrees of freedom                                177         177
-##   P-value (Chi-square)                            0.003       0.005
-##   Scaling correction factor                                   1.020
-##        Yuan-Bentler correction (Mplus variant)                     
-## 
-## Model Test Baseline Model:
-## 
-##   Test statistic                              1557.809    1230.314
-##   Degrees of freedom                               210         210
-##   P-value                                        0.000       0.000
-##   Scaling correction factor                                  1.266
-## 
-## User Model versus Baseline Model:
-## 
-##   Comparative Fit Index (CFI)                    0.958       0.949
-##   Tucker-Lewis Index (TLI)                       0.950       0.940
-##                                                                   
-##   Robust Comparative Fit Index (CFI)                         0.959
-##   Robust Tucker-Lewis Index (TLI)                            0.951
-## 
-## Loglikelihood and Information Criteria:
-## 
-##   Loglikelihood user model (H0)              -5671.720   -5671.720
-##   Scaling correction factor                                  1.907
-##       for the MLR correction                                      
-##   Loglikelihood unrestricted model (H1)      -5554.899   -5554.899
-##   Scaling correction factor                                  1.284
-##       for the MLR correction                                      
-##                                                                   
-##   Akaike (AIC)                               11493.441   11493.441
-##   Bayesian (BIC)                             11740.438   11740.438
-##   Sample-size adjusted Bayesian (BIC)        11502.834   11502.834
-## 
-## Root Mean Square Error of Approximation:
-## 
-##   RMSEA                                          0.040       0.038
-##   90 Percent confidence interval - lower         0.024       0.022
-##   90 Percent confidence interval - upper         0.053       0.052
-##   P-value RMSEA <= 0.05                          0.884       0.920
-##                                                                   
-##   Robust RMSEA                                               0.039
-##   90 Percent confidence interval - lower                     0.022
-##   90 Percent confidence interval - upper                     0.052
-## 
-## Standardized Root Mean Square Residual:
-## 
-##   SRMR                                           0.061       0.061
-## 
-## Parameter Estimates:
-## 
-##   Standard errors                             Sandwich
-##   Information bread                           Observed
-##   Observed information based on                Hessian
-## 
-## Latent Variables:
-##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
-##   F1 =~                                                                 
-##     item31            1.000                               0.293    0.645
-##     item33            0.755    0.145    5.204    0.000    0.221    0.490
-##     item1             1.782    0.655    2.721    0.007    0.522    0.856
-##     item37            1.345    0.379    3.548    0.000    0.394    0.559
-##   F2 =~                                                                 
-##     item10            1.000                               0.858    0.782
-##     item47            0.859    0.109    7.846    0.000    0.736    0.809
-##     item36            0.947    0.137    6.937    0.000    0.813    0.701
-##     item35            0.740    0.139    5.318    0.000    0.634    0.507
-##     item13            0.475    0.114    4.169    0.000    0.407    0.374
-##     item44           -0.714    0.139   -5.146    0.000   -0.612   -0.490
-##   F3 =~                                                                 
-##     item43            1.000                               1.291    0.951
-##     item26            0.918    0.056   16.327    0.000    1.185    0.843
-##     item32            0.895    0.064   13.889    0.000    1.155    0.872
-##   F4 =~                                                                 
-##     item14            1.000                               0.658    0.351
-##     item42            1.470    0.481    3.058    0.002    0.967    0.559
-##     item12            0.797    0.266    2.995    0.003    0.524    0.459
-##     item11            0.527    0.254    2.078    0.038    0.347    0.269
-##     item16            0.993    0.429    2.313    0.021    0.653    0.447
-##   F5 =~                                                                 
-##     item19            1.000                               0.870    0.679
-##     item34            1.313    0.167    7.871    0.000    1.142    0.826
-##     item2             0.995    0.150    6.653    0.000    0.866    0.615
-## 
-## Covariances:
-##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
-##  .item31 ~~                                                             
-##    .item33            0.070    0.027    2.632    0.008    0.070    0.513
-##  .item12 ~~                                                             
-##    .item11            0.716    0.139    5.135    0.000    0.716    0.569
-##   F1 ~~                                                                 
-##     F2                0.050    0.027    1.849    0.064    0.197    0.197
-##     F3               -0.008    0.035   -0.239    0.811   -0.022   -0.022
-##     F4                0.080    0.031    2.530    0.011    0.413    0.413
-##     F5                0.010    0.026    0.395    0.693    0.040    0.040
-##   F2 ~~                                                                 
-##     F3               -0.076    0.076   -1.000    0.317   -0.069   -0.069
-##     F4                0.119    0.083    1.424    0.154    0.210    0.210
-##     F5               -0.259    0.087   -2.972    0.003   -0.347   -0.347
-##   F3 ~~                                                                 
-##     F4                0.073    0.102    0.716    0.474    0.086    0.086
-##     F5               -0.034    0.102   -0.336    0.737   -0.031   -0.031
-##   F4 ~~                                                                 
-##     F5                0.089    0.076    1.171    0.242    0.155    0.155
-## 
-## Intercepts:
-##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
-##    .item31            0.879    0.032   27.295    0.000    0.879    1.935
-##    .item33            0.869    0.032   27.150    0.000    0.869    1.925
-##    .item1             0.990    0.043   22.904    0.000    0.990    1.624
-##    .item37            0.995    0.050   19.900    0.000    0.995    1.411
-##    .item10            2.543    0.078   32.704    0.000    2.543    2.318
-##    .item47            2.035    0.065   31.553    0.000    2.035    2.237
-##    .item36            2.095    0.082   25.511    0.000    2.095    1.808
-##    .item35            2.070    0.089   23.362    0.000    2.070    1.656
-##    .item13            2.834    0.077   36.750    0.000    2.834    2.605
-##    .item44            2.995    0.089   33.796    0.000    2.995    2.396
-##    .item43            1.578    0.096   16.401    0.000    1.578    1.163
-##    .item26            1.482    0.100   14.868    0.000    1.482    1.054
-##    .item32            1.533    0.094   16.314    0.000    1.533    1.156
-##    .item14            3.020    0.133   22.749    0.000    3.020    1.613
-##    .item42            2.935    0.122   23.959    0.000    2.935    1.698
-##    .item12            2.005    0.081   24.793    0.000    2.005    1.758
-##    .item11            2.382    0.091   26.054    0.000    2.382    1.847
-##    .item16            3.211    0.104   30.991    0.000    3.211    2.197
-##    .item19            3.930    0.091   43.244    0.000    3.930    3.065
-##    .item34            3.583    0.098   36.558    0.000    3.583    2.592
-##    .item2             2.482    0.100   24.897    0.000    2.482    1.765
-##     F1                0.000                               0.000    0.000
-##     F2                0.000                               0.000    0.000
-##     F3                0.000                               0.000    0.000
-##     F4                0.000                               0.000    0.000
-##     F5                0.000                               0.000    0.000
-## 
-## Variances:
-##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
-##    .item31            0.121    0.035    3.491    0.000    0.121    0.584
-##    .item33            0.155    0.070    2.218    0.027    0.155    0.760
-##    .item1             0.099    0.090    1.099    0.272    0.099    0.267
-##    .item37            0.342    0.130    2.621    0.009    0.342    0.688
-##    .item10            0.468    0.128    3.650    0.000    0.468    0.389
-##    .item47            0.286    0.054    5.312    0.000    0.286    0.345
-##    .item36            0.682    0.094    7.244    0.000    0.682    0.508
-##    .item35            1.161    0.155    7.465    0.000    1.161    0.743
-##    .item13            1.018    0.112    9.101    0.000    1.018    0.860
-##    .item44            1.188    0.138    8.579    0.000    1.188    0.760
-##    .item43            0.175    0.101    1.731    0.083    0.175    0.095
-##    .item26            0.573    0.164    3.503    0.000    0.573    0.290
-##    .item32            0.422    0.114    3.684    0.000    0.422    0.240
-##    .item14            3.075    0.292   10.534    0.000    3.075    0.877
-##    .item42            2.051    0.322    6.376    0.000    2.051    0.687
-##    .item12            1.027    0.150    6.867    0.000    1.027    0.789
-##    .item11            1.543    0.172    8.957    0.000    1.543    0.928
-##    .item16            1.710    0.272    6.292    0.000    1.710    0.800
-##    .item19            0.886    0.131    6.783    0.000    0.886    0.539
-##    .item34            0.606    0.178    3.402    0.001    0.606    0.317
-##    .item2             1.229    0.150    8.214    0.000    1.229    0.621
-##     F1                0.086    0.036    2.376    0.017    1.000    1.000
-##     F2                0.735    0.145    5.067    0.000    1.000    1.000
-##     F3                1.667    0.246    6.771    0.000    1.000    1.000
-##     F4                0.433    0.228    1.902    0.057    1.000    1.000
-##     F5                0.757    0.162    4.668    0.000    1.000    1.000
-## 
-## R-Square:
-##                    Estimate
-##     item31            0.416
-##     item33            0.240
-##     item1             0.733
-##     item37            0.312
-##     item10            0.611
-##     item47            0.655
-##     item36            0.492
-##     item35            0.257
-##     item13            0.140
-##     item44            0.240
-##     item43            0.905
-##     item26            0.710
-##     item32            0.760
-##     item14            0.123
-##     item42            0.313
-##     item12            0.211
-##     item11            0.072
-##     item16            0.200
-##     item19            0.461
-##     item34            0.683
-##     item2             0.379
-\end{verbatim}
-
-\begin{verbatim}
-##               F1        F2        F3        F4        F5     total
-## alpha  0.7547222 0.4818562 0.9175522 0.5566040 0.7413266 0.5705737
-## omega  0.7047603 0.6261744 0.9185244 0.4777356 0.7527269 0.7006145
-## omega2 0.7047603 0.6261744 0.9185244 0.4777356 0.7527269 0.7006145
-## omega3 0.6939390 0.6265598 0.9183878 0.4742914 0.7572671 0.6879404
-## avevar 0.4397748 0.3749622 0.7902041 0.1887734 0.5081583 0.4058147
-\end{verbatim}
-
-\begin{verbatim}
-## lavaan 0.6-9 ended normally after 86 iterations
-## 
-##   Estimator                                         ML
-##   Optimization method                           NLMINB
-##   Number of model parameters                        91
-##                                                       
-##   Number of observations                           199
-##   Number of missing patterns                         1
-##                                                       
-## Model Test User Model:
-##                                                Standard      Robust
-##   Test Statistic                                312.650     319.502
-##   Degrees of freedom                                233         233
-##   P-value (Chi-square)                            0.000       0.000
-##   Scaling correction factor                                   0.979
-##        Yuan-Bentler correction (Mplus variant)                     
-## 
-## Model Test Baseline Model:
-## 
-##   Test statistic                              1718.830    1439.817
-##   Degrees of freedom                               276         276
-##   P-value                                        0.000       0.000
-##   Scaling correction factor                                  1.194
-## 
-## User Model versus Baseline Model:
-## 
-##   Comparative Fit Index (CFI)                    0.945       0.926
-##   Tucker-Lewis Index (TLI)                       0.935       0.912
-##                                                                   
-##   Robust Comparative Fit Index (CFI)                         0.939
-##   Robust Tucker-Lewis Index (TLI)                            0.928
-## 
-## Loglikelihood and Information Criteria:
-## 
-##   Loglikelihood user model (H0)              -6703.605   -6703.605
-##   Scaling correction factor                                  1.802
-##       for the MLR correction                                      
-##   Loglikelihood unrestricted model (H1)      -6547.280   -6547.280
-##   Scaling correction factor                                  1.210
-##       for the MLR correction                                      
-##                                                                   
-##   Akaike (AIC)                               13589.210   13589.210
-##   Bayesian (BIC)                             13888.900   13888.900
-##   Sample-size adjusted Bayesian (BIC)        13600.607   13600.607
-## 
-## Root Mean Square Error of Approximation:
-## 
-##   RMSEA                                          0.041       0.043
-##   90 Percent confidence interval - lower         0.028       0.031
-##   90 Percent confidence interval - upper         0.053       0.055
-##   P-value RMSEA <= 0.05                          0.885       0.830
-##                                                                   
-##   Robust RMSEA                                               0.043
-##   90 Percent confidence interval - lower                     0.030
-##   90 Percent confidence interval - upper                     0.054
-## 
-## Standardized Root Mean Square Residual:
-## 
-##   SRMR                                           0.065       0.065
-## 
-## Parameter Estimates:
-## 
-##   Standard errors                             Sandwich
-##   Information bread                           Observed
-##   Observed information based on                Hessian
-## 
-## Latent Variables:
-##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
-##   F1 =~                                                                 
-##     item31            1.000                               0.294    0.646
-##     item33            0.752    0.145    5.183    0.000    0.221    0.489
-##     item1             1.776    0.638    2.781    0.005    0.521    0.855
-##     item37            1.344    0.379    3.549    0.000    0.395    0.560
-##   F2 =~                                                                 
-##     item10            1.000                               0.830    0.757
-##     item47            0.899    0.124    7.268    0.000    0.747    0.821
-##     item36            0.997    0.151    6.609    0.000    0.828    0.714
-##     item35            0.766    0.147    5.201    0.000    0.636    0.509
-##     item13            0.398    0.119    3.347    0.001    0.330    0.303
-##     item44           -0.751    0.146   -5.135    0.000   -0.624   -0.499
-##   F3 =~                                                                 
-##     item43            1.000                               1.297    0.956
-##     item26            0.904    0.055   16.458    0.000    1.173    0.838
-##     item32            0.887    0.063   14.039    0.000    1.150    0.868
-##   F4 =~                                                                 
-##     item14            1.000                               0.632    0.337
-##     item42            1.476    0.486    3.039    0.002    0.932    0.540
-##     item12            0.855    0.351    2.437    0.015    0.540    0.474
-##     item11            0.595    0.375    1.586    0.113    0.376    0.292
-##     item16            1.088    0.568    1.916    0.055    0.687    0.470
-##   F5 =~                                                                 
-##     item19            1.000                               0.889    0.689
-##     item34            1.271    0.147    8.639    0.000    1.130    0.817
-##     item2             0.990    0.147    6.759    0.000    0.880    0.626
-##   F6 =~                                                                 
-##     item38            1.000                               0.526    0.388
-##     item28            2.058    3.153    0.653    0.514    1.083    0.737
-##     item45            1.518    0.693    2.192    0.028    0.799    0.512
-## 
-## Covariances:
-##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
-##  .item31 ~~                                                             
-##    .item33            0.070    0.026    2.680    0.007    0.070    0.513
-##  .item10 ~~                                                             
-##    .item13            0.218    0.098    2.213    0.027    0.218    0.293
-##  .item12 ~~                                                             
-##    .item11            0.694    0.153    4.549    0.000    0.694    0.560
-##  .item26 ~~                                                             
-##    .item19            0.179    0.072    2.487    0.013    0.179    0.250
-##   F1 ~~                                                                 
-##     F2                0.047    0.026    1.860    0.063    0.195    0.195
-##     F3               -0.008    0.035   -0.238    0.812   -0.022   -0.022
-##     F4                0.075    0.036    2.120    0.034    0.407    0.407
-##     F5                0.011    0.027    0.403    0.687    0.041    0.041
-##     F6                0.021    0.053    0.406    0.685    0.138    0.138
-##   F2 ~~                                                                 
-##     F3               -0.086    0.072   -1.181    0.237   -0.079   -0.079
-##     F4                0.094    0.084    1.116    0.265    0.179    0.179
-##     F5               -0.258    0.086   -3.002    0.003   -0.350   -0.350
-##     F6               -0.035    0.146   -0.240    0.810   -0.080   -0.080
-##   F3 ~~                                                                 
-##     F4                0.079    0.098    0.804    0.421    0.096    0.096
-##     F5               -0.039    0.105   -0.374    0.708   -0.034   -0.034
-##     F6               -0.025    0.132   -0.187    0.851   -0.036   -0.036
-##   F4 ~~                                                                 
-##     F5                0.087    0.076    1.133    0.257    0.154    0.154
-##     F6                0.081    0.054    1.488    0.137    0.243    0.243
-##   F5 ~~                                                                 
-##     F6                0.114    0.150    0.759    0.448    0.244    0.244
-## 
-## Intercepts:
-##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
-##    .item31            0.879    0.032   27.295    0.000    0.879    1.935
-##    .item33            0.869    0.032   27.150    0.000    0.869    1.925
-##    .item1             0.990    0.043   22.904    0.000    0.990    1.624
-##    .item37            0.995    0.050   19.900    0.000    0.995    1.411
-##    .item10            2.543    0.078   32.704    0.000    2.543    2.318
-##    .item47            2.035    0.065   31.553    0.000    2.035    2.237
-##    .item36            2.095    0.082   25.511    0.000    2.095    1.808
-##    .item35            2.070    0.089   23.362    0.000    2.070    1.656
-##    .item13            2.834    0.077   36.750    0.000    2.834    2.605
-##    .item44            2.995    0.089   33.796    0.000    2.995    2.396
-##    .item43            1.578    0.096   16.401    0.000    1.578    1.163
-##    .item26            1.482    0.100   14.868    0.000    1.482    1.060
-##    .item32            1.533    0.094   16.314    0.000    1.533    1.156
-##    .item14            3.020    0.133   22.749    0.000    3.020    1.613
-##    .item42            2.935    0.122   23.959    0.000    2.935    1.698
-##    .item12            2.005    0.081   24.793    0.000    2.005    1.758
-##    .item11            2.382    0.091   26.054    0.000    2.382    1.847
-##    .item16            3.211    0.104   30.991    0.000    3.211    2.197
-##    .item19            3.930    0.091   43.244    0.000    3.930    3.043
-##    .item34            3.583    0.098   36.558    0.000    3.583    2.592
-##    .item2             2.482    0.100   24.897    0.000    2.482    1.765
-##    .item38            2.201    0.096   22.896    0.000    2.201    1.623
-##    .item28            2.111    0.104   20.264    0.000    2.111    1.437
-##    .item45            2.432    0.111   21.981    0.000    2.432    1.558
-##     F1                0.000                               0.000    0.000
-##     F2                0.000                               0.000    0.000
-##     F3                0.000                               0.000    0.000
-##     F4                0.000                               0.000    0.000
-##     F5                0.000                               0.000    0.000
-##     F6                0.000                               0.000    0.000
-## 
-## Variances:
-##                    Estimate  Std.Err  z-value  P(>|z|)   Std.lv  Std.all
-##    .item31            0.120    0.034    3.520    0.000    0.120    0.583
-##    .item33            0.155    0.070    2.220    0.026    0.155    0.761
-##    .item1             0.100    0.087    1.155    0.248    0.100    0.269
-##    .item37            0.342    0.129    2.641    0.008    0.342    0.687
-##    .item10            0.513    0.131    3.925    0.000    0.513    0.427
-##    .item47            0.270    0.057    4.734    0.000    0.270    0.327
-##    .item36            0.657    0.096    6.878    0.000    0.657    0.490
-##    .item35            1.158    0.157    7.382    0.000    1.158    0.741
-##    .item13            1.075    0.103   10.395    0.000    1.075    0.908
-##    .item44            1.174    0.137    8.550    0.000    1.174    0.751
-##    .item43            0.160    0.091    1.757    0.079    0.160    0.087
-##    .item26            0.582    0.166    3.505    0.000    0.582    0.297
-##    .item32            0.434    0.114    3.813    0.000    0.434    0.247
-##    .item14            3.108    0.316    9.836    0.000    3.108    0.886
-##    .item42            2.116    0.334    6.345    0.000    2.116    0.709
-##    .item12            1.009    0.148    6.804    0.000    1.009    0.776
-##    .item11            1.522    0.190    8.005    0.000    1.522    0.915
-##    .item16            1.664    0.316    5.267    0.000    1.664    0.779
-##    .item19            0.877    0.132    6.664    0.000    0.877    0.526
-##    .item34            0.634    0.162    3.905    0.000    0.634    0.332
-##    .item2             1.203    0.151    7.993    0.000    1.203    0.608
-##    .item38            1.562    0.478    3.270    0.001    1.562    0.849
-##    .item28            0.985    1.584    0.622    0.534    0.985    0.456
-##    .item45            1.798    0.670    2.681    0.007    1.798    0.738
-##     F1                0.086    0.036    2.407    0.016    1.000    1.000
-##     F2                0.690    0.150    4.608    0.000    1.000    1.000
-##     F3                1.682    0.244    6.901    0.000    1.000    1.000
-##     F4                0.399    0.251    1.588    0.112    1.000    1.000
-##     F5                0.791    0.161    4.899    0.000    1.000    1.000
-##     F6                0.277    0.473    0.586    0.558    1.000    1.000
-## 
-## R-Square:
-##                    Estimate
-##     item31            0.417
-##     item33            0.239
-##     item1             0.731
-##     item37            0.313
-##     item10            0.573
-##     item47            0.673
-##     item36            0.510
-##     item35            0.259
-##     item13            0.092
-##     item44            0.249
-##     item43            0.913
-##     item26            0.703
-##     item32            0.753
-##     item14            0.114
-##     item42            0.291
-##     item12            0.224
-##     item11            0.085
-##     item16            0.221
-##     item19            0.474
-##     item34            0.668
-##     item2             0.392
-##     item38            0.151
-##     item28            0.544
-##     item45            0.262
-\end{verbatim}
-
-\begin{verbatim}
-##               F1        F2        F3        F4        F5        F6     total
-## alpha  0.7547222 0.4818562 0.9175522 0.5566040 0.7413266 0.5529540 0.5867087
-## omega  0.7047233 0.5882585 0.9176537 0.4814294 0.7559836 0.5718535 0.6975681
-## omega2 0.7047233 0.5882585 0.9176537 0.4814294 0.7559836 0.5718535 0.6975681
-## omega3 0.6939357 0.5880241 0.9123335 0.4801057 0.7686670 0.5694246 0.6768555
-## avevar 0.4396193 0.3689684 0.7883714 0.1875180 0.5116007 0.3247497 0.3906214
-\end{verbatim}
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
-Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
+\leavevmode\hypertarget{ref-R-papaja}{}%
+Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
 
-\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
-R Core Team. (2020). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+\leavevmode\hypertarget{ref-bakerBasicsItemResponse2017}{}%
+Baker, F. B. (2017). \emph{The {Basics} of {Item Response Theory Using R}} (1st ed. 2017.). {Springer}.
+
+\leavevmode\hypertarget{ref-bandalosFactorAnalysisExploratory2018}{}%
+Bandalos, D. L., \& Finney, S. J. (2018). Factor analysis: {Exploratory} and confirmatory. In \emph{The reviewer's guide to quantitative methods in the social sciences} (pp. 98--122). {Routledge}.
+
+\leavevmode\hypertarget{ref-R-tinylabels}{}%
+Barth, M. (2021). \emph{{tinylabels}: Lightweight variable labels}. Retrieved from \url{https://github.com/mariusbarth/tinylabels}
+
+\leavevmode\hypertarget{ref-bartlettNoteMultiplyingFactors1954}{}%
+Bartlett, M. (1954). A {Note} on the {Multiplying Factors} for {Various Chi}-square {Approximations}. \emph{Journal of the Royal Statistical Society. Series B, Methodological}, \emph{16}(2), 296--298.
+
+\leavevmode\hypertarget{ref-R-MOTE}{}%
+Buchanan, E.
+M., Gillenwaters, A., Scofield, J.
+E., \& Valentine, K.
+D.
+(2019).
+\emph{{MOTE: Measure of the Effect}: Package to assist in effect size calculations and their confidence intervals}.
+Retrieved from \url{http://github.com/doomlab/MOTE}
+
+\leavevmode\hypertarget{ref-cattellScreeTestNumber1966}{}%
+Cattell, R. B. (1966). The {Scree Test For The Number Of Factors}. \emph{Multivariate Behavioral Research}, \emph{1}(2), 245--276. \url{https://doi.org/10.1207/s15327906mbr0102_10}
+
+\leavevmode\hypertarget{ref-childEssentialsFactorAnalysis2006}{}%
+Child, D. (2006). \emph{Essentials of factor analysis} (3rd ed.). {New York: Continuum}.
+
+\leavevmode\hypertarget{ref-desjardinsHandbookEducationalMeasurement2018}{}%
+Desjardins, C., \& Bulut, O. (2018). \emph{Handbook of {Educational Measurement} and {Psychometrics Using R}}. \url{https://doi.org/10.1201/b20498}
+
+\leavevmode\hypertarget{ref-R-paran}{}%
+Dinno, A. (2018). \emph{Paran: Horn's test of principal components/factors}. Retrieved from \url{https://CRAN.R-project.org/package=paran}
+
+\leavevmode\hypertarget{ref-R-semPlot}{}%
+Epskamp, S. (2019). \emph{semPlot: Path diagrams and visual analysis of various SEM packages' output}. Retrieved from \url{https://CRAN.R-project.org/package=semPlot}
+
+\leavevmode\hypertarget{ref-R-qgraph}{}%
+Epskamp, S., Cramer, A.
+O.
+J., Waldorp, L.
+J., Schmittmann, V.
+D., \& Borsboom, D.
+(2012).
+{qgraph}: Network visualizations of relationships in psychometric data.
+\emph{Journal of Statistical Software}, \emph{48}(4), 1--18.
+
+\leavevmode\hypertarget{ref-furrPsychometricsIntroduction2014}{}%
+Furr, R. M. (2014). \emph{Psychometrics : An introduction} (2nd ed.). {Thousand Oaks}: {Thousand Oaks : SAGE}.
+
+\leavevmode\hypertarget{ref-R-purrr}{}%
+Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
+
+\leavevmode\hypertarget{ref-hornRationaleTestNumber1965}{}%
+Horn, J. L. (1965). A rationale and test for the number of factors in factor analysis. \emph{Psychometrika}, \emph{30}(2), 179--185. \url{https://doi.org/10.1007/BF02289447}
+
+\leavevmode\hypertarget{ref-hutchesonMultivariateSocialScientist1999}{}%
+Hutcheson, G. D. (1999). \emph{The multivariate social scientist : Introductory statistics using generalized linear models}. {London : SAGE}.
+
+\leavevmode\hypertarget{ref-R-DiagrammeRsvg}{}%
+Iannone, R. (2016). \emph{DiagrammeRsvg: Export DiagrammeR graphviz graphs as SVG}. Retrieved from \url{https://CRAN.R-project.org/package=DiagrammeRsvg}
+
+\leavevmode\hypertarget{ref-R-DiagrammeR}{}%
+Iannone, R. (2021). \emph{DiagrammeR: Graph/network visualization}. Retrieved from \url{https://github.com/rich-iannone/DiagrammeR}
+
+\leavevmode\hypertarget{ref-R-semTools}{}%
+Jorgensen, T.
+D., Pornprasertmanit, S., Schoemann, A.
+M., \& Rosseel, Y.
+(2021).
+\emph{\texttt{semTools}: {U}seful tools for structural equation modeling}.
+Retrieved from \url{https://CRAN.R-project.org/package=semTools}
+
+\leavevmode\hypertarget{ref-kaiserIndexFactorialSimplicity1974}{}%
+Kaiser, H. F. (1974). An index of factorial simplicity. \emph{Psychometrika}, \emph{39}(1), 31--36. \url{https://doi.org/10.1007/bf02291575}
+
+\leavevmode\hypertarget{ref-lorenzo-sevaHullMethodSelecting2011}{}%
+Lorenzo-Seva, U., Timmerman, M., \& Kiers, H.
+(2011).
+The {Hull Method} for {Selecting} the {Number} of {Common Factors}.
+\emph{Multivariate Behavioral Research}, \emph{46}, 340--364.
+\url{https://doi.org/10.1080/00273171.2011.564527}
+
+\leavevmode\hypertarget{ref-mardiaMeasuresMultivariateSkewness1970}{}%
+Mardia, K. V. (1970). Measures of multivariate skewness and kurtosis with applications. \emph{Biometrika}, \emph{57}(3), 519--530. \url{https://doi.org/10.1093/biomet/57.3.519}
+
+\leavevmode\hypertarget{ref-mulaikFoundationsFactorAnalysis2009}{}%
+Mulaik, S. A. (2009). \emph{Foundations of {Factor Analysis}} (Vol. 7). {London}: {London: Chapman and Hall/CRC}. \url{https://doi.org/10.1201/b15851}
+
+\leavevmode\hypertarget{ref-R-tibble}{}%
+Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
+
+\leavevmode\hypertarget{ref-R-EFA.MRFA}{}%
+Navarro-Gonzalez, D., \& Lorenzo-Seva, U. (2021). \emph{EFA.MRFA: Dimensionality assessment using minimum rank factor analysis}. Retrieved from \url{https://CRAN.R-project.org/package=EFA.MRFA}
+
+\leavevmode\hypertarget{ref-R-rsvg}{}%
+Ooms, J. (2021). \emph{Rsvg: Render SVG images into PDF, PNG, PostScript, or bitmap arrays}. Retrieved from \url{https://CRAN.R-project.org/package=rsvg}
+
+\leavevmode\hypertarget{ref-R-base}{}%
+R Core Team. (2021). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-R-psych}{}%
+Revelle, W.
+(2021).
+\emph{Psych: Procedures for psychological, psychometric, and personality research}.
+Evanston, Illinois: Northwestern University.
+Retrieved from \url{https://CRAN.R-project.org/package=psych}
+
+\leavevmode\hypertarget{ref-R-lavaan}{}%
+Rosseel, Y. (2012). {lavaan}: An {R} package for structural equation modeling. \emph{Journal of Statistical Software}, \emph{48}(2), 1--36. Retrieved from \url{https://www.jstatsoft.org/v48/i02/}
+
+\leavevmode\hypertarget{ref-R-dlookr}{}%
+Ryu, C. (2021). \emph{Dlookr: Tools for data diagnosis, exploration, transformation}. Retrieved from \url{https://CRAN.R-project.org/package=dlookr}
+
+\leavevmode\hypertarget{ref-shapiroAnalysisVarianceTest1965}{}%
+Shapiro, S. S., \& Wilk, M. B. (1965). An analysis of variance test for normality (complete samples). \emph{Biometrika}, \emph{52}(3-4), 591--611. \url{https://doi.org/10.1093/biomet/52.3-4.591}
+
+\leavevmode\hypertarget{ref-velicerDeterminingNumberComponents1976}{}%
+Velicer, W. (1976). Determining the {Number} of {Components} from the {Matrix} of {Partial Correlations}. \emph{Psychometrika}, \emph{41}, 321--327. \url{https://doi.org/10.1007/BF02293557}
+
+\leavevmode\hypertarget{ref-R-MASS}{}%
+Venables, W. N., \& Ripley, B. D. (2002). \emph{Modern applied statistics with s} (Fourth). New York: Springer. Retrieved from \url{https://www.stats.ox.ac.uk/pub/MASS4/}
+
+\leavevmode\hypertarget{ref-watkinsStepbyStepGuideExploratory2020}{}%
+Watkins, M. (2020). \emph{A {Step}-by-{Step Guide} to {Exploratory Factor Analysis} with {R} and {RStudio}}. \url{https://doi.org/10.4324/9781003120001}
+
+\leavevmode\hypertarget{ref-R-ggplot2}{}%
+Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
+
+\leavevmode\hypertarget{ref-R-stringr}{}%
+Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
+
+\leavevmode\hypertarget{ref-R-forcats}{}%
+Wickham, H. (2021a). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
+
+\leavevmode\hypertarget{ref-R-tidyr}{}%
+Wickham, H. (2021b). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
+
+\leavevmode\hypertarget{ref-R-tidyverse}{}%
+Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
+D., François, R., \ldots{} Yutani, H.
+(2019).
+Welcome to the {tidyverse}.
+\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
+\url{https://doi.org/10.21105/joss.01686}
+
+\leavevmode\hypertarget{ref-R-readxl}{}%
+Wickham, H., \& Bryan, J. (2019). \emph{Readxl: Read excel files}. Retrieved from \url{https://CRAN.R-project.org/package=readxl}
+
+\leavevmode\hypertarget{ref-R-dplyr}{}%
+Wickham, H., François, R., Henry, L., \& Müller, K. (2021). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
+
+\leavevmode\hypertarget{ref-R-readr}{}%
+Wickham, H., \& Hester, J. (2021). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
+
+\leavevmode\hypertarget{ref-R-kableExtra}{}%
+Zhu, H. (2021). \emph{kableExtra: Construct complex table with 'kable' and pipe syntax}. Retrieved from \url{https://CRAN.R-project.org/package=kableExtra}
 

### 2021-08-31 manuscript.Rmd

@@
 library(kableExtra)
+library(paran) # Parallel analysis
+library(EFA.MRFA) # Hull method
 library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
-library(DiagrammeRsvg)
-library(rsvg)
-r_refs("r-references.bib")
+library(DiagrammeRsvg) #For DiagrammeR
+library(rsvg) #For DiagrammeR
+r_refs("references.bib")
 ```
@@
 nocite: |
-  `r cite_r("r-references.bib")`
+  `r cite_r("references.bib")`
 ---
@@
 ```
+
+```{r setup-chunk, include=FALSE}
+knitr::opts_chunk$set(dev = "png",
+                      dpi = 300,
+                      echo = FALSE,
+                      cache = TRUE)
+```
+
 # Introduction
@@
 
-```{r flowchart }
+```{r flowchart, include=FALSE}
 Flowchart1 <- grViz("digraph nicegraph{
@@
 Second, to conduct an exploratory factor analysis(EFA)  to understand the latent structure.
-Third to gather structural validity evidence for the latent structure obtained in EFA.
-[@furrPsychometricsIntroduction2014]. Lastly, we gathered item information using Item response theory (IRT)[@bakerBasicsItemResponse2017]
+Third to gather structural validity evidence for the latent structure obtained in EFA [@furrPsychometricsIntroduction2014].
+Lastly, we gathered item information using Item response theory (IRT)[@bakerBasicsItemResponse2017]
 
@@
 # Results
-```{r Normality assumption EFA}
+```{r Normality assumption EFA, include=FALSE}
 LB <- read_excel("recoded not reversed_EFA.xlsx")
@@
 
-as.data.frame(upper)
 min.cor <- abs(min(upper)) #minimum cor.coefficient of the matrix
@@
 
-```{r figCor,fig.cap= "Iter-correlation of the items",results='asis'}
+```{r figCor,out.width="50%",fig.cap= "Iter-correlation of the items",results='asis'}
 
@@
 The corrected item-total correlations ranged between `r apa(low.r.corec,2,F)` to `r apa(high.r.corec,2,F)`.
+
+```{r factor_identification, eval=FALSE, include=FALSE}
+
+#correlations <- polychoric(LB.factor, correct = 0)
+
+# Parallel analysis
+ paran(correlations$rho, iterations=500, centile=0, quietly=FALSE,
+      status=TRUE, all=FALSE, cfa=FALSE, graph=TRUE,
+      color=TRUE, col=c("black","red","blue"),
+      lty=c(1,2,3), lwd=1, legend=TRUE, file="parallel.png",
+      width=640, height=640, grdevice=png, seed=0, mat=NA, n=NA)
+
+# HULL
+hullEFA(LB,extr = "ULS", index_hull = "CAF", display = TRUE, graph = TRUE,
+        details = TRUE)
+
+```
+
+Scree plot ( Fig\@ref(fig:fac.id)) suggested a six-factor solution.Horn's parallel analysis [@hornRationaleTestNumber1965], like the Monte Carlo study, draws several sets of random data with the same number of participants as the original data set and compares the mean eigenvalues among the simulated and original data sets to retain optimal factors.This extraction method also supported a five-factor model.
+In our data set parallel analysis with 500 iterations indicated six-factor solution.
+However, In MAP method [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] suggested a five-factor solution.
+
+```{r fac.id, out.height= "50%",  fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot, (C) Hull method', fig.show="hold",fig.ncol = 2, out.width="50%",  warning=FALSE}
+knitr::include_graphics('parallel.png')
+scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
+      hline=NULL,add=F)
+knitr::include_graphics('HUll method.png')
+
+```
 

### 2021-08-31 manuscript.Rmd

@@
 totR = length(LB)*(length(LB)-1)/2
-A <- print (BigR/totR)*100
+cor.per <- print (BigR/totR)*100
 
@@
 Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001] indicated the correlations between items are adequate for the EFA.
-However only `r apa(((BigR/totR)*100), 2,T)`% of the inter-item correlation coefficients were greater than .30 in the obtained matrix.
+However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than .30 in the obtained matrix.
 The inter item correlation ranged between `r apa(min.cor,2,F)` to `r apa(max.cor,2,F)`.
@@
 However, In MAP method [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] suggested a five-factor solution.
+As a result, we tested both five factor and six factor solutions.
 
@@
 
+```
+
+```{r EFA, include=FALSE}
+fa.5F.1 <- fa(r=correlations$rho, nfactors = 5, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+A <- print(fa.5F.1, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.5F.1 <- dplyr::select(LB ,
+                                    - c(item20,item17,item3, item15,item40, item4,item11, item39,
+                                        item18, item45, item29, item25, item8, item46 ))
+
+correlations.red.5F.1 <- polychoric(reduced.model.5F.1,correct = 0)
+
+fa.5F.2 <- fa(r=correlations.red.5F.1$rho, nfactors = 5, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+B <- print(fa.5F.2, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.5F.2 <- dplyr::select(LB,- c(item20,item17,item3, item15,item40, item4,item11, item39,
+                                           item18, item45, item29, item25, item8, item46,
+                                           item33, item12,item31, item37,
+                                           item22, item38, item6, item48))
+correlations.red.5F.2 <- polychoric(reduced.model.5F.2,correct = 0)
+
+fa.5F.3 <- fa(r=correlations.red.5F.2$rho, nfactors = 5, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+
+C <- print(fa.5F.3, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.5F.3 <- dplyr::select(LB,- c(item20,item17,item3, item15,item40, item4,item11, item39,
+                                           item18, item45, item29, item25, item8, item46,
+                                           item33, item12,item31, item37,
+                                           item22, item38, item6, item48, item9, item42,
+                                           item23))
+correlations.red.5F.3 <- polychoric(reduced.model.5F.3,correct = 0)
+
+fa.5F.4 <- fa(r=correlations.red.5F.3$rho, nfactors = 5, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+
+D <- print(fa.5F.4, cut = .3, digits = 3, sort = TRUE)
+
+```
+
+```{r TabEFA5, results='asis'}
+Fac.5 <- fa.5F.4 
+Factorloading <- cbind(Fac.5$loadings, Fac.5$communality)
+colnames(Factorloading)= c("F1", "F2","F3", "F4", "F5", "Communalities")
+apa_table(unclass(Factorloading))
+```
+
+```{r communalities, include=FALSE}
+min.com <- min(Fac.5$communality)
+max.com <- max(Fac.5$communality)
+```
+
+The initial five-factor solution with all 48 items showed the presence of cross-loading items (item 42, 16, & 1) and poor factor loading (<.30) items (item 20,3 ,15, 17, 40, 4, 11, 39, 18, 45, 29, 25, 8 , & 46).
+At first we discard the items with poor  factor loading and ran another EFA on the remaining 34 items.
+This iteration of EFA also appeared as a misfit in terms of poor factor loading (Item 12, 22, 38, 6) and cross-loading (items 23, 31, 37, 48) .
+Another two rounds of EFA were conducted with gradually identifying problematic items and discarding them from the model.
+Finally, a five-factor EFA solution with 23 items was accepted with RMSR = 0.04, no loading smaller than .30 and no cross-loading greater than .30.
+The communalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`.
+The histogram of the absolute values of non-redundant residual-correlations showed  correlations greater than the absolute value of .05 is ------[@desjardinsHandbookEducationalMeasurement2018a].
+```{r FivRes, out.height= "50%",  fig.align='center', fig.cap=' Residulas of five-dactor solution'}
+residual.5F =residuals(fa.5F.4, diag = FALSE, na.rm =T)
+hist(residual.5F, col ="red", main = NULL, xlab = "Five factor oblique rotation: Residuals",ylim=c(0, 300))
+abline(h =48, lwd = 2, lty = 2)
+abline(v =.05,lwd = 2, lty = 2)
 ```

### 2021-08-31 manuscript.tex

@@
 In our data set parallel analysis with 500 iterations indicated six-factor solution.
-However, In MAP method (Velicer, 1976) and Hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) suggested a five-factor solution Parallel analysis is also more immune to the normality assumptions violation(\textbf{RN1263?}).
+However, In MAP method (Velicer, 1976) and Hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) suggested a five-factor solution.
+As a result, we tested both five factor and six factor solutions.
+The histogram of the absolute values of non-redundant residual-correlations the proportion of non-redundant residual correlations greater than the absolute value of .05 should be small
 
@@
 \caption{Factor Identification (A) Parallel analysis (B) Scree Plot, (C) Hull method}(\#fig:fac.id)
+\end{figure}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:TabEFA5}}
+
+\begin{tabular}{lllllll}
+\toprule
+ & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{F2} & \multicolumn{1}{c}{F3} & \multicolumn{1}{c}{F4} & \multicolumn{1}{c}{F5} & \multicolumn{1}{c}{Communalities}\\
+\midrule
+item1 & 0.06 & -0.03 & 0.01 & 0.03 & 0.35 & 0.13\\
+item2 & 0.12 & -0.10 & -0.11 & 0.69 & -0.03 & 0.51\\
+item5 & 0.01 & 0.16 & 0.09 & 0.01 & 0.69 & 0.52\\
+item7 & 0.06 & -0.09 & 0.66 & -0.01 & -0.03 & 0.45\\
+item10 & -0.01 & 0.82 & 0.07 & 0.02 & 0.02 & 0.68\\
+item13 & -0.06 & 0.34 & -0.03 & 0.10 & 0.00 & 0.13\\
+item14 & 0.00 & 0.05 & 0.89 & -0.08 & -0.08 & 0.81\\
+item16 & 0.10 & 0.05 & 0.29 & -0.11 & 0.31 & 0.21\\
+item19 & 0.02 & -0.06 & 0.00 & 0.80 & 0.03 & 0.64\\
+item21 & -0.05 & -0.02 & -0.34 & 0.03 & -0.06 & 0.12\\
+item24 & -0.03 & 0.10 & 0.10 & 0.11 & 0.54 & 0.33\\
+item26 & 0.93 & 0.00 & 0.13 & -0.01 & 0.13 & 0.90\\
+item27 & -0.01 & 0.07 & 0.38 & -0.12 & 0.21 & 0.21\\
+item28 & 0.02 & 0.00 & -0.05 & 0.01 & 0.31 & 0.10\\
+item30 & 0.06 & 0.01 & 0.11 & -0.04 & 0.52 & 0.29\\
+item32 & 0.80 & 0.00 & 0.05 & 0.13 & 0.10 & 0.67\\
+item34 & -0.01 & -0.14 & 0.02 & 0.84 & 0.12 & 0.74\\
+item35 & -0.04 & 0.46 & 0.04 & -0.17 & 0.04 & 0.25\\
+item36 & 0.09 & 0.63 & 0.10 & -0.15 & 0.11 & 0.45\\
+item41 & 0.05 & 0.07 & 0.70 & 0.30 & 0.14 & 0.60\\
+item43 & 0.99 & 0.00 & 0.06 & 0.01 & 0.03 & 0.99\\
+item44 & -0.03 & -0.47 & -0.01 & 0.10 & 0.01 & 0.24\\
+item47 & 0.02 & 0.82 & -0.05 & -0.06 & 0.16 & 0.70\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+The initial five-factor solution with all 48 items showed the presence of cross-loading items (item 42, 16, \& 1) and poor factor loading (\textless.30) items (item 20,3 ,15, 17, 40, 4, 11, 39, 18, 45, 29, 25, 8 , \& 46).
+At first we discard the items with poor factor loading and ran another EFA on the remaining 34 items.
+This iteration of EFA also appeared as a misfit in terms of poor factor loading (Item 12, 22, 38, 6) and cross-loading (items 23, 31, 37, 48) .
+Another two rounds of EFA were conducted with gradually identifying problematic items and discarding them from the model.
+Finally, a five-factor EFA solution with 23 items was accepted with RMSR = 0.04, no loading smaller than .30 and no cross-loading greater than .30.
+
+\begin{figure}
+
+{\centering \includegraphics[height=0.5\textheight]{manuscript_files/figure-latex/FivRes-1}
+
+}
+
+\caption{ Residulas of five-dactor solution}\label{fig:FivRes}
 \end{figure}
@@
 Cattell, R. B. (1966). The {Scree Test For The Number Of Factors}. \emph{Multivariate Behavioral Research}, \emph{1}(2), 245--276. \url{https://doi.org/10.1207/s15327906mbr0102_10}
+
+\leavevmode\hypertarget{ref-R-shiny}{}%
+Chang, W., Cheng, J., Allaire, J., Sievert, C., Schloerke, B., Xie, Y., \ldots{} Borges, B.
+(2021).
+\emph{Shiny: Web application framework for r}.
+Retrieved from \url{https://CRAN.R-project.org/package=shiny}
 

### 2021-08-31 manuscript.Rmd

@@
 library(rsvg) #For DiagrammeR
+library(correlation)
+library(ggcorrplot)
 r_refs("references.bib")
@@
 PA is apparently robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020].
-The obtained latent structure was confirmed by weighted least squares (WLS) extraction method as well.
+The obtained latent structure was confirmed by minimum residuals extraction method as well.
 We used a combination factor indentification method including scree plot[@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method[@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
@@
 
-qgraph(correlations$rho, cut =.30, details =T, posCol = "green", negCol = "orangered3", 
-       labels = names(LB))
+ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower")
+#p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
+#to show pvalue in the fig add p.mat=p.mat
 ```
@@
               residuals = TRUE, SMC = TRUE, n.obs =428)
-A <- print(fa.5F.1, cut = .3, digits = 3, sort = TRUE)
+AA <- print(fa.5F.1, cut = .3, digits = 3, sort = TRUE)
 
@@
               residuals = TRUE, SMC = TRUE, n.obs =428)
-B <- print(fa.5F.2, cut = .3, digits = 3, sort = TRUE)
+BB <- print(fa.5F.2, cut = .3, digits = 3, sort = TRUE)
 
@@
 
-C <- print(fa.5F.3, cut = .3, digits = 3, sort = TRUE)
+CC <- print(fa.5F.3, cut = .3, digits = 3, sort = TRUE)
 
@@
 
-D <- print(fa.5F.4, cut = .3, digits = 3, sort = TRUE)
+DD <- print(fa.5F.4, cut = .3, digits = 3, sort = TRUE)
 
@@
 
-```{r TabEFA5, results='asis'}
+```{r include=FALSE}
+fa.diagram(fa.5F.4,sort=TRUE,labels=NULL,flabels=NULL,cut=.3,
+                 simple=TRUE,errors=F,
+                 digits=1,e.size=.1,rsize=3,side=2,main= "Five Factor Solution Oblique",cex=NULL,color.lines=TRUE,
+                 marg=c(.5,.5,1.5,.5),adj=2) 
+```
+
+```{r minres 5 factor supplimentary analyisis, eval=FALSE, include=FALSE}
+fa.5F.min.1 <- fa(r=correlations$rho, nfactors = 5, fm= "minres",rotate ="varimax",
+                residuals = TRUE, SMC = TRUE, n.obs =428)
+EE <- print(fa.5F.min.1, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.5F.min.1 <- dplyr::select(LB ,
+                                    - c(item20,item17,item3, item15,item40, item4,item11, item39,
+                                        item18, item45, item29, item25, item8, item46 ))
+
+correlations.red.5F.min.1 <- polychoric(reduced.model.5F.min.1,correct = 0)
+
+fa.5F.min.2 <- fa(r=correlations.red.5F.min.1$rho, nfactors = 5, fm= "minres",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+FF <- print(fa.5F.min.2, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.5F.min.2 <- dplyr::select(LB,- c(item20,item17,item3, item15,item40, item4,item11, item39,
+                                           item18, item45, item29, item25, item8, item46,
+                                           item33, item12,item31, item37,
+                                           item22, item38, item6, item48))
+
+correlations.red.5F.min.2 <- polychoric(reduced.model.5F.min.2, correct = 0)
+
+fa.5F.min.3 <- fa(r=correlations.red.5F.min.2$rho, nfactors = 5, fm= "minres",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+
+GG <- print(fa.5F.min.3, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.5F.min.3 <- dplyr::select(LB,- c(item20,item17,item3, item15,item40, item4,item11, item39,
+                                               item18, item45, item29, item25, item8, item46,
+                                               item33, item12,item31, item37,
+                                               item22, item38, item6, item48,
+                                               item9, item42, item23))
+correlations.red.5F.min.3 <- polychoric(reduced.model.5F.min.3,correct = 0)
+
+fa.5F.min.4 <- fa(r=correlations.red.5F.min.3$rho, nfactors = 5, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+
+HH <- print(fa.5F.min.4, cut = .3, digits = 3, sort = TRUE)
+
+```
+
+```{r EFA 6 Factors Promax, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, results='hide', width=}
+#LB.factor <- sapply(LB, as.factor)
+#correlations <- polychoric(LB.factor, correct = 0)
+
+fa.6F.1 <- fa(r=correlations$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+II <- print(fa.6F.1, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.6F.1 <- dplyr::select(LB ,
+                                    -c(item15, item17, item40, item4, item3, item46, item8,item29, item25 ))
+
+correlations.red.6F.1 <- polychoric(reduced.model.6F.1,correct = 0)
+
+fa.6F.2 <- fa(r=correlations.red.6F.1$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+JJ <- print(fa.6F.2, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.6F.2 <- dplyr::select(LB,-c(item15, item17, item40, item4, item3, item46, item8,item29, item25, item9, item33, item48, item16, item6 ))
+
+correlations.red.6F.2 <- polychoric(reduced.model.6F.2,correct = 0)
+
+fa.6F.3 <- fa(r=correlations.red.6F.2$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+
+KK <- print(fa.6F.3, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.6F.3 <- dplyr::select(LB,- -c(item15, item17, item40, item4, item3, item46, item8,item29, item25, item9, item33, item48, item16, item6, item11, item23, item18, item39))
+
+correlations.red.6F.3 <- polychoric(reduced.model.6F.3,correct = 0)
+
+fa.6F.4 <- fa(r=correlations.red.6F.3$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)
+
+LL <- print(fa.6F.4, cut = .3, digits = 3, sort = TRUE)
+
+# Residuals
+residual.6F =residuals(fa.6F.4 , diag = FALSE, na.rm =T)
+#Count of numbers of residuals>.05
+BigRRR= sum(residual.6F>abs(.05), na.rm =T)
+print(BigRRR)
+
+#Total number of off diagonal elements in the data matrix
+totRRR = length(reduced.model.6F.3)*(length(reduced.model.6F.3)-1)/2
+
+# Proportion of off-diagonal elements >.10
+sumRRR <- sum(BigRRR/totRRR*100)
+
+hist(residual.6F, col ="red", main = NULL, xlab = "Five factor oblique rotation: Residuals",ylim=c(0, 250))
+abline(h =27, lwd = 2, lty = 2)
+abline(v =.05,lwd = 2, lty = 2)
+```
+
+```{r factordetails, include=FALSE}
 Fac.5 <- fa.5F.4 
+#Commonality
+min.com <- min(Fac.5$communality)
+max.com <- max(Fac.5$communality)
+
+# factor loadings
+
 Factorloading <- cbind(Fac.5$loadings, Fac.5$communality)
 colnames(Factorloading)= c("F1", "F2","F3", "F4", "F5", "Communalities")
-apa_table(unclass(Factorloading))
-```
 
-```{r communalities, include=FALSE}
-min.com <- min(Fac.5$communality)
-max.com <- max(Fac.5$communality)
+min.loadings <- abs(min(Fac.5$loadings))
+max.loadings <- max(Fac.5$loadings)
+
+# Residuals
+residual.5F =residuals(fa.5F.4, diag = FALSE, na.rm =T)
+#Count of numbers of residuals>.05
+BigRR= sum(residual.5F>abs(.05), na.rm =T)
+print(BigRR)
+
+#Total number of off diagonal elements in the data matrix
+totRR = length(reduced.model.5F.3)*(length(reduced.model.5F.3)-1)/2
+
+# Proportion of off-diagonal elements >.10
+sumR <- sum(BigRR/totRR*100)
+
 ```
@@
 Another two rounds of EFA were conducted with gradually identifying problematic items and discarding them from the model.
-Finally, a five-factor EFA solution with 23 items was accepted with RMSR = 0.04, no loading smaller than .30 and no cross-loading greater than .30.
-The communalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`.
-The histogram of the absolute values of non-redundant residual-correlations showed  correlations greater than the absolute value of .05 is ------[@desjardinsHandbookEducationalMeasurement2018a].
-```{r FivRes, out.height= "50%",  fig.align='center', fig.cap=' Residulas of five-dactor solution'}
-residual.5F =residuals(fa.5F.4, diag = FALSE, na.rm =T)
-hist(residual.5F, col ="red", main = NULL, xlab = "Five factor oblique rotation: Residuals",ylim=c(0, 300))
-abline(h =48, lwd = 2, lty = 2)
+Finally, a five-factor EFA solution with 23 items was accepted with low RMSR = 0.04, no loading smaller than .30 and no cross-loading greater than .30.
+The latent construct was also confirmed by using minimum residual  extraction method (see the supplementary).
+Table\@ref(tab:tabEFA5) displays the structural coefficients and commonality of the items.
+The absolute value of the structural coefficients ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients.
+The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`.
+However, the histogram of the absolute values of non-redundant residual-correlations (Fig\@ref(fig:Residuals) showed `r apa(sumR,2, T)`% correlations greater than the absolute value of .05, indicating under-factoring.
+[@desjardinsHandbookEducationalMeasurement2018a].
+Subsequently, we fitted a six-factor solution.
+However, in the six factor solution a factor emerged with only two salient variable loading thus disqualifying the six-factor solution.
+
+In the five
+
+```{r TabEFA5, results='asis'}
+
+apa_table(unclass(Factorloading))
+```
+
+```{r Residuals, out.height= "50%",  fig.align='center', fig.cap=' Histogram of residulas:  five-factor solution,  out.width="50%",  warning=FALSE'}
+hist(residual.5F, col ="red", main = NULL, xlab = "Five-factor solution", ylim=c(0, 250))
+abline(h =47, lwd = 2, lty = 2)
 abline(v =.05,lwd = 2, lty = 2)
+
 ```

### 2021-08-31 manuscript.tex

@@
 PA is apparently robust to the normality assumption violations (Watkins, 2020).
-The obtained latent structure was confirmed by weighted least squares (WLS) extraction method as well.
+The obtained latent structure was confirmed by minimum residuals extraction method as well.
 We used a combination factor indentification method including scree plot(Cattell, 1966), Horn's parallel analysis (Horn, 1965), minimum average partials method(Velicer, 1976), and hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) to identify factor numbers.
@@
 As a result, we tested both five factor and six factor solutions.
-The histogram of the absolute values of non-redundant residual-correlations the proportion of non-redundant residual correlations greater than the absolute value of .05 should be small
 
@@
 \end{figure}
+
+The initial five-factor solution with all 48 items showed the presence of cross-loading items (item 42, 16, \& 1) and poor factor loading (\textless.30) items (item 20,3 ,15, 17, 40, 4, 11, 39, 18, 45, 29, 25, 8 , \& 46).
+At first we discard the items with poor factor loading and ran another EFA on the remaining 34 items.
+This iteration of EFA also appeared as a misfit in terms of poor factor loading (Item 12, 22, 38, 6) and cross-loading (items 23, 31, 37, 48) .
+Another two rounds of EFA were conducted with gradually identifying problematic items and discarding them from the model.
+Finally, a five-factor EFA solution with 23 items was accepted with low RMSR = 0.04, no loading smaller than .30 and no cross-loading greater than .30.
+The latent construct was also confirmed by using minimum residual extraction method (see the supplementary).
+Table\ref{tab:tabEFA5} displays the structural coefficients and commonality of the items.
+The absolute value of the structural coefficients ranged from .47 to .99 indicating strong coefficients.
+The commonalities ranged between .10 to .99.
+However, the histogram of the absolute values of non-redundant residual-correlations showed 26.09\% correlations greater than the absolute value of .05, indicating under factoring.
+(\textbf{desjardinsHandbookEducationalMeasurement2018a?}).
 
@@
 \end{table}
-
-The initial five-factor solution with all 48 items showed the presence of cross-loading items (item 42, 16, \& 1) and poor factor loading (\textless.30) items (item 20,3 ,15, 17, 40, 4, 11, 39, 18, 45, 29, 25, 8 , \& 46).
-At first we discard the items with poor factor loading and ran another EFA on the remaining 34 items.
-This iteration of EFA also appeared as a misfit in terms of poor factor loading (Item 12, 22, 38, 6) and cross-loading (items 23, 31, 37, 48) .
-Another two rounds of EFA were conducted with gradually identifying problematic items and discarding them from the model.
-Finally, a five-factor EFA solution with 23 items was accepted with RMSR = 0.04, no loading smaller than .30 and no cross-loading greater than .30.
 

### 2021-08-31 manuscript.Rmd

@@
 title             : "_Light Exposure Behavior Assessment (LEBA)_: Develop of a novel instrument to capture light exposure-related behaviours"
-shorttitle        : "Title"
+shorttitle        : "LEBA"
 
@@
       - Data Visualization
-  - name          : "Manuel Spitschan "
-    affiliation   : "3"
-    corresponding : yes   
-    address       : ""
-    email         : ""
-    role:         
-      - Data Analysis
-      - Writing - Original Draft Preparation
-      - Data Visualization
-
   - name          : "Manuel Spitschan "
@@
 
-bibliography      : ["r-references.bib"]
+bibliography      : ["references.bib"]
 
@@
 output            : papaja::apa6_pdf
+
 ---
@@
 
-```{r flowchart, include=FALSE}
+```{r flowchart, include=FALSE, out.height= "100%", out.width= "100%"}
 Flowchart1 <- grViz("digraph nicegraph{
@@
 
-Scree plot ( Fig\@ref(fig:fac.id)) suggested a six-factor solution.Horn's parallel analysis [@hornRationaleTestNumber1965], like the Monte Carlo study, draws several sets of random data with the same number of participants as the original data set and compares the mean eigenvalues among the simulated and original data sets to retain optimal factors.This extraction method also supported a five-factor model.
+Scree plot ( Fig\@ref(fig:facid)) suggested a six-factor solution.Horn's parallel analysis [@hornRationaleTestNumber1965], like the Monte Carlo study, draws several sets of random data with the same number of participants as the original data set and compares the mean eigenvalues among the simulated and original data sets to retain optimal factors.This extraction method also supported a five-factor model.
 In our data set parallel analysis with 500 iterations indicated six-factor solution.
@@
 
-```{r fac.id, out.height= "50%",  fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot, (C) Hull method', fig.show="hold",fig.ncol = 2, out.width="50%",  warning=FALSE}
+```{r facid, out.height= "50%",  fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot, (C) Hull method', fig.show="hold",fig.ncol = 2, out.width="50%",  warning=FALSE}
 knitr::include_graphics('parallel.png')
@@
 
-```{r EFA 6 Factors Promax, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, results='hide', width=}
+```{r EFA 6 Factors Promax, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, results='hide'}
 #LB.factor <- sapply(LB, as.factor)
@@
 
-In the five
-
 ```{r TabEFA5, results='asis'}
@@
 
-```{r Residuals, out.height= "50%",  fig.align='center', fig.cap=' Histogram of residulas:  five-factor solution,  out.width="50%",  warning=FALSE'}
+```{r Residuals, out.height= "50%",  fig.align='center', fig.cap= ' Histogram of residulas:  five-factor solution',  out.width="50%",  warning=FALSE}
 hist(residual.5F, col ="red", main = NULL, xlab = "Five-factor solution", ylim=c(0, 250))

### 2021-08-31 manuscript.Rmd

@@
 output            : papaja::apa6_pdf
-
+fontfamily        : arev
 ---
@@
 knitr::opts_chunk$set(dev = "png",
-                      dpi = 300,
+                      dpi = 600,
                       echo = FALSE,
                       cache = TRUE)
+
 ```
@@
 
-```{r flowchart, include=FALSE, out.height= "100%", out.width= "100%"}
+```{r flowchart, include=FALSE }
 Flowchart1 <- grViz("digraph nicegraph{
@@
 
-```{r, out.height= "50%",  fig.align='center', fig.cap='ABC'}
+```{r,  out.width = '100%', out.height= '100%', fig.align = 'center', fig.cap='ABC'}
 knitr::include_graphics('Flowchart1.png')
@@
 Second, to conduct an exploratory factor analysis(EFA)  to understand the latent structure.
-Third to gather structural validity evidence for the latent structure obtained in EFA [@furrPsychometricsIntroduction2014].
+Third to gather structural validity evidence for the latent structure obtained in EFA.
 Lastly, we gathered item information using Item response theory (IRT)[@bakerBasicsItemResponse2017]
@@
 ```{r tabDes, results='asis'}
-apa_table(Des.combined, caption = "Descriptive Statistics")
+apa_table(Des.combined, caption = "Descriptive Statistics", align = "c", longtable = TRUE)
 ```
@@
 The initial five-factor solution with all 48 items showed the presence of cross-loading items (item 42, 16, & 1) and poor factor loading (<.30) items (item 20,3 ,15, 17, 40, 4, 11, 39, 18, 45, 29, 25, 8 , & 46).
-At first we discard the items with poor  factor loading and ran another EFA on the remaining 34 items.
-This iteration of EFA also appeared as a misfit in terms of poor factor loading (Item 12, 22, 38, 6) and cross-loading (items 23, 31, 37, 48) .
+At first we discarded the items with poor  factor loading and ran another EFA on the remaining 34 items.
+This iteration of EFA also appeared as a misfit in terms of poor factor-loading (Item 12, 22, 38, 6) and cross-loading (items 23, 31, 37, 48) .
 Another two rounds of EFA were conducted with gradually identifying problematic items and discarding them from the model.
 Finally, a five-factor EFA solution with 23 items was accepted with low RMSR = 0.04, no loading smaller than .30 and no cross-loading greater than .30.
-The latent construct was also confirmed by using minimum residual  extraction method (see the supplementary).
-Table\@ref(tab:tabEFA5) displays the structural coefficients and commonality of the items.
-The absolute value of the structural coefficients ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients.
+The obtained latent construct was also confirmed by using minimum residual  extraction method (see the supplementary).
+Table\@ref(tab:tabEFA5) displays the factor loadin (structural coefficients) and commonality of the items.
+The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients.
 The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`.

### 2021-08-31 manuscript.Rmd

@@
 ---
-
-```{r analysis-preferences}
-# Seed for random number generation
-set.seed(42)
-knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
-```
 
@@
 normality <- normality(LB) 
+normalityprefix <- apa(normality$statistic, 2,T)
+normalitysufix <- "*"
+normality.names <- paste(normalityprefix,normalitysufix, sep = "" )
 
@@
 
-Des.combined <- cbind(apa(Descriptives$mean,2,T), apa(Descriptives$sd,2,T), apa(Descriptives$skew,2,T),apa(Descriptives$kurtosis,2,T), apa(normality$statistic,2,T), apa(normality$p_value,2,F), apa(Item.total$r.cor,2,F))
+Des.combined <- cbind(apa(Descriptives$mean,2,T), apa(Descriptives$sd,2,T), apa(Descriptives$skew,2,T),apa(Descriptives$kurtosis,2,T), normality.names,  apa(Item.total$r.cor,2,F))
 
-colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics", "p", "Item-Total Correlation")
+colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics", "Item-Total Correlation")
 
@@
 ```{r tabDes, results='asis'}
-apa_table(Des.combined, caption = "Descriptive Statistics", align = "c", longtable = TRUE)
+apa_table(Des.combined, caption = "Descriptive Statistics", align = "c", note = "*p<.001", longtable =T)
 ```
@@
 The obtained latent construct was also confirmed by using minimum residual  extraction method (see the supplementary).
-Table\@ref(tab:tabEFA5) displays the factor loadin (structural coefficients) and commonality of the items.
+Table\@ref(tab:tabEFA5) displays the factor-loading (structural coefficients) and commonality of the items.
 The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients.

### 2021-09-01 manuscript.Rmd

@@
 
-```{r figCor,out.width="50%",fig.cap= "Iter-correlation of the items",results='asis'}
+```{r figCor,out.width="50%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}
 
@@
 
-```{r include=FALSE}
-fa.diagram(fa.5F.4,sort=TRUE,labels=NULL,flabels=NULL,cut=.3,
-                 simple=TRUE,errors=F,
-                 digits=1,e.size=.1,rsize=3,side=2,main= "Five Factor Solution Oblique",cex=NULL,color.lines=TRUE,
-                 marg=c(.5,.5,1.5,.5),adj=2) 
+```{r EFAplotcode, include=FALSE}
+#library(DiagrammeR)
+EFAplot.LR <- grViz("
+digraph boxes_and_circles {
+
+graph [layout = dot,rankdir = LR, fontsize = 40]
+
+# node definitions with substituted label text
+node [fontname = Helvetica, shape = circle,  margin = 0.5, width = 3.5, height = .5,
+fixedsize = true, fontsize = 35]
+F1 [label = 'Blue 
+Filter']
+F2 [label = 'Natural 
+Light']
+F3 [label = 'Sleep
+Environment']
+F4 [label = 'Cell Phone']
+F5 [label = 'Awareness']
+node [fontname = Helvetica, shape = box]
+b [label = 'item43']
+c [label = 'item26']
+d [label = 'item32']
+e [label = 'item10']
+f [label = 'item47']
+g [label = 'item36']
+h [label = 'item44']
+i [label = 'item35']
+j [label = 'item13']
+k [label = 'item14']
+l [label = 'item41']
+m [label = 'item7']
+n [label = 'item27']
+o [label = 'item21']
+p [label = 'item34']
+q [label = 'item19']
+r [label = 'item2']
+s [label = 'item5']
+t [label = 'item24']
+u [label = 'item30']
+v [label = 'item1']
+w [label = 'item16']
+x [label = 'item28']
+
+{rank = same; F1 F2 F3 F4 F5}
+# edge definitions with the node IDs
+edge [fontname = Helvetica, fontsize = 35]
+F1 -> b[label = '0.99']
+F1-> c [label = '0.93']
+F1-> d [label = '0.80']
+F2 -> e [label = '0.82']
+F2 -> f[label = '0.82']
+F2 -> g [label = '0.63']
+F2 -> h[ label = '-0.47', color =red]
+F2 -> i [label = '0.46']
+F2 -> j [label = '0.34']
+F3 -> k [label = '0.89']
+F3 -> l [label = '0.70']
+F3 -> m [label = '0.66']
+F3 -> n [label = '0.38']
+F3 -> o [label = '-0.34', color =red]
+F4 -> p [label = '0.84']
+F4 -> q [label = '0.80']
+F4 -> r [label = '0.69']
+F5 -> s [label = '0.69']
+F5 -> t [label = '0.54']
+F5 -> u [label = '0.52']
+F5 -> v [label = '0.35']
+F5 -> w [label = '0.31']
+F5 -> x [label = '0.31']
+
+}
+")
+
+export_svg(EFAplot.LR) %>%
+  charToRaw() %>%
+  rsvg() %>%
+  png::writePNG("EFAplot.LR.png")
+
+```
+
+```{r EFAplot,  fig.cap='Five Factor Solution', fig.align='center', out.width= "120%", out.height= "100%", warning=FALSE}
+knitr::include_graphics('EFAplot.LR.png')
+
 ```
@@
 ```{r minres 5 factor supplimentary analyisis, eval=FALSE, include=FALSE}
+
+#Supplementary EFA with Minres Extraction
+
 fa.5F.min.1 <- fa(r=correlations$rho, nfactors = 5, fm= "minres",rotate ="varimax",
@@
 ```{r EFA 6 Factors Promax, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, results='hide'}
+# EFA with 6 factor (rejected)
+
 #LB.factor <- sapply(LB, as.factor)
@@
 ```{r factordetails, include=FALSE}
+#Preparing the EFA table
+
+factor.des = matrix(, nrow = 24, ncol = 6)
+as.table(factor.des)
+rownames(factor.des) <- c("item43", "item26",  "item32",   
+                          "item10",  "item47",  "item36", "item44",  "item35",  "item13", 
+                          "item14", "item41",  "item7","item27","item21",
+                          "item34", "item19", "item2",
+                          "item5", "item24", "item30", "item1", "item16", "item28","% of variance")
+
+colnames(factor.des) <- c("F1", "F2", "F3", "F4", "F5", "Communality")
+
+factor.des[,1] <- c(.99, .93, .80, "-","-","-","-","-","-","-","-","-","-","-","-",
+                    "-","-","-","-","-","-","-","-", 11)
+
+factor.des[,2] <- c("-", "-", "-", .82,.82,.63,-.47,.46,.34,"-","-","-","-","-","-",
+                    "-","-","-","-","-","-","-","-", 10)
+
+factor.des[,3] <- c("-", "-", "-", "-","-","-","-","-","-",.89,.70,.66,.38,-.34,"-",
+                    "-","-","-","-","-","-","-","-", 9)
+
+factor.des[,4] <- c("-", "-", "-", "-","-","-","-","-","-","-","-","-","-","-",.84,
+                    .80,.67,"-","-","-","-","-","-", 9)
+
+factor.des[,5] <- c("-", "-", "-", "-","-","-","-","-","-","-","-","-","-","-","-","-","-"
+                    ,.69,.54,.52,.35,.31,.31, 6)
+
+factor.des[,6] <- c (.99, .90,.67,.68,.70,.45,.24,.24,.13,.81,.60,.45,.21,.12,.74,.64,.54,
+                     .51,.33,.29,.13,.21,.10, "-")
+
+#Commonality
 Fac.5 <- fa.5F.4
-#Commonality
 min.com <- min(Fac.5$communality)
@@
 
-# factor loadings
-
-Factorloading <- cbind(Fac.5$loadings, Fac.5$communality)
-colnames(Factorloading)= c("F1", "F2","F3", "F4", "F5", "Communalities")
-
-min.loadings <- abs(min(Fac.5$loadings))
+# loadings
+min.loadings <- min(Fac.5$loadings)
 max.loadings <- max(Fac.5$loadings)
@@
 
-apa_table(unclass(Factorloading))
+apa_table(factor.des,align = "c", note = "Only loading higher than .30 is reported")
 ```

### 2021-09-01 manuscript.Rmd

@@
 
-This line is just a test for pushing in the github repo.
+1. Describe EFA and CFA sample separately.
+2. Sampling technique: Convince sampling (non-probability sample)
+3. Method: cross-sectional survey
+4. How many missing data?
+5. How incomplete data were addressed.
+6. Why such sample was chosen?
 
-## Material
+EFA: For exploring initial factor structure, a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]
+
+CFA: For estimating the sample size for the confirmatory factor analysis we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006] where 10 participants per parameters is required to earn trustworthiness of the result.
+Our sample size exceeds the requirement.
+
+## Procedure
+### Development of the Scale
+1. How the items were generated
+2. How the literature was reviewed to identify construct adequacy of the items.
+3. Discuss the expert panel review process to assess content validity
 
@@
 
-```{r,  out.width = '100%', out.height= '100%', fig.align = 'center', fig.cap='ABC'}
+```{r,  out.width = '100%', out.height= '100%', fig.align = 'center', fig.cap='Development and psychometric properties of LEBA '}
 knitr::include_graphics('Flowchart1.png')
@@
 Our study had four objectives.
-First, to develop an instrument to assess individual's light exposure behavior .
+First, to develop an instrument to assess an individual's light exposure behavior.
 Second, to conduct an exploratory factor analysis(EFA)  to understand the latent structure.
-Third to gather structural validity evidence for the latent structure obtained in EFA.
+The third one is to gather structural validity evidence for the latent structure obtained in EFA.
 Lastly, we gathered item information using Item response theory (IRT)[@bakerBasicsItemResponse2017]
@@
 ### Data Collection
-Timeline of data collection, ethical approval, mode of data collection, how consent was recorded.
-
-### Item generation and Content Validity: Expert Panel Review
-How we developed the 48 items?
+Timeline of data collection, 
+ethical approval
+mode of data collection
+how consent was recorded.
 
@@
 
-We used R (version 4.1.0), including several R-packages for our analyses.
-Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix were assessed.
+We used R (version 4.1.0), including several R packages, for our analyses.
+Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
 Our data violated both the univariate and multivariate normality assumptions.
-Due to these violations and the  ordinal nature of our response data we used polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA.
+Due to these violations and the ordinal nature of our response data, we used a polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA.
 We employed principal axis (pa) a factor extraction method with varimax rotation.
-PA is apparently robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020].
-The obtained latent structure was confirmed by minimum residuals extraction method as well.
-We used a combination factor indentification method including scree plot[@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method[@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
-Additionally, to identify the simple structure we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018; @childEssentialsFactorAnalysis2006; @mulaikFoundationsFactorAnalysis2009; @watkinsStepbyStepGuideExploratory2020]
+PA is robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020].
+The obtained latent structure was confirmed by the minimum residuals extraction method as well.
+We used a combination factor identification method including scree plot[@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method[@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
+Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018;
 
 # Results
+
 ```{r Normality assumption EFA, include=FALSE}
@@
 
-Sampling adequacy was investigated by Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy[@kaiserIndexFactorialSimplicity1974] .
-The overall KMO vale for 23 items was `r printnum(KMO$MSA)` which was above the cutoff value of .50 indicating a mediocre sample [@hutchesonMultivariateSocialScientist1999].
+Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy[@kaiserIndexFactorialSimplicity1974] .
+The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cutoff value (.50) indicating a mediocre sample [@hutchesonMultivariateSocialScientist1999].
 
@@
 some of the items were skewed with high Kurtosis values.
-The Shapiro-Wilk test of normality [@shapiroAnalysisVarianceTest1965] indicated all the items violated normality assumptions.
-Multivariate normality assumptions were investigated by Marida's test [@mardiaMeasuresMultivariateSkewness1970].
-Multivariate skew = `r printnum(mardia$b1p)` (p <0.001) and multivariate kurtosis = `r printnum(mardia$b2p)` (p <0.001) indicated  multivariate normality assumptions violation.
+Our data violated both univariate normality (Shapiro-Wilk statistics; [@shapiroAnalysisVarianceTest1965]) and multivariate normality assumptions (Marida's test;[@mardiaMeasuresMultivariateSkewness1970]).
+Multivariate skew was  = `r printnum(mardia$b1p)` (p <0.001) and multivariate kurtosis was = `r printnum(mardia$b2p)` (p <0.001).
 Due to these violations and ordinal nature of the response data  polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018].
 Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001] indicated the correlations between items are adequate for the EFA.
-However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than .30 in the obtained matrix.
+However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than .30.
 The inter item correlation ranged between `r apa(min.cor,2,F)` to `r apa(max.cor,2,F)`.
-The corrected item-total correlations ranged between `r apa(low.r.corec,2,F)` to `r apa(high.r.corec,2,F)`.
+And the corrected item-total correlations ranged between `r apa(low.r.corec,2,F)` to `r apa(high.r.corec,2,F)`.
 
@@
 
-Scree plot ( Fig\@ref(fig:facid)) suggested a six-factor solution.Horn's parallel analysis [@hornRationaleTestNumber1965], like the Monte Carlo study, draws several sets of random data with the same number of participants as the original data set and compares the mean eigenvalues among the simulated and original data sets to retain optimal factors.This extraction method also supported a five-factor model.
-In our data set parallel analysis with 500 iterations indicated six-factor solution.
-However, In MAP method [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] suggested a five-factor solution.
-As a result, we tested both five factor and six factor solutions.
+Scree plot ( Figure \@ref(fig:facid)) suggested a six-factor solution.
+Horn's parallel analysis [@hornRationaleTestNumber1965] with 500 iterations also indicated a six-factor solution.
+However, the MAP method [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] suggested a five-factor solution.
+As a result, we tested both five-factor and six-factor solutions.
 
@@
 Filter']
-F2 [label = 'Natural 
-Light']
+F2 [label = 'Outdoor']
 F3 [label = 'Sleep
@@
 
+```
+
+```{r Cronbach alpha for 5 fators, message=TRUE, warning=FALSE, include=FALSE}
+Five.F1 <- dplyr::select(LB, item43, item26, item32)
+Five.F2 <- dplyr::select(LB, item10, item47, item36, item44, item35, item13) 
+Five.F3 <-  dplyr::select(LB, item14, item41,item7, item27, item21)
+Five.F4 <-  dplyr::select(LB, item19,item34,item2)
+Five.F5 <- dplyr::select(LB, item5, item24, item30, item1, item16, item28)
+
+Five.F1.alpha <- psych::alpha(Five.F1, check.keys = T) 
+Five.F2.alpha <- psych::alpha(Five.F2, check.keys = T)
+Five.F3.alpha <- psych::alpha(Five.F3, check.keys = T)
+Five.F4.alpha <- psych::alpha(Five.F4, check.keys = T) 
+Five.F5.alpha <- psych::alpha(Five.F5, check.keys = T) 
 ```
@@
 #Preparing the EFA table
-
-factor.des = matrix(, nrow = 24, ncol = 6)
+factor.des = matrix(, nrow = 25, ncol = 6)
 as.table(factor.des)
@@
                           "item34", "item19", "item2",
-                          "item5", "item24", "item30", "item1", "item16", "item28","% of variance")
+                          "item5", "item24", "item30", "item1", "item16", "item28", "internal Consistency","% of variance")
 
@@
 factor.des[,1] <- c(.99, .93, .80, "-","-","-","-","-","-","-","-","-","-","-","-",
-                    "-","-","-","-","-","-","-","-", 11)
+                    "-","-","-","-","-","-","-","-",apa(Five.F1.alpha$total[,1],2,F), 11)
 
 factor.des[,2] <- c("-", "-", "-", .82,.82,.63,-.47,.46,.34,"-","-","-","-","-","-",
-                    "-","-","-","-","-","-","-","-", 10)
+                    "-","-","-","-","-","-","-","-",apa(Five.F2.alpha$total[,1],2,F), 10)
 
 factor.des[,3] <- c("-", "-", "-", "-","-","-","-","-","-",.89,.70,.66,.38,-.34,"-",
-                    "-","-","-","-","-","-","-","-", 9)
+                    "-","-","-","-","-","-","-","-", apa(Five.F3.alpha$total[,1],2,F),9)
 
 factor.des[,4] <- c("-", "-", "-", "-","-","-","-","-","-","-","-","-","-","-",.84,
-                    .80,.67,"-","-","-","-","-","-", 9)
+                    .80,.67,"-","-","-","-","-","-",apa(Five.F4.alpha$total[,1],2,F), 9)
 
 factor.des[,5] <- c("-", "-", "-", "-","-","-","-","-","-","-","-","-","-","-","-","-","-"
-                    ,.69,.54,.52,.35,.31,.31, 6)
+                    ,.69,.54,.52,.35,.31,.31,apa(Five.F5.alpha$total[,1],2,F), 6)
 
 factor.des[,6] <- c (.99, .90,.67,.68,.70,.45,.24,.24,.13,.81,.60,.45,.21,.12,.74,.64,.54,
-                     .51,.33,.29,.13,.21,.10, "-")
+                     .51,.33,.29,.13,.21,.10, "-", "-")
 
@@
 
-The initial five-factor solution with all 48 items showed the presence of cross-loading items (item 42, 16, & 1) and poor factor loading (<.30) items (item 20,3 ,15, 17, 40, 4, 11, 39, 18, 45, 29, 25, 8 , & 46).
-At first we discarded the items with poor  factor loading and ran another EFA on the remaining 34 items.
-This iteration of EFA also appeared as a misfit in terms of poor factor-loading (Item 12, 22, 38, 6) and cross-loading (items 23, 31, 37, 48) .
+The initial five-factor solution with all 48 items showed presence of cross-loading items (item 42, 16, & 1) and poor factor loading (<.30) items (item 20, 3 ,15, 17, 40, 4, 11, 39, 18, 45, 29, 25, 8 , & 46).
+At first, we discarded the items with poor factor-loading and ran another EFA on the remaining 34 items.
+This iteration of EFA also appeared as a misfit with items with poor factor-loading (Item 12, 22, 38, 6) and cross-loading (items 23, 31, 37, 48) .
 Another two rounds of EFA were conducted with gradually identifying problematic items and discarding them from the model.
-Finally, a five-factor EFA solution with 23 items was accepted with low RMSR = 0.04, no loading smaller than .30 and no cross-loading greater than .30.
-The obtained latent construct was also confirmed by using minimum residual  extraction method (see the supplementary).
-Table\@ref(tab:tabEFA5) displays the factor-loading (structural coefficients) and commonality of the items.
+Finally, a five-factor EFA solution with 23 items was accepted with low RMSR = 0.04 [@brownConfirmatoryFactorAnalysis2015], all factor-loading higher than .30 and no cross-loading greater than .30.
+We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (see the supplementary).
+Table\@ref(tab:TabEFA5) displays the factor-loading (structural coefficients) and communality of the items.
 The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients.
@@
 Subsequently, we fitted a six-factor solution.
-However, in the six factor solution a factor emerged with only two salient variable loading thus disqualifying the six-factor solution.
+However, a factor emerged with only two salient variable loading in the six-factor solution, thus disqualifying the six-factor solution.
+
+In the five-factor solution, the first factor contained three items and explained 11% of the total variance with a satisfactory internal reliability coefficient ($\alpha$ =.86).
+All the items in this factor stemmed from the individual's preference to use blue light filters in different light environments.
+The second factor contained six items and explained 10% of the total variance with a satisfactory internal reliability coefficient ($\alpha$ =.71).
+Items under this factor commonly investigate an individual's hours spent outdoor.
+The third factor contained five items and explained 9% of the total variance.
+Items under this factor dealt with the specific behaviors pertaining to sleep.
+However, the internal consistency reliability coefficient was not satisfactory ($\alpha$ =.62).
+The fourth factor contained three items and explained 9% of the total variance with a satisfactory internal consistency ($\alpha$ =.77).
+These three items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time.
+Lastly, the fifth factor contained six items and explained 6% of the total variance.
+Under this factor tried to measure an individual's behavior lead by the awareness of light's influence on health.
+However, this factor showed unsatisfactory internal consistency reliability ($\alpha$ =.49).
+It is essential to attain a balance between psychometric properties and the interpretability of the common themes when exploring the latent structure.
+As all of the emerged factors are highly interpretable, regardless of the apparent low reliability of the two factors,  we retain the five-factor solution with 23 items for our confirmatory factor analysis (CFA).
+Two items showed negative factor-loading (items 44 and 21).
+Upon inspection, it was understood that these items are negatively correlated to the common theme, and thus in the CFA analysis, we reversed the response code for these two items.
 
@@
 LB.cfa <- read_excel("recoded not reversed_CFA.xlsx")
-LB.model.Cor <- "F1 =~ item5 + item24 + item30 + item1 + item16 + item28
+LB.model.Cor <- "F1 =~ item43 + item26 + item32
              F2 =~ item10 + item47 + item36 + item44 + item35 + item13
-            F3 =~ item43 + item26 + item32
-           F4 =~  item14 + item41+ item7 + item27 + item21
-            F5 =~ item19 + item34 + item2"
+            F3 =~  item14 + item41+ item7 + item27 + item21
+            F4 =~ item19 + item34 + item2
+F5 =~ item5 + item24 + item30 + item1 + item16 + item28"
 
@@
 ```{r CFA23withMI, include=FALSE}
-LB.model.Cor.3 <- "F1 =~ item5 + item24 + item30 + item1 + item16 + item28
+LB.model.Cor.3 <- "F1 =~ item43 + item26 + item32
              F2 =~ item10 + item47 + item36 + item44 + item35 + item13
-            F3 =~ item43 + item26 + item32
-           F4 =~  item14 + item41+ item7 + item27 + item21
-            F5 =~ item19 + item34 + item2
+            F3 =~  item14 + item41+ item7 + item27 + item21
+            F4 =~ item19 + item34 + item2
+F5 =~ item5 + item24 + item30 + item1 + item16 + item28 
 item44 ~~ item13
@@
 ```{r CFI18items, include=FALSE}
-LB.model.Cor.2 <- "F1 =~ item5 + item24 + item30 + item16 
+LB.model.Cor.2 <- "F1 =~ item43 + item26 + item32
              F2 =~ item10 + item47 + item36 + item44 + item35 
-            F3 =~ item43 + item26 + item32
-           F4 =~  item14 + item41+ item7 
-            F5 =~ item19 + item34 + item2
+            F3 =~  item14 + item41+ item7 
+            F4 =~ item19 + item34 + item2
+F5 =~ item5 + item24 + item30 + item16 
 item14 ~~  item7"
 
-#item 1 &28 discarded from F1;
+#item 1 &28 discarded from F5;
 #item13 discarded from F2
-#item 27 & 21 discarded from F4
+#item 27 & 21 discarded from F3
 
@@
 
+## IRT
+
 # Discussion

### 2021-09-01 manuscript.tex

--- 2021-08-31 manuscript.tex
@@
 \usepackage{amsmath,amssymb}
-\usepackage{lmodern}
+\usepackage[]{arev}
 \usepackage{ifxetex,ifluatex}
@@
   pdftitle={Light Exposure Behavior Assessment (LEBA): Develop of a novel instrument to capture light exposure-related behaviours},
-  pdfauthor={Mushfiqul Anwar Siraji1, Rafael Robert Lazar2, Manuel Spitschan3, \& Manuel Spitschan3},
+  pdfauthor={Mushfiqul Anwar Siraji1, Rafael Robert Lazar2, \& Manuel Spitschan3},
   pdflang={en-EN},
@@
 \makeatother
-\shorttitle{Title}
+\shorttitle{LEBA}
 \keywords{keywords\newline\indent Word count: X}
@@
 \title{\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours}
-\author{Mushfiqul Anwar Siraji\textsuperscript{1}, Rafael Robert Lazar\textsuperscript{2}, Manuel Spitschan\textsuperscript{3}, \& Manuel Spitschan\textsuperscript{3}}
+\author{Mushfiqul Anwar Siraji\textsuperscript{1}, Rafael Robert Lazar\textsuperscript{2}, \& Manuel Spitschan\textsuperscript{3}}
 \date{}
@@
 The authors made the following contributions.
-Mushfiqul Anwar Siraji: Data Analysis, Writing - Original Draft Preparation, Data Visualization; Rafael Robert Lazar: Data Analysis, Writing - Original Draft Preparation, Data Visualization; Manuel Spitschan: Data Analysis, Writing - Original Draft Preparation, Data Visualization; Manuel Spitschan: Data Analysis, Writing - Original Draft Preparation, Data Visualization.
+Mushfiqul Anwar Siraji: Data Analysis, Writing - Original Draft Preparation, Data Visualization; Rafael Robert Lazar: Data Analysis, Writing - Original Draft Preparation, Data Visualization; Manuel Spitschan: Data Analysis, Writing - Original Draft Preparation, Data Visualization.
 
@@
 
-This line is just a test for pushing in the github repo.
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Describe EFA and CFA sample separately.
+\item
+  Sampling technique: Convince sampling (non-probability sample)
+\item
+  Method: cross-sectional survey
+\item
+  How many missing data?
+\item
+  How incomplete data were addressed.
+\item
+  Why such sample was chosen?
+\end{enumerate}
 
-\hypertarget{material}{%
-\subsection{Material}\label{material}}
+EFA: For exploring initial factor structure, a sample of 250-300 is recommended (Comrey \& Lee, 1992; Schönbrodt \& Perugini, 2013)
 
-\begin{figure}
-
-{\centering \includegraphics[width=4.17in,height=0.5\textheight]{Flowchart1}
-
-}
-
-\caption{ABC}\label{fig:unnamed-chunk-1}
-\end{figure}
+CFA: For estimating the sample size for the confirmatory factor analysis we followed the N:q rule (Bentler \& Chou, 1987; Jackson, 2003; Kline, 2015; Worthington \& Whittaker, 2006) where 10 participants per parameters is required to earn trustworthiness of the result.
+Our sample size exceeds the requirement.
 
@@
 
+\hypertarget{development-of-the-scale}{%
+\subsubsection{Development of the Scale}\label{development-of-the-scale}}
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  How the items were generated
+\item
+  How the literature was reviewed to identify construct adequacy of the items.
+\item
+  Discuss the expert panel review process to assess content validity
+\end{enumerate}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth,height=1\textheight]{Flowchart1}
+
+}
+
+\caption{Development and psychometric properties of LEBA }\label{fig:unnamed-chunk-1}
+\end{figure}
+
+\hypertarget{procedure-1}{%
+\subsection{Procedure}\label{procedure-1}}
+
 Our study had four objectives.
-First, to develop an instrument to assess individual's light exposure behavior .
+First, to develop an instrument to assess an individual's light exposure behavior.
 Second, to conduct an exploratory factor analysis(EFA) to understand the latent structure.
-Third to gather structural validity evidence for the latent structure obtained in EFA (Furr, 2014).
+The third one is to gather structural validity evidence for the latent structure obtained in EFA.
 Lastly, we gathered item information using Item response theory (IRT)(Baker, 2017)
@@
 
-Timeline of data collection, ethical approval, mode of data collection, how consent was recorded.
-
-\hypertarget{item-generation-and-content-validity-expert-panel-review}{%
-\subsubsection{Item generation and Content Validity: Expert Panel Review}\label{item-generation-and-content-validity-expert-panel-review}}
-
-How we developed the 48 items?
+Timeline of data collection,
+ethical approval
+mode of data collection
+how consent was recorded.
 
@@
 
-We used R (version 4.1.0), including several R-packages for our analyses.
-Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix were assessed.
+We used R (version 4.1.0), including several R packages, for our analyses.
+Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
 Our data violated both the univariate and multivariate normality assumptions.
-Due to these violations and the ordinal nature of our response data we used polychoric correlation matrix (Desjardins \& Bulut, 2018) for the EFA.
+Due to these violations and the ordinal nature of our response data, we used a polychoric correlation matrix (C.
+Desjardins \& Bulut, 2018) for the EFA.
 We employed principal axis (pa) a factor extraction method with varimax rotation.
-PA is apparently robust to the normality assumption violations (Watkins, 2020).
-The obtained latent structure was confirmed by weighted least squares (WLS) extraction method as well.
-We used a combination factor indentification method including scree plot(Cattell, 1966), Horn's parallel analysis (Horn, 1965), minimum average partials method(Velicer, 1976), and hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) to identify factor numbers.
-Additionally, to identify the simple structure we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \textless0.3 (iii) no items with cross-loading greater than .3 across factors (Bandalos \& Finney, 2018; Child, 2006; Mulaik, 2009; Watkins, 2020)
+PA is robust to the normality assumption violations (Watkins, 2020).
+The obtained latent structure was confirmed by the minimum residuals extraction method as well.
+We used a combination factor identification method including scree plot(Cattell, 1966), Horn's parallel analysis (Horn, 1965), minimum average partials method(Velicer, 1976), and hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) to identify factor numbers.
+Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \textless0.3 (iii) no items with cross-loading greater than .3 across factors {[}Bandalos and Finney (2018);
 
@@
 
-Sampling adequacy was investigated by Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy(Kaiser, 1974) .
-The overall KMO vale for 23 items was 0.63 which was above the cutoff value of .50 indicating a mediocre sample (Hutcheson, 1999).
+Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy(Kaiser, 1974) .
+The overall KMO vale for 48 items was 0.63 which was above the cutoff value (.50) indicating a mediocre sample (Hutcheson, 1999).
+
+\begin{center}
+\begin{ThreePartTable}
+
+\begin{TableNotes}[para]
+\normalsize{\textit{Note.} *p<.001}
+\end{TableNotes}
+
+\begin{longtable}{ccccccc}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:tabDes}Descriptive Statistics}\\
+\toprule
+ & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{Item-Total Correlation}\\
+\midrule
+\endfirsthead
+\caption*{\normalfont{Table \ref{tab:tabDes} continued}}\\
+\toprule
+ & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{Item-Total Correlation}\\
+\midrule
+\endhead
+Item1 & 1.12 & 0.49 & 5.02 & 27.80 & 0.25* & .16\\
+Item2 & 2.16 & 1.19 & 0.71 & -0.54 & 0.84* & .14\\
+Item3 & 4.14 & 0.99 & -1.23 & 1.14 & 0.79* & .19\\
+Item4 & 2.87 & 1.59 & 0.08 & -1.60 & 0.83* & .19\\
+Item5 & 1.76 & 1.23 & 1.35 & 0.44 & 0.66* & .38\\
+Item6 & 2.73 & 1.46 & 0.20 & -1.36 & 0.87* & .33\\
+Item7 & 3.86 & 1.67 & -0.99 & -0.85 & 0.65* & .23\\
+Item8 & 3.76 & 1.14 & -0.68 & -0.45 & 0.86* & .00\\
+Item9 & 3.42 & 1.83 & -0.45 & -1.69 & 0.69* & .33\\
+Item10 & 2.74 & 1.04 & 0.09 & -0.74 & 0.91* & .28\\
+Item11 & 2.60 & 1.25 & 0.29 & -0.86 & 0.89* & .35\\
+Item12 & 2.11 & 1.17 & 0.77 & -0.39 & 0.83* & .32\\
+Item13 & 2.94 & 1.03 & -0.12 & -0.40 & 0.91* & .10\\
+Item14 & 3.62 & 1.64 & -0.68 & -1.25 & 0.74* & .32\\
+Item15 & 1.64 & 1.18 & 1.79 & 2.02 & 0.60* & .15\\
+Item16 & 3.51 & 1.30 & -0.70 & -0.59 & 0.85* & .39\\
+Item17 & 1.96 & 0.98 & 1.02 & 0.69 & 0.82* & .05\\
+Item18 & 2.44 & 1.31 & 0.38 & -1.14 & 0.86* & .11\\
+Item19 & 3.80 & 1.29 & -0.87 & -0.42 & 0.82* & .17\\
+Item20 & 4.01 & 1.40 & -1.22 & 0.07 & 0.70* & .13\\
+Item21 & 1.33 & 0.91 & 3.03 & 8.43 & 0.41* & .01\\
+Item22 & 2.59 & 1.41 & 0.27 & -1.27 & 0.86* & .19\\
+Item23 & 1.31 & 0.81 & 2.75 & 6.92 & 0.43* & .21\\
+Item24 & 1.47 & 1.18 & 2.38 & 4.00 & 0.43* & .28\\
+Item25 & 2.56 & 1.27 & 0.33 & -1.00 & 0.89* & .11\\
+Item26 & 1.54 & 1.25 & 2.13 & 2.86 & 0.46* & .36\\
+Item27 & 4.30 & 1.08 & -1.79 & 2.53 & 0.67* & .22\\
+Item28 & 2.27 & 1.39 & 0.74 & -0.81 & 0.81* & .25\\
+Item29 & 3.26 & 1.09 & -0.26 & -0.45 & 0.91* & .14\\
+Item30 & 2.22 & 1.48 & 0.71 & -1.02 & 0.76* & .30\\
+Item31 & 1.05 & 0.36 & 7.23 & 52.98 & 0.13* & .18\\
+Item32 & 1.54 & 1.21 & 2.07 & 2.75 & 0.49* & .31\\
+Item33 & 1.04 & 0.33 & 8.99 & 85.28 & 0.10* & .16\\
+Item34 & 3.36 & 1.38 & -0.48 & -1.03 & 0.87* & .16\\
+Item35 & 2.26 & 1.25 & 0.70 & -0.60 & 0.85* & .19\\
+Item36 & 2.36 & 1.22 & 0.59 & -0.62 & 0.87* & .25\\
+Item37 & 1.14 & 0.59 & 4.79 & 24.05 & 0.25* & .16\\
+Item38 & 2.25 & 1.27 & 0.69 & -0.64 & 0.84* & .18\\
+Item39 & 3.93 & 1.48 & -1.06 & -0.44 & 0.71* & .18\\
+Item40 & 3.57 & 1.07 & -0.65 & -0.17 & 0.88* & .21\\
+Item41 & 3.55 & 1.65 & -0.60 & -1.34 & 0.76* & .43\\
+Item42 & 3.00 & 1.62 & -0.08 & -1.61 & 0.83* & .44\\
+Item43 & 1.56 & 1.23 & 2.00 & 2.45 & 0.50* & .32\\
+Item44 & 2.97 & 1.20 & -0.06 & -0.94 & 0.91* & -.10\\
+Item45 & 2.79 & 1.55 & 0.19 & -1.48 & 0.85* & .20\\
+Item46 & 2.14 & 1.31 & 0.77 & -0.78 & 0.80* & .26\\
+Item47 & 2.18 & 0.90 & 0.60 & 0.12 & 0.86* & .26\\
+Item48 & 1.48 & 1.11 & 2.18 & 3.35 & 0.48* & .24\\
+\bottomrule
+\addlinespace
+\insertTableNotes
+\end{longtable}
+
+\end{ThreePartTable}
+\end{center}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.5\linewidth]{manuscript_files/figure-latex/figCor-1}
+
+}
+
+\caption{Correlation plot of the items}\label{fig:figCor}
+\end{figure}
+
+Table\ref{tab:tabDes} summarizes the univariate descriptive statistics for the 48 items.
+some of the items were skewed with high Kurtosis values.
+Our data violated both univariate normality (Shapiro-Wilk statistics; (Shapiro \& Wilk, 1965)) and multivariate normality assumptions (Marida's test;(Mardia, 1970)).
+Multivariate skew was = 583.80 (p \textless0.001) and multivariate kurtosis was = 2,749.15 (p \textless0.001).
+Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen (C.
+Desjardins \& Bulut, 2018).
+Bartlett's test of sphericity (Bartlett, 1954), \(\chi^2\) (1128) = 5042.86, p \textless{} .001{]} indicated the correlations between items are adequate for the EFA.
+However only 4.96\% of the inter-item correlation coefficients were greater than .30.
+The inter item correlation ranged between .44 to .91.
+And the corrected item-total correlations ranged between .10 to .44.
+
+Scree plot ( Figure \ref{fig:facid}) suggested a six-factor solution.
+Horn's parallel analysis (Horn, 1965) with 500 iterations also indicated a six-factor solution.
+However, the MAP method (Velicer, 1976) and Hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) suggested a five-factor solution.
+As a result, we tested both five-factor and six-factor solutions.
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{parallel} \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/facid-2} \includegraphics[width=0.5\linewidth,height=0.5\textheight]{HUll method}
+
+}
+
+\caption{Factor Identification (A) Parallel analysis (B) Scree Plot, (C) Hull method}\label{fig:facid}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1.2\linewidth,height=1\textheight]{EFAplot.LR}
+
+}
+
+\caption{Five Factor Solution}\label{fig:EFAplot}
+\end{figure}
+
+The initial five-factor solution with all 48 items showed presence of cross-loading items (item 42, 16, \& 1) and poor factor loading (\textless.30) items (item 20, 3 ,15, 17, 40, 4, 11, 39, 18, 45, 29, 25, 8 , \& 46).
+At first, we discarded the items with poor factor-loading and ran another EFA on the remaining 34 items.
+This iteration of EFA also appeared as a misfit with items with poor factor-loading (Item 12, 22, 38, 6) and cross-loading (items 23, 31, 37, 48) .
+Another two rounds of EFA were conducted with gradually identifying problematic items and discarding them from the model.
+Finally, a five-factor EFA solution with 23 items was accepted with low RMSR = 0.04 (Brown, 2015), all factor-loading higher than .30 and no cross-loading greater than .30.
+We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (see the supplementary).
+Table\ref{tab:TabEFA5} displays the factor-loading (structural coefficients) and communality of the items.
+The absolute value of the factor-loading ranged from -.47 to .99 indicating strong coefficients.
+The commonalities ranged between .10 to .99.
+However, the histogram of the absolute values of non-redundant residual-correlations (Fig\ref{fig:Residuals} showed 26.09\% correlations greater than the absolute value of .05, indicating under-factoring.
+(C.
+D.
+Desjardins, 2018).
+Subsequently, we fitted a six-factor solution.
+However, a factor emerged with only two salient variable loading in the six-factor solution, thus disqualifying the six-factor solution.
+
+In the five-factor solution, the first factor contained three items and explained 11\% of the total variance with a satisfactory internal reliability coefficient (\(\alpha\) =.86).
+All the items in this factor stemmed from the individual's preference to use blue light filters in different light environments.
+The second factor contained six items and explained 10\% of the total variance with a satisfactory internal reliability coefficient (\(\alpha\) =.71).
+Items under this factor commonly investigate an individual's hours spent outdoor.
+The third factor contained five items and explained 9\% of the total variance.
+Items under this factor dealt with the specific behaviors pertaining to sleep.
+However, the internal consistency reliability coefficient was not satisfactory (\(\alpha\) =.62).
+The fourth factor contained three items and explained 9\% of the total variance with a satisfactory internal consistency (\(\alpha\) =.77).
+These three items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time.
+Lastly, the fifth factor contained six items and explained 6\% of the total variance.
+Under this factor tried to measure an individual's behavior lead by the awareness of light's influence on health.
+However, this factor showed unsatisfactory internal consistency reliability (\(\alpha\) =.49).
+It is essential to attain a balance between psychometric properties and the interpretability of the common themes when exploring the latent structure.
+As all of the emerged factors are highly interpretable, regardless of the apparent low reliability of the two factors, we retain the five-factor solution with 23 items for our confirmatory factor analysis (CFA).
+Two items showed negative factor-loading (items 44 and 21).
+Upon inspection, it was understood that these items are negatively correlated to the common theme, and thus in the CFA analysis, we reversed the response code for these two items.
 
@@
 
-\caption{\label{tab:tabDes}Descriptive Statistics}
+\caption{\label{tab:TabEFA5}}
 
-\begin{tabular}{llllllll}
+\begin{tabular}{ccccccc}
 \toprule
- & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{p} & \multicolumn{1}{c}{Item-Total Correlation}\\
+ & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{F2} & \multicolumn{1}{c}{F3} & \multicolumn{1}{c}{F4} & \multicolumn{1}{c}{F5} & \multicolumn{1}{c}{Communality}\\
 \midrule
-Item1 & 1.12 & 0.49 & 5.02 & 27.80 & 0.25 & .00 & .16\\
-Item2 & 2.16 & 1.19 & 0.71 & -0.54 & 0.84 & .00 & .14\\
-Item3 & 4.14 & 0.99 & -1.23 & 1.14 & 0.79 & .00 & .19\\
-Item4 & 2.87 & 1.59 & 0.08 & -1.60 & 0.83 & .00 & .19\\
-Item5 & 1.76 & 1.23 & 1.35 & 0.44 & 0.66 & .00 & .38\\
-Item6 & 2.73 & 1.46 & 0.20 & -1.36 & 0.87 & .00 & .33\\
-Item7 & 3.86 & 1.67 & -0.99 & -0.85 & 0.65 & .00 & .23\\
-Item8 & 3.76 & 1.14 & -0.68 & -0.45 & 0.86 & .00 & .00\\
-Item9 & 3.42 & 1.83 & -0.45 & -1.69 & 0.69 & .00 & .33\\
-Item10 & 2.74 & 1.04 & 0.09 & -0.74 & 0.91 & .00 & .28\\
-Item11 & 2.60 & 1.25 & 0.29 & -0.86 & 0.89 & .00 & .35\\
-Item12 & 2.11 & 1.17 & 0.77 & -0.39 & 0.83 & .00 & .32\\
-Item13 & 2.94 & 1.03 & -0.12 & -0.40 & 0.91 & .00 & .10\\
-Item14 & 3.62 & 1.64 & -0.68 & -1.25 & 0.74 & .00 & .32\\
-Item15 & 1.64 & 1.18 & 1.79 & 2.02 & 0.60 & .00 & .15\\
-Item16 & 3.51 & 1.30 & -0.70 & -0.59 & 0.85 & .00 & .39\\
-Item17 & 1.96 & 0.98 & 1.02 & 0.69 & 0.82 & .00 & .05\\
-Item18 & 2.44 & 1.31 & 0.38 & -1.14 & 0.86 & .00 & .11\\
-Item19 & 3.80 & 1.29 & -0.87 & -0.42 & 0.82 & .00 & .17\\
-Item20 & 4.01 & 1.40 & -1.22 & 0.07 & 0.70 & .00 & .13\\
-Item21 & 1.33 & 0.91 & 3.03 & 8.43 & 0.41 & .00 & .01\\
-Item22 & 2.59 & 1.41 & 0.27 & -1.27 & 0.86 & .00 & .19\\
-Item23 & 1.31 & 0.81 & 2.75 & 6.92 & 0.43 & .00 & .21\\
-Item24 & 1.47 & 1.18 & 2.38 & 4.00 & 0.43 & .00 & .28\\
-Item25 & 2.56 & 1.27 & 0.33 & -1.00 & 0.89 & .00 & .11\\
-Item26 & 1.54 & 1.25 & 2.13 & 2.86 & 0.46 & .00 & .36\\
-Item27 & 4.30 & 1.08 & -1.79 & 2.53 & 0.67 & .00 & .22\\
-Item28 & 2.27 & 1.39 & 0.74 & -0.81 & 0.81 & .00 & .25\\
-Item29 & 3.26 & 1.09 & -0.26 & -0.45 & 0.91 & .00 & .14\\
-Item30 & 2.22 & 1.48 & 0.71 & -1.02 & 0.76 & .00 & .30\\
-Item31 & 1.05 & 0.36 & 7.23 & 52.98 & 0.13 & .00 & .18\\
-Item32 & 1.54 & 1.21 & 2.07 & 2.75 & 0.49 & .00 & .31\\
-Item33 & 1.04 & 0.33 & 8.99 & 85.28 & 0.10 & .00 & .16\\
-Item34 & 3.36 & 1.38 & -0.48 & -1.03 & 0.87 & .00 & .16\\
-Item35 & 2.26 & 1.25 & 0.70 & -0.60 & 0.85 & .00 & .19\\
-Item36 & 2.36 & 1.22 & 0.59 & -0.62 & 0.87 & .00 & .25\\
-Item37 & 1.14 & 0.59 & 4.79 & 24.05 & 0.25 & .00 & .16\\
-Item38 & 2.25 & 1.27 & 0.69 & -0.64 & 0.84 & .00 & .18\\
-Item39 & 3.93 & 1.48 & -1.06 & -0.44 & 0.71 & .00 & .18\\
-Item40 & 3.57 & 1.07 & -0.65 & -0.17 & 0.88 & .00 & .21\\
-Item41 & 3.55 & 1.65 & -0.60 & -1.34 & 0.76 & .00 & .43\\
-Item42 & 3.00 & 1.62 & -0.08 & -1.61 & 0.83 & .00 & .44\\
-Item43 & 1.56 & 1.23 & 2.00 & 2.45 & 0.50 & .00 & .32\\
-Item44 & 2.97 & 1.20 & -0.06 & -0.94 & 0.91 & .00 & -.10\\
-Item45 & 2.79 & 1.55 & 0.19 & -1.48 & 0.85 & .00 & .20\\
-Item46 & 2.14 & 1.31 & 0.77 & -0.78 & 0.80 & .00 & .26\\
-Item47 & 2.18 & 0.90 & 0.60 & 0.12 & 0.86 & .00 & .26\\
-Item48 & 1.48 & 1.11 & 2.18 & 3.35 & 0.48 & .00 & .24\\
+item43 & 0.99 & - & - & - & - & 0.99\\
+item26 & 0.93 & - & - & - & - & 0.9\\
+item32 & 0.8 & - & - & - & - & 0.67\\
+item10 & - & 0.82 & - & - & - & 0.68\\
+item47 & - & 0.82 & - & - & - & 0.7\\
+item36 & - & 0.63 & - & - & - & 0.45\\
+item44 & - & -0.47 & - & - & - & 0.24\\
+item35 & - & 0.46 & - & - & - & 0.24\\
+item13 & - & 0.34 & - & - & - & 0.13\\
+item14 & - & - & 0.89 & - & - & 0.81\\
+item41 & - & - & 0.7 & - & - & 0.6\\
+item7 & - & - & 0.66 & - & - & 0.45\\
+item27 & - & - & 0.38 & - & - & 0.21\\
+item21 & - & - & -0.34 & - & - & 0.12\\
+item34 & - & - & - & 0.84 & - & 0.74\\
+item19 & - & - & - & 0.8 & - & 0.64\\
+item2 & - & - & - & 0.67 & - & 0.54\\
+item5 & - & - & - & - & 0.69 & 0.51\\
+item24 & - & - & - & - & 0.54 & 0.33\\
+item30 & - & - & - & - & 0.52 & 0.29\\
+item1 & - & - & - & - & 0.35 & 0.13\\
+item16 & - & - & - & - & 0.31 & 0.21\\
+item28 & - & - & - & - & 0.31 & 0.1\\
+\% of variance & 11 & 10 & 9 & 9 & 6 & -\\
 \bottomrule
+\addlinespace
 \end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Only loading higher than .30 is reported}
+\end{tablenotes}
 
@@
 \begin{figure}
-\includegraphics[width=0.5\linewidth]{manuscript_files/figure-latex/figCor-1} \caption{Iter-correlation of the items}\label{fig:figCor}
-\end{figure}
 
-Table\ref{tab:tabDes} summarizes the univariate descriptive statistics for the 48 items.
-some of the items were skewed with high Kurtosis values.
-The Shapiro-Wilk test of normality (Shapiro \& Wilk, 1965) indicated all the items violated normality assumptions.
-Multivariate normality assumptions were investigated by Marida's test (Mardia, 1970).
-Multivariate skew = 583.80 (p \textless0.001) and multivariate kurtosis = 2,749.15 (p \textless0.001) indicated multivariate normality assumptions violation.
-Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen (Desjardins \& Bulut, 2018).
-Bartlett's test of sphericity (Bartlett, 1954), \(\chi^2\) (1128) = 5042.86, p \textless{} .001{]} indicated the correlations between items are adequate for the EFA.
-However only 4.96\% of the inter-item correlation coefficients were greater than .30 in the obtained matrix.
-The inter item correlation ranged between .44 to .91.
-The corrected item-total correlations ranged between .10 to .44.
-
-Scree plot ( Fig@ref(fig:fac.id)) suggested a six-factor solution.Horn's parallel analysis (Horn, 1965), like the Monte Carlo study, draws several sets of random data with the same number of participants as the original data set and compares the mean eigenvalues among the simulated and original data sets to retain optimal factors.This extraction method also supported a five-factor model.
-In our data set parallel analysis with 500 iterations indicated six-factor solution.
-However, In MAP method (Velicer, 1976) and Hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) suggested a five-factor solution Parallel analysis is also more immune to the normality assumptions violation(\textbf{RN1263?}).
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{parallel} \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/fac.id-2} \includegraphics[width=0.5\linewidth,height=0.5\textheight]{HUll method}
+{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/Residuals-1}
 
@@
 
-\caption{Factor Identification (A) Parallel analysis (B) Scree Plot, (C) Hull method}(\#fig:fac.id)
+\caption{ Histogram of residulas:  five-factor solution}\label{fig:Residuals}
 \end{figure}
@@
 \section{Confirmatory Factor Analysis}\label{confirmatory-factor-analysis}}
+
+\hypertarget{irt}{%
+\subsection{IRT}\label{irt}}
 
@@
 
+\leavevmode\hypertarget{ref-bentlerPracticalIssuesStructural1987}{}%
+Bentler, P. M., \& Chou, C.-P. (1987). Practical {Issues} in {Structural Modeling}. \emph{Sociological Methods \& Research}, \emph{16}(1), 78--117. \url{https://doi.org/10.1177/0049124187016001004}
+
+\leavevmode\hypertarget{ref-brownConfirmatoryFactorAnalysis2015}{}%
+Brown, T. A. (2015). \emph{Confirmatory factor analysis for applied research} (2nd ed.). {New York, NY, US}: {The Guilford Press}.
+
 \leavevmode\hypertarget{ref-R-MOTE}{}%
@@
 
-\leavevmode\hypertarget{ref-childEssentialsFactorAnalysis2006}{}%
-Child, D. (2006). \emph{Essentials of factor analysis} (3rd ed.). {New York: Continuum}.
+\leavevmode\hypertarget{ref-R-shiny}{}%
+Chang, W., Cheng, J., Allaire, J., Sievert, C., Schloerke, B., Xie, Y., \ldots{} Borges, B.
+(2021).
+\emph{Shiny: Web application framework for r}.
+Retrieved from \url{https://CRAN.R-project.org/package=shiny}
+
+\leavevmode\hypertarget{ref-comreyFirstCourseFactor1992}{}%
+Comrey, A. L., \& Lee, H. B. (1992). \emph{A first course in factor analysis, 2nd ed}. {Hillsdale, NJ, US}: {Lawrence Erlbaum Associates, Inc}.
 
@@
 Desjardins, C., \& Bulut, O. (2018). \emph{Handbook of {Educational Measurement} and {Psychometrics Using R}}. \url{https://doi.org/10.1201/b20498}
+
+\leavevmode\hypertarget{ref-desjardinsHandbookEducationalMeasurement2018a}{}%
+Desjardins, C. D. (2018). \emph{Handbook of educational measurement and psychometrics using {R}} (O. Bulut \& ProQuest (Firm), Eds.). {Boca Raton, FL : CRC Press}.
 
@@
 
-\leavevmode\hypertarget{ref-furrPsychometricsIntroduction2014}{}%
-Furr, R. M. (2014). \emph{Psychometrics : An introduction} (2nd ed.). {Thousand Oaks}: {Thousand Oaks : SAGE}.
-
 \leavevmode\hypertarget{ref-R-purrr}{}%
@@
 
+\leavevmode\hypertarget{ref-jacksonRevisitingSampleSize2003}{}%
+Jackson, D.
+L.
+(2003).
+Revisiting {Sample Size} and {Number} of {Parameter Estimates}: {Some Support} for the {N}:q {Hypothesis}.
+\emph{Structural Equation Modeling}, \emph{10}(1), 128--141.
+\url{https://doi.org/10.1207/S15328007SEM1001_6}
+
 \leavevmode\hypertarget{ref-R-semTools}{}%
@@
 
+\leavevmode\hypertarget{ref-R-ggcorrplot}{}%
+Kassambara, A. (2019). \emph{Ggcorrplot: Visualization of a correlation matrix using 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=ggcorrplot}
+
+\leavevmode\hypertarget{ref-klinePrinciplesPracticeStructural2015}{}%
+Kline, R. B. (2015). \emph{Principles and practice of structural equation modeling}. {The Guilford Press}.
+
 \leavevmode\hypertarget{ref-lorenzo-sevaHullMethodSelecting2011}{}%
@@
 
+\leavevmode\hypertarget{ref-R-correlation}{}%
+Makowski, D., Ben-Shachar, M.
+S., Patil, I., \& Lüdecke, D.
+(2020).
+Methods and algorithms for correlation analysis in r.
+\emph{Journal of Open Source Software}, \emph{5}(51), 2306.
+\url{https://doi.org/10.21105/joss.02306}
+
 \leavevmode\hypertarget{ref-mardiaMeasuresMultivariateSkewness1970}{}%
 Mardia, K. V. (1970). Measures of multivariate skewness and kurtosis with applications. \emph{Biometrika}, \emph{57}(3), 519--530. \url{https://doi.org/10.1093/biomet/57.3.519}
-
-\leavevmode\hypertarget{ref-mulaikFoundationsFactorAnalysis2009}{}%
-Mulaik, S. A. (2009). \emph{Foundations of {Factor Analysis}} (Vol. 7). {London}: {London: Chapman and Hall/CRC}. \url{https://doi.org/10.1201/b15851}
 
@@
 Ryu, C. (2021). \emph{Dlookr: Tools for data diagnosis, exploration, transformation}. Retrieved from \url{https://CRAN.R-project.org/package=dlookr}
+
+\leavevmode\hypertarget{ref-schonbrodtWhatSampleSize2013}{}%
+Schönbrodt, F.
+D., \& Perugini, M.
+(2013).
+At what sample size do correlations stabilize?
+\emph{Journal of Research in Personality}, \emph{47}(5), 609--612.
+\url{https://doi.org/10.1016/j.jrp.2013.05.009}
 
@@
 
+\leavevmode\hypertarget{ref-worthingtonScaleDevelopmentResearch2006}{}%
+Worthington, R.
+L., \& Whittaker, T.
+A.
+(2006).
+Scale {Development Research}: {A Content Analysis} and {Recommendations} for {Best Practices}.
+\emph{The Counseling Psychologist}, \emph{34}(6), 806--838.
+\url{https://doi.org/10.1177/0011000006288127}
+
 \leavevmode\hypertarget{ref-R-kableExtra}{}%

### 2021-09-01 manuscript.Rmd

@@
 
-CFA: For estimating the sample size for the confirmatory factor analysis we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006] where 10 participants per parameters is required to earn trustworthiness of the result.
+CFA: For estimating the sample size for the confirmatory factor analysis we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006] where 10 participants per parameter is required to earn trustworthiness of the result.
 Our sample size exceeds the requirement.

### 2021-09-01 manuscript.tex

@@
 
-CFA: For estimating the sample size for the confirmatory factor analysis we followed the N:q rule (Bentler \& Chou, 1987; Jackson, 2003; Kline, 2015; Worthington \& Whittaker, 2006) where 10 participants per parameters is required to earn trustworthiness of the result.
+CFA: For estimating the sample size for the confirmatory factor analysis we followed the N:q rule (Bentler \& Chou, 1987; Jackson, 2003; Kline, 2015; Worthington \& Whittaker, 2006) where 10 participants per parameter is required to earn trustworthiness of the result.
 Our sample size exceeds the requirement.

### 2021-09-04 manuscript.Rmd

@@
 library(papaja) # devtools::install_github("crsh/papaja")
-library(readr)
-library(readxl)
 library(lavaan)
@@
 library(ggcorrplot)
+library(car) #Reversecoding
+library(Hmisc)
 r_refs("references.bib")
@@
 ## Participants
+
+```{r include=FALSE}
+data <- readRDS("leba_2021-09-03.rds")
+sem.data <- data[, 6:53] #EFA & CFA data
+sem.data[ sem.data == 0] <- 1 #Merged "0"s and "1"s into "1"s
+
+#renaming the column-header
+prefix <- "item"
+sufix <- c(1:48)
+colnam <- paste(prefix,sufix, sep = "" )
+colnames(sem.data) <- colnam
+
+#Separating the EFA and CFA sample
+EFA.data <- sem.data[1:428, ]
+CFA.data <- sem.data[429:690,]
+
+```
 
@@
 
-                     node[shape = rectangle, margin = 0.2, width = 6.5, height = 1, fixedsize = true]
+                     node[shape = rectangle, margin = 0.2, width = 6.5, height = 1, 
+                    fixedsize = true]
 
@@
 
-                    node[shape = rectangle, margin = 0.2, width = 6.5, height = 2, fixedsize = true]
+                    node[shape = rectangle, margin = 0.2, width = 6.5, height = 2, 
+                    fixedsize = true]
                     C[label = 'Factor Identification
@@
 ```{r Normality assumption EFA, include=FALSE}
-LB <- read_excel("recoded not reversed_EFA.xlsx")
-LB$X1 <- NULL
+
 #KMO test
-KMO <- KMO(LB)
+KMO <- KMO(EFA.data)
 
 # Test of correlation matrix
-bartlet <- cortest.bartlett(LB, n =428)
+bartlet <- cortest.bartlett(EFA.data, n =428)
 
-# Univariante normality
-normality <- normality(LB) 
-normalityprefix <- apa(normality$statistic, 2,T)
+# Univariate normality
+
+#for ( i in 1:length (EFA.data)){numeric <- is.numeric(i) print(numeric)}
+
+shapiro.test(EFA.data$item1)
+
+n1 <- shapiro.test(EFA.data$item1)
+n2 <- shapiro.test(EFA.data$item2)
+n3 <- shapiro.test(EFA.data$item3)
+n4 <- shapiro.test(EFA.data$item4)
+n5 <- shapiro.test(EFA.data$item5)
+n6 <- shapiro.test(EFA.data$item6)
+n7 <- shapiro.test(EFA.data$item7)
+n8 <- shapiro.test(EFA.data$item8)
+n9 <- shapiro.test(EFA.data$item9)
+n10 <- shapiro.test(EFA.data$item10)
+n11 <- shapiro.test(EFA.data$item11)
+n12 <- shapiro.test(EFA.data$item12)
+n13 <- shapiro.test(EFA.data$item13)
+n14 <- shapiro.test(EFA.data$item14)
+n15 <- shapiro.test(EFA.data$item15)
+n16 <- shapiro.test(EFA.data$item16)
+n17 <- shapiro.test(EFA.data$item17)
+n18 <- shapiro.test(EFA.data$item18)
+n19 <- shapiro.test(EFA.data$item19)
+n20 <- shapiro.test(EFA.data$item20)
+n21 <- shapiro.test(EFA.data$item21)
+n22 <- shapiro.test(EFA.data$item22)
+n23 <- shapiro.test(EFA.data$item23)
+n24 <- shapiro.test(EFA.data$item24)
+n25 <- shapiro.test(EFA.data$item25)
+n26 <- shapiro.test(EFA.data$item26)
+n27 <- shapiro.test(EFA.data$item27)
+n28 <- shapiro.test(EFA.data$item28)
+n29 <- shapiro.test(EFA.data$item29)
+n30 <- shapiro.test(EFA.data$item30)
+n31 <- shapiro.test(EFA.data$item31)
+n32 <- shapiro.test(EFA.data$item32)
+n33 <- shapiro.test(EFA.data$item33)
+n34 <- shapiro.test(EFA.data$item34)
+n35 <- shapiro.test(EFA.data$item35)
+n36 <- shapiro.test(EFA.data$item36)
+n37 <- shapiro.test(EFA.data$item37)
+n38 <- shapiro.test(EFA.data$item38)
+n39 <- shapiro.test(EFA.data$item39)
+n40 <- shapiro.test(EFA.data$item40)
+n41 <- shapiro.test(EFA.data$item41)
+n42 <- shapiro.test(EFA.data$item42)
+n43 <- shapiro.test(EFA.data$item43)
+n44 <- shapiro.test(EFA.data$item44)
+n45 <- shapiro.test(EFA.data$item45)
+n46 <- shapiro.test(EFA.data$item46)
+n47 <- shapiro.test(EFA.data$item47)
+n48 <- shapiro.test(EFA.data$item48)
+
+normality.tab = matrix(, nrow = 48, ncol = 2)
+as.table(normality.tab)
+
+rownameprefix <- "Item"
+rownamesufix <- seq(1:48)
+my.item.names <- paste(rownameprefix,rownamesufix, sep = "" )
+
+rownames(normality.tab) <- my.item.names
+colnames(normality.tab) <- c("statistic", "p")
+
+normality.tab[,1] <- c(apa((n1$statistic),2,T),
+                       apa((n1$statistic),2,T),
+                       apa((n3$statistic),2,T),
+                       apa((n4$statistic),2,T),
+                       apa((n5$statistic),2,T),
+                       apa((n6$statistic),2,T),
+                       apa((n7$statistic),2,T),
+                       apa((n8$statistic),2,T),
+                       apa((n9$statistic),2,T),
+                       apa((n10$statistic),2,T),
+                       apa((n11$statistic),2,T),
+                       apa((n12$statistic),2,T),
+                       apa((n13$statistic),2,T),
+                       apa((n14$statistic),2,T),
+                       apa((n14$statistic),2,T),
+                       apa((n16$statistic),2,T),
+                       apa((n17$statistic),2,T),
+                       apa((n18$statistic),2,T),
+                       apa((n19$statistic),2,T),
+                       apa((n20$statistic),2,T),
+                       apa((n21$statistic),2,T),
+                       apa((n22$statistic),2,T),
+                       apa((n23$statistic),2,T),
+                       apa((n24$statistic),2,T),
+                       apa((n25$statistic),2,T),
+                       apa((n26$statistic),2,T),
+                       apa((n27$statistic),2,T),
+                       apa((n28$statistic),2,T),
+                       apa((n29$statistic),2,T),
+                       apa((n30$statistic),2,T),
+                       apa((n31$statistic),2,T),
+                       apa((n32$statistic),2,T),
+                       apa((n33$statistic),2,T),
+                       apa((n34$statistic),2,T),
+                       apa((n35$statistic),2,T),
+                       apa((n36$statistic),2,T),
+                       apa((n37$statistic),2,T),
+                       apa((n38$statistic),2,T),
+                       apa((n39$statistic),2,T),
+                       apa((n40$statistic),2,T),
+                       apa((n41$statistic),2,T),
+                       apa((n42$statistic),2,T),
+                       apa((n43$statistic),2,T),
+                       apa((n44$statistic),2,T),
+                       apa((n45$statistic),2,T),
+                       apa((n46$statistic),2,T),
+                       apa((n47$statistic),2,T),
+                       apa((n48$statistic),2,T))
+
+normality.tab[,2] <- c(apa((n1$p.value),2,T),
+                       apa((n1$p.value),2,T),
+                       apa((n3$p.value),2,T),
+                       apa((n4$p.value),2,T),
+                       apa((n5$p.value),2,T),
+                       apa((n6$p.value),2,T),
+                       apa((n7$p.value),2,T),
+                       apa((n8$p.value),2,T),
+                       apa((n9$p.value),2,T),
+                       apa((n10$p.value),2,T),
+                       apa((n11$p.value),2,T),
+                       apa((n12$p.value),2,T),
+                       apa((n13$p.value),2,T),
+                       apa((n14$p.value),2,T),
+                       apa((n14$p.value),2,T),
+                       apa((n16$p.value),2,T),
+                       apa((n17$p.value),2,T),
+                       apa((n18$p.value),2,T),
+                       apa((n19$p.value),2,T),
+                       apa((n20$p.value),2,T),
+                       apa((n21$p.value),2,T),
+                       apa((n22$p.value),2,T),
+                       apa((n23$p.value),2,T),
+                       apa((n24$p.value),2,T),
+                       apa((n25$p.value),2,T),
+                       apa((n26$p.value),2,T),
+                       apa((n27$p.value),2,T),
+                       apa((n28$p.value),2,T),
+                       apa((n29$p.value),2,T),
+                       apa((n30$p.value),2,T),
+                       apa((n31$p.value),2,T),
+                       apa((n32$p.value),2,T),
+                       apa((n33$p.value),2,T),
+                       apa((n34$p.value),2,T),
+                       apa((n35$p.value),2,T),
+                       apa((n36$p.value),2,T),
+                       apa((n37$p.value),2,T),
+                       apa((n38$p.value),2,T),
+                       apa((n39$p.value),2,T),
+                       apa((n40$p.value),2,T),
+                       apa((n41$p.value),2,T),
+                       apa((n42$p.value),2,T),
+                       apa((n43$p.value),2,T),
+                       apa((n44$p.value),2,T),
+                       apa((n45$p.value),2,T),
+                       apa((n46$p.value),2,T),
+                       apa((n47$p.value),2,T),
+                       apa((n48$p.value),2,T))
+
+normalityprefix <- normality.tab[,1]
 normalitysufix <- "*"
@@
 # Multivariate Normality
-mardia <- mardia(LB, na.rm = T, plot =F)
+mardia <- mardia(EFA.data, na.rm = T, plot =F)
 
 # Descriptives
-Descriptives <- psych::describe(LB)
-alpha <- psych::alpha(LB)
+Descriptives <- psych::describe(EFA.data)
+alpha <- psych::alpha(EFA.data)
 Item.total <- alpha$item.stats
@@
 
-colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics", "Item-Total Correlation")
+colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics", 
+                           "Item-Total Correlation")
 
@@
 #Polychoric Correlation matrix
-LB.factor <- sapply(LB, as.factor)
-correlations <- polychoric(LB.factor, correct = 0)
+
+correlations <- polychoric(EFA.data, correct = 0)
 upper <- correlations$rho[upper.tri(correlations$rho, diag = F)]
@@
 BigR = sum(correlations$rho >= abs(.30) & correlations$rho < abs(1.0), na.rm =T)/2 
-totR = length(LB)*(length(LB)-1)/2
+totR = length(EFA.data)*(length(EFA.data)-1)/2
 cor.per <- print (BigR/totR)*100
@@
 # Item analysis
-Item_analysis <- psych::alpha(LB)
+Item_analysis <- psych::alpha(EFA.data)
 Item_analysis$item.stats$r.cor
@@
 
-#correlations <- polychoric(LB.factor, correct = 0)
+#correlations <- polychoric(EFA.factor, correct = 0)
 
@@
 # HULL
-hullEFA(LB,extr = "ULS", index_hull = "CAF", display = TRUE, graph = TRUE,
+hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = TRUE,
         details = TRUE)
+
+#MAP
+psych::VSS(EFA.data, rotate = "varimax", fm = 'minres', n.obs =428 )
 
@@
 
-reduced.model.5F.1 <- dplyr::select(LB ,
-                                    - c(item20,item17,item3, item15,item40, item4,item11, item39,
-                                        item18, item45, item29, item25, item8, item46 ))
+reduced.model.5F.1 <- dplyr::select(EFA.data ,
+                                    -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14))
 
@@
               residuals = TRUE, SMC = TRUE, n.obs =428)
+
 BB <- print(fa.5F.2, cut = .3, digits = 3, sort = TRUE)
 
-reduced.model.5F.2 <- dplyr::select(LB,- c(item20,item17,item3, item15,item40, item4,item11, item39,
-                                           item18, item45, item29, item25, item8, item46,
-                                           item33, item12,item31, item37,
-                                           item22, item38, item6, item48))
+reduced.model.5F.2 <- dplyr::select(EFA.data, -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14, item34, item47, item21, item13))
+
 correlations.red.5F.2 <- polychoric(reduced.model.5F.2,correct = 0)
@@
 fa.5F.3 <- fa(r=correlations.red.5F.2$rho, nfactors = 5, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
+              residuals = TRUE, SMC = TRUE, n.obs =428,max.iter = 500 )
 
@@
 
-reduced.model.5F.3 <- dplyr::select(LB,- c(item20,item17,item3, item15,item40, item4,item11, item39,
-                                           item18, item45, item29, item25, item8, item46,
-                                           item33, item12,item31, item37,
-                                           item22, item38, item6, item48, item9, item42,
-                                           item23))
-correlations.red.5F.3 <- polychoric(reduced.model.5F.3,correct = 0)
-
-fa.5F.4 <- fa(r=correlations.red.5F.3$rho, nfactors = 5, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-DD <- print(fa.5F.4, cut = .3, digits = 3, sort = TRUE)
-
+var1 <- CC$Vaccounted[2,1]*100
+var2 <- CC$Vaccounted[2,2]*100
+var3 <- CC$Vaccounted[2,3]*100
+var4 <- CC$Vaccounted[2,4]*100
+var5 <- CC$Vaccounted[2,5]*100
 ```
@@
 fixedsize = true, fontsize = 35]
-F1 [label = 'Blue 
-Filter']
-F2 [label = 'Outdoor']
-F3 [label = 'Sleep
-Environment']
-F4 [label = 'Cell Phone']
-F5 [label = 'Awareness']
+F1 [label = 'F1']
+F2 [label = 'F2']
+F3 [label = 'F3']
+F4 [label = 'F4']
+F5 [label = 'F5']
 node [fontname = Helvetica, shape = box]
-b [label = 'item43']
-c [label = 'item26']
-d [label = 'item32']
-e [label = 'item10']
-f [label = 'item47']
-g [label = 'item36']
-h [label = 'item44']
-i [label = 'item35']
-j [label = 'item13']
-k [label = 'item14']
-l [label = 'item41']
-m [label = 'item7']
-n [label = 'item27']
-o [label = 'item21']
-p [label = 'item34']
-q [label = 'item19']
-r [label = 'item2']
-s [label = 'item5']
-t [label = 'item24']
-u [label = 'item30']
-v [label = 'item1']
-w [label = 'item16']
-x [label = 'item28']
+b [label = 'item16']
+c [label = 'item36']
+d [label = 'item17']
+e [label = 'item11']
+f [label = 'item10']
+g [label = 'item12']
+h [label = 'item7']
+i [label = 'item8']
+j [label = 'item9']
+k [label = 'item27']
+l [label = 'item3']
+m [label = 'item40']
+n [label = 'item30']
+o [label = 'item41']
+p [label = 'item33']
+q [label = 'item32']
+r [label = 'item35']
+s [label = 'item37']
+t [label = 'item38']
+u [label = 'item46']
+v [label = 'item45']
+w [label = 'item25']
+x [label = 'item4']
+y [label = 'item1']
+z [label = 'item26']
 
@@
 F1-> d [label = '0.80']
-F2 -> e [label = '0.82']
-F2 -> f[label = '0.82']
-F2 -> g [label = '0.63']
-F2 -> h[ label = '-0.47', color =red]
-F2 -> i [label = '0.46']
-F2 -> j [label = '0.34']
-F3 -> k [label = '0.89']
-F3 -> l [label = '0.70']
-F3 -> m [label = '0.66']
-F3 -> n [label = '0.38']
-F3 -> o [label = '-0.34', color =red]
-F4 -> p [label = '0.84']
-F4 -> q [label = '0.80']
-F4 -> r [label = '0.69']
-F5 -> s [label = '0.69']
-F5 -> t [label = '0.54']
-F5 -> u [label = '0.52']
-F5 -> v [label = '0.35']
-F5 -> w [label = '0.31']
-F5 -> x [label = '0.31']
-
+F2 -> e [label = '0.79']
+F2 -> f[label = '0.76']
+F2 -> g [label = '0.65']
+F2 -> h[ label = '0.50']
+F2 -> i [label = '-.49',color =red]
+F2 -> j [label = '0.32']
+F3 -> k [label = '0.80']
+F3 -> l [label = '0.80']
+F3 -> m [label = '0.65']
+F3 -> n [label = '0.49']
+F3 -> o [label = '36']
+F4 -> p [label = '0.74']
+F4 -> q [label = '0.73']
+F4 -> r [label = '0.66']
+F4 -> s [label = '-0.39', color =red]
+F4 -> t [label = '0.39']
+F5 -> u [label = '0.60']
+F5 -> v [label = '0.59']
+F5 -> w [label = '0.41']
+F5 -> x [label = '0.41']
+F5 -> y [label = '0.40']
+F5 -> z [label = '0.35']
 }
@@
 ```{r Cronbach alpha for 5 fators, message=TRUE, warning=FALSE, include=FALSE}
-Five.F1 <- dplyr::select(LB, item43, item26, item32)
-Five.F2 <- dplyr::select(LB, item10, item47, item36, item44, item35, item13) 
-Five.F3 <-  dplyr::select(LB, item14, item41,item7, item27, item21)
-Five.F4 <-  dplyr::select(LB, item19,item34,item2)
-Five.F5 <- dplyr::select(LB, item5, item24, item30, item1, item16, item28)
+Five.F1 <- dplyr::select(EFA.data, item16, item36, item17)
+Five.F2 <- dplyr::select(EFA.data, item11, item10, item12, item7, item8, item9) 
+Five.F3 <-  dplyr::select(EFA.data, item27, item3,item40, item30, item41)
+Five.F4 <-  dplyr::select(EFA.data, item33,item32,item35, item37, item38)
+Five.F5 <- dplyr::select(EFA.data, item46, item45, item25, item4, item1, item26)
 
@@
 Five.F5.alpha <- psych::alpha(Five.F5, check.keys = T)
+
+F1.alpha <- Five.F1.alpha$total$raw_alpha
+F2.alpha <- Five.F2.alpha$total$raw_alpha
+F3.alpha <- Five.F3.alpha$total$raw_alpha
+F4.alpha <- Five.F4.alpha$total$raw_alpha
+F5.alpha <- Five.F5.alpha$total$raw_alpha
 ```
@@
 
-reduced.model.5F.min.1 <- dplyr::select(LB ,
-                                    - c(item20,item17,item3, item15,item40, item4,item11, item39,
-                                        item18, item45, item29, item25, item8, item46 ))
+reduced.model.5F.min.1 <- dplyr::select(EFA.data ,
+                                    -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14))
 
@@
               residuals = TRUE, SMC = TRUE, n.obs =428)
+
 FF <- print(fa.5F.min.2, cut = .3, digits = 3, sort = TRUE)
 
-reduced.model.5F.min.2 <- dplyr::select(LB,- c(item20,item17,item3, item15,item40, item4,item11, item39,
-                                           item18, item45, item29, item25, item8, item46,
-                                           item33, item12,item31, item37,
-                                           item22, item38, item6, item48))
+reduced.model.5F.min.2 <- dplyr::select(EFA.data, -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14, item34, item47, item21, item13))
 
@@
 GG <- print(fa.5F.min.3, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.5F.min.3 <- dplyr::select(LB,- c(item20,item17,item3, item15,item40, item4,item11, item39,
-                                               item18, item45, item29, item25, item8, item46,
-                                               item33, item12,item31, item37,
-                                               item22, item38, item6, item48,
-                                               item9, item42, item23))
-correlations.red.5F.min.3 <- polychoric(reduced.model.5F.min.3,correct = 0)
-
-fa.5F.min.4 <- fa(r=correlations.red.5F.min.3$rho, nfactors = 5, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-HH <- print(fa.5F.min.4, cut = .3, digits = 3, sort = TRUE)
-
 ```
@@
 
-#LB.factor <- sapply(LB, as.factor)
-#correlations <- polychoric(LB.factor, correct = 0)
+#EFA.factor <- sapply(EFA.data, as.factor)
+#correlations <- polychoric(EFA.factor, correct = 0)
 
@@
               residuals = TRUE, SMC = TRUE, n.obs =428)
+
 II <- print(fa.6F.1, cut = .3, digits = 3, sort = TRUE)
 
-reduced.model.6F.1 <- dplyr::select(LB ,
-                                    -c(item15, item17, item40, item4, item3, item46, item8,item29, item25 ))
+reduced.model.6F.1 <- dplyr::select(EFA.data ,
+                                    -c(item34, item44, item48, item43, item39, item22, item2, item20, item21, item24,item30, item14, item28, item6, item15, item23))
 
@@
               residuals = TRUE, SMC = TRUE, n.obs =428)
+
 JJ <- print(fa.6F.2, cut = .3, digits = 3, sort = TRUE)
 
-reduced.model.6F.2 <- dplyr::select(LB,-c(item15, item17, item40, item4, item3, item46, item8,item29, item25, item9, item33, item48, item16, item6 ))
+reduced.model.6F.2 <- dplyr::select(EFA.data, -c(item34, item44, item48, item43, item39, item22, item2, item20, item21, item24,item30, item14, item28, item6, item15, item23, item18, item42, item47, item41))
 
@@
 fa.6F.3 <- fa(r=correlations.red.6F.2$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
+              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)
 
@@
 
-reduced.model.6F.3 <- dplyr::select(LB,- -c(item15, item17, item40, item4, item3, item46, item8,item29, item25, item9, item33, item48, item16, item6, item11, item23, item18, item39))
-
-correlations.red.6F.3 <- polychoric(reduced.model.6F.3,correct = 0)
-
-fa.6F.4 <- fa(r=correlations.red.6F.3$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)
-
-LL <- print(fa.6F.4, cut = .3, digits = 3, sort = TRUE)
-
 # Residuals
-residual.6F =residuals(fa.6F.4 , diag = FALSE, na.rm =T)
+residual.6F =residuals(fa.6F.3 , diag = FALSE, na.rm =T)
 #Count of numbers of residuals>.05
@@
 #Total number of off diagonal elements in the data matrix
-totRRR = length(reduced.model.6F.3)*(length(reduced.model.6F.3)-1)/2
+totRRR = length(reduced.model.6F.2)*(length(reduced.model.6F.2)-1)/2
 
@@
 #Preparing the EFA table
-factor.des = matrix(, nrow = 25, ncol = 6)
+factor.des = matrix(, nrow = 27, ncol = 6)
 as.table(factor.des)
-rownames(factor.des) <- c("item43", "item26",  "item32",   
-                          "item10",  "item47",  "item36", "item44",  "item35",  "item13", 
-                          "item14", "item41",  "item7","item27","item21",
-                          "item34", "item19", "item2",
-                          "item5", "item24", "item30", "item1", "item16", "item28", "internal Consistency","% of variance")
+rownames(factor.des) <- c("item16", "item36",  "item17",   
+                          "item11",  "item10",  "item12", "item7",  "item8",  "item9", 
+                          "item27", "item3",  "item40","item30","item41",
+                          "item33", "item32", "item35","item37", "item38",
+                          "item46", "item45", "item25", "item4", "item1", "item26", "internal Consistency","% of variance")
 
@@
 
-factor.des[,1] <- c(.99, .93, .80, "-","-","-","-","-","-","-","-","-","-","-","-",
-                    "-","-","-","-","-","-","-","-",apa(Five.F1.alpha$total[,1],2,F), 11)
+factor.des[,1] <- c(.99, .94, .80, "-","-","-","-","-","-","-","-","-","-","-","-",
+                    "-","-","-","-","-","-","-","-","-","-",apa(Five.F1.alpha$total[,1],2,F), apa(var1,2,F))
 
-factor.des[,2] <- c("-", "-", "-", .82,.82,.63,-.47,.46,.34,"-","-","-","-","-","-",
-                    "-","-","-","-","-","-","-","-",apa(Five.F2.alpha$total[,1],2,F), 10)
+factor.des[,2] <- c("-", "-", "-", .80,.76,.65,.50,-.50,.32,"-","-","-","-","-","-",
+                    "-","-","-","-","-","-","-","-","-","-",apa(Five.F2.alpha$total[,1],2,F), apa(var2,2,F))
 
-factor.des[,3] <- c("-", "-", "-", "-","-","-","-","-","-",.89,.70,.66,.38,-.34,"-",
-                    "-","-","-","-","-","-","-","-", apa(Five.F3.alpha$total[,1],2,F),9)
+factor.des[,3] <- c("-", "-", "-", "-","-","-","-","-","-",.80,.80,.65,.45,-.36,"-",
+                    "-","-","-","-","-","-","-","-","-","-", apa(Five.F3.alpha$total[,1],2,F),apa(var3,2,F))
 
-factor.des[,4] <- c("-", "-", "-", "-","-","-","-","-","-","-","-","-","-","-",.84,
-                    .80,.67,"-","-","-","-","-","-",apa(Five.F4.alpha$total[,1],2,F), 9)
+factor.des[,4] <- c("-", "-", "-", "-","-","-","-","-","-","-","-","-","-","-",.74,
+                    .73,.66,-.39,.36,"-","-","-","-","-","-",apa(Five.F4.alpha$total[,1],2,F), apa(var4,2,F))
 
-factor.des[,5] <- c("-", "-", "-", "-","-","-","-","-","-","-","-","-","-","-","-","-","-"
-                    ,.69,.54,.52,.35,.31,.31,apa(Five.F5.alpha$total[,1],2,F), 6)
+factor.des[,5] <- c("-", "-", "-", "-","-","-","-","-","-","-","-","-","-","-","-","-","-","-","-",
+                    .60,.59,.41,.41,.40,.39,apa(Five.F5.alpha$total[,1],2,F), apa(var5,2,F))
 
-factor.des[,6] <- c (.99, .90,.67,.68,.70,.45,.24,.24,.13,.81,.60,.45,.21,.12,.74,.64,.54,
-                     .51,.33,.29,.13,.21,.10, "-", "-")
+factor.des[,6] <- c (.99, .90,.66,.64, .59, .47, .27, .25, .11, .66, .68, .46, .35, .33, .56, .62, .45, .17, .18, .42, .37, .19, .22, .17, .17, "-", "-")
 
 #Commonality
-Fac.5 <- fa.5F.4
+Fac.5 <- fa.5F.3
 min.com <- min(Fac.5$communality)
@@
 # Residuals
-residual.5F =residuals(fa.5F.4, diag = FALSE, na.rm =T)
+residual.5F =residuals(fa.5F.3, diag = FALSE, na.rm =T)
 #Count of numbers of residuals>.05
@@
 #Total number of off diagonal elements in the data matrix
-totRR = length(reduced.model.5F.3)*(length(reduced.model.5F.3)-1)/2
+totRR = length(reduced.model.5F.2)*(length(reduced.model.5F.2)-1)/2
 
@@
 
-The initial five-factor solution with all 48 items showed presence of cross-loading items (item 42, 16, & 1) and poor factor loading (<.30) items (item 20, 3 ,15, 17, 40, 4, 11, 39, 18, 45, 29, 25, 8 , & 46).
-At first, we discarded the items with poor factor-loading and ran another EFA on the remaining 34 items.
-This iteration of EFA also appeared as a misfit with items with poor factor-loading (Item 12, 22, 38, 6) and cross-loading (items 23, 31, 37, 48) .
-Another two rounds of EFA were conducted with gradually identifying problematic items and discarding them from the model.
-Finally, a five-factor EFA solution with 23 items was accepted with low RMSR = 0.04 [@brownConfirmatoryFactorAnalysis2015], all factor-loading higher than .30 and no cross-loading greater than .30.
+Three rounds of EFA starting with all 48 items were conducted and problematic items were gradually discarded (cross-loading items and poor factor loading (<.30) items).
+Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 [@brownConfirmatoryFactorAnalysis2015], all factor-loading higher than .30 and no cross-loading greater than .30.
 We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (see the supplementary).
@@
 The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`.
-However, the histogram of the absolute values of non-redundant residual-correlations (Fig\@ref(fig:Residuals) showed `r apa(sumR,2, T)`% correlations greater than the absolute value of .05, indicating under-factoring.
+However, the histogram of the absolute values of non-redundant residual-correlations (Fig\@ref(fig:Residuals) showed `r apa(sumR,2, T)`% correlations greater than the absolute value of .05, indicating a possible under-factoring.
 [@desjardinsHandbookEducationalMeasurement2018a].
 Subsequently, we fitted a six-factor solution.
-However, a factor emerged with only two salient variable loading in the six-factor solution, thus disqualifying the six-factor solution.
+However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution.
 
-In the five-factor solution, the first factor contained three items and explained 11% of the total variance with a satisfactory internal reliability coefficient ($\alpha$ =.86).
+In the five-factor solution, the first factor contained three items and explained `r apa(var1,2,F)`% of the total variance with a satisfactory internal reliability coefficient ($\alpha$ = `r apa(F1.alpha,2,F)`).
 All the items in this factor stemmed from the individual's preference to use blue light filters in different light environments.
-The second factor contained six items and explained 10% of the total variance with a satisfactory internal reliability coefficient ($\alpha$ =.71).
+The second factor contained six items and explained `r apa(var2,2,F)`% of the total variance with a satisfactory internal reliability coefficient ($\alpha$ = `r apa(F2.alpha,2,F)`).
 Items under this factor commonly investigate an individual's hours spent outdoor.
-The third factor contained five items and explained 9% of the total variance.
+The third factor contained five items and explained `r apa(var3,2,F)`% of the total variance.
 Items under this factor dealt with the specific behaviors pertaining to sleep.
-However, the internal consistency reliability coefficient was not satisfactory ($\alpha$ =.62).
-The fourth factor contained three items and explained 9% of the total variance with a satisfactory internal consistency ($\alpha$ =.77).
-These three items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time.
-Lastly, the fifth factor contained six items and explained 6% of the total variance.
-Under this factor tried to measure an individual's behavior lead by the awareness of light's influence on health.
-However, this factor showed unsatisfactory internal consistency reliability ($\alpha$ =.49).
+However, the internal consistency reliability coefficient was not satisfactory ($\alpha$ = `r apa(F3.alpha,2,F)`).
+The fourth factor contained five items and explained `r apa(var4,2,F)`% of the total variance with an  internal consistency coefficient, $\alpha$ = `r apa(F4.alpha,2,F)`.
+These five items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time.
+Lastly, the fifth factor contained six items and explained `r apa(var5,2,F)`% of the total variance.This factor tried to measure an individual's behavior lead by the awareness of light's influence on health.
+However, this factor showed unsatisfactory internal consistency reliability ($\alpha$ = `r apa(F5.alpha,2,F)`).
 It is essential to attain a balance between psychometric properties and the interpretability of the common themes when exploring the latent structure.
@@
 hist(residual.5F, col ="red", main = NULL, xlab = "Five-factor solution", ylim=c(0, 250))
-abline(h =47, lwd = 2, lty = 2)
+abline(h =51, lwd = 2, lty = 2)
 abline(v =.05,lwd = 2, lty = 2)
@@
 
-```{r CFA 23 items, include=FALSE}
-LB.cfa <- read_excel("recoded not reversed_CFA.xlsx")
+```{r CFA 23 items, eval=FALSE, include=FALSE}
+
+#CFA.data <- sem.data[429:690,]
+
+Ritem44 = recode(CFA.data$item44, '1=5; 2=4; 3=3; 4=2; 5=1')
+Ritem21 = recode(CFA.data$item44, '1=5; 2=4; 3=3; 4=2; 5=1')
+
+CFA.data <- CFA.data %>% 
+  mutate(Ritem44 = Ritem44, Ritem21 = Ritem21)
+
 LB.model.Cor <- "F1 =~ item43 + item26 + item32
-             F2 =~ item10 + item47 + item36 + item44 + item35 + item13
-            F3 =~  item14 + item41+ item7 + item27 + item21
+                 F2 =~ item10 + item47 + item36 + Ritem44 + item35 + item13
+                 F3 =~  item14 + item41+ item7 + item27 + Ritem21
                  F4 =~ item19 + item34 + item2
@@
 
-fit.Cor <- cfa(LB.model.Cor, data = LB.cfa, estimator = "MLR", mimic = "Mplus")
+fit.Cor <- cfa(LB.model.Cor, data = CFA.data, estimator = "MLR", mimic = "Mplus", check.gradient = FALSE)
 
@@
 
-```{r CFA23withMI, include=FALSE}
+```{r CFA23withMI, eval=FALSE, include=FALSE}
 LB.model.Cor.3 <- "F1 =~ item43 + item26 + item32
@@
 ## Fit the model 
-fit.Cor.3 <- cfa(LB.model.Cor.3, data = LB.cfa, estimator = "MLR", mimic = "Mplus")
+fit.Cor.3 <- cfa(LB.model.Cor.3, data = CFA.data, estimator = "MLR", mimic = "Mplus")
 
@@
 
-```{r CFI18items, include=FALSE}
+```{r CFI18items, eval=FALSE, include=FALSE}
 LB.model.Cor.2 <- "F1 =~ item43 + item26 + item32

### 2021-09-04 manuscript.Rmd
Delete manuscript_files/figure-latex directory

@@
 
-```{r include=FALSE}
+```{r preparingData, include=FALSE}
 data <- readRDS("leba_2021-09-03.rds")
+
+# Separating EFA and CFA samples with descriptive column
+descriptives.data <- data
+
+## Merge "0"s and "1"s into "1"s 9select,subset assign)
+descriptives.data[ , 6:53 ][ descriptives.data[ , 6:53 ] == 0 ] <- 1
+EFA.descriptives <- descriptives.data[1:428,]
+CFA.descriptives <- descriptives.data[429:690, ]
+
+#Separating the EFA and CFA(only items)
 sem.data <- data[, 6:53] #EFA & CFA data
@@
 
-#renaming the column-header
+## renaming the column-header
 prefix <- "item"
@@
 
-#Separating the EFA and CFA sample
+### EFA data
 EFA.data <- sem.data[1:428, ]
+
+### CFA Data
 CFA.data <- sem.data[429:690,]
+CFARitem8 = recode(CFA.data$item8, '1=5; 2=4; 3=3; 4=2; 5=1')
+CFARitem37 = recode(CFA.data$item37, '1=5; 2=4; 3=3; 4=2; 5=1')
+CFA.data <- CFA.data %>% 
+  mutate(Ritem8 = CFARitem8, Ritem37 = CFARitem37)
+
+### IRT data
+IRT.data <- sem.data
+IRTRitem8 = recode(IRT.data$item8, '1=5; 2=4; 3=3; 4=2; 5=1')
+IRTRitem37 = recode(IRT.data$item37, '1=5; 2=4; 3=3; 4=2; 5=1')
+IRT.data <- IRT.data %>% 
+  mutate(Ritem8 = IRTRitem8, Ritem37 = IRTRitem37)
+```
+
+```{r descriptives, eval=FALSE, include=FALSE}
+#Use these  data frames for descriptive
+EFA.descriptives #Only EFA
+CFA.descriptives #Only CFA
 
@@
 # Univariate normality
-
-#for ( i in 1:length (EFA.data)){numeric <- is.numeric(i) print(numeric)}
-
-shapiro.test(EFA.data$item1)
 
@@
 
-# Calulating the percentange of correlations higher than .30
+# Calculating the percentange of correlations higher than .30
 
@@
 
-```{r factor_identification, eval=FALSE, include=FALSE}
+```{r factor_identification, include=FALSE}
 
@@
       hline=NULL,add=F)
-knitr::include_graphics('HUll method.png')
+knitr::include_graphics('HUll method.jpeg')
 

### 2021-09-04 manuscript.tex

@@
 \endhead
-Item1 & 1.12 & 0.49 & 5.02 & 27.80 & 0.25* & .16\\
-Item2 & 2.16 & 1.19 & 0.71 & -0.54 & 0.84* & .14\\
-Item3 & 4.14 & 0.99 & -1.23 & 1.14 & 0.79* & .19\\
-Item4 & 2.87 & 1.59 & 0.08 & -1.60 & 0.83* & .19\\
-Item5 & 1.76 & 1.23 & 1.35 & 0.44 & 0.66* & .38\\
-Item6 & 2.73 & 1.46 & 0.20 & -1.36 & 0.87* & .33\\
-Item7 & 3.86 & 1.67 & -0.99 & -0.85 & 0.65* & .23\\
-Item8 & 3.76 & 1.14 & -0.68 & -0.45 & 0.86* & .00\\
-Item9 & 3.42 & 1.83 & -0.45 & -1.69 & 0.69* & .33\\
+Item1 & 2.27 & 1.39 & 0.74 & -0.81 & 0.81* & .25\\
+Item2 & 2.87 & 1.59 & 0.08 & -1.60 & 0.81* & .19\\
+Item3 & 3.36 & 1.38 & -0.48 & -1.03 & 0.87* & .16\\
+Item4 & 1.47 & 1.18 & 2.38 & 4.00 & 0.43* & .28\\
+Item5 & 4.01 & 1.40 & -1.22 & 0.07 & 0.70* & .13\\
+Item6 & 2.79 & 1.55 & 0.19 & -1.48 & 0.85* & .20\\
+Item7 & 2.26 & 1.25 & 0.70 & -0.60 & 0.85* & .19\\
+Item8 & 2.97 & 1.20 & -0.06 & -0.94 & 0.91* & -.10\\
+Item9 & 2.94 & 1.03 & -0.12 & -0.40 & 0.91* & .10\\
 Item10 & 2.74 & 1.04 & 0.09 & -0.74 & 0.91* & .28\\
-Item11 & 2.60 & 1.25 & 0.29 & -0.86 & 0.89* & .35\\
-Item12 & 2.11 & 1.17 & 0.77 & -0.39 & 0.83* & .32\\
-Item13 & 2.94 & 1.03 & -0.12 & -0.40 & 0.91* & .10\\
-Item14 & 3.62 & 1.64 & -0.68 & -1.25 & 0.74* & .32\\
-Item15 & 1.64 & 1.18 & 1.79 & 2.02 & 0.60* & .15\\
-Item16 & 3.51 & 1.30 & -0.70 & -0.59 & 0.85* & .39\\
-Item17 & 1.96 & 0.98 & 1.02 & 0.69 & 0.82* & .05\\
-Item18 & 2.44 & 1.31 & 0.38 & -1.14 & 0.86* & .11\\
-Item19 & 3.80 & 1.29 & -0.87 & -0.42 & 0.82* & .17\\
-Item20 & 4.01 & 1.40 & -1.22 & 0.07 & 0.70* & .13\\
-Item21 & 1.33 & 0.91 & 3.03 & 8.43 & 0.41* & .01\\
-Item22 & 2.59 & 1.41 & 0.27 & -1.27 & 0.86* & .19\\
-Item23 & 1.31 & 0.81 & 2.75 & 6.92 & 0.43* & .21\\
-Item24 & 1.47 & 1.18 & 2.38 & 4.00 & 0.43* & .28\\
-Item25 & 2.56 & 1.27 & 0.33 & -1.00 & 0.89* & .11\\
-Item26 & 1.54 & 1.25 & 2.13 & 2.86 & 0.46* & .36\\
-Item27 & 4.30 & 1.08 & -1.79 & 2.53 & 0.67* & .22\\
-Item28 & 2.27 & 1.39 & 0.74 & -0.81 & 0.81* & .25\\
-Item29 & 3.26 & 1.09 & -0.26 & -0.45 & 0.91* & .14\\
-Item30 & 2.22 & 1.48 & 0.71 & -1.02 & 0.76* & .30\\
-Item31 & 1.05 & 0.36 & 7.23 & 52.98 & 0.13* & .18\\
-Item32 & 1.54 & 1.21 & 2.07 & 2.75 & 0.49* & .31\\
-Item33 & 1.04 & 0.33 & 8.99 & 85.28 & 0.10* & .16\\
-Item34 & 3.36 & 1.38 & -0.48 & -1.03 & 0.87* & .16\\
-Item35 & 2.26 & 1.25 & 0.70 & -0.60 & 0.85* & .19\\
-Item36 & 2.36 & 1.22 & 0.59 & -0.62 & 0.87* & .25\\
-Item37 & 1.14 & 0.59 & 4.79 & 24.05 & 0.25* & .16\\
-Item38 & 2.25 & 1.27 & 0.69 & -0.64 & 0.84* & .18\\
-Item39 & 3.93 & 1.48 & -1.06 & -0.44 & 0.71* & .18\\
-Item40 & 3.57 & 1.07 & -0.65 & -0.17 & 0.88* & .21\\
-Item41 & 3.55 & 1.65 & -0.60 & -1.34 & 0.76* & .43\\
-Item42 & 3.00 & 1.62 & -0.08 & -1.61 & 0.83* & .44\\
-Item43 & 1.56 & 1.23 & 2.00 & 2.45 & 0.50* & .32\\
-Item44 & 2.97 & 1.20 & -0.06 & -0.94 & 0.91* & -.10\\
-Item45 & 2.79 & 1.55 & 0.19 & -1.48 & 0.85* & .20\\
-Item46 & 2.14 & 1.31 & 0.77 & -0.78 & 0.80* & .26\\
-Item47 & 2.18 & 0.90 & 0.60 & 0.12 & 0.86* & .26\\
-Item48 & 1.48 & 1.11 & 2.18 & 3.35 & 0.48* & .24\\
+Item11 & 2.18 & 0.90 & 0.60 & 0.12 & 0.86* & .26\\
+Item12 & 2.36 & 1.22 & 0.59 & -0.62 & 0.87* & .25\\
+Item13 & 2.73 & 1.46 & 0.20 & -1.36 & 0.87* & .33\\
+Item14 & 2.14 & 1.31 & 0.77 & -0.78 & 0.80* & .26\\
+Item15 & 3.26 & 1.09 & -0.26 & -0.45 & 0.80* & .14\\
+Item16 & 1.56 & 1.23 & 2.00 & 2.45 & 0.50* & .32\\
+Item17 & 1.54 & 1.21 & 2.07 & 2.75 & 0.49* & .31\\
+Item18 & 1.12 & 0.49 & 5.02 & 27.80 & 0.25* & .16\\
+Item19 & 1.05 & 0.36 & 7.23 & 52.98 & 0.13* & .18\\
+Item20 & 1.04 & 0.33 & 8.99 & 85.28 & 0.10* & .16\\
+Item21 & 1.14 & 0.59 & 4.79 & 24.05 & 0.25* & .16\\
+Item22 & 3.57 & 1.07 & -0.65 & -0.17 & 0.88* & .21\\
+Item23 & 2.56 & 1.27 & 0.33 & -1.00 & 0.89* & .11\\
+Item24 & 4.14 & 0.99 & -1.23 & 1.14 & 0.79* & .19\\
+Item25 & 2.59 & 1.41 & 0.27 & -1.27 & 0.86* & .19\\
+Item26 & 2.25 & 1.27 & 0.69 & -0.64 & 0.84* & .18\\
+Item27 & 3.80 & 1.29 & -0.87 & -0.42 & 0.82* & .17\\
+Item28 & 3.76 & 1.14 & -0.68 & -0.45 & 0.86* & .00\\
+Item29 & 2.44 & 1.31 & 0.38 & -1.14 & 0.86* & .11\\
+Item30 & 1.48 & 1.11 & 2.18 & 3.35 & 0.48* & .24\\
+Item31 & 3.00 & 1.62 & -0.08 & -1.61 & 0.83* & .44\\
+Item32 & 3.55 & 1.65 & -0.60 & -1.34 & 0.76* & .43\\
+Item33 & 3.62 & 1.64 & -0.68 & -1.25 & 0.74* & .32\\
+Item34 & 3.42 & 1.83 & -0.45 & -1.69 & 0.69* & .33\\
+Item35 & 3.86 & 1.67 & -0.99 & -0.85 & 0.65* & .23\\
+Item36 & 1.54 & 1.25 & 2.13 & 2.86 & 0.46* & .36\\
+Item37 & 1.33 & 0.91 & 3.03 & 8.43 & 0.41* & .01\\
+Item38 & 4.30 & 1.08 & -1.79 & 2.53 & 0.67* & .22\\
+Item39 & 1.96 & 0.98 & 1.02 & 0.69 & 0.82* & .05\\
+Item40 & 2.16 & 1.19 & 0.71 & -0.54 & 0.84* & .14\\
+Item41 & 1.31 & 0.81 & 2.75 & 6.92 & 0.43* & .21\\
+Item42 & 3.93 & 1.48 & -1.06 & -0.44 & 0.71* & .18\\
+Item43 & 1.64 & 1.18 & 1.79 & 2.02 & 0.60* & .15\\
+Item44 & 3.51 & 1.30 & -0.70 & -0.59 & 0.85* & .39\\
+Item45 & 2.22 & 1.48 & 0.71 & -1.02 & 0.76* & .30\\
+Item46 & 1.76 & 1.23 & 1.35 & 0.44 & 0.66* & .38\\
+Item47 & 2.11 & 1.17 & 0.77 & -0.39 & 0.83* & .32\\
+Item48 & 2.60 & 1.25 & 0.29 & -0.86 & 0.89* & .35\\
 \bottomrule
@@
 
-The initial five-factor solution with all 48 items showed presence of cross-loading items (item 42, 16, \& 1) and poor factor loading (\textless.30) items (item 20, 3 ,15, 17, 40, 4, 11, 39, 18, 45, 29, 25, 8 , \& 46).
-At first, we discarded the items with poor factor-loading and ran another EFA on the remaining 34 items.
-This iteration of EFA also appeared as a misfit with items with poor factor-loading (Item 12, 22, 38, 6) and cross-loading (items 23, 31, 37, 48) .
-Another two rounds of EFA were conducted with gradually identifying problematic items and discarding them from the model.
-Finally, a five-factor EFA solution with 23 items was accepted with low RMSR = 0.04 (Brown, 2015), all factor-loading higher than .30 and no cross-loading greater than .30.
+Three rounds of EFA starting with all 48 items were conducted and problematic items were gradually discarded (cross-loading items and poor factor loading (\textless.30) items).
+Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 (Brown, 2015), all factor-loading higher than .30 and no cross-loading greater than .30.
 We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (see the supplementary).
 Table\ref{tab:TabEFA5} displays the factor-loading (structural coefficients) and communality of the items.
-The absolute value of the factor-loading ranged from -.47 to .99 indicating strong coefficients.
-The commonalities ranged between .10 to .99.
-However, the histogram of the absolute values of non-redundant residual-correlations (Fig\ref{fig:Residuals} showed 26.09\% correlations greater than the absolute value of .05, indicating under-factoring.
+The absolute value of the factor-loading ranged from -.49 to .99 indicating strong coefficients.
+The commonalities ranged between .11 to .99.
+However, the histogram of the absolute values of non-redundant residual-correlations (Fig\ref{fig:Residuals} showed 26.00\% correlations greater than the absolute value of .05, indicating a possible under-factoring.
 (C.
@@
 Subsequently, we fitted a six-factor solution.
-However, a factor emerged with only two salient variable loading in the six-factor solution, thus disqualifying the six-factor solution.
+However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution.
 
-In the five-factor solution, the first factor contained three items and explained 11\% of the total variance with a satisfactory internal reliability coefficient (\(\alpha\) =.86).
+In the five-factor solution, the first factor contained three items and explained 10.25\% of the total variance with a satisfactory internal reliability coefficient (\(\alpha\) = .86).
 All the items in this factor stemmed from the individual's preference to use blue light filters in different light environments.
-The second factor contained six items and explained 10\% of the total variance with a satisfactory internal reliability coefficient (\(\alpha\) =.71).
+The second factor contained six items and explained 9.93\% of the total variance with a satisfactory internal reliability coefficient (\(\alpha\) = .71).
 Items under this factor commonly investigate an individual's hours spent outdoor.
-The third factor contained five items and explained 9\% of the total variance.
+The third factor contained five items and explained 8.83\% of the total variance.
 Items under this factor dealt with the specific behaviors pertaining to sleep.
-However, the internal consistency reliability coefficient was not satisfactory (\(\alpha\) =.62).
-The fourth factor contained three items and explained 9\% of the total variance with a satisfactory internal consistency (\(\alpha\) =.77).
-These three items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time.
-Lastly, the fifth factor contained six items and explained 6\% of the total variance.
-Under this factor tried to measure an individual's behavior lead by the awareness of light's influence on health.
-However, this factor showed unsatisfactory internal consistency reliability (\(\alpha\) =.49).
+However, the internal consistency reliability coefficient was not satisfactory (\(\alpha\) = .68).
+The fourth factor contained five items and explained 8.44\% of the total variance with an internal consistency coefficient, \(\alpha\) = .62.
+These five items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time.
+Lastly, the fifth factor contained six items and explained 6.14\% of the total variance.This factor tried to measure an individual's behavior lead by the awareness of light's influence on health.
+However, this factor showed unsatisfactory internal consistency reliability (\(\alpha\) = .53).
 It is essential to attain a balance between psychometric properties and the interpretability of the common themes when exploring the latent structure.
@@
 \midrule
-item43 & 0.99 & - & - & - & - & 0.99\\
-item26 & 0.93 & - & - & - & - & 0.9\\
-item32 & 0.8 & - & - & - & - & 0.67\\
-item10 & - & 0.82 & - & - & - & 0.68\\
-item47 & - & 0.82 & - & - & - & 0.7\\
-item36 & - & 0.63 & - & - & - & 0.45\\
-item44 & - & -0.47 & - & - & - & 0.24\\
-item35 & - & 0.46 & - & - & - & 0.24\\
-item13 & - & 0.34 & - & - & - & 0.13\\
-item14 & - & - & 0.89 & - & - & 0.81\\
-item41 & - & - & 0.7 & - & - & 0.6\\
-item7 & - & - & 0.66 & - & - & 0.45\\
-item27 & - & - & 0.38 & - & - & 0.21\\
-item21 & - & - & -0.34 & - & - & 0.12\\
-item34 & - & - & - & 0.84 & - & 0.74\\
-item19 & - & - & - & 0.8 & - & 0.64\\
-item2 & - & - & - & 0.67 & - & 0.54\\
-item5 & - & - & - & - & 0.69 & 0.51\\
-item24 & - & - & - & - & 0.54 & 0.33\\
-item30 & - & - & - & - & 0.52 & 0.29\\
-item1 & - & - & - & - & 0.35 & 0.13\\
-item16 & - & - & - & - & 0.31 & 0.21\\
-item28 & - & - & - & - & 0.31 & 0.1\\
-\% of variance & 11 & 10 & 9 & 9 & 6 & -\\
+item16 & 0.99 & - & - & - & - & 0.99\\
+item36 & 0.94 & - & - & - & - & 0.9\\
+item17 & 0.8 & - & - & - & - & 0.66\\
+item11 & - & 0.8 & - & - & - & 0.64\\
+item10 & - & 0.76 & - & - & - & 0.59\\
+item12 & - & 0.65 & - & - & - & 0.47\\
+item7 & - & 0.5 & - & - & - & 0.27\\
+item8 & - & -0.5 & - & - & - & 0.25\\
+item9 & - & 0.32 & - & - & - & 0.11\\
+item27 & - & - & 0.8 & - & - & 0.66\\
+item3 & - & - & 0.8 & - & - & 0.68\\
+item40 & - & - & 0.65 & - & - & 0.46\\
+item30 & - & - & 0.45 & - & - & 0.35\\
+item41 & - & - & -0.36 & - & - & 0.33\\
+item33 & - & - & - & 0.74 & - & 0.56\\
+item32 & - & - & - & 0.73 & - & 0.62\\
+item35 & - & - & - & 0.66 & - & 0.45\\
+item37 & - & - & - & -0.39 & - & 0.17\\
+item38 & - & - & - & 0.36 & - & 0.18\\
+item46 & - & - & - & - & 0.6 & 0.42\\
+item45 & - & - & - & - & 0.59 & 0.37\\
+item25 & - & - & - & - & 0.41 & 0.19\\
+item4 & - & - & - & - & 0.41 & 0.22\\
+item1 & - & - & - & - & 0.4 & 0.17\\
+item26 & - & - & - & - & 0.39 & 0.17\\
+internal Consistency & .86 & .71 & .68 & .62 & .53 & -\\
+\% of variance & 10.25 & 9.93 & 8.83 & 8.44 & 6.14 & -\\
 \bottomrule
@@
 
+\leavevmode\hypertarget{ref-R-car}{}%
+Fox, J., \& Weisberg, S. (2019). \emph{An {R} companion to applied regression} (Third). Thousand Oaks {CA}: Sage. Retrieved from \url{https://socialsciences.mcmaster.ca/jfox/Books/Companion/}
+
+\leavevmode\hypertarget{ref-R-carData}{}%
+Fox, J., Weisberg, S., \& Price, B. (2020). \emph{carData: Companion to applied regression data sets}. Retrieved from \url{https://CRAN.R-project.org/package=carData}
+
+\leavevmode\hypertarget{ref-R-Hmisc}{}%
+Harrell Jr, F. E., Charles Dupont, with contributions from, \& others., many. (2021). \emph{Hmisc: Harrell miscellaneous}. Retrieved from \url{https://CRAN.R-project.org/package=Hmisc}
+
 \leavevmode\hypertarget{ref-R-purrr}{}%
@@
 
+\leavevmode\hypertarget{ref-R-lattice}{}%
+Sarkar, D. (2008). \emph{Lattice: Multivariate data visualization with r}. New York: Springer. Retrieved from \url{http://lmdvr.r-forge.r-project.org}
+
 \leavevmode\hypertarget{ref-schonbrodtWhatSampleSize2013}{}%
@@
 Shapiro, S. S., \& Wilk, M. B. (1965). An analysis of variance test for normality (complete samples). \emph{Biometrika}, \emph{52}(3-4), 591--611. \url{https://doi.org/10.1093/biomet/52.3-4.591}
+
+\leavevmode\hypertarget{ref-R-survival-book}{}%
+Terry M. Therneau, \& Patricia M. Grambsch. (2000). \emph{Modeling survival data: Extending the {C}ox model}. New York: Springer.
 
@@
 
+\leavevmode\hypertarget{ref-R-Formula}{}%
+Zeileis, A., \& Croissant, Y.
+(2010).
+Extended model formulas in {R}: Multiple parts and multiple responses.
+\emph{Journal of Statistical Software}, \emph{34}(1), 1--13.
+\url{https://doi.org/10.18637/jss.v034.i01}
+
 \leavevmode\hypertarget{ref-R-kableExtra}{}%

### 2021-09-04 manuscript.Rmd

@@
 library(lavaan)
-library(semPlot)
+library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
 library(semTools)
@@
 CFA.descriptives <- descriptives.data[429:690, ]
+IRT.descriptives <- descriptives.data
 
@@
 
-### EFA data
-EFA.data <- sem.data[1:428, ]
-
-### CFA Data
-CFA.data <- sem.data[429:690,]
-CFARitem8 = recode(CFA.data$item8, '1=5; 2=4; 3=3; 4=2; 5=1')
-CFARitem37 = recode(CFA.data$item37, '1=5; 2=4; 3=3; 4=2; 5=1')
-CFA.data <- CFA.data %>% 
-  mutate(Ritem8 = CFARitem8, Ritem37 = CFARitem37)
-
 ### IRT data
@@
 #Use these  data frames for descriptive
-EFA.descriptives #Only EFA
-CFA.descriptives #Only CFA
+EFA.descriptives #Only EFA, n =428
+CFA.descriptives #Only CFA, n =262  
+IRT.descriptives# Total sample, n = 690
 
@@
 
-```{r Normality assumption EFA, include=FALSE}
+```{r EFAdata, include=FALSE}
+### EFA data
+EFA.data <- sem.data[1:428, ]
+```
+
+```{r EFAassumptions, include=FALSE}
 
@@
 as.table(normality.tab)
-
 rownameprefix <- "Item"
@@
 my.item.names <- paste(rownameprefix,rownamesufix, sep = "" )
-
 rownames(normality.tab) <- my.item.names
@@
 
-# Descriptives
+# Descriptive Stats
 Descriptives <- psych::describe(EFA.data)
@@
 
-colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics", 
-                           "Item-Total Correlation")
+colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics","Item-Total Correlation")
 
@@
 my.names <- paste(rownameprefix,rownamesufix, sep = "" )
+rownames(Des.combined) = (my.names)
+```
 
-rownames(Des.combined) = (my.names)
-
+```{r CorrelationMatrix, include=FALSE}
 #Polychoric Correlation matrix
@@
 min.cor <- abs(min(upper)) #minimum cor.coefficient of the matrix
-max.cor <- abs(max(upper)) # max. correlation coefficent of the matrix
+max.cor <- abs(max(upper)) # max. correlation coefficient of the matrix
 
-# Calculating the percentange of correlations higher than .30
+# Calculating the percentage of correlations higher than .30
 
@@
 cor.per <- print (BigR/totR)*100
+```
 
+```{r ItemAnalysis, include=FALSE}
 # Item analysis
@@
 The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cutoff value (.50) indicating a mediocre sample [@hutchesonMultivariateSocialScientist1999].
+Table\@ref(tab:tabDes) summarizes the univariate descriptive statistics for the 48 items.
+some of the items were skewed with high Kurtosis values.
+Our data violated both univariate normality (Shapiro-Wilk statistics; [@shapiroAnalysisVarianceTest1965]) and multivariate normality assumptions (Marida's test;[@mardiaMeasuresMultivariateSkewness1970]).
+Multivariate skew was  = `r printnum(mardia$b1p)` (p <0.001) and multivariate kurtosis was = `r printnum(mardia$b2p)` (p <0.001).
+Due to these violations and ordinal nature of the response data  polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018].
+Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001] indicated the correlations between items are adequate for the EFA.
+However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than .30.
+The inter item correlation ranged between `r apa(min.cor,2,F)` to `r apa(max.cor,2,F)`.
+And the corrected item-total correlations ranged between `r apa(low.r.corec,2,F)` to `r apa(high.r.corec,2,F)`.
 
@@
 ```
-
-Table\@ref(tab:tabDes) summarizes the univariate descriptive statistics for the 48 items.
-some of the items were skewed with high Kurtosis values.
-Our data violated both univariate normality (Shapiro-Wilk statistics; [@shapiroAnalysisVarianceTest1965]) and multivariate normality assumptions (Marida's test;[@mardiaMeasuresMultivariateSkewness1970]).
-Multivariate skew was  = `r printnum(mardia$b1p)` (p <0.001) and multivariate kurtosis was = `r printnum(mardia$b2p)` (p <0.001).
-Due to these violations and ordinal nature of the response data  polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018].
-Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001] indicated the correlations between items are adequate for the EFA.
-However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than .30.
-The inter item correlation ranged between `r apa(min.cor,2,F)` to `r apa(max.cor,2,F)`.
-And the corrected item-total correlations ranged between `r apa(low.r.corec,2,F)` to `r apa(high.r.corec,2,F)`.
 
@@
 ```{r Cronbach alpha for 5 fators, message=TRUE, warning=FALSE, include=FALSE}
+
 Five.F1 <- dplyr::select(EFA.data, item16, item36, item17)
@@
 
-#EFA.factor <- sapply(EFA.data, as.factor)
 #correlations <- polychoric(EFA.factor, correct = 0)
@@
 
-```{r CFA 23 items, eval=FALSE, include=FALSE}
+```{r CFA data frame, include=FALSE}
 
-#CFA.data <- sem.data[429:690,]
+### CFA Data
+CFA.data <- sem.data[429:690,]
+CFARitem8 = recode(CFA.data$item8, '1=5; 2=4; 3=3; 4=2; 5=1')
+CFARitem37 = recode(CFA.data$item37, '1=5; 2=4; 3=3; 4=2; 5=1')
+CFARitem26 = recode(CFA.data$item26, '1=5; 2=4; 3=3; 4=2; 5=1')
+CFA.data <- CFA.data %>% 
+  mutate(Ritem8 = CFARitem8, Ritem37 = CFARitem37, Ritem26 = CFARitem26)
+```
 
-Ritem44 = recode(CFA.data$item44, '1=5; 2=4; 3=3; 4=2; 5=1')
-Ritem21 = recode(CFA.data$item44, '1=5; 2=4; 3=3; 4=2; 5=1')
+```{r CFA 25items, include=FALSE }
 
-CFA.data <- CFA.data %>% 
-  mutate(Ritem44 = Ritem44, Ritem21 = Ritem21)
+LB.model.Cor.1 <- "F1 =~ item16 + item36 + item17
+                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
+                 F3 =~  item27+ item3+ item40 + item30 + item41
+                 F4 =~ a1*item32 +item35 + Ritem37 + item38+ a2*item33 
+                 F5 =~ item46+ item45+ item25+ item4+ item1+ item26
 
-LB.model.Cor <- "F1 =~ item43 + item26 + item32
-                 F2 =~ item10 + item47 + item36 + Ritem44 + item35 + item13
-                 F3 =~  item14 + item41+ item7 + item27 + Ritem21
-                 F4 =~ item19 + item34 + item2
-                 F5 =~ item5 + item24 + item30 + item1 + item16 + item28"
+a1==a2"
 
-fit.Cor <- cfa(LB.model.Cor, data = CFA.data, estimator = "MLR", mimic = "Mplus", check.gradient = FALSE)
+fit.Cor.1 <- cfa(LB.model.Cor.1, data = CFA.data, ordered = names(CFA.data),estimator = "WLSMV")
 
 ## Summary of Model 
-summary(fit.Cor, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
+summary(fit.Cor.1, fit.measures =TRUE,standardized = TRUE)
 
 ## Selected Fit measures 
-fit.1 <- fitmeasures (fit.Cor,c("gfi", "agfi", "nfi","rfi", 
-                       "cfi.robust","tli.robust",
+fit.1 <- fitmeasures (fit.Cor.1,c("gfi", "agfi", "nfi","rfi", 
+                       "cfi.scaled","tli.scaled",
                        "rmsea.robust", 
@@
 
-semTools::reliability(fit.Cor)
+semTools::reliability(fit.Cor.1)
 
@@
 
-```{r CFA23withMI, eval=FALSE, include=FALSE}
-LB.model.Cor.3 <- "F1 =~ item43 + item26 + item32
-             F2 =~ item10 + item47 + item36 + item44 + item35 + item13
-            F3 =~  item14 + item41+ item7 + item27 + item21
-            F4 =~ item19 + item34 + item2
-F5 =~ item5 + item24 + item30 + item1 + item16 + item28 
-item44 ~~ item13
-item14 ~~  item7
-item10 ~~ item13"
+```{r mod1, include=FALSE}
+modfit.Cor.one <- modindices(fit.Cor.1, sort. = TRUE) 
+modfit.Cor.one[modfit.Cor.one$mi>3.84,]
+```
+
+```{r CFA23withMI, include=FALSE}
+LB.model.Cor.2 <- "F1 =~ item16 + item36 + item17
+                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
+                 F3 =~  item27+ item3+ item40 + item30 + item41
+                 F4 =~ a1*item32 +item35 + item38+ a2*item33 
+                 F5 =~ item46+ item45+ item25+ item4+ item1
+                       a1==a2 
+                item30 ~~  item41"
+
+#Ritem26 & 37 are removed
 
 ## Fit the model 
-fit.Cor.3 <- cfa(LB.model.Cor.3, data = CFA.data, estimator = "MLR", mimic = "Mplus")
+fit.Cor.2 <- cfa(LB.model.Cor.2, data = CFA.data, ordered = names(CFA.data),estimator = "WLSMV")
 
-reliability <- semTools::reliability(fit.Cor.3, return.total = T)
+reliability <- semTools::reliability(fit.Cor.2, return.total = T)
 as.table(reliability)
-## Summary of Model 
-summary(fit.Cor.3, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
-
-## Selected Fit measures 
-fit.3 <- fitmeasures (fit.Cor.3,c("gfi", "agfi", "nfi","rfi", 
-                       "cfi.robust","tli.robust",
-                       "rmsea.robust", 
-                       "srmr","aic"))
-
-rownames <-  ("fitIndices")
-colnames <- c("gfi", "agfi", "nfi","rfi", 
-                       "cfi.robust","tli.robust",
-                       "rmsea.robust", 
-                       "srmr","aic")
-
-```
-
-```{r CFI18items, eval=FALSE, include=FALSE}
-LB.model.Cor.2 <- "F1 =~ item43 + item26 + item32
-             F2 =~ item10 + item47 + item36 + item44 + item35 
-            F3 =~  item14 + item41+ item7 
-            F4 =~ item19 + item34 + item2
-F5 =~ item5 + item24 + item30 + item16 
-item14 ~~  item7"
-
-#item 1 &28 discarded from F5;
-#item13 discarded from F2
-#item 27 & 21 discarded from F3
-
-## Fit the model 
-fit.Cor.2 <- cfa(LB.model.Cor.2, data = LB.cfa, estimator = "MLR", mimic = "Mplus")
-
 ## Summary of Model 
@@
 fit.2 <- fitmeasures (fit.Cor.2,c("gfi", "agfi", "nfi","rfi", 
-                       "cfi.robust","tli.robust",
-                       "rmsea.robust", 
+                       "cfi.scaled","tli.scaled",
+                       "rmsea.scaled", 
                        "srmr","aic"))
 
-rownames <-  ("fitIndices")
-colnames <- c("gfi", "agfi", "nfi","rfi", 
-                       "cfi.robust","tli.robust",
-                       "rmsea.robust", 
-                       "srmr","aic")
+```
+
+```{r mod2, include=FALSE}
+modfit.Cor.one <- modindices(fit.Cor.2, sort. = TRUE) 
+modfit.Cor.one[modfit.Cor.one$mi>3.84,]
+```
+
+```{r figcfa, fig.cap = "(A) Five Factor Model of LEBA", , out.width="100%",  warning=FALSE}
+library(semPlot)
+
+semPaths (fit.Cor.2 , 
+          what= "std",
+          #whatLabels = "std",
+          intercepts = F,
+          #style ="lisrel",
+          #residScale = 6,
+          theme = "colorblind",
+          nCharNodes = 0,
+          reorder =T,
+          rotation =2,
+          layout ="tree",
+          cardinal = T,
+          curvePivot =T,
+          sizeMan =8,
+          sizeMan2 = 1.5,
+          sizeLat = 8,
+          #edge.color = "black",
+          thresholds = FALSE,
+          equalizeManifests =T,
+          fade = FALSE,
+          edge.label.cex = .65,
+          exoCov = FALSE)
 

### 2021-09-04 manuscript.Rmd

@@
 
-#Commonality
+#Communality
 Fac.5 <- fa.5F.3
@@
 
-# loadings
+# loading
 min.loadings <- min(Fac.5$loadings)
@@
                  F4 =~ a1*item32 +item35 + Ritem37 + item38+ a2*item33 
-                 F5 =~ item46+ item45+ item25+ item4+ item1+ item26
+                 F5 =~ item46+ item45+ item25+ item4+ item1+ Ritem26
 
@@
                        "cfi.scaled","tli.scaled",
-                       "rmsea.robust", 
-                       "srmr","aic"))
+                       "rmsea.scaled", 
+                       "srmr"))
 
@@
                        "rmsea.scaled", 
-                       "srmr","aic"))
+                       "srmr"))
 

### 2021-09-04 manuscript.Rmd

@@
 CFA.descriptives <- descriptives.data[429:690, ]
-IRT.descriptives <- descriptives.data
 
@@
 colnames(sem.data) <- colnam
-
-### IRT data
-IRT.data <- sem.data
-IRTRitem8 = recode(IRT.data$item8, '1=5; 2=4; 3=3; 4=2; 5=1')
-IRTRitem37 = recode(IRT.data$item37, '1=5; 2=4; 3=3; 4=2; 5=1')
-IRT.data <- IRT.data %>% 
-  mutate(Ritem8 = IRTRitem8, Ritem37 = IRTRitem37)
 ```
@@
 CFA.descriptives #Only CFA, n =262  
-IRT.descriptives# Total sample, n = 690
+descriptives.data# Total sample, n = 690
 
@@
 
+```{r IRT data, include=FALSE}
+
+F1.IRT.data <- sem.data %>% 
+  select(item16, item36,  item17)
+
+F2.IRT.data <- sem.data %>% 
+  select(item16, item36,  item17)
+
+"F1 =~ item16 + item36 + item17
+                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
+                 F3 =~  item27+ item3+ item40 + item30 + item41
+                 F4 =~ a1*item32 +item35 + item38+ a2*item33 
+                 F5 =~ item46+ item45+ item25+ item4+ item1
+
+IRTRitem8 = recode(IRT.data$item8, '1=5; 2=4; 3=3; 4=2; 5=1')
+
+IRT.data <- IRT.data %>% 
+  mutate(Ritem8 = IRTRitem8, Ritem37 = IRTRitem37)
+```
+
 # Discussion

### 2021-09-04 manuscript.Rmd

@@
 
-```{r,  out.width = '100%', out.height= '100%', fig.align = 'center', fig.cap='Development and psychometric properties of LEBA '}
+```{r FlowchartFig,  out.width = '100%', out.height= '100%', fig.align = 'center', fig.cap='Development and psychometric properties of LEBA '}
 knitr::include_graphics('Flowchart1.png')
@@
 Due to these violations and the ordinal nature of our response data, we used a polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA.
-We employed principal axis (pa) a factor extraction method with varimax rotation.
+We employed principal axis (pa), a factor extraction method with varimax rotation.
 PA is robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020].
@@
 
-```{r facid, out.height= "50%",  fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot, (C) Hull method', fig.show="hold",fig.ncol = 2, out.width="50%",  warning=FALSE}
+```{r factor_identification_fig, out.height= "50%",  fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot, (C) Hull method', fig.show="hold",fig.ncol = 2, out.width="50%",  warning=FALSE}
 knitr::include_graphics('parallel.png')
@@
 
-Three rounds of EFA starting with all 48 items were conducted and problematic items were gradually discarded (cross-loading items and poor factor loading (<.30) items).
+Three rounds of EFA with all 48 items were conducted, and problematic items were gradually discarded (cross-loading items and poor factor loading (<.30) items).
 Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 [@brownConfirmatoryFactorAnalysis2015], all factor-loading higher than .30 and no cross-loading greater than .30.
@@
 These five items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time.
-Lastly, the fifth factor contained six items and explained `r apa(var5,2,F)`% of the total variance.This factor tried to measure an individual's behavior lead by the awareness of light's influence on health.
+Lastly, the fifth factor contained six items and explained `r apa(var5,2,F)`% of the total variance.
+This factor tried to measure an individual's behavior lead by the awareness of light's influence on health.
 However, this factor showed unsatisfactory internal consistency reliability ($\alpha$ = `r apa(F5.alpha,2,F)`).
@@
 
-LB.model.Cor.1 <- "F1 =~ item16 + item36 + item17
+LB.model.Cor.1 <- "F1 =~ a1*item16 + item36 + a2*item17
                  F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
                  F3 =~  item27+ item3+ item40 + item30 + item41
-                 F4 =~ a1*item32 +item35 + Ritem37 + item38+ a2*item33 
-                 F5 =~ item46+ item45+ item25+ item4+ item1+ Ritem26
-
-a1==a2"
+                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
+                 F5 =~ item46+ item45+ item25+ item4+ item1 
+                       a1==a2
+                       a3==a4"
 
@@
 ## Summary of Model 
-summary(fit.Cor.1, fit.measures =TRUE,standardized = TRUE)
+cfa.sum.1 <- summary(fit.Cor.1, fit.measures =TRUE,standardized = TRUE,rsq =TRUE)
 
@@
                        "cfi.scaled","tli.scaled",
-                       "rmsea.scaled", 
-                       "srmr"))
-
-semTools::reliability(fit.Cor.1)
+                       "rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr"))
+
+reliability1 <- semTools::reliability(fit.Cor.1)
 
@@
 ```{r CFA23withMI, include=FALSE}
-LB.model.Cor.2 <- "F1 =~ item16 + item36 + item17
+LB.model.Cor.2 <- "F1 =~ a1*item16 + item36 + a2*item17
                  F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
                  F3 =~  item27+ item3+ item40 + item30 + item41
-                 F4 =~ a1*item32 +item35 + item38+ a2*item33 
+                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
                  F5 =~ item46+ item45+ item25+ item4+ item1 
                        a1==a2
-                item30 ~~  item41"
-
-#Ritem26 & 37 are removed
+                       a3==a4
+                item30 ~~  item41
+                       "
+
+#item26 & 37 are removed
 
@@
 
-reliability <- semTools::reliability(fit.Cor.2, return.total = T)
-as.table(reliability)
+reliability2 <- semTools::reliability(fit.Cor.2, return.total = T)
 ## Summary of Model 
-summary(fit.Cor.2, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
+cfa.sum.2 <- summary(fit.Cor.2, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
 
@@
                        "cfi.scaled","tli.scaled",
-                       "rmsea.scaled", 
-                       "srmr"))
+                       "rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr"))
 
@@
 modfit.Cor.one[modfit.Cor.one$mi>3.84,]
+```
+
+We conducted a categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator as our response data was in ordinary nature [@desjardinsHandbookEducationalMeasurement2018a].
+Commonly used Model fit suggestions of [@huCutoffCriteriaFit1999] focused on (i) the comparative fit index (CFI;) (ii) the Tucker Lewis index (TLI) (CFI/TLI, $goodfit \geq .95$, $acceptable fit\geq .90$) (ii) the root mean square error of approximation (RMSEA; close to .06 or below), (iii) the standardized root mean square (SRMR; close to .08 or below) to estimate the model fit.
+The chi-square test is also used to estimate the absolute model fit.
+Table\@ref(tab:tabCfa) summarizes the fit indices of our fitted model.
+The fitted model failed to attain an absolute fit estimated by the chi-square test.
+However, the chi-square test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit [@RN1231].
+The other absolute fit index we obtained in our analysis was SRMR which does not work well with categorical data [@RN1272].
+Subsequently, we judged the model fit based on the incremental fit indices: CFI, TLI and parsimony fit index-RMSEA.
+Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 and 19-17 .
+However SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`).
+Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI])   and SRMR value (SRMR = `r apa(fit.2[10],2,F)`) was also close to the suggestions of @huCutoffCriteriaFit1999.
+
+```{r tabCfa, results='asis'}
+CFa.matrix <- matrix("NA", nrow =2, ncol = 9)
+colnames(CFa.matrix) = c("Model", "Chi-Squre", "df", "CFI", "TLI", "RMSEA", "RMSEA 90% Lower CI", "RMSEA 90% Upper CI", "SRMR")
+CFa.matrix[1,] = c("Five factor model", 
+                   apa(cfa.sum.1$FIT[6],2,T), 
+                   apa(cfa.sum.1$FIT[7],2,T), 
+                   apa(cfa.sum.1$FIT[19],2,F), 
+                   apa(cfa.sum.1$FIT[20],2,T),
+                   apa(cfa.sum.1$FIT[27],2,T),
+                   apa(cfa.sum.1$FIT[28],2,T),
+                   apa(cfa.sum.1$FIT[29],2,T),
+                   apa(cfa.sum.1$FIT[35],2,T))
+
+CFa.matrix[2,] = c("Five factor model", 
+                   apa(cfa.sum.2$FIT[6],2,T), 
+                   apa(cfa.sum.2$FIT[7],2,T), 
+                   apa(cfa.sum.2$FIT[19],2,F), 
+                   apa(cfa.sum.2$FIT[20],2,T),
+                   apa(cfa.sum.2$FIT[27],2,T),
+                   apa(cfa.sum.2$FIT[28],2,T),
+                   apa(cfa.sum.2$FIT[29],2,T),
+                   apa(cfa.sum.2$FIT[35],2,T))
+
+apa_table(CFa.matrix, caption = "Fit indices of CFA")
+
 ```
@@
 
+```{r InvarianceAnalysis_data, include=FALSE}
+invariance.data <- cbind(CFA.data, data$slypos_demographics_language.factor[429:690])
+colnames(invariance.data)[52] <- "English_Speaking"
+
+invariance.data %>% 
+  group_by(English_Speaking) %>% 
+  count()
+```
+
+```{r Invarianceshortcut}
+#library("semTools")
+invariance.model <- measurementInvariance(model = LB.model.Cor.2,
+                                          data = invariance.data,
+                                          group = "English_Speaking",
+                                          ordered =   names(CFA.data),
+                                          estimator = "WLSMV",
+                                          strict = T)
+invariance.model$fit.configural
+```
+
+```{r Invariance detail, include=FALSE}
+# Configural invariance ####
+
+LB.model.Cor.3 <- "F1 =~ a1*item16 + a2*item36 + item17
+                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
+                 F3 =~  item27+ item3+ item40 + item30 + item41
+                 F4 =~ a4*item32 +a3*item35 + item38+ item33 
+                 F5 =~ item46+ item45+ item25+ item4+ item1 
+                       a1==a2
+                       a4==a3
+                item30 ~~  item41
+F4~~1*F4"
+
+configural <- cfa(model = LB.model.Cor.2,
+                  data = invariance.data,
+                  group = "English_Speaking",
+                  ordered =   names(CFA.data),
+                  estimator = "WLSMV")
+
+summary(configural, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
+
+fitmeasures (configural,c("gfi", "agfi", "nfi","rfi", 
+                       "cfi.scaled","tli.scaled",
+                       "rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr"))
+
+weak <- cfa(model = LB.model.Cor.2,
+                  data = invariance.data,
+                  group = "English_Speaking",
+                  ordered =   names(CFA.data),
+                  estimator = "WLSMV", 
+            group.equal = "loadings")
+
+summary(weak, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
+
+fitmeasures (weak,c("gfi", "agfi", "nfi","rfi", 
+                       "cfi.scaled","tli.scaled",
+                       "rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr"))
+
+First.comp <- compareFit (configural, weak)
+summary(First.comp)
+
+strong <- cfa(model = LB.model.Cor.2,
+                  data = invariance.data,
+                  group = "English_Speaking",
+                  ordered =   names(CFA.data),
+                  estimator = "WLSMV", 
+              group.equal = c("loadings", "intercepts"))
+summary(strong, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
+
+Second.comp <- compareFit  (weak, strong)
+summary(Second.comp)
+
+strict <- cfa(model = LB.model.Cor.2,
+                  data = invariance.data,
+                  group = "English_Speaking",
+                  ordered =   names(CFA.data),
+                  estimator = "WLSMV",  
+              group.equal = c("loadings", "intercepts", "residuals"))
+
+summary(strict, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
+fitmeasures (strict,c("gfi", "agfi", "nfi","rfi", "cfi.robust","tli.robust","rmsea", "srmr","aic"))
+
+Third.comp <- compareFit(strict,strong)
+summary(Third.comp)
+
+structural <-cfa(model = LB.model.Cor.2,
+                  data = invariance.data,
+                  group = "English_Speaking",
+                  ordered =   names(CFA.data),
+                  estimator = "WLSMV",  
+                 group.equal = c("loadings", "intercepts", "residuals", "means","lv.variances","lv.covariances"))
+
+summary(strucrural, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
+fitmeasures (structural,c("gfi", "agfi", "nfi","rfi", "cfi","tli","rmsea", "srmr","aic"))
+
+fourth.comp <- compareFit  (structural,strict)
+summary(fourth.comp)
+comfit.par <- compareFit(configural, weak, strong, strict, structural)
+summary (comfit.par)
+
+#library("semTable")
+models <-  list("Configural" = configural, 
+                "Metric" = weak, 
+                "Scalar" = strong, 
+                "Residual" = strict, 
+                "Structural"=structural)
+
+Invariance.table <- compareLavaan(models,
+              nesting = "Configural > Metric > Scalar > Residual  > Structural", 
+              fitmeas = c("chisq", "df", "pvalue", "cfi.scaled","tli.scaled","rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr" ),
+              scaled = TRUE,
+              chidif = TRUE, digits = 2)
+
+```
+
+```{r Invariance Tab}
+apa_table(Invariance.table)
+```
+
 ## IRT

### 2021-09-09 manuscript.Rmd
Updates

@@
 library(Hmisc)
+library(semTable)
 r_refs("references.bib")
@@
 
-summary(strucrural, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
+summary(structural, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
 fitmeasures (structural,c("gfi", "agfi", "nfi","rfi", "cfi","tli","rmsea", "srmr","aic"))
@@
 
-#library("semTable")
 models <-  list("Configural" = configural, 

### 2021-09-10 manuscript.Rmd
Knitable Script (dependency problem yet to solve)

@@
 library(semTable)
+
 r_refs("references.bib")
@@
 
-```{r factor_identification_fig, out.height= "50%",  fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot, (C) Hull method', fig.show="hold",fig.ncol = 2, out.width="50%",  warning=FALSE}
+```{r factor_identification_fig, eval=FALSE, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot, fig.ncol=2, warning=FALSE, (C) Hull method', fig.show="hold", include=FALSE, out.height="50%", out.width="50%"}
 knitr::include_graphics('parallel.png')
@@
 
-```{r EFAplot,  fig.cap='Five Factor Solution', fig.align='center', out.width= "120%", out.height= "100%", warning=FALSE}
+```{r EFAplot, eval=FALSE, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, include=FALSE, out.height="100%", out.width="120%"}
 knitr::include_graphics('EFAplot.LR.png')
@@
 
-```{r IRT data, include=FALSE}
+```{r IRT data, eval=FALSE, include=FALSE}
 
@@
 
-"F1 =~ item16 + item36 + item17
-                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
-                 F3 =~  item27+ item3+ item40 + item30 + item41
-                 F4 =~ a1*item32 +item35 + item38+ a2*item33 
-                 F5 =~ item46+ item45+ item25+ item4+ item1
-
-IRTRitem8 = recode(IRT.data$item8, '1=5; 2=4; 3=3; 4=2; 5=1')
-
-IRT.data <- IRT.data %>% 
-  mutate(Ritem8 = IRTRitem8, Ritem37 = IRTRitem37)
 ```

### 2021-09-10 manuscript.Rmd

@@
 
-```{r setup, include = FALSE}
+```{r dependencymanager, include = FALSE}
+library(packrat)
+packrat::init()
+```
+
+```{r setup}
+
+knitr::opts_chunk$set(include = FALSE)
 library(papaja) # devtools::install_github("crsh/papaja")
@@
 library(rsvg) #For DiagrammeR
-library(correlation)
+#library(correlation)
 library(ggcorrplot)
 library(car) #Reversecoding
-library(Hmisc)
 library(semTable)
@@
 ```{r preparingData, include=FALSE}
-data <- readRDS("leba_2021-09-03.rds")
+data <- readRDS("leba_2021-09-08.rds")
 
@@
 ## Merge "0"s and "1"s into "1"s 9select,subset assign)
-descriptives.data[ , 6:53 ][ descriptives.data[ , 6:53 ] == 0 ] <- 1
+descriptives.data[ , 9:56 ][ descriptives.data[ , 9:56 ] == 0 ] <- 1
 EFA.descriptives <- descriptives.data[1:428,]
@@
 #Separating the EFA and CFA(only items)
-sem.data <- data[, 6:53] #EFA & CFA data
+sem.data <- data[, 9:56] #EFA & CFA data
 sem.data[ sem.data == 0] <- 1 #Merged "0"s and "1"s into "1"s
@@
   rsvg() %>%
-  png::writePNG("Flowchart1.png")
-
-```
-
-```{r FlowchartFig,  out.width = '100%', out.height= '100%', fig.align = 'center', fig.cap='Development and psychometric properties of LEBA '}
-knitr::include_graphics('Flowchart1.png')
+  png::writePNG("mFlowchart1.png")
+
+```
+
+```{r FlowchartFig, fig.align='center', fig.cap='Development', include=FALSE, out.height='100%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/Flowchart1.png')
 ```
@@
 
-#correlations <- polychoric(EFA.factor, correct = 0)
-
 # Parallel analysis
@@
       color=TRUE, col=c("black","red","blue"),
-      lty=c(1,2,3), lwd=1, legend=TRUE, file="parallel.png",
+      lty=c(1,2,3), lwd=1, legend=TRUE, file="Manuscript.figures/parallel.png",
       width=640, height=640, grdevice=png, seed=0, mat=NA, n=NA)
@@
 # HULL
-hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = TRUE,
+hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
         details = TRUE)
@@
 ```{r factor_identification_fig, eval=FALSE, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot, fig.ncol=2, warning=FALSE, (C) Hull method', fig.show="hold", include=FALSE, out.height="50%", out.width="50%"}
-knitr::include_graphics('parallel.png')
+knitr::include_graphics('Manuscript.figures/parallel.png')
 scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
       hline=NULL,add=F)
-knitr::include_graphics('HUll method.jpeg')
+knitr::include_graphics('Manuscript.figures/Hull.png')
 
@@
   rsvg() %>%
-  png::writePNG("EFAplot.LR.png")
-
-```
-
-```{r EFAplot, eval=FALSE, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, include=FALSE, out.height="100%", out.width="120%"}
-knitr::include_graphics('EFAplot.LR.png')
+  png::writePNG("Manuscript.figures/EFAplot.LR.png")
+
+```
+
+```{r EFAplot, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, include=FALSE, out.height="100%", out.width="120%"}
+knitr::include_graphics('Manuscript.figures/EFAplot.LR.png')
 
@@
 
-```{r Invarianceshortcut}
+```{r Invarianceshortcut, include=FALSE}
 #library("semTools")

### 2021-09-10 manuscript.Rmd
Dependency fix attempt 1

@@
 packrat::init()
+packrat::snapshot()
 ```
@@
   rsvg() %>%
-  png::writePNG("mFlowchart1.png")
+  png::writePNG("Manuscript.figures/Flowchart1.png")
 

### 2021-09-10 manuscript.Rmd

@@
 packrat::init()
-packrat::snapshot()
+#packrat::snapshot(ignore.stale=TRUE) #use to find and install required dependencies.
+```
+
+```{r eval=FALSE, include=FALSE}
+#if "packrat" doesnot work you can run this chunk manually to get all required packs"
+
+install.packages("devtools")
+install.packages("semTools")
+install.packages("MOTE")
+install.packages("psych")
+install.packages("dlookr")
+install.packages("tidyverse")
+install.packages("qgraph")
+install.packages("kableExtra")
+install.packages("paran")
+install.packages("EFA.MRFA")
+install.packages("rsvg")
+install.packages("ggcorrplot")
+install.packages("car")
+install.packages("semTable")
+install.packages("magick")
+devtools::install_github('rich-iannone/DiagrammeR')
+devtools::install_github("crsh/papaja", force = T)
+install.packages("DiagrammeRsvg")
+devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
+devtools::install_github("crsh/citr")
+
 ```
@@
 
-knitr::opts_chunk$set(include = FALSE)
 library(papaja) # devtools::install_github("crsh/papaja")
@@
 library(semTable)
-
+library(magick)
 r_refs("references.bib")
@@
 
-```{r FlowchartFig, fig.align='center', fig.cap='Development', include=FALSE, out.height='100%', out.width='100%'}
+```{r FlowchartFig, fig.align='center', fig.cap='Development', out.height='100%', out.width='100%'}
 knitr::include_graphics('Manuscript.figures/Flowchart1.png')
@@
 
-```{r tabDes, results='asis'}
+```{r tabDes}
 apa_table(Des.combined, caption = "Descriptive Statistics", align = "c", note = "*p<.001", longtable =T)
@@
 
-```{r factor_identification_fig, eval=FALSE, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot, fig.ncol=2, warning=FALSE, (C) Hull method', fig.show="hold", include=FALSE, out.height="50%", out.width="50%"}
+```{r factor_identification_fig, eval=FALSE, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot, fig.ncol=2, warning=FALSE, (C) Hull method', fig.show="hold", out.height="50%", out.width="50%"}
 knitr::include_graphics('Manuscript.figures/parallel.png')
@@
 #library(DiagrammeR)
-EFAplot.LR <- grViz("
+EFAplot <- grViz("
 digraph boxes_and_circles {
@@
 
-export_svg(EFAplot.LR) %>%
+export_svg(EFAplot) %>%
   charToRaw() %>%
   rsvg() %>%
-  png::writePNG("Manuscript.figures/EFAplot.LR.png")
-
-```
-
-```{r EFAplot, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, include=FALSE, out.height="100%", out.width="120%"}
-knitr::include_graphics('Manuscript.figures/EFAplot.LR.png')
+  png::writePNG("Manuscript.figures/EFAplot.png")
+
+```
+
+```{r EFAplot, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, out.height="100%", out.width="120%"}
+knitr::include_graphics('Manuscript.figures/EFAplot.png')
 
@@
 The fitted model failed to attain an absolute fit estimated by the chi-square test.
-However, the chi-square test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit [@RN1231].
+However, the chi-square test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit [@brownConfirmatoryFactorAnalysis2015].
 The other absolute fit index we obtained in our analysis was SRMR which does not work well with categorical data [@RN1272].
@@
 
-apa_table(CFa.matrix, caption = "Fit indices of CFA")
+apa_table(CFa.matrix, caption = "Fit indices of CFA", align = "c", landscape = T)
 
@@
 ```{r figcfa, fig.cap = "(A) Five Factor Model of LEBA", , out.width="100%",  warning=FALSE}
-library(semPlot)
+#library(semPlot)
 
@@
 
-```{r Invarianceshortcut, include=FALSE}
-#library("semTools")
-invariance.model <- measurementInvariance(model = LB.model.Cor.2,
-                                          data = invariance.data,
-                                          group = "English_Speaking",
-                                          ordered =   names(CFA.data),
-                                          estimator = "WLSMV",
-                                          strict = T)
-invariance.model$fit.configural
-```
-
 ```{r Invariance detail, include=FALSE}
 # Configural invariance ####
-
-LB.model.Cor.3 <- "F1 =~ a1*item16 + a2*item36 + item17
-                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
-                 F3 =~  item27+ item3+ item40 + item30 + item41
-                 F4 =~ a4*item32 +a3*item35 + item38+ item33 
-                 F5 =~ item46+ item45+ item25+ item4+ item1 
-                       a1==a2
-                       a4==a3
-                item30 ~~  item41
-F4~~1*F4"
 
@@
               nesting = "Configural > Metric > Scalar > Residual  > Structural", 
-              fitmeas = c("chisq", "df", "pvalue", "cfi.scaled","tli.scaled","rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr" ),
-              scaled = TRUE,
-              chidif = TRUE, digits = 2)
-
-```
-
-```{r Invariance Tab}
-apa_table(Invariance.table)
+              fitmeas = c("chisq.scaled", "df",  "cfi.scaled","tli.scaled","rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr" ),
+              scaled = T,
+              chidif = T, digits = 2)
+
+colnames(Invariance.table) <- c("Chi-Square", "df", "CFI", "TLI", "RMSEA", "RMSEA 90% Lower CI", "RMSEA 90% Upper", "SRMR", "Chi-Sqr comparison", "df*", "p")
+
+```
+
+```{r InvarianceTab}
+apa_table(Invariance.table, align = "c",  caption = "Invariance Analysis", note = " a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual;* =  df of model comparison", landscape = T, font_size = "scriptsize" )
+
 ```

### 2021-09-10 manuscript.Rmd

@@
 packrat::init()
-#packrat::snapshot(ignore.stale=TRUE) #use to find and install required dependencies.
+packrat::snapshot(ignore.stale=TRUE) #use to find and install required dependencies.
 ```
@@
 install.packages("magick")
+install.packages("mirt")
+install.packages("cowplot")
 devtools::install_github('rich-iannone/DiagrammeR')
@@
 library(magick)
+library(mirt)
 r_refs("references.bib")
@@
 
-                    graph [layout = dot,fontsize = 14]
+                    graph [layout = dot,fontsize = 20]
 
                      node[shape = rectangle, margin = 0.2, width = 6.5, height = 1, 
-                    fixedsize = true]
+                    fixedsize = true,fontsize = 20]
 
@@
                     node[shape = rectangle, margin = 0.2, width = 6.5, height = 2, 
-                    fixedsize = true]
+                    fixedsize = true, fontsize = 20]
                     C[label = 'Factor Identification
@@
                       style = rounded
-                     node[ margin = 0.2,width = 6.5, height = 1, fixedsize = true ]
-
-                     1[label = '5 Factor Solution Retained 23 Items']
+                     node[ margin = 0.2,width = 6.5, height = 1, fixedsize = true, fontsize = 18 ]
+
+                     1[label = '5 Factor Solution Retained 25 Items']
                      2[label = 'Reliability Analysis on EFA Sample (N=428)
-                    Alpha F1 =.49; F2 = .71; F3 = .86; F4 =.62; F5 =.77']
-
-                     3[label = 'Confirmatory Factor Analysis on Modified Model
-                     on the Five Factor Model (21 Items; N=199)
-                      Acceptable Fit ( CFI = .92; TLI .91; RMSEA = .05, SRMR = .07)']
-
-                     4[label = 'Reliability Analysis on CFA (N=199) 
-                      Alpha F1=.47; F2=.67; F3 =.92; F4=.58; F5= .74']
+                    Alpha F1 =.86; F2 = .71; F3 = .68; F4 =.62; F5 =.52']
+
+                     3[label = 'Confirmatory Factor Analysis 
+                     on the Five Factor Model (25 Items; N=262)
+                      Acceptable Fit ( CFI = .94; TLI .93; RMSEA = .06, SRMR = .11)']
+
+                    4[label = 'Confirmatory Factor Analysis 
+                     on the Five Factor Model (23 Items; N=262)
+                      Acceptable Fit ( CFI = .97; TLI .96; RMSEA = .04, SRMR = .09)']
+                     5[label = 'Reliability Analysis on CFA (23 Items; N=262) 
+                      Alpha F1=.93; F2=.80; F3 =.62; F4=.72; F5=.45']
                     }
@@
                      node[ margin = 0.2,width = 6.5, height = 1, fixedsize = true ]
-                    5[label = '6-Factor  one factor with only two salient loadings']
-                    6[label = 'Rejected']
+                    6[label = '6-Factor  one factor with only two salient loadings']
+                    7[label = 'Rejected']
                     }
@@
                      3 ->4
-                     C ->5
-                     5 ->6
+                     4 ->5
+                     C ->6
+                     6 ->7
 
@@
 bartlet <- cortest.bartlett(EFA.data, n =428)
+
+#Histogram
+#psych::multi.hist(EFA.data[,sapply(EFA.data, is.numeric)])
 
@@
 
+determinets <- det(correlations$rho) 
 # Calculating the percentage of correlations higher than .30
@@
 
-hist(residual.6F, col ="red", main = NULL, xlab = "Five factor oblique rotation: Residuals",ylim=c(0, 250))
-abline(h =27, lwd = 2, lty = 2)
+hist(residual.6F, main = NULL, xlab = "Six factor Solution: Residuals",ylim=c(0, 400))
+abline(h =65, lwd = 2, lty = 2)
 abline(v =.05,lwd = 2, lty = 2)
@@
 ```{r Residuals, out.height= "50%",  fig.align='center', fig.cap= ' Histogram of residulas:  five-factor solution',  out.width="50%",  warning=FALSE}
-hist(residual.5F, col ="red", main = NULL, xlab = "Five-factor solution", ylim=c(0, 250))
+hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))
 abline(h =51, lwd = 2, lty = 2)
@@
   mutate(Ritem8 = CFARitem8, Ritem37 = CFARitem37, Ritem26 = CFARitem26)
+
+#Hitogram
+#psych::multi.hist(CFA.data[,sapply(CFA.data, is.numeric)])
 ```
@@
 colnames(CFa.matrix) = c("Model", "Chi-Squre", "df", "CFI", "TLI", "RMSEA", "RMSEA 90% Lower CI", "RMSEA 90% Upper CI", "SRMR")
-CFa.matrix[1,] = c("Five factor model", 
+CFa.matrix[1,] = c("Five factor model:25", 
                    apa(cfa.sum.1$FIT[6],2,T), 
@@
 
-CFa.matrix[2,] = c("Five factor model", 
+CFa.matrix[2,] = c("Five factor model:23", 
                    apa(cfa.sum.2$FIT[6],2,T), 
@@
 
-F1.IRT.data <- sem.data %>% 
-  select(item16, item36,  item17)
-
-F2.IRT.data <- sem.data %>% 
-  select(item16, item36,  item17)
+IRTitem8 = recode(sem.data$item8, '1=5; 2=4; 3=3; 4=2; 5=1')
+IRTitem37 = recode(sem.data$item37, '1=5; 2=4; 3=3; 4=2; 5=1')
+IRTitem26 = recode(sem.data$item26, '1=5; 2=4; 3=3; 4=2; 5=1')
+sem.data <- sem.data %>% 
+  mutate(Ritem8 = IRTitem8, Ritem37 = IRTitem37, Ritem26 = IRTitem26)
+
+F1 <- sem.data %>% 
+  dplyr::select(item16, item36,  item17)
+
+F2 <- sem.data %>% 
+  dplyr::select(item11,  item10 , item12, item7, Ritem8, item9)
+
+F3 <- sem.data %>% 
+ dplyr::select(item27, item3,  item40,  item30,  item41)
+
+F4 <- sem.data %>% 
+ dplyr::select(item32, item35,  item38,  item33)
+
+F5 <- sem.data %>% 
+  dplyr::select(item46, item45, item25, item4, item1 )
+
+## F1 IRT model####
+F1_fit <- mirt(F1, model = 1, itemtype = 'graded', 
+               SE = TRUE, Se.type = 'MHRM',
+               technical = list(NCYCLES = 10000))
+
+## F2 IRT model####
+F2_fit <- mirt(F2, model = 1, itemtype = 'graded', SE = TRUE,
+               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
+
+## F3 IRT model####
+F3_fit <- mirt(F3, model = 1, itemtype = 'graded', SE = TRUE,
+               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
+
+## F4 IRT model####
+F4_fit <- mirt(F4, model = 1, itemtype = 'graded', SE = TRUE,
+               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
+
+## F5 IRT model####
+F5_fit <- mirt(F5, model = 1, itemtype = 'graded', SE = TRUE,
+               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
+
+# Model Parameters ####
+## F1 Model Parameters####
+F1_params <- coef(F1_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
+F1_items <- data.frame(F1_params$items)
+F1l_se <- coef(F1_fit, printSE = TRUE)
+
+## F2 Model Parameters####
+F2_params <- coef(F2_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
+F2_items <- data.frame(F2_params$items)
+F2_se <- coef(F2_fit, printSE = TRUE)
+
+## F3 Model Parameters####
+F3_params <- coef(F3_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
+F3_items <- data.frame(F3_params$items)
+F3_se <- coef(F3_fit, printSE = TRUE)
+
+## F4 Model Parameters####
+F4_params <- coef(F4_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
+F4_items <- data.frame(F4_params$items)
+F4_se <- coef(F4_fit, printSE = TRUE)
+
+## F5 Model Parameters####
+F5_params <- coef(F5_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
+F5_items <- data.frame(F5_params$items)
+F5_se <- coef(F5_fit, printSE = TRUE)
+
+# Person Fit ####
+## F1 Person fit ####
+F1.personfit <- personfit(F1_fit) 
+F1.personfit_model_misfits <- subset(F1.personfit, Zh < -2)
+rownames(F1.personfit_model_misfits)
+nrow(F1.personfit_model_misfits)
+hist(F1.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
+abline(v = -2, lwd = 2, lty = 2)
+
+## F2 Person fit ####
+F2.personfit <- personfit(F2_fit) 
+F2.personfit_model_misfits <- subset(F2.personfit, Zh < -2)
+rownames(F2.personfit_model_misfits)
+nrow(F2.personfit_model_misfits)
+hist(F2.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
+abline(v = -2, lwd = 2, lty = 2)
+
+## F3 Person fit ####
+F3.personfit <- personfit(F3_fit) 
+F3.personfit_model_misfits <- subset(F3.personfit, Zh < -2)
+rownames(F3.personfit_model_misfits)
+nrow(F3.personfit_model_misfits)
+hist(F3.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
+abline(v = -2, lwd = 2, lty = 2)
+
+## F4 Person fit ####
+F4.personfit <- personfit(F4_fit) 
+F4.personfit_model_misfits <- subset(F4.personfit, Zh < -2)
+rownames(F4.personfit_model_misfits)
+nrow(F4.personfit_model_misfits)
+hist(F4.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
+abline(v = -2, lwd = 2, lty = 2)
+
+## F5 Person fit ####
+F5.personfit <- personfit(F5_fit) 
+F5.personfit_model_misfits <- subset(F5.personfit, Zh < -2)
+rownames(F3.personfit_model_misfits)
+nrow(F5.personfit_model_misfits)
+hist(F5.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
+abline(v = -2, lwd = 2, lty = 2)
+
+# Item Fit ####
+
+## F1 Item Fit ####
+F1_itemfit <- itemfit(F1_fit,fit_stats = c("S_X2", "G2","Zh", "infit"),
+                                  impute=10)
+
+F1.missfit <- F1_itemfit[F1_itemfit$p.S_X2 < 0.05, ]
+
+## F2 Item Fit ####
+F2_itemfit <- itemfit(F2_fit,fit_stats = c("S_X2", "G2","Zh", "infit"),
+                      impute=10)
+
+F2.missfit <- F2_itemfit[F2_itemfit$p.S_X2 < 0.05, ]
+
+## F3 Item Fit ####
+F3_itemfit <- itemfit(F3_fit,fit_stats = c("S_X2", "G2","Zh", "infit"),
+                      impute=10)
+
+F3.missfit <- F3_itemfit[F3_itemfit$p.S_X2 < 0.05, ]
+
+## F4 Item Fit ####
+F4_itemfit <- itemfit(F4_fit,fit_stats = c("S_X2", "G2","Zh", "infit"),
+                      impute=10)
+
+F4.missfit <- F4_itemfit[F4_itemfit$p.S_X2 < 0.05, ]
+
+## F5 Item Fit ####
+F5_itemfit <- itemfit(F5_fit,fit_stats = c("S_X2", "G2","Zh", "infit"),
+                      impute=10)
+
+F5.missfit <- F5_itemfit[F5_itemfit$p.S_X2 < 0.05, ]
+
+# Plots ####
+## F1 Plots ####
+F1_OCC <- plot(F1_fit, type = "trace", facet =T, main = "Blue Filter OCC")
+F1_info <- plot(F1_fit, type = "infoSE", main = "Blue Filter Test Information")
+F1_iteminfo <- plot(F1_fit, type = "infotrace", main = "Blue Filter Item Information")
+
+## F2 Plots ####
+F2_OCC <- plot(F2_fit, type = "trace", facet =T, main = "Natural Light OCC")
+F2_info <- plot(F2_fit, type = "infoSE", main = "Natural Light Test Information")
+F2_iteminfo <- plot(F2_fit, type = "infotrace", main = "Natural Light Item Information")
+
+## F3 Plots ####
+F3_OCC <-plot(F3_fit, type = "trace", facet =T, main = "Smart Device OCC")
+F3_info <- plot(F3_fit, type = "infoSE", main = "Smart Device Test Information")
+F3_iteminfo <- plot(F3_fit, type = "infotrace", main = "Smart Device Item Information")
+
+## F4 Plots ####
+F4_OCC <-plot(F4_fit, type = "trace", facet =T, main = "Sleep Environment OCC")
+F4_info <- plot(F4_fit, type = "infoSE", main = "Sleep Environment Test Information")
+F4_iteminfo <- plot(F4_fit, type = "infotrace", main = "Sleep Environment Item Information")
+
+## F5 Plots ####
+F5_OCC <-plot(F5_fit, type = "trace", facet =T, main = "Electric Light OCC")
+F5_info <- plot(F5_fit, type = "infoSE", main = "Electric Light Test Information")
+F5_iteminfo <- plot(F5_fit, type = "infotrace", main = "Electric Light Item Information")
+
+## Plot grid ####
+library(cowplot)
+plot_grid(F1_OCC, F2_OCC,F3_OCC,F4_OCC,F5_OCC, 
+          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)
+
+plot_grid(F1_info, F2_info,F3_info,F4_info,F5_info, 
+          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)
+
+plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
+          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)
 

### 2021-09-13 manuscript.Rmd

@@
 packrat::init()
-packrat::snapshot(ignore.stale=TRUE) #use to find and install required dependencies.
+#use to find and install required dependencies.
+#packrat::snapshot(ignore.stale=TRUE) 
+packrat::restore()
 ```

### 2021-09-13 manuscript.Rmd

--- 2021-09-10 manuscript.Rmd
@@
 packrat::init()
-packrat::snapshot(ignore.stale=TRUE) #use to find and install required dependencies.
+#Only use when you have added some pack
+#packrat::snapshot(ignore.stale=TRUE)
+
+#To find and install required dependencies.
+packrat::restore()
 ```

### 2021-09-13 manuscript.Rmd

@@
 library(mirt)
+library(gtsummary)
 r_refs("references.bib")

### 2021-09-13 manuscript.Rmd

@@
 
-```{r dependencymanager, include = FALSE}
+```{r dependencymanager, include = FALSE, warning=F}
+knitr::opts_chunk$set(warning = F, error = F, message = F)
 library(packrat)

### 2021-09-13 manuscript.Rmd

@@
 library(rsvg) #For DiagrammeR
-#library(correlation)
 library(ggcorrplot)

### 2021-09-14 manuscript.Rmd
Added ffiliations

@@
   - name          : "Mushfiqul Anwar Siraji"
-    affiliation   : "1"
-    corresponding : no   
-    address       : "Monash University, Malaysia"
+    affiliation   : "1, *"
     email         : "mushfiqul.anwarsiraji@monash.edu"
     role:         
-      - Data Analysis
-      - Writing - Original Draft Preparation
-      - Data Visualization
+      - Formal Analysis
+      - Visualization
+      - Writing – original draft
 
   - name          : "Rafael Robert Lazar"
-    affiliation   : "2"
+    affiliation   : "2, 3, *"
     role:
-      - Data Analysis
-      - Writing - Original Draft Preparation
-      - Data Visualization
-  - name          : "Manuel Spitschan "
-    affiliation   : "3"
+      - Data curation
+      - Investigation
+      - Project administration
+      - Visualization
+      - Writing – original draft
+      - Writing – review & editing;
+
+  - name          : "Juliëtte	van Duijnhoven"
+    affiliation   : "4"
+    email         : "j.v.duijnhoven1@tue.nl"
+    role:         
+      - Conceptualization
+      - Methodology
+      - Investigation
+      - Writing – review & editing
+
+  - name          : "Luc Schlangen"
+    affiliation   : "5"
+    email         : "l.j.m.schlangen@tue.nl"
+    role:         
+      - Conceptualization
+      - Methodology
+      - Investigation
+      - Writing – review & editing
+
+  - name          : "Shamsul Haque"
+    affiliation   : "1"
+    email         : "shamsul@monash.edu"
+    role:         
+      - Conceptualization
+      - Supervision
+      - Writing – review & editing
+
+  - name          : "Vineetha Kalavally"
+    affiliation   : "6"
+    email         : "vineetha@monash.edu"
+    role:         
+      - Supervision
+      - Writing – review & editing
+
+  - name          : "Céline Vetter"
+    affiliation   : "7, 8"
+    email         : "celine.vetter@colorado.edu"
+    role:         
+      - Conceptualization
+      - Writing – review & editing
+
+  - name          : "Gena Glickman"
+    affiliation   : "9"
+    email         : "gena.glickman@usuhs.edu"
+    role:         
+      - Conceptualization
+      - Methodology
+      - Writing – review & editing
+
+  - name          : "Karin Smolders"
+    affiliation   : "10"
+    email         : "k.c.h.j.smolders@tue.nl"
+    role:         
+      - Conceptualization
+      - Methodology
+      - Writing – review & editing
+
+  - name          : "Manuel Spitschan"
     corresponding : yes
-    address       : ""
-    email         : ""
+    affiliation   : "11, 2, 3"
+    email         : "manuel.spitschan@psy.ox.ac.uk"
     role:         
-      - Data Analysis
-      - Writing - Original Draft Preparation
-      - Data Visualization
+      - Conceptualization
+      - Data curation
+      - Investigation
+      - Project administration
+      - Visualization
+      - Methodology
+      - Writing – original draft
+      - Writing – review & editing
 
@@
   - id            : "1"
-    institution   : "Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Monash University, Malaysia"
+    institution   : "Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
   - id            : "2"
-    institution   : "University of Basel"
+    institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"
+  - id            : "3"
+    institution   : "University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland"
+  - id            : "4"
+    institution   : "Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands"
+  - id            : "5"
+    institution   : "Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Intelligent Lighting Institute, Eindhoven, Netherlands"
+  - id            : "6"
+    institution   : "Monash University, Department of Electrical and Computer Systems Engineering, Malaysia, Selangor, Malaysia"
+  - id            : "7"
+    institution   : "University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA"
+  - id            : "8"
+    institution   : "Ximes GmbH, Frankfurt, Germany"
+  - id            : "9"
+    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
+  - id            : "10"
+    institution   : "Eindhoven University of Technology, Human-Technology Interaction Group, Eindhoven, Netherlands"
+  - id            : "11"
+    institution   : "University of Oxford, Department of Experimental Psychology, Oxford, UK"
+  - id            : "*"
+    institution   : "Joint first author"
 

### 2021-09-14 manuscript.Rmd
Added ffiliations

@@
 ---
-title             : "_Light Exposure Behavior Assessment (LEBA)_: Develop of a novel instrument to capture light exposure-related behaviours"
+title             : "_Light Exposure Behavior Assessment (LEBA)_: Development of a novel instrument to capture light exposure-related behaviours"
 shorttitle        : "LEBA"

### 2021-09-14 manuscript.Rmd
Added affiliations

@@
 
-```{r IRT data, eval=FALSE, include=FALSE}
+```{r IRT data, include=FALSE}
 
@@
 F5_se <- coef(F5_fit, printSE = TRUE)
+
+itemparameters <- rbind(F1_items,F2_items, F3_items, F4_items,F5_items)
 
@@
 
-# Item Fit ####
-
-## F1 Item Fit ####
-F1_itemfit <- itemfit(F1_fit,fit_stats = c("S_X2", "G2","Zh", "infit"),
-                                  impute=10)
-
-F1.missfit <- F1_itemfit[F1_itemfit$p.S_X2 < 0.05, ]
-
-## F2 Item Fit ####
-F2_itemfit <- itemfit(F2_fit,fit_stats = c("S_X2", "G2","Zh", "infit"),
-                      impute=10)
-
-F2.missfit <- F2_itemfit[F2_itemfit$p.S_X2 < 0.05, ]
-
-## F3 Item Fit ####
-F3_itemfit <- itemfit(F3_fit,fit_stats = c("S_X2", "G2","Zh", "infit"),
-                      impute=10)
-
-F3.missfit <- F3_itemfit[F3_itemfit$p.S_X2 < 0.05, ]
-
-## F4 Item Fit ####
-F4_itemfit <- itemfit(F4_fit,fit_stats = c("S_X2", "G2","Zh", "infit"),
-                      impute=10)
-
-F4.missfit <- F4_itemfit[F4_itemfit$p.S_X2 < 0.05, ]
-
-## F5 Item Fit ####
-F5_itemfit <- itemfit(F5_fit,fit_stats = c("S_X2", "G2","Zh", "infit"),
-                      impute=10)
-
-F5.missfit <- F5_itemfit[F5_itemfit$p.S_X2 < 0.05, ]
-
 # Plots ####
@@
 F1_info <- plot(F1_fit, type = "infoSE", main = "Blue Filter Test Information")
-F1_iteminfo <- plot(F1_fit, type = "infotrace", main = "Blue Filter Item Information")
+F1_iteminfo <- plot(F1_fit, type = "infotrace", 
+                    facet_items = T, main = NULL)
 
@@
 F2_info <- plot(F2_fit, type = "infoSE", main = "Natural Light Test Information")
-F2_iteminfo <- plot(F2_fit, type = "infotrace", main = "Natural Light Item Information")
+F2_iteminfo <- plot(F2_fit, type = "infotrace", facet_items = T, main = NULL)
 
@@
 F3_info <- plot(F3_fit, type = "infoSE", main = "Smart Device Test Information")
-F3_iteminfo <- plot(F3_fit, type = "infotrace", main = "Smart Device Item Information")
+F3_iteminfo <- plot(F3_fit, type = "infotrace", 
+                    facet_items = T, main = NULL)
 
@@
 F4_info <- plot(F4_fit, type = "infoSE", main = "Sleep Environment Test Information")
-F4_iteminfo <- plot(F4_fit, type = "infotrace", main = "Sleep Environment Item Information")
+F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = NULL)
 
@@
 F5_info <- plot(F5_fit, type = "infoSE", main = "Electric Light Test Information")
-F5_iteminfo <- plot(F5_fit, type = "infotrace", main = "Electric Light Item Information")
+F5_iteminfo <- plot(F5_fit, type = "infotrace", facet_items = T,main = NULL)
 
@@
 library(cowplot)
-plot_grid(F1_OCC, F2_OCC,F3_OCC,F4_OCC,F5_OCC, 
+OCC <- plot_grid(F1_OCC, F2_OCC,F3_OCC,F4_OCC,F5_OCC, 
           labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)
 
-plot_grid(F1_info, F2_info,F3_info,F4_info,F5_info, 
+Test_Info <- plot_grid(F1_info, F2_info,F3_info,F4_info,F5_info, 
           labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)
 
+Item_Information <- plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
+          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)
+
+```
+
+We combined the EFA and CFA sample (N= 690) and fit each factor of LEBA as a unidimensional construct, and used the graded response model to obtain item parameters(\@ref(tab:IRTparameters).
+Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait, and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
+Currently, apart from some general suggestions, there exists no definitive rule to judge the item discrimination and item information parameter quality.
+In this current study, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information <.2).
+@bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70.
+Among the 23 items, 10 items were highly discriminating.
+Items 16 and 33 had very high discrimination parameters (28.55 & 13.50), indicating their limited applicability to people with a very high level of the latent attribute.
+Examination of the item information curve indicated 6 items (1, 25, 9, 38, 30, & 41) had relatively flat information curves thus discarded.
+
+```{r IRTparameters}
+apa_table(itemparameters, caption = "IRT Item parameters for the LEBA Scale", note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
+```
+
+```{r Iteminformationcurve, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="120%", out.height="150%"}
 plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
-          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)
-
+          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10 )
+
+```
+
+```{r}
+F2.redu <- sem.data %>% 
+  dplyr::select(item11,  item10 , item12, item7, Ritem8)
+F3.redu <- sem.data %>% 
+ dplyr::select(item27, item3,  item40)
+
+F4.redu <- sem.data %>% 
+ dplyr::select(item32, item35,  item33)
+
+F5 <- sem.data %>% 
+  dplyr::select(item46, item45, item25 )
 ```

### 2021-09-14 manuscript.Rmd
preliminary participants section

--- 2021-09-14 manuscript.Rmd
@@
 
+```{r prepareDescTable, include=FALSE}
+
+listdescVars <- colnames(descriptives.data[c(1:3,5:7)])
+
+#seperating naming and  reducing data for descriptive Table 
+desctable.data <- select(descriptives.data, c(listdescVars,
+                          IncludedInCFA))
+
+#renaming TRUE and FALSE from the IncludedInCFA to EFA and CFA for Descriptive Table
+desctable.data$IncludedInCFA[desctable.data$IncludedInCFA == T ] <-
+ "2. CFA Sample"
+desctable.data$IncludedInCFA[desctable.data$IncludedInCFA == F ] <- 
+ "1. EFA Sample"
+
+# recode the Gender factor so it will only show "Gender Diverse" in the summary table
+desctable.data$slypos_demographics_gender.factor <-
+  recode_factor(desctable.data$slypos_demographics_gender.factor, "No" = "Yes",
+         "Yes"= "No")
+
+# create descriptive table for the demographic vars (excluding tz & Country) with gtsummary
+desctable.data %>%
+  tbl_summary(
+    by = IncludedInCFA,
+    statistic = list(all_continuous() ~ "{mean} ({sd})",
+                     all_categorical() ~ "{n} ({p}%)"),
+    digits = all_continuous() ~ 2,
+    label = list(slypos_demographics_age ~ "Age",
+                 slypos_demographics_sex.factor ~ "Sex",
+                 slypos_demographics_gender.factor ~ "Gender-Variant Identity",
+                 slypos_demographics_language.factor ~ "Native English Speaker",
+                 slypos_demographics_work_or_school.factor ~ "Occupational Status",
+                 slypos_demographics_school.factor ~ "Occupational setting"
+                 ),
+    missing = "no"
+    ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
+modify_header(label ~ "**Variable**") %>%
+as_kable(format = 'pipe') -> desc_kable #save it as a kable
+
+```
+
+```{r DescTabPrint, results='asis'}
+
+desc_kable
+
+```
+
+Table 1 summarizes the demographic characteristics of the online survey participants.
+Anonymous online questionnaire responses from a total of *n* = `r nrow(desctable.data)` participants were included in the analysis of the current study, split into samples for exploratory (EFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "1.
+EFA Sample",])`) and confirmatory factor analysis (CFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "2.
+CFA Sample",])`).
+Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses.
+XX participants were excluded from analysis due to not passing at least one of the "attention check" items.
+The EFA sample included participants filling out the questionnaire from XX.XX.XXXX to YY.YY.YYYY, whereas participants who filled out the questionnaire from ZZ.ZZ.ZZZZ to 03.09.2021 were included in the CFA analysis.
+Participants reported filling out the online survey from a diverse range of geographic locations.
+The four most common geographic locations included:
+
 1.  Describe EFA and CFA sample separately.
@@
 ## Procedure
+
 ### Development of the Scale
+
 1.  How the items were generated
@@
 ## Procedure
+
 Our study had four objectives.
@@
 ### Data Collection
-Timeline of data collection, 
-ethical approval
-mode of data collection
-how consent was recorded.
+
+Timeline of data collection, ethical approval mode of data collection how consent was recorded.
 
@@
 We used a combination factor identification method including scree plot[@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method[@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
-Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018;
+Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018;
 
@@
 Our data violated both univariate normality (Shapiro-Wilk statistics; [@shapiroAnalysisVarianceTest1965]) and multivariate normality assumptions (Marida's test;[@mardiaMeasuresMultivariateSkewness1970]).
-Multivariate skew was  = `r printnum(mardia$b1p)` (p <0.001) and multivariate kurtosis was = `r printnum(mardia$b2p)` (p <0.001).
+Multivariate skew was = `r printnum(mardia$b1p)` (p \<0.001) and multivariate kurtosis was = `r printnum(mardia$b2p)` (p \<0.001).
 Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018].
-Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001] indicated the correlations between items are adequate for the EFA.
+Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p \< .001] indicated the correlations between items are adequate for the EFA.
 However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than .30.
@@
 
-Three rounds of EFA with all 48 items were conducted, and problematic items were gradually discarded (cross-loading items and poor factor loading (<.30) items).
+Three rounds of EFA with all 48 items were conducted, and problematic items were gradually discarded (cross-loading items and poor factor loading (\<.30) items).
 Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 [@brownConfirmatoryFactorAnalysis2015], all factor-loading higher than .30 and no cross-loading greater than .30.
@@
 \newpage
+
 # References
 
+```{=tex}
 \begingroup
@@
 \setlength{\leftskip}{0.5in}
-
-<div id="refs" custom-style="Bibliography"></div>
+```
+::: {#refs custom-style="Bibliography"}
+:::
+
 \endgroup

### 2021-09-15 manuscript.Rmd

--- 2021-09-14 manuscript.Rmd
@@
 F1_iteminfo <- plot(F1_fit, type = "infotrace", 
-                    facet_items = T, main = NULL)
+                    facet_items = T, main = "Blue Filter")
 
@@
 F2_info <- plot(F2_fit, type = "infoSE", main = "Natural Light Test Information")
-F2_iteminfo <- plot(F2_fit, type = "infotrace", facet_items = T, main = NULL)
+F2_iteminfo <- plot(F2_fit, type = "infotrace", facet_items = T, main = "Natural Light")
 
@@
 F3_iteminfo <- plot(F3_fit, type = "infotrace", 
-                    facet_items = T, main = NULL)
+                    facet_items = T, main = "Smart Device")
 
@@
 F4_info <- plot(F4_fit, type = "infoSE", main = "Sleep Environment Test Information")
-F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = NULL)
+F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = "Sleep Environment")
 
@@
 F5_info <- plot(F5_fit, type = "infoSE", main = "Electric Light Test Information")
-F5_iteminfo <- plot(F5_fit, type = "infotrace", facet_items = T,main = NULL)
+F5_iteminfo <- plot(F5_fit, type = "infotrace", facet_items = T,main = "Electric Light")
 
@@
 
-```{r Iteminformationcurve, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="120%", out.height="150%"}
+```{r Iteminformationcurve, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
 plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 

### 2021-09-15 manuscript.Rmd

@@
 classoption       : "man"
-output            : papaja::apa6_pdf
-fontfamily        : arev
+output            : 
+  papaja::apa6_pdf:
+    latex_engine: xelatex
+mainfont: Helvetica
+
 ---

### 2021-09-15 manuscript.Rmd

@@
 
-reliability2 <- semTools::reliability(fit.Cor.2, return.total = T)
+rel.k <- semTools::reliability(fit.Cor.2, return.total = T)
 ## Summary of Model 
@@
 Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR value (SRMR = `r apa(fit.2[10],2,F)`) was also close to the suggestions of @huCutoffCriteriaFit1999.
+The internal consistency reliability coefficients McDonald's omega were `r apa(rel.k[5,1],2,F)`, `r apa(rel.k[5,2],2,F)`, `r apa(rel.k[5,3],2,F)`, `r apa(rel.k[5,4],2,F)`, `r apa(rel.k[5,5],2,F)` respectively indicating satisfactory reliability for F1, F2 and F4 [@najeracatalanReliabilityPopulationClassification2019]
 

### 2021-09-15 instrument.tex
Update

--- 2021-09-01 manuscript.tex
@@
   english,
-  man]{apa6}
+  man,floatsintext]{apa6}
 \usepackage{amsmath,amssymb}
-\usepackage[]{arev}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{lmodern}
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+  \setmainfont[]{Helvetica}
 \fi
@@
 \hypersetup{
-  pdftitle={Light Exposure Behavior Assessment (LEBA): Develop of a novel instrument to capture light exposure-related behaviours},
-  pdfauthor={Mushfiqul Anwar Siraji1, Rafael Robert Lazar2, \& Manuel Spitschan3},
+  pdftitle={Light Exposure Behavior Assessment (LEBA): Long and Short Form},
+  pdfauthor={Mushfiqul Anwar Siraji, Rafael Robert Lazar, Juliëtte van Duijnhoven, Luc Schlangen, Shamsul Haque, Vineetha Kalavally, Céline Vetter, Gena Glickman, Karin Smolders, \& Manuel Spitschan},
   pdflang={en-EN},
-  pdfkeywords={keywords},
   hidelinks,
@@
 \urlstyle{same} % disable monospaced font for URLs
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
 \usepackage{graphicx}
@@
 % \newenvironment{ltable}
-%   {\begin{landscape}\begin{center}\begin{threeparttable}}
-%   {\end{threeparttable}\end{center}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+%   {\begin{landscape}\centering\begin{threeparttable}}
+%   {\end{threeparttable}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
 
@@
 % \setlength{\parskip}{0pt plus 0pt minus 0pt}
-
-% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
-% See https://github.com/crsh/papaja/issues/292
-\makeatletter
-\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-1em}%
-  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
-
-\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-\z@\relax}%
-  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
-\makeatother
 
@@
 \shorttitle{LEBA}
-\keywords{keywords\newline\indent Word count: X}
-\DeclareDelayedFloatFlavor{ThreePartTable}{table}
-\DeclareDelayedFloatFlavor{lltable}{table}
-\DeclareDelayedFloatFlavor*{longtable}{table}
-\makeatletter
-\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
-\makeatother
-\usepackage{lineno}
-
-\linenumbers
 \usepackage{csquotes}
-\ifxetex
+\ifXeTeX
   % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
@@
 \fi
-\ifluatex
+\ifLuaTeX
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
-\title{\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours}
-\author{Mushfiqul Anwar Siraji\textsuperscript{1}, Rafael Robert Lazar\textsuperscript{2}, \& Manuel Spitschan\textsuperscript{3}}
+\title{\emph{Light Exposure Behavior Assessment (LEBA)}: Long and Short Form}
+\author{Mushfiqul Anwar Siraji\textsuperscript{}, Rafael Robert Lazar\textsuperscript{}, Juliëtte van Duijnhoven\textsuperscript{}, Luc Schlangen\textsuperscript{}, Shamsul Haque\textsuperscript{}, Vineetha Kalavally\textsuperscript{}, Céline Vetter\textsuperscript{}, Gena Glickman\textsuperscript{}, Karin Smolders\textsuperscript{}, \& Manuel Spitschan\textsuperscript{}}
 \date{}
 
-\authornote{
-
-Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-Enter author note here.
-
-The authors made the following contributions.
-Mushfiqul Anwar Siraji: Data Analysis, Writing - Original Draft Preparation, Data Visualization; Rafael Robert Lazar: Data Analysis, Writing - Original Draft Preparation, Data Visualization; Manuel Spitschan: Data Analysis, Writing - Original Draft Preparation, Data Visualization.
-
-Correspondence concerning this article should be addressed to Manuel Spitschan, . E-mail:
-
-}
-
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Monash University, Malaysia\\\textsuperscript{2} University of Basel}
-
-\abstract{
-One or two sentences providing a \textbf{basic introduction} to the field, comprehensible to a scientist in any discipline.
-
-Two to three sentences of \textbf{more detailed background}, comprehensible to scientists in related disciplines.
-
-One sentence clearly stating the \textbf{general problem} being addressed by this particular study.
-
-One sentence summarizing the main result (with the words ``\textbf{here we show}'' or their equivalent).
-
-Two or three sentences explaining what the \textbf{main result} reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
-
-One or two sentences to put the results into a more \textbf{general context}.
-
-Two or three sentences to provide a \textbf{broader perspective}, readily comprehensible to a scientist in any discipline.
-}
+\affiliation{\phantom{0}}
 
@@
 
-\hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\textbf{Disclaimer}: This is a non-public version of LEBA and still a work in progress.
 
-\hypertarget{methods}{%
-\section{Methods}\label{methods}}
+LEBA captures light exposure-related behaviours on a 5 point Likert type scale ranging from 1 to 5 (Never =1; Rarely= 2; Sometimes =3; Often = 4; Always =5).
+The score of each factor is calculated by the summation of scores of items belonging to the corresponding factor.
 
-\hypertarget{participants}{%
-\subsection{Participants}\label{participants}}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Describe EFA and CFA sample separately.
-\item
-  Sampling technique: Convince sampling (non-probability sample)
-\item
-  Method: cross-sectional survey
-\item
-  How many missing data?
-\item
-  How incomplete data were addressed.
-\item
-  Why such sample was chosen?
-\end{enumerate}
-
-EFA: For exploring initial factor structure, a sample of 250-300 is recommended (Comrey \& Lee, 1992; Schönbrodt \& Perugini, 2013)
-
-CFA: For estimating the sample size for the confirmatory factor analysis we followed the N:q rule (Bentler \& Chou, 1987; Jackson, 2003; Kline, 2015; Worthington \& Whittaker, 2006) where 10 participants per parameter is required to earn trustworthiness of the result.
-Our sample size exceeds the requirement.
-
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
-
-\hypertarget{development-of-the-scale}{%
-\subsubsection{Development of the Scale}\label{development-of-the-scale}}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  How the items were generated
-\item
-  How the literature was reviewed to identify construct adequacy of the items.
-\item
-  Discuss the expert panel review process to assess content validity
-\end{enumerate}
-
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth,height=1\textheight]{Flowchart1}
-
-}
-
-\caption{Development and psychometric properties of LEBA }\label{fig:unnamed-chunk-1}
-\end{figure}
-
-\hypertarget{procedure-1}{%
-\subsection{Procedure}\label{procedure-1}}
-
-Our study had four objectives.
-First, to develop an instrument to assess an individual's light exposure behavior.
-Second, to conduct an exploratory factor analysis(EFA) to understand the latent structure.
-The third one is to gather structural validity evidence for the latent structure obtained in EFA.
-Lastly, we gathered item information using Item response theory (IRT)(Baker, 2017)
-
-\hypertarget{data-collection}{%
-\subsubsection{Data Collection}\label{data-collection}}
-
-Timeline of data collection,
-ethical approval
-mode of data collection
-how consent was recorded.
-
-\hypertarget{analytic-strategies}{%
-\subsection{Analytic Strategies}\label{analytic-strategies}}
-
-We used R (version 4.1.0), including several R packages, for our analyses.
-Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
-Our data violated both the univariate and multivariate normality assumptions.
-Due to these violations and the ordinal nature of our response data, we used a polychoric correlation matrix (C.
-Desjardins \& Bulut, 2018) for the EFA.
-We employed principal axis (pa) a factor extraction method with varimax rotation.
-PA is robust to the normality assumption violations (Watkins, 2020).
-The obtained latent structure was confirmed by the minimum residuals extraction method as well.
-We used a combination factor identification method including scree plot(Cattell, 1966), Horn's parallel analysis (Horn, 1965), minimum average partials method(Velicer, 1976), and hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) to identify factor numbers.
-Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \textless0.3 (iii) no items with cross-loading greater than .3 across factors {[}Bandalos and Finney (2018);
-
-\hypertarget{results}{%
-\section{Results}\label{results}}
-
-Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy(Kaiser, 1974) .
-The overall KMO vale for 48 items was 0.63 which was above the cutoff value (.50) indicating a mediocre sample (Hutcheson, 1999).
-
-\begin{center}
-\begin{ThreePartTable}
-
-\begin{TableNotes}[para]
-\normalsize{\textit{Note.} *p<.001}
-\end{TableNotes}
-
-\begin{longtable}{ccccccc}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
-\caption{\label{tab:tabDes}Descriptive Statistics}\\
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.00}}@{}}
 \toprule
- & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{Item-Total Correlation}\\
-\midrule
-\endfirsthead
-\caption*{\normalfont{Table \ref{tab:tabDes} continued}}\\
-\toprule
- & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{Item-Total Correlation}\\
+Long Form (23 Items) \\
 \midrule
 \endhead
-Item1 & 1.12 & 0.49 & 5.02 & 27.80 & 0.25* & .16\\
-Item2 & 2.16 & 1.19 & 0.71 & -0.54 & 0.84* & .14\\
-Item3 & 4.14 & 0.99 & -1.23 & 1.14 & 0.79* & .19\\
-Item4 & 2.87 & 1.59 & 0.08 & -1.60 & 0.83* & .19\\
-Item5 & 1.76 & 1.23 & 1.35 & 0.44 & 0.66* & .38\\
-Item6 & 2.73 & 1.46 & 0.20 & -1.36 & 0.87* & .33\\
-Item7 & 3.86 & 1.67 & -0.99 & -0.85 & 0.65* & .23\\
-Item8 & 3.76 & 1.14 & -0.68 & -0.45 & 0.86* & .00\\
-Item9 & 3.42 & 1.83 & -0.45 & -1.69 & 0.69* & .33\\
-Item10 & 2.74 & 1.04 & 0.09 & -0.74 & 0.91* & .28\\
-Item11 & 2.60 & 1.25 & 0.29 & -0.86 & 0.89* & .35\\
-Item12 & 2.11 & 1.17 & 0.77 & -0.39 & 0.83* & .32\\
-Item13 & 2.94 & 1.03 & -0.12 & -0.40 & 0.91* & .10\\
-Item14 & 3.62 & 1.64 & -0.68 & -1.25 & 0.74* & .32\\
-Item15 & 1.64 & 1.18 & 1.79 & 2.02 & 0.60* & .15\\
-Item16 & 3.51 & 1.30 & -0.70 & -0.59 & 0.85* & .39\\
-Item17 & 1.96 & 0.98 & 1.02 & 0.69 & 0.82* & .05\\
-Item18 & 2.44 & 1.31 & 0.38 & -1.14 & 0.86* & .11\\
-Item19 & 3.80 & 1.29 & -0.87 & -0.42 & 0.82* & .17\\
-Item20 & 4.01 & 1.40 & -1.22 & 0.07 & 0.70* & .13\\
-Item21 & 1.33 & 0.91 & 3.03 & 8.43 & 0.41* & .01\\
-Item22 & 2.59 & 1.41 & 0.27 & -1.27 & 0.86* & .19\\
-Item23 & 1.31 & 0.81 & 2.75 & 6.92 & 0.43* & .21\\
-Item24 & 1.47 & 1.18 & 2.38 & 4.00 & 0.43* & .28\\
-Item25 & 2.56 & 1.27 & 0.33 & -1.00 & 0.89* & .11\\
-Item26 & 1.54 & 1.25 & 2.13 & 2.86 & 0.46* & .36\\
-Item27 & 4.30 & 1.08 & -1.79 & 2.53 & 0.67* & .22\\
-Item28 & 2.27 & 1.39 & 0.74 & -0.81 & 0.81* & .25\\
-Item29 & 3.26 & 1.09 & -0.26 & -0.45 & 0.91* & .14\\
-Item30 & 2.22 & 1.48 & 0.71 & -1.02 & 0.76* & .30\\
-Item31 & 1.05 & 0.36 & 7.23 & 52.98 & 0.13* & .18\\
-Item32 & 1.54 & 1.21 & 2.07 & 2.75 & 0.49* & .31\\
-Item33 & 1.04 & 0.33 & 8.99 & 85.28 & 0.10* & .16\\
-Item34 & 3.36 & 1.38 & -0.48 & -1.03 & 0.87* & .16\\
-Item35 & 2.26 & 1.25 & 0.70 & -0.60 & 0.85* & .19\\
-Item36 & 2.36 & 1.22 & 0.59 & -0.62 & 0.87* & .25\\
-Item37 & 1.14 & 0.59 & 4.79 & 24.05 & 0.25* & .16\\
-Item38 & 2.25 & 1.27 & 0.69 & -0.64 & 0.84* & .18\\
-Item39 & 3.93 & 1.48 & -1.06 & -0.44 & 0.71* & .18\\
-Item40 & 3.57 & 1.07 & -0.65 & -0.17 & 0.88* & .21\\
-Item41 & 3.55 & 1.65 & -0.60 & -1.34 & 0.76* & .43\\
-Item42 & 3.00 & 1.62 & -0.08 & -1.61 & 0.83* & .44\\
-Item43 & 1.56 & 1.23 & 2.00 & 2.45 & 0.50* & .32\\
-Item44 & 2.97 & 1.20 & -0.06 & -0.94 & 0.91* & -.10\\
-Item45 & 2.79 & 1.55 & 0.19 & -1.48 & 0.85* & .20\\
-Item46 & 2.14 & 1.31 & 0.77 & -0.78 & 0.80* & .26\\
-Item47 & 2.18 & 0.90 & 0.60 & 0.12 & 0.86* & .26\\
-Item48 & 1.48 & 1.11 & 2.18 & 3.35 & 0.48* & .24\\
+\textbf{F1: Blue Filter} \\
+I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day. \\
+I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day. \\
+I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1 hour before attempting to fall asleep. \\
+\textbf{F2: Natural Light} \\
+I spend 30 minutes or less per day (in total) outside. \\
+I spend between 1 and 3 hours per day (in total) outside. \\
+I spend between 30 minutes and 1 hour per day (in total) outside. \\
+I spend more than 3 hours per day (in total) outside. \\
+I spend as much time outside as possible. \\
+I go for a walk or exercise outside within 2 hours after waking up. \\
+\textbf{F3: Smart Device} \\
+I use my mobile phone within 1 hour before attempting to fall asleep. \\
+I look at my mobile phone screen immediately after waking up. \\
+I check my phone when I wake up at night. \\
+I look at my smartwatch within 1 hour before attempting to fall asleep. \\
+I look at my smartwatch when I wake up at night. \\
+\textbf{F4: Sleep Environment} \\
+I dim my mobile phone screen within 1 hour before attempting to fall asleep. \\
+I use a blue-filter app on my computer screen within 1 hour before attempting to fall asleep. \\
+I use as little light as possible when I get up during the night. \\
+I dim my computer screen within 1 hour before attempting to fall asleep. \\
+\textbf{F5: Electric Light} \\
+I use tunable lights to create a healthy light environment. \\
+I use LEDs to create a healthy light environment. \\
+I use a desk lamp when I do focused work. \\
+I use an alarm with a dawn simulation light. \\
+I turn on the lights immediately after waking up. \\
 \bottomrule
-\addlinespace
-\insertTableNotes
 \end{longtable}
-
-\end{ThreePartTable}
-\end{center}
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.5\linewidth]{manuscript_files/figure-latex/figCor-1}
-
-}
-
-\caption{Correlation plot of the items}\label{fig:figCor}
-\end{figure}
-
-Table\ref{tab:tabDes} summarizes the univariate descriptive statistics for the 48 items.
-some of the items were skewed with high Kurtosis values.
-Our data violated both univariate normality (Shapiro-Wilk statistics; (Shapiro \& Wilk, 1965)) and multivariate normality assumptions (Marida's test;(Mardia, 1970)).
-Multivariate skew was = 583.80 (p \textless0.001) and multivariate kurtosis was = 2,749.15 (p \textless0.001).
-Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen (C.
-Desjardins \& Bulut, 2018).
-Bartlett's test of sphericity (Bartlett, 1954), \(\chi^2\) (1128) = 5042.86, p \textless{} .001{]} indicated the correlations between items are adequate for the EFA.
-However only 4.96\% of the inter-item correlation coefficients were greater than .30.
-The inter item correlation ranged between .44 to .91.
-And the corrected item-total correlations ranged between .10 to .44.
-
-Scree plot ( Figure \ref{fig:facid}) suggested a six-factor solution.
-Horn's parallel analysis (Horn, 1965) with 500 iterations also indicated a six-factor solution.
-However, the MAP method (Velicer, 1976) and Hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) suggested a five-factor solution.
-As a result, we tested both five-factor and six-factor solutions.
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{parallel} \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/facid-2} \includegraphics[width=0.5\linewidth,height=0.5\textheight]{HUll method}
-
-}
-
-\caption{Factor Identification (A) Parallel analysis (B) Scree Plot, (C) Hull method}\label{fig:facid}
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics[width=1.2\linewidth,height=1\textheight]{EFAplot.LR}
-
-}
-
-\caption{Five Factor Solution}\label{fig:EFAplot}
-\end{figure}
-
-The initial five-factor solution with all 48 items showed presence of cross-loading items (item 42, 16, \& 1) and poor factor loading (\textless.30) items (item 20, 3 ,15, 17, 40, 4, 11, 39, 18, 45, 29, 25, 8 , \& 46).
-At first, we discarded the items with poor factor-loading and ran another EFA on the remaining 34 items.
-This iteration of EFA also appeared as a misfit with items with poor factor-loading (Item 12, 22, 38, 6) and cross-loading (items 23, 31, 37, 48) .
-Another two rounds of EFA were conducted with gradually identifying problematic items and discarding them from the model.
-Finally, a five-factor EFA solution with 23 items was accepted with low RMSR = 0.04 (Brown, 2015), all factor-loading higher than .30 and no cross-loading greater than .30.
-We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (see the supplementary).
-Table\ref{tab:TabEFA5} displays the factor-loading (structural coefficients) and communality of the items.
-The absolute value of the factor-loading ranged from -.47 to .99 indicating strong coefficients.
-The commonalities ranged between .10 to .99.
-However, the histogram of the absolute values of non-redundant residual-correlations (Fig\ref{fig:Residuals} showed 26.09\% correlations greater than the absolute value of .05, indicating under-factoring.
-(C.
-D.
-Desjardins, 2018).
-Subsequently, we fitted a six-factor solution.
-However, a factor emerged with only two salient variable loading in the six-factor solution, thus disqualifying the six-factor solution.
-
-In the five-factor solution, the first factor contained three items and explained 11\% of the total variance with a satisfactory internal reliability coefficient (\(\alpha\) =.86).
-All the items in this factor stemmed from the individual's preference to use blue light filters in different light environments.
-The second factor contained six items and explained 10\% of the total variance with a satisfactory internal reliability coefficient (\(\alpha\) =.71).
-Items under this factor commonly investigate an individual's hours spent outdoor.
-The third factor contained five items and explained 9\% of the total variance.
-Items under this factor dealt with the specific behaviors pertaining to sleep.
-However, the internal consistency reliability coefficient was not satisfactory (\(\alpha\) =.62).
-The fourth factor contained three items and explained 9\% of the total variance with a satisfactory internal consistency (\(\alpha\) =.77).
-These three items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time.
-Lastly, the fifth factor contained six items and explained 6\% of the total variance.
-Under this factor tried to measure an individual's behavior lead by the awareness of light's influence on health.
-However, this factor showed unsatisfactory internal consistency reliability (\(\alpha\) =.49).
-It is essential to attain a balance between psychometric properties and the interpretability of the common themes when exploring the latent structure.
-As all of the emerged factors are highly interpretable, regardless of the apparent low reliability of the two factors, we retain the five-factor solution with 23 items for our confirmatory factor analysis (CFA).
-Two items showed negative factor-loading (items 44 and 21).
-Upon inspection, it was understood that these items are negatively correlated to the common theme, and thus in the CFA analysis, we reversed the response code for these two items.
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:TabEFA5}}
-
-\begin{tabular}{ccccccc}
-\toprule
- & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{F2} & \multicolumn{1}{c}{F3} & \multicolumn{1}{c}{F4} & \multicolumn{1}{c}{F5} & \multicolumn{1}{c}{Communality}\\
-\midrule
-item43 & 0.99 & - & - & - & - & 0.99\\
-item26 & 0.93 & - & - & - & - & 0.9\\
-item32 & 0.8 & - & - & - & - & 0.67\\
-item10 & - & 0.82 & - & - & - & 0.68\\
-item47 & - & 0.82 & - & - & - & 0.7\\
-item36 & - & 0.63 & - & - & - & 0.45\\
-item44 & - & -0.47 & - & - & - & 0.24\\
-item35 & - & 0.46 & - & - & - & 0.24\\
-item13 & - & 0.34 & - & - & - & 0.13\\
-item14 & - & - & 0.89 & - & - & 0.81\\
-item41 & - & - & 0.7 & - & - & 0.6\\
-item7 & - & - & 0.66 & - & - & 0.45\\
-item27 & - & - & 0.38 & - & - & 0.21\\
-item21 & - & - & -0.34 & - & - & 0.12\\
-item34 & - & - & - & 0.84 & - & 0.74\\
-item19 & - & - & - & 0.8 & - & 0.64\\
-item2 & - & - & - & 0.67 & - & 0.54\\
-item5 & - & - & - & - & 0.69 & 0.51\\
-item24 & - & - & - & - & 0.54 & 0.33\\
-item30 & - & - & - & - & 0.52 & 0.29\\
-item1 & - & - & - & - & 0.35 & 0.13\\
-item16 & - & - & - & - & 0.31 & 0.21\\
-item28 & - & - & - & - & 0.31 & 0.1\\
-\% of variance & 11 & 10 & 9 & 9 & 6 & -\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} Only loading higher than .30 is reported}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/Residuals-1}
-
-}
-
-\caption{ Histogram of residulas:  five-factor solution}\label{fig:Residuals}
-\end{figure}
-
-\hypertarget{confirmatory-factor-analysis}{%
-\section{Confirmatory Factor Analysis}\label{confirmatory-factor-analysis}}
-
-\hypertarget{irt}{%
-\subsection{IRT}\label{irt}}
-
-\hypertarget{discussion}{%
-\section{Discussion}\label{discussion}}
 
@@
 
-\hypertarget{references}{%
-\section{References}\label{references}}
-
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-
-\hypertarget{refs}{}
-\begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-R-papaja}{}%
-Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
-
-\leavevmode\hypertarget{ref-bakerBasicsItemResponse2017}{}%
-Baker, F. B. (2017). \emph{The {Basics} of {Item Response Theory Using R}} (1st ed. 2017.). {Springer}.
-
-\leavevmode\hypertarget{ref-bandalosFactorAnalysisExploratory2018}{}%
-Bandalos, D. L., \& Finney, S. J. (2018). Factor analysis: {Exploratory} and confirmatory. In \emph{The reviewer's guide to quantitative methods in the social sciences} (pp. 98--122). {Routledge}.
-
-\leavevmode\hypertarget{ref-R-tinylabels}{}%
-Barth, M. (2021). \emph{{tinylabels}: Lightweight variable labels}. Retrieved from \url{https://github.com/mariusbarth/tinylabels}
-
-\leavevmode\hypertarget{ref-bartlettNoteMultiplyingFactors1954}{}%
-Bartlett, M. (1954). A {Note} on the {Multiplying Factors} for {Various Chi}-square {Approximations}. \emph{Journal of the Royal Statistical Society. Series B, Methodological}, \emph{16}(2), 296--298.
-
-\leavevmode\hypertarget{ref-bentlerPracticalIssuesStructural1987}{}%
-Bentler, P. M., \& Chou, C.-P. (1987). Practical {Issues} in {Structural Modeling}. \emph{Sociological Methods \& Research}, \emph{16}(1), 78--117. \url{https://doi.org/10.1177/0049124187016001004}
-
-\leavevmode\hypertarget{ref-brownConfirmatoryFactorAnalysis2015}{}%
-Brown, T. A. (2015). \emph{Confirmatory factor analysis for applied research} (2nd ed.). {New York, NY, US}: {The Guilford Press}.
-
-\leavevmode\hypertarget{ref-R-MOTE}{}%
-Buchanan, E.
-M., Gillenwaters, A., Scofield, J.
-E., \& Valentine, K.
-D.
-(2019).
-\emph{{MOTE: Measure of the Effect}: Package to assist in effect size calculations and their confidence intervals}.
-Retrieved from \url{http://github.com/doomlab/MOTE}
-
-\leavevmode\hypertarget{ref-cattellScreeTestNumber1966}{}%
-Cattell, R. B. (1966). The {Scree Test For The Number Of Factors}. \emph{Multivariate Behavioral Research}, \emph{1}(2), 245--276. \url{https://doi.org/10.1207/s15327906mbr0102_10}
-
-\leavevmode\hypertarget{ref-R-shiny}{}%
-Chang, W., Cheng, J., Allaire, J., Sievert, C., Schloerke, B., Xie, Y., \ldots{} Borges, B.
-(2021).
-\emph{Shiny: Web application framework for r}.
-Retrieved from \url{https://CRAN.R-project.org/package=shiny}
-
-\leavevmode\hypertarget{ref-comreyFirstCourseFactor1992}{}%
-Comrey, A. L., \& Lee, H. B. (1992). \emph{A first course in factor analysis, 2nd ed}. {Hillsdale, NJ, US}: {Lawrence Erlbaum Associates, Inc}.
-
-\leavevmode\hypertarget{ref-desjardinsHandbookEducationalMeasurement2018}{}%
-Desjardins, C., \& Bulut, O. (2018). \emph{Handbook of {Educational Measurement} and {Psychometrics Using R}}. \url{https://doi.org/10.1201/b20498}
-
-\leavevmode\hypertarget{ref-desjardinsHandbookEducationalMeasurement2018a}{}%
-Desjardins, C. D. (2018). \emph{Handbook of educational measurement and psychometrics using {R}} (O. Bulut \& ProQuest (Firm), Eds.). {Boca Raton, FL : CRC Press}.
-
-\leavevmode\hypertarget{ref-R-paran}{}%
-Dinno, A. (2018). \emph{Paran: Horn's test of principal components/factors}. Retrieved from \url{https://CRAN.R-project.org/package=paran}
-
-\leavevmode\hypertarget{ref-R-semPlot}{}%
-Epskamp, S. (2019). \emph{semPlot: Path diagrams and visual analysis of various SEM packages' output}. Retrieved from \url{https://CRAN.R-project.org/package=semPlot}
-
-\leavevmode\hypertarget{ref-R-qgraph}{}%
-Epskamp, S., Cramer, A.
-O.
-J., Waldorp, L.
-J., Schmittmann, V.
-D., \& Borsboom, D.
-(2012).
-{qgraph}: Network visualizations of relationships in psychometric data.
-\emph{Journal of Statistical Software}, \emph{48}(4), 1--18.
-
-\leavevmode\hypertarget{ref-R-purrr}{}%
-Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
-
-\leavevmode\hypertarget{ref-hornRationaleTestNumber1965}{}%
-Horn, J. L. (1965). A rationale and test for the number of factors in factor analysis. \emph{Psychometrika}, \emph{30}(2), 179--185. \url{https://doi.org/10.1007/BF02289447}
-
-\leavevmode\hypertarget{ref-hutchesonMultivariateSocialScientist1999}{}%
-Hutcheson, G. D. (1999). \emph{The multivariate social scientist : Introductory statistics using generalized linear models}. {London : SAGE}.
-
-\leavevmode\hypertarget{ref-R-DiagrammeRsvg}{}%
-Iannone, R. (2016). \emph{DiagrammeRsvg: Export DiagrammeR graphviz graphs as SVG}. Retrieved from \url{https://CRAN.R-project.org/package=DiagrammeRsvg}
-
-\leavevmode\hypertarget{ref-R-DiagrammeR}{}%
-Iannone, R. (2021). \emph{DiagrammeR: Graph/network visualization}. Retrieved from \url{https://github.com/rich-iannone/DiagrammeR}
-
-\leavevmode\hypertarget{ref-jacksonRevisitingSampleSize2003}{}%
-Jackson, D.
-L.
-(2003).
-Revisiting {Sample Size} and {Number} of {Parameter Estimates}: {Some Support} for the {N}:q {Hypothesis}.
-\emph{Structural Equation Modeling}, \emph{10}(1), 128--141.
-\url{https://doi.org/10.1207/S15328007SEM1001_6}
-
-\leavevmode\hypertarget{ref-R-semTools}{}%
-Jorgensen, T.
-D., Pornprasertmanit, S., Schoemann, A.
-M., \& Rosseel, Y.
-(2021).
-\emph{\texttt{semTools}: {U}seful tools for structural equation modeling}.
-Retrieved from \url{https://CRAN.R-project.org/package=semTools}
-
-\leavevmode\hypertarget{ref-kaiserIndexFactorialSimplicity1974}{}%
-Kaiser, H. F. (1974). An index of factorial simplicity. \emph{Psychometrika}, \emph{39}(1), 31--36. \url{https://doi.org/10.1007/bf02291575}
-
-\leavevmode\hypertarget{ref-R-ggcorrplot}{}%
-Kassambara, A. (2019). \emph{Ggcorrplot: Visualization of a correlation matrix using 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=ggcorrplot}
-
-\leavevmode\hypertarget{ref-klinePrinciplesPracticeStructural2015}{}%
-Kline, R. B. (2015). \emph{Principles and practice of structural equation modeling}. {The Guilford Press}.
-
-\leavevmode\hypertarget{ref-lorenzo-sevaHullMethodSelecting2011}{}%
-Lorenzo-Seva, U., Timmerman, M., \& Kiers, H.
-(2011).
-The {Hull Method} for {Selecting} the {Number} of {Common Factors}.
-\emph{Multivariate Behavioral Research}, \emph{46}, 340--364.
-\url{https://doi.org/10.1080/00273171.2011.564527}
-
-\leavevmode\hypertarget{ref-R-correlation}{}%
-Makowski, D., Ben-Shachar, M.
-S., Patil, I., \& Lüdecke, D.
-(2020).
-Methods and algorithms for correlation analysis in r.
-\emph{Journal of Open Source Software}, \emph{5}(51), 2306.
-\url{https://doi.org/10.21105/joss.02306}
-
-\leavevmode\hypertarget{ref-mardiaMeasuresMultivariateSkewness1970}{}%
-Mardia, K. V. (1970). Measures of multivariate skewness and kurtosis with applications. \emph{Biometrika}, \emph{57}(3), 519--530. \url{https://doi.org/10.1093/biomet/57.3.519}
-
-\leavevmode\hypertarget{ref-R-tibble}{}%
-Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
-
-\leavevmode\hypertarget{ref-R-EFA.MRFA}{}%
-Navarro-Gonzalez, D., \& Lorenzo-Seva, U. (2021). \emph{EFA.MRFA: Dimensionality assessment using minimum rank factor analysis}. Retrieved from \url{https://CRAN.R-project.org/package=EFA.MRFA}
-
-\leavevmode\hypertarget{ref-R-rsvg}{}%
-Ooms, J. (2021). \emph{Rsvg: Render SVG images into PDF, PNG, PostScript, or bitmap arrays}. Retrieved from \url{https://CRAN.R-project.org/package=rsvg}
-
-\leavevmode\hypertarget{ref-R-base}{}%
-R Core Team. (2021). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
-
-\leavevmode\hypertarget{ref-R-psych}{}%
-Revelle, W.
-(2021).
-\emph{Psych: Procedures for psychological, psychometric, and personality research}.
-Evanston, Illinois: Northwestern University.
-Retrieved from \url{https://CRAN.R-project.org/package=psych}
-
-\leavevmode\hypertarget{ref-R-lavaan}{}%
-Rosseel, Y. (2012). {lavaan}: An {R} package for structural equation modeling. \emph{Journal of Statistical Software}, \emph{48}(2), 1--36. Retrieved from \url{https://www.jstatsoft.org/v48/i02/}
-
-\leavevmode\hypertarget{ref-R-dlookr}{}%
-Ryu, C. (2021). \emph{Dlookr: Tools for data diagnosis, exploration, transformation}. Retrieved from \url{https://CRAN.R-project.org/package=dlookr}
-
-\leavevmode\hypertarget{ref-schonbrodtWhatSampleSize2013}{}%
-Schönbrodt, F.
-D., \& Perugini, M.
-(2013).
-At what sample size do correlations stabilize?
-\emph{Journal of Research in Personality}, \emph{47}(5), 609--612.
-\url{https://doi.org/10.1016/j.jrp.2013.05.009}
-
-\leavevmode\hypertarget{ref-shapiroAnalysisVarianceTest1965}{}%
-Shapiro, S. S., \& Wilk, M. B. (1965). An analysis of variance test for normality (complete samples). \emph{Biometrika}, \emph{52}(3-4), 591--611. \url{https://doi.org/10.1093/biomet/52.3-4.591}
-
-\leavevmode\hypertarget{ref-velicerDeterminingNumberComponents1976}{}%
-Velicer, W. (1976). Determining the {Number} of {Components} from the {Matrix} of {Partial Correlations}. \emph{Psychometrika}, \emph{41}, 321--327. \url{https://doi.org/10.1007/BF02293557}
-
-\leavevmode\hypertarget{ref-R-MASS}{}%
-Venables, W. N., \& Ripley, B. D. (2002). \emph{Modern applied statistics with s} (Fourth). New York: Springer. Retrieved from \url{https://www.stats.ox.ac.uk/pub/MASS4/}
-
-\leavevmode\hypertarget{ref-watkinsStepbyStepGuideExploratory2020}{}%
-Watkins, M. (2020). \emph{A {Step}-by-{Step Guide} to {Exploratory Factor Analysis} with {R} and {RStudio}}. \url{https://doi.org/10.4324/9781003120001}
-
-\leavevmode\hypertarget{ref-R-ggplot2}{}%
-Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
-
-\leavevmode\hypertarget{ref-R-stringr}{}%
-Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
-
-\leavevmode\hypertarget{ref-R-forcats}{}%
-Wickham, H. (2021a). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
-
-\leavevmode\hypertarget{ref-R-tidyr}{}%
-Wickham, H. (2021b). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
-
-\leavevmode\hypertarget{ref-R-tidyverse}{}%
-Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
-D., François, R., \ldots{} Yutani, H.
-(2019).
-Welcome to the {tidyverse}.
-\emph{Journal of Open Source Software}, \emph{4}(43), 1686.
-\url{https://doi.org/10.21105/joss.01686}
-
-\leavevmode\hypertarget{ref-R-readxl}{}%
-Wickham, H., \& Bryan, J. (2019). \emph{Readxl: Read excel files}. Retrieved from \url{https://CRAN.R-project.org/package=readxl}
-
-\leavevmode\hypertarget{ref-R-dplyr}{}%
-Wickham, H., François, R., Henry, L., \& Müller, K. (2021). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
-
-\leavevmode\hypertarget{ref-R-readr}{}%
-Wickham, H., \& Hester, J. (2021). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
-
-\leavevmode\hypertarget{ref-worthingtonScaleDevelopmentResearch2006}{}%
-Worthington, R.
-L., \& Whittaker, T.
-A.
-(2006).
-Scale {Development Research}: {A Content Analysis} and {Recommendations} for {Best Practices}.
-\emph{The Counseling Psychologist}, \emph{34}(6), 806--838.
-\url{https://doi.org/10.1177/0011000006288127}
-
-\leavevmode\hypertarget{ref-R-kableExtra}{}%
-Zhu, H. (2021). \emph{kableExtra: Construct complex table with 'kable' and pipe syntax}. Retrieved from \url{https://CRAN.R-project.org/package=kableExtra}
-
-\end{CSLReferences}
-
-\endgroup
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.00}}@{}}
+\toprule
+Short Form (17 Items) \\
+\midrule
+\endhead
+\textbf{F1: Blue Filter} \\
+I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day. \\
+I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day. \\
+I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1 hour before attempting to fall asleep. \\
+\textbf{F2: Natural Light} \\
+I spend 30 minutes or less per day (in total) outside. \\
+I spend between 1 and 3 hours per day (in total) outside. \\
+I spend more than 3 hours per day (in total) outside. \\
+I spend as much time outside as possible. \\
+I go for a walk or exercise outside within 2 hours after waking up. \\
+\textbf{F3: Smart Device} \\
+I use my mobile phone within 1 hour before attempting to fall asleep. \\
+I look at my mobile phone screen immediately after waking up. \\
+I check my phone when I wake up at night. \\
+\textbf{F4: Sleep Environment} \\
+I dim my mobile phone screen within 1 hour before attempting to fall asleep. \\
+I use a blue-filter app on my computer screen within 1 hour before attempting to fall asleep. \\
+I dim my computer screen within 1 hour before attempting to fall asleep. \\
+\textbf{F5: Electric Light} \\
+I use tunable lights to create a healthy light environment. \\
+I use LEDs to create a healthy light environment. \\
+I use an alarm with a dawn simulation light. \\
+\bottomrule
+\end{longtable}
 

### 2021-09-15 instrument.tex
Update

@@
   pdftitle={Light Exposure Behavior Assessment (LEBA): Long and Short Form},
-  pdfauthor={Mushfiqul Anwar Siraji, Rafael Robert Lazar, Juliëtte van Duijnhoven, Luc Schlangen, Shamsul Haque, Vineetha Kalavally, Céline Vetter, Gena Glickman, Karin Smolders, \& Manuel Spitschan},
+  pdfauthor={Mushfiqul Anwar Siraji*, Rafael Robert Lazar*, Juliëtte van Duijnhoven, Luc Schlangen, Shamsul Haque, Vineetha Kalavally, Céline Vetter, Gena Glickman, Karin Smolders, \& Manuel Spitschan**},
   pdflang={en-EN},
@@
 \title{\emph{Light Exposure Behavior Assessment (LEBA)}: Long and Short Form}
-\author{Mushfiqul Anwar Siraji\textsuperscript{}, Rafael Robert Lazar\textsuperscript{}, Juliëtte van Duijnhoven\textsuperscript{}, Luc Schlangen\textsuperscript{}, Shamsul Haque\textsuperscript{}, Vineetha Kalavally\textsuperscript{}, Céline Vetter\textsuperscript{}, Gena Glickman\textsuperscript{}, Karin Smolders\textsuperscript{}, \& Manuel Spitschan\textsuperscript{}}
+\author{Mushfiqul Anwar Siraji\textsuperscript{*}, Rafael Robert Lazar\textsuperscript{*}, Juliëtte van Duijnhoven\textsuperscript{}, Luc Schlangen\textsuperscript{}, Shamsul Haque\textsuperscript{}, Vineetha Kalavally\textsuperscript{}, Céline Vetter\textsuperscript{}, Gena Glickman\textsuperscript{}, Karin Smolders\textsuperscript{}, \& Manuel Spitschan\textsuperscript{**}}
 \date{}
 
-\affiliation{\phantom{0}}
+\affiliation{\vspace{0.5cm}\textsuperscript{*} Joint first authors\\\textsuperscript{**} Corresponding author: \href{mailto:manuel.spitschan@psy.ox.ac.uk}{\nolinkurl{manuel.spitschan@psy.ox.ac.uk}}}
 
@@
 
-\textbf{Disclaimer}: This is a non-public version of LEBA and still a work in progress.
+\textbf{Disclaimer}: This is a non-public version of LEBA (dated \today) and still a work in progress. Please do not distribute!
 
-LEBA captures light exposure-related behaviours on a 5 point Likert type scale ranging from 1 to 5 (Never =1; Rarely= 2; Sometimes =3; Often = 4; Always =5).
+LEBA captures light exposure-related behaviours on a 5 point Likert type scale ranging from 1 to 5 (Never/Does not apply/I don't know = 1; Rarely = 2; Sometimes = 3; Often = 4; Always = 5).
 The score of each factor is calculated by the summation of scores of items belonging to the corresponding factor.
+
+\newpage
 

### 2021-09-15 instrument.tex
Updates with smaller floats

@@
 \endhead
-\textbf{F1: Blue Filter} \\
+\textbf{F1: Blue-light filters} \\
 I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day. \\
@@
 I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1 hour before attempting to fall asleep. \\
-\textbf{F2: Natural Light} \\
+\textbf{F2: Natural light exposure} \\
 I spend 30 minutes or less per day (in total) outside. \\
@@
 I go for a walk or exercise outside within 2 hours after waking up. \\
-\textbf{F3: Smart Device} \\
+\textbf{F3: Use of smartphones and wearables} \\
 I use my mobile phone within 1 hour before attempting to fall asleep. \\
@@
 I look at my smartwatch when I wake up at night. \\
-\textbf{F4: Sleep Environment} \\
+\textbf{F4: Light in the sleep environment} \\
 I dim my mobile phone screen within 1 hour before attempting to fall asleep. \\
@@
 I dim my computer screen within 1 hour before attempting to fall asleep. \\
-\textbf{F5: Electric Light} \\
+\textbf{F5: Electric home light} \\
 I use tunable lights to create a healthy light environment. \\
@@
 I check my phone when I wake up at night. \\
-\textbf{F4: Sleep Environment} \\
+\textbf{F4: Light in the sleep environment} \\
 I dim my mobile phone screen within 1 hour before attempting to fall asleep. \\

### 2021-09-15 manuscript.Rmd
Updates with smaller floats

@@
 # Introduction
-
+Our study had four objectives.
+First, to develop an instrument to assess an individual's light exposure behavior.
+Second, to conduct an exploratory factor analysis(EFA) to understand the latent structure.
+The third one is to gather structural validity evidence for the latent structure obtained in EFA.
+Lastly, we gathered item information using Item response theory (IRT)[@bakerBasicsItemResponse2017]
 # Methods
@@
 ```
-
-## Procedure
-
-Our study had four objectives.
-First, to develop an instrument to assess an individual's light exposure behavior.
-Second, to conduct an exploratory factor analysis(EFA) to understand the latent structure.
-The third one is to gather structural validity evidence for the latent structure obtained in EFA.
-Lastly, we gathered item information using Item response theory (IRT)[@bakerBasicsItemResponse2017]
 
@@
 
-```{r Iteminformationcurve, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
+```{r itminfo, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
 plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 

### 2021-09-16 manuscript.Rmd

@@
 
-## Merge "0"s and "1"s into "1"s 9select,subset assign)
+## Merge "0"s and "1"s into "1"s select,subset assign)
 descriptives.data[ , 9:56 ][ descriptives.data[ , 9:56 ] == 0 ] <- 1

### 2021-09-17 manuscript.Rmd
Adding text to Methods section

--- 2021-09-15 manuscript.Rmd
@@
     latex_engine: xelatex
-mainfont: Helvetica
-
+mainfont: Arial
 ---
@@
 # Introduction
+
 Our study had four objectives.
@@
 The third one is to gather structural validity evidence for the latent structure obtained in EFA.
-Lastly, we gathered item information using Item response theory (IRT)[@bakerBasicsItemResponse2017]
-# Methods
+Lastly, we gathered item information using Item response theory (IRT)[@bakerBasicsItemResponse2017] \# Methods
+
+## Ethical approval
+
+The cantonal ethics commission (Ethikkommission Nordwest- und Zentralschweiz, project ID Req-2021-00488) reviewed this project and issued an official clarification of responsibility (full document see Suppl.
+Fig X in appendix) stating: "The research project does not fall under the scope of the Human Research Act, because your project is using only anonymised data.
+An authorisation from the ethics committee is therefore not required and the EKNZ is not responsible for its review."
+
+## Data Availability
+
+## Survey characteristics
+
+Data was collected in a quantitative cross-sectional approach via a fully anonymous online survey hosted on REDCap [CITE REDCAP HERE 1, 2] by way of the University of Basel (sciCORE; <https://redcap.scicore.unibas.ch/>).
+Participants for the anonymous online survey were recruited via the website of a Comic co-released with the survey [CITE COMIC HERE; <https://enlightenyourclock.org/participate-in-research/>], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution via f.lux software [CITE f.lux Michael Herf?].
+
+Completing the online survey took approx.
+15 to 20 minutes and was not compensated.
+The first page of the survey comprised a participant information sheet, where participants' informed consent to participate was obtained before any of the questions were displayed.
+Underaged participants (\<18 years) were urged to obtain assent from their parents/legal guardians, before filling in the survey.
+Information on the first page included the objectives of the study, inclusion criteria, estimated duration, the use, storage and sharing of the data, compensation (none), and information about the type of questions in the survey.
+Moreover, participants needed to confirm that they were participating the survey for the first time.
+To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention.
+What is 4+5?").
+The data analysed in this study was collected between 17.05.2021 and 03.09.2021.
+Questions incorporating retrospective recall were all aligned to the period of "past four weeks", matching the presented LEBA instrument.
+
+In addition to the LEBA questionnaire, which is subject of the current study, the following variables and items were assessed but not included in the analysis:
+
+-   Sleep disturbance and sleep-related impairment [CITE]
+-   Sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration [CITE]
+-   Meal timing & caffeine consumption [CITE]
+-   Light sensitivity (photophobia vs. photophilia) [CITE]
+-   Self-reported pubertal stage (only if younger than 18 years old) [CITE]
+
+Furthermore, the following 1-item demographic variables were assessed:
+
+-   Age
+-   Sex
+-   Gender identity
+-   Occupational Status
+-   COVID-related Occupational setting during the past four weeks
+-   Time zone & country of residence
+-   English as native language
 
@@
 modify_header(label ~ "**Variable**") %>% 
-as_kable(format = 'pipe') -> desc_kable #save it as a kable
+as_kable(format = 'pipe') -> desc_kable #save it as a knitr::kable
 
@@
 
-desc_kable
-
-```
-
-Table 1 summarizes the demographic characteristics of the online survey participants.
-Anonymous online questionnaire responses from a total of *n* = `r nrow(desctable.data)` participants were included in the analysis of the current study, split into samples for exploratory (EFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "1.
+desc_kable %>% kable_styling(desc_kable, repeat_header_text = "Participants' Demographic Characteristics")
+
+```
+
+Table 1 summarizes the survey participants' demographic characteristics.
+Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses.
+XX participants were excluded from analysis due to not passing at least one of the "attention check" items.
+Anonymous responses from a total of *n* = `r nrow(desctable.data)` participants were included in the analysis of the current study, split into samples for exploratory (EFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "1.
 EFA Sample",])`) and confirmatory factor analysis (CFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "2.
 CFA Sample",])`).
-Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses.
-XX participants were excluded from analysis due to not passing at least one of the "attention check" items.
-The EFA sample included participants filling out the questionnaire from XX.XX.XXXX to YY.YY.YYYY, whereas participants who filled out the questionnaire from ZZ.ZZ.ZZZZ to 03.09.2021 were included in the CFA analysis.
-Participants reported filling out the online survey from a diverse range of geographic locations.
+The EFA sample included participants filling out the questionnaire from 17.05.2021 to XX.XX.XXXX , whereas participants who filled out the questionnaire from YY.YY.YYYY to 03.09.2021 were included in the CFA analysis.
+Participants indicated filling out the online survey from a diverse range of geographic locations.
 The four most common geographic locations included:
+
+`r kable(head(summary(descriptives.data$slypos_demographics_tz.factor), 4), format = "latex")`
+
+For a full list of geographic locations, see Suppl. Table X in the appendix.
+
+Age among all participants ranged from `r min(desctable.data$slypos_demographics_age)` years to `r max(desctable.data$slypos_demographics_age)` years (EFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
+EFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
+EFA Sample"])`; CFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
+CFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
+CFA Sample"])`), with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 0)` years of age (Overall: *M* = `r mean(desctable.data$slypos_demographics_age)`, *SD* = `r sd(desctable.data$slypos_demographics_age)`; EFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
+EFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
+EFA Sample"])`; CFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
+CFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
+CFA Sample"])`).
+In total 47% of participants indicated female sex (EFA: 44%; CFA: 52%), 51% indicated male (EFA: 54%; CFA: 46%) and 2% indicated other sex (EFA: 2.1%, CFA: 1.9%).
+Overall 7.2% (EFA: 7.8%; CFA: 6.2%) participants indicated a gender-variant identity.
+In a "Yes/No" question regarding native language 46% of respondents (EFA: 46%; CFA: 45%) indicated to be native English speakers.
+For their "Occupational Status", more than half (57%) of the overall sample reported that they currently work (EFA: 55%; CFA: 61%), whereas 25% (EFA: 29%; CFA: 20%) reported that they go to school and 17% (EFA: 17%; CFA: 19%) responded that they do neither.
+With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample 44% (EFA: 45%; CFA: 42%) of the participants indicated that they were in a home office/ home schooling setting., while 16% overall (EFA: 16%; CFA: 16%) reported face-to-face work/schooling.
+Lastly, 21% overall (EFA: 22%; CFA: 20%) reported a combination of home- and face-to-face work/schooling, whereas 19% overall (EFA: 17%; CFA: 23%) filled in the "Neither (no work or school, or indication)" response option.
+We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable "Age" and Pearson's Chi-squared test for all other categorical variables via the gtsummary R package's "add_p" function [CITE].
+The p-values were corrected for multiple testing applying false discovery rate (FDR) via the "add_q" function of the same package.
+After p-value (FDR) correction for multiple testing, none of the demographic variables were significantly different between the EFA sample and the CFA sample (all q-values *q* ≥ .2, indicating equivalence.
 
@@
 Currently, apart from some general suggestions, there exists no definitive rule to judge the item discrimination and item information parameter quality.
-In this current study, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information <.2).
-@bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70.
+In this current study, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information \<.2).
+@bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70.
 Among the 23 items, 10 items were highly discriminating.

### 2021-09-21 manuscript.Rmd

@@
 
-```{r setup-chunk, include=FALSE}
-knitr::opts_chunk$set(dev = "png",
-                      dpi = 600,
-                      echo = FALSE,
-                      cache = TRUE)
-
-```
-
 # Introduction
@@
 The third one is to gather structural validity evidence for the latent structure obtained in EFA.
-Lastly, we gathered item information using Item response theory (IRT)[@bakerBasicsItemResponse2017] \# Methods
+Lastly, we gathered item information using Item response theory (IRT)[@bakerBasicsItemResponse2017]
+
+# Methods
 
@@
 
-```{r FlowchartFig, fig.align='center', fig.cap='Development', out.height='100%', out.width='100%'}
+```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development', out.height='100%', out.width='100%'}
 knitr::include_graphics('Manuscript.figures/Flowchart1.png')
@@
 
-```{r tabDes}
+```{r tabDes,results='asis'}
 apa_table(Des.combined, caption = "Descriptive Statistics", align = "c", note = "*p<.001", longtable =T)
@@
 
-```{r figCor,out.width="50%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}
+```{r figCor,out.width="70%",out.width="100%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}
 
@@
 
-```{r EFAplot, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, out.height="100%", out.width="120%"}
+```{r EFAplot, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, out.height="50%", out.width="100%", results='asis'}
 knitr::include_graphics('Manuscript.figures/EFAplot.png')
@@
 
-apa_table(factor.des,align = "c", note = "Only loading higher than .30 is reported")
-```
-
-```{r Residuals, out.height= "50%",  fig.align='center', fig.cap= ' Histogram of residulas:  five-factor solution',  out.width="50%",  warning=FALSE}
+apa_table(factor.des,align = "c", caption = "Factor loadings and communality of the retained items", note = "Only loading higher than .30 is reported", font_size = "tiny")
+```
+
+```{r Residuals, out.height= "50%",  fig.align='center', fig.cap= ' Histogram of residulas:  five-factor solution',  out.width="50%",  warning=FALSE, results='asis'}
 hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))
@@
 
-```{r tabCfa, results='asis'}
+```{r cfaMat, results='asis'}
 CFa.matrix <- matrix("NA", nrow =2, ncol = 9)
@@
                    apa(cfa.sum.2$FIT[35],2,T))
-
-apa_table(CFa.matrix, caption = "Fit indices of CFA", align = "c", landscape = T)
-
-```
-
-```{r figcfa, fig.cap = "(A) Five Factor Model of LEBA", , out.width="100%",  warning=FALSE}
+```
+
+```{r tabCfa, results='asis'}
+apa_table(CFa.matrix, caption = "Fit indices of CFA", align = "c", landscape = T, note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index;RMSEA:Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square ")
+```
+
+```{r figcfa, fig.cap = "(A) Five Factor Model of LEBA", , out.width="100%",  warning=FALSE, results='asis'}
 #library(semPlot)
@@
 
-```{r InvarianceTab}
+```{r InvarianceTab, results='asis'}
 apa_table(Invariance.table, align = "c",  caption = "Invariance Analysis", note = " a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual;* =  df of model comparison", landscape = T, font_size = "scriptsize" )
@@
 
-## IRT
+## Developing the short form of LEBA
 
@@
 
-We combined the EFA and CFA sample (N= 690) and fit each factor of LEBA as a unidimensional construct, and used the graded response model to obtain item parameters(\@ref(tab:IRTparameters).
+To develop a shorter form of the LEBA we sought to Item response theory.IRT complements the conventional classical test theory-based analysis by gathering information on item discrimination and item difficulty[@bakerBasicsItemResponse2017].
+Here, an item’s quality is judged based on item information in relation to participants’ latent trait level ($\theta$).
+We gathered evidence on item quality  by fitting  each factor of LEBA with the graded response model to the combined EFA sample and CFA sample (n =690)(\@ref(tab:IRTparameters).
 Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait, and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
 Currently, apart from some general suggestions, there exists no definitive rule to judge the item discrimination and item information parameter quality.
-In this current study, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information \<.2).
+Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information \<.2) to develop the short form of LEBA.
 @bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70.
-Among the 23 items, 10 items were highly discriminating.
-Items 16 and 33 had very high discrimination parameters (28.55 & 13.50), indicating their limited applicability to people with a very high level of the latent attribute.
+Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), low ( 5 items) indicating  a good range of discrimination along the latent trait.
 Examination of the item information curve indicated 6 items (1, 25, 9, 38, 30, & 41) had relatively flat information curves thus discarded.
 
-```{r IRTparameters}
+```{r IRTparameters, results='asis'}
 apa_table(itemparameters, caption = "IRT Item parameters for the LEBA Scale", note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
@@
 ```{r itminfo, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
-plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
-          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10 )
-
-```
-
-```{r}
+knitr::include_graphics('Manuscript.figures/Item Informationjpg.jpg')
+
+```
+
+```{r shortIRT, include=FALSE}
+F1 <- sem.data %>% 
+  dplyr::select(item16, item36,  item17)
 F2.redu <- sem.data %>% 
@@
   dplyr::select(item46, item45, item25 )
+
+F1_fit <- mirt(F1, model = 1, itemtype = 'graded', 
+               SE = TRUE, Se.type = 'MHRM',
+               technical = list(NCYCLES = 10000))
+
+F2_fit.redu <- mirt(F2.redu, model = 1, itemtype = 'graded', SE = TRUE,
+               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
+
+F3_fit.redu <- mirt(F3.redu, model = 1, itemtype = 'graded', SE = TRUE,
+               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
+
+F4_fit.redu <- mirt(F4.redu, model = 1, itemtype = 'graded', SE = TRUE,
+               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
+
+F5_fit <- mirt(F5, model = 1, itemtype = 'graded', SE = TRUE,
+               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
+
+# Plots2 ####
+
+F1_info <- plot(F1_fit, type = "infoSE", main = "Blue Filter")
+
+F2_info.redu <- plot(F2_fit.redu, type = "infoSE", main = "Natural Light Test Information")
+
+F3_info.redu <- plot(F3_fit.redu, type = "infoSE", main = "Smart Device Test Information")
+
+F4_info.redu <- plot(F4_fit.redu, type = "infoSE", main = "Sleep Environment Test Information")
+
+F5_info <- plot(F5_fit, type = "infoSE", main = "Electric Light Test Information")
+
+Test_Info <- plot_grid(F1_info, F2_info.redu,F3_info.redu,F4_info.redu,F5_info, 
+          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)
+
+```
+
+Test information curve (TIC) indicate the amount of information an the full-scale carry along the latent trait continuum.
+As we treated each factor of LEBA as an unidmensional construct we obtain 5 TICs ().
+These information curves indicated except Blue filter factor, the other factor's curve is roughly centered on the center of the trait continuum (($\theta$)) and the The amount of information changed rather steadily with the change of ($\theta$).
+Thus we conferred the LEBA scale (except blue filter)  estimated the light exposure related behavior with precision near the center of trait continuum [@bakerBasicsItemResponse2017] which is sufficient to discriminate between latent trait measured by the each factor.
+The blue filter factor had a peak to the right side of the center of latent trait indicating its ability to providing information only for people who already have some preference towards using blue-filters.
+
+```{r fscore, include=FALSE}
+LEBA.Total <- sem.data %>% 
+  rowwise() %>% 
+  mutate(F1.Total = sum(item16, item36,  item17))
+
+LEBA.Total <- LEBA.Total %>% 
+  rowwise() %>% 
+  mutate(F2.Total = sum(item11,  item10 , item12, item7, Ritem8))
+
+LEBA.Total <- LEBA.Total %>% 
+  rowwise() %>% 
+  mutate(F3.Total = sum(item27, item3,  item40))
+
+LEBA.Total <- LEBA.Total %>% 
+  rowwise() %>% 
+  mutate(F4.Total = sum(item32, item35,  item33))
+
+LEBA.Total <- LEBA.Total %>% 
+  rowwise() %>% 
+  mutate(F5.Total = sum(item46, item45, item25))
+
+F1.estimation <- as.vector(fscores(F1_fit, method = "EAP",
+                                           full.scores = TRUE, 
+                                           full.scores.SE = F))
+
+F2.estimation <- as.vector(fscores(F2_fit.redu, method = "EAP",
+                                           full.scores = TRUE, 
+                                           full.scores.SE = F))
+
+F3.estimation <- as.vector(fscores(F3_fit.redu, method = "EAP",
+                                           full.scores = TRUE, 
+                                           full.scores.SE = F))
+
+F4.estimation <- as.vector(fscores(F4_fit.redu, method = "EAP",
+                                           full.scores = TRUE, 
+                                           full.scores.SE = F))
+
+F5.estimation <- as.vector(fscores(F5_fit, method = "EAP",
+                                           full.scores = TRUE, 
+                                           full.scores.SE = F))
+
+Ability.F1 <- data.frame(Rawscore = LEBA.Total$F1.Total,
+                      Theta =  F1.estimation)
+
+Ability.F2 <- data.frame(Rawscore = LEBA.Total$F2.Total,
+                      Theta =  F2.estimation)
+
+Ability.F3 <- data.frame(Rawscore = LEBA.Total$F3.Total,
+                      Theta =  F3.estimation)
+
+Ability.F4 <- data.frame(Rawscore = LEBA.Total$F3.Total,
+                      Theta =  F3.estimation)
+
+Ability.F5 <- data.frame(Rawscore = LEBA.Total$F3.Total,
+                      Theta =  F3.estimation)
+
+ggplot(Ability.F1, aes(x =Theta, y =Rawscore)) +
+  geom_point() +
+  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
+  xlim(-2,2) +
+  ylim(0,15)
+
+ggplot(Ability.F2, aes(x =Theta, y =Rawscore)) +
+  geom_point() +
+  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
+  xlim(-2,2) +
+  ylim(0,15)
+
+ggplot(Ability.F3, aes(x =Theta, y =Rawscore)) +
+  geom_point() +
+  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
+  xlim(-2,2) +
+  ylim(0,15)
+
+ggplot(Ability.F4, aes(x =Theta, y =Rawscore)) +
+  geom_point() +
+  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
+  xlim(-2,2) +
+  ylim(0,15)
+
+ggplot(Ability.F5, aes(x =Theta, y =Rawscore)) +
+  geom_point() +
+  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
+  xlim(-2,2) +
+  ylim(0,15)
+
+Score.correation <- cbind(Ability.F1,Ability.F2, Ability.F3, Ability.F4, Ability.F5)
+colnames(Score.correation) <- c("F1.Raw", "F1.Estimated","F2.Raw", "F2.Estimated","F3.Raw", "F3.Estimated","F4.Raw", "F4.Estimated","F5.Raw", "F5.Estimated")
+
+F1.cor <- corr.test(Score.correation$F1.Raw, Score.correation$F1.Estimated)
+
+F2.cor <- corr.test(Score.correation$F2.Raw, Score.correation$F2.Estimated)
+
+F3.cor <- corr.test(Score.correation$F3.Raw, Score.correation$F3.Estimated)
+
+F4.cor <- corr.test(Score.correation$F4.Raw, Score.correation$F4.Estimated)
+
+F5.cor <- corr.test(Score.correation$F5.Raw, Score.correation$F5.Estimated)
+
+#Putting significance star for correlation
+F1.p <-F1.cor$p
+F1.stars <- ifelse(F1.p < .001, "***"
+                   , ifelse(p < .01, "**"
+                            , ifelse(p < .05, "*"
+                                     , ifelse(p < .10, "+", " "))))
+
+F2.p <-F2.cor$p
+F2.stars <- ifelse(F2.p < .001, "**"
+                   , ifelse(p < .01, "**"
+                            , ifelse(p < .05, "*"
+                                     , ifelse(p < .10, "+", " "))))
+
+F3.p <-F3.cor$p
+F3.stars <- ifelse(F3.p < .001, "***"
+                   , ifelse(p < .01, "**"
+                            , ifelse(p < .05, "*"
+                                     , ifelse(p < .10, "+", " "))))
+
+F4.p <-F4.cor$p
+F4.stars <- ifelse(F4.p < .001, "***"
+                   , ifelse(p < .01, "**"
+                            , ifelse(p < .05, "*"
+                                     , ifelse(p < .10, "+", " "))))
+
+F5.p <-F5.cor$p
+F5.stars <- ifelse(F5.p < .001, "***"
+                   , ifelse(p < .01, "**"
+                            , ifelse(p < .05, "*"
+                                     , ifelse(p < .10, "+", " "))))
+
+theta.correlation.matrix <- matrix("NA", nrow =1, ncol = 5)
+
+theta.correlation.matrix[1,1] <- paste(apa(F1.cor$r,2,F), F1.stars,sep="")
+theta.correlation.matrix[1,2] <- paste(apa(F2.cor$r,2,F), F2.stars,sep="")
+theta.correlation.matrix[1,3] <- paste(apa(F3.cor$r,2,F), F3.stars,sep="")
+theta.correlation.matrix[1,4] <- paste(apa(F4.cor$r,2,F), F4.stars,sep="")
+theta.correlation.matrix[1,5] <- paste(apa(F5.cor$r,2,F), F5.stars,sep="")
+
+as.data.frame(theta.correlation.matrix)
+colnames(theta.correlation.matrix) <- c("F1", "F2", "F3", "F4", "F5")
+```
+
+```{r, results='asis'}
+apa_table (theta.correlation.matrix, caption = "correlation coefficents of obtained scores and estimated latent trait for each factots", note = "* p < 0.05; ** p < 0.01; *** p < 0.001"  )
 ```

### 2021-09-21 manuscript.Rmd

--- 2021-09-21 manuscript.Rmd
@@
 
-ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower")
+ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
+           ggtheme = ggplot2::theme_minimal, tl.cex = 8,tl.srt = 90 )
 #p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")

### 2021-09-21 manuscript.Rmd

--- 2021-09-21 manuscript.Rmd
@@
                       style = rounded
-                     node[ margin = 0.2,width = 6.5, height = 1, fixedsize = true, fontsize = 18 ]
+                     node[ margin = 0.2,width = 7, height = 1, fixedsize = true, fontsize = 18 ]
 
@@
 
-ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower")
+ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
+           ggtheme = ggplot2::theme_minimal, tl.cex = 6,tl.srt = 90 )
 #p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")

### 2021-09-21 manuscript.Rmd

@@
 
-```{r dependencymanager, include = FALSE, warning=F}
+```{r dependencymanager, warning=FALSE, include=FALSE}
 knitr::opts_chunk$set(warning = F, error = F, message = F)
@@
 #Only use when you have added some pack
-#packrat::snapshot(ignore.stale=TRUE)
+packrat::snapshot(ignore.stale=TRUE)
 
@@
 ```{r eval=FALSE, include=FALSE}
-#if "packrat" doesnot work you can run this chunk manually to get all required packs"
+#if "packrat" does not work you can run this chunk manually to get all required packs"
 
@@
 We conducted a categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator as our response data was in ordinary nature [@desjardinsHandbookEducationalMeasurement2018a].
-Commonly used Model fit suggestions of [@huCutoffCriteriaFit1999] focused on (i) the comparative fit index (CFI;) (ii) the Tucker Lewis index (TLI) (CFI/TLI, $goodfit \geq .95$, $acceptable fit\geq .90$) (ii) the root mean square error of approximation (RMSEA; close to .06 or below), (iii) the standardized root mean square (SRMR; close to .08 or below) to estimate the model fit.
+Commonly used Model fit guidelines [@huCutoffCriteriaFit1999; @schumacker2004beginner] focused on (i) the comparative fit index (CFI;) (ii) the Tucker Lewis index (TLI) (CFI/TLI, $goodfit \geq .95$, $acceptable fit\geq .90$) (ii) the root mean square error of approximation (RMSEA; close to .06 or below), (iii) the standardized root mean square (SRMR; close to .08 or below) to estimate the model fit.
 The chi-square test is also used to estimate the absolute model fit.

### 2021-10-06 manuscript.Rmd
edited 2 references

@@
 
-Data was collected in a quantitative cross-sectional approach via a fully anonymous online survey hosted on REDCap [CITE REDCAP HERE 1, 2] by way of the University of Basel (sciCORE; <https://redcap.scicore.unibas.ch/>).
-Participants for the anonymous online survey were recruited via the website of a Comic co-released with the survey [CITE COMIC HERE; <https://enlightenyourclock.org/participate-in-research/>], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution via f.lux software [CITE f.lux Michael Herf?].
+Data was collected in a quantitative cross-sectional approach via a fully anonymous online survey hosted on REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel (sciCORE; <https://redcap.scicore.unibas.ch/>).
+Participants were recruited via the website of a Comic co-released with the survey [CITE COMIC HERE; <https://enlightenyourclock.org/participate-in-research/>], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution via f.lux software [CITE f.lux Michael Herf?].
 
@@
 To develop a shorter form of the LEBA we sought to Item response theory.IRT complements the conventional classical test theory-based analysis by gathering information on item discrimination and item difficulty[@bakerBasicsItemResponse2017].
-Here, an item’s quality is judged based on item information in relation to participants’ latent trait level ($\theta$).
+Here, an item's quality is judged based on item information in relation to participants' latent trait level ($\theta$).
 We gathered evidence on item quality by fitting each factor of LEBA with the graded response model to the combined EFA sample and CFA sample (n =690)(\@ref(tab:IRTparameters).

### 2021-10-07 manuscript.Rmd
updates

--- 2021-09-21 manuscript.Rmd
@@
 #Only use when you have added some pack
-packrat::snapshot(ignore.stale=TRUE)
+#packrat::snapshot(ignore.stale=TRUE)
 

### 2021-10-09 manuscript.Rmd
added notes on Introduction
Updates frtom siraji

@@
 # Introduction
+
+-   Light exposure is important
+
+-   Light exposure Behavior is important
+
+-   Table: Overview Existing Related Scales: items in total / items on light exposure (behaviour)
+
+-   Existing Scales: Review them in text
+
+-   None of these do light exposure behavior.
 
@@
 Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR value (SRMR = `r apa(fit.2[10],2,F)`) was also close to the suggestions of @huCutoffCriteriaFit1999.
-The internal consistency reliability coefficients McDonald's omega were `r apa(rel.k[5,1],2,F)`, `r apa(rel.k[5,2],2,F)`, `r apa(rel.k[5,3],2,F)`, `r apa(rel.k[5,4],2,F)`, `r apa(rel.k[5,5],2,F)` respectively indicating satisfactory reliability for F1, F2 and F4 [@najeracatalanReliabilityPopulationClassification2019]
+The internal consistency reliability coefficients coefficient alpha `r apa(rel.k[5,1],2,F)`, `r apa(rel.k[5,2],2,F)`, `r apa(rel.k[5,3],2,F)`, `r apa(rel.k[5,4],2,F)`, `r apa(rel.k[5,5],2,F)` respectively indicating satisfactory reliability for F1, F2 and F4 [@najeracatalanReliabilityPopulationClassification2019]
 

### 2021-10-12 manuscript.Rmd
EFA Plot direction

@@
 ```{r EFAplotcode, include=FALSE}
-#library(DiagrammeR)
+
 EFAplot <- grViz("
@@
 fixedsize = true, fontsize = 35]
+F5 [label = 'F5']
+F4 [label = 'F4']
+F3 [label = 'F3']
+F2 [label = 'F2']
 F1 [label = 'F1']
-F2 [label = 'F2']
-F3 [label = 'F3']
-F4 [label = 'F4']
-F5 [label = 'F5']
+
 node [fontname = Helvetica, shape = box]
@@
 edge [fontname = Helvetica, fontsize = 35]
-F1 -> b[label = '0.99']
-F1-> c [label = '0.93']
-F1-> d [label = '0.80']
+F5 -> u [label = '0.60']
+F5 -> v [label = '0.59']
+F5 -> w [label = '0.41']
+F5 -> x [label = '0.41']
+F5 -> y [label = '0.40']
+F5 -> z [label = '0.35']
+F4 -> p [label = '0.74']
+F4 -> q [label = '0.73']
+F4 -> r [label = '0.66']
+F4 -> s [label = '-0.39', color =red]
+F4 -> t [label = '0.39']
+F3 -> k [label = '0.80']
+F3 -> l [label = '0.80']
+F3 -> m [label = '0.65']
+F3 -> n [label = '0.49']
+F3 -> o [label = '36']
 F2 -> e [label = '0.79']
@@
 F2 -> j [label = '0.32']
-F3 -> k [label = '0.80']
-F3 -> l [label = '0.80']
-F3 -> m [label = '0.65']
-F3 -> n [label = '0.49']
-F3 -> o [label = '36']
-F4 -> p [label = '0.74']
-F4 -> q [label = '0.73']
-F4 -> r [label = '0.66']
-F4 -> s [label = '-0.39', color =red]
-F4 -> t [label = '0.39']
-F5 -> u [label = '0.60']
-F5 -> v [label = '0.59']
-F5 -> w [label = '0.41']
-F5 -> x [label = '0.41']
-F5 -> y [label = '0.40']
-F5 -> z [label = '0.35']
+F1 -> b[label = '0.99']
+F1-> c [label = '0.93']
+F1-> d [label = '0.80']
 }

### 2021-10-12 manuscript.Rmd
Flowchart1 Font

@@
 
-                    graph [layout = dot,fontsize = 20]
-
-                     node[shape = rectangle, margin = 0.2, width = 6.5, height = 1, 
+                    graph [fontname = Helvetica,layout = dot,fontsize = 20, ]
+
+                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 6.5, height = 1, 
                     fixedsize = true,fontsize = 20]
@@
 
-                    node[shape = rectangle, margin = 0.2, width = 6.5, height = 2, 
+                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 7.5, height = 2, 
                     fixedsize = true, fontsize = 20]
-                    C[label = 'Factor Identification
-                    Scree Plot: 6 Factors
-                    Parallel Analysis: 6 Factors
-                    Minimum Average Partial Method: 5 Factors
-                    Hull Method: 5 Factors']
+                    C[label = 
+                    <
+                    Factor Identification<br align = 'left'/>
+                    Scree Plot: 6 Factors<br align = 'left'/>
+                    Parallel Analysis: 6 Factors<br align = 'left'/>
+                    Minimum Average Partial Method: 5 Factors<br align = 'left'/>
+                    Hull Method: 5 Factors<br align = 'left'/>
+                    >
+                    ]
 
                      subgraph cluster_1 {
-                      graph[shape = rectangle]
+                      graph[fontname = Helvetica, shape = rectangle]
                       style = rounded
-                     node[ margin = 0.2,width = 7, height = 1, fixedsize = true, fontsize = 18 ]
+                     node[fontname = Helvetica, margin = 0.2,width = 9, height = 1, 
+                    fixedsize = true, fontsize = 18 ]
 
@@
                 subgraph cluster_2 {
-                      graph[shape = rectangle]
+                      graph[fontname = Helvetica,shape = rectangle]
                       style = rounded
-                     node[ margin = 0.2,width = 6.5, height = 1, fixedsize = true ]
+                     node[fontname = Helvetica, margin = 0.2,width = 6.5, height = 1, 
+                fixedsize = true, fontsize = 18 ]
                     6[label = '6-Factor  one factor with only two salient loadings']
@@
 
-                     edge[color = black,arrowhead = vee, arrowsize = 1.25]
+                     edge[fontname = Helvetica,color = black,arrowhead = vee, arrowsize = 1.25]
                      A ->B

### 2021-10-12 manuscript.Rmd
Updates

@@
 knitr::opts_chunk$set(warning = F, error = F, message = F)
+set.seed(123)
+```
+
+```{undefined eval=FALSE, include=FALSE}
 library(packrat)
@@
                       style = rounded
-                     node[fontname = Helvetica, margin = 0.2,width = 6.5, height = 1, 
+                     node[fontname = Helvetica, margin = 0.2,width = 8, height = 1, 
                 fixedsize = true, fontsize = 18 ]
-                    6[label = '6-Factor  one factor with only two salient loadings']
+                    6[label = '6-Factor solution: one factor emerged with only two salient loadings']
                     7[label = 'Rejected']
@@
 
+```{r MinVar, eval=FALSE, include=FALSE}
+# ScreePlot with minimum variance explained, message=FALSE, warning=FALSE}
+library(FactoMineR)
+library(factoextra)
+#PCA graph of variables
+pca = PCA(EFA.data)
+#Component ploted against percentage of explained variables
+fviz_eig(pca, addlabels = T, max.overlaps = Inf)
+```
+
 Scree plot ( Figure \@ref(fig:facid)) suggested a six-factor solution.

### 2021-10-12 manuscript.Rmd
Hull Method Overall plot font set to Hel

@@
 set.seed(123)
+par(family = "Helvetica")
 ```
@@
 library(packrat)
+#This chunk is disabled. Only run this to install the dependencies automatically.
 packrat::init()
@@
 
-```{r factor_identification, include=FALSE}
+```{r Parallel}
 
 # Parallel analysis
-paran(correlations$rho, iterations=500, centile=0, quietly=FALSE,
+Horn <- paran(correlations$rho, iterations=500, centile=0, quietly=FALSE,
            status=TRUE, all=FALSE, cfa=FALSE, graph=TRUE,
            color=TRUE, col=c("black","red","blue"),
-      lty=c(1,2,3), lwd=1, legend=TRUE, file="Manuscript.figures/parallel.png",
+           lty=c(1,2,3), lwd=1, legend=TRUE, 
            width=640, height=640, grdevice=png, seed=0, mat=NA, n=NA)
 
+Adjusted.EV <- data.frame(Horn$AdjEv)
+Adjusted.EV$type = c('Adjusted Ev')
+Adjusted.EV$num = c(row.names(Adjusted.EV))
+Adjusted.EV$num = as.numeric(Adjusted.EV$num)
+colnames(Adjusted.EV) = c('eigenvalue', 'type', 'num')
+
+Random.EV <- data.frame(Horn$RndEv)
+Random.EV$type = c('Random EV')
+Random.EV$num = c(row.names(Random.EV))
+Random.EV$num = as.numeric(Random.EV$num)
+colnames(Random.EV) = c('eigenvalue', 'type', 'num')
+
+Unadjusted.EV <- data.frame(Horn$Ev)
+Unadjusted.EV$type = c('Unadjusted EV')
+Unadjusted.EV$num = c(row.names(Unadjusted.EV))
+Unadjusted.EV$num = as.numeric(Unadjusted.EV$num)
+colnames(Unadjusted.EV) = c('eigenvalue', 'type', 'num')
+
+apatheme=theme_bw()+
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.background = element_blank(),
+        panel.border = element_blank(),
+        text=element_text(family = "Helvetica",),
+        legend.title=element_blank(),
+        axis.line.x = element_line(color='black'),
+        axis.line.y = element_line(color='black'))
+
+parallel = ggplot(Adjusted.EV, aes(x=num, y=eigenvalue, shape=type, color=type)) +
+  #Add lines connecting data points
+  geom_line()+
+    geom_line(data = Random.EV) +
+  geom_line(data = Unadjusted.EV)+
+    #Add the data points.
+  geom_point(size=1)+
+  geom_point(data = Random.EV, size=1)+
+  geom_point(data = Unadjusted.EV, size=1)+
+  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,1)) +
+   #Label the x-axis 'Factor Number', and ensure that it ranges from 1-max # of factors, increasing by one with each 'tick' mark.
+  scale_x_continuous(name='Factor Number', limits=c(0, 48),breaks=seq(0,48,4))+
+    #Add vertical line indicating parallel analysis suggested max # of factors to retain
+  geom_hline(yintercept=1, linetype = 'dashed') + apatheme
+
+```
+
+```{r ScreePlot}
+Scree <- scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
+      hline=NULL,add=F)
+
+FA.Scree <- data.frame(Scree$fv)
+FA.Scree$type = c('Factor Analysis')
+FA.Scree$num = c(row.names(FA.Scree))
+FA.Scree$num = as.numeric(FA.Scree$num)
+colnames(FA.Scree) = c('eigenvalue', 'type', 'num')
+
+PA.Scree <- data.frame(Scree$pcv)
+PA.Scree$type = c('Principal Component Analysis')
+PA.Scree$num = c(row.names(PA.Scree))
+PA.Scree$num = as.numeric(PA.Scree$num)
+colnames(PA.Scree) = c('eigenvalue', 'type', 'num')
+
+scree.plot <-ggplot(FA.Scree, aes(x=num, y=eigenvalue,color=type, shape=type))+
+   geom_line()+
+  geom_line(data = PA.Scree)+ 
+  geom_point(size=1)+
+  geom_point(data = PA.Scree, size=1)+
+  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,1)) +
+  scale_x_continuous(name='Factor Number', limits=c(0, 48),breaks=seq(0,48,4))+
+  geom_hline(yintercept=1, linetype = 'dashed') + apatheme 
+```
+
+```{r Hull}
 # HULL
@@
         details = TRUE)
-
+hull <- ggplot2::last_plot()
+Hull <- hull+ ggtitle(NULL) +xlab("Factor Number")+ylab("CAF")+ theme(panel.grid.major = element_blank(),
+                                               panel.grid.minor = element_blank(),
+                                               panel.background = element_blank(),
+                                               axis.line.x = element_line(color='black'),
+                                               axis.line.y = element_line(color='black'))
+
+```
+
+```{r}
 #MAP
 psych::VSS(EFA.data, rotate = "varimax", fm = 'minres', n.obs =428 )
-
-```
-
-```{r MinVar, eval=FALSE, include=FALSE}
-# ScreePlot with minimum variance explained, message=FALSE, warning=FALSE}
-library(FactoMineR)
-library(factoextra)
-#PCA graph of variables
-pca = PCA(EFA.data)
-#Component ploted against percentage of explained variables
-fviz_eig(pca, addlabels = T, max.overlaps = Inf)
-```
-
-Scree plot ( Figure \@ref(fig:facid)) suggested a six-factor solution.
+```
+
+Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution.
 Horn's parallel analysis [@hornRationaleTestNumber1965] with 500 iterations also indicated a six-factor solution.
@@
 
-```{r factor_identification_fig, eval=FALSE, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot, fig.ncol=2, warning=FALSE, (C) Hull method', fig.show="hold", out.height="50%", out.width="50%"}
-knitr::include_graphics('Manuscript.figures/parallel.png')
-scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
-      hline=NULL,add=F)
-knitr::include_graphics('Manuscript.figures/Hull.png')
+```{r facIdFig, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE}
+cowplot::plot_grid(parallel, scree.plot,Hull, labels = c('(A)', '(B)', '(C)'), label_size = 8)
 

### 2021-10-14 manuscript.Rmd
packrat updated

@@
 devtools::install_github("crsh/citr")
-
+remotes::install_github("jthomasmock/gtExtras")
+install.packages("gt")
 ```

### 2021-10-15 manuscript.Rmd
packrat updates

--- 2021-10-12 manuscript.Rmd
@@
 devtools::install_github("crsh/citr")
-
+remotes::install_github("jthomasmock/gtExtras")
+install.packages("gt")
+install.packages("plyr")
 ```
@@
 library(dlookr)
+library(plyr)
 library(tidyverse)

### 2021-10-16 manuscript.Rmd
Updates

@@
 ```{r dependencymanager, warning=FALSE, include=FALSE}
-knitr::opts_chunk$set(warning = F, error = F, message = F)
+knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600)
 set.seed(123)
@@
 
-```{r setup}
+```{r setup, include=FALSE}
 
@@
 
-Our study had four objectives.
-First, to develop an instrument to assess an individual's light exposure behavior.
-Second, to conduct an exploratory factor analysis(EFA) to understand the latent structure.
-The third one is to gather structural validity evidence for the latent structure obtained in EFA.
-Lastly, we gathered item information using Item response theory (IRT)[@bakerBasicsItemResponse2017]
++-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
+| Name                                            | Authors | Translations | Description                                                                            | Relevant Items |
++=================================================+=========+==============+========================================================================================+================+
+| Visual Light Sensitivity Questionnaire-8        |         |              | Eight-question survey to assess the presence and severity of photosensitivity symptoms |                |
++-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
+| Office Light Survey                             |         |              | To assess electrical lighting environment in Office                                    |                |
++-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
+| Harvard Light Exposure Assessment Questionnaire |         |              | Self-administered semiquantitative light questionnaire                                 |                |
++-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
+| Hospital Lighting Survey                        |         |              | 23 items questionnaire to assess light environment in a hospital                       |                |
++-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
+| Morningness-Eveningness Questionnaire           |         |              | 19 items questionnaire to understand your body clock                                   |                |
++-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
+| Munich Chronotype Questionnaire (MCTQ)          |         |              | 17 items questionnaire to understand individuals phase of entrainment                  |                |
++-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
+| Assessment of Sleep Environment                 |         |              | 13 items questionnaire measuring your sleep environment quality                        |                |
++-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
+| The Pittsburgh Sleep Quality Index (PSQI)       |         |              | 9 items inventory to measure sleep quality and sleeping pattern                        |                |
++-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
+|                                                 |         |              |                                                                                        |                |
++-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
+|                                                 |         |              |                                                                                        |                |
++-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
+
+: Existing related Scales
 
@@
 
-```{r Parallel}
+```{r Parallel, include=FALSE}
 
@@
 
-```{r ScreePlot}
+```{r ScreePlot, include=FALSE}
 Scree <- scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
@@
 
-```{r Hull}
+```{r Hull, include=FALSE}
 # HULL
@@
 
-```{r}
+```{r MAP, include=FALSE}
 #MAP

### 2021-10-16 manuscript.Rmd
Minor updates

@@
 install.packages("gt")
-install.packages("plyr")
+remotes::install_github("jthomasmock/gtExtras")
+install.packages("questionr")
 ```
@@
 
-```{r itminfo, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
-knitr::include_graphics('Manuscript.figures/Item Informationjpg.jpg')
-
-```
-
 ```{r shortIRT, include=FALSE}
@@
 
+```{r itminfo, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
+cowplot::plot_grid(F1_info, F2_info,F3_info,F4_info,F5_info, 
+          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)
+
+```
+
 ```{r fscore, include=FALSE}

### 2021-10-16 manuscript.Rmd
Added gt table

--- 2021-10-16 manuscript.Rmd
@@
     latex_engine: xelatex
-mainfont: Arial
+mainfont: Helvetica
 ---
@@
 install.packages("ggcorrplot")
-install.packages("car")
 install.packages("semTable")
@@
 install.packages("gt")
-install.packages("plyr")
+remotes::install_github("jthomasmock/gtExtras")
+install.packages("questionr")
+devtools::install_github("lbusett/insert_table")
 ```
@@
 library(MOTE)
+library(car)#revercoding 
 library(psych)
@@
 library(ggcorrplot)
-library(car) #Reversecoding
 library(semTable)
@@
 library(gtsummary)
+library(gt)
+library(gtExtras)
+library(likert)
+library(kutils)
 r_refs("references.bib")
@@
 
-+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
-| Name                                            | Authors | Translations | Description                                                                            | Relevant Items |
-+=================================================+=========+==============+========================================================================================+================+
-| Visual Light Sensitivity Questionnaire-8        |         |              | Eight-question survey to assess the presence and severity of photosensitivity symptoms |                |
-+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
-| Office Light Survey                             |         |              | To assess electrical lighting environment in Office                                    |                |
-+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
-| Harvard Light Exposure Assessment Questionnaire |         |              | Self-administered semiquantitative light questionnaire                                 |                |
-+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
-| Hospital Lighting Survey                        |         |              | 23 items questionnaire to assess light environment in a hospital                       |                |
-+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
-| Morningness-Eveningness Questionnaire           |         |              | 19 items questionnaire to understand your body clock                                   |                |
-+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
-| Munich Chronotype Questionnaire (MCTQ)          |         |              | 17 items questionnaire to understand individuals phase of entrainment                  |                |
-+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
-| Assessment of Sleep Environment                 |         |              | 13 items questionnaire measuring your sleep environment quality                        |                |
-+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
-| The Pittsburgh Sleep Quality Index (PSQI)       |         |              | 9 items inventory to measure sleep quality and sleeping pattern                        |                |
-+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
+```{=html}
+<!-- -->
+```
+    \newpage
+    \begin{landscape}
+
++-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
+| Name                                            | Authors | Description                                                                            | Relevant Items | Adaptations |
++=================================================+=========+========================================================================================+:==============:+=============+
+| Visual Light Sensitivity Questionnaire-8        | a       | Eight-question survey to assess the presence and severity of photosensitivity symptoms | all            | jhghjgjhgfd |
++-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
+| Office Light Survey                             | b       | Multi-item questionnaire to assess electrical lighting environment in office           | aa             | gh          |
++-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
+| Harvard Light Exposure Assessment Questionnaire | c       | Self-administered semiquantitative light qestionnaire                                  | aa             | as          |
++-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
+| Hospital Lighting Survey                        | d       | 23 items questionnaire to assess light environment in a hospital                       | dd             | fg          |
++-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
+| Morningness-Eveningness Questionnaire           | e       | 19 items questionnaire to understand your body clock                                   | ff             | hj          |
++-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
+| Munich Chronotype Questionnaire (MCTQ)          | f       | 17 items questionnaire to understand individuals phase of entrainment                  | ff             | jk          |
++-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
+| Assessment of Sleep Environment                 | g       | 13 items questionnaire measuring your sleep environment quality                        | ff             | kl          |
++-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
+| The Pittsburgh Sleep Quality Index (PSQI)       | h       | 9 items inventory to measure sleep quality and sleeping pattern                        | ff             | klfrgfgvfg  |
++-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
 |                                                 |         |                                                                                        |                |             |
-+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
++-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
 |                                                 |         |                                                                                        |                |             |
-+-------------------------------------------------+---------+--------------+----------------------------------------------------------------------------------------+----------------+
++-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
 
 : Existing related Scales
+
+    \end{landscape}
 
@@
 
-```{r figCor,out.width="70%",out.width="100%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}
+```{r figCor,out.width="100%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}
 
@@
 
-```{r facIdFig, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE}
+```{r facIdFig, out.height="100%", out.width="200%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE}
 cowplot::plot_grid(parallel, scree.plot,Hull, labels = c('(A)', '(B)', '(C)'), label_size = 8)
@@
 
+```{r gtvis, include =F}
+## Recoding sem.data$item8
+gt.data <- sem.data
+gt.data$item8 <- as.character(gt.data$item8)
+gt.data$item8 <- fct_recode(gt.data$item8,
+  "5" = "1",
+  "4" = "2",
+  "2" = "4",
+  "1" = "5"
+)
+
+## Recoding gt.data$item26
+gt.data$item26 <- as.character(gt.data$item26)
+gt.data$item26 <- fct_recode(gt.data$item26,
+  "5" = "1",
+  "4" = "2",
+  "2" = "4",
+  "1" = "5"
+)
+## Recoding gt.data$item37
+gt.data$item37 <- as.character(gt.data$item26)
+gt.data$item37 <- fct_recode(gt.data$item26,
+  "5" = "1",
+  "4" = "2",
+  "2" = "4",
+  "1" = "5"
+)
+
+names(gt.data)[names(gt.data) == "item1"] <- "item01"
+names(gt.data)[names(gt.data) == "item3"] <- "item03"
+names(gt.data)[names(gt.data) == "item4"] <- "item04"
+names(gt.data)[names(gt.data) == "item7"] <- "item07"
+names(gt.data)[names(gt.data) == "item8"] <- "item08"
+names(gt.data)[names(gt.data) == "item9"] <- "item09"
+
+#EFA data
+gt.efa.data <- gt.data[1:428, ]
+
+gt.efa.data.table <- gt.efa.data %>% 
+  dplyr::select(item16, item36, item17,
+                 item11, item10,item12,item07,item08,item09,
+                 item27,  item03, item40,  item30, item41,
+                 item33, item32,item35, item37,item38, 
+                 item46, item45, item25, item04, item01,item26)
+
+#Creating long data
+gt.efa.long <- as.data.frame(gather(gt.efa.data.table, Items, value))
+gt.efa.long$value <- as.numeric(as.character(gt.efa.long$value))
+
+#Summarizing and creating gt object
+gt.efa.tab <- gt.efa.long %>% 
+  group_by(Items) %>% 
+  # calculate summary stats & create data for the histogram and density plot
+  dplyr::summarise(
+    nr = n(),
+    mean = mean(value, na.rm = TRUE),
+    med = median(value, na.rm = TRUE),
+    sd = sd(value, na.rm = TRUE),
+    hist_data = list(value),
+    dens_data = list(value),
+    .groups = "drop"
+  ) %>% 
+  gt()
+
+#Preparation for likert data
+efa.LEBA.likert <- as.data.frame(gt.efa.data.table)
+
+recod_LEBA <- c( "1" = "Never", "2" = "Rarely", "3"= "Sometimes","4" = "Often",
+                 "5" = "Always")
+efa.LEBA.likert <-  mutate(efa.LEBA.likert, across(starts_with("item"), ~unname(recod_LEBA[.])))
+
+efa.LEBA.Factor = as.data.frame(lapply(efa.LEBA.likert,factor,
+                                   ordered = T))
+#get the items name
+efa.items <- names(efa.LEBA.Factor) 
+#Calculate percentage
+efa.percentage <- kutils::likert(efa.LEBA.Factor, vlist = efa.items )
+
+efa.percentage <- efa.percentage$table %>% 
+  as.data.frame(.)
+
+#data wrangling
+labels <- c("Always", "Never","Often", "Rarely", "Sometimes","Total")
+as.data.frame(labels)
+
+full.efa.percentage <- cbind(labels,efa.percentage) #tables with labels  
+full.efa.percentage<- t(full.efa.percentage ) #transpose
+as.data.frame(full.efa.percentage)
+full.efa.percentage1 <- full.efa.percentage[-1,-6] #removing 1st row and total column
+full.efa.percentage2 <- full.efa.percentage1[, c(2, 4, 5, 3,1)]# rearranging
+as.data.frame(full.efa.percentage2)
+
+colnames(full.efa.percentage2) <- c("Never","Rarely","Sometimes","Often","Always")
+
+efa.Items <- rownames(full.efa.percentage2)
+as.data.frame(efa.Items)
+full.efa.percentage3 <- cbind(efa.Items,full.efa.percentage2)
+
+full.efa.percentage3 <- full.efa.percentage3[order(efa.Items),] 
+full.efa.percentage3 <- as.data.frame(full.efa.percentage3[,-1]) %>% 
+  gt()
+
+gt.efa.table <- gt.efa.tab$'_data'
+gt.liket.efa <- full.efa.percentage3$"_data"
+
+efaTable <-  cbind( gt.efa.table, gt.liket.efa)%>% 
+  gt()
+
+gt.cfa.data <- gt.data[429:690,]
+gt.cfa.data.table <- gt.cfa.data %>% 
+  dplyr::select(item16, item36, item17,
+                 item11, item10,item12,item07,item08,item09,
+                 item27,  item03, item40,  item30, item41,
+                 item32,item35,item38, item33, 
+                 item46, item45, item25, item04, item01 )
+
+gt.cfa.long <- gather(gt.cfa.data.table, Items, value)
+gt.cfa.long$value <- as.numeric(as.character(gt.cfa.long$value))
+gt.cfa.tab <- gt.cfa.long %>% 
+  group_by(Items) %>% 
+# calculate summary stats & create data for the histogram and density plot
+  summarise(
+    nr = n(),
+    mean = mean(value, na.rm = TRUE),
+    med = median(value, na.rm = TRUE),
+    sd = sd(value, na.rm = TRUE),
+    hist_data = list(value),
+    dens_data = list(value),
+    .groups = "drop"
+  ) %>%
+
+  gt()
+
+#Preparation for likert data
+cfa.LEBA.likert <- as.data.frame(gt.cfa.data.table)
+
+recod_LEBA <- c( "1" = "Never", "2" = "Rarely", "3"= "Sometimes","4" = "Often",
+                 "5" = "Always")
+cfa.LEBA.likert <-  mutate(cfa.LEBA.likert, across(starts_with("item"), ~unname(recod_LEBA[.])))
+
+cfa.LEBA.Factor = as.data.frame(lapply(cfa.LEBA.likert,factor,
+                                   ordered = T))
+#get the items name
+cfa.items <- names(cfa.LEBA.Factor) 
+#Calculate percentage
+cfa.percentage <- kutils::likert(cfa.LEBA.Factor, vlist = cfa.items )
+
+cfa.percentage <- cfa.percentage$table %>% 
+  as.data.frame(.)
+
+#data wrangling
+labels <- c("Always", "Never","Often", "Rarely", "Sometimes","Total")
+as.data.frame(labels)
+
+full.cfa.percentage <- cbind(labels,cfa.percentage) #tables with labels  
+full.cfa.percentage <- t(full.cfa.percentage ) #transpose
+as.data.frame(full.cfa.percentage)
+full.cfa.percentage1 <- full.cfa.percentage[-1,-6] #removing 1st row and total column
+full.cfa.percentage2 <- full.cfa.percentage1[, c(2, 4, 5, 3,1)]# rearranging
+as.data.frame(full.cfa.percentage2)
+
+colnames(full.cfa.percentage2) <- c("Never","Rarely","Sometimes","Often","Always")
+
+cfa.Items <- rownames(full.cfa.percentage2)
+as.data.frame(cfa.Items)
+full.cfa.percentage3 <- cbind(cfa.Items,full.cfa.percentage2)
+
+full.cfa.percentage3 <- full.cfa.percentage3[order(cfa.Items),] 
+full.cfa.percentage3 <- as.data.frame(full.cfa.percentage3[,-1]) %>% 
+  gt()
+
+gt.cfa.table <- gt.cfa.tab$'_data'
+gt.liket.cfa <- full.cfa.percentage3$"_data"
+
+cfaTable <-  cbind( gt.cfa.table, gt.liket.cfa) %>% 
+  gt()
+
+efa.gt <- efaTable$"_data"
+cfa.gt <- cfaTable$"_data"
+
+gt.fullTable <-  rbind( efa.gt, cfa.gt) %>% 
+  gt() %>% 
+# histogram and density plots
+  gtExtras::gt_sparkline(
+    hist_data,
+    type = "histogram",
+    line_color = "black", 
+    fill_color = "grey",
+    bw = 1,
+    same_limit = TRUE)%>%
+  gtExtras::gt_sparkline(
+    dens_data,
+    type = "density",
+    line_color = "black", 
+    fill_color = "grey",
+    bw = 0.75,
+    same_limit = TRUE
+  )%>%
+# format decimals
+  fmt_number(columns = mean:sd, decimals = 1) %>%
+# header
+  tab_header(
+    title = md("**LEBA**"),
+    subtitle = md("Summary results of LEBA (N =690)")
+  ) %>% 
+  tab_footnote(
+    footnote = md("**Histogram**"),
+    locations = cells_column_labels(columns = hist_data)
+  ) %>%
+  tab_footnote(
+    footnote = md("**Density**"),
+    locations = cells_column_labels(columns = dens_data)
+  ) %>% 
+#create groups of columns
+tab_spanner(
+  label = "Items",
+  columns = Items
+) %>%
+  tab_spanner(
+    label = "Summary Statistics",
+    columns = nr:sd
+  ) %>%
+  tab_spanner(
+    label = "Graphics",
+    columns = hist_data:dens_data
+  ) %>% 
+  tab_spanner(
+    label = "Response Pattern",
+    columns = Never:Always
+  ) %>%
+# change column names to appear in the table
+cols_label(
+  Items = ("LEBA  Items"),
+  nr = ("n"),
+  mean = ("Mean"),
+  med = ("Median "),
+  sd = (("SD")),
+  hist_data = "Histogram",
+  dens_data = "Density"
+) %>%
+# set alignment as per wish
+  cols_align(
+    align = "center",
+    columns = everything()
+  ) %>%
+  opt_align_table_header(align = "left") %>%
+# add coloured dots and lines on the first column
+  gt_plt_dot(
+    mean,
+    Items,
+    palette = "ggthemes::fivethirtyeight"
+  ) %>% 
+    tab_row_group(
+      group = "CFA (n =262)",
+     rows = 26:48
+
+  ) %>% 
+  tab_row_group(
+  group = "EFA (n = 428)",
+    rows = 1:25  
+  ) %>% gtsave("Manuscript.figures/gt.png")
+
+```
+
+```{r gtPic, echo=FALSE, out.height="100%", out.width="200%", results= 'asis'}
+knitr::include_graphics('Manuscript.figures/gt.png')
+
+```
+
 # Confirmatory Factor Analysis
@@
 CFA.data <- sem.data[429:690,]
-CFARitem8 = recode(CFA.data$item8, '1=5; 2=4; 3=3; 4=2; 5=1')
-CFARitem37 = recode(CFA.data$item37, '1=5; 2=4; 3=3; 4=2; 5=1')
-CFARitem26 = recode(CFA.data$item26, '1=5; 2=4; 3=3; 4=2; 5=1')
-CFA.data <- CFA.data %>% 
-  mutate(Ritem8 = CFARitem8, Ritem37 = CFARitem37, Ritem26 = CFARitem26)
+
+## Recoding CFA.data$item8 into CFA.data$Ritem8
+CFA.data$Ritem8 <- as.character(CFA.data$item8)
+CFA.data$Ritem8 <- fct_recode(CFA.data$Ritem8,
+  "5" = "1",
+  "4" = "2",
+  "2" = "4",
+  "1" = "5"
+)
+CFA.data$Ritem8 <- as.numeric(as.character(CFA.data$Ritem8))
+
+## Recoding CFA.data$item37 into CFA.data$item37_rec
+CFA.data$Ritem37 <- as.character(CFA.data$item37)
+CFA.data$Ritem37 <- fct_recode(CFA.data$Ritem37,
+  "5" = "1",
+  "4" = "2",
+  "2" = "4",
+  "1" = "5"
+)
+CFA.data$Ritem37 <- as.numeric(as.character(CFA.data$Ritem37))
+
+## Recoding CFA.data$item26 into CFA.data$Ritem26
+CFA.data$Ritem26 <- as.character(CFA.data$item26)
+CFA.data$Ritem26 <- fct_recode(CFA.data$Ritem26,
+  "5" = "1",
+  "4" = "2",
+  "2" = "4",
+  "1" = "5"
+)
 
@@
 ```{r IRT data, include=FALSE}
-
-IRTitem8 = recode(sem.data$item8, '1=5; 2=4; 3=3; 4=2; 5=1')
-IRTitem37 = recode(sem.data$item37, '1=5; 2=4; 3=3; 4=2; 5=1')
-IRTitem26 = recode(sem.data$item26, '1=5; 2=4; 3=3; 4=2; 5=1')
-sem.data <- sem.data %>% 
-  mutate(Ritem8 = IRTitem8, Ritem37 = IRTitem37, Ritem26 = IRTitem26)
+## Recoding sem.data$item8 into sem.data$Ritem8
+sem.data$Ritem8 <- as.character(sem.data$item8)
+sem.data$Ritem8 <- fct_recode(sem.data$Ritem8,
+  "5" = "1",
+  "4" = "2",
+  "2" = "4",
+  "1" = "5"
+)
+sem.data$Ritem8 <- as.numeric(as.character(sem.data$Ritem8))
+# Recoding sem.data$item26 
+sem.data$Ritem26 <- as.character(sem.data$item26)
+sem.data$Ritem26 <- fct_recode(sem.data$Ritem26,
+  "5" = "1",
+  "4" = "2",
+  "2" = "4",
+  "1" = "5"
+)
+sem.data$Ritem26 <- as.numeric(as.character(sem.data$Ritem26))
+
+# Recoding sem.data$item37 i
+sem.data$Ritem37 <- as.character(sem.data$item37)
+sem.data$Ritem37 <- fct_recode(sem.data$Ritem37,
+  "5" = "1",
+  "4" = "2",
+  "2" = "4",
+  "1" = "5"
+)
+sem.data$Ritem37 <- as.numeric(as.character(sem.data$Ritem37))
 
@@
 F1_OCC <- plot(F1_fit, type = "trace", facet =T, main = "Blue Filter OCC")
-F1_info <- plot(F1_fit, type = "infoSE", main = "Blue Filter Test Information")
+F1_info <- plot(F1_fit, type = "infoSE", main = "F1")
 F1_iteminfo <- plot(F1_fit, type = "infotrace", 
@@
 F2_OCC <- plot(F2_fit, type = "trace", facet =T, main = "Natural Light OCC")
-F2_info <- plot(F2_fit, type = "infoSE", main = "Natural Light Test Information")
+F2_info <- plot(F2_fit, type = "infoSE", main = "F2")
 F2_iteminfo <- plot(F2_fit, type = "infotrace", facet_items = T, main = "Natural Light")
@@
 F3_OCC <-plot(F3_fit, type = "trace", facet =T, main = "Smart Device OCC")
-F3_info <- plot(F3_fit, type = "infoSE", main = "Smart Device Test Information")
+F3_info <- plot(F3_fit, type = "infoSE", main = "F3")
 F3_iteminfo <- plot(F3_fit, type = "infotrace", 
@@
 F4_OCC <-plot(F4_fit, type = "trace", facet =T, main = "Sleep Environment OCC")
-F4_info <- plot(F4_fit, type = "infoSE", main = "Sleep Environment Test Information")
+F4_info <- plot(F4_fit, type = "infoSE", main = "F4")
 F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = "Sleep Environment")
@@
 F5_OCC <-plot(F5_fit, type = "trace", facet =T, main = "Electric Light OCC")
-F5_info <- plot(F5_fit, type = "infoSE", main = "Electric Light Test Information")
+F5_info <- plot(F5_fit, type = "infoSE", main = "F5")
 F5_iteminfo <- plot(F5_fit, type = "infotrace", facet_items = T,main = "Electric Light")
@@
 
-F1_info <- plot(F1_fit, type = "infoSE", main = "Blue Filter")
-
-F2_info.redu <- plot(F2_fit.redu, type = "infoSE", main = "Natural Light Test Information")
-
-F3_info.redu <- plot(F3_fit.redu, type = "infoSE", main = "Smart Device Test Information")
-
-F4_info.redu <- plot(F4_fit.redu, type = "infoSE", main = "Sleep Environment Test Information")
-
-F5_info <- plot(F5_fit, type = "infoSE", main = "Electric Light Test Information")
+F1_info <- plot(F1_fit, type = "infoSE", main = "F1")
+
+F2_info.redu <- plot(F2_fit.redu, type = "infoSE", main = "F2")
+
+F3_info.redu <- plot(F3_fit.redu, type = "infoSE", main = "F3")
+
+F4_info.redu <- plot(F4_fit.redu, type = "infoSE", main = "F4")
+
+F5_info <- plot(F5_fit, type = "infoSE", main = "F5")
 
@@
 The blue filter factor had a peak to the right side of the center of latent trait indicating its ability to providing information only for people who already have some preference towards using blue-filters.
+
+```{r itminfo, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
+plot_grid(F1_info, F2_info.redu,F3_info.redu,F4_info.redu,F5_info, 
+          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)
+
+```
 

### 2021-10-17 manuscript.Rmd
Updates

@@
   geom_point(data = Unadjusted.EV, size=1)+
-  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,1)) +
+  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
    #Label the x-axis 'Factor Number', and ensure that it ranges from 1-max # of factors, increasing by one with each 'tick' mark.
@@
   geom_point(data = PA.Scree, size=1)+
-  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,1)) +
+  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
   scale_x_continuous(name='Factor Number', limits=c(0, 48),breaks=seq(0,48,4))+
@@
 
-```{r facIdFig, out.height="100%", out.width="200%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE}
-cowplot::plot_grid(parallel, scree.plot,Hull, labels = c('(A)', '(B)', '(C)'), label_size = 8)
+```{r facIdFig, out.height="100%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}
+cowplot::plot_grid(parallel, scree.plot,Hull, labels = c('(A)', '(B)', '(C)'),ncol=1, label_size = 8)
 

### 2021-10-17 manuscript.Rmd
Chunks renamed,clutter free snapshot

@@
 
-```{r dependencymanager, warning=FALSE, include=FALSE}
+```{r setup, warning=FALSE, include=FALSE}
 knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600)
@@
 
-```{undefined eval=FALSE, include=FALSE}
+```{r depMan, eval=FALSE, include=FALSE}
 library(packrat)
@@
 
-```{r eval=FALSE, include=FALSE}
+```{r install, eval=FALSE, include=FALSE}
 #if "packrat" does not work you can run this chunk manually to get all required packs"
@@
 
-```{r setup, include=FALSE}
+```{r library, include=FALSE}
 
@@
 
-```{=html}
-<!-- -->
-```
-    \newpage
-    \begin{landscape}
-
 +-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
@@
 
-    \end{landscape}
-
 # Methods
@@
 
-```{r preparingData, include=FALSE}
+```{r Data, include=FALSE}
 data <- readRDS("leba_2021-09-08.rds")
@@
 colnames(sem.data) <- colnam
-```
-
-```{r descriptives, eval=FALSE, include=FALSE}
-#Use these  data frames for descriptive
-EFA.descriptives #Only EFA, n =428
-CFA.descriptives #Only CFA, n =262  
-descriptives.data# Total sample, n = 690
-
 ```
@@
 
-```{r flowchart, include=FALSE }
+```{r Manuflowchart, include=FALSE }
 Flowchart1 <- grViz("digraph nicegraph{
@@
 # Results
+
+```{r ggplot2, include=F}
+apatheme=theme_bw()+
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.background = element_blank(),
+        text=element_text(family = "Helvetica",),
+        legend.title=element_blank(),
+        axis.line.x = element_line(color='black'),
+        axis.line.y = element_line(color='black'),
+        panel.border = element_rect(color = "black",
+                                    fill = NA,
+                                    size = 1))
+```
 
@@
 
-```{r CorrelationMatrix, include=FALSE}
+```{r CorrMatrix, include=FALSE}
 #Polychoric Correlation matrix
@@
 
-```{r figCor,out.width="100%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}
+```{r figCor, out.width="100%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}
 
@@
 
-```{r Parallel, include=FALSE}
+```{r ParallelEFA, include=FALSE}
 
@@
 colnames(Unadjusted.EV) = c('eigenvalue', 'type', 'num')
-
-apatheme=theme_bw()+
-  theme(panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank(),
-        panel.background = element_blank(),
-        panel.border = element_blank(),
-        text=element_text(family = "Helvetica",),
-        legend.title=element_blank(),
-        axis.line.x = element_line(color='black'),
-        axis.line.y = element_line(color='black'))
 
@@
 
-```{r Hull, include=FALSE}
+```{r HullEFA, include=FALSE}
 # HULL
@@
 hull <- ggplot2::last_plot()
-Hull <- hull+ ggtitle(NULL) +xlab("Factor Number")+ylab("CAF")+ theme(panel.grid.major = element_blank(),
-                                               panel.grid.minor = element_blank(),
-                                               panel.background = element_blank(),
-                                               axis.line.x = element_line(color='black'),
-                                               axis.line.y = element_line(color='black'))
-
-```
-
-```{r MAP, include=FALSE}
+Hull <- hull+ ggtitle(NULL) +xlab("Factor Number")+ylab("CAF")+ 
+  apatheme +scale_color_manual(labels = c("Out side the convex Hull", "On the convex Hull"), values = c("red", "cyan2")) 
+```
+
+```{r MAPefa, include=FALSE}
 #MAP
@@
 
-```{r facIdFig, out.height="100%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}
-cowplot::plot_grid(parallel, scree.plot,Hull, labels = c('(A)', '(B)', '(C)'),ncol=1, label_size = 8)
+```{r facIdFig, out.height="120%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}
+cowplot::plot_grid(parallel, scree.plot,Hull, labels = "AUTO",ncol=1, label_size = 8,align = "v")
 
@@
 
-```{r TabEFA5, results='asis'}
-
-apa_table(factor.des,align = "c", caption = "Factor loadings and communality of the retained items", note = "Only loading higher than .30 is reported", font_size = "tiny")
-```
-
-```{r Residuals, out.height= "50%",  fig.align='center', fig.cap= ' Histogram of residulas:  five-factor solution',  out.width="50%",  warning=FALSE, results='asis'}
+```{r EFATable, results='asis'}
+
+apa_table(factor.des,align = "c", caption = "Factor loadings and communality of the retained items", note = "Only loading higher than .30 is reported", font_size = "small")
+```
+
+```{r EFAResiduals, out.height= "50%",  fig.align='center', fig.cap= ' Histogram of residulas:  five-factor solution',  out.width="50%",  warning=FALSE, results='asis'}
 hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))

### 2021-10-17 manuscript.Rmd
looping

@@
 install.packages("cowplot")
+install.packages("VIM")
 devtools::install_github('rich-iannone/DiagrammeR')
@@
 library(likert)
+library(VIM) #Missing data
 library(kutils)
@@
 +=================================================+=========+========================================================================================+:==============:+=============+
-| Visual Light Sensitivity Questionnaire-8        | a       | Eight-question survey to assess the presence and severity of photosensitivity symptoms | all            | jhghjgjhgfd |
+| Visual Light Sensitivity Questionnaire-8        |         | Eight-question survey to assess the presence and severity of photosensitivity symptoms | all            | jhghjgjhgfd |
 +-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
@@
 EFA.data <- sem.data[1:428, ]
+#library(VIM)
+missing <- aggr(EFA.data, plot =T)
+
 ```
@@
 
-n1 <- shapiro.test(EFA.data$item1)
-n2 <- shapiro.test(EFA.data$item2)
-n3 <- shapiro.test(EFA.data$item3)
-n4 <- shapiro.test(EFA.data$item4)
-n5 <- shapiro.test(EFA.data$item5)
-n6 <- shapiro.test(EFA.data$item6)
-n7 <- shapiro.test(EFA.data$item7)
-n8 <- shapiro.test(EFA.data$item8)
-n9 <- shapiro.test(EFA.data$item9)
-n10 <- shapiro.test(EFA.data$item10)
-n11 <- shapiro.test(EFA.data$item11)
-n12 <- shapiro.test(EFA.data$item12)
-n13 <- shapiro.test(EFA.data$item13)
-n14 <- shapiro.test(EFA.data$item14)
-n15 <- shapiro.test(EFA.data$item15)
-n16 <- shapiro.test(EFA.data$item16)
-n17 <- shapiro.test(EFA.data$item17)
-n18 <- shapiro.test(EFA.data$item18)
-n19 <- shapiro.test(EFA.data$item19)
-n20 <- shapiro.test(EFA.data$item20)
-n21 <- shapiro.test(EFA.data$item21)
-n22 <- shapiro.test(EFA.data$item22)
-n23 <- shapiro.test(EFA.data$item23)
-n24 <- shapiro.test(EFA.data$item24)
-n25 <- shapiro.test(EFA.data$item25)
-n26 <- shapiro.test(EFA.data$item26)
-n27 <- shapiro.test(EFA.data$item27)
-n28 <- shapiro.test(EFA.data$item28)
-n29 <- shapiro.test(EFA.data$item29)
-n30 <- shapiro.test(EFA.data$item30)
-n31 <- shapiro.test(EFA.data$item31)
-n32 <- shapiro.test(EFA.data$item32)
-n33 <- shapiro.test(EFA.data$item33)
-n34 <- shapiro.test(EFA.data$item34)
-n35 <- shapiro.test(EFA.data$item35)
-n36 <- shapiro.test(EFA.data$item36)
-n37 <- shapiro.test(EFA.data$item37)
-n38 <- shapiro.test(EFA.data$item38)
-n39 <- shapiro.test(EFA.data$item39)
-n40 <- shapiro.test(EFA.data$item40)
-n41 <- shapiro.test(EFA.data$item41)
-n42 <- shapiro.test(EFA.data$item42)
-n43 <- shapiro.test(EFA.data$item43)
-n44 <- shapiro.test(EFA.data$item44)
-n45 <- shapiro.test(EFA.data$item45)
-n46 <- shapiro.test(EFA.data$item46)
-n47 <- shapiro.test(EFA.data$item47)
-n48 <- shapiro.test(EFA.data$item48)
-
-normality.tab = matrix(, nrow = 48, ncol = 2)
-as.table(normality.tab)
+#creating normality function
+shapiro_test_df <- function(df, bonf= TRUE, alpha= 0.05) {
+  l <- lapply(df, shapiro.test)
+  s <- do.call("c", lapply(l, "[[", 1))
+  p <- do.call("c", lapply(l, "[[", 2))
+  if (bonf == TRUE) {
+    sig <- ifelse(p > alpha / length(l), "H0", "*")
+  } else {
+    sig <- ifelse(p > alpha, "H0", "*")
+  }
+  return(list(statistic= s,
+              p.value= p,
+              significance= sig,
+              method= ifelse(bonf == TRUE, "Shapiro-Wilks test with Bonferroni Correction",
+                             "Shapiro-Wilks test without Bonferroni Correction")))
+}
+
+Shapiro.efa <- shapiro_test_df(EFA.data)
+
+efa.normality.tab = matrix(nrow = 48, ncol = 2)
 rownameprefix <- "Item"
@@
 my.item.names <- paste(rownameprefix,rownamesufix, sep = "" )
-rownames(normality.tab) <- my.item.names
-colnames(normality.tab) <- c("statistic", "p")
-
-normality.tab[,1] <- c(apa((n1$statistic),2,T),
-                       apa((n1$statistic),2,T),
-                       apa((n3$statistic),2,T),
-                       apa((n4$statistic),2,T),
-                       apa((n5$statistic),2,T),
-                       apa((n6$statistic),2,T),
-                       apa((n7$statistic),2,T),
-                       apa((n8$statistic),2,T),
-                       apa((n9$statistic),2,T),
-                       apa((n10$statistic),2,T),
-                       apa((n11$statistic),2,T),
-                       apa((n12$statistic),2,T),
-                       apa((n13$statistic),2,T),
-                       apa((n14$statistic),2,T),
-                       apa((n14$statistic),2,T),
-                       apa((n16$statistic),2,T),
-                       apa((n17$statistic),2,T),
-                       apa((n18$statistic),2,T),
-                       apa((n19$statistic),2,T),
-                       apa((n20$statistic),2,T),
-                       apa((n21$statistic),2,T),
-                       apa((n22$statistic),2,T),
-                       apa((n23$statistic),2,T),
-                       apa((n24$statistic),2,T),
-                       apa((n25$statistic),2,T),
-                       apa((n26$statistic),2,T),
-                       apa((n27$statistic),2,T),
-                       apa((n28$statistic),2,T),
-                       apa((n29$statistic),2,T),
-                       apa((n30$statistic),2,T),
-                       apa((n31$statistic),2,T),
-                       apa((n32$statistic),2,T),
-                       apa((n33$statistic),2,T),
-                       apa((n34$statistic),2,T),
-                       apa((n35$statistic),2,T),
-                       apa((n36$statistic),2,T),
-                       apa((n37$statistic),2,T),
-                       apa((n38$statistic),2,T),
-                       apa((n39$statistic),2,T),
-                       apa((n40$statistic),2,T),
-                       apa((n41$statistic),2,T),
-                       apa((n42$statistic),2,T),
-                       apa((n43$statistic),2,T),
-                       apa((n44$statistic),2,T),
-                       apa((n45$statistic),2,T),
-                       apa((n46$statistic),2,T),
-                       apa((n47$statistic),2,T),
-                       apa((n48$statistic),2,T))
-
-normality.tab[,2] <- c(apa((n1$p.value),2,T),
-                       apa((n1$p.value),2,T),
-                       apa((n3$p.value),2,T),
-                       apa((n4$p.value),2,T),
-                       apa((n5$p.value),2,T),
-                       apa((n6$p.value),2,T),
-                       apa((n7$p.value),2,T),
-                       apa((n8$p.value),2,T),
-                       apa((n9$p.value),2,T),
-                       apa((n10$p.value),2,T),
-                       apa((n11$p.value),2,T),
-                       apa((n12$p.value),2,T),
-                       apa((n13$p.value),2,T),
-                       apa((n14$p.value),2,T),
-                       apa((n14$p.value),2,T),
-                       apa((n16$p.value),2,T),
-                       apa((n17$p.value),2,T),
-                       apa((n18$p.value),2,T),
-                       apa((n19$p.value),2,T),
-                       apa((n20$p.value),2,T),
-                       apa((n21$p.value),2,T),
-                       apa((n22$p.value),2,T),
-                       apa((n23$p.value),2,T),
-                       apa((n24$p.value),2,T),
-                       apa((n25$p.value),2,T),
-                       apa((n26$p.value),2,T),
-                       apa((n27$p.value),2,T),
-                       apa((n28$p.value),2,T),
-                       apa((n29$p.value),2,T),
-                       apa((n30$p.value),2,T),
-                       apa((n31$p.value),2,T),
-                       apa((n32$p.value),2,T),
-                       apa((n33$p.value),2,T),
-                       apa((n34$p.value),2,T),
-                       apa((n35$p.value),2,T),
-                       apa((n36$p.value),2,T),
-                       apa((n37$p.value),2,T),
-                       apa((n38$p.value),2,T),
-                       apa((n39$p.value),2,T),
-                       apa((n40$p.value),2,T),
-                       apa((n41$p.value),2,T),
-                       apa((n42$p.value),2,T),
-                       apa((n43$p.value),2,T),
-                       apa((n44$p.value),2,T),
-                       apa((n45$p.value),2,T),
-                       apa((n46$p.value),2,T),
-                       apa((n47$p.value),2,T),
-                       apa((n48$p.value),2,T))
-
-normalityprefix <- normality.tab[,1]
-normalitysufix <- "*"
-normality.names <- paste(normalityprefix,normalitysufix, sep = "" )
+rownames(efa.normality.tab) <- my.item.names
+colnames(efa.normality.tab) <- c("statistic", "p")
+
+efa.normality.tab[,1] <- apa(Shapiro.efa$statistic,2,T)
+efa.normality.tab[,2] <- apa(Shapiro.efa$p.value,2,T)
+
+efa.normalityprefix <- efa.normality.tab[,1]
+efa.normalitysufix <- Shapiro.efa$significance
+efa.normality.stat <- paste(efa.normalityprefix,efa.normalitysufix, sep = "" )
 
@@
 
-Des.combined <- cbind(apa(Descriptives$mean,2,T), apa(Descriptives$sd,2,T), apa(Descriptives$skew,2,T),apa(Descriptives$kurtosis,2,T), normality.names,  apa(Item.total$r.cor,2,F))
+Des.combined <- cbind(apa(Descriptives$mean,2,T), apa(Descriptives$sd,2,T), apa(Descriptives$skew,2,T),apa(Descriptives$kurtosis,2,T), efa.normality.stat,  apa(Item.total$r.cor,2,F))
 
 colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics","Item-Total Correlation")
-
 rownameprefix <- "Item"
@@
 
-```{r facIdFig, out.height="120%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}
+```{r facIdFig, out.height="200%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}
 cowplot::plot_grid(parallel, scree.plot,Hull, labels = "AUTO",ncol=1, label_size = 8,align = "v")
@@
 
-F1_info <- plot(F1_fit, type = "infoSE", main = "F1")
-
-F2_info.redu <- plot(F2_fit.redu, type = "infoSE", main = "F2")
-
-F3_info.redu <- plot(F3_fit.redu, type = "infoSE", main = "F3")
-
-F4_info.redu <- plot(F4_fit.redu, type = "infoSE", main = "F4")
-
-F5_info <- plot(F5_fit, type = "infoSE", main = "F5")
-
-Test_Info <- plot_grid(F1_info, F2_info.redu,F3_info.redu,F4_info.redu,F5_info, 
-          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)
+F1_item.info <- plot(F1_fit, type = "infotrace", main = "F1")
+
+F2_item.info.redu <- plot(F2_fit.redu, type = "infotrace", main = "F2")
+
+F3_item.info.redu <- plot(F3_fit.redu, type = "infotrace", main = "F3")
+
+F4_item.info.redu <- plot(F4_fit.redu, type = "infotrace", main = "F4")
+
+F5_item.info <- plot(F5_fit, type = "infotrace", main = "F5")
 
@@
 ```{r itminfo, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
-plot_grid(F1_info, F2_info.redu,F3_info.redu,F4_info.redu,F5_info, 
-          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)
+plot_grid(F1_item.info, F2_item.info.redu,F3_item.info.redu,F4_item.info.redu,F5_item.info, 
+          labels = "AUTO", label_size = 10)
 

### 2021-10-17 manuscript.Rmd
draft table of related scales

@@
 
-+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
++-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
 | Name                                            | Authors                     | Description                                                                            | Relevant Items | Adaptations |
-+=================================================+=========+========================================================================================+:==============:+=============+
-| Visual Light Sensitivity Questionnaire-8        |         | Eight-question survey to assess the presence and severity of photosensitivity symptoms | all            | jhghjgjhgfd |
-+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Office Light Survey                             | b       | Multi-item questionnaire to assess electrical lighting environment in office           | aa             | gh          |
-+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Harvard Light Exposure Assessment Questionnaire | c       | Self-administered semiquantitative light qestionnaire                                  | aa             | as          |
-+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Hospital Lighting Survey                        | d       | 23 items questionnaire to assess light environment in a hospital                       | dd             | fg          |
-+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Morningness-Eveningness Questionnaire           | e       | 19 items questionnaire to understand your body clock                                   | ff             | hj          |
-+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Munich Chronotype Questionnaire (MCTQ)          | f       | 17 items questionnaire to understand individuals phase of entrainment                  | ff             | jk          |
-+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Assessment of Sleep Environment                 | g       | 13 items questionnaire measuring your sleep environment quality                        | ff             | kl          |
-+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
-| The Pittsburgh Sleep Quality Index (PSQI)       | h       | 9 items inventory to measure sleep quality and sleeping pattern                        | ff             | klfrgfgvfg  |
-+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
++=================================================+=============================+========================================================================================+:==============:+=============+
+| Visual Light Sensitivity Questionnaire-8        | [\@verriotto2017new]        | Eight-question survey to assess the presence and severity of photosensitivity symptoms | all            | jhghjgjhgfd |
++-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
+| Office Light Survey                             | [\@eklund1996development]   | Multi-item questionnaire to assess electrical lighting environment in office           | aa             | gh          |
++-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
+| Harvard Light Exposure Assessment Questionnaire | [\@bajaj2011validation]     | Self-administered semiquantitative light qestionnaire                                  | aa             | as          |
++-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
+| Hospital Lighting Survey                        | [\@dianat2013objective]     | 23 items questionnaire to assess light environment in a hospital                       | dd             | fg          |
++-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
+| Morningness-Eveningness Questionnaire           | [\@horne1976self]           | 19 items questionnaire to understand your body clock                                   | ff             | hj          |
++-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
+| Munich Chronotype Questionnaire (MCTQ)          | [\@roenneberg2003life]      | 17 items questionnaire to understand individuals phase of entrainment                  | ff             | jk          |
++-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
+| Assessment of Sleep Environment                 | [\@grandner2014development] | 13 items questionnaire measuring your sleep environment quality                        | ff             | kl          |
++-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
+| The Pittsburgh Sleep Quality Index (PSQI)       | [\@buysse1989pittsburgh]    | 9 items inventory to measure sleep quality and sleeping pattern                        | ff             | klfrgfgvfg  |
++-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
 |                                                 |                             |                                                                                        |                |             |
-+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
++-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
 |                                                 |                             |                                                                                        |                |             |
-+-------------------------------------------------+---------+----------------------------------------------------------------------------------------+----------------+-------------+
++-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
 

### 2021-10-17 manuscript.Rmd
updates
Bye Bye Hard Coding!

@@
 
-Timeline of data collection, ethical approval mode of data collection how consent was recorded.
+Timeline of data collection, mode of data collection.
 
@@
 #Preparing the EFA table
-factor.des = matrix(, nrow = 27, ncol = 6)
-as.table(factor.des)
-rownames(factor.des) <- c("item16", "item36",  "item17",   
-                          "item11",  "item10",  "item12", "item7",  "item8",  "item9", 
-                          "item27", "item3",  "item40","item30","item41",
-                          "item33", "item32", "item35","item37", "item38",
-                          "item46", "item45", "item25", "item4", "item1", "item26", "internal Consistency","% of variance")
-
-colnames(factor.des) <- c("F1", "F2", "F3", "F4", "F5", "Communality")
-
-factor.des[,1] <- c(.99, .94, .80, "-","-","-","-","-","-","-","-","-","-","-","-",
-                    "-","-","-","-","-","-","-","-","-","-",apa(Five.F1.alpha$total[,1],2,F), apa(var1,2,F))
-
-factor.des[,2] <- c("-", "-", "-", .80,.76,.65,.50,-.50,.32,"-","-","-","-","-","-",
-                    "-","-","-","-","-","-","-","-","-","-",apa(Five.F2.alpha$total[,1],2,F), apa(var2,2,F))
-
-factor.des[,3] <- c("-", "-", "-", "-","-","-","-","-","-",.80,.80,.65,.45,-.36,"-",
-                    "-","-","-","-","-","-","-","-","-","-", apa(Five.F3.alpha$total[,1],2,F),apa(var3,2,F))
-
-factor.des[,4] <- c("-", "-", "-", "-","-","-","-","-","-","-","-","-","-","-",.74,
-                    .73,.66,-.39,.36,"-","-","-","-","-","-",apa(Five.F4.alpha$total[,1],2,F), apa(var4,2,F))
-
-factor.des[,5] <- c("-", "-", "-", "-","-","-","-","-","-","-","-","-","-","-","-","-","-","-","-",
-                    .60,.59,.41,.41,.40,.39,apa(Five.F5.alpha$total[,1],2,F), apa(var5,2,F))
-
-factor.des[,6] <- c (.99, .90,.66,.64, .59, .47, .27, .25, .11, .66, .68, .46, .35, .33, .56, .62, .45, .17, .18, .42, .37, .19, .22, .17, .17, "-", "-")
+fa_table <- function(x, cut) {
+  #get sorted loadings
+  loadings <- fa.sort(x)$loadings %>% round(2)
+  #supress loadings
+  loadings[abs(loadings) < abs(cut)] <- ""
+  #get additional info
+  add_info <- cbind(x$communality, 
+                    x$uniquenesses,
+                    x$complexity) %>%
+    # make it a data frame
+    as.data.frame() %>%
+    # column names
+    rename("Communality" = V1,
+           "Uniqueness" = V2,
+           "Complexity" = V3) %>%
+    #get the item names from the vector
+    rownames_to_column("item")
+  #build table
+  loadings %>%
+    unclass() %>%
+    as.data.frame() %>%
+    rownames_to_column("item") %>%
+    left_join(add_info) %>%
+    mutate(across(where(is.numeric), round, 3))
+}
+efa.tab <- fa_table(fa.5F.3,.3)
+
+variance <- fa.5F.3$Vaccounted %>% 
+  as.data.frame()%>% 
+  round(2)
+library(data.table)
+efa.table <- rbind(setDT(efa.tab), setDT(variance[2,]), fill=TRUE)
+efa.table[26,1] <- "% of variance"
 
@@
 
-apa_table(factor.des,align = "c", caption = "Factor loadings and communality of the retained items", note = "Only loading higher than .30 is reported", font_size = "small")
+apa_table(efa.table,align = "c", caption = "Factor loadings and communality of the retained items", note = "Only loading higher than .30 is reported", font_size = "small")
 ```

### 2021-10-17 manuscript.Rmd
Updates

@@
 
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
 | Name                                            | Authors                     | Description                                                                            | Relevant Items | Adaptations |
-+=================================================+=============================+========================================================================================+:==============:+=============+
+|-------------------------------------------------|-----------------------------|----------------------------------------------------------------------------------------|:--------------:|-------------|
 | Visual Light Sensitivity Questionnaire-8        | [\@verriotto2017new]        | Eight-question survey to assess the presence and severity of photosensitivity symptoms |      all       | jhghjgjhgfd |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
 | Office Light Survey                             | [\@eklund1996development]   | Multi-item questionnaire to assess electrical lighting environment in office           |       aa       | gh          |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
 | Harvard Light Exposure Assessment Questionnaire | [\@bajaj2011validation]     | Self-administered semiquantitative light qestionnaire                                  |       aa       | as          |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
 | Hospital Lighting Survey                        | [\@dianat2013objective]     | 23 items questionnaire to assess light environment in a hospital                       |       dd       | fg          |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
 | Morningness-Eveningness Questionnaire           | [\@horne1976self]           | 19 items questionnaire to understand your body clock                                   |       ff       | hj          |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
 | Munich Chronotype Questionnaire (MCTQ)          | [\@roenneberg2003life]      | 17 items questionnaire to understand individuals phase of entrainment                  |       ff       | jk          |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
 | Assessment of Sleep Environment                 | [\@grandner2014development] | 13 items questionnaire measuring your sleep environment quality                        |       ff       | kl          |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
 | The Pittsburgh Sleep Quality Index (PSQI)       | [\@buysse1989pittsburgh]    | 9 items inventory to measure sleep quality and sleeping pattern                        |       ff       | klfrgfgvfg  |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
 |                                                 |                             |                                                                                        |                |             |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
 |                                                 |                             |                                                                                        |                |             |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
 
@@
 # Results
+
+## Exploratory Factor Analysis
 

### 2021-10-17 manuscript.Rmd
Undated EFA table

--- 2021-10-17 manuscript.Rmd
@@
 #Preparing the EFA table
+library(data.table)
 fa_table <- function(x, cut) {
@@
   #build table
-  loadings %>%
+  loadings <- loadings %>%
     unclass() %>%
@@
     left_join(add_info) %>%
-    mutate(across(where(is.numeric), round, 3))
-}
-efa.tab <- fa_table(fa.5F.3,.3)
-
-variance <- fa.5F.3$Vaccounted %>% 
+    mutate(across(where(is.numeric), round, 3)) %>% 
+    as.data.frame()
+  variance <- x$Vaccounted %>% 
   as.data.frame()%>% 
   round(2)
-library(data.table)
-efa.table <- rbind(setDT(efa.tab), setDT(variance[2,]), fill=TRUE)
-efa.table[26,1] <- "% of variance"
+  loadings <- rbind(setDT(loadings), setDT(variance[2,]), fill=TRUE)
+
+}
+
+efa.table <- fa_table(fa.5F.3,.3) 
+nr <- nrow(efa.table)
+efa.table[nr, 1] <- "% of Variance"
 

### 2021-10-17 manuscript.Rmd
softcoded numbers in "Participants"

--- 2021-10-17 manuscript.Rmd
@@
 -   Occupational Status
--   COVID-related Occupational setting during the past four weeks
+-   COVID-19 related Occupational setting during the past four weeks
 -   Time zone & country of residence
@@
     ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
-modify_header(label ~ "**Variable**") %>% 
-as_kable(format = 'pipe') -> desc_kable #save it as a knitr::kable
-
+modify_header(label ~ "**Variable**") -> desc_table
+
+as_tibble(desc_table) -> desc_tibble 
+as_kable(desc_table, format = 'pipe') -> desc_kable #save it as a knitr::kable
+
+#as_kable_extra(desc_table) -> desc_kable_extra
 ```
@@
 XX participants were excluded from analysis due to not passing at least one of the "attention check" items.
-Anonymous responses from a total of *n* = `r nrow(desctable.data)` participants were included in the analysis of the current study, split into samples for exploratory (EFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "1.
+For exploring initial factor structure (EFA) , a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013].
+For estimating the sample size for the confirmatory factor analysis (CFA) we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per parameter is required to earn trustworthiness of the result.
+Our sample size exceeds these requirements: Anonymous responses from a total of *n* = `r nrow(desctable.data)` participants were included in the analysis of the current study, split into samples for exploratory (EFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "1.
 EFA Sample",])`) and confirmatory factor analysis (CFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "2.
@@
 
-Age among all participants ranged from `r min(desctable.data$slypos_demographics_age)` years to `r max(desctable.data$slypos_demographics_age)` years (EFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
+Age among all participants ranged from `r min(desctable.data$slypos_demographics_age)` years to `r max(desctable.data$slypos_demographics_age)` years [EFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
 EFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
@@
 CFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`), with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 0)` years of age (Overall: *M* = `r mean(desctable.data$slypos_demographics_age)`, *SD* = `r sd(desctable.data$slypos_demographics_age)`; EFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
+CFA Sample"])`], with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 0)` years of age [Overall: *M* = `r mean(desctable.data$slypos_demographics_age)`, *SD* = `r sd(desctable.data$slypos_demographics_age)`; EFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
 EFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
@@
 CFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`).
-In total 47% of participants indicated female sex (EFA: 44%; CFA: 52%), 51% indicated male (EFA: 54%; CFA: 46%) and 2% indicated other sex (EFA: 2.1%, CFA: 1.9%).
-Overall 7.2% (EFA: 7.8%; CFA: 6.2%) participants indicated a gender-variant identity.
-In a "Yes/No" question regarding native language 46% of respondents (EFA: 46%; CFA: 45%) indicated to be native English speakers.
-For their "Occupational Status", more than half (57%) of the overall sample reported that they currently work (EFA: 55%; CFA: 61%), whereas 25% (EFA: 29%; CFA: 20%) reported that they go to school and 17% (EFA: 17%; CFA: 19%) responded that they do neither.
-With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample 44% (EFA: 45%; CFA: 42%) of the participants indicated that they were in a home office/ home schooling setting., while 16% overall (EFA: 16%; CFA: 16%) reported face-to-face work/schooling.
-Lastly, 21% overall (EFA: 22%; CFA: 20%) reported a combination of home- and face-to-face work/schooling, whereas 19% overall (EFA: 17%; CFA: 23%) filled in the "Neither (no work or school, or indication)" response option.
-We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable "Age" and Pearson's Chi-squared test for all other categorical variables via the gtsummary R package's "add_p" function [CITE].
+CFA Sample"])`].
+In total `r desc_tibble[3,2]` of the participants indicated female sex [EFA: `r desc_tibble[3,3]`; CFA: `r desc_tibble[3,4]`], `r desc_tibble[4,2]` indicated male [EFA: `r desc_tibble[4,3]`; CFA: `r desc_tibble[4,4]`] and `r desc_tibble[5,2]` indicated other sex [EFA: `r desc_tibble[5,3]`, CFA: `r desc_tibble[5,4]`].
+Overall, `r desc_tibble[6,2]` [EFA: `r desc_tibble[6,3]`; CFA: `r desc_tibble[6,4]`] participants indicated a gender-variant identity.
+In a "Yes/No" question regarding native language, `r desc_tibble[7,2]` of respondents [EFA: `r desc_tibble[7,3]`; CFA: `r desc_tibble[7,4]`] indicated to be native English speakers.
+For their "Occupational Status", more than half of the overall sample reported that they currently work [Overall: `r desc_tibble[9,2]`; EFA: `r desc_tibble[9,3]`; CFA: `r desc_tibble[9,4]`], whereas `r desc_tibble[10,2]` [EFA: `r desc_tibble[10,3]`; CFA: `r desc_tibble[10,4]`] reported that they go to school and `r desc_tibble[11,2]` [EFA: `r desc_tibble[11,3]`; CFA: `r desc_tibble[11,4]`] responded that they do "Neither".
+With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` [EFA: `r desc_tibble[13,3]`; CFA: `r desc_tibble[13,4]`] of the participants indicated that they were in a home office/ home schooling setting., while `r desc_tibble[14,2]` overall [EFA: `r desc_tibble[14,3]` ; CFA: `r desc_tibble[14,4]`] reported face-to-face work/schooling.
+Lastly, `r desc_tibble[15,2]` overall [EFA: `r desc_tibble[15,3]` ; CFA: `r desc_tibble[15,4]`] reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]` overall [EFA: `r desc_tibble[16,3]`; CFA: `r desc_tibble[16,4]`] filled in the "Neither (no work or school, or indication)" response option.
+We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable "Age" and Pearson's Chi-squared test for all other categorical variables via the gtsummary R package's "add_p" function [@sjoberg2021] .
 The p-values were corrected for multiple testing applying false discovery rate (FDR) via the "add_q" function of the same package.
-After p-value (FDR) correction for multiple testing, none of the demographic variables were significantly different between the EFA sample and the CFA sample (all q-values *q* ≥ .2, indicating equivalence.
+After p-value (FDR) correction for multiple testing, none of the demographic variables were significantly different between the EFA sample and the CFA sample (all q-values *q* ≥ `r min(desc_tibble$"**q-value**", na.rm=T)` , indicating equivalence).
 
@@
 6.  Why such sample was chosen?
-
-EFA: For exploring initial factor structure, a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]
-
-CFA: For estimating the sample size for the confirmatory factor analysis we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006] where 10 participants per parameter is required to earn trustworthiness of the result.
-Our sample size exceeds the requirement.
 
@@
 # Results
-
-## Exploratory Factor Analysis
 
@@
 #Preparing the EFA table
-fa_table <- function(x, cut) {
-  #get sorted loadings
-  loadings <- fa.sort(x)$loadings %>% round(2)
-  #supress loadings
-  loadings[abs(loadings) < abs(cut)] <- ""
-  #get additional info
-  add_info <- cbind(x$communality, 
-                    x$uniquenesses,
-                    x$complexity) %>%
-    # make it a data frame
-    as.data.frame() %>%
-    # column names
-    rename("Communality" = V1,
-           "Uniqueness" = V2,
-           "Complexity" = V3) %>%
-    #get the item names from the vector
-    rownames_to_column("item")
-  #build table
-  loadings %>%
-    unclass() %>%
-    as.data.frame() %>%
-    rownames_to_column("item") %>%
-    left_join(add_info) %>%
-    mutate(across(where(is.numeric), round, 3))
-}
-efa.tab <- fa_table(fa.5F.3,.3)
-
-variance <- fa.5F.3$Vaccounted %>% 
-  as.data.frame()%>% 
-  round(2)
-library(data.table)
-efa.table <- rbind(setDT(efa.tab), setDT(variance[2,]), fill=TRUE)
-efa.table[26,1] <- "% of variance"
+factor.des = matrix(, nrow = 27, ncol = 6)
+as.table(factor.des)
+rownames(factor.des) <- c("item16", "item36",  "item17",   
+                          "item11",  "item10",  "item12", "item7",  "item8",  "item9", 
+                          "item27", "item3",  "item40","item30","item41",
+                          "item33", "item32", "item35","item37", "item38",
+                          "item46", "item45", "item25", "item4", "item1", "item26", "internal Consistency","% of variance")
+
+colnames(factor.des) <- c("F1", "F2", "F3", "F4", "F5", "Communality")
+
+factor.des[,1] <- c(.99, .94, .80, "-","-","-","-","-","-","-","-","-","-","-","-",
+                    "-","-","-","-","-","-","-","-","-","-",apa(Five.F1.alpha$total[,1],2,F), apa(var1,2,F))
+
+factor.des[,2] <- c("-", "-", "-", .80,.76,.65,.50,-.50,.32,"-","-","-","-","-","-",
+                    "-","-","-","-","-","-","-","-","-","-",apa(Five.F2.alpha$total[,1],2,F), apa(var2,2,F))
+
+factor.des[,3] <- c("-", "-", "-", "-","-","-","-","-","-",.80,.80,.65,.45,-.36,"-",
+                    "-","-","-","-","-","-","-","-","-","-", apa(Five.F3.alpha$total[,1],2,F),apa(var3,2,F))
+
+factor.des[,4] <- c("-", "-", "-", "-","-","-","-","-","-","-","-","-","-","-",.74,
+                    .73,.66,-.39,.36,"-","-","-","-","-","-",apa(Five.F4.alpha$total[,1],2,F), apa(var4,2,F))
+
+factor.des[,5] <- c("-", "-", "-", "-","-","-","-","-","-","-","-","-","-","-","-","-","-","-","-",
+                    .60,.59,.41,.41,.40,.39,apa(Five.F5.alpha$total[,1],2,F), apa(var5,2,F))
+
+factor.des[,6] <- c (.99, .90,.66,.64, .59, .47, .27, .25, .11, .66, .68, .46, .35, .33, .56, .62, .45, .17, .18, .42, .37, .19, .22, .17, .17, "-", "-")
 
@@
 
-apa_table(efa.table,align = "c", caption = "Factor loadings and communality of the retained items", note = "Only loading higher than .30 is reported", font_size = "small")
+apa_table(factor.des,align = "c", caption = "Factor loadings and communality of the retained items", note = "Only loading higher than .30 is reported", font_size = "small")
 ```

### 2021-10-17 manuscript.Rmd

@@
 #Preparing the EFA table
-factor.des = matrix(, nrow = 27, ncol = 6)
-as.table(factor.des)
-rownames(factor.des) <- c("item16", "item36",  "item17",   
-                          "item11",  "item10",  "item12", "item7",  "item8",  "item9", 
-                          "item27", "item3",  "item40","item30","item41",
-                          "item33", "item32", "item35","item37", "item38",
-                          "item46", "item45", "item25", "item4", "item1", "item26", "internal Consistency","% of variance")
-
-colnames(factor.des) <- c("F1", "F2", "F3", "F4", "F5", "Communality")
-
-factor.des[,1] <- c(.99, .94, .80, "-","-","-","-","-","-","-","-","-","-","-","-",
-                    "-","-","-","-","-","-","-","-","-","-",apa(Five.F1.alpha$total[,1],2,F), apa(var1,2,F))
-
-factor.des[,2] <- c("-", "-", "-", .80,.76,.65,.50,-.50,.32,"-","-","-","-","-","-",
-                    "-","-","-","-","-","-","-","-","-","-",apa(Five.F2.alpha$total[,1],2,F), apa(var2,2,F))
-
-factor.des[,3] <- c("-", "-", "-", "-","-","-","-","-","-",.80,.80,.65,.45,-.36,"-",
-                    "-","-","-","-","-","-","-","-","-","-", apa(Five.F3.alpha$total[,1],2,F),apa(var3,2,F))
-
-factor.des[,4] <- c("-", "-", "-", "-","-","-","-","-","-","-","-","-","-","-",.74,
-                    .73,.66,-.39,.36,"-","-","-","-","-","-",apa(Five.F4.alpha$total[,1],2,F), apa(var4,2,F))
-
-factor.des[,5] <- c("-", "-", "-", "-","-","-","-","-","-","-","-","-","-","-","-","-","-","-","-",
-                    .60,.59,.41,.41,.40,.39,apa(Five.F5.alpha$total[,1],2,F), apa(var5,2,F))
-
-factor.des[,6] <- c (.99, .90,.66,.64, .59, .47, .27, .25, .11, .66, .68, .46, .35, .33, .56, .62, .45, .17, .18, .42, .37, .19, .22, .17, .17, "-", "-")
+library(data.table)
+fa_table <- function(x, cut) {
+  #get sorted loadings
+  loadings <- fa.sort(x)$loadings %>% round(2)
+  #supress loadings
+  loadings[abs(loadings) < abs(cut)] <- ""
+  #get additional info
+  add_info <- cbind(x$communality, 
+                    x$uniquenesses,
+                    x$complexity) %>%
+    # make it a data frame
+    as.data.frame() %>%
+    # column names
+    rename("Communality" = V1,
+           "Uniqueness" = V2,
+           "Complexity" = V3) %>%
+    #get the item names from the vector
+    rownames_to_column("item")
+  #build table
+  loadings <- loadings %>%
+    unclass() %>%
+    as.data.frame() %>%
+    rownames_to_column("item") %>%
+    left_join(add_info) %>%
+    mutate(across(where(is.numeric), round, 3)) %>% 
+    as.data.frame()
+  variance <- x$Vaccounted %>% 
+  as.data.frame()%>% 
+  round(2)
+  loadings <- rbind(setDT(loadings), setDT(variance[2,]), fill=TRUE)
+
+}
+
+efa.table <- fa_table(fa.5F.3,.3) 
+nr <- nrow(efa.table)
+efa.table[nr, 1] <- "% of Variance"
 

### 2021-10-18 manuscript.Rmd
IRT

--- 2021-10-17 manuscript.Rmd
@@
 +=================================================+=============================+========================================================================================+:==============:+=============+
-| Visual Light Sensitivity Questionnaire-8        | [\@verriotto2017new]        | Eight-question survey to assess the presence and severity of photosensitivity symptoms | all            | jhghjgjhgfd |
+| Visual Light Sensitivity Questionnaire-8        | [@verriotto2017new]        | Eight-question survey to assess the presence and severity of photosensitivity symptoms | all            | jhghjgjhgfd |
 +-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Office Light Survey                             | [\@eklund1996development]   | Multi-item questionnaire to assess electrical lighting environment in office           | aa             | gh          |
+| Office Light Survey                             | [@eklund1996development]   | Multi-item questionnaire to assess electrical lighting environment in office           | aa             | gh          |
 +-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Harvard Light Exposure Assessment Questionnaire | [\@bajaj2011validation]     | Self-administered semiquantitative light qestionnaire                                  | aa             | as          |
+| Harvard Light Exposure Assessment Questionnaire | [@bajaj2011validation]     | Self-administered semiquantitative light qestionnaire                                  | aa             | as          |
 +-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Hospital Lighting Survey                        | [\@dianat2013objective]     | 23 items questionnaire to assess light environment in a hospital                       | dd             | fg          |
+| Hospital Lighting Survey                        | [@dianat2013objective]     | 23 items questionnaire to assess light environment in a hospital                       | dd             | fg          |
 +-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Morningness-Eveningness Questionnaire           | [\@horne1976self]           | 19 items questionnaire to understand your body clock                                   | ff             | hj          |
+| Morningness-Eveningness Questionnaire           | [@horne1976self]           | 19 items questionnaire to understand your body clock                                   | ff             | hj          |
 +-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Munich Chronotype Questionnaire (MCTQ)          | [\@roenneberg2003life]      | 17 items questionnaire to understand individuals phase of entrainment                  | ff             | jk          |
+| Munich Chronotype Questionnaire (MCTQ)          | [@roenneberg2003life]      | 17 items questionnaire to understand individuals phase of entrainment                  | ff             | jk          |
 +-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Assessment of Sleep Environment                 | [\@grandner2014development] | 13 items questionnaire measuring your sleep environment quality                        | ff             | kl          |
+| Assessment of Sleep Environment                 | [@grandner2014development] | 13 items questionnaire measuring your sleep environment quality                        | ff             | kl          |
 +-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| The Pittsburgh Sleep Quality Index (PSQI)       | [\@buysse1989pittsburgh]    | 9 items inventory to measure sleep quality and sleeping pattern                        | ff             | klfrgfgvfg  |
+| The Pittsburgh Sleep Quality Index (PSQI)       | [@buysse1989pittsburgh]    | 9 items inventory to measure sleep quality and sleeping pattern                        | ff             | klfrgfgvfg  |
 +-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
@@
 F1_iteminfo <- plot(F1_fit, type = "infotrace", 
-                    facet_items = T, main = "Blue Filter")
+                    facet_items = T, main = "F1")
 
@@
 F2_info <- plot(F2_fit, type = "infoSE", main = "F2")
-F2_iteminfo <- plot(F2_fit, type = "infotrace", facet_items = T, main = "Natural Light")
+F2_iteminfo <- plot(F2_fit, type = "infotrace", facet_items = T, main = "F2")
 
@@
 F3_iteminfo <- plot(F3_fit, type = "infotrace", 
-                    facet_items = T, main = "Smart Device")
+                    facet_items = T, main = "F3")
 
@@
 F4_info <- plot(F4_fit, type = "infoSE", main = "F4")
-F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = "Sleep Environment")
+F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = "F4")
 
@@
 F5_info <- plot(F5_fit, type = "infoSE", main = "F5")
-F5_iteminfo <- plot(F5_fit, type = "infotrace", facet_items = T,main = "Electric Light")
+F5_iteminfo <- plot(F5_fit, type = "infotrace", facet_items = T,main = "F5")
 
@@
 Test_Info <- plot_grid(F1_info, F2_info,F3_info,F4_info,F5_info, 
-          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)
+          labels = "AUTO", label_size = 10)
 
 Item_Information <- plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
-          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)
+          labels = "AUTO", label_size = 10)
 
@@
 
+```{r itmeinfo, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
+plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
+          labels = "AUTO", label_size = 10,align = "v" )
+
+```
+
 ```{r shortIRT, include=FALSE}
@@
 
-F1_item.info <- plot(F1_fit, type = "infotrace", main = "F1")
-
-F2_item.info.redu <- plot(F2_fit.redu, type = "infotrace", main = "F2")
-
-F3_item.info.redu <- plot(F3_fit.redu, type = "infotrace", main = "F3")
-
-F4_item.info.redu <- plot(F4_fit.redu, type = "infotrace", main = "F4")
-
-F5_item.info <- plot(F5_fit, type = "infotrace", main = "F5")
+F1_test.info <- plot(F1_fit, type = "infoSE", main = "F1")
+
+F2_test.info.redu <- plot(F2_fit.redu, type = "infoSE", main = "F2")
+
+F3_test.info.redu <- plot(F3_fit.redu, type = "infoSE", main = "F3")
+
+F4_test.info.redu <- plot(F4_fit.redu, type = "infoSE", main = "F4")
+
+F5_test.info <- plot(F5_fit, type = "infoSE", main = "F5")
 
@@
 
-```{r itminfo, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
-plot_grid(F1_item.info, F2_item.info.redu,F3_item.info.redu,F4_item.info.redu,F5_item.info, 
-          labels = "AUTO", label_size = 10)
+```{r Testinfo, fig.cap="Test information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
+plot_grid(F1_test.info, F2_test.info.redu,F3_test.info.redu,F4_test.info.redu,F5_test.info, 
+          labels = "AUTO", label_size = 10, align = "v" )
 

### 2021-10-22 instrument.tex
Factor Renamed

@@
 \endhead
-\textbf{F1: Blue-light filters} \\
+\textbf{F1: Blue-light filters/ Wearing Blue-light Filters} \\
 I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day. \\
@@
 I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1 hour before attempting to fall asleep. \\
-\textbf{F2: Natural light exposure} \\
+\textbf{F2: Natural light exposure/ Time Outdoors(in Daylight)/ Time Spend Outside} \\
 I spend 30 minutes or less per day (in total) outside. \\
@@
 I go for a walk or exercise outside within 2 hours after waking up. \\
-\textbf{F3: Use of smartphones and wearables} \\
+\textbf{F3: Use of smartphones and wearables/ Smartwatch and Phone Use in Bed} \\
 I use my mobile phone within 1 hour before attempting to fall asleep. \\
@@
 I look at my smartwatch when I wake up at night. \\
-\textbf{F4: Light in the sleep environment} \\
+\textbf{F4: Light in the sleep environment/Surround Sleep/(Pre)Bedtime Light Use} \\
 I dim my mobile phone screen within 1 hour before attempting to fall asleep. \\
@@
 I dim my computer screen within 1 hour before attempting to fall asleep. \\
-\textbf{F5: Electric home light} \\
+\textbf{F5: Electric home light/Morning and daytime light Use} \\
 I use tunable lights to create a healthy light environment. \\

### 2021-10-22 Appendix A.Rmd
Factor name finalised

--- 2021-10-18 manuscript.Rmd
@@
 ---
-title             : "_Light Exposure Behavior Assessment (LEBA)_: Development of a novel instrument to capture light exposure-related behaviours"
-shorttitle        : "LEBA"
-
-author: 
-  - name          : "Mushfiqul Anwar Siraji"
-    affiliation   : "1, *"
-    email         : "mushfiqul.anwarsiraji@monash.edu"
-    role:         
-      - Formal Analysis
-      - Visualization
-      - Writing – original draft
-
-  - name          : "Rafael Robert Lazar"
-    affiliation   : "2, 3, *"
-    role:
-      - Data curation
-      - Investigation
-      - Project administration
-      - Visualization
-      - Writing – original draft
-      - Writing – review & editing;
-
-  - name          : "Juliëtte	van Duijnhoven"
-    affiliation   : "4"
-    email         : "j.v.duijnhoven1@tue.nl"
-    role:         
-      - Conceptualization
-      - Methodology
-      - Investigation
-      - Writing – review & editing
-
-  - name          : "Luc Schlangen"
-    affiliation   : "5"
-    email         : "l.j.m.schlangen@tue.nl"
-    role:         
-      - Conceptualization
-      - Methodology
-      - Investigation
-      - Writing – review & editing
-
-  - name          : "Shamsul Haque"
-    affiliation   : "1"
-    email         : "shamsul@monash.edu"
-    role:         
-      - Conceptualization
-      - Supervision
-      - Writing – review & editing
-
-  - name          : "Vineetha Kalavally"
-    affiliation   : "6"
-    email         : "vineetha@monash.edu"
-    role:         
-      - Supervision
-      - Writing – review & editing
-
-  - name          : "Céline Vetter"
-    affiliation   : "7, 8"
-    email         : "celine.vetter@colorado.edu"
-    role:         
-      - Conceptualization
-      - Writing – review & editing
-
-  - name          : "Gena Glickman"
-    affiliation   : "9"
-    email         : "gena.glickman@usuhs.edu"
-    role:         
-      - Conceptualization
-      - Methodology
-      - Writing – review & editing
-
-  - name          : "Karin Smolders"
-    affiliation   : "10"
-    email         : "k.c.h.j.smolders@tue.nl"
-    role:         
-      - Conceptualization
-      - Methodology
-      - Writing – review & editing
-
-  - name          : "Manuel Spitschan"
-    corresponding : yes
-    affiliation   : "11, 2, 3"
-    email         : "manuel.spitschan@psy.ox.ac.uk"
-    role:         
-      - Conceptualization
-      - Data curation
-      - Investigation
-      - Project administration
-      - Visualization
-      - Methodology
-      - Writing – original draft
-      - Writing – review & editing
-
-affiliation:
-  - id            : "1"
-    institution   : "Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
-  - id            : "2"
-    institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"
-  - id            : "3"
-    institution   : "University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland"
-  - id            : "4"
-    institution   : "Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands"
-  - id            : "5"
-    institution   : "Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Intelligent Lighting Institute, Eindhoven, Netherlands"
-  - id            : "6"
-    institution   : "Monash University, Department of Electrical and Computer Systems Engineering, Malaysia, Selangor, Malaysia"
-  - id            : "7"
-    institution   : "University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA"
-  - id            : "8"
-    institution   : "Ximes GmbH, Frankfurt, Germany"
-  - id            : "9"
-    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
-  - id            : "10"
-    institution   : "Eindhoven University of Technology, Human-Technology Interaction Group, Eindhoven, Netherlands"
-  - id            : "11"
-    institution   : "University of Oxford, Department of Experimental Psychology, Oxford, UK"
-  - id            : "*"
-    institution   : "Joint first author"
-
-authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
-
-abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
-
-keywords          : "keywords"
-wordcount         : "X"
-
-bibliography      : ["references.bib"]
-
-floatsintext      : no
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
-
-documentclass     : "apa6"
-classoption       : "man"
-output            : 
-  papaja::apa6_pdf:
-    latex_engine: xelatex
-mainfont: Helvetica
+title: "Appendix A"
+author: "Team LEBA"
+date: "10/22/2021"
+output: pdf_document
 ---
@@
 ```
-
-```{r depMan, eval=FALSE, include=FALSE}
-library(packrat)
-#This chunk is disabled. Only run this to install the dependencies automatically.
-packrat::init()
-#Only use when you have added some pack
-#packrat::snapshot(ignore.stale=TRUE)
-
-#To find and install required dependencies.
-packrat::restore()
-```
-
-```{r install, eval=FALSE, include=FALSE}
-#if "packrat" does not work you can run this chunk manually to get all required packs"
-
-install.packages("devtools")
-install.packages("semTools")
-install.packages("MOTE")
-install.packages("psych")
-install.packages("dlookr")
-install.packages("tidyverse")
-install.packages("qgraph")
-install.packages("kableExtra")
-install.packages("paran")
-install.packages("EFA.MRFA")
-install.packages("rsvg")
-install.packages("ggcorrplot")
-install.packages("semTable")
-install.packages("magick")
-install.packages("mirt")
-install.packages("cowplot")
-install.packages("VIM")
-devtools::install_github('rich-iannone/DiagrammeR')
-devtools::install_github("crsh/papaja", force = T)
-install.packages("DiagrammeRsvg")
-devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
-devtools::install_github("crsh/citr")
-remotes::install_github("jthomasmock/gtExtras")
-install.packages("gt")
-remotes::install_github("jthomasmock/gtExtras")
-install.packages("questionr")
-devtools::install_github("lbusett/insert_table")
-```
-
-```{r library, include=FALSE}
-
-library(papaja) # devtools::install_github("crsh/papaja")
-library(lavaan)
-library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
-library(semTools)
-library(MOTE)
-library(car)#revercoding 
-library(psych)
-library(dlookr)
-library(plyr)
-library(tidyverse)
-library(qgraph)
-library(kableExtra)
-library(paran) # Parallel analysis
-library(EFA.MRFA) # Hull method
-library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
-library(DiagrammeRsvg) #For DiagrammeR
-library(rsvg) #For DiagrammeR
-library(ggcorrplot)
-library(semTable)
-library(magick)
-library(mirt)
-library(gtsummary)
-library(gt)
-library(gtExtras)
-library(likert)
-library(VIM) #Missing data
-library(kutils)
-r_refs("references.bib")
-```
-
----
-nocite: |
-  `r cite_r("references.bib")`
----
-
-# Introduction
-
--   Light exposure is important
-
--   Light exposure Behavior is important
-
--   Table: Overview Existing Related Scales: items in total / items on light exposure (behaviour)
-
--   Existing Scales: Review them in text
-
--   None of these do light exposure behavior.
-
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Name                                            | Authors                     | Description                                                                            | Relevant Items | Adaptations |
-+=================================================+=============================+========================================================================================+:==============:+=============+
-| Visual Light Sensitivity Questionnaire-8        | [@verriotto2017new]        | Eight-question survey to assess the presence and severity of photosensitivity symptoms | all            | jhghjgjhgfd |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Office Light Survey                             | [@eklund1996development]   | Multi-item questionnaire to assess electrical lighting environment in office           | aa             | gh          |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Harvard Light Exposure Assessment Questionnaire | [@bajaj2011validation]     | Self-administered semiquantitative light qestionnaire                                  | aa             | as          |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Hospital Lighting Survey                        | [@dianat2013objective]     | 23 items questionnaire to assess light environment in a hospital                       | dd             | fg          |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Morningness-Eveningness Questionnaire           | [@horne1976self]           | 19 items questionnaire to understand your body clock                                   | ff             | hj          |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Munich Chronotype Questionnaire (MCTQ)          | [@roenneberg2003life]      | 17 items questionnaire to understand individuals phase of entrainment                  | ff             | jk          |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Assessment of Sleep Environment                 | [@grandner2014development] | 13 items questionnaire measuring your sleep environment quality                        | ff             | kl          |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| The Pittsburgh Sleep Quality Index (PSQI)       | [@buysse1989pittsburgh]    | 9 items inventory to measure sleep quality and sleeping pattern                        | ff             | klfrgfgvfg  |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-|                                                 |                             |                                                                                        |                |             |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-|                                                 |                             |                                                                                        |                |             |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-
-: Existing related Scales
-
-# Methods
-
-## Ethical approval
-
-The cantonal ethics commission (Ethikkommission Nordwest- und Zentralschweiz, project ID Req-2021-00488) reviewed this project and issued an official clarification of responsibility (full document see Suppl.
-Fig X in appendix) stating: "The research project does not fall under the scope of the Human Research Act, because your project is using only anonymised data.
-An authorisation from the ethics committee is therefore not required and the EKNZ is not responsible for its review."
-
-## Data Availability
-
-## Survey characteristics
-
-Data was collected in a quantitative cross-sectional approach via a fully anonymous online survey hosted on REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel (sciCORE; <https://redcap.scicore.unibas.ch/>).
-Participants were recruited via the website of a Comic co-released with the survey [CITE COMIC HERE; <https://enlightenyourclock.org/participate-in-research/>], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution via f.lux software [CITE f.lux Michael Herf?].
-
-Completing the online survey took approx.
-15 to 20 minutes and was not compensated.
-The first page of the survey comprised a participant information sheet, where participants' informed consent to participate was obtained before any of the questions were displayed.
-Underaged participants (\<18 years) were urged to obtain assent from their parents/legal guardians, before filling in the survey.
-Information on the first page included the objectives of the study, inclusion criteria, estimated duration, the use, storage and sharing of the data, compensation (none), and information about the type of questions in the survey.
-Moreover, participants needed to confirm that they were participating the survey for the first time.
-To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention.
-What is 4+5?").
-The data analysed in this study was collected between 17.05.2021 and 03.09.2021.
-Questions incorporating retrospective recall were all aligned to the period of "past four weeks", matching the presented LEBA instrument.
-
-In addition to the LEBA questionnaire, which is subject of the current study, the following variables and items were assessed but not included in the analysis:
-
--   Sleep disturbance and sleep-related impairment [CITE]
--   Sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration [CITE]
--   Meal timing & caffeine consumption [CITE]
--   Light sensitivity (photophobia vs. photophilia) [CITE]
--   Self-reported pubertal stage (only if younger than 18 years old) [CITE]
-
-Furthermore, the following 1-item demographic variables were assessed:
-
--   Age
--   Sex
--   Gender identity
--   Occupational Status
--   COVID-related Occupational setting during the past four weeks
--   Time zone & country of residence
--   English as native language
-
-## Participants
-
-```{r Data, include=FALSE}
-data <- readRDS("leba_2021-09-08.rds")
-
-# Separating EFA and CFA samples with descriptive column
-descriptives.data <- data
-
-## Merge "0"s and "1"s into "1"s select,subset assign)
-descriptives.data[ , 9:56 ][ descriptives.data[ , 9:56 ] == 0 ] <- 1
-EFA.descriptives <- descriptives.data[1:428,]
-CFA.descriptives <- descriptives.data[429:690, ]
-
-#Separating the EFA and CFA(only items)
-sem.data <- data[, 9:56] #EFA & CFA data
-sem.data[ sem.data == 0] <- 1 #Merged "0"s and "1"s into "1"s
-
-## renaming the column-header
-prefix <- "item"
-sufix <- c(1:48)
-colnam <- paste(prefix,sufix, sep = "" )
-colnames(sem.data) <- colnam
-```
-
-```{r prepareDescTable, include=FALSE}
-
-listdescVars <- colnames(descriptives.data[c(1:3,5:7)])
-
-#seperating naming and  reducing data for descriptive Table 
-desctable.data <- select(descriptives.data, c(listdescVars,
-                          IncludedInCFA))
-
-#renaming TRUE and FALSE from the IncludedInCFA to EFA and CFA for Descriptive Table
-desctable.data$IncludedInCFA[desctable.data$IncludedInCFA == T ] <-
- "2. CFA Sample"
-desctable.data$IncludedInCFA[desctable.data$IncludedInCFA == F ] <- 
- "1. EFA Sample"
-
-# recode the Gender factor so it will only show "Gender Diverse" in the summary table
-desctable.data$slypos_demographics_gender.factor <-
-  recode_factor(desctable.data$slypos_demographics_gender.factor, "No" = "Yes",
-         "Yes"= "No")
-
-# create descriptive table for the demographic vars (excluding tz & Country) with gtsummary
-desctable.data %>%
-  tbl_summary(
-    by = IncludedInCFA,
-    statistic = list(all_continuous() ~ "{mean} ({sd})",
-                     all_categorical() ~ "{n} ({p}%)"),
-    digits = all_continuous() ~ 2,
-    label = list(slypos_demographics_age ~ "Age",
-                 slypos_demographics_sex.factor ~ "Sex",
-                 slypos_demographics_gender.factor ~ "Gender-Variant Identity",
-                 slypos_demographics_language.factor ~ "Native English Speaker",
-                 slypos_demographics_work_or_school.factor ~ "Occupational Status",
-                 slypos_demographics_school.factor ~ "Occupational setting"
-                 ),
-    missing = "no"
-    ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
-modify_header(label ~ "**Variable**") %>% 
-as_kable(format = 'pipe') -> desc_kable #save it as a knitr::kable
-
-```
-
-```{r DescTabPrint, results='asis'}
-
-desc_kable %>% kable_styling(desc_kable, repeat_header_text = "Participants' Demographic Characteristics")
-
-```
-
-Table 1 summarizes the survey participants' demographic characteristics.
-Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses.
-XX participants were excluded from analysis due to not passing at least one of the "attention check" items.
-Anonymous responses from a total of *n* = `r nrow(desctable.data)` participants were included in the analysis of the current study, split into samples for exploratory (EFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "1.
-EFA Sample",])`) and confirmatory factor analysis (CFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "2.
-CFA Sample",])`).
-The EFA sample included participants filling out the questionnaire from 17.05.2021 to XX.XX.XXXX , whereas participants who filled out the questionnaire from YY.YY.YYYY to 03.09.2021 were included in the CFA analysis.
-Participants indicated filling out the online survey from a diverse range of geographic locations.
-The four most common geographic locations included:
-
-`r kable(head(summary(descriptives.data$slypos_demographics_tz.factor), 4), format = "latex")`
-
-For a full list of geographic locations, see Suppl. Table X in the appendix.
-
-Age among all participants ranged from `r min(desctable.data$slypos_demographics_age)` years to `r max(desctable.data$slypos_demographics_age)` years (EFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
-EFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
-EFA Sample"])`; CFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`), with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 0)` years of age (Overall: *M* = `r mean(desctable.data$slypos_demographics_age)`, *SD* = `r sd(desctable.data$slypos_demographics_age)`; EFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
-EFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
-EFA Sample"])`; CFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`).
-In total 47% of participants indicated female sex (EFA: 44%; CFA: 52%), 51% indicated male (EFA: 54%; CFA: 46%) and 2% indicated other sex (EFA: 2.1%, CFA: 1.9%).
-Overall 7.2% (EFA: 7.8%; CFA: 6.2%) participants indicated a gender-variant identity.
-In a "Yes/No" question regarding native language 46% of respondents (EFA: 46%; CFA: 45%) indicated to be native English speakers.
-For their "Occupational Status", more than half (57%) of the overall sample reported that they currently work (EFA: 55%; CFA: 61%), whereas 25% (EFA: 29%; CFA: 20%) reported that they go to school and 17% (EFA: 17%; CFA: 19%) responded that they do neither.
-With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample 44% (EFA: 45%; CFA: 42%) of the participants indicated that they were in a home office/ home schooling setting., while 16% overall (EFA: 16%; CFA: 16%) reported face-to-face work/schooling.
-Lastly, 21% overall (EFA: 22%; CFA: 20%) reported a combination of home- and face-to-face work/schooling, whereas 19% overall (EFA: 17%; CFA: 23%) filled in the "Neither (no work or school, or indication)" response option.
-We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable "Age" and Pearson's Chi-squared test for all other categorical variables via the gtsummary R package's "add_p" function [CITE].
-The p-values were corrected for multiple testing applying false discovery rate (FDR) via the "add_q" function of the same package.
-After p-value (FDR) correction for multiple testing, none of the demographic variables were significantly different between the EFA sample and the CFA sample (all q-values *q* ≥ .2, indicating equivalence.
-
-1.  Describe EFA and CFA sample separately.
-2.  Sampling technique: Convince sampling (non-probability sample)
-3.  Method: cross-sectional survey
-4.  How many missing data?
-5.  How incomplete data were addressed.
-6.  Why such sample was chosen?
-
-EFA: For exploring initial factor structure, a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]
-
-CFA: For estimating the sample size for the confirmatory factor analysis we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006] where 10 participants per parameter is required to earn trustworthiness of the result.
-Our sample size exceeds the requirement.
-
-## Procedure
-
-### Development of the Scale
-
-1.  How the items were generated
-2.  How the literature was reviewed to identify construct adequacy of the items.
-3.  Discuss the expert panel review process to assess content validity
-
-```{r Manuflowchart, include=FALSE }
-Flowchart1 <- grViz("digraph nicegraph{
-
-                    graph [fontname = Helvetica,layout = dot,fontsize = 20, ]
-
-                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 6.5, height = 1, 
-                    fixedsize = true,fontsize = 20]
-
-                    A[label = '48 items were generataed by a robust expert panel'] 
-                    B[label = 'Exploratory Factor Analysis on 48 Items (N = 428)']
-
-                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 7.5, height = 2, 
-                    fixedsize = true, fontsize = 20]
-                    C[label = 
-                    <
-                    Factor Identification<br align = 'left'/>
-                    Scree Plot: 6 Factors<br align = 'left'/>
-                    Parallel Analysis: 6 Factors<br align = 'left'/>
-                    Minimum Average Partial Method: 5 Factors<br align = 'left'/>
-                    Hull Method: 5 Factors<br align = 'left'/>
-                    >
-                    ]
-
-                     subgraph cluster_1 {
-                      graph[fontname = Helvetica, shape = rectangle]
-                      style = rounded
-                     node[fontname = Helvetica, margin = 0.2,width = 9, height = 1, 
-                    fixedsize = true, fontsize = 18 ]
-
-                     1[label = '5 Factor Solution Retained 25 Items']
-                     2[label = 'Reliability Analysis on EFA Sample (N=428)
-                    Alpha F1 =.86; F2 = .71; F3 = .68; F4 =.62; F5 =.52']
-
-                     3[label = 'Confirmatory Factor Analysis 
-                     on the Five Factor Model (25 Items; N=262)
-                      Acceptable Fit ( CFI = .94; TLI .93; RMSEA = .06, SRMR = .11)']
-
-                    4[label = 'Confirmatory Factor Analysis 
-                     on the Five Factor Model (23 Items; N=262)
-                      Acceptable Fit ( CFI = .97; TLI .96; RMSEA = .04, SRMR = .09)']
-                     5[label = 'Reliability Analysis on CFA (23 Items; N=262) 
-                      Alpha F1=.93; F2=.80; F3 =.62; F4=.72; F5=.45']
-                    }
-                subgraph cluster_2 {
-                      graph[fontname = Helvetica,shape = rectangle]
-                      style = rounded
-                     node[fontname = Helvetica, margin = 0.2,width = 8, height = 1, 
-                fixedsize = true, fontsize = 18 ]
-                    6[label = '6-Factor solution: one factor emerged with only two salient loadings']
-                    7[label = 'Rejected']
-                    }
-
-                     edge[fontname = Helvetica,color = black,arrowhead = vee, arrowsize = 1.25]
-                     A ->B
-                     B ->C
-                     C ->1
-                     1 ->2
-                     2 ->3
-                     3 ->4
-                     4 ->5
-                     C ->6
-                     6 ->7
-
-}")
-
-export_svg(Flowchart1) %>%
-  charToRaw() %>%
-  rsvg() %>%
-  png::writePNG("Manuscript.figures/Flowchart1.png")
-
-```
-
-```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development', out.height='100%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/Flowchart1.png')
-```
-
-### Data Collection
-
-Timeline of data collection, mode of data collection.
-
-## Analytic Strategies
-
-We used R (version 4.1.0), including several R packages, for our analyses.
-Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
-Our data violated both the univariate and multivariate normality assumptions.
-Due to these violations and the ordinal nature of our response data, we used a polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA.
-We employed principal axis (pa), a factor extraction method with varimax rotation.
-PA is robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020].
-The obtained latent structure was confirmed by the minimum residuals extraction method as well.
-We used a combination factor identification method including scree plot[@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method[@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
-Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018;
-
-# Results
-
-## Exploratory Factor Analysis
-
-```{r ggplot2, include=F}
-apatheme=theme_bw()+
-  theme(panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank(),
-        panel.background = element_blank(),
-        text=element_text(family = "Helvetica",),
-        legend.title=element_blank(),
-        axis.line.x = element_line(color='black'),
-        axis.line.y = element_line(color='black'),
-        panel.border = element_rect(color = "black",
-                                    fill = NA,
-                                    size = 1))
-```
-
-```{r EFAdata, include=FALSE}
-### EFA data
-EFA.data <- sem.data[1:428, ]
-#library(VIM)
-missing <- aggr(EFA.data, plot =T)
-
-```
-
-```{r EFAassumptions, include=FALSE}
-
-#KMO test
-KMO <- KMO(EFA.data)
-
-# Test of correlation matrix
-bartlet <- cortest.bartlett(EFA.data, n =428)
-
-#Histogram
-#psych::multi.hist(EFA.data[,sapply(EFA.data, is.numeric)])
-
-# Univariate normality
-
-#creating normality function
-shapiro_test_df <- function(df, bonf= TRUE, alpha= 0.05) {
-  l <- lapply(df, shapiro.test)
-  s <- do.call("c", lapply(l, "[[", 1))
-  p <- do.call("c", lapply(l, "[[", 2))
-  if (bonf == TRUE) {
-    sig <- ifelse(p > alpha / length(l), "H0", "*")
-  } else {
-    sig <- ifelse(p > alpha, "H0", "*")
-  }
-  return(list(statistic= s,
-              p.value= p,
-              significance= sig,
-              method= ifelse(bonf == TRUE, "Shapiro-Wilks test with Bonferroni Correction",
-                             "Shapiro-Wilks test without Bonferroni Correction")))
-}
-
-Shapiro.efa <- shapiro_test_df(EFA.data)
-
-efa.normality.tab = matrix(nrow = 48, ncol = 2)
-rownameprefix <- "Item"
-rownamesufix <- seq(1:48)
-my.item.names <- paste(rownameprefix,rownamesufix, sep = "" )
-rownames(efa.normality.tab) <- my.item.names
-colnames(efa.normality.tab) <- c("statistic", "p")
-
-efa.normality.tab[,1] <- apa(Shapiro.efa$statistic,2,T)
-efa.normality.tab[,2] <- apa(Shapiro.efa$p.value,2,T)
-
-efa.normalityprefix <- efa.normality.tab[,1]
-efa.normalitysufix <- Shapiro.efa$significance
-efa.normality.stat <- paste(efa.normalityprefix,efa.normalitysufix, sep = "" )
-
-# Multivariate Normality
-mardia <- mardia(EFA.data, na.rm = T, plot =F)
-
-# Descriptive Stats
-Descriptives <- psych::describe(EFA.data)
-alpha <- psych::alpha(EFA.data)
-Item.total <- alpha$item.stats
-
-Des.combined <- cbind(apa(Descriptives$mean,2,T), apa(Descriptives$sd,2,T), apa(Descriptives$skew,2,T),apa(Descriptives$kurtosis,2,T), efa.normality.stat,  apa(Item.total$r.cor,2,F))
-
-colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics","Item-Total Correlation")
-rownameprefix <- "Item"
-rownamesufix <- seq(1:48)
-my.names <- paste(rownameprefix,rownamesufix, sep = "" )
-rownames(Des.combined) = (my.names)
-```
-
-```{r CorrMatrix, include=FALSE}
-#Polychoric Correlation matrix
-
-correlations <- polychoric(EFA.data, correct = 0)
-upper <- correlations$rho[upper.tri(correlations$rho, diag = F)]
-
-min.cor <- abs(min(upper)) #minimum cor.coefficient of the matrix
-max.cor <- abs(max(upper)) # max. correlation coefficient of the matrix
-
-determinets <- det(correlations$rho) 
-# Calculating the percentage of correlations higher than .30
-
-BigR = sum(correlations$rho >= abs(.30) & correlations$rho < abs(1.0), na.rm =T)/2 
-totR = length(EFA.data)*(length(EFA.data)-1)/2
-cor.per <- print (BigR/totR)*100
-```
-
-```{r ItemAnalysis, include=FALSE}
-# Item analysis
-Item_analysis <- psych::alpha(EFA.data)
-Item_analysis$item.stats$r.cor
-R.cor.sum <- summary(Item_analysis$item.stats$r.cor)
-low.r.corec <- abs(R.cor.sum[1])  #minimum item total correlation
-high.r.corec <- R.cor.sum[6]     # maximum item total correlation
-```
-
-Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy[@kaiserIndexFactorialSimplicity1974] .
-The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cutoff value (.50) indicating a mediocre sample [@hutchesonMultivariateSocialScientist1999].
-Table\@ref(tab:tabDes) summarizes the univariate descriptive statistics for the 48 items.
-some of the items were skewed with high Kurtosis values.
-Our data violated both univariate normality (Shapiro-Wilk statistics; [@shapiroAnalysisVarianceTest1965]) and multivariate normality assumptions (Marida's test;[@mardiaMeasuresMultivariateSkewness1970]).
-Multivariate skew was = `r printnum(mardia$b1p)` (p \<0.001) and multivariate kurtosis was = `r printnum(mardia$b2p)` (p \<0.001).
-Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018].
-Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p \< .001] indicated the correlations between items are adequate for the EFA.
-However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than .30.
-The inter item correlation ranged between `r apa(min.cor,2,F)` to `r apa(max.cor,2,F)`.
-And the corrected item-total correlations ranged between `r apa(low.r.corec,2,F)` to `r apa(high.r.corec,2,F)`.
-
-```{r tabDes,results='asis'}
-apa_table(Des.combined, caption = "Descriptive Statistics", align = "c", note = "*p<.001", longtable =T)
-```
-
-```{r figCor, out.width="100%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}
-
-ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
-           ggtheme = ggplot2::theme_minimal, tl.cex = 6,tl.srt = 90 )
-#p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
-#to show pvalue in the fig add p.mat=p.mat
-```
-
-```{r ParallelEFA, include=FALSE}
-
-# Parallel analysis
-Horn <- paran(correlations$rho, iterations=500, centile=0, quietly=FALSE,
-           status=TRUE, all=FALSE, cfa=FALSE, graph=TRUE,
-           color=TRUE, col=c("black","red","blue"),
-           lty=c(1,2,3), lwd=1, legend=TRUE, 
-           width=640, height=640, grdevice=png, seed=0, mat=NA, n=NA)
-
-Adjusted.EV <- data.frame(Horn$AdjEv)
-Adjusted.EV$type = c('Adjusted Ev')
-Adjusted.EV$num = c(row.names(Adjusted.EV))
-Adjusted.EV$num = as.numeric(Adjusted.EV$num)
-colnames(Adjusted.EV) = c('eigenvalue', 'type', 'num')
-
-Random.EV <- data.frame(Horn$RndEv)
-Random.EV$type = c('Random EV')
-Random.EV$num = c(row.names(Random.EV))
-Random.EV$num = as.numeric(Random.EV$num)
-colnames(Random.EV) = c('eigenvalue', 'type', 'num')
-
-Unadjusted.EV <- data.frame(Horn$Ev)
-Unadjusted.EV$type = c('Unadjusted EV')
-Unadjusted.EV$num = c(row.names(Unadjusted.EV))
-Unadjusted.EV$num = as.numeric(Unadjusted.EV$num)
-colnames(Unadjusted.EV) = c('eigenvalue', 'type', 'num')
-
-parallel = ggplot(Adjusted.EV, aes(x=num, y=eigenvalue, shape=type, color=type)) +
-  #Add lines connecting data points
-  geom_line()+
-    geom_line(data = Random.EV) +
-  geom_line(data = Unadjusted.EV)+
-    #Add the data points.
-  geom_point(size=1)+
-  geom_point(data = Random.EV, size=1)+
-  geom_point(data = Unadjusted.EV, size=1)+
-  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
-   #Label the x-axis 'Factor Number', and ensure that it ranges from 1-max # of factors, increasing by one with each 'tick' mark.
-  scale_x_continuous(name='Factor Number', limits=c(0, 48),breaks=seq(0,48,4))+
-    #Add vertical line indicating parallel analysis suggested max # of factors to retain
-  geom_hline(yintercept=1, linetype = 'dashed') + apatheme
-
-```
-
-```{r ScreePlot, include=FALSE}
-Scree <- scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
-      hline=NULL,add=F)
-
-FA.Scree <- data.frame(Scree$fv)
-FA.Scree$type = c('Factor Analysis')
-FA.Scree$num = c(row.names(FA.Scree))
-FA.Scree$num = as.numeric(FA.Scree$num)
-colnames(FA.Scree) = c('eigenvalue', 'type', 'num')
-
-PA.Scree <- data.frame(Scree$pcv)
-PA.Scree$type = c('Principal Component Analysis')
-PA.Scree$num = c(row.names(PA.Scree))
-PA.Scree$num = as.numeric(PA.Scree$num)
-colnames(PA.Scree) = c('eigenvalue', 'type', 'num')
-
-scree.plot <-ggplot(FA.Scree, aes(x=num, y=eigenvalue,color=type, shape=type))+
-   geom_line()+
-  geom_line(data = PA.Scree)+ 
-  geom_point(size=1)+
-  geom_point(data = PA.Scree, size=1)+
-  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
-  scale_x_continuous(name='Factor Number', limits=c(0, 48),breaks=seq(0,48,4))+
-  geom_hline(yintercept=1, linetype = 'dashed') + apatheme 
-```
-
-```{r HullEFA, include=FALSE}
-# HULL
-hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
-        details = TRUE)
-hull <- ggplot2::last_plot()
-Hull <- hull+ ggtitle(NULL) +xlab("Factor Number")+ylab("CAF")+ 
-  apatheme +scale_color_manual(labels = c("Out side the convex Hull", "On the convex Hull"), values = c("red", "cyan2")) 
-```
-
-```{r MAPefa, include=FALSE}
-#MAP
-psych::VSS(EFA.data, rotate = "varimax", fm = 'minres', n.obs =428 )
-```
-
-Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution.
-Horn's parallel analysis [@hornRationaleTestNumber1965] with 500 iterations also indicated a six-factor solution.
-However, the MAP method [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] suggested a five-factor solution.
-As a result, we tested both five-factor and six-factor solutions.
-
-```{r facIdFig, out.height="200%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}
-cowplot::plot_grid(parallel, scree.plot,Hull, labels = "AUTO",ncol=1, label_size = 8,align = "v")
-
-```
-
-```{r EFA, include=FALSE}
-fa.5F.1 <- fa(r=correlations$rho, nfactors = 5, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-AA <- print(fa.5F.1, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.5F.1 <- dplyr::select(EFA.data ,
-                                    -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14))
-
-correlations.red.5F.1 <- polychoric(reduced.model.5F.1,correct = 0)
-
-fa.5F.2 <- fa(r=correlations.red.5F.1$rho, nfactors = 5, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-BB <- print(fa.5F.2, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.5F.2 <- dplyr::select(EFA.data, -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14, item34, item47, item21, item13))
-
-correlations.red.5F.2 <- polychoric(reduced.model.5F.2,correct = 0)
-
-fa.5F.3 <- fa(r=correlations.red.5F.2$rho, nfactors = 5, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428,max.iter = 500 )
-
-CC <- print(fa.5F.3, cut = .3, digits = 3, sort = TRUE)
-
-var1 <- CC$Vaccounted[2,1]*100
-var2 <- CC$Vaccounted[2,2]*100
-var3 <- CC$Vaccounted[2,3]*100
-var4 <- CC$Vaccounted[2,4]*100
-var5 <- CC$Vaccounted[2,5]*100
-```
-
-```{r EFAplotcode, include=FALSE}
-
-EFAplot <- grViz("
-digraph boxes_and_circles {
-
-graph [layout = dot,rankdir = LR, fontsize = 40]
-
-# node definitions with substituted label text
-node [fontname = Helvetica, shape = circle,  margin = 0.5, width = 3.5, height = .5,
-fixedsize = true, fontsize = 35]
-F5 [label = 'F5']
-F4 [label = 'F4']
-F3 [label = 'F3']
-F2 [label = 'F2']
-F1 [label = 'F1']
-
-node [fontname = Helvetica, shape = box]
-b [label = 'item16']
-c [label = 'item36']
-d [label = 'item17']
-e [label = 'item11']
-f [label = 'item10']
-g [label = 'item12']
-h [label = 'item7']
-i [label = 'item8']
-j [label = 'item9']
-k [label = 'item27']
-l [label = 'item3']
-m [label = 'item40']
-n [label = 'item30']
-o [label = 'item41']
-p [label = 'item33']
-q [label = 'item32']
-r [label = 'item35']
-s [label = 'item37']
-t [label = 'item38']
-u [label = 'item46']
-v [label = 'item45']
-w [label = 'item25']
-x [label = 'item4']
-y [label = 'item1']
-z [label = 'item26']
-
-{rank = same; F1 F2 F3 F4 F5}
-# edge definitions with the node IDs
-edge [fontname = Helvetica, fontsize = 35]
-F5 -> u [label = '0.60']
-F5 -> v [label = '0.59']
-F5 -> w [label = '0.41']
-F5 -> x [label = '0.41']
-F5 -> y [label = '0.40']
-F5 -> z [label = '0.35']
-F4 -> p [label = '0.74']
-F4 -> q [label = '0.73']
-F4 -> r [label = '0.66']
-F4 -> s [label = '-0.39', color =red]
-F4 -> t [label = '0.39']
-F3 -> k [label = '0.80']
-F3 -> l [label = '0.80']
-F3 -> m [label = '0.65']
-F3 -> n [label = '0.49']
-F3 -> o [label = '36']
-F2 -> e [label = '0.79']
-F2 -> f[label = '0.76']
-F2 -> g [label = '0.65']
-F2 -> h[ label = '0.50']
-F2 -> i [label = '-.49',color =red]
-F2 -> j [label = '0.32']
-F1 -> b[label = '0.99']
-F1-> c [label = '0.93']
-F1-> d [label = '0.80']
-}
-")
-
-export_svg(EFAplot) %>%
-  charToRaw() %>%
-  rsvg() %>%
-  png::writePNG("Manuscript.figures/EFAplot.png")
-
-```
-
-```{r EFAplot, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, out.height="50%", out.width="100%", results='asis'}
-knitr::include_graphics('Manuscript.figures/EFAplot.png')
-
-```
-
-```{r Cronbach alpha for 5 fators, message=TRUE, warning=FALSE, include=FALSE}
-
-Five.F1 <- dplyr::select(EFA.data, item16, item36, item17)
-Five.F2 <- dplyr::select(EFA.data, item11, item10, item12, item7, item8, item9) 
-Five.F3 <-  dplyr::select(EFA.data, item27, item3,item40, item30, item41)
-Five.F4 <-  dplyr::select(EFA.data, item33,item32,item35, item37, item38)
-Five.F5 <- dplyr::select(EFA.data, item46, item45, item25, item4, item1, item26)
-
-Five.F1.alpha <- psych::alpha(Five.F1, check.keys = T) 
-Five.F2.alpha <- psych::alpha(Five.F2, check.keys = T)
-Five.F3.alpha <- psych::alpha(Five.F3, check.keys = T)
-Five.F4.alpha <- psych::alpha(Five.F4, check.keys = T) 
-Five.F5.alpha <- psych::alpha(Five.F5, check.keys = T)
-
-F1.alpha <- Five.F1.alpha$total$raw_alpha
-F2.alpha <- Five.F2.alpha$total$raw_alpha
-F3.alpha <- Five.F3.alpha$total$raw_alpha
-F4.alpha <- Five.F4.alpha$total$raw_alpha
-F5.alpha <- Five.F5.alpha$total$raw_alpha
-```
-
-```{r minres 5 factor supplimentary analyisis, eval=FALSE, include=FALSE}
-
-#Supplementary EFA with Minres Extraction
-
-fa.5F.min.1 <- fa(r=correlations$rho, nfactors = 5, fm= "minres",rotate ="varimax",
-                residuals = TRUE, SMC = TRUE, n.obs =428)
-EE <- print(fa.5F.min.1, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.5F.min.1 <- dplyr::select(EFA.data ,
-                                    -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14))
-
-correlations.red.5F.min.1 <- polychoric(reduced.model.5F.min.1,correct = 0)
-
-fa.5F.min.2 <- fa(r=correlations.red.5F.min.1$rho, nfactors = 5, fm= "minres",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-FF <- print(fa.5F.min.2, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.5F.min.2 <- dplyr::select(EFA.data, -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14, item34, item47, item21, item13))
-
-correlations.red.5F.min.2 <- polychoric(reduced.model.5F.min.2, correct = 0)
-
-fa.5F.min.3 <- fa(r=correlations.red.5F.min.2$rho, nfactors = 5, fm= "minres",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-GG <- print(fa.5F.min.3, cut = .3, digits = 3, sort = TRUE)
-```
-
-```{r EFA 6 Factors Promax, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, results='hide'}
-# EFA with 6 factor (rejected)
-
-#correlations <- polychoric(EFA.factor, correct = 0)
-
-fa.6F.1 <- fa(r=correlations$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-II <- print(fa.6F.1, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.6F.1 <- dplyr::select(EFA.data ,
-                                    -c(item34, item44, item48, item43, item39, item22, item2, item20, item21, item24,item30, item14, item28, item6, item15, item23))
-
-correlations.red.6F.1 <- polychoric(reduced.model.6F.1,correct = 0)
-
-fa.6F.2 <- fa(r=correlations.red.6F.1$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-JJ <- print(fa.6F.2, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.6F.2 <- dplyr::select(EFA.data, -c(item34, item44, item48, item43, item39, item22, item2, item20, item21, item24,item30, item14, item28, item6, item15, item23, item18, item42, item47, item41))
-
-correlations.red.6F.2 <- polychoric(reduced.model.6F.2,correct = 0)
-
-fa.6F.3 <- fa(r=correlations.red.6F.2$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)
-
-KK <- print(fa.6F.3, cut = .3, digits = 3, sort = TRUE)
-
-# Residuals
-residual.6F =residuals(fa.6F.3 , diag = FALSE, na.rm =T)
-#Count of numbers of residuals>.05
-BigRRR= sum(residual.6F>abs(.05), na.rm =T)
-print(BigRRR)
-
-#Total number of off diagonal elements in the data matrix
-totRRR = length(reduced.model.6F.2)*(length(reduced.model.6F.2)-1)/2
-
-# Proportion of off-diagonal elements >.10
-sumRRR <- sum(BigRRR/totRRR*100)
-
-hist(residual.6F, main = NULL, xlab = "Six factor Solution: Residuals",ylim=c(0, 400))
-abline(h =65, lwd = 2, lty = 2)
-abline(v =.05,lwd = 2, lty = 2)
-```
-
-```{r factordetails, include=FALSE}
-#Preparing the EFA table
-library(data.table)
-fa_table <- function(x, cut) {
-  #get sorted loadings
-  loadings <- fa.sort(x)$loadings %>% round(2)
-  #supress loadings
-  loadings[abs(loadings) < abs(cut)] <- ""
-  #get additional info
-  add_info <- cbind(x$communality, 
-                    x$uniquenesses,
-                    x$complexity) %>%
-    # make it a data frame
-    as.data.frame() %>%
-    # column names
-    rename("Communality" = V1,
-           "Uniqueness" = V2,
-           "Complexity" = V3) %>%
-    #get the item names from the vector
-    rownames_to_column("item")
-  #build table
-  loadings <- loadings %>%
-    unclass() %>%
-    as.data.frame() %>%
-    rownames_to_column("item") %>%
-    left_join(add_info) %>%
-    mutate(across(where(is.numeric), round, 3)) %>% 
-    as.data.frame()
-  variance <- x$Vaccounted %>% 
-  as.data.frame()%>% 
-  round(2)
-  loadings <- rbind(setDT(loadings), setDT(variance[2,]), fill=TRUE)
-
-}
-
-efa.table <- fa_table(fa.5F.3,.3) 
-nr <- nrow(efa.table)
-efa.table[nr, 1] <- "% of Variance"
-
-#Communality
-Fac.5 <- fa.5F.3
-min.com <- min(Fac.5$communality)
-max.com <- max(Fac.5$communality)
-
-# loading
-min.loadings <- min(Fac.5$loadings)
-max.loadings <- max(Fac.5$loadings)
-
-# Residuals
-residual.5F =residuals(fa.5F.3, diag = FALSE, na.rm =T)
-#Count of numbers of residuals>.05
-BigRR= sum(residual.5F>abs(.05), na.rm =T)
-print(BigRR)
-
-#Total number of off diagonal elements in the data matrix
-totRR = length(reduced.model.5F.2)*(length(reduced.model.5F.2)-1)/2
-
-# Proportion of off-diagonal elements >.10
-sumR <- sum(BigRR/totRR*100)
-
-```
-
-Three rounds of EFA with all 48 items were conducted, and problematic items were gradually discarded (cross-loading items and poor factor loading (\<.30) items).
-Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 [@brownConfirmatoryFactorAnalysis2015], all factor-loading higher than .30 and no cross-loading greater than .30.
-We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (see the supplementary).
-Table\@ref(tab:TabEFA5) displays the factor-loading (structural coefficients) and communality of the items.
-The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients.
-The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`.
-However, the histogram of the absolute values of non-redundant residual-correlations (Fig\@ref(fig:Residuals) showed `r apa(sumR,2, T)`% correlations greater than the absolute value of .05, indicating a possible under-factoring.
-[@desjardinsHandbookEducationalMeasurement2018a].
-Subsequently, we fitted a six-factor solution.
-However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution.
-
-In the five-factor solution, the first factor contained three items and explained `r apa(var1,2,F)`% of the total variance with a satisfactory internal reliability coefficient ($\alpha$ = `r apa(F1.alpha,2,F)`).
-All the items in this factor stemmed from the individual's preference to use blue light filters in different light environments.
-The second factor contained six items and explained `r apa(var2,2,F)`% of the total variance with a satisfactory internal reliability coefficient ($\alpha$ = `r apa(F2.alpha,2,F)`).
-Items under this factor commonly investigate an individual's hours spent outdoor.
-The third factor contained five items and explained `r apa(var3,2,F)`% of the total variance.
-Items under this factor dealt with the specific behaviors pertaining to sleep.
-However, the internal consistency reliability coefficient was not satisfactory ($\alpha$ = `r apa(F3.alpha,2,F)`).
-The fourth factor contained five items and explained `r apa(var4,2,F)`% of the total variance with an internal consistency coefficient, $\alpha$ = `r apa(F4.alpha,2,F)`.
-These five items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time.
-Lastly, the fifth factor contained six items and explained `r apa(var5,2,F)`% of the total variance.
-This factor tried to measure an individual's behavior lead by the awareness of light's influence on health.
-However, this factor showed unsatisfactory internal consistency reliability ($\alpha$ = `r apa(F5.alpha,2,F)`).
-It is essential to attain a balance between psychometric properties and the interpretability of the common themes when exploring the latent structure.
-As all of the emerged factors are highly interpretable, regardless of the apparent low reliability of the two factors, we retain the five-factor solution with 23 items for our confirmatory factor analysis (CFA).
-Two items showed negative factor-loading (items 44 and 21).
-Upon inspection, it was understood that these items are negatively correlated to the common theme, and thus in the CFA analysis, we reversed the response code for these two items.
-
-```{r EFATable, results='asis'}
-
-apa_table(efa.table,align = "c", caption = "Factor loadings and communality of the retained items", note = "Only loading higher than .30 is reported", font_size = "small")
-```
-
-```{r EFAResiduals, out.height= "50%",  fig.align='center', fig.cap= ' Histogram of residulas:  five-factor solution',  out.width="50%",  warning=FALSE, results='asis'}
-hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))
-abline(h =51, lwd = 2, lty = 2)
-abline(v =.05,lwd = 2, lty = 2)
-
-```
-
-```{r gtvis, include =F}
-## Recoding sem.data$item8
-gt.data <- sem.data
-gt.data$item8 <- as.character(gt.data$item8)
-gt.data$item8 <- fct_recode(gt.data$item8,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-
-## Recoding gt.data$item26
-gt.data$item26 <- as.character(gt.data$item26)
-gt.data$item26 <- fct_recode(gt.data$item26,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-## Recoding gt.data$item37
-gt.data$item37 <- as.character(gt.data$item26)
-gt.data$item37 <- fct_recode(gt.data$item26,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-
-names(gt.data)[names(gt.data) == "item1"] <- "item01"
-names(gt.data)[names(gt.data) == "item3"] <- "item03"
-names(gt.data)[names(gt.data) == "item4"] <- "item04"
-names(gt.data)[names(gt.data) == "item7"] <- "item07"
-names(gt.data)[names(gt.data) == "item8"] <- "item08"
-names(gt.data)[names(gt.data) == "item9"] <- "item09"
-
-#EFA data
-gt.efa.data <- gt.data[1:428, ]
-
-gt.efa.data.table <- gt.efa.data %>% 
-  dplyr::select(item16, item36, item17,
-                 item11, item10,item12,item07,item08,item09,
-                 item27,  item03, item40,  item30, item41,
-                 item33, item32,item35, item37,item38, 
-                 item46, item45, item25, item04, item01,item26)
-
-#Creating long data
-gt.efa.long <- as.data.frame(gather(gt.efa.data.table, Items, value))
-gt.efa.long$value <- as.numeric(as.character(gt.efa.long$value))
-
-#Summarizing and creating gt object
-gt.efa.tab <- gt.efa.long %>% 
-  group_by(Items) %>% 
-  # calculate summary stats & create data for the histogram and density plot
-  dplyr::summarise(
-    nr = n(),
-    mean = mean(value, na.rm = TRUE),
-    med = median(value, na.rm = TRUE),
-    sd = sd(value, na.rm = TRUE),
-    hist_data = list(value),
-    dens_data = list(value),
-    .groups = "drop"
-  ) %>% 
-  gt()
-
-#Preparation for likert data
-efa.LEBA.likert <- as.data.frame(gt.efa.data.table)
-
-recod_LEBA <- c( "1" = "Never", "2" = "Rarely", "3"= "Sometimes","4" = "Often",
-                 "5" = "Always")
-efa.LEBA.likert <-  mutate(efa.LEBA.likert, across(starts_with("item"), ~unname(recod_LEBA[.])))
-
-efa.LEBA.Factor = as.data.frame(lapply(efa.LEBA.likert,factor,
-                                   ordered = T))
-#get the items name
-efa.items <- names(efa.LEBA.Factor) 
-#Calculate percentage
-efa.percentage <- kutils::likert(efa.LEBA.Factor, vlist = efa.items )
-
-efa.percentage <- efa.percentage$table %>% 
-  as.data.frame(.)
-
-#data wrangling
-labels <- c("Always", "Never","Often", "Rarely", "Sometimes","Total")
-as.data.frame(labels)
-
-full.efa.percentage <- cbind(labels,efa.percentage) #tables with labels  
-full.efa.percentage<- t(full.efa.percentage ) #transpose
-as.data.frame(full.efa.percentage)
-full.efa.percentage1 <- full.efa.percentage[-1,-6] #removing 1st row and total column
-full.efa.percentage2 <- full.efa.percentage1[, c(2, 4, 5, 3,1)]# rearranging
-as.data.frame(full.efa.percentage2)
-
-colnames(full.efa.percentage2) <- c("Never","Rarely","Sometimes","Often","Always")
-
-efa.Items <- rownames(full.efa.percentage2)
-as.data.frame(efa.Items)
-full.efa.percentage3 <- cbind(efa.Items,full.efa.percentage2)
-
-full.efa.percentage3 <- full.efa.percentage3[order(efa.Items),] 
-full.efa.percentage3 <- as.data.frame(full.efa.percentage3[,-1]) %>% 
-  gt()
-
-gt.efa.table <- gt.efa.tab$'_data'
-gt.liket.efa <- full.efa.percentage3$"_data"
-
-efaTable <-  cbind( gt.efa.table, gt.liket.efa)%>% 
-  gt()
-
-gt.cfa.data <- gt.data[429:690,]
-gt.cfa.data.table <- gt.cfa.data %>% 
-  dplyr::select(item16, item36, item17,
-                 item11, item10,item12,item07,item08,item09,
-                 item27,  item03, item40,  item30, item41,
-                 item32,item35,item38, item33, 
-                 item46, item45, item25, item04, item01 )
-
-gt.cfa.long <- gather(gt.cfa.data.table, Items, value)
-gt.cfa.long$value <- as.numeric(as.character(gt.cfa.long$value))
-gt.cfa.tab <- gt.cfa.long %>% 
-  group_by(Items) %>% 
-# calculate summary stats & create data for the histogram and density plot
-  summarise(
-    nr = n(),
-    mean = mean(value, na.rm = TRUE),
-    med = median(value, na.rm = TRUE),
-    sd = sd(value, na.rm = TRUE),
-    hist_data = list(value),
-    dens_data = list(value),
-    .groups = "drop"
-  ) %>%
-
-  gt()
-
-#Preparation for likert data
-cfa.LEBA.likert <- as.data.frame(gt.cfa.data.table)
-
-recod_LEBA <- c( "1" = "Never", "2" = "Rarely", "3"= "Sometimes","4" = "Often",
-                 "5" = "Always")
-cfa.LEBA.likert <-  mutate(cfa.LEBA.likert, across(starts_with("item"), ~unname(recod_LEBA[.])))
-
-cfa.LEBA.Factor = as.data.frame(lapply(cfa.LEBA.likert,factor,
-                                   ordered = T))
-#get the items name
-cfa.items <- names(cfa.LEBA.Factor) 
-#Calculate percentage
-cfa.percentage <- kutils::likert(cfa.LEBA.Factor, vlist = cfa.items )
-
-cfa.percentage <- cfa.percentage$table %>% 
-  as.data.frame(.)
-
-#data wrangling
-labels <- c("Always", "Never","Often", "Rarely", "Sometimes","Total")
-as.data.frame(labels)
-
-full.cfa.percentage <- cbind(labels,cfa.percentage) #tables with labels  
-full.cfa.percentage <- t(full.cfa.percentage ) #transpose
-as.data.frame(full.cfa.percentage)
-full.cfa.percentage1 <- full.cfa.percentage[-1,-6] #removing 1st row and total column
-full.cfa.percentage2 <- full.cfa.percentage1[, c(2, 4, 5, 3,1)]# rearranging
-as.data.frame(full.cfa.percentage2)
-
-colnames(full.cfa.percentage2) <- c("Never","Rarely","Sometimes","Often","Always")
-
-cfa.Items <- rownames(full.cfa.percentage2)
-as.data.frame(cfa.Items)
-full.cfa.percentage3 <- cbind(cfa.Items,full.cfa.percentage2)
-
-full.cfa.percentage3 <- full.cfa.percentage3[order(cfa.Items),] 
-full.cfa.percentage3 <- as.data.frame(full.cfa.percentage3[,-1]) %>% 
-  gt()
-
-gt.cfa.table <- gt.cfa.tab$'_data'
-gt.liket.cfa <- full.cfa.percentage3$"_data"
-
-cfaTable <-  cbind( gt.cfa.table, gt.liket.cfa) %>% 
-  gt()
-
-efa.gt <- efaTable$"_data"
-cfa.gt <- cfaTable$"_data"
-
-gt.fullTable <-  rbind( efa.gt, cfa.gt) %>% 
-  gt() %>% 
-# histogram and density plots
-  gtExtras::gt_sparkline(
-    hist_data,
-    type = "histogram",
-    line_color = "black", 
-    fill_color = "grey",
-    bw = 1,
-    same_limit = TRUE)%>%
-  gtExtras::gt_sparkline(
-    dens_data,
-    type = "density",
-    line_color = "black", 
-    fill_color = "grey",
-    bw = 0.75,
-    same_limit = TRUE
-  )%>%
-# format decimals
-  fmt_number(columns = mean:sd, decimals = 1) %>%
-# header
-  tab_header(
-    title = md("**LEBA**"),
-    subtitle = md("Summary results of LEBA (N =690)")
-  ) %>% 
-  tab_footnote(
-    footnote = md("**Histogram**"),
-    locations = cells_column_labels(columns = hist_data)
-  ) %>%
-  tab_footnote(
-    footnote = md("**Density**"),
-    locations = cells_column_labels(columns = dens_data)
-  ) %>% 
-#create groups of columns
-tab_spanner(
-  label = "Items",
-  columns = Items
-) %>%
-  tab_spanner(
-    label = "Summary Statistics",
-    columns = nr:sd
-  ) %>%
-  tab_spanner(
-    label = "Graphics",
-    columns = hist_data:dens_data
-  ) %>% 
-  tab_spanner(
-    label = "Response Pattern",
-    columns = Never:Always
-  ) %>%
-# change column names to appear in the table
-cols_label(
-  Items = ("LEBA  Items"),
-  nr = ("n"),
-  mean = ("Mean"),
-  med = ("Median "),
-  sd = (("SD")),
-  hist_data = "Histogram",
-  dens_data = "Density"
-) %>%
-# set alignment as per wish
-  cols_align(
-    align = "center",
-    columns = everything()
-  ) %>%
-  opt_align_table_header(align = "left") %>%
-# add coloured dots and lines on the first column
-  gt_plt_dot(
-    mean,
-    Items,
-    palette = "ggthemes::fivethirtyeight"
-  ) %>% 
-    tab_row_group(
-      group = "CFA (n =262)",
-     rows = 26:48
-
-  ) %>% 
-  tab_row_group(
-  group = "EFA (n = 428)",
-    rows = 1:25  
-  ) %>% gtsave("Manuscript.figures/gt.png")
-
-```
-
-```{r gtPic, echo=FALSE, out.height="100%", out.width="200%", results= 'asis'}
-knitr::include_graphics('Manuscript.figures/gt.png')
-
-```
-
-# Confirmatory Factor Analysis
-
-```{r CFA data frame, include=FALSE}
-
-### CFA Data
-CFA.data <- sem.data[429:690,]
-
-## Recoding CFA.data$item8 into CFA.data$Ritem8
-CFA.data$Ritem8 <- as.character(CFA.data$item8)
-CFA.data$Ritem8 <- fct_recode(CFA.data$Ritem8,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-CFA.data$Ritem8 <- as.numeric(as.character(CFA.data$Ritem8))
-
-## Recoding CFA.data$item37 into CFA.data$item37_rec
-CFA.data$Ritem37 <- as.character(CFA.data$item37)
-CFA.data$Ritem37 <- fct_recode(CFA.data$Ritem37,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-CFA.data$Ritem37 <- as.numeric(as.character(CFA.data$Ritem37))
-
-## Recoding CFA.data$item26 into CFA.data$Ritem26
-CFA.data$Ritem26 <- as.character(CFA.data$item26)
-CFA.data$Ritem26 <- fct_recode(CFA.data$Ritem26,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-
-#Hitogram
-#psych::multi.hist(CFA.data[,sapply(CFA.data, is.numeric)])
-```
-
-```{r CFA 25items, include=FALSE }
-
-LB.model.Cor.1 <- "F1 =~ a1*item16 + item36 + a2*item17
-                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
-                 F3 =~  item27+ item3+ item40 + item30 + item41
-                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
-                 F5 =~ item46+ item45+ item25+ item4+ item1 
-                       a1==a2
-                       a3==a4"
-
-fit.Cor.1 <- cfa(LB.model.Cor.1, data = CFA.data, ordered = names(CFA.data),estimator = "WLSMV")
-
-## Summary of Model 
-cfa.sum.1 <- summary(fit.Cor.1, fit.measures =TRUE,standardized = TRUE,rsq =TRUE)
-
-## Selected Fit measures 
-fit.1 <- fitmeasures (fit.Cor.1,c("gfi", "agfi", "nfi","rfi", 
-                       "cfi.scaled","tli.scaled",
-                       "rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr"))
-
-reliability1 <- semTools::reliability(fit.Cor.1)
-
-```
-
-```{r mod1, include=FALSE}
-modfit.Cor.one <- modindices(fit.Cor.1, sort. = TRUE) 
-modfit.Cor.one[modfit.Cor.one$mi>3.84,]
-```
-
-```{r CFA23withMI, include=FALSE}
-LB.model.Cor.2 <- "F1 =~ a1*item16 + item36 + a2*item17
-                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
-                 F3 =~  item27+ item3+ item40 + item30 + item41
-                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
-                 F5 =~ item46+ item45+ item25+ item4+ item1 
-                       a1==a2
-                       a3==a4
-                item30 ~~  item41
-                       "
-
-#item26 & 37 are removed
-
-## Fit the model 
-fit.Cor.2 <- cfa(LB.model.Cor.2, data = CFA.data, ordered = names(CFA.data),estimator = "WLSMV")
-
-rel.k <- semTools::reliability(fit.Cor.2, return.total = T)
-## Summary of Model 
-cfa.sum.2 <- summary(fit.Cor.2, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
-
-## Selected Fit measures 
-fit.2 <- fitmeasures (fit.Cor.2,c("gfi", "agfi", "nfi","rfi", 
-                       "cfi.scaled","tli.scaled",
-                       "rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr"))
-
-```
-
-```{r mod2, include=FALSE}
-modfit.Cor.one <- modindices(fit.Cor.2, sort. = TRUE) 
-modfit.Cor.one[modfit.Cor.one$mi>3.84,]
-```
-
-We conducted a categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator as our response data was in ordinary nature [@desjardinsHandbookEducationalMeasurement2018a].
-Commonly used Model fit guidelines [@huCutoffCriteriaFit1999; @schumacker2004beginner] focused on (i) the comparative fit index (CFI;) (ii) the Tucker Lewis index (TLI) (CFI/TLI, $goodfit \geq .95$, $acceptable fit\geq .90$) (ii) the root mean square error of approximation (RMSEA; close to .06 or below), (iii) the standardized root mean square (SRMR; close to .08 or below) to estimate the model fit.
-The chi-square test is also used to estimate the absolute model fit.
-Table\@ref(tab:tabCfa) summarizes the fit indices of our fitted model.
-The fitted model failed to attain an absolute fit estimated by the chi-square test.
-However, the chi-square test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit [@brownConfirmatoryFactorAnalysis2015].
-The other absolute fit index we obtained in our analysis was SRMR which does not work well with categorical data [@RN1272].
-Subsequently, we judged the model fit based on the incremental fit indices: CFI, TLI and parsimony fit index-RMSEA.
-Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 and 19-17 .
-However SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`).
-Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR value (SRMR = `r apa(fit.2[10],2,F)`) was also close to the suggestions of @huCutoffCriteriaFit1999.
-The internal consistency reliability coefficients coefficient alpha `r apa(rel.k[5,1],2,F)`, `r apa(rel.k[5,2],2,F)`, `r apa(rel.k[5,3],2,F)`, `r apa(rel.k[5,4],2,F)`, `r apa(rel.k[5,5],2,F)` respectively indicating satisfactory reliability for F1, F2 and F4 [@najeracatalanReliabilityPopulationClassification2019]
-
-```{r cfaMat, results='asis'}
-CFa.matrix <- matrix("NA", nrow =2, ncol = 9)
-colnames(CFa.matrix) = c("Model", "Chi-Squre", "df", "CFI", "TLI", "RMSEA", "RMSEA 90% Lower CI", "RMSEA 90% Upper CI", "SRMR")
-CFa.matrix[1,] = c("Five factor model:25", 
-                   apa(cfa.sum.1$FIT[6],2,T), 
-                   apa(cfa.sum.1$FIT[7],2,T), 
-                   apa(cfa.sum.1$FIT[19],2,F), 
-                   apa(cfa.sum.1$FIT[20],2,T),
-                   apa(cfa.sum.1$FIT[27],2,T),
-                   apa(cfa.sum.1$FIT[28],2,T),
-                   apa(cfa.sum.1$FIT[29],2,T),
-                   apa(cfa.sum.1$FIT[35],2,T))
-
-CFa.matrix[2,] = c("Five factor model:23", 
-                   apa(cfa.sum.2$FIT[6],2,T), 
-                   apa(cfa.sum.2$FIT[7],2,T), 
-                   apa(cfa.sum.2$FIT[19],2,F), 
-                   apa(cfa.sum.2$FIT[20],2,T),
-                   apa(cfa.sum.2$FIT[27],2,T),
-                   apa(cfa.sum.2$FIT[28],2,T),
-                   apa(cfa.sum.2$FIT[29],2,T),
-                   apa(cfa.sum.2$FIT[35],2,T))
-```
-
-```{r tabCfa, results='asis'}
-apa_table(CFa.matrix, caption = "Fit indices of CFA", align = "c", landscape = T, note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index;RMSEA:Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square ")
-```
-
-```{r figcfa, fig.cap = "(A) Five Factor Model of LEBA", , out.width="100%",  warning=FALSE, results='asis'}
-#library(semPlot)
-
-semPaths (fit.Cor.2 , 
-          what= "std",
-          #whatLabels = "std",
-          intercepts = F,
-          #style ="lisrel",
-          #residScale = 6,
-          theme = "colorblind",
-          nCharNodes = 0,
-          reorder =T,
-          rotation =2,
-          layout ="tree",
-          cardinal = T,
-          curvePivot =T,
-          sizeMan =8,
-          sizeMan2 = 1.5,
-          sizeLat = 8,
-          #edge.color = "black",
-          thresholds = FALSE,
-          equalizeManifests =T,
-          fade = FALSE,
-          edge.label.cex = .65,
-          exoCov = FALSE)
-
-```
-
-```{r InvarianceAnalysis_data, include=FALSE}
-invariance.data <- cbind(CFA.data, data$slypos_demographics_language.factor[429:690])
-colnames(invariance.data)[52] <- "English_Speaking"
-
-invariance.data %>% 
-  group_by(English_Speaking) %>% 
-  count()
-```
-
-```{r Invariance detail, include=FALSE}
-# Configural invariance ####
-
-configural <- cfa(model = LB.model.Cor.2,
-                  data = invariance.data,
-                  group = "English_Speaking",
-                  ordered =   names(CFA.data),
-                  estimator = "WLSMV")
-
-summary(configural, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
-
-fitmeasures (configural,c("gfi", "agfi", "nfi","rfi", 
-                       "cfi.scaled","tli.scaled",
-                       "rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr"))
-
-weak <- cfa(model = LB.model.Cor.2,
-                  data = invariance.data,
-                  group = "English_Speaking",
-                  ordered =   names(CFA.data),
-                  estimator = "WLSMV", 
-            group.equal = "loadings")
-
-summary(weak, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
-
-fitmeasures (weak,c("gfi", "agfi", "nfi","rfi", 
-                       "cfi.scaled","tli.scaled",
-                       "rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr"))
-
-First.comp <- compareFit (configural, weak)
-summary(First.comp)
-
-strong <- cfa(model = LB.model.Cor.2,
-                  data = invariance.data,
-                  group = "English_Speaking",
-                  ordered =   names(CFA.data),
-                  estimator = "WLSMV", 
-              group.equal = c("loadings", "intercepts"))
-summary(strong, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
-
-Second.comp <- compareFit  (weak, strong)
-summary(Second.comp)
-
-strict <- cfa(model = LB.model.Cor.2,
-                  data = invariance.data,
-                  group = "English_Speaking",
-                  ordered =   names(CFA.data),
-                  estimator = "WLSMV",  
-              group.equal = c("loadings", "intercepts", "residuals"))
-
-summary(strict, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
-fitmeasures (strict,c("gfi", "agfi", "nfi","rfi", "cfi.robust","tli.robust","rmsea", "srmr","aic"))
-
-Third.comp <- compareFit(strict,strong)
-summary(Third.comp)
-
-structural <-cfa(model = LB.model.Cor.2,
-                  data = invariance.data,
-                  group = "English_Speaking",
-                  ordered =   names(CFA.data),
-                  estimator = "WLSMV",  
-                 group.equal = c("loadings", "intercepts", "residuals", "means","lv.variances","lv.covariances"))
-
-summary(structural, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
-fitmeasures (structural,c("gfi", "agfi", "nfi","rfi", "cfi","tli","rmsea", "srmr","aic"))
-
-fourth.comp <- compareFit  (structural,strict)
-summary(fourth.comp)
-comfit.par <- compareFit(configural, weak, strong, strict, structural)
-summary (comfit.par)
-
-models <-  list("Configural" = configural, 
-                "Metric" = weak, 
-                "Scalar" = strong, 
-                "Residual" = strict, 
-                "Structural"=structural)
-
-Invariance.table <- compareLavaan(models,
-              nesting = "Configural > Metric > Scalar > Residual  > Structural", 
-              fitmeas = c("chisq.scaled", "df",  "cfi.scaled","tli.scaled","rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr" ),
-              scaled = T,
-              chidif = T, digits = 2)
-
-colnames(Invariance.table) <- c("Chi-Square", "df", "CFI", "TLI", "RMSEA", "RMSEA 90% Lower CI", "RMSEA 90% Upper", "SRMR", "Chi-Sqr comparison", "df*", "p")
-
-```
-
-```{r InvarianceTab, results='asis'}
-apa_table(Invariance.table, align = "c",  caption = "Invariance Analysis", note = " a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual;* =  df of model comparison", landscape = T, font_size = "scriptsize" )
-
-```
-
-## Developing the short form of LEBA
-
-```{r IRT data, include=FALSE}
-## Recoding sem.data$item8 into sem.data$Ritem8
-sem.data$Ritem8 <- as.character(sem.data$item8)
-sem.data$Ritem8 <- fct_recode(sem.data$Ritem8,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-sem.data$Ritem8 <- as.numeric(as.character(sem.data$Ritem8))
-# Recoding sem.data$item26 
-sem.data$Ritem26 <- as.character(sem.data$item26)
-sem.data$Ritem26 <- fct_recode(sem.data$Ritem26,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-sem.data$Ritem26 <- as.numeric(as.character(sem.data$Ritem26))
-
-# Recoding sem.data$item37 i
-sem.data$Ritem37 <- as.character(sem.data$item37)
-sem.data$Ritem37 <- fct_recode(sem.data$Ritem37,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-sem.data$Ritem37 <- as.numeric(as.character(sem.data$Ritem37))
-
-F1 <- sem.data %>% 
-  dplyr::select(item16, item36,  item17)
-
-F2 <- sem.data %>% 
-  dplyr::select(item11,  item10 , item12, item7, Ritem8, item9)
-
-F3 <- sem.data %>% 
- dplyr::select(item27, item3,  item40,  item30,  item41)
-
-F4 <- sem.data %>% 
- dplyr::select(item32, item35,  item38,  item33)
-
-F5 <- sem.data %>% 
-  dplyr::select(item46, item45, item25, item4, item1 )
-
-## F1 IRT model####
-F1_fit <- mirt(F1, model = 1, itemtype = 'graded', 
-               SE = TRUE, Se.type = 'MHRM',
-               technical = list(NCYCLES = 10000))
-
-## F2 IRT model####
-F2_fit <- mirt(F2, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-## F3 IRT model####
-F3_fit <- mirt(F3, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-## F4 IRT model####
-F4_fit <- mirt(F4, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-## F5 IRT model####
-F5_fit <- mirt(F5, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-# Model Parameters ####
-## F1 Model Parameters####
-F1_params <- coef(F1_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
-F1_items <- data.frame(F1_params$items)
-F1l_se <- coef(F1_fit, printSE = TRUE)
-
-## F2 Model Parameters####
-F2_params <- coef(F2_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
-F2_items <- data.frame(F2_params$items)
-F2_se <- coef(F2_fit, printSE = TRUE)
-
-## F3 Model Parameters####
-F3_params <- coef(F3_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
-F3_items <- data.frame(F3_params$items)
-F3_se <- coef(F3_fit, printSE = TRUE)
-
-## F4 Model Parameters####
-F4_params <- coef(F4_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
-F4_items <- data.frame(F4_params$items)
-F4_se <- coef(F4_fit, printSE = TRUE)
-
-## F5 Model Parameters####
-F5_params <- coef(F5_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
-F5_items <- data.frame(F5_params$items)
-F5_se <- coef(F5_fit, printSE = TRUE)
-
-itemparameters <- rbind(F1_items,F2_items, F3_items, F4_items,F5_items)
-
-# Person Fit ####
-## F1 Person fit ####
-F1.personfit <- personfit(F1_fit) 
-F1.personfit_model_misfits <- subset(F1.personfit, Zh < -2)
-rownames(F1.personfit_model_misfits)
-nrow(F1.personfit_model_misfits)
-hist(F1.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-
-## F2 Person fit ####
-F2.personfit <- personfit(F2_fit) 
-F2.personfit_model_misfits <- subset(F2.personfit, Zh < -2)
-rownames(F2.personfit_model_misfits)
-nrow(F2.personfit_model_misfits)
-hist(F2.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-
-## F3 Person fit ####
-F3.personfit <- personfit(F3_fit) 
-F3.personfit_model_misfits <- subset(F3.personfit, Zh < -2)
-rownames(F3.personfit_model_misfits)
-nrow(F3.personfit_model_misfits)
-hist(F3.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-
-## F4 Person fit ####
-F4.personfit <- personfit(F4_fit) 
-F4.personfit_model_misfits <- subset(F4.personfit, Zh < -2)
-rownames(F4.personfit_model_misfits)
-nrow(F4.personfit_model_misfits)
-hist(F4.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-
-## F5 Person fit ####
-F5.personfit <- personfit(F5_fit) 
-F5.personfit_model_misfits <- subset(F5.personfit, Zh < -2)
-rownames(F3.personfit_model_misfits)
-nrow(F5.personfit_model_misfits)
-hist(F5.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-
-# Plots ####
-## F1 Plots ####
-F1_OCC <- plot(F1_fit, type = "trace", facet =T, main = "Blue Filter OCC")
-F1_info <- plot(F1_fit, type = "infoSE", main = "F1")
-F1_iteminfo <- plot(F1_fit, type = "infotrace", 
-                    facet_items = T, main = "F1")
-
-## F2 Plots ####
-F2_OCC <- plot(F2_fit, type = "trace", facet =T, main = "Natural Light OCC")
-F2_info <- plot(F2_fit, type = "infoSE", main = "F2")
-F2_iteminfo <- plot(F2_fit, type = "infotrace", facet_items = T, main = "F2")
-
-## F3 Plots ####
-F3_OCC <-plot(F3_fit, type = "trace", facet =T, main = "Smart Device OCC")
-F3_info <- plot(F3_fit, type = "infoSE", main = "F3")
-F3_iteminfo <- plot(F3_fit, type = "infotrace", 
-                    facet_items = T, main = "F3")
-
-## F4 Plots ####
-F4_OCC <-plot(F4_fit, type = "trace", facet =T, main = "Sleep Environment OCC")
-F4_info <- plot(F4_fit, type = "infoSE", main = "F4")
-F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = "F4")
-
-## F5 Plots ####
-F5_OCC <-plot(F5_fit, type = "trace", facet =T, main = "Electric Light OCC")
-F5_info <- plot(F5_fit, type = "infoSE", main = "F5")
-F5_iteminfo <- plot(F5_fit, type = "infotrace", facet_items = T,main = "F5")
-
-## Plot grid ####
-library(cowplot)
-OCC <- plot_grid(F1_OCC, F2_OCC,F3_OCC,F4_OCC,F5_OCC, 
-          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)
-
-Test_Info <- plot_grid(F1_info, F2_info,F3_info,F4_info,F5_info, 
-          labels = "AUTO", label_size = 10)
-
-Item_Information <- plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
-          labels = "AUTO", label_size = 10)
-
-```
-
-To develop a shorter form of the LEBA we sought to Item response theory.IRT complements the conventional classical test theory-based analysis by gathering information on item discrimination and item difficulty[@bakerBasicsItemResponse2017].
-Here, an item's quality is judged based on item information in relation to participants' latent trait level ($\theta$).
-We gathered evidence on item quality by fitting each factor of LEBA with the graded response model to the combined EFA sample and CFA sample (n =690)(\@ref(tab:IRTparameters).
-Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait, and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
-Currently, apart from some general suggestions, there exists no definitive rule to judge the item discrimination and item information parameter quality.
-Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information \<.2) to develop the short form of LEBA.
-@bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70.
-Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), low ( 5 items) indicating a good range of discrimination along the latent trait.
-Examination of the item information curve indicated 6 items (1, 25, 9, 38, 30, & 41) had relatively flat information curves thus discarded.
-
-```{r IRTparameters, results='asis'}
-apa_table(itemparameters, caption = "IRT Item parameters for the LEBA Scale", note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
-```
-
-```{r itmeinfo, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
-plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
-          labels = "AUTO", label_size = 10,align = "v" )
-
-```
-
-```{r shortIRT, include=FALSE}
-F1 <- sem.data %>% 
-  dplyr::select(item16, item36,  item17)
-F2.redu <- sem.data %>% 
-  dplyr::select(item11,  item10 , item12, item7, Ritem8)
-F3.redu <- sem.data %>% 
- dplyr::select(item27, item3,  item40)
-
-F4.redu <- sem.data %>% 
- dplyr::select(item32, item35,  item33)
-
-F5 <- sem.data %>% 
-  dplyr::select(item46, item45, item25 )
-
-F1_fit <- mirt(F1, model = 1, itemtype = 'graded', 
-               SE = TRUE, Se.type = 'MHRM',
-               technical = list(NCYCLES = 10000))
-
-F2_fit.redu <- mirt(F2.redu, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-F3_fit.redu <- mirt(F3.redu, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-F4_fit.redu <- mirt(F4.redu, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-F5_fit <- mirt(F5, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-# Plots2 ####
-
-F1_test.info <- plot(F1_fit, type = "infoSE", main = "F1")
-
-F2_test.info.redu <- plot(F2_fit.redu, type = "infoSE", main = "F2")
-
-F3_test.info.redu <- plot(F3_fit.redu, type = "infoSE", main = "F3")
-
-F4_test.info.redu <- plot(F4_fit.redu, type = "infoSE", main = "F4")
-
-F5_test.info <- plot(F5_fit, type = "infoSE", main = "F5")
-
-```
-
-Test information curve (TIC) indicate the amount of information an the full-scale carry along the latent trait continuum.
-As we treated each factor of LEBA as an unidmensional construct we obtain 5 TICs ().
-These information curves indicated except Blue filter factor, the other factor's curve is roughly centered on the center of the trait continuum (($\theta$)) and the The amount of information changed rather steadily with the change of ($\theta$).
-Thus we conferred the LEBA scale (except blue filter) estimated the light exposure related behavior with precision near the center of trait continuum [@bakerBasicsItemResponse2017] which is sufficient to discriminate between latent trait measured by the each factor.
-The blue filter factor had a peak to the right side of the center of latent trait indicating its ability to providing information only for people who already have some preference towards using blue-filters.
-
-```{r Testinfo, fig.cap="Test information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
-plot_grid(F1_test.info, F2_test.info.redu,F3_test.info.redu,F4_test.info.redu,F5_test.info, 
-          labels = "AUTO", label_size = 10, align = "v" )
-
-```
-
-```{r fscore, include=FALSE}
-LEBA.Total <- sem.data %>% 
-  rowwise() %>% 
-  mutate(F1.Total = sum(item16, item36,  item17))
-
-LEBA.Total <- LEBA.Total %>% 
-  rowwise() %>% 
-  mutate(F2.Total = sum(item11,  item10 , item12, item7, Ritem8))
-
-LEBA.Total <- LEBA.Total %>% 
-  rowwise() %>% 
-  mutate(F3.Total = sum(item27, item3,  item40))
-
-LEBA.Total <- LEBA.Total %>% 
-  rowwise() %>% 
-  mutate(F4.Total = sum(item32, item35,  item33))
-
-LEBA.Total <- LEBA.Total %>% 
-  rowwise() %>% 
-  mutate(F5.Total = sum(item46, item45, item25))
-
-F1.estimation <- as.vector(fscores(F1_fit, method = "EAP",
-                                           full.scores = TRUE, 
-                                           full.scores.SE = F))
-
-F2.estimation <- as.vector(fscores(F2_fit.redu, method = "EAP",
-                                           full.scores = TRUE, 
-                                           full.scores.SE = F))
-
-F3.estimation <- as.vector(fscores(F3_fit.redu, method = "EAP",
-                                           full.scores = TRUE, 
-                                           full.scores.SE = F))
-
-F4.estimation <- as.vector(fscores(F4_fit.redu, method = "EAP",
-                                           full.scores = TRUE, 
-                                           full.scores.SE = F))
-
-F5.estimation <- as.vector(fscores(F5_fit, method = "EAP",
-                                           full.scores = TRUE, 
-                                           full.scores.SE = F))
-
-Ability.F1 <- data.frame(Rawscore = LEBA.Total$F1.Total,
-                      Theta =  F1.estimation)
-
-Ability.F2 <- data.frame(Rawscore = LEBA.Total$F2.Total,
-                      Theta =  F2.estimation)
-
-Ability.F3 <- data.frame(Rawscore = LEBA.Total$F3.Total,
-                      Theta =  F3.estimation)
-
-Ability.F4 <- data.frame(Rawscore = LEBA.Total$F3.Total,
-                      Theta =  F3.estimation)
-
-Ability.F5 <- data.frame(Rawscore = LEBA.Total$F3.Total,
-                      Theta =  F3.estimation)
-
-ggplot(Ability.F1, aes(x =Theta, y =Rawscore)) +
-  geom_point() +
-  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
-  xlim(-2,2) +
-  ylim(0,15)
-
-ggplot(Ability.F2, aes(x =Theta, y =Rawscore)) +
-  geom_point() +
-  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
-  xlim(-2,2) +
-  ylim(0,15)
-
-ggplot(Ability.F3, aes(x =Theta, y =Rawscore)) +
-  geom_point() +
-  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
-  xlim(-2,2) +
-  ylim(0,15)
-
-ggplot(Ability.F4, aes(x =Theta, y =Rawscore)) +
-  geom_point() +
-  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
-  xlim(-2,2) +
-  ylim(0,15)
-
-ggplot(Ability.F5, aes(x =Theta, y =Rawscore)) +
-  geom_point() +
-  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
-  xlim(-2,2) +
-  ylim(0,15)
-
-Score.correation <- cbind(Ability.F1,Ability.F2, Ability.F3, Ability.F4, Ability.F5)
-colnames(Score.correation) <- c("F1.Raw", "F1.Estimated","F2.Raw", "F2.Estimated","F3.Raw", "F3.Estimated","F4.Raw", "F4.Estimated","F5.Raw", "F5.Estimated")
-
-F1.cor <- corr.test(Score.correation$F1.Raw, Score.correation$F1.Estimated)
-
-F2.cor <- corr.test(Score.correation$F2.Raw, Score.correation$F2.Estimated)
-
-F3.cor <- corr.test(Score.correation$F3.Raw, Score.correation$F3.Estimated)
-
-F4.cor <- corr.test(Score.correation$F4.Raw, Score.correation$F4.Estimated)
-
-F5.cor <- corr.test(Score.correation$F5.Raw, Score.correation$F5.Estimated)
-
-#Putting significance star for correlation
-F1.p <-F1.cor$p
-F1.stars <- ifelse(F1.p < .001, "***"
-                   , ifelse(p < .01, "**"
-                            , ifelse(p < .05, "*"
-                                     , ifelse(p < .10, "+", " "))))
-
-F2.p <-F2.cor$p
-F2.stars <- ifelse(F2.p < .001, "**"
-                   , ifelse(p < .01, "**"
-                            , ifelse(p < .05, "*"
-                                     , ifelse(p < .10, "+", " "))))
-
-F3.p <-F3.cor$p
-F3.stars <- ifelse(F3.p < .001, "***"
-                   , ifelse(p < .01, "**"
-                            , ifelse(p < .05, "*"
-                                     , ifelse(p < .10, "+", " "))))
-
-F4.p <-F4.cor$p
-F4.stars <- ifelse(F4.p < .001, "***"
-                   , ifelse(p < .01, "**"
-                            , ifelse(p < .05, "*"
-                                     , ifelse(p < .10, "+", " "))))
-
-F5.p <-F5.cor$p
-F5.stars <- ifelse(F5.p < .001, "***"
-                   , ifelse(p < .01, "**"
-                            , ifelse(p < .05, "*"
-                                     , ifelse(p < .10, "+", " "))))
-
-theta.correlation.matrix <- matrix("NA", nrow =1, ncol = 5)
-
-theta.correlation.matrix[1,1] <- paste(apa(F1.cor$r,2,F), F1.stars,sep="")
-theta.correlation.matrix[1,2] <- paste(apa(F2.cor$r,2,F), F2.stars,sep="")
-theta.correlation.matrix[1,3] <- paste(apa(F3.cor$r,2,F), F3.stars,sep="")
-theta.correlation.matrix[1,4] <- paste(apa(F4.cor$r,2,F), F4.stars,sep="")
-theta.correlation.matrix[1,5] <- paste(apa(F5.cor$r,2,F), F5.stars,sep="")
-
-as.data.frame(theta.correlation.matrix)
-colnames(theta.correlation.matrix) <- c("F1", "F2", "F3", "F4", "F5")
-```
-
-```{r, results='asis'}
-apa_table (theta.correlation.matrix, caption = "correlation coefficents of obtained scores and estimated latent trait for each factots", note = "* p < 0.05; ** p < 0.01; *** p < 0.001"  )
-```
-
-# Discussion
-
-\newpage
-
-# References
-
-```{=tex}
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-```
-::: {#refs custom-style="Bibliography"}
-:::
-
-\endgroup

### 2021-10-22 Appendix A.Rmd
Conflicts

@@
 ```
+
+```{r library, include=FALSE}
+
+library(papaja) # devtools::install_github("crsh/papaja")
+library(lavaan)
+library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
+library(semTools)
+library(MOTE)
+library(car)#revercoding 
+library(psych)
+library(dlookr)
+library(plyr)
+library(tidyverse)
+library(qgraph)
+library(kableExtra)
+library(paran) # Parallel analysis
+library(EFA.MRFA) # Hull method
+library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
+library(DiagrammeRsvg) #For DiagrammeR
+library(rsvg) #For DiagrammeR
+library(ggcorrplot)
+library(semTable)
+library(magick)
+library(mirt)
+library(gtsummary)
+library(gt)
+library(gtExtras)
+library(likert)
+library(VIM) #Missing data
+library(kutils)
+r_refs("references.bib")
+```

### 2021-10-22 Appendix-B.Rmd
Appendices

--- 2021-10-18 manuscript.Rmd
@@
 ---
-title             : "_Light Exposure Behavior Assessment (LEBA)_: Development of a novel instrument to capture light exposure-related behaviours"
-shorttitle        : "LEBA"
-
-author: 
-  - name          : "Mushfiqul Anwar Siraji"
-    affiliation   : "1, *"
-    email         : "mushfiqul.anwarsiraji@monash.edu"
-    role:         
-      - Formal Analysis
-      - Visualization
-      - Writing – original draft
-
-  - name          : "Rafael Robert Lazar"
-    affiliation   : "2, 3, *"
-    role:
-      - Data curation
-      - Investigation
-      - Project administration
-      - Visualization
-      - Writing – original draft
-      - Writing – review & editing;
-
-  - name          : "Juliëtte	van Duijnhoven"
-    affiliation   : "4"
-    email         : "j.v.duijnhoven1@tue.nl"
-    role:         
-      - Conceptualization
-      - Methodology
-      - Investigation
-      - Writing – review & editing
-
-  - name          : "Luc Schlangen"
-    affiliation   : "5"
-    email         : "l.j.m.schlangen@tue.nl"
-    role:         
-      - Conceptualization
-      - Methodology
-      - Investigation
-      - Writing – review & editing
-
-  - name          : "Shamsul Haque"
-    affiliation   : "1"
-    email         : "shamsul@monash.edu"
-    role:         
-      - Conceptualization
-      - Supervision
-      - Writing – review & editing
-
-  - name          : "Vineetha Kalavally"
-    affiliation   : "6"
-    email         : "vineetha@monash.edu"
-    role:         
-      - Supervision
-      - Writing – review & editing
-
-  - name          : "Céline Vetter"
-    affiliation   : "7, 8"
-    email         : "celine.vetter@colorado.edu"
-    role:         
-      - Conceptualization
-      - Writing – review & editing
-
-  - name          : "Gena Glickman"
-    affiliation   : "9"
-    email         : "gena.glickman@usuhs.edu"
-    role:         
-      - Conceptualization
-      - Methodology
-      - Writing – review & editing
-
-  - name          : "Karin Smolders"
-    affiliation   : "10"
-    email         : "k.c.h.j.smolders@tue.nl"
-    role:         
-      - Conceptualization
-      - Methodology
-      - Writing – review & editing
-
-  - name          : "Manuel Spitschan"
-    corresponding : yes
-    affiliation   : "11, 2, 3"
-    email         : "manuel.spitschan@psy.ox.ac.uk"
-    role:         
-      - Conceptualization
-      - Data curation
-      - Investigation
-      - Project administration
-      - Visualization
-      - Methodology
-      - Writing – original draft
-      - Writing – review & editing
-
-affiliation:
-  - id            : "1"
-    institution   : "Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
-  - id            : "2"
-    institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"
-  - id            : "3"
-    institution   : "University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland"
-  - id            : "4"
-    institution   : "Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands"
-  - id            : "5"
-    institution   : "Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Intelligent Lighting Institute, Eindhoven, Netherlands"
-  - id            : "6"
-    institution   : "Monash University, Department of Electrical and Computer Systems Engineering, Malaysia, Selangor, Malaysia"
-  - id            : "7"
-    institution   : "University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA"
-  - id            : "8"
-    institution   : "Ximes GmbH, Frankfurt, Germany"
-  - id            : "9"
-    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
-  - id            : "10"
-    institution   : "Eindhoven University of Technology, Human-Technology Interaction Group, Eindhoven, Netherlands"
-  - id            : "11"
-    institution   : "University of Oxford, Department of Experimental Psychology, Oxford, UK"
-  - id            : "*"
-    institution   : "Joint first author"
-
-authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
-
-abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
-
-keywords          : "keywords"
-wordcount         : "X"
-
-bibliography      : ["references.bib"]
-
-floatsintext      : no
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
-
-documentclass     : "apa6"
-classoption       : "man"
-output            : 
-  papaja::apa6_pdf:
-    latex_engine: xelatex
-mainfont: Helvetica
+title: "Appendix B"
+author: "Team LEBA"
+date: "10/22/2021"
+output: pdf_document
 ---
 
-```{r setup, warning=FALSE, include=FALSE}
+```{r Asetup, warning=FALSE, include=FALSE}
 knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600)
@@
 
-```{r depMan, eval=FALSE, include=FALSE}
-library(packrat)
-#This chunk is disabled. Only run this to install the dependencies automatically.
-packrat::init()
-#Only use when you have added some pack
-#packrat::snapshot(ignore.stale=TRUE)
-
-#To find and install required dependencies.
-packrat::restore()
-```
-
-```{r install, eval=FALSE, include=FALSE}
-#if "packrat" does not work you can run this chunk manually to get all required packs"
-
-install.packages("devtools")
-install.packages("semTools")
-install.packages("MOTE")
-install.packages("psych")
-install.packages("dlookr")
-install.packages("tidyverse")
-install.packages("qgraph")
-install.packages("kableExtra")
-install.packages("paran")
-install.packages("EFA.MRFA")
-install.packages("rsvg")
-install.packages("ggcorrplot")
-install.packages("semTable")
-install.packages("magick")
-install.packages("mirt")
-install.packages("cowplot")
-install.packages("VIM")
-devtools::install_github('rich-iannone/DiagrammeR')
-devtools::install_github("crsh/papaja", force = T)
-install.packages("DiagrammeRsvg")
-devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
-devtools::install_github("crsh/citr")
-remotes::install_github("jthomasmock/gtExtras")
-install.packages("gt")
-remotes::install_github("jthomasmock/gtExtras")
-install.packages("questionr")
-devtools::install_github("lbusett/insert_table")
-```
-
-```{r library, include=FALSE}
+```{r Alibrary, include=FALSE}
 
@@
 library(kutils)
-r_refs("references.bib")
+library(Hmisc)
 ```
 
----
-nocite: |
-  `r cite_r("references.bib")`
----
-
-# Introduction
-
--   Light exposure is important
-
--   Light exposure Behavior is important
-
--   Table: Overview Existing Related Scales: items in total / items on light exposure (behaviour)
-
--   Existing Scales: Review them in text
-
--   None of these do light exposure behavior.
-
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Name                                            | Authors                     | Description                                                                            | Relevant Items | Adaptations |
-+=================================================+=============================+========================================================================================+:==============:+=============+
-| Visual Light Sensitivity Questionnaire-8        | [@verriotto2017new]        | Eight-question survey to assess the presence and severity of photosensitivity symptoms | all            | jhghjgjhgfd |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Office Light Survey                             | [@eklund1996development]   | Multi-item questionnaire to assess electrical lighting environment in office           | aa             | gh          |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Harvard Light Exposure Assessment Questionnaire | [@bajaj2011validation]     | Self-administered semiquantitative light qestionnaire                                  | aa             | as          |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Hospital Lighting Survey                        | [@dianat2013objective]     | 23 items questionnaire to assess light environment in a hospital                       | dd             | fg          |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Morningness-Eveningness Questionnaire           | [@horne1976self]           | 19 items questionnaire to understand your body clock                                   | ff             | hj          |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Munich Chronotype Questionnaire (MCTQ)          | [@roenneberg2003life]      | 17 items questionnaire to understand individuals phase of entrainment                  | ff             | jk          |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Assessment of Sleep Environment                 | [@grandner2014development] | 13 items questionnaire measuring your sleep environment quality                        | ff             | kl          |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| The Pittsburgh Sleep Quality Index (PSQI)       | [@buysse1989pittsburgh]    | 9 items inventory to measure sleep quality and sleeping pattern                        | ff             | klfrgfgvfg  |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-|                                                 |                             |                                                                                        |                |             |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-|                                                 |                             |                                                                                        |                |             |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-
-: Existing related Scales
-
-# Methods
-
-## Ethical approval
-
-The cantonal ethics commission (Ethikkommission Nordwest- und Zentralschweiz, project ID Req-2021-00488) reviewed this project and issued an official clarification of responsibility (full document see Suppl.
-Fig X in appendix) stating: "The research project does not fall under the scope of the Human Research Act, because your project is using only anonymised data.
-An authorisation from the ethics committee is therefore not required and the EKNZ is not responsible for its review."
-
-## Data Availability
-
-## Survey characteristics
-
-Data was collected in a quantitative cross-sectional approach via a fully anonymous online survey hosted on REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel (sciCORE; <https://redcap.scicore.unibas.ch/>).
-Participants were recruited via the website of a Comic co-released with the survey [CITE COMIC HERE; <https://enlightenyourclock.org/participate-in-research/>], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution via f.lux software [CITE f.lux Michael Herf?].
-
-Completing the online survey took approx.
-15 to 20 minutes and was not compensated.
-The first page of the survey comprised a participant information sheet, where participants' informed consent to participate was obtained before any of the questions were displayed.
-Underaged participants (\<18 years) were urged to obtain assent from their parents/legal guardians, before filling in the survey.
-Information on the first page included the objectives of the study, inclusion criteria, estimated duration, the use, storage and sharing of the data, compensation (none), and information about the type of questions in the survey.
-Moreover, participants needed to confirm that they were participating the survey for the first time.
-To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention.
-What is 4+5?").
-The data analysed in this study was collected between 17.05.2021 and 03.09.2021.
-Questions incorporating retrospective recall were all aligned to the period of "past four weeks", matching the presented LEBA instrument.
-
-In addition to the LEBA questionnaire, which is subject of the current study, the following variables and items were assessed but not included in the analysis:
-
--   Sleep disturbance and sleep-related impairment [CITE]
--   Sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration [CITE]
--   Meal timing & caffeine consumption [CITE]
--   Light sensitivity (photophobia vs. photophilia) [CITE]
--   Self-reported pubertal stage (only if younger than 18 years old) [CITE]
-
-Furthermore, the following 1-item demographic variables were assessed:
-
--   Age
--   Sex
--   Gender identity
--   Occupational Status
--   COVID-related Occupational setting during the past four weeks
--   Time zone & country of residence
--   English as native language
-
-## Participants
-
-```{r Data, include=FALSE}
+```{r AData, include=FALSE}
 data <- readRDS("leba_2021-09-08.rds")
-
-# Separating EFA and CFA samples with descriptive column
-descriptives.data <- data
-
-## Merge "0"s and "1"s into "1"s select,subset assign)
-descriptives.data[ , 9:56 ][ descriptives.data[ , 9:56 ] == 0 ] <- 1
-EFA.descriptives <- descriptives.data[1:428,]
-CFA.descriptives <- descriptives.data[429:690, ]
 
@@
 sem.data <- data[, 9:56] #EFA & CFA data
-sem.data[ sem.data == 0] <- 1 #Merged "0"s and "1"s into "1"s
-
 ## renaming the column-header
@@
 colnames(sem.data) <- colnam
-```
-
-```{r prepareDescTable, include=FALSE}
-
-listdescVars <- colnames(descriptives.data[c(1:3,5:7)])
-
-#seperating naming and  reducing data for descriptive Table 
-desctable.data <- select(descriptives.data, c(listdescVars,
-                          IncludedInCFA))
-
-#renaming TRUE and FALSE from the IncludedInCFA to EFA and CFA for Descriptive Table
-desctable.data$IncludedInCFA[desctable.data$IncludedInCFA == T ] <-
- "2. CFA Sample"
-desctable.data$IncludedInCFA[desctable.data$IncludedInCFA == F ] <- 
- "1. EFA Sample"
-
-# recode the Gender factor so it will only show "Gender Diverse" in the summary table
-desctable.data$slypos_demographics_gender.factor <-
-  recode_factor(desctable.data$slypos_demographics_gender.factor, "No" = "Yes",
-         "Yes"= "No")
-
-# create descriptive table for the demographic vars (excluding tz & Country) with gtsummary
-desctable.data %>%
-  tbl_summary(
-    by = IncludedInCFA,
-    statistic = list(all_continuous() ~ "{mean} ({sd})",
-                     all_categorical() ~ "{n} ({p}%)"),
-    digits = all_continuous() ~ 2,
-    label = list(slypos_demographics_age ~ "Age",
-                 slypos_demographics_sex.factor ~ "Sex",
-                 slypos_demographics_gender.factor ~ "Gender-Variant Identity",
-                 slypos_demographics_language.factor ~ "Native English Speaker",
-                 slypos_demographics_work_or_school.factor ~ "Occupational Status",
-                 slypos_demographics_school.factor ~ "Occupational setting"
-                 ),
-    missing = "no"
-    ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
-modify_header(label ~ "**Variable**") %>% 
-as_kable(format = 'pipe') -> desc_kable #save it as a knitr::kable
+EFA.data <- sem.data[1:428, ]
 
@@
 
-```{r DescTabPrint, results='asis'}
-
-desc_kable %>% kable_styling(desc_kable, repeat_header_text = "Participants' Demographic Characteristics")
-
-```
-
-Table 1 summarizes the survey participants' demographic characteristics.
-Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses.
-XX participants were excluded from analysis due to not passing at least one of the "attention check" items.
-Anonymous responses from a total of *n* = `r nrow(desctable.data)` participants were included in the analysis of the current study, split into samples for exploratory (EFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "1.
-EFA Sample",])`) and confirmatory factor analysis (CFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "2.
-CFA Sample",])`).
-The EFA sample included participants filling out the questionnaire from 17.05.2021 to XX.XX.XXXX , whereas participants who filled out the questionnaire from YY.YY.YYYY to 03.09.2021 were included in the CFA analysis.
-Participants indicated filling out the online survey from a diverse range of geographic locations.
-The four most common geographic locations included:
-
-`r kable(head(summary(descriptives.data$slypos_demographics_tz.factor), 4), format = "latex")`
-
-For a full list of geographic locations, see Suppl. Table X in the appendix.
-
-Age among all participants ranged from `r min(desctable.data$slypos_demographics_age)` years to `r max(desctable.data$slypos_demographics_age)` years (EFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
-EFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
-EFA Sample"])`; CFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`), with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 0)` years of age (Overall: *M* = `r mean(desctable.data$slypos_demographics_age)`, *SD* = `r sd(desctable.data$slypos_demographics_age)`; EFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
-EFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
-EFA Sample"])`; CFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`).
-In total 47% of participants indicated female sex (EFA: 44%; CFA: 52%), 51% indicated male (EFA: 54%; CFA: 46%) and 2% indicated other sex (EFA: 2.1%, CFA: 1.9%).
-Overall 7.2% (EFA: 7.8%; CFA: 6.2%) participants indicated a gender-variant identity.
-In a "Yes/No" question regarding native language 46% of respondents (EFA: 46%; CFA: 45%) indicated to be native English speakers.
-For their "Occupational Status", more than half (57%) of the overall sample reported that they currently work (EFA: 55%; CFA: 61%), whereas 25% (EFA: 29%; CFA: 20%) reported that they go to school and 17% (EFA: 17%; CFA: 19%) responded that they do neither.
-With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample 44% (EFA: 45%; CFA: 42%) of the participants indicated that they were in a home office/ home schooling setting., while 16% overall (EFA: 16%; CFA: 16%) reported face-to-face work/schooling.
-Lastly, 21% overall (EFA: 22%; CFA: 20%) reported a combination of home- and face-to-face work/schooling, whereas 19% overall (EFA: 17%; CFA: 23%) filled in the "Neither (no work or school, or indication)" response option.
-We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable "Age" and Pearson's Chi-squared test for all other categorical variables via the gtsummary R package's "add_p" function [CITE].
-The p-values were corrected for multiple testing applying false discovery rate (FDR) via the "add_q" function of the same package.
-After p-value (FDR) correction for multiple testing, none of the demographic variables were significantly different between the EFA sample and the CFA sample (all q-values *q* ≥ .2, indicating equivalence.
-
-1.  Describe EFA and CFA sample separately.
-2.  Sampling technique: Convince sampling (non-probability sample)
-3.  Method: cross-sectional survey
-4.  How many missing data?
-5.  How incomplete data were addressed.
-6.  Why such sample was chosen?
-
-EFA: For exploring initial factor structure, a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013]
-
-CFA: For estimating the sample size for the confirmatory factor analysis we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006] where 10 participants per parameter is required to earn trustworthiness of the result.
-Our sample size exceeds the requirement.
-
-## Procedure
-
-### Development of the Scale
-
-1.  How the items were generated
-2.  How the literature was reviewed to identify construct adequacy of the items.
-3.  Discuss the expert panel review process to assess content validity
-
-```{r Manuflowchart, include=FALSE }
-Flowchart1 <- grViz("digraph nicegraph{
-
-                    graph [fontname = Helvetica,layout = dot,fontsize = 20, ]
-
-                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 6.5, height = 1, 
-                    fixedsize = true,fontsize = 20]
-
-                    A[label = '48 items were generataed by a robust expert panel'] 
-                    B[label = 'Exploratory Factor Analysis on 48 Items (N = 428)']
-
-                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 7.5, height = 2, 
-                    fixedsize = true, fontsize = 20]
-                    C[label = 
-                    <
-                    Factor Identification<br align = 'left'/>
-                    Scree Plot: 6 Factors<br align = 'left'/>
-                    Parallel Analysis: 6 Factors<br align = 'left'/>
-                    Minimum Average Partial Method: 5 Factors<br align = 'left'/>
-                    Hull Method: 5 Factors<br align = 'left'/>
-                    >
-                    ]
-
-                     subgraph cluster_1 {
-                      graph[fontname = Helvetica, shape = rectangle]
-                      style = rounded
-                     node[fontname = Helvetica, margin = 0.2,width = 9, height = 1, 
-                    fixedsize = true, fontsize = 18 ]
-
-                     1[label = '5 Factor Solution Retained 25 Items']
-                     2[label = 'Reliability Analysis on EFA Sample (N=428)
-                    Alpha F1 =.86; F2 = .71; F3 = .68; F4 =.62; F5 =.52']
-
-                     3[label = 'Confirmatory Factor Analysis 
-                     on the Five Factor Model (25 Items; N=262)
-                      Acceptable Fit ( CFI = .94; TLI .93; RMSEA = .06, SRMR = .11)']
-
-                    4[label = 'Confirmatory Factor Analysis 
-                     on the Five Factor Model (23 Items; N=262)
-                      Acceptable Fit ( CFI = .97; TLI .96; RMSEA = .04, SRMR = .09)']
-                     5[label = 'Reliability Analysis on CFA (23 Items; N=262) 
-                      Alpha F1=.93; F2=.80; F3 =.62; F4=.72; F5=.45']
-                    }
-                subgraph cluster_2 {
-                      graph[fontname = Helvetica,shape = rectangle]
-                      style = rounded
-                     node[fontname = Helvetica, margin = 0.2,width = 8, height = 1, 
-                fixedsize = true, fontsize = 18 ]
-                    6[label = '6-Factor solution: one factor emerged with only two salient loadings']
-                    7[label = 'Rejected']
-                    }
-
-                     edge[fontname = Helvetica,color = black,arrowhead = vee, arrowsize = 1.25]
-                     A ->B
-                     B ->C
-                     C ->1
-                     1 ->2
-                     2 ->3
-                     3 ->4
-                     4 ->5
-                     C ->6
-                     6 ->7
-
-}")
-
-export_svg(Flowchart1) %>%
-  charToRaw() %>%
-  rsvg() %>%
-  png::writePNG("Manuscript.figures/Flowchart1.png")
-
-```
-
-```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development', out.height='100%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/Flowchart1.png')
-```
-
-### Data Collection
-
-Timeline of data collection, mode of data collection.
-
-## Analytic Strategies
-
-We used R (version 4.1.0), including several R packages, for our analyses.
-Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
-Our data violated both the univariate and multivariate normality assumptions.
-Due to these violations and the ordinal nature of our response data, we used a polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA.
-We employed principal axis (pa), a factor extraction method with varimax rotation.
-PA is robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020].
-The obtained latent structure was confirmed by the minimum residuals extraction method as well.
-We used a combination factor identification method including scree plot[@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method[@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
-Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018;
-
-# Results
-
-## Exploratory Factor Analysis
-
-```{r ggplot2, include=F}
+```{r Aggplot2, include=F}
 apatheme=theme_bw()+
@@
 
-```{r EFAdata, include=FALSE}
-### EFA data
-EFA.data <- sem.data[1:428, ]
-#library(VIM)
-missing <- aggr(EFA.data, plot =T)
-
-```
-
-```{r EFAassumptions, include=FALSE}
+```{r AEFAassumptions, include=FALSE}
 
@@
 bartlet <- cortest.bartlett(EFA.data, n =428)
-
-#Histogram
-#psych::multi.hist(EFA.data[,sapply(EFA.data, is.numeric)])
 
@@
               significance= sig,
-              method= ifelse(bonf == TRUE, "Shapiro-Wilks test with Bonferroni Correction",
-                             "Shapiro-Wilks test without Bonferroni Correction")))
+              method= ifelse(bonf == TRUE, "Shapiro-Wilks test with Bonferroni Correction","Shapiro-Wilks test without Bonferroni Correction")))
 }
@@
 
-```{r CorrMatrix, include=FALSE}
+```{r AtabDes, results='asis'}
+apa_table(Des.combined, caption = "Descriptive Statistics for Unmerged response options", align = "c", note = "*p<.001", placement = "h")
+```
+
+```{r ACorrMatrix, include=FALSE}
 #Polychoric Correlation matrix
@@
 
-```{r ItemAnalysis, include=FALSE}
-# Item analysis
-Item_analysis <- psych::alpha(EFA.data)
-Item_analysis$item.stats$r.cor
-R.cor.sum <- summary(Item_analysis$item.stats$r.cor)
-low.r.corec <- abs(R.cor.sum[1])  #minimum item total correlation
-high.r.corec <- R.cor.sum[6]     # maximum item total correlation
-```
-
-Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy[@kaiserIndexFactorialSimplicity1974] .
-The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cutoff value (.50) indicating a mediocre sample [@hutchesonMultivariateSocialScientist1999].
-Table\@ref(tab:tabDes) summarizes the univariate descriptive statistics for the 48 items.
-some of the items were skewed with high Kurtosis values.
-Our data violated both univariate normality (Shapiro-Wilk statistics; [@shapiroAnalysisVarianceTest1965]) and multivariate normality assumptions (Marida's test;[@mardiaMeasuresMultivariateSkewness1970]).
-Multivariate skew was = `r printnum(mardia$b1p)` (p \<0.001) and multivariate kurtosis was = `r printnum(mardia$b2p)` (p \<0.001).
-Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018].
-Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p \< .001] indicated the correlations between items are adequate for the EFA.
-However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than .30.
-The inter item correlation ranged between `r apa(min.cor,2,F)` to `r apa(max.cor,2,F)`.
-And the corrected item-total correlations ranged between `r apa(low.r.corec,2,F)` to `r apa(high.r.corec,2,F)`.
-
-```{r tabDes,results='asis'}
-apa_table(Des.combined, caption = "Descriptive Statistics", align = "c", note = "*p<.001", longtable =T)
-```
-
-```{r figCor, out.width="100%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}
+```{r AfigCor, fig.align='center', fig.cap="Correlation plot of the items",  out.width="100%", include=FALSE,}
 
@@
 
-```{r ParallelEFA, include=FALSE}
+```{r AParallelEFA, include=FALSE}
 
@@
 
-```{r ScreePlot, include=FALSE}
+```{r AScreePlot, include=FALSE}
 Scree <- scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
@@
 
-```{r HullEFA, include=FALSE}
-# HULL
-hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
-        details = TRUE)
-hull <- ggplot2::last_plot()
-Hull <- hull+ ggtitle(NULL) +xlab("Factor Number")+ylab("CAF")+ 
-  apatheme +scale_color_manual(labels = c("Out side the convex Hull", "On the convex Hull"), values = c("red", "cyan2")) 
-```
-
-```{r MAPefa, include=FALSE}
+```{r AMAPefa, include=FALSE}
 #MAP
@@
 
-Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution.
-Horn's parallel analysis [@hornRationaleTestNumber1965] with 500 iterations also indicated a six-factor solution.
-However, the MAP method [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] suggested a five-factor solution.
-As a result, we tested both five-factor and six-factor solutions.
-
-```{r facIdFig, out.height="200%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}
-cowplot::plot_grid(parallel, scree.plot,Hull, labels = "AUTO",ncol=1, label_size = 8,align = "v")
+```{r AfacIdFig, out.height="200%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot',  warning=FALSE, results= 'asis'}
+cowplot::plot_grid(parallel, scree.plot, labels = "AUTO",ncol=1, label_size = 8,align = "v")
 
@@
 
-```{r EFA, include=FALSE}
+Horn's parallel analysis with 500 iterations indicated a five-factor solution.
+However, Scree plot and the MAP method suggested 6-factor solution.
+five-factor solution (Figure\\ \\\@ref:AfacIdFig).
+As a result, we tested both five-factor and six-factor solutions.
+
+```{r AEFA, include=FALSE}
 fa.5F.1 <- fa(r=correlations$rho, nfactors = 5, fm= "pa",rotate ="varimax",
@@
 reduced.model.5F.1 <- dplyr::select(EFA.data ,
-                                    -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14))
+                                    -c(item32, item34, item24, item37, item22, item5,
+                                        item28, item30, item39,item23, item45, item6, item29, item2, item41))
 
@@
 
-reduced.model.5F.2 <- dplyr::select(EFA.data, -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14, item34, item47, item21, item13))
+reduced.model.5F.2 <- dplyr::select(EFA.data, -c( item32, item34, item24, item37, item22, item5,
+                                        item28, item30, item39,item23, item45, item6, item29, item2, item41, item46, item13, item15, item25, item1, item26, item14))
 
@@
 
-var1 <- CC$Vaccounted[2,1]*100
-var2 <- CC$Vaccounted[2,2]*100
-var3 <- CC$Vaccounted[2,3]*100
-var4 <- CC$Vaccounted[2,4]*100
-var5 <- CC$Vaccounted[2,5]*100
+reduced.model.5F.3 <- dplyr::select(EFA.data, -c( item32, item34, item24, item37, item22, item5,
+                                        item28, item30, item39,item23, item45, item6, item29, item2, item41, item46, item13, item15, item25, item1, item26, item14, item43, item42))
+
+correlations.red.5F.3 <- polychoric(reduced.model.5F.3,correct = 0)
+
+fa.5F.4 <- fa(r=correlations.red.5F.3$rho, nfactors = 5, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428,max.iter = 500 )
+
+CC <- print(fa.5F.4, cut = .3, digits = 3, sort = TRUE)
 ```
 
-```{r EFAplotcode, include=FALSE}
-
-EFAplot <- grViz("
-digraph boxes_and_circles {
-
-graph [layout = dot,rankdir = LR, fontsize = 40]
-
-# node definitions with substituted label text
-node [fontname = Helvetica, shape = circle,  margin = 0.5, width = 3.5, height = .5,
-fixedsize = true, fontsize = 35]
-F5 [label = 'F5']
-F4 [label = 'F4']
-F3 [label = 'F3']
-F2 [label = 'F2']
-F1 [label = 'F1']
-
-node [fontname = Helvetica, shape = box]
-b [label = 'item16']
-c [label = 'item36']
-d [label = 'item17']
-e [label = 'item11']
-f [label = 'item10']
-g [label = 'item12']
-h [label = 'item7']
-i [label = 'item8']
-j [label = 'item9']
-k [label = 'item27']
-l [label = 'item3']
-m [label = 'item40']
-n [label = 'item30']
-o [label = 'item41']
-p [label = 'item33']
-q [label = 'item32']
-r [label = 'item35']
-s [label = 'item37']
-t [label = 'item38']
-u [label = 'item46']
-v [label = 'item45']
-w [label = 'item25']
-x [label = 'item4']
-y [label = 'item1']
-z [label = 'item26']
-
-{rank = same; F1 F2 F3 F4 F5}
-# edge definitions with the node IDs
-edge [fontname = Helvetica, fontsize = 35]
-F5 -> u [label = '0.60']
-F5 -> v [label = '0.59']
-F5 -> w [label = '0.41']
-F5 -> x [label = '0.41']
-F5 -> y [label = '0.40']
-F5 -> z [label = '0.35']
-F4 -> p [label = '0.74']
-F4 -> q [label = '0.73']
-F4 -> r [label = '0.66']
-F4 -> s [label = '-0.39', color =red]
-F4 -> t [label = '0.39']
-F3 -> k [label = '0.80']
-F3 -> l [label = '0.80']
-F3 -> m [label = '0.65']
-F3 -> n [label = '0.49']
-F3 -> o [label = '36']
-F2 -> e [label = '0.79']
-F2 -> f[label = '0.76']
-F2 -> g [label = '0.65']
-F2 -> h[ label = '0.50']
-F2 -> i [label = '-.49',color =red]
-F2 -> j [label = '0.32']
-F1 -> b[label = '0.99']
-F1-> c [label = '0.93']
-F1-> d [label = '0.80']
-}
-")
-
-export_svg(EFAplot) %>%
-  charToRaw() %>%
-  rsvg() %>%
-  png::writePNG("Manuscript.figures/EFAplot.png")
-
-```
-
-```{r EFAplot, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, out.height="50%", out.width="100%", results='asis'}
-knitr::include_graphics('Manuscript.figures/EFAplot.png')
-
-```
-
-```{r Cronbach alpha for 5 fators, message=TRUE, warning=FALSE, include=FALSE}
-
-Five.F1 <- dplyr::select(EFA.data, item16, item36, item17)
-Five.F2 <- dplyr::select(EFA.data, item11, item10, item12, item7, item8, item9) 
-Five.F3 <-  dplyr::select(EFA.data, item27, item3,item40, item30, item41)
-Five.F4 <-  dplyr::select(EFA.data, item33,item32,item35, item37, item38)
-Five.F5 <- dplyr::select(EFA.data, item46, item45, item25, item4, item1, item26)
-
-Five.F1.alpha <- psych::alpha(Five.F1, check.keys = T) 
-Five.F2.alpha <- psych::alpha(Five.F2, check.keys = T)
-Five.F3.alpha <- psych::alpha(Five.F3, check.keys = T)
-Five.F4.alpha <- psych::alpha(Five.F4, check.keys = T) 
-Five.F5.alpha <- psych::alpha(Five.F5, check.keys = T)
-
-F1.alpha <- Five.F1.alpha$total$raw_alpha
-F2.alpha <- Five.F2.alpha$total$raw_alpha
-F3.alpha <- Five.F3.alpha$total$raw_alpha
-F4.alpha <- Five.F4.alpha$total$raw_alpha
-F5.alpha <- Five.F5.alpha$total$raw_alpha
-```
-
-```{r minres 5 factor supplimentary analyisis, eval=FALSE, include=FALSE}
-
-#Supplementary EFA with Minres Extraction
-
-fa.5F.min.1 <- fa(r=correlations$rho, nfactors = 5, fm= "minres",rotate ="varimax",
-                residuals = TRUE, SMC = TRUE, n.obs =428)
-EE <- print(fa.5F.min.1, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.5F.min.1 <- dplyr::select(EFA.data ,
-                                    -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14))
-
-correlations.red.5F.min.1 <- polychoric(reduced.model.5F.min.1,correct = 0)
-
-fa.5F.min.2 <- fa(r=correlations.red.5F.min.1$rho, nfactors = 5, fm= "minres",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-FF <- print(fa.5F.min.2, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.5F.min.2 <- dplyr::select(EFA.data, -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14, item34, item47, item21, item13))
-
-correlations.red.5F.min.2 <- polychoric(reduced.model.5F.min.2, correct = 0)
-
-fa.5F.min.3 <- fa(r=correlations.red.5F.min.2$rho, nfactors = 5, fm= "minres",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-GG <- print(fa.5F.min.3, cut = .3, digits = 3, sort = TRUE)
-```
-
-```{r EFA 6 Factors Promax, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, results='hide'}
-# EFA with 6 factor (rejected)
-
-#correlations <- polychoric(EFA.factor, correct = 0)
-
-fa.6F.1 <- fa(r=correlations$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-II <- print(fa.6F.1, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.6F.1 <- dplyr::select(EFA.data ,
-                                    -c(item34, item44, item48, item43, item39, item22, item2, item20, item21, item24,item30, item14, item28, item6, item15, item23))
-
-correlations.red.6F.1 <- polychoric(reduced.model.6F.1,correct = 0)
-
-fa.6F.2 <- fa(r=correlations.red.6F.1$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-JJ <- print(fa.6F.2, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.6F.2 <- dplyr::select(EFA.data, -c(item34, item44, item48, item43, item39, item22, item2, item20, item21, item24,item30, item14, item28, item6, item15, item23, item18, item42, item47, item41))
-
-correlations.red.6F.2 <- polychoric(reduced.model.6F.2,correct = 0)
-
-fa.6F.3 <- fa(r=correlations.red.6F.2$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)
-
-KK <- print(fa.6F.3, cut = .3, digits = 3, sort = TRUE)
-
-# Residuals
-residual.6F =residuals(fa.6F.3 , diag = FALSE, na.rm =T)
-#Count of numbers of residuals>.05
-BigRRR= sum(residual.6F>abs(.05), na.rm =T)
-print(BigRRR)
-
-#Total number of off diagonal elements in the data matrix
-totRRR = length(reduced.model.6F.2)*(length(reduced.model.6F.2)-1)/2
-
-# Proportion of off-diagonal elements >.10
-sumRRR <- sum(BigRRR/totRRR*100)
-
-hist(residual.6F, main = NULL, xlab = "Six factor Solution: Residuals",ylim=c(0, 400))
-abline(h =65, lwd = 2, lty = 2)
-abline(v =.05,lwd = 2, lty = 2)
-```
-
-```{r factordetails, include=FALSE}
+```{r Afactordetails, include=FALSE}
 #Preparing the EFA table
@@
 
-efa.table <- fa_table(fa.5F.3,.3) 
+efa.table <- fa_table(fa.5F.4,.3) 
 nr <- nrow(efa.table)
@@
 #Communality
-Fac.5 <- fa.5F.3
+Fac.5 <- fa.5F.4
 min.com <- min(Fac.5$communality)
@@
 # Residuals
-residual.5F =residuals(fa.5F.3, diag = FALSE, na.rm =T)
+residual.5F =residuals(fa.5F.4, diag = FALSE, na.rm =T)
 #Count of numbers of residuals>.05
@@
 #Total number of off diagonal elements in the data matrix
-totRR = length(reduced.model.5F.2)*(length(reduced.model.5F.2)-1)/2
+totRR = length(reduced.model.5F.3)*(length(reduced.model.5F.3)-1)/2
 
@@
 
-Three rounds of EFA with all 48 items were conducted, and problematic items were gradually discarded (cross-loading items and poor factor loading (\<.30) items).
-Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 [@brownConfirmatoryFactorAnalysis2015], all factor-loading higher than .30 and no cross-loading greater than .30.
-We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (see the supplementary).
-Table\@ref(tab:TabEFA5) displays the factor-loading (structural coefficients) and communality of the items.
-The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients.
-The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`.
-However, the histogram of the absolute values of non-redundant residual-correlations (Fig\@ref(fig:Residuals) showed `r apa(sumR,2, T)`% correlations greater than the absolute value of .05, indicating a possible under-factoring.
-[@desjardinsHandbookEducationalMeasurement2018a].
-Subsequently, we fitted a six-factor solution.
-However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution.
+```{r AEFATable, results='asis'}
 
-In the five-factor solution, the first factor contained three items and explained `r apa(var1,2,F)`% of the total variance with a satisfactory internal reliability coefficient ($\alpha$ = `r apa(F1.alpha,2,F)`).
-All the items in this factor stemmed from the individual's preference to use blue light filters in different light environments.
-The second factor contained six items and explained `r apa(var2,2,F)`% of the total variance with a satisfactory internal reliability coefficient ($\alpha$ = `r apa(F2.alpha,2,F)`).
-Items under this factor commonly investigate an individual's hours spent outdoor.
-The third factor contained five items and explained `r apa(var3,2,F)`% of the total variance.
-Items under this factor dealt with the specific behaviors pertaining to sleep.
-However, the internal consistency reliability coefficient was not satisfactory ($\alpha$ = `r apa(F3.alpha,2,F)`).
-The fourth factor contained five items and explained `r apa(var4,2,F)`% of the total variance with an internal consistency coefficient, $\alpha$ = `r apa(F4.alpha,2,F)`.
-These five items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time.
-Lastly, the fifth factor contained six items and explained `r apa(var5,2,F)`% of the total variance.
-This factor tried to measure an individual's behavior lead by the awareness of light's influence on health.
-However, this factor showed unsatisfactory internal consistency reliability ($\alpha$ = `r apa(F5.alpha,2,F)`).
-It is essential to attain a balance between psychometric properties and the interpretability of the common themes when exploring the latent structure.
-As all of the emerged factors are highly interpretable, regardless of the apparent low reliability of the two factors, we retain the five-factor solution with 23 items for our confirmatory factor analysis (CFA).
-Two items showed negative factor-loading (items 44 and 21).
-Upon inspection, it was understood that these items are negatively correlated to the common theme, and thus in the CFA analysis, we reversed the response code for these two items.
-
-```{r EFATable, results='asis'}
-
-apa_table(efa.table,align = "c", caption = "Factor loadings and communality of the retained items", note = "Only loading higher than .30 is reported", font_size = "small")
+apa_table(efa.table,align = "c", caption = "Factor loadings and communality of the retained items [Unmerged Responses]", note = "Only loading higher than .30 is reported", font_size = "small", placement = "h")
 ```
 
-```{r EFAResiduals, out.height= "50%",  fig.align='center', fig.cap= ' Histogram of residulas:  five-factor solution',  out.width="50%",  warning=FALSE, results='asis'}
+| **Five Factor Solution[Unmerged Responses] (24 Items)** |
+|---------------------------------------------------------|
+| **F1**                                                  |
+| `r label(sem.data$item19)`                              |
+| `r label(sem.data$item20)`                              |
+| `r label(sem.data$item18)`                              |
+| `r label(sem.data$item21)`                              |
+| `r label(sem.data$item4)`                               |
+| **F2**                                                  |
+| `r label(sem.data$item11)`                              |
+| `r label(sem.data$item10)`                              |
+| `r label(sem.data$item12)`                              |
+| `r label(sem.data$item8)`                               |
+| `r label(sem.data$item7)`                               |
+| `r label(sem.data$item9)`                               |
+| **F3**                                                  |
+| `r label(sem.data$item3)`                               |
+| `r label(sem.data$item27)`                              |
+| `r label(sem.data$item40)`                              |
+| **F4**                                                  |
+| `r label(sem.data$item35)`                              |
+| `r label(sem.data$item48)`                              |
+| `r label(sem.data$item33)`                              |
+| `r label(sem.data$item47)`                              |
+| `r label(sem.data$item44)`                              |
+| `r label(sem.data$item31)`                              |
+| `r label(sem.data$item38)`                              |
+| **F5**                                                  |
+| `r label(sem.data$item16)`                              |
+| `r label(sem.data$item17)`                              |
+| `r label(sem.data$item36)`                              |
+
+```{r AEFAResiduals, fig.align='center', fig.cap=' Histogram of residulas:  five-factor solution', warning=FALSE, include=FALSE, out.height="50%", out.width="50%"}
 hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))
-abline(h =51, lwd = 2, lty = 2)
+abline(h =35, lwd = 2, lty = 2)
 abline(v =.05,lwd = 2, lty = 2)
@@
 ```
-
-```{r gtvis, include =F}
-## Recoding sem.data$item8
-gt.data <- sem.data
-gt.data$item8 <- as.character(gt.data$item8)
-gt.data$item8 <- fct_recode(gt.data$item8,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-
-## Recoding gt.data$item26
-gt.data$item26 <- as.character(gt.data$item26)
-gt.data$item26 <- fct_recode(gt.data$item26,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-## Recoding gt.data$item37
-gt.data$item37 <- as.character(gt.data$item26)
-gt.data$item37 <- fct_recode(gt.data$item26,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-
-names(gt.data)[names(gt.data) == "item1"] <- "item01"
-names(gt.data)[names(gt.data) == "item3"] <- "item03"
-names(gt.data)[names(gt.data) == "item4"] <- "item04"
-names(gt.data)[names(gt.data) == "item7"] <- "item07"
-names(gt.data)[names(gt.data) == "item8"] <- "item08"
-names(gt.data)[names(gt.data) == "item9"] <- "item09"
-
-#EFA data
-gt.efa.data <- gt.data[1:428, ]
-
-gt.efa.data.table <- gt.efa.data %>% 
-  dplyr::select(item16, item36, item17,
-                 item11, item10,item12,item07,item08,item09,
-                 item27,  item03, item40,  item30, item41,
-                 item33, item32,item35, item37,item38, 
-                 item46, item45, item25, item04, item01,item26)
-
-#Creating long data
-gt.efa.long <- as.data.frame(gather(gt.efa.data.table, Items, value))
-gt.efa.long$value <- as.numeric(as.character(gt.efa.long$value))
-
-#Summarizing and creating gt object
-gt.efa.tab <- gt.efa.long %>% 
-  group_by(Items) %>% 
-  # calculate summary stats & create data for the histogram and density plot
-  dplyr::summarise(
-    nr = n(),
-    mean = mean(value, na.rm = TRUE),
-    med = median(value, na.rm = TRUE),
-    sd = sd(value, na.rm = TRUE),
-    hist_data = list(value),
-    dens_data = list(value),
-    .groups = "drop"
-  ) %>% 
-  gt()
-
-#Preparation for likert data
-efa.LEBA.likert <- as.data.frame(gt.efa.data.table)
-
-recod_LEBA <- c( "1" = "Never", "2" = "Rarely", "3"= "Sometimes","4" = "Often",
-                 "5" = "Always")
-efa.LEBA.likert <-  mutate(efa.LEBA.likert, across(starts_with("item"), ~unname(recod_LEBA[.])))
-
-efa.LEBA.Factor = as.data.frame(lapply(efa.LEBA.likert,factor,
-                                   ordered = T))
-#get the items name
-efa.items <- names(efa.LEBA.Factor) 
-#Calculate percentage
-efa.percentage <- kutils::likert(efa.LEBA.Factor, vlist = efa.items )
-
-efa.percentage <- efa.percentage$table %>% 
-  as.data.frame(.)
-
-#data wrangling
-labels <- c("Always", "Never","Often", "Rarely", "Sometimes","Total")
-as.data.frame(labels)
-
-full.efa.percentage <- cbind(labels,efa.percentage) #tables with labels  
-full.efa.percentage<- t(full.efa.percentage ) #transpose
-as.data.frame(full.efa.percentage)
-full.efa.percentage1 <- full.efa.percentage[-1,-6] #removing 1st row and total column
-full.efa.percentage2 <- full.efa.percentage1[, c(2, 4, 5, 3,1)]# rearranging
-as.data.frame(full.efa.percentage2)
-
-colnames(full.efa.percentage2) <- c("Never","Rarely","Sometimes","Often","Always")
-
-efa.Items <- rownames(full.efa.percentage2)
-as.data.frame(efa.Items)
-full.efa.percentage3 <- cbind(efa.Items,full.efa.percentage2)
-
-full.efa.percentage3 <- full.efa.percentage3[order(efa.Items),] 
-full.efa.percentage3 <- as.data.frame(full.efa.percentage3[,-1]) %>% 
-  gt()
-
-gt.efa.table <- gt.efa.tab$'_data'
-gt.liket.efa <- full.efa.percentage3$"_data"
-
-efaTable <-  cbind( gt.efa.table, gt.liket.efa)%>% 
-  gt()
-
-gt.cfa.data <- gt.data[429:690,]
-gt.cfa.data.table <- gt.cfa.data %>% 
-  dplyr::select(item16, item36, item17,
-                 item11, item10,item12,item07,item08,item09,
-                 item27,  item03, item40,  item30, item41,
-                 item32,item35,item38, item33, 
-                 item46, item45, item25, item04, item01 )
-
-gt.cfa.long <- gather(gt.cfa.data.table, Items, value)
-gt.cfa.long$value <- as.numeric(as.character(gt.cfa.long$value))
-gt.cfa.tab <- gt.cfa.long %>% 
-  group_by(Items) %>% 
-# calculate summary stats & create data for the histogram and density plot
-  summarise(
-    nr = n(),
-    mean = mean(value, na.rm = TRUE),
-    med = median(value, na.rm = TRUE),
-    sd = sd(value, na.rm = TRUE),
-    hist_data = list(value),
-    dens_data = list(value),
-    .groups = "drop"
-  ) %>%
-
-  gt()
-
-#Preparation for likert data
-cfa.LEBA.likert <- as.data.frame(gt.cfa.data.table)
-
-recod_LEBA <- c( "1" = "Never", "2" = "Rarely", "3"= "Sometimes","4" = "Often",
-                 "5" = "Always")
-cfa.LEBA.likert <-  mutate(cfa.LEBA.likert, across(starts_with("item"), ~unname(recod_LEBA[.])))
-
-cfa.LEBA.Factor = as.data.frame(lapply(cfa.LEBA.likert,factor,
-                                   ordered = T))
-#get the items name
-cfa.items <- names(cfa.LEBA.Factor) 
-#Calculate percentage
-cfa.percentage <- kutils::likert(cfa.LEBA.Factor, vlist = cfa.items )
-
-cfa.percentage <- cfa.percentage$table %>% 
-  as.data.frame(.)
-
-#data wrangling
-labels <- c("Always", "Never","Often", "Rarely", "Sometimes","Total")
-as.data.frame(labels)
-
-full.cfa.percentage <- cbind(labels,cfa.percentage) #tables with labels  
-full.cfa.percentage <- t(full.cfa.percentage ) #transpose
-as.data.frame(full.cfa.percentage)
-full.cfa.percentage1 <- full.cfa.percentage[-1,-6] #removing 1st row and total column
-full.cfa.percentage2 <- full.cfa.percentage1[, c(2, 4, 5, 3,1)]# rearranging
-as.data.frame(full.cfa.percentage2)
-
-colnames(full.cfa.percentage2) <- c("Never","Rarely","Sometimes","Often","Always")
-
-cfa.Items <- rownames(full.cfa.percentage2)
-as.data.frame(cfa.Items)
-full.cfa.percentage3 <- cbind(cfa.Items,full.cfa.percentage2)
-
-full.cfa.percentage3 <- full.cfa.percentage3[order(cfa.Items),] 
-full.cfa.percentage3 <- as.data.frame(full.cfa.percentage3[,-1]) %>% 
-  gt()
-
-gt.cfa.table <- gt.cfa.tab$'_data'
-gt.liket.cfa <- full.cfa.percentage3$"_data"
-
-cfaTable <-  cbind( gt.cfa.table, gt.liket.cfa) %>% 
-  gt()
-
-efa.gt <- efaTable$"_data"
-cfa.gt <- cfaTable$"_data"
-
-gt.fullTable <-  rbind( efa.gt, cfa.gt) %>% 
-  gt() %>% 
-# histogram and density plots
-  gtExtras::gt_sparkline(
-    hist_data,
-    type = "histogram",
-    line_color = "black", 
-    fill_color = "grey",
-    bw = 1,
-    same_limit = TRUE)%>%
-  gtExtras::gt_sparkline(
-    dens_data,
-    type = "density",
-    line_color = "black", 
-    fill_color = "grey",
-    bw = 0.75,
-    same_limit = TRUE
-  )%>%
-# format decimals
-  fmt_number(columns = mean:sd, decimals = 1) %>%
-# header
-  tab_header(
-    title = md("**LEBA**"),
-    subtitle = md("Summary results of LEBA (N =690)")
-  ) %>% 
-  tab_footnote(
-    footnote = md("**Histogram**"),
-    locations = cells_column_labels(columns = hist_data)
-  ) %>%
-  tab_footnote(
-    footnote = md("**Density**"),
-    locations = cells_column_labels(columns = dens_data)
-  ) %>% 
-#create groups of columns
-tab_spanner(
-  label = "Items",
-  columns = Items
-) %>%
-  tab_spanner(
-    label = "Summary Statistics",
-    columns = nr:sd
-  ) %>%
-  tab_spanner(
-    label = "Graphics",
-    columns = hist_data:dens_data
-  ) %>% 
-  tab_spanner(
-    label = "Response Pattern",
-    columns = Never:Always
-  ) %>%
-# change column names to appear in the table
-cols_label(
-  Items = ("LEBA  Items"),
-  nr = ("n"),
-  mean = ("Mean"),
-  med = ("Median "),
-  sd = (("SD")),
-  hist_data = "Histogram",
-  dens_data = "Density"
-) %>%
-# set alignment as per wish
-  cols_align(
-    align = "center",
-    columns = everything()
-  ) %>%
-  opt_align_table_header(align = "left") %>%
-# add coloured dots and lines on the first column
-  gt_plt_dot(
-    mean,
-    Items,
-    palette = "ggthemes::fivethirtyeight"
-  ) %>% 
-    tab_row_group(
-      group = "CFA (n =262)",
-     rows = 26:48
-
-  ) %>% 
-  tab_row_group(
-  group = "EFA (n = 428)",
-    rows = 1:25  
-  ) %>% gtsave("Manuscript.figures/gt.png")
-
-```
-
-```{r gtPic, echo=FALSE, out.height="100%", out.width="200%", results= 'asis'}
-knitr::include_graphics('Manuscript.figures/gt.png')
-
-```
-
-# Confirmatory Factor Analysis
-
-```{r CFA data frame, include=FALSE}
-
-### CFA Data
-CFA.data <- sem.data[429:690,]
-
-## Recoding CFA.data$item8 into CFA.data$Ritem8
-CFA.data$Ritem8 <- as.character(CFA.data$item8)
-CFA.data$Ritem8 <- fct_recode(CFA.data$Ritem8,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-CFA.data$Ritem8 <- as.numeric(as.character(CFA.data$Ritem8))
-
-## Recoding CFA.data$item37 into CFA.data$item37_rec
-CFA.data$Ritem37 <- as.character(CFA.data$item37)
-CFA.data$Ritem37 <- fct_recode(CFA.data$Ritem37,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-CFA.data$Ritem37 <- as.numeric(as.character(CFA.data$Ritem37))
-
-## Recoding CFA.data$item26 into CFA.data$Ritem26
-CFA.data$Ritem26 <- as.character(CFA.data$item26)
-CFA.data$Ritem26 <- fct_recode(CFA.data$Ritem26,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-
-#Hitogram
-#psych::multi.hist(CFA.data[,sapply(CFA.data, is.numeric)])
-```
-
-```{r CFA 25items, include=FALSE }
-
-LB.model.Cor.1 <- "F1 =~ a1*item16 + item36 + a2*item17
-                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
-                 F3 =~  item27+ item3+ item40 + item30 + item41
-                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
-                 F5 =~ item46+ item45+ item25+ item4+ item1 
-                       a1==a2
-                       a3==a4"
-
-fit.Cor.1 <- cfa(LB.model.Cor.1, data = CFA.data, ordered = names(CFA.data),estimator = "WLSMV")
-
-## Summary of Model 
-cfa.sum.1 <- summary(fit.Cor.1, fit.measures =TRUE,standardized = TRUE,rsq =TRUE)
-
-## Selected Fit measures 
-fit.1 <- fitmeasures (fit.Cor.1,c("gfi", "agfi", "nfi","rfi", 
-                       "cfi.scaled","tli.scaled",
-                       "rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr"))
-
-reliability1 <- semTools::reliability(fit.Cor.1)
-
-```
-
-```{r mod1, include=FALSE}
-modfit.Cor.one <- modindices(fit.Cor.1, sort. = TRUE) 
-modfit.Cor.one[modfit.Cor.one$mi>3.84,]
-```
-
-```{r CFA23withMI, include=FALSE}
-LB.model.Cor.2 <- "F1 =~ a1*item16 + item36 + a2*item17
-                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
-                 F3 =~  item27+ item3+ item40 + item30 + item41
-                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
-                 F5 =~ item46+ item45+ item25+ item4+ item1 
-                       a1==a2
-                       a3==a4
-                item30 ~~  item41
-                       "
-
-#item26 & 37 are removed
-
-## Fit the model 
-fit.Cor.2 <- cfa(LB.model.Cor.2, data = CFA.data, ordered = names(CFA.data),estimator = "WLSMV")
-
-rel.k <- semTools::reliability(fit.Cor.2, return.total = T)
-## Summary of Model 
-cfa.sum.2 <- summary(fit.Cor.2, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
-
-## Selected Fit measures 
-fit.2 <- fitmeasures (fit.Cor.2,c("gfi", "agfi", "nfi","rfi", 
-                       "cfi.scaled","tli.scaled",
-                       "rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr"))
-
-```
-
-```{r mod2, include=FALSE}
-modfit.Cor.one <- modindices(fit.Cor.2, sort. = TRUE) 
-modfit.Cor.one[modfit.Cor.one$mi>3.84,]
-```
-
-We conducted a categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator as our response data was in ordinary nature [@desjardinsHandbookEducationalMeasurement2018a].
-Commonly used Model fit guidelines [@huCutoffCriteriaFit1999; @schumacker2004beginner] focused on (i) the comparative fit index (CFI;) (ii) the Tucker Lewis index (TLI) (CFI/TLI, $goodfit \geq .95$, $acceptable fit\geq .90$) (ii) the root mean square error of approximation (RMSEA; close to .06 or below), (iii) the standardized root mean square (SRMR; close to .08 or below) to estimate the model fit.
-The chi-square test is also used to estimate the absolute model fit.
-Table\@ref(tab:tabCfa) summarizes the fit indices of our fitted model.
-The fitted model failed to attain an absolute fit estimated by the chi-square test.
-However, the chi-square test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit [@brownConfirmatoryFactorAnalysis2015].
-The other absolute fit index we obtained in our analysis was SRMR which does not work well with categorical data [@RN1272].
-Subsequently, we judged the model fit based on the incremental fit indices: CFI, TLI and parsimony fit index-RMSEA.
-Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 and 19-17 .
-However SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`).
-Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR value (SRMR = `r apa(fit.2[10],2,F)`) was also close to the suggestions of @huCutoffCriteriaFit1999.
-The internal consistency reliability coefficients coefficient alpha `r apa(rel.k[5,1],2,F)`, `r apa(rel.k[5,2],2,F)`, `r apa(rel.k[5,3],2,F)`, `r apa(rel.k[5,4],2,F)`, `r apa(rel.k[5,5],2,F)` respectively indicating satisfactory reliability for F1, F2 and F4 [@najeracatalanReliabilityPopulationClassification2019]
-
-```{r cfaMat, results='asis'}
-CFa.matrix <- matrix("NA", nrow =2, ncol = 9)
-colnames(CFa.matrix) = c("Model", "Chi-Squre", "df", "CFI", "TLI", "RMSEA", "RMSEA 90% Lower CI", "RMSEA 90% Upper CI", "SRMR")
-CFa.matrix[1,] = c("Five factor model:25", 
-                   apa(cfa.sum.1$FIT[6],2,T), 
-                   apa(cfa.sum.1$FIT[7],2,T), 
-                   apa(cfa.sum.1$FIT[19],2,F), 
-                   apa(cfa.sum.1$FIT[20],2,T),
-                   apa(cfa.sum.1$FIT[27],2,T),
-                   apa(cfa.sum.1$FIT[28],2,T),
-                   apa(cfa.sum.1$FIT[29],2,T),
-                   apa(cfa.sum.1$FIT[35],2,T))
-
-CFa.matrix[2,] = c("Five factor model:23", 
-                   apa(cfa.sum.2$FIT[6],2,T), 
-                   apa(cfa.sum.2$FIT[7],2,T), 
-                   apa(cfa.sum.2$FIT[19],2,F), 
-                   apa(cfa.sum.2$FIT[20],2,T),
-                   apa(cfa.sum.2$FIT[27],2,T),
-                   apa(cfa.sum.2$FIT[28],2,T),
-                   apa(cfa.sum.2$FIT[29],2,T),
-                   apa(cfa.sum.2$FIT[35],2,T))
-```
-
-```{r tabCfa, results='asis'}
-apa_table(CFa.matrix, caption = "Fit indices of CFA", align = "c", landscape = T, note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index;RMSEA:Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square ")
-```
-
-```{r figcfa, fig.cap = "(A) Five Factor Model of LEBA", , out.width="100%",  warning=FALSE, results='asis'}
-#library(semPlot)
-
-semPaths (fit.Cor.2 , 
-          what= "std",
-          #whatLabels = "std",
-          intercepts = F,
-          #style ="lisrel",
-          #residScale = 6,
-          theme = "colorblind",
-          nCharNodes = 0,
-          reorder =T,
-          rotation =2,
-          layout ="tree",
-          cardinal = T,
-          curvePivot =T,
-          sizeMan =8,
-          sizeMan2 = 1.5,
-          sizeLat = 8,
-          #edge.color = "black",
-          thresholds = FALSE,
-          equalizeManifests =T,
-          fade = FALSE,
-          edge.label.cex = .65,
-          exoCov = FALSE)
-
-```
-
-```{r InvarianceAnalysis_data, include=FALSE}
-invariance.data <- cbind(CFA.data, data$slypos_demographics_language.factor[429:690])
-colnames(invariance.data)[52] <- "English_Speaking"
-
-invariance.data %>% 
-  group_by(English_Speaking) %>% 
-  count()
-```
-
-```{r Invariance detail, include=FALSE}
-# Configural invariance ####
-
-configural <- cfa(model = LB.model.Cor.2,
-                  data = invariance.data,
-                  group = "English_Speaking",
-                  ordered =   names(CFA.data),
-                  estimator = "WLSMV")
-
-summary(configural, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
-
-fitmeasures (configural,c("gfi", "agfi", "nfi","rfi", 
-                       "cfi.scaled","tli.scaled",
-                       "rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr"))
-
-weak <- cfa(model = LB.model.Cor.2,
-                  data = invariance.data,
-                  group = "English_Speaking",
-                  ordered =   names(CFA.data),
-                  estimator = "WLSMV", 
-            group.equal = "loadings")
-
-summary(weak, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
-
-fitmeasures (weak,c("gfi", "agfi", "nfi","rfi", 
-                       "cfi.scaled","tli.scaled",
-                       "rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr"))
-
-First.comp <- compareFit (configural, weak)
-summary(First.comp)
-
-strong <- cfa(model = LB.model.Cor.2,
-                  data = invariance.data,
-                  group = "English_Speaking",
-                  ordered =   names(CFA.data),
-                  estimator = "WLSMV", 
-              group.equal = c("loadings", "intercepts"))
-summary(strong, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
-
-Second.comp <- compareFit  (weak, strong)
-summary(Second.comp)
-
-strict <- cfa(model = LB.model.Cor.2,
-                  data = invariance.data,
-                  group = "English_Speaking",
-                  ordered =   names(CFA.data),
-                  estimator = "WLSMV",  
-              group.equal = c("loadings", "intercepts", "residuals"))
-
-summary(strict, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
-fitmeasures (strict,c("gfi", "agfi", "nfi","rfi", "cfi.robust","tli.robust","rmsea", "srmr","aic"))
-
-Third.comp <- compareFit(strict,strong)
-summary(Third.comp)
-
-structural <-cfa(model = LB.model.Cor.2,
-                  data = invariance.data,
-                  group = "English_Speaking",
-                  ordered =   names(CFA.data),
-                  estimator = "WLSMV",  
-                 group.equal = c("loadings", "intercepts", "residuals", "means","lv.variances","lv.covariances"))
-
-summary(structural, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
-fitmeasures (structural,c("gfi", "agfi", "nfi","rfi", "cfi","tli","rmsea", "srmr","aic"))
-
-fourth.comp <- compareFit  (structural,strict)
-summary(fourth.comp)
-comfit.par <- compareFit(configural, weak, strong, strict, structural)
-summary (comfit.par)
-
-models <-  list("Configural" = configural, 
-                "Metric" = weak, 
-                "Scalar" = strong, 
-                "Residual" = strict, 
-                "Structural"=structural)
-
-Invariance.table <- compareLavaan(models,
-              nesting = "Configural > Metric > Scalar > Residual  > Structural", 
-              fitmeas = c("chisq.scaled", "df",  "cfi.scaled","tli.scaled","rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr" ),
-              scaled = T,
-              chidif = T, digits = 2)
-
-colnames(Invariance.table) <- c("Chi-Square", "df", "CFI", "TLI", "RMSEA", "RMSEA 90% Lower CI", "RMSEA 90% Upper", "SRMR", "Chi-Sqr comparison", "df*", "p")
-
-```
-
-```{r InvarianceTab, results='asis'}
-apa_table(Invariance.table, align = "c",  caption = "Invariance Analysis", note = " a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual;* =  df of model comparison", landscape = T, font_size = "scriptsize" )
-
-```
-
-## Developing the short form of LEBA
-
-```{r IRT data, include=FALSE}
-## Recoding sem.data$item8 into sem.data$Ritem8
-sem.data$Ritem8 <- as.character(sem.data$item8)
-sem.data$Ritem8 <- fct_recode(sem.data$Ritem8,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-sem.data$Ritem8 <- as.numeric(as.character(sem.data$Ritem8))
-# Recoding sem.data$item26 
-sem.data$Ritem26 <- as.character(sem.data$item26)
-sem.data$Ritem26 <- fct_recode(sem.data$Ritem26,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-sem.data$Ritem26 <- as.numeric(as.character(sem.data$Ritem26))
-
-# Recoding sem.data$item37 i
-sem.data$Ritem37 <- as.character(sem.data$item37)
-sem.data$Ritem37 <- fct_recode(sem.data$Ritem37,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-sem.data$Ritem37 <- as.numeric(as.character(sem.data$Ritem37))
-
-F1 <- sem.data %>% 
-  dplyr::select(item16, item36,  item17)
-
-F2 <- sem.data %>% 
-  dplyr::select(item11,  item10 , item12, item7, Ritem8, item9)
-
-F3 <- sem.data %>% 
- dplyr::select(item27, item3,  item40,  item30,  item41)
-
-F4 <- sem.data %>% 
- dplyr::select(item32, item35,  item38,  item33)
-
-F5 <- sem.data %>% 
-  dplyr::select(item46, item45, item25, item4, item1 )
-
-## F1 IRT model####
-F1_fit <- mirt(F1, model = 1, itemtype = 'graded', 
-               SE = TRUE, Se.type = 'MHRM',
-               technical = list(NCYCLES = 10000))
-
-## F2 IRT model####
-F2_fit <- mirt(F2, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-## F3 IRT model####
-F3_fit <- mirt(F3, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-## F4 IRT model####
-F4_fit <- mirt(F4, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-## F5 IRT model####
-F5_fit <- mirt(F5, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-# Model Parameters ####
-## F1 Model Parameters####
-F1_params <- coef(F1_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
-F1_items <- data.frame(F1_params$items)
-F1l_se <- coef(F1_fit, printSE = TRUE)
-
-## F2 Model Parameters####
-F2_params <- coef(F2_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
-F2_items <- data.frame(F2_params$items)
-F2_se <- coef(F2_fit, printSE = TRUE)
-
-## F3 Model Parameters####
-F3_params <- coef(F3_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
-F3_items <- data.frame(F3_params$items)
-F3_se <- coef(F3_fit, printSE = TRUE)
-
-## F4 Model Parameters####
-F4_params <- coef(F4_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
-F4_items <- data.frame(F4_params$items)
-F4_se <- coef(F4_fit, printSE = TRUE)
-
-## F5 Model Parameters####
-F5_params <- coef(F5_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
-F5_items <- data.frame(F5_params$items)
-F5_se <- coef(F5_fit, printSE = TRUE)
-
-itemparameters <- rbind(F1_items,F2_items, F3_items, F4_items,F5_items)
-
-# Person Fit ####
-## F1 Person fit ####
-F1.personfit <- personfit(F1_fit) 
-F1.personfit_model_misfits <- subset(F1.personfit, Zh < -2)
-rownames(F1.personfit_model_misfits)
-nrow(F1.personfit_model_misfits)
-hist(F1.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-
-## F2 Person fit ####
-F2.personfit <- personfit(F2_fit) 
-F2.personfit_model_misfits <- subset(F2.personfit, Zh < -2)
-rownames(F2.personfit_model_misfits)
-nrow(F2.personfit_model_misfits)
-hist(F2.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-
-## F3 Person fit ####
-F3.personfit <- personfit(F3_fit) 
-F3.personfit_model_misfits <- subset(F3.personfit, Zh < -2)
-rownames(F3.personfit_model_misfits)
-nrow(F3.personfit_model_misfits)
-hist(F3.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-
-## F4 Person fit ####
-F4.personfit <- personfit(F4_fit) 
-F4.personfit_model_misfits <- subset(F4.personfit, Zh < -2)
-rownames(F4.personfit_model_misfits)
-nrow(F4.personfit_model_misfits)
-hist(F4.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-
-## F5 Person fit ####
-F5.personfit <- personfit(F5_fit) 
-F5.personfit_model_misfits <- subset(F5.personfit, Zh < -2)
-rownames(F3.personfit_model_misfits)
-nrow(F5.personfit_model_misfits)
-hist(F5.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-
-# Plots ####
-## F1 Plots ####
-F1_OCC <- plot(F1_fit, type = "trace", facet =T, main = "Blue Filter OCC")
-F1_info <- plot(F1_fit, type = "infoSE", main = "F1")
-F1_iteminfo <- plot(F1_fit, type = "infotrace", 
-                    facet_items = T, main = "F1")
-
-## F2 Plots ####
-F2_OCC <- plot(F2_fit, type = "trace", facet =T, main = "Natural Light OCC")
-F2_info <- plot(F2_fit, type = "infoSE", main = "F2")
-F2_iteminfo <- plot(F2_fit, type = "infotrace", facet_items = T, main = "F2")
-
-## F3 Plots ####
-F3_OCC <-plot(F3_fit, type = "trace", facet =T, main = "Smart Device OCC")
-F3_info <- plot(F3_fit, type = "infoSE", main = "F3")
-F3_iteminfo <- plot(F3_fit, type = "infotrace", 
-                    facet_items = T, main = "F3")
-
-## F4 Plots ####
-F4_OCC <-plot(F4_fit, type = "trace", facet =T, main = "Sleep Environment OCC")
-F4_info <- plot(F4_fit, type = "infoSE", main = "F4")
-F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = "F4")
-
-## F5 Plots ####
-F5_OCC <-plot(F5_fit, type = "trace", facet =T, main = "Electric Light OCC")
-F5_info <- plot(F5_fit, type = "infoSE", main = "F5")
-F5_iteminfo <- plot(F5_fit, type = "infotrace", facet_items = T,main = "F5")
-
-## Plot grid ####
-library(cowplot)
-OCC <- plot_grid(F1_OCC, F2_OCC,F3_OCC,F4_OCC,F5_OCC, 
-          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)
-
-Test_Info <- plot_grid(F1_info, F2_info,F3_info,F4_info,F5_info, 
-          labels = "AUTO", label_size = 10)
-
-Item_Information <- plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
-          labels = "AUTO", label_size = 10)
-
-```
-
-To develop a shorter form of the LEBA we sought to Item response theory.IRT complements the conventional classical test theory-based analysis by gathering information on item discrimination and item difficulty[@bakerBasicsItemResponse2017].
-Here, an item's quality is judged based on item information in relation to participants' latent trait level ($\theta$).
-We gathered evidence on item quality by fitting each factor of LEBA with the graded response model to the combined EFA sample and CFA sample (n =690)(\@ref(tab:IRTparameters).
-Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait, and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
-Currently, apart from some general suggestions, there exists no definitive rule to judge the item discrimination and item information parameter quality.
-Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information \<.2) to develop the short form of LEBA.
-@bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70.
-Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), low ( 5 items) indicating a good range of discrimination along the latent trait.
-Examination of the item information curve indicated 6 items (1, 25, 9, 38, 30, & 41) had relatively flat information curves thus discarded.
-
-```{r IRTparameters, results='asis'}
-apa_table(itemparameters, caption = "IRT Item parameters for the LEBA Scale", note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
-```
-
-```{r itmeinfo, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
-plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
-          labels = "AUTO", label_size = 10,align = "v" )
-
-```
-
-```{r shortIRT, include=FALSE}
-F1 <- sem.data %>% 
-  dplyr::select(item16, item36,  item17)
-F2.redu <- sem.data %>% 
-  dplyr::select(item11,  item10 , item12, item7, Ritem8)
-F3.redu <- sem.data %>% 
- dplyr::select(item27, item3,  item40)
-
-F4.redu <- sem.data %>% 
- dplyr::select(item32, item35,  item33)
-
-F5 <- sem.data %>% 
-  dplyr::select(item46, item45, item25 )
-
-F1_fit <- mirt(F1, model = 1, itemtype = 'graded', 
-               SE = TRUE, Se.type = 'MHRM',
-               technical = list(NCYCLES = 10000))
-
-F2_fit.redu <- mirt(F2.redu, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-F3_fit.redu <- mirt(F3.redu, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-F4_fit.redu <- mirt(F4.redu, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-F5_fit <- mirt(F5, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-# Plots2 ####
-
-F1_test.info <- plot(F1_fit, type = "infoSE", main = "F1")
-
-F2_test.info.redu <- plot(F2_fit.redu, type = "infoSE", main = "F2")
-
-F3_test.info.redu <- plot(F3_fit.redu, type = "infoSE", main = "F3")
-
-F4_test.info.redu <- plot(F4_fit.redu, type = "infoSE", main = "F4")
-
-F5_test.info <- plot(F5_fit, type = "infoSE", main = "F5")
-
-```
-
-Test information curve (TIC) indicate the amount of information an the full-scale carry along the latent trait continuum.
-As we treated each factor of LEBA as an unidmensional construct we obtain 5 TICs ().
-These information curves indicated except Blue filter factor, the other factor's curve is roughly centered on the center of the trait continuum (($\theta$)) and the The amount of information changed rather steadily with the change of ($\theta$).
-Thus we conferred the LEBA scale (except blue filter) estimated the light exposure related behavior with precision near the center of trait continuum [@bakerBasicsItemResponse2017] which is sufficient to discriminate between latent trait measured by the each factor.
-The blue filter factor had a peak to the right side of the center of latent trait indicating its ability to providing information only for people who already have some preference towards using blue-filters.
-
-```{r Testinfo, fig.cap="Test information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
-plot_grid(F1_test.info, F2_test.info.redu,F3_test.info.redu,F4_test.info.redu,F5_test.info, 
-          labels = "AUTO", label_size = 10, align = "v" )
-
-```
-
-```{r fscore, include=FALSE}
-LEBA.Total <- sem.data %>% 
-  rowwise() %>% 
-  mutate(F1.Total = sum(item16, item36,  item17))
-
-LEBA.Total <- LEBA.Total %>% 
-  rowwise() %>% 
-  mutate(F2.Total = sum(item11,  item10 , item12, item7, Ritem8))
-
-LEBA.Total <- LEBA.Total %>% 
-  rowwise() %>% 
-  mutate(F3.Total = sum(item27, item3,  item40))
-
-LEBA.Total <- LEBA.Total %>% 
-  rowwise() %>% 
-  mutate(F4.Total = sum(item32, item35,  item33))
-
-LEBA.Total <- LEBA.Total %>% 
-  rowwise() %>% 
-  mutate(F5.Total = sum(item46, item45, item25))
-
-F1.estimation <- as.vector(fscores(F1_fit, method = "EAP",
-                                           full.scores = TRUE, 
-                                           full.scores.SE = F))
-
-F2.estimation <- as.vector(fscores(F2_fit.redu, method = "EAP",
-                                           full.scores = TRUE, 
-                                           full.scores.SE = F))
-
-F3.estimation <- as.vector(fscores(F3_fit.redu, method = "EAP",
-                                           full.scores = TRUE, 
-                                           full.scores.SE = F))
-
-F4.estimation <- as.vector(fscores(F4_fit.redu, method = "EAP",
-                                           full.scores = TRUE, 
-                                           full.scores.SE = F))
-
-F5.estimation <- as.vector(fscores(F5_fit, method = "EAP",
-                                           full.scores = TRUE, 
-                                           full.scores.SE = F))
-
-Ability.F1 <- data.frame(Rawscore = LEBA.Total$F1.Total,
-                      Theta =  F1.estimation)
-
-Ability.F2 <- data.frame(Rawscore = LEBA.Total$F2.Total,
-                      Theta =  F2.estimation)
-
-Ability.F3 <- data.frame(Rawscore = LEBA.Total$F3.Total,
-                      Theta =  F3.estimation)
-
-Ability.F4 <- data.frame(Rawscore = LEBA.Total$F3.Total,
-                      Theta =  F3.estimation)
-
-Ability.F5 <- data.frame(Rawscore = LEBA.Total$F3.Total,
-                      Theta =  F3.estimation)
-
-ggplot(Ability.F1, aes(x =Theta, y =Rawscore)) +
-  geom_point() +
-  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
-  xlim(-2,2) +
-  ylim(0,15)
-
-ggplot(Ability.F2, aes(x =Theta, y =Rawscore)) +
-  geom_point() +
-  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
-  xlim(-2,2) +
-  ylim(0,15)
-
-ggplot(Ability.F3, aes(x =Theta, y =Rawscore)) +
-  geom_point() +
-  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
-  xlim(-2,2) +
-  ylim(0,15)
-
-ggplot(Ability.F4, aes(x =Theta, y =Rawscore)) +
-  geom_point() +
-  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
-  xlim(-2,2) +
-  ylim(0,15)
-
-ggplot(Ability.F5, aes(x =Theta, y =Rawscore)) +
-  geom_point() +
-  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
-  xlim(-2,2) +
-  ylim(0,15)
-
-Score.correation <- cbind(Ability.F1,Ability.F2, Ability.F3, Ability.F4, Ability.F5)
-colnames(Score.correation) <- c("F1.Raw", "F1.Estimated","F2.Raw", "F2.Estimated","F3.Raw", "F3.Estimated","F4.Raw", "F4.Estimated","F5.Raw", "F5.Estimated")
-
-F1.cor <- corr.test(Score.correation$F1.Raw, Score.correation$F1.Estimated)
-
-F2.cor <- corr.test(Score.correation$F2.Raw, Score.correation$F2.Estimated)
-
-F3.cor <- corr.test(Score.correation$F3.Raw, Score.correation$F3.Estimated)
-
-F4.cor <- corr.test(Score.correation$F4.Raw, Score.correation$F4.Estimated)
-
-F5.cor <- corr.test(Score.correation$F5.Raw, Score.correation$F5.Estimated)
-
-#Putting significance star for correlation
-F1.p <-F1.cor$p
-F1.stars <- ifelse(F1.p < .001, "***"
-                   , ifelse(p < .01, "**"
-                            , ifelse(p < .05, "*"
-                                     , ifelse(p < .10, "+", " "))))
-
-F2.p <-F2.cor$p
-F2.stars <- ifelse(F2.p < .001, "**"
-                   , ifelse(p < .01, "**"
-                            , ifelse(p < .05, "*"
-                                     , ifelse(p < .10, "+", " "))))
-
-F3.p <-F3.cor$p
-F3.stars <- ifelse(F3.p < .001, "***"
-                   , ifelse(p < .01, "**"
-                            , ifelse(p < .05, "*"
-                                     , ifelse(p < .10, "+", " "))))
-
-F4.p <-F4.cor$p
-F4.stars <- ifelse(F4.p < .001, "***"
-                   , ifelse(p < .01, "**"
-                            , ifelse(p < .05, "*"
-                                     , ifelse(p < .10, "+", " "))))
-
-F5.p <-F5.cor$p
-F5.stars <- ifelse(F5.p < .001, "***"
-                   , ifelse(p < .01, "**"
-                            , ifelse(p < .05, "*"
-                                     , ifelse(p < .10, "+", " "))))
-
-theta.correlation.matrix <- matrix("NA", nrow =1, ncol = 5)
-
-theta.correlation.matrix[1,1] <- paste(apa(F1.cor$r,2,F), F1.stars,sep="")
-theta.correlation.matrix[1,2] <- paste(apa(F2.cor$r,2,F), F2.stars,sep="")
-theta.correlation.matrix[1,3] <- paste(apa(F3.cor$r,2,F), F3.stars,sep="")
-theta.correlation.matrix[1,4] <- paste(apa(F4.cor$r,2,F), F4.stars,sep="")
-theta.correlation.matrix[1,5] <- paste(apa(F5.cor$r,2,F), F5.stars,sep="")
-
-as.data.frame(theta.correlation.matrix)
-colnames(theta.correlation.matrix) <- c("F1", "F2", "F3", "F4", "F5")
-```
-
-```{r, results='asis'}
-apa_table (theta.correlation.matrix, caption = "correlation coefficents of obtained scores and estimated latent trait for each factots", note = "* p < 0.05; ** p < 0.01; *** p < 0.001"  )
-```
-
-# Discussion
-
-\newpage
-
-# References
-
-```{=tex}
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-```
-::: {#refs custom-style="Bibliography"}
-:::
-
-\endgroup

### 2021-10-22 instrument.tex
Appendices

--- 2021-09-15 instrument.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-%
-\documentclass[
-  english,
-  man,floatsintext]{apa6}
-\usepackage{amsmath,amssymb}
-\usepackage{lmodern}
-\usepackage{iftex}
-\ifPDFTeX
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-  \setmainfont[]{Helvetica}
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
+\clearpage
 \makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
+\efloat@restorefloats
 \makeatother
-\usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Light Exposure Behavior Assessment (LEBA): Long and Short Form},
-  pdfauthor={Mushfiqul Anwar Siraji*, Rafael Robert Lazar*, Juliëtte van Duijnhoven, Luc Schlangen, Shamsul Haque, Vineetha Kalavally, Céline Vetter, Gena Glickman, Karin Smolders, \& Manuel Spitschan**},
-  pdflang={en-EN},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-% Make \paragraph and \subparagraph free-standing
-\ifx\paragraph\undefined\else
-  \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-  \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-% Manuscript styling
-\usepackage{upgreek}
-\captionsetup{font=singlespacing,justification=justified}
 
-% Table formatting
-\usepackage{longtable}
-\usepackage{lscape}
-% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
-\usepackage{multirow}		% Table styling
-\usepackage{tabularx}		% Control Column width
-\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
-\usepackage{threeparttablex}            % Lets threeparttable work with longtable
+\begin{appendix}
+\section{}
+\textbf{Disclaimer}: This is a non-public version of LEBA (dated \today)
+and still a work in progress. Please do not distribute!
 
-% Create new environments so endfloat can handle them
-% \newenvironment{ltable}
-%   {\begin{landscape}\centering\begin{threeparttable}}
-%   {\end{threeparttable}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
-
-% Enables adjusting longtable caption width to table width
-% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
-\makeatletter
-\newcommand\LastLTentrywidth{1em}
-\newlength\longtablewidth
-\setlength{\longtablewidth}{1in}
-\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
-
-% \setlength{\parindent}{0.5in}
-% \setlength{\parskip}{0pt plus 0pt minus 0pt}
-
-% \usepackage{etoolbox}
-\makeatletter
-\patchcmd{\HyOrg@maketitle}
-  {\section{\normalfont\normalsize\abstractname}}
-  {\section*{\normalfont\normalsize\abstractname}}
-  {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\HyOrg@maketitle}
-  {\section{\protect\normalfont{\@title}}}
-  {\section*{\protect\normalfont{\@title}}}
-  {}{\typeout{Failed to patch title.}}
-\makeatother
-\shorttitle{LEBA}
-\usepackage{csquotes}
-\ifXeTeX
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-
-\title{\emph{Light Exposure Behavior Assessment (LEBA)}: Long and Short Form}
-\author{Mushfiqul Anwar Siraji\textsuperscript{*}, Rafael Robert Lazar\textsuperscript{*}, Juliëtte van Duijnhoven\textsuperscript{}, Luc Schlangen\textsuperscript{}, Shamsul Haque\textsuperscript{}, Vineetha Kalavally\textsuperscript{}, Céline Vetter\textsuperscript{}, Gena Glickman\textsuperscript{}, Karin Smolders\textsuperscript{}, \& Manuel Spitschan\textsuperscript{**}}
-\date{}
-
-\affiliation{\vspace{0.5cm}\textsuperscript{*} Joint first authors\\\textsuperscript{**} Corresponding author: \href{mailto:manuel.spitschan@psy.ox.ac.uk}{\nolinkurl{manuel.spitschan@psy.ox.ac.uk}}}
-
-\begin{document}
-\maketitle
-
-\textbf{Disclaimer}: This is a non-public version of LEBA (dated \today) and still a work in progress. Please do not distribute!
-
-LEBA captures light exposure-related behaviours on a 5 point Likert type scale ranging from 1 to 5 (Never/Does not apply/I don't know = 1; Rarely = 2; Sometimes = 3; Often = 4; Always = 5).
-The score of each factor is calculated by the summation of scores of items belonging to the corresponding factor.
+LEBA captures light exposure-related behaviours on a 5 point Likert type
+scale ranging from 1 to 5 (Never/Does not apply/I don't know = 1; Rarely
+= 2; Sometimes = 3; Often = 4; Always = 5). The score of each factor is
+calculated by the summation of scores of items belonging to the
+corresponding factor.
 
@@
 \endhead
-\textbf{F1: Blue Filter} \\
-I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day. \\
-I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day. \\
-I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1 hour before attempting to fall asleep. \\
-\textbf{F2: Natural Light} \\
+\textbf{F1: Wearing blue light filters} \\
+I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors
+during the day. \\
+I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors
+during the day. \\
+I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1
+hour before attempting to fall asleep. \\
+\textbf{F2: Spending time outdoors} \\
 I spend 30 minutes or less per day (in total) outside. \\
@@
 I go for a walk or exercise outside within 2 hours after waking up. \\
-\textbf{F3: Smart Device} \\
+\textbf{F3: Using phone and smartwatch in bed} \\
 I use my mobile phone within 1 hour before attempting to fall asleep. \\
@@
 I check my phone when I wake up at night. \\
-I look at my smartwatch within 1 hour before attempting to fall asleep. \\
+I look at my smartwatch within 1 hour before attempting to fall
+asleep. \\
 I look at my smartwatch when I wake up at night. \\
-\textbf{F4: Sleep Environment} \\
-I dim my mobile phone screen within 1 hour before attempting to fall asleep. \\
-I use a blue-filter app on my computer screen within 1 hour before attempting to fall asleep. \\
+\textbf{F4: Using light before bedtime} \\
+I dim my mobile phone screen within 1 hour before attempting to fall
+asleep. \\
+I use a blue-filter app on my computer screen within 1 hour before
+attempting to fall asleep. \\
 I use as little light as possible when I get up during the night. \\
-I dim my computer screen within 1 hour before attempting to fall asleep. \\
-\textbf{F5: Electric Light} \\
+I dim my computer screen within 1 hour before attempting to fall
+asleep. \\
+\textbf{F5: Using light in the morning and during daytime} \\
 I use tunable lights to create a healthy light environment. \\
@@
 I check my phone when I wake up at night. \\
-\textbf{F4: Sleep Environment} \\
-I dim my mobile phone screen within 1 hour before attempting to fall asleep. \\
-I use a blue-filter app on my computer screen within 1 hour before attempting to fall asleep. \\
-I dim my computer screen within 1 hour before attempting to fall asleep. \\
-\textbf{F5: Electric Light} \\
+\textbf{F4: Using light before bedtime} \\
+I dim my mobile phone screen within 1 hour before attempting to fall
+asleep. \\
+I use a blue-filter app on my computer screen within 1 hour before
+attempting to fall asleep. \\
+I dim my computer screen within 1 hour before attempting to fall
+asleep. \\
+\textbf{F5: Using light in the morning and during daytime} \\
 I use tunable lights to create a healthy light environment. \\
@@
 \end{longtable}
-
-\end{document}
+\end{appendix}

### 2021-10-22 manuscript.Rmd
Appendices

--- 2021-10-17 manuscript.Rmd
@@
       - Writing – original draft
+      - Writing – review & editing;
 
@@
     latex_engine: xelatex
+
 mainfont: Helvetica
+appendix:
+  - "instrument.Rmd"
+  - "Appendix-B.Rmd"
+
 ---
@@
 | Name                                            | Authors                     | Description                                                                            | Relevant Items | Adaptations |
+
++=================================================+=============================+========================================================================================+:==============:+=============+
+| Visual Light Sensitivity Questionnaire-8        | [@verriotto2017new]        | Eight-question survey to assess the presence and severity of photosensitivity symptoms | all            | jhghjgjhgfd |
++-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
+| Office Light Survey                             | [@eklund1996development]   | Multi-item questionnaire to assess electrical lighting environment in office           | aa             | gh          |
++-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
+| Harvard Light Exposure Assessment Questionnaire | [@bajaj2011validation]     | Self-administered semiquantitative light qestionnaire                                  | aa             | as          |
++-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
+| Hospital Lighting Survey                        | [@dianat2013objective]     | 23 items questionnaire to assess light environment in a hospital                       | dd             | fg          |
++-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
+| Morningness-Eveningness Questionnaire           | [@horne1976self]           | 19 items questionnaire to understand your body clock                                   | ff             | hj          |
++-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
+| Munich Chronotype Questionnaire (MCTQ)          | [@roenneberg2003life]      | 17 items questionnaire to understand individuals phase of entrainment                  | ff             | jk          |
++-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
+| Assessment of Sleep Environment                 | [@grandner2014development] | 13 items questionnaire measuring your sleep environment quality                        | ff             | kl          |
++-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
+| The Pittsburgh Sleep Quality Index (PSQI)       | [@buysse1989pittsburgh]    | 9 items inventory to measure sleep quality and sleeping pattern                        | ff             | klfrgfgvfg  |
++-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
+=======
 |-------------------------------------------------|-----------------------------|----------------------------------------------------------------------------------------|:--------------:|-------------|
@@
 | The Pittsburgh Sleep Quality Index (PSQI)       | [\@buysse1989pittsburgh]    | 9 items inventory to measure sleep quality and sleeping pattern                        |       ff       | klfrgfgvfg  |
-|                                                 |                             |                                                                                        |                |             |
-|                                                 |                             |                                                                                        |                |             |
 
@@
 
+# Model Fit (degrees of freedom too low to check model fit)
+#F1.model <- M2(F1_fit)
+#F2.model <- M2(F2_fit)
+#F3.model <- M2(F3_fit)
+#F4.model <- M2(F4_fit)
+#F5.model <- M2(F5_fit)
+
+#Item fit
+F1.item.fit<- itemfit(F1_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
+                                  impute=10)
+
+F2.item.fit<- itemfit(F2_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
+                                  impute=10)
+F3.item.fit<- itemfit(F3_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
+                                  impute=10)
+F4.item.fit<- itemfit(F4_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
+                                  impute=10)
+
+F5.item.fit<- itemfit(F5_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
+                                  impute=10)
+
+#Identigying Missfit items based on RMSEA Value
+F1.item_misfits <- subset(F1.item.fit, RMSEA.S_X2 >= .06)
+F2.item_misfits <- subset(F2.item.fit, RMSEA.S_X2 >= .06)
+F3.item_misfits <- subset(F3.item.fit, RMSEA.S_X2 >= .06)
+F4.item_misfits <- subset(F4.item.fit, RMSEA.S_X2 >= .06)
+F5.item_misfits <- subset(F5.item.fit, RMSEA.S_X2 >= .06)
+
 # Person Fit ####
@@
 F4_info <- plot(F4_fit, type = "infoSE", main = "F4")
-F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = "Sleep Environment")
+F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = "F4",cex = .8)
 
@@
 Test_Info <- plot_grid(F1_info, F2_info,F3_info,F4_info,F5_info, 
-          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)
+          labels = "AUTO", label_size = 10)
 
 Item_Information <- plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
-          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)
-
+          labels = "AUTO", label_size = 10)
+
+```
+
+```{r IRTreliability, include=F}
+#conditional reliability
+F1.reliability <- plot(F1_fit, type = 'rxx', theta_lim = c(-6, 6), 
+      main="" )
+F2.reliability <- plot(F2_fit, type = 'rxx', theta_lim = c(-6, 6), 
+      main="" )
+F3.reliability <- plot(F3_fit, type = 'rxx', theta_lim = c(-6, 6), 
+      main="" )
+F4.reliability <- plot(F4_fit, type = 'rxx', theta_lim = c(-6, 6), 
+      main="" )
+F5.reliability <- plot(F5_fit, type = 'rxx', theta_lim = c(-6, 6), 
+      main="" )
+
+##IRT reliability (marginal reliability of scales)
+F1.marginal.rel <- marginal_rxx(F1_fit)
+F2.marginal.rel <-marginal_rxx(F2_fit)
+F3.marginal.rel <-marginal_rxx(F3_fit)
+F4.marginal.rel <-marginal_rxx(F4_fit)
+F5.marginal.rel <-marginal_rxx(F5_fit)
+
+##Scale characteristic curve
+F1.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
+F2.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
+F3.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
+F4.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
+F5.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
 ```
@@
 
+```{r itmeinfo, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
+plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
+          labels = "AUTO", label_size = 10,align = "v")
+
+```
+
 ```{r shortIRT, include=FALSE}
@@
 
-```{r, results='asis'}
+```{r IRTscoreCor, results='asis'}
 apa_table (theta.correlation.matrix, caption = "correlation coefficents of obtained scores and estimated latent trait for each factots", note = "* p < 0.05; ** p < 0.01; *** p < 0.001"  )

### 2021-10-23 manuscript.Rmd
CFI reference updates

@@
 We conducted a categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator as our response data was in ordinary nature [@desjardinsHandbookEducationalMeasurement2018a].
-Commonly used Model fit guidelines [@huCutoffCriteriaFit1999; @schumacker2004beginner] focused on (i) the comparative fit index (CFI;) (ii) the Tucker Lewis index (TLI) (CFI/TLI, $goodfit \geq .95$, $acceptable fit\geq .90$) (ii) the root mean square error of approximation (RMSEA; close to .06 or below), (iii) the standardized root mean square (SRMR; close to .08 or below) to estimate the model fit.
-The chi-square test is also used to estimate the absolute model fit.
+Several indices exist to measure the the model fit.
+These can be categorized as absolute fit, comparative fit and parsimony fit indices [@brownConfirmatoryFactorAnalysis2015].
+Absolute fit assess the model fit at an absolute level using indices including chi-square test statistics and the standardized root mean square (SRMR).parsimony  fit indices including the root mean square error of approximation (RMSEA)  considers the number of free parameters in the model to assess the parsimony of the model.
+Comparative fit indices  evaluate the fit of the specified model solution in relation to a more restricted baseline model restricting all covariances among the idicators as zero.
+Comparative fit index (CFI) and the Tucker Lewis index (TLI) are such two comparative fit indices.
+Commonly used Model fit guidelines [@huCutoffCriteriaFit1999; @schumacker2004beginner] includes (i) Reporting of chi-square test statistics (A non-significant test statistics is required to reflect model fit) (i) CFI and  TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (ii) RMSEA (close to .06 or below), (iii) SRMR (close to .08 or below) to estimate the model fit.
 Table\@ref(tab:tabCfa) summarizes the fit indices of our fitted model.
@@
 However, the chi-square test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit [@brownConfirmatoryFactorAnalysis2015].
-The other absolute fit index we obtained in our analysis was SRMR which does not work well with categorical data [@RN1272].
-Subsequently, we judged the model fit based on the incremental fit indices: CFI, TLI and parsimony fit index-RMSEA.
+Another absolute fit index we obtained in our analysis was SRMR which does not work well with categorical data [@RN1272].
+Subsequently, we judged the model fit based on the comparative fit indices: CFI, TLI and parsimony fit index-RMSEA.
 Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 and 19-17 .

### 2021-10-23 manuscript.Rmd
simsem

@@
 library(kutils)
+library(simsem)
 r_refs("references.bib")
@@
 
+```{r simulation, eval=FALSE, include=FALSE}
+library("simsem")
+pop.model <- "F1 =~ a1*item16 + .95*item36 + a2*item17
+                 F2 =~ .87*item11 + .85*item10 + .74*item12+ .60*item7+ .50*Ritem8+ .49*item9
+                 F3 =~  .78*item27+ .77*item3+ .68*item40 + .13*item30 + .20*item41
+                 F4 =~ a3*item32 + .63*item35 + .33*item38+ a4*item33 
+                 F5 =~ .80*item46+ .53*item45+ .36*item25+ .30*item4+ .22*item1 
+                       a1==a2
+                       a3==a4
+                item30 ~~ .82*item41
+F1~~1*F1
+F2~~1*F2
+F3~~1*F3
+F4~~1*F4
+F5~~1*F5
+"
+
+sam.model <- "F1 =~ a1*item16 + item36 + a2*item17
+                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
+                 F3 =~  item27+ item3+ item40 + item30 + item41
+                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
+                 F5 =~ item46+ item45+ item25+ item4+ item1 
+                       a1==a2
+                       a3==a4
+                item30 ~~  item41
+                       "
+
+sim.300 <- sim(200, model = sam.model, n =200, generate = pop.model, lavaanfun = "lavaan", auto.var =T, auto.fix.first =F, seed = 123)
+summary(simulation)
+summaryParam(simulation, detail =T, alpha = .05)
+
+#power should be higher than .80, average CI width should be lower than .15
+#Estimate standard error bias
+
+SD.Bias <- (summaryParam(simulation)[3]-summaryParam(simulation)[2])/summaryParam(simulation)[3]
+```
+
 ```{r figcfa, fig.cap = "(A) Five Factor Model of LEBA", , out.width="100%",  warning=FALSE, results='asis'}
@@
 
+```{r clean}
+cleanFolder <- function() {
+  answer <- NA
+  while(!(answer %in% c('y', 'n'))) {
+    answer <- readline(paste("Clean ", getwd(),"? (y/n)"))
+  }
+  if(answer == 'y') {
+    rules <- c('.log', '.vrb', '.nav', '.snm', '.toc', 
+               '-tikzDictionary', '.tex', '.synctex.gz')
+    file.remove(list.files(pattern = paste0('\\',rules ,'$', collapse = '|')))
+  }
+}
+```
+
 # Discussion

### 2021-10-29 Appendix-B.tex
* Instrument description and Other LaTeX issues. Instrument is now in landscape mood.

\clearpage
\makeatletter
\efloat@restorefloats
\makeatother

\begin{appendix}
\section{}
\begin{table}[h]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:AtabDes}Descriptive Statistics for Unmerged response options}

\begin{tabular}{ccccccc}
\toprule
 & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{Item-Total Correlation}\\
\midrule
Item1 & 2.16 & 1.51 & 0.49 & -0.86 & 0.90* & .21\\
Item2 & 2.76 & 1.75 & -0.10 & -1.42 & 0.88* & .20\\
Item3 & 3.34 & 1.43 & -0.58 & -0.77 & 0.88* & .18\\
Item4 & 1.30 & 1.31 & 1.93 & 2.92 & 0.62* & .32\\
Item5 & 3.95 & 1.56 & -1.42 & 0.75 & 0.70* & .19\\
Item6 & 2.70 & 1.66 & 0.02 & -1.33 & 0.90* & .18\\
Item7 & 2.23 & 1.28 & 0.60 & -0.59 & 0.89* & .18\\
Item8 & 2.95 & 1.24 & -0.19 & -0.70 & 0.93* & -.07\\
Item9 & 2.92 & 1.09 & -0.37 & 0.11 & 0.91* & .14\\
Item10 & 2.73 & 1.07 & -0.03 & -0.52 & 0.92* & .27\\
Item11 & 2.17 & 0.93 & 0.44 & 0.20 & 0.89* & .25\\
Item12 & 2.34 & 1.26 & 0.46 & -0.58 & 0.91* & .24\\
Item13 & 2.71 & 1.49 & 0.14 & -1.29 & 0.89* & .28\\
Item14 & 2.11 & 1.34 & 0.68 & -0.78 & 0.84* & .24\\
Item15 & 3.26 & 1.11 & -0.34 & -0.21 & 0.91* & .11\\
Item16 & 1.46 & 1.31 & 1.71 & 1.90 & 0.65* & .33\\
Item17 & 1.43 & 1.30 & 1.76 & 2.12 & 0.64* & .30\\
Item18 & 0.92 & 0.67 & 2.00 & 9.41 & 0.62* & .32\\
Item19 & 0.85 & 0.56 & 1.71 & 10.74 & 0.55* & .34\\
Item20 & 0.83 & 0.54 & 1.76 & 13.92 & 0.53* & .31\\
Item21 & 0.94 & 0.75 & 2.46 & 10.66 & 0.58* & .27\\
Item22 & 3.57 & 1.08 & -0.72 & 0.08 & 0.88* & .19\\
Item23 & 2.53 & 1.31 & 0.22 & -0.91 & 0.92* & .11\\
Item24 & 4.13 & 1.01 & -1.39 & 2.01 & 0.78* & .19\\
Item25 & 2.57 & 1.43 & 0.22 & -1.23 & 0.88* & .17\\
Item26 & 2.23 & 1.30 & 0.59 & -0.63 & 0.88* & .16\\
Item27 & 3.78 & 1.34 & -1.01 & 0.08 & 0.82* & .18\\
Item28 & 3.75 & 1.16 & -0.78 & -0.10 & 0.86* & .01\\
Item29 & 2.38 & 1.40 & 0.20 & -1.04 & 0.92* & .11\\
Item30 & 0.94 & 1.42 & 1.66 & 1.69 & 0.68* & .24\\
Item31 & 2.91 & 1.76 & -0.24 & -1.41 & 0.87* & .45\\
Item32 & 3.49 & 1.76 & -0.71 & -1.06 & 0.78* & .43\\
Item33 & 3.56 & 1.75 & -0.79 & -0.95 & 0.77* & .32\\
Item34 & 3.30 & 2.00 & -0.54 & -1.50 & 0.74* & .34\\
Item35 & 3.80 & 1.79 & -1.07 & -0.59 & 0.67* & .24\\
Item36 & 1.36 & 1.38 & 1.75 & 2.05 & 0.65* & .38\\
Item37 & 1.30 & 0.94 & 2.79 & 7.65 & 0.48* & -.01\\
Item38 & 4.27 & 1.18 & -2.07 & 4.01 & 0.65* & .23\\
Item39 & 1.94 & 1.01 & 0.85 & 0.61 & 0.86* & .05\\
Item40 & 2.13 & 1.24 & 0.56 & -0.54 & 0.89* & .16\\
Item41 & 0.87 & 1.08 & 1.68 & 2.74 & 0.73* & .21\\
Item42 & 3.90 & 1.55 & -1.15 & -0.12 & 0.72* & .17\\
Item43 & 1.59 & 1.23 & 1.59 & 1.70 & 0.69* & .22\\
Item44 & 3.46 & 1.41 & -0.92 & -0.01 & 0.86* & .38\\
Item45 & 2.04 & 1.66 & 0.46 & -1.12 & 0.87* & .29\\
Item46 & 1.57 & 1.40 & 0.97 & -0.07 & 0.82* & .38\\
Item47 & 2.07 & 1.23 & 0.59 & -0.42 & 0.89* & .34\\
Item48 & 2.57 & 1.30 & 0.14 & -0.74 & 0.93* & .31\\
\bottomrule
\addlinespace
\end{tabular}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} *p<.001}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\begin{figure}

{\centering \includegraphics[width=1\linewidth,height=2\textheight]{manuscript_files/figure-latex/AfacIdFig-1}

}

\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}(\#fig:AfacIdFig)
\end{figure}

Horn's parallel analysis with 500 iterations indicated a five-factor
solution. However, Scree plot and the MAP method suggested 6-factor
solution. five-factor solution (Figure@ref:AfacIdFig). As a result, we
tested both five-factor and six-factor solutions.

\begin{table}[h]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:AEFATable}Factor loadings and communality of the retained items [Unmerged Responses]}

\small{

\begin{tabular}{ccccccccc}
\toprule
item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness} & \multicolumn{1}{c}{Complexity}\\
\midrule
item19 & 0.99 &  &  &  &  & 1.01 & -0.01 & 1.06\\
item20 & 0.91 &  &  &  &  & 0.87 & 0.13 & 1.11\\
item18 & 0.82 &  &  &  &  & 0.71 & 0.29 & 1.12\\
item21 & 0.8 &  &  &  &  & 0.68 & 0.32 & 1.16\\
item4 & 0.47 &  &  &  &  & 0.25 & 0.75 & 1.30\\
item11 &  & 0.83 &  &  &  & 0.69 & 0.31 & 1.01\\
item10 &  & 0.81 &  &  &  & 0.67 & 0.33 & 1.03\\
item12 &  & 0.56 &  &  &  & 0.37 & 0.63 & 1.37\\
item8 &  & -0.44 &  &  &  & 0.21 & 0.79 & 1.11\\
item7 &  & 0.42 &  &  &  & 0.23 & 0.77 & 1.61\\
item9 &  & 0.33 &  &  &  & 0.12 & 0.88 & 1.10\\
item16 &  &  & 0.95 &  &  & 0.95 & 0.05 & 1.10\\
item17 &  &  & 0.74 &  &  & 0.60 & 0.41 & 1.17\\
item36 & 0.3 &  & 0.73 &  &  & 0.65 & 0.35 & 1.43\\
item3 &  &  &  & 0.85 &  & 0.75 & 0.25 & 1.05\\
item27 &  &  &  & 0.78 &  & 0.62 & 0.38 & 1.03\\
item40 &  &  &  & 0.71 &  & 0.51 & 0.49 & 1.05\\
item35 &  &  &  &  & 0.58 & 0.35 & 0.65 & 1.09\\
item48 &  &  &  &  & 0.57 & 0.35 & 0.65 & 1.14\\
item33 &  &  &  &  & 0.55 & 0.32 & 0.68 & 1.08\\
item47 &  &  &  &  & 0.52 & 0.29 & 0.71 & 1.19\\
item44 &  &  &  &  & 0.45 & 0.22 & 0.78 & 1.15\\
item31 &  &  &  &  & 0.41 & 0.21 & 0.79 & 1.48\\
item38 &  &  &  &  & 0.33 & 0.13 & 0.87 & 1.32\\
\% of Variance & 0.15 & 0.09 & 0.09 & 0.08 & 0.08 & NA & NA & NA\\
\bottomrule
\addlinespace
\end{tabular}

}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} Only loading higher than .30 is reported}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.00}}@{}}
\toprule
\textbf{Five Factor Solution{[}Unmerged Responses{]} (24 Items)} \\
\midrule
\endhead
\textbf{F1} \\
I use light therapy applying a blue light box. \\
I use light therapy applying a light visor. \\
I use light therapy applying a white light box. \\
I use light therapy applying another form of light device. \\
I use an alarm with a dawn simulation light. \\
\textbf{F2} \\
I spend more than 3 hours per day (in total) outside. \\
I spend between 1 and 3 hours per day (in total) outside. \\
I spend as much time outside as possible. \\
I spend 30 minutes or less per day (in total) outside. \\
I go for a walk or exercise outside within 2 hours after waking up. \\
I spend between 30 minutes and 1 hour per day (in total) outside. \\
\textbf{F3} \\
I look at my mobile phone screen immediately after waking up. \\
I use my mobile phone within 1 hour before attempting to fall asleep. \\
I check my phone when I wake up at night. \\
\textbf{F4} \\
I use a blue-filter app on my computer screen within 1 hour before
attempting to fall asleep. \\
I seek out knowledge on how to improve my light exposure. \\
I dim my computer screen within 1 hour before attempting to fall
asleep. \\
I discuss the effects of light on my body with other people. \\
I modify my light environment to match my current needs. \\
I dim my room light within 1 hour before attempting to fall asleep. \\
I use as little light as possible when I get up during the night. \\
\textbf{F5} \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors
during the day. \\
I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1
hour before attempting to fall asleep. \\
\bottomrule
\end{longtable}
\end{appendix}

### 2021-10-29 instrument.tex
* Instrument description and Other LaTeX issues. Instrument is now in landscape mood.

@@
 calculated by the summation of scores of items belonging to the
-corresponding factor.
+corresponding factor. The following instruction is given before
+displaying the items: ``Please indicate how often you performed the
+following behaviours in the past 4 weeks.''
 
@@
 
+\blandscape
+
+\hypertarget{leba-long-form-23-items}{%
+\section{LEBA Long Form (23 Items)}\label{leba-long-form-23-items}}
+
 \begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.00}}@{}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.05}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.27}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.34}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.08}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.11}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.07}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.08}}@{}}
 \toprule
-Long Form (23 Items) \\
+& Items & Never/Does not apply/I don't know & Rarely & Sometimes & Often
+& Always \\
 \midrule
 \endhead
-\textbf{F1: Wearing blue light filters} \\
-I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors
-during the day. \\
-I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors
-during the day. \\
-I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1
-hour before attempting to fall asleep. \\
-\textbf{F2: Spending time outdoors} \\
-I spend 30 minutes or less per day (in total) outside. \\
-I spend between 1 and 3 hours per day (in total) outside. \\
-I spend between 30 minutes and 1 hour per day (in total) outside. \\
-I spend more than 3 hours per day (in total) outside. \\
-I spend as much time outside as possible. \\
-I go for a walk or exercise outside within 2 hours after waking up. \\
-\textbf{F3: Using phone and smartwatch in bed} \\
-I use my mobile phone within 1 hour before attempting to fall asleep. \\
-I look at my mobile phone screen immediately after waking up. \\
-I check my phone when I wake up at night. \\
-I look at my smartwatch within 1 hour before attempting to fall
-asleep. \\
-I look at my smartwatch when I wake up at night. \\
-\textbf{F4: Using light before bedtime} \\
-I dim my mobile phone screen within 1 hour before attempting to fall
-asleep. \\
-I use a blue-filter app on my computer screen within 1 hour before
-attempting to fall asleep. \\
-I use as little light as possible when I get up during the night. \\
-I dim my computer screen within 1 hour before attempting to fall
-asleep. \\
-\textbf{F5: Using light in the morning and during daytime} \\
-I use tunable lights to create a healthy light environment. \\
-I use LEDs to create a healthy light environment. \\
-I use a desk lamp when I do focused work. \\
-I use an alarm with a dawn simulation light. \\
-I turn on the lights immediately after waking up. \\
+1 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
+indoors during the day. & & & & & \\
+2 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
+outdoors during the day. & & & & & \\
+3 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
+within 1 hour before attempting to fall asleep. & & & & & \\
+4 & I spend 30 minutes or less per day (in total) outside. & & & & & \\
+5 & I spend between 1 and 3 hours per day (in total) outside. & & & &
+& \\
+6 & I spend between 30 minutes and 1 hour per day (in total) outside. &
+& & & & \\
+7 & I spend more than 3 hours per day (in total) outside. & & & & & \\
+8 & I spend as much time outside as possible. & & & & & \\
+9 & I go for a walk or exercise outside within 2 hours after waking up.
+& & & & & \\
+10 & I use my mobile phone within 1 hour before attempting to fall
+asleep. & & & & & \\
+11 & I look at my mobile phone screen immediately after waking up. & & &
+& & \\
+12 & I check my phone when I wake up at night. & & & & & \\
+13 & I look at my smartwatch within 1 hour before attempting to fall
+asleep. & & & & & \\
+14 & I look at my smartwatch when I wake up at night. & & & & & \\
+15 & I dim my mobile phone screen within 1 hour before attempting to
+fall asleep. & & & & & \\
+16 & I use a blue-filter app on my computer screen within 1 hour before
+attempting to fall asleep. & & & & & \\
+17 & I use as little light as possible when I get up during the night. &
+& & & & \\
+18 & I dim my computer screen within 1 hour before attempting to fall
+asleep. & & & & & \\
+19 & I use tunable lights to create a healthy light environment. & & & &
+& \\
+20 & I use LEDs to create a healthy light environment. & & & & & \\
+21 & I use a desk lamp when I do focused work. & & & & & \\
+22 & I use an alarm with a dawn simulation light. & & & & & \\
+23 & I turn on the lights immediately after waking up. & & & & & \\
 \bottomrule
@@
 
+\elandscape
+
 \newpage
 
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.00}}@{}}
+\blandscape
+
+\hypertarget{latent-structure-reliability-and-structural-validity}{%
+\subsection{Latent Structure, Reliability and Structural
+Validity}\label{latent-structure-reliability-and-structural-validity}}
+
+The long form of LEBA consists 23 items with five factors.
+
+\begin{longtable}[]{@{}lll@{}}
 \toprule
-Short Form (17 Items) \\
+Factor names & Items & Reliability Coefficients \\
 \midrule
 \endhead
-\textbf{F1: Wearing blue light filters} \\
-I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors
-during the day. \\
-I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors
-during the day. \\
-I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1
-hour before attempting to fall asleep. \\
-\textbf{F2: Spending time outdoors} \\
-I spend 30 minutes or less per day (in total) outside. \\
-I spend between 1 and 3 hours per day (in total) outside. \\
-I spend more than 3 hours per day (in total) outside. \\
-I spend as much time outside as possible. \\
-I go for a walk or exercise outside within 2 hours after waking up. \\
-\textbf{F3: Using phone and smartwatch in bed} \\
-I use my mobile phone within 1 hour before attempting to fall asleep. \\
-I look at my mobile phone screen immediately after waking up. \\
-I check my phone when I wake up at night. \\
-\textbf{F4: Using light before bedtime} \\
-I dim my mobile phone screen within 1 hour before attempting to fall
-asleep. \\
-I use a blue-filter app on my computer screen within 1 hour before
-attempting to fall asleep. \\
-I dim my computer screen within 1 hour before attempting to fall
-asleep. \\
-\textbf{F5: Using light in the morning and during daytime} \\
-I use tunable lights to create a healthy light environment. \\
-I use LEDs to create a healthy light environment. \\
-I use an alarm with a dawn simulation light. \\
+\textbf{F1: Wearing blue light filters} & 1-3 & .93 \\
+\textbf{F2: Spending time outdoors} & 4-9 (Item 4 is reversed) & .80 \\
+\textbf{F3: Using phone and smartwatch in bed} & 10-14 & .61 \\
+\textbf{F4: Using light before bedtime} & 15-18 & .72 \\
+\textbf{F5: Using light in the morning and during daytime} & 19-23 &
+.45 \\
 \bottomrule
 \end{longtable}
+
+LEBA -long form showed satisfactory structural validity (CFI =.97; TLI =
+.96; RMSEA = .05{[}.04-.06, 90\% CI{]}; SRMR = .09).
+
+\hypertarget{how-to-cite}{%
+\subsection{How to cite:}\label{how-to-cite}}
+
+\elandscape
+
+\newpage
+
+\blandscape
+
+\hypertarget{leba-short-form-17-items}{%
+\section{LEBA Short Form (17 Items)}\label{leba-short-form-17-items}}
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.05}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.27}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.34}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.08}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.11}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.07}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.08}}@{}}
+\toprule
+& Short Form (17 Items) & Never/Does not apply/I don't know & Rarely &
+Sometimes & Often & Always \\
+\midrule
+\endhead
+01 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
+indoors during the day. & & & & & \\
+02 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
+outdoors during the day. & & & & & \\
+03 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
+within 1 hour before attempting to fall asleep. & & & & & \\
+04 & I spend 30 minutes or less per day (in total) outside. & & & & & \\
+05 & I spend between 1 and 3 hours per day (in total) outside. & & & &
+& \\
+06 & I spend more than 3 hours per day (in total) outside. & & & & & \\
+07 & I spend as much time outside as possible. & & & & & \\
+08 & I go for a walk or exercise outside within 2 hours after waking up.
+& & & & & \\
+09 & I use my mobile phone within 1 hour before attempting to fall
+asleep. & & & & & \\
+10 & I look at my mobile phone screen immediately after waking up. & & &
+& & \\
+11 & I check my phone when I wake up at night. & & & & & \\
+12 & I dim my mobile phone screen within 1 hour before attempting to
+fall asleep. & & & & & \\
+13 & I use a blue-filter app on my computer screen within 1 hour before
+attempting to fall asleep. & & & & & \\
+14 & I dim my computer screen within 1 hour before attempting to fall
+asleep. & & & & & \\
+15 & I use tunable lights to create a healthy light environment. & & & &
+& \\
+16 & I use LEDs to create a healthy light environment. & & & & & \\
+17 & I use an alarm with a dawn simulation light. & & & & & \\
+\bottomrule
+\end{longtable}
+
+\elandscape
+
+\newpage
+
+\blandscape
+
+\hypertarget{latent-structure-reliability-and-structural-validity-1}{%
+\subsection{Latent Structure, Reliability and Structural
+Validity}\label{latent-structure-reliability-and-structural-validity-1}}
+
+The short form of LEBA consists 23 items with five factors.
+
+\begin{longtable}[]{@{}ll@{}}
+\toprule
+Factor names & Items \\
+\midrule
+\endhead
+\textbf{F1: Wearing blue light filters} & 1-3 \\
+\textbf{F2: Spending time outdoors} & 4-8 (Item 4 is reversed) \\
+\textbf{F3: Using phone and smartwatch in bed} & 9-11 \\
+\textbf{F4: Using light before bedtime} & 12-14 \\
+\textbf{F5: Using light in the morning and during daytime} & 15-17 \\
+\bottomrule
+\end{longtable}
+
+\hypertarget{how-to-cite-1}{%
+\subsection{How to cite:}\label{how-to-cite-1}}
+
+\elandscape
 \end{appendix}

### 2021-10-29 manuscript.Rmd
* Instrument description and Other LaTeX issues. Instrument is now in landscape mood.

@@
     latex_engine: xelatex
+    includes:
+      in_header: header.tex
 
@@
   - "Appendix-B.Rmd"
-
 ---
@@
 
-```{r depMan, eval=FALSE, include=FALSE}
+```{r depMan, include=FALSE}
 library(packrat)
-#This chunk is disabled. Only run this to install the dependencies automatically.
 packrat::init()
+
+#To find and install required dependencies.
+packrat::restore()
 #Only use when you have added some pack
@@
 
-#To find and install required dependencies.
-packrat::restore()
 ```
@@
 
+\blandscape
+
++-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
 | Name                                            | Authors                    | Description                                                                               | Relevant Items | Adaptations |
-
-+=================================================+=============================+========================================================================================+:==============:+=============+
-| Visual Light Sensitivity Questionnaire-8        | [@verriotto2017new]        | Eight-question survey to assess the presence and severity of photosensitivity symptoms | all            | jhghjgjhgfd |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Office Light Survey                             | [@eklund1996development]   | Multi-item questionnaire to assess electrical lighting environment in office           | aa             | gh          |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Harvard Light Exposure Assessment Questionnaire | [@bajaj2011validation]     | Self-administered semiquantitative light qestionnaire                                  | aa             | as          |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Hospital Lighting Survey                        | [@dianat2013objective]     | 23 items questionnaire to assess light environment in a hospital                       | dd             | fg          |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Morningness-Eveningness Questionnaire           | [@horne1976self]           | 19 items questionnaire to understand your body clock                                   | ff             | hj          |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Munich Chronotype Questionnaire (MCTQ)          | [@roenneberg2003life]      | 17 items questionnaire to understand individuals phase of entrainment                  | ff             | jk          |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| Assessment of Sleep Environment                 | [@grandner2014development] | 13 items questionnaire measuring your sleep environment quality                        | ff             | kl          |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-| The Pittsburgh Sleep Quality Index (PSQI)       | [@buysse1989pittsburgh]    | 9 items inventory to measure sleep quality and sleeping pattern                        | ff             | klfrgfgvfg  |
-+-------------------------------------------------+-----------------------------+----------------------------------------------------------------------------------------+----------------+-------------+
-=======
-|-------------------------------------------------|-----------------------------|----------------------------------------------------------------------------------------|:--------------:|-------------|
-| Visual Light Sensitivity Questionnaire-8        | [\@verriotto2017new]        | Eight-question survey to assess the presence and severity of photosensitivity symptoms |      all       | jhghjgjhgfd |
-| Office Light Survey                             | [\@eklund1996development]   | Multi-item questionnaire to assess electrical lighting environment in office           |       aa       | gh          |
-| Harvard Light Exposure Assessment Questionnaire | [\@bajaj2011validation]     | Self-administered semiquantitative light qestionnaire                                  |       aa       | as          |
-| Hospital Lighting Survey                        | [\@dianat2013objective]     | 23 items questionnaire to assess light environment in a hospital                       |       dd       | fg          |
-| Morningness-Eveningness Questionnaire           | [\@horne1976self]           | 19 items questionnaire to understand your body clock                                   |       ff       | hj          |
-| Munich Chronotype Questionnaire (MCTQ)          | [\@roenneberg2003life]      | 17 items questionnaire to understand individuals phase of entrainment                  |       ff       | jk          |
-| Assessment of Sleep Environment                 | [\@grandner2014development] | 13 items questionnaire measuring your sleep environment quality                        |       ff       | kl          |
-| The Pittsburgh Sleep Quality Index (PSQI)       | [\@buysse1989pittsburgh]    | 9 items inventory to measure sleep quality and sleeping pattern                        |       ff       | klfrgfgvfg  |
++=================================================+============================+===========================================================================================+================+=============+
+| Visual Light Sensitivity Questionnaire-8        | [@verriotto2017new]        | Eight-question survey to assess the presence and severity of photosensitivity symptoms    | All items      |             |
++-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
+| Office Light Survey                             | [@eklund1996development]   | Multi-item questionnaire to assess electrical lighting environment in office              |                |             |
++-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
+| Harvard Light Exposure Assessment Questionnaire | [@bajaj2011validation]     | Self-administered semi-quantitative light questionnaire                                   | All Items      |             |
++-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
+| Hospital Lighting Survey                        | [@dianat2013objective]     | 23 items questionnaire to assess light environment in a hospital                          |                |             |
++-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
+| Morningness-Eveningness Questionnaire           | [@horne1976self]           | 19 items questionnaire to understand your body clock                                      |                |             |
++-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
+| Munich Chronotype Questionnaire (MCTQ)          | [@roenneberg2003life]      | 17 items questionnaire to understand individuals phase of entrainment                     |                |             |
++-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
+| Assessment of Sleep Environment                 | [@grandner2014development] | 13 items questionnaire measuring your sleep environment quality                           |                |             |
++-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
+| The Pittsburgh Sleep Quality Index (PSQI)       | [@buysse1989pittsburgh]    | 9 items inventory to measure sleep quality and sleeping pattern                           |                |             |
++-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
+| Visual Light Sensitivity Questionnaire-8        | [@verriotto2017new] \|     | Eight-question survey to assess the presence and severity of photosensitivity symptoms \| | All items \|   |             |
++-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
+|                                                 |                            |                                                                                           |                |             |
++-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
 
 : Existing related Scales
+
+\elandscape
 

### 2021-11-03 manuscript.Rmd
added references for Survey and related questionnaires

@@
 
-+-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
++-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
 | Name                                                              | Authors                  | Description                                                                                                                                                  | Relevant Items                       | Adaptations |
-+=================================================+============================+===========================================================================================+================+=============+
++===================================================================+==========================+==============================================================================================================================================================+======================================+=============+
 | Visual Light Sensitivity Questionnaire-8                          | [@verriotto2017new]      | Eight-question survey to assess the presence and severity of photosensitivity symptoms                                                                       | All items                            |             |
-+-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
++-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
 | Office Light Survey                                               | [@eklund1996development] | Multi-item questionnaire to assess electrical lighting environment in office                                                                                 |                                      |             |
-+-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
++-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
 | Harvard Light Exposure Assessment Questionnaire                   | [@bajaj2011validation]   | Self-administered semi-quantitative light questionnaire                                                                                                      | All Items                            |             |
-+-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
++-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
 | Hospital Lighting Survey                                          | [@dianat2013objective]   | 23 items questionnaire to assess light environment in a hospital                                                                                             |                                      |             |
-+-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
++-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
 | Morningness-Eveningness Questionnaire                             | [@horne1976self]         | 19 items questionnaire to understand your body clock                                                                                                         |                                      |             |
-+-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
++-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
 | Munich Chronotype Questionnaire (MCTQ)                            | [@roenneberg2003life]    | 17 items questionnaire to understand individuals phase of entrainment                                                                                        |                                      |             |
-+-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
-| Assessment of Sleep Environment                 | [@grandner2014development] | 13 items questionnaire measuring your sleep environment quality                           |                |             |
-+-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
++-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
+| Assessment of Sleep Environment                                   | [@Olivier.2016]          | 13 items questionnaire measuring your sleep environment quality                                                                                              |                                      |             |
++-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
 | The Pittsburgh Sleep Quality Index (PSQI)                         | [@buysse1989pittsburgh]  | 9 items inventory to measure sleep quality and sleeping pattern                                                                                              |                                      |             |
-+-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
-| Visual Light Sensitivity Questionnaire-8        | [@verriotto2017new] \|     | Eight-question survey to assess the presence and severity of photosensitivity symptoms \| | All items \|   |             |
-+-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
-|                                                 |                            |                                                                                           |                |             |
-+-------------------------------------------------+----------------------------+-------------------------------------------------------------------------------------------+----------------+-------------+
++-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
+| Self-Rating of Biological Rhythm Disorder for Adolescents (SBRDA) | [@Xie.2021]              | 29 items questionnaire assessing four dimensions of biological rhythm disorder in adolescents (digital media use, sleep, eating habits, and activity)        | Items 3., 22., 23., 24., 25.
+and 29.
+|             |
++-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
+| Photosensitivity Assessment Questionnaire (PAQ)                   | [@Wu.2017]               | 16 dichotomous (yes/no) items questionnaire to assess "photophobia" and "photophilia", giving two final scores of "photophobic" and "photophilic" behaviours | All items                            |             |
++-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
 
@@
 Data was collected in a quantitative cross-sectional approach via a fully anonymous online survey hosted on REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel (sciCORE; <https://redcap.scicore.unibas.ch/>).
-Participants were recruited via the website of a Comic co-released with the survey [CITE COMIC HERE; <https://enlightenyourclock.org/participate-in-research/>], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution via f.lux software [CITE f.lux Michael Herf?].
+Participants were recruited via the website of a Comic co-released with the survey[@Weinzaepflen.2021; <https://enlightenyourclock.org/participate-in-research/>], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution via f.lux software [CITE f.lux Michael Herf?].
 
@@
 
--   Sleep disturbance and sleep-related impairment [CITE]
--   Sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration [CITE]
--   Meal timing & caffeine consumption [CITE]
--   Light sensitivity (photophobia vs. photophilia) [CITE]
--   Self-reported pubertal stage (only if younger than 18 years old) [CITE]
+-   Sleep disturbance and sleep-related impairment (adult and pediatric versions) [@Bevans.2019; @Buysse.2010; @Forrest.2018; @Harb.2015; @Yu.2011]
+-   Sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration (version for adults and adolescents) [@roenneberg2003life]
+-   Sleep environment [@Olivier.2016]
+-   Meal timing & caffeine consumption [custom items]
+-   Light sensitivity (photophobia vs. photophilia) [@Wu.2017]
+-   Self-reported pubertal stage (only if younger than 18 years old) [@Petersen.1988]
 

### 2021-11-04 manuscript.Rmd
added f.lux software citation

@@
 Data was collected in a quantitative cross-sectional approach via a fully anonymous online survey hosted on REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel (sciCORE; <https://redcap.scicore.unibas.ch/>).
-Participants were recruited via the website of a Comic co-released with the survey[@Weinzaepflen.2021; <https://enlightenyourclock.org/participate-in-research/>], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution via f.lux software [CITE f.lux Michael Herf?].
+Participants were recruited via the website of a Comic co-released with the survey[@Weinzaepflen.2021; <https://enlightenyourclock.org/participate-in-research/>], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux software [@f.lux].
 

### 2021-11-05 manuscript.Rmd
Minor change with subset command

--- 2021-10-29 manuscript.Rmd
@@
 descriptives.data[ , 9:56 ][ descriptives.data[ , 9:56 ] == 0 ] <- 1
-EFA.descriptives <- descriptives.data[1:428,]
-CFA.descriptives <- descriptives.data[429:690, ]
+#EFA.descriptives <- descriptives.data[1:428,]
+EFA.descriptives <- subset(descriptives.data, IncludedInEFA == "TRUE")
+#CFA.descriptives <- descriptives.data[429:690, ]
+CFA.descriptives<- subset(descriptives.data, IncludedInEFA == "FALSE")
 

### 2021-11-05 manuscript.Rmd
* IRT analysis Strong evidence based claim that LEBA short-form is psychometrically valid.

@@
 
+```{r CFA21}
+LB.model.Cor.3 <- "F1 =~ a1*item16 + item36 + a2*item17
+                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
+                 F3 =~  item27+ item3+ item40 
+                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
+                 F5 =~ item46+ item45+ item25+ item4+ item1 
+                       a1==a2
+                       a3==a4
+
+                       "
+
+#item30 & 41 are removed
+
+## Fit the model 
+fit.Cor.3 <- cfa(LB.model.Cor.3, data = CFA.data, ordered = names(CFA.data),estimator = "WLSMV")
+
+rel.k.1 <- semTools::reliability(fit.Cor.3, return.total = T)
+## Summary of Model 
+cfa.sum.3 <- summary(fit.Cor.3, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
+
+## Selected Fit measures 
+fit.3 <- fitmeasures (fit.Cor.3,c("gfi", "agfi", "nfi","rfi", 
+                                  "cfi.scaled","tli.scaled",
+                                  "rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr"))
+
+```
+
 We conducted a categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator as our response data was in ordinary nature [@desjardinsHandbookEducationalMeasurement2018a].
@@
 Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR value (SRMR = `r apa(fit.2[10],2,F)`) was also close to the suggestions of @huCutoffCriteriaFit1999.
-The internal consistency reliability coefficients coefficient alpha `r apa(rel.k[5,1],2,F)`, `r apa(rel.k[5,2],2,F)`, `r apa(rel.k[5,3],2,F)`, `r apa(rel.k[5,4],2,F)`, `r apa(rel.k[5,5],2,F)` respectively indicating satisfactory reliability for F1, F2 and F4 [@najeracatalanReliabilityPopulationClassification2019]
+The internal consistency reliability coefficients coefficient alpha `r apa(rel.k[1,1],2,F)`, `r apa(rel.k[1,2],2,F)`, `r apa(rel.k[1,3],2,F)`, `r apa(rel.k[1,4],2,F)`, `r apa(rel.k[1,5],2,F)` respectively indicating satisfactory reliability for F1, F2 and F4 [@najeracatalanReliabilityPopulationClassification2019]
+
+```{r cfa4F, eval=FALSE, include=FALSE}
+LB.model.Cor.4 <- "F1 =~ a1*item16 + item36 + a2*item17
+                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
+                 F3 =~  item27+ item3+ item40 
+                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
+                        a1==a2
+                       a3==a4
+
+                       "
+
+## Fit the model 
+fit.Cor.4 <- cfa(LB.model.Cor.4, data = CFA.data, ordered = names(CFA.data),estimator = "WLSMV")
+
+rel.k.4 <- semTools::reliability(fit.Cor.4, return.total = T)
+## Summary of Model 
+cfa.sum.4 <- summary(fit.Cor.4, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
+
+## Selected Fit measures 
+fit.4 <- fitmeasures (fit.Cor.4,c("gfi", "agfi", "nfi","rfi", 
+                                  "cfi.scaled","tli.scaled",
+                                  "rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr"))
+
+```
 
@@
 
-## Developing the short form of LEBA
+## Analysing the quality of items by Item Information Theory
+
+We sought the IRT to gether information regarding the item quality.
+IRT complements the conventional classical test theory-based analysis by gathering information on item discrimination and item difficulty[@bakerBasicsItemResponse2017].
+Here, an item's quality is judged based on item information in relation to participants' latent trait level ($\theta$).
+We gathered evidence on item quality by fitting each factor of LEBA with the graded response model (\@ref(tab:IRTparameters) to the combined EFA sample and CFA sample (n =690).
+Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait, and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
+Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information <.2) to develop the short form of LEBA.
+@bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70.
+Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), low ( 5 items) indicating a good range of discrimination along the latent trait.
+Examination of the item information curve indicated 6 items (1, 25, 9, 38, 30, & 41) had relatively flat information curves thus discarded.
+We also gathered evidence of item fit and person fit to our fitted model.
 
@@
 
-#Identigying Missfit items based on RMSEA Value
+#Identifying Missfit items based on RMSEA Value
 F1.item_misfits <- subset(F1.item.fit, RMSEA.S_X2 >= .06)
@@
 
-To develop a shorter form of the LEBA we sought to Item response theory.IRT complements the conventional classical test theory-based analysis by gathering information on item discrimination and item difficulty[@bakerBasicsItemResponse2017].
-Here, an item's quality is judged based on item information in relation to participants' latent trait level ($\theta$).
-We gathered evidence on item quality by fitting each factor of LEBA with the graded response model to the combined EFA sample and CFA sample (n =690)(\@ref(tab:IRTparameters).
-Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait, and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
-Currently, apart from some general suggestions, there exists no definitive rule to judge the item discrimination and item information parameter quality.
-Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information \<.2) to develop the short form of LEBA.
-@bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70.
-Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), low ( 5 items) indicating a good range of discrimination along the latent trait.
-Examination of the item information curve indicated 6 items (1, 25, 9, 38, 30, & 41) had relatively flat information curves thus discarded.
-
 ```{r IRTparameters, results='asis'}
@@
 
+#Item fit
+F1.item.fit<- itemfit(F1_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
+                                  impute=10)
+
+F2.item.fit<- itemfit(F2_fit.redu, fit_stats = c("S_X2", "G2","Zh", "infit"),
+                                  impute=10)
+F3.item.fit<- itemfit(F3_fit.redu, fit_stats = c("S_X2", "G2","Zh", "infit"),
+                                  impute=10)
+F4.item.fit<- itemfit(F4_fit.redu, fit_stats = c("S_X2", "G2","Zh", "infit"),
+                                  impute=10)
+
+F5.item.fit<- itemfit(F5_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
+                                  impute=10)
+
+#Identifying Missfit items based on RMSEA Value
+F1.item_misfits <- subset(F1.item.fit, RMSEA.S_X2 >= .06)
+F2.item_misfits <- subset(F2.item.fit, RMSEA.S_X2 >= .06)
+F3.item_misfits <- subset(F3.item.fit, RMSEA.S_X2 >= .06)
+F4.item_misfits <- subset(F4.item.fit, RMSEA.S_X2 >= .06)
+F5.item_misfits <- subset(F5.item.fit, RMSEA.S_X2 >= .06)
+
+# Person Fit ####
+## F1 Person fit ####
+F1.personfit <- personfit(F1_fit) 
+F1.personfit_model_misfits <- subset(F1.personfit, Zh < -2)
+rownames(F1.personfit_model_misfits)
+nrow(F1.personfit_model_misfits)
+hist(F1.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
+abline(v = -2, lwd = 2, lty = 2)
+
+## F2 Person fit ####
+F2.personfit <- personfit(F2_fit.redu) 
+F2.personfit_model_misfits <- subset(F2.personfit, Zh < -2)
+rownames(F2.personfit_model_misfits)
+nrow(F2.personfit_model_misfits)
+hist(F2.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
+abline(v = -2, lwd = 2, lty = 2)
+
+## F3 Person fit ####
+F3.personfit <- personfit(F3_fit.redu) 
+F3.personfit_model_misfits <- subset(F3.personfit, Zh < -2)
+rownames(F3.personfit_model_misfits)
+nrow(F3.personfit_model_misfits)
+hist(F3.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
+abline(v = -2, lwd = 2, lty = 2)
+
+## F4 Person fit ####
+F4.personfit <- personfit(F4_fit.redu) 
+F4.personfit_model_misfits <- subset(F4.personfit, Zh < -2)
+rownames(F4.personfit_model_misfits)
+nrow(F4.personfit_model_misfits)
+hist(F4.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
+abline(v = -2, lwd = 2, lty = 2)
+
+## F5 Person fit ####
+F5.personfit <- personfit(F5_fit) 
+F5.personfit_model_misfits <- subset(F5.personfit, Zh < -2)
+rownames(F3.personfit_model_misfits)
+nrow(F5.personfit_model_misfits)
+hist(F5.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
+abline(v = -2, lwd = 2, lty = 2)
+
+F1.reliability <- plot(F1_fit, type = 'rxx', theta_lim = c(-6, 6), 
+      main="" )
+F2.reliability <- plot(F2_fit.redu, type = 'rxx', theta_lim = c(-6, 6), 
+      main="" )
+F3.reliability <- plot(F3_fit.redu, type = 'rxx', theta_lim = c(-6, 6), 
+      main="" )
+F4.reliability <- plot(F4_fit.redu, type = 'rxx', theta_lim = c(-6, 6), 
+      main="" )
+F5.reliability <- plot(F5_fit, type = 'rxx', theta_lim = c(-6, 6), 
+      main="" )
+
+##IRT reliability (marginal reliability of scales)
+F1.marginal.rel <- marginal_rxx(F1_fit)
+F2.marginal.rel <-marginal_rxx(F2_fit.redu)
+F3.marginal.rel <-marginal_rxx(F3_fit.redu)
+F4.marginal.rel <-marginal_rxx(F4_fit.redu)
+F5.marginal.rel <-marginal_rxx(F5_fit)
+
 # Plots2 ####
@@
 
-```
-
-Test information curve (TIC) indicate the amount of information an the full-scale carry along the latent trait continuum.
-As we treated each factor of LEBA as an unidmensional construct we obtain 5 TICs ().
-These information curves indicated except Blue filter factor, the other factor's curve is roughly centered on the center of the trait continuum (($\theta$)) and the The amount of information changed rather steadily with the change of ($\theta$).
-Thus we conferred the LEBA scale (except blue filter) estimated the light exposure related behavior with precision near the center of trait continuum [@bakerBasicsItemResponse2017] which is sufficient to discriminate between latent trait measured by the each factor.
-The blue filter factor had a peak to the right side of the center of latent trait indicating its ability to providing information only for people who already have some preference towards using blue-filters.
+##Scale characteristic curve
+F1.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
+F2.scale <- plot(F2_fit.redu, type = 'score', theta_lim = c(-6, 6), main = "")
+F3.scale <- plot(F3_fit.redu, type = 'score', theta_lim = c(-6, 6), main = "")
+F4.scale <- plot(F4_fit.redu, type = 'score', theta_lim = c(-6, 6), main = "")
+F5.scale <- plot(F5_fit, type = 'score', theta_lim = c(-6, 6), main = "")
+
+```
 
@@
 ```
+
+Test information curve (TIC) indicate the amount of information an the full-scale carry along the latent trait continuum.
+As we treated each factor of LEBA as an unidmensional construct we obtain 5 TICs.
+These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum (($\theta$)).
+Also the amount of information changed rather steadily with the change of ($\theta$).
+Thus we conferred the LEBA scale (except blue filter) estimated the light exposure related behavior with precision near the center of trait continuum [@bakerBasicsItemResponse2017] which is sufficient to discriminate between latent trait measured by the each factor.
+The blue filter factor had a peak to the right side of the center of latent trait indicating its ability to providing information only for people who already have some preference towards using blue-filters.
+
+Our result also indicated all the items fitted well to the respective models as assessed by assessed by RMSEA value obtained from Signed-X2 index implementation.
+All of the items had RMSEA value <.06 indicating adequate fit.
+Person fit indicates the validity and meaningfulness of the fitted model at the participants latent trait level [@desjardinsHandbookEducationalMeasurement2018].
+We estimated the person fit statistics using standardized fit index Zh statistics [@drasgow1985appropriateness].
+Zh < -2 should be considered as a misfit.
+Fig indicates that Zh is larger than -2 for most participants, suggesting a good fit of the selected IRT models.
+
+The overall we can concluded that  IRT analysis  indicated LEBA is  a psychometrically sound measure.
+Item fit indexes and person fit index for all five fitted model were acceptable.
+Items had diverse slope parameters  indicating a good range of discrimination- the ability to differentiate respondents with different levels of the light exposure related behavior.
+All-in-all we can recommend the LEBA to be used to capture light exposure related behavior.
 
@@
 
-```{r clean}
+```{r clean, eval=FALSE, include=FALSE}
 cleanFolder <- function() {
@@
 }
+cleanFolder()
 ```

### 2021-11-06 Appendix-B.Rmd
* Instrument description and Other LaTeX issues. Instrument is now in landscape mood.
* Packrat issue is solve Kniting will be continued for duplicate chunk names Font issue for plotting is solved

@@
 
-```{r Asetup, warning=FALSE, include=FALSE}
+```{r setupAppB, warning=FALSE, include=FALSE}
 knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600)
@@
 
-```{r Alibrary, include=FALSE}
+```{r libraryAppB, include=FALSE}
 
@@
 library(Hmisc)
+
 ```
 
-```{r AData, include=FALSE}
+```{r DataAppB, include=FALSE}
 data <- readRDS("leba_2021-09-08.rds")
@@
 
-```{r Aggplot2, include=F}
+```{r ggplot2AppB, include=F}
 apatheme=theme_bw()+
@@
 
-```{r AEFAassumptions, include=FALSE}
+```{r EFAassumptionsAppB, include=FALSE}
 
@@
 
-```{r AtabDes, results='asis'}
+```{r tabDesAppB, results='asis'}
 apa_table(Des.combined, caption = "Descriptive Statistics for Unmerged response options", align = "c", note = "*p<.001", placement = "h")
@@
 
-```{r ACorrMatrix, include=FALSE}
+```{r CorrMatrixAppB, include=FALSE}
 #Polychoric Correlation matrix
@@
 
-```{r AfigCor, fig.align='center', fig.cap="Correlation plot of the items",  out.width="100%", include=FALSE,}
+```{r figCorAppB, fig.align='center', fig.cap="Correlation plot of the items",  out.width="100%"}
 
@@
 
-```{r AParallelEFA, include=FALSE}
+```{r ParallelEFAAppB, include=FALSE}
 
@@
 
-```{r AScreePlot, include=FALSE}
+```{r ScreePlotAppB, include=FALSE}
 Scree <- scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
@@
 
-```{r AMAPefa, include=FALSE}
+```{r MAPefaAppB, include=FALSE}
 #MAP
@@
 
-```{r AfacIdFig, out.height="200%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot',  warning=FALSE, results= 'asis'}
+```{r facIdFigAppB, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot', warning=FALSE, out.height="100%", out.width="100%"}
 cowplot::plot_grid(parallel, scree.plot, labels = "AUTO",ncol=1, label_size = 8,align = "v")
@@
 However, Scree plot and the MAP method suggested 6-factor solution.
-five-factor solution (Figure\\ \\\@ref:AfacIdFig).
+five-factor solution .
 As a result, we tested both five-factor and six-factor solutions.
 
-```{r AEFA, include=FALSE}
+```{r EFAAppB, include=FALSE}
 fa.5F.1 <- fa(r=correlations$rho, nfactors = 5, fm= "pa",rotate ="varimax",
@@
 
-```{r Afactordetails, include=FALSE}
+```{r factordetailsAppB, include=FALSE}
 #Preparing the EFA table
@@
 
-```{r AEFATable, results='asis'}
+```{r EFATableAppB, results='asis'}
 
@@
 
-```{r AEFAResiduals, fig.align='center', fig.cap=' Histogram of residulas:  five-factor solution', warning=FALSE, include=FALSE, out.height="50%", out.width="50%"}
+```{r EFAResidualsAppB, echo=FALSE, fig.align='center', fig.cap=' Histogram of residulas:  five-factor solution', warning=FALSE, out.height="50%", out.width="50%", results='asis'}
 hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))

### 2021-11-06 Appendix-B.tex
* Packrat issue is solve Kniting will be continued for duplicate chunk names Font issue for plotting is solved

@@
 
-\caption{\label{tab:AtabDes}Descriptive Statistics for Unmerged response options}
+\caption{\label{tab:tabDesAppB-25}Descriptive Statistics for Unmerged response options}
 
@@
 
-{\centering \includegraphics[width=1\linewidth,height=2\textheight]{manuscript_files/figure-latex/AfacIdFig-1}
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-27-1}
 
@@
 
-\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}(\#fig:AfacIdFig)
+\caption{Correlation plot of the items}(\#fig:figCorAppB-27)
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth,height=1\textheight]{manuscript_files/figure-latex/facIdFigAppB-31-1}
+
+}
+
+\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}(\#fig:facIdFigAppB-31)
 \end{figure}
@@
 solution. However, Scree plot and the MAP method suggested 6-factor
-solution. five-factor solution (Figure@ref:AfacIdFig). As a result, we
-tested both five-factor and six-factor solutions.
+solution. five-factor solution . As a result, we tested both five-factor
+and six-factor solutions.
 
@@
 
-\caption{\label{tab:AEFATable}Factor loadings and communality of the retained items [Unmerged Responses]}
+\caption{\label{tab:EFATableAppB-34}Factor loadings and communality of the retained items [Unmerged Responses]}
 
@@
 \toprule
-\textbf{Five Factor Solution{[}Unmerged Responses{]} (24 Items)} \\
+\begin{minipage}[b]{\linewidth}\raggedright
+\textbf{Five Factor Solution{[}Unmerged Responses{]} (24 Items)}
+\end{minipage} \\
 \midrule
@@
 \end{longtable}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/EFAResidualsAppB-35-1}
+
+}
+
+\caption{ Histogram of residulas:  five-factor solution}(\#fig:EFAResidualsAppB-35)
+\end{figure}
 \end{appendix}

### 2021-11-06 instrument.tex
* Packrat issue is solve Kniting will be continued for duplicate chunk names Font issue for plotting is solved

@@
 \toprule
-& Items & Never/Does not apply/I don't know & Rarely & Sometimes & Often
-& Always \\
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Items
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Never/Does not apply/I don't know
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Rarely
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Sometimes
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Often
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Always
+\end{minipage} \\
 \midrule
@@
 \toprule
-& Short Form (17 Items) & Never/Does not apply/I don't know & Rarely &
-Sometimes & Often & Always \\
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Short Form (17 Items)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Never/Does not apply/I don't know
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Rarely
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Sometimes
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Often
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Always
+\end{minipage} \\
 \midrule
@@
 \textbf{F2: Spending time outdoors} & 4-8 (Item 4 is reversed) \\
-\textbf{F3: Using phone and smartwatch in bed} & 9-11 \\
+\textbf{F3: Using phone and smart-watch in bed} & 9-11 \\
 \textbf{F4: Using light before bedtime} & 12-14 \\

### 2021-11-06 manuscript.Rmd
* Packrat issue is solve Kniting will be continued for duplicate chunk names Font issue for plotting is solved

@@
   - "Appendix-B.Rmd"
+
 ---
@@
 knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600)
+options(knitr.duplicate.label = "allow")
 set.seed(123)
@@
 library(packrat)
-packrat::init()
+packrat::init(infer.dependencies = F)# install dependencies only for Rmd files in this project
 
@@
 install.packages("psych")
+install.packages("lavaan")
 install.packages("dlookr")
@@
 install.packages("gt")
-remotes::install_github("jthomasmock/gtExtras")
+
 install.packages("questionr")
-devtools::install_github("lbusett/insert_table")
+
 ```
@@
 library(simsem)
+library(extrafont)
+extrafont::font_import()
 r_refs("references.bib")
@@
 
-```{r CFA data frame, include=FALSE}
+```{r CFAdataframe, include=FALSE}
 
@@
 
-```{r CFA 25items, include=FALSE }
+```{r CFA25items, include=FALSE }
 
@@
 modfit.Cor.one[modfit.Cor.one$mi>3.84,]
-```
-
-```{r CFA21}
-LB.model.Cor.3 <- "F1 =~ a1*item16 + item36 + a2*item17
-                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
-                 F3 =~  item27+ item3+ item40 
-                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
-                 F5 =~ item46+ item45+ item25+ item4+ item1 
-                       a1==a2
-                       a3==a4
-
-                       "
-
-#item30 & 41 are removed
-
-## Fit the model 
-fit.Cor.3 <- cfa(LB.model.Cor.3, data = CFA.data, ordered = names(CFA.data),estimator = "WLSMV")
-
-rel.k.1 <- semTools::reliability(fit.Cor.3, return.total = T)
-## Summary of Model 
-cfa.sum.3 <- summary(fit.Cor.3, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
-
-## Selected Fit measures 
-fit.3 <- fitmeasures (fit.Cor.3,c("gfi", "agfi", "nfi","rfi", 
-                                  "cfi.scaled","tli.scaled",
-                                  "rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr"))
-
 ```
@@
 The internal consistency reliability coefficients coefficient alpha `r apa(rel.k[1,1],2,F)`, `r apa(rel.k[1,2],2,F)`, `r apa(rel.k[1,3],2,F)`, `r apa(rel.k[1,4],2,F)`, `r apa(rel.k[1,5],2,F)` respectively indicating satisfactory reliability for F1, F2 and F4 [@najeracatalanReliabilityPopulationClassification2019]
-
-```{r cfa4F, eval=FALSE, include=FALSE}
-LB.model.Cor.4 <- "F1 =~ a1*item16 + item36 + a2*item17
-                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
-                 F3 =~  item27+ item3+ item40 
-                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
-                        a1==a2
-                       a3==a4
-
-                       "
-
-## Fit the model 
-fit.Cor.4 <- cfa(LB.model.Cor.4, data = CFA.data, ordered = names(CFA.data),estimator = "WLSMV")
-
-rel.k.4 <- semTools::reliability(fit.Cor.4, return.total = T)
-## Summary of Model 
-cfa.sum.4 <- summary(fit.Cor.4, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
-
-## Selected Fit measures 
-fit.4 <- fitmeasures (fit.Cor.4,c("gfi", "agfi", "nfi","rfi", 
-                                  "cfi.scaled","tli.scaled",
-                                  "rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr"))
-
-```
 
@@
 
-```{r Invariance detail, include=FALSE}
+```{r Invariancedetail, include=FALSE}
 # Configural invariance ####
@@
 
-```{r IRT data, include=FALSE}
+```{r IRTdata, include=FALSE}
 ## Recoding sem.data$item8 into sem.data$Ritem8
@@
 \endgroup
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('instrument.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('Appendix-B.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('instrument.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('Appendix-B.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('instrument.Rmd')
+```

### 2021-11-06 Appendix-B.Rmd
Font issue remains unsolved in the appendix B

@@
 ---
+
+## Supplimentary Analysis
 
@@
 library(Hmisc)
+library(extrafont)
+extrafont::font_import()
 
@@
 
-```{r facIdFigAppB, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot', warning=FALSE, out.height="100%", out.width="100%"}
+```{r facIdFigAppB, eval=FALSE, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot', warning=FALSE, include=FALSE, out.height="100%", out.width="100%"}
 cowplot::plot_grid(parallel, scree.plot, labels = "AUTO",ncol=1, label_size = 8,align = "v")

### 2021-11-06 Appendix-B.tex
Font issue remains unsolved in the appendix B

--- 2021-10-29 Appendix-B.tex
@@
 \section{}
+\hypertarget{supplimentary-analysis}{%
+\subsection{Supplimentary Analysis}\label{supplimentary-analysis}}
+
 \begin{table}[h]
@@
 
-\caption{\label{tab:AtabDes}Descriptive Statistics for Unmerged response options}
+\caption{\label{tab:tabDesAppB}Descriptive Statistics for Unmerged response options}
 
@@
 
-{\centering \includegraphics[width=1\linewidth,height=2\textheight]{manuscript_files/figure-latex/AfacIdFig-1}
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-1}
 
@@
 
-\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}(\#fig:AfacIdFig)
+\caption{Correlation plot of the items}(\#fig:figCorAppB)
 \end{figure}
@@
 
-\caption{\label{tab:AEFATable}Factor loadings and communality of the retained items [Unmerged Responses]}
+\caption{\label{tab:EFATableAppB}Factor loadings and communality of the retained items [Unmerged Responses]}
 
@@
 \end{longtable}
+
+\begin{figure}
+
+{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/EFAResidualsAppB-1}
+
+}
+
+\caption{ Histogram of residulas:  five-factor solution}(\#fig:EFAResidualsAppB)
+\end{figure}
 \end{appendix}

### 2021-11-06 manuscript.Rmd
Font issue remains unsolved in the appendix B

@@
       in_header: header.tex
-
-mainfont: Helvetica
 appendix:
@@
   - "Appendix-B.Rmd"
-
+mainfont: Helvetica
 ---
@@
 \endgroup
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('instrument.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('Appendix-B.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('instrument.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('Appendix-B.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('instrument.Rmd')
-```

### 2021-11-07 Appendix-B.Rmd
* Knitting with appendix is now possible.
The font issue rooted from Siraji's OS.

@@
 
-```{r facIdFigAppB, eval=FALSE, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot', warning=FALSE, include=FALSE, out.height="100%", out.width="100%"}
+```{r facIdFigAppB, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot', warning=FALSE,  out.height="100%", out.width="100%"}
 cowplot::plot_grid(parallel, scree.plot, labels = "AUTO",ncol=1, label_size = 8,align = "v")

### 2021-11-07 Appendix-B.tex
* Knitting with appendix is now possible.
The font issue rooted from Siraji's OS.

@@
 
-\caption{\label{tab:tabDesAppB}Descriptive Statistics for Unmerged response options}
+\caption{\label{tab:tabDesAppB-30}Descriptive Statistics for Unmerged response options}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-1}
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-32-1}
 
@@
 
-\caption{Correlation plot of the items}(\#fig:figCorAppB)
+\caption{Correlation plot of the items}(\#fig:figCorAppB-32)
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth,height=1\textheight]{manuscript_files/figure-latex/facIdFigAppB-36-1}
+
+}
+
+\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}(\#fig:facIdFigAppB-36)
 \end{figure}
@@
 
-\caption{\label{tab:EFATableAppB}Factor loadings and communality of the retained items [Unmerged Responses]}
+\caption{\label{tab:EFATableAppB-39}Factor loadings and communality of the retained items [Unmerged Responses]}
 
@@
 
-{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/EFAResidualsAppB-1}
+{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/EFAResidualsAppB-40-1}
 
@@
 
-\caption{ Histogram of residulas:  five-factor solution}(\#fig:EFAResidualsAppB)
+\caption{ Histogram of residulas:  five-factor solution}(\#fig:EFAResidualsAppB-40)
 \end{figure}

### 2021-11-07 manuscript.Rmd
* Knitting with appendix is now possible.
The font issue rooted from Siraji's OS.

@@
 
-\blandscape
-
 +-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
@@
 : Existing related Scales
-
-\elandscape
 
@@
 }
-cleanFolder()
+cleanFolder(y)
 ```
@@
 \endgroup
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('instrument.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('Appendix-B.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('instrument.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('Appendix-B.Rmd')
+```

### 2021-11-07 Appendix-B.tex
* supplementary analysis on EFA (Minimum residulas and six-factor solution) is added
Some minor formating here and there.

--- 2021-11-06 Appendix-B.tex
@@
 
-\caption{\label{tab:tabDesAppB}Descriptive Statistics for Unmerged response options}
+\caption{\label{tab:tabDesAppB-50}Descriptive Statistics for Unmerged response options}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-1}
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-52-1}
 
@@
 
-\caption{Correlation plot of the items}(\#fig:figCorAppB)
+\caption{Correlation plot of the items}(\#fig:figCorAppB-52)
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth,height=1\textheight]{manuscript_files/figure-latex/facIdFigAppB-56-1}
+
+}
+
+\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}(\#fig:facIdFigAppB-56)
 \end{figure}
@@
 
-\caption{\label{tab:EFATableAppB}Factor loadings and communality of the retained items [Unmerged Responses]}
+\caption{\label{tab:EFATableAppB-59}Factor loadings and communality of the retained items [Unmerged Responses]}
 
@@
 
-{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/EFAResidualsAppB-1}
+{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/EFAResidualsAppB-60-1}
 
@@
 
-\caption{ Histogram of residulas:  five-factor solution}(\#fig:EFAResidualsAppB)
+\caption{ Histogram of residulas:  five-factor solution}(\#fig:EFAResidualsAppB-60)
 \end{figure}

### 2021-11-07 Supplymentary.Rmd
* supplementary analysis on EFA (Minimum residulas and six-factor solution) is added
Some minor formating here and there.

--- 2021-11-06 manuscript.Rmd
@@
 ---
-title             : "_Light Exposure Behavior Assessment (LEBA)_: Development of a novel instrument to capture light exposure-related behaviours"
-shorttitle        : "LEBA"
-
-author: 
-  - name          : "Mushfiqul Anwar Siraji"
-    affiliation   : "1, *"
-    email         : "mushfiqul.anwarsiraji@monash.edu"
-    role:         
-      - Formal Analysis
-      - Visualization
-      - Writing – original draft
-      - Writing – review & editing;
-
-  - name          : "Rafael Robert Lazar"
-    affiliation   : "2, 3, *"
-    role:
-      - Data curation
-      - Investigation
-      - Project administration
-      - Visualization
-      - Writing – original draft
-      - Writing – review & editing;
-
-  - name          : "Juliëtte	van Duijnhoven"
-    affiliation   : "4"
-    email         : "j.v.duijnhoven1@tue.nl"
-    role:         
-      - Conceptualization
-      - Methodology
-      - Investigation
-      - Writing – review & editing
-
-  - name          : "Luc Schlangen"
-    affiliation   : "5"
-    email         : "l.j.m.schlangen@tue.nl"
-    role:         
-      - Conceptualization
-      - Methodology
-      - Investigation
-      - Writing – review & editing
-
-  - name          : "Shamsul Haque"
-    affiliation   : "1"
-    email         : "shamsul@monash.edu"
-    role:         
-      - Conceptualization
-      - Supervision
-      - Writing – review & editing
-
-  - name          : "Vineetha Kalavally"
-    affiliation   : "6"
-    email         : "vineetha@monash.edu"
-    role:         
-      - Supervision
-      - Writing – review & editing
-
-  - name          : "Céline Vetter"
-    affiliation   : "7, 8"
-    email         : "celine.vetter@colorado.edu"
-    role:         
-      - Conceptualization
-      - Writing – review & editing
-
-  - name          : "Gena Glickman"
-    affiliation   : "9"
-    email         : "gena.glickman@usuhs.edu"
-    role:         
-      - Conceptualization
-      - Methodology
-      - Writing – review & editing
-
-  - name          : "Karin Smolders"
-    affiliation   : "10"
-    email         : "k.c.h.j.smolders@tue.nl"
-    role:         
-      - Conceptualization
-      - Methodology
-      - Writing – review & editing
-
-  - name          : "Manuel Spitschan"
-    corresponding : yes
-    affiliation   : "11, 2, 3"
-    email         : "manuel.spitschan@psy.ox.ac.uk"
-    role:         
-      - Conceptualization
-      - Data curation
-      - Investigation
-      - Project administration
-      - Visualization
-      - Methodology
-      - Writing – original draft
-      - Writing – review & editing
-
-affiliation:
-  - id            : "1"
-    institution   : "Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
-  - id            : "2"
-    institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"
-  - id            : "3"
-    institution   : "University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland"
-  - id            : "4"
-    institution   : "Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands"
-  - id            : "5"
-    institution   : "Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Intelligent Lighting Institute, Eindhoven, Netherlands"
-  - id            : "6"
-    institution   : "Monash University, Department of Electrical and Computer Systems Engineering, Malaysia, Selangor, Malaysia"
-  - id            : "7"
-    institution   : "University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA"
-  - id            : "8"
-    institution   : "Ximes GmbH, Frankfurt, Germany"
-  - id            : "9"
-    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
-  - id            : "10"
-    institution   : "Eindhoven University of Technology, Human-Technology Interaction Group, Eindhoven, Netherlands"
-  - id            : "11"
-    institution   : "University of Oxford, Department of Experimental Psychology, Oxford, UK"
-  - id            : "*"
-    institution   : "Joint first author"
-
-authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
-
-abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
-
-keywords          : "keywords"
-wordcount         : "X"
-
-bibliography      : ["references.bib"]
-
-floatsintext      : no
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
-
-documentclass     : "apa6"
-classoption       : "man"
-output            : 
-  papaja::apa6_pdf:
-    latex_engine: xelatex
-    includes:
-      in_header: header.tex
-appendix:
-  - "instrument.Rmd"
-  - "Appendix-B.Rmd"
-mainfont: Helvetica
+title: "Supplimentary Analysis"
+output: pdf_document
 ---
 
-```{r setup, warning=FALSE, include=FALSE}
+```{r options, warning=FALSE, include=FALSE}
 knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600)
-options(knitr.duplicate.label = "allow")
 set.seed(123)
@@
 
-```{r depMan, include=FALSE}
-library(packrat)
-packrat::init(infer.dependencies = F)# install dependencies only for Rmd files in this project
+```{r MinRes, include=F}
+library(psych)
+library(tabledown)
+library(kableExtra)#without this pdf rendering will not happen
 
-#To find and install required dependencies.
-packrat::restore()
-#Only use when you have added some pack
-packrat::snapshot(ignore.stale=TRUE)
-
-```
-
-```{r install, eval=FALSE, include=FALSE}
-#if "packrat" does not work you can run this chunk manually to get all required packs"
-
-install.packages("devtools")
-install.packages("semTools")
-install.packages("MOTE")
-install.packages("psych")
-install.packages("lavaan")
-install.packages("dlookr")
-install.packages("tidyverse")
-install.packages("qgraph")
-install.packages("kableExtra")
-install.packages("paran")
-install.packages("EFA.MRFA")
-install.packages("rsvg")
-install.packages("ggcorrplot")
-install.packages("semTable")
-install.packages("magick")
-install.packages("mirt")
-install.packages("cowplot")
-install.packages("VIM")
-devtools::install_github('rich-iannone/DiagrammeR')
-devtools::install_github("crsh/papaja", force = T)
-install.packages("DiagrammeRsvg")
-devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
-devtools::install_github("crsh/citr")
-remotes::install_github("jthomasmock/gtExtras")
-install.packages("gt")
-
-install.packages("questionr")
-
-```
-
-```{r library, include=FALSE}
-
-library(papaja) # devtools::install_github("crsh/papaja")
-library(lavaan)
-library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
-library(semTools)
-library(MOTE)
-library(car)#revercoding 
-library(psych)
-library(dlookr)
-library(plyr)
-library(tidyverse)
-library(qgraph)
-library(kableExtra)
-library(paran) # Parallel analysis
-library(EFA.MRFA) # Hull method
-library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
-library(DiagrammeRsvg) #For DiagrammeR
-library(rsvg) #For DiagrammeR
-library(ggcorrplot)
-library(semTable)
-library(magick)
-library(mirt)
-library(gtsummary)
-library(gt)
-library(gtExtras)
-library(likert)
-library(VIM) #Missing data
-library(kutils)
-library(simsem)
-library(extrafont)
-extrafont::font_import()
-r_refs("references.bib")
-```
-
----
-nocite: |
-  `r cite_r("references.bib")`
----
-
-# Introduction
-
--   Light exposure is important
-
--   Light exposure Behavior is important
-
--   Table: Overview Existing Related Scales: items in total / items on light exposure (behaviour)
-
--   Existing Scales: Review them in text
-
--   None of these do light exposure behavior.
-
-\blandscape
-
-+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| Name                                                              | Authors                  | Description                                                                                                                                                  | Relevant Items                       | Adaptations |
-+===================================================================+==========================+==============================================================================================================================================================+======================================+=============+
-| Visual Light Sensitivity Questionnaire-8                          | [@verriotto2017new]      | Eight-question survey to assess the presence and severity of photosensitivity symptoms                                                                       | All items                            |             |
-+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| Office Light Survey                                               | [@eklund1996development] | Multi-item questionnaire to assess electrical lighting environment in office                                                                                 |                                      |             |
-+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| Harvard Light Exposure Assessment Questionnaire                   | [@bajaj2011validation]   | Self-administered semi-quantitative light questionnaire                                                                                                      | All Items                            |             |
-+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| Hospital Lighting Survey                                          | [@dianat2013objective]   | 23 items questionnaire to assess light environment in a hospital                                                                                             |                                      |             |
-+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| Morningness-Eveningness Questionnaire                             | [@horne1976self]         | 19 items questionnaire to understand your body clock                                                                                                         |                                      |             |
-+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| Munich Chronotype Questionnaire (MCTQ)                            | [@roenneberg2003life]    | 17 items questionnaire to understand individuals phase of entrainment                                                                                        |                                      |             |
-+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| Assessment of Sleep Environment                                   | [@Olivier.2016]          | 13 items questionnaire measuring your sleep environment quality                                                                                              |                                      |             |
-+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| The Pittsburgh Sleep Quality Index (PSQI)                         | [@buysse1989pittsburgh]  | 9 items inventory to measure sleep quality and sleeping pattern                                                                                              |                                      |             |
-+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| Self-Rating of Biological Rhythm Disorder for Adolescents (SBRDA) | [@Xie.2021]              | 29 items questionnaire assessing four dimensions of biological rhythm disorder in adolescents (digital media use, sleep, eating habits, and activity)        | Items 3., 22., 23., 24., 25.
-and 29.
-|             |
-+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| Photosensitivity Assessment Questionnaire (PAQ)                   | [@Wu.2017]               | 16 dichotomous (yes/no) items questionnaire to assess "photophobia" and "photophilia", giving two final scores of "photophobic" and "photophilic" behaviours | All items                            |             |
-+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-
-: Existing related Scales
-
-\elandscape
-
-# Methods
-
-## Ethical approval
-
-The cantonal ethics commission (Ethikkommission Nordwest- und Zentralschweiz, project ID Req-2021-00488) reviewed this project and issued an official clarification of responsibility (full document see Suppl.
-Fig X in appendix) stating: "The research project does not fall under the scope of the Human Research Act, because your project is using only anonymised data.
-An authorisation from the ethics committee is therefore not required and the EKNZ is not responsible for its review."
-
-## Data Availability
-
-## Survey characteristics
-
-Data was collected in a quantitative cross-sectional approach via a fully anonymous online survey hosted on REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel (sciCORE; <https://redcap.scicore.unibas.ch/>).
-Participants were recruited via the website of a Comic co-released with the survey[@Weinzaepflen.2021; <https://enlightenyourclock.org/participate-in-research/>], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux software [@f.lux].
-
-Completing the online survey took approx.
-15 to 20 minutes and was not compensated.
-The first page of the survey comprised a participant information sheet, where participants' informed consent to participate was obtained before any of the questions were displayed.
-Underaged participants (\<18 years) were urged to obtain assent from their parents/legal guardians, before filling in the survey.
-Information on the first page included the objectives of the study, inclusion criteria, estimated duration, the use, storage and sharing of the data, compensation (none), and information about the type of questions in the survey.
-Moreover, participants needed to confirm that they were participating the survey for the first time.
-To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention.
-What is 4+5?").
-The data analysed in this study was collected between 17.05.2021 and 03.09.2021.
-Questions incorporating retrospective recall were all aligned to the period of "past four weeks", matching the presented LEBA instrument.
-
-In addition to the LEBA questionnaire, which is subject of the current study, the following variables and items were assessed but not included in the analysis:
-
--   Sleep disturbance and sleep-related impairment (adult and pediatric versions) [@Bevans.2019; @Buysse.2010; @Forrest.2018; @Harb.2015; @Yu.2011]
--   Sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration (version for adults and adolescents) [@roenneberg2003life]
--   Sleep environment [@Olivier.2016]
--   Meal timing & caffeine consumption [custom items]
--   Light sensitivity (photophobia vs. photophilia) [@Wu.2017]
--   Self-reported pubertal stage (only if younger than 18 years old) [@Petersen.1988]
-
-Furthermore, the following 1-item demographic variables were assessed:
-
--   Age
--   Sex
--   Gender identity
--   Occupational Status
--   COVID-19 related Occupational setting during the past four weeks
--   Time zone & country of residence
--   English as native language
-
-## Participants
-
-```{r Data, include=FALSE}
 data <- readRDS("leba_2021-09-08.rds")
@@
 colnames(sem.data) <- colnam
-```
 
-```{r prepareDescTable, include=FALSE}
-
-listdescVars <- colnames(descriptives.data[c(1:3,5:7)])
-
-#seperating naming and  reducing data for descriptive Table 
-desctable.data <- select(descriptives.data, c(listdescVars,
-                          IncludedInCFA))
-
-#renaming TRUE and FALSE from the IncludedInCFA to EFA and CFA for Descriptive Table
-desctable.data$IncludedInCFA[desctable.data$IncludedInCFA == T ] <-
- "2. CFA Sample"
-desctable.data$IncludedInCFA[desctable.data$IncludedInCFA == F ] <- 
- "1. EFA Sample"
-
-# recode the Gender factor so it will only show "Gender Diverse" in the summary table
-desctable.data$slypos_demographics_gender.factor <-
-  recode_factor(desctable.data$slypos_demographics_gender.factor, "No" = "Yes",
-         "Yes"= "No")
-
-# create descriptive table for the demographic vars (excluding tz & Country) with gtsummary
-desctable.data %>%
-  tbl_summary(
-    by = IncludedInCFA,
-    statistic = list(all_continuous() ~ "{mean} ({sd})",
-                     all_categorical() ~ "{n} ({p}%)"),
-    digits = all_continuous() ~ 2,
-    label = list(slypos_demographics_age ~ "Age",
-                 slypos_demographics_sex.factor ~ "Sex",
-                 slypos_demographics_gender.factor ~ "Gender-Variant Identity",
-                 slypos_demographics_language.factor ~ "Native English Speaker",
-                 slypos_demographics_work_or_school.factor ~ "Occupational Status",
-                 slypos_demographics_school.factor ~ "Occupational setting"
-                 ),
-    missing = "no"
-    ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
-modify_header(label ~ "**Variable**") -> desc_table
-
-as_tibble(desc_table) -> desc_tibble 
-as_kable(desc_table, format = 'pipe') -> desc_kable #save it as a knitr::kable
-
-#as_kable_extra(desc_table) -> desc_kable_extra
-```
-
-```{r DescTabPrint, results='asis'}
-
-desc_kable %>% kable_styling(desc_kable, repeat_header_text = "Participants' Demographic Characteristics")
-
-```
-
-Table 1 summarizes the survey participants' demographic characteristics.
-Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses.
-XX participants were excluded from analysis due to not passing at least one of the "attention check" items.
-For exploring initial factor structure (EFA) , a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013].
-For estimating the sample size for the confirmatory factor analysis (CFA) we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per parameter is required to earn trustworthiness of the result.
-Our sample size exceeds these requirements: Anonymous responses from a total of *n* = `r nrow(desctable.data)` participants were included in the analysis of the current study, split into samples for exploratory (EFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "1.
-EFA Sample",])`) and confirmatory factor analysis (CFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "2.
-CFA Sample",])`).
-The EFA sample included participants filling out the questionnaire from 17.05.2021 to XX.XX.XXXX , whereas participants who filled out the questionnaire from YY.YY.YYYY to 03.09.2021 were included in the CFA analysis.
-Participants indicated filling out the online survey from a diverse range of geographic locations.
-The four most common geographic locations included:
-
-`r kable(head(summary(descriptives.data$slypos_demographics_tz.factor), 4), format = "latex")`
-
-For a full list of geographic locations, see Suppl. Table X in the appendix.
-
-Age among all participants ranged from `r min(desctable.data$slypos_demographics_age)` years to `r max(desctable.data$slypos_demographics_age)` years [EFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
-EFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
-EFA Sample"])`; CFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`], with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 0)` years of age [Overall: *M* = `r mean(desctable.data$slypos_demographics_age)`, *SD* = `r sd(desctable.data$slypos_demographics_age)`; EFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
-EFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
-EFA Sample"])`; CFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`].
-In total `r desc_tibble[3,2]` of the participants indicated female sex [EFA: `r desc_tibble[3,3]`; CFA: `r desc_tibble[3,4]`], `r desc_tibble[4,2]` indicated male [EFA: `r desc_tibble[4,3]`; CFA: `r desc_tibble[4,4]`] and `r desc_tibble[5,2]` indicated other sex [EFA: `r desc_tibble[5,3]`, CFA: `r desc_tibble[5,4]`].
-Overall, `r desc_tibble[6,2]` [EFA: `r desc_tibble[6,3]`; CFA: `r desc_tibble[6,4]`] participants indicated a gender-variant identity.
-In a "Yes/No" question regarding native language, `r desc_tibble[7,2]` of respondents [EFA: `r desc_tibble[7,3]`; CFA: `r desc_tibble[7,4]`] indicated to be native English speakers.
-For their "Occupational Status", more than half of the overall sample reported that they currently work [Overall: `r desc_tibble[9,2]`; EFA: `r desc_tibble[9,3]`; CFA: `r desc_tibble[9,4]`], whereas `r desc_tibble[10,2]` [EFA: `r desc_tibble[10,3]`; CFA: `r desc_tibble[10,4]`] reported that they go to school and `r desc_tibble[11,2]` [EFA: `r desc_tibble[11,3]`; CFA: `r desc_tibble[11,4]`] responded that they do "Neither".
-With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` [EFA: `r desc_tibble[13,3]`; CFA: `r desc_tibble[13,4]`] of the participants indicated that they were in a home office/ home schooling setting., while `r desc_tibble[14,2]` overall [EFA: `r desc_tibble[14,3]` ; CFA: `r desc_tibble[14,4]`] reported face-to-face work/schooling.
-Lastly, `r desc_tibble[15,2]` overall [EFA: `r desc_tibble[15,3]` ; CFA: `r desc_tibble[15,4]`] reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]` overall [EFA: `r desc_tibble[16,3]`; CFA: `r desc_tibble[16,4]`] filled in the "Neither (no work or school, or indication)" response option.
-We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable "Age" and Pearson's Chi-squared test for all other categorical variables via the gtsummary R package's "add_p" function [@sjoberg2021] .
-The p-values were corrected for multiple testing applying false discovery rate (FDR) via the "add_q" function of the same package.
-After p-value (FDR) correction for multiple testing, none of the demographic variables were significantly different between the EFA sample and the CFA sample (all q-values *q* ≥ `r min(desc_tibble$"**q-value**", na.rm=T)` , indicating equivalence).
-
-1.  Describe EFA and CFA sample separately.
-2.  Sampling technique: Convince sampling (non-probability sample)
-3.  Method: cross-sectional survey
-4.  How many missing data?
-5.  How incomplete data were addressed.
-6.  Why such sample was chosen?
-
-## Procedure
-
-### Development of the Scale
-
-1.  How the items were generated
-2.  How the literature was reviewed to identify construct adequacy of the items.
-3.  Discuss the expert panel review process to assess content validity
-
-```{r Manuflowchart, include=FALSE }
-Flowchart1 <- grViz("digraph nicegraph{
-
-                    graph [fontname = Helvetica,layout = dot,fontsize = 20, ]
-
-                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 6.5, height = 1, 
-                    fixedsize = true,fontsize = 20]
-
-                    A[label = '48 items were generataed by a robust expert panel'] 
-                    B[label = 'Exploratory Factor Analysis on 48 Items (N = 428)']
-
-                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 7.5, height = 2, 
-                    fixedsize = true, fontsize = 20]
-                    C[label = 
-                    <
-                    Factor Identification<br align = 'left'/>
-                    Scree Plot: 6 Factors<br align = 'left'/>
-                    Parallel Analysis: 6 Factors<br align = 'left'/>
-                    Minimum Average Partial Method: 5 Factors<br align = 'left'/>
-                    Hull Method: 5 Factors<br align = 'left'/>
-                    >
-                    ]
-
-                     subgraph cluster_1 {
-                      graph[fontname = Helvetica, shape = rectangle]
-                      style = rounded
-                     node[fontname = Helvetica, margin = 0.2,width = 9, height = 1, 
-                    fixedsize = true, fontsize = 18 ]
-
-                     1[label = '5 Factor Solution Retained 25 Items']
-                     2[label = 'Reliability Analysis on EFA Sample (N=428)
-                    Alpha F1 =.86; F2 = .71; F3 = .68; F4 =.62; F5 =.52']
-
-                     3[label = 'Confirmatory Factor Analysis 
-                     on the Five Factor Model (25 Items; N=262)
-                      Acceptable Fit ( CFI = .94; TLI .93; RMSEA = .06, SRMR = .11)']
-
-                    4[label = 'Confirmatory Factor Analysis 
-                     on the Five Factor Model (23 Items; N=262)
-                      Acceptable Fit ( CFI = .97; TLI .96; RMSEA = .04, SRMR = .09)']
-                     5[label = 'Reliability Analysis on CFA (23 Items; N=262) 
-                      Alpha F1=.93; F2=.80; F3 =.62; F4=.72; F5=.45']
-                    }
-                subgraph cluster_2 {
-                      graph[fontname = Helvetica,shape = rectangle]
-                      style = rounded
-                     node[fontname = Helvetica, margin = 0.2,width = 8, height = 1, 
-                fixedsize = true, fontsize = 18 ]
-                    6[label = '6-Factor solution: one factor emerged with only two salient loadings']
-                    7[label = 'Rejected']
-                    }
-
-                     edge[fontname = Helvetica,color = black,arrowhead = vee, arrowsize = 1.25]
-                     A ->B
-                     B ->C
-                     C ->1
-                     1 ->2
-                     2 ->3
-                     3 ->4
-                     4 ->5
-                     C ->6
-                     6 ->7
-
-}")
-
-export_svg(Flowchart1) %>%
-  charToRaw() %>%
-  rsvg() %>%
-  png::writePNG("Manuscript.figures/Flowchart1.png")
-
-```
-
-```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development', out.height='100%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/Flowchart1.png')
-```
-
-### Data Collection
-
-Timeline of data collection, mode of data collection.
-
-## Analytic Strategies
-
-We used R (version 4.1.0), including several R packages, for our analyses.
-Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
-Our data violated both the univariate and multivariate normality assumptions.
-Due to these violations and the ordinal nature of our response data, we used a polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA.
-We employed principal axis (pa), a factor extraction method with varimax rotation.
-PA is robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020].
-The obtained latent structure was confirmed by the minimum residuals extraction method as well.
-We used a combination factor identification method including scree plot[@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method[@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
-Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018;
-
-# Results
-
-## Exploratory Factor Analysis
-
-```{r ggplot2, include=F}
-apatheme=theme_bw()+
-  theme(panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank(),
-        panel.background = element_blank(),
-        text=element_text(family = "Helvetica",),
-        legend.title=element_blank(),
-        axis.line.x = element_line(color='black'),
-        axis.line.y = element_line(color='black'),
-        panel.border = element_rect(color = "black",
-                                    fill = NA,
-                                    size = 1))
-```
-
-```{r EFAdata, include=FALSE}
 ### EFA data
 EFA.data <- sem.data[1:428, ]
-#library(VIM)
-missing <- aggr(EFA.data, plot =T)
-
-```
-
-```{r EFAassumptions, include=FALSE}
-
-#KMO test
-KMO <- KMO(EFA.data)
-
-# Test of correlation matrix
-bartlet <- cortest.bartlett(EFA.data, n =428)
-
-#Histogram
-#psych::multi.hist(EFA.data[,sapply(EFA.data, is.numeric)])
-
-# Univariate normality
-
-#creating normality function
-shapiro_test_df <- function(df, bonf= TRUE, alpha= 0.05) {
-  l <- lapply(df, shapiro.test)
-  s <- do.call("c", lapply(l, "[[", 1))
-  p <- do.call("c", lapply(l, "[[", 2))
-  if (bonf == TRUE) {
-    sig <- ifelse(p > alpha / length(l), "H0", "*")
-  } else {
-    sig <- ifelse(p > alpha, "H0", "*")
-  }
-  return(list(statistic= s,
-              p.value= p,
-              significance= sig,
-              method= ifelse(bonf == TRUE, "Shapiro-Wilks test with Bonferroni Correction",
-                             "Shapiro-Wilks test without Bonferroni Correction")))
-}
-
-Shapiro.efa <- shapiro_test_df(EFA.data)
-
-efa.normality.tab = matrix(nrow = 48, ncol = 2)
-rownameprefix <- "Item"
-rownamesufix <- seq(1:48)
-my.item.names <- paste(rownameprefix,rownamesufix, sep = "" )
-rownames(efa.normality.tab) <- my.item.names
-colnames(efa.normality.tab) <- c("statistic", "p")
-
-efa.normality.tab[,1] <- apa(Shapiro.efa$statistic,2,T)
-efa.normality.tab[,2] <- apa(Shapiro.efa$p.value,2,T)
-
-efa.normalityprefix <- efa.normality.tab[,1]
-efa.normalitysufix <- Shapiro.efa$significance
-efa.normality.stat <- paste(efa.normalityprefix,efa.normalitysufix, sep = "" )
-
-# Multivariate Normality
-mardia <- mardia(EFA.data, na.rm = T, plot =F)
-
-# Descriptive Stats
-Descriptives <- psych::describe(EFA.data)
-alpha <- psych::alpha(EFA.data)
-Item.total <- alpha$item.stats
-
-Des.combined <- cbind(apa(Descriptives$mean,2,T), apa(Descriptives$sd,2,T), apa(Descriptives$skew,2,T),apa(Descriptives$kurtosis,2,T), efa.normality.stat,  apa(Item.total$r.cor,2,F))
-
-colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics","Item-Total Correlation")
-rownameprefix <- "Item"
-rownamesufix <- seq(1:48)
-my.names <- paste(rownameprefix,rownamesufix, sep = "" )
-rownames(Des.combined) = (my.names)
-```
-
-```{r CorrMatrix, include=FALSE}
 #Polychoric Correlation matrix
 
-correlations <- polychoric(EFA.data, correct = 0)
-upper <- correlations$rho[upper.tri(correlations$rho, diag = F)]
-
-min.cor <- abs(min(upper)) #minimum cor.coefficient of the matrix
-max.cor <- abs(max(upper)) # max. correlation coefficient of the matrix
-
-determinets <- det(correlations$rho) 
-# Calculating the percentage of correlations higher than .30
-
-BigR = sum(correlations$rho >= abs(.30) & correlations$rho < abs(1.0), na.rm =T)/2 
-totR = length(EFA.data)*(length(EFA.data)-1)/2
-cor.per <- print (BigR/totR)*100
-```
-
-```{r ItemAnalysis, include=FALSE}
-# Item analysis
-Item_analysis <- psych::alpha(EFA.data)
-Item_analysis$item.stats$r.cor
-R.cor.sum <- summary(Item_analysis$item.stats$r.cor)
-low.r.corec <- abs(R.cor.sum[1])  #minimum item total correlation
-high.r.corec <- R.cor.sum[6]     # maximum item total correlation
-```
-
-Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy[@kaiserIndexFactorialSimplicity1974] .
-The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cutoff value (.50) indicating a mediocre sample [@hutchesonMultivariateSocialScientist1999].
-Table\@ref(tab:tabDes) summarizes the univariate descriptive statistics for the 48 items.
-some of the items were skewed with high Kurtosis values.
-Our data violated both univariate normality (Shapiro-Wilk statistics; [@shapiroAnalysisVarianceTest1965]) and multivariate normality assumptions (Marida's test;[@mardiaMeasuresMultivariateSkewness1970]).
-Multivariate skew was = `r printnum(mardia$b1p)` (p \<0.001) and multivariate kurtosis was = `r printnum(mardia$b2p)` (p \<0.001).
-Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018].
-Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p \< .001] indicated the correlations between items are adequate for the EFA.
-However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than .30.
-The inter item correlation ranged between `r apa(min.cor,2,F)` to `r apa(max.cor,2,F)`.
-And the corrected item-total correlations ranged between `r apa(low.r.corec,2,F)` to `r apa(high.r.corec,2,F)`.
-
-```{r tabDes,results='asis'}
-apa_table(Des.combined, caption = "Descriptive Statistics", align = "c", note = "*p<.001", longtable =T)
-```
-
-```{r figCor, out.width="100%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}
-
-ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
-           ggtheme = ggplot2::theme_minimal, tl.cex = 6,tl.srt = 90 )
-#p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
-#to show pvalue in the fig add p.mat=p.mat
-```
-
-```{r ParallelEFA, include=FALSE}
-
-# Parallel analysis
-Horn <- paran(correlations$rho, iterations=500, centile=0, quietly=FALSE,
-           status=TRUE, all=FALSE, cfa=FALSE, graph=TRUE,
-           color=TRUE, col=c("black","red","blue"),
-           lty=c(1,2,3), lwd=1, legend=TRUE, 
-           width=640, height=640, grdevice=png, seed=0, mat=NA, n=NA)
-
-Adjusted.EV <- data.frame(Horn$AdjEv)
-Adjusted.EV$type = c('Adjusted Ev')
-Adjusted.EV$num = c(row.names(Adjusted.EV))
-Adjusted.EV$num = as.numeric(Adjusted.EV$num)
-colnames(Adjusted.EV) = c('eigenvalue', 'type', 'num')
-
-Random.EV <- data.frame(Horn$RndEv)
-Random.EV$type = c('Random EV')
-Random.EV$num = c(row.names(Random.EV))
-Random.EV$num = as.numeric(Random.EV$num)
-colnames(Random.EV) = c('eigenvalue', 'type', 'num')
-
-Unadjusted.EV <- data.frame(Horn$Ev)
-Unadjusted.EV$type = c('Unadjusted EV')
-Unadjusted.EV$num = c(row.names(Unadjusted.EV))
-Unadjusted.EV$num = as.numeric(Unadjusted.EV$num)
-colnames(Unadjusted.EV) = c('eigenvalue', 'type', 'num')
-
-parallel = ggplot(Adjusted.EV, aes(x=num, y=eigenvalue, shape=type, color=type)) +
-  #Add lines connecting data points
-  geom_line()+
-    geom_line(data = Random.EV) +
-  geom_line(data = Unadjusted.EV)+
-    #Add the data points.
-  geom_point(size=1)+
-  geom_point(data = Random.EV, size=1)+
-  geom_point(data = Unadjusted.EV, size=1)+
-  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
-   #Label the x-axis 'Factor Number', and ensure that it ranges from 1-max # of factors, increasing by one with each 'tick' mark.
-  scale_x_continuous(name='Factor Number', limits=c(0, 48),breaks=seq(0,48,4))+
-    #Add vertical line indicating parallel analysis suggested max # of factors to retain
-  geom_hline(yintercept=1, linetype = 'dashed') + apatheme
-
-```
-
-```{r ScreePlot, include=FALSE}
-Scree <- scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
-      hline=NULL,add=F)
-
-FA.Scree <- data.frame(Scree$fv)
-FA.Scree$type = c('Factor Analysis')
-FA.Scree$num = c(row.names(FA.Scree))
-FA.Scree$num = as.numeric(FA.Scree$num)
-colnames(FA.Scree) = c('eigenvalue', 'type', 'num')
-
-PA.Scree <- data.frame(Scree$pcv)
-PA.Scree$type = c('Principal Component Analysis')
-PA.Scree$num = c(row.names(PA.Scree))
-PA.Scree$num = as.numeric(PA.Scree$num)
-colnames(PA.Scree) = c('eigenvalue', 'type', 'num')
-
-scree.plot <-ggplot(FA.Scree, aes(x=num, y=eigenvalue,color=type, shape=type))+
-   geom_line()+
-  geom_line(data = PA.Scree)+ 
-  geom_point(size=1)+
-  geom_point(data = PA.Scree, size=1)+
-  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
-  scale_x_continuous(name='Factor Number', limits=c(0, 48),breaks=seq(0,48,4))+
-  geom_hline(yintercept=1, linetype = 'dashed') + apatheme 
-```
-
-```{r HullEFA, include=FALSE}
-# HULL
-hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
-        details = TRUE)
-hull <- ggplot2::last_plot()
-Hull <- hull+ ggtitle(NULL) +xlab("Factor Number")+ylab("CAF")+ 
-  apatheme +scale_color_manual(labels = c("Out side the convex Hull", "On the convex Hull"), values = c("red", "cyan2")) 
-```
-
-```{r MAPefa, include=FALSE}
-#MAP
-psych::VSS(EFA.data, rotate = "varimax", fm = 'minres', n.obs =428 )
-```
-
-Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution.
-Horn's parallel analysis [@hornRationaleTestNumber1965] with 500 iterations also indicated a six-factor solution.
-However, the MAP method [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] suggested a five-factor solution.
-As a result, we tested both five-factor and six-factor solutions.
-
-```{r facIdFig, out.height="200%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}
-cowplot::plot_grid(parallel, scree.plot,Hull, labels = "AUTO",ncol=1, label_size = 8,align = "v")
-
-```
-
-```{r EFA, include=FALSE}
-fa.5F.1 <- fa(r=correlations$rho, nfactors = 5, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-AA <- print(fa.5F.1, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.5F.1 <- dplyr::select(EFA.data ,
-                                    -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14))
-
-correlations.red.5F.1 <- polychoric(reduced.model.5F.1,correct = 0)
-
-fa.5F.2 <- fa(r=correlations.red.5F.1$rho, nfactors = 5, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-BB <- print(fa.5F.2, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.5F.2 <- dplyr::select(EFA.data, -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14, item34, item47, item21, item13))
-
-correlations.red.5F.2 <- polychoric(reduced.model.5F.2,correct = 0)
-
-fa.5F.3 <- fa(r=correlations.red.5F.2$rho, nfactors = 5, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428,max.iter = 500 )
-
-CC <- print(fa.5F.3, cut = .3, digits = 3, sort = TRUE)
-
-var1 <- CC$Vaccounted[2,1]*100
-var2 <- CC$Vaccounted[2,2]*100
-var3 <- CC$Vaccounted[2,3]*100
-var4 <- CC$Vaccounted[2,4]*100
-var5 <- CC$Vaccounted[2,5]*100
-```
-
-```{r EFAplotcode, include=FALSE}
-
-EFAplot <- grViz("
-digraph boxes_and_circles {
-
-graph [layout = dot,rankdir = LR, fontsize = 40]
-
-# node definitions with substituted label text
-node [fontname = Helvetica, shape = circle,  margin = 0.5, width = 3.5, height = .5,
-fixedsize = true, fontsize = 35]
-F5 [label = 'F5']
-F4 [label = 'F4']
-F3 [label = 'F3']
-F2 [label = 'F2']
-F1 [label = 'F1']
-
-node [fontname = Helvetica, shape = box]
-b [label = 'item16']
-c [label = 'item36']
-d [label = 'item17']
-e [label = 'item11']
-f [label = 'item10']
-g [label = 'item12']
-h [label = 'item7']
-i [label = 'item8']
-j [label = 'item9']
-k [label = 'item27']
-l [label = 'item3']
-m [label = 'item40']
-n [label = 'item30']
-o [label = 'item41']
-p [label = 'item33']
-q [label = 'item32']
-r [label = 'item35']
-s [label = 'item37']
-t [label = 'item38']
-u [label = 'item46']
-v [label = 'item45']
-w [label = 'item25']
-x [label = 'item4']
-y [label = 'item1']
-z [label = 'item26']
-
-{rank = same; F1 F2 F3 F4 F5}
-# edge definitions with the node IDs
-edge [fontname = Helvetica, fontsize = 35]
-F5 -> u [label = '0.60']
-F5 -> v [label = '0.59']
-F5 -> w [label = '0.41']
-F5 -> x [label = '0.41']
-F5 -> y [label = '0.40']
-F5 -> z [label = '0.35']
-F4 -> p [label = '0.74']
-F4 -> q [label = '0.73']
-F4 -> r [label = '0.66']
-F4 -> s [label = '-0.39', color =red]
-F4 -> t [label = '0.39']
-F3 -> k [label = '0.80']
-F3 -> l [label = '0.80']
-F3 -> m [label = '0.65']
-F3 -> n [label = '0.49']
-F3 -> o [label = '36']
-F2 -> e [label = '0.79']
-F2 -> f[label = '0.76']
-F2 -> g [label = '0.65']
-F2 -> h[ label = '0.50']
-F2 -> i [label = '-.49',color =red]
-F2 -> j [label = '0.32']
-F1 -> b[label = '0.99']
-F1-> c [label = '0.93']
-F1-> d [label = '0.80']
-}
-")
-
-export_svg(EFAplot) %>%
-  charToRaw() %>%
-  rsvg() %>%
-  png::writePNG("Manuscript.figures/EFAplot.png")
-
-```
-
-```{r EFAplot, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, out.height="50%", out.width="100%", results='asis'}
-knitr::include_graphics('Manuscript.figures/EFAplot.png')
-
-```
-
-```{r Cronbach alpha for 5 fators, message=TRUE, warning=FALSE, include=FALSE}
-
-Five.F1 <- dplyr::select(EFA.data, item16, item36, item17)
-Five.F2 <- dplyr::select(EFA.data, item11, item10, item12, item7, item8, item9) 
-Five.F3 <-  dplyr::select(EFA.data, item27, item3,item40, item30, item41)
-Five.F4 <-  dplyr::select(EFA.data, item33,item32,item35, item37, item38)
-Five.F5 <- dplyr::select(EFA.data, item46, item45, item25, item4, item1, item26)
-
-Five.F1.alpha <- psych::alpha(Five.F1, check.keys = T) 
-Five.F2.alpha <- psych::alpha(Five.F2, check.keys = T)
-Five.F3.alpha <- psych::alpha(Five.F3, check.keys = T)
-Five.F4.alpha <- psych::alpha(Five.F4, check.keys = T) 
-Five.F5.alpha <- psych::alpha(Five.F5, check.keys = T)
-
-F1.alpha <- Five.F1.alpha$total$raw_alpha
-F2.alpha <- Five.F2.alpha$total$raw_alpha
-F3.alpha <- Five.F3.alpha$total$raw_alpha
-F4.alpha <- Five.F4.alpha$total$raw_alpha
-F5.alpha <- Five.F5.alpha$total$raw_alpha
-```
-
-```{r minres 5 factor supplimentary analyisis, eval=FALSE, include=FALSE}
+correlations <- psych::polychoric(EFA.data, correct = 0)
 
@@
 GG <- print(fa.5F.min.3, cut = .3, digits = 3, sort = TRUE)
+
+minresTab <- tabledown::fac.tab(fa.5F.min.3, cut =.3,complexity = F)
 ```
 
-```{r EFA 6 Factors Promax, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, results='hide'}
+```{r MinResTab}
+papaja::apa_table(minresTab, align = "c", caption = "Factor loadings and communality of the retained items(Minmum Residual)", note = "Only loading higher than .30 is reported", font_size = "small")
+
+```
+
+```{r sixFac, include=F}
 # EFA with 6 factor (rejected)
@@
 abline(v =.05,lwd = 2, lty = 2)
+sixFac <- tabledown::fac.tab(fa.6F.3, cut =.3,complexity = F)
 ```
 
-```{r factordetails, include=FALSE}
-#Preparing the EFA table
-library(data.table)
-fa_table <- function(x, cut) {
-  #get sorted loadings
-  loadings <- fa.sort(x)$loadings %>% round(2)
-  #supress loadings
-  loadings[abs(loadings) < abs(cut)] <- ""
-  #get additional info
-  add_info <- cbind(x$communality, 
-                    x$uniquenesses,
-                    x$complexity) %>%
-    # make it a data frame
-    as.data.frame() %>%
-    # column names
-    rename("Communality" = V1,
-           "Uniqueness" = V2,
-           "Complexity" = V3) %>%
-    #get the item names from the vector
-    rownames_to_column("item")
-  #build table
-  loadings <- loadings %>%
-    unclass() %>%
-    as.data.frame() %>%
-    rownames_to_column("item") %>%
-    left_join(add_info) %>%
-    mutate(across(where(is.numeric), round, 3)) %>% 
-    as.data.frame()
-  variance <- x$Vaccounted %>% 
-  as.data.frame()%>% 
-  round(2)
-  loadings <- rbind(setDT(loadings), setDT(variance[2,]), fill=TRUE)
-
-}
-
-efa.table <- fa_table(fa.5F.3,.3) 
-nr <- nrow(efa.table)
-efa.table[nr, 1] <- "% of Variance"
-
-#Communality
-Fac.5 <- fa.5F.3
-min.com <- min(Fac.5$communality)
-max.com <- max(Fac.5$communality)
-
-# loading
-min.loadings <- min(Fac.5$loadings)
-max.loadings <- max(Fac.5$loadings)
-
-# Residuals
-residual.5F =residuals(fa.5F.3, diag = FALSE, na.rm =T)
-#Count of numbers of residuals>.05
-BigRR= sum(residual.5F>abs(.05), na.rm =T)
-print(BigRR)
-
-#Total number of off diagonal elements in the data matrix
-totRR = length(reduced.model.5F.2)*(length(reduced.model.5F.2)-1)/2
-
-# Proportion of off-diagonal elements >.10
-sumR <- sum(BigRR/totRR*100)
-
+```{r sixFacTab}
+papaja::apa_table(sixFac, align = "c", caption = "Factor loadings and communality of the retained items(six factor)", note = "Only loading higher than .30 is reported", font_size = "small")
 ```
-
-Three rounds of EFA with all 48 items were conducted, and problematic items were gradually discarded (cross-loading items and poor factor loading (\<.30) items).
-Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 [@brownConfirmatoryFactorAnalysis2015], all factor-loading higher than .30 and no cross-loading greater than .30.
-We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (see the supplementary).
-Table\@ref(tab:TabEFA5) displays the factor-loading (structural coefficients) and communality of the items.
-The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients.
-The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`.
-However, the histogram of the absolute values of non-redundant residual-correlations (Fig\@ref(fig:Residuals) showed `r apa(sumR,2, T)`% correlations greater than the absolute value of .05, indicating a possible under-factoring.
-[@desjardinsHandbookEducationalMeasurement2018a].
-Subsequently, we fitted a six-factor solution.
-However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution.
-
-In the five-factor solution, the first factor contained three items and explained `r apa(var1,2,F)`% of the total variance with a satisfactory internal reliability coefficient ($\alpha$ = `r apa(F1.alpha,2,F)`).
-All the items in this factor stemmed from the individual's preference to use blue light filters in different light environments.
-The second factor contained six items and explained `r apa(var2,2,F)`% of the total variance with a satisfactory internal reliability coefficient ($\alpha$ = `r apa(F2.alpha,2,F)`).
-Items under this factor commonly investigate an individual's hours spent outdoor.
-The third factor contained five items and explained `r apa(var3,2,F)`% of the total variance.
-Items under this factor dealt with the specific behaviors pertaining to sleep.
-However, the internal consistency reliability coefficient was not satisfactory ($\alpha$ = `r apa(F3.alpha,2,F)`).
-The fourth factor contained five items and explained `r apa(var4,2,F)`% of the total variance with an internal consistency coefficient, $\alpha$ = `r apa(F4.alpha,2,F)`.
-These five items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time.
-Lastly, the fifth factor contained six items and explained `r apa(var5,2,F)`% of the total variance.
-This factor tried to measure an individual's behavior lead by the awareness of light's influence on health.
-However, this factor showed unsatisfactory internal consistency reliability ($\alpha$ = `r apa(F5.alpha,2,F)`).
-It is essential to attain a balance between psychometric properties and the interpretability of the common themes when exploring the latent structure.
-As all of the emerged factors are highly interpretable, regardless of the apparent low reliability of the two factors, we retain the five-factor solution with 23 items for our confirmatory factor analysis (CFA).
-Two items showed negative factor-loading (items 44 and 21).
-Upon inspection, it was understood that these items are negatively correlated to the common theme, and thus in the CFA analysis, we reversed the response code for these two items.
-
-```{r EFATable, results='asis'}
-
-apa_table(efa.table,align = "c", caption = "Factor loadings and communality of the retained items", note = "Only loading higher than .30 is reported", font_size = "small")
-```
-
-```{r EFAResiduals, out.height= "50%",  fig.align='center', fig.cap= ' Histogram of residulas:  five-factor solution',  out.width="50%",  warning=FALSE, results='asis'}
-hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))
-abline(h =51, lwd = 2, lty = 2)
-abline(v =.05,lwd = 2, lty = 2)
-
-```
-
-```{r gtvis, include =F}
-## Recoding sem.data$item8
-gt.data <- sem.data
-gt.data$item8 <- as.character(gt.data$item8)
-gt.data$item8 <- fct_recode(gt.data$item8,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-
-## Recoding gt.data$item26
-gt.data$item26 <- as.character(gt.data$item26)
-gt.data$item26 <- fct_recode(gt.data$item26,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-## Recoding gt.data$item37
-gt.data$item37 <- as.character(gt.data$item26)
-gt.data$item37 <- fct_recode(gt.data$item26,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-
-names(gt.data)[names(gt.data) == "item1"] <- "item01"
-names(gt.data)[names(gt.data) == "item3"] <- "item03"
-names(gt.data)[names(gt.data) == "item4"] <- "item04"
-names(gt.data)[names(gt.data) == "item7"] <- "item07"
-names(gt.data)[names(gt.data) == "item8"] <- "item08"
-names(gt.data)[names(gt.data) == "item9"] <- "item09"
-
-#EFA data
-gt.efa.data <- gt.data[1:428, ]
-
-gt.efa.data.table <- gt.efa.data %>% 
-  dplyr::select(item16, item36, item17,
-                 item11, item10,item12,item07,item08,item09,
-                 item27,  item03, item40,  item30, item41,
-                 item33, item32,item35, item37,item38, 
-                 item46, item45, item25, item04, item01,item26)
-
-#Creating long data
-gt.efa.long <- as.data.frame(gather(gt.efa.data.table, Items, value))
-gt.efa.long$value <- as.numeric(as.character(gt.efa.long$value))
-
-#Summarizing and creating gt object
-gt.efa.tab <- gt.efa.long %>% 
-  group_by(Items) %>% 
-  # calculate summary stats & create data for the histogram and density plot
-  dplyr::summarise(
-    nr = n(),
-    mean = mean(value, na.rm = TRUE),
-    med = median(value, na.rm = TRUE),
-    sd = sd(value, na.rm = TRUE),
-    hist_data = list(value),
-    dens_data = list(value),
-    .groups = "drop"
-  ) %>% 
-  gt()
-
-#Preparation for likert data
-efa.LEBA.likert <- as.data.frame(gt.efa.data.table)
-
-recod_LEBA <- c( "1" = "Never", "2" = "Rarely", "3"= "Sometimes","4" = "Often",
-                 "5" = "Always")
-efa.LEBA.likert <-  mutate(efa.LEBA.likert, across(starts_with("item"), ~unname(recod_LEBA[.])))
-
-efa.LEBA.Factor = as.data.frame(lapply(efa.LEBA.likert,factor,
-                                   ordered = T))
-#get the items name
-efa.items <- names(efa.LEBA.Factor) 
-#Calculate percentage
-efa.percentage <- kutils::likert(efa.LEBA.Factor, vlist = efa.items )
-
-efa.percentage <- efa.percentage$table %>% 
-  as.data.frame(.)
-
-#data wrangling
-labels <- c("Always", "Never","Often", "Rarely", "Sometimes","Total")
-as.data.frame(labels)
-
-full.efa.percentage <- cbind(labels,efa.percentage) #tables with labels  
-full.efa.percentage<- t(full.efa.percentage ) #transpose
-as.data.frame(full.efa.percentage)
-full.efa.percentage1 <- full.efa.percentage[-1,-6] #removing 1st row and total column
-full.efa.percentage2 <- full.efa.percentage1[, c(2, 4, 5, 3,1)]# rearranging
-as.data.frame(full.efa.percentage2)
-
-colnames(full.efa.percentage2) <- c("Never","Rarely","Sometimes","Often","Always")
-
-efa.Items <- rownames(full.efa.percentage2)
-as.data.frame(efa.Items)
-full.efa.percentage3 <- cbind(efa.Items,full.efa.percentage2)
-
-full.efa.percentage3 <- full.efa.percentage3[order(efa.Items),] 
-full.efa.percentage3 <- as.data.frame(full.efa.percentage3[,-1]) %>% 
-  gt()
-
-gt.efa.table <- gt.efa.tab$'_data'
-gt.liket.efa <- full.efa.percentage3$"_data"
-
-efaTable <-  cbind( gt.efa.table, gt.liket.efa)%>% 
-  gt()
-
-gt.cfa.data <- gt.data[429:690,]
-gt.cfa.data.table <- gt.cfa.data %>% 
-  dplyr::select(item16, item36, item17,
-                 item11, item10,item12,item07,item08,item09,
-                 item27,  item03, item40,  item30, item41,
-                 item32,item35,item38, item33, 
-                 item46, item45, item25, item04, item01 )
-
-gt.cfa.long <- gather(gt.cfa.data.table, Items, value)
-gt.cfa.long$value <- as.numeric(as.character(gt.cfa.long$value))
-gt.cfa.tab <- gt.cfa.long %>% 
-  group_by(Items) %>% 
-# calculate summary stats & create data for the histogram and density plot
-  summarise(
-    nr = n(),
-    mean = mean(value, na.rm = TRUE),
-    med = median(value, na.rm = TRUE),
-    sd = sd(value, na.rm = TRUE),
-    hist_data = list(value),
-    dens_data = list(value),
-    .groups = "drop"
-  ) %>%
-
-  gt()
-
-#Preparation for likert data
-cfa.LEBA.likert <- as.data.frame(gt.cfa.data.table)
-
-recod_LEBA <- c( "1" = "Never", "2" = "Rarely", "3"= "Sometimes","4" = "Often",
-                 "5" = "Always")
-cfa.LEBA.likert <-  mutate(cfa.LEBA.likert, across(starts_with("item"), ~unname(recod_LEBA[.])))
-
-cfa.LEBA.Factor = as.data.frame(lapply(cfa.LEBA.likert,factor,
-                                   ordered = T))
-#get the items name
-cfa.items <- names(cfa.LEBA.Factor) 
-#Calculate percentage
-cfa.percentage <- kutils::likert(cfa.LEBA.Factor, vlist = cfa.items )
-
-cfa.percentage <- cfa.percentage$table %>% 
-  as.data.frame(.)
-
-#data wrangling
-labels <- c("Always", "Never","Often", "Rarely", "Sometimes","Total")
-as.data.frame(labels)
-
-full.cfa.percentage <- cbind(labels,cfa.percentage) #tables with labels  
-full.cfa.percentage <- t(full.cfa.percentage ) #transpose
-as.data.frame(full.cfa.percentage)
-full.cfa.percentage1 <- full.cfa.percentage[-1,-6] #removing 1st row and total column
-full.cfa.percentage2 <- full.cfa.percentage1[, c(2, 4, 5, 3,1)]# rearranging
-as.data.frame(full.cfa.percentage2)
-
-colnames(full.cfa.percentage2) <- c("Never","Rarely","Sometimes","Often","Always")
-
-cfa.Items <- rownames(full.cfa.percentage2)
-as.data.frame(cfa.Items)
-full.cfa.percentage3 <- cbind(cfa.Items,full.cfa.percentage2)
-
-full.cfa.percentage3 <- full.cfa.percentage3[order(cfa.Items),] 
-full.cfa.percentage3 <- as.data.frame(full.cfa.percentage3[,-1]) %>% 
-  gt()
-
-gt.cfa.table <- gt.cfa.tab$'_data'
-gt.liket.cfa <- full.cfa.percentage3$"_data"
-
-cfaTable <-  cbind( gt.cfa.table, gt.liket.cfa) %>% 
-  gt()
-
-efa.gt <- efaTable$"_data"
-cfa.gt <- cfaTable$"_data"
-
-gt.fullTable <-  rbind( efa.gt, cfa.gt) %>% 
-  gt() %>% 
-# histogram and density plots
-  gtExtras::gt_sparkline(
-    hist_data,
-    type = "histogram",
-    line_color = "black", 
-    fill_color = "grey",
-    bw = 1,
-    same_limit = TRUE)%>%
-  gtExtras::gt_sparkline(
-    dens_data,
-    type = "density",
-    line_color = "black", 
-    fill_color = "grey",
-    bw = 0.75,
-    same_limit = TRUE
-  )%>%
-# format decimals
-  fmt_number(columns = mean:sd, decimals = 1) %>%
-# header
-  tab_header(
-    title = md("**LEBA**"),
-    subtitle = md("Summary results of LEBA (N =690)")
-  ) %>% 
-  tab_footnote(
-    footnote = md("**Histogram**"),
-    locations = cells_column_labels(columns = hist_data)
-  ) %>%
-  tab_footnote(
-    footnote = md("**Density**"),
-    locations = cells_column_labels(columns = dens_data)
-  ) %>% 
-#create groups of columns
-tab_spanner(
-  label = "Items",
-  columns = Items
-) %>%
-  tab_spanner(
-    label = "Summary Statistics",
-    columns = nr:sd
-  ) %>%
-  tab_spanner(
-    label = "Graphics",
-    columns = hist_data:dens_data
-  ) %>% 
-  tab_spanner(
-    label = "Response Pattern",
-    columns = Never:Always
-  ) %>%
-# change column names to appear in the table
-cols_label(
-  Items = ("LEBA  Items"),
-  nr = ("n"),
-  mean = ("Mean"),
-  med = ("Median "),
-  sd = (("SD")),
-  hist_data = "Histogram",
-  dens_data = "Density"
-) %>%
-# set alignment as per wish
-  cols_align(
-    align = "center",
-    columns = everything()
-  ) %>%
-  opt_align_table_header(align = "left") %>%
-# add coloured dots and lines on the first column
-  gt_plt_dot(
-    mean,
-    Items,
-    palette = "ggthemes::fivethirtyeight"
-  ) %>% 
-    tab_row_group(
-      group = "CFA (n =262)",
-     rows = 26:48
-
-  ) %>% 
-  tab_row_group(
-  group = "EFA (n = 428)",
-    rows = 1:25  
-  ) %>% gtsave("Manuscript.figures/gt.png")
-
-```
-
-```{r gtPic, echo=FALSE, out.height="100%", out.width="200%", results= 'asis'}
-knitr::include_graphics('Manuscript.figures/gt.png')
-
-```
-
-# Confirmatory Factor Analysis
-
-```{r CFAdataframe, include=FALSE}
-
-### CFA Data
-CFA.data <- sem.data[429:690,]
-
-## Recoding CFA.data$item8 into CFA.data$Ritem8
-CFA.data$Ritem8 <- as.character(CFA.data$item8)
-CFA.data$Ritem8 <- fct_recode(CFA.data$Ritem8,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-CFA.data$Ritem8 <- as.numeric(as.character(CFA.data$Ritem8))
-
-## Recoding CFA.data$item37 into CFA.data$item37_rec
-CFA.data$Ritem37 <- as.character(CFA.data$item37)
-CFA.data$Ritem37 <- fct_recode(CFA.data$Ritem37,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-CFA.data$Ritem37 <- as.numeric(as.character(CFA.data$Ritem37))
-
-## Recoding CFA.data$item26 into CFA.data$Ritem26
-CFA.data$Ritem26 <- as.character(CFA.data$item26)
-CFA.data$Ritem26 <- fct_recode(CFA.data$Ritem26,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-
-#Hitogram
-#psych::multi.hist(CFA.data[,sapply(CFA.data, is.numeric)])
-```
-
-```{r CFA25items, include=FALSE }
-
-LB.model.Cor.1 <- "F1 =~ a1*item16 + item36 + a2*item17
-                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
-                 F3 =~  item27+ item3+ item40 + item30 + item41
-                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
-                 F5 =~ item46+ item45+ item25+ item4+ item1 
-                       a1==a2
-                       a3==a4"
-
-fit.Cor.1 <- cfa(LB.model.Cor.1, data = CFA.data, ordered = names(CFA.data),estimator = "WLSMV")
-
-## Summary of Model 
-cfa.sum.1 <- summary(fit.Cor.1, fit.measures =TRUE,standardized = TRUE,rsq =TRUE)
-
-## Selected Fit measures 
-fit.1 <- fitmeasures (fit.Cor.1,c("gfi", "agfi", "nfi","rfi", 
-                       "cfi.scaled","tli.scaled",
-                       "rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr"))
-
-reliability1 <- semTools::reliability(fit.Cor.1)
-
-```
-
-```{r mod1, include=FALSE}
-modfit.Cor.one <- modindices(fit.Cor.1, sort. = TRUE) 
-modfit.Cor.one[modfit.Cor.one$mi>3.84,]
-```
-
-```{r CFA23withMI, include=FALSE}
-LB.model.Cor.2 <- "F1 =~ a1*item16 + item36 + a2*item17
-                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
-                 F3 =~  item27+ item3+ item40 + item30 + item41
-                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
-                 F5 =~ item46+ item45+ item25+ item4+ item1 
-                       a1==a2
-                       a3==a4
-                item30 ~~  item41
-                       "
-
-#item26 & 37 are removed
-
-## Fit the model 
-fit.Cor.2 <- cfa(LB.model.Cor.2, data = CFA.data, ordered = names(CFA.data),estimator = "WLSMV")
-
-rel.k <- semTools::reliability(fit.Cor.2, return.total = T)
-## Summary of Model 
-cfa.sum.2 <- summary(fit.Cor.2, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
-
-## Selected Fit measures 
-fit.2 <- fitmeasures (fit.Cor.2,c("gfi", "agfi", "nfi","rfi", 
-                       "cfi.scaled","tli.scaled",
-                       "rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr"))
-
-```
-
-```{r mod2, include=FALSE}
-modfit.Cor.one <- modindices(fit.Cor.2, sort. = TRUE) 
-modfit.Cor.one[modfit.Cor.one$mi>3.84,]
-```
-
-We conducted a categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator as our response data was in ordinary nature [@desjardinsHandbookEducationalMeasurement2018a].
-Several indices exist to measure the the model fit.
-These can be categorized as absolute fit, comparative fit and parsimony fit indices [@brownConfirmatoryFactorAnalysis2015].
-Absolute fit assess the model fit at an absolute level using indices including chi-square test statistics and the standardized root mean square (SRMR).parsimony fit indices including the root mean square error of approximation (RMSEA) considers the number of free parameters in the model to assess the parsimony of the model.
-Comparative fit indices evaluate the fit of the specified model solution in relation to a more restricted baseline model restricting all covariances among the idicators as zero.
-Comparative fit index (CFI) and the Tucker Lewis index (TLI) are such two comparative fit indices.
-Commonly used Model fit guidelines [@huCutoffCriteriaFit1999; @schumacker2004beginner] includes (i) Reporting of chi-square test statistics (A non-significant test statistics is required to reflect model fit) (i) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (ii) RMSEA (close to .06 or below), (iii) SRMR (close to .08 or below) to estimate the model fit.
-Table\@ref(tab:tabCfa) summarizes the fit indices of our fitted model.
-The fitted model failed to attain an absolute fit estimated by the chi-square test.
-However, the chi-square test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit [@brownConfirmatoryFactorAnalysis2015].
-Another absolute fit index we obtained in our analysis was SRMR which does not work well with categorical data [@RN1272].
-Subsequently, we judged the model fit based on the comparative fit indices: CFI, TLI and parsimony fit index-RMSEA.
-Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 and 19-17 .
-However SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`).
-Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR value (SRMR = `r apa(fit.2[10],2,F)`) was also close to the suggestions of @huCutoffCriteriaFit1999.
-The internal consistency reliability coefficients coefficient alpha `r apa(rel.k[1,1],2,F)`, `r apa(rel.k[1,2],2,F)`, `r apa(rel.k[1,3],2,F)`, `r apa(rel.k[1,4],2,F)`, `r apa(rel.k[1,5],2,F)` respectively indicating satisfactory reliability for F1, F2 and F4 [@najeracatalanReliabilityPopulationClassification2019]
-
-```{r cfaMat, results='asis'}
-CFa.matrix <- matrix("NA", nrow =2, ncol = 9)
-colnames(CFa.matrix) = c("Model", "Chi-Squre", "df", "CFI", "TLI", "RMSEA", "RMSEA 90% Lower CI", "RMSEA 90% Upper CI", "SRMR")
-CFa.matrix[1,] = c("Five factor model:25", 
-                   apa(cfa.sum.1$FIT[6],2,T), 
-                   apa(cfa.sum.1$FIT[7],2,T), 
-                   apa(cfa.sum.1$FIT[19],2,F), 
-                   apa(cfa.sum.1$FIT[20],2,T),
-                   apa(cfa.sum.1$FIT[27],2,T),
-                   apa(cfa.sum.1$FIT[28],2,T),
-                   apa(cfa.sum.1$FIT[29],2,T),
-                   apa(cfa.sum.1$FIT[35],2,T))
-
-CFa.matrix[2,] = c("Five factor model:23", 
-                   apa(cfa.sum.2$FIT[6],2,T), 
-                   apa(cfa.sum.2$FIT[7],2,T), 
-                   apa(cfa.sum.2$FIT[19],2,F), 
-                   apa(cfa.sum.2$FIT[20],2,T),
-                   apa(cfa.sum.2$FIT[27],2,T),
-                   apa(cfa.sum.2$FIT[28],2,T),
-                   apa(cfa.sum.2$FIT[29],2,T),
-                   apa(cfa.sum.2$FIT[35],2,T))
-```
-
-```{r tabCfa, results='asis'}
-apa_table(CFa.matrix, caption = "Fit indices of CFA", align = "c", landscape = T, note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index;RMSEA:Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square ")
-```
-
-```{r simulation, eval=FALSE, include=FALSE}
-library("simsem")
-pop.model <- "F1 =~ a1*item16 + .95*item36 + a2*item17
-                 F2 =~ .87*item11 + .85*item10 + .74*item12+ .60*item7+ .50*Ritem8+ .49*item9
-                 F3 =~  .78*item27+ .77*item3+ .68*item40 + .13*item30 + .20*item41
-                 F4 =~ a3*item32 + .63*item35 + .33*item38+ a4*item33 
-                 F5 =~ .80*item46+ .53*item45+ .36*item25+ .30*item4+ .22*item1 
-                       a1==a2
-                       a3==a4
-                item30 ~~ .82*item41
-F1~~1*F1
-F2~~1*F2
-F3~~1*F3
-F4~~1*F4
-F5~~1*F5
-"
-
-sam.model <- "F1 =~ a1*item16 + item36 + a2*item17
-                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
-                 F3 =~  item27+ item3+ item40 + item30 + item41
-                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
-                 F5 =~ item46+ item45+ item25+ item4+ item1 
-                       a1==a2
-                       a3==a4
-                item30 ~~  item41
-                       "
-
-sim.300 <- sim(200, model = sam.model, n =200, generate = pop.model, lavaanfun = "lavaan", auto.var =T, auto.fix.first =F, seed = 123)
-summary(simulation)
-summaryParam(simulation, detail =T, alpha = .05)
-
-#power should be higher than .80, average CI width should be lower than .15
-#Estimate standard error bias
-
-SD.Bias <- (summaryParam(simulation)[3]-summaryParam(simulation)[2])/summaryParam(simulation)[3]
-```
-
-```{r figcfa, fig.cap = "(A) Five Factor Model of LEBA", , out.width="100%",  warning=FALSE, results='asis'}
-#library(semPlot)
-
-semPaths (fit.Cor.2 , 
-          what= "std",
-          #whatLabels = "std",
-          intercepts = F,
-          #style ="lisrel",
-          #residScale = 6,
-          theme = "colorblind",
-          nCharNodes = 0,
-          reorder =T,
-          rotation =2,
-          layout ="tree",
-          cardinal = T,
-          curvePivot =T,
-          sizeMan =8,
-          sizeMan2 = 1.5,
-          sizeLat = 8,
-          #edge.color = "black",
-          thresholds = FALSE,
-          equalizeManifests =T,
-          fade = FALSE,
-          edge.label.cex = .65,
-          exoCov = FALSE)
-
-```
-
-```{r InvarianceAnalysis_data, include=FALSE}
-invariance.data <- cbind(CFA.data, data$slypos_demographics_language.factor[429:690])
-colnames(invariance.data)[52] <- "English_Speaking"
-
-invariance.data %>% 
-  group_by(English_Speaking) %>% 
-  count()
-```
-
-```{r Invariancedetail, include=FALSE}
-# Configural invariance ####
-
-configural <- cfa(model = LB.model.Cor.2,
-                  data = invariance.data,
-                  group = "English_Speaking",
-                  ordered =   names(CFA.data),
-                  estimator = "WLSMV")
-
-summary(configural, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
-
-fitmeasures (configural,c("gfi", "agfi", "nfi","rfi", 
-                       "cfi.scaled","tli.scaled",
-                       "rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr"))
-
-weak <- cfa(model = LB.model.Cor.2,
-                  data = invariance.data,
-                  group = "English_Speaking",
-                  ordered =   names(CFA.data),
-                  estimator = "WLSMV", 
-            group.equal = "loadings")
-
-summary(weak, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
-
-fitmeasures (weak,c("gfi", "agfi", "nfi","rfi", 
-                       "cfi.scaled","tli.scaled",
-                       "rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr"))
-
-First.comp <- compareFit (configural, weak)
-summary(First.comp)
-
-strong <- cfa(model = LB.model.Cor.2,
-                  data = invariance.data,
-                  group = "English_Speaking",
-                  ordered =   names(CFA.data),
-                  estimator = "WLSMV", 
-              group.equal = c("loadings", "intercepts"))
-summary(strong, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
-
-Second.comp <- compareFit  (weak, strong)
-summary(Second.comp)
-
-strict <- cfa(model = LB.model.Cor.2,
-                  data = invariance.data,
-                  group = "English_Speaking",
-                  ordered =   names(CFA.data),
-                  estimator = "WLSMV",  
-              group.equal = c("loadings", "intercepts", "residuals"))
-
-summary(strict, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
-fitmeasures (strict,c("gfi", "agfi", "nfi","rfi", "cfi.robust","tli.robust","rmsea", "srmr","aic"))
-
-Third.comp <- compareFit(strict,strong)
-summary(Third.comp)
-
-structural <-cfa(model = LB.model.Cor.2,
-                  data = invariance.data,
-                  group = "English_Speaking",
-                  ordered =   names(CFA.data),
-                  estimator = "WLSMV",  
-                 group.equal = c("loadings", "intercepts", "residuals", "means","lv.variances","lv.covariances"))
-
-summary(structural, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
-fitmeasures (structural,c("gfi", "agfi", "nfi","rfi", "cfi","tli","rmsea", "srmr","aic"))
-
-fourth.comp <- compareFit  (structural,strict)
-summary(fourth.comp)
-comfit.par <- compareFit(configural, weak, strong, strict, structural)
-summary (comfit.par)
-
-models <-  list("Configural" = configural, 
-                "Metric" = weak, 
-                "Scalar" = strong, 
-                "Residual" = strict, 
-                "Structural"=structural)
-
-Invariance.table <- compareLavaan(models,
-              nesting = "Configural > Metric > Scalar > Residual  > Structural", 
-              fitmeas = c("chisq.scaled", "df",  "cfi.scaled","tli.scaled","rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr" ),
-              scaled = T,
-              chidif = T, digits = 2)
-
-colnames(Invariance.table) <- c("Chi-Square", "df", "CFI", "TLI", "RMSEA", "RMSEA 90% Lower CI", "RMSEA 90% Upper", "SRMR", "Chi-Sqr comparison", "df*", "p")
-
-```
-
-```{r InvarianceTab, results='asis'}
-apa_table(Invariance.table, align = "c",  caption = "Invariance Analysis", note = " a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual;* =  df of model comparison", landscape = T, font_size = "scriptsize" )
-
-```
-
-## Analysing the quality of items by Item Information Theory
-
-We sought the IRT to gether information regarding the item quality.
-IRT complements the conventional classical test theory-based analysis by gathering information on item discrimination and item difficulty[@bakerBasicsItemResponse2017].
-Here, an item's quality is judged based on item information in relation to participants' latent trait level ($\theta$).
-We gathered evidence on item quality by fitting each factor of LEBA with the graded response model (\@ref(tab:IRTparameters) to the combined EFA sample and CFA sample (n =690).
-Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait, and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
-Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information <.2) to develop the short form of LEBA.
-@bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70.
-Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), low ( 5 items) indicating a good range of discrimination along the latent trait.
-Examination of the item information curve indicated 6 items (1, 25, 9, 38, 30, & 41) had relatively flat information curves thus discarded.
-We also gathered evidence of item fit and person fit to our fitted model.
-
-```{r IRTdata, include=FALSE}
-## Recoding sem.data$item8 into sem.data$Ritem8
-sem.data$Ritem8 <- as.character(sem.data$item8)
-sem.data$Ritem8 <- fct_recode(sem.data$Ritem8,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-sem.data$Ritem8 <- as.numeric(as.character(sem.data$Ritem8))
-# Recoding sem.data$item26 
-sem.data$Ritem26 <- as.character(sem.data$item26)
-sem.data$Ritem26 <- fct_recode(sem.data$Ritem26,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-sem.data$Ritem26 <- as.numeric(as.character(sem.data$Ritem26))
-
-# Recoding sem.data$item37 i
-sem.data$Ritem37 <- as.character(sem.data$item37)
-sem.data$Ritem37 <- fct_recode(sem.data$Ritem37,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-sem.data$Ritem37 <- as.numeric(as.character(sem.data$Ritem37))
-
-F1 <- sem.data %>% 
-  dplyr::select(item16, item36,  item17)
-
-F2 <- sem.data %>% 
-  dplyr::select(item11,  item10 , item12, item7, Ritem8, item9)
-
-F3 <- sem.data %>% 
- dplyr::select(item27, item3,  item40,  item30,  item41)
-
-F4 <- sem.data %>% 
- dplyr::select(item32, item35,  item38,  item33)
-
-F5 <- sem.data %>% 
-  dplyr::select(item46, item45, item25, item4, item1 )
-
-## F1 IRT model####
-F1_fit <- mirt(F1, model = 1, itemtype = 'graded', 
-               SE = TRUE, Se.type = 'MHRM',
-               technical = list(NCYCLES = 10000))
-
-## F2 IRT model####
-F2_fit <- mirt(F2, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-## F3 IRT model####
-F3_fit <- mirt(F3, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-## F4 IRT model####
-F4_fit <- mirt(F4, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-## F5 IRT model####
-F5_fit <- mirt(F5, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-# Model Parameters ####
-## F1 Model Parameters####
-F1_params <- coef(F1_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
-F1_items <- data.frame(F1_params$items)
-F1l_se <- coef(F1_fit, printSE = TRUE)
-
-## F2 Model Parameters####
-F2_params <- coef(F2_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
-F2_items <- data.frame(F2_params$items)
-F2_se <- coef(F2_fit, printSE = TRUE)
-
-## F3 Model Parameters####
-F3_params <- coef(F3_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
-F3_items <- data.frame(F3_params$items)
-F3_se <- coef(F3_fit, printSE = TRUE)
-
-## F4 Model Parameters####
-F4_params <- coef(F4_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
-F4_items <- data.frame(F4_params$items)
-F4_se <- coef(F4_fit, printSE = TRUE)
-
-## F5 Model Parameters####
-F5_params <- coef(F5_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
-F5_items <- data.frame(F5_params$items)
-F5_se <- coef(F5_fit, printSE = TRUE)
-
-itemparameters <- rbind(F1_items,F2_items, F3_items, F4_items,F5_items)
-
-# Model Fit (degrees of freedom too low to check model fit)
-#F1.model <- M2(F1_fit)
-#F2.model <- M2(F2_fit)
-#F3.model <- M2(F3_fit)
-#F4.model <- M2(F4_fit)
-#F5.model <- M2(F5_fit)
-
-#Item fit
-F1.item.fit<- itemfit(F1_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
-                                  impute=10)
-
-F2.item.fit<- itemfit(F2_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
-                                  impute=10)
-F3.item.fit<- itemfit(F3_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
-                                  impute=10)
-F4.item.fit<- itemfit(F4_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
-                                  impute=10)
-
-F5.item.fit<- itemfit(F5_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
-                                  impute=10)
-
-#Identifying Missfit items based on RMSEA Value
-F1.item_misfits <- subset(F1.item.fit, RMSEA.S_X2 >= .06)
-F2.item_misfits <- subset(F2.item.fit, RMSEA.S_X2 >= .06)
-F3.item_misfits <- subset(F3.item.fit, RMSEA.S_X2 >= .06)
-F4.item_misfits <- subset(F4.item.fit, RMSEA.S_X2 >= .06)
-F5.item_misfits <- subset(F5.item.fit, RMSEA.S_X2 >= .06)
-
-# Person Fit ####
-## F1 Person fit ####
-F1.personfit <- personfit(F1_fit) 
-F1.personfit_model_misfits <- subset(F1.personfit, Zh < -2)
-rownames(F1.personfit_model_misfits)
-nrow(F1.personfit_model_misfits)
-hist(F1.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-
-## F2 Person fit ####
-F2.personfit <- personfit(F2_fit) 
-F2.personfit_model_misfits <- subset(F2.personfit, Zh < -2)
-rownames(F2.personfit_model_misfits)
-nrow(F2.personfit_model_misfits)
-hist(F2.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-
-## F3 Person fit ####
-F3.personfit <- personfit(F3_fit) 
-F3.personfit_model_misfits <- subset(F3.personfit, Zh < -2)
-rownames(F3.personfit_model_misfits)
-nrow(F3.personfit_model_misfits)
-hist(F3.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-
-## F4 Person fit ####
-F4.personfit <- personfit(F4_fit) 
-F4.personfit_model_misfits <- subset(F4.personfit, Zh < -2)
-rownames(F4.personfit_model_misfits)
-nrow(F4.personfit_model_misfits)
-hist(F4.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-
-## F5 Person fit ####
-F5.personfit <- personfit(F5_fit) 
-F5.personfit_model_misfits <- subset(F5.personfit, Zh < -2)
-rownames(F3.personfit_model_misfits)
-nrow(F5.personfit_model_misfits)
-hist(F5.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-
-# Plots ####
-## F1 Plots ####
-F1_OCC <- plot(F1_fit, type = "trace", facet =T, main = "Blue Filter OCC")
-F1_info <- plot(F1_fit, type = "infoSE", main = "F1")
-F1_iteminfo <- plot(F1_fit, type = "infotrace", 
-                    facet_items = T, main = "F1")
-
-## F2 Plots ####
-F2_OCC <- plot(F2_fit, type = "trace", facet =T, main = "Natural Light OCC")
-F2_info <- plot(F2_fit, type = "infoSE", main = "F2")
-F2_iteminfo <- plot(F2_fit, type = "infotrace", facet_items = T, main = "F2")
-
-## F3 Plots ####
-F3_OCC <-plot(F3_fit, type = "trace", facet =T, main = "Smart Device OCC")
-F3_info <- plot(F3_fit, type = "infoSE", main = "F3")
-F3_iteminfo <- plot(F3_fit, type = "infotrace", 
-                    facet_items = T, main = "F3")
-
-## F4 Plots ####
-F4_OCC <-plot(F4_fit, type = "trace", facet =T, main = "Sleep Environment OCC")
-F4_info <- plot(F4_fit, type = "infoSE", main = "F4")
-F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = "F4",cex = .8)
-
-## F5 Plots ####
-F5_OCC <-plot(F5_fit, type = "trace", facet =T, main = "Electric Light OCC")
-F5_info <- plot(F5_fit, type = "infoSE", main = "F5")
-F5_iteminfo <- plot(F5_fit, type = "infotrace", facet_items = T,main = "F5")
-
-## Plot grid ####
-library(cowplot)
-OCC <- plot_grid(F1_OCC, F2_OCC,F3_OCC,F4_OCC,F5_OCC, 
-          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)
-
-Test_Info <- plot_grid(F1_info, F2_info,F3_info,F4_info,F5_info, 
-          labels = "AUTO", label_size = 10)
-
-Item_Information <- plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
-          labels = "AUTO", label_size = 10)
-
-```
-
-```{r IRTreliability, include=F}
-#conditional reliability
-F1.reliability <- plot(F1_fit, type = 'rxx', theta_lim = c(-6, 6), 
-      main="" )
-F2.reliability <- plot(F2_fit, type = 'rxx', theta_lim = c(-6, 6), 
-      main="" )
-F3.reliability <- plot(F3_fit, type = 'rxx', theta_lim = c(-6, 6), 
-      main="" )
-F4.reliability <- plot(F4_fit, type = 'rxx', theta_lim = c(-6, 6), 
-      main="" )
-F5.reliability <- plot(F5_fit, type = 'rxx', theta_lim = c(-6, 6), 
-      main="" )
-
-##IRT reliability (marginal reliability of scales)
-F1.marginal.rel <- marginal_rxx(F1_fit)
-F2.marginal.rel <-marginal_rxx(F2_fit)
-F3.marginal.rel <-marginal_rxx(F3_fit)
-F4.marginal.rel <-marginal_rxx(F4_fit)
-F5.marginal.rel <-marginal_rxx(F5_fit)
-
-##Scale characteristic curve
-F1.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
-F2.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
-F3.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
-F4.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
-F5.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
-```
-
-```{r IRTparameters, results='asis'}
-apa_table(itemparameters, caption = "IRT Item parameters for the LEBA Scale", note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
-```
-
-```{r itmeinfo, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
-plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
-          labels = "AUTO", label_size = 10,align = "v")
-
-```
-
-```{r shortIRT, include=FALSE}
-F1 <- sem.data %>% 
-  dplyr::select(item16, item36,  item17)
-F2.redu <- sem.data %>% 
-  dplyr::select(item11,  item10 , item12, item7, Ritem8)
-F3.redu <- sem.data %>% 
- dplyr::select(item27, item3,  item40)
-
-F4.redu <- sem.data %>% 
- dplyr::select(item32, item35,  item33)
-
-F5 <- sem.data %>% 
-  dplyr::select(item46, item45, item25 )
-
-F1_fit <- mirt(F1, model = 1, itemtype = 'graded', 
-               SE = TRUE, Se.type = 'MHRM',
-               technical = list(NCYCLES = 10000))
-
-F2_fit.redu <- mirt(F2.redu, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-F3_fit.redu <- mirt(F3.redu, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-F4_fit.redu <- mirt(F4.redu, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-F5_fit <- mirt(F5, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-#Item fit
-F1.item.fit<- itemfit(F1_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
-                                  impute=10)
-
-F2.item.fit<- itemfit(F2_fit.redu, fit_stats = c("S_X2", "G2","Zh", "infit"),
-                                  impute=10)
-F3.item.fit<- itemfit(F3_fit.redu, fit_stats = c("S_X2", "G2","Zh", "infit"),
-                                  impute=10)
-F4.item.fit<- itemfit(F4_fit.redu, fit_stats = c("S_X2", "G2","Zh", "infit"),
-                                  impute=10)
-
-F5.item.fit<- itemfit(F5_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
-                                  impute=10)
-
-#Identifying Missfit items based on RMSEA Value
-F1.item_misfits <- subset(F1.item.fit, RMSEA.S_X2 >= .06)
-F2.item_misfits <- subset(F2.item.fit, RMSEA.S_X2 >= .06)
-F3.item_misfits <- subset(F3.item.fit, RMSEA.S_X2 >= .06)
-F4.item_misfits <- subset(F4.item.fit, RMSEA.S_X2 >= .06)
-F5.item_misfits <- subset(F5.item.fit, RMSEA.S_X2 >= .06)
-
-# Person Fit ####
-## F1 Person fit ####
-F1.personfit <- personfit(F1_fit) 
-F1.personfit_model_misfits <- subset(F1.personfit, Zh < -2)
-rownames(F1.personfit_model_misfits)
-nrow(F1.personfit_model_misfits)
-hist(F1.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-
-## F2 Person fit ####
-F2.personfit <- personfit(F2_fit.redu) 
-F2.personfit_model_misfits <- subset(F2.personfit, Zh < -2)
-rownames(F2.personfit_model_misfits)
-nrow(F2.personfit_model_misfits)
-hist(F2.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-
-## F3 Person fit ####
-F3.personfit <- personfit(F3_fit.redu) 
-F3.personfit_model_misfits <- subset(F3.personfit, Zh < -2)
-rownames(F3.personfit_model_misfits)
-nrow(F3.personfit_model_misfits)
-hist(F3.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-
-## F4 Person fit ####
-F4.personfit <- personfit(F4_fit.redu) 
-F4.personfit_model_misfits <- subset(F4.personfit, Zh < -2)
-rownames(F4.personfit_model_misfits)
-nrow(F4.personfit_model_misfits)
-hist(F4.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-
-## F5 Person fit ####
-F5.personfit <- personfit(F5_fit) 
-F5.personfit_model_misfits <- subset(F5.personfit, Zh < -2)
-rownames(F3.personfit_model_misfits)
-nrow(F5.personfit_model_misfits)
-hist(F5.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-
-F1.reliability <- plot(F1_fit, type = 'rxx', theta_lim = c(-6, 6), 
-      main="" )
-F2.reliability <- plot(F2_fit.redu, type = 'rxx', theta_lim = c(-6, 6), 
-      main="" )
-F3.reliability <- plot(F3_fit.redu, type = 'rxx', theta_lim = c(-6, 6), 
-      main="" )
-F4.reliability <- plot(F4_fit.redu, type = 'rxx', theta_lim = c(-6, 6), 
-      main="" )
-F5.reliability <- plot(F5_fit, type = 'rxx', theta_lim = c(-6, 6), 
-      main="" )
-
-##IRT reliability (marginal reliability of scales)
-F1.marginal.rel <- marginal_rxx(F1_fit)
-F2.marginal.rel <-marginal_rxx(F2_fit.redu)
-F3.marginal.rel <-marginal_rxx(F3_fit.redu)
-F4.marginal.rel <-marginal_rxx(F4_fit.redu)
-F5.marginal.rel <-marginal_rxx(F5_fit)
-
-# Plots2 ####
-
-F1_test.info <- plot(F1_fit, type = "infoSE", main = "F1")
-
-F2_test.info.redu <- plot(F2_fit.redu, type = "infoSE", main = "F2")
-
-F3_test.info.redu <- plot(F3_fit.redu, type = "infoSE", main = "F3")
-
-F4_test.info.redu <- plot(F4_fit.redu, type = "infoSE", main = "F4")
-
-F5_test.info <- plot(F5_fit, type = "infoSE", main = "F5")
-
-##Scale characteristic curve
-F1.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
-F2.scale <- plot(F2_fit.redu, type = 'score', theta_lim = c(-6, 6), main = "")
-F3.scale <- plot(F3_fit.redu, type = 'score', theta_lim = c(-6, 6), main = "")
-F4.scale <- plot(F4_fit.redu, type = 'score', theta_lim = c(-6, 6), main = "")
-F5.scale <- plot(F5_fit, type = 'score', theta_lim = c(-6, 6), main = "")
-
-```
-
-```{r Testinfo, fig.cap="Test information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
-plot_grid(F1_test.info, F2_test.info.redu,F3_test.info.redu,F4_test.info.redu,F5_test.info, 
-          labels = "AUTO", label_size = 10, align = "v" )
-
-```
-
-Test information curve (TIC) indicate the amount of information an the full-scale carry along the latent trait continuum.
-As we treated each factor of LEBA as an unidmensional construct we obtain 5 TICs.
-These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum (($\theta$)).
-Also the amount of information changed rather steadily with the change of ($\theta$).
-Thus we conferred the LEBA scale (except blue filter) estimated the light exposure related behavior with precision near the center of trait continuum [@bakerBasicsItemResponse2017] which is sufficient to discriminate between latent trait measured by the each factor.
-The blue filter factor had a peak to the right side of the center of latent trait indicating its ability to providing information only for people who already have some preference towards using blue-filters.
-
-Our result also indicated all the items fitted well to the respective models as assessed by assessed by RMSEA value obtained from Signed-X2 index implementation.
-All of the items had RMSEA value <.06 indicating adequate fit.
-Person fit indicates the validity and meaningfulness of the fitted model at the participants latent trait level [@desjardinsHandbookEducationalMeasurement2018].
-We estimated the person fit statistics using standardized fit index Zh statistics [@drasgow1985appropriateness].
-Zh < -2 should be considered as a misfit.
-Fig indicates that Zh is larger than -2 for most participants, suggesting a good fit of the selected IRT models.
-
-The overall we can concluded that  IRT analysis  indicated LEBA is  a psychometrically sound measure.
-Item fit indexes and person fit index for all five fitted model were acceptable.
-Items had diverse slope parameters  indicating a good range of discrimination- the ability to differentiate respondents with different levels of the light exposure related behavior.
-All-in-all we can recommend the LEBA to be used to capture light exposure related behavior.
-
-```{r fscore, include=FALSE}
-LEBA.Total <- sem.data %>% 
-  rowwise() %>% 
-  mutate(F1.Total = sum(item16, item36,  item17))
-
-LEBA.Total <- LEBA.Total %>% 
-  rowwise() %>% 
-  mutate(F2.Total = sum(item11,  item10 , item12, item7, Ritem8))
-
-LEBA.Total <- LEBA.Total %>% 
-  rowwise() %>% 
-  mutate(F3.Total = sum(item27, item3,  item40))
-
-LEBA.Total <- LEBA.Total %>% 
-  rowwise() %>% 
-  mutate(F4.Total = sum(item32, item35,  item33))
-
-LEBA.Total <- LEBA.Total %>% 
-  rowwise() %>% 
-  mutate(F5.Total = sum(item46, item45, item25))
-
-F1.estimation <- as.vector(fscores(F1_fit, method = "EAP",
-                                           full.scores = TRUE, 
-                                           full.scores.SE = F))
-
-F2.estimation <- as.vector(fscores(F2_fit.redu, method = "EAP",
-                                           full.scores = TRUE, 
-                                           full.scores.SE = F))
-
-F3.estimation <- as.vector(fscores(F3_fit.redu, method = "EAP",
-                                           full.scores = TRUE, 
-                                           full.scores.SE = F))
-
-F4.estimation <- as.vector(fscores(F4_fit.redu, method = "EAP",
-                                           full.scores = TRUE, 
-                                           full.scores.SE = F))
-
-F5.estimation <- as.vector(fscores(F5_fit, method = "EAP",
-                                           full.scores = TRUE, 
-                                           full.scores.SE = F))
-
-Ability.F1 <- data.frame(Rawscore = LEBA.Total$F1.Total,
-                      Theta =  F1.estimation)
-
-Ability.F2 <- data.frame(Rawscore = LEBA.Total$F2.Total,
-                      Theta =  F2.estimation)
-
-Ability.F3 <- data.frame(Rawscore = LEBA.Total$F3.Total,
-                      Theta =  F3.estimation)
-
-Ability.F4 <- data.frame(Rawscore = LEBA.Total$F3.Total,
-                      Theta =  F3.estimation)
-
-Ability.F5 <- data.frame(Rawscore = LEBA.Total$F3.Total,
-                      Theta =  F3.estimation)
-
-ggplot(Ability.F1, aes(x =Theta, y =Rawscore)) +
-  geom_point() +
-  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
-  xlim(-2,2) +
-  ylim(0,15)
-
-ggplot(Ability.F2, aes(x =Theta, y =Rawscore)) +
-  geom_point() +
-  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
-  xlim(-2,2) +
-  ylim(0,15)
-
-ggplot(Ability.F3, aes(x =Theta, y =Rawscore)) +
-  geom_point() +
-  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
-  xlim(-2,2) +
-  ylim(0,15)
-
-ggplot(Ability.F4, aes(x =Theta, y =Rawscore)) +
-  geom_point() +
-  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
-  xlim(-2,2) +
-  ylim(0,15)
-
-ggplot(Ability.F5, aes(x =Theta, y =Rawscore)) +
-  geom_point() +
-  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
-  xlim(-2,2) +
-  ylim(0,15)
-
-Score.correation <- cbind(Ability.F1,Ability.F2, Ability.F3, Ability.F4, Ability.F5)
-colnames(Score.correation) <- c("F1.Raw", "F1.Estimated","F2.Raw", "F2.Estimated","F3.Raw", "F3.Estimated","F4.Raw", "F4.Estimated","F5.Raw", "F5.Estimated")
-
-F1.cor <- corr.test(Score.correation$F1.Raw, Score.correation$F1.Estimated)
-
-F2.cor <- corr.test(Score.correation$F2.Raw, Score.correation$F2.Estimated)
-
-F3.cor <- corr.test(Score.correation$F3.Raw, Score.correation$F3.Estimated)
-
-F4.cor <- corr.test(Score.correation$F4.Raw, Score.correation$F4.Estimated)
-
-F5.cor <- corr.test(Score.correation$F5.Raw, Score.correation$F5.Estimated)
-
-#Putting significance star for correlation
-F1.p <-F1.cor$p
-F1.stars <- ifelse(F1.p < .001, "***"
-                   , ifelse(p < .01, "**"
-                            , ifelse(p < .05, "*"
-                                     , ifelse(p < .10, "+", " "))))
-
-F2.p <-F2.cor$p
-F2.stars <- ifelse(F2.p < .001, "**"
-                   , ifelse(p < .01, "**"
-                            , ifelse(p < .05, "*"
-                                     , ifelse(p < .10, "+", " "))))
-
-F3.p <-F3.cor$p
-F3.stars <- ifelse(F3.p < .001, "***"
-                   , ifelse(p < .01, "**"
-                            , ifelse(p < .05, "*"
-                                     , ifelse(p < .10, "+", " "))))
-
-F4.p <-F4.cor$p
-F4.stars <- ifelse(F4.p < .001, "***"
-                   , ifelse(p < .01, "**"
-                            , ifelse(p < .05, "*"
-                                     , ifelse(p < .10, "+", " "))))
-
-F5.p <-F5.cor$p
-F5.stars <- ifelse(F5.p < .001, "***"
-                   , ifelse(p < .01, "**"
-                            , ifelse(p < .05, "*"
-                                     , ifelse(p < .10, "+", " "))))
-
-theta.correlation.matrix <- matrix("NA", nrow =1, ncol = 5)
-
-theta.correlation.matrix[1,1] <- paste(apa(F1.cor$r,2,F), F1.stars,sep="")
-theta.correlation.matrix[1,2] <- paste(apa(F2.cor$r,2,F), F2.stars,sep="")
-theta.correlation.matrix[1,3] <- paste(apa(F3.cor$r,2,F), F3.stars,sep="")
-theta.correlation.matrix[1,4] <- paste(apa(F4.cor$r,2,F), F4.stars,sep="")
-theta.correlation.matrix[1,5] <- paste(apa(F5.cor$r,2,F), F5.stars,sep="")
-
-as.data.frame(theta.correlation.matrix)
-colnames(theta.correlation.matrix) <- c("F1", "F2", "F3", "F4", "F5")
-```
-
-```{r IRTscoreCor, results='asis'}
-apa_table (theta.correlation.matrix, caption = "correlation coefficents of obtained scores and estimated latent trait for each factots", note = "* p < 0.05; ** p < 0.01; *** p < 0.001"  )
-```
-
-```{r clean, eval=FALSE, include=FALSE}
-cleanFolder <- function() {
-  answer <- NA
-  while(!(answer %in% c('y', 'n'))) {
-    answer <- readline(paste("Clean ", getwd(),"? (y/n)"))
-  }
-  if(answer == 'y') {
-    rules <- c('.log', '.vrb', '.nav', '.snm', '.toc', 
-               '-tikzDictionary', '.tex', '.synctex.gz')
-    file.remove(list.files(pattern = paste0('\\',rules ,'$', collapse = '|')))
-  }
-}
-cleanFolder()
-```
-
-# Discussion
-
-\newpage
-
-# References
-
-```{=tex}
-\begingroup
-\setlength{\parindent}{-0.5in}
-\setlength{\leftskip}{0.5in}
-```
-::: {#refs custom-style="Bibliography"}
-:::
-
-\endgroup

### 2021-11-07 manuscript.Rmd
* supplementary analysis on EFA (Minimum residulas and six-factor solution) is added
Some minor formating here and there.

@@
 appendix:
+  - "Supplymentary.Rmd"
   - "instrument.Rmd"
@@
 
-```{r depMan, include=FALSE}
+```{r depMan}
 library(packrat)
@@
 library(simsem)
-library(extrafont)
-extrafont::font_import()
+library(tabledown)
+#library(extrafont)
+#extrafont::font_import()
 r_refs("references.bib")
@@
 +-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| Assessment of Sleep Environment                                   | [@Olivier.2016]          | 13 items questionnaire measuring your sleep environment quality                                                                                              |                                      |             |
+| Assessment of Sleep Environment                                   | \[@Olivier.2016\]        | 13 items questionnaire measuring your sleep environment quality                                                                                              |                                      |             |
 +-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
@@
 +-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| Self-Rating of Biological Rhythm Disorder for Adolescents (SBRDA) | [@Xie.2021]              | 29 items questionnaire assessing four dimensions of biological rhythm disorder in adolescents (digital media use, sleep, eating habits, and activity)        | Items 3., 22., 23., 24., 25.
+| Self-Rating of Biological Rhythm Disorder for Adolescents (SBRDA) | \[@Xie.2021\]            | 29 items questionnaire assessing four dimensions of biological rhythm disorder in adolescents (digital media use, sleep, eating habits, and activity)        | Items 3., 22., 23., 24., 25.
 and 29.
@@
 +-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| Photosensitivity Assessment Questionnaire (PAQ)                   | [@Wu.2017]               | 16 dichotomous (yes/no) items questionnaire to assess "photophobia" and "photophilia", giving two final scores of "photophobic" and "photophilic" behaviours | All items                            |             |
+| Photosensitivity Assessment Questionnaire (PAQ)                   | \[@Wu.2017\]             | 16 dichotomous (yes/no) items questionnaire to assess "photophobia" and "photophilia", giving two final scores of "photophobic" and "photophilic" behaviours | All items                            |             |
 +-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
@@
 
-Data was collected in a quantitative cross-sectional approach via a fully anonymous online survey hosted on REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel (sciCORE; <https://redcap.scicore.unibas.ch/>).
-Participants were recruited via the website of a Comic co-released with the survey[@Weinzaepflen.2021; <https://enlightenyourclock.org/participate-in-research/>], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux software [@f.lux].
+Data was collected in a quantitative cross-sectional approach via a fully anonymous online survey hosted on REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
+Participants were recruited via the website of a Comic co-released with the survey[@Weinzaepflen.2021]( https://enlightenyourclock.org/participate-in-research), social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux software [@f.lux].
 
@@
 The first page of the survey comprised a participant information sheet, where participants' informed consent to participate was obtained before any of the questions were displayed.
-Underaged participants (\<18 years) were urged to obtain assent from their parents/legal guardians, before filling in the survey.
+Underaged participants (<18 years) were urged to obtain assent from their parents/legal guardians, before filling in the survey.
 Information on the first page included the objectives of the study, inclusion criteria, estimated duration, the use, storage and sharing of the data, compensation (none), and information about the type of questions in the survey.
@@
 -   Sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration (version for adults and adolescents) [@roenneberg2003life]
--   Sleep environment [@Olivier.2016]
+-   Sleep environment [\@Olivier.2016]
 -   Meal timing & caffeine consumption [custom items]
--   Light sensitivity (photophobia vs. photophilia) [@Wu.2017]
+-   Light sensitivity (photophobia vs. photophilia) [\@Wu.2017]
 -   Self-reported pubertal stage (only if younger than 18 years old) [@Petersen.1988]
@@
 
-Age among all participants ranged from `r min(desctable.data$slypos_demographics_age)` years to `r max(desctable.data$slypos_demographics_age)` years [EFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
+Age among all participants ranged from `r min(desctable.data$slypos_demographics_age)` years to `r max(desctable.data$slypos_demographics_age)` years \[EFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
 EFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
@@
 CFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`], with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 0)` years of age [Overall: *M* = `r mean(desctable.data$slypos_demographics_age)`, *SD* = `r sd(desctable.data$slypos_demographics_age)`; EFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
+CFA Sample"])`\], with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 0)` years of age \[Overall: *M* = `r mean(desctable.data$slypos_demographics_age)`, *SD* = `r sd(desctable.data$slypos_demographics_age)`; EFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
 EFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
@@
 CFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`].
-In total `r desc_tibble[3,2]` of the participants indicated female sex [EFA: `r desc_tibble[3,3]`; CFA: `r desc_tibble[3,4]`], `r desc_tibble[4,2]` indicated male [EFA: `r desc_tibble[4,3]`; CFA: `r desc_tibble[4,4]`] and `r desc_tibble[5,2]` indicated other sex [EFA: `r desc_tibble[5,3]`, CFA: `r desc_tibble[5,4]`].
-Overall, `r desc_tibble[6,2]` [EFA: `r desc_tibble[6,3]`; CFA: `r desc_tibble[6,4]`] participants indicated a gender-variant identity.
-In a "Yes/No" question regarding native language, `r desc_tibble[7,2]` of respondents [EFA: `r desc_tibble[7,3]`; CFA: `r desc_tibble[7,4]`] indicated to be native English speakers.
-For their "Occupational Status", more than half of the overall sample reported that they currently work [Overall: `r desc_tibble[9,2]`; EFA: `r desc_tibble[9,3]`; CFA: `r desc_tibble[9,4]`], whereas `r desc_tibble[10,2]` [EFA: `r desc_tibble[10,3]`; CFA: `r desc_tibble[10,4]`] reported that they go to school and `r desc_tibble[11,2]` [EFA: `r desc_tibble[11,3]`; CFA: `r desc_tibble[11,4]`] responded that they do "Neither".
-With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` [EFA: `r desc_tibble[13,3]`; CFA: `r desc_tibble[13,4]`] of the participants indicated that they were in a home office/ home schooling setting., while `r desc_tibble[14,2]` overall [EFA: `r desc_tibble[14,3]` ; CFA: `r desc_tibble[14,4]`] reported face-to-face work/schooling.
-Lastly, `r desc_tibble[15,2]` overall [EFA: `r desc_tibble[15,3]` ; CFA: `r desc_tibble[15,4]`] reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]` overall [EFA: `r desc_tibble[16,3]`; CFA: `r desc_tibble[16,4]`] filled in the "Neither (no work or school, or indication)" response option.
+CFA Sample"])`\].
+In total `r desc_tibble[3,2]` of the participants indicated female sex \[EFA: `r desc_tibble[3,3]`; CFA: `r desc_tibble[3,4]`\], `r desc_tibble[4,2]` indicated male \[EFA: `r desc_tibble[4,3]`; CFA: `r desc_tibble[4,4]`\] and `r desc_tibble[5,2]` indicated other sex \[EFA: `r desc_tibble[5,3]`, CFA: `r desc_tibble[5,4]`\].
+Overall, `r desc_tibble[6,2]` \[EFA: `r desc_tibble[6,3]`; CFA: `r desc_tibble[6,4]`\] participants indicated a gender-variant identity.
+In a "Yes/No" question regarding native language, `r desc_tibble[7,2]` of respondents \[EFA: `r desc_tibble[7,3]`; CFA: `r desc_tibble[7,4]`\] indicated to be native English speakers.
+For their "Occupational Status", more than half of the overall sample reported that they currently work \[Overall: `r desc_tibble[9,2]`; EFA: `r desc_tibble[9,3]`; CFA: `r desc_tibble[9,4]`\], whereas `r desc_tibble[10,2]` \[EFA: `r desc_tibble[10,3]`; CFA: `r desc_tibble[10,4]`\] reported that they go to school and `r desc_tibble[11,2]` \[EFA: `r desc_tibble[11,3]`; CFA: `r desc_tibble[11,4]`\] responded that they do "Neither".
+With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` \[EFA: `r desc_tibble[13,3]`; CFA: `r desc_tibble[13,4]`\] of the participants indicated that they were in a home office/ home schooling setting., while `r desc_tibble[14,2]` overall \[EFA: `r desc_tibble[14,3]` ; CFA: `r desc_tibble[14,4]`\] reported face-to-face work/schooling.
+Lastly, `r desc_tibble[15,2]` overall \[EFA: `r desc_tibble[15,3]` ; CFA: `r desc_tibble[15,4]`\] reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]` overall \[EFA: `r desc_tibble[16,3]`; CFA: `r desc_tibble[16,4]`\] filled in the "Neither (no work or school, or indication)" response option.
 We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable "Age" and Pearson's Chi-squared test for all other categorical variables via the gtsummary R package's "add_p" function [@sjoberg2021] .
@@
 
-We used R (version 4.1.0), including several R packages, for our analyses.
+We used R (version 4.1.0), including several R packages, for our analyses.Initially, our tool have six poin Likert type response scale(0:Does not apply/I don’t know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Alsways).
+As our purpose was to capture light exposure related behavior, "Does not apply/I don’t know" and "Never" were providing similar information.
+As such we decided to collapse "Does not apply/I don’t know" and "Never" options into one making it a 5 point Likert type response scale.
 Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
@@
 Due to these violations and the ordinal nature of our response data, we used a polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA.
-We employed principal axis (pa), a factor extraction method with varimax rotation.
+We employed principal axis (PA) as a factor extraction method with varimax rotation.
 PA is robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020].
-The obtained latent structure was confirmed by the minimum residuals extraction method as well.
+The obtained latent structure was confirmed by another factor extraction method: the minimum residuals extraction method as well.
 We used a combination factor identification method including scree plot[@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method[@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
-Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018;
+Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018]
+We also conducted psychometric analysis on non-merged response options data (supplementary analysis) and rejected the latent structure obtained as the factors were less interpretable.
 
@@
 #library(VIM)
-missing <- aggr(EFA.data, plot =T)
+missing <- VIM::aggr(EFA.data, plot =T)
 
@@
 #KMO test
-KMO <- KMO(EFA.data)
+KMO <- psych::KMO(EFA.data)
 
 # Test of correlation matrix
-bartlet <- cortest.bartlett(EFA.data, n =428)
+bartlet <- psych::cortest.bartlett(EFA.data, n =428)
 
@@
 # Multivariate Normality
-mardia <- mardia(EFA.data, na.rm = T, plot =F)
+mardia <- psych::mardia(EFA.data, na.rm = T, plot =F)
 
@@
 
-correlations <- polychoric(EFA.data, correct = 0)
+correlations <- psych::polychoric(EFA.data, correct = 0)
 upper <- correlations$rho[upper.tri(correlations$rho, diag = F)]
@@
 Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018].
-Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p \< .001] indicated the correlations between items are adequate for the EFA.
+Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p \< .001\] indicated the correlations between items are adequate for the EFA.
 However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than .30.
@@
 Horn's parallel analysis [@hornRationaleTestNumber1965] with 500 iterations also indicated a six-factor solution.
-However, the MAP method [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] suggested a five-factor solution.
+However, the  minimum average partial (MAP) method [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] suggested a five-factor solution.
 As a result, we tested both five-factor and six-factor solutions.
@@
 
-```{r minres 5 factor supplimentary analyisis, eval=FALSE, include=FALSE}
-
-#Supplementary EFA with Minres Extraction
-
-fa.5F.min.1 <- fa(r=correlations$rho, nfactors = 5, fm= "minres",rotate ="varimax",
-                residuals = TRUE, SMC = TRUE, n.obs =428)
-EE <- print(fa.5F.min.1, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.5F.min.1 <- dplyr::select(EFA.data ,
-                                    -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14))
-
-correlations.red.5F.min.1 <- polychoric(reduced.model.5F.min.1,correct = 0)
-
-fa.5F.min.2 <- fa(r=correlations.red.5F.min.1$rho, nfactors = 5, fm= "minres",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-FF <- print(fa.5F.min.2, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.5F.min.2 <- dplyr::select(EFA.data, -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14, item34, item47, item21, item13))
-
-correlations.red.5F.min.2 <- polychoric(reduced.model.5F.min.2, correct = 0)
-
-fa.5F.min.3 <- fa(r=correlations.red.5F.min.2$rho, nfactors = 5, fm= "minres",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-GG <- print(fa.5F.min.3, cut = .3, digits = 3, sort = TRUE)
-```
-
-```{r EFA 6 Factors Promax, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, results='hide'}
-# EFA with 6 factor (rejected)
-
-#correlations <- polychoric(EFA.factor, correct = 0)
-
-fa.6F.1 <- fa(r=correlations$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-II <- print(fa.6F.1, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.6F.1 <- dplyr::select(EFA.data ,
-                                    -c(item34, item44, item48, item43, item39, item22, item2, item20, item21, item24,item30, item14, item28, item6, item15, item23))
-
-correlations.red.6F.1 <- polychoric(reduced.model.6F.1,correct = 0)
-
-fa.6F.2 <- fa(r=correlations.red.6F.1$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-JJ <- print(fa.6F.2, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.6F.2 <- dplyr::select(EFA.data, -c(item34, item44, item48, item43, item39, item22, item2, item20, item21, item24,item30, item14, item28, item6, item15, item23, item18, item42, item47, item41))
-
-correlations.red.6F.2 <- polychoric(reduced.model.6F.2,correct = 0)
-
-fa.6F.3 <- fa(r=correlations.red.6F.2$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)
-
-KK <- print(fa.6F.3, cut = .3, digits = 3, sort = TRUE)
-
-# Residuals
-residual.6F =residuals(fa.6F.3 , diag = FALSE, na.rm =T)
-#Count of numbers of residuals>.05
-BigRRR= sum(residual.6F>abs(.05), na.rm =T)
-print(BigRRR)
-
-#Total number of off diagonal elements in the data matrix
-totRRR = length(reduced.model.6F.2)*(length(reduced.model.6F.2)-1)/2
-
-# Proportion of off-diagonal elements >.10
-sumRRR <- sum(BigRRR/totRRR*100)
-
-hist(residual.6F, main = NULL, xlab = "Six factor Solution: Residuals",ylim=c(0, 400))
-abline(h =65, lwd = 2, lty = 2)
-abline(v =.05,lwd = 2, lty = 2)
-```
-
-```{r factordetails, include=FALSE}
-#Preparing the EFA table
-library(data.table)
-fa_table <- function(x, cut) {
-  #get sorted loadings
-  loadings <- fa.sort(x)$loadings %>% round(2)
-  #supress loadings
-  loadings[abs(loadings) < abs(cut)] <- ""
-  #get additional info
-  add_info <- cbind(x$communality, 
-                    x$uniquenesses,
-                    x$complexity) %>%
-    # make it a data frame
-    as.data.frame() %>%
-    # column names
-    rename("Communality" = V1,
-           "Uniqueness" = V2,
-           "Complexity" = V3) %>%
-    #get the item names from the vector
-    rownames_to_column("item")
-  #build table
-  loadings <- loadings %>%
-    unclass() %>%
-    as.data.frame() %>%
-    rownames_to_column("item") %>%
-    left_join(add_info) %>%
-    mutate(across(where(is.numeric), round, 3)) %>% 
-    as.data.frame()
-  variance <- x$Vaccounted %>% 
-  as.data.frame()%>% 
-  round(2)
-  loadings <- rbind(setDT(loadings), setDT(variance[2,]), fill=TRUE)
-
-}
-
-efa.table <- fa_table(fa.5F.3,.3) 
-nr <- nrow(efa.table)
-efa.table[nr, 1] <- "% of Variance"
+```{r tabledown}
+efa.table <- tabledown::fac.tab(fa.5F.3,cut=.3, complexity = F)
 
@@
 
-Three rounds of EFA with all 48 items were conducted, and problematic items were gradually discarded (cross-loading items and poor factor loading (\<.30) items).
+With initial 48 items we conducted three rounds of EFA gradually discarded problematic items.
+(cross-loading items and poor factor loading (<.30) items).
 Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 [@brownConfirmatoryFactorAnalysis2015], all factor-loading higher than .30 and no cross-loading greater than .30.
-We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (see the supplementary).
-Table\@ref(tab:TabEFA5) displays the factor-loading (structural coefficients) and communality of the items.
+We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (Table\@ref(tab:MinResTab)).
+Table\@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items.
 The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients.
 The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`.
-However, the histogram of the absolute values of non-redundant residual-correlations (Fig\@ref(fig:Residuals) showed `r apa(sumR,2, T)`% correlations greater than the absolute value of .05, indicating a possible under-factoring.
+However, the histogram of the absolute values of non-redundant residual-correlations (Fig\@ref(fig:EFAResiduals) showed `r apa(sumR,0, T)`% correlations greater than the absolute value of .05, indicating a possible under-factoring.
 [@desjardinsHandbookEducationalMeasurement2018a].
 Subsequently, we fitted a six-factor solution.
-However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution.
+However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution (Table\@ref(tab:sixFacTab)).
 
@@
 Items under this factor dealt with the specific behaviors pertaining to sleep.
-However, the internal consistency reliability coefficient was not satisfactory ($\alpha$ = `r apa(F3.alpha,2,F)`).
+The internal consistency reliability coefficient was, $\alpha$ = `r apa(F3.alpha,2,F)`.
 The fourth factor contained five items and explained `r apa(var4,2,F)`% of the total variance with an internal consistency coefficient, $\alpha$ = `r apa(F4.alpha,2,F)`.
@@
 However, this factor showed unsatisfactory internal consistency reliability ($\alpha$ = `r apa(F5.alpha,2,F)`).
-It is essential to attain a balance between psychometric properties and the interpretability of the common themes when exploring the latent structure.
-As all of the emerged factors are highly interpretable, regardless of the apparent low reliability of the two factors, we retain the five-factor solution with 23 items for our confirmatory factor analysis (CFA).
+It is essential to attain a balance between psychometric properties and interpretability of the common themes when exploring the latent structure.
+As all of the emerged factors are highly interpretable and relevant towards our aim to capture light exposure related behavior, regardless of the apparent low reliability of the two factors, we retain the five-factor solution with 23 items for our confirmatory factor analysis (CFA).
 Two items showed negative factor-loading (items 44 and 21).
@@
 
-# Confirmatory Factor Analysis
+## Confirmatory Factor Analysis
 
@@
 
-We conducted a categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator as our response data was in ordinary nature [@desjardinsHandbookEducationalMeasurement2018a].
-Several indices exist to measure the the model fit.
-These can be categorized as absolute fit, comparative fit and parsimony fit indices [@brownConfirmatoryFactorAnalysis2015].
+We conducted a categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator as our response data was in ordinary nature[@desjardinsHandbookEducationalMeasurement2018].
+Several indices are suggested to measure model fit.
+These indices can be categorized as absolute, comparative and parsimony fit indices [@brownConfirmatoryFactorAnalysis2015].
 Absolute fit assess the model fit at an absolute level using indices including chi-square test statistics and the standardized root mean square (SRMR).parsimony fit indices including the root mean square error of approximation (RMSEA) considers the number of free parameters in the model to assess the parsimony of the model.
@@
 Commonly used Model fit guidelines [@huCutoffCriteriaFit1999; @schumacker2004beginner] includes (i) Reporting of chi-square test statistics (A non-significant test statistics is required to reflect model fit) (i) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (ii) RMSEA (close to .06 or below), (iii) SRMR (close to .08 or below) to estimate the model fit.
-Table\@ref(tab:tabCfa) summarizes the fit indices of our fitted model.
-The fitted model failed to attain an absolute fit estimated by the chi-square test.
+Table \@ref(tab:tabCfa) summarizes the fit indices of our fitted model.
+Our fitted model failed to attain an absolute fit estimated by the chi-square test.
 However, the chi-square test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit [@brownConfirmatoryFactorAnalysis2015].
@@
 Subsequently, we judged the model fit based on the comparative fit indices: CFI, TLI and parsimony fit index-RMSEA.
-Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 and 19-17 .
+Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`\[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI\]) with two imposed equity constrain on item pairs 32-33 and 19-17 .
 However SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`).
-Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR value (SRMR = `r apa(fit.2[10],2,F)`) was also close to the suggestions of @huCutoffCriteriaFit1999.
-The internal consistency reliability coefficients coefficient alpha `r apa(rel.k[1,1],2,F)`, `r apa(rel.k[1,2],2,F)`, `r apa(rel.k[1,3],2,F)`, `r apa(rel.k[1,4],2,F)`, `r apa(rel.k[1,5],2,F)` respectively indicating satisfactory reliability for F1, F2 and F4 [@najeracatalanReliabilityPopulationClassification2019]
+Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`\[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI\]) and SRMR value (SRMR = `r apa(fit.2[10],2,F)`) was also close to the suggestions of @huCutoffCriteriaFit1999.
+Since reliability coefficient Cronbach's alpha tends to mis-measure reliability for multidimensional construct [@sijtsma2009use] we report  Mcdonald's omega(total) as the internal consistency reliability  coefficient.
+Mcdonald's omega(total) is reported to be a satisfactory lower bound reliability coefficient that works for both unidimensional and multidimensional construct [@zinbarg2005cronbach].
+Mcdonald's omega(total) for the five factors were `r apa(rel.k[1,1],2,F)`, `r apa(rel.k[5,2],2,F)`, `r apa(rel.k[5,3],2,F)`, `r apa(rel.k[5,4],2,F)`, `r apa(rel.k[5,5],2,F)` respectively.
+Mcdonald's omega(total) coefficient for the total scale was `r apa(rel.k[5,6],2,F)`.
 
@@
 Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait, and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
-Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information <.2) to develop the short form of LEBA.
-@bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70.
+Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information \<.2) to develop the short form of LEBA.
+@bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70.
 Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), low ( 5 items) indicating a good range of discrimination along the latent trait.
@@
 Our result also indicated all the items fitted well to the respective models as assessed by assessed by RMSEA value obtained from Signed-X2 index implementation.
-All of the items had RMSEA value <.06 indicating adequate fit.
+All of the items had RMSEA value \<.06 indicating adequate fit.
 Person fit indicates the validity and meaningfulness of the fitted model at the participants latent trait level [@desjardinsHandbookEducationalMeasurement2018].
 We estimated the person fit statistics using standardized fit index Zh statistics [@drasgow1985appropriateness].
-Zh < -2 should be considered as a misfit.
+Zh \< -2 should be considered as a misfit.
 Fig indicates that Zh is larger than -2 for most participants, suggesting a good fit of the selected IRT models.
@@
 
+```{=tex}
 \endgroup
-
+```
 ```{r echo = FALSE, results = 'asis', cache = FALSE}
@@
 ```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('instrument.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('Appendix-B.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('Supplymentary.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('instrument.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('Appendix-B.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('Supplymentary.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('instrument.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('Appendix-B.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('Supplymentary.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('instrument.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('Appendix-B.Rmd')
+```

### 2021-11-09 manuscript.Rmd
* lines are no longer broken this was caused by visual editor

@@
 packrat::snapshot(ignore.stale=TRUE)
-
-```
-
-```{r install, eval=FALSE, include=FALSE}
-#if "packrat" does not work you can run this chunk manually to get all required packs"
-
-install.packages("devtools")
-install.packages("semTools")
-install.packages("MOTE")
-install.packages("psych")
-install.packages("lavaan")
-install.packages("dlookr")
-install.packages("tidyverse")
-install.packages("qgraph")
-install.packages("kableExtra")
-install.packages("paran")
-install.packages("EFA.MRFA")
-install.packages("rsvg")
-install.packages("ggcorrplot")
-install.packages("semTable")
-install.packages("magick")
-install.packages("mirt")
-install.packages("cowplot")
-install.packages("VIM")
-devtools::install_github('rich-iannone/DiagrammeR')
-devtools::install_github("crsh/papaja", force = T)
-install.packages("DiagrammeRsvg")
-devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
-devtools::install_github("crsh/citr")
-remotes::install_github("jthomasmock/gtExtras")
-install.packages("gt")
-
-install.packages("questionr")
 
@@
 Data was collected in a quantitative cross-sectional approach via a fully anonymous online survey hosted on REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
-Participants were recruited via the website of a Comic co-released with the survey[@Weinzaepflen.2021]( https://enlightenyourclock.org/participate-in-research), social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux software [@f.lux].
+Participants were recruited via the website of a Comic co-released with the survey\[\@Weinzaepflen.2021\]( <https://enlightenyourclock.org/participate-in-research>), social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux software \[\@f.lux\].
 
@@
 The first page of the survey comprised a participant information sheet, where participants' informed consent to participate was obtained before any of the questions were displayed.
-Underaged participants (<18 years) were urged to obtain assent from their parents/legal guardians, before filling in the survey.
+Underaged participants (\<18 years) were urged to obtain assent from their parents/legal guardians, before filling in the survey.
 Information on the first page included the objectives of the study, inclusion criteria, estimated duration, the use, storage and sharing of the data, compensation (none), and information about the type of questions in the survey.
@@
 
--   Sleep disturbance and sleep-related impairment (adult and pediatric versions) [@Bevans.2019; @Buysse.2010; @Forrest.2018; @Harb.2015; @Yu.2011]
+-   Sleep disturbance and sleep-related impairment (adult and pediatric versions) \[\@Bevans.2019; \@Buysse.2010; \@Forrest.2018; \@Harb.2015; \@Yu.2011\]
 -   Sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration (version for adults and adolescents) [@roenneberg2003life]
--   Sleep environment [\@Olivier.2016]
--   Meal timing & caffeine consumption [custom items]
--   Light sensitivity (photophobia vs. photophilia) [\@Wu.2017]
--   Self-reported pubertal stage (only if younger than 18 years old) [@Petersen.1988]
+-   Sleep environment \[\@Olivier.2016\]
+-   Meal timing & caffeine consumption \[custom items\]
+-   Light sensitivity (photophobia vs. photophilia) \[\@Wu.2017\]
+-   Self-reported pubertal stage (only if younger than 18 years old) \[\@Petersen.1988\]
 
@@
 
-#as_kable_extra(desc_table) -> desc_kable_extra
+as_gt(desc_table) -> desc_gt
 ```
@@
 desc_kable %>% kable_styling(desc_kable, repeat_header_text = "Participants' Demographic Characteristics")
+
+#desc_gt %>% gt::tab_header("Participants' Demographic Characteristics")
 
@@
 XX participants were excluded from analysis due to not passing at least one of the "attention check" items.
-For exploring initial factor structure (EFA) , a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013].
-For estimating the sample size for the confirmatory factor analysis (CFA) we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per parameter is required to earn trustworthiness of the result.
+For exploring initial factor structure (EFA) , a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013\].
+For estimating the sample size for the confirmatory factor analysis (CFA) we followed the N:q rule \[@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per parameter is required to earn trustworthiness of the result.
 Our sample size exceeds these requirements: Anonymous responses from a total of *n* = `r nrow(desctable.data)` participants were included in the analysis of the current study, split into samples for exploratory (EFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "1.
@@
 
-We used R (version 4.1.0), including several R packages, for our analyses.Initially, our tool have six poin Likert type response scale(0:Does not apply/I don’t know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Alsways).
-As our purpose was to capture light exposure related behavior, "Does not apply/I don’t know" and "Never" were providing similar information.
-As such we decided to collapse "Does not apply/I don’t know" and "Never" options into one making it a 5 point Likert type response scale.
+We used R (version 4.1.0), including several R packages, for our analyses.Initially, our tool have six poin Likert type response scale(0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Alsways).
+As our purpose was to capture light exposure related behavior, "Does not apply/I don't know" and "Never" were providing similar information.
+As such we decided to collapse "Does not apply/I don't know" and "Never" options into one making it a 5 point Likert type response scale.
 Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
@@
 We used a combination factor identification method including scree plot[@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method[@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
-Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018]
-We also conducted psychometric analysis on non-merged response options data (supplementary analysis) and rejected the latent structure obtained as the factors were less interpretable.
+Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018] We also conducted psychometric analysis on non-merged response options data (supplementary analysis) and rejected the latent structure obtained as the factors were less interpretable.
 
@@
 
-```{r tabledown}
+```{r tabledown, include=F}
 efa.table <- tabledown::fac.tab(fa.5F.3,cut=.3, complexity = F)
@@
 With initial 48 items we conducted three rounds of EFA gradually discarded problematic items.
-(cross-loading items and poor factor loading (<.30) items).
+(cross-loading items and poor factor loading (\<.30) items).
 Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 [@brownConfirmatoryFactorAnalysis2015], all factor-loading higher than .30 and no cross-loading greater than .30.
@@
 The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`.
-However, the histogram of the absolute values of non-redundant residual-correlations (Fig\@ref(fig:EFAResiduals) showed `r apa(sumR,0, T)`% correlations greater than the absolute value of .05, indicating a possible under-factoring.
+However, the histogram of the absolute values of non-redundant residual-correlations Fig\@ref(fig:EFAResiduals) showed `r apa(sumR,0, T)`% correlations greater than the absolute value of .05, indicating a possible under-factoring.
 [@desjardinsHandbookEducationalMeasurement2018a].
@@
 Subsequently, we judged the model fit based on the comparative fit indices: CFI, TLI and parsimony fit index-RMSEA.
-Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`\[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI\]) with two imposed equity constrain on item pairs 32-33 and 19-17 .
+Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`,\[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI\]) with two imposed equity constrain on item pairs 32-33 and 19-17 .
 However SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`).
@@
 
-```{r IRTscoreCor, results='asis'}
+```{r IRTscoreCor, eval=FALSE, include=FALSE, results='asis'}
 apa_table (theta.correlation.matrix, caption = "correlation coefficents of obtained scores and estimated latent trait for each factots", note = "* p < 0.05; ** p < 0.01; *** p < 0.001"  )
-```
-
-```{r clean, eval=FALSE, include=FALSE}
-cleanFolder <- function() {
-  answer <- NA
-  while(!(answer %in% c('y', 'n'))) {
-    answer <- readline(paste("Clean ", getwd(),"? (y/n)"))
-  }
-  if(answer == 'y') {
-    rules <- c('.log', '.vrb', '.nav', '.snm', '.toc', 
-               '-tikzDictionary', '.tex', '.synctex.gz')
-    file.remove(list.files(pattern = paste0('\\',rules ,'$', collapse = '|')))
-  }
-}
-cleanFolder(y)
 ```
@@
 ```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('Appendix-B.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('instrument.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('Appendix-B.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('Supplymentary.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('instrument.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('Appendix-B.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('Supplymentary.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('instrument.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('Appendix-B.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('Supplymentary.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('instrument.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('Appendix-B.Rmd')
-```

### 2021-11-09 install_packages.R

@@ -1,0 +1,32 @@
+
+#if "packrat" does not work you can run this chunk manually to get all required packs"
+
+install.packages("devtools")
+install.packages("semTools")
+install.packages("MOTE")
+install.packages("psych")
+install.packages("lavaan")
+install.packages("dlookr")
+install.packages("tidyverse")
+install.packages("qgraph")
+install.packages("kableExtra")
+install.packages("paran")
+install.packages("EFA.MRFA")
+install.packages("rsvg")
+install.packages("ggcorrplot")
+install.packages("semTable")
+install.packages("magick")
+install.packages("mirt")
+install.packages("cowplot")
+install.packages("VIM")
+devtools::install_github('rich-iannone/DiagrammeR')
+devtools::install_github("crsh/papaja", force = T)
+install.packages("DiagrammeRsvg")
+devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
+devtools::install_github("crsh/citr")
+remotes::install_github("jthomasmock/gtExtras")
+install.packages("gt")
+
+install.packages("questionr")
+
+```

### 2021-11-10 Appendix-B.Rmd
* rnev introduced
loading is much faster

@@
 
-```{r EFAResidualsAppB, echo=FALSE, fig.align='center', fig.cap=' Histogram of residulas:  five-factor solution', warning=FALSE, out.height="50%", out.width="50%", results='asis'}
+```{r EFAResidualsAppB, eval=FALSE, fig.align='center', fig.cap=' Histogram of residulas:  five-factor solution', warning=FALSE, include=FALSE,  results='asis'}
 hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))

### 2021-11-10 Appendix-B.tex
* rnev introduced
loading is much faster

--- 2021-11-06 Appendix-B.tex
@@
 \caption{Correlation plot of the items}(\#fig:figCorAppB)
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth,height=1\textheight]{manuscript_files/figure-latex/facIdFigAppB-1}
+
+}
+
+\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}(\#fig:facIdFigAppB)
 \end{figure}
@@
 \end{longtable}
-
-\begin{figure}
-
-{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/EFAResidualsAppB-1}
-
-}
-
-\caption{ Histogram of residulas:  five-factor solution}(\#fig:EFAResidualsAppB)
-\end{figure}
 \end{appendix}

### 2021-11-10 Supplymentary.tex
* rnev introduced
loading is much faster

\clearpage
\makeatletter
\efloat@restorefloats
\makeatother

\begin{appendix}
\section{}
\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:MinResTab}Factor loadings and communality of the retained items(Minmum Residual)}

\small{

\begin{tabular}{cccccccc}
\toprule
item & \multicolumn{1}{c}{MR1} & \multicolumn{1}{c}{MR2} & \multicolumn{1}{c}{MR3} & \multicolumn{1}{c}{MR4} & \multicolumn{1}{c}{MR5} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness}\\
\midrule
item16 & 1 &  &  &  &  & 0.996 & 0.004\\
item36 & 0.94 &  &  &  &  & 0.897 & 0.103\\
item17 & 0.8 &  &  &  &  & 0.658 & 0.342\\
item11 &  & 0.79 &  &  &  & 0.642 & 0.358\\
item10 &  & 0.76 &  &  &  & 0.592 & 0.408\\
item12 &  & 0.65 &  &  &  & 0.465 & 0.535\\
item7 &  & 0.5 &  &  &  & 0.267 & 0.733\\
item8 &  & -0.49 &  &  &  & 0.252 & 0.748\\
item9 &  & 0.32 &  &  &  & 0.113 & 0.887\\
item27 &  &  & 0.8 &  &  & 0.659 & 0.341\\
item3 &  &  & 0.8 &  &  & 0.683 & 0.317\\
item40 &  &  & 0.65 &  &  & 0.464 & 0.536\\
item30 &  &  & 0.45 &  &  & 0.353 & 0.647\\
item41 &  &  & 0.36 &  &  & 0.329 & 0.671\\
item33 &  &  &  & 0.74 &  & 0.555 & 0.445\\
item32 &  &  &  & 0.73 &  & 0.623 & 0.377\\
item35 &  &  &  & 0.66 &  & 0.455 & 0.545\\
item37 &  &  &  & -0.39 &  & 0.175 & 0.825\\
item38 &  &  &  & 0.38 &  & 0.178 & 0.822\\
item46 &  &  &  &  & 0.6 & 0.422 & 0.578\\
item45 &  &  &  &  & 0.59 & 0.374 & 0.626\\
item25 &  &  &  &  & 0.41 & 0.193 & 0.807\\
item4 &  &  &  &  & 0.41 & 0.219 & 0.781\\
item1 &  &  &  &  & 0.4 & 0.17 & 0.83\\
item26 &  &  &  &  & 0.35 & 0.165 & 0.835\\
\% of Variance & 0.1 & 0.1 & 0.09 & 0.08 & 0.06 &  & \\
\bottomrule
\addlinespace
\end{tabular}

}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} Only loading higher than .30 is reported}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:sixFacTab}Factor loadings and communality of the retained items(six factor)}

\small{

\begin{tabular}{ccccccccc}
\toprule
item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA6} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness}\\
\midrule
item19 & 1.78 &  &  &  &  &  & 3.318 & -2.318\\
item5 &  &  &  &  &  &  & 0.11 & 0.89\\
item16 &  & 1 &  &  &  &  & 1.004 & -0.004\\
item36 &  & 0.91 &  &  &  &  & 0.86 & 0.14\\
item17 &  & 0.81 &  &  &  &  & 0.691 & 0.309\\
item11 &  &  & 0.83 &  &  &  & 0.71 & 0.29\\
item10 &  &  & 0.79 &  &  &  & 0.638 & 0.362\\
item12 &  &  & 0.63 &  &  &  & 0.465 & 0.535\\
item8 &  &  & -0.5 &  &  &  & 0.269 & 0.731\\
item7 &  &  & 0.47 &  &  &  & 0.268 & 0.732\\
item9 &  &  & 0.32 &  &  &  & 0.163 & 0.837\\
item33 &  &  &  & 0.83 &  &  & 0.698 & 0.302\\
item32 &  &  &  & 0.75 &  &  & 0.666 & 0.334\\
item35 &  &  &  & 0.64 &  &  & 0.446 & 0.554\\
item31 &  &  &  & 0.48 &  &  & 0.331 & 0.669\\
item38 &  &  &  & 0.39 &  &  & 0.191 & 0.809\\
item37 &  &  &  & -0.35 &  &  & 0.153 & 0.847\\
item3 &  &  &  &  & 0.85 &  & 0.748 & 0.252\\
item27 &  &  &  &  & 0.8 &  & 0.644 & 0.356\\
item40 &  &  &  &  & 0.68 &  & 0.507 & 0.493\\
item46 &  &  &  &  &  & 0.6 & 0.431 & 0.569\\
item45 &  &  &  &  &  & 0.56 & 0.341 & 0.659\\
item4 &  &  &  &  &  & 0.43 & 0.265 & 0.735\\
item25 &  &  &  &  &  & 0.4 & 0.178 & 0.822\\
item1 &  &  &  &  &  & 0.36 & 0.142 & 0.858\\
item26 &  &  &  &  &  & 0.36 & 0.173 & 0.827\\
item13 &  &  &  &  &  &  & 0.087 & 0.913\\
item29 &  &  &  &  &  &  & 0.108 & 0.892\\
\% of Variance & 0.12 & 0.09 & 0.09 & 0.08 & 0.07 & 0.06 &  & \\
\bottomrule
\addlinespace
\end{tabular}

}

\begin{tablenotes}[para]
\normalsize{\textit{Note.} Only loading higher than .30 is reported}
\end{tablenotes}

\end{threeparttable}
\end{center}

\end{table}
\end{appendix}

### 2021-11-10 manuscript.Rmd
* rnev introduced
loading is much faster

@@
       in_header: header.tex
-appendix:
-  - "Supplymentary.Rmd"
-  - "instrument.Rmd"
-  - "Appendix-B.Rmd"
+
 mainfont: Helvetica
@@
 
-```{r depMan}
-library(packrat)
-packrat::init(infer.dependencies = F)# install dependencies only for Rmd files in this project
-
-#To find and install required dependencies.
-packrat::restore()
-#Only use when you have added some pack
-packrat::snapshot(ignore.stale=TRUE)
-
+```{r depMan, include=F}
+renv::init()
+#renv::snapshot()
+#renv::status()
+renv::restore()
 ```
@@
 +-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| Assessment of Sleep Environment                                   | \[@Olivier.2016\]        | 13 items questionnaire measuring your sleep environment quality                                                                                              |                                      |             |
+| Assessment of Sleep Environment                                   | [@Olivier.2016]       | 13 items questionnaire measuring your sleep environment quality                                                                                              |                                      |             |
 +-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
@@
 +-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| Self-Rating of Biological Rhythm Disorder for Adolescents (SBRDA) | \[@Xie.2021\]            | 29 items questionnaire assessing four dimensions of biological rhythm disorder in adolescents (digital media use, sleep, eating habits, and activity)        | Items 3., 22., 23., 24., 25.
+| Self-Rating of Biological Rhythm Disorder for Adolescents (SBRDA) | [@Xie.2021]           | 29 items questionnaire assessing four dimensions of biological rhythm disorder in adolescents (digital media use, sleep, eating habits, and activity)        | Items 3., 22., 23., 24., 25.
 and 29.
@@
 +-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| Photosensitivity Assessment Questionnaire (PAQ)                   | \[@Wu.2017\]             | 16 dichotomous (yes/no) items questionnaire to assess "photophobia" and "photophilia", giving two final scores of "photophobic" and "photophilic" behaviours | All items                            |             |
+| Photosensitivity Assessment Questionnaire (PAQ)                   | [@Wu.2017]            | 16 dichotomous (yes/no) items questionnaire to assess "photophobia" and "photophilia", giving two final scores of "photophobic" and "photophilic" behaviours | All items                            |             |
 +-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
@@
 Data was collected in a quantitative cross-sectional approach via a fully anonymous online survey hosted on REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
-Participants were recruited via the website of a Comic co-released with the survey\[\@Weinzaepflen.2021\]( <https://enlightenyourclock.org/participate-in-research>), social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux software \[\@f.lux\].
+Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) of a Comic co-released with the survey[@Weinzaepflen.2021] , social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux software [@f.lux].
 
@@
 
--   Sleep disturbance and sleep-related impairment (adult and pediatric versions) \[\@Bevans.2019; \@Buysse.2010; \@Forrest.2018; \@Harb.2015; \@Yu.2011\]
+-   Sleep disturbance and sleep-related impairment (adult and pediatric versions) [@Bevans.2019; @Buysse.2010; @Forrest.2018; @Harb.2015; @Yu.2011]
 -   Sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration (version for adults and adolescents) [@roenneberg2003life]
--   Sleep environment \[\@Olivier.2016\]
--   Meal timing & caffeine consumption \[custom items\]
--   Light sensitivity (photophobia vs. photophilia) \[\@Wu.2017\]
--   Self-reported pubertal stage (only if younger than 18 years old) \[\@Petersen.1988\]
+-   Sleep environment [@Olivier.2016\
+-   Meal timing & caffeine consumption [custom items]
+-   Light sensitivity (photophobia vs. photophilia) [@Wu.2017]
+-   Self-reported pubertal stage (only if younger than 18 years old) [@Petersen.1988]
 
@@
 XX participants were excluded from analysis due to not passing at least one of the "attention check" items.
-For exploring initial factor structure (EFA) , a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013\].
-For estimating the sample size for the confirmatory factor analysis (CFA) we followed the N:q rule \[@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per parameter is required to earn trustworthiness of the result.
+For exploring initial factor structure (EFA) , a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013].
+For estimating the sample size for the confirmatory factor analysis (CFA) we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per parameter is required to earn trustworthiness of the result.
 Our sample size exceeds these requirements: Anonymous responses from a total of *n* = `r nrow(desctable.data)` participants were included in the analysis of the current study, split into samples for exploratory (EFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "1.
@@
 
-Age among all participants ranged from `r min(desctable.data$slypos_demographics_age)` years to `r max(desctable.data$slypos_demographics_age)` years \[EFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
+Age among all participants ranged from `r min(desctable.data$slypos_demographics_age)` years to `r max(desctable.data$slypos_demographics_age)` years [EFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
 EFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
@@
 CFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`\], with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 0)` years of age \[Overall: *M* = `r mean(desctable.data$slypos_demographics_age)`, *SD* = `r sd(desctable.data$slypos_demographics_age)`; EFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
+CFA Sample"])`], with an overall mean of ~ `r round(mean(desctable.data$slypos_demographics_age), 0)` years of age [Overall: *M* = `r mean(desctable.data$slypos_demographics_age)`, *SD* = `r sd(desctable.data$slypos_demographics_age)`; EFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
 EFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
@@
 CFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`\].
-In total `r desc_tibble[3,2]` of the participants indicated female sex \[EFA: `r desc_tibble[3,3]`; CFA: `r desc_tibble[3,4]`\], `r desc_tibble[4,2]` indicated male \[EFA: `r desc_tibble[4,3]`; CFA: `r desc_tibble[4,4]`\] and `r desc_tibble[5,2]` indicated other sex \[EFA: `r desc_tibble[5,3]`, CFA: `r desc_tibble[5,4]`\].
-Overall, `r desc_tibble[6,2]` \[EFA: `r desc_tibble[6,3]`; CFA: `r desc_tibble[6,4]`\] participants indicated a gender-variant identity.
-In a "Yes/No" question regarding native language, `r desc_tibble[7,2]` of respondents \[EFA: `r desc_tibble[7,3]`; CFA: `r desc_tibble[7,4]`\] indicated to be native English speakers.
-For their "Occupational Status", more than half of the overall sample reported that they currently work \[Overall: `r desc_tibble[9,2]`; EFA: `r desc_tibble[9,3]`; CFA: `r desc_tibble[9,4]`\], whereas `r desc_tibble[10,2]` \[EFA: `r desc_tibble[10,3]`; CFA: `r desc_tibble[10,4]`\] reported that they go to school and `r desc_tibble[11,2]` \[EFA: `r desc_tibble[11,3]`; CFA: `r desc_tibble[11,4]`\] responded that they do "Neither".
-With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` \[EFA: `r desc_tibble[13,3]`; CFA: `r desc_tibble[13,4]`\] of the participants indicated that they were in a home office/ home schooling setting., while `r desc_tibble[14,2]` overall \[EFA: `r desc_tibble[14,3]` ; CFA: `r desc_tibble[14,4]`\] reported face-to-face work/schooling.
-Lastly, `r desc_tibble[15,2]` overall \[EFA: `r desc_tibble[15,3]` ; CFA: `r desc_tibble[15,4]`\] reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]` overall \[EFA: `r desc_tibble[16,3]`; CFA: `r desc_tibble[16,4]`\] filled in the "Neither (no work or school, or indication)" response option.
+CFA Sample"])`].
+In total `r desc_tibble[3,2]` of the participants indicated female sex [EFA: `r desc_tibble[3,3]`; CFA: `r desc_tibble[3,4]`], `r desc_tibble[4,2]` indicated male [EFA: `r desc_tibble[4,3]`; CFA: `r desc_tibble[4,4]`] and `r desc_tibble[5,2]` indicated other sex [EFA: `r desc_tibble[5,3]`, CFA: `r desc_tibble[5,4]`].
+Overall, `r desc_tibble[6,2]` [EFA: `r desc_tibble[6,3]`; CFA: `r desc_tibble[6,4]`] participants indicated a gender-variant identity.
+In a "Yes/No" question regarding native language, `r desc_tibble[7,2]` of respondents [EFA: `r desc_tibble[7,3]`; CFA: `r desc_tibble[7,4]`] indicated to be native English speakers.
+For their "Occupational Status", more than half of the overall sample reported that they currently work [Overall: `r desc_tibble[9,2]`; EFA: `r desc_tibble[9,3]`; CFA: `r desc_tibble[9,4]`], whereas `r desc_tibble[10,2]` [EFA: `r desc_tibble[10,3]`; CFA: `r desc_tibble[10,4]`] reported that they go to school and `r desc_tibble[11,2]` [EFA: `r desc_tibble[11,3]`; CFA: `r desc_tibble[11,4]`] responded that they do "Neither".
+With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` [EFA: `r desc_tibble[13,3]`; CFA: `r desc_tibble[13,4]`\] of the participants indicated that they were in a home office/ home schooling setting., while `r desc_tibble[14,2]` overall [EFA: `r desc_tibble[14,3]` ; CFA: `r desc_tibble[14,4]`] reported face-to-face work/schooling.
+Lastly, `r desc_tibble[15,2]` overall [EFA: `r desc_tibble[15,3]` ; CFA: `r desc_tibble[15,4]`] reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]` overall [EFA: `r desc_tibble[16,3]`; CFA: `r desc_tibble[16,4]`] filled in the "Neither (no work or school, or indication)" response option.
 We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable "Age" and Pearson's Chi-squared test for all other categorical variables via the gtsummary R package's "add_p" function [@sjoberg2021] .
@@
 ```
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('instrument.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('Appendix-B.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('instrument.Rmd')
-```

### 2021-11-10 manuscript.tex
* rnev introduced
loading is much faster

@@
   man]{apa6}
+\title{\emph{Light Exposure Behavior Assessment (LEBA)}: Development of a novel instrument to capture light exposure-related behaviours}
+\author{Mushfiqul Anwar Siraji\textsuperscript{1, *}, Rafael Robert Lazar\textsuperscript{2, 3, *}, Juliëtte van Duijnhoven\textsuperscript{4}, Luc Schlangen\textsuperscript{5}, Shamsul Haque\textsuperscript{1}, Vineetha Kalavally\textsuperscript{6}, Céline Vetter\textsuperscript{7, 8}, Gena Glickman\textsuperscript{9}, Karin Smolders\textsuperscript{10}, \& Manuel Spitschan\textsuperscript{11, 2, 3}}
+\date{}
+
 \usepackage{amsmath,amssymb}
-\usepackage[]{arev}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{lmodern}
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
 \hypersetup{
-  pdftitle={Light Exposure Behavior Assessment (LEBA): Develop of a novel instrument to capture light exposure-related behaviours},
-  pdfauthor={Mushfiqul Anwar Siraji1, Rafael Robert Lazar2, \& Manuel Spitschan3},
+  pdftitle={Light Exposure Behavior Assessment (LEBA): Development of a novel instrument to capture light exposure-related behaviours},
+  pdfauthor={Mushfiqul Anwar Siraji1, *, Rafael Robert Lazar2, 3, *, Juliëtte van Duijnhoven4, Luc Schlangen5, Shamsul Haque1, Vineetha Kalavally6, Céline Vetter7, 8, Gena Glickman9, Karin Smolders10, \& Manuel Spitschan11, 2, 3},
   pdflang={en-EN},
@@
 \fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\usepackage{pdflscape}
+\newcommand{\blandscape}{\begin{landscape}}
+\newcommand{\elandscape}{\end{landscape}}
 % Manuscript styling
@@
 \usepackage{csquotes}
-\ifxetex
+\ifXeTeX
   % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
@@
 \fi
-\ifluatex
+\ifLuaTeX
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
-
-\title{\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours}
-\author{Mushfiqul Anwar Siraji\textsuperscript{1}, Rafael Robert Lazar\textsuperscript{2}, \& Manuel Spitschan\textsuperscript{3}}
-\date{}
 
@@
 The authors made the following contributions.
-Mushfiqul Anwar Siraji: Data Analysis, Writing - Original Draft Preparation, Data Visualization; Rafael Robert Lazar: Data Analysis, Writing - Original Draft Preparation, Data Visualization; Manuel Spitschan: Data Analysis, Writing - Original Draft Preparation, Data Visualization.
-
-Correspondence concerning this article should be addressed to Manuel Spitschan, . E-mail:
+Mushfiqul Anwar Siraji: Formal Analysis, Visualization, Writing -- original draft, Writing -- review \& editing;; Rafael Robert Lazar: Data curation, Investigation, Project administration, Visualization, Writing -- original draft, Writing -- review \& editing;; Juliëtte van Duijnhoven: Conceptualization, Methodology, Investigation, Writing -- review \& editing; Luc Schlangen: Conceptualization, Methodology, Investigation, Writing -- review \& editing; Shamsul Haque: Conceptualization, Supervision, Writing -- review \& editing; Vineetha Kalavally: Supervision, Writing -- review \& editing; Céline Vetter: Conceptualization, Writing -- review \& editing; Gena Glickman: Conceptualization, Methodology, Writing -- review \& editing; Karin Smolders: Conceptualization, Methodology, Writing -- review \& editing; Manuel Spitschan: Conceptualization, Data curation, Investigation, Project administration, Visualization, Methodology, Writing -- original draft, Writing -- review \& editing.
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Monash University, Malaysia\\\textsuperscript{2} University of Basel}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia\\\textsuperscript{2} Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland\\\textsuperscript{3} University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland\\\textsuperscript{4} Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands\\\textsuperscript{5} Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Intelligent Lighting Institute, Eindhoven, Netherlands\\\textsuperscript{6} Monash University, Department of Electrical and Computer Systems Engineering, Malaysia, Selangor, Malaysia\\\textsuperscript{7} University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA\\\textsuperscript{8} Ximes GmbH, Frankfurt, Germany\\\textsuperscript{9} Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA\\\textsuperscript{10} Eindhoven University of Technology, Human-Technology Interaction Group, Eindhoven, Netherlands\\\textsuperscript{11} University of Oxford, Department of Experimental Psychology, Oxford, UK\\\textsuperscript{*} Joint first author}
 
@@
 
+\begin{verbatim}
+## * The library is already synchronized with the lockfile.
+\end{verbatim}
+
 \hypertarget{introduction}{%
@@
 
+\begin{itemize}
+\item
+  Light exposure is important
+\item
+  Light exposure Behavior is important
+\item
+  Table: Overview Existing Related Scales: items in total / items on light exposure (behaviour)
+\item
+  Existing Scales: Review them in text
+\item
+  None of these do light exposure behavior.
+\end{itemize}
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.22}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.09}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.52}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.13}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.05}}@{}}
+\caption{Existing related Scales}\tabularnewline
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+Name
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Authors
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Description
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Relevant Items
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Adaptations
+\end{minipage} \\
+\midrule
+\endfirsthead
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+Name
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Authors
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Description
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Relevant Items
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Adaptations
+\end{minipage} \\
+\midrule
+\endhead
+Visual Light Sensitivity Questionnaire-8 & (Verriotto et al., 2017) & Eight-question survey to assess the presence and severity of photosensitivity symptoms & All items & \\
+Office Light Survey & (Eklund \& Boyce, 1996) & Multi-item questionnaire to assess electrical lighting environment in office & & \\
+Harvard Light Exposure Assessment Questionnaire & (Bajaj, Rosner, Lockley, \& Schernhammer, 2011) & Self-administered semi-quantitative light questionnaire & All Items & \\
+Hospital Lighting Survey & (Dianat, Sedghi, Bagherzade, Jafarabadi, \& Stedmon, 2013) & 23 items questionnaire to assess light environment in a hospital & & \\
+Morningness-Eveningness Questionnaire & (Horne \& Östberg, 1976) & 19 items questionnaire to understand your body clock & & \\
+Munich Chronotype Questionnaire (MCTQ) & (Roenneberg, Wirz-Justice, \& Merrow, 2003) & 17 items questionnaire to understand individuals phase of entrainment & & \\
+Assessment of Sleep Environment & (Olivier et al., 2016) \textbar{} 13 & items questionnaire measuring your sleep environment quality \textbar{} & \begin{minipage}[t]{\linewidth}\raggedright
+\begin{verbatim}
+                              |
+\end{verbatim}
+\end{minipage} & \\
+The Pittsburgh Sleep Quality Index (PSQI) & (Daniel J. Buysse, Reynolds III, Monk, Berman, \& Kupfer, 1989) & 9 items inventory to measure sleep quality and sleeping pattern & & \\
+Self-Rating of Biological Rhythm Disorder for Adolescents (SBRDA) & (Xie, Wu, Tao, Wan, \& Tao, 2021) \textbar{} 29 & items questionnaire assessing four dimensions of biological rhythm disorder in adolescents (digital media use, sleep, eating habits, and activity) \textbar{} It & ems 3., 22., 23., 24., 25.
+and 29.
+\textbar{} & \\
+Photosensitivity Assessment Questionnaire (PAQ) & (Wu \& Hallett, 2017) \textbar{} 16 & dichotomous (yes/no) items questionnaire to assess ``photophobia'' and ``photophilia,'' giving two final scores of ``photophobic'' and ``photophilic'' behaviours \textbar{} Al & l items \textbar{} & \\
+\bottomrule
+\end{longtable}
+
 \hypertarget{methods}{%
@@
 
+\hypertarget{ethical-approval}{%
+\subsection{Ethical approval}\label{ethical-approval}}
+
+The cantonal ethics commission (Ethikkommission Nordwest- und Zentralschweiz, project ID Req-2021-00488) reviewed this project and issued an official clarification of responsibility (full document see Suppl.
+Fig X in appendix) stating: ``The research project does not fall under the scope of the Human Research Act, because your project is using only anonymised data.
+An authorisation from the ethics committee is therefore not required and the EKNZ is not responsible for its review.''
+
+\hypertarget{data-availability}{%
+\subsection{Data Availability}\label{data-availability}}
+
+\hypertarget{survey-characteristics}{%
+\subsection{Survey characteristics}\label{survey-characteristics}}
+
+Data was collected in a quantitative cross-sectional approach via a fully anonymous online survey hosted on REDCap (Harris et al., 2019, 2009) by way of the University of Basel \href{https://redcap.scicore.unibas.ch}{sciCORE}.
+Participants were recruited via the \href{https://enlightenyourclock.org/participate-in-research}{website} of a Comic co-released with the survey(Weinzaepflen \& Spitschan, 2021) , social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux software (F.lux Software LLC, 2021).
+
+Completing the online survey took approx.
+15 to 20 minutes and was not compensated.
+The first page of the survey comprised a participant information sheet, where participants' informed consent to participate was obtained before any of the questions were displayed.
+Underaged participants (\textless18 years) were urged to obtain assent from their parents/legal guardians, before filling in the survey.
+Information on the first page included the objectives of the study, inclusion criteria, estimated duration, the use, storage and sharing of the data, compensation (none), and information about the type of questions in the survey.
+Moreover, participants needed to confirm that they were participating the survey for the first time.
+To ensure high data quality, five attention check items were included in the survey (e.g., ``We want to make sure you are paying attention.
+What is 4+5?'').
+The data analysed in this study was collected between 17.05.2021 and 03.09.2021.
+Questions incorporating retrospective recall were all aligned to the period of ``past four weeks,'' matching the presented LEBA instrument.
+
+In addition to the LEBA questionnaire, which is subject of the current study, the following variables and items were assessed but not included in the analysis:
+
+\begin{itemize}
+\tightlist
+\item
+  Sleep disturbance and sleep-related impairment (adult and pediatric versions) (Bevans et al., 2019; Daniel J.
+Buysse et al., 2010; Forrest et al., 2018; Harb, Hidalgo, \& Martau, 2015; L.
+Yu et al., 2011)
+\item
+  Sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration (version for adults and adolescents) (Roenneberg et al., 2003)
+\item
+  Sleep environment {[}Olivier et al. (2016)\\
+\item
+  Meal timing \& caffeine consumption {[}custom items{]}
+\item
+  Light sensitivity (photophobia vs.~photophilia) (Wu \& Hallett, 2017)
+\item
+  Self-reported pubertal stage (only if younger than 18 years old) (Petersen, Crockett, Richards, \& Boxer, 1988)
+\end{itemize}
+
+Furthermore, the following 1-item demographic variables were assessed:
+
+\begin{itemize}
+\tightlist
+\item
+  Age
+\item
+  Sex
+\item
+  Gender identity
+\item
+  Occupational Status
+\item
+  COVID-19 related Occupational setting during the past four weeks
+\item
+  Time zone \& country of residence
+\item
+  English as native language
+\end{itemize}
+
 \hypertarget{participants}{%
 \subsection{Participants}\label{participants}}
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.35}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.14}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.18}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.18}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.08}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.08}}@{}}
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\textbf{Variable}
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+\textbf{Overall}, N = 690
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+\textbf{1. EFA Sample}, N = 428
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+\textbf{2. CFA Sample}, N = 262
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+\textbf{p-value}
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+\textbf{q-value}
+\end{minipage} \\
+\midrule
+\endhead
+\textbf{Age} & 32.95 (14.57) & 32.99 (15.11) & 32.89 (13.66) & 0.5 & 0.5 \\
+\textbf{Sex} & & & & 0.14 & 0.4 \\
+Female & 325 (47\%) & 189 (44\%) & 136 (52\%) & & \\
+Male & 351 (51\%) & 230 (54\%) & 121 (46\%) & & \\
+Other & 14 (2.0\%) & 9 (2.1\%) & 5 (1.9\%) & & \\
+\textbf{Gender-Variant Identity} & 49 (7.2\%) & 33 (7.8\%) & 16 (6.2\%) & 0.4 & 0.5 \\
+\textbf{Native English Speaker} & 320 (46\%) & 191 (45\%) & 129 (49\%) & 0.2 & 0.5 \\
+\textbf{Occupational Status} & & & & 0.040 & 0.2 \\
+Work & 396 (57\%) & 235 (55\%) & 161 (61\%) & & \\
+School & 174 (25\%) & 122 (29\%) & 52 (20\%) & & \\
+Neither & 120 (17\%) & 71 (17\%) & 49 (19\%) & & \\
+\textbf{Occupational setting} & & & & 0.3 & 0.5 \\
+Home office/Home schooling & 303 (44\%) & 194 (45\%) & 109 (42\%) & & \\
+Face-to-face work/Face-to-face schooling & 109 (16\%) & 68 (16\%) & 41 (16\%) & & \\
+Combination of home- and face-to-face- work/schooling & 147 (21\%) & 94 (22\%) & 53 (20\%) & & \\
+Neither (no work or school, or in vacation) & 131 (19\%) & 72 (17\%) & 59 (23\%) & & \\
+\bottomrule
+\end{longtable}
+
+Table 1 summarizes the survey participants' demographic characteristics.
+Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses.
+XX participants were excluded from analysis due to not passing at least one of the ``attention check'' items.
+For exploring initial factor structure (EFA) , a sample of 250-300 is recommended (Comrey \& Lee, 1992; Schönbrodt \& Perugini, 2013).
+For estimating the sample size for the confirmatory factor analysis (CFA) we followed the N:q rule (Bentler \& Chou, 1987; Jackson, 2003; Kline, 2015; Worthington \& Whittaker, 2006), where ten participants per parameter is required to earn trustworthiness of the result.
+Our sample size exceeds these requirements: Anonymous responses from a total of \emph{n} = 690 participants were included in the analysis of the current study, split into samples for exploratory (EFA: \emph{n} = 428) and confirmatory factor analysis (CFA: \emph{n} = 262).
+The EFA sample included participants filling out the questionnaire from 17.05.2021 to XX.XX.XXXX , whereas participants who filled out the questionnaire from YY.YY.YYYY to 03.09.2021 were included in the CFA analysis.
+Participants indicated filling out the online survey from a diverse range of geographic locations.
+The four most common geographic locations included:
+
+\begin{tabular}{l|r}
+\hline
+  & x\\
+\hline
+United States - America/New\_York (UTC -04:00) & 63\\
+\hline
+United Kingdom - Europe/London (UTC) & 57\\
+\hline
+Germany - Europe/Berlin (UTC +01:00) & 53\\
+\hline
+India - Asia/Kolkata (UTC +05:30) & 38\\
+\hline
+\end{tabular}
+
+For a full list of geographic locations, see Suppl. Table X in the appendix.
+
+Age among all participants ranged from 11 years to 84 years {[}EFA: \emph{min} = 11, \emph{max} = 84; CFA: \emph{min} = 12, \emph{max} = 74{]}, with an overall mean of \textasciitilde{} 33 years of age {[}Overall: \emph{M} = 32.95, \emph{SD} = 14.57; EFA: \emph{M} = 32.99, \emph{SD} = 15.11; CFA: \emph{M} = 32.89, \emph{SD} = 13.66{]}.
+In total 325 (47\%) of the participants indicated female sex {[}EFA: 189 (44\%); CFA: 136 (52\%){]}, 351 (51\%) indicated male {[}EFA: 230 (54\%); CFA: 121 (46\%){]} and 14 (2.0\%) indicated other sex {[}EFA: 9 (2.1\%), CFA: 5 (1.9\%){]}.
+Overall, 49 (7.2\%) {[}EFA: 33 (7.8\%); CFA: 16 (6.2\%){]} participants indicated a gender-variant identity.
+In a ``Yes/No'' question regarding native language, 320 (46\%) of respondents {[}EFA: 191 (45\%); CFA: 129 (49\%){]} indicated to be native English speakers.
+For their ``Occupational Status,'' more than half of the overall sample reported that they currently work {[}Overall: 396 (57\%); EFA: 235 (55\%); CFA: 161 (61\%){]}, whereas 174 (25\%) {[}EFA: 122 (29\%); CFA: 52 (20\%){]} reported that they go to school and 120 (17\%) {[}EFA: 71 (17\%); CFA: 49 (19\%){]} responded that they do ``Neither.'' With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample 303 (44\%) {[}EFA: 194 (45\%); CFA: 109 (42\%){]} of the participants indicated that they were in a home office/ home schooling setting., while 109 (16\%) overall {[}EFA: 68 (16\%) ; CFA: 41 (16\%){]} reported face-to-face work/schooling.
+Lastly, 147 (21\%) overall {[}EFA: 94 (22\%) ; CFA: 53 (20\%){]} reported a combination of home- and face-to-face work/schooling, whereas 131 (19\%) overall {[}EFA: 72 (17\%); CFA: 59 (23\%){]} filled in the ``Neither (no work or school, or indication)'' response option.
+We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable ``Age'' and Pearson's Chi-squared test for all other categorical variables via the gtsummary R package's ``add\_p'' function (Sjoberg et al., 2021a) .
+The p-values were corrected for multiple testing applying false discovery rate (FDR) via the ``add\_q'' function of the same package.
+After p-value (FDR) correction for multiple testing, none of the demographic variables were significantly different between the EFA sample and the CFA sample (all q-values \emph{q} ≥ 0.2 , indicating equivalence).
 
@@
 
-EFA: For exploring initial factor structure, a sample of 250-300 is recommended (Comrey \& Lee, 1992; Schönbrodt \& Perugini, 2013)
-
-CFA: For estimating the sample size for the confirmatory factor analysis we followed the N:q rule (Bentler \& Chou, 1987; Jackson, 2003; Kline, 2015; Worthington \& Whittaker, 2006) where 10 participants per parameter is required to earn trustworthiness of the result.
-Our sample size exceeds the requirement.
-
 \hypertarget{procedure}{%
@@
 
-{\centering \includegraphics[width=1\linewidth,height=1\textheight]{Flowchart1}
+{\centering \includegraphics[width=1\linewidth,height=1\textheight]{Manuscript.figures/Flowchart1}
 
@@
 
-\caption{Development and psychometric properties of LEBA }\label{fig:unnamed-chunk-1}
+\caption{Development}\label{fig:FlowchartFig}
 \end{figure}
-
-\hypertarget{procedure-1}{%
-\subsection{Procedure}\label{procedure-1}}
-
-Our study had four objectives.
-First, to develop an instrument to assess an individual's light exposure behavior.
-Second, to conduct an exploratory factor analysis(EFA) to understand the latent structure.
-The third one is to gather structural validity evidence for the latent structure obtained in EFA.
-Lastly, we gathered item information using Item response theory (IRT)(Baker, 2017)
 
@@
 
-Timeline of data collection,
-ethical approval
-mode of data collection
-how consent was recorded.
+Timeline of data collection, mode of data collection.
 
@@
 
-We used R (version 4.1.0), including several R packages, for our analyses.
+We used R (version 4.1.0), including several R packages, for our analyses.Initially, our tool have six poin Likert type response scale(0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Alsways).
+As our purpose was to capture light exposure related behavior, ``Does not apply/I don't know'' and ``Never'' were providing similar information.
+As such we decided to collapse ``Does not apply/I don't know'' and ``Never'' options into one making it a 5 point Likert type response scale.
 Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
@@
 Desjardins \& Bulut, 2018) for the EFA.
-We employed principal axis (pa) a factor extraction method with varimax rotation.
+We employed principal axis (PA) as a factor extraction method with varimax rotation.
 PA is robust to the normality assumption violations (Watkins, 2020).
-The obtained latent structure was confirmed by the minimum residuals extraction method as well.
+The obtained latent structure was confirmed by another factor extraction method: the minimum residuals extraction method as well.
 We used a combination factor identification method including scree plot(Cattell, 1966), Horn's parallel analysis (Horn, 1965), minimum average partials method(Velicer, 1976), and hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) to identify factor numbers.
-Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \textless0.3 (iii) no items with cross-loading greater than .3 across factors {[}Bandalos and Finney (2018);
+Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \textless0.3 (iii) no items with cross-loading greater than .3 across factors (Bandalos \& Finney, 2018) We also conducted psychometric analysis on non-merged response options data (supplementary analysis) and rejected the latent structure obtained as the factors were less interpretable.
 
@@
 
+\hypertarget{exploratory-factor-analysis}{%
+\subsection{Exploratory Factor Analysis}\label{exploratory-factor-analysis}}
+
 Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy(Kaiser, 1974) .
 The overall KMO vale for 48 items was 0.63 which was above the cutoff value (.50) indicating a mediocre sample (Hutcheson, 1999).
+Table\ref{tab:tabDes} summarizes the univariate descriptive statistics for the 48 items.
+some of the items were skewed with high Kurtosis values.
+Our data violated both univariate normality (Shapiro-Wilk statistics; (Shapiro \& Wilk, 1965)) and multivariate normality assumptions (Marida's test;(Mardia, 1970)).
+Multivariate skew was = 583.80 (p \textless0.001) and multivariate kurtosis was = 2,749.15 (p \textless0.001).
+Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen (C.
+Desjardins \& Bulut, 2018).
+Bartlett's test of sphericity (Bartlett, 1954), \(\chi^2\) (1128) = 5042.86, p \textless{} .001{]} indicated the correlations between items are adequate for the EFA.
+However only 4.96\% of the inter-item correlation coefficients were greater than .30.
+The inter item correlation ranged between .44 to .91.
+And the corrected item-total correlations ranged between .10 to .44.
 
@@
 Item1 & 2.27 & 1.39 & 0.74 & -0.81 & 0.81* & .25\\
-Item2 & 2.87 & 1.59 & 0.08 & -1.60 & 0.81* & .19\\
+Item2 & 2.87 & 1.59 & 0.08 & -1.60 & 0.83* & .19\\
 Item3 & 3.36 & 1.38 & -0.48 & -1.03 & 0.87* & .16\\
@@
 Item14 & 2.14 & 1.31 & 0.77 & -0.78 & 0.80* & .26\\
-Item15 & 3.26 & 1.09 & -0.26 & -0.45 & 0.80* & .14\\
+Item15 & 3.26 & 1.09 & -0.26 & -0.45 & 0.91* & .14\\
 Item16 & 1.56 & 1.23 & 2.00 & 2.45 & 0.50* & .32\\
@@
 
-{\centering \includegraphics[width=0.5\linewidth]{manuscript_files/figure-latex/figCor-1}
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCor-1}
 
@@
 
-Table\ref{tab:tabDes} summarizes the univariate descriptive statistics for the 48 items.
-some of the items were skewed with high Kurtosis values.
-Our data violated both univariate normality (Shapiro-Wilk statistics; (Shapiro \& Wilk, 1965)) and multivariate normality assumptions (Marida's test;(Mardia, 1970)).
-Multivariate skew was = 583.80 (p \textless0.001) and multivariate kurtosis was = 2,749.15 (p \textless0.001).
-Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen (C.
-Desjardins \& Bulut, 2018).
-Bartlett's test of sphericity (Bartlett, 1954), \(\chi^2\) (1128) = 5042.86, p \textless{} .001{]} indicated the correlations between items are adequate for the EFA.
-However only 4.96\% of the inter-item correlation coefficients were greater than .30.
-The inter item correlation ranged between .44 to .91.
-And the corrected item-total correlations ranged between .10 to .44.
-
-Scree plot ( Figure \ref{fig:facid}) suggested a six-factor solution.
+Scree plot ( Figure \ref{fig:facIdFig}) suggested a six-factor solution.
 Horn's parallel analysis (Horn, 1965) with 500 iterations also indicated a six-factor solution.
-However, the MAP method (Velicer, 1976) and Hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) suggested a five-factor solution.
+However, the minimum average partial (MAP) method (Velicer, 1976) and Hull method (Lorenzo-Seva et al., 2011) suggested a five-factor solution.
 As a result, we tested both five-factor and six-factor solutions.
@@
 
-{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{parallel} \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/facid-2} \includegraphics[width=0.5\linewidth,height=0.5\textheight]{HUll method}
+{\centering \includegraphics[width=1\linewidth,height=2\textheight]{manuscript_files/figure-latex/facIdFig-1}
 
@@
 
-\caption{Factor Identification (A) Parallel analysis (B) Scree Plot, (C) Hull method}\label{fig:facid}
+\caption{Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method}\label{fig:facIdFig}
 \end{figure}
@@
 
-{\centering \includegraphics[width=1.2\linewidth,height=1\textheight]{EFAplot.LR}
+{\centering \includegraphics[width=1\linewidth,height=0.5\textheight]{Manuscript.figures/EFAplot}
 
@@
 
-Three rounds of EFA starting with all 48 items were conducted and problematic items were gradually discarded (cross-loading items and poor factor loading (\textless.30) items).
+With initial 48 items we conducted three rounds of EFA gradually discarded problematic items.
+(cross-loading items and poor factor loading (\textless.30) items).
 Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 (Brown, 2015), all factor-loading higher than .30 and no cross-loading greater than .30.
-We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (see the supplementary).
-Table\ref{tab:TabEFA5} displays the factor-loading (structural coefficients) and communality of the items.
+We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (Table\ref{tab:MinResTab}).
+Table\ref{tab:EFATable} displays the factor-loading (structural coefficients) and communality of the items.
 The absolute value of the factor-loading ranged from -.49 to .99 indicating strong coefficients.
 The commonalities ranged between .11 to .99.
-However, the histogram of the absolute values of non-redundant residual-correlations (Fig\ref{fig:Residuals} showed 26.00\% correlations greater than the absolute value of .05, indicating a possible under-factoring.
+However, the histogram of the absolute values of non-redundant residual-correlations Fig\ref{fig:EFAResiduals} showed 26\% correlations greater than the absolute value of .05, indicating a possible under-factoring.
 (C.
@@
 Subsequently, we fitted a six-factor solution.
-However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution.
+However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution (Table\ref{tab:sixFacTab}).
 
@@
 Items under this factor dealt with the specific behaviors pertaining to sleep.
-However, the internal consistency reliability coefficient was not satisfactory (\(\alpha\) = .68).
+The internal consistency reliability coefficient was, \(\alpha\) = .68.
 The fourth factor contained five items and explained 8.44\% of the total variance with an internal consistency coefficient, \(\alpha\) = .62.
 These five items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time.
-Lastly, the fifth factor contained six items and explained 6.14\% of the total variance.This factor tried to measure an individual's behavior lead by the awareness of light's influence on health.
+Lastly, the fifth factor contained six items and explained 6.14\% of the total variance.
+This factor tried to measure an individual's behavior lead by the awareness of light's influence on health.
 However, this factor showed unsatisfactory internal consistency reliability (\(\alpha\) = .53).
-It is essential to attain a balance between psychometric properties and the interpretability of the common themes when exploring the latent structure.
-As all of the emerged factors are highly interpretable, regardless of the apparent low reliability of the two factors, we retain the five-factor solution with 23 items for our confirmatory factor analysis (CFA).
+It is essential to attain a balance between psychometric properties and interpretability of the common themes when exploring the latent structure.
+As all of the emerged factors are highly interpretable and relevant towards our aim to capture light exposure related behavior, regardless of the apparent low reliability of the two factors, we retain the five-factor solution with 23 items for our confirmatory factor analysis (CFA).
 Two items showed negative factor-loading (items 44 and 21).
@@
 
-\caption{\label{tab:TabEFA5}}
-
-\begin{tabular}{ccccccc}
+\caption{\label{tab:EFATable}Factor loadings and communality of the retained items}
+
+\small{
+
+\begin{tabular}{cccccccc}
 \toprule
- & \multicolumn{1}{c}{F1} & \multicolumn{1}{c}{F2} & \multicolumn{1}{c}{F3} & \multicolumn{1}{c}{F4} & \multicolumn{1}{c}{F5} & \multicolumn{1}{c}{Communality}\\
+item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness}\\
 \midrule
-item16 & 0.99 & - & - & - & - & 0.99\\
-item36 & 0.94 & - & - & - & - & 0.9\\
-item17 & 0.8 & - & - & - & - & 0.66\\
-item11 & - & 0.8 & - & - & - & 0.64\\
-item10 & - & 0.76 & - & - & - & 0.59\\
-item12 & - & 0.65 & - & - & - & 0.47\\
-item7 & - & 0.5 & - & - & - & 0.27\\
-item8 & - & -0.5 & - & - & - & 0.25\\
-item9 & - & 0.32 & - & - & - & 0.11\\
-item27 & - & - & 0.8 & - & - & 0.66\\
-item3 & - & - & 0.8 & - & - & 0.68\\
-item40 & - & - & 0.65 & - & - & 0.46\\
-item30 & - & - & 0.45 & - & - & 0.35\\
-item41 & - & - & -0.36 & - & - & 0.33\\
-item33 & - & - & - & 0.74 & - & 0.56\\
-item32 & - & - & - & 0.73 & - & 0.62\\
-item35 & - & - & - & 0.66 & - & 0.45\\
-item37 & - & - & - & -0.39 & - & 0.17\\
-item38 & - & - & - & 0.36 & - & 0.18\\
-item46 & - & - & - & - & 0.6 & 0.42\\
-item45 & - & - & - & - & 0.59 & 0.37\\
-item25 & - & - & - & - & 0.41 & 0.19\\
-item4 & - & - & - & - & 0.41 & 0.22\\
-item1 & - & - & - & - & 0.4 & 0.17\\
-item26 & - & - & - & - & 0.39 & 0.17\\
-internal Consistency & .86 & .71 & .68 & .62 & .53 & -\\
-\% of variance & 10.25 & 9.93 & 8.83 & 8.44 & 6.14 & -\\
+item16 & 0.99 &  &  &  &  & 0.993 & 0.007\\
+item36 & 0.94 &  &  &  &  & 0.899 & 0.101\\
+item17 & 0.8 &  &  &  &  & 0.658 & 0.342\\
+item11 &  & 0.79 &  &  &  & 0.642 & 0.358\\
+item10 &  & 0.76 &  &  &  & 0.592 & 0.408\\
+item12 &  & 0.65 &  &  &  & 0.465 & 0.535\\
+item7 &  & 0.5 &  &  &  & 0.267 & 0.733\\
+item8 &  & -0.49 &  &  &  & 0.252 & 0.748\\
+item9 &  & 0.32 &  &  &  & 0.113 & 0.887\\
+item27 &  &  & 0.8 &  &  & 0.658 & 0.342\\
+item3 &  &  & 0.8 &  &  & 0.682 & 0.318\\
+item40 &  &  & 0.65 &  &  & 0.464 & 0.536\\
+item30 &  &  & 0.45 &  &  & 0.353 & 0.647\\
+item41 &  &  & 0.36 &  &  & 0.329 & 0.671\\
+item33 &  &  &  & 0.74 &  & 0.555 & 0.445\\
+item32 &  &  &  & 0.73 &  & 0.624 & 0.376\\
+item35 &  &  &  & 0.66 &  & 0.454 & 0.546\\
+item37 &  &  &  & -0.39 &  & 0.174 & 0.826\\
+item38 &  &  &  & 0.38 &  & 0.178 & 0.822\\
+item46 &  &  &  &  & 0.6 & 0.422 & 0.578\\
+item45 &  &  &  &  & 0.59 & 0.374 & 0.626\\
+item25 &  &  &  &  & 0.41 & 0.193 & 0.807\\
+item4 &  &  &  &  & 0.41 & 0.219 & 0.781\\
+item1 &  &  &  &  & 0.4 & 0.17 & 0.83\\
+item26 &  &  &  &  & 0.35 & 0.165 & 0.835\\
+\% of Variance & 0.1 & 0.1 & 0.09 & 0.08 & 0.06 &  & \\
 \bottomrule
@@
 
+}
+
 \begin{tablenotes}[para]
@@
 
-{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/Residuals-1}
+{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/EFAResiduals-1}
 
@@
 
-\caption{ Histogram of residulas:  five-factor solution}\label{fig:Residuals}
+\caption{ Histogram of residulas:  five-factor solution}\label{fig:EFAResiduals}
 \end{figure}
 
+\begin{figure}
+\includegraphics[width=2\linewidth,height=1\textheight]{Manuscript.figures/gt} \caption{ }\label{fig:gtPic}
+\end{figure}
+
 \hypertarget{confirmatory-factor-analysis}{%
-\section{Confirmatory Factor Analysis}\label{confirmatory-factor-analysis}}
-
-\hypertarget{irt}{%
-\subsection{IRT}\label{irt}}
+\subsection{Confirmatory Factor Analysis}\label{confirmatory-factor-analysis}}
+
+We conducted a categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator as our response data was in ordinary nature(C.
+Desjardins \& Bulut, 2018).
+Several indices are suggested to measure model fit.
+These indices can be categorized as absolute, comparative and parsimony fit indices (Brown, 2015).
+Absolute fit assess the model fit at an absolute level using indices including chi-square test statistics and the standardized root mean square (SRMR).parsimony fit indices including the root mean square error of approximation (RMSEA) considers the number of free parameters in the model to assess the parsimony of the model.
+Comparative fit indices evaluate the fit of the specified model solution in relation to a more restricted baseline model restricting all covariances among the idicators as zero.
+Comparative fit index (CFI) and the Tucker Lewis index (TLI) are such two comparative fit indices.
+Commonly used Model fit guidelines (Hu \& Bentle, 1999; Schumacker \& Lomax, 2004) includes (i) Reporting of chi-square test statistics (A non-significant test statistics is required to reflect model fit) (i) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (ii) RMSEA (close to .06 or below), (iii) SRMR (close to .08 or below) to estimate the model fit.
+Table \ref{tab:tabCfa} summarizes the fit indices of our fitted model.
+Our fitted model failed to attain an absolute fit estimated by the chi-square test.
+However, the chi-square test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit (Brown, 2015).
+Another absolute fit index we obtained in our analysis was SRMR which does not work well with categorical data (C.-Y.
+Yu, 2002).
+Subsequently, we judged the model fit based on the comparative fit indices: CFI, TLI and parsimony fit index-RMSEA.
+Our fitted model attained acceptable fit (CFI =.94; TLI = .93); RMSEA = .06,\[.05-.07, 90% CI
+\]) with two imposed equity constrain on item pairs 32-33 and 19-17 .
+However SRMR value was higher than the guideline (SRMR = .12).
+Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 \& 26) for very low r-square value, our model attained best fit (CFI =.97; TLI = .96); RMSEA = .05\[.04-.06, 90% CI
+\]) and SRMR value (SRMR = .09) was also close to the suggestions of Hu and Bentle (1999).
+Since reliability coefficient Cronbach's alpha tends to mis-measure reliability for multidimensional construct (Sijtsma, 2009) we report Mcdonald's omega(total) as the internal consistency reliability coefficient.
+Mcdonald's omega(total) is reported to be a satisfactory lower bound reliability coefficient that works for both unidimensional and multidimensional construct (Zinbarg, Revelle, Yovel, \& Li, 2005).
+Mcdonald's omega(total) for the five factors were .90, .80, .61, .72, .45 respectively.
+Mcdonald's omega(total) coefficient for the total scale was .73.
+
+\begin{lltable}
+
+\begin{TableNotes}[para]
+\normalsize{\textit{Note.} df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index;RMSEA:Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square }
+\end{TableNotes}
+
+\begin{longtable}{ccccccccc}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:tabCfa}Fit indices of CFA}\\
+\toprule
+Model & \multicolumn{1}{c}{Chi-Squre} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{CFI} & \multicolumn{1}{c}{TLI} & \multicolumn{1}{c}{RMSEA} & \multicolumn{1}{c}{RMSEA 90\% Lower CI} & \multicolumn{1}{c}{RMSEA 90\% Upper CI} & \multicolumn{1}{c}{SRMR}\\
+\midrule
+\endfirsthead
+\caption*{\normalfont{Table \ref{tab:tabCfa} continued}}\\
+\toprule
+Model & \multicolumn{1}{c}{Chi-Squre} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{CFI} & \multicolumn{1}{c}{TLI} & \multicolumn{1}{c}{RMSEA} & \multicolumn{1}{c}{RMSEA 90\% Lower CI} & \multicolumn{1}{c}{RMSEA 90\% Upper CI} & \multicolumn{1}{c}{SRMR}\\
+\midrule
+\endhead
+Five factor model:25 & 448.51 & 222.00 & .94 & 0.93 & 0.06 & 0.05 & 0.07 & 0.12\\
+Five factor model:23 & 346.59 & 221.00 & .97 & 0.96 & 0.05 & 0.04 & 0.06 & 0.09\\
+\bottomrule
+\addlinespace
+\insertTableNotes
+\end{longtable}
+
+\end{lltable}
+
+\begin{figure}
+\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figcfa-1} \caption{(A) Five Factor Model of LEBA}\label{fig:figcfa}
+\end{figure}
+
+\begin{lltable}
+
+\begin{TableNotes}[para]
+\normalsize{\textit{Note.}  a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual;* =  df of model comparison}
+\end{TableNotes}
+
+\scriptsize{
+
+\begin{longtable}{cccccccccccc}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:InvarianceTab}Invariance Analysis}\\
+\toprule
+ & \multicolumn{1}{c}{Chi-Square} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{CFI} & \multicolumn{1}{c}{TLI} & \multicolumn{1}{c}{RMSEA} & \multicolumn{1}{c}{RMSEA 90\% Lower CI} & \multicolumn{1}{c}{RMSEA 90\% Upper} & \multicolumn{1}{c}{SRMR} & \multicolumn{1}{c}{Chi-Sqr comparison} & \multicolumn{1}{c}{df*} & \multicolumn{1}{c}{p}\\
+\midrule
+\endfirsthead
+\caption*{\normalfont{Table \ref{tab:InvarianceTab} continued}}\\
+\toprule
+ & \multicolumn{1}{c}{Chi-Square} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{CFI} & \multicolumn{1}{c}{TLI} & \multicolumn{1}{c}{RMSEA} & \multicolumn{1}{c}{RMSEA 90\% Lower CI} & \multicolumn{1}{c}{RMSEA 90\% Upper} & \multicolumn{1}{c}{SRMR} & \multicolumn{1}{c}{Chi-Sqr comparison} & \multicolumn{1}{c}{df*} & \multicolumn{1}{c}{p}\\
+\midrule
+\endhead
+Configural & 632.20 & 442.00 & 0.95 & 0.94 & 0.06 & 0.05 & 0.07 & 0.13 & - & - & -\\
+Metric & 644.58 & 458.00 & 0.95 & 0.95 & 0.06 & 0.05 & 0.07 & 0.13 & 18.019a & 16 & 0.323\\
+Scalar & 714.19 & 522.00 & 0.95 & 0.95 & 0.05 & 0.04 & 0.06 & 0.13 & 67.961b & 64 & 0.344\\
+Residual & 714.19 & 522.00 & 0.95 & 0.95 & 0.05 & 0.04 & 0.06 & 0.13 & 0c & 0 & NA\\
+Structural & 691.49 & 542.00 & 0.96 & 0.96 & 0.05 & 0.04 & 0.06 & 0.13 & 12.617d & 20 & 0.893\\
+\bottomrule
+\addlinespace
+\insertTableNotes
+\end{longtable}
+
+}
+
+\end{lltable}
+
+\hypertarget{analysing-the-quality-of-items-by-item-information-theory}{%
+\subsection{Analysing the quality of items by Item Information Theory}\label{analysing-the-quality-of-items-by-item-information-theory}}
+
+We sought the IRT to gether information regarding the item quality.
+IRT complements the conventional classical test theory-based analysis by gathering information on item discrimination and item difficulty(Baker, 2017).
+Here, an item's quality is judged based on item information in relation to participants' latent trait level (\(\theta\)).
+We gathered evidence on item quality by fitting each factor of LEBA with the graded response model (\ref{tab:IRTparameters} to the combined EFA sample and CFA sample (n =690).
+Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait, and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
+Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information \textless.2) to develop the short form of LEBA.
+Baker (2017) categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \textgreater1.70.
+Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), low ( 5 items) indicating a good range of discrimination along the latent trait.
+Examination of the item information curve indicated 6 items (1, 25, 9, 38, 30, \& 41) had relatively flat information curves thus discarded.
+We also gathered evidence of item fit and person fit to our fitted model.
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:IRTparameters}IRT Item parameters for the LEBA Scale}
+
+\begin{tabular}{llllll}
+\toprule
+ & \multicolumn{1}{c}{a} & \multicolumn{1}{c}{b1} & \multicolumn{1}{c}{b2} & \multicolumn{1}{c}{b3} & \multicolumn{1}{c}{b4}\\
+\midrule
+item16 & 28.13 & 0.78 & 0.90 & 1.06 & 1.40\\
+item36 & 4.49 & 0.94 & 1.08 & 1.23 & 1.40\\
+item17 & 2.81 & 0.97 & 1.11 & 1.38 & 1.62\\
+item11 & 3.27 & -0.79 & 0.65 & 1.54 & 2.31\\
+item10 & 3.07 & -1.27 & -0.09 & 0.82 & 2.00\\
+item12 & 1.72 & -0.67 & 0.44 & 1.28 & 2.11\\
+item7 & 1.09 & -0.50 & 0.73 & 1.63 & 2.97\\
+Ritem8 & 1.19 & -2.26 & -0.48 & 0.64 & 1.91\\
+item9 & 0.91 & -2.63 & -0.96 & 1.11 & 3.49\\
+item27 & 2.21 & -1.88 & -1.19 & -0.73 & 0.30\\
+item3 & 3.03 & -1.24 & -0.77 & -0.20 & 0.66\\
+item40 & 1.55 & -0.51 & 0.46 & 1.32 & 2.22\\
+item30 & 0.49 & 3.27 & 3.74 & 4.64 & 6.52\\
+item41 & 0.51 & 3.87 & 4.78 & 6.39 & 8.91\\
+item32 & 1.62 & -1.03 & -0.78 & -0.42 & 0.16\\
+item35 & 1.37 & -1.09 & -0.98 & -0.75 & -0.40\\
+item38 & 0.40 & -7.48 & -5.56 & -4.23 & -0.90\\
+item33 & 12.31 & -0.66 & -0.48 & -0.24 & 0.13\\
+item46 & 2.22 & 0.68 & 0.89 & 1.38 & 2.17\\
+item45 & 1.51 & 0.30 & 0.55 & 1.17 & 1.91\\
+item25 & 0.52 & -1.37 & -0.04 & 1.89 & 4.22\\
+item4 & 0.84 & 2.44 & 2.80 & 3.18 & 3.67\\
+item1 & 0.39 & -0.91 & 1.52 & 3.25 & 5.53\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} a = item discrimination parameter; b(1-4) = response category difficulty parameter}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{figure}
+\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/itmeinfo-1} \caption{Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light}\label{fig:itmeinfo}
+\end{figure}
+
+\begin{figure}
+\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/Testinfo-1} \caption{Test information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light}\label{fig:Testinfo}
+\end{figure}
+
+Test information curve (TIC) indicate the amount of information an the full-scale carry along the latent trait continuum.
+As we treated each factor of LEBA as an unidmensional construct we obtain 5 TICs.
+These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum ((\(\theta\))).
+Also the amount of information changed rather steadily with the change of (\(\theta\)).
+Thus we conferred the LEBA scale (except blue filter) estimated the light exposure related behavior with precision near the center of trait continuum (Baker, 2017) which is sufficient to discriminate between latent trait measured by the each factor.
+The blue filter factor had a peak to the right side of the center of latent trait indicating its ability to providing information only for people who already have some preference towards using blue-filters.
+
+Our result also indicated all the items fitted well to the respective models as assessed by assessed by RMSEA value obtained from Signed-X2 index implementation.
+All of the items had RMSEA value \textless.06 indicating adequate fit.
+Person fit indicates the validity and meaningfulness of the fitted model at the participants latent trait level (C.
+Desjardins \& Bulut, 2018).
+We estimated the person fit statistics using standardized fit index Zh statistics (Drasgow, Levine, \& Williams, 1985).
+Zh \textless{} -2 should be considered as a misfit.
+Fig indicates that Zh is larger than -2 for most participants, suggesting a good fit of the selected IRT models.
+
+The overall we can concluded that IRT analysis indicated LEBA is a psychometrically sound measure.
+Item fit indexes and person fit index for all five fitted model were acceptable.
+Items had diverse slope parameters indicating a good range of discrimination- the ability to differentiate respondents with different levels of the light exposure related behavior.
+All-in-all we can recommend the LEBA to be used to capture light exposure related behavior.
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-R-papaja}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-tabledown}{}}%
+Anwar Siraji, M. (2021). \emph{Tabledown: A companion pack for the book "basic \& advanced psychometrics in r"}. Retrieved from \url{https://github.com/masiraji/tabledown}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
 Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
 
-\leavevmode\hypertarget{ref-bakerBasicsItemResponse2017}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bajaj2011validation}{}}%
+Bajaj, A., Rosner, B., Lockley, S.
+W., \& Schernhammer, E.
+S.
+(2011).
+Validation of a light questionnaire with real-life photopic illuminance measurements: The harvard light exposure assessment questionnaire.
+\emph{Cancer Epidemiology and Prevention Biomarkers}, \emph{20}(7), 1341--1349.
+
+\leavevmode\vadjust pre{\hypertarget{ref-bakerBasicsItemResponse2017}{}}%
 Baker, F. B. (2017). \emph{The {Basics} of {Item Response Theory Using R}} (1st ed. 2017.). {Springer}.
 
-\leavevmode\hypertarget{ref-bandalosFactorAnalysisExploratory2018}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bandalosFactorAnalysisExploratory2018}{}}%
 Bandalos, D. L., \& Finney, S. J. (2018). Factor analysis: {Exploratory} and confirmatory. In \emph{The reviewer's guide to quantitative methods in the social sciences} (pp. 98--122). {Routledge}.
 
-\leavevmode\hypertarget{ref-R-tinylabels}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-tinylabels}{}}%
 Barth, M. (2021). \emph{{tinylabels}: Lightweight variable labels}. Retrieved from \url{https://github.com/mariusbarth/tinylabels}
 
-\leavevmode\hypertarget{ref-bartlettNoteMultiplyingFactors1954}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bartlettNoteMultiplyingFactors1954}{}}%
 Bartlett, M. (1954). A {Note} on the {Multiplying Factors} for {Various Chi}-square {Approximations}. \emph{Journal of the Royal Statistical Society. Series B, Methodological}, \emph{16}(2), 296--298.
 
-\leavevmode\hypertarget{ref-bentlerPracticalIssuesStructural1987}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-bentlerPracticalIssuesStructural1987}{}}%
 Bentler, P. M., \& Chou, C.-P. (1987). Practical {Issues} in {Structural Modeling}. \emph{Sociological Methods \& Research}, \emph{16}(1), 78--117. \url{https://doi.org/10.1177/0049124187016001004}
 
-\leavevmode\hypertarget{ref-brownConfirmatoryFactorAnalysis2015}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Bevans.2019}{}}%
+Bevans, K.
+B., Meltzer, L.
+J., La Motte, A.
+de, Kratchman, A., Viél, D., \& Forrest, C.
+B.
+(2019).
+Qualitative development and content validation of the PROMIS pediatric sleep health items.
+\emph{Behavioral Sleep Medicine}, \emph{17}(5), 657--671.
+\url{https://doi.org/10.1080/15402002.2018.1461102}
+
+\leavevmode\vadjust pre{\hypertarget{ref-brownConfirmatoryFactorAnalysis2015}{}}%
 Brown, T. A. (2015). \emph{Confirmatory factor analysis for applied research} (2nd ed.). {New York, NY, US}: {The Guilford Press}.
 
-\leavevmode\hypertarget{ref-R-MOTE}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-likert}{}}%
+Bryer, J., \& Speerschneider, K. (2016). \emph{Likert: Analysis and visualization likert items}. Retrieved from \url{https://CRAN.R-project.org/package=likert}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-MOTE}{}}%
 Buchanan, E.
@@
 
-\leavevmode\hypertarget{ref-cattellScreeTestNumber1966}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-buysse1989pittsburgh}{}}%
+Buysse, Daniel J., Reynolds III, C.
+F., Monk, T.
+H., Berman, S.
+R., \& Kupfer, D.
+J.
+(1989).
+The pittsburgh sleep quality index: A new instrument for psychiatric practice and research.
+\emph{Psychiatry Research}, \emph{28}(2), 193--213.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Buysse.2010}{}}%
+Buysse, Daniel J., Yu, L., Moul, D.
+E., Germain, A., Stover, A., Dodds, N.
+E., \ldots{} Pilkonis, P.
+A.
+(2010).
+Development and validation of patient-reported outcome measures for sleep disturbance and sleep-related impairments.
+\emph{Sleep}, \emph{33}(6), 781--792.
+\url{https://doi.org/10.1093/sleep/33.6.781}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cattellScreeTestNumber1966}{}}%
 Cattell, R. B. (1966). The {Scree Test For The Number Of Factors}. \emph{Multivariate Behavioral Research}, \emph{1}(2), 245--276. \url{https://doi.org/10.1207/s15327906mbr0102_10}
 
-\leavevmode\hypertarget{ref-R-shiny}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-mirt}{}}%
+Chalmers, R.
+P.
+(2012).
+{mirt}: A multidimensional item response theory package for the {R} environment.
+\emph{Journal of Statistical Software}, \emph{48}(6), 1--29.
+\url{https://doi.org/10.18637/jss.v048.i06}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-shiny}{}}%
 Chang, W., Cheng, J., Allaire, J., Sievert, C., Schloerke, B., Xie, Y., \ldots{} Borges, B.
@@
 
-\leavevmode\hypertarget{ref-comreyFirstCourseFactor1992}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-comreyFirstCourseFactor1992}{}}%
 Comrey, A. L., \& Lee, H. B. (1992). \emph{A first course in factor analysis, 2nd ed}. {Hillsdale, NJ, US}: {Lawrence Erlbaum Associates, Inc}.
 
-\leavevmode\hypertarget{ref-desjardinsHandbookEducationalMeasurement2018}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-corx}{}}%
+Conigrave, J. (2020). \emph{Corx: Create and format correlation matrices}. Retrieved from \url{https://CRAN.R-project.org/package=corx}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-xtable}{}}%
+Dahl, D. B., Scott, D., Roosen, C., Magnusson, A., \& Swinton, J. (2019). \emph{Xtable: Export tables to LaTeX or HTML}. Retrieved from \url{https://CRAN.R-project.org/package=xtable}
+
+\leavevmode\vadjust pre{\hypertarget{ref-desjardinsHandbookEducationalMeasurement2018a}{}}%
+Desjardins, C. D. (2018). \emph{Handbook of educational measurement and psychometrics using {R}}. (O. Bulut \& ProQuest (Firm), Eds.). {Boca Raton, FL : CRC Press}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-desjardinsHandbookEducationalMeasurement2018}{}}%
 Desjardins, C., \& Bulut, O. (2018). \emph{Handbook of {Educational Measurement} and {Psychometrics Using R}}. \url{https://doi.org/10.1201/b20498}
 
-\leavevmode\hypertarget{ref-desjardinsHandbookEducationalMeasurement2018a}{}%
-Desjardins, C. D. (2018). \emph{Handbook of educational measurement and psychometrics using {R}} (O. Bulut \& ProQuest (Firm), Eds.). {Boca Raton, FL : CRC Press}.
-
-\leavevmode\hypertarget{ref-R-paran}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-dianat2013objective}{}}%
+Dianat, I., Sedghi, A., Bagherzade, J., Jafarabadi, M.
+A., \& Stedmon, A.
+W.
+(2013).
+Objective and subjective assessments of lighting in a hospital setting: Implications for health, safety and performance.
+\emph{Ergonomics}, \emph{56}(10), 1535--1545.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-paran}{}}%
 Dinno, A. (2018). \emph{Paran: Horn's test of principal components/factors}. Retrieved from \url{https://CRAN.R-project.org/package=paran}
 
-\leavevmode\hypertarget{ref-R-semPlot}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-drasgow1985appropriateness}{}}%
+Drasgow, F., Levine, M.
+V., \& Williams, E.
+A.
+(1985).
+Appropriateness measurement with polychotomous item response models and standardized indices.
+\emph{British Journal of Mathematical and Statistical Psychology}, \emph{38}(1), 67--86.
+
+\leavevmode\vadjust pre{\hypertarget{ref-eklund1996development}{}}%
+Eklund, N., \& Boyce, P. (1996). The development of a reliable, valid, and simple office lighting survey. \emph{Journal of the Illuminating Engineering Society}, \emph{25}(2), 25--40.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-semPlot}{}}%
 Epskamp, S. (2019). \emph{semPlot: Path diagrams and visual analysis of various SEM packages' output}. Retrieved from \url{https://CRAN.R-project.org/package=semPlot}
 
-\leavevmode\hypertarget{ref-R-qgraph}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-qgraph}{}}%
 Epskamp, S., Cramer, A.
@@
 
-\leavevmode\hypertarget{ref-R-car}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-f.lux}{}}%
+F.lux Software LLC. (2021). F.lux (Version 4.120). Retrieved from \url{https://justgetflux.com/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Forrest.2018}{}}%
+Forrest, C.
+B., Meltzer, L.
+J., Marcus, C.
+L., La Motte, A.
+de, Kratchman, A., Buysse, D.
+J., \ldots{} Bevans, K.
+B.
+(2018).
+Development and validation of the PROMIS pediatric sleep disturbance and sleep-related impairment item banks.
+\emph{Sleep}, \emph{41}(6).
+\url{https://doi.org/10.1093/sleep/zsy054}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-car}{}}%
 Fox, J., \& Weisberg, S. (2019). \emph{An {R} companion to applied regression} (Third). Thousand Oaks {CA}: Sage. Retrieved from \url{https://socialsciences.mcmaster.ca/jfox/Books/Companion/}
 
-\leavevmode\hypertarget{ref-R-carData}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-carData}{}}%
 Fox, J., Weisberg, S., \& Price, B. (2020). \emph{carData: Companion to applied regression data sets}. Retrieved from \url{https://CRAN.R-project.org/package=carData}
 
-\leavevmode\hypertarget{ref-R-Hmisc}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Harb.2015}{}}%
+Harb, F., Hidalgo, M.
+P., \& Martau, B.
+(2015).
+Lack of exposure to natural light in the workspace is associated with physiological, sleep and depressive symptoms.
+\emph{Chronobiology International}, \emph{32}(3), 368--375.
+\url{https://doi.org/10.3109/07420528.2014.982757}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-Hmisc}{}}%
 Harrell Jr, F. E., Charles Dupont, with contributions from, \& others., many. (2021). \emph{Hmisc: Harrell miscellaneous}. Retrieved from \url{https://CRAN.R-project.org/package=Hmisc}
 
-\leavevmode\hypertarget{ref-R-purrr}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-harris2019redcap}{}}%
+Harris, P.
+A., Taylor, R., Minor, B.
+L., Elliott, V., Fernandez, M., O'Neal, L., \ldots{} others.
+(2019).
+The REDCap consortium: Building an international community of software platform partners.
+\emph{Journal of Biomedical Informatics}, \emph{95}, 103208.
+
+\leavevmode\vadjust pre{\hypertarget{ref-harris2009research}{}}%
+Harris, P.
+A., Taylor, R., Thielke, R., Payne, J., Gonzalez, N., \& Conde, J.
+G.
+(2009).
+Research electronic data capture (REDCap)---a metadata-driven methodology and workflow process for providing translational research informatics support.
+\emph{Journal of Biomedical Informatics}, \emph{42}(2), 377--381.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-purrr}{}}%
 Henry, L., \& Wickham, H. (2020). \emph{Purrr: Functional programming tools}. Retrieved from \url{https://CRAN.R-project.org/package=purrr}
 
-\leavevmode\hypertarget{ref-hornRationaleTestNumber1965}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-hornRationaleTestNumber1965}{}}%
 Horn, J. L. (1965). A rationale and test for the number of factors in factor analysis. \emph{Psychometrika}, \emph{30}(2), 179--185. \url{https://doi.org/10.1007/BF02289447}
 
-\leavevmode\hypertarget{ref-hutchesonMultivariateSocialScientist1999}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-horne1976self}{}}%
+Horne, J. A., \& Östberg, O. (1976). A self-assessment questionnaire to determine morningness-eveningness in human circadian rhythms. \emph{International Journal of Chronobiology}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-huCutoffCriteriaFit1999}{}}%
+Hu, L., \& Bentle, P.
+M.
+(1999).
+Cutoff criteria for fit indexes in covariance structure analysis: {Conventional} criteria versus new alternatives.
+\emph{Structural Equation Modeling: A Multidisciplinary Journal}, \emph{6}(1), 1--55.
+\url{https://doi.org/10.1080/10705519909540118}
+
+\leavevmode\vadjust pre{\hypertarget{ref-hutchesonMultivariateSocialScientist1999}{}}%
 Hutcheson, G. D. (1999). \emph{The multivariate social scientist : Introductory statistics using generalized linear models}. {London : SAGE}.
 
-\leavevmode\hypertarget{ref-R-DiagrammeRsvg}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-DiagrammeRsvg}{}}%
 Iannone, R. (2016). \emph{DiagrammeRsvg: Export DiagrammeR graphviz graphs as SVG}. Retrieved from \url{https://CRAN.R-project.org/package=DiagrammeRsvg}
 
-\leavevmode\hypertarget{ref-R-DiagrammeR}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-DiagrammeR}{}}%
 Iannone, R. (2021). \emph{DiagrammeR: Graph/network visualization}. Retrieved from \url{https://github.com/rich-iannone/DiagrammeR}
 
-\leavevmode\hypertarget{ref-jacksonRevisitingSampleSize2003}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-jacksonRevisitingSampleSize2003}{}}%
 Jackson, D.
@@
 
-\leavevmode\hypertarget{ref-R-semTools}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-semTable}{}}%
+Johnson, P., \& Kite, B. (2020). \emph{semTable: Structural equation modeling tables}. Retrieved from \url{https://CRAN.R-project.org/package=semTable}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-kutils}{}}%
+Johnson, P., Kite, B., \& Redmon, C. (2020). \emph{Kutils: Project management tools}. Retrieved from \url{https://CRAN.R-project.org/package=kutils}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-semTools}{}}%
 Jorgensen, T.
@@
 
-\leavevmode\hypertarget{ref-kaiserIndexFactorialSimplicity1974}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-kaiserIndexFactorialSimplicity1974}{}}%
 Kaiser, H. F. (1974). An index of factorial simplicity. \emph{Psychometrika}, \emph{39}(1), 31--36. \url{https://doi.org/10.1007/bf02291575}
 
-\leavevmode\hypertarget{ref-R-ggcorrplot}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-ggcorrplot}{}}%
 Kassambara, A. (2019). \emph{Ggcorrplot: Visualization of a correlation matrix using 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=ggcorrplot}
 
-\leavevmode\hypertarget{ref-klinePrinciplesPracticeStructural2015}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-klinePrinciplesPracticeStructural2015}{}}%
 Kline, R. B. (2015). \emph{Principles and practice of structural equation modeling}. {The Guilford Press}.
 
-\leavevmode\hypertarget{ref-lorenzo-sevaHullMethodSelecting2011}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-VIM}{}}%
+Kowarik, A., \& Templ, M. (2016). Imputation with the {R} package {VIM}. \emph{Journal of Statistical Software}, \emph{74}(7), 1--16. \url{https://doi.org/10.18637/jss.v074.i07}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-lavaanPlot}{}}%
+Lishinski, A. (2021). \emph{lavaanPlot: Path diagrams for 'lavaan' models via 'DiagrammeR'}. Retrieved from \url{https://CRAN.R-project.org/package=lavaanPlot}
+
+\leavevmode\vadjust pre{\hypertarget{ref-lorenzo-sevaHullMethodSelecting2011}{}}%
 Lorenzo-Seva, U., Timmerman, M., \& Kiers, H.
@@
 
-\leavevmode\hypertarget{ref-R-correlation}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-correlation}{}}%
 Makowski, D., Ben-Shachar, M.
@@
 
-\leavevmode\hypertarget{ref-mardiaMeasuresMultivariateSkewness1970}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-mardiaMeasuresMultivariateSkewness1970}{}}%
 Mardia, K. V. (1970). Measures of multivariate skewness and kurtosis with applications. \emph{Biometrika}, \emph{57}(3), 519--530. \url{https://doi.org/10.1093/biomet/57.3.519}
 
-\leavevmode\hypertarget{ref-R-tibble}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-gtExtras}{}}%
+Mock, T. (2021). \emph{gtExtras: A collection of helper functions for the gt package}. Retrieved from \url{https://github.com/jthomasmock/gtExtras}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tibble}{}}%
 Müller, K., \& Wickham, H. (2021). \emph{Tibble: Simple data frames}. Retrieved from \url{https://CRAN.R-project.org/package=tibble}
 
-\leavevmode\hypertarget{ref-R-EFA.MRFA}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-EFA.MRFA}{}}%
 Navarro-Gonzalez, D., \& Lorenzo-Seva, U. (2021). \emph{EFA.MRFA: Dimensionality assessment using minimum rank factor analysis}. Retrieved from \url{https://CRAN.R-project.org/package=EFA.MRFA}
 
-\leavevmode\hypertarget{ref-R-rsvg}{}%
-Ooms, J. (2021). \emph{Rsvg: Render SVG images into PDF, PNG, PostScript, or bitmap arrays}. Retrieved from \url{https://CRAN.R-project.org/package=rsvg}
-
-\leavevmode\hypertarget{ref-R-base}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Olivier.2016}{}}%
+Olivier, K., Gallagher, R.
+A., Killgore, W.
+D.
+S., Carrazco, N., Alfonso-Miller, P., \ldots{} Grandner, M.
+A.
+(2016).
+Development and initial validation of the assessment of sleep environment: A novel inventory for describing and quantifying the impact of environmental factors on sleep.
+\emph{Sleep}, \emph{39}(Abstract Supplement: A367).
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-magick}{}}%
+Ooms, J. (2021a). \emph{Magick: Advanced graphics and image-processing in r}. Retrieved from \url{https://CRAN.R-project.org/package=magick}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-rsvg}{}}%
+Ooms, J. (2021b). \emph{Rsvg: Render SVG images into PDF, PNG, PostScript, or bitmap arrays}. Retrieved from \url{https://CRAN.R-project.org/package=rsvg}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Petersen.1988}{}}%
+Petersen, A.
+C., Crockett, L., Richards, M., \& Boxer, A.
+(1988).
+A self-report measure of pubertal status: Reliability, validity, and initial norms.
+\emph{Journal of Youth and Adolescence}, \emph{17}(2), 117--133.
+\url{https://doi.org/10.1007/BF01537962}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-simsem}{}}%
+Pornprasertmanit, S., Miller, P., Schoemann, A., \& Jorgensen, T. D. (2021). \emph{Simsem: SIMulated structural equation modeling}. Retrieved from \url{https://CRAN.R-project.org/package=simsem}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
 R Core Team. (2021). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}
 
-\leavevmode\hypertarget{ref-R-psych}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-psych}{}}%
 Revelle, W.
@@
 
-\leavevmode\hypertarget{ref-R-lavaan}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-roenneberg2003life}{}}%
+Roenneberg, T., Wirz-Justice, A., \& Merrow, M. (2003). Life between clocks: Daily temporal patterns of human chronotypes. \emph{Journal of Biological Rhythms}, \emph{18}(1), 80--90.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-lavaan}{}}%
 Rosseel, Y. (2012). {lavaan}: An {R} package for structural equation modeling. \emph{Journal of Statistical Software}, \emph{48}(2), 1--36. Retrieved from \url{https://www.jstatsoft.org/v48/i02/}
 
-\leavevmode\hypertarget{ref-R-dlookr}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-dlookr}{}}%
 Ryu, C. (2021). \emph{Dlookr: Tools for data diagnosis, exploration, transformation}. Retrieved from \url{https://CRAN.R-project.org/package=dlookr}
 
-\leavevmode\hypertarget{ref-R-lattice}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-lattice}{}}%
 Sarkar, D. (2008). \emph{Lattice: Multivariate data visualization with r}. New York: Springer. Retrieved from \url{http://lmdvr.r-forge.r-project.org}
 
-\leavevmode\hypertarget{ref-schonbrodtWhatSampleSize2013}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-schonbrodtWhatSampleSize2013}{}}%
 Schönbrodt, F.
@@
 
-\leavevmode\hypertarget{ref-shapiroAnalysisVarianceTest1965}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-schumacker2004beginner}{}}%
+Schumacker, R. E., \& Lomax, R. G. (2004). \emph{A beginner's guide to structural equation modeling}. psychology press.
+
+\leavevmode\vadjust pre{\hypertarget{ref-shapiroAnalysisVarianceTest1965}{}}%
 Shapiro, S. S., \& Wilk, M. B. (1965). An analysis of variance test for normality (complete samples). \emph{Biometrika}, \emph{52}(3-4), 591--611. \url{https://doi.org/10.1093/biomet/52.3-4.591}
 
-\leavevmode\hypertarget{ref-R-survival-book}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-sijtsma2009use}{}}%
+Sijtsma, K. (2009). On the use, the misuse, and the very limited usefulness of cronbach's alpha. \emph{Psychometrika}, \emph{74}(1), 107.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-gtsummary}{}}%
+Sjoberg, D.
+D., Curry, M., Hannum, M., Larmarange, J., Whiting, K., \& Zabor, E.
+C.
+(2021b).
+\emph{Gtsummary: Presentation-ready data summary and analytic result tables}.
+Retrieved from \url{https://CRAN.R-project.org/package=gtsummary}
+
+\leavevmode\vadjust pre{\hypertarget{ref-sjoberg2021}{}}%
+Sjoberg, D.
+D., Curry, M., Hannum, M., Larmarange, J., Whiting, K., \& Zabor, E.
+C.
+(2021a).
+\emph{Gtsummary: Presentation-ready data summary and analytic result tables}.
+Retrieved from \url{https://CRAN.R-project.org/package=gtsummary}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-colorspace_c}{}}%
+Stauffer, R., Mayr, G.
+J., Dabernig, M., \& Zeileis, A.
+(2009).
+Somewhere over the rainbow: How to make effective use of colors in meteorological visualizations.
+\emph{Bulletin of the American Meteorological Society}, \emph{96}(2), 203--216.
+\url{https://doi.org/10.1175/BAMS-D-13-00155.1}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-survival-book}{}}%
 Terry M. Therneau, \& Patricia M. Grambsch. (2000). \emph{Modeling survival data: Extending the {C}ox model}. New York: Springer.
 
-\leavevmode\hypertarget{ref-velicerDeterminingNumberComponents1976}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-packrat}{}}%
+Ushey, K., McPherson, J., Cheng, J., Atkins, A., \& Allaire, J.
+(2021).
+\emph{Packrat: A dependency management system for projects and their r package dependencies}.
+Retrieved from \url{https://CRAN.R-project.org/package=packrat}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidySEM}{}}%
+van Lissa, C. J. (2021). \emph{tidySEM: Tidy structural equation modeling}. Retrieved from \url{https://CRAN.R-project.org/package=tidySEM}
+
+\leavevmode\vadjust pre{\hypertarget{ref-velicerDeterminingNumberComponents1976}{}}%
 Velicer, W. (1976). Determining the {Number} of {Components} from the {Matrix} of {Partial Correlations}. \emph{Psychometrika}, \emph{41}, 321--327. \url{https://doi.org/10.1007/BF02293557}
 
-\leavevmode\hypertarget{ref-R-MASS}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-MASS}{}}%
 Venables, W. N., \& Ripley, B. D. (2002). \emph{Modern applied statistics with s} (Fourth). New York: Springer. Retrieved from \url{https://www.stats.ox.ac.uk/pub/MASS4/}
 
-\leavevmode\hypertarget{ref-watkinsStepbyStepGuideExploratory2020}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-verriotto2017new}{}}%
+Verriotto, J.
+D., Gonzalez, A., Aguilar, M.
+C., Parel, J.-M.
+A., Feuer, W.
+J., Smith, A.
+R., \& Lam, B.
+L.
+(2017).
+New methods for quantification of visual photosensitivity threshold and symptoms.
+\emph{Translational Vision Science \& Technology}, \emph{6}(4), 18--18.
+
+\leavevmode\vadjust pre{\hypertarget{ref-watkinsStepbyStepGuideExploratory2020}{}}%
 Watkins, M. (2020). \emph{A {Step}-by-{Step Guide} to {Exploratory Factor Analysis} with {R} and {RStudio}}. \url{https://doi.org/10.4324/9781003120001}
 
-\leavevmode\hypertarget{ref-R-ggplot2}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Weinzaepflen.2021}{}}%
+Weinzaepflen, C., \& Spitschan, M. (2021). Enlighten your clock: How your body tells time. {Open Science Framework}. \url{https://doi.org/10.17605/OSF.IO/ZQXVH}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-plyr}{}}%
+Wickham, H. (2011). The split-apply-combine strategy for data analysis. \emph{Journal of Statistical Software}, \emph{40}(1), 1--29. Retrieved from \url{http://www.jstatsoft.org/v40/i01/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-ggplot2}{}}%
 Wickham, H. (2016). \emph{ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}
 
-\leavevmode\hypertarget{ref-R-stringr}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-stringr}{}}%
 Wickham, H. (2019). \emph{Stringr: Simple, consistent wrappers for common string operations}. Retrieved from \url{https://CRAN.R-project.org/package=stringr}
 
-\leavevmode\hypertarget{ref-R-forcats}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-forcats}{}}%
 Wickham, H. (2021a). \emph{Forcats: Tools for working with categorical variables (factors)}. Retrieved from \url{https://CRAN.R-project.org/package=forcats}
 
-\leavevmode\hypertarget{ref-R-tidyr}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyr}{}}%
 Wickham, H. (2021b). \emph{Tidyr: Tidy messy data}. Retrieved from \url{https://CRAN.R-project.org/package=tidyr}
 
-\leavevmode\hypertarget{ref-R-tidyverse}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyverse}{}}%
 Wickham, H., Averick, M., Bryan, J., Chang, W., McGowan, L.
@@
 
-\leavevmode\hypertarget{ref-R-readxl}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-readxl}{}}%
 Wickham, H., \& Bryan, J. (2019). \emph{Readxl: Read excel files}. Retrieved from \url{https://CRAN.R-project.org/package=readxl}
 
-\leavevmode\hypertarget{ref-R-dplyr}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-dplyr}{}}%
 Wickham, H., François, R., Henry, L., \& Müller, K. (2021). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}
 
-\leavevmode\hypertarget{ref-R-readr}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-readr}{}}%
 Wickham, H., \& Hester, J. (2021). \emph{Readr: Read rectangular text data}. Retrieved from \url{https://CRAN.R-project.org/package=readr}
 
-\leavevmode\hypertarget{ref-worthingtonScaleDevelopmentResearch2006}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-cowplot}{}}%
+Wilke, C. O. (2020). \emph{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=cowplot}
+
+\leavevmode\vadjust pre{\hypertarget{ref-worthingtonScaleDevelopmentResearch2006}{}}%
 Worthington, R.
@@
 
-\leavevmode\hypertarget{ref-R-Formula}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Wu.2017}{}}%
+Wu, Y., \& Hallett, M. (2017). Photophobia in neurologic disorders. \emph{Translational Neurodegeneration}, \emph{6}(1), 26. \url{https://doi.org/10.1186/s40035-017-0095-3}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Xie.2021}{}}%
+Xie, Y., Wu, X., Tao, S., Wan, Y., \& Tao, F.
+(2021).
+Development and validation of the self-rating of biological rhythm disorder for chinese adolescents.
+\emph{Chronobiology International}, 1--7.
+\url{https://doi.org/10.1080/07420528.2021.1989450}
+
+\leavevmode\vadjust pre{\hypertarget{ref-RN1272}{}}%
+Yu, C.-Y. (2002). \emph{Evaluating cutoff criteria of model fit indices for latent variable models with binary and continuous outcomes} (Thesis). {ProQuest Dissertations Publishing}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-Yu.2011}{}}%
+Yu, L., Buysse, D.
+J., Germain, A., Moul, D.
+E., Stover, A., Dodds, N.
+E., \ldots{} Pilkonis, P.
+A.
+(2011).
+Development of short forms from the PROMIS{\texttrademark} sleep disturbance and sleep-related impairment item banks.
+\emph{Behavioral Sleep Medicine}, \emph{10}(1), 6--24.
+\url{https://doi.org/10.1080/15402002.2012.636266}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-Formula}{}}%
 Zeileis, A., \& Croissant, Y.
@@
 
-\leavevmode\hypertarget{ref-R-kableExtra}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-colorspace_a}{}}%
+Zeileis, A., Fisher, J.
+C., Hornik, K., Ihaka, R., McWhite, C.
+D., Murrell, P., \ldots{} Wilke, C.
+O.
+(2020).
+{colorspace}: A toolbox for manipulating and assessing colors and palettes.
+\emph{Journal of Statistical Software}, \emph{96}(1), 1--49.
+\url{https://doi.org/10.18637/jss.v096.i01}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-colorspace_b}{}}%
+Zeileis, A., Hornik, K., \& Murrell, P.
+(2009).
+Escaping {RGB}land: Selecting colors for statistical graphics.
+\emph{Computational Statistics \& Data Analysis}, \emph{53}(9), 3259--3270.
+\url{https://doi.org/10.1016/j.csda.2008.11.033}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-kableExtra}{}}%
 Zhu, H. (2021). \emph{kableExtra: Construct complex table with 'kable' and pipe syntax}. Retrieved from \url{https://CRAN.R-project.org/package=kableExtra}
 
+\leavevmode\vadjust pre{\hypertarget{ref-zinbarg2005cronbach}{}}%
+Zinbarg, R.
+E., Revelle, W., Yovel, I., \& Li, W.
+(2005).
+Cronbach's \(\alpha\), revelle's \(\beta\), and McDonald's \(\omega\) h: Their relations with each other and two alternative conceptualizations of reliability.
+\emph{Psychometrika}, \emph{70}(1), 123--133.
+
 \end{CSLReferences}

### 2021-11-10 install_packages.R

@@ -1,32 +1,0 @@
-
-#if "packrat" does not work you can run this chunk manually to get all required packs"
-
-install.packages("devtools")
-install.packages("semTools")
-install.packages("MOTE")
-install.packages("psych")
-install.packages("lavaan")
-install.packages("dlookr")
-install.packages("tidyverse")
-install.packages("qgraph")
-install.packages("kableExtra")
-install.packages("paran")
-install.packages("EFA.MRFA")
-install.packages("rsvg")
-install.packages("ggcorrplot")
-install.packages("semTable")
-install.packages("magick")
-install.packages("mirt")
-install.packages("cowplot")
-install.packages("VIM")
-devtools::install_github('rich-iannone/DiagrammeR')
-devtools::install_github("crsh/papaja", force = T)
-install.packages("DiagrammeRsvg")
-devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
-devtools::install_github("crsh/citr")
-remotes::install_github("jthomasmock/gtExtras")
-install.packages("gt")
-
-install.packages("questionr")
-
-```

### 2021-11-10 manuscript.Rmd
*systemfonts are not responding

@@
 
-```{r depMan, include=F}
+```{r depMan, eval=FALSE, include=FALSE}
 renv::init()
-#renv::snapshot()
-#renv::status()
+renv::snapshot()
+Nrenv::status()
 renv::restore()
@@
 library(tabledown)
-#library(extrafont)
-#extrafont::font_import()
+
 r_refs("references.bib")

### 2021-11-10 manuscript.Rmd
* attempt 1 on solving systemfonts pack issue
Updated ReadME

@@
       in_header: header.tex
-
+appendix:
+  - "Supplymentary.Rmd"
+  - "instrument.Rmd"
+  - "Appendix-B.Rmd"
 mainfont: Helvetica
@@
 ```{r depMan, eval=FALSE, include=FALSE}
-renv::init()
-renv::snapshot()
-Nrenv::status()
-renv::restore()
+#renv::init()
+#renv::snapshot()
+#renv::status()
+#renv::restore()
 ```

### 2021-11-10 manuscript.tex
Updated ReadME

@@
 
-\begin{verbatim}
-## * The library is already synchronized with the lockfile.
-\end{verbatim}
-
 \hypertarget{introduction}{%
@@
 \midrule
-item16 & 28.13 & 0.78 & 0.90 & 1.06 & 1.40\\
+item16 & 28.55 & 0.78 & 0.90 & 1.06 & 1.40\\
 item36 & 4.49 & 0.94 & 1.08 & 1.23 & 1.40\\
@@
 item32 & 1.62 & -1.03 & -0.78 & -0.42 & 0.16\\
-item35 & 1.37 & -1.09 & -0.98 & -0.75 & -0.40\\
-item38 & 0.40 & -7.48 & -5.56 & -4.23 & -0.90\\
-item33 & 12.31 & -0.66 & -0.48 & -0.24 & 0.13\\
+item35 & 1.36 & -1.09 & -0.98 & -0.75 & -0.40\\
+item38 & 0.40 & -7.50 & -5.58 & -4.25 & -0.91\\
+item33 & 13.51 & -0.66 & -0.48 & -0.24 & 0.13\\
 item46 & 2.22 & 0.68 & 0.89 & 1.38 & 2.17\\
@@
 
+\clearpage
+\makeatletter
+\efloat@restorefloats
+\makeatother
+
+\begin{appendix}
+\section{}
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:MinResTab}Factor loadings and communality of the retained items(Minmum Residual)}
+
+\small{
+
+\begin{tabular}{cccccccc}
+\toprule
+item & \multicolumn{1}{c}{MR1} & \multicolumn{1}{c}{MR2} & \multicolumn{1}{c}{MR3} & \multicolumn{1}{c}{MR4} & \multicolumn{1}{c}{MR5} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness}\\
+\midrule
+item16 & 1 &  &  &  &  & 0.996 & 0.004\\
+item36 & 0.94 &  &  &  &  & 0.897 & 0.103\\
+item17 & 0.8 &  &  &  &  & 0.658 & 0.342\\
+item11 &  & 0.79 &  &  &  & 0.642 & 0.358\\
+item10 &  & 0.76 &  &  &  & 0.592 & 0.408\\
+item12 &  & 0.65 &  &  &  & 0.465 & 0.535\\
+item7 &  & 0.5 &  &  &  & 0.267 & 0.733\\
+item8 &  & -0.49 &  &  &  & 0.252 & 0.748\\
+item9 &  & 0.32 &  &  &  & 0.113 & 0.887\\
+item27 &  &  & 0.8 &  &  & 0.659 & 0.341\\
+item3 &  &  & 0.8 &  &  & 0.683 & 0.317\\
+item40 &  &  & 0.65 &  &  & 0.464 & 0.536\\
+item30 &  &  & 0.45 &  &  & 0.353 & 0.647\\
+item41 &  &  & 0.36 &  &  & 0.329 & 0.671\\
+item33 &  &  &  & 0.74 &  & 0.555 & 0.445\\
+item32 &  &  &  & 0.73 &  & 0.623 & 0.377\\
+item35 &  &  &  & 0.66 &  & 0.455 & 0.545\\
+item37 &  &  &  & -0.39 &  & 0.175 & 0.825\\
+item38 &  &  &  & 0.38 &  & 0.178 & 0.822\\
+item46 &  &  &  &  & 0.6 & 0.422 & 0.578\\
+item45 &  &  &  &  & 0.59 & 0.374 & 0.626\\
+item25 &  &  &  &  & 0.41 & 0.193 & 0.807\\
+item4 &  &  &  &  & 0.41 & 0.219 & 0.781\\
+item1 &  &  &  &  & 0.4 & 0.17 & 0.83\\
+item26 &  &  &  &  & 0.35 & 0.165 & 0.835\\
+\% of Variance & 0.1 & 0.1 & 0.09 & 0.08 & 0.06 &  & \\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Only loading higher than .30 is reported}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:sixFacTab}Factor loadings and communality of the retained items(six factor)}
+
+\small{
+
+\begin{tabular}{ccccccccc}
+\toprule
+item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA6} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness}\\
+\midrule
+item19 & 1.78 &  &  &  &  &  & 3.318 & -2.318\\
+item5 &  &  &  &  &  &  & 0.11 & 0.89\\
+item16 &  & 1 &  &  &  &  & 1.004 & -0.004\\
+item36 &  & 0.91 &  &  &  &  & 0.86 & 0.14\\
+item17 &  & 0.81 &  &  &  &  & 0.691 & 0.309\\
+item11 &  &  & 0.83 &  &  &  & 0.71 & 0.29\\
+item10 &  &  & 0.79 &  &  &  & 0.638 & 0.362\\
+item12 &  &  & 0.63 &  &  &  & 0.465 & 0.535\\
+item8 &  &  & -0.5 &  &  &  & 0.269 & 0.731\\
+item7 &  &  & 0.47 &  &  &  & 0.268 & 0.732\\
+item9 &  &  & 0.32 &  &  &  & 0.163 & 0.837\\
+item33 &  &  &  & 0.83 &  &  & 0.698 & 0.302\\
+item32 &  &  &  & 0.75 &  &  & 0.666 & 0.334\\
+item35 &  &  &  & 0.64 &  &  & 0.446 & 0.554\\
+item31 &  &  &  & 0.48 &  &  & 0.331 & 0.669\\
+item38 &  &  &  & 0.39 &  &  & 0.191 & 0.809\\
+item37 &  &  &  & -0.35 &  &  & 0.153 & 0.847\\
+item3 &  &  &  &  & 0.85 &  & 0.748 & 0.252\\
+item27 &  &  &  &  & 0.8 &  & 0.644 & 0.356\\
+item40 &  &  &  &  & 0.68 &  & 0.507 & 0.493\\
+item46 &  &  &  &  &  & 0.6 & 0.431 & 0.569\\
+item45 &  &  &  &  &  & 0.56 & 0.341 & 0.659\\
+item4 &  &  &  &  &  & 0.43 & 0.265 & 0.735\\
+item25 &  &  &  &  &  & 0.4 & 0.178 & 0.822\\
+item1 &  &  &  &  &  & 0.36 & 0.142 & 0.858\\
+item26 &  &  &  &  &  & 0.36 & 0.173 & 0.827\\
+item13 &  &  &  &  &  &  & 0.087 & 0.913\\
+item29 &  &  &  &  &  &  & 0.108 & 0.892\\
+\% of Variance & 0.12 & 0.09 & 0.09 & 0.08 & 0.07 & 0.06 &  & \\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Only loading higher than .30 is reported}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+\end{appendix}
+
+\clearpage
+\makeatletter
+\efloat@restorefloats
+\makeatother
+
+\begin{appendix}
+\section{}
+\textbf{Disclaimer}: This is a non-public version of LEBA (dated \today)
+and still a work in progress. Please do not distribute!
+
+LEBA captures light exposure-related behaviours on a 5 point Likert type
+scale ranging from 1 to 5 (Never/Does not apply/I don't know = 1; Rarely
+= 2; Sometimes = 3; Often = 4; Always = 5). The score of each factor is
+calculated by the summation of scores of items belonging to the
+corresponding factor. The following instruction is given before
+displaying the items: ``Please indicate how often you performed the
+following behaviours in the past 4 weeks.''
+
+\newpage
+
+\blandscape
+
+\hypertarget{leba-long-form-23-items}{%
+\section{LEBA Long Form (23 Items)}\label{leba-long-form-23-items}}
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.05}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.27}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.34}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.08}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.11}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.07}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.08}}@{}}
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Items
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Never/Does not apply/I don't know
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Rarely
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Sometimes
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Often
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Always
+\end{minipage} \\
+\midrule
+\endhead
+1 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
+indoors during the day. & & & & & \\
+2 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
+outdoors during the day. & & & & & \\
+3 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
+within 1 hour before attempting to fall asleep. & & & & & \\
+4 & I spend 30 minutes or less per day (in total) outside. & & & & & \\
+5 & I spend between 1 and 3 hours per day (in total) outside. & & & &
+& \\
+6 & I spend between 30 minutes and 1 hour per day (in total) outside. &
+& & & & \\
+7 & I spend more than 3 hours per day (in total) outside. & & & & & \\
+8 & I spend as much time outside as possible. & & & & & \\
+9 & I go for a walk or exercise outside within 2 hours after waking up.
+& & & & & \\
+10 & I use my mobile phone within 1 hour before attempting to fall
+asleep. & & & & & \\
+11 & I look at my mobile phone screen immediately after waking up. & & &
+& & \\
+12 & I check my phone when I wake up at night. & & & & & \\
+13 & I look at my smartwatch within 1 hour before attempting to fall
+asleep. & & & & & \\
+14 & I look at my smartwatch when I wake up at night. & & & & & \\
+15 & I dim my mobile phone screen within 1 hour before attempting to
+fall asleep. & & & & & \\
+16 & I use a blue-filter app on my computer screen within 1 hour before
+attempting to fall asleep. & & & & & \\
+17 & I use as little light as possible when I get up during the night. &
+& & & & \\
+18 & I dim my computer screen within 1 hour before attempting to fall
+asleep. & & & & & \\
+19 & I use tunable lights to create a healthy light environment. & & & &
+& \\
+20 & I use LEDs to create a healthy light environment. & & & & & \\
+21 & I use a desk lamp when I do focused work. & & & & & \\
+22 & I use an alarm with a dawn simulation light. & & & & & \\
+23 & I turn on the lights immediately after waking up. & & & & & \\
+\bottomrule
+\end{longtable}
+
+\elandscape
+
+\newpage
+
+\blandscape
+
+\hypertarget{latent-structure-reliability-and-structural-validity}{%
+\subsection{Latent Structure, Reliability and Structural
+Validity}\label{latent-structure-reliability-and-structural-validity}}
+
+The long form of LEBA consists 23 items with five factors.
+
+Factor names
+
+Items
+
+Reliability Coefficients
+
+McDonald's Omega
+
+(N=262)
+
+Reliability Coefficients
+
+Cronbach's alpha
+
+F1: Wearing blue light filters
+
+1-3
+
+.93
+
+.90
+
+F2: Spending time outdoors
+
+4-9 (Item 4 is reversed)
+
+.80
+
+.78
+
+F3: Using phone and smartwatch in bed
+
+10-14
+
+.61
+
+.62
+
+F4: Using light before bedtime
+
+15-18
+
+.72
+
+.62
+
+F5: Using light in the morning and during daytime
+
+19-23
+
+.45
+
+.41
+
+.73(Total scale)
+
+LEBA -long form showed satisfactory structural validity (CFI =.97; TLI =
+.96; RMSEA = .05{[}.04-.06, 90\% CI{]}; SRMR = .09).
+
+\hypertarget{how-to-cite}{%
+\subsection{How to cite:}\label{how-to-cite}}
+
+\elandscape
+
+\newpage
+
+\blandscape
+
+\hypertarget{leba-short-form-17-items}{%
+\section{LEBA Short Form (17 Items)}\label{leba-short-form-17-items}}
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.05}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.27}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.34}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.08}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.11}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.07}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.08}}@{}}
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Short Form (17 Items)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Never/Does not apply/I don't know
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Rarely
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Sometimes
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Often
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Always
+\end{minipage} \\
+\midrule
+\endhead
+01 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
+indoors during the day. & & & & & \\
+02 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
+outdoors during the day. & & & & & \\
+03 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
+within 1 hour before attempting to fall asleep. & & & & & \\
+04 & I spend 30 minutes or less per day (in total) outside. & & & & & \\
+05 & I spend between 1 and 3 hours per day (in total) outside. & & & &
+& \\
+06 & I spend more than 3 hours per day (in total) outside. & & & & & \\
+07 & I spend as much time outside as possible. & & & & & \\
+08 & I go for a walk or exercise outside within 2 hours after waking up.
+& & & & & \\
+09 & I use my mobile phone within 1 hour before attempting to fall
+asleep. & & & & & \\
+10 & I look at my mobile phone screen immediately after waking up. & & &
+& & \\
+11 & I check my phone when I wake up at night. & & & & & \\
+12 & I dim my mobile phone screen within 1 hour before attempting to
+fall asleep. & & & & & \\
+13 & I use a blue-filter app on my computer screen within 1 hour before
+attempting to fall asleep. & & & & & \\
+14 & I dim my computer screen within 1 hour before attempting to fall
+asleep. & & & & & \\
+15 & I use tunable lights to create a healthy light environment. & & & &
+& \\
+16 & I use LEDs to create a healthy light environment. & & & & & \\
+17 & I use an alarm with a dawn simulation light. & & & & & \\
+\bottomrule
+\end{longtable}
+
+\elandscape
+
+\newpage
+
+\blandscape
+
+\hypertarget{latent-structure-reliability-and-structural-validity-1}{%
+\subsection{Latent Structure, Reliability and Structural
+Validity}\label{latent-structure-reliability-and-structural-validity-1}}
+
+The short form of LEBA consists 23 items with five factors.
+
+\begin{longtable}[]{@{}ll@{}}
+\toprule
+Factor names & Items \\
+\midrule
+\endhead
+\textbf{F1: Wearing blue light filters} & 1-3 \\
+\textbf{F2: Spending time outdoors} & 4-8 (Item 4 is reversed) \\
+\textbf{F3: Using phone and smart-watch in bed} & 9-11 \\
+\textbf{F4: Using light before bedtime} & 12-14 \\
+\textbf{F5: Using light in the morning and during daytime} & 15-17 \\
+\bottomrule
+\end{longtable}
+
+\hypertarget{how-to-cite-1}{%
+\subsection{How to cite:}\label{how-to-cite-1}}
+
+\elandscape
+\end{appendix}
+
+\clearpage
+\makeatletter
+\efloat@restorefloats
+\makeatother
+
+\begin{appendix}
+\section{}
+\hypertarget{supplimentary-analysis}{%
+\subsection{Supplimentary Analysis}\label{supplimentary-analysis}}
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:tabDesAppB}Descriptive Statistics for Unmerged response options}
+
+\begin{tabular}{ccccccc}
+\toprule
+ & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{Item-Total Correlation}\\
+\midrule
+Item1 & 2.16 & 1.51 & 0.49 & -0.86 & 0.90* & .21\\
+Item2 & 2.76 & 1.75 & -0.10 & -1.42 & 0.88* & .20\\
+Item3 & 3.34 & 1.43 & -0.58 & -0.77 & 0.88* & .18\\
+Item4 & 1.30 & 1.31 & 1.93 & 2.92 & 0.62* & .32\\
+Item5 & 3.95 & 1.56 & -1.42 & 0.75 & 0.70* & .19\\
+Item6 & 2.70 & 1.66 & 0.02 & -1.33 & 0.90* & .18\\
+Item7 & 2.23 & 1.28 & 0.60 & -0.59 & 0.89* & .18\\
+Item8 & 2.95 & 1.24 & -0.19 & -0.70 & 0.93* & -.07\\
+Item9 & 2.92 & 1.09 & -0.37 & 0.11 & 0.91* & .14\\
+Item10 & 2.73 & 1.07 & -0.03 & -0.52 & 0.92* & .27\\
+Item11 & 2.17 & 0.93 & 0.44 & 0.20 & 0.89* & .25\\
+Item12 & 2.34 & 1.26 & 0.46 & -0.58 & 0.91* & .24\\
+Item13 & 2.71 & 1.49 & 0.14 & -1.29 & 0.89* & .28\\
+Item14 & 2.11 & 1.34 & 0.68 & -0.78 & 0.84* & .24\\
+Item15 & 3.26 & 1.11 & -0.34 & -0.21 & 0.91* & .11\\
+Item16 & 1.46 & 1.31 & 1.71 & 1.90 & 0.65* & .33\\
+Item17 & 1.43 & 1.30 & 1.76 & 2.12 & 0.64* & .30\\
+Item18 & 0.92 & 0.67 & 2.00 & 9.41 & 0.62* & .32\\
+Item19 & 0.85 & 0.56 & 1.71 & 10.74 & 0.55* & .34\\
+Item20 & 0.83 & 0.54 & 1.76 & 13.92 & 0.53* & .31\\
+Item21 & 0.94 & 0.75 & 2.46 & 10.66 & 0.58* & .27\\
+Item22 & 3.57 & 1.08 & -0.72 & 0.08 & 0.88* & .19\\
+Item23 & 2.53 & 1.31 & 0.22 & -0.91 & 0.92* & .11\\
+Item24 & 4.13 & 1.01 & -1.39 & 2.01 & 0.78* & .19\\
+Item25 & 2.57 & 1.43 & 0.22 & -1.23 & 0.88* & .17\\
+Item26 & 2.23 & 1.30 & 0.59 & -0.63 & 0.88* & .16\\
+Item27 & 3.78 & 1.34 & -1.01 & 0.08 & 0.82* & .18\\
+Item28 & 3.75 & 1.16 & -0.78 & -0.10 & 0.86* & .01\\
+Item29 & 2.38 & 1.40 & 0.20 & -1.04 & 0.92* & .11\\
+Item30 & 0.94 & 1.42 & 1.66 & 1.69 & 0.68* & .24\\
+Item31 & 2.91 & 1.76 & -0.24 & -1.41 & 0.87* & .45\\
+Item32 & 3.49 & 1.76 & -0.71 & -1.06 & 0.78* & .43\\
+Item33 & 3.56 & 1.75 & -0.79 & -0.95 & 0.77* & .32\\
+Item34 & 3.30 & 2.00 & -0.54 & -1.50 & 0.74* & .34\\
+Item35 & 3.80 & 1.79 & -1.07 & -0.59 & 0.67* & .24\\
+Item36 & 1.36 & 1.38 & 1.75 & 2.05 & 0.65* & .38\\
+Item37 & 1.30 & 0.94 & 2.79 & 7.65 & 0.48* & -.01\\
+Item38 & 4.27 & 1.18 & -2.07 & 4.01 & 0.65* & .23\\
+Item39 & 1.94 & 1.01 & 0.85 & 0.61 & 0.86* & .05\\
+Item40 & 2.13 & 1.24 & 0.56 & -0.54 & 0.89* & .16\\
+Item41 & 0.87 & 1.08 & 1.68 & 2.74 & 0.73* & .21\\
+Item42 & 3.90 & 1.55 & -1.15 & -0.12 & 0.72* & .17\\
+Item43 & 1.59 & 1.23 & 1.59 & 1.70 & 0.69* & .22\\
+Item44 & 3.46 & 1.41 & -0.92 & -0.01 & 0.86* & .38\\
+Item45 & 2.04 & 1.66 & 0.46 & -1.12 & 0.87* & .29\\
+Item46 & 1.57 & 1.40 & 0.97 & -0.07 & 0.82* & .38\\
+Item47 & 2.07 & 1.23 & 0.59 & -0.42 & 0.89* & .34\\
+Item48 & 2.57 & 1.30 & 0.14 & -0.74 & 0.93* & .31\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} *p<.001}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-1}
+
+}
+
+\caption{Correlation plot of the items}\label{fig:figCorAppB}
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth,height=1\textheight]{manuscript_files/figure-latex/facIdFigAppB-1}
+
+}
+
+\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}\label{fig:facIdFigAppB}
+\end{figure}
+
+Horn's parallel analysis with 500 iterations indicated a five-factor
+solution. However, Scree plot and the MAP method suggested 6-factor
+solution. five-factor solution . As a result, we tested both five-factor
+and six-factor solutions.
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:EFATableAppB}Factor loadings and communality of the retained items [Unmerged Responses]}
+
+\small{
+
+\begin{tabular}{ccccccccc}
+\toprule
+item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness} & \multicolumn{1}{c}{Complexity}\\
+\midrule
+item19 & 0.99 &  &  &  &  & 1.01 & -0.01 & 1.06\\
+item20 & 0.91 &  &  &  &  & 0.87 & 0.13 & 1.11\\
+item18 & 0.82 &  &  &  &  & 0.71 & 0.29 & 1.12\\
+item21 & 0.8 &  &  &  &  & 0.68 & 0.32 & 1.16\\
+item4 & 0.47 &  &  &  &  & 0.25 & 0.75 & 1.30\\
+item11 &  & 0.83 &  &  &  & 0.69 & 0.31 & 1.01\\
+item10 &  & 0.81 &  &  &  & 0.67 & 0.33 & 1.03\\
+item12 &  & 0.56 &  &  &  & 0.37 & 0.63 & 1.37\\
+item8 &  & -0.44 &  &  &  & 0.21 & 0.79 & 1.11\\
+item7 &  & 0.42 &  &  &  & 0.23 & 0.77 & 1.61\\
+item9 &  & 0.33 &  &  &  & 0.12 & 0.88 & 1.10\\
+item16 &  &  & 0.95 &  &  & 0.95 & 0.05 & 1.10\\
+item17 &  &  & 0.74 &  &  & 0.60 & 0.41 & 1.17\\
+item36 & 0.3 &  & 0.73 &  &  & 0.65 & 0.35 & 1.43\\
+item3 &  &  &  & 0.85 &  & 0.75 & 0.25 & 1.05\\
+item27 &  &  &  & 0.78 &  & 0.62 & 0.38 & 1.03\\
+item40 &  &  &  & 0.71 &  & 0.51 & 0.49 & 1.05\\
+item35 &  &  &  &  & 0.58 & 0.35 & 0.65 & 1.09\\
+item48 &  &  &  &  & 0.57 & 0.35 & 0.65 & 1.14\\
+item33 &  &  &  &  & 0.55 & 0.32 & 0.68 & 1.08\\
+item47 &  &  &  &  & 0.52 & 0.29 & 0.71 & 1.19\\
+item44 &  &  &  &  & 0.45 & 0.22 & 0.78 & 1.15\\
+item31 &  &  &  &  & 0.41 & 0.21 & 0.79 & 1.48\\
+item38 &  &  &  &  & 0.33 & 0.13 & 0.87 & 1.32\\
+\% of Variance & 0.15 & 0.09 & 0.09 & 0.08 & 0.08 & NA & NA & NA\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Only loading higher than .30 is reported}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.00}}@{}}
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\textbf{Five Factor Solution{[}Unmerged Responses{]} (24 Items)}
+\end{minipage} \\
+\midrule
+\endhead
+\textbf{F1} \\
+I use light therapy applying a blue light box. \\
+I use light therapy applying a light visor. \\
+I use light therapy applying a white light box. \\
+I use light therapy applying another form of light device. \\
+I use an alarm with a dawn simulation light. \\
+\textbf{F2} \\
+I spend more than 3 hours per day (in total) outside. \\
+I spend between 1 and 3 hours per day (in total) outside. \\
+I spend as much time outside as possible. \\
+I spend 30 minutes or less per day (in total) outside. \\
+I go for a walk or exercise outside within 2 hours after waking up. \\
+I spend between 30 minutes and 1 hour per day (in total) outside. \\
+\textbf{F3} \\
+I look at my mobile phone screen immediately after waking up. \\
+I use my mobile phone within 1 hour before attempting to fall asleep. \\
+I check my phone when I wake up at night. \\
+\textbf{F4} \\
+I use a blue-filter app on my computer screen within 1 hour before
+attempting to fall asleep. \\
+I seek out knowledge on how to improve my light exposure. \\
+I dim my computer screen within 1 hour before attempting to fall
+asleep. \\
+I discuss the effects of light on my body with other people. \\
+I modify my light environment to match my current needs. \\
+I dim my room light within 1 hour before attempting to fall asleep. \\
+I use as little light as possible when I get up during the night. \\
+\textbf{F5} \\
+I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors
+during the day. \\
+I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors
+during the day. \\
+I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1
+hour before attempting to fall asleep. \\
+\bottomrule
+\end{longtable}
+\end{appendix}
+
 \end{document}

### 2021-11-10 Supplymentary.Rmd
supplementary analysis

@@
 par(family = "Helvetica")
+```
+
+```{r lib, include=FALSE}
+
+library(papaja) # devtools::install_github("crsh/papaja")
+library(lavaan)
+library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
+library(semTools)
+library(MOTE)
+library(car)#revercoding 
+library(psych)
+library(dlookr)
+library(plyr)
+library(tidyverse)
+library(qgraph)
+library(kableExtra)
+library(paran) # Parallel analysis
+library(EFA.MRFA) # Hull method
+library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
+library(DiagrammeRsvg) #For DiagrammeR
+library(rsvg) #For DiagrammeR
+library(ggcorrplot)
+library(semTable)
+library(magick)
+library(mirt)
+library(gtsummary)
+library(gt)
+library(gtExtras)
+library(likert)
+library(VIM) #Missing data
+library(kutils)
+library(simsem)
+library(tabledown)
+library(Hmisc)
+r_refs("references.bib")
 ```
@@
 ```
+
+# Factor Analysis with Unmerged Response Option
+```{r DataAppB, include=FALSE}
+data <- readRDS("leba_2021-09-08.rds")
+
+#Separating the EFA and CFA(only items)
+sem.data <- data[, 9:56] #EFA & CFA data
+## renaming the column-header
+prefix <- "item"
+sufix <- c(1:48)
+colnam <- paste(prefix,sufix, sep = "" )
+colnames(sem.data) <- colnam
+EFA.data <- sem.data[1:428, ]
+
+```
+
+```{r ggplot2AppB, include=F}
+apatheme=ggplot2::theme_bw()+
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.background = element_blank(),
+        text=element_text(family = "Helvetica",),
+        legend.title=element_blank(),
+        axis.line.x = element_line(color='black'),
+        axis.line.y = element_line(color='black'),
+        panel.border = element_rect(color = "black",
+                                    fill = NA,
+                                    size = 1))
+```
+
+```{r EFAassumptionsAppB, include=FALSE}
+
+#KMO test
+KMO <- KMO(EFA.data)
+
+# Test of correlation matrix
+bartlet <- cortest.bartlett(EFA.data, n =428)
+
+# Univariate normality
+
+#creating normality function
+shapiro_test_df <- function(df, bonf= TRUE, alpha= 0.05) {
+  l <- lapply(df, shapiro.test)
+  s <- do.call("c", lapply(l, "[[", 1))
+  p <- do.call("c", lapply(l, "[[", 2))
+  if (bonf == TRUE) {
+    sig <- ifelse(p > alpha / length(l), "H0", "*")
+  } else {
+    sig <- ifelse(p > alpha, "H0", "*")
+  }
+  return(list(statistic= s,
+              p.value= p,
+              significance= sig,
+              method= ifelse(bonf == TRUE, "Shapiro-Wilks test with Bonferroni Correction","Shapiro-Wilks test without Bonferroni Correction")))
+}
+
+Shapiro.efa <- shapiro_test_df(EFA.data)
+
+efa.normality.tab = matrix(nrow = 48, ncol = 2)
+rownameprefix <- "Item"
+rownamesufix <- seq(1:48)
+my.item.names <- paste(rownameprefix,rownamesufix, sep = "" )
+rownames(efa.normality.tab) <- my.item.names
+colnames(efa.normality.tab) <- c("statistic", "p")
+
+efa.normality.tab[,1] <- apa(Shapiro.efa$statistic,2,T)
+efa.normality.tab[,2] <- apa(Shapiro.efa$p.value,2,T)
+
+efa.normalityprefix <- efa.normality.tab[,1]
+efa.normalitysufix <- Shapiro.efa$significance
+efa.normality.stat <- paste(efa.normalityprefix,efa.normalitysufix, sep = "" )
+
+# Multivariate Normality
+mardia <- mardia(EFA.data, na.rm = T, plot =F)
+
+# Descriptive Stats
+Descriptives <- psych::describe(EFA.data)
+alpha <- psych::alpha(EFA.data)
+Item.total <- alpha$item.stats
+
+Des.combined <- cbind(apa(Descriptives$mean,2,T), apa(Descriptives$sd,2,T), apa(Descriptives$skew,2,T),apa(Descriptives$kurtosis,2,T), efa.normality.stat,  apa(Item.total$r.cor,2,F))
+
+colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics","Item-Total Correlation")
+rownameprefix <- "Item"
+rownamesufix <- seq(1:48)
+my.names <- paste(rownameprefix,rownamesufix, sep = "" )
+rownames(Des.combined) = (my.names)
+```
+
+```{r tabDesAppB, results='asis'}
+apa_table(Des.combined, caption = "Descriptive Statistics for Unmerged response options", align = "c", note = "*p<.001", placement = "h")
+```
+
+```{r CorrMatrixAppB, include=FALSE}
+#Polychoric Correlation matrix
+
+correlations <- polychoric(EFA.data, correct = 0)
+upper <- correlations$rho[upper.tri(correlations$rho, diag = F)]
+
+min.cor <- abs(min(upper)) #minimum cor.coefficient of the matrix
+max.cor <- abs(max(upper)) # max. correlation coefficient of the matrix
+
+determinets <- det(correlations$rho) 
+# Calculating the percentage of correlations higher than .30
+
+BigR = sum(correlations$rho >= abs(.30) & correlations$rho < abs(1.0), na.rm =T)/2 
+totR = length(EFA.data)*(length(EFA.data)-1)/2
+cor.per <- print (BigR/totR)*100
+```
+
+```{r figCorAppB, fig.align='center', fig.cap="Correlation plot of the items",  out.width="100%"}
+
+ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
+           ggtheme = ggplot2::theme_minimal, tl.cex = 6,tl.srt = 90 )
+#p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
+#to show pvalue in the fig add p.mat=p.mat
+```
+
+```{r ParallelEFAAppB, include=FALSE}
+
+# Parallel analysis
+Horn <- paran(correlations$rho, iterations=500, centile=0, quietly=FALSE,
+           status=TRUE, all=FALSE, cfa=FALSE, graph=TRUE,
+           color=TRUE, col=c("black","red","blue"),
+           lty=c(1,2,3), lwd=1, legend=TRUE, 
+           width=640, height=640, grdevice=png, seed=0, mat=NA, n=NA)
+
+Adjusted.EV <- data.frame(Horn$AdjEv)
+Adjusted.EV$type = c('Adjusted Ev')
+Adjusted.EV$num = c(row.names(Adjusted.EV))
+Adjusted.EV$num = as.numeric(Adjusted.EV$num)
+colnames(Adjusted.EV) = c('eigenvalue', 'type', 'num')
+
+Random.EV <- data.frame(Horn$RndEv)
+Random.EV$type = c('Random EV')
+Random.EV$num = c(row.names(Random.EV))
+Random.EV$num = as.numeric(Random.EV$num)
+colnames(Random.EV) = c('eigenvalue', 'type', 'num')
+
+Unadjusted.EV <- data.frame(Horn$Ev)
+Unadjusted.EV$type = c('Unadjusted EV')
+Unadjusted.EV$num = c(row.names(Unadjusted.EV))
+Unadjusted.EV$num = as.numeric(Unadjusted.EV$num)
+colnames(Unadjusted.EV) = c('eigenvalue', 'type', 'num')
+
+parallel = ggplot(Adjusted.EV, aes(x=num, y=eigenvalue, shape=type, color=type)) +
+  #Add lines connecting data points
+  geom_line()+
+    geom_line(data = Random.EV) +
+  geom_line(data = Unadjusted.EV)+
+    #Add the data points.
+  geom_point(size=1)+
+  geom_point(data = Random.EV, size=1)+
+  geom_point(data = Unadjusted.EV, size=1)+
+  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
+   #Label the x-axis 'Factor Number', and ensure that it ranges from 1-max # of factors, increasing by one with each 'tick' mark.
+  scale_x_continuous(name='Factor Number', limits=c(0, 48),breaks=seq(0,48,4))+
+    #Add vertical line indicating parallel analysis suggested max # of factors to retain
+  geom_hline(yintercept=1, linetype = 'dashed') + apatheme
+
+```
+
+```{r ScreePlotAppB, include=FALSE}
+Scree <- scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
+      hline=NULL,add=F)
+
+FA.Scree <- data.frame(Scree$fv)
+FA.Scree$type = c('Factor Analysis')
+FA.Scree$num = c(row.names(FA.Scree))
+FA.Scree$num = as.numeric(FA.Scree$num)
+colnames(FA.Scree) = c('eigenvalue', 'type', 'num')
+
+PA.Scree <- data.frame(Scree$pcv)
+PA.Scree$type = c('Principal Component Analysis')
+PA.Scree$num = c(row.names(PA.Scree))
+PA.Scree$num = as.numeric(PA.Scree$num)
+colnames(PA.Scree) = c('eigenvalue', 'type', 'num')
+
+scree.plot <-ggplot(FA.Scree, aes(x=num, y=eigenvalue,color=type, shape=type))+
+   geom_line()+
+  geom_line(data = PA.Scree)+ 
+  geom_point(size=1)+
+  geom_point(data = PA.Scree, size=1)+
+  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
+  scale_x_continuous(name='Factor Number', limits=c(0, 48),breaks=seq(0,48,4))+
+  geom_hline(yintercept=1, linetype = 'dashed') + apatheme 
+```
+
+```{r MAPefaAppB, include=FALSE}
+#MAP
+psych::VSS(EFA.data, rotate = "varimax", fm = 'minres', n.obs =428 )
+```
+
+```{r facIdFigAppB, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot', warning=FALSE,  out.height="100%", out.width="100%"}
+cowplot::plot_grid(parallel, scree.plot, labels = "AUTO",ncol=1, label_size = 8,align = "v")
+
+```
+
+Horn's parallel analysis with 500 iterations indicated a five-factor solution.
+However, Scree plot and the MAP method suggested 6-factor solution.
+five-factor solution .
+As a result, we tested both five-factor and six-factor solutions.
+
+```{r EFAAppB, include=FALSE}
+fa.5F.1 <- fa(r=correlations$rho, nfactors = 5, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+AA <- print(fa.5F.1, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.5F.1 <- dplyr::select(EFA.data ,
+                                    -c(item32, item34, item24, item37, item22, item5,
+                                        item28, item30, item39,item23, item45, item6, item29, item2, item41))
+
+correlations.red.5F.1 <- polychoric(reduced.model.5F.1,correct = 0)
+
+fa.5F.2 <- fa(r=correlations.red.5F.1$rho, nfactors = 5, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+
+BB <- print(fa.5F.2, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.5F.2 <- dplyr::select(EFA.data, -c( item32, item34, item24, item37, item22, item5,
+                                        item28, item30, item39,item23, item45, item6, item29, item2, item41, item46, item13, item15, item25, item1, item26, item14))
+
+correlations.red.5F.2 <- polychoric(reduced.model.5F.2,correct = 0)
+
+fa.5F.3 <- fa(r=correlations.red.5F.2$rho, nfactors = 5, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428,max.iter = 500 )
+
+CC <- print(fa.5F.3, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.5F.3 <- dplyr::select(EFA.data, -c( item32, item34, item24, item37, item22, item5,
+                                        item28, item30, item39,item23, item45, item6, item29, item2, item41, item46, item13, item15, item25, item1, item26, item14, item43, item42))
+
+correlations.red.5F.3 <- polychoric(reduced.model.5F.3,correct = 0)
+
+fa.5F.4 <- fa(r=correlations.red.5F.3$rho, nfactors = 5, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428,max.iter = 500 )
+
+CC <- print(fa.5F.4, cut = .3, digits = 3, sort = TRUE)
+```
+
+```{r factordetailsAppB, include=FALSE}
+#Preparing the EFA table
+library(data.table)
+fa_table <- function(x, cut) {
+  #get sorted loadings
+  loadings <- fa.sort(x)$loadings %>% round(2)
+  #supress loadings
+  loadings[abs(loadings) < abs(cut)] <- ""
+  #get additional info
+  add_info <- cbind(x$communality, 
+                    x$uniquenesses,
+                    x$complexity) %>%
+    # make it a data frame
+    as.data.frame() %>%
+    # column names
+    rename("Communality" = V1,
+           "Uniqueness" = V2,
+           "Complexity" = V3) %>%
+    #get the item names from the vector
+    rownames_to_column("item")
+  #build table
+  loadings <- loadings %>%
+    unclass() %>%
+    as.data.frame() %>%
+    rownames_to_column("item") %>%
+    left_join(add_info) %>%
+    mutate(across(where(is.numeric), round, 3)) %>% 
+    as.data.frame()
+  variance <- x$Vaccounted %>% 
+  as.data.frame()%>% 
+  round(2)
+  loadings <- rbind(setDT(loadings), setDT(variance[2,]), fill=TRUE)
+
+}
+
+efa.table <- fa_table(fa.5F.4,.3) 
+nr <- nrow(efa.table)
+efa.table[nr, 1] <- "% of Variance"
+
+#Communality
+Fac.5 <- fa.5F.4
+min.com <- min(Fac.5$communality)
+max.com <- max(Fac.5$communality)
+
+# loading
+min.loadings <- min(Fac.5$loadings)
+max.loadings <- max(Fac.5$loadings)
+
+# Residuals
+residual.5F =residuals(fa.5F.4, diag = FALSE, na.rm =T)
+#Count of numbers of residuals>.05
+BigRR= sum(residual.5F>abs(.05), na.rm =T)
+print(BigRR)
+
+#Total number of off diagonal elements in the data matrix
+totRR = length(reduced.model.5F.3)*(length(reduced.model.5F.3)-1)/2
+
+# Proportion of off-diagonal elements >.10
+sumR <- sum(BigRR/totRR*100)
+
+```
+
+```{r EFATableAppB, results='asis'}
+
+apa_table(efa.table,align = "c", caption = "Factor loadings and communality of the retained items [Unmerged Responses]", note = "Only loading higher than .30 is reported", font_size = "small", placement = "h")
+```
+
+| **Five Factor Solution[Unmerged Responses] (24 Items)** |
+|---------------------------------------------------------|
+| **F1**                                                  |
+| `r label(sem.data$item19)`                              |
+| `r label(sem.data$item20)`                              |
+| `r label(sem.data$item18)`                              |
+| `r label(sem.data$item21)`                              |
+| `r label(sem.data$item4)`                               |
+| **F2**                                                  |
+| `r label(sem.data$item11)`                              |
+| `r label(sem.data$item10)`                              |
+| `r label(sem.data$item12)`                              |
+| `r label(sem.data$item8)`                               |
+| `r label(sem.data$item7)`                               |
+| `r label(sem.data$item9)`                               |
+| **F3**                                                  |
+| `r label(sem.data$item3)`                               |
+| `r label(sem.data$item27)`                              |
+| `r label(sem.data$item40)`                              |
+| **F4**                                                  |
+| `r label(sem.data$item35)`                              |
+| `r label(sem.data$item48)`                              |
+| `r label(sem.data$item33)`                              |
+| `r label(sem.data$item47)`                              |
+| `r label(sem.data$item44)`                              |
+| `r label(sem.data$item31)`                              |
+| `r label(sem.data$item38)`                              |
+| **F5**                                                  |
+| `r label(sem.data$item16)`                              |
+| `r label(sem.data$item17)`                              |
+| `r label(sem.data$item36)`                              |
+
+```{r EFAResidualsAppB, eval=FALSE, fig.align='center', fig.cap=' Histogram of residulas:  five-factor solution', warning=FALSE, include=FALSE,  results='asis'}
+hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))
+abline(h =35, lwd = 2, lty = 2)
+abline(v =.05,lwd = 2, lty = 2)
+
+```

### 2021-11-10 Supplymentary.tex
supplementary analysis

@@
 \end{table}
+
+\hypertarget{factor-analysis-with-unmerged-response-option}{%
+\section{Factor Analysis with Unmerged Response
+Option}\label{factor-analysis-with-unmerged-response-option}}
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:tabDesAppB}Descriptive Statistics for Unmerged response options}
+
+\begin{tabular}{ccccccc}
+\toprule
+ & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{Item-Total Correlation}\\
+\midrule
+Item1 & 2.16 & 1.51 & 0.49 & -0.86 & 0.90* & .21\\
+Item2 & 2.76 & 1.75 & -0.10 & -1.42 & 0.88* & .20\\
+Item3 & 3.34 & 1.43 & -0.58 & -0.77 & 0.88* & .18\\
+Item4 & 1.30 & 1.31 & 1.93 & 2.92 & 0.62* & .32\\
+Item5 & 3.95 & 1.56 & -1.42 & 0.75 & 0.70* & .19\\
+Item6 & 2.70 & 1.66 & 0.02 & -1.33 & 0.90* & .18\\
+Item7 & 2.23 & 1.28 & 0.60 & -0.59 & 0.89* & .18\\
+Item8 & 2.95 & 1.24 & -0.19 & -0.70 & 0.93* & -.07\\
+Item9 & 2.92 & 1.09 & -0.37 & 0.11 & 0.91* & .14\\
+Item10 & 2.73 & 1.07 & -0.03 & -0.52 & 0.92* & .27\\
+Item11 & 2.17 & 0.93 & 0.44 & 0.20 & 0.89* & .25\\
+Item12 & 2.34 & 1.26 & 0.46 & -0.58 & 0.91* & .24\\
+Item13 & 2.71 & 1.49 & 0.14 & -1.29 & 0.89* & .28\\
+Item14 & 2.11 & 1.34 & 0.68 & -0.78 & 0.84* & .24\\
+Item15 & 3.26 & 1.11 & -0.34 & -0.21 & 0.91* & .11\\
+Item16 & 1.46 & 1.31 & 1.71 & 1.90 & 0.65* & .33\\
+Item17 & 1.43 & 1.30 & 1.76 & 2.12 & 0.64* & .30\\
+Item18 & 0.92 & 0.67 & 2.00 & 9.41 & 0.62* & .32\\
+Item19 & 0.85 & 0.56 & 1.71 & 10.74 & 0.55* & .34\\
+Item20 & 0.83 & 0.54 & 1.76 & 13.92 & 0.53* & .31\\
+Item21 & 0.94 & 0.75 & 2.46 & 10.66 & 0.58* & .27\\
+Item22 & 3.57 & 1.08 & -0.72 & 0.08 & 0.88* & .19\\
+Item23 & 2.53 & 1.31 & 0.22 & -0.91 & 0.92* & .11\\
+Item24 & 4.13 & 1.01 & -1.39 & 2.01 & 0.78* & .19\\
+Item25 & 2.57 & 1.43 & 0.22 & -1.23 & 0.88* & .17\\
+Item26 & 2.23 & 1.30 & 0.59 & -0.63 & 0.88* & .16\\
+Item27 & 3.78 & 1.34 & -1.01 & 0.08 & 0.82* & .18\\
+Item28 & 3.75 & 1.16 & -0.78 & -0.10 & 0.86* & .01\\
+Item29 & 2.38 & 1.40 & 0.20 & -1.04 & 0.92* & .11\\
+Item30 & 0.94 & 1.42 & 1.66 & 1.69 & 0.68* & .24\\
+Item31 & 2.91 & 1.76 & -0.24 & -1.41 & 0.87* & .45\\
+Item32 & 3.49 & 1.76 & -0.71 & -1.06 & 0.78* & .43\\
+Item33 & 3.56 & 1.75 & -0.79 & -0.95 & 0.77* & .32\\
+Item34 & 3.30 & 2.00 & -0.54 & -1.50 & 0.74* & .34\\
+Item35 & 3.80 & 1.79 & -1.07 & -0.59 & 0.67* & .24\\
+Item36 & 1.36 & 1.38 & 1.75 & 2.05 & 0.65* & .38\\
+Item37 & 1.30 & 0.94 & 2.79 & 7.65 & 0.48* & -.01\\
+Item38 & 4.27 & 1.18 & -2.07 & 4.01 & 0.65* & .23\\
+Item39 & 1.94 & 1.01 & 0.85 & 0.61 & 0.86* & .05\\
+Item40 & 2.13 & 1.24 & 0.56 & -0.54 & 0.89* & .16\\
+Item41 & 0.87 & 1.08 & 1.68 & 2.74 & 0.73* & .21\\
+Item42 & 3.90 & 1.55 & -1.15 & -0.12 & 0.72* & .17\\
+Item43 & 1.59 & 1.23 & 1.59 & 1.70 & 0.69* & .22\\
+Item44 & 3.46 & 1.41 & -0.92 & -0.01 & 0.86* & .38\\
+Item45 & 2.04 & 1.66 & 0.46 & -1.12 & 0.87* & .29\\
+Item46 & 1.57 & 1.40 & 0.97 & -0.07 & 0.82* & .38\\
+Item47 & 2.07 & 1.23 & 0.59 & -0.42 & 0.89* & .34\\
+Item48 & 2.57 & 1.30 & 0.14 & -0.74 & 0.93* & .31\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} *p<.001}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-1}
+
+}
+
+\caption{Correlation plot of the items}(\#fig:figCorAppB)
+\end{figure}
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth,height=1\textheight]{manuscript_files/figure-latex/facIdFigAppB-1}
+
+}
+
+\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}(\#fig:facIdFigAppB)
+\end{figure}
+
+Horn's parallel analysis with 500 iterations indicated a five-factor
+solution. However, Scree plot and the MAP method suggested 6-factor
+solution. five-factor solution . As a result, we tested both five-factor
+and six-factor solutions.
+
+\begin{table}[h]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:EFATableAppB}Factor loadings and communality of the retained items [Unmerged Responses]}
+
+\small{
+
+\begin{tabular}{ccccccccc}
+\toprule
+item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness} & \multicolumn{1}{c}{Complexity}\\
+\midrule
+item19 & 0.99 &  &  &  &  & 1.01 & -0.01 & 1.06\\
+item20 & 0.91 &  &  &  &  & 0.87 & 0.13 & 1.11\\
+item18 & 0.82 &  &  &  &  & 0.71 & 0.29 & 1.12\\
+item21 & 0.8 &  &  &  &  & 0.68 & 0.32 & 1.16\\
+item4 & 0.47 &  &  &  &  & 0.25 & 0.75 & 1.30\\
+item11 &  & 0.83 &  &  &  & 0.69 & 0.31 & 1.01\\
+item10 &  & 0.81 &  &  &  & 0.67 & 0.33 & 1.03\\
+item12 &  & 0.56 &  &  &  & 0.37 & 0.63 & 1.37\\
+item8 &  & -0.44 &  &  &  & 0.21 & 0.79 & 1.11\\
+item7 &  & 0.42 &  &  &  & 0.23 & 0.77 & 1.61\\
+item9 &  & 0.33 &  &  &  & 0.12 & 0.88 & 1.10\\
+item16 &  &  & 0.95 &  &  & 0.95 & 0.05 & 1.10\\
+item17 &  &  & 0.74 &  &  & 0.60 & 0.41 & 1.17\\
+item36 & 0.3 &  & 0.73 &  &  & 0.65 & 0.35 & 1.43\\
+item3 &  &  &  & 0.85 &  & 0.75 & 0.25 & 1.05\\
+item27 &  &  &  & 0.78 &  & 0.62 & 0.38 & 1.03\\
+item40 &  &  &  & 0.71 &  & 0.51 & 0.49 & 1.05\\
+item35 &  &  &  &  & 0.58 & 0.35 & 0.65 & 1.09\\
+item48 &  &  &  &  & 0.57 & 0.35 & 0.65 & 1.14\\
+item33 &  &  &  &  & 0.55 & 0.32 & 0.68 & 1.08\\
+item47 &  &  &  &  & 0.52 & 0.29 & 0.71 & 1.19\\
+item44 &  &  &  &  & 0.45 & 0.22 & 0.78 & 1.15\\
+item31 &  &  &  &  & 0.41 & 0.21 & 0.79 & 1.48\\
+item38 &  &  &  &  & 0.33 & 0.13 & 0.87 & 1.32\\
+\% of Variance & 0.15 & 0.09 & 0.09 & 0.08 & 0.08 & NA & NA & NA\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} Only loading higher than .30 is reported}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 0\tabcolsep) * \real{1.00}}@{}}
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\textbf{Five Factor Solution{[}Unmerged Responses{]} (24 Items)}
+\end{minipage} \\
+\midrule
+\endhead
+\textbf{F1} \\
+I use light therapy applying a blue light box. \\
+I use light therapy applying a light visor. \\
+I use light therapy applying a white light box. \\
+I use light therapy applying another form of light device. \\
+I use an alarm with a dawn simulation light. \\
+\textbf{F2} \\
+I spend more than 3 hours per day (in total) outside. \\
+I spend between 1 and 3 hours per day (in total) outside. \\
+I spend as much time outside as possible. \\
+I spend 30 minutes or less per day (in total) outside. \\
+I go for a walk or exercise outside within 2 hours after waking up. \\
+I spend between 30 minutes and 1 hour per day (in total) outside. \\
+\textbf{F3} \\
+I look at my mobile phone screen immediately after waking up. \\
+I use my mobile phone within 1 hour before attempting to fall asleep. \\
+I check my phone when I wake up at night. \\
+\textbf{F4} \\
+I use a blue-filter app on my computer screen within 1 hour before
+attempting to fall asleep. \\
+I seek out knowledge on how to improve my light exposure. \\
+I dim my computer screen within 1 hour before attempting to fall
+asleep. \\
+I discuss the effects of light on my body with other people. \\
+I modify my light environment to match my current needs. \\
+I dim my room light within 1 hour before attempting to fall asleep. \\
+I use as little light as possible when I get up during the night. \\
+\textbf{F5} \\
+I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors
+during the day. \\
+I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors
+during the day. \\
+I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1
+hour before attempting to fall asleep. \\
+\bottomrule
+\end{longtable}
 \end{appendix}

### 2021-11-10 manuscript.Rmd
supplementary analysis

@@
   - "instrument.Rmd"
-  - "Appendix-B.Rmd"
 mainfont: Helvetica

### 2021-11-10 manuscript.Rmd
renv::restore() is added
* Table 2 now has header. But footer is missing

@@
 
-```{r depMan, eval=FALSE, include=FALSE}
+```{r depMan, include=FALSE}
 #renv::init()
@@
 #renv::status()
-#renv::restore()
+renv::restore()
 ```
@@
     ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
-modify_header(label ~ "**Variable**") -> desc_table
+modify_header(label ~ "**Variable**") %>% modify_caption("Dempgraphics") -> desc_table
 
@@
 
-as_gt(desc_table) -> desc_gt
 ```
@@
 For their "Occupational Status", more than half of the overall sample reported that they currently work [Overall: `r desc_tibble[9,2]`; EFA: `r desc_tibble[9,3]`; CFA: `r desc_tibble[9,4]`], whereas `r desc_tibble[10,2]` [EFA: `r desc_tibble[10,3]`; CFA: `r desc_tibble[10,4]`] reported that they go to school and `r desc_tibble[11,2]` [EFA: `r desc_tibble[11,3]`; CFA: `r desc_tibble[11,4]`] responded that they do "Neither".
-With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` [EFA: `r desc_tibble[13,3]`; CFA: `r desc_tibble[13,4]`\] of the participants indicated that they were in a home office/ home schooling setting., while `r desc_tibble[14,2]` overall [EFA: `r desc_tibble[14,3]` ; CFA: `r desc_tibble[14,4]`] reported face-to-face work/schooling.
+With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` [EFA: `r desc_tibble[13,3]`; CFA: `r desc_tibble[13,4]`] of the participants indicated that they were in a home office/ home schooling setting., while `r desc_tibble[14,2]` overall [EFA: `r desc_tibble[14,3]` ; CFA: `r desc_tibble[14,4]`] reported face-to-face work/schooling.
 Lastly, `r desc_tibble[15,2]` overall [EFA: `r desc_tibble[15,3]` ; CFA: `r desc_tibble[15,4]`] reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]` overall [EFA: `r desc_tibble[16,3]`; CFA: `r desc_tibble[16,4]`] filled in the "Neither (no work or school, or indication)" response option.

### 2021-11-11 Supplymentary.Rmd
* Successfully Knitting with appendix but formating is not right

@@
 
-```{r EFAResidualsAppB, eval=FALSE, fig.align='center', fig.cap=' Histogram of residulas:  five-factor solution', warning=FALSE, include=FALSE,  results='asis'}
+```{r EFAResidualsAppB,  fig.align='center', fig.cap=' Histogram of residulas:  five-factor solution', warning=FALSE, results='asis'}
 hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))

### 2021-11-11 Supplymentary.Rmd
* Table 2 is now formatted * Polygon edge not found error is solved.
* installation script is uploaded

@@
 apatheme=ggplot2::theme_bw()+
-  theme(panel.grid.major = element_blank(),
+  ggplot2::theme(panel.grid.major = element_blank(),
         panel.grid.minor = element_blank(),
         panel.background = element_blank(),
-        text=element_text(family = "Helvetica",),
+        #text=element_text(family = "Helvetica",),
         legend.title=element_blank(),
@@
 
-```{r facIdFigAppB, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot', warning=FALSE,  out.height="100%", out.width="100%"}
+```{r facIdFigAppB, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot', warning=FALSE}
 cowplot::plot_grid(parallel, scree.plot, labels = "AUTO",ncol=1, label_size = 8,align = "v")

### 2021-11-11 instrument.tex
* rnev introduced
loading is much faster
supplementary analysis
* Table 2 is now formatted * Polygon edge not found error is solved.
* installation script is uploaded

@@
 
-\begin{longtable}[]{@{}lll@{}}
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.33}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.15}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.26}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.26}}@{}}
 \toprule
-Factor names & Items & Reliability Coefficients \\
+\begin{minipage}[b]{\linewidth}\raggedright
+Factor names
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Items
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Reliability Coefficients: McDonald's Omega
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Reliability Coefficients: Cronbach's alpha
+\end{minipage} \\
 \midrule
 \endhead
-\textbf{F1: Wearing blue light filters} & 1-3 & .93 \\
-\textbf{F2: Spending time outdoors} & 4-9 (Item 4 is reversed) & .80 \\
-\textbf{F3: Using phone and smartwatch in bed} & 10-14 & .61 \\
-\textbf{F4: Using light before bedtime} & 15-18 & .72 \\
-\textbf{F5: Using light in the morning and during daytime} & 19-23 &
-.45 \\
+\textbf{F1: Wearing blue light filters} & 1-3 & .93 & .90 \\
+F2: Spending time outdoors & 4-9 (Item 4 is reversed) & .80 & .78 \\
+\textbf{F3: Using phone and smartwatch in bed} & 10-14 & .61 & .62 \\
+\textbf{F4: Using light before bedtime} & 15-18 & .72 & .62 \\
+\textbf{F5: Using light in the morning and during daytime} & 19-23 & .45
+& .41 \\
+& & .73(Total scale) & \\
 \bottomrule

### 2021-11-11 manuscript.Rmd
* Table 2 is now formatted * Polygon edge not found error is solved.
* installation script is uploaded

@@
 as_tibble(desc_table) -> desc_tibble 
-as_kable(desc_table, format = 'pipe') -> desc_kable #save it as a knitr::kable
+as_kable_extra(desc_table, format = "latex",booktabs = T) -> desc_kable #save it as a knitr::kable
 
@@
 
-desc_kable %>% kable_styling(desc_kable, repeat_header_text = "Participants' Demographic Characteristics")
-
-#desc_gt %>% gt::tab_header("Participants' Demographic Characteristics")
+desc_kable %>% kable_styling(latex_options = c("scale_down"))
 

### 2021-11-11 manuscript.tex
supplementary analysis
* Successfully Knitting with appendix but formating is not right
* Table 2 is now formatted * Polygon edge not found error is solved.
* installation script is uploaded

@@
 
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.35}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.14}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.18}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.18}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.08}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.08}}@{}}
+\begin{table}
+
+\caption{\label{tab:prepareDescTable}Dempgraphics}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}[t]{llllll}
 \toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\textbf{Variable}
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-\textbf{Overall}, N = 690
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-\textbf{1. EFA Sample}, N = 428
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-\textbf{2. CFA Sample}, N = 262
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-\textbf{p-value}
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-\textbf{q-value}
-\end{minipage} \\
+Variable & Overall, N = 690 & 1. EFA Sample, N = 428 & 2. CFA Sample, N = 262 & p-value & q-value\\
 \midrule
-\endhead
-\textbf{Age} & 32.95 (14.57) & 32.99 (15.11) & 32.89 (13.66) & 0.5 & 0.5 \\
-\textbf{Sex} & & & & 0.14 & 0.4 \\
-Female & 325 (47\%) & 189 (44\%) & 136 (52\%) & & \\
-Male & 351 (51\%) & 230 (54\%) & 121 (46\%) & & \\
-Other & 14 (2.0\%) & 9 (2.1\%) & 5 (1.9\%) & & \\
-\textbf{Gender-Variant Identity} & 49 (7.2\%) & 33 (7.8\%) & 16 (6.2\%) & 0.4 & 0.5 \\
-\textbf{Native English Speaker} & 320 (46\%) & 191 (45\%) & 129 (49\%) & 0.2 & 0.5 \\
-\textbf{Occupational Status} & & & & 0.040 & 0.2 \\
-Work & 396 (57\%) & 235 (55\%) & 161 (61\%) & & \\
-School & 174 (25\%) & 122 (29\%) & 52 (20\%) & & \\
-Neither & 120 (17\%) & 71 (17\%) & 49 (19\%) & & \\
-\textbf{Occupational setting} & & & & 0.3 & 0.5 \\
-Home office/Home schooling & 303 (44\%) & 194 (45\%) & 109 (42\%) & & \\
-Face-to-face work/Face-to-face schooling & 109 (16\%) & 68 (16\%) & 41 (16\%) & & \\
-Combination of home- and face-to-face- work/schooling & 147 (21\%) & 94 (22\%) & 53 (20\%) & & \\
-Neither (no work or school, or in vacation) & 131 (19\%) & 72 (17\%) & 59 (23\%) & & \\
+Age & 32.95 (14.57) & 32.99 (15.11) & 32.89 (13.66) & 0.5 & 0.5\\
+Sex &  &  &  & 0.14 & 0.4\\
+\hspace{1em}Female & 325 (47\%) & 189 (44\%) & 136 (52\%) &  & \\
+\hspace{1em}Male & 351 (51\%) & 230 (54\%) & 121 (46\%) &  & \\
+\hspace{1em}Other & 14 (2.0\%) & 9 (2.1\%) & 5 (1.9\%) &  & \\
+\addlinespace
+Gender-Variant Identity & 49 (7.2\%) & 33 (7.8\%) & 16 (6.2\%) & 0.4 & 0.5\\
+Native English Speaker & 320 (46\%) & 191 (45\%) & 129 (49\%) & 0.2 & 0.5\\
+Occupational Status &  &  &  & 0.040 & 0.2\\
+\hspace{1em}Work & 396 (57\%) & 235 (55\%) & 161 (61\%) &  & \\
+\hspace{1em}School & 174 (25\%) & 122 (29\%) & 52 (20\%) &  & \\
+\addlinespace
+\hspace{1em}Neither & 120 (17\%) & 71 (17\%) & 49 (19\%) &  & \\
+Occupational setting &  &  &  & 0.3 & 0.5\\
+\hspace{1em}Home office/Home schooling & 303 (44\%) & 194 (45\%) & 109 (42\%) &  & \\
+\hspace{1em}Face-to-face work/Face-to-face schooling & 109 (16\%) & 68 (16\%) & 41 (16\%) &  & \\
+\hspace{1em}Combination of home- and face-to-face- work/schooling & 147 (21\%) & 94 (22\%) & 53 (20\%) &  & \\
+\addlinespace
+\hspace{1em}Neither (no work or school, or in vacation) & 131 (19\%) & 72 (17\%) & 59 (23\%) &  & \\
 \bottomrule
-\end{longtable}
+\multicolumn{6}{l}{\rule{0pt}{1em}\textsuperscript{1} Mean (SD); n (\%)}\\
+\multicolumn{6}{l}{\rule{0pt}{1em}\textsuperscript{2} Wilcoxon rank sum test; Pearson's Chi-squared test}\\
+\multicolumn{6}{l}{\rule{0pt}{1em}\textsuperscript{3} False discovery rate correction for multiple testing}\\
+\end{tabular}}
+\end{table}
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-extrafont}{}}%
+Winston Chang. (2014). \emph{Extrafont: Tools for using fonts}. Retrieved from \url{https://CRAN.R-project.org/package=extrafont}
+
 \leavevmode\vadjust pre{\hypertarget{ref-worthingtonScaleDevelopmentResearch2006}{}}%
@@
 \end{table}
-\end{appendix}
-
-\clearpage
-\makeatletter
-\efloat@restorefloats
-\makeatother
-
-\begin{appendix}
-\section{}
-\textbf{Disclaimer}: This is a non-public version of LEBA (dated \today)
-and still a work in progress. Please do not distribute!
-
-LEBA captures light exposure-related behaviours on a 5 point Likert type
-scale ranging from 1 to 5 (Never/Does not apply/I don't know = 1; Rarely
-= 2; Sometimes = 3; Often = 4; Always = 5). The score of each factor is
-calculated by the summation of scores of items belonging to the
-corresponding factor. The following instruction is given before
-displaying the items: ``Please indicate how often you performed the
-following behaviours in the past 4 weeks.''
-
-\newpage
-
-\blandscape
-
-\hypertarget{leba-long-form-23-items}{%
-\section{LEBA Long Form (23 Items)}\label{leba-long-form-23-items}}
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.05}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.27}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.34}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.08}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.11}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.07}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.08}}@{}}
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Items
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Never/Does not apply/I don't know
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Rarely
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Sometimes
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Often
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Always
-\end{minipage} \\
-\midrule
-\endhead
-1 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
-indoors during the day. & & & & & \\
-2 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
-outdoors during the day. & & & & & \\
-3 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
-within 1 hour before attempting to fall asleep. & & & & & \\
-4 & I spend 30 minutes or less per day (in total) outside. & & & & & \\
-5 & I spend between 1 and 3 hours per day (in total) outside. & & & &
-& \\
-6 & I spend between 30 minutes and 1 hour per day (in total) outside. &
-& & & & \\
-7 & I spend more than 3 hours per day (in total) outside. & & & & & \\
-8 & I spend as much time outside as possible. & & & & & \\
-9 & I go for a walk or exercise outside within 2 hours after waking up.
-& & & & & \\
-10 & I use my mobile phone within 1 hour before attempting to fall
-asleep. & & & & & \\
-11 & I look at my mobile phone screen immediately after waking up. & & &
-& & \\
-12 & I check my phone when I wake up at night. & & & & & \\
-13 & I look at my smartwatch within 1 hour before attempting to fall
-asleep. & & & & & \\
-14 & I look at my smartwatch when I wake up at night. & & & & & \\
-15 & I dim my mobile phone screen within 1 hour before attempting to
-fall asleep. & & & & & \\
-16 & I use a blue-filter app on my computer screen within 1 hour before
-attempting to fall asleep. & & & & & \\
-17 & I use as little light as possible when I get up during the night. &
-& & & & \\
-18 & I dim my computer screen within 1 hour before attempting to fall
-asleep. & & & & & \\
-19 & I use tunable lights to create a healthy light environment. & & & &
-& \\
-20 & I use LEDs to create a healthy light environment. & & & & & \\
-21 & I use a desk lamp when I do focused work. & & & & & \\
-22 & I use an alarm with a dawn simulation light. & & & & & \\
-23 & I turn on the lights immediately after waking up. & & & & & \\
-\bottomrule
-\end{longtable}
-
-\elandscape
-
-\newpage
-
-\blandscape
-
-\hypertarget{latent-structure-reliability-and-structural-validity}{%
-\subsection{Latent Structure, Reliability and Structural
-Validity}\label{latent-structure-reliability-and-structural-validity}}
-
-The long form of LEBA consists 23 items with five factors.
-
-Factor names
-
-Items
-
-Reliability Coefficients
-
-McDonald's Omega
-
-(N=262)
-
-Reliability Coefficients
-
-Cronbach's alpha
-
-F1: Wearing blue light filters
-
-1-3
-
-.93
-
-.90
-
-F2: Spending time outdoors
-
-4-9 (Item 4 is reversed)
-
-.80
-
-.78
-
-F3: Using phone and smartwatch in bed
-
-10-14
-
-.61
-
-.62
-
-F4: Using light before bedtime
-
-15-18
-
-.72
-
-.62
-
-F5: Using light in the morning and during daytime
-
-19-23
-
-.45
-
-.41
-
-.73(Total scale)
-
-LEBA -long form showed satisfactory structural validity (CFI =.97; TLI =
-.96; RMSEA = .05{[}.04-.06, 90\% CI{]}; SRMR = .09).
-
-\hypertarget{how-to-cite}{%
-\subsection{How to cite:}\label{how-to-cite}}
-
-\elandscape
-
-\newpage
-
-\blandscape
-
-\hypertarget{leba-short-form-17-items}{%
-\section{LEBA Short Form (17 Items)}\label{leba-short-form-17-items}}
-
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.05}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.27}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.34}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.08}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.11}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.07}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.08}}@{}}
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Short Form (17 Items)
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Never/Does not apply/I don't know
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Rarely
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Sometimes
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Often
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Always
-\end{minipage} \\
-\midrule
-\endhead
-01 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
-indoors during the day. & & & & & \\
-02 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
-outdoors during the day. & & & & & \\
-03 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
-within 1 hour before attempting to fall asleep. & & & & & \\
-04 & I spend 30 minutes or less per day (in total) outside. & & & & & \\
-05 & I spend between 1 and 3 hours per day (in total) outside. & & & &
-& \\
-06 & I spend more than 3 hours per day (in total) outside. & & & & & \\
-07 & I spend as much time outside as possible. & & & & & \\
-08 & I go for a walk or exercise outside within 2 hours after waking up.
-& & & & & \\
-09 & I use my mobile phone within 1 hour before attempting to fall
-asleep. & & & & & \\
-10 & I look at my mobile phone screen immediately after waking up. & & &
-& & \\
-11 & I check my phone when I wake up at night. & & & & & \\
-12 & I dim my mobile phone screen within 1 hour before attempting to
-fall asleep. & & & & & \\
-13 & I use a blue-filter app on my computer screen within 1 hour before
-attempting to fall asleep. & & & & & \\
-14 & I dim my computer screen within 1 hour before attempting to fall
-asleep. & & & & & \\
-15 & I use tunable lights to create a healthy light environment. & & & &
-& \\
-16 & I use LEDs to create a healthy light environment. & & & & & \\
-17 & I use an alarm with a dawn simulation light. & & & & & \\
-\bottomrule
-\end{longtable}
-
-\elandscape
-
-\newpage
-
-\blandscape
-
-\hypertarget{latent-structure-reliability-and-structural-validity-1}{%
-\subsection{Latent Structure, Reliability and Structural
-Validity}\label{latent-structure-reliability-and-structural-validity-1}}
-
-The short form of LEBA consists 23 items with five factors.
-
-\begin{longtable}[]{@{}ll@{}}
-\toprule
-Factor names & Items \\
-\midrule
-\endhead
-\textbf{F1: Wearing blue light filters} & 1-3 \\
-\textbf{F2: Spending time outdoors} & 4-8 (Item 4 is reversed) \\
-\textbf{F3: Using phone and smart-watch in bed} & 9-11 \\
-\textbf{F4: Using light before bedtime} & 12-14 \\
-\textbf{F5: Using light in the morning and during daytime} & 15-17 \\
-\bottomrule
-\end{longtable}
-
-\hypertarget{how-to-cite-1}{%
-\subsection{How to cite:}\label{how-to-cite-1}}
-
-\elandscape
-\end{appendix}
-
-\clearpage
-\makeatletter
-\efloat@restorefloats
-\makeatother
-
-\begin{appendix}
-\section{}
-\hypertarget{supplimentary-analysis}{%
-\subsection{Supplimentary Analysis}\label{supplimentary-analysis}}
+
+\hypertarget{factor-analysis-with-unmerged-response-option}{%
+\section{Factor Analysis with Unmerged Response
+Option}\label{factor-analysis-with-unmerged-response-option}}
 
@@
 
-{\centering \includegraphics[width=1\linewidth,height=1\textheight]{manuscript_files/figure-latex/facIdFigAppB-1}
+{\centering \includegraphics{manuscript_files/figure-latex/facIdFigAppB-1}
 
@@
 \end{longtable}
+
+\begin{figure}
+
+{\centering \includegraphics{manuscript_files/figure-latex/EFAResidualsAppB-1}
+
+}
+
+\caption{ Histogram of residulas:  five-factor solution}\label{fig:EFAResidualsAppB}
+\end{figure}
 \end{appendix}
 
+\clearpage
+\makeatletter
+\efloat@restorefloats
+\makeatother
+
+\begin{appendix}
+\section{}
+\textbf{Disclaimer}: This is a non-public version of LEBA (dated \today)
+and still a work in progress. Please do not distribute!
+
+LEBA captures light exposure-related behaviours on a 5 point Likert type
+scale ranging from 1 to 5 (Never/Does not apply/I don't know = 1; Rarely
+= 2; Sometimes = 3; Often = 4; Always = 5). The score of each factor is
+calculated by the summation of scores of items belonging to the
+corresponding factor. The following instruction is given before
+displaying the items: ``Please indicate how often you performed the
+following behaviours in the past 4 weeks.''
+
+\newpage
+
+\blandscape
+
+\hypertarget{leba-long-form-23-items}{%
+\section{LEBA Long Form (23 Items)}\label{leba-long-form-23-items}}
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.05}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.27}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.34}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.08}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.11}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.07}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.08}}@{}}
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Items
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Never/Does not apply/I don't know
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Rarely
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Sometimes
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Often
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Always
+\end{minipage} \\
+\midrule
+\endhead
+1 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
+indoors during the day. & & & & & \\
+2 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
+outdoors during the day. & & & & & \\
+3 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
+within 1 hour before attempting to fall asleep. & & & & & \\
+4 & I spend 30 minutes or less per day (in total) outside. & & & & & \\
+5 & I spend between 1 and 3 hours per day (in total) outside. & & & &
+& \\
+6 & I spend between 30 minutes and 1 hour per day (in total) outside. &
+& & & & \\
+7 & I spend more than 3 hours per day (in total) outside. & & & & & \\
+8 & I spend as much time outside as possible. & & & & & \\
+9 & I go for a walk or exercise outside within 2 hours after waking up.
+& & & & & \\
+10 & I use my mobile phone within 1 hour before attempting to fall
+asleep. & & & & & \\
+11 & I look at my mobile phone screen immediately after waking up. & & &
+& & \\
+12 & I check my phone when I wake up at night. & & & & & \\
+13 & I look at my smartwatch within 1 hour before attempting to fall
+asleep. & & & & & \\
+14 & I look at my smartwatch when I wake up at night. & & & & & \\
+15 & I dim my mobile phone screen within 1 hour before attempting to
+fall asleep. & & & & & \\
+16 & I use a blue-filter app on my computer screen within 1 hour before
+attempting to fall asleep. & & & & & \\
+17 & I use as little light as possible when I get up during the night. &
+& & & & \\
+18 & I dim my computer screen within 1 hour before attempting to fall
+asleep. & & & & & \\
+19 & I use tunable lights to create a healthy light environment. & & & &
+& \\
+20 & I use LEDs to create a healthy light environment. & & & & & \\
+21 & I use a desk lamp when I do focused work. & & & & & \\
+22 & I use an alarm with a dawn simulation light. & & & & & \\
+23 & I turn on the lights immediately after waking up. & & & & & \\
+\bottomrule
+\end{longtable}
+
+\elandscape
+
+\newpage
+
+\blandscape
+
+\hypertarget{latent-structure-reliability-and-structural-validity}{%
+\subsection{Latent Structure, Reliability and Structural
+Validity}\label{latent-structure-reliability-and-structural-validity}}
+
+The long form of LEBA consists 23 items with five factors.
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.33}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.15}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.26}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.26}}@{}}
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+Factor names
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Items
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Reliability Coefficients: McDonald's Omega
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Reliability Coefficients: Cronbach's alpha
+\end{minipage} \\
+\midrule
+\endhead
+\textbf{F1: Wearing blue light filters} & 1-3 & .93 & .90 \\
+F2: Spending time outdoors & 4-9 (Item 4 is reversed) & .80 & .78 \\
+\textbf{F3: Using phone and smartwatch in bed} & 10-14 & .61 & .62 \\
+\textbf{F4: Using light before bedtime} & 15-18 & .72 & .62 \\
+\textbf{F5: Using light in the morning and during daytime} & 19-23 & .45
+& .41 \\
+& & .73(Total scale) & \\
+\bottomrule
+\end{longtable}
+
+LEBA -long form showed satisfactory structural validity (CFI =.97; TLI =
+.96; RMSEA = .05{[}.04-.06, 90\% CI{]}; SRMR = .09).
+
+\hypertarget{how-to-cite}{%
+\subsection{How to cite:}\label{how-to-cite}}
+
+\elandscape
+
+\newpage
+
+\blandscape
+
+\hypertarget{leba-short-form-17-items}{%
+\section{LEBA Short Form (17 Items)}\label{leba-short-form-17-items}}
+
+\begin{longtable}[]{@{}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.05}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.27}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.34}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.08}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.11}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.07}}
+  >{\raggedright\arraybackslash}p{(\columnwidth - 12\tabcolsep) * \real{0.08}}@{}}
+\toprule
+\begin{minipage}[b]{\linewidth}\raggedright
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Short Form (17 Items)
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Never/Does not apply/I don't know
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Rarely
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Sometimes
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Often
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
+Always
+\end{minipage} \\
+\midrule
+\endhead
+01 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
+indoors during the day. & & & & & \\
+02 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
+outdoors during the day. & & & & & \\
+03 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses
+within 1 hour before attempting to fall asleep. & & & & & \\
+04 & I spend 30 minutes or less per day (in total) outside. & & & & & \\
+05 & I spend between 1 and 3 hours per day (in total) outside. & & & &
+& \\
+06 & I spend more than 3 hours per day (in total) outside. & & & & & \\
+07 & I spend as much time outside as possible. & & & & & \\
+08 & I go for a walk or exercise outside within 2 hours after waking up.
+& & & & & \\
+09 & I use my mobile phone within 1 hour before attempting to fall
+asleep. & & & & & \\
+10 & I look at my mobile phone screen immediately after waking up. & & &
+& & \\
+11 & I check my phone when I wake up at night. & & & & & \\
+12 & I dim my mobile phone screen within 1 hour before attempting to
+fall asleep. & & & & & \\
+13 & I use a blue-filter app on my computer screen within 1 hour before
+attempting to fall asleep. & & & & & \\
+14 & I dim my computer screen within 1 hour before attempting to fall
+asleep. & & & & & \\
+15 & I use tunable lights to create a healthy light environment. & & & &
+& \\
+16 & I use LEDs to create a healthy light environment. & & & & & \\
+17 & I use an alarm with a dawn simulation light. & & & & & \\
+\bottomrule
+\end{longtable}
+
+\elandscape
+
+\newpage
+
+\blandscape
+
+\hypertarget{latent-structure-reliability-and-structural-validity-1}{%
+\subsection{Latent Structure, Reliability and Structural
+Validity}\label{latent-structure-reliability-and-structural-validity-1}}
+
+The short form of LEBA consists 23 items with five factors.
+
+\begin{longtable}[]{@{}ll@{}}
+\toprule
+Factor names & Items \\
+\midrule
+\endhead
+\textbf{F1: Wearing blue light filters} & 1-3 \\
+\textbf{F2: Spending time outdoors} & 4-8 (Item 4 is reversed) \\
+\textbf{F3: Using phone and smart-watch in bed} & 9-11 \\
+\textbf{F4: Using light before bedtime} & 12-14 \\
+\textbf{F5: Using light in the morning and during daytime} & 15-17 \\
+\bottomrule
+\end{longtable}
+
+\hypertarget{how-to-cite-1}{%
+\subsection{How to cite:}\label{how-to-cite-1}}
+
+\elandscape
+\end{appendix}
+
 \end{document}

### 2021-11-11 install_packages.R

@@ -1,0 +1,74 @@
+
+#maintenance 
+install.packages("devtools")
+install.packages("remotes")
+install.packages("usethis")
+
+#APA Style Manuscript template
+devtools::install_github("crsh/papaja", force =T)
+
+#APA format number
+install.packages("MOTE")
+
+#LaTex Friendly Table
+install.packages("kableExtra")
+
+#gt family
+remotes::install_github("jthomasmock/gtExtras")
+install.packages("gt")
+#remotes::install_github("ddsjoberg/gtsummary")
+install.packages("gtsummary")
+
+# IRT
+install.packages("mirt")
+
+
+#Likert data
+install.packages("likert")
+install.packages("kutils")
+
+
+
+### Psychomterics
+#devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
+##SEM
+install.packages("lavaan")
+install.packages("semPlot")
+install.packages("semTable")
+install.packages("semTools")
+
+## Correlation
+install.packages("ggcorrplot")
+
+##Descriptives and EFA
+install.packages("psych")
+install.packages("dlookr")
+install.packages("qgraph")
+install.packages("tidyverse")
+install.packages("paran")
+install.packages("EFA.MRFA")
+install.packages("VIM")#Missing data
+
+
+
+#Ploting and diagram
+install.packages("DiagrammeR")
+#devtools::install_github('rich-iannone/DiagrammeR')
+install.packages("DiagrammeRsvg")
+install.packages("ggplot2")
+install.packages("cowplot")
+install.packages("rsvg")
+
+
+#Addons
+devtools::install_github("crsh/citr")
+install.packages("questionr")
+
+#Others
+install.packages("magick")
+
+#fonts
+install.packages("extrafont")
+extrafont::fonttable()
+extrafont::loadfonts()
+extrafont:::fonttable_file()

### 2021-11-12 Supplymentary.Rmd
* renv is removed. pacman is used install packages

@@
 #Preparing the EFA table
-library(data.table)
-fa_table <- function(x, cut) {
-  #get sorted loadings
-  loadings <- fa.sort(x)$loadings %>% round(2)
-  #supress loadings
-  loadings[abs(loadings) < abs(cut)] <- ""
-  #get additional info
-  add_info <- cbind(x$communality, 
-                    x$uniquenesses,
-                    x$complexity) %>%
-    # make it a data frame
-    as.data.frame() %>%
-    # column names
-    rename("Communality" = V1,
-           "Uniqueness" = V2,
-           "Complexity" = V3) %>%
-    #get the item names from the vector
-    rownames_to_column("item")
-  #build table
-  loadings <- loadings %>%
-    unclass() %>%
-    as.data.frame() %>%
-    rownames_to_column("item") %>%
-    left_join(add_info) %>%
-    mutate(across(where(is.numeric), round, 3)) %>% 
-    as.data.frame()
-  variance <- x$Vaccounted %>% 
-  as.data.frame()%>% 
-  round(2)
-  loadings <- rbind(setDT(loadings), setDT(variance[2,]), fill=TRUE)
 
-}
-
-efa.table <- fa_table(fa.5F.4,.3) 
-nr <- nrow(efa.table)
-efa.table[nr, 1] <- "% of Variance"
+efa.table <- tabledown::fac.tab(fa.5F.4,.3)
 

### 2021-11-12 Supplymentary.tex
* Successfully Knitting with appendix but formating is not right
* Table 2 is now formatted * Polygon edge not found error is solved.
* installation script is uploaded
* renv is removed. pacman is used install packages

@@
 
-\caption{\label{tab:MinResTab}Factor loadings and communality of the retained items(Minmum Residual)}
+\caption{\label{tab:MinResTab-31}Factor loadings and communality of the retained items(Minmum Residual)}
 
@@
 
-\caption{\label{tab:sixFacTab}Factor loadings and communality of the retained items(six factor)}
+\caption{\label{tab:sixFacTab-33}Factor loadings and communality of the retained items(six factor)}
 
@@
 
-\caption{\label{tab:tabDesAppB}Descriptive Statistics for Unmerged response options}
+\caption{\label{tab:tabDesAppB-37}Descriptive Statistics for Unmerged response options}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-1}
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-39-1}
 
@@
 
-\caption{Correlation plot of the items}(\#fig:figCorAppB)
+\caption{Correlation plot of the items}(\#fig:figCorAppB-39)
 \end{figure}
@@
 
-{\centering \includegraphics[width=1\linewidth,height=1\textheight]{manuscript_files/figure-latex/facIdFigAppB-1}
+{\centering \includegraphics{manuscript_files/figure-latex/facIdFigAppB-43-1}
 
@@
 
-\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}(\#fig:facIdFigAppB)
+\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}(\#fig:facIdFigAppB-43)
 \end{figure}
@@
 
-\caption{\label{tab:EFATableAppB}Factor loadings and communality of the retained items [Unmerged Responses]}
+\caption{\label{tab:EFATableAppB-46}Factor loadings and communality of the retained items [Unmerged Responses]}
 
@@
 \midrule
-item19 & 0.99 &  &  &  &  & 1.01 & -0.01 & 1.06\\
-item20 & 0.91 &  &  &  &  & 0.87 & 0.13 & 1.11\\
-item18 & 0.82 &  &  &  &  & 0.71 & 0.29 & 1.12\\
-item21 & 0.8 &  &  &  &  & 0.68 & 0.32 & 1.16\\
-item4 & 0.47 &  &  &  &  & 0.25 & 0.75 & 1.30\\
-item11 &  & 0.83 &  &  &  & 0.69 & 0.31 & 1.01\\
-item10 &  & 0.81 &  &  &  & 0.67 & 0.33 & 1.03\\
-item12 &  & 0.56 &  &  &  & 0.37 & 0.63 & 1.37\\
-item8 &  & -0.44 &  &  &  & 0.21 & 0.79 & 1.11\\
-item7 &  & 0.42 &  &  &  & 0.23 & 0.77 & 1.61\\
-item9 &  & 0.33 &  &  &  & 0.12 & 0.88 & 1.10\\
-item16 &  &  & 0.95 &  &  & 0.95 & 0.05 & 1.10\\
-item17 &  &  & 0.74 &  &  & 0.60 & 0.41 & 1.17\\
-item36 & 0.3 &  & 0.73 &  &  & 0.65 & 0.35 & 1.43\\
-item3 &  &  &  & 0.85 &  & 0.75 & 0.25 & 1.05\\
-item27 &  &  &  & 0.78 &  & 0.62 & 0.38 & 1.03\\
-item40 &  &  &  & 0.71 &  & 0.51 & 0.49 & 1.05\\
-item35 &  &  &  &  & 0.58 & 0.35 & 0.65 & 1.09\\
-item48 &  &  &  &  & 0.57 & 0.35 & 0.65 & 1.14\\
-item33 &  &  &  &  & 0.55 & 0.32 & 0.68 & 1.08\\
-item47 &  &  &  &  & 0.52 & 0.29 & 0.71 & 1.19\\
-item44 &  &  &  &  & 0.45 & 0.22 & 0.78 & 1.15\\
-item31 &  &  &  &  & 0.41 & 0.21 & 0.79 & 1.48\\
-item38 &  &  &  &  & 0.33 & 0.13 & 0.87 & 1.32\\
-\% of Variance & 0.15 & 0.09 & 0.09 & 0.08 & 0.08 & NA & NA & NA\\
+item19 & 0.99 &  &  &  &  & 1.007 & -0.007 & 1.058\\
+item20 & 0.91 &  &  &  &  & 0.874 & 0.126 & 1.114\\
+item18 & 0.82 &  &  &  &  & 0.711 & 0.289 & 1.123\\
+item21 & 0.8 &  &  &  &  & 0.683 & 0.317 & 1.163\\
+item4 & 0.47 &  &  &  &  & 0.25 & 0.75 & 1.298\\
+item11 &  & 0.83 &  &  &  & 0.687 & 0.313 & 1.007\\
+item10 &  & 0.81 &  &  &  & 0.67 & 0.33 & 1.031\\
+item12 &  & 0.56 &  &  &  & 0.371 & 0.629 & 1.374\\
+item8 &  & -0.44 &  &  &  & 0.206 & 0.794 & 1.106\\
+item7 &  & 0.42 &  &  &  & 0.226 & 0.774 & 1.614\\
+item9 &  & 0.33 &  &  &  & 0.115 & 0.885 & 1.1\\
+item16 &  &  & 0.95 &  &  & 0.946 & 0.054 & 1.097\\
+item17 &  &  & 0.74 &  &  & 0.595 & 0.405 & 1.168\\
+item36 & 0.3 &  & 0.73 &  &  & 0.653 & 0.347 & 1.431\\
+item3 &  &  &  & 0.85 &  & 0.746 & 0.254 & 1.048\\
+item27 &  &  &  & 0.78 &  & 0.624 & 0.376 & 1.028\\
+item40 &  &  &  & 0.71 &  & 0.512 & 0.488 & 1.05\\
+item35 &  &  &  &  & 0.58 & 0.351 & 0.649 & 1.091\\
+item48 &  &  &  &  & 0.57 & 0.354 & 0.646 & 1.144\\
+item33 &  &  &  &  & 0.55 & 0.32 & 0.68 & 1.085\\
+item47 &  &  &  &  & 0.52 & 0.294 & 0.706 & 1.186\\
+item44 &  &  &  &  & 0.45 & 0.216 & 0.784 & 1.145\\
+item31 &  &  &  &  & 0.41 & 0.206 & 0.794 & 1.477\\
+item38 &  &  &  &  & 0.33 & 0.129 & 0.871 & 1.317\\
+\% of Variance & 0.15 & 0.09 & 0.09 & 0.08 & 0.08 &  &  & \\
 \bottomrule
@@
 \end{longtable}
+
+\begin{figure}
+
+{\centering \includegraphics{manuscript_files/figure-latex/EFAResidualsAppB-47-1}
+
+}
+
+\caption{ Histogram of residulas:  five-factor solution}(\#fig:EFAResidualsAppB-47)
+\end{figure}
 \end{appendix}

### 2021-11-12 manuscript.Rmd
* renv is removed. pacman is used install packages

@@
 
-```{r depMan, include=FALSE}
-#renv::init()
-#renv::snapshot()
-#renv::status()
-renv::restore()
+```{r pacman, include=FALSE}
+#You need to run this chunck 1X in your system 
+#install.packages("pacman")
+pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem)
+pacman::p_install_gh("jthomasmock/gtExtras")
+pacman::p_install_gh("crsh/papaja","crsh/citr", "masiraji/tabledown")
+pacman::p_install_gh("masiraji/tabledown")
+
 ```
@@
 #seperating naming and  reducing data for descriptive Table 
-desctable.data <- select(descriptives.data, c(listdescVars,
+desctable.data <- dplyr::select(descriptives.data, c(listdescVars,
                           IncludedInCFA))
@@
 # calculate summary stats & create data for the histogram and density plot
-  summarise(
+  dplyr::summarise(
     nr = n(),
@@
 ```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('Supplymentary.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('instrument.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('Supplymentary.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('instrument.Rmd')
+```

### 2021-11-12 Supplymentary.tex
Table 1 is formatted

@@
 
-\caption{\label{tab:MinResTab-31}Factor loadings and communality of the retained items(Minmum Residual)}
+\caption{\label{tab:MinResTab-33}Factor loadings and communality of the retained items(Minmum Residual)}
 
@@
 
-\caption{\label{tab:sixFacTab-33}Factor loadings and communality of the retained items(six factor)}
+\caption{\label{tab:sixFacTab-35}Factor loadings and communality of the retained items(six factor)}
 
@@
 
-\caption{\label{tab:tabDesAppB-37}Descriptive Statistics for Unmerged response options}
+\caption{\label{tab:tabDesAppB-39}Descriptive Statistics for Unmerged response options}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-39-1}
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-41-1}
 
@@
 
-\caption{Correlation plot of the items}(\#fig:figCorAppB-39)
+\caption{Correlation plot of the items}(\#fig:figCorAppB-41)
 \end{figure}
@@
 
-{\centering \includegraphics{manuscript_files/figure-latex/facIdFigAppB-43-1}
+{\centering \includegraphics{manuscript_files/figure-latex/facIdFigAppB-45-1}
 
@@
 
-\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}(\#fig:facIdFigAppB-43)
+\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}(\#fig:facIdFigAppB-45)
 \end{figure}
@@
 
-\caption{\label{tab:EFATableAppB-46}Factor loadings and communality of the retained items [Unmerged Responses]}
+\caption{\label{tab:EFATableAppB-48}Factor loadings and communality of the retained items [Unmerged Responses]}
 
@@
 
-{\centering \includegraphics{manuscript_files/figure-latex/EFAResidualsAppB-47-1}
+{\centering \includegraphics{manuscript_files/figure-latex/EFAResidualsAppB-49-1}
 
@@
 
-\caption{ Histogram of residulas:  five-factor solution}(\#fig:EFAResidualsAppB-47)
+\caption{ Histogram of residulas:  five-factor solution}(\#fig:EFAResidualsAppB-49)
 \end{figure}

### 2021-11-12 manuscript.Rmd
Table 1 is formatted

@@
 #install.packages("pacman")
-pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem)
+pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl)
 pacman::p_install_gh("jthomasmock/gtExtras")
@@
 library(tabledown)
-
+library(readxl)
 r_refs("references.bib")
@@
 
-+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| Name                                                              | Authors                  | Description                                                                                                                                                  | Relevant Items                       | Adaptations |
-+===================================================================+==========================+==============================================================================================================================================================+======================================+=============+
-| Visual Light Sensitivity Questionnaire-8                          | [@verriotto2017new]      | Eight-question survey to assess the presence and severity of photosensitivity symptoms                                                                       | All items                            |             |
-+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| Office Light Survey                                               | [@eklund1996development] | Multi-item questionnaire to assess electrical lighting environment in office                                                                                 |                                      |             |
-+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| Harvard Light Exposure Assessment Questionnaire                   | [@bajaj2011validation]   | Self-administered semi-quantitative light questionnaire                                                                                                      | All Items                            |             |
-+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| Hospital Lighting Survey                                          | [@dianat2013objective]   | 23 items questionnaire to assess light environment in a hospital                                                                                             |                                      |             |
-+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| Morningness-Eveningness Questionnaire                             | [@horne1976self]         | 19 items questionnaire to understand your body clock                                                                                                         |                                      |             |
-+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| Munich Chronotype Questionnaire (MCTQ)                            | [@roenneberg2003life]    | 17 items questionnaire to understand individuals phase of entrainment                                                                                        |                                      |             |
-+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| Assessment of Sleep Environment                                   | [@Olivier.2016]       | 13 items questionnaire measuring your sleep environment quality                                                                                              |                                      |             |
-+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| The Pittsburgh Sleep Quality Index (PSQI)                         | [@buysse1989pittsburgh]  | 9 items inventory to measure sleep quality and sleeping pattern                                                                                              |                                      |             |
-+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| Self-Rating of Biological Rhythm Disorder for Adolescents (SBRDA) | [@Xie.2021]           | 29 items questionnaire assessing four dimensions of biological rhythm disorder in adolescents (digital media use, sleep, eating habits, and activity)        | Items 3., 22., 23., 24., 25.
-and 29.
-|             |
-+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-| Photosensitivity Assessment Questionnaire (PAQ)                   | [@Wu.2017]            | 16 dichotomous (yes/no) items questionnaire to assess "photophobia" and "photophilia", giving two final scores of "photophobic" and "photophilic" behaviours | All items                            |             |
-+-------------------------------------------------------------------+--------------------------+--------------------------------------------------------------------------------------------------------------------------------------------------------------+--------------------------------------+-------------+
-
-: Existing related Scales
+```{r}
+relevant.scale.data <- readxl::read_excel("Table_raw/relevant_scales.xlsx")
+```
+
+```{r}
+kable(relevant.scale.data,booktabs = T)
+```
 
@@
 -   Sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration (version for adults and adolescents) [@roenneberg2003life]
--   Sleep environment [@Olivier.2016\
+-   Sleep environment [@Olivier.2016]
 -   Meal timing & caffeine consumption [custom items]
@@
 CFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`], with an overall mean of ~ `r round(mean(desctable.data$slypos_demographics_age), 0)` years of age [Overall: *M* = `r mean(desctable.data$slypos_demographics_age)`, *SD* = `r sd(desctable.data$slypos_demographics_age)`; EFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
+CFA Sample"])`], with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 0)` years of age [Overall: *M* = `r mean(desctable.data$slypos_demographics_age)`, *SD* = `r sd(desctable.data$slypos_demographics_age)`; EFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
 EFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
@@
 We used a combination factor identification method including scree plot[@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method[@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
-Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018] We also conducted psychometric analysis on non-merged response options data (supplementary analysis) and rejected the latent structure obtained as the factors were less interpretable.
+Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018] We also conducted psychometric analysis on non-merged response options data (supplementary analysis) and rejected the latent structure obtained as the factors were less interpretable.
 
@@
 Our data violated both univariate normality (Shapiro-Wilk statistics; [@shapiroAnalysisVarianceTest1965]) and multivariate normality assumptions (Marida's test;[@mardiaMeasuresMultivariateSkewness1970]).
-Multivariate skew was = `r printnum(mardia$b1p)` (p \<0.001) and multivariate kurtosis was = `r printnum(mardia$b2p)` (p \<0.001).
+Multivariate skew was = `r printnum(mardia$b1p)` (p <0.001) and multivariate kurtosis was = `r printnum(mardia$b2p)` (p <0.001).
 Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018].
-Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p \< .001\] indicated the correlations between items are adequate for the EFA.
+Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001] indicated the correlations between items are adequate for the EFA.
 However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than .30.
@@
 With initial 48 items we conducted three rounds of EFA gradually discarded problematic items.
-(cross-loading items and poor factor loading (\<.30) items).
+(cross-loading items and poor factor loading (<.30) items).
 Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 [@brownConfirmatoryFactorAnalysis2015], all factor-loading higher than .30 and no cross-loading greater than .30.
@@
 
-In the five-factor solution, the first factor contained three items and explained `r apa(var1,2,F)`% of the total variance with a satisfactory internal reliability coefficient ($\alpha$ = `r apa(F1.alpha,2,F)`).
+In the five-factor solution, the first factor contained three items and explained `r apa(var1,2,F)`% of the total variance with a satisfactory internal reliability coefficient ($alpha$ = `r apa(F1.alpha,2,F)`).
 All the items in this factor stemmed from the individual's preference to use blue light filters in different light environments.
-The second factor contained six items and explained `r apa(var2,2,F)`% of the total variance with a satisfactory internal reliability coefficient ($\alpha$ = `r apa(F2.alpha,2,F)`).
+The second factor contained six items and explained `r apa(var2,2,F)`% of the total variance with a satisfactory internal reliability coefficient ($alpha$ = `r apa(F2.alpha,2,F)`).
 Items under this factor commonly investigate an individual's hours spent outdoor.
@@
 Items under this factor dealt with the specific behaviors pertaining to sleep.
-The internal consistency reliability coefficient was, $\alpha$ = `r apa(F3.alpha,2,F)`.
-The fourth factor contained five items and explained `r apa(var4,2,F)`% of the total variance with an internal consistency coefficient, $\alpha$ = `r apa(F4.alpha,2,F)`.
+The internal consistency reliability coefficient was, $alpha$ = `r apa(F3.alpha,2,F)`.
+The fourth factor contained five items and explained `r apa(var4,2,F)`% of the total variance with an internal consistency coefficient, $alpha$ = `r apa(F4.alpha,2,F)`.
 These five items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time.
@@
 This factor tried to measure an individual's behavior lead by the awareness of light's influence on health.
-However, this factor showed unsatisfactory internal consistency reliability ($\alpha$ = `r apa(F5.alpha,2,F)`).
+However, this factor showed unsatisfactory internal consistency reliability ($alpha$ = `r apa(F5.alpha,2,F)`).
 It is essential to attain a balance between psychometric properties and interpretability of the common themes when exploring the latent structure.
@@
 Subsequently, we judged the model fit based on the comparative fit indices: CFI, TLI and parsimony fit index-RMSEA.
-Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`,\[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI\]) with two imposed equity constrain on item pairs 32-33 and 19-17 .
+Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`,[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 and 19-17 .
 However SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`).
-Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`\[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI\]) and SRMR value (SRMR = `r apa(fit.2[10],2,F)`) was also close to the suggestions of @huCutoffCriteriaFit1999.
+Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR value (SRMR = `r apa(fit.2[10],2,F)`) was also close to the suggestions of @huCutoffCriteriaFit1999.
 Since reliability coefficient Cronbach's alpha tends to mis-measure reliability for multidimensional construct [@sijtsma2009use] we report Mcdonald's omega(total) as the internal consistency reliability coefficient.
@@
 IRT complements the conventional classical test theory-based analysis by gathering information on item discrimination and item difficulty[@bakerBasicsItemResponse2017].
-Here, an item's quality is judged based on item information in relation to participants' latent trait level ($\theta$).
+Here, an item's quality is judged based on item information in relation to participants' latent trait level ($theta$).
 We gathered evidence on item quality by fitting each factor of LEBA with the graded response model (\@ref(tab:IRTparameters) to the combined EFA sample and CFA sample (n =690).
 Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait, and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
-Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information \<.2) to develop the short form of LEBA.
-@bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70.
+Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information <.2) to develop the short form of LEBA.
+@bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70.
 Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), low ( 5 items) indicating a good range of discrimination along the latent trait.
@@
 As we treated each factor of LEBA as an unidmensional construct we obtain 5 TICs.
-These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum (($\theta$)).
-Also the amount of information changed rather steadily with the change of ($\theta$).
+These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum (($theta$)).
+Also the amount of information changed rather steadily with the change of ($theta$).
 Thus we conferred the LEBA scale (except blue filter) estimated the light exposure related behavior with precision near the center of trait continuum [@bakerBasicsItemResponse2017] which is sufficient to discriminate between latent trait measured by the each factor.
@@
 We estimated the person fit statistics using standardized fit index Zh statistics [@drasgow1985appropriateness].
-Zh \< -2 should be considered as a misfit.
+Zh < -2 should be considered as a misfit.
 Fig indicates that Zh is larger than -2 for most participants, suggesting a good fit of the selected IRT models.
@@
 ```
-
 ```{r echo = FALSE, results = 'asis', cache = FALSE}

### 2021-11-12 manuscript.tex
Table 1 is formatted

@@
 \urlstyle{same} % disable monospaced font for URLs
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
 \usepackage{graphicx}
@@
 
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.22}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.09}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.52}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.13}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.05}}@{}}
-\caption{Existing related Scales}\tabularnewline
+\begin{tabular}{lllll}
 \toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-Name
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Authors
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Description
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Relevant Items
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Adaptations
-\end{minipage} \\
+Name & Author & Description & Relevant Items & Adaptations\\
 \midrule
-\endfirsthead
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-Name
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Authors
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Description
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Relevant Items
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Adaptations
-\end{minipage} \\
-\midrule
-\endhead
-Visual Light Sensitivity Questionnaire-8 & (Verriotto et al., 2017) & Eight-question survey to assess the presence and severity of photosensitivity symptoms & All items & \\
-Office Light Survey & (Eklund \& Boyce, 1996) & Multi-item questionnaire to assess electrical lighting environment in office & & \\
-Harvard Light Exposure Assessment Questionnaire & (Bajaj, Rosner, Lockley, \& Schernhammer, 2011) & Self-administered semi-quantitative light questionnaire & All Items & \\
-Hospital Lighting Survey & (Dianat, Sedghi, Bagherzade, Jafarabadi, \& Stedmon, 2013) & 23 items questionnaire to assess light environment in a hospital & & \\
-Morningness-Eveningness Questionnaire & (Horne \& Östberg, 1976) & 19 items questionnaire to understand your body clock & & \\
-Munich Chronotype Questionnaire (MCTQ) & (Roenneberg, Wirz-Justice, \& Merrow, 2003) & 17 items questionnaire to understand individuals phase of entrainment & & \\
-Assessment of Sleep Environment & (Olivier et al., 2016) \textbar{} 13 & items questionnaire measuring your sleep environment quality \textbar{} & \begin{minipage}[t]{\linewidth}\raggedright
-\begin{verbatim}
-                              |
-\end{verbatim}
-\end{minipage} & \\
-The Pittsburgh Sleep Quality Index (PSQI) & (Daniel J. Buysse, Reynolds III, Monk, Berman, \& Kupfer, 1989) & 9 items inventory to measure sleep quality and sleeping pattern & & \\
-Self-Rating of Biological Rhythm Disorder for Adolescents (SBRDA) & (Xie, Wu, Tao, Wan, \& Tao, 2021) \textbar{} 29 & items questionnaire assessing four dimensions of biological rhythm disorder in adolescents (digital media use, sleep, eating habits, and activity) \textbar{} It & ems 3., 22., 23., 24., 25.
-and 29.
-\textbar{} & \\
-Photosensitivity Assessment Questionnaire (PAQ) & (Wu \& Hallett, 2017) \textbar{} 16 & dichotomous (yes/no) items questionnaire to assess ``photophobia'' and ``photophilia,'' giving two final scores of ``photophobic'' and ``photophilic'' behaviours \textbar{} Al & l items \textbar{} & \\
+Visual Light Sensitivity Questionnaire-8 & {}[@verriotto2017new] & Eight-question survey to assess the presence and severity of photosensitivity symptoms & NA & NA\\
+Office Light Survey & {}[@eklund1996development] & Multi-item questionnaire to assess electrical lighting environment in office & NA & NA\\
+Harvard Light Exposure Assessment Questionnaire & {}[@bajaj2011validation] & Self-administered semi-quantitative light questionnaire & NA & NA\\
+Hospital Lighting Survey & {}[@dianat2013objective] & 23 items questionnaire to assess light environment in a hospital & NA & NA\\
+Morningness-Eveningness Questionnaire & {}[@horne1976self] & 19 items questionnaire to understand your body clock & NA & NA\\
+\addlinespace
+Munich Chronotype Questionnaire (MCTQ) & {}[@roenneberg2003life] & 17 items questionnaire to understand individuals phase of entrainment & NA & NA\\
+Assessment of Sleep Environment & {}[@Olivier.2016] | 13 & items questionnaire measuring your sleep environment quality & NA & NA\\
+The Pittsburgh Sleep Quality Index (PSQI) & {}[@buysse1989pittsburgh] & 9 items inventory to measure sleep quality and sleeping pattern & NA & NA\\
+Self-Rating of Biological Rhythm Disorder for Adolescents (SBRDA) & {}[@Xie.2021] | 29 & items questionnaire assessing four dimensions of biological rhythm disorder in adolescents (digital media use, sleep, eating habits, and activity) & Item 3,22-25 and 29 & NA\\
+Photosensitivity Assessment Questionnaire (PAQ) & {}[@Wu.2017] | 16 & dichotomous (yes/no) items questionnaire to assess "photophobia" and "photophilia", giving two final scores of "photophobic" and "photophilic" behaviours & All itms & NA\\
 \bottomrule
-\end{longtable}
+\end{tabular}
 
@@
 \item
-  Sleep disturbance and sleep-related impairment (adult and pediatric versions) (Bevans et al., 2019; Daniel J.
-Buysse et al., 2010; Forrest et al., 2018; Harb, Hidalgo, \& Martau, 2015; L.
-Yu et al., 2011)
-\item
-  Sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration (version for adults and adolescents) (Roenneberg et al., 2003)
-\item
-  Sleep environment {[}Olivier et al. (2016)\\
+  Sleep disturbance and sleep-related impairment (adult and pediatric versions) (Bevans et al., 2019; Buysse et al., 2010; Forrest et al., 2018; Harb, Hidalgo, \& Martau, 2015; L. Yu et al., 2011)
+\item
+  Sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration (version for adults and adolescents) (Roenneberg, Wirz-Justice, \& Merrow, 2003)
+\item
+  Sleep environment (Olivier et al., 2016)
 \item
@@
 Desjardins \& Bulut, 2018).
-Bartlett's test of sphericity (Bartlett, 1954), \(\chi^2\) (1128) = 5042.86, p \textless{} .001{]} indicated the correlations between items are adequate for the EFA.
+Bartlett's test of sphericity (Bartlett, 1954), \(chi^2\) (1128) = 5042.86, p \textless{} .001{]} indicated the correlations between items are adequate for the EFA.
 However only 4.96\% of the inter-item correlation coefficients were greater than .30.
@@
 
-In the five-factor solution, the first factor contained three items and explained 10.25\% of the total variance with a satisfactory internal reliability coefficient (\(\alpha\) = .86).
+In the five-factor solution, the first factor contained three items and explained 10.25\% of the total variance with a satisfactory internal reliability coefficient (\(alpha\) = .86).
 All the items in this factor stemmed from the individual's preference to use blue light filters in different light environments.
-The second factor contained six items and explained 9.93\% of the total variance with a satisfactory internal reliability coefficient (\(\alpha\) = .71).
+The second factor contained six items and explained 9.93\% of the total variance with a satisfactory internal reliability coefficient (\(alpha\) = .71).
 Items under this factor commonly investigate an individual's hours spent outdoor.
@@
 Items under this factor dealt with the specific behaviors pertaining to sleep.
-The internal consistency reliability coefficient was, \(\alpha\) = .68.
-The fourth factor contained five items and explained 8.44\% of the total variance with an internal consistency coefficient, \(\alpha\) = .62.
+The internal consistency reliability coefficient was, \(alpha\) = .68.
+The fourth factor contained five items and explained 8.44\% of the total variance with an internal consistency coefficient, \(alpha\) = .62.
 These five items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time.
@@
 This factor tried to measure an individual's behavior lead by the awareness of light's influence on health.
-However, this factor showed unsatisfactory internal consistency reliability (\(\alpha\) = .53).
+However, this factor showed unsatisfactory internal consistency reliability (\(alpha\) = .53).
 It is essential to attain a balance between psychometric properties and interpretability of the common themes when exploring the latent structure.
@@
 Subsequently, we judged the model fit based on the comparative fit indices: CFI, TLI and parsimony fit index-RMSEA.
-Our fitted model attained acceptable fit (CFI =.94; TLI = .93); RMSEA = .06,\[.05-.07, 90% CI
-\]) with two imposed equity constrain on item pairs 32-33 and 19-17 .
+Our fitted model attained acceptable fit (CFI =.94; TLI = .93); RMSEA = .06,{[}.05-.07, 90\% CI{]}) with two imposed equity constrain on item pairs 32-33 and 19-17 .
 However SRMR value was higher than the guideline (SRMR = .12).
-Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 \& 26) for very low r-square value, our model attained best fit (CFI =.97; TLI = .96); RMSEA = .05\[.04-.06, 90% CI
-\]) and SRMR value (SRMR = .09) was also close to the suggestions of Hu and Bentle (1999).
+Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 \& 26) for very low r-square value, our model attained best fit (CFI =.97; TLI = .96); RMSEA = .05{[}.04-.06, 90\% CI{]}) and SRMR value (SRMR = .09) was also close to the suggestions of Hu and Bentle (1999).
 Since reliability coefficient Cronbach's alpha tends to mis-measure reliability for multidimensional construct (Sijtsma, 2009) we report Mcdonald's omega(total) as the internal consistency reliability coefficient.
@@
 IRT complements the conventional classical test theory-based analysis by gathering information on item discrimination and item difficulty(Baker, 2017).
-Here, an item's quality is judged based on item information in relation to participants' latent trait level (\(\theta\)).
+Here, an item's quality is judged based on item information in relation to participants' latent trait level (\(theta\)).
 We gathered evidence on item quality by fitting each factor of LEBA with the graded response model (\ref{tab:IRTparameters} to the combined EFA sample and CFA sample (n =690).
@@
 As we treated each factor of LEBA as an unidmensional construct we obtain 5 TICs.
-These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum ((\(\theta\))).
-Also the amount of information changed rather steadily with the change of (\(\theta\)).
+These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum ((\(theta\))).
+Also the amount of information changed rather steadily with the change of (\(theta\)).
 Thus we conferred the LEBA scale (except blue filter) estimated the light exposure related behavior with precision near the center of trait continuum (Baker, 2017) which is sufficient to discriminate between latent trait measured by the each factor.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-bajaj2011validation}{}}%
-Bajaj, A., Rosner, B., Lockley, S.
-W., \& Schernhammer, E.
-S.
-(2011).
-Validation of a light questionnaire with real-life photopic illuminance measurements: The harvard light exposure assessment questionnaire.
-\emph{Cancer Epidemiology and Prevention Biomarkers}, \emph{20}(7), 1341--1349.
-
 \leavevmode\vadjust pre{\hypertarget{ref-bakerBasicsItemResponse2017}{}}%
@@
 Bandalos, D. L., \& Finney, S. J. (2018). Factor analysis: {Exploratory} and confirmatory. In \emph{The reviewer's guide to quantitative methods in the social sciences} (pp. 98--122). {Routledge}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-questionr}{}}%
+Barnier, J., Briatte, F., \& Larmarange, J. (2020). \emph{Questionr: Functions to make surveys processing easier}. Retrieved from \url{https://CRAN.R-project.org/package=questionr}
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-buysse1989pittsburgh}{}}%
-Buysse, Daniel J., Reynolds III, C.
-F., Monk, T.
-H., Berman, S.
-R., \& Kupfer, D.
-J.
-(1989).
-The pittsburgh sleep quality index: A new instrument for psychiatric practice and research.
-\emph{Psychiatry Research}, \emph{28}(2), 193--213.
-
 \leavevmode\vadjust pre{\hypertarget{ref-Buysse.2010}{}}%
-Buysse, Daniel J., Yu, L., Moul, D.
+Buysse, D.
+J., Yu, L., Moul, D.
 E., Germain, A., Stover, A., Dodds, N.
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-dianat2013objective}{}}%
-Dianat, I., Sedghi, A., Bagherzade, J., Jafarabadi, M.
-A., \& Stedmon, A.
-W.
-(2013).
-Objective and subjective assessments of lighting in a hospital setting: Implications for health, safety and performance.
-\emph{Ergonomics}, \emph{56}(10), 1535--1545.
-
 \leavevmode\vadjust pre{\hypertarget{ref-R-paran}{}}%
@@
 \emph{British Journal of Mathematical and Statistical Psychology}, \emph{38}(1), 67--86.
-
-\leavevmode\vadjust pre{\hypertarget{ref-eklund1996development}{}}%
-Eklund, N., \& Boyce, P. (1996). The development of a reliable, valid, and simple office lighting survey. \emph{Journal of the Illuminating Engineering Society}, \emph{25}(2), 25--40.
 
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-horne1976self}{}}%
-Horne, J. A., \& Östberg, O. (1976). A self-assessment questionnaire to determine morningness-eveningness in human circadian rhythms. \emph{International Journal of Chronobiology}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-huCutoffCriteriaFit1999}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-verriotto2017new}{}}%
-Verriotto, J.
-D., Gonzalez, A., Aguilar, M.
-C., Parel, J.-M.
-A., Feuer, W.
-J., Smith, A.
-R., \& Lam, B.
-L.
-(2017).
-New methods for quantification of visual photosensitivity threshold and symptoms.
-\emph{Translational Vision Science \& Technology}, \emph{6}(4), 18--18.
-
 \leavevmode\vadjust pre{\hypertarget{ref-watkinsStepbyStepGuideExploratory2020}{}}%
@@
 Wu, Y., \& Hallett, M. (2017). Photophobia in neurologic disorders. \emph{Translational Neurodegeneration}, \emph{6}(1), 26. \url{https://doi.org/10.1186/s40035-017-0095-3}
-
-\leavevmode\vadjust pre{\hypertarget{ref-Xie.2021}{}}%
-Xie, Y., Wu, X., Tao, S., Wan, Y., \& Tao, F.
-(2021).
-Development and validation of the self-rating of biological rhythm disorder for chinese adolescents.
-\emph{Chronobiology International}, 1--7.
-\url{https://doi.org/10.1080/07420528.2021.1989450}
 
@@
 
-\caption{\label{tab:MinResTab}Factor loadings and communality of the retained items(Minmum Residual)}
+\caption{\label{tab:MinResTab-33}Factor loadings and communality of the retained items(Minmum Residual)}
 
@@
 
-\caption{\label{tab:sixFacTab}Factor loadings and communality of the retained items(six factor)}
+\caption{\label{tab:sixFacTab-35}Factor loadings and communality of the retained items(six factor)}
 
@@
 
-\caption{\label{tab:tabDesAppB}Descriptive Statistics for Unmerged response options}
+\caption{\label{tab:tabDesAppB-39}Descriptive Statistics for Unmerged response options}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-1}
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-41-1}
 
@@
 
-\caption{Correlation plot of the items}\label{fig:figCorAppB}
+\caption{Correlation plot of the items}\label{fig:figCorAppB-41}
 \end{figure}
@@
 
-{\centering \includegraphics{manuscript_files/figure-latex/facIdFigAppB-1}
+{\centering \includegraphics{manuscript_files/figure-latex/facIdFigAppB-45-1}
 
@@
 
-\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}\label{fig:facIdFigAppB}
+\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}\label{fig:facIdFigAppB-45}
 \end{figure}
@@
 
-\caption{\label{tab:EFATableAppB}Factor loadings and communality of the retained items [Unmerged Responses]}
+\caption{\label{tab:EFATableAppB-48}Factor loadings and communality of the retained items [Unmerged Responses]}
 
@@
 
-{\centering \includegraphics{manuscript_files/figure-latex/EFAResidualsAppB-1}
+{\centering \includegraphics{manuscript_files/figure-latex/EFAResidualsAppB-49-1}
 
@@
 
-\caption{ Histogram of residulas:  five-factor solution}\label{fig:EFAResidualsAppB}
+\caption{ Histogram of residulas:  five-factor solution}\label{fig:EFAResidualsAppB-49}
 \end{figure}

### 2021-11-12 Supplymentary.tex
Table 1 now readable with behaving format

@@
 
-\caption{\label{tab:MinResTab-33}Factor loadings and communality of the retained items(Minmum Residual)}
+\caption{\label{tab:MinResTab-56}Factor loadings and communality of the retained items(Minmum Residual)}
 
@@
 
-\caption{\label{tab:sixFacTab-35}Factor loadings and communality of the retained items(six factor)}
+\caption{\label{tab:sixFacTab-58}Factor loadings and communality of the retained items(six factor)}
 
@@
 
-\caption{\label{tab:tabDesAppB-39}Descriptive Statistics for Unmerged response options}
+\caption{\label{tab:tabDesAppB-62}Descriptive Statistics for Unmerged response options}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-41-1}
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-64-1}
 
@@
 
-\caption{Correlation plot of the items}(\#fig:figCorAppB-41)
+\caption{Correlation plot of the items}(\#fig:figCorAppB-64)
 \end{figure}
@@
 
-{\centering \includegraphics{manuscript_files/figure-latex/facIdFigAppB-45-1}
+{\centering \includegraphics{manuscript_files/figure-latex/facIdFigAppB-68-1}
 
@@
 
-\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}(\#fig:facIdFigAppB-45)
+\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}(\#fig:facIdFigAppB-68)
 \end{figure}
@@
 
-\caption{\label{tab:EFATableAppB-48}Factor loadings and communality of the retained items [Unmerged Responses]}
+\caption{\label{tab:EFATableAppB-71}Factor loadings and communality of the retained items [Unmerged Responses]}
 
@@
 
-{\centering \includegraphics{manuscript_files/figure-latex/EFAResidualsAppB-49-1}
+{\centering \includegraphics{manuscript_files/figure-latex/EFAResidualsAppB-72-1}
 
@@
 
-\caption{ Histogram of residulas:  five-factor solution}(\#fig:EFAResidualsAppB-49)
+\caption{ Histogram of residulas:  five-factor solution}(\#fig:EFAResidualsAppB-72)
 \end{figure}

### 2021-11-12 manuscript.Rmd
Table 1 now readable with behaving format

@@
   `r cite_r("references.bib")`
+  [@verriotto2017new][@eklund1996development][@bajaj2011validation][@dianat2013objective]
+  [@horne1976self][@roenneberg2003life][@Olivier.2016][@buysse1989pittsburgh][@Xie.2021]
+  [@Wu.2017]
 ---
@@
 
-```{r}
-kable(relevant.scale.data,booktabs = T)
+```{r results='asis'}
+relevant.scale.data %>%
+   kable( booktabs = T, caption ="Releated Scales", format ="latex", longtable =T) %>% 
+  kable_styling(latex_options = c("repeat_header")) %>% 
+  column_spec(1:4, width = "4cm")
 ```
@@
 
-```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development', out.height='100%', out.width='100%'}
+```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of LEBA', out.height='100%', out.width='100%'}
 knitr::include_graphics('Manuscript.figures/Flowchart1.png')
@@
 ### Data Collection
-
 Timeline of data collection, mode of data collection.
@@
 ## Analytic Strategies
-
 We used R (version 4.1.0), including several R packages, for our analyses.Initially, our tool have six poin Likert type response scale(0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Alsways).
@@
 Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018].
-Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001] indicated the correlations between items are adequate for the EFA.
+Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001] indicated the correlations between items are adequate for the EFA.
 However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than .30.
@@
 
-In the five-factor solution, the first factor contained three items and explained `r apa(var1,2,F)`% of the total variance with a satisfactory internal reliability coefficient ($alpha$ = `r apa(F1.alpha,2,F)`).
+In the five-factor solution, the first factor contained three items and explained `r apa(var1,2,F)`% of the total variance with a satisfactory internal reliability coefficient ($\alpha$ = `r apa(F1.alpha,2,F)`).
 All the items in this factor stemmed from the individual's preference to use blue light filters in different light environments.
-The second factor contained six items and explained `r apa(var2,2,F)`% of the total variance with a satisfactory internal reliability coefficient ($alpha$ = `r apa(F2.alpha,2,F)`).
+The second factor contained six items and explained `r apa(var2,2,F)`% of the total variance with a satisfactory internal reliability coefficient ($\alpha$ = `r apa(F2.alpha,2,F)`).
 Items under this factor commonly investigate an individual's hours spent outdoor.
@@
 Items under this factor dealt with the specific behaviors pertaining to sleep.
-The internal consistency reliability coefficient was, $alpha$ = `r apa(F3.alpha,2,F)`.
-The fourth factor contained five items and explained `r apa(var4,2,F)`% of the total variance with an internal consistency coefficient, $alpha$ = `r apa(F4.alpha,2,F)`.
+The internal consistency reliability coefficient was, $\alpha$ = `r apa(F3.alpha,2,F)`.
+The fourth factor contained five items and explained `r apa(var4,2,F)`% of the total variance with an internal consistency coefficient, $\alpha$ = `r apa(F4.alpha,2,F)`.
 These five items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time.
@@
 This factor tried to measure an individual's behavior lead by the awareness of light's influence on health.
-However, this factor showed unsatisfactory internal consistency reliability ($alpha$ = `r apa(F5.alpha,2,F)`).
+However, this factor showed unsatisfactory internal consistency reliability ($\alpha$ = `r apa(F5.alpha,2,F)`).
 It is essential to attain a balance between psychometric properties and interpretability of the common themes when exploring the latent structure.
@@
 IRT complements the conventional classical test theory-based analysis by gathering information on item discrimination and item difficulty[@bakerBasicsItemResponse2017].
-Here, an item's quality is judged based on item information in relation to participants' latent trait level ($theta$).
+Here, an item's quality is judged based on item information in relation to participants' latent trait level ($\theta$).
 We gathered evidence on item quality by fitting each factor of LEBA with the graded response model (\@ref(tab:IRTparameters) to the combined EFA sample and CFA sample (n =690).
@@
 As we treated each factor of LEBA as an unidmensional construct we obtain 5 TICs.
-These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum (($theta$)).
-Also the amount of information changed rather steadily with the change of ($theta$).
+These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum (($\theta$)).
+Also the amount of information changed rather steadily with the change of ($\theta$).
 Thus we conferred the LEBA scale (except blue filter) estimated the light exposure related behavior with precision near the center of trait continuum [@bakerBasicsItemResponse2017] which is sufficient to discriminate between latent trait measured by the each factor.
@@
 Our result also indicated all the items fitted well to the respective models as assessed by assessed by RMSEA value obtained from Signed-X2 index implementation.
-All of the items had RMSEA value \<.06 indicating adequate fit.
+All of the items had RMSEA value <.06 indicating adequate fit.
 Person fit indicates the validity and meaningfulness of the fitted model at the participants latent trait level [@desjardinsHandbookEducationalMeasurement2018].
@@
 ```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('Supplymentary.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('instrument.Rmd')
+```

### 2021-11-12 manuscript.tex
Table 1 now readable with behaving format

@@
 
-\begin{tabular}{lllll}
+\begin{longtable}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{4cm}}
+\caption{\label{tab:unnamed-chunk-2}Releated Scales}\\
 \toprule
-Name & Author & Description & Relevant Items & Adaptations\\
+Name & Author & Description & Relevant Items\\
 \midrule
-Visual Light Sensitivity Questionnaire-8 & {}[@verriotto2017new] & Eight-question survey to assess the presence and severity of photosensitivity symptoms & NA & NA\\
-Office Light Survey & {}[@eklund1996development] & Multi-item questionnaire to assess electrical lighting environment in office & NA & NA\\
-Harvard Light Exposure Assessment Questionnaire & {}[@bajaj2011validation] & Self-administered semi-quantitative light questionnaire & NA & NA\\
-Hospital Lighting Survey & {}[@dianat2013objective] & 23 items questionnaire to assess light environment in a hospital & NA & NA\\
-Morningness-Eveningness Questionnaire & {}[@horne1976self] & 19 items questionnaire to understand your body clock & NA & NA\\
+\endfirsthead
+\caption[]{\label{tab:unnamed-chunk-2}Releated Scales \textit{(continued)}}\\
+\toprule
+Name & Author & Description & Relevant Items\\
+\midrule
+\endhead
+
+\endfoot
+\bottomrule
+\endlastfoot
+Visual Light Sensitivity Questionnaire-8 & Verriotto et al., 2017 & Eight-question survey to assess the presence and severity of photosensitivity symptoms & NA\\
+Office Light Survey & Eklundet al., 1996 & A survey to assess electrical lighting environment in office & NA\\
+Harvard Light Exposure Assessment Questionnaire & Bajaj et al., 2011 & Self-administered semi-quantitative light questionnaire & NA\\
+Hospital Lighting Survey & Dianat et el.,.2013 & 23 items questionnaire to assess light environment in a hospital & NA\\
+Morningness-Eveningness Questionnaire & Horne et al.,1976 & 19 items questionnaire to understand your body clock & NA\\
 \addlinespace
-Munich Chronotype Questionnaire (MCTQ) & {}[@roenneberg2003life] & 17 items questionnaire to understand individuals phase of entrainment & NA & NA\\
-Assessment of Sleep Environment & {}[@Olivier.2016] | 13 & items questionnaire measuring your sleep environment quality & NA & NA\\
-The Pittsburgh Sleep Quality Index (PSQI) & {}[@buysse1989pittsburgh] & 9 items inventory to measure sleep quality and sleeping pattern & NA & NA\\
-Self-Rating of Biological Rhythm Disorder for Adolescents (SBRDA) & {}[@Xie.2021] | 29 & items questionnaire assessing four dimensions of biological rhythm disorder in adolescents (digital media use, sleep, eating habits, and activity) & Item 3,22-25 and 29 & NA\\
-Photosensitivity Assessment Questionnaire (PAQ) & {}[@Wu.2017] | 16 & dichotomous (yes/no) items questionnaire to assess "photophobia" and "photophilia", giving two final scores of "photophobic" and "photophilic" behaviours & All itms & NA\\
-\bottomrule
-\end{tabular}
+Munich Chronotype Questionnaire (MCTQ) & Roenneberg et al.,2003 & 17 items questionnaire to understand individuals phase of entrainment & NA\\
+Assessment of Sleep Environment & Olivier et.al.,.2016] & 13 items questionnaire measuring your sleep environment quality & NA\\
+The Pittsburgh Sleep Quality Index (PSQI) & Buysse ei al.,1989 & 9 items inventory to measure sleep quality and sleeping pattern & NA\\
+Self-Rating of Biological Rhythm Disorder for Adolescents (SBRDA) & Xie et al.,2021 & 29 Items questionnaire assessing four dimensions of biological rhythm disorder in adolescents & Item 3,22-25 and 29\\
+Photosensitivity Assessment Questionnaire (PAQ) & Wu et al.,2017 & 16 dichotomous (yes/no) items questionnaire to assess "photophobia" and "photophilia" & All itms\\*
+\end{longtable}
 
@@
 \item
-  Sleep disturbance and sleep-related impairment (adult and pediatric versions) (Bevans et al., 2019; Buysse et al., 2010; Forrest et al., 2018; Harb, Hidalgo, \& Martau, 2015; L. Yu et al., 2011)
+  Sleep disturbance and sleep-related impairment (adult and pediatric versions) (Bevans et al., 2019; Daniel J.
+Buysse et al., 2010; Forrest et al., 2018; Harb, Hidalgo, \& Martau, 2015; L.
+Yu et al., 2011)
 \item
@@
 
-\caption{Development}\label{fig:FlowchartFig}
+\caption{Development of LEBA}\label{fig:FlowchartFig}
 \end{figure}
@@
 Desjardins \& Bulut, 2018).
-Bartlett's test of sphericity (Bartlett, 1954), \(chi^2\) (1128) = 5042.86, p \textless{} .001{]} indicated the correlations between items are adequate for the EFA.
+Bartlett's test of sphericity (Bartlett, 1954), \(\chi^2\) (1128) = 5042.86, p \textless{} .001{]} indicated the correlations between items are adequate for the EFA.
 However only 4.96\% of the inter-item correlation coefficients were greater than .30.
@@
 
-In the five-factor solution, the first factor contained three items and explained 10.25\% of the total variance with a satisfactory internal reliability coefficient (\(alpha\) = .86).
+In the five-factor solution, the first factor contained three items and explained 10.25\% of the total variance with a satisfactory internal reliability coefficient (\(\alpha\) = .86).
 All the items in this factor stemmed from the individual's preference to use blue light filters in different light environments.
-The second factor contained six items and explained 9.93\% of the total variance with a satisfactory internal reliability coefficient (\(alpha\) = .71).
+The second factor contained six items and explained 9.93\% of the total variance with a satisfactory internal reliability coefficient (\(\alpha\) = .71).
 Items under this factor commonly investigate an individual's hours spent outdoor.
@@
 Items under this factor dealt with the specific behaviors pertaining to sleep.
-The internal consistency reliability coefficient was, \(alpha\) = .68.
-The fourth factor contained five items and explained 8.44\% of the total variance with an internal consistency coefficient, \(alpha\) = .62.
+The internal consistency reliability coefficient was, \(\alpha\) = .68.
+The fourth factor contained five items and explained 8.44\% of the total variance with an internal consistency coefficient, \(\alpha\) = .62.
 These five items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time.
@@
 This factor tried to measure an individual's behavior lead by the awareness of light's influence on health.
-However, this factor showed unsatisfactory internal consistency reliability (\(alpha\) = .53).
+However, this factor showed unsatisfactory internal consistency reliability (\(\alpha\) = .53).
 It is essential to attain a balance between psychometric properties and interpretability of the common themes when exploring the latent structure.
@@
 IRT complements the conventional classical test theory-based analysis by gathering information on item discrimination and item difficulty(Baker, 2017).
-Here, an item's quality is judged based on item information in relation to participants' latent trait level (\(theta\)).
+Here, an item's quality is judged based on item information in relation to participants' latent trait level (\(\theta\)).
 We gathered evidence on item quality by fitting each factor of LEBA with the graded response model (\ref{tab:IRTparameters} to the combined EFA sample and CFA sample (n =690).
@@
 As we treated each factor of LEBA as an unidmensional construct we obtain 5 TICs.
-These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum ((\(theta\))).
-Also the amount of information changed rather steadily with the change of (\(theta\)).
+These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum ((\(\theta\))).
+Also the amount of information changed rather steadily with the change of (\(\theta\)).
 Thus we conferred the LEBA scale (except blue filter) estimated the light exposure related behavior with precision near the center of trait continuum (Baker, 2017) which is sufficient to discriminate between latent trait measured by the each factor.
@@
 Aust, F., \& Barth, M. (2020). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bajaj2011validation}{}}%
+Bajaj, A., Rosner, B., Lockley, S.
+W., \& Schernhammer, E.
+S.
+(2011).
+Validation of a light questionnaire with real-life photopic illuminance measurements: The harvard light exposure assessment questionnaire.
+\emph{Cancer Epidemiology and Prevention Biomarkers}, \emph{20}(7), 1341--1349.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-buysse1989pittsburgh}{}}%
+Buysse, Daniel J., Reynolds III, C.
+F., Monk, T.
+H., Berman, S.
+R., \& Kupfer, D.
+J.
+(1989).
+The pittsburgh sleep quality index: A new instrument for psychiatric practice and research.
+\emph{Psychiatry Research}, \emph{28}(2), 193--213.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Buysse.2010}{}}%
-Buysse, D.
-J., Yu, L., Moul, D.
+Buysse, Daniel J., Yu, L., Moul, D.
 E., Germain, A., Stover, A., Dodds, N.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-dianat2013objective}{}}%
+Dianat, I., Sedghi, A., Bagherzade, J., Jafarabadi, M.
+A., \& Stedmon, A.
+W.
+(2013).
+Objective and subjective assessments of lighting in a hospital setting: Implications for health, safety and performance.
+\emph{Ergonomics}, \emph{56}(10), 1535--1545.
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-paran}{}}%
@@
 \emph{British Journal of Mathematical and Statistical Psychology}, \emph{38}(1), 67--86.
+
+\leavevmode\vadjust pre{\hypertarget{ref-eklund1996development}{}}%
+Eklund, N., \& Boyce, P. (1996). The development of a reliable, valid, and simple office lighting survey. \emph{Journal of the Illuminating Engineering Society}, \emph{25}(2), 25--40.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-horne1976self}{}}%
+Horne, J. A., \& Östberg, O. (1976). A self-assessment questionnaire to determine morningness-eveningness in human circadian rhythms. \emph{International Journal of Chronobiology}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-huCutoffCriteriaFit1999}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-verriotto2017new}{}}%
+Verriotto, J.
+D., Gonzalez, A., Aguilar, M.
+C., Parel, J.-M.
+A., Feuer, W.
+J., Smith, A.
+R., \& Lam, B.
+L.
+(2017).
+New methods for quantification of visual photosensitivity threshold and symptoms.
+\emph{Translational Vision Science \& Technology}, \emph{6}(4), 18--18.
+
 \leavevmode\vadjust pre{\hypertarget{ref-watkinsStepbyStepGuideExploratory2020}{}}%
@@
 Wu, Y., \& Hallett, M. (2017). Photophobia in neurologic disorders. \emph{Translational Neurodegeneration}, \emph{6}(1), 26. \url{https://doi.org/10.1186/s40035-017-0095-3}
+
+\leavevmode\vadjust pre{\hypertarget{ref-Xie.2021}{}}%
+Xie, Y., Wu, X., Tao, S., Wan, Y., \& Tao, F.
+(2021).
+Development and validation of the self-rating of biological rhythm disorder for chinese adolescents.
+\emph{Chronobiology International}, 1--7.
+\url{https://doi.org/10.1080/07420528.2021.1989450}
 
@@
 
-\caption{Correlation plot of the items}\label{fig:figCorAppB-41}
+\caption{Correlation plot of the items}\label{fig:figCorAppB-64}
 \end{figure}
@@
 
-\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}\label{fig:facIdFigAppB-45}
+\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}\label{fig:facIdFigAppB-68}
 \end{figure}
@@
 
-\caption{ Histogram of residulas:  five-factor solution}\label{fig:EFAResidualsAppB-49}
+\caption{ Histogram of residulas:  five-factor solution}\label{fig:EFAResidualsAppB-72}
 \end{figure}

### 2021-11-12 install_packages.R

@@ -60,10 +60,10 @@ install.packages("cowplot")
 install.packages("rsvg")
 
 
-#Addons
+#Addins
 devtools::install_github("crsh/citr")
 install.packages("questionr")
-
+install.packages("wordcountaddin")
 #Others
 install.packages("magick")
 

### 2021-11-13 manuscript.Rmd
* Ordinal reliability estimates are introduced.

@@
   - "instrument.Rmd"
-mainfont: Helvetica
+mainfont: Arial
 ---
@@
 set.seed(123)
-par(family = "Helvetica")
-```
-
-```{r pacman, include=FALSE}
+par(family = "Arial")
+```
+
+```{r pacman, eval=FALSE, include=FALSE}
 #You need to run this chunck 1X in your system 
@@
 ## Analytic Strategies
-We used R (version 4.1.0), including several R packages, for our analyses.Initially, our tool have six poin Likert type response scale(0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Alsways).
+We used R (version 4.1.0), including several R packages, for our analyses.Initially, our tool have six point Likert type response scale (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Always).
 As our purpose was to capture light exposure related behavior, "Does not apply/I don't know" and "Never" were providing similar information.
@@
 
-Five.F1.alpha <- psych::alpha(Five.F1, check.keys = T) 
-Five.F2.alpha <- psych::alpha(Five.F2, check.keys = T)
-Five.F3.alpha <- psych::alpha(Five.F3, check.keys = T)
-Five.F4.alpha <- psych::alpha(Five.F4, check.keys = T) 
-Five.F5.alpha <- psych::alpha(Five.F5, check.keys = T)
+#ordinal alpha
+Five.F1.alpha <- psych::alpha(polychoric(Five.F1)$rho,check.keys=TRUE)
+Five.F2.alpha <- psych::alpha(polychoric(Five.F2)$rho,check.keys=TRUE)
+Five.F3.alpha <- psych::alpha(polychoric(Five.F3)$rho,check.keys=TRUE)
+Five.F4.alpha <- psych::alpha(polychoric(Five.F4)$rho,check.keys=TRUE)
+Five.F5.alpha <- psych::alpha(polychoric(Five.F5)$rho,check.keys=TRUE)
 
@@
 
-In the five-factor solution, the first factor contained three items and explained `r apa(var1,2,F)`% of the total variance with a satisfactory internal reliability coefficient ($\alpha$ = `r apa(F1.alpha,2,F)`).
+Internal consistency reliability coefficient Cronbach's alpha assumes that all the factor- loading of the items under a factor are equal [@graham2006congeneric; @novick1967coefficient] which is not the case in our sample.
+Additionally Cronbach's alpha coefficient has a tendency to deflate the estimates for  Likert type data as the calculation is based on pearson-correlation matrix which requires that response data should be in continuous of nature [@gadermann2012estimating; @zumbo2007ordinal].
+Subsequently to get  better estimates of reliability we reported ordinal alpha which used polychoric-correlation matrix and assumed that the responses data were ordered in nature instead of continuous.
+Ordinal alpha coefficient value ranges from 0 to 1 and higher value represents better reliability.
+In the five-factor solution, the first factor contained three items and explained `r apa(var1,2,F)`% of the total variance with a  internal reliability coefficient ordinal $\alpha$ = `r apa(F1.alpha,2,F)`.
 All the items in this factor stemmed from the individual's preference to use blue light filters in different light environments.
-The second factor contained six items and explained `r apa(var2,2,F)`% of the total variance with a satisfactory internal reliability coefficient ($\alpha$ = `r apa(F2.alpha,2,F)`).
+The second factor contained six items and explained `r apa(var2,2,F)`% of the total variance with a  internal reliability coefficient ordinal $\alpha$ = `r apa(F2.alpha,2,F)`.
 Items under this factor commonly investigate an individual's hours spent outdoor.
@@
 Items under this factor dealt with the specific behaviors pertaining to sleep.
-The internal consistency reliability coefficient was, $\alpha$ = `r apa(F3.alpha,2,F)`.
-The fourth factor contained five items and explained `r apa(var4,2,F)`% of the total variance with an internal consistency coefficient, $\alpha$ = `r apa(F4.alpha,2,F)`.
+The internal consistency reliability coefficient was, ordinal $\alpha$ = `r apa(F3.alpha,2,F)`.
+The fourth factor contained five items and explained `r apa(var4,2,F)`% of the total variance with an internal consistency coefficient, ordinal $\alpha$ = `r apa(F4.alpha,2,F)`.
 These five items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time.
@@
 This factor tried to measure an individual's behavior lead by the awareness of light's influence on health.
-However, this factor showed unsatisfactory internal consistency reliability ($\alpha$ = `r apa(F5.alpha,2,F)`).
+The  internal consistency reliability was, ordinal $\alpha$ = `r apa(F5.alpha,2,F)` .
 It is essential to attain a balance between psychometric properties and interpretability of the common themes when exploring the latent structure.
-As all of the emerged factors are highly interpretable and relevant towards our aim to capture light exposure related behavior, regardless of the apparent low reliability of the two factors, we retain the five-factor solution with 23 items for our confirmatory factor analysis (CFA).
+As all of the emerged factors are highly interpretable and relevant towards our aim to capture light exposure related behavior, regardless of the apparent low reliability of the fifth factor, we retain all the five-factors with 23 items for our confirmatory factor analysis (CFA).
 Two items showed negative factor-loading (items 44 and 21).
@@
 Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR value (SRMR = `r apa(fit.2[10],2,F)`) was also close to the suggestions of @huCutoffCriteriaFit1999.
-Since reliability coefficient Cronbach's alpha tends to mis-measure reliability for multidimensional construct [@sijtsma2009use] we report Mcdonald's omega(total) as the internal consistency reliability coefficient.
-Mcdonald's omega(total) is reported to be a satisfactory lower bound reliability coefficient that works for both unidimensional and multidimensional construct [@zinbarg2005cronbach].
-Mcdonald's omega(total) for the five factors were `r apa(rel.k[1,1],2,F)`, `r apa(rel.k[5,2],2,F)`, `r apa(rel.k[5,3],2,F)`, `r apa(rel.k[5,4],2,F)`, `r apa(rel.k[5,5],2,F)` respectively.
-Mcdonald's omega(total) coefficient for the total scale was `r apa(rel.k[5,6],2,F)`.
+
+Internal consistency ordinal $\alpha$ for the five factors of LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)` respectively.
+We also estimated the internal consistency reliability of the total scale using Mcdonald's omega(total) coefficient which is a better reliability estimate for multidimensional constructs[@dunn2014alpha; @sijtsma2009use].
+McDonald's omega(total) coefficient for the total scale was `r apa(rel.k[5,6],2,F)`.
 

### 2021-11-13 manuscript.Rmd
* Invariance explained

@@
 Lastly, `r desc_tibble[15,2]` overall [EFA: `r desc_tibble[15,3]` ; CFA: `r desc_tibble[15,4]`] reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]` overall [EFA: `r desc_tibble[16,3]`; CFA: `r desc_tibble[16,4]`] filled in the "Neither (no work or school, or indication)" response option.
-We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable "Age" and Pearson's Chi-squared test for all other categorical variables via the gtsummary R package's "add_p" function [@sjoberg2021] .
+We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable "Age" and Pearson's $\chi^2$ test for all other categorical variables via the gtsummary R package's "add_p" function [@sjoberg2021] .
 The p-values were corrected for multiple testing applying false discovery rate (FDR) via the "add_q" function of the same package.
@@
 These indices can be categorized as absolute, comparative and parsimony fit indices [@brownConfirmatoryFactorAnalysis2015].
-Absolute fit assess the model fit at an absolute level using indices including chi-square test statistics and the standardized root mean square (SRMR).parsimony fit indices including the root mean square error of approximation (RMSEA) considers the number of free parameters in the model to assess the parsimony of the model.
+Absolute fit assess the model fit at an absolute level using indices including $\chi^2$ test statistics and the standardized root mean square (SRMR).parsimony fit indices including the root mean square error of approximation (RMSEA) considers the number of free parameters in the model to assess the parsimony of the model.
 Comparative fit indices evaluate the fit of the specified model solution in relation to a more restricted baseline model restricting all covariances among the idicators as zero.
 Comparative fit index (CFI) and the Tucker Lewis index (TLI) are such two comparative fit indices.
-Commonly used Model fit guidelines [@huCutoffCriteriaFit1999; @schumacker2004beginner] includes (i) Reporting of chi-square test statistics (A non-significant test statistics is required to reflect model fit) (i) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (ii) RMSEA (close to .06 or below), (iii) SRMR (close to .08 or below) to estimate the model fit.
+Commonly used Model fit guidelines [@huCutoffCriteriaFit1999; @schumacker2004beginner] includes (i) Reporting of $\chi^2$ test statistics (A non-significant test statistics is required to reflect model fit) (i) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (ii) RMSEA (close to .06 or below), (iii) SRMR (close to .08 or below) to estimate the model fit.
 Table \@ref(tab:tabCfa) summarizes the fit indices of our fitted model.
-Our fitted model failed to attain an absolute fit estimated by the chi-square test.
-However, the chi-square test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit [@brownConfirmatoryFactorAnalysis2015].
+Our fitted model failed to attain an absolute fit estimated by the $\chi^2$ test.
+However, the $\chi^2$ test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit [@brownConfirmatoryFactorAnalysis2015].
 Another absolute fit index we obtained in our analysis was SRMR which does not work well with categorical data [@RN1272].
@@
 
+# Measurement Invariance
+Measurement invariance (MI) evaluates whether a construct has the psychometric equivalence and same meaning across groups or measurement occasions [@putnick2016measurement;@klinePrinciplesPracticeStructural2015].
+We used a structural equation modeling framework to assess the measurement invariance of our developed tool across two groups: **native English speakers** and **non-native English speakers**.
+Our measurement invariance testing involved establishing configural, metric, scalar, and residual invariance [@widaman1997exploring].
+MI models are nested type models of which configural model is the first and least restrictive model.
+The configural model assumes that the number of factors and item number under each factor will be equal across two groups.
+The metric invariance model, along with the assumption of the configural model, assumes that factor-loadings of the items across the two groups will be equal, indicating each item contributes to the measured construct equivalently for both groups.
+Along with these assumptions, scalar invariance assumes that item intercepts to be equivalent across groups.
+The scalar invariance model indicates the equivalence of response scale across the groups, i.e., persons with the same level of the underlying construct will score the same across the groups.
+The residual invariance model holds all the mentioned assumptions as true and adds the assumption of equality in error variances and covariances across the groups.
+This model is the highest level of MI and assures the equivalence of precision of items across the groups in measuring the underlying constructs.
+The invariance model fit was assessed using the fit indices including $\chi^2$ test, CFI and TLI (close to .95 or above), RMSEA (close to .06 or below) [@huCutoffCriteriaFit1999].
+We excluded SRMR from our consideration as it does not behave optimally for categorical variables [@RN1272].
+Table \@ref(tab:InvarianceTab) summarized the fit indices.
+The comparison among different measurement invariance models was made using the $\chi^2$ difference test ($\Delta \chi^2$)  to assess whether our obtained latent structure of "LEBA" attains the highest level of the MI.
+If the $\Delta \chi^2$ test for model fit is not statistically significant (p<0.05) [@dimitrov2010testing], the particular invariance model was accepted.
+We started our analysis by comparing the model fit of the least restrictive model:configural model to metric MI model and continued successive comparisons.
+Table \@ref(tab:InvarianceTab) indicates that our fitted model had acceptable fit indices for all of the fitted MI models.
+The model fit does not significantly decrease across the nested models up to the scalar MI model.
+The chi-square value difference between the scalar and residual model is zero, indicating model fit remained the same for both: scalar and residual MI model, indicating the acceptability of the residual MI model.
+
 ```{r InvarianceAnalysis_data, include=FALSE}
@@
 
+#Metric
 weak <- cfa(model = LB.model.Cor.2,
@@
 
+#Scaler
 strong <- cfa(model = LB.model.Cor.2,
@@
 
+#residual
 strict <- cfa(model = LB.model.Cor.2,
@@
 summary(Third.comp)
-
+#structural
 structural <-cfa(model = LB.model.Cor.2,
@@
 summary(fourth.comp)
-comfit.par <- compareFit(configural, weak, strong, strict, structural)
+comfit.par <- compareFit(configural, weak, strong, strict)
 summary (comfit.par)
@@
                 "Scalar" = strong, 
-                "Residual" = strict, 
-                "Structural"=structural)
+                "Residual" = strict)
 
 Invariance.table <- compareLavaan(models,
-              nesting = "Configural > Metric > Scalar > Residual  > Structural", 
-              fitmeas = c("chisq.scaled", "df",  "cfi.scaled","tli.scaled","rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled","srmr" ),
+              nesting = "Configural > Metric > Scalar > Residual", 
+              fitmeas = c("chisq.scaled", "df",  "cfi.scaled","tli.scaled","rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled" ),
               scaled = T,
@@
 
-colnames(Invariance.table) <- c("Chi-Square", "df", "CFI", "TLI", "RMSEA", "RMSEA 90% Lower CI", "RMSEA 90% Upper", "SRMR", "Chi-Sqr comparison", "df*", "p")
+colnames(Invariance.table) <- c("Chi-Square", "df", "CFI", "TLI", "RMSEA", "RMSEA 90% Lower CI", "RMSEA 90% Upper", "Chi-Square Difference", "df difference*", "p")
 
@@
 ```{r InvarianceTab, results='asis'}
-apa_table(Invariance.table, align = "c",  caption = "Invariance Analysis", note = " a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual;* =  df of model comparison", landscape = T, font_size = "scriptsize" )
+apa_table(Invariance.table, align = "c",  caption = "Invariance Analysis", note = " a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual;* =  df of model comparison", landscape = T, font_size = "footnotesize" )
 

### 2021-11-13 manuscript.tex
* Invariance explained

@@
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-  \setmainfont[]{Helvetica}
+  \setmainfont[]{Arial}
 \fi
@@
 Lastly, 147 (21\%) overall {[}EFA: 94 (22\%) ; CFA: 53 (20\%){]} reported a combination of home- and face-to-face work/schooling, whereas 131 (19\%) overall {[}EFA: 72 (17\%); CFA: 59 (23\%){]} filled in the ``Neither (no work or school, or indication)'' response option.
-We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable ``Age'' and Pearson's Chi-squared test for all other categorical variables via the gtsummary R package's ``add\_p'' function (Sjoberg et al., 2021a) .
+We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable ``Age'' and Pearson's \(\chi^2\) test for all other categorical variables via the gtsummary R package's ``add\_p'' function (Sjoberg et al., 2021a) .
 The p-values were corrected for multiple testing applying false discovery rate (FDR) via the ``add\_q'' function of the same package.
@@
 
-We used R (version 4.1.0), including several R packages, for our analyses.Initially, our tool have six poin Likert type response scale(0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Alsways).
+We used R (version 4.1.0), including several R packages, for our analyses.Initially, our tool have six point Likert type response scale (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Always).
 As our purpose was to capture light exposure related behavior, ``Does not apply/I don't know'' and ``Never'' were providing similar information.
@@
 
-In the five-factor solution, the first factor contained three items and explained 10.25\% of the total variance with a satisfactory internal reliability coefficient (\(\alpha\) = .86).
+Internal consistency reliability coefficient Cronbach's alpha assumes that all the factor- loading of the items under a factor are equal (Graham, 2006; Novick \& Lewis, 1967) which is not the case in our sample.
+Additionally Cronbach's alpha coefficient has a tendency to deflate the estimates for Likert type data as the calculation is based on pearson-correlation matrix which requires that response data should be in continuous of nature (Gadermann, Guhn, \& Zumbo, 2012; Zumbo, Gadermann, \& Zeisser, 2007).
+Subsequently to get better estimates of reliability we reported ordinal alpha which used polychoric-correlation matrix and assumed that the responses data were ordered in nature instead of continuous.
+Ordinal alpha coefficient value ranges from 0 to 1 and higher value represents better reliability.
+In the five-factor solution, the first factor contained three items and explained 10.25\% of the total variance with a internal reliability coefficient ordinal \(\alpha\) = .94.
 All the items in this factor stemmed from the individual's preference to use blue light filters in different light environments.
-The second factor contained six items and explained 9.93\% of the total variance with a satisfactory internal reliability coefficient (\(\alpha\) = .71).
+The second factor contained six items and explained 9.93\% of the total variance with a internal reliability coefficient ordinal \(\alpha\) = .76.
 Items under this factor commonly investigate an individual's hours spent outdoor.
@@
 Items under this factor dealt with the specific behaviors pertaining to sleep.
-The internal consistency reliability coefficient was, \(\alpha\) = .68.
-The fourth factor contained five items and explained 8.44\% of the total variance with an internal consistency coefficient, \(\alpha\) = .62.
+The internal consistency reliability coefficient was, ordinal \(\alpha\) = .75.
+The fourth factor contained five items and explained 8.44\% of the total variance with an internal consistency coefficient, ordinal \(\alpha\) = .72.
 These five items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time.
@@
 This factor tried to measure an individual's behavior lead by the awareness of light's influence on health.
-However, this factor showed unsatisfactory internal consistency reliability (\(\alpha\) = .53).
+The internal consistency reliability was, ordinal \(\alpha\) = .62 .
 It is essential to attain a balance between psychometric properties and interpretability of the common themes when exploring the latent structure.
-As all of the emerged factors are highly interpretable and relevant towards our aim to capture light exposure related behavior, regardless of the apparent low reliability of the two factors, we retain the five-factor solution with 23 items for our confirmatory factor analysis (CFA).
+As all of the emerged factors are highly interpretable and relevant towards our aim to capture light exposure related behavior, regardless of the apparent low reliability of the fifth factor, we retain all the five-factors with 23 items for our confirmatory factor analysis (CFA).
 Two items showed negative factor-loading (items 44 and 21).
@@
 These indices can be categorized as absolute, comparative and parsimony fit indices (Brown, 2015).
-Absolute fit assess the model fit at an absolute level using indices including chi-square test statistics and the standardized root mean square (SRMR).parsimony fit indices including the root mean square error of approximation (RMSEA) considers the number of free parameters in the model to assess the parsimony of the model.
+Absolute fit assess the model fit at an absolute level using indices including \(\chi^2\) test statistics and the standardized root mean square (SRMR).parsimony fit indices including the root mean square error of approximation (RMSEA) considers the number of free parameters in the model to assess the parsimony of the model.
 Comparative fit indices evaluate the fit of the specified model solution in relation to a more restricted baseline model restricting all covariances among the idicators as zero.
 Comparative fit index (CFI) and the Tucker Lewis index (TLI) are such two comparative fit indices.
-Commonly used Model fit guidelines (Hu \& Bentle, 1999; Schumacker \& Lomax, 2004) includes (i) Reporting of chi-square test statistics (A non-significant test statistics is required to reflect model fit) (i) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (ii) RMSEA (close to .06 or below), (iii) SRMR (close to .08 or below) to estimate the model fit.
+Commonly used Model fit guidelines (Hu \& Bentle, 1999; Schumacker \& Lomax, 2004) includes (i) Reporting of \(\chi^2\) test statistics (A non-significant test statistics is required to reflect model fit) (i) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (ii) RMSEA (close to .06 or below), (iii) SRMR (close to .08 or below) to estimate the model fit.
 Table \ref{tab:tabCfa} summarizes the fit indices of our fitted model.
-Our fitted model failed to attain an absolute fit estimated by the chi-square test.
-However, the chi-square test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit (Brown, 2015).
+Our fitted model failed to attain an absolute fit estimated by the \(\chi^2\) test.
+However, the \(\chi^2\) test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit (Brown, 2015).
 Another absolute fit index we obtained in our analysis was SRMR which does not work well with categorical data (C.-Y.
@@
 Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 \& 26) for very low r-square value, our model attained best fit (CFI =.97; TLI = .96); RMSEA = .05{[}.04-.06, 90\% CI{]}) and SRMR value (SRMR = .09) was also close to the suggestions of Hu and Bentle (1999).
-Since reliability coefficient Cronbach's alpha tends to mis-measure reliability for multidimensional construct (Sijtsma, 2009) we report Mcdonald's omega(total) as the internal consistency reliability coefficient.
-Mcdonald's omega(total) is reported to be a satisfactory lower bound reliability coefficient that works for both unidimensional and multidimensional construct (Zinbarg, Revelle, Yovel, \& Li, 2005).
-Mcdonald's omega(total) for the five factors were .90, .80, .61, .72, .45 respectively.
-Mcdonald's omega(total) coefficient for the total scale was .73.
+
+Internal consistency ordinal \(\alpha\) for the five factors of LEBA were .96, .83, .70, .69, .52 respectively.
+We also estimated the internal consistency reliability of the total scale using Mcdonald's omega(total) coefficient which is a better reliability estimate for multidimensional constructs(Dunn, Baguley, \& Brunsden, 2014; Sijtsma, 2009).
+McDonald's omega(total) coefficient for the total scale was .73.
 
@@
 
+\hypertarget{measurement-invariance}{%
+\section{Measurement Invariance}\label{measurement-invariance}}
+
+Measurement invariance (MI) evaluates whether a construct has the psychometric equivalence and same meaning across groups or measurement occasions (Kline, 2015; Putnick \& Bornstein, 2016).
+We used structural equation modeling framework to assess measurement invariance of our developed tool across two groups: \textbf{native English speakers} and \textbf{non-native English speakers}.
+Our measurement invariance testing involved establishing configural, metric , scalar , and residual invariance (Widaman \& Reise, 1997).
+MI models are nested type models of which configural model is the first and least restrictive model.
+Configural model assumes that the number of factors and item number under each factors will be equal across two groups.
+Metric invariance model along with the assumption of configural model assumes that factor-loadings of the items across the two groups will be equal indicating each item contributes to the measured construct equivalently for the both groups.
+Along with these assumptions scalar invariance assumes that item intercepts to be equivalent across groups.
+Scalar invariance model indicates the equivalence of response scale across the groups, i.e.~persons with the same level of the underlying construct will score the same across the groups.
+Residual invariance model holds all the mentioned assumptions as true and also adds the assumption of equality in error variances and covariances across the groups.
+This model is the highest level of MI and assures the equivalence of precision of items across the groups in measuring the underlying constructs.
+The invariance model fit was assessed using the fit indices including \(\chi^2\) test, CFI and TLI (close to .95 or above) , RMSEA (close to .06 or below).
+following the guidelines of Hu and Bentle (1999).
+We excluded SRMR from our consideration as it does not behave optimally for categorical variables (C.-Y.
+Yu, 2002).
+Table \ref{tab:InvarianceTab} summarized the fit indices.
+The comparison among different measurement invariance model was made by using \(\chi^2\) difference test (\(\Delta \chi^2\)) to assess whether our obtained latent structure of ``LEBA'' attains the highest level of the MI.
+If the \(\Delta \chi^2\) is not statistically significant (p\textless0.05) (Dimitrov, 2010) the particular invariance model was accepted.
+We started our analysis by comparing the model fit of the lest restrictive model:configural model to metric MI model and continued successive comparisons.
+Table \ref{tab:InvarianceTab} indicates that our fiited model attains residual invariance: the highest level of invariance in terms of CFI, TLI, RMSEA and non-significant \(\Delta \chi^2\) test.
+
 \begin{lltable}
@@
 
-\scriptsize{
-
-\begin{longtable}{cccccccccccc}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\footnotesize{
+
+\begin{longtable}{ccccccccccc}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
 \caption{\label{tab:InvarianceTab}Invariance Analysis}\\
 \toprule
- & \multicolumn{1}{c}{Chi-Square} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{CFI} & \multicolumn{1}{c}{TLI} & \multicolumn{1}{c}{RMSEA} & \multicolumn{1}{c}{RMSEA 90\% Lower CI} & \multicolumn{1}{c}{RMSEA 90\% Upper} & \multicolumn{1}{c}{SRMR} & \multicolumn{1}{c}{Chi-Sqr comparison} & \multicolumn{1}{c}{df*} & \multicolumn{1}{c}{p}\\
+ & \multicolumn{1}{c}{Chi-Square} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{CFI} & \multicolumn{1}{c}{TLI} & \multicolumn{1}{c}{RMSEA} & \multicolumn{1}{c}{RMSEA 90\% Lower CI} & \multicolumn{1}{c}{RMSEA 90\% Upper} & \multicolumn{1}{c}{Chi-Square Difference} & \multicolumn{1}{c}{df difference*} & \multicolumn{1}{c}{p}\\
 \midrule
@@
 \toprule
- & \multicolumn{1}{c}{Chi-Square} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{CFI} & \multicolumn{1}{c}{TLI} & \multicolumn{1}{c}{RMSEA} & \multicolumn{1}{c}{RMSEA 90\% Lower CI} & \multicolumn{1}{c}{RMSEA 90\% Upper} & \multicolumn{1}{c}{SRMR} & \multicolumn{1}{c}{Chi-Sqr comparison} & \multicolumn{1}{c}{df*} & \multicolumn{1}{c}{p}\\
+ & \multicolumn{1}{c}{Chi-Square} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{CFI} & \multicolumn{1}{c}{TLI} & \multicolumn{1}{c}{RMSEA} & \multicolumn{1}{c}{RMSEA 90\% Lower CI} & \multicolumn{1}{c}{RMSEA 90\% Upper} & \multicolumn{1}{c}{Chi-Square Difference} & \multicolumn{1}{c}{df difference*} & \multicolumn{1}{c}{p}\\
 \midrule
 \endhead
-Configural & 632.20 & 442.00 & 0.95 & 0.94 & 0.06 & 0.05 & 0.07 & 0.13 & - & - & -\\
-Metric & 644.58 & 458.00 & 0.95 & 0.95 & 0.06 & 0.05 & 0.07 & 0.13 & 18.019a & 16 & 0.323\\
-Scalar & 714.19 & 522.00 & 0.95 & 0.95 & 0.05 & 0.04 & 0.06 & 0.13 & 67.961b & 64 & 0.344\\
-Residual & 714.19 & 522.00 & 0.95 & 0.95 & 0.05 & 0.04 & 0.06 & 0.13 & 0c & 0 & NA\\
-Structural & 691.49 & 542.00 & 0.96 & 0.96 & 0.05 & 0.04 & 0.06 & 0.13 & 12.617d & 20 & 0.893\\
+Configural & 632.20 & 442.00 & 0.95 & 0.94 & 0.06 & 0.05 & 0.07 & - & - & -\\
+Metric & 644.58 & 458.00 & 0.95 & 0.95 & 0.06 & 0.05 & 0.07 & 18.019a & 16 & 0.323\\
+Scalar & 714.19 & 522.00 & 0.95 & 0.95 & 0.05 & 0.04 & 0.06 & 67.961b & 64 & 0.344\\
+Residual & 714.19 & 522.00 & 0.95 & 0.95 & 0.05 & 0.04 & 0.06 & 0c & 0 & NA\\
 \bottomrule
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-dimitrov2010testing}{}}%
+Dimitrov, D. M. (2010). Testing for factorial invariance in the context of construct validation. \emph{Measurement and Evaluation in Counseling and Development}, \emph{43}(2), 121--149.
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-paran}{}}%
@@
 \emph{British Journal of Mathematical and Statistical Psychology}, \emph{38}(1), 67--86.
+
+\leavevmode\vadjust pre{\hypertarget{ref-dunn2014alpha}{}}%
+Dunn, T.
+J., Baguley, T., \& Brunsden, V.
+(2014).
+From alpha to omega: A practical solution to the pervasive problem of internal consistency estimation.
+\emph{British Journal of Psychology}, \emph{105}(3), 399--412.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-gadermann2012estimating}{}}%
+Gadermann, A.
+M., Guhn, M., \& Zumbo, B.
+D.
+(2012).
+Estimating ordinal reliability for likert-type and ordinal item response data: A conceptual, empirical, and practical guide.
+\emph{Practical Assessment, Research, and Evaluation}, \emph{17}(1), 3.
+
+\leavevmode\vadjust pre{\hypertarget{ref-graham2006congeneric}{}}%
+Graham, J.
+M.
+(2006).
+Congeneric and (essentially) tau-equivalent estimates of score reliability: What they are and how to use them.
+\emph{Educational and Psychological Measurement}, \emph{66}(6), 930--944.
+
 \leavevmode\vadjust pre{\hypertarget{ref-Harb.2015}{}}%
@@
 Navarro-Gonzalez, D., \& Lorenzo-Seva, U. (2021). \emph{EFA.MRFA: Dimensionality assessment using minimum rank factor analysis}. Retrieved from \url{https://CRAN.R-project.org/package=EFA.MRFA}
+
+\leavevmode\vadjust pre{\hypertarget{ref-novick1967coefficient}{}}%
+Novick, M. R., \& Lewis, C. (1967). Coefficient alpha and the reliability of composite measurements. \emph{Psychometrika}, \emph{32}(1), 1--13.
 
@@
 Pornprasertmanit, S., Miller, P., Schoemann, A., \& Jorgensen, T. D. (2021). \emph{Simsem: SIMulated structural equation modeling}. Retrieved from \url{https://CRAN.R-project.org/package=simsem}
+
+\leavevmode\vadjust pre{\hypertarget{ref-putnick2016measurement}{}}%
+Putnick, D.
+L., \& Bornstein, M.
+H.
+(2016).
+Measurement invariance conventions and reporting: The state of the art and future directions for psychological research.
+\emph{Developmental Review}, \emph{41}, 71--90.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-widaman1997exploring}{}}%
+Widaman, K. F., \& Reise, S. P. (1997). Exploring the measurement invariance of psychological instruments: Applications in the substance use domain.
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-cowplot}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-rsem}{}}%
+Yuan, K.-H., \& Zhang, Z. (2020). \emph{Rsem: Robust structural equation modeling with missing data and auxiliary variables}. Retrieved from \url{https://CRAN.R-project.org/package=rsem}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-Formula}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-coefficientalpha}{}}%
+Zhang, Z., \& Yuan, K.-H. (2020). \emph{Coefficientalpha: Robust coefficient alpha and omega with missing and non-normal data}. Retrieved from \url{https://CRAN.R-project.org/package=coefficientalpha}
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-kableExtra}{}}%
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-zinbarg2005cronbach}{}}%
-Zinbarg, R.
-E., Revelle, W., Yovel, I., \& Li, W.
-(2005).
-Cronbach's \(\alpha\), revelle's \(\beta\), and McDonald's \(\omega\) h: Their relations with each other and two alternative conceptualizations of reliability.
-\emph{Psychometrika}, \emph{70}(1), 123--133.
+\leavevmode\vadjust pre{\hypertarget{ref-zumbo2007ordinal}{}}%
+Zumbo, B. D., Gadermann, A. M., \& Zeisser, C. (2007). Ordinal versions of coefficients alpha and theta for likert rating scales. \emph{Journal of Modern Applied Statistical Methods}, \emph{6}(1), 4.
 

### 2021-11-13 manuscript.Rmd
* item fit and person fit are added

@@
         panel.background = element_blank(),
-        text=element_text(family = "Helvetica",),
+        #text=element_text(family = "Helvetica",),
         legend.title=element_blank(),
@@
 
-## Analysing the quality of items by Item Information Theory
-
-We sought the IRT to gether information regarding the item quality.
-IRT complements the conventional classical test theory-based analysis by gathering information on item discrimination and item difficulty[@bakerBasicsItemResponse2017].
-Here, an item's quality is judged based on item information in relation to participants' latent trait level ($\theta$).
-We gathered evidence on item quality by fitting each factor of LEBA with the graded response model (\@ref(tab:IRTparameters) to the combined EFA sample and CFA sample (n =690).
-Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait, and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
+## Developing Short form of LEBA
+
+We sought the item response theory (IRT) to develop the short form of LEBA.
+IRT the conventional classical test theory-based analysis by gathering information on item quality by indices like item difficulty,item discrimination, and item information[@bakerBasicsItemResponse2017].
+IRT judges the item's quality on item information in relation to participants' latent trait level ($\theta$).
+We gathered evidence on item quality by fitting each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690).
+Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait level ($\theta$), and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
 Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information <.2) to develop the short form of LEBA.
 @bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70.
-Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), low ( 5 items) indicating a good range of discrimination along the latent trait.
-Examination of the item information curve indicated 6 items (1, 25, 9, 38, 30, & 41) had relatively flat information curves thus discarded.
-We also gathered evidence of item fit and person fit to our fitted model.
+Table \@ref(tab:IRTparameters) summarizes the IRT parameters of our scale.
+Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$).
+Examination of the item information curve \@ref(fig:itmeinfo) indicated 6 items (1, 25, 9, 38, 30, & 41) had relatively flat information curves thus discarded creating a short form of LEBA with 5 factors and 17 items.
 
@@
 
-```{r itmeinfo, fig.cap="Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
+```{r itmeinfo, fig.cap="Item information curves (a) Blue filter (b) Natural light (c)Smart device (d)Sleep environment (e)Electic light", warning=FALSE, out.width="100%", out.height="120%"}
 plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
@@
 
-F5 <- sem.data %>% 
+F5.redu <- sem.data %>% 
   dplyr::select(item46, item45, item25 )
@@
 
-F5_fit <- mirt(F5, model = 1, itemtype = 'graded', SE = TRUE,
+F5_fit.redu <- mirt(F5, model = 1, itemtype = 'graded', SE = TRUE,
                Se.type = 'MHRM',technical = list(NCYCLES = 10000))
@@
 
-F5.item.fit<- itemfit(F5_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
+F5.item.fit<- itemfit(F5_fit.redu, fit_stats = c("S_X2", "G2","Zh", "infit"),
                                   impute=10)
+
+#Itemfit short
+#Item fit
+F1.item.fit<- itemfit(F1_fit, fit_stats = c("S_X2"),
+                                  impute=10)
+
+F2.item.fit<- itemfit(F2_fit.redu, fit_stats = c("S_X2"),
+                                  impute=10)
+F3.item.fit<- itemfit(F3_fit.redu, fit_stats = c("S_X2"),
+                                  impute=10)
+F4.item.fit<- itemfit(F4_fit.redu, fit_stats = c("S_X2"),
+                                  impute=10)
+
+F5.item.fit<- itemfit(F5_fit.redu, fit_stats = c("S_X2"),
+                                  impute=10)
+
+itemfit <- rbind(F1.item.fit,F2.item.fit,F3.item.fit,F4.item.fit,F5.item.fit)
+
+colnames(itemfit) <- c("Signed Chi-square", "df", "RMSEA", "p")
 
@@
 abline(v = -2, lwd = 2, lty = 2)
+F1.person <- ggplot(F1.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5)+geom_vline(xintercept = -2)+
+  labs( y="Number of Participants", x = "Zh Statistics")+apatheme
 
@@
 
+F2.person <- ggplot(F2.personfit, aes(x=Zh)) + geom_histogram(binwidth=.4)+
+  scale_x_continuous(limits = c(-5, 1))+geom_vline(xintercept = -2)+
+  labs( y="Number of Participants", x = "Zh Statistics")+apatheme
+
 ## F3 Person fit ####
@@
 
+F3.person <- ggplot(F3.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5)+geom_vline(xintercept = -2)+
+  labs( y="Number of Participants", x = "Zh Statistics")+apatheme
+
 ## F4 Person fit ####
@@
 
+F4.person <- ggplot(F4.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5)+geom_vline(xintercept = -2)+
+  labs( y="Number of Participants", x = "Zh Statistics")+apatheme
+
 ## F5 Person fit ####
@@
 abline(v = -2, lwd = 2, lty = 2)
+
+F5.person <- ggplot(F5.personfit, aes(x=Zh)) + geom_histogram(binwidth=.4)+geom_vline(xintercept = -2)+
+  labs( y="Number of Participants", x = "Zh Statistics")+apatheme
 
@@
 
-```{r Testinfo, fig.cap="Test information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light", warning=FALSE, out.width="100%", out.height="120%"}
-plot_grid(F1_test.info, F2_test.info.redu,F3_test.info.redu,F4_test.info.redu,F5_test.info, 
+```{r Testinfo, fig.cap="Test information curves (a) Blue filter (b) Natural light (c) Smart device (d) Sleep environment (E) Electic light", warning=FALSE, out.width="100%", out.height="120%"}
+plot_grid(F4.personfit, F2.personfit,F3.personfit,F4.personfit,F4.personfit,
           labels = "AUTO", label_size = 10, align = "v" )
@@
 
-Test information curve (TIC) indicate the amount of information an the full-scale carry along the latent trait continuum.
-As we treated each factor of LEBA as an unidmensional construct we obtain 5 TICs.
+Test information curve (TIC) (\@ref(fig:Testinfo)) indicate the amount of information an the full-scale carry along the latent trait continuum.
+As we treated each factor of short-LEBA as an unidmensional construct we obtain 5 TICs (\@ref(fig:Testinfo)).
 These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum (($\theta$)).
@@
 
-Our result also indicated all the items fitted well to the respective models as assessed by assessed by RMSEA value obtained from Signed-X2 index implementation.
+Table \@ref(tab:itemfittab) summarizes the item fit indexes of the items.
+All the items fitted well to the respective models as assessed by  RMSEA value obtained from Signed-$\chi^2$ index implementation.
 All of the items had RMSEA value <.06 indicating adequate fit.
+Figure \@ref(fig:persornfit) depicts the person fit of out fitted models.
 Person fit indicates the validity and meaningfulness of the fitted model at the participants latent trait level [@desjardinsHandbookEducationalMeasurement2018].
@@
 Fig indicates that Zh is larger than -2 for most participants, suggesting a good fit of the selected IRT models.
+```{r itemfittab, results='asis',warning=F, message=F}
+apa_table(itemfit)
+```
+
+```{r personfit, fig.cap="Person fit of the five fitted IRT models (a) Blue filter (b) Natural light (c)Smart device (d)Sleep environment (e)Electic light", warning=FALSE, out.width="100%", out.height="120%"}
+plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
+          labels = "AUTO", label_size = 10,align = "v")
+
+```
 
@@
 ```
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('Supplymentary.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('instrument.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('Supplymentary.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('instrument.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('Supplymentary.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('instrument.Rmd')
-```

### 2021-11-13 Supplymentary.tex
* IRT Finalize

@@
 
-\caption{\label{tab:MinResTab-56}Factor loadings and communality of the retained items(Minmum Residual)}
+\caption{\label{tab:MinResTab}Factor loadings and communality of the retained items(Minmum Residual)}
 
@@
 
-\caption{\label{tab:sixFacTab-58}Factor loadings and communality of the retained items(six factor)}
+\caption{\label{tab:sixFacTab}Factor loadings and communality of the retained items(six factor)}
 
@@
 
-\caption{\label{tab:tabDesAppB-62}Descriptive Statistics for Unmerged response options}
+\caption{\label{tab:tabDesAppB}Descriptive Statistics for Unmerged response options}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-64-1}
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-1}
 
@@
 
-\caption{Correlation plot of the items}(\#fig:figCorAppB-64)
+\caption{Correlation plot of the items}(\#fig:figCorAppB)
 \end{figure}
@@
 
-{\centering \includegraphics{manuscript_files/figure-latex/facIdFigAppB-68-1}
+{\centering \includegraphics{manuscript_files/figure-latex/facIdFigAppB-1}
 
@@
 
-\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}(\#fig:facIdFigAppB-68)
+\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}(\#fig:facIdFigAppB)
 \end{figure}
@@
 
-\caption{\label{tab:EFATableAppB-71}Factor loadings and communality of the retained items [Unmerged Responses]}
+\caption{\label{tab:EFATableAppB}Factor loadings and communality of the retained items [Unmerged Responses]}
 
@@
 
-{\centering \includegraphics{manuscript_files/figure-latex/EFAResidualsAppB-72-1}
+{\centering \includegraphics{manuscript_files/figure-latex/EFAResidualsAppB-1}
 
@@
 
-\caption{ Histogram of residulas:  five-factor solution}(\#fig:EFAResidualsAppB-72)
+\caption{ Histogram of residulas:  five-factor solution}(\#fig:EFAResidualsAppB)
 \end{figure}

### 2021-11-13 manuscript.Rmd
* IRT Finalize

@@
 ## Analytic Strategies
-We used R (version 4.1.0), including several R packages, for our analyses.Initially, our tool have six point Likert type response scale (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Always).
-As our purpose was to capture light exposure related behavior, "Does not apply/I don't know" and "Never" were providing similar information.
-As such we decided to collapse "Does not apply/I don't know" and "Never" options into one making it a 5 point Likert type response scale.
+For our analysis we used R (version 4.1.0), with several R packages.
+Initially, our tool had six point Likert type response scale (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Always).
+Our purpose was to capture light exposure related behavior and these two response options: "Does not apply/I don't know" and "Never" were providing similar information.
+As such we decided to collapse them into one making it a 5 point Likert type response scale.
 Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
 Our data violated both the univariate and multivariate normality assumptions.
-Due to these violations and the ordinal nature of our response data, we used a polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA.
-We employed principal axis (PA) as a factor extraction method with varimax rotation.
+Due to these violations and the ordinal nature of our response data, we used  polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA.
+We employed principal axis (PA) as  factor extraction method with varimax rotation.
 PA is robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020].
-The obtained latent structure was confirmed by another factor extraction method: the minimum residuals extraction method as well.
-We used a combination factor identification method including scree plot[@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method[@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
-Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018] We also conducted psychometric analysis on non-merged response options data (supplementary analysis) and rejected the latent structure obtained as the factors were less interpretable.
+The obtained latent structure was confirmed by another factor extraction method: "the minimum residuals extraction" as well.
+We used a combination of factor identification method including scree plot [@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method [@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
+Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018].
+We also conducted psychometric analysis on non-merged response options data (supplementary analysis) and rejected the latent structure obtained as the factors were less interpretable.
 
 # Results
-
-## Exploratory Factor Analysis
 
@@
 Descriptives <- psych::describe(EFA.data)
-alpha <- psych::alpha(EFA.data)
+alpha <- psych::alpha(EFA.data,check.keys=TRUE)
 Item.total <- alpha$item.stats
 
-Des.combined <- cbind(apa(Descriptives$mean,2,T), apa(Descriptives$sd,2,T), apa(Descriptives$skew,2,T),apa(Descriptives$kurtosis,2,T), efa.normality.stat,  apa(Item.total$r.cor,2,F))
+Des.combined <- cbind(apa(Descriptives$mean,2,T), apa(Descriptives$sd,2,T), apa(Descriptives$skew,2,T),apa(Descriptives$kurtosis,2,T), efa.normality.stat,  apa(Item.total$r.cor,2,T))
 
@@
 
+## Item Analysis
+```{r ItemAnalysis, include=FALSE}
+# Item analysis
+Item_analysis <- psych::alpha(EFA.data,check.keys=TRUE)
+Item_analysis$item.stats$r.cor
+low.r.corec <- (min(Item_analysis$item.stats$r.cor))  #minimum item total correlation
+high.r.corec <- (max(Item_analysis$item.stats$r.cor))     # maximum item total correlation
+```
+
+Table \@ref(tab:tabDes) summarizes the univariate descriptive statistics for the 48 items.
+Some of the items were skewed with high Kurtosis values.
+Our data violated both univariate normality (Shapiro-Wilk statistics; [@shapiroAnalysisVarianceTest1965]) and multivariate normality assumptions [Marida's test;[@mardiaMeasuresMultivariateSkewness1970]].
+Multivariate skew was = `r printnum(mardia$b1p)` (p <0.001) and multivariate kurtosis was = `r printnum(mardia$b2p)` (p <0.001).
+Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018].
+The corrected item-total correlation ranges between `r apa(low.r.corec,2,F)` -`r apa(high.r.corec,2,F)`.
+No item was discarded based on descriptive statistics or item analysis.
+
+## Exploratory Factor Analysis
+
 ```{r CorrMatrix, include=FALSE}
@@
 
-```{r ItemAnalysis, include=FALSE}
-# Item analysis
-Item_analysis <- psych::alpha(EFA.data)
-Item_analysis$item.stats$r.cor
-R.cor.sum <- summary(Item_analysis$item.stats$r.cor)
-low.r.corec <- abs(R.cor.sum[1])  #minimum item total correlation
-high.r.corec <- R.cor.sum[6]     # maximum item total correlation
-```
-
-Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy[@kaiserIndexFactorialSimplicity1974] .
+Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy [@kaiserIndexFactorialSimplicity1974] .
 The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cutoff value (.50) indicating a mediocre sample [@hutchesonMultivariateSocialScientist1999].
-Table\@ref(tab:tabDes) summarizes the univariate descriptive statistics for the 48 items.
-some of the items were skewed with high Kurtosis values.
-Our data violated both univariate normality (Shapiro-Wilk statistics; [@shapiroAnalysisVarianceTest1965]) and multivariate normality assumptions (Marida's test;[@mardiaMeasuresMultivariateSkewness1970]).
-Multivariate skew was = `r printnum(mardia$b1p)` (p <0.001) and multivariate kurtosis was = `r printnum(mardia$b2p)` (p <0.001).
-Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018].
 Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001] indicated the correlations between items are adequate for the EFA.
@@
 ```
-
 Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution.
@@
 
-With initial 48 items we conducted three rounds of EFA gradually discarded problematic items.
+With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items.
 (cross-loading items and poor factor loading (<.30) items).
@@
 However, the histogram of the absolute values of non-redundant residual-correlations Fig\@ref(fig:EFAResiduals) showed `r apa(sumR,0, T)`% correlations greater than the absolute value of .05, indicating a possible under-factoring.
-[@desjardinsHandbookEducationalMeasurement2018a].
+[@desjardinsHandbookEducationalMeasurement2018].
 Subsequently, we fitted a six-factor solution.
 However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution (Table\@ref(tab:sixFacTab)).
-
-Internal consistency reliability coefficient Cronbach's alpha assumes that all the factor- loading of the items under a factor are equal [@graham2006congeneric; @novick1967coefficient] which is not the case in our sample.
+Internal consistency reliability coefficient Cronbach's alpha assumes all the factor-loadings of the items under a factor are equal [@graham2006congeneric; @novick1967coefficient] which is not the case in our sample.
 Additionally Cronbach's alpha coefficient has a tendency to deflate the estimates for  Likert type data as the calculation is based on pearson-correlation matrix which requires that response data should be in continuous of nature [@gadermann2012estimating; @zumbo2007ordinal].
-Subsequently to get  better estimates of reliability we reported ordinal alpha which used polychoric-correlation matrix and assumed that the responses data were ordered in nature instead of continuous.
+Subsequently to get  better estimates of reliability we reported ordinal alpha which used polychoric-correlation matrix and assumed that the responses data were ordered in nature instead of continuous [@zumbo2007ordinal].
 Ordinal alpha coefficient value ranges from 0 to 1 and higher value represents better reliability.
@@
 The second factor contained six items and explained `r apa(var2,2,F)`% of the total variance with a  internal reliability coefficient ordinal $\alpha$ = `r apa(F2.alpha,2,F)`.
-Items under this factor commonly investigate an individual's hours spent outdoor.
+Items under this factor commonly investigated an individual's hours spent outdoor.
 The third factor contained five items and explained `r apa(var3,2,F)`% of the total variance.
-Items under this factor dealt with the specific behaviors pertaining to sleep.
+Items under this factor dealt with the specific behaviors pertaining to using phone and smart-watch in bed.
 The internal consistency reliability coefficient was, ordinal $\alpha$ = `r apa(F3.alpha,2,F)`.
 The fourth factor contained five items and explained `r apa(var4,2,F)`% of the total variance with an internal consistency coefficient, ordinal $\alpha$ = `r apa(F4.alpha,2,F)`.
-These five items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time.
+These five items investigated the behaviors related to individual's light exposure before bedtime.
 Lastly, the fifth factor contained six items and explained `r apa(var5,2,F)`% of the total variance.
-This factor tried to measure an individual's behavior lead by the awareness of light's influence on health.
+This factor  captured individual's morning and daytime light exposure related behavior.
 The  internal consistency reliability was, ordinal $\alpha$ = `r apa(F5.alpha,2,F)` .
@@
 ```
-
-We conducted a categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator as our response data was in ordinary nature[@desjardinsHandbookEducationalMeasurement2018].
-Several indices are suggested to measure model fit.
-These indices can be categorized as absolute, comparative and parsimony fit indices [@brownConfirmatoryFactorAnalysis2015].
-Absolute fit assess the model fit at an absolute level using indices including $\chi^2$ test statistics and the standardized root mean square (SRMR).parsimony fit indices including the root mean square error of approximation (RMSEA) considers the number of free parameters in the model to assess the parsimony of the model.
+We conducted categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator since our response data was of ordinary nature [@desjardinsHandbookEducationalMeasurement2018].
+Several indices are suggested to measure model fit which can be categorized as absolute, comparative and parsimony fit indices [@brownConfirmatoryFactorAnalysis2015].
+Absolute fit assess the model fit at an absolute level using indices including $\chi^2$ test statistics and the standardized root mean square (SRMR).
+Parsimony fit indices including the root mean square error of approximation (RMSEA) considers the number of free parameters in the model to assess the parsimony of the model.
 Comparative fit indices evaluate the fit of the specified model solution in relation to a more restricted baseline model restricting all covariances among the idicators as zero.
 Comparative fit index (CFI) and the Tucker Lewis index (TLI) are such two comparative fit indices.
-Commonly used Model fit guidelines [@huCutoffCriteriaFit1999; @schumacker2004beginner] includes (i) Reporting of $\chi^2$ test statistics (A non-significant test statistics is required to reflect model fit) (i) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (ii) RMSEA (close to .06 or below), (iii) SRMR (close to .08 or below) to estimate the model fit.
+Commonly used Model fit guidelines [@huCutoffCriteriaFit1999; @schumacker2004beginner] includes (i) Reporting of $\chi^2$ test statistics (A non-significant test statistics is required to reflect model fit) (ii) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (iii) RMSEA (close to .06 or below), (iv) SRMR (close to .08 or below) to estimate the model fit.
 Table \@ref(tab:tabCfa) summarizes the fit indices of our fitted model.
@@
 Another absolute fit index we obtained in our analysis was SRMR which does not work well with categorical data [@RN1272].
-Subsequently, we judged the model fit based on the comparative fit indices: CFI, TLI and parsimony fit index-RMSEA.
+We judged the model fit based on the comparative fit indices: CFI, TLI and parsimony fit index:RMSEA.
 Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`,[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 and 19-17 .
@@
 Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR value (SRMR = `r apa(fit.2[10],2,F)`) was also close to the suggestions of @huCutoffCriteriaFit1999.
-
 Internal consistency ordinal $\alpha$ for the five factors of LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)` respectively.
-We also estimated the internal consistency reliability of the total scale using Mcdonald's omega(total) coefficient which is a better reliability estimate for multidimensional constructs[@dunn2014alpha; @sijtsma2009use].
+We also estimated the internal consistency reliability of the total scale using Mcdonald's $\omega$ (total) coefficient which is a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
 McDonald's omega(total) coefficient for the total scale was `r apa(rel.k[5,6],2,F)`.
@@
 
-# Measurement Invariance
+## Measurement Invariance
 Measurement invariance (MI) evaluates whether a construct has the psychometric equivalence and same meaning across groups or measurement occasions [@putnick2016measurement;@klinePrinciplesPracticeStructural2015].
-We used a structural equation modeling framework to assess the measurement invariance of our developed tool across two groups: **native English speakers** and **non-native English speakers**.
-Our measurement invariance testing involved establishing configural, metric, scalar, and residual invariance [@widaman1997exploring].
-MI models are nested type models of which configural model is the first and least restrictive model.
+We used  structural equation modeling framework to assess the measurement invariance of our developed tool across two groups: **native English speakers** and **non-native English speakers**.
+Our measurement invariance testing involved successively comparing the nested models:  configural, metric, scalar, and residual invariance models with each others [@widaman1997exploring].
+Among these nested models  configural model is the first and least restrictive model.
 The configural model assumes that the number of factors and item number under each factor will be equal across two groups.
-The metric invariance model, along with the assumption of the configural model, assumes that factor-loadings of the items across the two groups will be equal, indicating each item contributes to the measured construct equivalently for both groups.
-Along with these assumptions, scalar invariance assumes that item intercepts to be equivalent across groups.
-The scalar invariance model indicates the equivalence of response scale across the groups, i.e., persons with the same level of the underlying construct will score the same across the groups.
-The residual invariance model holds all the mentioned assumptions as true and adds the assumption of equality in error variances and covariances across the groups.
+The metric invariance model assumes configural invariance of the fitted model and requires the factor-loadings of the items across the two groups to be equal.
+Having the factor-loadings equal across groups indicates each item contributes to the measured construct equivalently.
+Scalar invariance assumes the metric invariance of the fitted model demands the item intercepts to be equivalent across groups.
+This equity of item intercepts indicates the equivalence of response scale across the groups, i.e., persons with the same level of the underlying construct will score the same across the groups.
+The residual invariance model assumes metric invariance for the fitted model and adds the assumption of equality in error variances and covariances across the groups.
 This model is the highest level of MI and assures the equivalence of precision of items across the groups in measuring the underlying constructs.
-The invariance model fit was assessed using the fit indices including $\chi^2$ test, CFI and TLI (close to .95 or above), RMSEA (close to .06 or below) [@huCutoffCriteriaFit1999].
+The invariance model fit of our scale was assessed using the fit indices including $\chi^2$ test, CFI and TLI (close to .95 or above), RMSEA (close to .06 or below) [@huCutoffCriteriaFit1999].
 We excluded SRMR from our consideration as it does not behave optimally for categorical variables [@RN1272].
 Table \@ref(tab:InvarianceTab) summarized the fit indices.
-The comparison among different measurement invariance models was made using the $\chi^2$ difference test ($\Delta \chi^2$)  to assess whether our obtained latent structure of "LEBA" attains the highest level of the MI.
-If the $\Delta \chi^2$ test for model fit is not statistically significant (p<0.05) [@dimitrov2010testing], the particular invariance model was accepted.
+The comparison among different measurement invariance models was made using the $\chi^2$ difference test ($\Delta \chi^2$)  to assess whether our obtained latent structure of "LEBA" attained the highest level of the MI.
+A non-significant $\Delta \chi^2$ test between two MI models fit indicates mode fit does not significantly decrease for the superior model [@dimitrov2010testing] thus allowing the superior level of invariance model to be accepted.
 We started our analysis by comparing the model fit of the least restrictive model:configural model to metric MI model and continued successive comparisons.
 Table \@ref(tab:InvarianceTab) indicates that our fitted model had acceptable fit indices for all of the fitted MI models.
-The model fit does not significantly decrease across the nested models up to the scalar MI model.
+The model fit did not significantly decrease across the nested models up to the scalar MI model.
 The chi-square value difference between the scalar and residual model is zero, indicating model fit remained the same for both: scalar and residual MI model, indicating the acceptability of the residual MI model.
@@
 
-F5_test.info <- plot(F5_fit, type = "infoSE", main = "F5")
+F5_test.info <- plot(F5_fit.redu, type = "infoSE", main = "F5")
 
@@
 F4.scale <- plot(F4_fit.redu, type = 'score', theta_lim = c(-6, 6), main = "")
-F5.scale <- plot(F5_fit, type = 'score', theta_lim = c(-6, 6), main = "")
+F5.scale <- plot(F5_fit.redu, type = 'score', theta_lim = c(-6, 6), main = "")
 
@@
 ```{r Testinfo, fig.cap="Test information curves (a) Blue filter (b) Natural light (c) Smart device (d) Sleep environment (E) Electic light", warning=FALSE, out.width="100%", out.height="120%"}
-plot_grid(F4.personfit, F2.personfit,F3.personfit,F4.personfit,F4.personfit,
+plot_grid(F1_test.info , F2_test.info.redu,F3_test.info.redu,F4_test.info.redu,F5_test.info,
           labels = "AUTO", label_size = 10, align = "v" )
@@
 
-Test information curve (TIC) (\@ref(fig:Testinfo)) indicate the amount of information an the full-scale carry along the latent trait continuum.
-As we treated each factor of short-LEBA as an unidmensional construct we obtain 5 TICs (\@ref(fig:Testinfo)).
+Test information curve (TIC) (Figure \@ref(fig:Testinfo)) indicate the amount of information an the full-scale carry along the latent trait continuum.
+As we treated each factor of short-LEBA as an unidmensional construct we obtain 5 TICs (figure \@ref(Fig:Testinfo)).
 These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum (($\theta$)).
@@
 ```{r personfit, fig.cap="Person fit of the five fitted IRT models (a) Blue filter (b) Natural light (c)Smart device (d)Sleep environment (e)Electic light", warning=FALSE, out.width="100%", out.height="120%"}
-plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
+plot_grid(F1.person, F2.person,F3.person,F4.person,F5.person, 
           labels = "AUTO", label_size = 10,align = "v")
 
+```
+
+Next, we generated scale characteristics curve (Figure \@ref(fig:scalechar)) which plotted estimated theta score against the expected true score.
+The purpose of this scale characteristics curve is to find the corresponding expected true score for the given estimated theta score.
+
+```{r scalechar, fig.cap="Scale characteristic curve of the five fitted IRT models (a) Blue filter (b) Natural light (c)Smart device (d)Sleep environment (e)Electic light", warning=FALSE, out.width="100%", out.height="120%"}
+
+plot_grid(F1.scale, F1.scale,F1.scale,F1.scale,F1.scale, 
+          labels = "AUTO", label_size = 10,align = "v")
 ```

### 2021-11-13 manuscript.tex
* IRT Finalize

@@
 
-We used R (version 4.1.0), including several R packages, for our analyses.Initially, our tool have six point Likert type response scale (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Always).
-As our purpose was to capture light exposure related behavior, ``Does not apply/I don't know'' and ``Never'' were providing similar information.
-As such we decided to collapse ``Does not apply/I don't know'' and ``Never'' options into one making it a 5 point Likert type response scale.
+For our analysis we used R (version 4.1.0), with several R packages.
+Initially, our tool had six point Likert type response scale (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Always).
+Our purpose was to capture light exposure related behavior and these two response options: ``Does not apply/I don't know'' and ``Never'' were providing similar information.
+As such we decided to collapse them into one making it a 5 point Likert type response scale.
 Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
 Our data violated both the univariate and multivariate normality assumptions.
-Due to these violations and the ordinal nature of our response data, we used a polychoric correlation matrix (C.
-Desjardins \& Bulut, 2018) for the EFA.
-We employed principal axis (PA) as a factor extraction method with varimax rotation.
+Due to these violations and the ordinal nature of our response data, we used polychoric correlation matrix (Desjardins \& Bulut, 2018) for the EFA.
+We employed principal axis (PA) as factor extraction method with varimax rotation.
 PA is robust to the normality assumption violations (Watkins, 2020).
-The obtained latent structure was confirmed by another factor extraction method: the minimum residuals extraction method as well.
-We used a combination factor identification method including scree plot(Cattell, 1966), Horn's parallel analysis (Horn, 1965), minimum average partials method(Velicer, 1976), and hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) to identify factor numbers.
-Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \textless0.3 (iii) no items with cross-loading greater than .3 across factors (Bandalos \& Finney, 2018) We also conducted psychometric analysis on non-merged response options data (supplementary analysis) and rejected the latent structure obtained as the factors were less interpretable.
+The obtained latent structure was confirmed by another factor extraction method: ``the minimum residuals extraction'' as well.
+We used a combination of factor identification method including scree plot (Cattell, 1966), Horn's parallel analysis (Horn, 1965), minimum average partials method (Velicer, 1976), and hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) to identify factor numbers.
+Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \textless0.3 (iii) no items with cross-loading greater than .3 across factors (Bandalos \& Finney, 2018).
+We also conducted psychometric analysis on non-merged response options data (supplementary analysis) and rejected the latent structure obtained as the factors were less interpretable.
 
@@
 
+\hypertarget{item-analysis}{%
+\subsection{Item Analysis}\label{item-analysis}}
+
+Table \ref{tab:tabDes} summarizes the univariate descriptive statistics for the 48 items.
+Some of the items were skewed with high Kurtosis values.
+Our data violated both univariate normality (Shapiro-Wilk statistics; (Shapiro \& Wilk, 1965)) and multivariate normality assumptions {[}Marida's test;(Mardia, 1970){]}.
+Multivariate skew was = 583.80 (p \textless0.001) and multivariate kurtosis was = 2,749.15 (p \textless0.001).
+Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen (Desjardins \& Bulut, 2018).
+The corrected item-total correlation ranges between .03 -.48.
+No item was discarded based on descriptive statistics or item analysis.
+
 \hypertarget{exploratory-factor-analysis}{%
@@
 
-Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy(Kaiser, 1974) .
+Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy (Kaiser, 1974) .
 The overall KMO vale for 48 items was 0.63 which was above the cutoff value (.50) indicating a mediocre sample (Hutcheson, 1999).
-Table\ref{tab:tabDes} summarizes the univariate descriptive statistics for the 48 items.
-some of the items were skewed with high Kurtosis values.
-Our data violated both univariate normality (Shapiro-Wilk statistics; (Shapiro \& Wilk, 1965)) and multivariate normality assumptions (Marida's test;(Mardia, 1970)).
-Multivariate skew was = 583.80 (p \textless0.001) and multivariate kurtosis was = 2,749.15 (p \textless0.001).
-Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen (C.
-Desjardins \& Bulut, 2018).
 Bartlett's test of sphericity (Bartlett, 1954), \(\chi^2\) (1128) = 5042.86, p \textless{} .001{]} indicated the correlations between items are adequate for the EFA.
@@
 The inter item correlation ranged between .44 to .91.
-And the corrected item-total correlations ranged between .10 to .44.
+And the corrected item-total correlations ranged between .03 to .48.
 
@@
 \endhead
-Item1 & 2.27 & 1.39 & 0.74 & -0.81 & 0.81* & .25\\
-Item2 & 2.87 & 1.59 & 0.08 & -1.60 & 0.83* & .19\\
-Item3 & 3.36 & 1.38 & -0.48 & -1.03 & 0.87* & .16\\
-Item4 & 1.47 & 1.18 & 2.38 & 4.00 & 0.43* & .28\\
-Item5 & 4.01 & 1.40 & -1.22 & 0.07 & 0.70* & .13\\
-Item6 & 2.79 & 1.55 & 0.19 & -1.48 & 0.85* & .20\\
-Item7 & 2.26 & 1.25 & 0.70 & -0.60 & 0.85* & .19\\
-Item8 & 2.97 & 1.20 & -0.06 & -0.94 & 0.91* & -.10\\
-Item9 & 2.94 & 1.03 & -0.12 & -0.40 & 0.91* & .10\\
-Item10 & 2.74 & 1.04 & 0.09 & -0.74 & 0.91* & .28\\
-Item11 & 2.18 & 0.90 & 0.60 & 0.12 & 0.86* & .26\\
-Item12 & 2.36 & 1.22 & 0.59 & -0.62 & 0.87* & .25\\
-Item13 & 2.73 & 1.46 & 0.20 & -1.36 & 0.87* & .33\\
-Item14 & 2.14 & 1.31 & 0.77 & -0.78 & 0.80* & .26\\
-Item15 & 3.26 & 1.09 & -0.26 & -0.45 & 0.91* & .14\\
-Item16 & 1.56 & 1.23 & 2.00 & 2.45 & 0.50* & .32\\
-Item17 & 1.54 & 1.21 & 2.07 & 2.75 & 0.49* & .31\\
-Item18 & 1.12 & 0.49 & 5.02 & 27.80 & 0.25* & .16\\
-Item19 & 1.05 & 0.36 & 7.23 & 52.98 & 0.13* & .18\\
-Item20 & 1.04 & 0.33 & 8.99 & 85.28 & 0.10* & .16\\
-Item21 & 1.14 & 0.59 & 4.79 & 24.05 & 0.25* & .16\\
-Item22 & 3.57 & 1.07 & -0.65 & -0.17 & 0.88* & .21\\
-Item23 & 2.56 & 1.27 & 0.33 & -1.00 & 0.89* & .11\\
-Item24 & 4.14 & 0.99 & -1.23 & 1.14 & 0.79* & .19\\
-Item25 & 2.59 & 1.41 & 0.27 & -1.27 & 0.86* & .19\\
-Item26 & 2.25 & 1.27 & 0.69 & -0.64 & 0.84* & .18\\
-Item27 & 3.80 & 1.29 & -0.87 & -0.42 & 0.82* & .17\\
-Item28 & 3.76 & 1.14 & -0.68 & -0.45 & 0.86* & .00\\
-Item29 & 2.44 & 1.31 & 0.38 & -1.14 & 0.86* & .11\\
-Item30 & 1.48 & 1.11 & 2.18 & 3.35 & 0.48* & .24\\
-Item31 & 3.00 & 1.62 & -0.08 & -1.61 & 0.83* & .44\\
-Item32 & 3.55 & 1.65 & -0.60 & -1.34 & 0.76* & .43\\
-Item33 & 3.62 & 1.64 & -0.68 & -1.25 & 0.74* & .32\\
-Item34 & 3.42 & 1.83 & -0.45 & -1.69 & 0.69* & .33\\
-Item35 & 3.86 & 1.67 & -0.99 & -0.85 & 0.65* & .23\\
-Item36 & 1.54 & 1.25 & 2.13 & 2.86 & 0.46* & .36\\
-Item37 & 1.33 & 0.91 & 3.03 & 8.43 & 0.41* & .01\\
-Item38 & 4.30 & 1.08 & -1.79 & 2.53 & 0.67* & .22\\
-Item39 & 1.96 & 0.98 & 1.02 & 0.69 & 0.82* & .05\\
-Item40 & 2.16 & 1.19 & 0.71 & -0.54 & 0.84* & .14\\
-Item41 & 1.31 & 0.81 & 2.75 & 6.92 & 0.43* & .21\\
-Item42 & 3.93 & 1.48 & -1.06 & -0.44 & 0.71* & .18\\
-Item43 & 1.64 & 1.18 & 1.79 & 2.02 & 0.60* & .15\\
-Item44 & 3.51 & 1.30 & -0.70 & -0.59 & 0.85* & .39\\
-Item45 & 2.22 & 1.48 & 0.71 & -1.02 & 0.76* & .30\\
-Item46 & 1.76 & 1.23 & 1.35 & 0.44 & 0.66* & .38\\
-Item47 & 2.11 & 1.17 & 0.77 & -0.39 & 0.83* & .32\\
-Item48 & 2.60 & 1.25 & 0.29 & -0.86 & 0.89* & .35\\
+Item1 & 2.27 & 1.39 & 0.74 & -0.81 & 0.81* & 0.19\\
+Item2 & 2.87 & 1.59 & 0.08 & -1.60 & 0.83* & 0.28\\
+Item3 & 3.36 & 1.38 & -0.48 & -1.03 & 0.87* & 0.23\\
+Item4 & 1.47 & 1.18 & 2.38 & 4.00 & 0.43* & 0.24\\
+Item5 & 4.01 & 1.40 & -1.22 & 0.07 & 0.70* & 0.17\\
+Item6 & 2.79 & 1.55 & 0.19 & -1.48 & 0.85* & 0.13\\
+Item7 & 2.26 & 1.25 & 0.70 & -0.60 & 0.85* & 0.32\\
+Item8 & 2.97 & 1.20 & -0.06 & -0.94 & 0.91* & 0.25\\
+Item9 & 2.94 & 1.03 & -0.12 & -0.40 & 0.91* & 0.08\\
+Item10 & 2.74 & 1.04 & 0.09 & -0.74 & 0.91* & 0.42\\
+Item11 & 2.18 & 0.90 & 0.60 & 0.12 & 0.86* & 0.41\\
+Item12 & 2.36 & 1.22 & 0.59 & -0.62 & 0.87* & 0.48\\
+Item13 & 2.73 & 1.46 & 0.20 & -1.36 & 0.87* & 0.25\\
+Item14 & 2.14 & 1.31 & 0.77 & -0.78 & 0.80* & 0.28\\
+Item15 & 3.26 & 1.09 & -0.26 & -0.45 & 0.91* & 0.03\\
+Item16 & 1.56 & 1.23 & 2.00 & 2.45 & 0.50* & 0.28\\
+Item17 & 1.54 & 1.21 & 2.07 & 2.75 & 0.49* & 0.21\\
+Item18 & 1.12 & 0.49 & 5.02 & 27.80 & 0.25* & 0.18\\
+Item19 & 1.05 & 0.36 & 7.23 & 52.98 & 0.13* & 0.17\\
+Item20 & 1.04 & 0.33 & 8.99 & 85.28 & 0.10* & 0.16\\
+Item21 & 1.14 & 0.59 & 4.79 & 24.05 & 0.25* & 0.21\\
+Item22 & 3.57 & 1.07 & -0.65 & -0.17 & 0.88* & 0.20\\
+Item23 & 2.56 & 1.27 & 0.33 & -1.00 & 0.89* & 0.08\\
+Item24 & 4.14 & 0.99 & -1.23 & 1.14 & 0.79* & 0.22\\
+Item25 & 2.59 & 1.41 & 0.27 & -1.27 & 0.86* & 0.15\\
+Item26 & 2.25 & 1.27 & 0.69 & -0.64 & 0.84* & 0.08\\
+Item27 & 3.80 & 1.29 & -0.87 & -0.42 & 0.82* & 0.17\\
+Item28 & 3.76 & 1.14 & -0.68 & -0.45 & 0.86* & 0.18\\
+Item29 & 2.44 & 1.31 & 0.38 & -1.14 & 0.86* & 0.13\\
+Item30 & 1.48 & 1.11 & 2.18 & 3.35 & 0.48* & 0.13\\
+Item31 & 3.00 & 1.62 & -0.08 & -1.61 & 0.83* & 0.39\\
+Item32 & 3.55 & 1.65 & -0.60 & -1.34 & 0.76* & 0.33\\
+Item33 & 3.62 & 1.64 & -0.68 & -1.25 & 0.74* & 0.37\\
+Item34 & 3.42 & 1.83 & -0.45 & -1.69 & 0.69* & 0.20\\
+Item35 & 3.86 & 1.67 & -0.99 & -0.85 & 0.65* & 0.20\\
+Item36 & 1.54 & 1.25 & 2.13 & 2.86 & 0.46* & 0.35\\
+Item37 & 1.33 & 0.91 & 3.03 & 8.43 & 0.41* & 0.09\\
+Item38 & 4.30 & 1.08 & -1.79 & 2.53 & 0.67* & 0.32\\
+Item39 & 1.96 & 0.98 & 1.02 & 0.69 & 0.82* & 0.07\\
+Item40 & 2.16 & 1.19 & 0.71 & -0.54 & 0.84* & 0.25\\
+Item41 & 1.31 & 0.81 & 2.75 & 6.92 & 0.43* & 0.14\\
+Item42 & 3.93 & 1.48 & -1.06 & -0.44 & 0.71* & 0.15\\
+Item43 & 1.64 & 1.18 & 1.79 & 2.02 & 0.60* & 0.22\\
+Item44 & 3.51 & 1.30 & -0.70 & -0.59 & 0.85* & 0.40\\
+Item45 & 2.22 & 1.48 & 0.71 & -1.02 & 0.76* & 0.29\\
+Item46 & 1.76 & 1.23 & 1.35 & 0.44 & 0.66* & 0.39\\
+Item47 & 2.11 & 1.17 & 0.77 & -0.39 & 0.83* & 0.37\\
+Item48 & 2.60 & 1.25 & 0.29 & -0.86 & 0.89* & 0.36\\
 \bottomrule
@@
 
-With initial 48 items we conducted three rounds of EFA gradually discarded problematic items.
+With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items.
 (cross-loading items and poor factor loading (\textless.30) items).
@@
 However, the histogram of the absolute values of non-redundant residual-correlations Fig\ref{fig:EFAResiduals} showed 26\% correlations greater than the absolute value of .05, indicating a possible under-factoring.
-(C.
-D.
-Desjardins, 2018).
+(Desjardins \& Bulut, 2018).
 Subsequently, we fitted a six-factor solution.
@@
 
-We conducted a categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator as our response data was in ordinary nature(C.
-Desjardins \& Bulut, 2018).
+We conducted a categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator as our response data was in ordinary nature(Desjardins \& Bulut, 2018).
 Several indices are suggested to measure model fit.
@@
 Measurement invariance (MI) evaluates whether a construct has the psychometric equivalence and same meaning across groups or measurement occasions (Kline, 2015; Putnick \& Bornstein, 2016).
-We used structural equation modeling framework to assess measurement invariance of our developed tool across two groups: \textbf{native English speakers} and \textbf{non-native English speakers}.
-Our measurement invariance testing involved establishing configural, metric , scalar , and residual invariance (Widaman \& Reise, 1997).
+We used a structural equation modeling framework to assess the measurement invariance of our developed tool across two groups: \textbf{native English speakers} and \textbf{non-native English speakers}.
+Our measurement invariance testing involved establishing configural, metric, scalar, and residual invariance (Widaman \& Reise, 1997).
 MI models are nested type models of which configural model is the first and least restrictive model.
-Configural model assumes that the number of factors and item number under each factors will be equal across two groups.
-Metric invariance model along with the assumption of configural model assumes that factor-loadings of the items across the two groups will be equal indicating each item contributes to the measured construct equivalently for the both groups.
-Along with these assumptions scalar invariance assumes that item intercepts to be equivalent across groups.
-Scalar invariance model indicates the equivalence of response scale across the groups, i.e.~persons with the same level of the underlying construct will score the same across the groups.
-Residual invariance model holds all the mentioned assumptions as true and also adds the assumption of equality in error variances and covariances across the groups.
+The configural model assumes that the number of factors and item number under each factor will be equal across two groups.
+The metric invariance model, along with the assumption of the configural model, assumes that factor-loadings of the items across the two groups will be equal, indicating each item contributes to the measured construct equivalently for both groups.
+Along with these assumptions, scalar invariance assumes that item intercepts to be equivalent across groups.
+The scalar invariance model indicates the equivalence of response scale across the groups, i.e., persons with the same level of the underlying construct will score the same across the groups.
+The residual invariance model holds all the mentioned assumptions as true and adds the assumption of equality in error variances and covariances across the groups.
 This model is the highest level of MI and assures the equivalence of precision of items across the groups in measuring the underlying constructs.
-The invariance model fit was assessed using the fit indices including \(\chi^2\) test, CFI and TLI (close to .95 or above) , RMSEA (close to .06 or below).
-following the guidelines of Hu and Bentle (1999).
+The invariance model fit was assessed using the fit indices including \(\chi^2\) test, CFI and TLI (close to .95 or above), RMSEA (close to .06 or below) (Hu \& Bentle, 1999).
 We excluded SRMR from our consideration as it does not behave optimally for categorical variables (C.-Y.
@@
 Table \ref{tab:InvarianceTab} summarized the fit indices.
-The comparison among different measurement invariance model was made by using \(\chi^2\) difference test (\(\Delta \chi^2\)) to assess whether our obtained latent structure of ``LEBA'' attains the highest level of the MI.
-If the \(\Delta \chi^2\) is not statistically significant (p\textless0.05) (Dimitrov, 2010) the particular invariance model was accepted.
-We started our analysis by comparing the model fit of the lest restrictive model:configural model to metric MI model and continued successive comparisons.
-Table \ref{tab:InvarianceTab} indicates that our fiited model attains residual invariance: the highest level of invariance in terms of CFI, TLI, RMSEA and non-significant \(\Delta \chi^2\) test.
+The comparison among different measurement invariance models was made using the \(\chi^2\) difference test (\(\Delta \chi^2\)) to assess whether our obtained latent structure of ``LEBA'' attains the highest level of the MI.
+If the \(\Delta \chi^2\) test for model fit is not statistically significant (p\textless0.05) (Dimitrov, 2010), the particular invariance model was accepted.
+We started our analysis by comparing the model fit of the least restrictive model:configural model to metric MI model and continued successive comparisons.
+Table \ref{tab:InvarianceTab} indicates that our fitted model had acceptable fit indices for all of the fitted MI models.
+The model fit does not significantly decrease across the nested models up to the scalar MI model.
+The chi-square value difference between the scalar and residual model is zero, indicating model fit remained the same for both: scalar and residual MI model, indicating the acceptability of the residual MI model.
 
@@
 
-\hypertarget{analysing-the-quality-of-items-by-item-information-theory}{%
-\subsection{Analysing the quality of items by Item Information Theory}\label{analysing-the-quality-of-items-by-item-information-theory}}
-
-We sought the IRT to gether information regarding the item quality.
-IRT complements the conventional classical test theory-based analysis by gathering information on item discrimination and item difficulty(Baker, 2017).
-Here, an item's quality is judged based on item information in relation to participants' latent trait level (\(\theta\)).
-We gathered evidence on item quality by fitting each factor of LEBA with the graded response model (\ref{tab:IRTparameters} to the combined EFA sample and CFA sample (n =690).
-Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait, and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
+\hypertarget{developing-short-form-of-leba}{%
+\subsection{Developing Short form of LEBA}\label{developing-short-form-of-leba}}
+
+We sought the item response theory (IRT) to develop the short form of LEBA.
+IRT the conventional classical test theory-based analysis by gathering information on item quality by indices like item difficulty,item discrimination, and item information(Baker, 2017).
+IRT judges the item's quality on item information in relation to participants' latent trait level (\(\theta\)).
+We gathered evidence on item quality by fitting each factor of LEBA with the graded response model (Samejima, Liden, \& Hambleton, 1997) to the combined EFA and CFA sample (n =690).
+Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait level (\(\theta\)), and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
 Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information \textless.2) to develop the short form of LEBA.
 Baker (2017) categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \textgreater1.70.
-Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), low ( 5 items) indicating a good range of discrimination along the latent trait.
-Examination of the item information curve indicated 6 items (1, 25, 9, 38, 30, \& 41) had relatively flat information curves thus discarded.
-We also gathered evidence of item fit and person fit to our fitted model.
+Table \ref{tab:IRTparameters} summarizes the IRT parameters of our scale.
+Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level (\(\theta\)).
+Examination of the item information curve \ref{fig:itmeinfo} indicated 6 items (1, 25, 9, 38, 30, \& 41) had relatively flat information curves thus discarded creating a short form of LEBA with 5 factors and 17 items.
 
@@
 \begin{figure}
-\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/itmeinfo-1} \caption{Item information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light}\label{fig:itmeinfo}
+\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/itmeinfo-1} \caption{Item information curves (a) Blue filter (b) Natural light (c)Smart device (d)Sleep environment (e)Electic light}\label{fig:itmeinfo}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/Testinfo-1} \caption{Test information curves (A) blue filter (B) natural light (C)smart device (D)sleep environment (E)electic light}\label{fig:Testinfo}
+\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/Testinfo-1} \caption{Test information curves (a) Blue filter (b) Natural light (c) Smart device (d) Sleep environment (E) Electic light}\label{fig:Testinfo}
 \end{figure}
 
-Test information curve (TIC) indicate the amount of information an the full-scale carry along the latent trait continuum.
-As we treated each factor of LEBA as an unidmensional construct we obtain 5 TICs.
+Test information curve (TIC) (\ref{fig:Testinfo}) indicate the amount of information an the full-scale carry along the latent trait continuum.
+As we treated each factor of short-LEBA as an unidmensional construct we obtain 5 TICs (\ref{fig:Testinfo}).
 These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum ((\(\theta\))).
@@
 
-Our result also indicated all the items fitted well to the respective models as assessed by assessed by RMSEA value obtained from Signed-X2 index implementation.
+Table \ref{tab:itemfittab} summarizes the item fit indexes of the items.
+All the items fitted well to the respective models as assessed by RMSEA value obtained from Signed-\(\chi^2\) index implementation.
 All of the items had RMSEA value \textless.06 indicating adequate fit.
-Person fit indicates the validity and meaningfulness of the fitted model at the participants latent trait level (C.
-Desjardins \& Bulut, 2018).
+Figure \ref{fig:persornfit} depicts the person fit of out fitted models.
+Person fit indicates the validity and meaningfulness of the fitted model at the participants latent trait level (Desjardins \& Bulut, 2018).
 We estimated the person fit statistics using standardized fit index Zh statistics (Drasgow, Levine, \& Williams, 1985).
@@
 Fig indicates that Zh is larger than -2 for most participants, suggesting a good fit of the selected IRT models.
+
+\begin{table}[tbp]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:itemfittab}}
+
+\begin{tabular}{lllll}
+\toprule
+Signed Chi-square & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{RMSEA} & \multicolumn{1}{c}{p} & \multicolumn{1}{c}{NA}\\
+\midrule
+item16 & 2.01 & 6.00 & 0.00 & 0.92\\
+item36 & 39.06 & 13.00 & 0.05 & 0.00\\
+item17 & 25.58 & 13.00 & 0.04 & 0.02\\
+item11 & 24.42 & 21.00 & 0.02 & 0.27\\
+item10 & 37.39 & 25.00 & 0.03 & 0.05\\
+item12 & 36.60 & 34.00 & 0.01 & 0.35\\
+item7 & 47.23 & 40.00 & 0.02 & 0.20\\
+Ritem8 & 81.87 & 36.00 & 0.04 & 0.00\\
+item27 & 16.41 & 11.00 & 0.03 & 0.13\\
+item3 & 15.10 & 11.00 & 0.02 & 0.18\\
+item40 & 9.91 & 9.00 & 0.01 & 0.36\\
+item32 & 41.38 & 15.00 & 0.05 & 0.00\\
+item35 & 41.68 & 14.00 & 0.05 & 0.00\\
+item33 & 47.04 & 14.00 & 0.06 & 0.00\\
+item46 & 49.04 & 33.00 & 0.03 & 0.04\\
+item45 & 39.55 & 32.00 & 0.02 & 0.17\\
+item25 & 51.56 & 36.00 & 0.03 & 0.04\\
+item4 & 35.12 & 35.00 & 0.00 & 0.46\\
+item1 & 32.85 & 39.00 & 0.00 & 0.75\\
+\bottomrule
+\end{tabular}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\begin{figure}
+\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/personfit-1} \caption{Person fit of the five fitted IRT models (a) Blue filter (b) Natural light (c)Smart device (d)Sleep environment (e)Electic light}\label{fig:personfit}
+\end{figure}
+
+Next, we generated scale characteristics curve (\ref{fig:scalechar}) which plotted estimated theta score against the expected true score.
+The purpose of this scale characteristics curve is to find the corresponding expected true score for the given estimated theta score.
+
+\begin{figure}
+\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/scalechar-1} \caption{Scale characteristic curve of the five fitted IRT models (a) Blue filter (b) Natural light (c)Smart device (d)Sleep environment (e)Electic light}\label{fig:scalechar}
+\end{figure}
 
@@
 Dahl, D. B., Scott, D., Roosen, C., Magnusson, A., \& Swinton, J. (2019). \emph{Xtable: Export tables to LaTeX or HTML}. Retrieved from \url{https://CRAN.R-project.org/package=xtable}
-
-\leavevmode\vadjust pre{\hypertarget{ref-desjardinsHandbookEducationalMeasurement2018a}{}}%
-Desjardins, C. D. (2018). \emph{Handbook of educational measurement and psychometrics using {R}}. (O. Bulut \& ProQuest (Firm), Eds.). {Boca Raton, FL : CRC Press}.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-samejima1997handbook}{}}%
+Samejima, F., Liden, W. van der, \& Hambleton, R. (1997). Handbook of modern item response theory. New York, NY: Springer.
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-lattice}{}}%
@@
 
-\caption{Correlation plot of the items}\label{fig:figCorAppB-64}
+\caption{Correlation plot of the items}\label{fig:figCorAppB}
 \end{figure}
@@
 
-\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}\label{fig:facIdFigAppB-68}
+\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}\label{fig:facIdFigAppB}
 \end{figure}
@@
 
-\caption{ Histogram of residulas:  five-factor solution}\label{fig:EFAResidualsAppB-72}
+\caption{ Histogram of residulas:  five-factor solution}\label{fig:EFAResidualsAppB}
 \end{figure}

### 2021-11-13 Supplymentary.Rmd
* Modification figure-captions

@@
 
-apa_table(efa.table,align = "c", caption = "Factor loadings and communality of the retained items [Unmerged Responses]", note = "Only loading higher than .30 is reported", font_size = "small", placement = "h")
+apa_table(efa.table,align = "c", caption = "Factor loadings and communality of the retained items [Unmerged Responses]", note = "Only loading higher than .30 is reported", font_size = "small", longtable =T)
 ```

### 2021-11-13 Supplymentary.tex
* Modification figure-captions

@@
 
-\begin{table}[h]
+\begin{center}
+\begin{ThreePartTable}
 
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:EFATableAppB}Factor loadings and communality of the retained items [Unmerged Responses]}
+\begin{TableNotes}[para]
+\normalsize{\textit{Note.} Only loading higher than .30 is reported}
+\end{TableNotes}
 
@@
 
-\begin{tabular}{ccccccccc}
+\begin{longtable}{ccccccccc}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:EFATableAppB}Factor loadings and communality of the retained items [Unmerged Responses]}\\
 \toprule
@@
 \midrule
+\endfirsthead
+\caption*{\normalfont{Table \ref{tab:EFATableAppB} continued}}\\
+\toprule
+item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness} & \multicolumn{1}{c}{Complexity}\\
+\midrule
+\endhead
 item19 & 0.99 &  &  &  &  & 1.007 & -0.007 & 1.058\\
@@
 \addlinespace
-\end{tabular}
+\insertTableNotes
+\end{longtable}
 
@@
 
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} Only loading higher than .30 is reported}
-\end{tablenotes}
-
-\end{threeparttable}
+\end{ThreePartTable}
 \end{center}
-
-\end{table}
 

### 2021-11-13 instrument.tex
* Modification figure-captions

@@
 \end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Reliability Coefficients: Cronbach's alpha
+Reliability Coefficients: Ordinal alpha
 \end{minipage} \\
@@
 \endhead
-\textbf{F1: Wearing blue light filters} & 1-3 & .93 & .90 \\
+F1: Wearing blue light filters & 1-3 & .93 & .90 \\
 F2: Spending time outdoors & 4-9 (Item 4 is reversed) & .80 & .78 \\
-\textbf{F3: Using phone and smartwatch in bed} & 10-14 & .61 & .62 \\
-\textbf{F4: Using light before bedtime} & 15-18 & .72 & .62 \\
-\textbf{F5: Using light in the morning and during daytime} & 19-23 & .45
-& .41 \\
+F3: Using phone and smartwatch in bed & 10-14 & .61 & .62 \\
+F4: Using light before bedtime & 15-18 & .72 & .62 \\
+F5: Using light in the morning and during daytime & 19-23 & .45 & .41 \\
 & & .73(Total scale) & \\

### 2021-11-13 manuscript.Rmd
* Modification figure-captions

@@
                       Alpha F1=.93; F2=.80; F3 =.62; F4=.72; F5=.45']
+                    8[label = 'LEBA Short Form (17 Items; N=690) 
+                      Based on Item Response Theory']
                     }
@@
                      4 ->5
+                    5->8
                      C ->6
@@
 
-```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of LEBA', out.height='100%', out.width='100%'}
+```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='100%', out.width='100%'}
 knitr::include_graphics('Manuscript.figures/Flowchart1.png')
@@
 
-```{r figCor, out.width="100%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}
+```{r figCor, out.height="150%",out.width="100%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}
 
@@
 
-```{r facIdFig, out.height="200%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}
+```{r facIdFig, out.height="250%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}
 cowplot::plot_grid(parallel, scree.plot,Hull, labels = "AUTO",ncol=1, label_size = 8,align = "v")
@@
 
-```{r EFAplot, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, out.height="50%", out.width="100%", results='asis'}
+```{r EFAplot, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, out.height="100%", out.width="200%", results='asis'}
 knitr::include_graphics('Manuscript.figures/EFAplot.png')
@@
 
-```{r EFAResiduals, out.height= "50%",  fig.align='center', fig.cap= ' Histogram of residulas:  five-factor solution',  out.width="50%",  warning=FALSE, results='asis'}
+```{r EFAResiduals, out.height= "50%",  fig.align='center', fig.cap= ' Histogram of residuals:  five-factor solution',  out.width="50%",  warning=FALSE, results='asis'}
 hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))
@@
     title = md("**LEBA**"),
-    subtitle = md("Summary results of LEBA (N =690)")
+    subtitle = md("Summary Descriptives of CFA and EFA Sample (N =690)")
   ) %>% 
@@
 
-```{r gtPic, echo=FALSE, out.height="100%", out.width="200%", results= 'asis'}
+```{r gtPic, echo=FALSE, out.height="100%", out.width="200%", fig.cap= ' Summary Descriptives of CFA and EFA Sample'}
 knitr::include_graphics('Manuscript.figures/gt.png')
@@
 
-```{r figcfa, fig.cap = "(A) Five Factor Model of LEBA", , out.width="100%",  warning=FALSE, results='asis'}
+```{r figcfa, fig.cap = "Five Factor CFA Model of LEBA", out.height="150%", out.width="100%",  warning=FALSE}
 #library(semPlot)
@@
 
-```{r itmeinfo, fig.cap="Item information curves (a) Blue filter (b) Natural light (c)Smart device (d)Sleep environment (e)Electic light", warning=FALSE, out.width="100%", out.height="120%"}
+```{r itmeinfo, fig.cap="Item information curves (a) Wearing blue light filters (b) Spending time outdoors (c)Using phone and smartwatchin bed (d)Using light before bedtime (e)Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
 plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
@@
 
-```{r Testinfo, fig.cap="Test information curves (a) Blue filter (b) Natural light (c) Smart device (d) Sleep environment (E) Electic light", warning=FALSE, out.width="100%", out.height="120%"}
+```{r Testinfo, fig.cap="Test information curves (a) Wearing blue light filters (b) Spending time outdoors (c)Using phone and smartwatchin bed (d)Using light before bedtime (e)Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
 plot_grid(F1_test.info , F2_test.info.redu,F3_test.info.redu,F4_test.info.redu,F5_test.info,
@@
 ```{r itemfittab, results='asis',warning=F, message=F}
-apa_table(itemfit)
-```
-
-```{r personfit, fig.cap="Person fit of the five fitted IRT models (a) Blue filter (b) Natural light (c)Smart device (d)Sleep environment (e)Electic light", warning=FALSE, out.width="100%", out.height="120%"}
+apa_table(itemfit, caption ="Item fit statistics for the fitted models")
+```
+
+```{r personfit, fig.cap="Person fit of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c)Using phone and smartwatchin bed (d)Using light before bedtime (e)Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
 plot_grid(F1.person, F2.person,F3.person,F4.person,F5.person, 
@@
 
-```{r scalechar, fig.cap="Scale characteristic curve of the five fitted IRT models (a) Blue filter (b) Natural light (c)Smart device (d)Sleep environment (e)Electic light", warning=FALSE, out.width="100%", out.height="120%"}
+```{r scalechar, fig.cap="Scale characteristic curve of the five fitted IRT models ((a) Wearing blue light filters (b) Spending time outdoors (c)Using phone and smartwatchin bed (d)Using light before bedtime (e)Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
 
@@
 ```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('Supplymentary.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('instrument.Rmd')
-```

### 2021-11-13 manuscript.tex
* Modification figure-captions

@@
 
-\caption{Development of LEBA}\label{fig:FlowchartFig}
+\caption{Development of long and short form of LEBA}\label{fig:FlowchartFig}
 \end{figure}
@@
 
-{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCor-1}
+{\centering \includegraphics[width=1\linewidth,height=1.5\textheight]{manuscript_files/figure-latex/figCor-1}
 
@@
 
-{\centering \includegraphics[width=1\linewidth,height=2\textheight]{manuscript_files/figure-latex/facIdFig-1}
+{\centering \includegraphics[width=1\linewidth,height=2.5\textheight]{manuscript_files/figure-latex/facIdFig-1}
 
@@
 
-{\centering \includegraphics[width=1\linewidth,height=0.5\textheight]{Manuscript.figures/EFAplot}
+{\centering \includegraphics[width=2\linewidth,height=1\textheight]{Manuscript.figures/EFAplot}
 
@@
 However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution (Table\ref{tab:sixFacTab}).
-
-Internal consistency reliability coefficient Cronbach's alpha assumes that all the factor- loading of the items under a factor are equal (Graham, 2006; Novick \& Lewis, 1967) which is not the case in our sample.
+Internal consistency reliability coefficient Cronbach's alpha assumes all the factor-loadings of the items under a factor are equal (Graham, 2006; Novick \& Lewis, 1967) which is not the case in our sample.
 Additionally Cronbach's alpha coefficient has a tendency to deflate the estimates for Likert type data as the calculation is based on pearson-correlation matrix which requires that response data should be in continuous of nature (Gadermann, Guhn, \& Zumbo, 2012; Zumbo, Gadermann, \& Zeisser, 2007).
-Subsequently to get better estimates of reliability we reported ordinal alpha which used polychoric-correlation matrix and assumed that the responses data were ordered in nature instead of continuous.
+Subsequently to get better estimates of reliability we reported ordinal alpha which used polychoric-correlation matrix and assumed that the responses data were ordered in nature instead of continuous (Zumbo et al., 2007).
 Ordinal alpha coefficient value ranges from 0 to 1 and higher value represents better reliability.
@@
 The second factor contained six items and explained 9.93\% of the total variance with a internal reliability coefficient ordinal \(\alpha\) = .76.
-Items under this factor commonly investigate an individual's hours spent outdoor.
+Items under this factor commonly investigated an individual's hours spent outdoor.
 The third factor contained five items and explained 8.83\% of the total variance.
-Items under this factor dealt with the specific behaviors pertaining to sleep.
+Items under this factor dealt with the specific behaviors pertaining to using phone and smart-watch in bed.
 The internal consistency reliability coefficient was, ordinal \(\alpha\) = .75.
 The fourth factor contained five items and explained 8.44\% of the total variance with an internal consistency coefficient, ordinal \(\alpha\) = .72.
-These five items stemmed from the behavior related to an individual's cellphone usage during the sleep-wakeup time.
+These five items investigated the behaviors related to individual's light exposure before bedtime.
 Lastly, the fifth factor contained six items and explained 6.14\% of the total variance.
-This factor tried to measure an individual's behavior lead by the awareness of light's influence on health.
+This factor captured individual's morning and daytime light exposure related behavior.
 The internal consistency reliability was, ordinal \(\alpha\) = .62 .
@@
 
-\caption{ Histogram of residulas:  five-factor solution}\label{fig:EFAResiduals}
+\caption{ Histogram of residuals:  five-factor solution}\label{fig:EFAResiduals}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=2\linewidth,height=1\textheight]{Manuscript.figures/gt} \caption{ }\label{fig:gtPic}
+\includegraphics[width=2\linewidth,height=1\textheight]{Manuscript.figures/gt} \caption{ Summary Descriptives of CFA and EFA Sample}\label{fig:gtPic}
 \end{figure}
@@
 
-We conducted a categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator as our response data was in ordinary nature(Desjardins \& Bulut, 2018).
-Several indices are suggested to measure model fit.
-These indices can be categorized as absolute, comparative and parsimony fit indices (Brown, 2015).
-Absolute fit assess the model fit at an absolute level using indices including \(\chi^2\) test statistics and the standardized root mean square (SRMR).parsimony fit indices including the root mean square error of approximation (RMSEA) considers the number of free parameters in the model to assess the parsimony of the model.
+We conducted categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator since our response data was of ordinary nature (Desjardins \& Bulut, 2018).
+Several indices are suggested to measure model fit which can be categorized as absolute, comparative and parsimony fit indices (Brown, 2015).
+Absolute fit assess the model fit at an absolute level using indices including \(\chi^2\) test statistics and the standardized root mean square (SRMR).
+Parsimony fit indices including the root mean square error of approximation (RMSEA) considers the number of free parameters in the model to assess the parsimony of the model.
 Comparative fit indices evaluate the fit of the specified model solution in relation to a more restricted baseline model restricting all covariances among the idicators as zero.
 Comparative fit index (CFI) and the Tucker Lewis index (TLI) are such two comparative fit indices.
-Commonly used Model fit guidelines (Hu \& Bentle, 1999; Schumacker \& Lomax, 2004) includes (i) Reporting of \(\chi^2\) test statistics (A non-significant test statistics is required to reflect model fit) (i) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (ii) RMSEA (close to .06 or below), (iii) SRMR (close to .08 or below) to estimate the model fit.
+Commonly used Model fit guidelines (Hu \& Bentle, 1999; Schumacker \& Lomax, 2004) includes (i) Reporting of \(\chi^2\) test statistics (A non-significant test statistics is required to reflect model fit) (ii) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (iii) RMSEA (close to .06 or below), (iv) SRMR (close to .08 or below) to estimate the model fit.
 Table \ref{tab:tabCfa} summarizes the fit indices of our fitted model.
@@
 However, the \(\chi^2\) test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit (Brown, 2015).
-Another absolute fit index we obtained in our analysis was SRMR which does not work well with categorical data (C.-Y.
+Another absolute fit index we obtained in our analysis was SRMR which does not work well with categorical data (C.
 Yu, 2002).
-Subsequently, we judged the model fit based on the comparative fit indices: CFI, TLI and parsimony fit index-RMSEA.
+We judged the model fit based on the comparative fit indices: CFI, TLI and parsimony fit index:RMSEA.
 Our fitted model attained acceptable fit (CFI =.94; TLI = .93); RMSEA = .06,{[}.05-.07, 90\% CI{]}) with two imposed equity constrain on item pairs 32-33 and 19-17 .
@@
 Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 \& 26) for very low r-square value, our model attained best fit (CFI =.97; TLI = .96); RMSEA = .05{[}.04-.06, 90\% CI{]}) and SRMR value (SRMR = .09) was also close to the suggestions of Hu and Bentle (1999).
-
 Internal consistency ordinal \(\alpha\) for the five factors of LEBA were .96, .83, .70, .69, .52 respectively.
-We also estimated the internal consistency reliability of the total scale using Mcdonald's omega(total) coefficient which is a better reliability estimate for multidimensional constructs(Dunn, Baguley, \& Brunsden, 2014; Sijtsma, 2009).
+We also estimated the internal consistency reliability of the total scale using Mcdonald's \(\omega\) (total) coefficient which is a better reliability estimate for multidimensional constructs (Dunn, Baguley, \& Brunsden, 2014; Sijtsma, 2009).
 McDonald's omega(total) coefficient for the total scale was .73.
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figcfa-1} \caption{(A) Five Factor Model of LEBA}\label{fig:figcfa}
+\includegraphics[width=1\linewidth,height=1.5\textheight]{manuscript_files/figure-latex/figcfa-1} \caption{Five Factor CFA Model of LEBA}\label{fig:figcfa}
 \end{figure}
@@
 \hypertarget{measurement-invariance}{%
-\section{Measurement Invariance}\label{measurement-invariance}}
+\subsection{Measurement Invariance}\label{measurement-invariance}}
 
 Measurement invariance (MI) evaluates whether a construct has the psychometric equivalence and same meaning across groups or measurement occasions (Kline, 2015; Putnick \& Bornstein, 2016).
-We used a structural equation modeling framework to assess the measurement invariance of our developed tool across two groups: \textbf{native English speakers} and \textbf{non-native English speakers}.
-Our measurement invariance testing involved establishing configural, metric, scalar, and residual invariance (Widaman \& Reise, 1997).
-MI models are nested type models of which configural model is the first and least restrictive model.
+We used structural equation modeling framework to assess the measurement invariance of our developed tool across two groups: \textbf{native English speakers} and \textbf{non-native English speakers}.
+Our measurement invariance testing involved successively comparing the nested models: configural, metric, scalar, and residual invariance models with each others (Widaman \& Reise, 1997).
+Among these nested models configural model is the first and least restrictive model.
 The configural model assumes that the number of factors and item number under each factor will be equal across two groups.
-The metric invariance model, along with the assumption of the configural model, assumes that factor-loadings of the items across the two groups will be equal, indicating each item contributes to the measured construct equivalently for both groups.
-Along with these assumptions, scalar invariance assumes that item intercepts to be equivalent across groups.
-The scalar invariance model indicates the equivalence of response scale across the groups, i.e., persons with the same level of the underlying construct will score the same across the groups.
-The residual invariance model holds all the mentioned assumptions as true and adds the assumption of equality in error variances and covariances across the groups.
+The metric invariance model assumes configural invariance of the fitted model and requires the factor-loadings of the items across the two groups to be equal.
+Having the factor-loadings equal across groups indicates each item contributes to the measured construct equivalently.
+Scalar invariance assumes the metric invariance of the fitted model demands the item intercepts to be equivalent across groups.
+This equity of item intercepts indicates the equivalence of response scale across the groups, i.e., persons with the same level of the underlying construct will score the same across the groups.
+The residual invariance model assumes metric invariance for the fitted model and adds the assumption of equality in error variances and covariances across the groups.
 This model is the highest level of MI and assures the equivalence of precision of items across the groups in measuring the underlying constructs.
-The invariance model fit was assessed using the fit indices including \(\chi^2\) test, CFI and TLI (close to .95 or above), RMSEA (close to .06 or below) (Hu \& Bentle, 1999).
-We excluded SRMR from our consideration as it does not behave optimally for categorical variables (C.-Y.
+The invariance model fit of our scale was assessed using the fit indices including \(\chi^2\) test, CFI and TLI (close to .95 or above), RMSEA (close to .06 or below) (Hu \& Bentle, 1999).
+We excluded SRMR from our consideration as it does not behave optimally for categorical variables (C.
 Yu, 2002).
 Table \ref{tab:InvarianceTab} summarized the fit indices.
-The comparison among different measurement invariance models was made using the \(\chi^2\) difference test (\(\Delta \chi^2\)) to assess whether our obtained latent structure of ``LEBA'' attains the highest level of the MI.
-If the \(\Delta \chi^2\) test for model fit is not statistically significant (p\textless0.05) (Dimitrov, 2010), the particular invariance model was accepted.
+The comparison among different measurement invariance models was made using the \(\chi^2\) difference test (\(\Delta \chi^2\)) to assess whether our obtained latent structure of ``LEBA'' attained the highest level of the MI.
+A non-significant \(\Delta \chi^2\) test between two MI models fit indicates mode fit does not significantly decrease for the superior model (Dimitrov, 2010) thus allowing the superior level of invariance model to be accepted.
 We started our analysis by comparing the model fit of the least restrictive model:configural model to metric MI model and continued successive comparisons.
 Table \ref{tab:InvarianceTab} indicates that our fitted model had acceptable fit indices for all of the fitted MI models.
-The model fit does not significantly decrease across the nested models up to the scalar MI model.
+The model fit did not significantly decrease across the nested models up to the scalar MI model.
 The chi-square value difference between the scalar and residual model is zero, indicating model fit remained the same for both: scalar and residual MI model, indicating the acceptability of the residual MI model.
@@
 \begin{figure}
-\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/itmeinfo-1} \caption{Item information curves (a) Blue filter (b) Natural light (c)Smart device (d)Sleep environment (e)Electic light}\label{fig:itmeinfo}
+\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/itmeinfo-1} \caption{Item information curves (a) Wearing blue light filters (b) Spending time outdoors (c)Using phone and smartwatchin bed (d)Using light before bedtime (e)Using light in the morning andduring daytime}\label{fig:itmeinfo}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/Testinfo-1} \caption{Test information curves (a) Blue filter (b) Natural light (c) Smart device (d) Sleep environment (E) Electic light}\label{fig:Testinfo}
+\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/Testinfo-1} \caption{Test information curves (a) Wearing blue light filters (b) Spending time outdoors (c)Using phone and smartwatchin bed (d)Using light before bedtime (e)Using light in the morning andduring daytime}\label{fig:Testinfo}
 \end{figure}
 
-Test information curve (TIC) (\ref{fig:Testinfo}) indicate the amount of information an the full-scale carry along the latent trait continuum.
-As we treated each factor of short-LEBA as an unidmensional construct we obtain 5 TICs (\ref{fig:Testinfo}).
+Test information curve (TIC) (Figure \ref{fig:Testinfo}) indicate the amount of information an the full-scale carry along the latent trait continuum.
+As we treated each factor of short-LEBA as an unidmensional construct we obtain 5 TICs (figure \ref{Fig:Testinfo}).
 These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum ((\(\theta\))).
@@
 
-\caption{\label{tab:itemfittab}}
+\caption{\label{tab:itemfittab}Item fit statistics for the fitted models}
 
@@
 \begin{figure}
-\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/personfit-1} \caption{Person fit of the five fitted IRT models (a) Blue filter (b) Natural light (c)Smart device (d)Sleep environment (e)Electic light}\label{fig:personfit}
+\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/personfit-1} \caption{Person fit of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c)Using phone and smartwatchin bed (d)Using light before bedtime (e)Using light in the morning andduring daytime}\label{fig:personfit}
 \end{figure}
 
-Next, we generated scale characteristics curve (\ref{fig:scalechar}) which plotted estimated theta score against the expected true score.
+Next, we generated scale characteristics curve (Figure \ref{fig:scalechar}) which plotted estimated theta score against the expected true score.
 The purpose of this scale characteristics curve is to find the corresponding expected true score for the given estimated theta score.
@@
 \begin{figure}
-\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/scalechar-1} \caption{Scale characteristic curve of the five fitted IRT models (a) Blue filter (b) Natural light (c)Smart device (d)Sleep environment (e)Electic light}\label{fig:scalechar}
+\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/scalechar-1} \caption{Scale characteristic curve of the five fitted IRT models ((a) Wearing blue light filters (b) Spending time outdoors (c)Using phone and smartwatchin bed (d)Using light before bedtime (e)Using light in the morning andduring daytime}\label{fig:scalechar}
 \end{figure}
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\vadjust pre{\hypertarget{ref-R-tabledown}{}}%
-Anwar Siraji, M. (2021). \emph{Tabledown: A companion pack for the book "basic \& advanced psychometrics in r"}. Retrieved from \url{https://github.com/masiraji/tabledown}
-
 \leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-R-ufs}{}}%
+Peters, G.-J. (2021). \emph{Ufs: Quantitative analysis made accessible}. Retrieved from \url{https://CRAN.R-project.org/package=ufs}
+
 \leavevmode\vadjust pre{\hypertarget{ref-Petersen.1988}{}}%
@@
 Sijtsma, K. (2009). On the use, the misuse, and the very limited usefulness of cronbach's alpha. \emph{Psychometrika}, \emph{74}(1), 107.
+
+\leavevmode\vadjust pre{\hypertarget{ref-R-tabledown}{}}%
+Siraji, M. A. (2021). \emph{Tabledown: A companion pack for the book "basic \& advanced psychometrics in r"}. Retrieved from \url{https://github.com/masiraji/tabledown}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-RN1272}{}}%
-Yu, C.-Y. (2002). \emph{Evaluating cutoff criteria of model fit indices for latent variable models with binary and continuous outcomes} (Thesis). {ProQuest Dissertations Publishing}.
+Yu, C. (2002). \emph{Evaluating cutoff criteria of model fit indices for latent variable models with binary and continuous outcomes} (Thesis). {ProQuest Dissertations Publishing}.
 
@@
 
-\begin{table}[h]
-
 \begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:EFATableAppB}Factor loadings and communality of the retained items [Unmerged Responses]}
+\begin{ThreePartTable}
+
+\begin{TableNotes}[para]
+\normalsize{\textit{Note.} Only loading higher than .30 is reported}
+\end{TableNotes}
 

### 2021-11-13 Supplymentary.Rmd
* Longtables are visible

@@
 ---
-title: "Supplimentary Analysis"
-output: pdf_document
+title             : "Supplementary"
+shorttitle        : "SA"
+
+author: 
+  - name          : "Mushfiqul Anwar Siraji"
+    affiliation   : "1, *"
+    email         : "mushfiqul.anwarsiraji@monash.edu"
+    role:         
+      - Formal Analysis
+      - Visualization
+      - Writing – original draft
+      - Writing – review & editing;
+
+  - name          : "Rafael Robert Lazar"
+    affiliation   : "2, 3, *"
+    role:
+      - Data curation
+      - Investigation
+      - Project administration
+      - Visualization
+      - Writing – original draft
+      - Writing – review & editing;
+
+  - name          : "Juliëtte	van Duijnhoven"
+    affiliation   : "4"
+    email         : "j.v.duijnhoven1@tue.nl"
+    role:         
+      - Conceptualization
+      - Methodology
+      - Investigation
+      - Writing – review & editing
+
+  - name          : "Luc Schlangen"
+    affiliation   : "5"
+    email         : "l.j.m.schlangen@tue.nl"
+    role:         
+      - Conceptualization
+      - Methodology
+      - Investigation
+      - Writing – review & editing
+
+  - name          : "Shamsul Haque"
+    affiliation   : "1"
+    email         : "shamsul@monash.edu"
+    role:         
+      - Conceptualization
+      - Supervision
+      - Writing – review & editing
+
+  - name          : "Vineetha Kalavally"
+    affiliation   : "6"
+    email         : "vineetha@monash.edu"
+    role:         
+      - Supervision
+      - Writing – review & editing
+
+  - name          : "Céline Vetter"
+    affiliation   : "7, 8"
+    email         : "celine.vetter@colorado.edu"
+    role:         
+      - Conceptualization
+      - Writing – review & editing
+
+  - name          : "Gena Glickman"
+    affiliation   : "9"
+    email         : "gena.glickman@usuhs.edu"
+    role:         
+      - Conceptualization
+      - Methodology
+      - Writing – review & editing
+
+  - name          : "Karin Smolders"
+    affiliation   : "10"
+    email         : "k.c.h.j.smolders@tue.nl"
+    role:         
+      - Conceptualization
+      - Methodology
+      - Writing – review & editing
+
+  - name          : "Manuel Spitschan"
+    corresponding : yes
+    affiliation   : "11, 2, 3"
+    email         : "manuel.spitschan@psy.ox.ac.uk"
+    role:         
+      - Conceptualization
+      - Data curation
+      - Investigation
+      - Project administration
+      - Visualization
+      - Methodology
+      - Writing – original draft
+      - Writing – review & editing
+
+affiliation:
+  - id            : "1"
+    institution   : "Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
+  - id            : "2"
+    institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"
+  - id            : "3"
+    institution   : "University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland"
+  - id            : "4"
+    institution   : "Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands"
+  - id            : "5"
+    institution   : "Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Intelligent Lighting Institute, Eindhoven, Netherlands"
+  - id            : "6"
+    institution   : "Monash University, Department of Electrical and Computer Systems Engineering, Malaysia, Selangor, Malaysia"
+  - id            : "7"
+    institution   : "University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA"
+  - id            : "8"
+    institution   : "Ximes GmbH, Frankfurt, Germany"
+  - id            : "9"
+    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
+  - id            : "10"
+    institution   : "Eindhoven University of Technology, Human-Technology Interaction Group, Eindhoven, Netherlands"
+  - id            : "11"
+    institution   : "University of Oxford, Department of Experimental Psychology, Oxford, UK"
+  - id            : "*"
+    institution   : "Joint first author"
+
+bibliography      : ["references.bib"]
+
+floatsintext      : no
+figurelist        : no
+tablelist         : no
+footnotelist      : no
+linenumbers       : yes
+mask              : no
+draft             : no
+documentclass     : "apa6"
+classoption       : "man"
+output            : 
+  papaja::apa6_pdf:
+    latex_engine: xelatex
+    includes:
+      in_header: header.tex
+
+mainfont: Arial
 ---
@@
 set.seed(123)
-par(family = "Helvetica")
+par(family = "Arial")
 ```
@@
 ```{r MinResTab}
-papaja::apa_table(minresTab, align = "c", caption = "Factor loadings and communality of the retained items(Minmum Residual)", note = "Only loading higher than .30 is reported", font_size = "small")
+papaja::apa_table(minresTab,  caption = "Factor loadings and communality of the retained items(Minmum Residual)", note = "Only loading higher than .30 is reported", longtable=T)
 
@@
 
-```{r sixFacTab}
-papaja::apa_table(sixFac, align = "c", caption = "Factor loadings and communality of the retained items(six factor)", note = "Only loading higher than .30 is reported", font_size = "small")
+```{r sixFacTab, results='asis'}
+papaja::apa_table(sixFac,  caption = "Factor loadings and communality of the retained items(six factor)", note = "Only loading higher than .30 is reported",longtable =T)
 ```
@@
 ```{r tabDesAppB, results='asis'}
-apa_table(Des.combined, caption = "Descriptive Statistics for Unmerged response options", align = "c", note = "*p<.001", placement = "h")
+apa_table(Des.combined, caption = "Descriptive Statistics for Unmerged response options",  note = "*p<.001", longtable =T)
 ```
@@
 
-```{r figCorAppB, fig.align='center', fig.cap="Correlation plot of the items",  out.width="100%"}
+```{r figCorAppB,  fig.cap="Correlation plot of the items",  out.width="100%"}
 
@@
 
-```{r facIdFigAppB, fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot', warning=FALSE}
+```{r facIdFigAppB,  fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot', warning=FALSE}
 cowplot::plot_grid(parallel, scree.plot, labels = "AUTO",ncol=1, label_size = 8,align = "v")
@@
 
-apa_table(efa.table,align = "c", caption = "Factor loadings and communality of the retained items [Unmerged Responses]", note = "Only loading higher than .30 is reported", font_size = "small", longtable =T)
+apa_table(efa.table, caption = "Factor loadings and communality of the retained items [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T)
 ```
@@
 
-```{r EFAResidualsAppB,  fig.align='center', fig.cap=' Histogram of residulas:  five-factor solution', warning=FALSE,  results='asis'}
+```{r EFAResidualsAppB,   fig.cap=' Histogram of residulas:  five-factor solution', warning=FALSE,  results='asis'}
 hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))

### 2021-11-13 Supplymentary.tex
* Longtables are visible

@@
 \section{}
-\begin{table}[tbp]
+\begin{center}
+\begin{ThreePartTable}
 
-\begin{center}
-\begin{threeparttable}
+\begin{TableNotes}[para]
+\normalsize{\textit{Note.} Only loading higher than .30 is reported}
+\end{TableNotes}
 
-\caption{\label{tab:MinResTab}Factor loadings and communality of the retained items(Minmum Residual)}
-
-\small{
-
-\begin{tabular}{cccccccc}
+\begin{longtable}{llllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:MinResTab}Factor loadings and communality of the retained items(Minmum Residual)}\\
 \toprule
@@
 \midrule
+\endfirsthead
+\caption*{\normalfont{Table \ref{tab:MinResTab} continued}}\\
+\toprule
+item & \multicolumn{1}{c}{MR1} & \multicolumn{1}{c}{MR2} & \multicolumn{1}{c}{MR3} & \multicolumn{1}{c}{MR4} & \multicolumn{1}{c}{MR5} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness}\\
+\midrule
+\endhead
 item16 & 1 &  &  &  &  & 0.996 & 0.004\\
@@
 \addlinespace
-\end{tabular}
+\insertTableNotes
+\end{longtable}
 
-}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} Only loading higher than .30 is reported}
-\end{tablenotes}
-
-\end{threeparttable}
+\end{ThreePartTable}
 \end{center}
 
-\end{table}
+\begin{center}
+\begin{ThreePartTable}
 
-\begin{table}[tbp]
+\begin{TableNotes}[para]
+\normalsize{\textit{Note.} Only loading higher than .30 is reported}
+\end{TableNotes}
 
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:sixFacTab}Factor loadings and communality of the retained items(six factor)}
-
-\small{
-
-\begin{tabular}{ccccccccc}
+\begin{longtable}{lllllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:sixFacTab}Factor loadings and communality of the retained items(six factor)}\\
 \toprule
@@
 \midrule
+\endfirsthead
+\caption*{\normalfont{Table \ref{tab:sixFacTab} continued}}\\
+\toprule
+item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA6} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness}\\
+\midrule
+\endhead
 item19 & 1.78 &  &  &  &  &  & 3.318 & -2.318\\
@@
 \addlinespace
-\end{tabular}
+\insertTableNotes
+\end{longtable}
 
-}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} Only loading higher than .30 is reported}
-\end{tablenotes}
-
-\end{threeparttable}
+\end{ThreePartTable}
 \end{center}
-
-\end{table}
 
@@
 
-\begin{table}[h]
+\begin{center}
+\begin{ThreePartTable}
 
-\begin{center}
-\begin{threeparttable}
+\begin{TableNotes}[para]
+\normalsize{\textit{Note.} *p<.001}
+\end{TableNotes}
 
-\caption{\label{tab:tabDesAppB}Descriptive Statistics for Unmerged response options}
-
-\begin{tabular}{ccccccc}
+\begin{longtable}{lllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:tabDesAppB}Descriptive Statistics for Unmerged response options}\\
 \toprule
@@
 \midrule
+\endfirsthead
+\caption*{\normalfont{Table \ref{tab:tabDesAppB} continued}}\\
+\toprule
+ & \multicolumn{1}{c}{Mean} & \multicolumn{1}{c}{SD} & \multicolumn{1}{c}{Skew} & \multicolumn{1}{c}{Kurtosis} & \multicolumn{1}{c}{Shapiro-Wilk Statistics} & \multicolumn{1}{c}{Item-Total Correlation}\\
+\midrule
+\endhead
 Item1 & 2.16 & 1.51 & 0.49 & -0.86 & 0.90* & .21\\
@@
 \addlinespace
-\end{tabular}
+\insertTableNotes
+\end{longtable}
 
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} *p<.001}
-\end{tablenotes}
-
-\end{threeparttable}
+\end{ThreePartTable}
 \end{center}
 
-\end{table}
-
 \begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-1}
-
-}
-
-\caption{Correlation plot of the items}(\#fig:figCorAppB)
+\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-1} \caption{Correlation plot of the items}(\#fig:figCorAppB)
 \end{figure}
@@
 \begin{figure}
-
-{\centering \includegraphics{manuscript_files/figure-latex/facIdFigAppB-1}
-
-}
-
-\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}(\#fig:facIdFigAppB)
+\centering
+\includegraphics{manuscript_files/figure-latex/facIdFigAppB-1.pdf}
+\caption{(\#fig:facIdFigAppB)Factor Identification (A) Parallel analysis
+(B) Scree Plot}
 \end{figure}
@@
 
-\small{
-
-\begin{longtable}{ccccccccc}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\begin{longtable}{lllllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
 \caption{\label{tab:EFATableAppB}Factor loadings and communality of the retained items [Unmerged Responses]}\\
@@
 \end{longtable}
-
-}
 
@@
 \begin{figure}
-
-{\centering \includegraphics{manuscript_files/figure-latex/EFAResidualsAppB-1}
-
-}
-
-\caption{ Histogram of residulas:  five-factor solution}(\#fig:EFAResidualsAppB)
+\centering
+\includegraphics{manuscript_files/figure-latex/EFAResidualsAppB-1.pdf}
+\caption{(\#fig:EFAResidualsAppB) Histogram of residulas: five-factor
+solution}
 \end{figure}

### 2021-11-13 instrument.tex
* Longtables are visible

--- 2021-11-06 instrument.tex
@@
 \toprule
-Factor names & Items & Reliability Coefficients \\
+Factor names & Items & Reliability Coefficients: ordinal alpha \\
 \midrule
 \endhead
-\textbf{F1: Wearing blue light filters} & 1-3 & .93 \\
-\textbf{F2: Spending time outdoors} & 4-9 (Item 4 is reversed) & .80 \\
-\textbf{F3: Using phone and smartwatch in bed} & 10-14 & .61 \\
-\textbf{F4: Using light before bedtime} & 15-18 & .72 \\
-\textbf{F5: Using light in the morning and during daytime} & 19-23 &
-.45 \\
+F1: Wearing blue light filters & 1-3 & .96 \\
+F2: Spending time outdoors & 4-9 (Item 4 is reversed) & .83 \\
+F3: Using phone and smartwatch in bed & 10-14 & .70 \\
+F4: Using light before bedtime & 15-18 & .69 \\
+F5: Using light in the morning and during daytime & 19-23 & .52 \\
+McDonald's Omega coefficient for the total scale & & .73(Total scale) \\
 \bottomrule

### 2021-11-13 manuscript.Rmd
* Longtables are visible

@@
 
-```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='100%', out.width='100%'}
+```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='150%', out.width='100%'}
 knitr::include_graphics('Manuscript.figures/Flowchart1.png')
@@
 ### Data Collection
+
 Timeline of data collection, mode of data collection.
@@
 ## Analytic Strategies
+
 For our analysis we used R (version 4.1.0), with several R packages.
@@
 And the corrected item-total correlations ranged between `r apa(low.r.corec,2,F)` to `r apa(high.r.corec,2,F)`.
-
 ```{r tabDes,results='asis'}
@@
 ```
+
 Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution.
@@
 
-```{r EFAResiduals, out.height= "50%",  fig.align='center', fig.cap= ' Histogram of residuals:  five-factor solution',  out.width="50%",  warning=FALSE, results='asis'}
+```{r EFAResiduals, out.height= "100%",  fig.align='center', fig.cap= ' Histogram of residuals:  five-factor solution',  out.width="100%",  warning=FALSE, results='asis'}
 hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))
@@
 
-```{r itmeinfo, fig.cap="Item information curves (a) Wearing blue light filters (b) Spending time outdoors (c)Using phone and smartwatchin bed (d)Using light before bedtime (e)Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
+```{r itmeinfo, fig.cap="Item information curves (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
 plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
@@
 
-```{r Testinfo, fig.cap="Test information curves (a) Wearing blue light filters (b) Spending time outdoors (c)Using phone and smartwatchin bed (d)Using light before bedtime (e)Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
+```{r Testinfo, fig.cap="Test information curves (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
 plot_grid(F1_test.info , F2_test.info.redu,F3_test.info.redu,F4_test.info.redu,F5_test.info,
@@
 All of the items had RMSEA value <.06 indicating adequate fit.
-Figure \@ref(fig:persornfit) depicts the person fit of out fitted models.
+Figure \@ref(fig:personfit) depicts the person fit of out fitted models.
 Person fit indicates the validity and meaningfulness of the fitted model at the participants latent trait level [@desjardinsHandbookEducationalMeasurement2018].
@@
 
-```{r personfit, fig.cap="Person fit of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c)Using phone and smartwatchin bed (d)Using light before bedtime (e)Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
+```{r personfit, fig.cap="Person fit of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
 plot_grid(F1.person, F2.person,F3.person,F4.person,F5.person, 
@@
 
-```{r scalechar, fig.cap="Scale characteristic curve of the five fitted IRT models ((a) Wearing blue light filters (b) Spending time outdoors (c)Using phone and smartwatchin bed (d)Using light before bedtime (e)Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
+```{r scalechar, fig.cap="Scale characteristic curve of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
 

### 2021-11-13 manuscript.tex
* Longtables are visible

@@
 
-{\centering \includegraphics[width=1\linewidth,height=1\textheight]{Manuscript.figures/Flowchart1}
+{\centering \includegraphics[width=1\linewidth,height=1.5\textheight]{Manuscript.figures/Flowchart1}
 
@@
 
-{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{manuscript_files/figure-latex/EFAResiduals-1}
+{\centering \includegraphics[width=1\linewidth,height=1\textheight]{manuscript_files/figure-latex/EFAResiduals-1}
 
@@
 \begin{figure}
-\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/itmeinfo-1} \caption{Item information curves (a) Wearing blue light filters (b) Spending time outdoors (c)Using phone and smartwatchin bed (d)Using light before bedtime (e)Using light in the morning andduring daytime}\label{fig:itmeinfo}
+\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/itmeinfo-1} \caption{Item information curves (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime}\label{fig:itmeinfo}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/Testinfo-1} \caption{Test information curves (a) Wearing blue light filters (b) Spending time outdoors (c)Using phone and smartwatchin bed (d)Using light before bedtime (e)Using light in the morning andduring daytime}\label{fig:Testinfo}
+\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/Testinfo-1} \caption{Test information curves (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime}\label{fig:Testinfo}
 \end{figure}
@@
 All of the items had RMSEA value \textless.06 indicating adequate fit.
-Figure \ref{fig:persornfit} depicts the person fit of out fitted models.
+Figure \ref{fig:personfit} depicts the person fit of out fitted models.
 Person fit indicates the validity and meaningfulness of the fitted model at the participants latent trait level (Desjardins \& Bulut, 2018).
@@
 \begin{figure}
-\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/personfit-1} \caption{Person fit of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c)Using phone and smartwatchin bed (d)Using light before bedtime (e)Using light in the morning andduring daytime}\label{fig:personfit}
+\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/personfit-1} \caption{Person fit of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime}\label{fig:personfit}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/scalechar-1} \caption{Scale characteristic curve of the five fitted IRT models ((a) Wearing blue light filters (b) Spending time outdoors (c)Using phone and smartwatchin bed (d)Using light before bedtime (e)Using light in the morning andduring daytime}\label{fig:scalechar}
+\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/scalechar-1} \caption{Scale characteristic curve of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime}\label{fig:scalechar}
 \end{figure}
@@
 \section{}
-\begin{table}[tbp]
-
 \begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:MinResTab}Factor loadings and communality of the retained items(Minmum Residual)}
-
-\small{
-
-\begin{tabular}{cccccccc}
+\begin{ThreePartTable}
+
+\begin{TableNotes}[para]
+\normalsize{\textit{Note.} Only loading higher than .30 is reported}
+\end{TableNotes}
+
+\begin{longtable}{llllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:MinResTab}Factor loadings and communality of the retained items(Minmum Residual)}\\
 \toprule
@@
 \addlinespace
-\end{tabular}
-
-}
-
-\begin{tablenotes}[para]
+\insertTableNotes
+\end{longtable}
+
+\end{ThreePartTable}
+\end{center}
+
+\begin{center}
+\begin{ThreePartTable}
+
+\begin{TableNotes}[para]
 \normalsize{\textit{Note.} Only loading higher than .30 is reported}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-\begin{table}[tbp]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:sixFacTab}Factor loadings and communality of the retained items(six factor)}
-
-\small{
-
-\begin{tabular}{ccccccccc}
+\end{TableNotes}
+
+\begin{longtable}{lllllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:sixFacTab}Factor loadings and communality of the retained items(six factor)}\\
 \toprule
@@
 \addlinespace
-\end{tabular}
-
-}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} Only loading higher than .30 is reported}
-\end{tablenotes}
-
-\end{threeparttable}
+\insertTableNotes
+\end{longtable}
+
+\end{ThreePartTable}
 \end{center}
-
-\end{table}
 
@@
 
-\begin{table}[h]
-
 \begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:tabDesAppB}Descriptive Statistics for Unmerged response options}
-
-\begin{tabular}{ccccccc}
+\begin{ThreePartTable}
+
+\begin{TableNotes}[para]
+\normalsize{\textit{Note.} *p<.001}
+\end{TableNotes}
+
+\begin{longtable}{lllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:tabDesAppB}Descriptive Statistics for Unmerged response options}\\
 \toprule
@@
 \addlinespace
-\end{tabular}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} *p<.001}
-\end{tablenotes}
-
-\end{threeparttable}
+\insertTableNotes
+\end{longtable}
+
+\end{ThreePartTable}
 \end{center}
 
-\end{table}
-
 \begin{figure}
-
-{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-1}
-
-}
-
-\caption{Correlation plot of the items}\label{fig:figCorAppB}
+\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-1} \caption{Correlation plot of the items}\label{fig:figCorAppB}
 \end{figure}
@@
 \begin{figure}
-
-{\centering \includegraphics{manuscript_files/figure-latex/facIdFigAppB-1}
-
-}
-
-\caption{Factor Identification (A) Parallel analysis (B) Scree Plot}\label{fig:facIdFigAppB}
+\centering
+\includegraphics{manuscript_files/figure-latex/facIdFigAppB-1.pdf}
+\caption{\label{fig:facIdFigAppB}Factor Identification (A) Parallel analysis
+(B) Scree Plot}
 \end{figure}
@@
 \begin{figure}
-
-{\centering \includegraphics{manuscript_files/figure-latex/EFAResidualsAppB-1}
-
-}
-
-\caption{ Histogram of residulas:  five-factor solution}\label{fig:EFAResidualsAppB}
+\centering
+\includegraphics{manuscript_files/figure-latex/EFAResidualsAppB-1.pdf}
+\caption{\label{fig:EFAResidualsAppB} Histogram of residulas: five-factor
+solution}
 \end{figure}
@@
 
-\begin{longtable}[]{@{}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.33}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.15}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.26}}
-  >{\raggedright\arraybackslash}p{(\columnwidth - 6\tabcolsep) * \real{0.26}}@{}}
-\toprule
-\begin{minipage}[b]{\linewidth}\raggedright
-Factor names
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Items
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Reliability Coefficients: McDonald's Omega
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
-Reliability Coefficients: Ordinal alpha
-\end{minipage} \\
+\begin{longtable}[]{@{}lll@{}}
+\toprule
+Factor names & Items & Reliability Coefficients: ordinal alpha \\
 \midrule
 \endhead
-F1: Wearing blue light filters & 1-3 & .93 & .90 \\
-F2: Spending time outdoors & 4-9 (Item 4 is reversed) & .80 & .78 \\
-F3: Using phone and smartwatch in bed & 10-14 & .61 & .62 \\
-F4: Using light before bedtime & 15-18 & .72 & .62 \\
-F5: Using light in the morning and during daytime & 19-23 & .45 & .41 \\
-& & .73(Total scale) & \\
+F1: Wearing blue light filters & 1-3 & .96 \\
+F2: Spending time outdoors & 4-9 (Item 4 is reversed) & .83 \\
+F3: Using phone and smartwatch in bed & 10-14 & .70 \\
+F4: Using light before bedtime & 15-18 & .69 \\
+F5: Using light in the morning and during daytime & 19-23 & .52 \\
+McDonald's Omega coefficient for the total scale & & .73(Total scale) \\
 \bottomrule

### 2021-11-14 manuscript.Rmd
adding country/timezone information in the participants text as bullet points

@@
     ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
-modify_header(label ~ "**Variable**") %>% modify_caption("Dempgraphics") -> desc_table
+modify_header(label ~ "**Variable**") %>% modify_caption("Demographics") -> desc_table
 
@@
 as_kable_extra(desc_table, format = "latex",booktabs = T) -> desc_kable #save it as a knitr::kable
+
+#summarise country/time zone data
+
+descriptives.data%>%
+  tbl_summary(
+    label = slypos_demographics_tz.factor ~ "Time zone - Country",
+    statistic = list(all_categorical() ~ "{n} ({p}%)"),
+    missing = "no",
+    sort = all_categorical() ~ "frequency",
+    include = "slypos_demographics_tz.factor"
+  )  %>% bold_labels() %>% 
+  modify_header(label ~ "") %>%
+  as_tibble(format = 'pipe') -> tz_tibble
 
@@
 Participants indicated filling out the online survey from a diverse range of geographic locations.
-The four most common geographic locations included:
-
-`r kable(head(summary(descriptives.data$slypos_demographics_tz.factor), 4), format = "latex")`
+The ten most common geographic locations included:
+
+- `r tz_tibble[2,1]`:     `r tz_tibble[2,2]` 
+- `r tz_tibble[3,1]`:     `r tz_tibble[3,2]`
+- `r tz_tibble[4,1]`:     `r tz_tibble[4,2]`
+- `r tz_tibble[5,1]`:     `r tz_tibble[5,2]`
+- `r tz_tibble[6,1]`:     `r tz_tibble[6,2]`
+- `r tz_tibble[7,1]`:     `r tz_tibble[7,2]`
+- `r tz_tibble[8,1]`:     `r tz_tibble[8,2]`
+- `r tz_tibble[9,1]`:     `r tz_tibble[9,2]`
+- `r tz_tibble[10,1]`:    `r tz_tibble[10,2]`
+- `r tz_tibble[11,1]`:    `r tz_tibble[11,2]`
 
@@
 For their "Occupational Status", more than half of the overall sample reported that they currently work [Overall: `r desc_tibble[9,2]`; EFA: `r desc_tibble[9,3]`; CFA: `r desc_tibble[9,4]`], whereas `r desc_tibble[10,2]` [EFA: `r desc_tibble[10,3]`; CFA: `r desc_tibble[10,4]`] reported that they go to school and `r desc_tibble[11,2]` [EFA: `r desc_tibble[11,3]`; CFA: `r desc_tibble[11,4]`] responded that they do "Neither".
-With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` [EFA: `r desc_tibble[13,3]`; CFA: `r desc_tibble[13,4]`] of the participants indicated that they were in a home office/ home schooling setting., while `r desc_tibble[14,2]` overall [EFA: `r desc_tibble[14,3]` ; CFA: `r desc_tibble[14,4]`] reported face-to-face work/schooling.
-Lastly, `r desc_tibble[15,2]` overall [EFA: `r desc_tibble[15,3]` ; CFA: `r desc_tibble[15,4]`] reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]` overall [EFA: `r desc_tibble[16,3]`; CFA: `r desc_tibble[16,4]`] filled in the "Neither (no work or school, or indication)" response option.
+With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` [EFA: `r desc_tibble[13,3]`; CFA: `r desc_tibble[13,4]`] of the participants indicated that they were in a home office/ home schooling setting, while `r desc_tibble[14,2]` overall [EFA: `r desc_tibble[14,3]` ; CFA: `r desc_tibble[14,4]`] reported face-to-face work/schooling.
+Lastly, `r desc_tibble[15,2]` overall [EFA: `r desc_tibble[15,3]` ; CFA: `r desc_tibble[15,4]`] reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]` overall [EFA: `r desc_tibble[16,3]`; CFA: `r desc_tibble[16,4]`] filled in the "Neither (no work or school, or on vacation)" response option.
 We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable "Age" and Pearson's $\chi^2$ test for all other categorical variables via the gtsummary R package's "add_p" function [@sjoberg2021] .

### 2021-11-15 manuscript.Rmd
GT pic referenced

@@
 
-1.  Describe EFA and CFA sample separately.
-2.  Sampling technique: Convince sampling (non-probability sample)
-3.  Method: cross-sectional survey
-4.  How many missing data?
-5.  How incomplete data were addressed.
-6.  Why such sample was chosen?
-
 ## Procedure
 
-### Development of the Scale
+### Item Generation
 
@@
 ```
-
-### Data Collection
-
-Timeline of data collection, mode of data collection.
 
@@
 Upon inspection, it was understood that these items are negatively correlated to the common theme, and thus in the CFA analysis, we reversed the response code for these two items.
+Figure \@ref(fig:gtPic) depicts the data distribution and endorsement pattern for the included items in our LEBA scale for both the EFA and CFA sample.
 

### 2021-11-15 manuscript.Rmd
* Semantic Scale Network added

@@
 For our analysis we used R (version 4.1.0), with several R packages.
-Initially, our tool had six point Likert type response scale (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Always).
+Initially, our tool had six point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Always).
 Our purpose was to capture light exposure related behavior and these two response options: "Does not apply/I don't know" and "Never" were providing similar information.
-As such we decided to collapse them into one making it a 5 point Likert type response scale.
+As such we decided to collapse them into one making it a 5 point Likert type response format.
 Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
@@
 Upon inspection, it was understood that these items are negatively correlated to the common theme, and thus in the CFA analysis, we reversed the response code for these two items.
-Figure \@ref(fig:gtPic) depicts the data distribution and endorsement pattern for the included items in our LEBA scale for both the EFA and CFA sample.
+Figure \@ref(fig:gtPic) depicts the data distribution and endorsement pattern for the included items in our LEBA tool for both the EFA and CFA sample.
 
@@
 We judged the model fit based on the comparative fit indices: CFI, TLI and parsimony fit index:RMSEA.
-Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`,[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 and 19-17 .
-However SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`).
-Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR value (SRMR = `r apa(fit.2[10],2,F)`) was also close to the suggestions of @huCutoffCriteriaFit1999.
+Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`,[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 [`r Hmisc::label(sem.data$item32)`;`r Hmisc::label(sem.data$item33)`] and 16-17 [`r Hmisc::label(sem.data$item16)`;`r Hmisc::label(sem.data$item17)`].
+Items pair 32-33 stemed from the preference of dimming electric device's brightness before bed time and items pair 16 and 19 stemed from the preference of using blue filtering or colored glasses during the daytime.
+Nevertheless, SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`).
+Further by allowing one pair of items (30-41) [`r Hmisc::label(sem.data$item30)`;`r Hmisc::label(sem.data$item41)`] to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR value (SRMR = `r apa(fit.2[10],2,F)`) was also close to the suggestions of @huCutoffCriteriaFit1999.
 Internal consistency ordinal $\alpha$ for the five factors of LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)` respectively.
@@
 This model is the highest level of MI and assures the equivalence of precision of items across the groups in measuring the underlying constructs.
-The invariance model fit of our scale was assessed using the fit indices including $\chi^2$ test, CFI and TLI (close to .95 or above), RMSEA (close to .06 or below) [@huCutoffCriteriaFit1999].
+The invariance model fit of our tool was assessed using the fit indices including $\chi^2$ test, CFI and TLI (close to .95 or above), RMSEA (close to .06 or below) [@huCutoffCriteriaFit1999].
 We excluded SRMR from our consideration as it does not behave optimally for categorical variables [@RN1272].
@@
 
+## Sementic Analysis 
+To find out if our developed tool is overlapping with existing instruments, we subjected the items of LEBA to the "Semantic Scale Network"(SSN) analysis[@rosenbusch2020semantic].
+The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic].
+Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy.
+LEBA  appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990].The cosine similarities lie between .47 to .51.
+Two factors of our LEBA tool: "Using phone and smart-watch in bed" and "Using light before bedtime" dealt with light exposure related behavior pertaining to sleep quality.
+As such the similarity index obtained is expected.
+
 ## Developing Short form of LEBA
-
 We sought the item response theory (IRT) to develop the short form of LEBA.
@@
 @bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70.
-Table \@ref(tab:IRTparameters) summarizes the IRT parameters of our scale.
-Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$).
+Table \@ref(tab:IRTparameters) summarizes the IRT parameters of our tool.
+Item discrimination parameters of our tool fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$).
 Examination of the item information curve \@ref(fig:itmeinfo) indicated 6 items (1, 25, 9, 38, 30, & 41) had relatively flat information curves thus discarded creating a short form of LEBA with 5 factors and 17 items.
@@
 Also the amount of information changed rather steadily with the change of ($\theta$).
-Thus we conferred the LEBA scale (except blue filter) estimated the light exposure related behavior with precision near the center of trait continuum [@bakerBasicsItemResponse2017] which is sufficient to discriminate between latent trait measured by the each factor.
+Thus we conferred the LEBA tool (except blue filter) estimated the light exposure related behavior with precision near the center of trait continuum [@bakerBasicsItemResponse2017] which is sufficient to discriminate between latent trait measured by the each factor.
 The blue filter factor had a peak to the right side of the center of latent trait indicating its ability to providing information only for people who already have some preference towards using blue-filters.

### 2021-11-15 manuscript.tex
* Semantic Scale Network added

@@
 Harvard Light Exposure Assessment Questionnaire & Bajaj et al., 2011 & Self-administered semi-quantitative light questionnaire & NA\\
-Hospital Lighting Survey & Dianat et el.,.2013 & 23 items questionnaire to assess light environment in a hospital & NA\\
-Morningness-Eveningness Questionnaire & Horne et al.,1976 & 19 items questionnaire to understand your body clock & NA\\
+Hospital Lighting Survey & Dianat et el., 2013 & 23 items questionnaire to assess light environment in a hospital & NA\\
+Morningness-Eveningness Questionnaire & Horne et al., 1976 & 19 items questionnaire to understand your body clock & NA\\
 \addlinespace
-Munich Chronotype Questionnaire (MCTQ) & Roenneberg et al.,2003 & 17 items questionnaire to understand individuals phase of entrainment & NA\\
-Assessment of Sleep Environment & Olivier et.al.,.2016] & 13 items questionnaire measuring your sleep environment quality & NA\\
-The Pittsburgh Sleep Quality Index (PSQI) & Buysse ei al.,1989 & 9 items inventory to measure sleep quality and sleeping pattern & NA\\
-Self-Rating of Biological Rhythm Disorder for Adolescents (SBRDA) & Xie et al.,2021 & 29 Items questionnaire assessing four dimensions of biological rhythm disorder in adolescents & Item 3,22-25 and 29\\
-Photosensitivity Assessment Questionnaire (PAQ) & Wu et al.,2017 & 16 dichotomous (yes/no) items questionnaire to assess "photophobia" and "photophilia" & All itms\\*
+Munich Chronotype Questionnaire (MCTQ) & Roenneberg et al., 2003 & 17 items questionnaire to understand individuals phase of entrainment & NA\\
+Assessment of Sleep Environment & Olivier et.al., 2016 & 13 items questionnaire measuring your sleep environment quality & NA\\
+The Pittsburgh Sleep Quality Index (PSQI) & Buysse et al., 1989 & 9 items inventory to measure sleep quality and sleeping pattern & NA\\
+Self-Rating of Biological Rhythm Disorder for Adolescents (SBRDA) & Xie et al., 2021 & 29 Items questionnaire assessing four dimensions of biological rhythm disorder in adolescents & Item 3,22-25 and 29\\
+Photosensitivity Assessment Questionnaire (PAQ) & Wu et al., 2017 & 16 dichotomous (yes/no) items questionnaire to assess "photophobia" and "photophilia" & All itms\\*
 \end{longtable}
@@
 
-\caption{\label{tab:prepareDescTable}Dempgraphics}
+\caption{\label{tab:prepareDescTable}Demographics}
 \centering
@@
 Participants indicated filling out the online survey from a diverse range of geographic locations.
-The four most common geographic locations included:
-
-\begin{tabular}{l|r}
-\hline
-  & x\\
-\hline
-United States - America/New\_York (UTC -04:00) & 63\\
-\hline
-United Kingdom - Europe/London (UTC) & 57\\
-\hline
-Germany - Europe/Berlin (UTC +01:00) & 53\\
-\hline
-India - Asia/Kolkata (UTC +05:30) & 38\\
-\hline
-\end{tabular}
+The ten most common geographic locations included:
+
+\begin{itemize}
+\tightlist
+\item
+  United States - America/New\_York (UTC -04:00): 63 (9.1\%)
+\item
+  United Kingdom - Europe/London (UTC): 57 (8.3\%)
+\item
+  Germany - Europe/Berlin (UTC +01:00): 53 (7.7\%)
+\item
+  India - Asia/Kolkata (UTC +05:30): 38 (5.5\%)
+\item
+  United States - America/Los\_Angeles (UTC -07:00): 37 (5.4\%)
+\item
+  United States - America/Chicago (UTC -05:00): 30 (4.3\%)
+\item
+  France - Europe/Paris (UTC +01:00): 22 (3.2\%)
+\item
+  Switzerland - Europe/Zurich (UTC +01:00): 21 (3.0\%)
+\item
+  Brazil - America/Sao\_Paulo (UTC -03:00): 19 (2.8\%)
+\item
+  Netherlands - Europe/Amsterdam (UTC +01:00): 19 (2.8\%)
+\end{itemize}
 
@@
 In a ``Yes/No'' question regarding native language, 320 (46\%) of respondents {[}EFA: 191 (45\%); CFA: 129 (49\%){]} indicated to be native English speakers.
-For their ``Occupational Status,'' more than half of the overall sample reported that they currently work {[}Overall: 396 (57\%); EFA: 235 (55\%); CFA: 161 (61\%){]}, whereas 174 (25\%) {[}EFA: 122 (29\%); CFA: 52 (20\%){]} reported that they go to school and 120 (17\%) {[}EFA: 71 (17\%); CFA: 49 (19\%){]} responded that they do ``Neither.'' With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample 303 (44\%) {[}EFA: 194 (45\%); CFA: 109 (42\%){]} of the participants indicated that they were in a home office/ home schooling setting., while 109 (16\%) overall {[}EFA: 68 (16\%) ; CFA: 41 (16\%){]} reported face-to-face work/schooling.
-Lastly, 147 (21\%) overall {[}EFA: 94 (22\%) ; CFA: 53 (20\%){]} reported a combination of home- and face-to-face work/schooling, whereas 131 (19\%) overall {[}EFA: 72 (17\%); CFA: 59 (23\%){]} filled in the ``Neither (no work or school, or indication)'' response option.
+For their ``Occupational Status,'' more than half of the overall sample reported that they currently work {[}Overall: 396 (57\%); EFA: 235 (55\%); CFA: 161 (61\%){]}, whereas 174 (25\%) {[}EFA: 122 (29\%); CFA: 52 (20\%){]} reported that they go to school and 120 (17\%) {[}EFA: 71 (17\%); CFA: 49 (19\%){]} responded that they do ``Neither.'' With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample 303 (44\%) {[}EFA: 194 (45\%); CFA: 109 (42\%){]} of the participants indicated that they were in a home office/ home schooling setting, while 109 (16\%) overall {[}EFA: 68 (16\%) ; CFA: 41 (16\%){]} reported face-to-face work/schooling.
+Lastly, 147 (21\%) overall {[}EFA: 94 (22\%) ; CFA: 53 (20\%){]} reported a combination of home- and face-to-face work/schooling, whereas 131 (19\%) overall {[}EFA: 72 (17\%); CFA: 59 (23\%){]} filled in the ``Neither (no work or school, or on vacation)'' response option.
 We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable ``Age'' and Pearson's \(\chi^2\) test for all other categorical variables via the gtsummary R package's ``add\_p'' function (Sjoberg et al., 2021a) .
@@
 
+\hypertarget{procedure}{%
+\subsection{Procedure}\label{procedure}}
+
+\hypertarget{item-generation}{%
+\subsubsection{Item Generation}\label{item-generation}}
+
 \begin{enumerate}
@@
 \item
-  Describe EFA and CFA sample separately.
-\item
-  Sampling technique: Convince sampling (non-probability sample)
-\item
-  Method: cross-sectional survey
-\item
-  How many missing data?
-\item
-  How incomplete data were addressed.
-\item
-  Why such sample was chosen?
-\end{enumerate}
-
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
-
-\hypertarget{development-of-the-scale}{%
-\subsubsection{Development of the Scale}\label{development-of-the-scale}}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
   How the items were generated
@@
 \end{figure}
-
-\hypertarget{data-collection}{%
-\subsubsection{Data Collection}\label{data-collection}}
-
-Timeline of data collection, mode of data collection.
 
@@
 Upon inspection, it was understood that these items are negatively correlated to the common theme, and thus in the CFA analysis, we reversed the response code for these two items.
+Figure \ref{fig:gtPic} depicts the data distribution and endorsement pattern for the included items in our LEBA scale for both the EFA and CFA sample.
 
@@
 We judged the model fit based on the comparative fit indices: CFI, TLI and parsimony fit index:RMSEA.
-Our fitted model attained acceptable fit (CFI =.94; TLI = .93); RMSEA = .06,{[}.05-.07, 90\% CI{]}) with two imposed equity constrain on item pairs 32-33 and 19-17 .
-However SRMR value was higher than the guideline (SRMR = .12).
-Further by allowing one pair of items (30-41) to covary their error variance and discarding two item (item 37 \& 26) for very low r-square value, our model attained best fit (CFI =.97; TLI = .96); RMSEA = .05{[}.04-.06, 90\% CI{]}) and SRMR value (SRMR = .09) was also close to the suggestions of Hu and Bentle (1999).
+Our fitted model attained acceptable fit (CFI =.94; TLI = .93); RMSEA = .06,{[}.05-.07, 90\% CI{]}) with two imposed equity constrain on item pairs 32-33 {[}I dim my mobile phone screen within 1 hour before attempting to fall asleep.;I dim my computer screen within 1 hour before attempting to fall asleep.{]} and 16-17 {[}I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day.;I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day.{]}.
+Items pair 32-33 stemed from the preference of dimming electric device's brightness before bed time and items pair 16 and 19 stemed from the preference of using blue filtering or colored glasses during the daytime.
+Nevertheless, SRMR value was higher than the guideline (SRMR = .12).
+Further by allowing one pair of items (30-41) {[}I look at my smartwatch within 1 hour before attempting to fall asleep.;I look at my smartwatch when I wake up at night.{]} to covary their error variance and discarding two item (item 37 \& 26) for very low r-square value, our model attained best fit (CFI =.97; TLI = .96); RMSEA = .05{[}.04-.06, 90\% CI{]}) and SRMR value (SRMR = .09) was also close to the suggestions of Hu and Bentle (1999).
 Internal consistency ordinal \(\alpha\) for the five factors of LEBA were .96, .83, .70, .69, .52 respectively.
@@
 \end{lltable}
+
+\hypertarget{sementic-analysis}{%
+\subsection{Sementic Analysis}\label{sementic-analysis}}
+
+To find out if our developed scale is overlapping with existing instruments, we subjected the items of LEBA to The ``Semantic Scale Network''(SSN)(Rosenbusch, Wanders, \& Pit, 2020).
+The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 (Rosenbusch et al., 2020).
+Pairs of scale with a cosine similarity index value of 1 indicates they are perfectly redundant scales.
+LEBA appeared most strongly related to scales about sleep: ``Sleep Disturbance Scale For Children'' (Bruni et al., 1996) and ``WHO-Composite International Diagnostic Interview (CIDI): Insomnia''(WHO, 1990).The cosine similarities lie between .47 to .51.
+Two factors of our LEBA tool: ``Using phone and smart-watch in bed'' and ``Using light before bedtime'' dealt with light exposure related behavior pertaining to sleep quality.
+As such the similarity index obtained is expected.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-bruni1996sleep}{}}%
+Bruni, O., Ottaviano, S., Guidetti, V., Romoli, M., Innocenzi, M., Cortesi, F., \& Giannotti, F.
+(1996).
+The sleep disturbance scale for children (SDSC) construct ion and validation of an instrument to evaluate sleep disturbances in childhood and adolescence.
+\emph{Journal of Sleep Research}, \emph{5}(4), 251--261.
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-likert}{}}%
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-rosenbusch2020semantic}{}}%
+Rosenbusch, H., Wanders, F., \& Pit, I.
+L.
+(2020).
+The semantic scale network: An online tool to detect semantic overlap of psychological scales and prevent scale redundancies.
+\emph{Psychological Methods}, \emph{25}(3), 380.
+
 \leavevmode\vadjust pre{\hypertarget{ref-R-lavaan}{}}%
@@
 Weinzaepflen, C., \& Spitschan, M. (2021). Enlighten your clock: How your body tells time. {Open Science Framework}. \url{https://doi.org/10.17605/OSF.IO/ZQXVH}
+
+\leavevmode\vadjust pre{\hypertarget{ref-who1990}{}}%
+WHO. (1990). Composite international diagnostic interview.
 

### 2021-11-15 Supplymentary.Rmd
Updated PDF

@@
 
-```{r EFAResidualsAppB,   fig.cap=' Histogram of residulas:  five-factor solution', warning=FALSE,  results='asis'}
+```{r EFAResidualsAppB, eval=FALSE, fig.cap=' Histogram of residulas:  five-factor solution', warning=FALSE, include=FALSE, results='asis'}
 hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))

### 2021-11-15 manuscript.Rmd
Header corrections
Updated PDF

@@
 
-## Procedure
-
-### Item Generation
+## Item Generation
 
@@
 For our analysis we used R (version 4.1.0), with several R packages.
-Initially, our tool had six point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Always).
+Initially, our tool had six point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always).
 Our purpose was to capture light exposure related behavior and these two response options: "Does not apply/I don't know" and "Never" were providing similar information.
@@
 Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018].
-We also conducted psychometric analysis on non-merged response options data (supplementary analysis) and rejected the latent structure obtained as the factors were less interpretable.
+We confirmed the latent structure obtained in the EFA by conducting a "Confirmatory Factor Analysis" (CFA) using "robust weighted least square estimator" (WLSMV).
+We estiablished the measurement invariance of our tool across native and non-native English speakers using structural equation model framework.
+To assess the possible semantic overlap of our tool with the existing tools, we sought to "Semantic Scale Network" [@rosenbusch2020semantic].
+Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA.
+We also conducted psychometric analysis on non-merged response options data (Supp. Table \@ref(tab:EFATableAppB)) and rejected the latent structure obtained as the factors were less interpretable.
 
@@
 The corrected item-total correlation ranges between `r apa(low.r.corec,2,F)` -`r apa(high.r.corec,2,F)`.
-No item was discarded based on descriptive statistics or item analysis.
+However, no item was discarded based on descriptive statistics or item analysis.
 
@@
 The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cutoff value (.50) indicating a mediocre sample [@hutchesonMultivariateSocialScientist1999].
-Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001] indicated the correlations between items are adequate for the EFA.
+Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001 indicated the correlations between items are adequate for the EFA.
 However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than .30.
 The inter item correlation ranged between `r apa(min.cor,2,F)` to `r apa(max.cor,2,F)`.
-And the corrected item-total correlations ranged between `r apa(low.r.corec,2,F)` to `r apa(high.r.corec,2,F)`.
+
 ```{r tabDes,results='asis'}
@@
 # loading
-min.loadings <- min(Fac.5$loadings)
-max.loadings <- max(Fac.5$loadings)
+min.loadings <- abs(min(Fac.5$loadings))
+max.loadings <- abs(max(Fac.5$loadings))
 
@@
 Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 [@brownConfirmatoryFactorAnalysis2015], all factor-loading higher than .30 and no cross-loading greater than .30.
-We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (Table\@ref(tab:MinResTab)).
-Table\@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items.
+We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (Table \@ref(tab:MinResTab)).
+Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items.
 The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients.
 The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`.
-However, the histogram of the absolute values of non-redundant residual-correlations Fig\@ref(fig:EFAResiduals) showed `r apa(sumR,0, T)`% correlations greater than the absolute value of .05, indicating a possible under-factoring.
+However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:EFAResiduals)) showed `r apa(sumR,0, T)`% correlations greater than the absolute value of .05, indicating a possible under-factoring.
 [@desjardinsHandbookEducationalMeasurement2018].
 Subsequently, we fitted a six-factor solution.
-However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution (Table\@ref(tab:sixFacTab)).
+However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution (Table \@ref(tab:sixFacTab)).
 Internal consistency reliability coefficient Cronbach's alpha assumes all the factor-loadings of the items under a factor are equal [@graham2006congeneric; @novick1967coefficient] which is not the case in our sample.
@@
 We also estimated the internal consistency reliability of the total scale using Mcdonald's $\omega$ (total) coefficient which is a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
-McDonald's omega(total) coefficient for the total scale was `r apa(rel.k[5,6],2,F)`.
+McDonald's $\omega$(total) coefficient for the total scale was `r apa(rel.k[5,6],2,F)`.
 
@@
 
-## Sementic Analysis 
+## Semantic Analysis 
 To find out if our developed tool is overlapping with existing instruments, we subjected the items of LEBA to the "Semantic Scale Network"(SSN) analysis[@rosenbusch2020semantic].
@@
 Test information curve (TIC) (Figure \@ref(fig:Testinfo)) indicate the amount of information an the full-scale carry along the latent trait continuum.
-As we treated each factor of short-LEBA as an unidmensional construct we obtain 5 TICs (figure \@ref(Fig:Testinfo)).
-These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum (($\theta$)).
+As we treated each factor of short-LEBA as an unidmensional construct we obtain 5 TICs (Figure \@ref(fig:Testinfo)).
+These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum ($\theta$).
 Also the amount of information changed rather steadily with the change of ($\theta$).
@@
 
-The overall we can concluded that IRT analysis indicated LEBA is a psychometrically sound measure.
+The overall we can concluded that IRT analysis indicated short form of LEBA is a psychometrically sound measure.
 Item fit indexes and person fit index for all five fitted model were acceptable.
 Items had diverse slope parameters indicating a good range of discrimination- the ability to differentiate respondents with different levels of the light exposure related behavior.
-All-in-all we can recommend the LEBA to be used to capture light exposure related behavior.
+All-in-all we can recommend the short form of LEBA to be used to capture light exposure related behavior.
 

### 2021-11-15 manuscript.tex
Updated PDF

@@
 
-\hypertarget{procedure}{%
-\subsection{Procedure}\label{procedure}}
-
 \hypertarget{item-generation}{%
-\subsubsection{Item Generation}\label{item-generation}}
+\subsection{Item Generation}\label{item-generation}}
 
@@
 For our analysis we used R (version 4.1.0), with several R packages.
-Initially, our tool had six point Likert type response scale (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Always).
+Initially, our tool had six point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Always).
 Our purpose was to capture light exposure related behavior and these two response options: ``Does not apply/I don't know'' and ``Never'' were providing similar information.
-As such we decided to collapse them into one making it a 5 point Likert type response scale.
+As such we decided to collapse them into one making it a 5 point Likert type response format.
 Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
@@
 Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \textless0.3 (iii) no items with cross-loading greater than .3 across factors (Bandalos \& Finney, 2018).
-We also conducted psychometric analysis on non-merged response options data (supplementary analysis) and rejected the latent structure obtained as the factors were less interpretable.
+We confirmed the latent structure obtained in the EFA by conducting a ``Confirmatory Factor Analysis'' (CFA) using ``robust weighted least square estimator'' (WLSMV).
+We estiablished the measurement invariance of our tool across native and non-native English speakers using structural equation model framework.
+To assess the possible semantic overlap of our tool with the existing tools, we sought to ``Semantic Scale Network'' (Rosenbusch, Wanders, \& Pit, 2020).
+Lastly, we sought ``Item Response Theory'' (IRT) based analysis on developing a short form of LEBA.
+We also conducted psychometric analysis on non-merged response options data (Supp. Table \ref{tab:EFATableAppB}) and rejected the latent structure obtained as the factors were less interpretable.
 
@@
 The corrected item-total correlation ranges between .03 -.48.
-No item was discarded based on descriptive statistics or item analysis.
+However, no item was discarded based on descriptive statistics or item analysis.
 
@@
 The overall KMO vale for 48 items was 0.63 which was above the cutoff value (.50) indicating a mediocre sample (Hutcheson, 1999).
-Bartlett's test of sphericity (Bartlett, 1954), \(\chi^2\) (1128) = 5042.86, p \textless{} .001{]} indicated the correlations between items are adequate for the EFA.
+Bartlett's test of sphericity (Bartlett, 1954), \(\chi^2\) (1128) = 5042.86, p \textless{} .001 indicated the correlations between items are adequate for the EFA.
 However only 4.96\% of the inter-item correlation coefficients were greater than .30.
@@
 Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 (Brown, 2015), all factor-loading higher than .30 and no cross-loading greater than .30.
-We confirmed this five-factor latent structure using varimax rotation with a minimum residual extraction method (Table\ref{tab:MinResTab}).
-Table\ref{tab:EFATable} displays the factor-loading (structural coefficients) and communality of the items.
-The absolute value of the factor-loading ranged from -.49 to .99 indicating strong coefficients.
+We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (Table\ref{tab:MinResTab}).
+Table \ref{tab:EFATable} displays the factor-loading (structural coefficients) and communality of the items.
+The absolute value of the factor-loading ranged from .49 to .99 indicating strong coefficients.
 The commonalities ranged between .11 to .99.
@@
 Upon inspection, it was understood that these items are negatively correlated to the common theme, and thus in the CFA analysis, we reversed the response code for these two items.
-Figure \ref{fig:gtPic} depicts the data distribution and endorsement pattern for the included items in our LEBA scale for both the EFA and CFA sample.
+Figure \ref{fig:gtPic} depicts the data distribution and endorsement pattern for the included items in our LEBA tool for both the EFA and CFA sample.
 
@@
 This model is the highest level of MI and assures the equivalence of precision of items across the groups in measuring the underlying constructs.
-The invariance model fit of our scale was assessed using the fit indices including \(\chi^2\) test, CFI and TLI (close to .95 or above), RMSEA (close to .06 or below) (Hu \& Bentle, 1999).
+The invariance model fit of our tool was assessed using the fit indices including \(\chi^2\) test, CFI and TLI (close to .95 or above), RMSEA (close to .06 or below) (Hu \& Bentle, 1999).
 We excluded SRMR from our consideration as it does not behave optimally for categorical variables (C.
@@
 
-\hypertarget{sementic-analysis}{%
-\subsection{Sementic Analysis}\label{sementic-analysis}}
-
-To find out if our developed scale is overlapping with existing instruments, we subjected the items of LEBA to The ``Semantic Scale Network''(SSN)(Rosenbusch, Wanders, \& Pit, 2020).
+\hypertarget{semantic-analysis}{%
+\subsection{Semantic Analysis}\label{semantic-analysis}}
+
+To find out if our developed tool is overlapping with existing instruments, we subjected the items of LEBA to the ``Semantic Scale Network''(SSN) analysis(Rosenbusch et al., 2020).
 The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 (Rosenbusch et al., 2020).
-Pairs of scale with a cosine similarity index value of 1 indicates they are perfectly redundant scales.
+Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy.
 LEBA appeared most strongly related to scales about sleep: ``Sleep Disturbance Scale For Children'' (Bruni et al., 1996) and ``WHO-Composite International Diagnostic Interview (CIDI): Insomnia''(WHO, 1990).The cosine similarities lie between .47 to .51.
@@
 Baker (2017) categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \textgreater1.70.
-Table \ref{tab:IRTparameters} summarizes the IRT parameters of our scale.
-Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level (\(\theta\)).
+Table \ref{tab:IRTparameters} summarizes the IRT parameters of our tool.
+Item discrimination parameters of our tool fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level (\(\theta\)).
 Examination of the item information curve \ref{fig:itmeinfo} indicated 6 items (1, 25, 9, 38, 30, \& 41) had relatively flat information curves thus discarded creating a short form of LEBA with 5 factors and 17 items.
@@
 Also the amount of information changed rather steadily with the change of (\(\theta\)).
-Thus we conferred the LEBA scale (except blue filter) estimated the light exposure related behavior with precision near the center of trait continuum (Baker, 2017) which is sufficient to discriminate between latent trait measured by the each factor.
+Thus we conferred the LEBA tool (except blue filter) estimated the light exposure related behavior with precision near the center of trait continuum (Baker, 2017) which is sufficient to discriminate between latent trait measured by the each factor.
 The blue filter factor had a peak to the right side of the center of latent trait indicating its ability to providing information only for people who already have some preference towards using blue-filters.
@@
 \end{longtable}
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/EFAResidualsAppB-1.pdf}
-\caption{\label{fig:EFAResidualsAppB} Histogram of residulas: five-factor
-solution}
-\end{figure}
 \end{appendix}

### 2021-11-15 manuscript.Rmd
*IRT plots updated

@@
 EFAplot <- grViz("
-digraph boxes_and_circles {
+digraph nicegraph {
 
@@
 
-```{r EFAplot, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, out.height="100%", out.width="200%", results='asis'}
+```{r EFAplot, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, out.height="60%", out.width="100%", results='asis'}
 knitr::include_graphics('Manuscript.figures/EFAplot.png')
@@
     rows = 1:25  
-  ) %>% gtsave("Manuscript.figures/gt.png")
-
-```
-
-```{r gtPic, echo=FALSE, out.height="100%", out.width="200%", fig.cap= ' Summary Descriptives of CFA and EFA Sample'}
+  ) %>% gtsave("Manuscript.figures/gt.png",vwidth = 3000)
+
+```
+
+```{r gtPic, echo=FALSE, out.height="100%", out.width="120%", fig.cap= ' Summary Descriptives of CFA and EFA Sample'}
 knitr::include_graphics('Manuscript.figures/gt.png')
@@
 
+```{r saveiteminfo, include=F}
+jpeg("Manuscript.figures/iteminfo.png", width = 800, height = 750)
+plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
+          labels = "AUTO", label_size = 10,align = "v",ncol = 2)
+
+dev.off()
+```
+
 ```{r IRTreliability, include=F}
@@
 
-```{r itmeinfo, fig.cap="Item information curves (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
-plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
-          labels = "AUTO", label_size = 10,align = "v")
+```{r itmeinfo, fig.cap="Item information curves (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="60%"}
+knitr::include_graphics('Manuscript.figures/iteminfo.png')
 
@@
 
-colnames(itemfit) <- c("Signed Chi-square", "df", "RMSEA", "p")
+colnames(itemfit) <- c("Item","Signed Chi-square", "df", "RMSEA", "p")
 
@@
 
-```{r Testinfo, fig.cap="Test information curves (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
+```{r savetestinfo, include=F, warning=F, message=F}
+jpeg("Manuscript.figures/testinfo.png", width = 800, height = 750)
 plot_grid(F1_test.info , F2_test.info.redu,F3_test.info.redu,F4_test.info.redu,F5_test.info,
           labels = "AUTO", label_size = 10, align = "v" )
-
+dev.off()
+```
+
+```{r Testinfo, fig.cap="Test information curves (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="60%"}
+
+knitr::include_graphics('Manuscript.figures/testinfo.png')
 ```

### 2021-11-15 manuscript.tex
*IRT plots updated

@@
 For our analysis we used R (version 4.1.0), with several R packages.
-Initially, our tool had six point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5: Always).
+Initially, our tool had six point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always).
 Our purpose was to capture light exposure related behavior and these two response options: ``Does not apply/I don't know'' and ``Never'' were providing similar information.
@@
 The inter item correlation ranged between .44 to .91.
-And the corrected item-total correlations ranged between .03 to .48.
 
@@
 
-{\centering \includegraphics[width=2\linewidth,height=1\textheight]{Manuscript.figures/EFAplot}
+{\centering \includegraphics[width=1\linewidth,height=0.6\textheight]{Manuscript.figures/EFAplot}
 
@@
 Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 (Brown, 2015), all factor-loading higher than .30 and no cross-loading greater than .30.
-We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (Table\ref{tab:MinResTab}).
+We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (Table \ref{tab:MinResTab}).
 Table \ref{tab:EFATable} displays the factor-loading (structural coefficients) and communality of the items.
@@
 The commonalities ranged between .11 to .99.
-However, the histogram of the absolute values of non-redundant residual-correlations Fig\ref{fig:EFAResiduals} showed 26\% correlations greater than the absolute value of .05, indicating a possible under-factoring.
+However, the histogram of the absolute values of non-redundant residual-correlations (Figure \ref{fig:EFAResiduals}) showed 26\% correlations greater than the absolute value of .05, indicating a possible under-factoring.
 (Desjardins \& Bulut, 2018).
 Subsequently, we fitted a six-factor solution.
-However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution (Table\ref{tab:sixFacTab}).
+However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution (Table \ref{tab:sixFacTab}).
 Internal consistency reliability coefficient Cronbach's alpha assumes all the factor-loadings of the items under a factor are equal (Graham, 2006; Novick \& Lewis, 1967) which is not the case in our sample.
@@
 \begin{figure}
-\includegraphics[width=2\linewidth,height=1\textheight]{Manuscript.figures/gt} \caption{ Summary Descriptives of CFA and EFA Sample}\label{fig:gtPic}
+\includegraphics[width=1.2\linewidth,height=1\textheight]{Manuscript.figures/gt} \caption{ Summary Descriptives of CFA and EFA Sample}\label{fig:gtPic}
 \end{figure}
@@
 We also estimated the internal consistency reliability of the total scale using Mcdonald's \(\omega\) (total) coefficient which is a better reliability estimate for multidimensional constructs (Dunn, Baguley, \& Brunsden, 2014; Sijtsma, 2009).
-McDonald's omega(total) coefficient for the total scale was .73.
+McDonald's \(\omega\)(total) coefficient for the total scale was .73.
 
@@
 \begin{figure}
-\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/itmeinfo-1} \caption{Item information curves (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime}\label{fig:itmeinfo}
+\includegraphics[width=1\linewidth,height=0.6\textheight]{Manuscript.figures/iteminfo} \caption{Item information curves (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime}\label{fig:itmeinfo}
 \end{figure}
@@
 \begin{figure}
-\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/Testinfo-1} \caption{Test information curves (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime}\label{fig:Testinfo}
+\includegraphics[width=1\linewidth,height=0.6\textheight]{Manuscript.figures/testinfo} \caption{Test information curves (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime}\label{fig:Testinfo}
 \end{figure}
@@
 Test information curve (TIC) (Figure \ref{fig:Testinfo}) indicate the amount of information an the full-scale carry along the latent trait continuum.
-As we treated each factor of short-LEBA as an unidmensional construct we obtain 5 TICs (figure \ref{Fig:Testinfo}).
-These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum ((\(\theta\))).
+As we treated each factor of short-LEBA as an unidmensional construct we obtain 5 TICs (Figure \ref{fig:Testinfo}).
+These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum (\(\theta\)).
 Also the amount of information changed rather steadily with the change of (\(\theta\)).
@@
 \toprule
-Signed Chi-square & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{RMSEA} & \multicolumn{1}{c}{p} & \multicolumn{1}{c}{NA}\\
+Item & \multicolumn{1}{c}{Signed Chi-square} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{RMSEA} & \multicolumn{1}{c}{p}\\
 \midrule

### 2021-11-15 manuscript.Rmd
Updated Flowchart1

@@
 
-                    graph [fontname = Helvetica,layout = dot,fontsize = 20, ]
-
-                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 6.5, height = 1, 
-                    fixedsize = true,fontsize = 20]
+                    graph [fontname = Helvetica,layout = dot,fontsize = 40, ]
+
+                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 15, height = 1, 
+                    fixedsize = true,fontsize = 40]
 
@@
 
-                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 7.5, height = 2, 
-                    fixedsize = true, fontsize = 20]
+                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 15, height = 6, 
+                    fixedsize = true, fontsize = 40]
                     C[label = 
@@
                       style = rounded
-                     node[fontname = Helvetica, margin = 0.2,width = 9, height = 1, 
-                    fixedsize = true, fontsize = 18 ]
+                     node[fontname = Helvetica, margin = 0.2,width = 18, height = 2, 
+                    fixedsize = true, fontsize = 38 ]
 
@@
                      2[label = 'Reliability Analysis on EFA Sample (N=428)
-                    Alpha F1 =.86; F2 = .71; F3 = .68; F4 =.62; F5 =.52']
+                    Ordinal alpha F1 =.94; F2 = .76; F3 = .75; F4 =.72; F5 =.62']
 
@@
                      5[label = 'Reliability Analysis on CFA (23 Items; N=262) 
-                      Alpha F1=.93; F2=.80; F3 =.62; F4=.72; F5=.45']
-                    8[label = 'LEBA Short Form (17 Items; N=690) 
+                      Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52']
+                    8[label = 'Measurement Invariance Analysis
+                    Residual measurement invariance achieved']
+                    9[label = 'Semantic Analysis']
+                    10[label = 'LEBA Short Form (17 Items; N=690) 
                       Based on Item Response Theory']
@@
                       style = rounded
-                     node[fontname = Helvetica, margin = 0.2,width = 8, height = 1, 
-                fixedsize = true, fontsize = 18 ]
+                     node[fontname = Helvetica, margin = 0.2,width = 18, height = 2, 
+                fixedsize = true, fontsize = 38 ]
                     6[label = '6-Factor solution: one factor emerged with only two salient loadings']
@@
                     5->8
+                    8 ->9
+                    9 ->10
                      C ->6
@@
 }")
-
 export_svg(Flowchart1) %>%
@@
   rsvg() %>%
-  png::writePNG("Manuscript.figures/Flowchart1.png")
-
-```
-
-```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='150%', out.width='100%'}
+  png::writePNG("Manuscript.figures/Flowchart1.png", dpi = 1200)
+
+```
+
+```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='160%', out.width='100%'}
 knitr::include_graphics('Manuscript.figures/Flowchart1.png')
@@
 
-{rank = same; F1 F2 F3 F4 F5}
 # edge definitions with the node IDs
@@
   rsvg() %>%
-  png::writePNG("Manuscript.figures/EFAplot.png")
+  png::writePNG("Manuscript.figures/EFAplot.png", dpi = 1200)
 
@@
 All the items fitted well to the respective models as assessed by  RMSEA value obtained from Signed-$\chi^2$ index implementation.
-All of the items had RMSEA value <.06 indicating adequate fit.
+All of the items had RMSEA value $\le$.06 indicating adequate fit.
 Figure \@ref(fig:personfit) depicts the person fit of out fitted models.

### 2021-11-15 manuscript.Rmd
scale curve is moved

@@
 ```{r setup, warning=FALSE, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600)
+knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=1200)
 options(knitr.duplicate.label = "allow")
@@
 library(MOTE)
-library(car)#revercoding 
+library(car)#reversecoding 
 library(psych)
@@
 ## Semantic Analysis 
-To find out if our developed tool is overlapping with existing instruments, we subjected the items of LEBA to the "Semantic Scale Network"(SSN) analysis[@rosenbusch2020semantic].
+To find out if our developed tool is overlapping with existing instruments, we subjected the items of LEBA to the "Semantic Scale Network"(SSN) analysis [@rosenbusch2020semantic].
 The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic].
@@
 Fig indicates that Zh is larger than -2 for most participants, suggesting a good fit of the selected IRT models.
+
 ```{r itemfittab, results='asis',warning=F, message=F}
@@
 
-Next, we generated scale characteristics curve (Figure \@ref(fig:scalechar)) which plotted estimated theta score against the expected true score.
-The purpose of this scale characteristics curve is to find the corresponding expected true score for the given estimated theta score.
-
-```{r scalechar, fig.cap="Scale characteristic curve of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
+```{r scalechar, eval=FALSE, fig.cap="Scale characteristic curve of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, include=FALSE, out.height="120%", out.width="100%"}
+
+#Finally we generated scale characteristics curve (Figure \@ref(fig:scalechar)) which plotted estimated theta score against the expected true score.
+The purpose of this scale characteristics curve is to find the corresponding expected true score for the given estimated theta score of the participants.
 

### 2021-11-15 manuscript.Rmd
Figure 5 Updates

@@
 
-# Proportion of off-diagonal elements >.10
+# Proportion of off-diagonal elements >.05
 sumR <- sum(BigRR/totRR*100)
@@
 ```{r EFAResiduals, out.height= "100%",  fig.align='center', fig.cap= ' Histogram of residuals:  five-factor solution',  out.width="100%",  warning=FALSE, results='asis'}
-hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))
+hist(residual.5F,  main = NULL, xlab = "Residuals", ylim=c(0, 400))
 abline(h =51, lwd = 2, lty = 2)

### 2021-11-15 Supplymentary.Rmd
Figure captions in sup.analysis are updated

@@
 
-```{r figCorAppB,  fig.cap="Correlation plot of the items",  out.width="100%"}
+```{r figCorAppB,  fig.cap="Correlation plot of the items [Unmerged response options]",  out.width="100%"}
 
@@
 
-```{r facIdFigAppB,  fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot', warning=FALSE}
+```{r facIdFigAppB,  fig.cap='Factor Identification  (A) Parallel analysis (B) Scree Plot' [Unmerged response options], warning=FALSE}
 cowplot::plot_grid(parallel, scree.plot, labels = "AUTO",ncol=1, label_size = 8,align = "v")
@@
 
-efa.table <- tabledown::fac.tab(fa.5F.4,.3)
+efa.table <- tabledown::fac.tab(fa.5F.4,.3, complexity = F)
 
@@
 ```{r EFATableAppB, results='asis'}
-
 apa_table(efa.table, caption = "Factor loadings and communality of the retained items [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T)

### 2021-11-15 manuscript.Rmd
Figure captions in sup.analysis are updated

@@
     rows = 1:25  
-  ) %>% gtsave("Manuscript.figures/gt.png",vwidth = 3000)
-
-```
-
-```{r gtPic, echo=FALSE, out.height="100%", out.width="120%", fig.cap= ' Summary Descriptives of CFA and EFA Sample'}
+  ) %>% gtsave("Manuscript.figures/gt.png",vwidth = 7000)
+
+```
+
+```{r gtPic, echo=FALSE, out.height="100%", out.width="200%", fig.cap= ' Summary Descriptives of CFA and EFA Sample'}
 knitr::include_graphics('Manuscript.figures/gt.png')

### 2021-11-15 manuscript.tex
Updated Flowchart1
Figure captions in sup.analysis are updated

@@
 
-{\centering \includegraphics[width=1\linewidth,height=1.5\textheight]{Manuscript.figures/Flowchart1}
+{\centering \includegraphics[width=1\linewidth,height=1.6\textheight]{Manuscript.figures/Flowchart1}
 
@@
 \begin{figure}
-\includegraphics[width=1.2\linewidth,height=1\textheight]{Manuscript.figures/gt} \caption{ Summary Descriptives of CFA and EFA Sample}\label{fig:gtPic}
+\includegraphics[width=2\linewidth,height=1\textheight]{Manuscript.figures/gt} \caption{ Summary Descriptives of CFA and EFA Sample}\label{fig:gtPic}
 \end{figure}
@@
 
-To find out if our developed tool is overlapping with existing instruments, we subjected the items of LEBA to the ``Semantic Scale Network''(SSN) analysis(Rosenbusch et al., 2020).
+To find out if our developed tool is overlapping with existing instruments, we subjected the items of LEBA to the ``Semantic Scale Network''(SSN) analysis (Rosenbusch et al., 2020).
 The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 (Rosenbusch et al., 2020).
@@
 All the items fitted well to the respective models as assessed by RMSEA value obtained from Signed-\(\chi^2\) index implementation.
-All of the items had RMSEA value \textless.06 indicating adequate fit.
+All of the items had RMSEA value \(\le\).06 indicating adequate fit.
 Figure \ref{fig:personfit} depicts the person fit of out fitted models.
@@
 \includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/personfit-1} \caption{Person fit of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime}\label{fig:personfit}
-\end{figure}
-
-Next, we generated scale characteristics curve (Figure \ref{fig:scalechar}) which plotted estimated theta score against the expected true score.
-The purpose of this scale characteristics curve is to find the corresponding expected true score for the given estimated theta score.
-
-\begin{figure}
-\includegraphics[width=1\linewidth,height=1.2\textheight]{manuscript_files/figure-latex/scalechar-1} \caption{Scale characteristic curve of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime}\label{fig:scalechar}
 \end{figure}

### 2021-11-15 Supplymentary.Rmd
* All tables and figures are now cross referenced in the text

--- 2021-11-13 Supplymentary.Rmd
@@
 
+# SA: Confirming the five factor solution obtained using minimum residual extraction method
+
 ```{r MinRes, include=F}
@@
 papaja::apa_table(minresTab,  caption = "Factor loadings and communality of the retained items(Minmum Residual)", note = "Only loading higher than .30 is reported", longtable=T)
+```
 
-```
+# SA: Factor analysis with six factors
 
@@
 
-# Factor Analysis with Unmerged Response Option
+# SA: Factor Analysis with Unmerged Response Option
+
 ```{r DataAppB, include=FALSE}
@@
 #KMO test
-KMO <- KMO(EFA.data)
+KMO.1 <- KMO(EFA.data)
 
 # Test of correlation matrix
-bartlet <- cortest.bartlett(EFA.data, n =428)
+bartlet.1 <- cortest.bartlett(EFA.data, n =428)
 
@@
 # Multivariate Normality
-mardia <- mardia(EFA.data, na.rm = T, plot =F)
+mardia.1 <- mardia(EFA.data, na.rm = T, plot =F)
 
@@
 
-```{r tabDesAppB, results='asis'}
-apa_table(Des.combined, caption = "Descriptive Statistics for Unmerged response options",  note = "*p<.001", longtable =T)
-```
-
-```{r CorrMatrixAppB, include=FALSE}
+```{r CorrMatrixAppB, include=FALSE, warning=F,message=F}
 #Polychoric Correlation matrix
@@
 
-min.cor <- abs(min(upper)) #minimum cor.coefficient of the matrix
-max.cor <- abs(max(upper)) # max. correlation coefficient of the matrix
+min.cor.1 <- apa(min(abs(upper)),2,F) #minimum cor.coefficient of the matrix
+max.cor.1 <- apa(max(abs(upper)),2,F) # max. correlation coefficient of the matrix
 
@@
 totR = length(EFA.data)*(length(EFA.data)-1)/2
-cor.per <- print (BigR/totR)*100
-```
-
-```{r figCorAppB,  fig.cap="Correlation plot of the items",  out.width="100%"}
-
-ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
-           ggtheme = ggplot2::theme_minimal, tl.cex = 6,tl.srt = 90 )
-#p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
-#to show pvalue in the fig add p.mat=p.mat
+cor.per.1 <- print (BigR/totR)*100
 ```
@@
 
-```{r facIdFigAppB,  fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot', warning=FALSE}
+Table \@ref(tab:tabDesAppB) summarizes the univariate descriptive statistics for the 48 items with un-merged options.
+Some of the items were skewed with high Kurtosis values.
+Our data violated both univariate normality (Shapiro-Wilk statistics) and multivariate normality assumptions [Marida's test].
+Multivariate skew was = `r printnum(mardia.1$b1p)` (p <0.001) and multivariate kurtosis was = `r printnum(mardia.1$b2p)` (p <0.001).
+Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen.
+Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy.
+The overall KMO vale for 48 items was `r printnum(KMO.1$MSA)` which was above the cutoff value (.50) indicating a mediocre sample.
+Bartlett's test of sphericity, $\chi^2$ (`r bartlet.1$df`) = `r apa(bartlet.1$chisq, 2, T)`, p < .001 indicated the correlations between items are adequate for the EFA.
+However only `r apa(cor.per.1, 2,T)`% of the inter-item correlation coefficients were greater than .30.
+The absolute value of inter-item correlation ranged between `r min.cor.1` to `r max.cor.1`.Figure \@ref(fig:figCorAppB) depicts the correlation matrix.
+For un-merged response option Horn's parallel analysis with 500 iterations indicated a five-factor solution.
+However, Scree plot and the MAP method suggested 6-factor solution.
+five-factor solution .
+As a result, we tested both five-factor and six-factor solutions.
+The six factor solution yielded a factor with only two salient loading (Table \@ref(tab:EFAsix).
+Thus we reject the six factor solution.
+The five factor solution retained 24 items (Table \@ref(tab:EFATableAppB)).
+However the factors are less interpretable in terms of common theme.
+Thus we reject the five factor solution.
+
+```{r tabDesAppB, results='asis'}
+apa_table(Des.combined, caption = "Descriptive Statistics for Unmerged response options",  note = "*p<.001", longtable =T)
+```
+
+```{r figCorAppB, fig.cap="Correlation plot of the items [Unmerged response options]", include=FALSE, out.width="100%"}
+
+ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
+           ggtheme = ggplot2::theme_minimal, tl.cex = 6,tl.srt = 90 )
+#p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
+#to show pvalue in the fig add p.mat=p.mat
+```
+
+```{r facIdFigAppB,  fig.cap='Factor Identification  (A) Parallel analysis (B) Scree Plot [Unmerged response options]', warning=FALSE}
 cowplot::plot_grid(parallel, scree.plot, labels = "AUTO",ncol=1, label_size = 8,align = "v")
@@
 ```
-
-Horn's parallel analysis with 500 iterations indicated a five-factor solution.
-However, Scree plot and the MAP method suggested 6-factor solution.
-five-factor solution .
-As a result, we tested both five-factor and six-factor solutions.
 
@@
 #Preparing the EFA table
-
-efa.table <- tabledown::fac.tab(fa.5F.4,.3)
-
-#Communality
-Fac.5 <- fa.5F.4
-min.com <- min(Fac.5$communality)
-max.com <- max(Fac.5$communality)
-
-# loading
-min.loadings <- min(Fac.5$loadings)
-max.loadings <- max(Fac.5$loadings)
-
-# Residuals
-residual.5F =residuals(fa.5F.4, diag = FALSE, na.rm =T)
-#Count of numbers of residuals>.05
-BigRR= sum(residual.5F>abs(.05), na.rm =T)
-print(BigRR)
-
-#Total number of off diagonal elements in the data matrix
-totRR = length(reduced.model.5F.3)*(length(reduced.model.5F.3)-1)/2
-
-# Proportion of off-diagonal elements >.10
-sumR <- sum(BigRR/totRR*100)
-
+efa.table <- tabledown::fac.tab(fa.5F.4,.3, complexity = F) 
 ```
@@
 ```{r EFATableAppB, results='asis'}
-
-apa_table(efa.table, caption = "Factor loadings and communality of the retained items [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T)
+apa_table(efa.table, caption = "Factor loadings and communality of the retained items in five factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T)
 ```
 
-| **Five Factor Solution[Unmerged Responses] (24 Items)** |
+```{r EFAAppsix, include=FALSE, warning=F,message=FALSE}
+fa.6F.1 <- fa(r=correlations$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+DD <- print(fa.6F.1, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.6F.1 <- dplyr::select(EFA.data ,
+                                    -c(item32, item34, item44,item24, item37, item22, item5,
+                                        item28,item39,item23, item45, item6, item29, item2, item41, item30))
+
+correlations.red.6F.2 <- polychoric(reduced.model.6F.1,correct = 0)
+
+fa.6F.2 <- fa(r=correlations.red.6F.2$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+
+EE <- print(fa.6F.2, cut = .3, digits = 3, sort = TRUE)
+reduced.model.6F.2 <- dplyr::select(EFA.data ,
+                                    -c(item32, item34, item44,item24, item37, item22, item5,
+                                        item28,item39,item23, item45, item6, item29, item2, item41, item30, item46, item36,item1, item25))
+correlations.red.6F.3 <- polychoric(reduced.model.6F.2,correct = 0)
+fa.6F.3 <- fa(r=correlations.red.6F.3$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+FF <- print(fa.6F.3, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.6F.3 <- dplyr::select(EFA.data ,
+                                    -c(item32, item34, item44,item24, item37, item22, item5,
+                                        item28,item39,item23, item45, item6, item29, item2, item41, item30, item46, item36,item1, item25, item18))
+correlations.red.6F.4 <- polychoric(reduced.model.6F.3,correct = 0)
+fa.6F.4 <- fa(r=correlations.red.6F.4$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+FF <- print(fa.6F.4, cut = .3, digits = 3, sort = TRUE)
+
+efa.table.2 <- tabledown::fac.tab(fa.6F.4,.3, complexity = F) 
+```
+
+```{r EFAsix, results='asis'}
+apa_table(efa.table.2, caption = "Factor loadings and communality of the retained items in six factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T)
+```
+
+# Items Retained in the Five Factor Solution [Unmerged Responses]
+
+| **Five Factor Solution [Unmerged Responses] (24 Items)** |
 |---------------------------------------------------------|
@@
 abline(v =.05,lwd = 2, lty = 2)
-
 ```

### 2021-11-15 Supplymentary.tex
*IRT plots updated
* All tables and figures are now cross referenced in the text

@@
 \begin{appendix}
-\section{}
+\hypertarget{sa-confirming-the-five-factor-solution-obtained-using-minimum-residual-extraction-method}{%
+\section{SA: Confirming the five factor solution obtained using minimum
+residual extraction
+method}\label{sa-confirming-the-five-factor-solution-obtained-using-minimum-residual-extraction-method}}
+
 \begin{center}
@@
 \end{center}
+
+\hypertarget{sa-factor-analysis-with-six-factors}{%
+\section{SA: Factor analysis with six
+factors}\label{sa-factor-analysis-with-six-factors}}
 
@@
 
-\hypertarget{factor-analysis-with-unmerged-response-option}{%
-\section{Factor Analysis with Unmerged Response
-Option}\label{factor-analysis-with-unmerged-response-option}}
+\hypertarget{sa-factor-analysis-with-unmerged-response-option}{%
+\section{SA: Factor Analysis with Unmerged Response
+Option}\label{sa-factor-analysis-with-unmerged-response-option}}
+
+Table @ref(tab:tabDesAppB) summarizes the univariate descriptive
+statistics for the 48 items with un-merged options. Some of the items
+were skewed with high Kurtosis values. Our data violated both univariate
+normality (Shapiro-Wilk statistics) and multivariate normality
+assumptions {[}Marida's test{]}. Multivariate skew was = 494.70 (p
+\textless0.001) and multivariate kurtosis was = 2,705.00 (p
+\textless0.001). Due to these violations and ordinal nature of the
+response data polychoric correlations over Pearson's correlations was
+chosen. Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO)
+measures of sampling adequacy. The overall KMO vale for 48 items was
+0.65 which was above the cutoff value (.50) indicating a mediocre
+sample. Bartlett's test of sphericity, \(\chi^2\) (1128) = 5515.20, p
+\textless{} .001 indicated the correlations between items are adequate
+for the EFA. However only 4.34\% of the inter-item correlation
+coefficients were greater than .30. The absolute value of inter-item
+correlation ranged between .00 to .96.Figure @ref(fig:figCorAppB)
+depicts the correlation matrix. For un-merged response option Horn's
+parallel analysis with 500 iterations indicated a five-factor solution.
+However, Scree plot and the MAP method suggested 6-factor solution.
+five-factor solution . As a result, we tested both five-factor and
+six-factor solutions. The six factor solution yielded a factor with only
+two salient loading (Table @ref(tab:EFAsix). Thus we reject the six
+factor solution. The five factor solution retained 24 items (Table
+@ref(tab:EFATableAppB)). However the factors are less interpretable in
+terms of common theme. Thus we reject the five factor solution.
 
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-1} \caption{Correlation plot of the items}(\#fig:figCorAppB)
-\end{figure}
-
-\begin{figure}
 \centering
@@
 \caption{(\#fig:facIdFigAppB)Factor Identification (A) Parallel analysis
-(B) Scree Plot}
+(B) Scree Plot {[}Unmerged response options{]}}
 \end{figure}
 
-Horn's parallel analysis with 500 iterations indicated a five-factor
-solution. However, Scree plot and the MAP method suggested 6-factor
-solution. five-factor solution . As a result, we tested both five-factor
-and six-factor solutions.
+\begin{center}
+\begin{ThreePartTable}
+
+\begin{TableNotes}[para]
+\normalsize{\textit{Note.} Only loading higher than .30 is reported}
+\end{TableNotes}
+
+\begin{longtable}{llllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:EFATableAppB}Factor loadings and communality of the retained items in five factor solution [Unmerged Responses]}\\
+\toprule
+item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness}\\
+\midrule
+\endfirsthead
+\caption*{\normalfont{Table \ref{tab:EFATableAppB} continued}}\\
+\toprule
+item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness}\\
+\midrule
+\endhead
+item19 & 0.99 &  &  &  &  & 1.007 & -0.007\\
+item20 & 0.91 &  &  &  &  & 0.874 & 0.126\\
+item18 & 0.82 &  &  &  &  & 0.711 & 0.289\\
+item21 & 0.8 &  &  &  &  & 0.683 & 0.317\\
+item4 & 0.47 &  &  &  &  & 0.25 & 0.75\\
+item11 &  & 0.83 &  &  &  & 0.687 & 0.313\\
+item10 &  & 0.81 &  &  &  & 0.67 & 0.33\\
+item12 &  & 0.56 &  &  &  & 0.371 & 0.629\\
+item8 &  & -0.44 &  &  &  & 0.206 & 0.794\\
+item7 &  & 0.42 &  &  &  & 0.226 & 0.774\\
+item9 &  & 0.33 &  &  &  & 0.115 & 0.885\\
+item16 &  &  & 0.95 &  &  & 0.946 & 0.054\\
+item17 &  &  & 0.74 &  &  & 0.595 & 0.405\\
+item36 & 0.3 &  & 0.73 &  &  & 0.653 & 0.347\\
+item3 &  &  &  & 0.85 &  & 0.746 & 0.254\\
+item27 &  &  &  & 0.78 &  & 0.624 & 0.376\\
+item40 &  &  &  & 0.71 &  & 0.512 & 0.488\\
+item35 &  &  &  &  & 0.58 & 0.351 & 0.649\\
+item48 &  &  &  &  & 0.57 & 0.354 & 0.646\\
+item33 &  &  &  &  & 0.55 & 0.32 & 0.68\\
+item47 &  &  &  &  & 0.52 & 0.294 & 0.706\\
+item44 &  &  &  &  & 0.45 & 0.216 & 0.784\\
+item31 &  &  &  &  & 0.41 & 0.206 & 0.794\\
+item38 &  &  &  &  & 0.33 & 0.129 & 0.871\\
+\% of Variance & 0.15 & 0.09 & 0.09 & 0.08 & 0.08 &  & \\
+\bottomrule
+\addlinespace
+\insertTableNotes
+\end{longtable}
+
+\end{ThreePartTable}
+\end{center}
 
@@
 \begin{longtable}{lllllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
-\caption{\label{tab:EFATableAppB}Factor loadings and communality of the retained items [Unmerged Responses]}\\
+\caption{\label{tab:EFAsix}Factor loadings and communality of the retained items in six factor solution [Unmerged Responses]}\\
 \toprule
-item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness} & \multicolumn{1}{c}{Complexity}\\
+item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{PA6} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness}\\
 \midrule
 \endfirsthead
-\caption*{\normalfont{Table \ref{tab:EFATableAppB} continued}}\\
+\caption*{\normalfont{Table \ref{tab:EFAsix} continued}}\\
 \toprule
-item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness} & \multicolumn{1}{c}{Complexity}\\
+item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{PA6} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness}\\
 \midrule
 \endhead
-item19 & 0.99 &  &  &  &  & 1.007 & -0.007 & 1.058\\
-item20 & 0.91 &  &  &  &  & 0.874 & 0.126 & 1.114\\
-item18 & 0.82 &  &  &  &  & 0.711 & 0.289 & 1.123\\
-item21 & 0.8 &  &  &  &  & 0.683 & 0.317 & 1.163\\
-item4 & 0.47 &  &  &  &  & 0.25 & 0.75 & 1.298\\
-item11 &  & 0.83 &  &  &  & 0.687 & 0.313 & 1.007\\
-item10 &  & 0.81 &  &  &  & 0.67 & 0.33 & 1.031\\
-item12 &  & 0.56 &  &  &  & 0.371 & 0.629 & 1.374\\
-item8 &  & -0.44 &  &  &  & 0.206 & 0.794 & 1.106\\
-item7 &  & 0.42 &  &  &  & 0.226 & 0.774 & 1.614\\
-item9 &  & 0.33 &  &  &  & 0.115 & 0.885 & 1.1\\
-item16 &  &  & 0.95 &  &  & 0.946 & 0.054 & 1.097\\
-item17 &  &  & 0.74 &  &  & 0.595 & 0.405 & 1.168\\
-item36 & 0.3 &  & 0.73 &  &  & 0.653 & 0.347 & 1.431\\
-item3 &  &  &  & 0.85 &  & 0.746 & 0.254 & 1.048\\
-item27 &  &  &  & 0.78 &  & 0.624 & 0.376 & 1.028\\
-item40 &  &  &  & 0.71 &  & 0.512 & 0.488 & 1.05\\
-item35 &  &  &  &  & 0.58 & 0.351 & 0.649 & 1.091\\
-item48 &  &  &  &  & 0.57 & 0.354 & 0.646 & 1.144\\
-item33 &  &  &  &  & 0.55 & 0.32 & 0.68 & 1.085\\
-item47 &  &  &  &  & 0.52 & 0.294 & 0.706 & 1.186\\
-item44 &  &  &  &  & 0.45 & 0.216 & 0.784 & 1.145\\
-item31 &  &  &  &  & 0.41 & 0.206 & 0.794 & 1.477\\
-item38 &  &  &  &  & 0.33 & 0.129 & 0.871 & 1.317\\
-\% of Variance & 0.15 & 0.09 & 0.09 & 0.08 & 0.08 &  &  & \\
+item19 & 0.98 &  &  &  &  &  & 0.995 & 0.005\\
+item20 & 0.92 &  &  &  &  &  & 0.904 & 0.096\\
+item21 & 0.79 &  &  &  &  &  & 0.666 & 0.334\\
+item4 & 0.49 &  &  &  &  &  & 0.296 & 0.704\\
+item43 & 0.32 &  &  &  &  & 0.31 & 0.282 & 0.718\\
+item10 &  & 0.81 &  &  &  &  & 0.67 & 0.33\\
+item11 &  & 0.81 &  &  &  &  & 0.668 & 0.332\\
+item12 &  & 0.58 &  &  &  &  & 0.408 & 0.592\\
+item8 &  & -0.45 &  &  &  &  & 0.218 & 0.782\\
+item7 &  & 0.42 &  &  &  &  & 0.229 & 0.771\\
+item9 &  & 0.33 &  &  &  &  & 0.115 & 0.885\\
+item3 &  &  & 0.85 &  &  &  & 0.731 & 0.269\\
+item27 &  &  & 0.77 &  &  &  & 0.606 & 0.394\\
+item40 &  &  & 0.72 &  &  &  & 0.533 & 0.467\\
+item35 &  &  &  & 0.64 &  &  & 0.426 & 0.574\\
+item33 &  &  &  & 0.62 &  &  & 0.413 & 0.587\\
+item48 &  &  &  & 0.52 &  &  & 0.305 & 0.695\\
+item47 &  &  &  & 0.48 &  &  & 0.259 & 0.741\\
+item31 &  &  &  & 0.39 &  &  & 0.206 & 0.794\\
+item38 &  &  &  & 0.32 &  &  & 0.18 & 0.82\\
+item17 &  &  &  &  & 0.85 &  & 0.786 & 0.214\\
+item16 &  &  &  &  & 0.78 &  & 0.681 & 0.319\\
+item13 &  &  &  &  &  & 0.57 & 0.336 & 0.664\\
+item14 &  &  &  &  &  & 0.5 & 0.356 & 0.644\\
+item15 &  &  &  &  &  & 0.48 & 0.277 & 0.723\\
+item42 &  &  &  &  &  & 0.37 & 0.168 & 0.832\\
+item26 &  &  &  &  &  &  & 0.064 & 0.936\\
+\% of Variance & 0.11 & 0.08 & 0.07 & 0.06 & 0.06 & 0.05 &  & \\
 \bottomrule
@@
 
+\hypertarget{items-retained-in-the-five-factor-solution-unmerged-responses}{%
+\section{Items Retained in the Five Factor Solution {[}Unmerged
+Responses{]}}\label{items-retained-in-the-five-factor-solution-unmerged-responses}}
+
 \begin{longtable}[]{@{}
@@
 \begin{minipage}[b]{\linewidth}\raggedright
-\textbf{Five Factor Solution{[}Unmerged Responses{]} (24 Items)}
+\textbf{Five Factor Solution {[}Unmerged Responses{]} (24 Items)}
 \end{minipage} \\
@@
 \end{longtable}
-
-\begin{figure}
-\centering
-\includegraphics{manuscript_files/figure-latex/EFAResidualsAppB-1.pdf}
-\caption{(\#fig:EFAResidualsAppB) Histogram of residulas: five-factor
-solution}
-\end{figure}
 \end{appendix}

### 2021-11-15 manuscript.Rmd
* All tables and figures are now cross referenced in the text

@@
 
-```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='160%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/Flowchart1.png')
-```
-
 ## Analytic Strategies
 
+Figure \@ref(fig:FlowchartFig) summarizes the steps of our psychometric analysis.
 For our analysis we used R (version 4.1.0), with several R packages.
@@
 
+```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='160%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/Flowchart1.png')
+```
+
 # Results
@@
 
-min.cor <- abs(min(upper)) #minimum cor.coefficient of the matrix
-max.cor <- abs(max(upper)) # max. correlation coefficient of the matrix
+min.cor <- apa(min(abs(upper)),2,F) #minimum cor.coefficient of the matrix
+max.cor <- apa(max(abs(upper)),2,F) # max. correlation coefficient of the matrix
 
@@
 However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than .30.
-The inter item correlation ranged between `r apa(min.cor,2,F)` to `r apa(max.cor,2,F)`.
+The absolute value of inter-item correlation ranged between `r min.cor` to `r max.cor`.
+Figure \@ref(fig:figCor) depicts the correlation matrix.
 
@@
 
-```{r EFAplot, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, out.height="60%", out.width="100%", results='asis'}
-knitr::include_graphics('Manuscript.figures/EFAplot.png')
-
-```
-
 ```{r Cronbach alpha for 5 fators, message=TRUE, warning=FALSE, include=FALSE}
@@
 The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`.
+Figure \@ref(fig:EFAplot) depicts the obtained five-five factor structure.
 However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:EFAResiduals)) showed `r apa(sumR,0, T)`% correlations greater than the absolute value of .05, indicating a possible under-factoring.
@@
 Figure \@ref(fig:gtPic) depicts the data distribution and endorsement pattern for the included items in our LEBA tool for both the EFA and CFA sample.
+
+```{r EFAplot, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, out.height="60%", out.width="100%", results='asis'}
+knitr::include_graphics('Manuscript.figures/EFAplot.png')
+
+```
 
@@
 McDonald's $\omega$(total) coefficient for the total scale was `r apa(rel.k[5,6],2,F)`.
+Figure \@ref(fig:figcfa) depicts the obtained CFA structure.
 
@@
 As we treated each factor of short-LEBA as an unidmensional construct we obtain 5 TICs (Figure \@ref(fig:Testinfo)).
-These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum ($\theta$).
-Also the amount of information changed rather steadily with the change of ($\theta$).
-Thus we conferred the LEBA tool (except blue filter) estimated the light exposure related behavior with precision near the center of trait continuum [@bakerBasicsItemResponse2017] which is sufficient to discriminate between latent trait measured by the each factor.
-The blue filter factor had a peak to the right side of the center of latent trait indicating its ability to providing information only for people who already have some preference towards using blue-filters.
+These information curves indicated except the first and fifth factors, the other three factor's TICs are roughly centered on the center of the trait continuum ($\theta$).The first and fifth factor had a peak to the right side of the center of latent trait.Thus we conferred the LEBA tool estimated the light exposure related behavior with precision near the center of trait continuum for 2nd, 3rd and 4th factors and near the right side of the center of trait continuum for 1st and 5th factors [@bakerBasicsItemResponse2017].
 

### 2021-11-15 manuscript.tex
* All tables and figures are now cross referenced in the text

@@
 
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth,height=1.6\textheight]{Manuscript.figures/Flowchart1}
-
-}
-
-\caption{Development of long and short form of LEBA}\label{fig:FlowchartFig}
-\end{figure}
-
 \hypertarget{analytic-strategies}{%
@@
 
+Figure \ref{fig:FlowchartFig} summarizes the steps of our psychometric analysis.
 For our analysis we used R (version 4.1.0), with several R packages.
@@
 
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth,height=1.6\textheight]{Manuscript.figures/Flowchart1}
+
+}
+
+\caption{Development of long and short form of LEBA}\label{fig:FlowchartFig}
+\end{figure}
+
 \hypertarget{results}{%
@@
 However only 4.96\% of the inter-item correlation coefficients were greater than .30.
-The inter item correlation ranged between .44 to .91.
+The absolute value of inter-item correlation ranged between .00 to .91.
+Figure \ref{fig:figCor} depicts the correlation matrix.
 
@@
 
-\begin{figure}
-
-{\centering \includegraphics[width=1\linewidth,height=0.6\textheight]{Manuscript.figures/EFAplot}
-
-}
-
-\caption{Five Factor Solution}\label{fig:EFAplot}
-\end{figure}
-
 With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items.
@@
 The commonalities ranged between .11 to .99.
+Figure \ref{fig:EFAplot} depicts the obtained five-five factor structure.
 However, the histogram of the absolute values of non-redundant residual-correlations (Figure \ref{fig:EFAResiduals}) showed 26\% correlations greater than the absolute value of .05, indicating a possible under-factoring.
@@
 Figure \ref{fig:gtPic} depicts the data distribution and endorsement pattern for the included items in our LEBA tool for both the EFA and CFA sample.
+
+\begin{figure}
+
+{\centering \includegraphics[width=1\linewidth,height=0.6\textheight]{Manuscript.figures/EFAplot}
+
+}
+
+\caption{Five Factor Solution}\label{fig:EFAplot}
+\end{figure}
 
@@
 McDonald's \(\omega\)(total) coefficient for the total scale was .73.
+Figure \ref{fig:figcfa} depicts the obtained CFA structure.
 
@@
 As we treated each factor of short-LEBA as an unidmensional construct we obtain 5 TICs (Figure \ref{fig:Testinfo}).
-These information curves indicated except blue filter factor, the other factor's TICs are roughly centered on the center of the trait continuum (\(\theta\)).
-Also the amount of information changed rather steadily with the change of (\(\theta\)).
-Thus we conferred the LEBA tool (except blue filter) estimated the light exposure related behavior with precision near the center of trait continuum (Baker, 2017) which is sufficient to discriminate between latent trait measured by the each factor.
-The blue filter factor had a peak to the right side of the center of latent trait indicating its ability to providing information only for people who already have some preference towards using blue-filters.
+These information curves indicated except the first and fifth factors, the other three factor's TICs are roughly centered on the center of the trait continuum (\(\theta\)).The first and fifth factor had a peak to the right side of the center of latent trait.Thus we conferred the LEBA tool estimated the light exposure related behavior with precision near the center of trait continuum for 2nd, 3rd and 4th factors and near the right side of the center of trait continuum for 1st and 5th factors (Baker, 2017).
 
@@
 
-\hypertarget{factor-analysis-with-unmerged-response-option}{%
-\section{Factor Analysis with Unmerged Response
-Option}\label{factor-analysis-with-unmerged-response-option}}
+\hypertarget{sa-factor-analysis-with-unmerged-response-option}{%
+\section{SA: Factor Analysis with Unmerged Response
+Option}\label{sa-factor-analysis-with-unmerged-response-option}}
+
+Table \ref{tab:tabDesAppB} summarizes the univariate descriptive
+statistics for the 48 items with un-merged options. Some of the items
+were skewed with high Kurtosis values. Our data violated both univariate
+normality (Shapiro-Wilk statistics) and multivariate normality
+assumptions {[}Marida's test{]}. Multivariate skew was = 494.70 (p
+\textless0.001) and multivariate kurtosis was = 2,705.00 (p
+\textless0.001). Due to these violations and ordinal nature of the
+response data polychoric correlations over Pearson's correlations was
+chosen. Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO)
+measures of sampling adequacy. The overall KMO vale for 48 items was
+0.65 which was above the cutoff value (.50) indicating a mediocre
+sample. Bartlett's test of sphericity, \(\chi^2\) (1128) = 5515.20, p
+\textless{} .001 indicated the correlations between items are adequate
+for the EFA. However only 4.34\% of the inter-item correlation
+coefficients were greater than .30. The absolute value of inter-item
+correlation ranged between .00 to .96.Figure \ref{fig:figCorAppB}
+depicts the correlation matrix. For un-merged response option Horn's
+parallel analysis with 500 iterations indicated a five-factor solution.
+However, Scree plot and the MAP method suggested 6-factor solution.
+five-factor solution . As a result, we tested both five-factor and
+six-factor solutions. The six factor solution yielded a factor with only
+two salient loading (Table \ref{tab:EFAsix}. Thus we reject the six
+factor solution. The five factor solution retained 24 items (Table
+\ref{tab:EFATableAppB}). However the factors are less interpretable in
+terms of common theme. Thus we reject the five factor solution.
 
@@
 \begin{figure}
-\includegraphics[width=1\linewidth]{manuscript_files/figure-latex/figCorAppB-1} \caption{Correlation plot of the items}\label{fig:figCorAppB}
-\end{figure}
-
-\begin{figure}
 \centering
@@
 \caption{\label{fig:facIdFigAppB}Factor Identification (A) Parallel analysis
-(B) Scree Plot}
+(B) Scree Plot {[}Unmerged response options{]}}
 \end{figure}
-
-Horn's parallel analysis with 500 iterations indicated a five-factor
-solution. However, Scree plot and the MAP method suggested 6-factor
-solution. five-factor solution . As a result, we tested both five-factor
-and six-factor solutions.
 
@@
 
-\begin{longtable}{lllllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
-\caption{\label{tab:EFATableAppB}Factor loadings and communality of the retained items [Unmerged Responses]}\\
-\toprule
-item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness} & \multicolumn{1}{c}{Complexity}\\
+\begin{longtable}{llllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:EFATableAppB}Factor loadings and communality of the retained items in five factor solution [Unmerged Responses]}\\
+\toprule
+item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness}\\
 \midrule
@@
 \toprule
-item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness} & \multicolumn{1}{c}{Complexity}\\
+item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness}\\
 \midrule
 \endhead
-item19 & 0.99 &  &  &  &  & 1.007 & -0.007 & 1.058\\
-item20 & 0.91 &  &  &  &  & 0.874 & 0.126 & 1.114\\
-item18 & 0.82 &  &  &  &  & 0.711 & 0.289 & 1.123\\
-item21 & 0.8 &  &  &  &  & 0.683 & 0.317 & 1.163\\
-item4 & 0.47 &  &  &  &  & 0.25 & 0.75 & 1.298\\
-item11 &  & 0.83 &  &  &  & 0.687 & 0.313 & 1.007\\
-item10 &  & 0.81 &  &  &  & 0.67 & 0.33 & 1.031\\
-item12 &  & 0.56 &  &  &  & 0.371 & 0.629 & 1.374\\
-item8 &  & -0.44 &  &  &  & 0.206 & 0.794 & 1.106\\
-item7 &  & 0.42 &  &  &  & 0.226 & 0.774 & 1.614\\
-item9 &  & 0.33 &  &  &  & 0.115 & 0.885 & 1.1\\
-item16 &  &  & 0.95 &  &  & 0.946 & 0.054 & 1.097\\
-item17 &  &  & 0.74 &  &  & 0.595 & 0.405 & 1.168\\
-item36 & 0.3 &  & 0.73 &  &  & 0.653 & 0.347 & 1.431\\
-item3 &  &  &  & 0.85 &  & 0.746 & 0.254 & 1.048\\
-item27 &  &  &  & 0.78 &  & 0.624 & 0.376 & 1.028\\
-item40 &  &  &  & 0.71 &  & 0.512 & 0.488 & 1.05\\
-item35 &  &  &  &  & 0.58 & 0.351 & 0.649 & 1.091\\
-item48 &  &  &  &  & 0.57 & 0.354 & 0.646 & 1.144\\
-item33 &  &  &  &  & 0.55 & 0.32 & 0.68 & 1.085\\
-item47 &  &  &  &  & 0.52 & 0.294 & 0.706 & 1.186\\
-item44 &  &  &  &  & 0.45 & 0.216 & 0.784 & 1.145\\
-item31 &  &  &  &  & 0.41 & 0.206 & 0.794 & 1.477\\
-item38 &  &  &  &  & 0.33 & 0.129 & 0.871 & 1.317\\
-\% of Variance & 0.15 & 0.09 & 0.09 & 0.08 & 0.08 &  &  & \\
+item19 & 0.99 &  &  &  &  & 1.007 & -0.007\\
+item20 & 0.91 &  &  &  &  & 0.874 & 0.126\\
+item18 & 0.82 &  &  &  &  & 0.711 & 0.289\\
+item21 & 0.8 &  &  &  &  & 0.683 & 0.317\\
+item4 & 0.47 &  &  &  &  & 0.25 & 0.75\\
+item11 &  & 0.83 &  &  &  & 0.687 & 0.313\\
+item10 &  & 0.81 &  &  &  & 0.67 & 0.33\\
+item12 &  & 0.56 &  &  &  & 0.371 & 0.629\\
+item8 &  & -0.44 &  &  &  & 0.206 & 0.794\\
+item7 &  & 0.42 &  &  &  & 0.226 & 0.774\\
+item9 &  & 0.33 &  &  &  & 0.115 & 0.885\\
+item16 &  &  & 0.95 &  &  & 0.946 & 0.054\\
+item17 &  &  & 0.74 &  &  & 0.595 & 0.405\\
+item36 & 0.3 &  & 0.73 &  &  & 0.653 & 0.347\\
+item3 &  &  &  & 0.85 &  & 0.746 & 0.254\\
+item27 &  &  &  & 0.78 &  & 0.624 & 0.376\\
+item40 &  &  &  & 0.71 &  & 0.512 & 0.488\\
+item35 &  &  &  &  & 0.58 & 0.351 & 0.649\\
+item48 &  &  &  &  & 0.57 & 0.354 & 0.646\\
+item33 &  &  &  &  & 0.55 & 0.32 & 0.68\\
+item47 &  &  &  &  & 0.52 & 0.294 & 0.706\\
+item44 &  &  &  &  & 0.45 & 0.216 & 0.784\\
+item31 &  &  &  &  & 0.41 & 0.206 & 0.794\\
+item38 &  &  &  &  & 0.33 & 0.129 & 0.871\\
+\% of Variance & 0.15 & 0.09 & 0.09 & 0.08 & 0.08 &  & \\
 \bottomrule
@@
 
+\begin{center}
+\begin{ThreePartTable}
+
+\begin{TableNotes}[para]
+\normalsize{\textit{Note.} Only loading higher than .30 is reported}
+\end{TableNotes}
+
+\begin{longtable}{lllllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
+\caption{\label{tab:EFAsix}Factor loadings and communality of the retained items in six factor solution [Unmerged Responses]}\\
+\toprule
+item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{PA6} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness}\\
+\midrule
+\endfirsthead
+\caption*{\normalfont{Table \ref{tab:EFAsix} continued}}\\
+\toprule
+item & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{PA6} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{Communality} & \multicolumn{1}{c}{Uniqueness}\\
+\midrule
+\endhead
+item19 & 0.98 &  &  &  &  &  & 0.995 & 0.005\\
+item20 & 0.92 &  &  &  &  &  & 0.904 & 0.096\\
+item21 & 0.79 &  &  &  &  &  & 0.666 & 0.334\\
+item4 & 0.49 &  &  &  &  &  & 0.296 & 0.704\\
+item43 & 0.32 &  &  &  &  & 0.31 & 0.282 & 0.718\\
+item10 &  & 0.81 &  &  &  &  & 0.67 & 0.33\\
+item11 &  & 0.81 &  &  &  &  & 0.668 & 0.332\\
+item12 &  & 0.58 &  &  &  &  & 0.408 & 0.592\\
+item8 &  & -0.45 &  &  &  &  & 0.218 & 0.782\\
+item7 &  & 0.42 &  &  &  &  & 0.229 & 0.771\\
+item9 &  & 0.33 &  &  &  &  & 0.115 & 0.885\\
+item3 &  &  & 0.85 &  &  &  & 0.731 & 0.269\\
+item27 &  &  & 0.77 &  &  &  & 0.606 & 0.394\\
+item40 &  &  & 0.72 &  &  &  & 0.533 & 0.467\\
+item35 &  &  &  & 0.64 &  &  & 0.426 & 0.574\\
+item33 &  &  &  & 0.62 &  &  & 0.413 & 0.587\\
+item48 &  &  &  & 0.52 &  &  & 0.305 & 0.695\\
+item47 &  &  &  & 0.48 &  &  & 0.259 & 0.741\\
+item31 &  &  &  & 0.39 &  &  & 0.206 & 0.794\\
+item38 &  &  &  & 0.32 &  &  & 0.18 & 0.82\\
+item17 &  &  &  &  & 0.85 &  & 0.786 & 0.214\\
+item16 &  &  &  &  & 0.78 &  & 0.681 & 0.319\\
+item13 &  &  &  &  &  & 0.57 & 0.336 & 0.664\\
+item14 &  &  &  &  &  & 0.5 & 0.356 & 0.644\\
+item15 &  &  &  &  &  & 0.48 & 0.277 & 0.723\\
+item42 &  &  &  &  &  & 0.37 & 0.168 & 0.832\\
+item26 &  &  &  &  &  &  & 0.064 & 0.936\\
+\% of Variance & 0.11 & 0.08 & 0.07 & 0.06 & 0.06 & 0.05 &  & \\
+\bottomrule
+\addlinespace
+\insertTableNotes
+\end{longtable}
+
+\end{ThreePartTable}
+\end{center}
+
+\hypertarget{items-retained-in-the-five-factor-solution-unmerged-responses}{%
+\section{Items Retained in the Five Factor Solution {[}Unmerged
+Responses{]}}\label{items-retained-in-the-five-factor-solution-unmerged-responses}}
+
 \begin{longtable}[]{@{}

### 2021-11-17 Supplymentary.Rmd
adding Geographic location table to Supplements (still needs work in the formatting)

@@
 ```
+
+# Geographic Locations of Survey Participants
+```{r TzTable, include=FALSE, warning=F,message=FALSE}
+descriptives.data%>%
+  tbl_summary(
+    label = slypos_demographics_tz.factor ~ "Time zone - Country",
+    statistic = list(all_categorical() ~ "{n} ({p}%)"),
+    missing = "no",
+    sort = all_categorical() ~ "frequency",
+    include = "slypos_demographics_tz.factor"
+  )  %>% bold_labels() %>% 
+  modify_header(label ~ "") %>%
+  modify_caption("Geographical Location") -> tz_table
+
+  as_tibble(tz_table, format = 'pipe') -> tz_tibble
+
+as_kable_extra(tz_table, format = "latex",booktabs = T) -> tz_kable
+
+```
+
+```{r tzTabPrint, results='asis'}
+
+tz_kable %>% kable_styling(latex_options = c("scale_down"))
+
+```

### 2021-11-17 manuscript.Rmd
added text on item generation

@@
 
+- What data will be available 
+- Where this data will be available 
+- under which licence
+- who to contact
+
 ## Survey characteristics
@@
 
-For a full list of geographic locations, see Suppl. Table X in the appendix.
+For a more complete list of geographic locations, see Suppl. Table X in the appendix.
 
@@
 
-1.  How the items were generated
-2.  How the literature was reviewed to identify construct adequacy of the items.
-3.  Discuss the expert panel review process to assess content validity
+To ensure construct adequacy we thoroughly assessed the current status of literature and identified a variety of light exposure related scales.
+However, no scales specifically measuring the behavioral component of light exposure were found (cf.
+Table 1).
+Consequentially we pursued to introduce a new openly available scale to address this research gap.
+For this purpose an expert researcher panel from the fields of chronobiology, light research, neuroscience and psychology (including seven of the authors, see authors roles) generated and collected preliminary item ideas.
+Special attention was paid to design items circumscribed to assess light exposure *behavior* as opposed to subjective measurements of the light environment (cf.[@eklund1996development] & [@dianat2013objective]) and semi-quantitive assesments of light sources' illuminance (cf.
+[@bajaj2011validation]) in order to maintain content validity.
+In a collective effort the generated items were then peer-reviewed,  amended, unified, and complemented with a suitable response scale (5 point Likert-scale ranging from 1 "Never/Does not apply/I don’t know" to 5 "Always").
+This process was finalized when all experts were in agreement, resulting in 48 items to implement in the first data collection.
 

### 2021-11-17 Supplymentary.tex
* table 1 updated

@@
 \end{longtable}
+
+\hypertarget{geographic-locations-of-survey-participants}{%
+\section{Geographic Locations of Survey
+Participants}\label{geographic-locations-of-survey-participants}}
+
+\begin{table}
+
+\caption{(\#tab:TzTable)Geographical Location}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}[t]{ll}
+\toprule
+ & N = 690\\
+\midrule
+Time zone - Country & \\
+\hspace{1em}United States - America/New\_York (UTC -04:00) & 63 (9.1\%)\\
+\hspace{1em}United Kingdom - Europe/London (UTC) & 57 (8.3\%)\\
+\hspace{1em}Germany - Europe/Berlin (UTC +01:00) & 53 (7.7\%)\\
+\hspace{1em}India - Asia/Kolkata (UTC +05:30) & 38 (5.5\%)\\
+\addlinespace
+\hspace{1em}United States - America/Los\_Angeles (UTC -07:00) & 37 (5.4\%)\\
+\hspace{1em}United States - America/Chicago (UTC -05:00) & 30 (4.3\%)\\
+\hspace{1em}France - Europe/Paris (UTC +01:00) & 22 (3.2\%)\\
+\hspace{1em}Switzerland - Europe/Zurich (UTC +01:00) & 21 (3.0\%)\\
+\hspace{1em}Brazil - America/Sao\_Paulo (UTC -03:00) & 19 (2.8\%)\\
+\addlinespace
+\hspace{1em}Netherlands - Europe/Amsterdam (UTC +01:00) & 19 (2.8\%)\\
+\hspace{1em}Canada - America/Toronto (UTC -04:00) & 16 (2.3\%)\\
+\hspace{1em}Poland - Europe/Warsaw (UTC +01:00) & 15 (2.2\%)\\
+\hspace{1em}Canada - America/Edmonton (UTC -06:00) & 14 (2.0\%)\\
+\hspace{1em}Finland - Europe/Helsinki (UTC +02:00) & 9 (1.3\%)\\
+\addlinespace
+\hspace{1em}Indonesia - Asia/Jakarta (UTC +07:00) & 9 (1.3\%)\\
+\hspace{1em}Italy - Europe/Rome (UTC +01:00) & 9 (1.3\%)\\
+\hspace{1em}Chile - America/Santiago (UTC -03:00) & 8 (1.2\%)\\
+\hspace{1em}Russian Federation - Europe/Moscow (UTC +03:00) & 8 (1.2\%)\\
+\hspace{1em}China - Asia/Shanghai (UTC +08:00) & 7 (1.0\%)\\
+\addlinespace
+\hspace{1em}Malaysia - Asia/Kuala\_Lumpur (UTC +08:00) & 7 (1.0\%)\\
+\hspace{1em}Spain - Europe/Madrid (UTC +01:00) & 7 (1.0\%)\\
+\hspace{1em}United States - America/Phoenix (UTC -07:00) & 7 (1.0\%)\\
+\hspace{1em}Canada - America/Vancouver (UTC -07:00) & 6 (0.9\%)\\
+\hspace{1em}New Zealand - Pacific/Auckland (UTC +13:00) & 6 (0.9\%)\\
+\addlinespace
+\hspace{1em}Philippines - Asia/Manila (UTC +08:00) & 6 (0.9\%)\\
+\hspace{1em}Turkey - Europe/Istanbul (UTC +03:00) & 6 (0.9\%)\\
+\hspace{1em}United States - America/Denver (UTC -06:00) & 6 (0.9\%)\\
+\hspace{1em}United States - America/Detroit (UTC -04:00) & 6 (0.9\%)\\
+\hspace{1em}Argentina - America/Argentina/Buenos\_Aires (UTC -03:00) & 5 (0.7\%)\\
+\addlinespace
+\hspace{1em}Australia - Australia/Melbourne (UTC +11:00) & 5 (0.7\%)\\
+\hspace{1em}Ireland - Europe/Dublin (UTC) & 5 (0.7\%)\\
+\hspace{1em}Lithuania - Europe/Vilnius (UTC +02:00) & 5 (0.7\%)\\
+\hspace{1em}South Africa - Africa/Johannesburg (UTC +02:00) & 5 (0.7\%)\\
+\hspace{1em}Australia - Australia/Brisbane (UTC +10:00) & 4 (0.6\%)\\
+\addlinespace
+\hspace{1em}Belgium - Europe/Brussels (UTC +01:00) & 4 (0.6\%)\\
+\hspace{1em}Israel - Asia/Jerusalem (UTC +02:00) & 4 (0.6\%)\\
+\hspace{1em}Sweden - Europe/Stockholm (UTC +01:00) & 4 (0.6\%)\\
+\hspace{1em}United States - America/Boise (UTC -06:00) & 4 (0.6\%)\\
+\hspace{1em}Czech Republic - Europe/Prague (UTC +01:00) & 3 (0.4\%)\\
+\addlinespace
+\hspace{1em}Denmark - Europe/Copenhagen (UTC +01:00) & 3 (0.4\%)\\
+\hspace{1em}Germany - Europe/Busingen (UTC +01:00) & 3 (0.4\%)\\
+\hspace{1em}Greece - Europe/Athens (UTC +02:00) & 3 (0.4\%)\\
+\hspace{1em}Iran & 3 (0.4\%)\\
+\hspace{1em}Japan - Asia/Tokyo (UTC +09:00) & 3 (0.4\%)\\
+\addlinespace
+\hspace{1em}Norway - Europe/Oslo (UTC +01:00) & 3 (0.4\%)\\
+\hspace{1em}Romania - Europe/Bucharest (UTC +02:00) & 3 (0.4\%)\\
+\hspace{1em}Serbia - Europe/Belgrade (UTC +01:00) & 3 (0.4\%)\\
+\hspace{1em}Slovenia - Europe/Ljubljana (UTC +01:00) & 3 (0.4\%)\\
+\hspace{1em}Taiwan & 3 (0.4\%)\\
+\addlinespace
+\hspace{1em}United States - America/Anchorage (UTC -08:00) & 3 (0.4\%)\\
+\hspace{1em}United States - America/Indiana/Indianapolis (UTC -04:00) & 3 (0.4\%)\\
+\hspace{1em}United States - America/Kentucky/Louisville (UTC -04:00) & 3 (0.4\%)\\
+\hspace{1em}Argentina - America/Argentina/Cordoba (UTC -03:00) & 2 (0.3\%)\\
+\hspace{1em}Australia - Australia/Adelaide (UTC +10:30) & 2 (0.3\%)\\
+\addlinespace
+\hspace{1em}Australia - Australia/Perth (UTC +08:00) & 2 (0.3\%)\\
+\hspace{1em}Australia - Australia/Sydney (UTC +11:00) & 2 (0.3\%)\\
+\hspace{1em}Brazil - America/Araguaina (UTC -03:00) & 2 (0.3\%)\\
+\hspace{1em}Brazil - America/Bahia (UTC -03:00) & 2 (0.3\%)\\
+\hspace{1em}Canada - America/Moncton (UTC -03:00) & 2 (0.3\%)\\
+\addlinespace
+\hspace{1em}Colombia - America/Bogota (UTC -05:00) & 2 (0.3\%)\\
+\hspace{1em}Costa Rica - America/Costa\_Rica (UTC -06:00) & 2 (0.3\%)\\
+\hspace{1em}Croatia - Europe/Zagreb (UTC +01:00) & 2 (0.3\%)\\
+\hspace{1em}Ecuador - America/Guayaquil (UTC -05:00) & 2 (0.3\%)\\
+\hspace{1em}Estonia - Europe/Tallinn (UTC +02:00) & 2 (0.3\%)\\
+\addlinespace
+\hspace{1em}Hong Kong - Asia/Hong\_Kong (UTC +08:00) & 2 (0.3\%)\\
+\hspace{1em}Hungary - Europe/Budapest (UTC +01:00) & 2 (0.3\%)\\
+\hspace{1em}Jordan - Asia/Amman (UTC +03:00) & 2 (0.3\%)\\
+\hspace{1em}Latvia - Europe/Riga (UTC +02:00) & 2 (0.3\%)\\
+\hspace{1em}Malaysia - Asia/Kuching (UTC +08:00) & 2 (0.3\%)\\
+\addlinespace
+\hspace{1em}Mexico - America/Mexico\_City (UTC -06:00) & 2 (0.3\%)\\
+\hspace{1em}Nepal - Asia/Kathmandu (UTC +05:45) & 2 (0.3\%)\\
+\hspace{1em}Portugal - Europe/Lisbon (UTC) & 2 (0.3\%)\\
+\hspace{1em}Slovakia - Europe/Bratislava (UTC +01:00) & 2 (0.3\%)\\
+\hspace{1em}Spain - Africa/Ceuta (UTC +01:00) & 2 (0.3\%)\\
+\addlinespace
+\hspace{1em}Sudan - Africa/Khartoum (UTC +02:00) & 2 (0.3\%)\\
+\hspace{1em}United States - America/Adak (UTC -09:00) & 2 (0.3\%)\\
+\hspace{1em}United States - Pacific/Honolulu (UTC -10:00) & 2 (0.3\%)\\
+\hspace{1em}Viet Nam - Asia/Ho\_Chi\_Minh (UTC +07:00),British - America/Tortola (UTC -04:00) & 2 (0.3\%)\\
+\hspace{1em}Albania - Europe/Tirane (UTC +01:00) & 1 (0.1\%)\\
+\addlinespace
+\hspace{1em}Argentina - America/Argentina/Jujuy (UTC -03:00) & 1 (0.1\%)\\
+\hspace{1em}Australia - Antarctica/Macquarie (UTC +11:00) & 1 (0.1\%)\\
+\hspace{1em}Australia - Australia/Darwin (UTC +09:30) & 1 (0.1\%)\\
+\hspace{1em}Austria - Europe/Vienna (UTC +01:00) & 1 (0.1\%)\\
+\hspace{1em}Bangladesh - Asia/Dhaka (UTC +06:00) & 1 (0.1\%)\\
+\addlinespace
+\hspace{1em}Brazil - America/Cuiaba (UTC -04:00) & 1 (0.1\%)\\
+\hspace{1em}Brazil - America/Fortaleza (UTC -03:00) & 1 (0.1\%)\\
+\hspace{1em}Bulgaria - Europe/Sofia (UTC +02:00) & 1 (0.1\%)\\
+\hspace{1em}Cameroon - Africa/Douala (UTC +01:00) & 1 (0.1\%)\\
+\hspace{1em}Canada - America/Blanc-Sablon (UTC -04:00) & 1 (0.1\%)\\
+\addlinespace
+\hspace{1em}Canada - America/Halifax (UTC -03:00) & 1 (0.1\%)\\
+\hspace{1em}Canada - America/Resolute (UTC -05:00) & 1 (0.1\%)\\
+\hspace{1em}Cayman Islands - America/Cayman (UTC -05:00) & 1 (0.1\%)\\
+\hspace{1em}Chile - Pacific/Easter (UTC -05:00) & 1 (0.1\%)\\
+\hspace{1em}Cyprus - Asia/Famagusta (UTC +02:00) & 1 (0.1\%)\\
+\addlinespace
+\hspace{1em}Guatemala - America/Guatemala (UTC -06:00) & 1 (0.1\%)\\
+\hspace{1em}Korea,Republic of - Asia/Seoul (UTC +09:00) & 1 (0.1\%)\\
+\hspace{1em}Macedonia & 1 (0.1\%)\\
+\hspace{1em}Martinique - America/Martinique (UTC -04:00) & 1 (0.1\%)\\
+\hspace{1em}Mexico - America/Monterrey (UTC -06:00) & 1 (0.1\%)\\
+\addlinespace
+\hspace{1em}Mongolia - Asia/Ulaanbaatar (UTC +08:00) & 1 (0.1\%)\\
+\hspace{1em}Myanmar - Asia/Yangon (UTC +06:30) & 1 (0.1\%)\\
+\hspace{1em}New Zealand - Pacific/Chatham (UTC +13:45) & 1 (0.1\%)\\
+\hspace{1em}Nigeria - Africa/Lagos (UTC +01:00) & 1 (0.1\%)\\
+\hspace{1em}Pakistan - Asia/Karachi (UTC +05:00) & 1 (0.1\%)\\
+\addlinespace
+\hspace{1em}Panama - America/Panama (UTC -05:00) & 1 (0.1\%)\\
+\hspace{1em}Russian Federation - Asia/Barnaul (UTC +07:00) & 1 (0.1\%)\\
+\hspace{1em}Russian Federation - Asia/Novosibirsk (UTC +07:00) & 1 (0.1\%)\\
+\hspace{1em}Russian Federation - Asia/Tomsk (UTC +07:00) & 1 (0.1\%)\\
+\hspace{1em}Russian Federation - Asia/Vladivostok (UTC +10:00) & 1 (0.1\%)\\
+\addlinespace
+\hspace{1em}Russian Federation - Asia/Yekaterinburg (UTC +05:00) & 1 (0.1\%)\\
+\hspace{1em}Saudi Arabia - Asia/Riyadh (UTC +03:00) & 1 (0.1\%)\\
+\hspace{1em}Singapore - Asia/Singapore (UTC +08:00) & 1 (0.1\%)\\
+\hspace{1em}Spain - Atlantic/Canary (UTC) & 1 (0.1\%)\\
+\hspace{1em}Tanzania & 1 (0.1\%)\\
+\addlinespace
+\hspace{1em}Ukraine - Europe/Kiev (UTC +02:00) & 1 (0.1\%)\\
+\hspace{1em}United States - America/Indiana/Tell\_City (UTC -05:00) & 1 (0.1\%)\\
+\hspace{1em}United States - America/North\_Dakota/Center (UTC -05:00) & 1 (0.1\%)\\
+\hspace{1em}United States - America/North\_Dakota/New\_Salem (UTC -05:00) & 1 (0.1\%)\\
+\hspace{1em}Aland Islands - Europe/Mariehamn (UTC +02:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Afghanistan - Asia/Kabul (UTC +04:30) & 0 (0\%)\\
+\hspace{1em}Algeria - Africa/Algiers (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}American Samoa - Pacific/Pago\_Pago (UTC -11:00) & 0 (0\%)\\
+\hspace{1em}Andorra - Europe/Andorra (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Angola - Africa/Luanda (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Anguilla - America/Anguilla (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Antarctica - Antarctica/Casey (UTC +11:00) & 0 (0\%)\\
+\hspace{1em}Antarctica - Antarctica/Davis (UTC +07:00) & 0 (0\%)\\
+\hspace{1em}Antarctica - Antarctica/DumontDUrville (UTC +10:00) & 0 (0\%)\\
+\hspace{1em}Antarctica - Antarctica/Mawson (UTC +05:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Antarctica - Antarctica/McMurdo (UTC +13:00) & 0 (0\%)\\
+\hspace{1em}Antarctica - Antarctica/Palmer (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Antarctica - Antarctica/Rothera (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Antarctica - Antarctica/Syowa (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Antarctica - Antarctica/Troll (UTC) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Antarctica - Antarctica/Vostok (UTC +06:00) & 0 (0\%)\\
+\hspace{1em}Antigua and Barbuda - America/Antigua (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Argentina - America/Argentina/Catamarca (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Argentina - America/Argentina/La\_Rioja (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Argentina - America/Argentina/Mendoza (UTC -03:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Argentina - America/Argentina/Rio\_Gallegos (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Argentina - America/Argentina/Salta (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Argentina - America/Argentina/San\_Juan (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Argentina - America/Argentina/San\_Luis (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Argentina - America/Argentina/Tucuman (UTC -03:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Argentina - America/Argentina/Ushuaia (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Armenia - Asia/Yerevan (UTC +04:00) & 0 (0\%)\\
+\hspace{1em}Aruba - America/Aruba (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Australia - Australia/Broken\_Hill (UTC +10:30) & 0 (0\%)\\
+\hspace{1em}Australia - Australia/Currie (UTC +11:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Australia - Australia/Eucla (UTC +08:45) & 0 (0\%)\\
+\hspace{1em}Australia - Australia/Hobart (UTC +11:00) & 0 (0\%)\\
+\hspace{1em}Australia - Australia/Lindeman (UTC +10:00) & 0 (0\%)\\
+\hspace{1em}Australia - Australia/Lord\_Howe (UTC +11:00) & 0 (0\%)\\
+\hspace{1em}Azerbaijan - Asia/Baku (UTC +04:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Bahamas - America/Nassau (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Bahrain - Asia/Bahrain (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Barbados - America/Barbados (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Belarus - Europe/Minsk (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Belize - America/Belize (UTC -06:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Benin - Africa/Porto-Novo (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Bermuda - Atlantic/Bermuda (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Bhutan - Asia/Thimphu (UTC +06:00),Plurinational State of - America/La\_Paz (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Bolivia,Sint Eustatius and Saba - America/Kralendijk (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Bonaire & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Bosnia and Herzegovina - Europe/Sarajevo (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Botswana - Africa/Gaborone (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Brazil - America/Belem (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Brazil - America/Boa\_Vista (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Brazil - America/Campo\_Grande (UTC -04:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Brazil - America/Eirunepe (UTC -05:00) & 0 (0\%)\\
+\hspace{1em}Brazil - America/Maceio (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Brazil - America/Manaus (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Brazil - America/Noronha (UTC -02:00) & 0 (0\%)\\
+\hspace{1em}Brazil - America/Porto\_Velho (UTC -04:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Brazil - America/Recife (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Brazil - America/Rio\_Branco (UTC -05:00) & 0 (0\%)\\
+\hspace{1em}Brazil - America/Santarem (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}British Indian Ocean Territory - Indian/Chagos (UTC +06:00) & 0 (0\%)\\
+\hspace{1em}Brunei Darussalam - Asia/Brunei (UTC +08:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Burkina Faso - Africa/Ouagadougou (UTC) & 0 (0\%)\\
+\hspace{1em}Burundi - Africa/Bujumbura (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Cambodia - Asia/Phnom\_Penh (UTC +07:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Atikokan (UTC -05:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Cambridge\_Bay (UTC -06:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Canada - America/Creston (UTC -07:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Dawson (UTC -07:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Dawson\_Creek (UTC -07:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Fort\_Nelson (UTC -07:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Glace\_Bay (UTC -03:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Canada - America/Goose\_Bay (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Inuvik (UTC -06:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Iqaluit (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Nipigon (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Pangnirtung (UTC -04:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Canada - America/Rainy\_River (UTC -05:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Rankin\_Inlet (UTC -05:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Regina (UTC -06:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/St\_Johns (UTC -02:30) & 0 (0\%)\\
+\hspace{1em}Canada - America/Swift\_Current (UTC -06:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Canada - America/Thunder\_Bay (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Whitehorse (UTC -07:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Winnipeg (UTC -05:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Yellowknife (UTC -06:00) & 0 (0\%)\\
+\hspace{1em}Cape Verde - Atlantic/Cape\_Verde (UTC -01:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Central African Republic - Africa/Bangui (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Chad - Africa/Ndjamena (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Chile - America/Punta\_Arenas (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}China - Asia/Urumqi (UTC +06:00) & 0 (0\%)\\
+\hspace{1em}Christmas Island - Indian/Christmas (UTC +07:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Cocos (Keeling) Islands - Indian/Cocos (UTC +06:30) & 0 (0\%)\\
+\hspace{1em}Comoros - Indian/Comoro (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Congo - Africa/Brazzaville (UTC +01:00),the Democratic Republic of the - Africa/Kinshasa (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Congo,the Democratic Republic of the - Africa/Lubumbashi (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Congo & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Cook Islands - Pacific/Rarotonga (UTC -10:00) & 0 (0\%)\\
+\hspace{1em}Cuba - America/Havana (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Curaçao - America/Curacao (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Cyprus - Asia/Nicosia (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Côte dIvoire - Africa/Abidjan (UTC) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Djibouti - Africa/Djibouti (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Dominica - America/Dominica (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Dominican Republic - America/Santo\_Domingo (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Ecuador - Pacific/Galapagos (UTC -06:00) & 0 (0\%)\\
+\hspace{1em}Egypt - Africa/Cairo (UTC +02:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}El Salvador - America/El\_Salvador (UTC -06:00) & 0 (0\%)\\
+\hspace{1em}Equatorial Guinea - Africa/Malabo (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Eritrea - Africa/Asmara (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Ethiopia - Africa/Addis\_Ababa (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Falkland Islands (Malvinas) - Atlantic/Stanley (UTC -03:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Faroe Islands - Atlantic/Faroe (UTC) & 0 (0\%)\\
+\hspace{1em}Fiji - Pacific/Fiji (UTC +12:00) & 0 (0\%)\\
+\hspace{1em}French Guiana - America/Cayenne (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}French Polynesia - Pacific/Gambier (UTC -09:00) & 0 (0\%)\\
+\hspace{1em}French Polynesia - Pacific/Marquesas (UTC -09:30) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}French Polynesia - Pacific/Tahiti (UTC -10:00) & 0 (0\%)\\
+\hspace{1em}French Southern Territories - Indian/Kerguelen (UTC +05:00) & 0 (0\%)\\
+\hspace{1em}Gabon - Africa/Libreville (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Gambia - Africa/Banjul (UTC) & 0 (0\%)\\
+\hspace{1em}Georgia - Asia/Tbilisi (UTC +04:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Ghana - Africa/Accra (UTC) & 0 (0\%)\\
+\hspace{1em}Gibraltar - Europe/Gibraltar (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Greenland - America/Danmarkshavn (UTC) & 0 (0\%)\\
+\hspace{1em}Greenland - America/Nuuk (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Greenland - America/Scoresbysund (UTC -01:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Greenland - America/Thule (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Grenada - America/Grenada (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Guadeloupe - America/Guadeloupe (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Guam - Pacific/Guam (UTC +10:00) & 0 (0\%)\\
+\hspace{1em}Guernsey - Europe/Guernsey (UTC) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Guinea - Africa/Conakry (UTC) & 0 (0\%)\\
+\hspace{1em}Guinea-Bissau - Africa/Bissau (UTC) & 0 (0\%)\\
+\hspace{1em}Guyana - America/Guyana (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Haiti - America/Port-au-Prince (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Holy See (Vatican City State) - Europe/Vatican (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Honduras - America/Tegucigalpa (UTC -06:00) & 0 (0\%)\\
+\hspace{1em}Iceland - Atlantic/Reykjavik (UTC) & 0 (0\%)\\
+\hspace{1em}Indonesia - Asia/Jayapura (UTC +09:00) & 0 (0\%)\\
+\hspace{1em}Indonesia - Asia/Makassar (UTC +08:00) & 0 (0\%)\\
+\hspace{1em}Indonesia - Asia/Pontianak (UTC +07:00),Islamic Republic of - Asia/Tehran (UTC +03:30) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Iraq - Asia/Baghdad (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Isle of Man - Europe/Isle\_of\_Man (UTC) & 0 (0\%)\\
+\hspace{1em}Jamaica - America/Jamaica (UTC -05:00) & 0 (0\%)\\
+\hspace{1em}Jersey - Europe/Jersey (UTC) & 0 (0\%)\\
+\hspace{1em}Kazakhstan - Asia/Almaty (UTC +06:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Kazakhstan - Asia/Aqtau (UTC +05:00) & 0 (0\%)\\
+\hspace{1em}Kazakhstan - Asia/Aqtobe (UTC +05:00) & 0 (0\%)\\
+\hspace{1em}Kazakhstan - Asia/Atyrau (UTC +05:00) & 0 (0\%)\\
+\hspace{1em}Kazakhstan - Asia/Oral (UTC +05:00) & 0 (0\%)\\
+\hspace{1em}Kazakhstan - Asia/Qostanay (UTC +06:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Kazakhstan - Asia/Qyzylorda (UTC +05:00) & 0 (0\%)\\
+\hspace{1em}Kenya - Africa/Nairobi (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Kiribati - Pacific/Enderbury (UTC +13:00) & 0 (0\%)\\
+\hspace{1em}Kiribati - Pacific/Kiritimati (UTC +14:00) & 0 (0\%)\\
+\hspace{1em}Kiribati - Pacific/Tarawa (UTC +12:00),Democratic Peoples Republic of - Asia/Pyongyang (UTC +09:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Korea & 0 (0\%)\\
+\hspace{1em}Kuwait - Asia/Kuwait (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Kyrgyzstan - Asia/Bishkek (UTC +06:00) & 0 (0\%)\\
+\hspace{1em}Lao Peoples Democratic Republic - Asia/Vientiane (UTC +07:00) & 0 (0\%)\\
+\hspace{1em}Lebanon - Asia/Beirut (UTC +02:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Lesotho - Africa/Maseru (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Liberia - Africa/Monrovia (UTC) & 0 (0\%)\\
+\hspace{1em}Libya - Africa/Tripoli (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Liechtenstein - Europe/Vaduz (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Luxembourg - Europe/Luxembourg (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Macao - Asia/Macau (UTC +08:00),the Former Yugoslav Republic of - Europe/Skopje (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Madagascar - Indian/Antananarivo (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Malawi - Africa/Blantyre (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Maldives - Indian/Maldives (UTC +05:00) & 0 (0\%)\\
+\hspace{1em}Mali - Africa/Bamako (UTC) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Malta - Europe/Malta (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Marshall Islands - Pacific/Kwajalein (UTC +12:00) & 0 (0\%)\\
+\hspace{1em}Marshall Islands - Pacific/Majuro (UTC +12:00) & 0 (0\%)\\
+\hspace{1em}Mauritania - Africa/Nouakchott (UTC) & 0 (0\%)\\
+\hspace{1em}Mauritius - Indian/Mauritius (UTC +04:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Mayotte - Indian/Mayotte (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Mexico - America/Bahia\_Banderas (UTC -06:00) & 0 (0\%)\\
+\hspace{1em}Mexico - America/Cancun (UTC -05:00) & 0 (0\%)\\
+\hspace{1em}Mexico - America/Chihuahua (UTC -07:00) & 0 (0\%)\\
+\hspace{1em}Mexico - America/Hermosillo (UTC -07:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Mexico - America/Matamoros (UTC -05:00) & 0 (0\%)\\
+\hspace{1em}Mexico - America/Mazatlan (UTC -07:00) & 0 (0\%)\\
+\hspace{1em}Mexico - America/Merida (UTC -06:00) & 0 (0\%)\\
+\hspace{1em}Mexico - America/Ojinaga (UTC -06:00) & 0 (0\%)\\
+\hspace{1em}Mexico - America/Tijuana (UTC -07:00),Federated States of - Pacific/Chuuk (UTC +10:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Micronesia,Federated States of - Pacific/Kosrae (UTC +11:00) & 0 (0\%)\\
+\hspace{1em}Micronesia,Federated States of - Pacific/Pohnpei (UTC +11:00) & 0 (0\%)\\
+\hspace{1em}Micronesia,Republic of - Europe/Chisinau (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Moldova & 0 (0\%)\\
+\hspace{1em}Monaco - Europe/Monaco (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Mongolia - Asia/Choibalsan (UTC +08:00) & 0 (0\%)\\
+\hspace{1em}Mongolia - Asia/Hovd (UTC +07:00) & 0 (0\%)\\
+\hspace{1em}Montenegro - Europe/Podgorica (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Montserrat - America/Montserrat (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Morocco - Africa/Casablanca (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Mozambique - Africa/Maputo (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Namibia - Africa/Windhoek (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Nauru - Pacific/Nauru (UTC +12:00) & 0 (0\%)\\
+\hspace{1em}New Caledonia - Pacific/Noumea (UTC +11:00) & 0 (0\%)\\
+\hspace{1em}Nicaragua - America/Managua (UTC -06:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Niger - Africa/Niamey (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Niue - Pacific/Niue (UTC -11:00) & 0 (0\%)\\
+\hspace{1em}Norfolk Island - Pacific/Norfolk (UTC +12:00) & 0 (0\%)\\
+\hspace{1em}Northern Mariana Islands - Pacific/Saipan (UTC +10:00) & 0 (0\%)\\
+\hspace{1em}Oman - Asia/Muscat (UTC +04:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Palau - Pacific/Palau (UTC +09:00),State of - Asia/Gaza (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Palestine,State of - Asia/Hebron (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Palestine & 0 (0\%)\\
+\hspace{1em}Papua New Guinea - Pacific/Bougainville (UTC +11:00) & 0 (0\%)\\
+\hspace{1em}Papua New Guinea - Pacific/Port\_Moresby (UTC +10:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Paraguay - America/Asuncion (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Peru - America/Lima (UTC -05:00) & 0 (0\%)\\
+\hspace{1em}Pitcairn - Pacific/Pitcairn (UTC -08:00) & 0 (0\%)\\
+\hspace{1em}Portugal - Atlantic/Azores (UTC -01:00) & 0 (0\%)\\
+\hspace{1em}Portugal - Atlantic/Madeira (UTC) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Puerto Rico - America/Puerto\_Rico (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Qatar - Asia/Qatar (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Asia/Anadyr (UTC +12:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Asia/Chita (UTC +09:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Asia/Irkutsk (UTC +08:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Russian Federation - Asia/Kamchatka (UTC +12:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Asia/Khandyga (UTC +09:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Asia/Krasnoyarsk (UTC +07:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Asia/Magadan (UTC +11:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Asia/Novokuznetsk (UTC +07:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Russian Federation - Asia/Omsk (UTC +06:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Asia/Sakhalin (UTC +11:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Asia/Srednekolymsk (UTC +11:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Asia/Ust-Nera (UTC +10:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Asia/Yakutsk (UTC +09:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Russian Federation - Europe/Astrakhan (UTC +04:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Europe/Kaliningrad (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Europe/Kirov (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Europe/Samara (UTC +04:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Europe/Saratov (UTC +04:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Russian Federation - Europe/Ulyanovsk (UTC +04:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Europe/Volgograd (UTC +04:00) & 0 (0\%)\\
+\hspace{1em}Rwanda - Africa/Kigali (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Réunion - Indian/Reunion (UTC +04:00) & 0 (0\%)\\
+\hspace{1em}Saint Barthélemy - America/St\_Barthelemy (UTC -04:00),Ascension and Tristan da Cunha - Atlantic/St\_Helena (UTC) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Saint Helena & 0 (0\%)\\
+\hspace{1em}Saint Kitts and Nevis - America/St\_Kitts (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Saint Lucia - America/St\_Lucia (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Saint Martin (French part) - America/Marigot (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Saint Pierre and Miquelon - America/Miquelon (UTC -02:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Saint Vincent and the Grenadines - America/St\_Vincent (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Samoa - Pacific/Apia (UTC +14:00) & 0 (0\%)\\
+\hspace{1em}San Marino - Europe/San\_Marino (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Sao Tome and Principe - Africa/Sao\_Tome (UTC) & 0 (0\%)\\
+\hspace{1em}Senegal - Africa/Dakar (UTC) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Seychelles - Indian/Mahe (UTC +04:00) & 0 (0\%)\\
+\hspace{1em}Sierra Leone - Africa/Freetown (UTC) & 0 (0\%)\\
+\hspace{1em}Sint Maarten (Dutch part) - America/Lower\_Princes (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Solomon Islands - Pacific/Guadalcanal (UTC +11:00) & 0 (0\%)\\
+\hspace{1em}Somalia - Africa/Mogadishu (UTC +03:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}South Georgia and the South Sandwich Islands - Atlantic/South\_Georgia (UTC -02:00) & 0 (0\%)\\
+\hspace{1em}South Sudan - Africa/Juba (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Sri Lanka - Asia/Colombo (UTC +05:30) & 0 (0\%)\\
+\hspace{1em}Suriname - America/Paramaribo (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Svalbard and Jan Mayen - Arctic/Longyearbyen (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Swaziland - Africa/Mbabane (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Syrian Arab Republic - Asia/Damascus (UTC +03:00),Province of China - Asia/Taipei (UTC +08:00) & 0 (0\%)\\
+\hspace{1em}Tajikistan - Asia/Dushanbe (UTC +05:00),United Republic of - Africa/Dar\_es\_Salaam (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Thailand - Asia/Bangkok (UTC +07:00) & 0 (0\%)\\
+\hspace{1em}Timor-Leste - Asia/Dili (UTC +09:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Togo - Africa/Lome (UTC) & 0 (0\%)\\
+\hspace{1em}Tokelau - Pacific/Fakaofo (UTC +13:00) & 0 (0\%)\\
+\hspace{1em}Tonga - Pacific/Tongatapu (UTC +13:00) & 0 (0\%)\\
+\hspace{1em}Trinidad and Tobago - America/Port\_of\_Spain (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Tunisia - Africa/Tunis (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Turkmenistan - Asia/Ashgabat (UTC +05:00) & 0 (0\%)\\
+\hspace{1em}Turks and Caicos Islands - America/Grand\_Turk (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Tuvalu - Pacific/Funafuti (UTC +12:00) & 0 (0\%)\\
+\hspace{1em}Uganda - Africa/Kampala (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Ukraine - Europe/Simferopol (UTC +03:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Ukraine - Europe/Uzhgorod (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Ukraine - Europe/Zaporozhye (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}United Arab Emirates - Asia/Dubai (UTC +04:00) & 0 (0\%)\\
+\hspace{1em}United States - America/Indiana/Knox (UTC -05:00) & 0 (0\%)\\
+\hspace{1em}United States - America/Indiana/Marengo (UTC -04:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}United States - America/Indiana/Petersburg (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}United States - America/Indiana/Vevay (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}United States - America/Indiana/Vincennes (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}United States - America/Indiana/Winamac (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}United States - America/Juneau (UTC -08:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}United States - America/Kentucky/Monticello (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}United States - America/Menominee (UTC -05:00) & 0 (0\%)\\
+\hspace{1em}United States - America/Metlakatla (UTC -08:00) & 0 (0\%)\\
+\hspace{1em}United States - America/Nome (UTC -08:00) & 0 (0\%)\\
+\hspace{1em}United States - America/North\_Dakota/Beulah (UTC -05:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}United States - America/Sitka (UTC -08:00) & 0 (0\%)\\
+\hspace{1em}United States - America/Yakutat (UTC -08:00) & 0 (0\%)\\
+\hspace{1em}United States Minor Outlying Islands - Pacific/Midway (UTC -11:00) & 0 (0\%)\\
+\hspace{1em}United States Minor Outlying Islands - Pacific/Wake (UTC +12:00) & 0 (0\%)\\
+\hspace{1em}Uruguay - America/Montevideo (UTC -03:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Uzbekistan - Asia/Samarkand (UTC +05:00) & 0 (0\%)\\
+\hspace{1em}Uzbekistan - Asia/Tashkent (UTC +05:00) & 0 (0\%)\\
+\hspace{1em}Vanuatu - Pacific/Efate (UTC +11:00),Bolivarian Republic of - America/Caracas (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Venezuela & 0 (0\%)\\
+\hspace{1em}Virgin Islands,U.S. - America/St\_Thomas (UTC -04:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Virgin Islands & 0 (0\%)\\
+\hspace{1em}Wallis and Futuna - Pacific/Wallis (UTC +12:00) & 0 (0\%)\\
+\hspace{1em}Western Sahara - Africa/El\_Aaiun (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Yemen - Asia/Aden (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Zambia - Africa/Lusaka (UTC +02:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Zimbabwe - Africa/Harare (UTC +02:00) & 0 (0\%)\\
+\bottomrule
+\multicolumn{2}{l}{\rule{0pt}{1em}\textsuperscript{1} n (\%)}\\
+\end{tabular}}
+\end{table}
 \end{appendix}

### 2021-11-17 manuscript.Rmd
* table 1 updated

--- 2021-11-15 manuscript.Rmd
@@
   [@verriotto2017new][@eklund1996development][@bajaj2011validation][@dianat2013objective]
-  [@horne1976self][@roenneberg2003life][@Olivier.2016][@buysse1989pittsburgh][@Xie.2021]
-  [@Wu.2017]
+  [@horne1976self][@roenneberg2003life][@Olivier.2016][@buysse1989pittsburgh][@Xie.2021][@bossini2006sensibilita]
 ---
@@
   kable_styling(latex_options = c("repeat_header")) %>% 
-  column_spec(1:4, width = "4cm")
+  column_spec(1:6, width = "2cm")
 ```
@@
 Figure \@ref(fig:FlowchartFig) summarizes the steps of our psychometric analysis.
-For our analysis we used R (version 4.1.0), with several R packages.
+In our analysis we used R (version 4.1.0), with several R packages.
 Initially, our tool had six point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always).
 Our purpose was to capture light exposure related behavior and these two response options: "Does not apply/I don't know" and "Never" were providing similar information.
-As such we decided to collapse them into one making it a 5 point Likert type response format.
+As such we decided to collapse them into one, making it a 5 point Likert type response format.
 Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
@@
 We used a combination of factor identification method including scree plot [@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method [@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
-Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018].
-We confirmed the latent structure obtained in the EFA by conducting a "Confirmatory Factor Analysis" (CFA) using "robust weighted least square estimator" (WLSMV).
-We estiablished the measurement invariance of our tool across native and non-native English speakers using structural equation model framework.
+Additionally, to determine the simple structure, we followed the guidelines recommended by psychometricians: (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018].
+We confirmed the latent structure obtained in the EFA by conducting a categorical "Confirmatory Factor Analysis" (CFA) using "robust weighted least square estimator" (WLSMV).
+We estiablished the measurement invariance of our tool across the native and non-native English speakers using structural equation model framework.
 To assess the possible semantic overlap of our tool with the existing tools, we sought to "Semantic Scale Network" [@rosenbusch2020semantic].
@@
 Figure \@ref(fig:EFAplot) depicts the obtained five-five factor structure.
-However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:EFAResiduals)) showed `r apa(sumR,0, T)`% correlations greater than the absolute value of .05, indicating a possible under-factoring.
+However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:EFAResiduals)) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring.
 [@desjardinsHandbookEducationalMeasurement2018].

### 2021-11-17 manuscript.tex
* table 1 updated

@@
 
-\begin{longtable}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{4cm}}
+\begin{longtable}[t]{>{\raggedright\arraybackslash}p{2cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedright\arraybackslash}p{2cm}}
 \caption{\label{tab:unnamed-chunk-2}Releated Scales}\\
 \toprule
-Name & Author & Description & Relevant Items\\
+Name & Author & Description & Relevant Items to capture light exposure related behavior & Scale type & Validity evidences\\
 \midrule
@@
 \toprule
-Name & Author & Description & Relevant Items\\
+Name & Author & Description & Relevant Items to capture light exposure related behavior & Scale type & Validity evidences\\
 \midrule
@@
 \endlastfoot
-Visual Light Sensitivity Questionnaire-8 & Verriotto et al., 2017 & Eight-question survey to assess the presence and severity of photosensitivity symptoms & NA\\
-Office Light Survey & Eklundet al., 1996 & A survey to assess electrical lighting environment in office & NA\\
-Harvard Light Exposure Assessment Questionnaire & Bajaj et al., 2011 & Self-administered semi-quantitative light questionnaire & NA\\
-Hospital Lighting Survey & Dianat et el., 2013 & 23 items questionnaire to assess light environment in a hospital & NA\\
-Morningness-Eveningness Questionnaire & Horne et al., 1976 & 19 items questionnaire to understand your body clock & NA\\
-\addlinespace
-Munich Chronotype Questionnaire (MCTQ) & Roenneberg et al., 2003 & 17 items questionnaire to understand individuals phase of entrainment & NA\\
-Assessment of Sleep Environment & Olivier et.al., 2016 & 13 items questionnaire measuring your sleep environment quality & NA\\
-The Pittsburgh Sleep Quality Index (PSQI) & Buysse et al., 1989 & 9 items inventory to measure sleep quality and sleeping pattern & NA\\
-Self-Rating of Biological Rhythm Disorder for Adolescents (SBRDA) & Xie et al., 2021 & 29 Items questionnaire assessing four dimensions of biological rhythm disorder in adolescents & Item 3,22-25 and 29\\
-Photosensitivity Assessment Questionnaire (PAQ) & Wu et al., 2017 & 16 dichotomous (yes/no) items questionnaire to assess "photophobia" and "photophilia" & All itms\\*
+Visual Light Sensitivity Questionnaire-8 & Verriotto et al., 2017 & Eight-question survey to assess the presence and severity of photosensitivity symptoms & None & 5-point Likert scale & Not available\\
+Office Light Survey & Eklundet al., 1996 & 30 items survey to assess electrical lighting environment in office & Item 29 & Mixed response format & Not available\\
+Harvard Light Exposure Assessment Questionnaire & Bajaj et al., 2011 & 1 item semi-quantitative light questionnaire & none & Semi-quantitative & NA\\
+Hospital Lighting Survey & Dianat et el., 2013 & 23 items questionnaire to assess light environment in a hospital & Item 16,17 & 5-point Likert scale & Face and Content validity\\
+Morningness-Eveningness Questionnaire & Horne et al., 1976 & 19 items questionnaire to understand your body clock & item 1,2,8,13,14 & Mixed response format & Correlation of total score and the oral temperature\\
+\addlinespace
+Munich Chronotype Questionnaire (MCTQ) & Roenneberg et al., 2003 & 17 items questionnaire to understand individuals phase of entrainment & Time spect outdoors & Mixed response format & Correlation between  total score and sleep-logs, actimetry, physiological parameters\\
+ Sleep Practices and Attitudes Questionnaire (SPAQ) & Olivier et.al., 2016 & 16 Factor questionnaire measuring practice, behavior and attitude related sleep & Subscale 8\&9 & 5-point Likert scale & Face and Construct validity\\
+The Pittsburgh Sleep Quality Index (PSQI) & Buysse et al., 1989 & 9 items inventory to measure sleep quality and sleeping pattern & item 1-4 & Mixed response format & Correlation of total score with clinical measurements\\
+Self-Rating of Biological Rhythm Disorder for Disorder for Adolescents (SBRDA) & Xie et al., 2021 & 29 Items questionnaire assessing four dimensions of biological rhythm disorder in adolescents & Item 3,6,22-25 and 29 & 5-point Likert scale & Construct validity\\
+Photosensitivity Assessment Questionnaire (PAQ) & Bossini et al.,2006 & 16 dichotomous (yes/no) items questionnaire to assess "photophobia" and "photophilia" & All itms & Binary response option & NA\\*
 \end{longtable}
@@
 Figure \ref{fig:FlowchartFig} summarizes the steps of our psychometric analysis.
-For our analysis we used R (version 4.1.0), with several R packages.
+In our analysis we used R (version 4.1.0), with several R packages.
 Initially, our tool had six point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always).
 Our purpose was to capture light exposure related behavior and these two response options: ``Does not apply/I don't know'' and ``Never'' were providing similar information.
-As such we decided to collapse them into one making it a 5 point Likert type response format.
+As such we decided to collapse them into one, making it a 5 point Likert type response format.
 Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
@@
 We used a combination of factor identification method including scree plot (Cattell, 1966), Horn's parallel analysis (Horn, 1965), minimum average partials method (Velicer, 1976), and hull method (Lorenzo-Seva, Timmerman, \& Kiers, 2011) to identify factor numbers.
-Additionally, to determine the simple structure, we followed the following guidelines recommended by psychometricians (i) no factors with fewer than three items (ii) no factors with a factor loading \textless0.3 (iii) no items with cross-loading greater than .3 across factors (Bandalos \& Finney, 2018).
-We confirmed the latent structure obtained in the EFA by conducting a ``Confirmatory Factor Analysis'' (CFA) using ``robust weighted least square estimator'' (WLSMV).
-We estiablished the measurement invariance of our tool across native and non-native English speakers using structural equation model framework.
+Additionally, to determine the simple structure, we followed the guidelines recommended by psychometricians: (i) no factors with fewer than three items (ii) no factors with a factor loading \textless0.3 (iii) no items with cross-loading greater than .3 across factors (Bandalos \& Finney, 2018).
+We confirmed the latent structure obtained in the EFA by conducting a categorical ``Confirmatory Factor Analysis'' (CFA) using ``robust weighted least square estimator'' (WLSMV).
+We estiablished the measurement invariance of our tool across the native and non-native English speakers using structural equation model framework.
 To assess the possible semantic overlap of our tool with the existing tools, we sought to ``Semantic Scale Network'' (Rosenbusch, Wanders, \& Pit, 2020).
@@
 Figure \ref{fig:EFAplot} depicts the obtained five-five factor structure.
-However, the histogram of the absolute values of non-redundant residual-correlations (Figure \ref{fig:EFAResiduals}) showed 26\% correlations greater than the absolute value of .05, indicating a possible under-factoring.
+However, the histogram of the absolute values of non-redundant residual-correlations (Figure \ref{fig:EFAResiduals}) showed 26\% correlations were greater than the absolute value of .05, indicating a possible under-factoring.
 (Desjardins \& Bulut, 2018).
@@
 \url{https://doi.org/10.1080/15402002.2018.1461102}
+
+\leavevmode\vadjust pre{\hypertarget{ref-bossini2006sensibilita}{}}%
+Bossini, L., Valdagno, M., Padula, L., De Capua, A., Pacchierotti, C., \& Castrogiovanni, P.
+(2006).
+Sensibilit{à} alla luce e psicopatologia: Validazione del questionario per la valutazione della fotosensibilit{à} (QVF).
+\emph{Med Psicosomatica}, \emph{51}, 167--176.
 
@@
 \end{longtable}
+
+\hypertarget{geographic-locations-of-survey-participants}{%
+\section{Geographic Locations of Survey
+Participants}\label{geographic-locations-of-survey-participants}}
+
+\begin{table}
+
+\caption{\label{tab:TzTable}Geographical Location}
+\centering
+\resizebox{\linewidth}{!}{
+\begin{tabular}[t]{ll}
+\toprule
+ & N = 690\\
+\midrule
+Time zone - Country & \\
+\hspace{1em}United States - America/New\_York (UTC -04:00) & 63 (9.1\%)\\
+\hspace{1em}United Kingdom - Europe/London (UTC) & 57 (8.3\%)\\
+\hspace{1em}Germany - Europe/Berlin (UTC +01:00) & 53 (7.7\%)\\
+\hspace{1em}India - Asia/Kolkata (UTC +05:30) & 38 (5.5\%)\\
+\addlinespace
+\hspace{1em}United States - America/Los\_Angeles (UTC -07:00) & 37 (5.4\%)\\
+\hspace{1em}United States - America/Chicago (UTC -05:00) & 30 (4.3\%)\\
+\hspace{1em}France - Europe/Paris (UTC +01:00) & 22 (3.2\%)\\
+\hspace{1em}Switzerland - Europe/Zurich (UTC +01:00) & 21 (3.0\%)\\
+\hspace{1em}Brazil - America/Sao\_Paulo (UTC -03:00) & 19 (2.8\%)\\
+\addlinespace
+\hspace{1em}Netherlands - Europe/Amsterdam (UTC +01:00) & 19 (2.8\%)\\
+\hspace{1em}Canada - America/Toronto (UTC -04:00) & 16 (2.3\%)\\
+\hspace{1em}Poland - Europe/Warsaw (UTC +01:00) & 15 (2.2\%)\\
+\hspace{1em}Canada - America/Edmonton (UTC -06:00) & 14 (2.0\%)\\
+\hspace{1em}Finland - Europe/Helsinki (UTC +02:00) & 9 (1.3\%)\\
+\addlinespace
+\hspace{1em}Indonesia - Asia/Jakarta (UTC +07:00) & 9 (1.3\%)\\
+\hspace{1em}Italy - Europe/Rome (UTC +01:00) & 9 (1.3\%)\\
+\hspace{1em}Chile - America/Santiago (UTC -03:00) & 8 (1.2\%)\\
+\hspace{1em}Russian Federation - Europe/Moscow (UTC +03:00) & 8 (1.2\%)\\
+\hspace{1em}China - Asia/Shanghai (UTC +08:00) & 7 (1.0\%)\\
+\addlinespace
+\hspace{1em}Malaysia - Asia/Kuala\_Lumpur (UTC +08:00) & 7 (1.0\%)\\
+\hspace{1em}Spain - Europe/Madrid (UTC +01:00) & 7 (1.0\%)\\
+\hspace{1em}United States - America/Phoenix (UTC -07:00) & 7 (1.0\%)\\
+\hspace{1em}Canada - America/Vancouver (UTC -07:00) & 6 (0.9\%)\\
+\hspace{1em}New Zealand - Pacific/Auckland (UTC +13:00) & 6 (0.9\%)\\
+\addlinespace
+\hspace{1em}Philippines - Asia/Manila (UTC +08:00) & 6 (0.9\%)\\
+\hspace{1em}Turkey - Europe/Istanbul (UTC +03:00) & 6 (0.9\%)\\
+\hspace{1em}United States - America/Denver (UTC -06:00) & 6 (0.9\%)\\
+\hspace{1em}United States - America/Detroit (UTC -04:00) & 6 (0.9\%)\\
+\hspace{1em}Argentina - America/Argentina/Buenos\_Aires (UTC -03:00) & 5 (0.7\%)\\
+\addlinespace
+\hspace{1em}Australia - Australia/Melbourne (UTC +11:00) & 5 (0.7\%)\\
+\hspace{1em}Ireland - Europe/Dublin (UTC) & 5 (0.7\%)\\
+\hspace{1em}Lithuania - Europe/Vilnius (UTC +02:00) & 5 (0.7\%)\\
+\hspace{1em}South Africa - Africa/Johannesburg (UTC +02:00) & 5 (0.7\%)\\
+\hspace{1em}Australia - Australia/Brisbane (UTC +10:00) & 4 (0.6\%)\\
+\addlinespace
+\hspace{1em}Belgium - Europe/Brussels (UTC +01:00) & 4 (0.6\%)\\
+\hspace{1em}Israel - Asia/Jerusalem (UTC +02:00) & 4 (0.6\%)\\
+\hspace{1em}Sweden - Europe/Stockholm (UTC +01:00) & 4 (0.6\%)\\
+\hspace{1em}United States - America/Boise (UTC -06:00) & 4 (0.6\%)\\
+\hspace{1em}Czech Republic - Europe/Prague (UTC +01:00) & 3 (0.4\%)\\
+\addlinespace
+\hspace{1em}Denmark - Europe/Copenhagen (UTC +01:00) & 3 (0.4\%)\\
+\hspace{1em}Germany - Europe/Busingen (UTC +01:00) & 3 (0.4\%)\\
+\hspace{1em}Greece - Europe/Athens (UTC +02:00) & 3 (0.4\%)\\
+\hspace{1em}Iran & 3 (0.4\%)\\
+\hspace{1em}Japan - Asia/Tokyo (UTC +09:00) & 3 (0.4\%)\\
+\addlinespace
+\hspace{1em}Norway - Europe/Oslo (UTC +01:00) & 3 (0.4\%)\\
+\hspace{1em}Romania - Europe/Bucharest (UTC +02:00) & 3 (0.4\%)\\
+\hspace{1em}Serbia - Europe/Belgrade (UTC +01:00) & 3 (0.4\%)\\
+\hspace{1em}Slovenia - Europe/Ljubljana (UTC +01:00) & 3 (0.4\%)\\
+\hspace{1em}Taiwan & 3 (0.4\%)\\
+\addlinespace
+\hspace{1em}United States - America/Anchorage (UTC -08:00) & 3 (0.4\%)\\
+\hspace{1em}United States - America/Indiana/Indianapolis (UTC -04:00) & 3 (0.4\%)\\
+\hspace{1em}United States - America/Kentucky/Louisville (UTC -04:00) & 3 (0.4\%)\\
+\hspace{1em}Argentina - America/Argentina/Cordoba (UTC -03:00) & 2 (0.3\%)\\
+\hspace{1em}Australia - Australia/Adelaide (UTC +10:30) & 2 (0.3\%)\\
+\addlinespace
+\hspace{1em}Australia - Australia/Perth (UTC +08:00) & 2 (0.3\%)\\
+\hspace{1em}Australia - Australia/Sydney (UTC +11:00) & 2 (0.3\%)\\
+\hspace{1em}Brazil - America/Araguaina (UTC -03:00) & 2 (0.3\%)\\
+\hspace{1em}Brazil - America/Bahia (UTC -03:00) & 2 (0.3\%)\\
+\hspace{1em}Canada - America/Moncton (UTC -03:00) & 2 (0.3\%)\\
+\addlinespace
+\hspace{1em}Colombia - America/Bogota (UTC -05:00) & 2 (0.3\%)\\
+\hspace{1em}Costa Rica - America/Costa\_Rica (UTC -06:00) & 2 (0.3\%)\\
+\hspace{1em}Croatia - Europe/Zagreb (UTC +01:00) & 2 (0.3\%)\\
+\hspace{1em}Ecuador - America/Guayaquil (UTC -05:00) & 2 (0.3\%)\\
+\hspace{1em}Estonia - Europe/Tallinn (UTC +02:00) & 2 (0.3\%)\\
+\addlinespace
+\hspace{1em}Hong Kong - Asia/Hong\_Kong (UTC +08:00) & 2 (0.3\%)\\
+\hspace{1em}Hungary - Europe/Budapest (UTC +01:00) & 2 (0.3\%)\\
+\hspace{1em}Jordan - Asia/Amman (UTC +03:00) & 2 (0.3\%)\\
+\hspace{1em}Latvia - Europe/Riga (UTC +02:00) & 2 (0.3\%)\\
+\hspace{1em}Malaysia - Asia/Kuching (UTC +08:00) & 2 (0.3\%)\\
+\addlinespace
+\hspace{1em}Mexico - America/Mexico\_City (UTC -06:00) & 2 (0.3\%)\\
+\hspace{1em}Nepal - Asia/Kathmandu (UTC +05:45) & 2 (0.3\%)\\
+\hspace{1em}Portugal - Europe/Lisbon (UTC) & 2 (0.3\%)\\
+\hspace{1em}Slovakia - Europe/Bratislava (UTC +01:00) & 2 (0.3\%)\\
+\hspace{1em}Spain - Africa/Ceuta (UTC +01:00) & 2 (0.3\%)\\
+\addlinespace
+\hspace{1em}Sudan - Africa/Khartoum (UTC +02:00) & 2 (0.3\%)\\
+\hspace{1em}United States - America/Adak (UTC -09:00) & 2 (0.3\%)\\
+\hspace{1em}United States - Pacific/Honolulu (UTC -10:00) & 2 (0.3\%)\\
+\hspace{1em}Viet Nam - Asia/Ho\_Chi\_Minh (UTC +07:00),British - America/Tortola (UTC -04:00) & 2 (0.3\%)\\
+\hspace{1em}Albania - Europe/Tirane (UTC +01:00) & 1 (0.1\%)\\
+\addlinespace
+\hspace{1em}Argentina - America/Argentina/Jujuy (UTC -03:00) & 1 (0.1\%)\\
+\hspace{1em}Australia - Antarctica/Macquarie (UTC +11:00) & 1 (0.1\%)\\
+\hspace{1em}Australia - Australia/Darwin (UTC +09:30) & 1 (0.1\%)\\
+\hspace{1em}Austria - Europe/Vienna (UTC +01:00) & 1 (0.1\%)\\
+\hspace{1em}Bangladesh - Asia/Dhaka (UTC +06:00) & 1 (0.1\%)\\
+\addlinespace
+\hspace{1em}Brazil - America/Cuiaba (UTC -04:00) & 1 (0.1\%)\\
+\hspace{1em}Brazil - America/Fortaleza (UTC -03:00) & 1 (0.1\%)\\
+\hspace{1em}Bulgaria - Europe/Sofia (UTC +02:00) & 1 (0.1\%)\\
+\hspace{1em}Cameroon - Africa/Douala (UTC +01:00) & 1 (0.1\%)\\
+\hspace{1em}Canada - America/Blanc-Sablon (UTC -04:00) & 1 (0.1\%)\\
+\addlinespace
+\hspace{1em}Canada - America/Halifax (UTC -03:00) & 1 (0.1\%)\\
+\hspace{1em}Canada - America/Resolute (UTC -05:00) & 1 (0.1\%)\\
+\hspace{1em}Cayman Islands - America/Cayman (UTC -05:00) & 1 (0.1\%)\\
+\hspace{1em}Chile - Pacific/Easter (UTC -05:00) & 1 (0.1\%)\\
+\hspace{1em}Cyprus - Asia/Famagusta (UTC +02:00) & 1 (0.1\%)\\
+\addlinespace
+\hspace{1em}Guatemala - America/Guatemala (UTC -06:00) & 1 (0.1\%)\\
+\hspace{1em}Korea,Republic of - Asia/Seoul (UTC +09:00) & 1 (0.1\%)\\
+\hspace{1em}Macedonia & 1 (0.1\%)\\
+\hspace{1em}Martinique - America/Martinique (UTC -04:00) & 1 (0.1\%)\\
+\hspace{1em}Mexico - America/Monterrey (UTC -06:00) & 1 (0.1\%)\\
+\addlinespace
+\hspace{1em}Mongolia - Asia/Ulaanbaatar (UTC +08:00) & 1 (0.1\%)\\
+\hspace{1em}Myanmar - Asia/Yangon (UTC +06:30) & 1 (0.1\%)\\
+\hspace{1em}New Zealand - Pacific/Chatham (UTC +13:45) & 1 (0.1\%)\\
+\hspace{1em}Nigeria - Africa/Lagos (UTC +01:00) & 1 (0.1\%)\\
+\hspace{1em}Pakistan - Asia/Karachi (UTC +05:00) & 1 (0.1\%)\\
+\addlinespace
+\hspace{1em}Panama - America/Panama (UTC -05:00) & 1 (0.1\%)\\
+\hspace{1em}Russian Federation - Asia/Barnaul (UTC +07:00) & 1 (0.1\%)\\
+\hspace{1em}Russian Federation - Asia/Novosibirsk (UTC +07:00) & 1 (0.1\%)\\
+\hspace{1em}Russian Federation - Asia/Tomsk (UTC +07:00) & 1 (0.1\%)\\
+\hspace{1em}Russian Federation - Asia/Vladivostok (UTC +10:00) & 1 (0.1\%)\\
+\addlinespace
+\hspace{1em}Russian Federation - Asia/Yekaterinburg (UTC +05:00) & 1 (0.1\%)\\
+\hspace{1em}Saudi Arabia - Asia/Riyadh (UTC +03:00) & 1 (0.1\%)\\
+\hspace{1em}Singapore - Asia/Singapore (UTC +08:00) & 1 (0.1\%)\\
+\hspace{1em}Spain - Atlantic/Canary (UTC) & 1 (0.1\%)\\
+\hspace{1em}Tanzania & 1 (0.1\%)\\
+\addlinespace
+\hspace{1em}Ukraine - Europe/Kiev (UTC +02:00) & 1 (0.1\%)\\
+\hspace{1em}United States - America/Indiana/Tell\_City (UTC -05:00) & 1 (0.1\%)\\
+\hspace{1em}United States - America/North\_Dakota/Center (UTC -05:00) & 1 (0.1\%)\\
+\hspace{1em}United States - America/North\_Dakota/New\_Salem (UTC -05:00) & 1 (0.1\%)\\
+\hspace{1em}Aland Islands - Europe/Mariehamn (UTC +02:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Afghanistan - Asia/Kabul (UTC +04:30) & 0 (0\%)\\
+\hspace{1em}Algeria - Africa/Algiers (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}American Samoa - Pacific/Pago\_Pago (UTC -11:00) & 0 (0\%)\\
+\hspace{1em}Andorra - Europe/Andorra (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Angola - Africa/Luanda (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Anguilla - America/Anguilla (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Antarctica - Antarctica/Casey (UTC +11:00) & 0 (0\%)\\
+\hspace{1em}Antarctica - Antarctica/Davis (UTC +07:00) & 0 (0\%)\\
+\hspace{1em}Antarctica - Antarctica/DumontDUrville (UTC +10:00) & 0 (0\%)\\
+\hspace{1em}Antarctica - Antarctica/Mawson (UTC +05:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Antarctica - Antarctica/McMurdo (UTC +13:00) & 0 (0\%)\\
+\hspace{1em}Antarctica - Antarctica/Palmer (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Antarctica - Antarctica/Rothera (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Antarctica - Antarctica/Syowa (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Antarctica - Antarctica/Troll (UTC) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Antarctica - Antarctica/Vostok (UTC +06:00) & 0 (0\%)\\
+\hspace{1em}Antigua and Barbuda - America/Antigua (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Argentina - America/Argentina/Catamarca (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Argentina - America/Argentina/La\_Rioja (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Argentina - America/Argentina/Mendoza (UTC -03:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Argentina - America/Argentina/Rio\_Gallegos (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Argentina - America/Argentina/Salta (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Argentina - America/Argentina/San\_Juan (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Argentina - America/Argentina/San\_Luis (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Argentina - America/Argentina/Tucuman (UTC -03:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Argentina - America/Argentina/Ushuaia (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Armenia - Asia/Yerevan (UTC +04:00) & 0 (0\%)\\
+\hspace{1em}Aruba - America/Aruba (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Australia - Australia/Broken\_Hill (UTC +10:30) & 0 (0\%)\\
+\hspace{1em}Australia - Australia/Currie (UTC +11:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Australia - Australia/Eucla (UTC +08:45) & 0 (0\%)\\
+\hspace{1em}Australia - Australia/Hobart (UTC +11:00) & 0 (0\%)\\
+\hspace{1em}Australia - Australia/Lindeman (UTC +10:00) & 0 (0\%)\\
+\hspace{1em}Australia - Australia/Lord\_Howe (UTC +11:00) & 0 (0\%)\\
+\hspace{1em}Azerbaijan - Asia/Baku (UTC +04:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Bahamas - America/Nassau (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Bahrain - Asia/Bahrain (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Barbados - America/Barbados (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Belarus - Europe/Minsk (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Belize - America/Belize (UTC -06:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Benin - Africa/Porto-Novo (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Bermuda - Atlantic/Bermuda (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Bhutan - Asia/Thimphu (UTC +06:00),Plurinational State of - America/La\_Paz (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Bolivia,Sint Eustatius and Saba - America/Kralendijk (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Bonaire & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Bosnia and Herzegovina - Europe/Sarajevo (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Botswana - Africa/Gaborone (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Brazil - America/Belem (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Brazil - America/Boa\_Vista (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Brazil - America/Campo\_Grande (UTC -04:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Brazil - America/Eirunepe (UTC -05:00) & 0 (0\%)\\
+\hspace{1em}Brazil - America/Maceio (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Brazil - America/Manaus (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Brazil - America/Noronha (UTC -02:00) & 0 (0\%)\\
+\hspace{1em}Brazil - America/Porto\_Velho (UTC -04:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Brazil - America/Recife (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Brazil - America/Rio\_Branco (UTC -05:00) & 0 (0\%)\\
+\hspace{1em}Brazil - America/Santarem (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}British Indian Ocean Territory - Indian/Chagos (UTC +06:00) & 0 (0\%)\\
+\hspace{1em}Brunei Darussalam - Asia/Brunei (UTC +08:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Burkina Faso - Africa/Ouagadougou (UTC) & 0 (0\%)\\
+\hspace{1em}Burundi - Africa/Bujumbura (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Cambodia - Asia/Phnom\_Penh (UTC +07:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Atikokan (UTC -05:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Cambridge\_Bay (UTC -06:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Canada - America/Creston (UTC -07:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Dawson (UTC -07:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Dawson\_Creek (UTC -07:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Fort\_Nelson (UTC -07:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Glace\_Bay (UTC -03:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Canada - America/Goose\_Bay (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Inuvik (UTC -06:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Iqaluit (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Nipigon (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Pangnirtung (UTC -04:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Canada - America/Rainy\_River (UTC -05:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Rankin\_Inlet (UTC -05:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Regina (UTC -06:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/St\_Johns (UTC -02:30) & 0 (0\%)\\
+\hspace{1em}Canada - America/Swift\_Current (UTC -06:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Canada - America/Thunder\_Bay (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Whitehorse (UTC -07:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Winnipeg (UTC -05:00) & 0 (0\%)\\
+\hspace{1em}Canada - America/Yellowknife (UTC -06:00) & 0 (0\%)\\
+\hspace{1em}Cape Verde - Atlantic/Cape\_Verde (UTC -01:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Central African Republic - Africa/Bangui (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Chad - Africa/Ndjamena (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Chile - America/Punta\_Arenas (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}China - Asia/Urumqi (UTC +06:00) & 0 (0\%)\\
+\hspace{1em}Christmas Island - Indian/Christmas (UTC +07:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Cocos (Keeling) Islands - Indian/Cocos (UTC +06:30) & 0 (0\%)\\
+\hspace{1em}Comoros - Indian/Comoro (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Congo - Africa/Brazzaville (UTC +01:00),the Democratic Republic of the - Africa/Kinshasa (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Congo,the Democratic Republic of the - Africa/Lubumbashi (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Congo & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Cook Islands - Pacific/Rarotonga (UTC -10:00) & 0 (0\%)\\
+\hspace{1em}Cuba - America/Havana (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Curaçao - America/Curacao (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Cyprus - Asia/Nicosia (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Côte dIvoire - Africa/Abidjan (UTC) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Djibouti - Africa/Djibouti (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Dominica - America/Dominica (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Dominican Republic - America/Santo\_Domingo (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Ecuador - Pacific/Galapagos (UTC -06:00) & 0 (0\%)\\
+\hspace{1em}Egypt - Africa/Cairo (UTC +02:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}El Salvador - America/El\_Salvador (UTC -06:00) & 0 (0\%)\\
+\hspace{1em}Equatorial Guinea - Africa/Malabo (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Eritrea - Africa/Asmara (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Ethiopia - Africa/Addis\_Ababa (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Falkland Islands (Malvinas) - Atlantic/Stanley (UTC -03:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Faroe Islands - Atlantic/Faroe (UTC) & 0 (0\%)\\
+\hspace{1em}Fiji - Pacific/Fiji (UTC +12:00) & 0 (0\%)\\
+\hspace{1em}French Guiana - America/Cayenne (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}French Polynesia - Pacific/Gambier (UTC -09:00) & 0 (0\%)\\
+\hspace{1em}French Polynesia - Pacific/Marquesas (UTC -09:30) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}French Polynesia - Pacific/Tahiti (UTC -10:00) & 0 (0\%)\\
+\hspace{1em}French Southern Territories - Indian/Kerguelen (UTC +05:00) & 0 (0\%)\\
+\hspace{1em}Gabon - Africa/Libreville (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Gambia - Africa/Banjul (UTC) & 0 (0\%)\\
+\hspace{1em}Georgia - Asia/Tbilisi (UTC +04:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Ghana - Africa/Accra (UTC) & 0 (0\%)\\
+\hspace{1em}Gibraltar - Europe/Gibraltar (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Greenland - America/Danmarkshavn (UTC) & 0 (0\%)\\
+\hspace{1em}Greenland - America/Nuuk (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Greenland - America/Scoresbysund (UTC -01:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Greenland - America/Thule (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Grenada - America/Grenada (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Guadeloupe - America/Guadeloupe (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Guam - Pacific/Guam (UTC +10:00) & 0 (0\%)\\
+\hspace{1em}Guernsey - Europe/Guernsey (UTC) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Guinea - Africa/Conakry (UTC) & 0 (0\%)\\
+\hspace{1em}Guinea-Bissau - Africa/Bissau (UTC) & 0 (0\%)\\
+\hspace{1em}Guyana - America/Guyana (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Haiti - America/Port-au-Prince (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Holy See (Vatican City State) - Europe/Vatican (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Honduras - America/Tegucigalpa (UTC -06:00) & 0 (0\%)\\
+\hspace{1em}Iceland - Atlantic/Reykjavik (UTC) & 0 (0\%)\\
+\hspace{1em}Indonesia - Asia/Jayapura (UTC +09:00) & 0 (0\%)\\
+\hspace{1em}Indonesia - Asia/Makassar (UTC +08:00) & 0 (0\%)\\
+\hspace{1em}Indonesia - Asia/Pontianak (UTC +07:00),Islamic Republic of - Asia/Tehran (UTC +03:30) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Iraq - Asia/Baghdad (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Isle of Man - Europe/Isle\_of\_Man (UTC) & 0 (0\%)\\
+\hspace{1em}Jamaica - America/Jamaica (UTC -05:00) & 0 (0\%)\\
+\hspace{1em}Jersey - Europe/Jersey (UTC) & 0 (0\%)\\
+\hspace{1em}Kazakhstan - Asia/Almaty (UTC +06:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Kazakhstan - Asia/Aqtau (UTC +05:00) & 0 (0\%)\\
+\hspace{1em}Kazakhstan - Asia/Aqtobe (UTC +05:00) & 0 (0\%)\\
+\hspace{1em}Kazakhstan - Asia/Atyrau (UTC +05:00) & 0 (0\%)\\
+\hspace{1em}Kazakhstan - Asia/Oral (UTC +05:00) & 0 (0\%)\\
+\hspace{1em}Kazakhstan - Asia/Qostanay (UTC +06:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Kazakhstan - Asia/Qyzylorda (UTC +05:00) & 0 (0\%)\\
+\hspace{1em}Kenya - Africa/Nairobi (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Kiribati - Pacific/Enderbury (UTC +13:00) & 0 (0\%)\\
+\hspace{1em}Kiribati - Pacific/Kiritimati (UTC +14:00) & 0 (0\%)\\
+\hspace{1em}Kiribati - Pacific/Tarawa (UTC +12:00),Democratic Peoples Republic of - Asia/Pyongyang (UTC +09:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Korea & 0 (0\%)\\
+\hspace{1em}Kuwait - Asia/Kuwait (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Kyrgyzstan - Asia/Bishkek (UTC +06:00) & 0 (0\%)\\
+\hspace{1em}Lao Peoples Democratic Republic - Asia/Vientiane (UTC +07:00) & 0 (0\%)\\
+\hspace{1em}Lebanon - Asia/Beirut (UTC +02:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Lesotho - Africa/Maseru (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Liberia - Africa/Monrovia (UTC) & 0 (0\%)\\
+\hspace{1em}Libya - Africa/Tripoli (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Liechtenstein - Europe/Vaduz (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Luxembourg - Europe/Luxembourg (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Macao - Asia/Macau (UTC +08:00),the Former Yugoslav Republic of - Europe/Skopje (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Madagascar - Indian/Antananarivo (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Malawi - Africa/Blantyre (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Maldives - Indian/Maldives (UTC +05:00) & 0 (0\%)\\
+\hspace{1em}Mali - Africa/Bamako (UTC) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Malta - Europe/Malta (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Marshall Islands - Pacific/Kwajalein (UTC +12:00) & 0 (0\%)\\
+\hspace{1em}Marshall Islands - Pacific/Majuro (UTC +12:00) & 0 (0\%)\\
+\hspace{1em}Mauritania - Africa/Nouakchott (UTC) & 0 (0\%)\\
+\hspace{1em}Mauritius - Indian/Mauritius (UTC +04:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Mayotte - Indian/Mayotte (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Mexico - America/Bahia\_Banderas (UTC -06:00) & 0 (0\%)\\
+\hspace{1em}Mexico - America/Cancun (UTC -05:00) & 0 (0\%)\\
+\hspace{1em}Mexico - America/Chihuahua (UTC -07:00) & 0 (0\%)\\
+\hspace{1em}Mexico - America/Hermosillo (UTC -07:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Mexico - America/Matamoros (UTC -05:00) & 0 (0\%)\\
+\hspace{1em}Mexico - America/Mazatlan (UTC -07:00) & 0 (0\%)\\
+\hspace{1em}Mexico - America/Merida (UTC -06:00) & 0 (0\%)\\
+\hspace{1em}Mexico - America/Ojinaga (UTC -06:00) & 0 (0\%)\\
+\hspace{1em}Mexico - America/Tijuana (UTC -07:00),Federated States of - Pacific/Chuuk (UTC +10:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Micronesia,Federated States of - Pacific/Kosrae (UTC +11:00) & 0 (0\%)\\
+\hspace{1em}Micronesia,Federated States of - Pacific/Pohnpei (UTC +11:00) & 0 (0\%)\\
+\hspace{1em}Micronesia,Republic of - Europe/Chisinau (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Moldova & 0 (0\%)\\
+\hspace{1em}Monaco - Europe/Monaco (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Mongolia - Asia/Choibalsan (UTC +08:00) & 0 (0\%)\\
+\hspace{1em}Mongolia - Asia/Hovd (UTC +07:00) & 0 (0\%)\\
+\hspace{1em}Montenegro - Europe/Podgorica (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Montserrat - America/Montserrat (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Morocco - Africa/Casablanca (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Mozambique - Africa/Maputo (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Namibia - Africa/Windhoek (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Nauru - Pacific/Nauru (UTC +12:00) & 0 (0\%)\\
+\hspace{1em}New Caledonia - Pacific/Noumea (UTC +11:00) & 0 (0\%)\\
+\hspace{1em}Nicaragua - America/Managua (UTC -06:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Niger - Africa/Niamey (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Niue - Pacific/Niue (UTC -11:00) & 0 (0\%)\\
+\hspace{1em}Norfolk Island - Pacific/Norfolk (UTC +12:00) & 0 (0\%)\\
+\hspace{1em}Northern Mariana Islands - Pacific/Saipan (UTC +10:00) & 0 (0\%)\\
+\hspace{1em}Oman - Asia/Muscat (UTC +04:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Palau - Pacific/Palau (UTC +09:00),State of - Asia/Gaza (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Palestine,State of - Asia/Hebron (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Palestine & 0 (0\%)\\
+\hspace{1em}Papua New Guinea - Pacific/Bougainville (UTC +11:00) & 0 (0\%)\\
+\hspace{1em}Papua New Guinea - Pacific/Port\_Moresby (UTC +10:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Paraguay - America/Asuncion (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Peru - America/Lima (UTC -05:00) & 0 (0\%)\\
+\hspace{1em}Pitcairn - Pacific/Pitcairn (UTC -08:00) & 0 (0\%)\\
+\hspace{1em}Portugal - Atlantic/Azores (UTC -01:00) & 0 (0\%)\\
+\hspace{1em}Portugal - Atlantic/Madeira (UTC) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Puerto Rico - America/Puerto\_Rico (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Qatar - Asia/Qatar (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Asia/Anadyr (UTC +12:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Asia/Chita (UTC +09:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Asia/Irkutsk (UTC +08:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Russian Federation - Asia/Kamchatka (UTC +12:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Asia/Khandyga (UTC +09:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Asia/Krasnoyarsk (UTC +07:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Asia/Magadan (UTC +11:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Asia/Novokuznetsk (UTC +07:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Russian Federation - Asia/Omsk (UTC +06:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Asia/Sakhalin (UTC +11:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Asia/Srednekolymsk (UTC +11:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Asia/Ust-Nera (UTC +10:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Asia/Yakutsk (UTC +09:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Russian Federation - Europe/Astrakhan (UTC +04:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Europe/Kaliningrad (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Europe/Kirov (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Europe/Samara (UTC +04:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Europe/Saratov (UTC +04:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Russian Federation - Europe/Ulyanovsk (UTC +04:00) & 0 (0\%)\\
+\hspace{1em}Russian Federation - Europe/Volgograd (UTC +04:00) & 0 (0\%)\\
+\hspace{1em}Rwanda - Africa/Kigali (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Réunion - Indian/Reunion (UTC +04:00) & 0 (0\%)\\
+\hspace{1em}Saint Barthélemy - America/St\_Barthelemy (UTC -04:00),Ascension and Tristan da Cunha - Atlantic/St\_Helena (UTC) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Saint Helena & 0 (0\%)\\
+\hspace{1em}Saint Kitts and Nevis - America/St\_Kitts (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Saint Lucia - America/St\_Lucia (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Saint Martin (French part) - America/Marigot (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Saint Pierre and Miquelon - America/Miquelon (UTC -02:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Saint Vincent and the Grenadines - America/St\_Vincent (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Samoa - Pacific/Apia (UTC +14:00) & 0 (0\%)\\
+\hspace{1em}San Marino - Europe/San\_Marino (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Sao Tome and Principe - Africa/Sao\_Tome (UTC) & 0 (0\%)\\
+\hspace{1em}Senegal - Africa/Dakar (UTC) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Seychelles - Indian/Mahe (UTC +04:00) & 0 (0\%)\\
+\hspace{1em}Sierra Leone - Africa/Freetown (UTC) & 0 (0\%)\\
+\hspace{1em}Sint Maarten (Dutch part) - America/Lower\_Princes (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Solomon Islands - Pacific/Guadalcanal (UTC +11:00) & 0 (0\%)\\
+\hspace{1em}Somalia - Africa/Mogadishu (UTC +03:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}South Georgia and the South Sandwich Islands - Atlantic/South\_Georgia (UTC -02:00) & 0 (0\%)\\
+\hspace{1em}South Sudan - Africa/Juba (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Sri Lanka - Asia/Colombo (UTC +05:30) & 0 (0\%)\\
+\hspace{1em}Suriname - America/Paramaribo (UTC -03:00) & 0 (0\%)\\
+\hspace{1em}Svalbard and Jan Mayen - Arctic/Longyearbyen (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Swaziland - Africa/Mbabane (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Syrian Arab Republic - Asia/Damascus (UTC +03:00),Province of China - Asia/Taipei (UTC +08:00) & 0 (0\%)\\
+\hspace{1em}Tajikistan - Asia/Dushanbe (UTC +05:00),United Republic of - Africa/Dar\_es\_Salaam (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Thailand - Asia/Bangkok (UTC +07:00) & 0 (0\%)\\
+\hspace{1em}Timor-Leste - Asia/Dili (UTC +09:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Togo - Africa/Lome (UTC) & 0 (0\%)\\
+\hspace{1em}Tokelau - Pacific/Fakaofo (UTC +13:00) & 0 (0\%)\\
+\hspace{1em}Tonga - Pacific/Tongatapu (UTC +13:00) & 0 (0\%)\\
+\hspace{1em}Trinidad and Tobago - America/Port\_of\_Spain (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Tunisia - Africa/Tunis (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Turkmenistan - Asia/Ashgabat (UTC +05:00) & 0 (0\%)\\
+\hspace{1em}Turks and Caicos Islands - America/Grand\_Turk (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Tuvalu - Pacific/Funafuti (UTC +12:00) & 0 (0\%)\\
+\hspace{1em}Uganda - Africa/Kampala (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Ukraine - Europe/Simferopol (UTC +03:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Ukraine - Europe/Uzhgorod (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}Ukraine - Europe/Zaporozhye (UTC +02:00) & 0 (0\%)\\
+\hspace{1em}United Arab Emirates - Asia/Dubai (UTC +04:00) & 0 (0\%)\\
+\hspace{1em}United States - America/Indiana/Knox (UTC -05:00) & 0 (0\%)\\
+\hspace{1em}United States - America/Indiana/Marengo (UTC -04:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}United States - America/Indiana/Petersburg (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}United States - America/Indiana/Vevay (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}United States - America/Indiana/Vincennes (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}United States - America/Indiana/Winamac (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}United States - America/Juneau (UTC -08:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}United States - America/Kentucky/Monticello (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}United States - America/Menominee (UTC -05:00) & 0 (0\%)\\
+\hspace{1em}United States - America/Metlakatla (UTC -08:00) & 0 (0\%)\\
+\hspace{1em}United States - America/Nome (UTC -08:00) & 0 (0\%)\\
+\hspace{1em}United States - America/North\_Dakota/Beulah (UTC -05:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}United States - America/Sitka (UTC -08:00) & 0 (0\%)\\
+\hspace{1em}United States - America/Yakutat (UTC -08:00) & 0 (0\%)\\
+\hspace{1em}United States Minor Outlying Islands - Pacific/Midway (UTC -11:00) & 0 (0\%)\\
+\hspace{1em}United States Minor Outlying Islands - Pacific/Wake (UTC +12:00) & 0 (0\%)\\
+\hspace{1em}Uruguay - America/Montevideo (UTC -03:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Uzbekistan - Asia/Samarkand (UTC +05:00) & 0 (0\%)\\
+\hspace{1em}Uzbekistan - Asia/Tashkent (UTC +05:00) & 0 (0\%)\\
+\hspace{1em}Vanuatu - Pacific/Efate (UTC +11:00),Bolivarian Republic of - America/Caracas (UTC -04:00) & 0 (0\%)\\
+\hspace{1em}Venezuela & 0 (0\%)\\
+\hspace{1em}Virgin Islands,U.S. - America/St\_Thomas (UTC -04:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Virgin Islands & 0 (0\%)\\
+\hspace{1em}Wallis and Futuna - Pacific/Wallis (UTC +12:00) & 0 (0\%)\\
+\hspace{1em}Western Sahara - Africa/El\_Aaiun (UTC +01:00) & 0 (0\%)\\
+\hspace{1em}Yemen - Asia/Aden (UTC +03:00) & 0 (0\%)\\
+\hspace{1em}Zambia - Africa/Lusaka (UTC +02:00) & 0 (0\%)\\
+\addlinespace
+\hspace{1em}Zimbabwe - Africa/Harare (UTC +02:00) & 0 (0\%)\\
+\bottomrule
+\multicolumn{2}{l}{\rule{0pt}{1em}\textsuperscript{1} n (\%)}\\
+\end{tabular}}
+\end{table}
 \end{appendix}

### 2021-11-17 Supplymentary.Rmd
*tab 1

@@
 
-hist(residual.6F, main = NULL, xlab = "Six factor Solution: Residuals",ylim=c(0, 400))
-abline(h =65, lwd = 2, lty = 2)
-abline(v =.05,lwd = 2, lty = 2)
+#hist(residual.6F, main = NULL, xlab = "Six factor Solution: Residuals",ylim=c(0, 400))
+#abline(h =65, lwd = 2, lty = 2)
+#abline(v =.05,lwd = 2, lty = 2)
 sixFac <- tabledown::fac.tab(fa.6F.3, cut =.3,complexity = F)
@@
 
-as_kable_extra(tz_table, format = "latex",booktabs = T) -> tz_kable
+as_kable(tz_table, format = "latex",booktabs = T, longtable =T) -> tz_kable
 
@@
 
-tz_kable %>% kable_styling(latex_options = c("scale_down"))
+tz_kable %>% 
+  kable_styling(latex_options = c("repeat_header")) %>% 
+  column_spec(1,width = "10cm") %>% 
+  column_spec(2,width = "2cm")
 

### 2021-11-17 Supplymentary.tex
*tab 1

--- 2021-11-15 Supplymentary.tex
@@
-\clearpage
+% Options for packages loaded elsewhere
+\PassOptionsToPackage{unicode}{hyperref}
+\PassOptionsToPackage{hyphens}{url}
+%
+\documentclass[
+  english,
+  man]{apa6}
+\title{Supplementary}
+\author{Mushfiqul Anwar Siraji\textsuperscript{1, *}, Rafael Robert Lazar\textsuperscript{2, 3, *}, Juliëtte van Duijnhoven\textsuperscript{4}, Luc Schlangen\textsuperscript{5}, Shamsul Haque\textsuperscript{1}, Vineetha Kalavally\textsuperscript{6}, Céline Vetter\textsuperscript{7, 8}, Gena Glickman\textsuperscript{9}, Karin Smolders\textsuperscript{10}, \& Manuel Spitschan\textsuperscript{11, 2, 3}}
+\date{}
+
+\usepackage{amsmath,amssymb}
+\usepackage{lmodern}
+\usepackage{iftex}
+\ifPDFTeX
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+  \usepackage{textcomp} % provide euro and other symbols
+\else % if luatex or xetex
+  \usepackage{unicode-math}
+  \defaultfontfeatures{Scale=MatchLowercase}
+  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
+  \setmainfont[]{Arial}
+\fi
+% Use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\IfFileExists{microtype.sty}{% use microtype if available
+  \usepackage[]{microtype}
+  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
 \makeatletter
-\efloat@restorefloats
+\@ifundefined{KOMAClassName}{% if non-KOMA class
+  \IfFileExists{parskip.sty}{%
+    \usepackage{parskip}
+  }{% else
+    \setlength{\parindent}{0pt}
+    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
+}{% if KOMA class
+  \KOMAoptions{parskip=half}}
 \makeatother
+\usepackage{xcolor}
+\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
+\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
+\hypersetup{
+  pdftitle={Supplementary},
+  pdfauthor={Mushfiqul Anwar Siraji1, *, Rafael Robert Lazar2, 3, *, Juliëtte van Duijnhoven4, Luc Schlangen5, Shamsul Haque1, Vineetha Kalavally6, Céline Vetter7, 8, Gena Glickman9, Karin Smolders10, \& Manuel Spitschan11, 2, 3},
+  pdflang={en-EN},
+  hidelinks,
+  pdfcreator={LaTeX via pandoc}}
+\urlstyle{same} % disable monospaced font for URLs
+\usepackage{longtable,booktabs,array}
+\usepackage{calc} % for calculating minipage widths
+% Correct order of tables after \paragraph or \subparagraph
+\usepackage{etoolbox}
+\makeatletter
+\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
+\makeatother
+% Allow footnotes in longtable head/foot
+\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
+\makesavenoteenv{longtable}
+\usepackage{graphicx}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+% Set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
+\setlength{\emergencystretch}{3em} % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
+% Make \paragraph and \subparagraph free-standing
+\ifx\paragraph\undefined\else
+  \let\oldparagraph\paragraph
+  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+  \let\oldsubparagraph\subparagraph
+  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
+\usepackage{pdflscape}
+\newcommand{\blandscape}{\begin{landscape}}
+\newcommand{\elandscape}{\end{landscape}}
+% Manuscript styling
+\usepackage{upgreek}
+\captionsetup{font=singlespacing,justification=justified}
 
-\begin{appendix}
+% Table formatting
+\usepackage{longtable}
+\usepackage{lscape}
+% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
+\usepackage{multirow}		% Table styling
+\usepackage{tabularx}		% Control Column width
+\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
+\usepackage{threeparttablex}            % Lets threeparttable work with longtable
+
+% Create new environments so endfloat can handle them
+% \newenvironment{ltable}
+%   {\begin{landscape}\centering\begin{threeparttable}}
+%   {\end{threeparttable}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
+
+% Enables adjusting longtable caption width to table width
+% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
+\makeatletter
+\newcommand\LastLTentrywidth{1em}
+\newlength\longtablewidth
+\setlength{\longtablewidth}{1in}
+\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
+
+% \setlength{\parindent}{0.5in}
+% \setlength{\parskip}{0pt plus 0pt minus 0pt}
+
+% \usepackage{etoolbox}
+\makeatletter
+\patchcmd{\HyOrg@maketitle}
+  {\section{\normalfont\normalsize\abstractname}}
+  {\section*{\normalfont\normalsize\abstractname}}
+  {}{\typeout{Failed to patch abstract.}}
+\patchcmd{\HyOrg@maketitle}
+  {\section{\protect\normalfont{\@title}}}
+  {\section*{\protect\normalfont{\@title}}}
+  {}{\typeout{Failed to patch title.}}
+\makeatother
+\shorttitle{SA}
+\DeclareDelayedFloatFlavor{ThreePartTable}{table}
+\DeclareDelayedFloatFlavor{lltable}{table}
+\DeclareDelayedFloatFlavor*{longtable}{table}
+\makeatletter
+\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
+\makeatother
+\usepackage{lineno}
+
+\linenumbers
+\usepackage{csquotes}
+\ifXeTeX
+  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
+  \usepackage{polyglossia}
+  \setmainlanguage[]{english}
+\else
+  \usepackage[main=english]{babel}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
+\fi
+\ifLuaTeX
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
+
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia\\\textsuperscript{2} Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland\\\textsuperscript{3} University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland\\\textsuperscript{4} Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands\\\textsuperscript{5} Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Intelligent Lighting Institute, Eindhoven, Netherlands\\\textsuperscript{6} Monash University, Department of Electrical and Computer Systems Engineering, Malaysia, Selangor, Malaysia\\\textsuperscript{7} University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA\\\textsuperscript{8} Ximes GmbH, Frankfurt, Germany\\\textsuperscript{9} Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA\\\textsuperscript{10} Eindhoven University of Technology, Human-Technology Interaction Group, Eindhoven, Netherlands\\\textsuperscript{11} University of Oxford, Department of Experimental Psychology, Oxford, UK\\\textsuperscript{*} Joint first author}
+
+\begin{document}
+\maketitle
+
 \hypertarget{sa-confirming-the-five-factor-solution-obtained-using-minimum-residual-extraction-method}{%
-\section{SA: Confirming the five factor solution obtained using minimum
-residual extraction
-method}\label{sa-confirming-the-five-factor-solution-obtained-using-minimum-residual-extraction-method}}
+\section{SA: Confirming the five factor solution obtained using minimum residual extraction method}\label{sa-confirming-the-five-factor-solution-obtained-using-minimum-residual-extraction-method}}
 
@@
 \hypertarget{sa-factor-analysis-with-six-factors}{%
-\section{SA: Factor analysis with six
-factors}\label{sa-factor-analysis-with-six-factors}}
+\section{SA: Factor analysis with six factors}\label{sa-factor-analysis-with-six-factors}}
 
@@
 \hypertarget{sa-factor-analysis-with-unmerged-response-option}{%
-\section{SA: Factor Analysis with Unmerged Response
-Option}\label{sa-factor-analysis-with-unmerged-response-option}}
+\section{SA: Factor Analysis with Unmerged Response Option}\label{sa-factor-analysis-with-unmerged-response-option}}
 
-Table @ref(tab:tabDesAppB) summarizes the univariate descriptive
-statistics for the 48 items with un-merged options. Some of the items
-were skewed with high Kurtosis values. Our data violated both univariate
-normality (Shapiro-Wilk statistics) and multivariate normality
-assumptions {[}Marida's test{]}. Multivariate skew was = 494.70 (p
-\textless0.001) and multivariate kurtosis was = 2,705.00 (p
-\textless0.001). Due to these violations and ordinal nature of the
-response data polychoric correlations over Pearson's correlations was
-chosen. Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO)
-measures of sampling adequacy. The overall KMO vale for 48 items was
-0.65 which was above the cutoff value (.50) indicating a mediocre
-sample. Bartlett's test of sphericity, \(\chi^2\) (1128) = 5515.20, p
-\textless{} .001 indicated the correlations between items are adequate
-for the EFA. However only 4.34\% of the inter-item correlation
-coefficients were greater than .30. The absolute value of inter-item
-correlation ranged between .00 to .96.Figure @ref(fig:figCorAppB)
-depicts the correlation matrix. For un-merged response option Horn's
-parallel analysis with 500 iterations indicated a five-factor solution.
+Table \ref{tab:tabDesAppB} summarizes the univariate descriptive statistics for the 48 items with un-merged options.
+Some of the items were skewed with high Kurtosis values.
+Our data violated both univariate normality (Shapiro-Wilk statistics) and multivariate normality assumptions {[}Marida's test{]}.
+Multivariate skew was = 494.70 (p \textless0.001) and multivariate kurtosis was = 2,705.00 (p \textless0.001).
+Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen.
+Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy.
+The overall KMO vale for 48 items was 0.65 which was above the cutoff value (.50) indicating a mediocre sample.
+Bartlett's test of sphericity, \(\chi^2\) (1128) = 5515.20, p \textless{} .001 indicated the correlations between items are adequate for the EFA.
+However only 4.34\% of the inter-item correlation coefficients were greater than .30.
+The absolute value of inter-item correlation ranged between .00 to .96.Figure \ref{fig:figCorAppB} depicts the correlation matrix.
+For un-merged response option Horn's parallel analysis with 500 iterations indicated a five-factor solution.
 However, Scree plot and the MAP method suggested 6-factor solution.
-five-factor solution . As a result, we tested both five-factor and
-six-factor solutions. The six factor solution yielded a factor with only
-two salient loading (Table @ref(tab:EFAsix). Thus we reject the six
-factor solution. The five factor solution retained 24 items (Table
-@ref(tab:EFATableAppB)). However the factors are less interpretable in
-terms of common theme. Thus we reject the five factor solution.
+five-factor solution .
+As a result, we tested both five-factor and six-factor solutions.
+The six factor solution yielded a factor with only two salient loading (Table \ref{tab:EFAsix}.
+Thus we reject the six factor solution.
+The five factor solution retained 24 items (Table \ref{tab:EFATableAppB}).
+However the factors are less interpretable in terms of common theme.
+Thus we reject the five factor solution.
 
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/facIdFigAppB-1.pdf}
-\caption{(\#fig:facIdFigAppB)Factor Identification (A) Parallel analysis
-(B) Scree Plot {[}Unmerged response options{]}}
+\includegraphics{Supplymentary_files/figure-latex/facIdFigAppB-1.pdf}
+\caption{\label{fig:facIdFigAppB}Factor Identification (A) Parallel analysis (B) Scree Plot {[}Unmerged response options{]}}
 \end{figure}
@@
 \hypertarget{items-retained-in-the-five-factor-solution-unmerged-responses}{%
-\section{Items Retained in the Five Factor Solution {[}Unmerged
-Responses{]}}\label{items-retained-in-the-five-factor-solution-unmerged-responses}}
+\section{Items Retained in the Five Factor Solution {[}Unmerged Responses{]}}\label{items-retained-in-the-five-factor-solution-unmerged-responses}}
 
@@
 \textbf{F4} \\
-I use a blue-filter app on my computer screen within 1 hour before
-attempting to fall asleep. \\
+I use a blue-filter app on my computer screen within 1 hour before attempting to fall asleep. \\
 I seek out knowledge on how to improve my light exposure. \\
-I dim my computer screen within 1 hour before attempting to fall
-asleep. \\
+I dim my computer screen within 1 hour before attempting to fall asleep. \\
 I discuss the effects of light on my body with other people. \\
@@
 \textbf{F5} \\
-I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors
-during the day. \\
-I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors
-during the day. \\
-I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1
-hour before attempting to fall asleep. \\
+I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day. \\
+I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day. \\
+I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1 hour before attempting to fall asleep. \\
 \bottomrule
 \end{longtable}
-\end{appendix}
+
+\hypertarget{geographic-locations-of-survey-participants}{%
+\section{Geographic Locations of Survey Participants}\label{geographic-locations-of-survey-participants}}
+
+\begingroup\fontsize{8}{10}\selectfont
+
+\begin{longtable}[t]{>{\raggedright\arraybackslash}p{10cm}>{\raggedright\arraybackslash}p{4cm}}
+\caption{\label{tab:TzTable}Geographical Location}\\
+\toprule
+ & **N = 690**\\
+\midrule
+\endfirsthead
+\caption[]{\label{tab:TzTable}Geographical Location \textit{(continued)}}\\
+\toprule
+ & **N = 690**\\
+\midrule
+\endhead
+
+\endfoot
+\bottomrule
+\endlastfoot
+\_\_Time zone - Country\_\_ & \\
+United States - America/New\_York (UTC -04:00) & 63 (9.1\%)\\
+United Kingdom - Europe/London (UTC) & 57 (8.3\%)\\
+Germany - Europe/Berlin (UTC +01:00) & 53 (7.7\%)\\
+India - Asia/Kolkata (UTC +05:30) & 38 (5.5\%)\\
+\addlinespace
+United States - America/Los\_Angeles (UTC -07:00) & 37 (5.4\%)\\
+United States - America/Chicago (UTC -05:00) & 30 (4.3\%)\\
+France - Europe/Paris (UTC +01:00) & 22 (3.2\%)\\
+Switzerland - Europe/Zurich (UTC +01:00) & 21 (3.0\%)\\
+Brazil - America/Sao\_Paulo (UTC -03:00) & 19 (2.8\%)\\
+\addlinespace
+Netherlands - Europe/Amsterdam (UTC +01:00) & 19 (2.8\%)\\
+Canada - America/Toronto (UTC -04:00) & 16 (2.3\%)\\
+Poland - Europe/Warsaw (UTC +01:00) & 15 (2.2\%)\\
+Canada - America/Edmonton (UTC -06:00) & 14 (2.0\%)\\
+Finland - Europe/Helsinki (UTC +02:00) & 9 (1.3\%)\\
+\addlinespace
+Indonesia - Asia/Jakarta (UTC +07:00) & 9 (1.3\%)\\
+Italy - Europe/Rome (UTC +01:00) & 9 (1.3\%)\\
+Chile - America/Santiago (UTC -03:00) & 8 (1.2\%)\\
+Russian Federation - Europe/Moscow (UTC +03:00) & 8 (1.2\%)\\
+China - Asia/Shanghai (UTC +08:00) & 7 (1.0\%)\\
+\addlinespace
+Malaysia - Asia/Kuala\_Lumpur (UTC +08:00) & 7 (1.0\%)\\
+Spain - Europe/Madrid (UTC +01:00) & 7 (1.0\%)\\
+United States - America/Phoenix (UTC -07:00) & 7 (1.0\%)\\
+Canada - America/Vancouver (UTC -07:00) & 6 (0.9\%)\\
+New Zealand - Pacific/Auckland (UTC +13:00) & 6 (0.9\%)\\
+\addlinespace
+Philippines - Asia/Manila (UTC +08:00) & 6 (0.9\%)\\
+Turkey - Europe/Istanbul (UTC +03:00) & 6 (0.9\%)\\
+United States - America/Denver (UTC -06:00) & 6 (0.9\%)\\
+United States - America/Detroit (UTC -04:00) & 6 (0.9\%)\\
+Argentina - America/Argentina/Buenos\_Aires (UTC -03:00) & 5 (0.7\%)\\
+\addlinespace
+Australia - Australia/Melbourne (UTC +11:00) & 5 (0.7\%)\\
+Ireland - Europe/Dublin (UTC) & 5 (0.7\%)\\
+Lithuania - Europe/Vilnius (UTC +02:00) & 5 (0.7\%)\\
+South Africa - Africa/Johannesburg (UTC +02:00) & 5 (0.7\%)\\
+Australia - Australia/Brisbane (UTC +10:00) & 4 (0.6\%)\\
+\addlinespace
+Belgium - Europe/Brussels (UTC +01:00) & 4 (0.6\%)\\
+Israel - Asia/Jerusalem (UTC +02:00) & 4 (0.6\%)\\
+Sweden - Europe/Stockholm (UTC +01:00) & 4 (0.6\%)\\
+United States - America/Boise (UTC -06:00) & 4 (0.6\%)\\
+Czech Republic - Europe/Prague (UTC +01:00) & 3 (0.4\%)\\
+\addlinespace
+Denmark - Europe/Copenhagen (UTC +01:00) & 3 (0.4\%)\\
+Germany - Europe/Busingen (UTC +01:00) & 3 (0.4\%)\\
+Greece - Europe/Athens (UTC +02:00) & 3 (0.4\%)\\
+Iran & 3 (0.4\%)\\
+Japan - Asia/Tokyo (UTC +09:00) & 3 (0.4\%)\\
+\addlinespace
+Norway - Europe/Oslo (UTC +01:00) & 3 (0.4\%)\\
+Romania - Europe/Bucharest (UTC +02:00) & 3 (0.4\%)\\
+Serbia - Europe/Belgrade (UTC +01:00) & 3 (0.4\%)\\
+Slovenia - Europe/Ljubljana (UTC +01:00) & 3 (0.4\%)\\
+Taiwan & 3 (0.4\%)\\
+\addlinespace
+United States - America/Anchorage (UTC -08:00) & 3 (0.4\%)\\
+United States - America/Indiana/Indianapolis (UTC -04:00) & 3 (0.4\%)\\
+United States - America/Kentucky/Louisville (UTC -04:00) & 3 (0.4\%)\\
+Argentina - America/Argentina/Cordoba (UTC -03:00) & 2 (0.3\%)\\
+Australia - Australia/Adelaide (UTC +10:30) & 2 (0.3\%)\\
+\addlinespace
+Australia - Australia/Perth (UTC +08:00) & 2 (0.3\%)\\
+Australia - Australia/Sydney (UTC +11:00) & 2 (0.3\%)\\
+Brazil - America/Araguaina (UTC -03:00) & 2 (0.3\%)\\
+Brazil - America/Bahia (UTC -03:00) & 2 (0.3\%)\\
+Canada - America/Moncton (UTC -03:00) & 2 (0.3\%)\\
+\addlinespace
+Colombia - America/Bogota (UTC -05:00) & 2 (0.3\%)\\
+Costa Rica - America/Costa\_Rica (UTC -06:00) & 2 (0.3\%)\\
+Croatia - Europe/Zagreb (UTC +01:00) & 2 (0.3\%)\\
+Ecuador - America/Guayaquil (UTC -05:00) & 2 (0.3\%)\\
+Estonia - Europe/Tallinn (UTC +02:00) & 2 (0.3\%)\\
+\addlinespace
+Hong Kong - Asia/Hong\_Kong (UTC +08:00) & 2 (0.3\%)\\
+Hungary - Europe/Budapest (UTC +01:00) & 2 (0.3\%)\\
+Jordan - Asia/Amman (UTC +03:00) & 2 (0.3\%)\\
+Latvia - Europe/Riga (UTC +02:00) & 2 (0.3\%)\\
+Malaysia - Asia/Kuching (UTC +08:00) & 2 (0.3\%)\\
+\addlinespace
+Mexico - America/Mexico\_City (UTC -06:00) & 2 (0.3\%)\\
+Nepal - Asia/Kathmandu (UTC +05:45) & 2 (0.3\%)\\
+Portugal - Europe/Lisbon (UTC) & 2 (0.3\%)\\
+Slovakia - Europe/Bratislava (UTC +01:00) & 2 (0.3\%)\\
+Spain - Africa/Ceuta (UTC +01:00) & 2 (0.3\%)\\
+\addlinespace
+Sudan - Africa/Khartoum (UTC +02:00) & 2 (0.3\%)\\
+United States - America/Adak (UTC -09:00) & 2 (0.3\%)\\
+United States - Pacific/Honolulu (UTC -10:00) & 2 (0.3\%)\\
+Viet Nam - Asia/Ho\_Chi\_Minh (UTC +07:00),British - America/Tortola (UTC -04:00) & 2 (0.3\%)\\
+Albania - Europe/Tirane (UTC +01:00) & 1 (0.1\%)\\
+\addlinespace
+Argentina - America/Argentina/Jujuy (UTC -03:00) & 1 (0.1\%)\\
+Australia - Antarctica/Macquarie (UTC +11:00) & 1 (0.1\%)\\
+Australia - Australia/Darwin (UTC +09:30) & 1 (0.1\%)\\
+Austria - Europe/Vienna (UTC +01:00) & 1 (0.1\%)\\
+Bangladesh - Asia/Dhaka (UTC +06:00) & 1 (0.1\%)\\
+\addlinespace
+Brazil - America/Cuiaba (UTC -04:00) & 1 (0.1\%)\\
+Brazil - America/Fortaleza (UTC -03:00) & 1 (0.1\%)\\
+Bulgaria - Europe/Sofia (UTC +02:00) & 1 (0.1\%)\\
+Cameroon - Africa/Douala (UTC +01:00) & 1 (0.1\%)\\
+Canada - America/Blanc-Sablon (UTC -04:00) & 1 (0.1\%)\\
+\addlinespace
+Canada - America/Halifax (UTC -03:00) & 1 (0.1\%)\\
+Canada - America/Resolute (UTC -05:00) & 1 (0.1\%)\\
+Cayman Islands - America/Cayman (UTC -05:00) & 1 (0.1\%)\\
+Chile - Pacific/Easter (UTC -05:00) & 1 (0.1\%)\\
+Cyprus - Asia/Famagusta (UTC +02:00) & 1 (0.1\%)\\
+\addlinespace
+Guatemala - America/Guatemala (UTC -06:00) & 1 (0.1\%)\\
+Korea,Republic of - Asia/Seoul (UTC +09:00) & 1 (0.1\%)\\
+Macedonia & 1 (0.1\%)\\
+Martinique - America/Martinique (UTC -04:00) & 1 (0.1\%)\\
+Mexico - America/Monterrey (UTC -06:00) & 1 (0.1\%)\\
+\addlinespace
+Mongolia - Asia/Ulaanbaatar (UTC +08:00) & 1 (0.1\%)\\
+Myanmar - Asia/Yangon (UTC +06:30) & 1 (0.1\%)\\
+New Zealand - Pacific/Chatham (UTC +13:45) & 1 (0.1\%)\\
+Nigeria - Africa/Lagos (UTC +01:00) & 1 (0.1\%)\\
+Pakistan - Asia/Karachi (UTC +05:00) & 1 (0.1\%)\\
+\addlinespace
+Panama - America/Panama (UTC -05:00) & 1 (0.1\%)\\
+Russian Federation - Asia/Barnaul (UTC +07:00) & 1 (0.1\%)\\
+Russian Federation - Asia/Novosibirsk (UTC +07:00) & 1 (0.1\%)\\
+Russian Federation - Asia/Tomsk (UTC +07:00) & 1 (0.1\%)\\
+Russian Federation - Asia/Vladivostok (UTC +10:00) & 1 (0.1\%)\\
+\addlinespace
+Russian Federation - Asia/Yekaterinburg (UTC +05:00) & 1 (0.1\%)\\
+Saudi Arabia - Asia/Riyadh (UTC +03:00) & 1 (0.1\%)\\
+Singapore - Asia/Singapore (UTC +08:00) & 1 (0.1\%)\\
+Spain - Atlantic/Canary (UTC) & 1 (0.1\%)\\
+Tanzania & 1 (0.1\%)\\
+\addlinespace
+Ukraine - Europe/Kiev (UTC +02:00) & 1 (0.1\%)\\
+United States - America/Indiana/Tell\_City (UTC -05:00) & 1 (0.1\%)\\
+United States - America/North\_Dakota/Center (UTC -05:00) & 1 (0.1\%)\\
+United States - America/North\_Dakota/New\_Salem (UTC -05:00) & 1 (0.1\%)\\
+Aland Islands - Europe/Mariehamn (UTC +02:00) & 0 (0\%)\\
+\addlinespace
+Afghanistan - Asia/Kabul (UTC +04:30) & 0 (0\%)\\
+Algeria - Africa/Algiers (UTC +01:00) & 0 (0\%)\\
+American Samoa - Pacific/Pago\_Pago (UTC -11:00) & 0 (0\%)\\
+Andorra - Europe/Andorra (UTC +01:00) & 0 (0\%)\\
+Angola - Africa/Luanda (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+Anguilla - America/Anguilla (UTC -04:00) & 0 (0\%)\\
+Antarctica - Antarctica/Casey (UTC +11:00) & 0 (0\%)\\
+Antarctica - Antarctica/Davis (UTC +07:00) & 0 (0\%)\\
+Antarctica - Antarctica/DumontDUrville (UTC +10:00) & 0 (0\%)\\
+Antarctica - Antarctica/Mawson (UTC +05:00) & 0 (0\%)\\
+\addlinespace
+Antarctica - Antarctica/McMurdo (UTC +13:00) & 0 (0\%)\\
+Antarctica - Antarctica/Palmer (UTC -03:00) & 0 (0\%)\\
+Antarctica - Antarctica/Rothera (UTC -03:00) & 0 (0\%)\\
+Antarctica - Antarctica/Syowa (UTC +03:00) & 0 (0\%)\\
+Antarctica - Antarctica/Troll (UTC) & 0 (0\%)\\
+\addlinespace
+Antarctica - Antarctica/Vostok (UTC +06:00) & 0 (0\%)\\
+Antigua and Barbuda - America/Antigua (UTC -04:00) & 0 (0\%)\\
+Argentina - America/Argentina/Catamarca (UTC -03:00) & 0 (0\%)\\
+Argentina - America/Argentina/La\_Rioja (UTC -03:00) & 0 (0\%)\\
+Argentina - America/Argentina/Mendoza (UTC -03:00) & 0 (0\%)\\
+\addlinespace
+Argentina - America/Argentina/Rio\_Gallegos (UTC -03:00) & 0 (0\%)\\
+Argentina - America/Argentina/Salta (UTC -03:00) & 0 (0\%)\\
+Argentina - America/Argentina/San\_Juan (UTC -03:00) & 0 (0\%)\\
+Argentina - America/Argentina/San\_Luis (UTC -03:00) & 0 (0\%)\\
+Argentina - America/Argentina/Tucuman (UTC -03:00) & 0 (0\%)\\
+\addlinespace
+Argentina - America/Argentina/Ushuaia (UTC -03:00) & 0 (0\%)\\
+Armenia - Asia/Yerevan (UTC +04:00) & 0 (0\%)\\
+Aruba - America/Aruba (UTC -04:00) & 0 (0\%)\\
+Australia - Australia/Broken\_Hill (UTC +10:30) & 0 (0\%)\\
+Australia - Australia/Currie (UTC +11:00) & 0 (0\%)\\
+\addlinespace
+Australia - Australia/Eucla (UTC +08:45) & 0 (0\%)\\
+Australia - Australia/Hobart (UTC +11:00) & 0 (0\%)\\
+Australia - Australia/Lindeman (UTC +10:00) & 0 (0\%)\\
+Australia - Australia/Lord\_Howe (UTC +11:00) & 0 (0\%)\\
+Azerbaijan - Asia/Baku (UTC +04:00) & 0 (0\%)\\
+\addlinespace
+Bahamas - America/Nassau (UTC -04:00) & 0 (0\%)\\
+Bahrain - Asia/Bahrain (UTC +03:00) & 0 (0\%)\\
+Barbados - America/Barbados (UTC -04:00) & 0 (0\%)\\
+Belarus - Europe/Minsk (UTC +03:00) & 0 (0\%)\\
+Belize - America/Belize (UTC -06:00) & 0 (0\%)\\
+\addlinespace
+Benin - Africa/Porto-Novo (UTC +01:00) & 0 (0\%)\\
+Bermuda - Atlantic/Bermuda (UTC -03:00) & 0 (0\%)\\
+Bhutan - Asia/Thimphu (UTC +06:00),Plurinational State of - America/La\_Paz (UTC -04:00) & 0 (0\%)\\
+Bolivia,Sint Eustatius and Saba - America/Kralendijk (UTC -04:00) & 0 (0\%)\\
+Bonaire & 0 (0\%)\\
+\addlinespace
+Bosnia and Herzegovina - Europe/Sarajevo (UTC +01:00) & 0 (0\%)\\
+Botswana - Africa/Gaborone (UTC +02:00) & 0 (0\%)\\
+Brazil - America/Belem (UTC -03:00) & 0 (0\%)\\
+Brazil - America/Boa\_Vista (UTC -04:00) & 0 (0\%)\\
+Brazil - America/Campo\_Grande (UTC -04:00) & 0 (0\%)\\
+\addlinespace
+Brazil - America/Eirunepe (UTC -05:00) & 0 (0\%)\\
+Brazil - America/Maceio (UTC -03:00) & 0 (0\%)\\
+Brazil - America/Manaus (UTC -04:00) & 0 (0\%)\\
+Brazil - America/Noronha (UTC -02:00) & 0 (0\%)\\
+Brazil - America/Porto\_Velho (UTC -04:00) & 0 (0\%)\\
+\addlinespace
+Brazil - America/Recife (UTC -03:00) & 0 (0\%)\\
+Brazil - America/Rio\_Branco (UTC -05:00) & 0 (0\%)\\
+Brazil - America/Santarem (UTC -03:00) & 0 (0\%)\\
+British Indian Ocean Territory - Indian/Chagos (UTC +06:00) & 0 (0\%)\\
+Brunei Darussalam - Asia/Brunei (UTC +08:00) & 0 (0\%)\\
+\addlinespace
+Burkina Faso - Africa/Ouagadougou (UTC) & 0 (0\%)\\
+Burundi - Africa/Bujumbura (UTC +02:00) & 0 (0\%)\\
+Cambodia - Asia/Phnom\_Penh (UTC +07:00) & 0 (0\%)\\
+Canada - America/Atikokan (UTC -05:00) & 0 (0\%)\\
+Canada - America/Cambridge\_Bay (UTC -06:00) & 0 (0\%)\\
+\addlinespace
+Canada - America/Creston (UTC -07:00) & 0 (0\%)\\
+Canada - America/Dawson (UTC -07:00) & 0 (0\%)\\
+Canada - America/Dawson\_Creek (UTC -07:00) & 0 (0\%)\\
+Canada - America/Fort\_Nelson (UTC -07:00) & 0 (0\%)\\
+Canada - America/Glace\_Bay (UTC -03:00) & 0 (0\%)\\
+\addlinespace
+Canada - America/Goose\_Bay (UTC -03:00) & 0 (0\%)\\
+Canada - America/Inuvik (UTC -06:00) & 0 (0\%)\\
+Canada - America/Iqaluit (UTC -04:00) & 0 (0\%)\\
+Canada - America/Nipigon (UTC -04:00) & 0 (0\%)\\
+Canada - America/Pangnirtung (UTC -04:00) & 0 (0\%)\\
+\addlinespace
+Canada - America/Rainy\_River (UTC -05:00) & 0 (0\%)\\
+Canada - America/Rankin\_Inlet (UTC -05:00) & 0 (0\%)\\
+Canada - America/Regina (UTC -06:00) & 0 (0\%)\\
+Canada - America/St\_Johns (UTC -02:30) & 0 (0\%)\\
+Canada - America/Swift\_Current (UTC -06:00) & 0 (0\%)\\
+\addlinespace
+Canada - America/Thunder\_Bay (UTC -04:00) & 0 (0\%)\\
+Canada - America/Whitehorse (UTC -07:00) & 0 (0\%)\\
+Canada - America/Winnipeg (UTC -05:00) & 0 (0\%)\\
+Canada - America/Yellowknife (UTC -06:00) & 0 (0\%)\\
+Cape Verde - Atlantic/Cape\_Verde (UTC -01:00) & 0 (0\%)\\
+\addlinespace
+Central African Republic - Africa/Bangui (UTC +01:00) & 0 (0\%)\\
+Chad - Africa/Ndjamena (UTC +01:00) & 0 (0\%)\\
+Chile - America/Punta\_Arenas (UTC -03:00) & 0 (0\%)\\
+China - Asia/Urumqi (UTC +06:00) & 0 (0\%)\\
+Christmas Island - Indian/Christmas (UTC +07:00) & 0 (0\%)\\
+\addlinespace
+Cocos (Keeling) Islands - Indian/Cocos (UTC +06:30) & 0 (0\%)\\
+Comoros - Indian/Comoro (UTC +03:00) & 0 (0\%)\\
+Congo - Africa/Brazzaville (UTC +01:00),the Democratic Republic of the - Africa/Kinshasa (UTC +01:00) & 0 (0\%)\\
+Congo,the Democratic Republic of the - Africa/Lubumbashi (UTC +02:00) & 0 (0\%)\\
+Congo & 0 (0\%)\\
+\addlinespace
+Cook Islands - Pacific/Rarotonga (UTC -10:00) & 0 (0\%)\\
+Cuba - America/Havana (UTC -04:00) & 0 (0\%)\\
+Curaçao - America/Curacao (UTC -04:00) & 0 (0\%)\\
+Cyprus - Asia/Nicosia (UTC +02:00) & 0 (0\%)\\
+Côte dIvoire - Africa/Abidjan (UTC) & 0 (0\%)\\
+\addlinespace
+Djibouti - Africa/Djibouti (UTC +03:00) & 0 (0\%)\\
+Dominica - America/Dominica (UTC -04:00) & 0 (0\%)\\
+Dominican Republic - America/Santo\_Domingo (UTC -04:00) & 0 (0\%)\\
+Ecuador - Pacific/Galapagos (UTC -06:00) & 0 (0\%)\\
+Egypt - Africa/Cairo (UTC +02:00) & 0 (0\%)\\
+\addlinespace
+El Salvador - America/El\_Salvador (UTC -06:00) & 0 (0\%)\\
+Equatorial Guinea - Africa/Malabo (UTC +01:00) & 0 (0\%)\\
+Eritrea - Africa/Asmara (UTC +03:00) & 0 (0\%)\\
+Ethiopia - Africa/Addis\_Ababa (UTC +03:00) & 0 (0\%)\\
+Falkland Islands (Malvinas) - Atlantic/Stanley (UTC -03:00) & 0 (0\%)\\
+\addlinespace
+Faroe Islands - Atlantic/Faroe (UTC) & 0 (0\%)\\
+Fiji - Pacific/Fiji (UTC +12:00) & 0 (0\%)\\
+French Guiana - America/Cayenne (UTC -03:00) & 0 (0\%)\\
+French Polynesia - Pacific/Gambier (UTC -09:00) & 0 (0\%)\\
+French Polynesia - Pacific/Marquesas (UTC -09:30) & 0 (0\%)\\
+\addlinespace
+French Polynesia - Pacific/Tahiti (UTC -10:00) & 0 (0\%)\\
+French Southern Territories - Indian/Kerguelen (UTC +05:00) & 0 (0\%)\\
+Gabon - Africa/Libreville (UTC +01:00) & 0 (0\%)\\
+Gambia - Africa/Banjul (UTC) & 0 (0\%)\\
+Georgia - Asia/Tbilisi (UTC +04:00) & 0 (0\%)\\
+\addlinespace
+Ghana - Africa/Accra (UTC) & 0 (0\%)\\
+Gibraltar - Europe/Gibraltar (UTC +01:00) & 0 (0\%)\\
+Greenland - America/Danmarkshavn (UTC) & 0 (0\%)\\
+Greenland - America/Nuuk (UTC -03:00) & 0 (0\%)\\
+Greenland - America/Scoresbysund (UTC -01:00) & 0 (0\%)\\
+\addlinespace
+Greenland - America/Thule (UTC -03:00) & 0 (0\%)\\
+Grenada - America/Grenada (UTC -04:00) & 0 (0\%)\\
+Guadeloupe - America/Guadeloupe (UTC -04:00) & 0 (0\%)\\
+Guam - Pacific/Guam (UTC +10:00) & 0 (0\%)\\
+Guernsey - Europe/Guernsey (UTC) & 0 (0\%)\\
+\addlinespace
+Guinea - Africa/Conakry (UTC) & 0 (0\%)\\
+Guinea-Bissau - Africa/Bissau (UTC) & 0 (0\%)\\
+Guyana - America/Guyana (UTC -04:00) & 0 (0\%)\\
+Haiti - America/Port-au-Prince (UTC -04:00) & 0 (0\%)\\
+Holy See (Vatican City State) - Europe/Vatican (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+Honduras - America/Tegucigalpa (UTC -06:00) & 0 (0\%)\\
+Iceland - Atlantic/Reykjavik (UTC) & 0 (0\%)\\
+Indonesia - Asia/Jayapura (UTC +09:00) & 0 (0\%)\\
+Indonesia - Asia/Makassar (UTC +08:00) & 0 (0\%)\\
+Indonesia - Asia/Pontianak (UTC +07:00),Islamic Republic of - Asia/Tehran (UTC +03:30) & 0 (0\%)\\
+\addlinespace
+Iraq - Asia/Baghdad (UTC +03:00) & 0 (0\%)\\
+Isle of Man - Europe/Isle\_of\_Man (UTC) & 0 (0\%)\\
+Jamaica - America/Jamaica (UTC -05:00) & 0 (0\%)\\
+Jersey - Europe/Jersey (UTC) & 0 (0\%)\\
+Kazakhstan - Asia/Almaty (UTC +06:00) & 0 (0\%)\\
+\addlinespace
+Kazakhstan - Asia/Aqtau (UTC +05:00) & 0 (0\%)\\
+Kazakhstan - Asia/Aqtobe (UTC +05:00) & 0 (0\%)\\
+Kazakhstan - Asia/Atyrau (UTC +05:00) & 0 (0\%)\\
+Kazakhstan - Asia/Oral (UTC +05:00) & 0 (0\%)\\
+Kazakhstan - Asia/Qostanay (UTC +06:00) & 0 (0\%)\\
+\addlinespace
+Kazakhstan - Asia/Qyzylorda (UTC +05:00) & 0 (0\%)\\
+Kenya - Africa/Nairobi (UTC +03:00) & 0 (0\%)\\
+Kiribati - Pacific/Enderbury (UTC +13:00) & 0 (0\%)\\
+Kiribati - Pacific/Kiritimati (UTC +14:00) & 0 (0\%)\\
+Kiribati - Pacific/Tarawa (UTC +12:00),Democratic Peoples Republic of - Asia/Pyongyang (UTC +09:00) & 0 (0\%)\\
+\addlinespace
+Korea & 0 (0\%)\\
+Kuwait - Asia/Kuwait (UTC +03:00) & 0 (0\%)\\
+Kyrgyzstan - Asia/Bishkek (UTC +06:00) & 0 (0\%)\\
+Lao Peoples Democratic Republic - Asia/Vientiane (UTC +07:00) & 0 (0\%)\\
+Lebanon - Asia/Beirut (UTC +02:00) & 0 (0\%)\\
+\addlinespace
+Lesotho - Africa/Maseru (UTC +02:00) & 0 (0\%)\\
+Liberia - Africa/Monrovia (UTC) & 0 (0\%)\\
+Libya - Africa/Tripoli (UTC +02:00) & 0 (0\%)\\
+Liechtenstein - Europe/Vaduz (UTC +01:00) & 0 (0\%)\\
+Luxembourg - Europe/Luxembourg (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+Macao - Asia/Macau (UTC +08:00),the Former Yugoslav Republic of - Europe/Skopje (UTC +01:00) & 0 (0\%)\\
+Madagascar - Indian/Antananarivo (UTC +03:00) & 0 (0\%)\\
+Malawi - Africa/Blantyre (UTC +02:00) & 0 (0\%)\\
+Maldives - Indian/Maldives (UTC +05:00) & 0 (0\%)\\
+Mali - Africa/Bamako (UTC) & 0 (0\%)\\
+\addlinespace
+Malta - Europe/Malta (UTC +01:00) & 0 (0\%)\\
+Marshall Islands - Pacific/Kwajalein (UTC +12:00) & 0 (0\%)\\
+Marshall Islands - Pacific/Majuro (UTC +12:00) & 0 (0\%)\\
+Mauritania - Africa/Nouakchott (UTC) & 0 (0\%)\\
+Mauritius - Indian/Mauritius (UTC +04:00) & 0 (0\%)\\
+\addlinespace
+Mayotte - Indian/Mayotte (UTC +03:00) & 0 (0\%)\\
+Mexico - America/Bahia\_Banderas (UTC -06:00) & 0 (0\%)\\
+Mexico - America/Cancun (UTC -05:00) & 0 (0\%)\\
+Mexico - America/Chihuahua (UTC -07:00) & 0 (0\%)\\
+Mexico - America/Hermosillo (UTC -07:00) & 0 (0\%)\\
+\addlinespace
+Mexico - America/Matamoros (UTC -05:00) & 0 (0\%)\\
+Mexico - America/Mazatlan (UTC -07:00) & 0 (0\%)\\
+Mexico - America/Merida (UTC -06:00) & 0 (0\%)\\
+Mexico - America/Ojinaga (UTC -06:00) & 0 (0\%)\\
+Mexico - America/Tijuana (UTC -07:00),Federated States of - Pacific/Chuuk (UTC +10:00) & 0 (0\%)\\
+\addlinespace
+Micronesia,Federated States of - Pacific/Kosrae (UTC +11:00) & 0 (0\%)\\
+Micronesia,Federated States of - Pacific/Pohnpei (UTC +11:00) & 0 (0\%)\\
+Micronesia,Republic of - Europe/Chisinau (UTC +02:00) & 0 (0\%)\\
+Moldova & 0 (0\%)\\
+Monaco - Europe/Monaco (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+Mongolia - Asia/Choibalsan (UTC +08:00) & 0 (0\%)\\
+Mongolia - Asia/Hovd (UTC +07:00) & 0 (0\%)\\
+Montenegro - Europe/Podgorica (UTC +01:00) & 0 (0\%)\\
+Montserrat - America/Montserrat (UTC -04:00) & 0 (0\%)\\
+Morocco - Africa/Casablanca (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+Mozambique - Africa/Maputo (UTC +02:00) & 0 (0\%)\\
+Namibia - Africa/Windhoek (UTC +02:00) & 0 (0\%)\\
+Nauru - Pacific/Nauru (UTC +12:00) & 0 (0\%)\\
+New Caledonia - Pacific/Noumea (UTC +11:00) & 0 (0\%)\\
+Nicaragua - America/Managua (UTC -06:00) & 0 (0\%)\\
+\addlinespace
+Niger - Africa/Niamey (UTC +01:00) & 0 (0\%)\\
+Niue - Pacific/Niue (UTC -11:00) & 0 (0\%)\\
+Norfolk Island - Pacific/Norfolk (UTC +12:00) & 0 (0\%)\\
+Northern Mariana Islands - Pacific/Saipan (UTC +10:00) & 0 (0\%)\\
+Oman - Asia/Muscat (UTC +04:00) & 0 (0\%)\\
+\addlinespace
+Palau - Pacific/Palau (UTC +09:00),State of - Asia/Gaza (UTC +02:00) & 0 (0\%)\\
+Palestine,State of - Asia/Hebron (UTC +02:00) & 0 (0\%)\\
+Palestine & 0 (0\%)\\
+Papua New Guinea - Pacific/Bougainville (UTC +11:00) & 0 (0\%)\\
+Papua New Guinea - Pacific/Port\_Moresby (UTC +10:00) & 0 (0\%)\\
+\addlinespace
+Paraguay - America/Asuncion (UTC -03:00) & 0 (0\%)\\
+Peru - America/Lima (UTC -05:00) & 0 (0\%)\\
+Pitcairn - Pacific/Pitcairn (UTC -08:00) & 0 (0\%)\\
+Portugal - Atlantic/Azores (UTC -01:00) & 0 (0\%)\\
+Portugal - Atlantic/Madeira (UTC) & 0 (0\%)\\
+\addlinespace
+Puerto Rico - America/Puerto\_Rico (UTC -04:00) & 0 (0\%)\\
+Qatar - Asia/Qatar (UTC +03:00) & 0 (0\%)\\
+Russian Federation - Asia/Anadyr (UTC +12:00) & 0 (0\%)\\
+Russian Federation - Asia/Chita (UTC +09:00) & 0 (0\%)\\
+Russian Federation - Asia/Irkutsk (UTC +08:00) & 0 (0\%)\\
+\addlinespace
+Russian Federation - Asia/Kamchatka (UTC +12:00) & 0 (0\%)\\
+Russian Federation - Asia/Khandyga (UTC +09:00) & 0 (0\%)\\
+Russian Federation - Asia/Krasnoyarsk (UTC +07:00) & 0 (0\%)\\
+Russian Federation - Asia/Magadan (UTC +11:00) & 0 (0\%)\\
+Russian Federation - Asia/Novokuznetsk (UTC +07:00) & 0 (0\%)\\
+\addlinespace
+Russian Federation - Asia/Omsk (UTC +06:00) & 0 (0\%)\\
+Russian Federation - Asia/Sakhalin (UTC +11:00) & 0 (0\%)\\
+Russian Federation - Asia/Srednekolymsk (UTC +11:00) & 0 (0\%)\\
+Russian Federation - Asia/Ust-Nera (UTC +10:00) & 0 (0\%)\\
+Russian Federation - Asia/Yakutsk (UTC +09:00) & 0 (0\%)\\
+\addlinespace
+Russian Federation - Europe/Astrakhan (UTC +04:00) & 0 (0\%)\\
+Russian Federation - Europe/Kaliningrad (UTC +02:00) & 0 (0\%)\\
+Russian Federation - Europe/Kirov (UTC +03:00) & 0 (0\%)\\
+Russian Federation - Europe/Samara (UTC +04:00) & 0 (0\%)\\
+Russian Federation - Europe/Saratov (UTC +04:00) & 0 (0\%)\\
+\addlinespace
+Russian Federation - Europe/Ulyanovsk (UTC +04:00) & 0 (0\%)\\
+Russian Federation - Europe/Volgograd (UTC +04:00) & 0 (0\%)\\
+Rwanda - Africa/Kigali (UTC +02:00) & 0 (0\%)\\
+Réunion - Indian/Reunion (UTC +04:00) & 0 (0\%)\\
+Saint Barthélemy - America/St\_Barthelemy (UTC -04:00),Ascension and Tristan da Cunha - Atlantic/St\_Helena (UTC) & 0 (0\%)\\
+\addlinespace
+Saint Helena & 0 (0\%)\\
+Saint Kitts and Nevis - America/St\_Kitts (UTC -04:00) & 0 (0\%)\\
+Saint Lucia - America/St\_Lucia (UTC -04:00) & 0 (0\%)\\
+Saint Martin (French part) - America/Marigot (UTC -04:00) & 0 (0\%)\\
+Saint Pierre and Miquelon - America/Miquelon (UTC -02:00) & 0 (0\%)\\
+\addlinespace
+Saint Vincent and the Grenadines - America/St\_Vincent (UTC -04:00) & 0 (0\%)\\
+Samoa - Pacific/Apia (UTC +14:00) & 0 (0\%)\\
+San Marino - Europe/San\_Marino (UTC +01:00) & 0 (0\%)\\
+Sao Tome and Principe - Africa/Sao\_Tome (UTC) & 0 (0\%)\\
+Senegal - Africa/Dakar (UTC) & 0 (0\%)\\
+\addlinespace
+Seychelles - Indian/Mahe (UTC +04:00) & 0 (0\%)\\
+Sierra Leone - Africa/Freetown (UTC) & 0 (0\%)\\
+Sint Maarten (Dutch part) - America/Lower\_Princes (UTC -04:00) & 0 (0\%)\\
+Solomon Islands - Pacific/Guadalcanal (UTC +11:00) & 0 (0\%)\\
+Somalia - Africa/Mogadishu (UTC +03:00) & 0 (0\%)\\
+\addlinespace
+South Georgia and the South Sandwich Islands - Atlantic/South\_Georgia (UTC -02:00) & 0 (0\%)\\
+South Sudan - Africa/Juba (UTC +03:00) & 0 (0\%)\\
+Sri Lanka - Asia/Colombo (UTC +05:30) & 0 (0\%)\\
+Suriname - America/Paramaribo (UTC -03:00) & 0 (0\%)\\
+Svalbard and Jan Mayen - Arctic/Longyearbyen (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+Swaziland - Africa/Mbabane (UTC +02:00) & 0 (0\%)\\
+Syrian Arab Republic - Asia/Damascus (UTC +03:00),Province of China - Asia/Taipei (UTC +08:00) & 0 (0\%)\\
+Tajikistan - Asia/Dushanbe (UTC +05:00),United Republic of - Africa/Dar\_es\_Salaam (UTC +03:00) & 0 (0\%)\\
+Thailand - Asia/Bangkok (UTC +07:00) & 0 (0\%)\\
+Timor-Leste - Asia/Dili (UTC +09:00) & 0 (0\%)\\
+\addlinespace
+Togo - Africa/Lome (UTC) & 0 (0\%)\\
+Tokelau - Pacific/Fakaofo (UTC +13:00) & 0 (0\%)\\
+Tonga - Pacific/Tongatapu (UTC +13:00) & 0 (0\%)\\
+Trinidad and Tobago - America/Port\_of\_Spain (UTC -04:00) & 0 (0\%)\\
+Tunisia - Africa/Tunis (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+Turkmenistan - Asia/Ashgabat (UTC +05:00) & 0 (0\%)\\
+Turks and Caicos Islands - America/Grand\_Turk (UTC -04:00) & 0 (0\%)\\
+Tuvalu - Pacific/Funafuti (UTC +12:00) & 0 (0\%)\\
+Uganda - Africa/Kampala (UTC +03:00) & 0 (0\%)\\
+Ukraine - Europe/Simferopol (UTC +03:00) & 0 (0\%)\\
+\addlinespace
+Ukraine - Europe/Uzhgorod (UTC +02:00) & 0 (0\%)\\
+Ukraine - Europe/Zaporozhye (UTC +02:00) & 0 (0\%)\\
+United Arab Emirates - Asia/Dubai (UTC +04:00) & 0 (0\%)\\
+United States - America/Indiana/Knox (UTC -05:00) & 0 (0\%)\\
+United States - America/Indiana/Marengo (UTC -04:00) & 0 (0\%)\\
+\addlinespace
+United States - America/Indiana/Petersburg (UTC -04:00) & 0 (0\%)\\
+United States - America/Indiana/Vevay (UTC -04:00) & 0 (0\%)\\
+United States - America/Indiana/Vincennes (UTC -04:00) & 0 (0\%)\\
+United States - America/Indiana/Winamac (UTC -04:00) & 0 (0\%)\\
+United States - America/Juneau (UTC -08:00) & 0 (0\%)\\
+\addlinespace
+United States - America/Kentucky/Monticello (UTC -04:00) & 0 (0\%)\\
+United States - America/Menominee (UTC -05:00) & 0 (0\%)\\
+United States - America/Metlakatla (UTC -08:00) & 0 (0\%)\\
+United States - America/Nome (UTC -08:00) & 0 (0\%)\\
+United States - America/North\_Dakota/Beulah (UTC -05:00) & 0 (0\%)\\
+\addlinespace
+United States - America/Sitka (UTC -08:00) & 0 (0\%)\\
+United States - America/Yakutat (UTC -08:00) & 0 (0\%)\\
+United States Minor Outlying Islands - Pacific/Midway (UTC -11:00) & 0 (0\%)\\
+United States Minor Outlying Islands - Pacific/Wake (UTC +12:00) & 0 (0\%)\\
+Uruguay - America/Montevideo (UTC -03:00) & 0 (0\%)\\
+\addlinespace
+Uzbekistan - Asia/Samarkand (UTC +05:00) & 0 (0\%)\\
+Uzbekistan - Asia/Tashkent (UTC +05:00) & 0 (0\%)\\
+Vanuatu - Pacific/Efate (UTC +11:00),Bolivarian Republic of - America/Caracas (UTC -04:00) & 0 (0\%)\\
+Venezuela & 0 (0\%)\\
+Virgin Islands,U.S. - America/St\_Thomas (UTC -04:00) & 0 (0\%)\\
+\addlinespace
+Virgin Islands & 0 (0\%)\\
+Wallis and Futuna - Pacific/Wallis (UTC +12:00) & 0 (0\%)\\
+Western Sahara - Africa/El\_Aaiun (UTC +01:00) & 0 (0\%)\\
+Yemen - Asia/Aden (UTC +03:00) & 0 (0\%)\\
+Zambia - Africa/Lusaka (UTC +02:00) & 0 (0\%)\\
+\addlinespace
+Zimbabwe - Africa/Harare (UTC +02:00) & 0 (0\%)\\*
+\end{longtable}
+\endgroup{}
+
+\end{document}

### 2021-11-17 manuscript.Rmd
*tab 1

@@
 
-```{r}
+```{r relscale, include=F, warning=F, message=F}
 relevant.scale.data <- readxl::read_excel("Table_raw/relevant_scales.xlsx")
@@
 
-```{r results='asis'}
+```{r scalePrint, results='asis'}
 relevant.scale.data %>%

### 2021-11-17 Supplymentary.tex
knitting in multiple devices

@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-%
-\documentclass[
-  english,
-  man]{apa6}
-\title{Supplementary}
-\author{Mushfiqul Anwar Siraji\textsuperscript{1, *}, Rafael Robert Lazar\textsuperscript{2, 3, *}, Juliëtte van Duijnhoven\textsuperscript{4}, Luc Schlangen\textsuperscript{5}, Shamsul Haque\textsuperscript{1}, Vineetha Kalavally\textsuperscript{6}, Céline Vetter\textsuperscript{7, 8}, Gena Glickman\textsuperscript{9}, Karin Smolders\textsuperscript{10}, \& Manuel Spitschan\textsuperscript{11, 2, 3}}
-\date{}
+\clearpage
+\makeatletter
+\efloat@restorefloats
+\makeatother
 
-\usepackage{amsmath,amssymb}
-\usepackage{lmodern}
-\usepackage{iftex}
-\ifPDFTeX
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-  \setmainfont[]{Arial}
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\hypersetup{
-  pdftitle={Supplementary},
-  pdfauthor={Mushfiqul Anwar Siraji1, *, Rafael Robert Lazar2, 3, *, Juliëtte van Duijnhoven4, Luc Schlangen5, Shamsul Haque1, Vineetha Kalavally6, Céline Vetter7, 8, Gena Glickman9, Karin Smolders10, \& Manuel Spitschan11, 2, 3},
-  pdflang={en-EN},
-  hidelinks,
-  pdfcreator={LaTeX via pandoc}}
-\urlstyle{same} % disable monospaced font for URLs
-\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
-\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
-% Make \paragraph and \subparagraph free-standing
-\ifx\paragraph\undefined\else
-  \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-  \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
-\usepackage{pdflscape}
-\newcommand{\blandscape}{\begin{landscape}}
-\newcommand{\elandscape}{\end{landscape}}
-% Manuscript styling
-\usepackage{upgreek}
-\captionsetup{font=singlespacing,justification=justified}
-
-% Table formatting
-\usepackage{longtable}
-\usepackage{lscape}
-% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
-\usepackage{multirow}		% Table styling
-\usepackage{tabularx}		% Control Column width
-\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
-\usepackage{threeparttablex}            % Lets threeparttable work with longtable
-
-% Create new environments so endfloat can handle them
-% \newenvironment{ltable}
-%   {\begin{landscape}\centering\begin{threeparttable}}
-%   {\end{threeparttable}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
-
-% Enables adjusting longtable caption width to table width
-% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
-\makeatletter
-\newcommand\LastLTentrywidth{1em}
-\newlength\longtablewidth
-\setlength{\longtablewidth}{1in}
-\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}
-
-% \setlength{\parindent}{0.5in}
-% \setlength{\parskip}{0pt plus 0pt minus 0pt}
-
-% \usepackage{etoolbox}
-\makeatletter
-\patchcmd{\HyOrg@maketitle}
-  {\section{\normalfont\normalsize\abstractname}}
-  {\section*{\normalfont\normalsize\abstractname}}
-  {}{\typeout{Failed to patch abstract.}}
-\patchcmd{\HyOrg@maketitle}
-  {\section{\protect\normalfont{\@title}}}
-  {\section*{\protect\normalfont{\@title}}}
-  {}{\typeout{Failed to patch title.}}
-\makeatother
-\shorttitle{SA}
-\DeclareDelayedFloatFlavor{ThreePartTable}{table}
-\DeclareDelayedFloatFlavor{lltable}{table}
-\DeclareDelayedFloatFlavor*{longtable}{table}
-\makeatletter
-\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
-\makeatother
-\usepackage{lineno}
-
-\linenumbers
-\usepackage{csquotes}
-\ifXeTeX
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia\\\textsuperscript{2} Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland\\\textsuperscript{3} University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland\\\textsuperscript{4} Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands\\\textsuperscript{5} Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Intelligent Lighting Institute, Eindhoven, Netherlands\\\textsuperscript{6} Monash University, Department of Electrical and Computer Systems Engineering, Malaysia, Selangor, Malaysia\\\textsuperscript{7} University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA\\\textsuperscript{8} Ximes GmbH, Frankfurt, Germany\\\textsuperscript{9} Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA\\\textsuperscript{10} Eindhoven University of Technology, Human-Technology Interaction Group, Eindhoven, Netherlands\\\textsuperscript{11} University of Oxford, Department of Experimental Psychology, Oxford, UK\\\textsuperscript{*} Joint first author}
-
-\begin{document}
-\maketitle
-
+\begin{appendix}
 \hypertarget{sa-confirming-the-five-factor-solution-obtained-using-minimum-residual-extraction-method}{%
-\section{SA: Confirming the five factor solution obtained using minimum residual extraction method}\label{sa-confirming-the-five-factor-solution-obtained-using-minimum-residual-extraction-method}}
+\section{SA: Confirming the five factor solution obtained using minimum
+residual extraction
+method}\label{sa-confirming-the-five-factor-solution-obtained-using-minimum-residual-extraction-method}}
 
@@
 \begin{longtable}{llllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
-\caption{\label{tab:MinResTab}Factor loadings and communality of the retained items(Minmum Residual)}\\
+\caption{\label{tab:MinResTab-8}Factor loadings and communality of the retained items(Minmum Residual)}\\
 \toprule
@@
 \endfirsthead
-\caption*{\normalfont{Table \ref{tab:MinResTab} continued}}\\
+\caption*{\normalfont{Table \ref{tab:MinResTab-8} continued}}\\
 \toprule
@@
 \hypertarget{sa-factor-analysis-with-six-factors}{%
-\section{SA: Factor analysis with six factors}\label{sa-factor-analysis-with-six-factors}}
+\section{SA: Factor analysis with six
+factors}\label{sa-factor-analysis-with-six-factors}}
 
@@
 \begin{longtable}{lllllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
-\caption{\label{tab:sixFacTab}Factor loadings and communality of the retained items(six factor)}\\
+\caption{\label{tab:sixFacTab-10}Factor loadings and communality of the retained items(six factor)}\\
 \toprule
@@
 \endfirsthead
-\caption*{\normalfont{Table \ref{tab:sixFacTab} continued}}\\
+\caption*{\normalfont{Table \ref{tab:sixFacTab-10} continued}}\\
 \toprule
@@
 \hypertarget{sa-factor-analysis-with-unmerged-response-option}{%
-\section{SA: Factor Analysis with Unmerged Response Option}\label{sa-factor-analysis-with-unmerged-response-option}}
+\section{SA: Factor Analysis with Unmerged Response
+Option}\label{sa-factor-analysis-with-unmerged-response-option}}
 
-Table \ref{tab:tabDesAppB} summarizes the univariate descriptive statistics for the 48 items with un-merged options.
-Some of the items were skewed with high Kurtosis values.
-Our data violated both univariate normality (Shapiro-Wilk statistics) and multivariate normality assumptions {[}Marida's test{]}.
-Multivariate skew was = 494.70 (p \textless0.001) and multivariate kurtosis was = 2,705.00 (p \textless0.001).
-Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen.
-Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy.
-The overall KMO vale for 48 items was 0.65 which was above the cutoff value (.50) indicating a mediocre sample.
-Bartlett's test of sphericity, \(\chi^2\) (1128) = 5515.20, p \textless{} .001 indicated the correlations between items are adequate for the EFA.
-However only 4.34\% of the inter-item correlation coefficients were greater than .30.
-The absolute value of inter-item correlation ranged between .00 to .96.Figure \ref{fig:figCorAppB} depicts the correlation matrix.
-For un-merged response option Horn's parallel analysis with 500 iterations indicated a five-factor solution.
+Table @ref(tab:tabDesAppB) summarizes the univariate descriptive
+statistics for the 48 items with un-merged options. Some of the items
+were skewed with high Kurtosis values. Our data violated both univariate
+normality (Shapiro-Wilk statistics) and multivariate normality
+assumptions {[}Marida's test{]}. Multivariate skew was = 494.70 (p
+\textless0.001) and multivariate kurtosis was = 2,705.00 (p
+\textless0.001). Due to these violations and ordinal nature of the
+response data polychoric correlations over Pearson's correlations was
+chosen. Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO)
+measures of sampling adequacy. The overall KMO vale for 48 items was
+0.65 which was above the cutoff value (.50) indicating a mediocre
+sample. Bartlett's test of sphericity, \(\chi^2\) (1128) = 5515.20, p
+\textless{} .001 indicated the correlations between items are adequate
+for the EFA. However only 4.34\% of the inter-item correlation
+coefficients were greater than .30. The absolute value of inter-item
+correlation ranged between .00 to .96.Figure @ref(fig:figCorAppB)
+depicts the correlation matrix. For un-merged response option Horn's
+parallel analysis with 500 iterations indicated a five-factor solution.
 However, Scree plot and the MAP method suggested 6-factor solution.
-five-factor solution .
-As a result, we tested both five-factor and six-factor solutions.
-The six factor solution yielded a factor with only two salient loading (Table \ref{tab:EFAsix}.
-Thus we reject the six factor solution.
-The five factor solution retained 24 items (Table \ref{tab:EFATableAppB}).
-However the factors are less interpretable in terms of common theme.
-Thus we reject the five factor solution.
+five-factor solution . As a result, we tested both five-factor and
+six-factor solutions. The six factor solution yielded a factor with only
+two salient loading (Table @ref(tab:EFAsix). Thus we reject the six
+factor solution. The five factor solution retained 24 items (Table
+@ref(tab:EFATableAppB)). However the factors are less interpretable in
+terms of common theme. Thus we reject the five factor solution.
 
@@
 \begin{longtable}{lllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
-\caption{\label{tab:tabDesAppB}Descriptive Statistics for Unmerged response options}\\
+\caption{\label{tab:tabDesAppB-18}Descriptive Statistics for Unmerged response options}\\
 \toprule
@@
 \endfirsthead
-\caption*{\normalfont{Table \ref{tab:tabDesAppB} continued}}\\
+\caption*{\normalfont{Table \ref{tab:tabDesAppB-18} continued}}\\
 \toprule
@@
 \centering
-\includegraphics{Supplymentary_files/figure-latex/facIdFigAppB-1.pdf}
-\caption{\label{fig:facIdFigAppB}Factor Identification (A) Parallel analysis (B) Scree Plot {[}Unmerged response options{]}}
+\includegraphics{manuscript_files/figure-latex/facIdFigAppB-20-1.pdf}
+\caption{(\#fig:facIdFigAppB-20)Factor Identification (A) Parallel
+analysis (B) Scree Plot {[}Unmerged response options{]}}
 \end{figure}
@@
 \begin{longtable}{llllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
-\caption{\label{tab:EFATableAppB}Factor loadings and communality of the retained items in five factor solution [Unmerged Responses]}\\
+\caption{\label{tab:EFATableAppB-23}Factor loadings and communality of the retained items in five factor solution [Unmerged Responses]}\\
 \toprule
@@
 \endfirsthead
-\caption*{\normalfont{Table \ref{tab:EFATableAppB} continued}}\\
+\caption*{\normalfont{Table \ref{tab:EFATableAppB-23} continued}}\\
 \toprule
@@
 \begin{longtable}{lllllllll}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
-\caption{\label{tab:EFAsix}Factor loadings and communality of the retained items in six factor solution [Unmerged Responses]}\\
+\caption{\label{tab:EFAsix-25}Factor loadings and communality of the retained items in six factor solution [Unmerged Responses]}\\
 \toprule
@@
 \endfirsthead
-\caption*{\normalfont{Table \ref{tab:EFAsix} continued}}\\
+\caption*{\normalfont{Table \ref{tab:EFAsix-25} continued}}\\
 \toprule
@@
 \hypertarget{items-retained-in-the-five-factor-solution-unmerged-responses}{%
-\section{Items Retained in the Five Factor Solution {[}Unmerged Responses{]}}\label{items-retained-in-the-five-factor-solution-unmerged-responses}}
+\section{Items Retained in the Five Factor Solution {[}Unmerged
+Responses{]}}\label{items-retained-in-the-five-factor-solution-unmerged-responses}}
 
@@
 \textbf{F4} \\
-I use a blue-filter app on my computer screen within 1 hour before attempting to fall asleep. \\
+I use a blue-filter app on my computer screen within 1 hour before
+attempting to fall asleep. \\
 I seek out knowledge on how to improve my light exposure. \\
-I dim my computer screen within 1 hour before attempting to fall asleep. \\
+I dim my computer screen within 1 hour before attempting to fall
+asleep. \\
 I discuss the effects of light on my body with other people. \\
@@
 \textbf{F5} \\
-I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day. \\
-I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day. \\
-I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1 hour before attempting to fall asleep. \\
+I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors
+during the day. \\
+I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors
+during the day. \\
+I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1
+hour before attempting to fall asleep. \\
 \bottomrule
@@
 \hypertarget{geographic-locations-of-survey-participants}{%
-\section{Geographic Locations of Survey Participants}\label{geographic-locations-of-survey-participants}}
+\section{Geographic Locations of Survey
+Participants}\label{geographic-locations-of-survey-participants}}
 
-\begingroup\fontsize{8}{10}\selectfont
-
-\begin{longtable}[t]{>{\raggedright\arraybackslash}p{10cm}>{\raggedright\arraybackslash}p{4cm}}
-\caption{\label{tab:TzTable}Geographical Location}\\
+\begin{longtable}[t]{>{\raggedright\arraybackslash}p{10cm}>{\raggedright\arraybackslash}p{2cm}}
+\caption{(\#tab:TzTable-27)Geographical Location}\\
 \toprule
@@
 \endfirsthead
-\caption[]{\label{tab:TzTable}Geographical Location \textit{(continued)}}\\
+\caption[]{(\#tab:TzTable-27)Geographical Location \textit{(continued)}}\\
 \toprule
@@
 \end{longtable}
-\endgroup{}
-
-\end{document}
+\end{appendix}

### 2021-11-17 manuscript.Rmd
knitting in multiple devices

@@
 ```{r pacman, eval=FALSE, include=FALSE}
-#You need to run this chunck 1X in your system 
-#install.packages("pacman")
+#You need to run this chunk 1X in your system 
+#install.packages("pacman")#Run this if you don't have pacman installed.
 pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl)

### 2021-11-17 manuscript.tex
knitting in multiple devices

--- 2021-11-15 manuscript.tex
@@
 
-\begin{longtable}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{4cm}}
-\caption{\label{tab:unnamed-chunk-2}Releated Scales}\\
-\toprule
-Name & Author & Description & Relevant Items\\
+\begin{longtable}[t]{>{\raggedright\arraybackslash}p{2cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedright\arraybackslash}p{2cm}>{\raggedright\arraybackslash}p{2cm}}
+\caption{\label{tab:scalePrint}Releated Scales}\\
+\toprule
+Name & Author & Description & Relevant Items & Scale type & Validity evidences\\
 \midrule
 \endfirsthead
-\caption[]{\label{tab:unnamed-chunk-2}Releated Scales \textit{(continued)}}\\
-\toprule
-Name & Author & Description & Relevant Items\\
+\caption[]{\label{tab:scalePrint}Releated Scales \textit{(continued)}}\\
+\toprule
+Name & Author & Description & Relevant Items & Scale type & Validity evidences\\
 \midrule
@@
 \endlastfoot
-Visual Light Sensitivity Questionnaire-8 & Verriotto et al., 2017 & Eight-question survey to assess the presence and severity of photosensitivity symptoms & NA\\
-Office Light Survey & Eklundet al., 1996 & A survey to assess electrical lighting environment in office & NA\\
-Harvard Light Exposure Assessment Questionnaire & Bajaj et al., 2011 & Self-administered semi-quantitative light questionnaire & NA\\
-Hospital Lighting Survey & Dianat et el., 2013 & 23 items questionnaire to assess light environment in a hospital & NA\\
-Morningness-Eveningness Questionnaire & Horne et al., 1976 & 19 items questionnaire to understand your body clock & NA\\
-\addlinespace
-Munich Chronotype Questionnaire (MCTQ) & Roenneberg et al., 2003 & 17 items questionnaire to understand individuals phase of entrainment & NA\\
-Assessment of Sleep Environment & Olivier et.al., 2016 & 13 items questionnaire measuring your sleep environment quality & NA\\
-The Pittsburgh Sleep Quality Index (PSQI) & Buysse et al., 1989 & 9 items inventory to measure sleep quality and sleeping pattern & NA\\
-Self-Rating of Biological Rhythm Disorder for Adolescents (SBRDA) & Xie et al., 2021 & 29 Items questionnaire assessing four dimensions of biological rhythm disorder in adolescents & Item 3,22-25 and 29\\
-Photosensitivity Assessment Questionnaire (PAQ) & Wu et al., 2017 & 16 dichotomous (yes/no) items questionnaire to assess "photophobia" and "photophilia" & All itms\\*
+Visual Light Sensitivity Questionnaire-8 & Verriotto et al., 2017 & Eight-question survey to assess the presence and severity of photosensitivity symptoms & None & 5-point Likert scale & Not available\\
+Office Light Survey & Eklundet al., 1996 & 30 items survey to assess electrical lighting environment in office & Item 29 & Mixed response format & Not available\\
+Harvard Light Exposure Assessment Questionnaire & Bajaj et al., 2011 & 1 item semi-quantitative light questionnaire & None & Semi-quantitative & Correlation with physical measuremernt\\
+Hospital Lighting Survey & Dianat et el., 2013 & 23 items questionnaire to assess light environment in a hospital & Item 16,17 & 5-point Likert scale & Face and Content validity\\
+Morningness-Eveningness Questionnaire & Horne et al., 1976 & 19 items questionnaire to understand your body clock & item 1,2,8,13,14 & Mixed response format & Correlation the oral temperature\\
+\addlinespace
+Munich Chronotype Questionnaire (MCTQ) & Roenneberg et al., 2003 & 17 items questionnaire to understand individuals phase of entrainment & Time spect outdoors & Mixed response format & Correlation with sleep-logs, actimetry, and physiological parameters\\
+ Sleep Practices and Attitudes Questionnaire (SPAQ) & Olivier et.al., 2016 & 16 Factor questionnaire measuring practice, behavior and attitude related sleep & Subscale 8\&9 & 5-point Likert scale & Face and Construct validity\\
+The Pittsburgh Sleep Quality Index (PSQI) & Buysse et al., 1989 & 9 items inventory to measure sleep quality and sleeping pattern & item 1-4 & Mixed response format & Correlation  with clinical measurements\\
+Self-Rating of Biological Rhythm Disorder for Disorder for Adolescents (SBRDA) & Xie et al., 2021 & 29 Items questionnaire assessing four dimensions of biological rhythm disorder in adolescents & Item 3,6,22-25 and 29 & 5-point Likert scale & Construct validity\\
+Photosensitivity Assessment Questionnaire (PAQ) & Bossini et al.,2006 & 16 dichotomous (yes/no) items questionnaire to assess "photophobia" and "photophilia" & All items & Binary response option & Not available\\*
 \end{longtable}
@@
 \subsection{Data Availability}\label{data-availability}}
+
+\begin{itemize}
+\tightlist
+\item
+  What data will be available
+\item
+  Where this data will be available
+\item
+  under which licence
+\item
+  who to contact
+\end{itemize}
 
@@
 
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  How the items were generated
-\item
-  How the literature was reviewed to identify construct adequacy of the items.
-\item
-  Discuss the expert panel review process to assess content validity
-\end{enumerate}
+To ensure construct adequacy we thoroughly assessed the current status of literature and identified a variety of light exposure related scales.
+However, no scales specifically measuring the behavioral component of light exposure were found (cf.~Table 1).
+Consequentially we pursued to introduce a new openly available scale to address this research gap.
+For this purpose an expert researcher panel from the fields of chronobiology, light research, neuroscience and psychology (including seven of the authors, see authors roles) generated and collected preliminary item ideas.
+Special attention was paid to design items circumscribed to assess light exposure \emph{behavior} as opposed to subjective measurements of the light environment (cf.(Eklund \& Boyce, 1996) \& (Dianat, Sedghi, Bagherzade, Jafarabadi, \& Stedmon, 2013)) and semi-quantitive assesments of light sources' illuminance (cf.
+(Bajaj, Rosner, Lockley, \& Schernhammer, 2011)) in order to maintain content validity.
+In a collective effort the generated items were then peer-reviewed, amended, unified, and complemented with a suitable response scale (5 point Likert-scale ranging from 1 ``Never/Does not apply/I don't know'' to 5 ``Always'').
+This process was finalized when all experts were in agreement, resulting in 48 items to implement in the first data collection.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-bossini2006sensibilita}{}}%
+Bossini, L., Valdagno, M., Padula, L., De Capua, A., Pacchierotti, C., \& Castrogiovanni, P.
+(2006).
+Sensibilit{à} alla luce e psicopatologia: Validazione del questionario per la valutazione della fotosensibilit{à} (QVF).
+\emph{Med Psicosomatica}, \emph{51}, 167--176.
+
 \leavevmode\vadjust pre{\hypertarget{ref-brownConfirmatoryFactorAnalysis2015}{}}%
@@
 \centering
-\includegraphics{manuscript_files/figure-latex/facIdFigAppB-1.pdf}
-\caption{\label{fig:facIdFigAppB}Factor Identification (A) Parallel analysis
-(B) Scree Plot {[}Unmerged response options{]}}
+\includegraphics{manuscript_files/figure-latex/facIdFigAppB-20-1.pdf}
+\caption{\label{fig:facIdFigAppB-20}Factor Identification (A) Parallel
+analysis (B) Scree Plot {[}Unmerged response options{]}}
 \end{figure}
@@
 \bottomrule
+\end{longtable}
+
+\hypertarget{geographic-locations-of-survey-participants}{%
+\section{Geographic Locations of Survey
+Participants}\label{geographic-locations-of-survey-participants}}
+
+\begin{longtable}[t]{>{\raggedright\arraybackslash}p{10cm}>{\raggedright\arraybackslash}p{2cm}}
+\caption{\label{tab:TzTable-27}Geographical Location}\\
+\toprule
+ & **N = 690**\\
+\midrule
+\endfirsthead
+\caption[]{\label{tab:TzTable-27}Geographical Location \textit{(continued)}}\\
+\toprule
+ & **N = 690**\\
+\midrule
+\endhead
+
+\endfoot
+\bottomrule
+\endlastfoot
+\_\_Time zone - Country\_\_ & \\
+United States - America/New\_York (UTC -04:00) & 63 (9.1\%)\\
+United Kingdom - Europe/London (UTC) & 57 (8.3\%)\\
+Germany - Europe/Berlin (UTC +01:00) & 53 (7.7\%)\\
+India - Asia/Kolkata (UTC +05:30) & 38 (5.5\%)\\
+\addlinespace
+United States - America/Los\_Angeles (UTC -07:00) & 37 (5.4\%)\\
+United States - America/Chicago (UTC -05:00) & 30 (4.3\%)\\
+France - Europe/Paris (UTC +01:00) & 22 (3.2\%)\\
+Switzerland - Europe/Zurich (UTC +01:00) & 21 (3.0\%)\\
+Brazil - America/Sao\_Paulo (UTC -03:00) & 19 (2.8\%)\\
+\addlinespace
+Netherlands - Europe/Amsterdam (UTC +01:00) & 19 (2.8\%)\\
+Canada - America/Toronto (UTC -04:00) & 16 (2.3\%)\\
+Poland - Europe/Warsaw (UTC +01:00) & 15 (2.2\%)\\
+Canada - America/Edmonton (UTC -06:00) & 14 (2.0\%)\\
+Finland - Europe/Helsinki (UTC +02:00) & 9 (1.3\%)\\
+\addlinespace
+Indonesia - Asia/Jakarta (UTC +07:00) & 9 (1.3\%)\\
+Italy - Europe/Rome (UTC +01:00) & 9 (1.3\%)\\
+Chile - America/Santiago (UTC -03:00) & 8 (1.2\%)\\
+Russian Federation - Europe/Moscow (UTC +03:00) & 8 (1.2\%)\\
+China - Asia/Shanghai (UTC +08:00) & 7 (1.0\%)\\
+\addlinespace
+Malaysia - Asia/Kuala\_Lumpur (UTC +08:00) & 7 (1.0\%)\\
+Spain - Europe/Madrid (UTC +01:00) & 7 (1.0\%)\\
+United States - America/Phoenix (UTC -07:00) & 7 (1.0\%)\\
+Canada - America/Vancouver (UTC -07:00) & 6 (0.9\%)\\
+New Zealand - Pacific/Auckland (UTC +13:00) & 6 (0.9\%)\\
+\addlinespace
+Philippines - Asia/Manila (UTC +08:00) & 6 (0.9\%)\\
+Turkey - Europe/Istanbul (UTC +03:00) & 6 (0.9\%)\\
+United States - America/Denver (UTC -06:00) & 6 (0.9\%)\\
+United States - America/Detroit (UTC -04:00) & 6 (0.9\%)\\
+Argentina - America/Argentina/Buenos\_Aires (UTC -03:00) & 5 (0.7\%)\\
+\addlinespace
+Australia - Australia/Melbourne (UTC +11:00) & 5 (0.7\%)\\
+Ireland - Europe/Dublin (UTC) & 5 (0.7\%)\\
+Lithuania - Europe/Vilnius (UTC +02:00) & 5 (0.7\%)\\
+South Africa - Africa/Johannesburg (UTC +02:00) & 5 (0.7\%)\\
+Australia - Australia/Brisbane (UTC +10:00) & 4 (0.6\%)\\
+\addlinespace
+Belgium - Europe/Brussels (UTC +01:00) & 4 (0.6\%)\\
+Israel - Asia/Jerusalem (UTC +02:00) & 4 (0.6\%)\\
+Sweden - Europe/Stockholm (UTC +01:00) & 4 (0.6\%)\\
+United States - America/Boise (UTC -06:00) & 4 (0.6\%)\\
+Czech Republic - Europe/Prague (UTC +01:00) & 3 (0.4\%)\\
+\addlinespace
+Denmark - Europe/Copenhagen (UTC +01:00) & 3 (0.4\%)\\
+Germany - Europe/Busingen (UTC +01:00) & 3 (0.4\%)\\
+Greece - Europe/Athens (UTC +02:00) & 3 (0.4\%)\\
+Iran & 3 (0.4\%)\\
+Japan - Asia/Tokyo (UTC +09:00) & 3 (0.4\%)\\
+\addlinespace
+Norway - Europe/Oslo (UTC +01:00) & 3 (0.4\%)\\
+Romania - Europe/Bucharest (UTC +02:00) & 3 (0.4\%)\\
+Serbia - Europe/Belgrade (UTC +01:00) & 3 (0.4\%)\\
+Slovenia - Europe/Ljubljana (UTC +01:00) & 3 (0.4\%)\\
+Taiwan & 3 (0.4\%)\\
+\addlinespace
+United States - America/Anchorage (UTC -08:00) & 3 (0.4\%)\\
+United States - America/Indiana/Indianapolis (UTC -04:00) & 3 (0.4\%)\\
+United States - America/Kentucky/Louisville (UTC -04:00) & 3 (0.4\%)\\
+Argentina - America/Argentina/Cordoba (UTC -03:00) & 2 (0.3\%)\\
+Australia - Australia/Adelaide (UTC +10:30) & 2 (0.3\%)\\
+\addlinespace
+Australia - Australia/Perth (UTC +08:00) & 2 (0.3\%)\\
+Australia - Australia/Sydney (UTC +11:00) & 2 (0.3\%)\\
+Brazil - America/Araguaina (UTC -03:00) & 2 (0.3\%)\\
+Brazil - America/Bahia (UTC -03:00) & 2 (0.3\%)\\
+Canada - America/Moncton (UTC -03:00) & 2 (0.3\%)\\
+\addlinespace
+Colombia - America/Bogota (UTC -05:00) & 2 (0.3\%)\\
+Costa Rica - America/Costa\_Rica (UTC -06:00) & 2 (0.3\%)\\
+Croatia - Europe/Zagreb (UTC +01:00) & 2 (0.3\%)\\
+Ecuador - America/Guayaquil (UTC -05:00) & 2 (0.3\%)\\
+Estonia - Europe/Tallinn (UTC +02:00) & 2 (0.3\%)\\
+\addlinespace
+Hong Kong - Asia/Hong\_Kong (UTC +08:00) & 2 (0.3\%)\\
+Hungary - Europe/Budapest (UTC +01:00) & 2 (0.3\%)\\
+Jordan - Asia/Amman (UTC +03:00) & 2 (0.3\%)\\
+Latvia - Europe/Riga (UTC +02:00) & 2 (0.3\%)\\
+Malaysia - Asia/Kuching (UTC +08:00) & 2 (0.3\%)\\
+\addlinespace
+Mexico - America/Mexico\_City (UTC -06:00) & 2 (0.3\%)\\
+Nepal - Asia/Kathmandu (UTC +05:45) & 2 (0.3\%)\\
+Portugal - Europe/Lisbon (UTC) & 2 (0.3\%)\\
+Slovakia - Europe/Bratislava (UTC +01:00) & 2 (0.3\%)\\
+Spain - Africa/Ceuta (UTC +01:00) & 2 (0.3\%)\\
+\addlinespace
+Sudan - Africa/Khartoum (UTC +02:00) & 2 (0.3\%)\\
+United States - America/Adak (UTC -09:00) & 2 (0.3\%)\\
+United States - Pacific/Honolulu (UTC -10:00) & 2 (0.3\%)\\
+Viet Nam - Asia/Ho\_Chi\_Minh (UTC +07:00),British - America/Tortola (UTC -04:00) & 2 (0.3\%)\\
+Albania - Europe/Tirane (UTC +01:00) & 1 (0.1\%)\\
+\addlinespace
+Argentina - America/Argentina/Jujuy (UTC -03:00) & 1 (0.1\%)\\
+Australia - Antarctica/Macquarie (UTC +11:00) & 1 (0.1\%)\\
+Australia - Australia/Darwin (UTC +09:30) & 1 (0.1\%)\\
+Austria - Europe/Vienna (UTC +01:00) & 1 (0.1\%)\\
+Bangladesh - Asia/Dhaka (UTC +06:00) & 1 (0.1\%)\\
+\addlinespace
+Brazil - America/Cuiaba (UTC -04:00) & 1 (0.1\%)\\
+Brazil - America/Fortaleza (UTC -03:00) & 1 (0.1\%)\\
+Bulgaria - Europe/Sofia (UTC +02:00) & 1 (0.1\%)\\
+Cameroon - Africa/Douala (UTC +01:00) & 1 (0.1\%)\\
+Canada - America/Blanc-Sablon (UTC -04:00) & 1 (0.1\%)\\
+\addlinespace
+Canada - America/Halifax (UTC -03:00) & 1 (0.1\%)\\
+Canada - America/Resolute (UTC -05:00) & 1 (0.1\%)\\
+Cayman Islands - America/Cayman (UTC -05:00) & 1 (0.1\%)\\
+Chile - Pacific/Easter (UTC -05:00) & 1 (0.1\%)\\
+Cyprus - Asia/Famagusta (UTC +02:00) & 1 (0.1\%)\\
+\addlinespace
+Guatemala - America/Guatemala (UTC -06:00) & 1 (0.1\%)\\
+Korea,Republic of - Asia/Seoul (UTC +09:00) & 1 (0.1\%)\\
+Macedonia & 1 (0.1\%)\\
+Martinique - America/Martinique (UTC -04:00) & 1 (0.1\%)\\
+Mexico - America/Monterrey (UTC -06:00) & 1 (0.1\%)\\
+\addlinespace
+Mongolia - Asia/Ulaanbaatar (UTC +08:00) & 1 (0.1\%)\\
+Myanmar - Asia/Yangon (UTC +06:30) & 1 (0.1\%)\\
+New Zealand - Pacific/Chatham (UTC +13:45) & 1 (0.1\%)\\
+Nigeria - Africa/Lagos (UTC +01:00) & 1 (0.1\%)\\
+Pakistan - Asia/Karachi (UTC +05:00) & 1 (0.1\%)\\
+\addlinespace
+Panama - America/Panama (UTC -05:00) & 1 (0.1\%)\\
+Russian Federation - Asia/Barnaul (UTC +07:00) & 1 (0.1\%)\\
+Russian Federation - Asia/Novosibirsk (UTC +07:00) & 1 (0.1\%)\\
+Russian Federation - Asia/Tomsk (UTC +07:00) & 1 (0.1\%)\\
+Russian Federation - Asia/Vladivostok (UTC +10:00) & 1 (0.1\%)\\
+\addlinespace
+Russian Federation - Asia/Yekaterinburg (UTC +05:00) & 1 (0.1\%)\\
+Saudi Arabia - Asia/Riyadh (UTC +03:00) & 1 (0.1\%)\\
+Singapore - Asia/Singapore (UTC +08:00) & 1 (0.1\%)\\
+Spain - Atlantic/Canary (UTC) & 1 (0.1\%)\\
+Tanzania & 1 (0.1\%)\\
+\addlinespace
+Ukraine - Europe/Kiev (UTC +02:00) & 1 (0.1\%)\\
+United States - America/Indiana/Tell\_City (UTC -05:00) & 1 (0.1\%)\\
+United States - America/North\_Dakota/Center (UTC -05:00) & 1 (0.1\%)\\
+United States - America/North\_Dakota/New\_Salem (UTC -05:00) & 1 (0.1\%)\\
+Aland Islands - Europe/Mariehamn (UTC +02:00) & 0 (0\%)\\
+\addlinespace
+Afghanistan - Asia/Kabul (UTC +04:30) & 0 (0\%)\\
+Algeria - Africa/Algiers (UTC +01:00) & 0 (0\%)\\
+American Samoa - Pacific/Pago\_Pago (UTC -11:00) & 0 (0\%)\\
+Andorra - Europe/Andorra (UTC +01:00) & 0 (0\%)\\
+Angola - Africa/Luanda (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+Anguilla - America/Anguilla (UTC -04:00) & 0 (0\%)\\
+Antarctica - Antarctica/Casey (UTC +11:00) & 0 (0\%)\\
+Antarctica - Antarctica/Davis (UTC +07:00) & 0 (0\%)\\
+Antarctica - Antarctica/DumontDUrville (UTC +10:00) & 0 (0\%)\\
+Antarctica - Antarctica/Mawson (UTC +05:00) & 0 (0\%)\\
+\addlinespace
+Antarctica - Antarctica/McMurdo (UTC +13:00) & 0 (0\%)\\
+Antarctica - Antarctica/Palmer (UTC -03:00) & 0 (0\%)\\
+Antarctica - Antarctica/Rothera (UTC -03:00) & 0 (0\%)\\
+Antarctica - Antarctica/Syowa (UTC +03:00) & 0 (0\%)\\
+Antarctica - Antarctica/Troll (UTC) & 0 (0\%)\\
+\addlinespace
+Antarctica - Antarctica/Vostok (UTC +06:00) & 0 (0\%)\\
+Antigua and Barbuda - America/Antigua (UTC -04:00) & 0 (0\%)\\
+Argentina - America/Argentina/Catamarca (UTC -03:00) & 0 (0\%)\\
+Argentina - America/Argentina/La\_Rioja (UTC -03:00) & 0 (0\%)\\
+Argentina - America/Argentina/Mendoza (UTC -03:00) & 0 (0\%)\\
+\addlinespace
+Argentina - America/Argentina/Rio\_Gallegos (UTC -03:00) & 0 (0\%)\\
+Argentina - America/Argentina/Salta (UTC -03:00) & 0 (0\%)\\
+Argentina - America/Argentina/San\_Juan (UTC -03:00) & 0 (0\%)\\
+Argentina - America/Argentina/San\_Luis (UTC -03:00) & 0 (0\%)\\
+Argentina - America/Argentina/Tucuman (UTC -03:00) & 0 (0\%)\\
+\addlinespace
+Argentina - America/Argentina/Ushuaia (UTC -03:00) & 0 (0\%)\\
+Armenia - Asia/Yerevan (UTC +04:00) & 0 (0\%)\\
+Aruba - America/Aruba (UTC -04:00) & 0 (0\%)\\
+Australia - Australia/Broken\_Hill (UTC +10:30) & 0 (0\%)\\
+Australia - Australia/Currie (UTC +11:00) & 0 (0\%)\\
+\addlinespace
+Australia - Australia/Eucla (UTC +08:45) & 0 (0\%)\\
+Australia - Australia/Hobart (UTC +11:00) & 0 (0\%)\\
+Australia - Australia/Lindeman (UTC +10:00) & 0 (0\%)\\
+Australia - Australia/Lord\_Howe (UTC +11:00) & 0 (0\%)\\
+Azerbaijan - Asia/Baku (UTC +04:00) & 0 (0\%)\\
+\addlinespace
+Bahamas - America/Nassau (UTC -04:00) & 0 (0\%)\\
+Bahrain - Asia/Bahrain (UTC +03:00) & 0 (0\%)\\
+Barbados - America/Barbados (UTC -04:00) & 0 (0\%)\\
+Belarus - Europe/Minsk (UTC +03:00) & 0 (0\%)\\
+Belize - America/Belize (UTC -06:00) & 0 (0\%)\\
+\addlinespace
+Benin - Africa/Porto-Novo (UTC +01:00) & 0 (0\%)\\
+Bermuda - Atlantic/Bermuda (UTC -03:00) & 0 (0\%)\\
+Bhutan - Asia/Thimphu (UTC +06:00),Plurinational State of - America/La\_Paz (UTC -04:00) & 0 (0\%)\\
+Bolivia,Sint Eustatius and Saba - America/Kralendijk (UTC -04:00) & 0 (0\%)\\
+Bonaire & 0 (0\%)\\
+\addlinespace
+Bosnia and Herzegovina - Europe/Sarajevo (UTC +01:00) & 0 (0\%)\\
+Botswana - Africa/Gaborone (UTC +02:00) & 0 (0\%)\\
+Brazil - America/Belem (UTC -03:00) & 0 (0\%)\\
+Brazil - America/Boa\_Vista (UTC -04:00) & 0 (0\%)\\
+Brazil - America/Campo\_Grande (UTC -04:00) & 0 (0\%)\\
+\addlinespace
+Brazil - America/Eirunepe (UTC -05:00) & 0 (0\%)\\
+Brazil - America/Maceio (UTC -03:00) & 0 (0\%)\\
+Brazil - America/Manaus (UTC -04:00) & 0 (0\%)\\
+Brazil - America/Noronha (UTC -02:00) & 0 (0\%)\\
+Brazil - America/Porto\_Velho (UTC -04:00) & 0 (0\%)\\
+\addlinespace
+Brazil - America/Recife (UTC -03:00) & 0 (0\%)\\
+Brazil - America/Rio\_Branco (UTC -05:00) & 0 (0\%)\\
+Brazil - America/Santarem (UTC -03:00) & 0 (0\%)\\
+British Indian Ocean Territory - Indian/Chagos (UTC +06:00) & 0 (0\%)\\
+Brunei Darussalam - Asia/Brunei (UTC +08:00) & 0 (0\%)\\
+\addlinespace
+Burkina Faso - Africa/Ouagadougou (UTC) & 0 (0\%)\\
+Burundi - Africa/Bujumbura (UTC +02:00) & 0 (0\%)\\
+Cambodia - Asia/Phnom\_Penh (UTC +07:00) & 0 (0\%)\\
+Canada - America/Atikokan (UTC -05:00) & 0 (0\%)\\
+Canada - America/Cambridge\_Bay (UTC -06:00) & 0 (0\%)\\
+\addlinespace
+Canada - America/Creston (UTC -07:00) & 0 (0\%)\\
+Canada - America/Dawson (UTC -07:00) & 0 (0\%)\\
+Canada - America/Dawson\_Creek (UTC -07:00) & 0 (0\%)\\
+Canada - America/Fort\_Nelson (UTC -07:00) & 0 (0\%)\\
+Canada - America/Glace\_Bay (UTC -03:00) & 0 (0\%)\\
+\addlinespace
+Canada - America/Goose\_Bay (UTC -03:00) & 0 (0\%)\\
+Canada - America/Inuvik (UTC -06:00) & 0 (0\%)\\
+Canada - America/Iqaluit (UTC -04:00) & 0 (0\%)\\
+Canada - America/Nipigon (UTC -04:00) & 0 (0\%)\\
+Canada - America/Pangnirtung (UTC -04:00) & 0 (0\%)\\
+\addlinespace
+Canada - America/Rainy\_River (UTC -05:00) & 0 (0\%)\\
+Canada - America/Rankin\_Inlet (UTC -05:00) & 0 (0\%)\\
+Canada - America/Regina (UTC -06:00) & 0 (0\%)\\
+Canada - America/St\_Johns (UTC -02:30) & 0 (0\%)\\
+Canada - America/Swift\_Current (UTC -06:00) & 0 (0\%)\\
+\addlinespace
+Canada - America/Thunder\_Bay (UTC -04:00) & 0 (0\%)\\
+Canada - America/Whitehorse (UTC -07:00) & 0 (0\%)\\
+Canada - America/Winnipeg (UTC -05:00) & 0 (0\%)\\
+Canada - America/Yellowknife (UTC -06:00) & 0 (0\%)\\
+Cape Verde - Atlantic/Cape\_Verde (UTC -01:00) & 0 (0\%)\\
+\addlinespace
+Central African Republic - Africa/Bangui (UTC +01:00) & 0 (0\%)\\
+Chad - Africa/Ndjamena (UTC +01:00) & 0 (0\%)\\
+Chile - America/Punta\_Arenas (UTC -03:00) & 0 (0\%)\\
+China - Asia/Urumqi (UTC +06:00) & 0 (0\%)\\
+Christmas Island - Indian/Christmas (UTC +07:00) & 0 (0\%)\\
+\addlinespace
+Cocos (Keeling) Islands - Indian/Cocos (UTC +06:30) & 0 (0\%)\\
+Comoros - Indian/Comoro (UTC +03:00) & 0 (0\%)\\
+Congo - Africa/Brazzaville (UTC +01:00),the Democratic Republic of the - Africa/Kinshasa (UTC +01:00) & 0 (0\%)\\
+Congo,the Democratic Republic of the - Africa/Lubumbashi (UTC +02:00) & 0 (0\%)\\
+Congo & 0 (0\%)\\
+\addlinespace
+Cook Islands - Pacific/Rarotonga (UTC -10:00) & 0 (0\%)\\
+Cuba - America/Havana (UTC -04:00) & 0 (0\%)\\
+Curaçao - America/Curacao (UTC -04:00) & 0 (0\%)\\
+Cyprus - Asia/Nicosia (UTC +02:00) & 0 (0\%)\\
+Côte dIvoire - Africa/Abidjan (UTC) & 0 (0\%)\\
+\addlinespace
+Djibouti - Africa/Djibouti (UTC +03:00) & 0 (0\%)\\
+Dominica - America/Dominica (UTC -04:00) & 0 (0\%)\\
+Dominican Republic - America/Santo\_Domingo (UTC -04:00) & 0 (0\%)\\
+Ecuador - Pacific/Galapagos (UTC -06:00) & 0 (0\%)\\
+Egypt - Africa/Cairo (UTC +02:00) & 0 (0\%)\\
+\addlinespace
+El Salvador - America/El\_Salvador (UTC -06:00) & 0 (0\%)\\
+Equatorial Guinea - Africa/Malabo (UTC +01:00) & 0 (0\%)\\
+Eritrea - Africa/Asmara (UTC +03:00) & 0 (0\%)\\
+Ethiopia - Africa/Addis\_Ababa (UTC +03:00) & 0 (0\%)\\
+Falkland Islands (Malvinas) - Atlantic/Stanley (UTC -03:00) & 0 (0\%)\\
+\addlinespace
+Faroe Islands - Atlantic/Faroe (UTC) & 0 (0\%)\\
+Fiji - Pacific/Fiji (UTC +12:00) & 0 (0\%)\\
+French Guiana - America/Cayenne (UTC -03:00) & 0 (0\%)\\
+French Polynesia - Pacific/Gambier (UTC -09:00) & 0 (0\%)\\
+French Polynesia - Pacific/Marquesas (UTC -09:30) & 0 (0\%)\\
+\addlinespace
+French Polynesia - Pacific/Tahiti (UTC -10:00) & 0 (0\%)\\
+French Southern Territories - Indian/Kerguelen (UTC +05:00) & 0 (0\%)\\
+Gabon - Africa/Libreville (UTC +01:00) & 0 (0\%)\\
+Gambia - Africa/Banjul (UTC) & 0 (0\%)\\
+Georgia - Asia/Tbilisi (UTC +04:00) & 0 (0\%)\\
+\addlinespace
+Ghana - Africa/Accra (UTC) & 0 (0\%)\\
+Gibraltar - Europe/Gibraltar (UTC +01:00) & 0 (0\%)\\
+Greenland - America/Danmarkshavn (UTC) & 0 (0\%)\\
+Greenland - America/Nuuk (UTC -03:00) & 0 (0\%)\\
+Greenland - America/Scoresbysund (UTC -01:00) & 0 (0\%)\\
+\addlinespace
+Greenland - America/Thule (UTC -03:00) & 0 (0\%)\\
+Grenada - America/Grenada (UTC -04:00) & 0 (0\%)\\
+Guadeloupe - America/Guadeloupe (UTC -04:00) & 0 (0\%)\\
+Guam - Pacific/Guam (UTC +10:00) & 0 (0\%)\\
+Guernsey - Europe/Guernsey (UTC) & 0 (0\%)\\
+\addlinespace
+Guinea - Africa/Conakry (UTC) & 0 (0\%)\\
+Guinea-Bissau - Africa/Bissau (UTC) & 0 (0\%)\\
+Guyana - America/Guyana (UTC -04:00) & 0 (0\%)\\
+Haiti - America/Port-au-Prince (UTC -04:00) & 0 (0\%)\\
+Holy See (Vatican City State) - Europe/Vatican (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+Honduras - America/Tegucigalpa (UTC -06:00) & 0 (0\%)\\
+Iceland - Atlantic/Reykjavik (UTC) & 0 (0\%)\\
+Indonesia - Asia/Jayapura (UTC +09:00) & 0 (0\%)\\
+Indonesia - Asia/Makassar (UTC +08:00) & 0 (0\%)\\
+Indonesia - Asia/Pontianak (UTC +07:00),Islamic Republic of - Asia/Tehran (UTC +03:30) & 0 (0\%)\\
+\addlinespace
+Iraq - Asia/Baghdad (UTC +03:00) & 0 (0\%)\\
+Isle of Man - Europe/Isle\_of\_Man (UTC) & 0 (0\%)\\
+Jamaica - America/Jamaica (UTC -05:00) & 0 (0\%)\\
+Jersey - Europe/Jersey (UTC) & 0 (0\%)\\
+Kazakhstan - Asia/Almaty (UTC +06:00) & 0 (0\%)\\
+\addlinespace
+Kazakhstan - Asia/Aqtau (UTC +05:00) & 0 (0\%)\\
+Kazakhstan - Asia/Aqtobe (UTC +05:00) & 0 (0\%)\\
+Kazakhstan - Asia/Atyrau (UTC +05:00) & 0 (0\%)\\
+Kazakhstan - Asia/Oral (UTC +05:00) & 0 (0\%)\\
+Kazakhstan - Asia/Qostanay (UTC +06:00) & 0 (0\%)\\
+\addlinespace
+Kazakhstan - Asia/Qyzylorda (UTC +05:00) & 0 (0\%)\\
+Kenya - Africa/Nairobi (UTC +03:00) & 0 (0\%)\\
+Kiribati - Pacific/Enderbury (UTC +13:00) & 0 (0\%)\\
+Kiribati - Pacific/Kiritimati (UTC +14:00) & 0 (0\%)\\
+Kiribati - Pacific/Tarawa (UTC +12:00),Democratic Peoples Republic of - Asia/Pyongyang (UTC +09:00) & 0 (0\%)\\
+\addlinespace
+Korea & 0 (0\%)\\
+Kuwait - Asia/Kuwait (UTC +03:00) & 0 (0\%)\\
+Kyrgyzstan - Asia/Bishkek (UTC +06:00) & 0 (0\%)\\
+Lao Peoples Democratic Republic - Asia/Vientiane (UTC +07:00) & 0 (0\%)\\
+Lebanon - Asia/Beirut (UTC +02:00) & 0 (0\%)\\
+\addlinespace
+Lesotho - Africa/Maseru (UTC +02:00) & 0 (0\%)\\
+Liberia - Africa/Monrovia (UTC) & 0 (0\%)\\
+Libya - Africa/Tripoli (UTC +02:00) & 0 (0\%)\\
+Liechtenstein - Europe/Vaduz (UTC +01:00) & 0 (0\%)\\
+Luxembourg - Europe/Luxembourg (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+Macao - Asia/Macau (UTC +08:00),the Former Yugoslav Republic of - Europe/Skopje (UTC +01:00) & 0 (0\%)\\
+Madagascar - Indian/Antananarivo (UTC +03:00) & 0 (0\%)\\
+Malawi - Africa/Blantyre (UTC +02:00) & 0 (0\%)\\
+Maldives - Indian/Maldives (UTC +05:00) & 0 (0\%)\\
+Mali - Africa/Bamako (UTC) & 0 (0\%)\\
+\addlinespace
+Malta - Europe/Malta (UTC +01:00) & 0 (0\%)\\
+Marshall Islands - Pacific/Kwajalein (UTC +12:00) & 0 (0\%)\\
+Marshall Islands - Pacific/Majuro (UTC +12:00) & 0 (0\%)\\
+Mauritania - Africa/Nouakchott (UTC) & 0 (0\%)\\
+Mauritius - Indian/Mauritius (UTC +04:00) & 0 (0\%)\\
+\addlinespace
+Mayotte - Indian/Mayotte (UTC +03:00) & 0 (0\%)\\
+Mexico - America/Bahia\_Banderas (UTC -06:00) & 0 (0\%)\\
+Mexico - America/Cancun (UTC -05:00) & 0 (0\%)\\
+Mexico - America/Chihuahua (UTC -07:00) & 0 (0\%)\\
+Mexico - America/Hermosillo (UTC -07:00) & 0 (0\%)\\
+\addlinespace
+Mexico - America/Matamoros (UTC -05:00) & 0 (0\%)\\
+Mexico - America/Mazatlan (UTC -07:00) & 0 (0\%)\\
+Mexico - America/Merida (UTC -06:00) & 0 (0\%)\\
+Mexico - America/Ojinaga (UTC -06:00) & 0 (0\%)\\
+Mexico - America/Tijuana (UTC -07:00),Federated States of - Pacific/Chuuk (UTC +10:00) & 0 (0\%)\\
+\addlinespace
+Micronesia,Federated States of - Pacific/Kosrae (UTC +11:00) & 0 (0\%)\\
+Micronesia,Federated States of - Pacific/Pohnpei (UTC +11:00) & 0 (0\%)\\
+Micronesia,Republic of - Europe/Chisinau (UTC +02:00) & 0 (0\%)\\
+Moldova & 0 (0\%)\\
+Monaco - Europe/Monaco (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+Mongolia - Asia/Choibalsan (UTC +08:00) & 0 (0\%)\\
+Mongolia - Asia/Hovd (UTC +07:00) & 0 (0\%)\\
+Montenegro - Europe/Podgorica (UTC +01:00) & 0 (0\%)\\
+Montserrat - America/Montserrat (UTC -04:00) & 0 (0\%)\\
+Morocco - Africa/Casablanca (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+Mozambique - Africa/Maputo (UTC +02:00) & 0 (0\%)\\
+Namibia - Africa/Windhoek (UTC +02:00) & 0 (0\%)\\
+Nauru - Pacific/Nauru (UTC +12:00) & 0 (0\%)\\
+New Caledonia - Pacific/Noumea (UTC +11:00) & 0 (0\%)\\
+Nicaragua - America/Managua (UTC -06:00) & 0 (0\%)\\
+\addlinespace
+Niger - Africa/Niamey (UTC +01:00) & 0 (0\%)\\
+Niue - Pacific/Niue (UTC -11:00) & 0 (0\%)\\
+Norfolk Island - Pacific/Norfolk (UTC +12:00) & 0 (0\%)\\
+Northern Mariana Islands - Pacific/Saipan (UTC +10:00) & 0 (0\%)\\
+Oman - Asia/Muscat (UTC +04:00) & 0 (0\%)\\
+\addlinespace
+Palau - Pacific/Palau (UTC +09:00),State of - Asia/Gaza (UTC +02:00) & 0 (0\%)\\
+Palestine,State of - Asia/Hebron (UTC +02:00) & 0 (0\%)\\
+Palestine & 0 (0\%)\\
+Papua New Guinea - Pacific/Bougainville (UTC +11:00) & 0 (0\%)\\
+Papua New Guinea - Pacific/Port\_Moresby (UTC +10:00) & 0 (0\%)\\
+\addlinespace
+Paraguay - America/Asuncion (UTC -03:00) & 0 (0\%)\\
+Peru - America/Lima (UTC -05:00) & 0 (0\%)\\
+Pitcairn - Pacific/Pitcairn (UTC -08:00) & 0 (0\%)\\
+Portugal - Atlantic/Azores (UTC -01:00) & 0 (0\%)\\
+Portugal - Atlantic/Madeira (UTC) & 0 (0\%)\\
+\addlinespace
+Puerto Rico - America/Puerto\_Rico (UTC -04:00) & 0 (0\%)\\
+Qatar - Asia/Qatar (UTC +03:00) & 0 (0\%)\\
+Russian Federation - Asia/Anadyr (UTC +12:00) & 0 (0\%)\\
+Russian Federation - Asia/Chita (UTC +09:00) & 0 (0\%)\\
+Russian Federation - Asia/Irkutsk (UTC +08:00) & 0 (0\%)\\
+\addlinespace
+Russian Federation - Asia/Kamchatka (UTC +12:00) & 0 (0\%)\\
+Russian Federation - Asia/Khandyga (UTC +09:00) & 0 (0\%)\\
+Russian Federation - Asia/Krasnoyarsk (UTC +07:00) & 0 (0\%)\\
+Russian Federation - Asia/Magadan (UTC +11:00) & 0 (0\%)\\
+Russian Federation - Asia/Novokuznetsk (UTC +07:00) & 0 (0\%)\\
+\addlinespace
+Russian Federation - Asia/Omsk (UTC +06:00) & 0 (0\%)\\
+Russian Federation - Asia/Sakhalin (UTC +11:00) & 0 (0\%)\\
+Russian Federation - Asia/Srednekolymsk (UTC +11:00) & 0 (0\%)\\
+Russian Federation - Asia/Ust-Nera (UTC +10:00) & 0 (0\%)\\
+Russian Federation - Asia/Yakutsk (UTC +09:00) & 0 (0\%)\\
+\addlinespace
+Russian Federation - Europe/Astrakhan (UTC +04:00) & 0 (0\%)\\
+Russian Federation - Europe/Kaliningrad (UTC +02:00) & 0 (0\%)\\
+Russian Federation - Europe/Kirov (UTC +03:00) & 0 (0\%)\\
+Russian Federation - Europe/Samara (UTC +04:00) & 0 (0\%)\\
+Russian Federation - Europe/Saratov (UTC +04:00) & 0 (0\%)\\
+\addlinespace
+Russian Federation - Europe/Ulyanovsk (UTC +04:00) & 0 (0\%)\\
+Russian Federation - Europe/Volgograd (UTC +04:00) & 0 (0\%)\\
+Rwanda - Africa/Kigali (UTC +02:00) & 0 (0\%)\\
+Réunion - Indian/Reunion (UTC +04:00) & 0 (0\%)\\
+Saint Barthélemy - America/St\_Barthelemy (UTC -04:00),Ascension and Tristan da Cunha - Atlantic/St\_Helena (UTC) & 0 (0\%)\\
+\addlinespace
+Saint Helena & 0 (0\%)\\
+Saint Kitts and Nevis - America/St\_Kitts (UTC -04:00) & 0 (0\%)\\
+Saint Lucia - America/St\_Lucia (UTC -04:00) & 0 (0\%)\\
+Saint Martin (French part) - America/Marigot (UTC -04:00) & 0 (0\%)\\
+Saint Pierre and Miquelon - America/Miquelon (UTC -02:00) & 0 (0\%)\\
+\addlinespace
+Saint Vincent and the Grenadines - America/St\_Vincent (UTC -04:00) & 0 (0\%)\\
+Samoa - Pacific/Apia (UTC +14:00) & 0 (0\%)\\
+San Marino - Europe/San\_Marino (UTC +01:00) & 0 (0\%)\\
+Sao Tome and Principe - Africa/Sao\_Tome (UTC) & 0 (0\%)\\
+Senegal - Africa/Dakar (UTC) & 0 (0\%)\\
+\addlinespace
+Seychelles - Indian/Mahe (UTC +04:00) & 0 (0\%)\\
+Sierra Leone - Africa/Freetown (UTC) & 0 (0\%)\\
+Sint Maarten (Dutch part) - America/Lower\_Princes (UTC -04:00) & 0 (0\%)\\
+Solomon Islands - Pacific/Guadalcanal (UTC +11:00) & 0 (0\%)\\
+Somalia - Africa/Mogadishu (UTC +03:00) & 0 (0\%)\\
+\addlinespace
+South Georgia and the South Sandwich Islands - Atlantic/South\_Georgia (UTC -02:00) & 0 (0\%)\\
+South Sudan - Africa/Juba (UTC +03:00) & 0 (0\%)\\
+Sri Lanka - Asia/Colombo (UTC +05:30) & 0 (0\%)\\
+Suriname - America/Paramaribo (UTC -03:00) & 0 (0\%)\\
+Svalbard and Jan Mayen - Arctic/Longyearbyen (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+Swaziland - Africa/Mbabane (UTC +02:00) & 0 (0\%)\\
+Syrian Arab Republic - Asia/Damascus (UTC +03:00),Province of China - Asia/Taipei (UTC +08:00) & 0 (0\%)\\
+Tajikistan - Asia/Dushanbe (UTC +05:00),United Republic of - Africa/Dar\_es\_Salaam (UTC +03:00) & 0 (0\%)\\
+Thailand - Asia/Bangkok (UTC +07:00) & 0 (0\%)\\
+Timor-Leste - Asia/Dili (UTC +09:00) & 0 (0\%)\\
+\addlinespace
+Togo - Africa/Lome (UTC) & 0 (0\%)\\
+Tokelau - Pacific/Fakaofo (UTC +13:00) & 0 (0\%)\\
+Tonga - Pacific/Tongatapu (UTC +13:00) & 0 (0\%)\\
+Trinidad and Tobago - America/Port\_of\_Spain (UTC -04:00) & 0 (0\%)\\
+Tunisia - Africa/Tunis (UTC +01:00) & 0 (0\%)\\
+\addlinespace
+Turkmenistan - Asia/Ashgabat (UTC +05:00) & 0 (0\%)\\
+Turks and Caicos Islands - America/Grand\_Turk (UTC -04:00) & 0 (0\%)\\
+Tuvalu - Pacific/Funafuti (UTC +12:00) & 0 (0\%)\\
+Uganda - Africa/Kampala (UTC +03:00) & 0 (0\%)\\
+Ukraine - Europe/Simferopol (UTC +03:00) & 0 (0\%)\\
+\addlinespace
+Ukraine - Europe/Uzhgorod (UTC +02:00) & 0 (0\%)\\
+Ukraine - Europe/Zaporozhye (UTC +02:00) & 0 (0\%)\\
+United Arab Emirates - Asia/Dubai (UTC +04:00) & 0 (0\%)\\
+United States - America/Indiana/Knox (UTC -05:00) & 0 (0\%)\\
+United States - America/Indiana/Marengo (UTC -04:00) & 0 (0\%)\\
+\addlinespace
+United States - America/Indiana/Petersburg (UTC -04:00) & 0 (0\%)\\
+United States - America/Indiana/Vevay (UTC -04:00) & 0 (0\%)\\
+United States - America/Indiana/Vincennes (UTC -04:00) & 0 (0\%)\\
+United States - America/Indiana/Winamac (UTC -04:00) & 0 (0\%)\\
+United States - America/Juneau (UTC -08:00) & 0 (0\%)\\
+\addlinespace
+United States - America/Kentucky/Monticello (UTC -04:00) & 0 (0\%)\\
+United States - America/Menominee (UTC -05:00) & 0 (0\%)\\
+United States - America/Metlakatla (UTC -08:00) & 0 (0\%)\\
+United States - America/Nome (UTC -08:00) & 0 (0\%)\\
+United States - America/North\_Dakota/Beulah (UTC -05:00) & 0 (0\%)\\
+\addlinespace
+United States - America/Sitka (UTC -08:00) & 0 (0\%)\\
+United States - America/Yakutat (UTC -08:00) & 0 (0\%)\\
+United States Minor Outlying Islands - Pacific/Midway (UTC -11:00) & 0 (0\%)\\
+United States Minor Outlying Islands - Pacific/Wake (UTC +12:00) & 0 (0\%)\\
+Uruguay - America/Montevideo (UTC -03:00) & 0 (0\%)\\
+\addlinespace
+Uzbekistan - Asia/Samarkand (UTC +05:00) & 0 (0\%)\\
+Uzbekistan - Asia/Tashkent (UTC +05:00) & 0 (0\%)\\
+Vanuatu - Pacific/Efate (UTC +11:00),Bolivarian Republic of - America/Caracas (UTC -04:00) & 0 (0\%)\\
+Venezuela & 0 (0\%)\\
+Virgin Islands,U.S. - America/St\_Thomas (UTC -04:00) & 0 (0\%)\\
+\addlinespace
+Virgin Islands & 0 (0\%)\\
+Wallis and Futuna - Pacific/Wallis (UTC +12:00) & 0 (0\%)\\
+Western Sahara - Africa/El\_Aaiun (UTC +01:00) & 0 (0\%)\\
+Yemen - Asia/Aden (UTC +03:00) & 0 (0\%)\\
+Zambia - Africa/Lusaka (UTC +02:00) & 0 (0\%)\\
+\addlinespace
+Zimbabwe - Africa/Harare (UTC +02:00) & 0 (0\%)\\*
 \end{longtable}

### 2021-11-17 manuscript.Rmd
minor text and table changes

--- 2021-11-17 manuscript.Rmd
@@
     ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
-modify_header(label ~ "**Variable**") %>% modify_caption("Demographics") -> desc_table
+modify_header(label ~ "**Variable**") %>% separate_p_footnotes() %>%
+  modify_caption("Demographic Characteristics") -> desc_table
 
@@
 Participants indicated filling out the online survey from a diverse range of geographic locations.
-The ten most common geographic locations included:
+The ten most common country + timezone combinations included:
 
@@
 
-For a more complete list of geographic locations, see Suppl. Table X in the appendix.
+For a complete list of geographic locations, see Suppl. Table X in the appendix.
 
@@
 The p-values were corrected for multiple testing applying false discovery rate (FDR) via the "add_q" function of the same package.
-After p-value (FDR) correction for multiple testing, none of the demographic variables were significantly different between the EFA sample and the CFA sample (all q-values *q* ≥ `r min(desc_tibble$"**q-value**", na.rm=T)` , indicating equivalence).
+After p-value (FDR) correction for multiple testing, none of the demographic variables were significantly different between the EFA sample and the CFA sample (all q-values *q* ≥ `r min(desc_tibble$"**q-value**", na.rm=T)`.
 
@@
 In a collective effort the generated items were then peer-reviewed,  amended, unified, and complemented with a suitable response scale (5 point Likert-scale ranging from 1 "Never/Does not apply/I don’t know" to 5 "Always").
-This process was finalized when all experts were in agreement, resulting in 48 items to implement in the first data collection.
+This process was finalized when all experts were in agreement, resulting in 48 items to implement in the data collection.
 

### 2021-11-18 manuscript.Rmd
Library Management

@@
 pacman::p_install_gh("jthomasmock/gtExtras")
-pacman::p_install_gh("crsh/papaja","crsh/citr", "masiraji/tabledown")
+pacman::p_install_gh("crsh/papaja")
 pacman::p_install_gh("masiraji/tabledown")
-
+pacman::p_install_gh("crsh/citr")
+
+#if you dont have LaTeX installed run the following line
+#tinytex::install_tinytex()
 ```

### 2021-12-02 manuscript.Rmd
lib management
Spelling

@@
 
-#if you dont have LaTeX installed run the following line
+#if you dont have LaTeX installed run the following lines
+#install.packages("tinytex")
 #tinytex::install_tinytex()
@@
 # HULL
-hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
+EFA.MRFA::hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
         details = TRUE)
@@
 Absolute fit assess the model fit at an absolute level using indices including $\chi^2$ test statistics and the standardized root mean square (SRMR).
-Parsimony fit indices including the root mean square error of approximation (RMSEA) considers the number of free parameters in the model to assess the parsimony of the model.
-Comparative fit indices evaluate the fit of the specified model solution in relation to a more restricted baseline model restricting all covariances among the idicators as zero.
+Parsimony fit indices including the root mean square error of approximation (RMSEA) considers the number of free parameters in the model to assesses the parsimony of the model.
+Comparative fit indices evaluate the fit of the specified model solution in relation to a more restricted baseline model restricting all covariances among the indicators as zero.
 Comparative fit index (CFI) and the Tucker Lewis index (TLI) are such two comparative fit indices.

### 2021-12-06 manuscript.Rmd
*Conclusion
ggcorplot colours updated

@@
 ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
-           ggtheme = ggplot2::theme_minimal, tl.cex = 6,tl.srt = 90 )
+           ggtheme = ggplot2::theme_minimal, tl.cex = 6,tl.srt = 90,colors = c("red", "white", "blue") )
 #p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
@@
 
-The overall we can concluded that IRT analysis indicated short form of LEBA is a psychometrically sound measure.
+Overall we concluded that IRT analysis indicated short form of LEBA is a psychometrically sound measure.
 Item fit indexes and person fit index for all five fitted model were acceptable.

### 2021-12-13 manuscript.Rmd
WrightMap

@@
 #install.packages("pacman")#Run this if you don't have pacman installed.
-pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl)
+pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr)
 pacman::p_install_gh("jthomasmock/gtExtras")
@@
 colnames(sem.data) <- colnam
+```
+
+```{r country, include=FALSE}
+library(stringr)
+country <- data
+
+TZ <- as.data.frame(str_split_fixed(country$slypos_demographics_tz.factor, "-", 2))
+
+num.countries <- unique(TZ$V1)
+num.Timezone <- unique(TZ$V2)
+
+UTC <- as.data.frame(str_split_fixed(TZ$V2, "UTC", 2))
+numUTC <- unique(UTC$V2)
 ```
@@
 
+# Model Parameters ####
+## F1 Model Parameters####
+F1_params <- coef(F1_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
+F1_items.redu <- data.frame(F1_params$items)
+F1l_se <- coef(F1_fit, printSE = TRUE)
+
+## F2 Model Parameters####
+F2_params <- coef(F2_fit.redu, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
+F2_items.redu <- data.frame(F2_params$items)
+F2_se <- coef(F2_fit.redu, printSE = TRUE)
+
+## F3 Model Parameters####
+F3_params <- coef(F3_fit.redu, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
+F3_items.redu <- data.frame(F3_params$items)
+F3_se <- coef(F3_fit.redu, printSE = TRUE)
+
+## F4 Model Parameters####
+F4_params <- coef(F4_fit.redu, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
+F4_items.redu <- data.frame(F4_params$items)
+F4_se <- coef(F4_fit.redu, printSE = TRUE)
+
+## F5 Model Parameters####
+F5_params <- coef(F5_fit.redu, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
+F5_items.redu<- data.frame(F5_params$items)
+F5_se.redu <- coef(F5_fit.redu, printSE = TRUE)
+
 F1.reliability <- plot(F1_fit, type = 'rxx', theta_lim = c(-6, 6), 
@@
 
+```{r}
+library(WrightMap)
+wrightMap(F1.estimation,F1_items.redu[,2])
+wrightMap(F2.estimation,F2_items.redu[,2])
+wrightMap(F3.estimation,F3_items.redu[,2])
+wrightMap(F4.estimation,F3_items.redu[,2])
+wrightMap(F5.estimation,F5_items.redu[,2])
+```
+
 ```{r IRTscoreCor, eval=FALSE, include=FALSE, results='asis'}

### 2021-12-15 manuscript.Rmd
Affiliation and abstract

@@
   - name          : "Juliëtte	van Duijnhoven"
-    affiliation   : "4"
+    affiliation   : "4, 5"
     email         : "j.v.duijnhoven1@tue.nl"
@@
   - name          : "Luc Schlangen"
-    affiliation   : "5"
+    affiliation   : "5, 6"
     email         : "l.j.m.schlangen@tue.nl"
@@
   - name          : "Vineetha Kalavally"
-    affiliation   : "6"
+    affiliation   : "7"
     email         : "vineetha@monash.edu"
@@
   - name          : "Céline Vetter"
-    affiliation   : "7, 8"
+    affiliation   : "8, 9"
     email         : "celine.vetter@colorado.edu"
@@
   - name          : "Gena Glickman"
-    affiliation   : "9"
+    affiliation   : "10"
     email         : "gena.glickman@usuhs.edu"
@@
   - name          : "Karin Smolders"
-    affiliation   : "10"
+    affiliation   : "5,6"
     email         : "k.c.h.j.smolders@tue.nl"
@@
     corresponding : yes
-    affiliation   : "11, 2, 3"
-    email         : "manuel.spitschan@psy.ox.ac.uk"
+    affiliation   : "11, 12, 13"
+    email         : "manuel.spitschan@tum.de "
     role:         
@@
   - id            : "5"
-    institution   : "Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Intelligent Lighting Institute, Eindhoven, Netherlands"
+    institution   : "Eindhoven University of Technology, Intelligent Lighting Institute, Eindhoven, Netherlands"
   - id            : "6"
-    institution   : "Monash University, Department of Electrical and Computer Systems Engineering, Malaysia, Selangor, Malaysia"
+    institution   : "Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Human-Technology Interaction, Eindhoven, Netherlands"
  - id            : "7"
+    institution   : "Monash University, Department of Electrical and Computer Systems Engineering, Selangor, Malaysia"
+  - id            : "8"
     institution   : "University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA"
-  - id            : "8"
-    institution   : "Ximes GmbH, Frankfurt, Germany"
+
   - id            : "9"
+    institution   : "XIMES GmbH, Vienna, Austria"
+  - id            : "10"
     institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
-  - id            : "10"
-    institution   : "Eindhoven University of Technology, Human-Technology Interaction Group, Eindhoven, Netherlands"
   - id            : "11"
-    institution   : "University of Oxford, Department of Experimental Psychology, Oxford, UK"
+    institution   : "Max Planck Institute for Biological Cybernetics, Tübingen, Germany"
+  - id            : "12"
+    institution   : "Technical University of Munich, Department of Sport and Health Sciences (TUM SG), Munich, Germany"
+  - id            : "13"
+    institution   : "University of Oxford, Department of Experimental Psychology, Oxford, United Kingdom"
   - id            : "*"
@@
 abstract: |
-  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
-
-  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
-
-  One sentence clearly stating the **general problem** being addressed by  this particular study.
-
-  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
-
-  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
-
-  One or two sentences to put the results into a more **general context**.
-
-  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
-
-  <!-- https://tinyurl.com/ybremelq -->
-
-keywords          : "keywords"
+  Light exposure is an important driver of health and well-being.
+Many aspects of light exposure are modulated by our behaviour.
+How these light-related behaviours can be shaped to optimise personal light exposure is currently unknown.
+Here, we present a novel, self-reported and psychometrically validated instrument to capture light exposure-related behaviour, the Light Exposure Behavior Assessment (LEBA).
+  An expert panel prepared the initial 48 item pool.
+Responses to these items were then collected in an online survey producing responses from an international sample (690 completed responses, 74 countries, 28 time zones).
+Exploratory factor analysis on an initial subset of our sample (n=428) rendered a five-factor solution with 25 items (Wearing blue light filters, spending time outdoors, using phone and smart-watch in bed, using light before bedtime, using light in the morning and during daytime).
+Confirmatory factor analysis on another subset of participants (n=262) yielded the best fit for the five-factor solution after discarding another two items (CFI=0.97, TLI=0.96, RMSEA=0.05, SRMR=0.09).
+The internal consistency reliability coefficient for the total instrument was McDonald’s omega =0.73.
+Measurement model invariance analysis between native and non-native English speakers showed our model attained the highest level of invariance (residual invariance; CFI=0.95, TLI =0.95, RMSEA=0.05).
+Lastly, a short form of LEBA (n=18) was developed using Item Response Theory on the complete sample (n=690).
+  The psychometric properties of the LEBA instrument indicate the usability to measure the light exposure-related behaviours across a variety of settings and may offer a scalable solution to characterize light exposure-related behaviours in remote samples.
+
+keywords          : "light exposure, light-related behaviours, non-visual effects of light, psychometrics"
 wordcount         : "X"
@@
 #install.packages("pacman")#Run this if you don't have pacman installed.
-pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr)
+pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap)
 pacman::p_install_gh("jthomasmock/gtExtras")
@@
 
-                    A[label = '48 items were generataed by a robust expert panel'] 
+                    A[label = '48 items were generated by a robust expert panel'] 
                     B[label = 'Exploratory Factor Analysis on 48 Items (N = 428)']
@@
                      on the Five Factor Model (23 Items; N=262)
-                      Acceptable Fit ( CFI = .97; TLI .96; RMSEA = .04, SRMR = .09)']
+                      Acceptable Fit ( CFI = .97; TLI= .96; RMSEA = .04, SRMR = .09)']
                      5[label = 'Reliability Analysis on CFA (23 Items; N=262) 
-                      Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52']
+                      Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52
+                      Mcdonald  omega(total) for the total scale = .73']
                     8[label = 'Measurement Invariance Analysis
@@
 #Histogram
-#psych::multi.hist(EFA.data[,sapply(EFA.data, is.numeric)])
+psych::multi.hist(EFA.data[,sapply(EFA.data, is.numeric)])
 
@@
 # Multivariate Normality
-mardia <- psych::mardia(EFA.data, na.rm = T, plot =F)
+mardia <- psych::mardia(EFA.data, na.rm = T, plot =T)
 
@@
   geom_line()+
-    geom_line(data = Random.EV) +
-  geom_line(data = Unadjusted.EV)+
+    #geom_line(data = Random.EV) +
+  #geom_line(data = Unadjusted.EV)+
     #Add the data points.
-  geom_point(size=1)+
-  geom_point(data = Random.EV, size=1)+
-  geom_point(data = Unadjusted.EV, size=1)+
-  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
+  geom_point(size=3)+
+  #geom_point(data = Random.EV, size=3)+
+  #geom_point(data = Unadjusted.EV, size=3)+
+  scale_y_continuous(name="Eigen Value", limits=c(0, 7), breaks=seq(0,7,1)) +
    #Label the x-axis 'Factor Number', and ensure that it ranges from 1-max # of factors, increasing by one with each 'tick' mark.
-  scale_x_continuous(name='Factor Number', limits=c(0, 48),breaks=seq(0,48,4))+
+  scale_x_continuous(name='Factor Number (Parallel Analysis)', limits=c(0, 48),breaks=seq(0,48,4))+
     #Add vertical line indicating parallel analysis suggested max # of factors to retain
-  geom_hline(yintercept=1, linetype = 'dashed') + apatheme
+  geom_hline(yintercept=1, linetype = 'dashed') + apatheme +theme(text = element_text(size = 25),legend.position = "None")
 
@@
    geom_line()+
-  geom_line(data = PA.Scree)+ 
-  geom_point(size=1)+
-  geom_point(data = PA.Scree, size=1)+
+  #geom_line(data = PA.Scree)+ 
+  geom_point(size=3)+
+  #geom_point(data = PA.Scree, size=3)+
   scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
-  scale_x_continuous(name='Factor Number', limits=c(0, 48),breaks=seq(0,48,4))+
-  geom_hline(yintercept=1, linetype = 'dashed') + apatheme 
+  scale_x_continuous(name='Factor Number (Scree Plot)', limits=c(0, 20),breaks=seq(0,20,4))+
+  geom_hline(yintercept=1, linetype = 'dashed') + apatheme +theme(text = element_text(size = 25),legend.position = "None")
+
 ```
@@
 hull <- ggplot2::last_plot()
-Hull <- hull+ ggtitle(NULL) +xlab("Factor Number")+ylab("CAF")+ 
-  apatheme +scale_color_manual(labels = c("Out side the convex Hull", "On the convex Hull"), values = c("red", "cyan2")) 
+Hull <- hull+ ggtitle(NULL) +xlab("Factor Number (Hull Method)")+ylab("CAF")+ 
+  apatheme +scale_color_manual(labels = c("Out side the convex Hull", "On the convex Hull"), values = c("red", "cyan2"))+theme(text = element_text(size = 25))  
 ```
@@
 
+```{r MIdes, include=FALSE}
+
+midata <- CFA.descriptives[,c(1:2,5:7)]
+colnames(midata) <- c("Age", "Gender",  "Native_Speaker", "Work/School", "Mode" )
+mides <- midata%>%
+  tbl_summary(
+    by = Native_Speaker,
+    statistic = list(all_continuous() ~ "{mean} ({sd})",
+                     all_categorical() ~ "{n} ({p}%)"),
+    digits = all_continuous() ~ 2,
+
+    missing = "no"
+    ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
+modify_header(label ~ "**Variable**") %>% separate_p_footnotes() %>%
+  modify_caption("Demographic Characteristics")
+
+as_tibble(mides) -> mides_tibble 
+as_kable_extra(mides, format = "latex",booktabs = T) -> mides_kable #save it as a knitr::kable
+
+```
+
 ```{r Invariancedetail, include=FALSE}
@@
 Item discrimination parameters of our tool fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$).
-Examination of the item information curve \@ref(fig:itmeinfo) indicated 6 items (1, 25, 9, 38, 30, & 41) had relatively flat information curves thus discarded creating a short form of LEBA with 5 factors and 17 items.
+Examination of the item information curve \@ref(fig:itmeinfo) indicated 5 items (1, 25,  38, 30, & 41) had relatively flat information curves (I($\theta$) <.20) thus discarded creating a short form of LEBA with 5 factors and 18 items.
 
@@
 ## F1 Plots ####
-F1_OCC <- plot(F1_fit, type = "trace", facet =T, main = "Blue Filter OCC")
-F1_info <- plot(F1_fit, type = "infoSE", main = "F1")
+F1_OCC <- plot(F1_fit, type = "trace", facet =T, main = "F1: Wearing blue light filters OCC")
+F1_info <- plot(F1_fit, type = "infoSE", main = "F1: Wearing blue light filters")
 F1_iteminfo <- plot(F1_fit, type = "infotrace", 
-                    facet_items = T, main = "F1")
+                    facet_items = T, main = "F1: Wearing blue light filters")
 
 ## F2 Plots ####
-F2_OCC <- plot(F2_fit, type = "trace", facet =T, main = "Natural Light OCC")
-F2_info <- plot(F2_fit, type = "infoSE", main = "F2")
-F2_iteminfo <- plot(F2_fit, type = "infotrace", facet_items = T, main = "F2")
+F2_OCC <- plot(F2_fit, type = "trace", facet =T, main = "F2: Spending time outdoors OCC")
+F2_info <- plot(F2_fit, type = "infoSE", main = "F2: Spending time outdoors")
+F2_iteminfo <- plot(F2_fit, type = "infotrace", facet_items = T, main = "F2: Spending time outdoors")
 
 ## F3 Plots ####
-F3_OCC <-plot(F3_fit, type = "trace", facet =T, main = "Smart Device OCC")
-F3_info <- plot(F3_fit, type = "infoSE", main = "F3")
+F3_OCC <-plot(F3_fit, type = "trace", facet =T, main = "F3: Using phone and smart-watch in bed OCC")
+F3_info <- plot(F3_fit, type = "infoSE", main = "F3: Using phone and smart-watch in bed")
 F3_iteminfo <- plot(F3_fit, type = "infotrace", 
-                    facet_items = T, main = "F3")
+                    facet_items = T, main = "F3: Using phone and smart-watch in bed")
 
 ## F4 Plots ####
-F4_OCC <-plot(F4_fit, type = "trace", facet =T, main = "Sleep Environment OCC")
-F4_info <- plot(F4_fit, type = "infoSE", main = "F4")
-F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = "F4",cex = .8)
+F4_OCC <-plot(F4_fit, type = "trace", facet =T, main = "F4: Using light before bedtime OCC")
+F4_info <- plot(F4_fit, type = "infoSE", main = "F4: Using light before bedtime")
+F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = "F4: Using light before bedtime",cex = .8)
 
 ## F5 Plots ####
-F5_OCC <-plot(F5_fit, type = "trace", facet =T, main = "Electric Light OCC")
-F5_info <- plot(F5_fit, type = "infoSE", main = "F5")
-F5_iteminfo <- plot(F5_fit, type = "infotrace", facet_items = T,main = "F5")
+F5_OCC <-plot(F5_fit, type = "trace", facet =T, main = "F5: Using light in the morning and during daytime OCC")
+F5_info <- plot(F5_fit, type = "infoSE", main = "F5: Using light in the morning and during daytime")
+F5_iteminfo <- plot(F5_fit, type = "infotrace", facet_items = T,main = "F5: Using light in the morning and during daytime")
 
@@
 
-```{r saveiteminfo, include=F}
+```{r saveiteminfo, include=FALSE}
 jpeg("Manuscript.figures/iteminfo.png", width = 800, height = 750)
@@
 
-```{r IRTreliability, include=F}
+```{r IRTreliability, include=FALSE}
 #conditional reliability
@@
 F2.redu <- sem.data %>% 
-  dplyr::select(item11,  item10 , item12, item7, Ritem8)
+  dplyr::select(item11,  item10 , item12, item7, Ritem8, item9)
 F3.redu <- sem.data %>% 
@@
 
-F5_fit.redu <- mirt(F5, model = 1, itemtype = 'graded', SE = TRUE,
+F5_fit.redu <- mirt(F5.redu, model = 1, itemtype = 'graded', SE = TRUE,
                Se.type = 'MHRM',technical = list(NCYCLES = 10000))
@@
 F1.person <- ggplot(F1.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5)+geom_vline(xintercept = -2)+
-  labs( y="Number of Participants", x = "Zh Statistics")+apatheme
+  labs( y="Number of Participants", x = "Zh Statistics: F1")+apatheme
 
@@
   scale_x_continuous(limits = c(-5, 1))+geom_vline(xintercept = -2)+
-  labs( y="Number of Participants", x = "Zh Statistics")+apatheme
+  labs( y="Number of Participants", x = "Zh Statistics: F2")+apatheme
 
@@
 F3.person <- ggplot(F3.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5)+geom_vline(xintercept = -2)+
-  labs( y="Number of Participants", x = "Zh Statistics")+apatheme
+  labs( y="Number of Participants", x = "Zh Statistics: F3")+apatheme
 
@@
 F4.person <- ggplot(F4.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5)+geom_vline(xintercept = -2)+
-  labs( y="Number of Participants", x = "Zh Statistics")+apatheme
+  labs( y="Number of Participants", x = "Zh Statistics: F4")+apatheme
 
@@
 F5.person <- ggplot(F5.personfit, aes(x=Zh)) + geom_histogram(binwidth=.4)+geom_vline(xintercept = -2)+
-  labs( y="Number of Participants", x = "Zh Statistics")+apatheme
+  labs( y="Number of Participants", x = "Zh Statistics:F5")+apatheme
 
@@
 
-F1_test.info <- plot(F1_fit, type = "infoSE", main = "F1")
-
-F2_test.info.redu <- plot(F2_fit.redu, type = "infoSE", main = "F2")
-
-F3_test.info.redu <- plot(F3_fit.redu, type = "infoSE", main = "F3")
-
-F4_test.info.redu <- plot(F4_fit.redu, type = "infoSE", main = "F4")
-
-F5_test.info <- plot(F5_fit.redu, type = "infoSE", main = "F5")
+F1_test.info <- plot(F1_fit, type = "infoSE", main = "F1: Wearing blue light filters")
+
+F2_test.info.redu <- plot(F2_fit.redu, type = "infoSE", main = "F2: Spending time outdoors")
+
+F3_test.info.redu <- plot(F3_fit.redu, type = "infoSE", main = "F3: Using phone and smart-watch in bed")
+
+F4_test.info.redu <- plot(F4_fit.redu, type = "infoSE", main = "F4: Using light before bedtime")
+
+F5_test.info <- plot(F5_fit.redu, type = "infoSE", main = "F5: Using light in the morning and during daytime")
 
@@
 
-```{r savetestinfo, include=F, warning=F, message=F}
+```{r savetestinfo, include=FALSE, warning=F, message=F}
 jpeg("Manuscript.figures/testinfo.png", width = 800, height = 750)
@@
   rowwise() %>% 
-  mutate(F2.Total = sum(item11,  item10 , item12, item7, Ritem8))
+  mutate(F2.Total = sum(item11,  item10 , item12, item7, Ritem8, item9))
 
@@
 
-```{r}
+```{r, warning=F, include=FALSE}
 library(WrightMap)
-wrightMap(F1.estimation,F1_items.redu[,2])
-wrightMap(F2.estimation,F2_items.redu[,2])
-wrightMap(F3.estimation,F3_items.redu[,2])
-wrightMap(F4.estimation,F3_items.redu[,2])
-wrightMap(F5.estimation,F5_items.redu[,2])
+library(RColorBrewer)
+F1.e <- as.data.frame(F1.estimation)
+F2.e <- as.data.frame(F2.estimation)
+F3.e <- as.data.frame(F3.estimation)
+F4.e <- as.data.frame(F4.estimation)
+F5.e <- as.data.frame(F5.estimation)
+
+estimation <- as.data.frame(cbind(F1.e,F2.e,F3.e,F4.e,F5.e))
+
+threshold <- rbind(F1_items.redu[,2:5],
+                   F2_items.redu[,2:5],
+                   F3_items.redu[,2:5],
+                   F4_items.redu[,2:5],
+                   F5_items.redu[,2:5])
+
+itemlevelcolors <- matrix(rep(brewer.pal(4, "Set1"), 18), byrow = TRUE, ncol = 4)
+
+```
+
+```{r WP, fig.cap="Person Item Map (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
+library(WrightMap)
+wrightMap(estimation, threshold, 
+          item.prop = 0.65,
+
+          main.title = "LEBA",
+          dim.names = c("F1", "F2", "F3", "F4", "F5"),
+          thr.sym.col.fg = itemlevelcolors,
+          thr.sym.col.bg = itemlevelcolors,
+          vertLines = TRUE,
+          show.thr.lab = T,
+          dim.color = brewer.pal(5, "Set3"))
+
 ```

### 2021-12-15 appendix-1.Rmd
Cross references are checked

--- 2021-11-17 Supplymentary.Rmd
@@
----
-title             : "Supplementary"
-shorttitle        : "SA"
-
-author: 
-  - name          : "Mushfiqul Anwar Siraji"
-    affiliation   : "1, *"
-    email         : "mushfiqul.anwarsiraji@monash.edu"
-    role:         
-      - Formal Analysis
-      - Visualization
-      - Writing – original draft
-      - Writing – review & editing;
-
-  - name          : "Rafael Robert Lazar"
-    affiliation   : "2, 3, *"
-    role:
-      - Data curation
-      - Investigation
-      - Project administration
-      - Visualization
-      - Writing – original draft
-      - Writing – review & editing;
-
-  - name          : "Juliëtte	van Duijnhoven"
-    affiliation   : "4"
-    email         : "j.v.duijnhoven1@tue.nl"
-    role:         
-      - Conceptualization
-      - Methodology
-      - Investigation
-      - Writing – review & editing
-
-  - name          : "Luc Schlangen"
-    affiliation   : "5"
-    email         : "l.j.m.schlangen@tue.nl"
-    role:         
-      - Conceptualization
-      - Methodology
-      - Investigation
-      - Writing – review & editing
-
-  - name          : "Shamsul Haque"
-    affiliation   : "1"
-    email         : "shamsul@monash.edu"
-    role:         
-      - Conceptualization
-      - Supervision
-      - Writing – review & editing
-
-  - name          : "Vineetha Kalavally"
-    affiliation   : "6"
-    email         : "vineetha@monash.edu"
-    role:         
-      - Supervision
-      - Writing – review & editing
-
-  - name          : "Céline Vetter"
-    affiliation   : "7, 8"
-    email         : "celine.vetter@colorado.edu"
-    role:         
-      - Conceptualization
-      - Writing – review & editing
-
-  - name          : "Gena Glickman"
-    affiliation   : "9"
-    email         : "gena.glickman@usuhs.edu"
-    role:         
-      - Conceptualization
-      - Methodology
-      - Writing – review & editing
-
-  - name          : "Karin Smolders"
-    affiliation   : "10"
-    email         : "k.c.h.j.smolders@tue.nl"
-    role:         
-      - Conceptualization
-      - Methodology
-      - Writing – review & editing
-
-  - name          : "Manuel Spitschan"
-    corresponding : yes
-    affiliation   : "11, 2, 3"
-    email         : "manuel.spitschan@psy.ox.ac.uk"
-    role:         
-      - Conceptualization
-      - Data curation
-      - Investigation
-      - Project administration
-      - Visualization
-      - Methodology
-      - Writing – original draft
-      - Writing – review & editing
-
-affiliation:
-  - id            : "1"
-    institution   : "Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
-  - id            : "2"
-    institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"
-  - id            : "3"
-    institution   : "University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland"
-  - id            : "4"
-    institution   : "Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands"
-  - id            : "5"
-    institution   : "Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Intelligent Lighting Institute, Eindhoven, Netherlands"
-  - id            : "6"
-    institution   : "Monash University, Department of Electrical and Computer Systems Engineering, Malaysia, Selangor, Malaysia"
-  - id            : "7"
-    institution   : "University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA"
-  - id            : "8"
-    institution   : "Ximes GmbH, Frankfurt, Germany"
-  - id            : "9"
-    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
-  - id            : "10"
-    institution   : "Eindhoven University of Technology, Human-Technology Interaction Group, Eindhoven, Netherlands"
-  - id            : "11"
-    institution   : "University of Oxford, Department of Experimental Psychology, Oxford, UK"
-  - id            : "*"
-    institution   : "Joint first author"
-
-bibliography      : ["references.bib"]
-
-floatsintext      : no
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
-documentclass     : "apa6"
-classoption       : "man"
-output            : 
-  papaja::apa6_pdf:
-    latex_engine: xelatex
-    includes:
-      in_header: header.tex
-
-mainfont: Arial
----
-
-```{r options, warning=FALSE, include=FALSE}
+```{r options-appendix, warning=FALSE, include=FALSE}
 knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600)
@@
 
-# SA: Confirming the five factor solution obtained using minimum residual extraction method
+```{r F1IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/F1testinfo.png')
+```
+
+```{r F2IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/F2testinfo.png')
+```
+
+```{r F3IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/F3testinfo.png')
+```
+
+```{r F4IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/F4testinfo.png')
+```
+
+```{r F5IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/F5testinfo.png')
+```
+
+# Confirming the five factor solution obtained using minimum residual extraction method
 
@@
 
-# SA: Factor analysis with six factors
+# Factor analysis with six factors
 
@@
 
-# SA: Factor Analysis with Unmerged Response Option
+# Factor Analysis with Unmerged Response Option
 
@@
 However only `r apa(cor.per.1, 2,T)`% of the inter-item correlation coefficients were greater than .30.
-The absolute value of inter-item correlation ranged between `r min.cor.1` to `r max.cor.1`.Figure \@ref(fig:figCorAppB) depicts the correlation matrix.
+The absolute value of inter-item correlation ranged between `r min.cor.1` to `r max.cor.1`.Figure \@ref(fig:corunm) depicts the correlation matrix.
 For un-merged response option Horn's parallel analysis with 500 iterations indicated a five-factor solution.
@@
 Thus we reject the six factor solution.
-The five factor solution retained 24 items (Table \@ref(tab:EFATableAppB)).
+The five factor solution retained 24 items (Table \@ref(tab:efaunmerged)).
 However the factors are less interpretable in terms of common theme.
@@
 
-```{r figCorAppB, fig.cap="Correlation plot of the items [Unmerged response options]", include=FALSE, out.width="100%"}
+```{r corunm, fig.cap="Correlation plot of the items [Unmerged response options]",  out.width="100%"}
 
@@
 
-```{r EFATableAppB, results='asis'}
+```{r efaunmerged, results='asis'}
 apa_table(efa.table, caption = "Factor loadings and communality of the retained items in five factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T)
@@
 # Geographic Locations of Survey Participants
-```{r TzTable, include=FALSE, warning=F,message=FALSE}
+```{r Timezone-tab, include=FALSE, warning=F,message=FALSE}
 descriptives.data%>%
@@
 
-```{r tzTabPrint, results='asis'}
+```{r tztabprint, results='asis'}
 

### 2021-12-15 manuscript.Rmd
Cross references are checked

@@
 authornote: |
-  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
-
-  Enter author note here.
+  This research is supported by funding from the Welcome Trust (204686/Z/16/Z), the European Training Network LIGHTCAP (project number 860613) under the Marie Skłodowska-Curie actions framework H2020-MSCA-ITN-2019, the BioClock project (number 1292.19.077) of the research program Dutch Research Agenda: Onderzoek op Routes door Consortia (NWA-ORC) which is (partly) financed by the Dutch Research Council (NWO), and the European Union and the nationals contributing in the context of the ECSEL Joint Undertaking programme (2021-2024) under the grant #101007319.
 
@@
 appendix:
-  - "Supplymentary.Rmd"
-  - "instrument.Rmd"
+  - "appendix-1.Rmd"
+  - "appendix-2.Rmd"
 mainfont: Arial
@@
 knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=1200)
-options(knitr.duplicate.label = "allow")
+#options(knitr.duplicate.label = "allow")
 set.seed(123)
@@
 
-```{r scalePrint, results='asis'}
+```{r scale-print, results='asis'}
 relevant.scale.data %>%
@@
 Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA.
-We also conducted psychometric analysis on non-merged response options data (Supp. Table \@ref(tab:EFATableAppB)) and rejected the latent structure obtained as the factors were less interpretable.
+We also conducted psychometric analysis on non-merged response options data (Supp. Table \@ref(tab:efaunmerged)) and rejected the latent structure obtained as the factors were less interpretable.
 
@@
     #Add the data points.
-  geom_point(size=3)+
+  geom_point(size=1)+
   #geom_point(data = Random.EV, size=3)+
@@
     #Add vertical line indicating parallel analysis suggested max # of factors to retain
-  geom_hline(yintercept=1, linetype = 'dashed') + apatheme +theme(text = element_text(size = 25),legend.position = "None")
+  geom_hline(yintercept=1, linetype = 'dashed') + apatheme +theme(,legend.position = "None") 
+#text = element_text(size = 25)
 
@@
   #geom_line(data = PA.Scree)+ 
-  geom_point(size=3)+
+  geom_point(size=1)+
   #geom_point(data = PA.Scree, size=3)+
@@
   scale_x_continuous(name='Factor Number (Scree Plot)', limits=c(0, 20),breaks=seq(0,20,4))+
-  geom_hline(yintercept=1, linetype = 'dashed') + apatheme +theme(text = element_text(size = 25),legend.position = "None")
+  geom_hline(yintercept=1, linetype = 'dashed') + apatheme +theme(legend.position = "None") 
+#text = element_text(size = 25
 
@@
 Hull <- hull+ ggtitle(NULL) +xlab("Factor Number (Hull Method)")+ylab("CAF")+ 
-  apatheme +scale_color_manual(labels = c("Out side the convex Hull", "On the convex Hull"), values = c("red", "cyan2"))+theme(text = element_text(size = 25))  
+  apatheme +scale_color_manual(labels = c("Out side the convex Hull", "On the convex Hull"), values = c("red", "cyan2"))+theme(legend.position = "None") 
 ```
@@
 
-```{r facIdFig, out.height="250%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}
+```{r facIdFig, out.height="350%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}
 cowplot::plot_grid(parallel, scree.plot,Hull, labels = "AUTO",ncol=1, label_size = 8,align = "v")
@@
 Item discrimination parameters of our tool fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$).
-Examination of the item information curve \@ref(fig:itmeinfo) indicated 5 items (1, 25,  38, 30, & 41) had relatively flat information curves (I($\theta$) <.20) thus discarded creating a short form of LEBA with 5 factors and 18 items.
+Examination of the item information curve (Sup.fig \@ref(fig:F2IF)-\@ref(fig:F5IF)) indicated 5 items (1, 25,  38, 30, & 41) had relatively flat information curves (I($\theta$) <.20) thus discarded creating a short form of LEBA with 5 factors and 18 items.
 
@@
 
-```{r saveiteminfo, include=FALSE}
+```{r saveiteminfo, eval=FALSE, include=FALSE}
 jpeg("Manuscript.figures/iteminfo.png", width = 800, height = 750)
@@
 
+```{r iteminfo, include=F, warning=F}
+F1_item1<- plot(F1_fit, type = "infotrace", 
+                    facet_items = T, which.items = 1, main = "")
+
+F1_item2 <- plot(F1_fit, type = "infotrace", 
+     facet_items = T, which.items = 2,main = "")
+
+F1_item3 <- plot(F1_fit, type = "infotrace", 
+     facet_items = T, which.items = 3,main = "")
+
+F2_item1 <- plot(F2_fit, type = "infotrace", facet_items = T, which.items = 1,main = "")
+F2_item2 <- plot(F2_fit, type = "infotrace", facet_items = T, which.items = 2,main = "")
+F2_item3 <- plot(F2_fit, type = "infotrace", facet_items = T, which.items = 3,main = "")
+F2_item4 <- plot(F2_fit, type = "infotrace", facet_items = T, which.items = 4,main = "")
+F2_item5 <- plot(F2_fit, type = "infotrace", facet_items = T, which.items = 5,main = "")
+F2_item6 <- plot(F2_fit, type = "infotrace", facet_items = T, which.items = 6,main = "")
+
+F3_item1 <- plot(F3_fit, type = "infotrace", 
+                    facet_items = T, which.items = 1,main = "")
+F3_item2 <- plot(F3_fit, type = "infotrace", 
+                    facet_items = T, which.items = 2,main = "")
+
+F3_item3 <- plot(F3_fit, type = "infotrace", 
+                    facet_items = T, which.items = 3,main = "")
+F3_item4 <- plot(F3_fit, type = "infotrace", 
+                    facet_items = T, which.items = 4,main = "")
+F3_item5 <- plot(F3_fit, type = "infotrace", 
+                    facet_items = T, which.items = 5,main = "")
+
+F4_item1 <- plot(F4_fit, type = "infotrace", facet_items = T,which.items = 1,main = "")
+F4_item2 <- plot(F4_fit, type = "infotrace", facet_items = T,which.items = 2,main = "")
+F4_item3 <- plot(F4_fit, type = "infotrace", facet_items = T,which.items = 3,main = "")
+F4_item4 <- plot(F4_fit, type = "infotrace", facet_items = T,which.items = 4,main = "")
+
+F5_item1 <- plot(F5_fit, type = "infotrace", facet_items = T,which.items = 1,main = "")
+F5_item2 <-plot(F5_fit, type = "infotrace", facet_items = T,which.items = 2,main = "")
+F5_item3 <-plot(F5_fit, type = "infotrace", facet_items = T,which.items = 3,main = "")
+F5_item4 <-plot(F5_fit, type = "infotrace", facet_items = T,which.items = 4,main = "")
+F5_item5 <-plot(F5_fit, type = "infotrace", facet_items = T,which.items = 5,main = "")
+
+F1title <- ggdraw() + 
+  draw_label(
+    "F1: Wearing blue light filters",
+    fontface = 'bold',
+    x = 0,
+    hjust = 0
+  ) +
+  theme(
+    # add margin on the left of the drawing canvas,
+    # so title is aligned with left edge of first plot
+    plot.margin = margin(0, 0, 0, 7)
+  )
+
+F2title <- ggdraw() + 
+  draw_label(
+    "F2: Spending time outdoors",
+    fontface = 'bold',
+    x = 0,
+    hjust = 0
+  ) +
+  theme(
+    # add margin on the left of the drawing canvas,
+    # so title is aligned with left edge of first plot
+    plot.margin = margin(0, 0, 0, 7)
+  )
+
+F3title <- ggdraw() + 
+  draw_label(
+    "F3: Using phone and smart-watch in bed",
+    fontface = 'bold',
+    x = 0,
+    hjust = 0
+  ) +
+  theme(
+    # add margin on the left of the drawing canvas,
+    # so title is aligned with left edge of first plot
+    plot.margin = margin(0, 0, 0, 7)
+  )
+
+F4title <- ggdraw() + 
+  draw_label(
+    "F4: Using light before bedtime",
+    fontface = 'bold',
+    x = 0,
+    hjust = 0
+  ) +
+  theme(
+    # add margin on the left of the drawing canvas,
+    # so title is aligned with left edge of first plot
+    plot.margin = margin(0, 0, 0, 7)
+  )
+
+F5title <- ggdraw() + 
+  draw_label(
+    "F5: Using light...daytime",
+    fontface = 'bold',
+    x = 0,
+    hjust = 0
+  ) +
+  theme(
+    # add margin on the left of the drawing canvas,
+    # so title is aligned with left edge of first plot
+    plot.margin = margin(0, 0, 0, 7)
+  )
+
+f1itemplot <- plot_grid(F1_item1, F1_item2,F1_item3,
+          labels = "AUTO", label_size = 10,align = "v")
+f2itemplot <- plot_grid(F2_item1, F2_item2,F2_item3,F2_item4,F2_item5,F2_item6,
+           label_size = 10,align = "v")
+f3itemplot <- plot_grid(F3_item1, F3_item2,F3_item3,F3_item4,F3_item5,
+           label_size = 10,align = "v")
+f4itemplot <- plot_grid(F4_item1, F4_item2,F4_item3,F4_item4,
+          labels = "AUTO", label_size = 10,align = "v")
+
+f5itemplot <- plot_grid(F5_item1, F5_item2,F5_item3,F5_item4,F5_item5,
+          label_size = 10,align = "v")
+```
+
+```{r f1itminf, include=F, warning=F}
+
+jpeg("Manuscript.figures/F1testinfo.png", width = 800, height = 750)
+
+plot_grid(
+  F1title, f1itemplot,
+  ncol = 1,
+  # rel_heights values control vertical title margins
+  rel_heights = c(0.1, 1)
+
+)
+dev.off()
+```
+
+```{r f2iteminf, include=F, warning=F}
+jpeg("Manuscript.figures/F2testinfo.png", width = 800, height = 750)
+plot_grid(
+  F2title, f2itemplot,
+  ncol = 1,
+  # rel_heights values control vertical title margins
+  rel_heights = c(0.1, 1)
+)
+dev.off()
+```
+
+```{r f3iteminf, include=F, warning=F}
+jpeg("Manuscript.figures/F3testinfo.png", width = 800, height = 750)
+plot_grid(
+  F3title, f3itemplot,
+  ncol = 1,
+  # rel_heights values control vertical title margins
+  rel_heights = c(0.1, 1)
+)
+dev.off()
+```
+
+```{r f4iteminf, include=F, warning=F}
+jpeg("Manuscript.figures/F4testinfo.png", width = 800, height = 750)
+plot_grid(
+  F4title, f4itemplot,
+  ncol = 1,
+  # rel_heights values control vertical title margins
+  rel_heights = c(0.1, 1)
+)
+dev.off()
+```
+
+```{r f5iteminf, include=F, warning=F}
+jpeg("Manuscript.figures/F5testinfo.png", width = 800, height = 750)
+plot_grid(
+  F5title, f5itemplot,
+  ncol = 1,
+  # rel_heights values control vertical title margins
+  rel_heights = c(0.1, 1)
+)
+dev.off()
+```
+
 ```{r IRTparameters, results='asis'}
@@
 
-```{r itmeinfo, fig.cap="Item information curves (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="60%"}
+```{r itmeinfo, eval=FALSE, fig.cap="Item information curves (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, include=FALSE, out.height="60%", out.width="100%"}
 knitr::include_graphics('Manuscript.figures/iteminfo.png')
@@
 
-```{r, warning=F, include=FALSE}
-library(WrightMap)
+```{r WPdata, warning=F, include=FALSE}
+
 library(RColorBrewer)
@@
 
-```{r WP, fig.cap="Person Item Map (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
-library(WrightMap)
-wrightMap(estimation, threshold, 
+```{r saveWrightmao, include=FALSE, warning=F, message=F}
+jpeg("Manuscript.figures/wm.png", width = 800, height = 750)
+WrightMap::wrightMap(estimation, threshold, 
           item.prop = 0.65,
@@
           dim.color = brewer.pal(5, "Set3"))
-
+dev.off()
+```
+
+```{r WP, fig.cap="Person Item Map", warning=FALSE, out.width="100%", out.height="120%"}
+
+knitr::include_graphics('Manuscript.figures/wm.png')
 ```
@@
 ```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('Supplymentary.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('instrument.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('Supplymentary.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('instrument.Rmd')
-```

### 2022-01-02 manuscript.Rmd
Discussion

@@
 # Methods
-
 ## Ethical approval
@@
 
-- What data will be available 
-- Where this data will be available 
-- under which licence
-- who to contact
+All code and data underlying this article is available on a public GitHub repository (https://github.com/leba-instrument/leba-manuscript).
 
@@
 The p-values were corrected for multiple testing applying false discovery rate (FDR) via the "add_q" function of the same package.
-After p-value (FDR) correction for multiple testing, none of the demographic variables were significantly different between the EFA sample and the CFA sample (all q-values *q* ≥ `r min(desc_tibble$"**q-value**", na.rm=T)`.
+After p-value (FDR) correction for multiple testing, none of the demographic variables were significantly different between the EFA sample and the CFA sample (all q-values *q* $\ge$ `r min(desc_tibble$"**q-value**", na.rm=T)`).
 
@@
 ## Item Analysis
+
 ```{r ItemAnalysis, include=FALSE}
@@
 ## Exploratory Factor Analysis
-
 ```{r CorrMatrix, include=FALSE}
@@
 F5.alpha <- Five.F5.alpha$total$raw_alpha
+
+alpha.tab <- rbind(F1.alpha,F2.alpha,F3.alpha,F4.alpha,F5.alpha )
+
 ```
@@
 ```
+
 We conducted categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator since our response data was of ordinary nature [@desjardinsHandbookEducationalMeasurement2018].
@@
 
+```{r textanalysis}
+
+devtools::install_github("unDocUMeantIt/koRpus")
+library(koRpus)# stable release
+koRpus::install.koRpus.lang(lang=c("en"))
+library(koRpus)
+library(koRpus.lang.en)
+
+ques <- tokenize("Table_raw/items.txt", 
+                 format = "file",
+                 fileEncoding = NULL,
+                 split = "[[:space:]]",
+                 ign.comp = "-",
+                 heuristics = "abbr",
+                 heur.fix = list(pre = c("\u2019", "'"), suf = c("\u2019", "'")),
+                 abbrev = NULL,
+                 tag = TRUE,
+                 lang = "en",
+                 sentc.end = c(".", "!", "?", ";", ":"),
+                 detect = c(parag = FALSE, hline = FALSE),
+                 clean.raw = NULL,
+                 perl = FALSE,
+                 stopwords = NULL,
+                 stemmer = NULL,
+                 doc_id = NA,
+                 add.desc = "kRp.env")
+
+readability <- readability(ques,
+                           hyphen = NULL,
+                           index = c(
+                             "Flesch.Kincaid"),
+                           parameters = list(),
+                           word.lists = list(Bormuth = NULL, Dale.Chall = NULL, Harris.Jacobson = NULL, Spache =
+                                               NULL),
+                           fileEncoding = "UTF-8",
+                           sentc.tag = "sentc",
+                           nonword.class = "nonpunct",
+                           nonword.tag = c(),
+                           quiet = FALSE,
+                           keep.input = NULL,
+                           as.feature = FALSE
+)
+
+```
+
 ## Developing Short form of LEBA
 We sought the item response theory (IRT) to develop the short form of LEBA.
-IRT the conventional classical test theory-based analysis by gathering information on item quality by indices like item difficulty,item discrimination, and item information[@bakerBasicsItemResponse2017].
-IRT judges the item's quality on item information in relation to participants' latent trait level ($\theta$).
-We gathered evidence on item quality by fitting each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690).
+IRT the conventional classical test theory-based analysis by gathering information on item quality by indices like item difficulty, item discrimination, and item information [@bakerBasicsItemResponse2017].
+Item is  judged based on item information in relation to participants' latent trait level ($\theta$).
+We fitted each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690).
 Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait level ($\theta$), and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
@@
 
+We developed a self-reported tool to capture different light exposure related behavior and evaluated its psychometric properties using classical test theory and item response theory based analysis.
+
+48 items were generated by an expert panel and  administered to a large sample (n = `r nrows(EFA.descriptives)` to explore the latent structure.
+Exploratory factor analysis revalied a five factor solution with 25 items.
+("Wearing blue light filters", "Spending time outdoors", "Using phone and smart-watch in bed", "Using light before bedtime",  and "Using light in the morning and during daytime").
+These five factors dealt with different light exposure related behavior.
+The internal consistency reliability coefficient ordinal alpha ranged between `r apa(range(alpha.tab),2,F)`.
+As all the retained factors were meaningful and contributed essentially towards our aim we retained all five factors.
+
+A CFA on a separate sample ((n = `r nrows(CFA.descriptives)` gave a five-factor solution (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR = `r apa(fit.2[10],2,F)`) after discarding two item.
+The internal consistency McDonald's $\omega_t$ of the five factors were  satisfactory (`r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`) Internal consistency reliability of the total scale (23 item) was also satisfactory, Mcdonald's $\omega_t$= `r apa(rel.k[5,6],2,F)`.
+
+Lastly, we developed a short-LEBA (n=23) using IRT analysis.
+We fitted a graded response model model to the combined efa and cfa sample ( n =`r nrows(data)`).
+We discarded 5 items with relatively flat item information curve [I($\theta$) <.20].
+No item was identified as a misfit item.
+In terms of item difficulty, our scale contained very high  high , moderate , and low discriminating items and covered a substantial range of underlying  attributes.
+Test information curve also indicated a good coverage of underlying trait continuum with precision.
+## Conclusion
+"The Light exposure behavior assessment"(LEBA) gave a five solution with 25 items in an exploratory factor analysis.
+A confirmatory factor analysis with this 25-item scale again offered a five-factor solution, but this time two more item was discarded.
+The 25-item "Bangla version of Rotter’s I-E scale"LEBA" was found reliable and valid.
+A short-form of LEBA was developed using IRT analysis.
+IRT analysis gave a 18 item scale with  a good range of covergange across the underlying trait continuum.
+All-in-all, we can recommend both forms to be used to capture individual’s light exposure related behavior
+
 \newpage

### 2022-01-02 manuscript.Rmd
Table abnd figs

@@
 #MAP
-psych::VSS(EFA.data, rotate = "varimax", fm = 'minres', n.obs =428 )
+map <- psych::VSS(EFA.data, rotate = "varimax", fm = 'minres', n.obs =428 )
+map.map <- as.data.frame(map$map)
+colnames(map.map) <- "MAP Statistic"
+map.statistics <- map$vss.stats[,c(1,2,5,6,7,10,11)]
+full.map <- cbind(map.map,map.statistics)
+
+write.csv(full.map, "Table_raw/map_stat")
 ```
@@
 
-devtools::install_github("unDocUMeantIt/koRpus")
+#devtools::install_github("unDocUMeantIt/koRpus")
 library(koRpus)# stable release
-koRpus::install.koRpus.lang(lang=c("en"))
+#koRpus::install.koRpus.lang(lang=c("en"))
 library(koRpus)
@@
 
-48 items were generated by an expert panel and  administered to a large sample (n = `r nrows(EFA.descriptives)` to explore the latent structure.
-Exploratory factor analysis revalied a five factor solution with 25 items.
+48 items were generated by an expert panel and  administered to a large sample (n = `r nrow(EFA.descriptives)` to explore the latent structure.
+Exploratory factor analysis revalued a five factor solution with 25 items.
 ("Wearing blue light filters", "Spending time outdoors", "Using phone and smart-watch in bed", "Using light before bedtime",  and "Using light in the morning and during daytime").
@@
 
-A CFA on a separate sample ((n = `r nrows(CFA.descriptives)` gave a five-factor solution (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR = `r apa(fit.2[10],2,F)`) after discarding two item.
+A CFA on a separate sample ((n = `r nrow(CFA.descriptives)` gave a five-factor solution (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR = `r apa(fit.2[10],2,F)`) after discarding two item.
 The internal consistency McDonald's $\omega_t$ of the five factors were  satisfactory (`r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`) Internal consistency reliability of the total scale (23 item) was also satisfactory, Mcdonald's $\omega_t$= `r apa(rel.k[5,6],2,F)`.
@@
 Lastly, we developed a short-LEBA (n=23) using IRT analysis.
-We fitted a graded response model model to the combined efa and cfa sample ( n =`r nrows(data)`).
+We fitted a graded response model model to the combined efa and cfa sample ( n =`r nrow(data)`).
 We discarded 5 items with relatively flat item information curve [I($\theta$) <.20].

### 2022-01-02 manuscript.Rmd
map analysis

@@
 Horn's parallel analysis [@hornRationaleTestNumber1965] with 500 iterations also indicated a six-factor solution.
-However, the minimum average partial (MAP) method [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] suggested a five-factor solution.
+However, the minimum average partial (MAP) method (Table \@ref(tab:Map-stat1)) [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution.
 As a result, we tested both five-factor and six-factor solutions.

### 2022-01-02 manuscript.Rmd
Discussion Updated

@@
 We estiablished the measurement invariance of our tool across the native and non-native English speakers using structural equation model framework.
-To assess the possible semantic overlap of our tool with the existing tools, we sought to "Semantic Scale Network" [@rosenbusch2020semantic].
+To assess the possible semantic overlap of our tool with the existing tools, we sought to "Semantic Scale Network" [@rosenbusch2020semantic].Also the readability index was analyzed using "Flesch-Kincaid Grade Level" [@flesch1948new].
 Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA.
@@
 
-## Semantic Analysis 
-To find out if our developed tool is overlapping with existing instruments, we subjected the items of LEBA to the "Semantic Scale Network"(SSN) analysis [@rosenbusch2020semantic].
+## Semantic Analysis and Readability
+To find out if our developed tool (23 items) is overlapping with existing instruments, we subjected the items of LEBA to the "Semantic Scale Network"(SSN) analysis [@rosenbusch2020semantic].
 The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic].
@@
 LEBA  appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990].The cosine similarities lie between .47 to .51.
-Two factors of our LEBA tool: "Using phone and smart-watch in bed" and "Using light before bedtime" dealt with light exposure related behavior pertaining to sleep quality.
-As such the similarity index obtained is expected.
+Flesch-Kincaid Grade Level [@flesch1948new] analysis on the the 23 items of our scale indicated required educational grade level was 3.33 and with a age abobe 8.33.
 
@@
 
-Overall we concluded that IRT analysis indicated short form of LEBA is a psychometrically sound measure.
-Item fit indexes and person fit index for all five fitted model were acceptable.
-Items had diverse slope parameters indicating a good range of discrimination- the ability to differentiate respondents with different levels of the light exposure related behavior.
-All-in-all we can recommend the short form of LEBA to be used to capture light exposure related behavior.
-
 ```{r fscore, include=FALSE}
@@
 48 items were generated by an expert panel and  administered to a large sample (n = `r nrow(EFA.descriptives)` to explore the latent structure.
-Exploratory factor analysis revalued a five factor solution with 25 items.
-("Wearing blue light filters", "Spending time outdoors", "Using phone and smart-watch in bed", "Using light before bedtime",  and "Using light in the morning and during daytime").
-These five factors dealt with different light exposure related behavior.
-The internal consistency reliability coefficient ordinal alpha ranged between `r apa(range(alpha.tab),2,F)`.
+Exploratory factor analysis revealed a five factor solution with 25 items.
+("Wearing blue light filters", "Spending time outdoors", "Using phone and smart-watch in bed", "Using light before bedtime",  and "Using light in the morning and during daytime").The internal consistency reliability coefficient ordinal alpha ranged between `r apa(range(alpha.tab),2,F)`.
 As all the retained factors were meaningful and contributed essentially towards our aim we retained all five factors.
@@
 A CFA on a separate sample ((n = `r nrow(CFA.descriptives)` gave a five-factor solution (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR = `r apa(fit.2[10],2,F)`) after discarding two item.
-The internal consistency McDonald's $\omega_t$ of the five factors were  satisfactory (`r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`) Internal consistency reliability of the total scale (23 item) was also satisfactory, Mcdonald's $\omega_t$= `r apa(rel.k[5,6],2,F)`.
+The internal consistency McDonald's $\omega_t$ of the five factors were  satisfactory (`r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`) Internal consistency reliability of the total scale (23 item) was also satisfactory, McDonald's $\omega_t$= `r apa(rel.k[5,6],2,F)`.
+In the same sample, our measurement invariance analysis  revealed that the latent structure attained the residual measurement invariance across subgroups: male and female (CFI: `r apa (residual.fitm[5,1],2,F)`, TLI: `r apa (residual.fitm[6,1],2,F)`, SRMR: `r apa (residual.fitm[6,1],2,F)`).
+
+The "Semantic Scale Network"(SSN) analysis [@rosenbusch2020semantic] on the retained 23 items showed "LEBA" was  related to  "Sleep Disturbance Scale For Children" (SDSC) [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990].
+Upon inspecting the item contents we found items under: "Using phone and smart-watch in bed" and "Using light before bedtime" have semantic overlap with the items of SDSC ans CIDI.
+Items in those two scales were looking into behaviors related to sleep.
+As such the similarity index obtained is expected.
+Flesch-Kincaid Grade Level [@flesch1948new] analysis on the the 23 items of our scale indicated required educational grade level was 3.33 and with a age above 8.33.
 
 Lastly, we developed a short-LEBA (n=23) using IRT analysis.
-We fitted a graded response model model to the combined efa and cfa sample ( n =`r nrow(data)`).
+We fitted a graded response model model to the combined EFA and CFA sample ( n =`r nrow(data)`).
 We discarded 5 items with relatively flat item information curve [I($\theta$) <.20].
-No item was identified as a misfit item.
-In terms of item difficulty, our scale contained very high  high , moderate , and low discriminating items and covered a substantial range of underlying  attributes.
+IRT analysis indicated short form of LEBA is a psychometrically sound measure.
+Item fit indexes and person fit index for all five fitted model were acceptable.
+Items had diverse slope parameters indicating a good range of discrimination- the ability to differentiate respondents with different levels of the light exposure related behavior.
 Test information curve also indicated a good coverage of underlying trait continuum with precision.
+
 ## Conclusion
@@
 A short-form of LEBA was developed using IRT analysis.
-IRT analysis gave a 18 item scale with  a good range of covergange across the underlying trait continuum.
+IRT analysis gave a 18 item scale with  a good range of coverage across the underlying trait continuum.
 All-in-all, we can recommend both forms to be used to capture individual’s light exposure related behavior

### 2022-01-02 manuscript.Rmd
Discussion update2

@@
 summary(strict, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
-fitmeasures (strict,c("gfi", "agfi", "nfi","rfi", "cfi.robust","tli.robust","rmsea", "srmr","aic"))
+residual.fitm <- as.data.frame(fitmeasures (strict,c("gfi", "agfi", "nfi","rfi", "cfi","tli","rmsea", "srmr","aic")))
 
@@
 
-A CFA on a separate sample ((n = `r nrow(CFA.descriptives)` gave a five-factor solution (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR = `r apa(fit.2[10],2,F)`) after discarding two item.
-The internal consistency McDonald's $\omega_t$ of the five factors were  satisfactory (`r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`) Internal consistency reliability of the total scale (23 item) was also satisfactory, McDonald's $\omega_t$= `r apa(rel.k[5,6],2,F)`.
+A CFA on a separate sample ((n = `r nrow(CFA.descriptives)` gave a five-factor solution (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`; RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI] and SRMR = `r apa(fit.2[10],2,F)`) after discarding two item.
+The internal consistency McDonald's $\omega_t$ of the five factors were  satisfactory (`r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`).
+Internal consistency reliability of the total scale (23 item) was also satisfactory, McDonald's $\omega_t$= `r apa(rel.k[5,6],2,F)`.
 In the same sample, our measurement invariance analysis  revealed that the latent structure attained the residual measurement invariance across subgroups: male and female (CFI: `r apa (residual.fitm[5,1],2,F)`, TLI: `r apa (residual.fitm[6,1],2,F)`, SRMR: `r apa (residual.fitm[6,1],2,F)`).
@@
 ```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('appendix-1.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('appendix-2.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('appendix-1.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('appendix-2.Rmd')
+```

### 2022-01-02 manuscript.Rmd
Discussion updates

--- 2022-01-02 manuscript.Rmd
@@
 We estiablished the measurement invariance of our tool across the native and non-native English speakers using structural equation model framework.
-To assess the possible semantic overlap of our tool with the existing tools, we sought to "Semantic Scale Network" [@rosenbusch2020semantic].Also the readability index was analyzed using "Flesch-Kincaid Grade Level" [@flesch1948new].
+To assess the possible semantic overlap of our tool with the existing tools, we sought to "Semantic Scale Network" [@rosenbusch2020semantic].To assess the possible semantic overlap of our tool with the existing tools, we sought to "Semantic Scale Network" [@rosenbusch2020semantic].
 Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA.
@@
 
-## Semantic Analysis and Readability
+## Semantic Analysis 
 To find out if our developed tool (23 items) is overlapping with existing instruments, we subjected the items of LEBA to the "Semantic Scale Network"(SSN) analysis [@rosenbusch2020semantic].

### 2022-01-02 manuscript.Rmd
Discusion update 4

@@
 pacman::p_install_gh("crsh/citr")
+devtools::install_github("unDocUMeantIt/koRpus")
+koRpus::install.koRpus.lang(lang=c("en"))
+library(koRpus)
+library(koRpus.lang.en)
 
@@
 library(readxl)
+library(koRpus)# stable release
+
 r_refs("references.bib")
@@
 
-```{r DescTabPrint, results='asis'}
-
+```{r Demoprint, results='asis'}
 desc_kable %>% kable_styling(latex_options = c("scale_down")) 
-
-```
-
-Table 1 summarizes the survey participants' demographic characteristics.
+```
+
+Table 2 summarizes the survey participants' demographic characteristics.
 Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses.
@@
 ```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('appendix-1.Rmd')
+```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('appendix-2.Rmd')
+```

### 2022-01-02 appendix-1.Rmd
Table abnd figs
Duplicate chunk error fixed

@@
-```{r options-appendix, warning=FALSE, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600)
-set.seed(123)
-par(family = "Arial")
-```
-
-```{r lib, include=FALSE}
-
-library(papaja) # devtools::install_github("crsh/papaja")
-library(lavaan)
-library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
-library(semTools)
-library(MOTE)
-library(car)#revercoding 
-library(psych)
-library(dlookr)
-library(plyr)
-library(tidyverse)
-library(qgraph)
-library(kableExtra)
-library(paran) # Parallel analysis
-library(EFA.MRFA) # Hull method
-library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
-library(DiagrammeRsvg) #For DiagrammeR
-library(rsvg) #For DiagrammeR
-library(ggcorrplot)
-library(semTable)
-library(magick)
-library(mirt)
-library(gtsummary)
-library(gt)
-library(gtExtras)
-library(likert)
-library(VIM) #Missing data
-library(kutils)
-library(simsem)
-library(tabledown)
-library(Hmisc)
-r_refs("references.bib")
+```{r factormp, warning=F}
+map <- readr::read_csv("Table_raw/map_stat")
+map <- map[,-1]
+papaja::apa_table(map,align = "c", caption = "MAP Statistics",  font_size = "small")
 ```
@@
 ```
-
-# Confirming the five factor solution obtained using minimum residual extraction method
-
-```{r MinRes, include=F}
-library(psych)
-library(tabledown)
-library(kableExtra)#without this pdf rendering will not happen
-
-data <- readRDS("leba_2021-09-08.rds")
-
-# Separating EFA and CFA samples with descriptive column
-descriptives.data <- data
-
-## Merge "0"s and "1"s into "1"s select,subset assign)
-descriptives.data[ , 9:56 ][ descriptives.data[ , 9:56 ] == 0 ] <- 1
-#EFA.descriptives <- descriptives.data[1:428,]
-EFA.descriptives <- subset(descriptives.data, IncludedInEFA == "TRUE")
-#CFA.descriptives <- descriptives.data[429:690, ]
-CFA.descriptives<- subset(descriptives.data, IncludedInEFA == "FALSE")
-
-#Separating the EFA and CFA(only items)
-sem.data <- data[, 9:56] #EFA & CFA data
-sem.data[ sem.data == 0] <- 1 #Merged "0"s and "1"s into "1"s
-
-## renaming the column-header
-prefix <- "item"
-sufix <- c(1:48)
-colnam <- paste(prefix,sufix, sep = "" )
-colnames(sem.data) <- colnam
-
-### EFA data
-EFA.data <- sem.data[1:428, ]
-#Polychoric Correlation matrix
-
-correlations <- psych::polychoric(EFA.data, correct = 0)
-
-#Supplementary EFA with Minres Extraction
-
-fa.5F.min.1 <- fa(r=correlations$rho, nfactors = 5, fm= "minres",rotate ="varimax",
-                residuals = TRUE, SMC = TRUE, n.obs =428)
-EE <- print(fa.5F.min.1, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.5F.min.1 <- dplyr::select(EFA.data ,
-                                    -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14))
-
-correlations.red.5F.min.1 <- polychoric(reduced.model.5F.min.1,correct = 0)
-
-fa.5F.min.2 <- fa(r=correlations.red.5F.min.1$rho, nfactors = 5, fm= "minres",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-FF <- print(fa.5F.min.2, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.5F.min.2 <- dplyr::select(EFA.data, -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14, item34, item47, item21, item13))
-
-correlations.red.5F.min.2 <- polychoric(reduced.model.5F.min.2, correct = 0)
-
-fa.5F.min.3 <- fa(r=correlations.red.5F.min.2$rho, nfactors = 5, fm= "minres",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-GG <- print(fa.5F.min.3, cut = .3, digits = 3, sort = TRUE)
-
-minresTab <- tabledown::fac.tab(fa.5F.min.3, cut =.3,complexity = F)
-```
-
-```{r MinResTab}
-papaja::apa_table(minresTab,  caption = "Factor loadings and communality of the retained items(Minmum Residual)", note = "Only loading higher than .30 is reported", longtable=T)
-```
-
-# Factor analysis with six factors
-
-```{r sixFac, include=F}
-# EFA with 6 factor (rejected)
-
-#correlations <- polychoric(EFA.factor, correct = 0)
-
-fa.6F.1 <- fa(r=correlations$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-II <- print(fa.6F.1, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.6F.1 <- dplyr::select(EFA.data ,
-                                    -c(item34, item44, item48, item43, item39, item22, item2, item20, item21, item24,item30, item14, item28, item6, item15, item23))
-
-correlations.red.6F.1 <- polychoric(reduced.model.6F.1,correct = 0)
-
-fa.6F.2 <- fa(r=correlations.red.6F.1$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-JJ <- print(fa.6F.2, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.6F.2 <- dplyr::select(EFA.data, -c(item34, item44, item48, item43, item39, item22, item2, item20, item21, item24,item30, item14, item28, item6, item15, item23, item18, item42, item47, item41))
-
-correlations.red.6F.2 <- polychoric(reduced.model.6F.2,correct = 0)
-
-fa.6F.3 <- fa(r=correlations.red.6F.2$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)
-
-KK <- print(fa.6F.3, cut = .3, digits = 3, sort = TRUE)
-
-# Residuals
-residual.6F =residuals(fa.6F.3 , diag = FALSE, na.rm =T)
-#Count of numbers of residuals>.05
-BigRRR= sum(residual.6F>abs(.05), na.rm =T)
-print(BigRRR)
-
-#Total number of off diagonal elements in the data matrix
-totRRR = length(reduced.model.6F.2)*(length(reduced.model.6F.2)-1)/2
-
-# Proportion of off-diagonal elements >.10
-sumRRR <- sum(BigRRR/totRRR*100)
-
-#hist(residual.6F, main = NULL, xlab = "Six factor Solution: Residuals",ylim=c(0, 400))
-#abline(h =65, lwd = 2, lty = 2)
-#abline(v =.05,lwd = 2, lty = 2)
-sixFac <- tabledown::fac.tab(fa.6F.3, cut =.3,complexity = F)
-```
-
-```{r sixFacTab, results='asis'}
-papaja::apa_table(sixFac,  caption = "Factor loadings and communality of the retained items(six factor)", note = "Only loading higher than .30 is reported",longtable =T)
-```
-
-# Factor Analysis with Unmerged Response Option
-
-```{r DataAppB, include=FALSE}
-data <- readRDS("leba_2021-09-08.rds")
-
-#Separating the EFA and CFA(only items)
-sem.data <- data[, 9:56] #EFA & CFA data
-## renaming the column-header
-prefix <- "item"
-sufix <- c(1:48)
-colnam <- paste(prefix,sufix, sep = "" )
-colnames(sem.data) <- colnam
-EFA.data <- sem.data[1:428, ]
-
-```
-
-```{r ggplot2AppB, include=F}
-apatheme=ggplot2::theme_bw()+
-  ggplot2::theme(panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank(),
-        panel.background = element_blank(),
-        #text=element_text(family = "Helvetica",),
-        legend.title=element_blank(),
-        axis.line.x = element_line(color='black'),
-        axis.line.y = element_line(color='black'),
-        panel.border = element_rect(color = "black",
-                                    fill = NA,
-                                    size = 1))
-```
-
-```{r EFAassumptionsAppB, include=FALSE}
-
-#KMO test
-KMO.1 <- KMO(EFA.data)
-
-# Test of correlation matrix
-bartlet.1 <- cortest.bartlett(EFA.data, n =428)
-
-# Univariate normality
-
-#creating normality function
-shapiro_test_df <- function(df, bonf= TRUE, alpha= 0.05) {
-  l <- lapply(df, shapiro.test)
-  s <- do.call("c", lapply(l, "[[", 1))
-  p <- do.call("c", lapply(l, "[[", 2))
-  if (bonf == TRUE) {
-    sig <- ifelse(p > alpha / length(l), "H0", "*")
-  } else {
-    sig <- ifelse(p > alpha, "H0", "*")
-  }
-  return(list(statistic= s,
-              p.value= p,
-              significance= sig,
-              method= ifelse(bonf == TRUE, "Shapiro-Wilks test with Bonferroni Correction","Shapiro-Wilks test without Bonferroni Correction")))
-}
-
-Shapiro.efa <- shapiro_test_df(EFA.data)
-
-efa.normality.tab = matrix(nrow = 48, ncol = 2)
-rownameprefix <- "Item"
-rownamesufix <- seq(1:48)
-my.item.names <- paste(rownameprefix,rownamesufix, sep = "" )
-rownames(efa.normality.tab) <- my.item.names
-colnames(efa.normality.tab) <- c("statistic", "p")
-
-efa.normality.tab[,1] <- apa(Shapiro.efa$statistic,2,T)
-efa.normality.tab[,2] <- apa(Shapiro.efa$p.value,2,T)
-
-efa.normalityprefix <- efa.normality.tab[,1]
-efa.normalitysufix <- Shapiro.efa$significance
-efa.normality.stat <- paste(efa.normalityprefix,efa.normalitysufix, sep = "" )
-
-# Multivariate Normality
-mardia.1 <- mardia(EFA.data, na.rm = T, plot =F)
-
-# Descriptive Stats
-Descriptives <- psych::describe(EFA.data)
-alpha <- psych::alpha(EFA.data)
-Item.total <- alpha$item.stats
-
-Des.combined <- cbind(apa(Descriptives$mean,2,T), apa(Descriptives$sd,2,T), apa(Descriptives$skew,2,T),apa(Descriptives$kurtosis,2,T), efa.normality.stat,  apa(Item.total$r.cor,2,F))
-
-colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics","Item-Total Correlation")
-rownameprefix <- "Item"
-rownamesufix <- seq(1:48)
-my.names <- paste(rownameprefix,rownamesufix, sep = "" )
-rownames(Des.combined) = (my.names)
-```
-
-```{r CorrMatrixAppB, include=FALSE, warning=F,message=F}
-#Polychoric Correlation matrix
-
-correlations <- polychoric(EFA.data, correct = 0)
-upper <- correlations$rho[upper.tri(correlations$rho, diag = F)]
-
-min.cor.1 <- apa(min(abs(upper)),2,F) #minimum cor.coefficient of the matrix
-max.cor.1 <- apa(max(abs(upper)),2,F) # max. correlation coefficient of the matrix
-
-determinets <- det(correlations$rho) 
-# Calculating the percentage of correlations higher than .30
-
-BigR = sum(correlations$rho >= abs(.30) & correlations$rho < abs(1.0), na.rm =T)/2 
-totR = length(EFA.data)*(length(EFA.data)-1)/2
-cor.per.1 <- print (BigR/totR)*100
-```
-
-```{r ParallelEFAAppB, include=FALSE}
-
-# Parallel analysis
-Horn <- paran(correlations$rho, iterations=500, centile=0, quietly=FALSE,
-           status=TRUE, all=FALSE, cfa=FALSE, graph=TRUE,
-           color=TRUE, col=c("black","red","blue"),
-           lty=c(1,2,3), lwd=1, legend=TRUE, 
-           width=640, height=640, grdevice=png, seed=0, mat=NA, n=NA)
-
-Adjusted.EV <- data.frame(Horn$AdjEv)
-Adjusted.EV$type = c('Adjusted Ev')
-Adjusted.EV$num = c(row.names(Adjusted.EV))
-Adjusted.EV$num = as.numeric(Adjusted.EV$num)
-colnames(Adjusted.EV) = c('eigenvalue', 'type', 'num')
-
-Random.EV <- data.frame(Horn$RndEv)
-Random.EV$type = c('Random EV')
-Random.EV$num = c(row.names(Random.EV))
-Random.EV$num = as.numeric(Random.EV$num)
-colnames(Random.EV) = c('eigenvalue', 'type', 'num')
-
-Unadjusted.EV <- data.frame(Horn$Ev)
-Unadjusted.EV$type = c('Unadjusted EV')
-Unadjusted.EV$num = c(row.names(Unadjusted.EV))
-Unadjusted.EV$num = as.numeric(Unadjusted.EV$num)
-colnames(Unadjusted.EV) = c('eigenvalue', 'type', 'num')
-
-parallel = ggplot(Adjusted.EV, aes(x=num, y=eigenvalue, shape=type, color=type)) +
-  #Add lines connecting data points
-  geom_line()+
-    geom_line(data = Random.EV) +
-  geom_line(data = Unadjusted.EV)+
-    #Add the data points.
-  geom_point(size=1)+
-  geom_point(data = Random.EV, size=1)+
-  geom_point(data = Unadjusted.EV, size=1)+
-  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
-   #Label the x-axis 'Factor Number', and ensure that it ranges from 1-max # of factors, increasing by one with each 'tick' mark.
-  scale_x_continuous(name='Factor Number', limits=c(0, 48),breaks=seq(0,48,4))+
-    #Add vertical line indicating parallel analysis suggested max # of factors to retain
-  geom_hline(yintercept=1, linetype = 'dashed') + apatheme
-
-```
-
-```{r ScreePlotAppB, include=FALSE}
-Scree <- scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
-      hline=NULL,add=F)
-
-FA.Scree <- data.frame(Scree$fv)
-FA.Scree$type = c('Factor Analysis')
-FA.Scree$num = c(row.names(FA.Scree))
-FA.Scree$num = as.numeric(FA.Scree$num)
-colnames(FA.Scree) = c('eigenvalue', 'type', 'num')
-
-PA.Scree <- data.frame(Scree$pcv)
-PA.Scree$type = c('Principal Component Analysis')
-PA.Scree$num = c(row.names(PA.Scree))
-PA.Scree$num = as.numeric(PA.Scree$num)
-colnames(PA.Scree) = c('eigenvalue', 'type', 'num')
-
-scree.plot <-ggplot(FA.Scree, aes(x=num, y=eigenvalue,color=type, shape=type))+
-   geom_line()+
-  geom_line(data = PA.Scree)+ 
-  geom_point(size=1)+
-  geom_point(data = PA.Scree, size=1)+
-  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
-  scale_x_continuous(name='Factor Number', limits=c(0, 48),breaks=seq(0,48,4))+
-  geom_hline(yintercept=1, linetype = 'dashed') + apatheme 
-```
-
-```{r MAPefaAppB, include=FALSE}
-#MAP
-psych::VSS(EFA.data, rotate = "varimax", fm = 'minres', n.obs =428 )
-```
-
-Table \@ref(tab:tabDesAppB) summarizes the univariate descriptive statistics for the 48 items with un-merged options.
-Some of the items were skewed with high Kurtosis values.
-Our data violated both univariate normality (Shapiro-Wilk statistics) and multivariate normality assumptions [Marida's test].
-Multivariate skew was = `r printnum(mardia.1$b1p)` (p <0.001) and multivariate kurtosis was = `r printnum(mardia.1$b2p)` (p <0.001).
-Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen.
-Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy.
-The overall KMO vale for 48 items was `r printnum(KMO.1$MSA)` which was above the cutoff value (.50) indicating a mediocre sample.
-Bartlett's test of sphericity, $\chi^2$ (`r bartlet.1$df`) = `r apa(bartlet.1$chisq, 2, T)`, p < .001 indicated the correlations between items are adequate for the EFA.
-However only `r apa(cor.per.1, 2,T)`% of the inter-item correlation coefficients were greater than .30.
-The absolute value of inter-item correlation ranged between `r min.cor.1` to `r max.cor.1`.Figure \@ref(fig:corunm) depicts the correlation matrix.
-For un-merged response option Horn's parallel analysis with 500 iterations indicated a five-factor solution.
-However, Scree plot and the MAP method suggested 6-factor solution.
-five-factor solution .
-As a result, we tested both five-factor and six-factor solutions.
-The six factor solution yielded a factor with only two salient loading (Table \@ref(tab:EFAsix).
-Thus we reject the six factor solution.
-The five factor solution retained 24 items (Table \@ref(tab:efaunmerged)).
-However the factors are less interpretable in terms of common theme.
-Thus we reject the five factor solution.
-
-```{r tabDesAppB, results='asis'}
-apa_table(Des.combined, caption = "Descriptive Statistics for Unmerged response options",  note = "*p<.001", longtable =T)
-```
-
-```{r corunm, fig.cap="Correlation plot of the items [Unmerged response options]",  out.width="100%"}
-
-ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
-           ggtheme = ggplot2::theme_minimal, tl.cex = 6,tl.srt = 90 )
-#p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
-#to show pvalue in the fig add p.mat=p.mat
-```
-
-```{r facIdFigAppB,  fig.cap='Factor Identification  (A) Parallel analysis (B) Scree Plot [Unmerged response options]', warning=FALSE}
-cowplot::plot_grid(parallel, scree.plot, labels = "AUTO",ncol=1, label_size = 8,align = "v")
-
-```
-
-```{r EFAAppB, include=FALSE}
-fa.5F.1 <- fa(r=correlations$rho, nfactors = 5, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-AA <- print(fa.5F.1, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.5F.1 <- dplyr::select(EFA.data ,
-                                    -c(item32, item34, item24, item37, item22, item5,
-                                        item28, item30, item39,item23, item45, item6, item29, item2, item41))
-
-correlations.red.5F.1 <- polychoric(reduced.model.5F.1,correct = 0)
-
-fa.5F.2 <- fa(r=correlations.red.5F.1$rho, nfactors = 5, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-BB <- print(fa.5F.2, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.5F.2 <- dplyr::select(EFA.data, -c( item32, item34, item24, item37, item22, item5,
-                                        item28, item30, item39,item23, item45, item6, item29, item2, item41, item46, item13, item15, item25, item1, item26, item14))
-
-correlations.red.5F.2 <- polychoric(reduced.model.5F.2,correct = 0)
-
-fa.5F.3 <- fa(r=correlations.red.5F.2$rho, nfactors = 5, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428,max.iter = 500 )
-
-CC <- print(fa.5F.3, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.5F.3 <- dplyr::select(EFA.data, -c( item32, item34, item24, item37, item22, item5,
-                                        item28, item30, item39,item23, item45, item6, item29, item2, item41, item46, item13, item15, item25, item1, item26, item14, item43, item42))
-
-correlations.red.5F.3 <- polychoric(reduced.model.5F.3,correct = 0)
-
-fa.5F.4 <- fa(r=correlations.red.5F.3$rho, nfactors = 5, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428,max.iter = 500 )
-
-CC <- print(fa.5F.4, cut = .3, digits = 3, sort = TRUE)
-```
-
-```{r factordetailsAppB, include=FALSE}
-#Preparing the EFA table
-efa.table <- tabledown::fac.tab(fa.5F.4,.3, complexity = F) 
-```
-
-```{r efaunmerged, results='asis'}
-apa_table(efa.table, caption = "Factor loadings and communality of the retained items in five factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T)
-```
-
-```{r EFAAppsix, include=FALSE, warning=F,message=FALSE}
-fa.6F.1 <- fa(r=correlations$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-DD <- print(fa.6F.1, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.6F.1 <- dplyr::select(EFA.data ,
-                                    -c(item32, item34, item44,item24, item37, item22, item5,
-                                        item28,item39,item23, item45, item6, item29, item2, item41, item30))
-
-correlations.red.6F.2 <- polychoric(reduced.model.6F.1,correct = 0)
-
-fa.6F.2 <- fa(r=correlations.red.6F.2$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-EE <- print(fa.6F.2, cut = .3, digits = 3, sort = TRUE)
-reduced.model.6F.2 <- dplyr::select(EFA.data ,
-                                    -c(item32, item34, item44,item24, item37, item22, item5,
-                                        item28,item39,item23, item45, item6, item29, item2, item41, item30, item46, item36,item1, item25))
-correlations.red.6F.3 <- polychoric(reduced.model.6F.2,correct = 0)
-fa.6F.3 <- fa(r=correlations.red.6F.3$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-FF <- print(fa.6F.3, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.6F.3 <- dplyr::select(EFA.data ,
-                                    -c(item32, item34, item44,item24, item37, item22, item5,
-                                        item28,item39,item23, item45, item6, item29, item2, item41, item30, item46, item36,item1, item25, item18))
-correlations.red.6F.4 <- polychoric(reduced.model.6F.3,correct = 0)
-fa.6F.4 <- fa(r=correlations.red.6F.4$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-FF <- print(fa.6F.4, cut = .3, digits = 3, sort = TRUE)
-
-efa.table.2 <- tabledown::fac.tab(fa.6F.4,.3, complexity = F) 
-```
-
-```{r EFAsix, results='asis'}
-apa_table(efa.table.2, caption = "Factor loadings and communality of the retained items in six factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T)
-```
-
-# Items Retained in the Five Factor Solution [Unmerged Responses]
-
-| **Five Factor Solution [Unmerged Responses] (24 Items)** |
-|---------------------------------------------------------|
-| **F1**                                                  |
-| `r label(sem.data$item19)`                              |
-| `r label(sem.data$item20)`                              |
-| `r label(sem.data$item18)`                              |
-| `r label(sem.data$item21)`                              |
-| `r label(sem.data$item4)`                               |
-| **F2**                                                  |
-| `r label(sem.data$item11)`                              |
-| `r label(sem.data$item10)`                              |
-| `r label(sem.data$item12)`                              |
-| `r label(sem.data$item8)`                               |
-| `r label(sem.data$item7)`                               |
-| `r label(sem.data$item9)`                               |
-| **F3**                                                  |
-| `r label(sem.data$item3)`                               |
-| `r label(sem.data$item27)`                              |
-| `r label(sem.data$item40)`                              |
-| **F4**                                                  |
-| `r label(sem.data$item35)`                              |
-| `r label(sem.data$item48)`                              |
-| `r label(sem.data$item33)`                              |
-| `r label(sem.data$item47)`                              |
-| `r label(sem.data$item44)`                              |
-| `r label(sem.data$item31)`                              |
-| `r label(sem.data$item38)`                              |
-| **F5**                                                  |
-| `r label(sem.data$item16)`                              |
-| `r label(sem.data$item17)`                              |
-| `r label(sem.data$item36)`                              |
-
-```{r EFAResidualsAppB, eval=FALSE, fig.cap=' Histogram of residulas:  five-factor solution', warning=FALSE, include=FALSE, results='asis'}
-hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))
-abline(h =35, lwd = 2, lty = 2)
-abline(v =.05,lwd = 2, lty = 2)
-```
-
-# Geographic Locations of Survey Participants
-```{r Timezone-tab, include=FALSE, warning=F,message=FALSE}
-descriptives.data%>%
-  tbl_summary(
-    label = slypos_demographics_tz.factor ~ "Time zone - Country",
-    statistic = list(all_categorical() ~ "{n} ({p}%)"),
-    missing = "no",
-    sort = all_categorical() ~ "frequency",
-    include = "slypos_demographics_tz.factor"
-  )  %>% bold_labels() %>% 
-  modify_header(label ~ "") %>%
-  modify_caption("Geographical Location") -> tz_table
-
-  as_tibble(tz_table, format = 'pipe') -> tz_tibble
-
-as_kable(tz_table, format = "latex",booktabs = T, longtable =T) -> tz_kable
-
-```
-
-```{r tztabprint, results='asis'}
-
-tz_kable %>% 
-  kable_styling(latex_options = c("repeat_header")) %>% 
-  column_spec(1,width = "10cm") %>% 
-  column_spec(2,width = "2cm")
-
-```

### 2022-01-02 appendix-2.Rmd
Duplicate chunk error fixed

--- 2021-11-17 Supplymentary.Rmd
@@
----
-title             : "Supplementary"
-shorttitle        : "SA"
-
-author: 
-  - name          : "Mushfiqul Anwar Siraji"
-    affiliation   : "1, *"
-    email         : "mushfiqul.anwarsiraji@monash.edu"
-    role:         
-      - Formal Analysis
-      - Visualization
-      - Writing – original draft
-      - Writing – review & editing;
-
-  - name          : "Rafael Robert Lazar"
-    affiliation   : "2, 3, *"
-    role:
-      - Data curation
-      - Investigation
-      - Project administration
-      - Visualization
-      - Writing – original draft
-      - Writing – review & editing;
-
-  - name          : "Juliëtte	van Duijnhoven"
-    affiliation   : "4"
-    email         : "j.v.duijnhoven1@tue.nl"
-    role:         
-      - Conceptualization
-      - Methodology
-      - Investigation
-      - Writing – review & editing
-
-  - name          : "Luc Schlangen"
-    affiliation   : "5"
-    email         : "l.j.m.schlangen@tue.nl"
-    role:         
-      - Conceptualization
-      - Methodology
-      - Investigation
-      - Writing – review & editing
-
-  - name          : "Shamsul Haque"
-    affiliation   : "1"
-    email         : "shamsul@monash.edu"
-    role:         
-      - Conceptualization
-      - Supervision
-      - Writing – review & editing
-
-  - name          : "Vineetha Kalavally"
-    affiliation   : "6"
-    email         : "vineetha@monash.edu"
-    role:         
-      - Supervision
-      - Writing – review & editing
-
-  - name          : "Céline Vetter"
-    affiliation   : "7, 8"
-    email         : "celine.vetter@colorado.edu"
-    role:         
-      - Conceptualization
-      - Writing – review & editing
-
-  - name          : "Gena Glickman"
-    affiliation   : "9"
-    email         : "gena.glickman@usuhs.edu"
-    role:         
-      - Conceptualization
-      - Methodology
-      - Writing – review & editing
-
-  - name          : "Karin Smolders"
-    affiliation   : "10"
-    email         : "k.c.h.j.smolders@tue.nl"
-    role:         
-      - Conceptualization
-      - Methodology
-      - Writing – review & editing
-
-  - name          : "Manuel Spitschan"
-    corresponding : yes
-    affiliation   : "11, 2, 3"
-    email         : "manuel.spitschan@psy.ox.ac.uk"
-    role:         
-      - Conceptualization
-      - Data curation
-      - Investigation
-      - Project administration
-      - Visualization
-      - Methodology
-      - Writing – original draft
-      - Writing – review & editing
-
-affiliation:
-  - id            : "1"
-    institution   : "Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
-  - id            : "2"
-    institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"
-  - id            : "3"
-    institution   : "University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland"
-  - id            : "4"
-    institution   : "Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands"
-  - id            : "5"
-    institution   : "Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Intelligent Lighting Institute, Eindhoven, Netherlands"
-  - id            : "6"
-    institution   : "Monash University, Department of Electrical and Computer Systems Engineering, Malaysia, Selangor, Malaysia"
-  - id            : "7"
-    institution   : "University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA"
-  - id            : "8"
-    institution   : "Ximes GmbH, Frankfurt, Germany"
-  - id            : "9"
-    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
-  - id            : "10"
-    institution   : "Eindhoven University of Technology, Human-Technology Interaction Group, Eindhoven, Netherlands"
-  - id            : "11"
-    institution   : "University of Oxford, Department of Experimental Psychology, Oxford, UK"
-  - id            : "*"
-    institution   : "Joint first author"
-
-bibliography      : ["references.bib"]
-
-floatsintext      : no
-figurelist        : no
-tablelist         : no
-footnotelist      : no
-linenumbers       : yes
-mask              : no
-draft             : no
-documentclass     : "apa6"
-classoption       : "man"
-output            : 
-  papaja::apa6_pdf:
-    latex_engine: xelatex
-    includes:
-      in_header: header.tex
-
-mainfont: Arial
----
-
-```{r options, warning=FALSE, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600)
-set.seed(123)
-par(family = "Arial")
-```
-
-```{r lib, include=FALSE}
-
-library(papaja) # devtools::install_github("crsh/papaja")
-library(lavaan)
-library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
-library(semTools)
-library(MOTE)
-library(car)#revercoding 
-library(psych)
-library(dlookr)
-library(plyr)
-library(tidyverse)
-library(qgraph)
-library(kableExtra)
-library(paran) # Parallel analysis
-library(EFA.MRFA) # Hull method
-library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
-library(DiagrammeRsvg) #For DiagrammeR
-library(rsvg) #For DiagrammeR
-library(ggcorrplot)
-library(semTable)
-library(magick)
-library(mirt)
-library(gtsummary)
-library(gt)
-library(gtExtras)
-library(likert)
-library(VIM) #Missing data
-library(kutils)
-library(simsem)
-library(tabledown)
-library(Hmisc)
-r_refs("references.bib")
-```
-
-# SA: Confirming the five factor solution obtained using minimum residual extraction method
-
 ```{r MinRes, include=F}
@@
 ```{r EFAAppsix, include=FALSE, warning=F,message=FALSE}
+
+library(Hmisc)
 fa.6F.1 <- fa(r=correlations$rho, nfactors = 6, fm= "pa",rotate ="varimax",

### 2022-01-02 manuscript.Rmd
Duplicate chunk error fixed

@@
   papaja::apa6_pdf:
+    keep_tex: false
     latex_engine: xelatex
@@
   - "appendix-2.Rmd"
+  - "appendix-3.Rmd"
 mainfont: Arial
@@
 Horn's parallel analysis [@hornRationaleTestNumber1965] with 500 iterations also indicated a six-factor solution.
-However, the minimum average partial (MAP) method (Table \@ref(tab:Map-stat1)) [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution.
+However, the minimum average partial (MAP) method (Table \@ref(tab:factormp)) [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution.
 As a result, we tested both five-factor and six-factor solutions.
@@
 Lastly, we developed a short-LEBA (n=23) using IRT analysis.
-We fitted a graded response model model to the combined EFA and CFA sample ( n =`r nrow(data)`).
+We fitted a graded response model model to the combined EFA and CFA sample (n =`r nrow(data)`).
 We discarded 5 items with relatively flat item information curve [I($\theta$) <.20].
@@
 ```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('appendix-1.Rmd')
-```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('appendix-2.Rmd')
-```

### 2022-01-02 appendix-2.Rmd
Cross-ref Table 1 & 2 requires more fixing

@@
 # Geographic Locations of Survey Participants
-```{r Timezone-tab, include=FALSE, warning=F,message=FALSE}
+```{r Timetab, include=FALSE, warning=F,message=FALSE}
 descriptives.data%>%

### 2022-01-02 manuscript.Rmd
Cross-ref Table 1 & 2 requires more fixing

@@
   papaja::apa6_pdf:
-    keep_tex: false
+    keep_tex: true
     latex_engine: xelatex
@@
 
-```{r scale-print, results='asis'}
+```{r simscalep}
 relevant.scale.data %>%
@@
 
-```{r Demoprint, results='asis'}
+```{r Demoprint}
 desc_kable %>% kable_styling(latex_options = c("scale_down")) 
@@
 
-Table 2 summarizes the survey participants' demographic characteristics.
+Table \@ref(tab:Demoprint) summarizes the survey participants' demographic characteristics.
 Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses.
@@
 To ensure construct adequacy we thoroughly assessed the current status of literature and identified a variety of light exposure related scales.
-However, no scales specifically measuring the behavioral component of light exposure were found (cf.
-Table 1).
+However, no scales specifically measuring the behavioral component of light exposure were found (\@ref(tab:simscale)).
 Consequentially we pursued to introduce a new openly available scale to address this research gap.
@@
                     9[label = 'Semantic Analysis']
-                    10[label = 'LEBA Short Form (17 Items; N=690) 
+                    10[label = 'LEBA Short Form (18 Items; N=690) 
                       Based on Item Response Theory']

### 2022-01-02 appendix-1.Rmd
Aesthetics

@@
 papaja::apa_table(map,align = "c", caption = "MAP Statistics",  font_size = "small")
+```
+
+```{r EFAResiduals, out.height= "100%",  fig.align='center', fig.cap= ' Histogram of residuals:  five-factor solution',  out.width="100%",  warning=FALSE, results='asis'}
+knitr::include_graphics('Manuscript.figures/EFAResidual.png')
+
 ```
@@
 ```
+
+```{r personfit, fig.cap="Person fit of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
+knitr::include_graphics("Manuscript.figures/personfit.png")
+```

### 2022-01-02 manuscript.Rmd
Aesthetics

@@
 koRpus::install.koRpus.lang(lang=c("en"))
-library(koRpus)
-library(koRpus.lang.en)
 
@@
 library(koRpus)# stable release
-
+library(koRpus.lang.en)
 r_refs("references.bib")
@@
 
-```{r Demoprint}
-desc_kable %>% kable_styling(latex_options = c("scale_down")) 
-```
-
-Table \@ref(tab:Demoprint) summarizes the survey participants' demographic characteristics.
+```{r demographics, warning=F, message=F}
+desc_kable %>% 
+  kable_styling(latex_options = c("scale_down")) 
+```
+
+Table 2 summarizes the survey participants' demographic characteristics.
 Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses.
@@
 To ensure construct adequacy we thoroughly assessed the current status of literature and identified a variety of light exposure related scales.
-However, no scales specifically measuring the behavioral component of light exposure were found (\@ref(tab:simscale)).
+However, no scales specifically measuring the behavioral component of light exposure were found (Table \@ref(tab:simscalep)).
 Consequentially we pursued to introduce a new openly available scale to address this research gap.
@@
   #Add lines connecting data points
-  geom_line()+
+  geom_line(colour ='black')+
     #geom_line(data = Random.EV) +
@@
     #Add the data points.
-  geom_point(size=1)+
+  geom_point(size=2,colour ='black')+
   #geom_point(data = Random.EV, size=3)+
@@
 scree.plot <-ggplot(FA.Scree, aes(x=num, y=eigenvalue,color=type, shape=type))+
-   geom_line()+
+   geom_line(colour ='black')+
   #geom_line(data = PA.Scree)+ 
-  geom_point(size=1)+
+  geom_point(size=2,colour ='black')+
   #geom_point(data = PA.Scree, size=3)+
-  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
+  scale_y_continuous(name="Eigen Value", limits=c(0, 7), breaks=seq(0,7,1)) +
   scale_x_continuous(name='Factor Number (Scree Plot)', limits=c(0, 20),breaks=seq(0,20,4))+
@@
 hull <- ggplot2::last_plot()
-Hull <- hull+ ggtitle(NULL) +xlab("Factor Number (Hull Method)")+ylab("CAF")+ 
+Hull <- hull+ ggtitle(NULL)+xlab("Factor Number (Hull Method)")+ylab("CAF")+ 
   apatheme +scale_color_manual(labels = c("Out side the convex Hull", "On the convex Hull"), values = c("red", "cyan2"))+theme(legend.position = "None") 
@@
 As a result, we tested both five-factor and six-factor solutions.
+```{r factors, include=F}
+jpeg("Manuscript.figures/factors.png", width = 400, height = 800)
+cowplot::plot_grid(parallel, scree.plot,Hull, labels = "AUTO",ncol=1, label_size = 8,align = "v")
+```
 
 ```{r facIdFig, out.height="350%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}
-cowplot::plot_grid(parallel, scree.plot,Hull, labels = "AUTO",ncol=1, label_size = 8,align = "v")
+knitr::include_graphics("Manuscript.figures/factors.png")
 
@@
 Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 [@brownConfirmatoryFactorAnalysis2015], all factor-loading higher than .30 and no cross-loading greater than .30.
-We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (Table \@ref(tab:MinResTab)).
+We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (Sup.Table \@ref(tab:MinResTab)).
 Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items.
@@
 Figure \@ref(fig:EFAplot) depicts the obtained five-five factor structure.
-However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:EFAResiduals)) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring.
+However, the histogram of the absolute values of non-redundant residual-correlations (Sup.Figure \@ref(fig:EFAResiduals)) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring.
 [@desjardinsHandbookEducationalMeasurement2018].
 Subsequently, we fitted a six-factor solution.
-However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution (Table \@ref(tab:sixFacTab)).
+However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution (Sup.Table \@ref(tab:sixFacTab)).
 Internal consistency reliability coefficient Cronbach's alpha assumes all the factor-loadings of the items under a factor are equal [@graham2006congeneric; @novick1967coefficient] which is not the case in our sample.
@@
 
-```{r EFAResiduals, out.height= "100%",  fig.align='center', fig.cap= ' Histogram of residuals:  five-factor solution',  out.width="100%",  warning=FALSE, results='asis'}
+```{r EFARes, message=FALSE, warning=FALSE, include=F}
+jpeg("Manuscript.figures/EFAResidual.png", width = 800, height = 750)
 hist(residual.5F,  main = NULL, xlab = "Residuals", ylim=c(0, 400))
@@
 All of the items had RMSEA value $\le$.06 indicating adequate fit.
-Figure \@ref(fig:personfit) depicts the person fit of out fitted models.
+Figure \@ref(Sup.fig:personfit) depicts the person fit of out fitted models.
 Person fit indicates the validity and meaningfulness of the fitted model at the participants latent trait level [@desjardinsHandbookEducationalMeasurement2018].
@@
 
-```{r personfit, fig.cap="Person fit of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
+```{r perfit, include=F}
+jpeg("Manuscript.figures/personfit.png", width = 800, height = 750)
+
 plot_grid(F1.person, F2.person,F3.person,F4.person,F5.person, 
@@
 
-```{r WP, fig.cap="Person Item Map", warning=FALSE, out.width="100%", out.height="120%"}
+```{r WP, eval=FALSE, fig.cap="Person Item Map", warning=FALSE, include=FALSE, out.height="120%", out.width="100%"}
 

### 2022-01-02 appendix-1.Rmd
Sup.files updated

@@
 map <- readr::read_csv("Table_raw/map_stat")
-map <- map[,-1]
-papaja::apa_table(map,align = "c", caption = "MAP Statistics",  font_size = "small")
+map1 <- (map$`MAP Statistic`)
+
+map1 <- MOTE::apa(map1,5,F)
+map1 <- as.character(map1)
+map1 <- as.data.frame(map1)
+colnames(map1) <- "MAP Statistics"
+map2 <- map[,-c(1,2)]
+map3 <- cbind(map1, map2)
+
+papaja::apa_table(map3, caption = "Map Statistics")
 ```
@@
 
+```
+
+```{r MI, include=F, warning=F}
+data <- readRDS("leba_2021-09-08.rds")
+
+# Separating EFA and CFA samples with descriptive column
+descriptives.data <- data
+
+## Merge "0"s and "1"s into "1"s select,subset assign)
+descriptives.data[ , 9:56 ][ descriptives.data[ , 9:56 ] == 0 ] <- 1
+#EFA.descriptives <- descriptives.data[1:428,]
+EFA.descriptives <- subset(descriptives.data, IncludedInEFA == "TRUE")
+#CFA.descriptives <- descriptives.data[429:690, ]
+CFA.descriptives<- subset(descriptives.data, IncludedInEFA == "FALSE")
+
+mi.desc_table <- CFA.descriptives[,c(1,2,5,6,7)] %>%
+  tbl_summary(
+    by = slypos_demographics_language.factor,
+    statistic = list(all_continuous() ~ "{mean} ({sd})",
+                     all_categorical() ~ "{n} ({p}%)"),
+    digits = all_continuous() ~ 2,
+    label = list(slypos_demographics_age ~ "Age",
+                 slypos_demographics_sex.factor ~ "Sex",
+                 slypos_demographics_work_or_school.factor ~ "Occupational Status",
+                 slypos_demographics_school.factor ~ "Occupational setting"
+                 ),
+    missing = "no"
+    ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
+modify_header(label ~ "**Variable**") %>% separate_p_footnotes() %>%
+  modify_caption("Demographic Characteristics: Native English Speakers")
+
+mides_kable <-  as_kable_extra(mi.desc_table, format = "latex",booktabs = T) 
+```
+
+```{r midesp, warning=F, message=F}
+mides_kable %>% 
+  kable_styling(latex_options = c("scale_down")) 
 ```

### 2022-01-02 appendix-2.Rmd
Sup.files updated

@@
 ```{r MinResTab}
-papaja::apa_table(minresTab,  caption = "Factor loadings and communality of the retained items(Minmum Residual)", note = "Only loading higher than .30 is reported", longtable=T)
+papaja::apa_table(minresTab,  caption = "Factor loadings and communality of the retained items (Minmum Residual)", note = "Only loading higher than .30 is reported", longtable=T, font_size = "small")
 ```
@@
 
+reduced.model.6F.3 <- dplyr::select(EFA.data, -c(item34, item44, item48, item43, item39, item22, item2, item20, item21, item24,item30, item14, item28, item6, item15, item23, item18, item42, item47, item41, item5, item13, item29))
+
+correlations.red.6F.3 <- polychoric(reduced.model.6F.3,correct = 0)
+
+fa.6F.4 <- fa(r=correlations.red.6F.3$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)
+
+ll <- print(fa.6F.4, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.6F.4 <- dplyr::select(EFA.data, -c(item34, item44, item48, item43, item39, item22, item2, item20, item21, item24,item30, item14, item28, item6, item15, item23, item18, item42, item47, item41, item5, item13, item29, item19))
+
+correlations.red.6F.4 <- polychoric(reduced.model.6F.4,correct = 0)
+
+fa.6F.5 <- fa(r=correlations.red.6F.4$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)
+
+mm <- print(fa.6F.5, cut = .3, digits = 3, sort = TRUE)
+
 # Residuals
-residual.6F =residuals(fa.6F.3 , diag = FALSE, na.rm =T)
+residual.6F =residuals(fa.6F.5 , diag = FALSE, na.rm =T)
 #Count of numbers of residuals>.05
@@
 #abline(v =.05,lwd = 2, lty = 2)
-sixFac <- tabledown::fac.tab(fa.6F.3, cut =.3,complexity = F)
+sixFac <- tabledown::fac.tab(fa.6F.5, cut =.3,complexity = F)
 ```
@@
 ```{r sixFacTab, results='asis'}
-papaja::apa_table(sixFac,  caption = "Factor loadings and communality of the retained items(six factor)", note = "Only loading higher than .30 is reported",longtable =T)
+papaja::apa_table(sixFac,  caption = "Factor loadings and communality of the retained items(six factor)", note = "Only loading higher than .30 is reported; Sixth factor has only two salient loadings",longtable =T, font_size = "small")
 ```
-
-# Factor Analysis with Unmerged Response Option
 
@@
                                     size = 1))
-```
-
-```{r EFAassumptionsAppB, include=FALSE}
-
-#KMO test
-KMO.1 <- KMO(EFA.data)
-
-# Test of correlation matrix
-bartlet.1 <- cortest.bartlett(EFA.data, n =428)
-
-# Univariate normality
-
-#creating normality function
-shapiro_test_df <- function(df, bonf= TRUE, alpha= 0.05) {
-  l <- lapply(df, shapiro.test)
-  s <- do.call("c", lapply(l, "[[", 1))
-  p <- do.call("c", lapply(l, "[[", 2))
-  if (bonf == TRUE) {
-    sig <- ifelse(p > alpha / length(l), "H0", "*")
-  } else {
-    sig <- ifelse(p > alpha, "H0", "*")
-  }
-  return(list(statistic= s,
-              p.value= p,
-              significance= sig,
-              method= ifelse(bonf == TRUE, "Shapiro-Wilks test with Bonferroni Correction","Shapiro-Wilks test without Bonferroni Correction")))
-}
-
-Shapiro.efa <- shapiro_test_df(EFA.data)
-
-efa.normality.tab = matrix(nrow = 48, ncol = 2)
-rownameprefix <- "Item"
-rownamesufix <- seq(1:48)
-my.item.names <- paste(rownameprefix,rownamesufix, sep = "" )
-rownames(efa.normality.tab) <- my.item.names
-colnames(efa.normality.tab) <- c("statistic", "p")
-
-efa.normality.tab[,1] <- apa(Shapiro.efa$statistic,2,T)
-efa.normality.tab[,2] <- apa(Shapiro.efa$p.value,2,T)
-
-efa.normalityprefix <- efa.normality.tab[,1]
-efa.normalitysufix <- Shapiro.efa$significance
-efa.normality.stat <- paste(efa.normalityprefix,efa.normalitysufix, sep = "" )
-
-# Multivariate Normality
-mardia.1 <- mardia(EFA.data, na.rm = T, plot =F)
-
-# Descriptive Stats
-Descriptives <- psych::describe(EFA.data)
-alpha <- psych::alpha(EFA.data)
-Item.total <- alpha$item.stats
-
-Des.combined <- cbind(apa(Descriptives$mean,2,T), apa(Descriptives$sd,2,T), apa(Descriptives$skew,2,T),apa(Descriptives$kurtosis,2,T), efa.normality.stat,  apa(Item.total$r.cor,2,F))
-
-colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics","Item-Total Correlation")
-rownameprefix <- "Item"
-rownamesufix <- seq(1:48)
-my.names <- paste(rownameprefix,rownamesufix, sep = "" )
-rownames(Des.combined) = (my.names)
-```
-
-```{r CorrMatrixAppB, include=FALSE, warning=F,message=F}
-#Polychoric Correlation matrix
-
-correlations <- polychoric(EFA.data, correct = 0)
-upper <- correlations$rho[upper.tri(correlations$rho, diag = F)]
-
-min.cor.1 <- apa(min(abs(upper)),2,F) #minimum cor.coefficient of the matrix
-max.cor.1 <- apa(max(abs(upper)),2,F) # max. correlation coefficient of the matrix
-
-determinets <- det(correlations$rho) 
-# Calculating the percentage of correlations higher than .30
-
-BigR = sum(correlations$rho >= abs(.30) & correlations$rho < abs(1.0), na.rm =T)/2 
-totR = length(EFA.data)*(length(EFA.data)-1)/2
-cor.per.1 <- print (BigR/totR)*100
-```
-
-```{r ParallelEFAAppB, include=FALSE}
-
-# Parallel analysis
-Horn <- paran(correlations$rho, iterations=500, centile=0, quietly=FALSE,
-           status=TRUE, all=FALSE, cfa=FALSE, graph=TRUE,
-           color=TRUE, col=c("black","red","blue"),
-           lty=c(1,2,3), lwd=1, legend=TRUE, 
-           width=640, height=640, grdevice=png, seed=0, mat=NA, n=NA)
-
-Adjusted.EV <- data.frame(Horn$AdjEv)
-Adjusted.EV$type = c('Adjusted Ev')
-Adjusted.EV$num = c(row.names(Adjusted.EV))
-Adjusted.EV$num = as.numeric(Adjusted.EV$num)
-colnames(Adjusted.EV) = c('eigenvalue', 'type', 'num')
-
-Random.EV <- data.frame(Horn$RndEv)
-Random.EV$type = c('Random EV')
-Random.EV$num = c(row.names(Random.EV))
-Random.EV$num = as.numeric(Random.EV$num)
-colnames(Random.EV) = c('eigenvalue', 'type', 'num')
-
-Unadjusted.EV <- data.frame(Horn$Ev)
-Unadjusted.EV$type = c('Unadjusted EV')
-Unadjusted.EV$num = c(row.names(Unadjusted.EV))
-Unadjusted.EV$num = as.numeric(Unadjusted.EV$num)
-colnames(Unadjusted.EV) = c('eigenvalue', 'type', 'num')
-
-parallel = ggplot(Adjusted.EV, aes(x=num, y=eigenvalue, shape=type, color=type)) +
-  #Add lines connecting data points
-  geom_line()+
-    geom_line(data = Random.EV) +
-  geom_line(data = Unadjusted.EV)+
-    #Add the data points.
-  geom_point(size=1)+
-  geom_point(data = Random.EV, size=1)+
-  geom_point(data = Unadjusted.EV, size=1)+
-  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
-   #Label the x-axis 'Factor Number', and ensure that it ranges from 1-max # of factors, increasing by one with each 'tick' mark.
-  scale_x_continuous(name='Factor Number', limits=c(0, 48),breaks=seq(0,48,4))+
-    #Add vertical line indicating parallel analysis suggested max # of factors to retain
-  geom_hline(yintercept=1, linetype = 'dashed') + apatheme
-
-```
-
-```{r ScreePlotAppB, include=FALSE}
-Scree <- scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
-      hline=NULL,add=F)
-
-FA.Scree <- data.frame(Scree$fv)
-FA.Scree$type = c('Factor Analysis')
-FA.Scree$num = c(row.names(FA.Scree))
-FA.Scree$num = as.numeric(FA.Scree$num)
-colnames(FA.Scree) = c('eigenvalue', 'type', 'num')
-
-PA.Scree <- data.frame(Scree$pcv)
-PA.Scree$type = c('Principal Component Analysis')
-PA.Scree$num = c(row.names(PA.Scree))
-PA.Scree$num = as.numeric(PA.Scree$num)
-colnames(PA.Scree) = c('eigenvalue', 'type', 'num')
-
-scree.plot <-ggplot(FA.Scree, aes(x=num, y=eigenvalue,color=type, shape=type))+
-   geom_line()+
-  geom_line(data = PA.Scree)+ 
-  geom_point(size=1)+
-  geom_point(data = PA.Scree, size=1)+
-  scale_y_continuous(name="Eigen Value", limits=c(0, 10), breaks=seq(0,10,2)) +
-  scale_x_continuous(name='Factor Number', limits=c(0, 48),breaks=seq(0,48,4))+
-  geom_hline(yintercept=1, linetype = 'dashed') + apatheme 
-```
-
-```{r MAPefaAppB, include=FALSE}
-#MAP
-psych::VSS(EFA.data, rotate = "varimax", fm = 'minres', n.obs =428 )
-```
-
-Table \@ref(tab:tabDesAppB) summarizes the univariate descriptive statistics for the 48 items with un-merged options.
-Some of the items were skewed with high Kurtosis values.
-Our data violated both univariate normality (Shapiro-Wilk statistics) and multivariate normality assumptions [Marida's test].
-Multivariate skew was = `r printnum(mardia.1$b1p)` (p <0.001) and multivariate kurtosis was = `r printnum(mardia.1$b2p)` (p <0.001).
-Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen.
-Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy.
-The overall KMO vale for 48 items was `r printnum(KMO.1$MSA)` which was above the cutoff value (.50) indicating a mediocre sample.
-Bartlett's test of sphericity, $\chi^2$ (`r bartlet.1$df`) = `r apa(bartlet.1$chisq, 2, T)`, p < .001 indicated the correlations between items are adequate for the EFA.
-However only `r apa(cor.per.1, 2,T)`% of the inter-item correlation coefficients were greater than .30.
-The absolute value of inter-item correlation ranged between `r min.cor.1` to `r max.cor.1`.Figure \@ref(fig:corunm) depicts the correlation matrix.
-For un-merged response option Horn's parallel analysis with 500 iterations indicated a five-factor solution.
-However, Scree plot and the MAP method suggested 6-factor solution.
-five-factor solution .
-As a result, we tested both five-factor and six-factor solutions.
-The six factor solution yielded a factor with only two salient loading (Table \@ref(tab:EFAsix).
-Thus we reject the six factor solution.
-The five factor solution retained 24 items (Table \@ref(tab:efaunmerged)).
-However the factors are less interpretable in terms of common theme.
-Thus we reject the five factor solution.
-
-```{r tabDesAppB, results='asis'}
-apa_table(Des.combined, caption = "Descriptive Statistics for Unmerged response options",  note = "*p<.001", longtable =T)
-```
-
-```{r corunm, fig.cap="Correlation plot of the items [Unmerged response options]",  out.width="100%"}
-
-ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
-           ggtheme = ggplot2::theme_minimal, tl.cex = 6,tl.srt = 90 )
-#p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
-#to show pvalue in the fig add p.mat=p.mat
-```
-
-```{r facIdFigAppB,  fig.cap='Factor Identification  (A) Parallel analysis (B) Scree Plot [Unmerged response options]', warning=FALSE}
-cowplot::plot_grid(parallel, scree.plot, labels = "AUTO",ncol=1, label_size = 8,align = "v")
-
 ```
@@
 ```{r efaunmerged, results='asis'}
-apa_table(efa.table, caption = "Factor loadings and communality of the retained items in five factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T)
+apa_table(efa.table, caption = "Factor loadings and communality of the retained items in five factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T, font_size = "small")
 ```
@@
 ```{r EFAsix, results='asis'}
-apa_table(efa.table.2, caption = "Factor loadings and communality of the retained items in six factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T)
+apa_table(efa.table.2, caption = "Factor loadings and communality of the retained items in six factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T, font_size = "small")
 ```
 
-# Items Retained in the Five Factor Solution [Unmerged Responses]
+## Items Retained in the Five Factor Solution [Unmerged Responses]
 
@@
 
-```{r EFAResidualsAppB, eval=FALSE, fig.cap=' Histogram of residulas:  five-factor solution', warning=FALSE, include=FALSE, results='asis'}
-hist(residual.5F,  main = NULL, xlab = "Five-factor solution", ylim=c(0, 400))
-abline(h =35, lwd = 2, lty = 2)
-abline(v =.05,lwd = 2, lty = 2)
-```
-
-# Geographic Locations of Survey Participants
 ```{r Timetab, include=FALSE, warning=F,message=FALSE}

### 2022-01-02 appendix-3.Rmd
Sup.files updated

```{r configure, include=FALSE}
library(Hmisc)
data <- readRDS("leba_2021-09-08.rds")
sem.data <- data[, 9:56] 
prefix <- "item"
sufix <- c(1:48)
colnam <- paste(prefix,sufix, sep = "" )
colnames(sem.data) <- colnam
```

**Disclaimer**: This is a non-public version of LEBA (dated \today) and still a work in progress. Please do not distribute!

LEBA captures light exposure-related behaviours on a 5 point Likert type scale ranging from 1 to 5 (Never/Does not apply/I don't know = 1; Rarely = 2; Sometimes = 3; Often = 4; Always = 5). The score of each factor is calculated by the summation of scores of items belonging to the corresponding factor. The following instruction is given before displaying the items: "Please indicate how often you performed the following behaviours in the past 4 weeks."

\newpage

\blandscape

# LEBA Long Form (23 Items)

|     | Items                      | Never | Rarely | Sometimes | Often | Always |
|-----|----------------------------|-------|--------|-----------|-------|--------|
| 1   | `r label(sem.data$item16)` |       |        |           |       |        |
| 2   | `r label(sem.data$item17)` |       |        |           |       |        |
| 3   | `r label(sem.data$item36)` |       |        |           |       |        |
| 4   | `r label(sem.data$item8)`  |       |        |           |       |        |
| 5   | `r label(sem.data$item10)` |       |        |           |       |        |
| 6   | `r label(sem.data$item9)`  |       |        |           |       |        |
| 7   | `r label(sem.data$item11)` |       |        |           |       |        |
| 8   | `r label(sem.data$item12)` |       |        |           |       |        |
| 9   | `r label(sem.data$item7)`  |       |        |           |       |        |
| 10  | `r label(sem.data$item27)` |       |        |           |       |        |
| 11  | `r label(sem.data$item3)`  |       |        |           |       |        |
| 12  | `r label(sem.data$item40)` |       |        |           |       |        |
| 13  | `r label(sem.data$item30)` |       |        |           |       |        |
| 14  | `r label(sem.data$item41)` |       |        |           |       |        |
| 15  | `r label(sem.data$item32)` |       |        |           |       |        |
| 16  | `r label(sem.data$item35)` |       |        |           |       |        |
| 17  | `r label(sem.data$item38)` |       |        |           |       |        |
| 18  | `r label(sem.data$item33)` |       |        |           |       |        |
| 19  | `r label(sem.data$item46)` |       |        |           |       |        |
| 20  | `r label(sem.data$item45)` |       |        |           |       |        |
| 21  | `r label(sem.data$item25)` |       |        |           |       |        |
| 22  | `r label(sem.data$item4)`  |       |        |           |       |        |
| 23  | `r label(sem.data$item1)`  |       |        |           |       |        |

\elandscape

\newpage

\blandscape

## Latent Structure, Reliability and Structural Validity

The long form of LEBA consists 23 items with five factors.

| Factor names                                      | Items                    | Reliability Coefficients: ordinal alpha |
|---------------------------------------------------|--------------------------|-----------------------------------------|
| F1: Wearing blue light filters                    | 1-3                      | .96                                     |
| F2: Spending time outdoors                        | 4-9 (Item 4 is reversed) | .83                                     |
| F3: Using phone and smartwatch in bed             | 10-14                    | .70                                     |
| F4: Using light before bedtime                    | 15-18                    | .69                                     |
| F5: Using light in the morning and during daytime | 19-23                    | .52                                     |
| McDonald's Omega coefficient for the total scale  |                          | .73 (Total scale)                       |

LEBA -long form showed satisfactory structural validity (CFI =.97; TLI = .96; RMSEA = .05\[.04-.06, 90% CI\]; SRMR = .09).

## How to cite:

\elandscape

\newpage

\blandscape

# LEBA Short Form (18 Items)

|     | Short Form (18 Items)      | Never | Rarely | Sometimes | Often | Always |
|-----|----------------------------|-------|--------|-----------|-------|--------|
| 01  | `r label(sem.data$item16)` |       |        |           |       |        |
| 02  | `r label(sem.data$item17)` |       |        |           |       |        |
| 03  | `r label(sem.data$item36)` |       |        |           |       |        |
| 04  | `r label(sem.data$item8)`  |       |        |           |       |        |
| 05  | `r label(sem.data$item9)`  |       |        |           |       |        |
| 06  | `r label(sem.data$item10)` |       |        |           |       |        |
| 07  | `r label(sem.data$item11)` |       |        |           |       |        |
| 08  | `r label(sem.data$item12)` |       |        |           |       |        |
| 09  | `r label(sem.data$item7)`  |       |        |           |       |        |
| 10  | `r label(sem.data$item27)` |       |        |           |       |        |
| 11  | `r label(sem.data$item3)`  |       |        |           |       |        |
| 12  | `r label(sem.data$item40)` |       |        |           |       |        |
| 13  | `r label(sem.data$item32)` |       |        |           |       |        |
| 14  | `r label(sem.data$item35)` |       |        |           |       |        |
| 15  | `r label(sem.data$item33)` |       |        |           |       |        |
| 16  | `r label(sem.data$item46)` |       |        |           |       |        |
| 17  | `r label(sem.data$item45)` |       |        |           |       |        |
| 18  | `r label(sem.data$item4)`  |       |        |           |       |        |

\elandscape

\newpage

\blandscape

## Latent Structure, Reliability and Structural Validity

The short form of LEBA consists 23 items with five factors.

| Factor names                                          | Items                    |
|-------------------------------------------------------|--------------------------|
| **F1: Wearing blue light filters**                    | 1-3                      |
| **F2: Spending time outdoors**                        | 4-8 (Item 4 is reversed) |
| **F3: Using phone and smart-watch in bed**            | 9-11                     |
| **F4: Using light before bedtime**                    | 12-14                    |
| **F5: Using light in the morning and during daytime** | 15-17                    |

## How to cite:

\elandscape

### 2022-01-02 manuscript.Rmd
Sup.files updated

@@
 # Results
-
 ```{r ggplot2, include=F}
@@
 Figure \@ref(fig:figCor) depicts the correlation matrix.
-
 ```{r tabDes,results='asis'}
@@
 Subsequently, we fitted a six-factor solution.
-However, a factor emerged with only one salient variable loading in the six-factor solution, thus disqualifying the six-factor solution (Sup.Table \@ref(tab:sixFacTab)).
+However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (Sup.Table \@ref(tab:sixFacTab)).
 Internal consistency reliability coefficient Cronbach's alpha assumes all the factor-loadings of the items under a factor are equal [@graham2006congeneric; @novick1967coefficient] which is not the case in our sample.
@@
 Internal consistency ordinal $\alpha$ for the five factors of LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)` respectively.
-We also estimated the internal consistency reliability of the total scale using Mcdonald's $\omega$ (total) coefficient which is a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
-McDonald's $\omega$(total) coefficient for the total scale was `r apa(rel.k[5,6],2,F)`.
+We also estimated the internal consistency reliability of the total scale using Mcdonald's $\omega_t$  coefficient which is a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
+McDonald's $\omega_t$ coefficient for the total scale was `r apa(rel.k[5,6],2,F)`.
 Figure \@ref(fig:figcfa) depicts the obtained CFA structure.
@@
 ## Measurement Invariance
+```{r InvarianceAnalysis_data, include=FALSE}
+invariance.data <- cbind(CFA.data, data$slypos_demographics_language.factor[429:690])
+colnames(invariance.data)[52] <- "English_Speaking"
+
+mi.count <- invariance.data %>% 
+  group_by(English_Speaking) %>% 
+  count() %>% 
+  as.data.frame()
+```
+
 Measurement invariance (MI) evaluates whether a construct has the psychometric equivalence and same meaning across groups or measurement occasions [@putnick2016measurement;@klinePrinciplesPracticeStructural2015].
-We used  structural equation modeling framework to assess the measurement invariance of our developed tool across two groups: **native English speakers** and **non-native English speakers**.
+We used  structural equation modeling framework to assess the measurement invariance of our developed tool across two groups: **native English speakers**(n= `r mi.count[1,2]`) and **non-native English speakers** (n = `r mi.count[2,2]`).
+For a detailed description these two groups please see Sup.
+Table \@ref(tab:midesp).
 Our measurement invariance testing involved successively comparing the nested models:  configural, metric, scalar, and residual invariance models with each others [@widaman1997exploring].
@@
 
-```{r InvarianceAnalysis_data, include=FALSE}
-invariance.data <- cbind(CFA.data, data$slypos_demographics_language.factor[429:690])
-colnames(invariance.data)[52] <- "English_Speaking"
-
-invariance.data %>% 
-  group_by(English_Speaking) %>% 
-  count()
-```
-
-```{r MIdes, include=FALSE}
-
-midata <- CFA.descriptives[,c(1:2,5:7)]
-colnames(midata) <- c("Age", "Gender",  "Native_Speaker", "Work/School", "Mode" )
-mides <- midata%>%
-  tbl_summary(
-    by = Native_Speaker,
-    statistic = list(all_continuous() ~ "{mean} ({sd})",
-                     all_categorical() ~ "{n} ({p}%)"),
-    digits = all_continuous() ~ 2,
-
-    missing = "no"
-    ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
-modify_header(label ~ "**Variable**") %>% separate_p_footnotes() %>%
-  modify_caption("Demographic Characteristics")
-
-as_tibble(mides) -> mides_tibble 
-as_kable_extra(mides, format = "latex",booktabs = T) -> mides_kable #save it as a knitr::kable
-
-```
-
 ```{r Invariancedetail, include=FALSE}
 # Configural invariance ####
-
 configural <- cfa(model = LB.model.Cor.2,
@@
 LEBA  appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990].The cosine similarities lie between .47 to .51.
-Flesch-Kincaid Grade Level [@flesch1948new] analysis on the the 23 items of our scale indicated required educational grade level was 3.33 and with a age abobe 8.33.
-
+Flesch-Kincaid Grade Level [@flesch1948new] analysis on the the 23 items of our scale indicated required educational grade level was 3.33 and with a age above 8.33.
 ```{r textanalysis}
-
 #devtools::install_github("unDocUMeantIt/koRpus")
@@
 library(koRpus.lang.en)
-
 ques <- tokenize("Table_raw/items.txt", 
@@
                            hyphen = NULL,
-                           index = c(
-                             "Flesch.Kincaid"),
+                           index = "Flesch.Kincaid",
                            parameters = list(),
-                           word.lists = list(Bormuth = NULL, Dale.Chall = NULL, Harris.Jacobson = NULL, Spache =
-                                               NULL),
+                           word.lists = list(Bormuth = NULL, Dale.Chall = NULL,                              Harris.Jacobson = NULL, Spache =NULL),
                            fileEncoding = "UTF-8",
@@
                            keep.input = NULL,
-                           as.feature = FALSE
-)
-
+                           as.feature = FALSE)
 ```
@@
           labels = "AUTO", label_size = 10)
-
 ```
@@
 All of the items had RMSEA value $\le$.06 indicating adequate fit.
-Figure \@ref(Sup.fig:personfit) depicts the person fit of out fitted models.
+Sup.Figure \@ref(fig:personfit) depicts the person fit of out fitted models.
 Person fit indicates the validity and meaningfulness of the fitted model at the participants latent trait level [@desjardinsHandbookEducationalMeasurement2018].
@@
 Exploratory factor analysis revealed a five factor solution with 25 items.
-("Wearing blue light filters", "Spending time outdoors", "Using phone and smart-watch in bed", "Using light before bedtime",  and "Using light in the morning and during daytime").The internal consistency reliability coefficient ordinal alpha ranged between `r apa(range(alpha.tab),2,F)`.
+("Wearing blue light filters", "Spending time outdoors", "Using phone and smart-watch in bed", "Using light before bedtime",  and "Using light in the morning and during daytime").
+The internal consistency reliability coefficient ordinal alpha ranged between `r apa(range(alpha.tab),2,F)`.
 As all the retained factors were meaningful and contributed essentially towards our aim we retained all five factors.
@@
 A CFA on a separate sample ((n = `r nrow(CFA.descriptives)` gave a five-factor solution (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR = `r apa(fit.2[10],2,F)`) after discarding two item.
-The internal consistency McDonald's $\omega_t$ of the five factors were  satisfactory (`r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`) Internal consistency reliability of the total scale (23 item) was also satisfactory, McDonald's $\omega_t$= `r apa(rel.k[5,6],2,F)`.
+The internal consistency McDonald's $\omega_t$ of the five factors were  satisfactory (`r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`) Internal consistency reliability of the total scale (23 items) was also satisfactory, McDonald's $\omega_t$= `r apa(rel.k[5,6],2,F)`.
 In the same sample, our measurement invariance analysis  revealed that the latent structure attained the residual measurement invariance across subgroups: male and female (CFI: `r apa (residual.fitm[5,1],2,F)`, TLI: `r apa (residual.fitm[6,1],2,F)`, SRMR: `r apa (residual.fitm[6,1],2,F)`).
@@
 The "Semantic Scale Network"(SSN) analysis [@rosenbusch2020semantic] on the retained 23 items showed "LEBA" was  related to  "Sleep Disturbance Scale For Children" (SDSC) [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990].
-Upon inspecting the item contents we found items under: "Using phone and smart-watch in bed" and "Using light before bedtime" have semantic overlap with the items of SDSC ans CIDI.
+Upon inspecting the item contents we found items under "Using phone and smart-watch in bed" and "Using light before bedtime" have semantic overlap with the items of SDSC ans CIDI.
 Items in those two scales were looking into behaviors related to sleep.
@@
 A confirmatory factor analysis with this 25-item scale again offered a five-factor solution, but this time two more item was discarded.
-The 25-item "Bangla version of Rotter’s I-E scale"LEBA" was found reliable and valid.
+The 23-item "LEBA" was found reliable and valid.
 A short-form of LEBA was developed using IRT analysis.
-IRT analysis gave a 18 item scale with  a good range of coverage across the underlying trait continuum.
+IRT analysis gave a 18-item scale with  a good range of coverage across the underlying trait continuum.
 All-in-all, we can recommend both forms to be used to capture individual’s light exposure related behavior

### 2022-01-04 manuscript.Rmd
All possible plots are in ggplot2

@@
 ```{r setup, warning=FALSE, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=1200)
+knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=1200, fig.width = 6,
+ fig.asp = 0.8,out.width = "80%")
 #options(knitr.duplicate.label = "allow")
@@
 }")
+library(jpeg)
 export_svg(Flowchart1) %>%
@@
   rsvg() %>%
-  png::writePNG("Manuscript.figures/Flowchart1.png", dpi = 1200)
+  writeJPEG("Manuscript.figures/Flowchart1.jpeg",bg = "white", quality = 1)
 
@@
 ```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='160%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/Flowchart1.png')
+knitr::include_graphics('Manuscript.figures/Flowchart1.jpeg')
 ```
@@
         panel.background = element_blank(),
-        #text=element_text(family = "Helvetica",),
+        #text=element_text(family = "Helvetica"),
+        axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 15),
+        axis.title.y = element_text(size = 15),
+        plot.title = element_text(size = 15),
+        legend.text = element_text(size = 15),
         legend.title=element_blank(),
@@
                                     size = 1))
+
 ```
@@
   apatheme +scale_color_manual(labels = c("Out side the convex Hull", "On the convex Hull"), values = c("red", "cyan2"))+theme(legend.position = "None")
+
 ```
@@
 ```{r factors, include=F}
-jpeg("Manuscript.figures/factors.png", width = 400, height = 800)
-cowplot::plot_grid(parallel, scree.plot,Hull, labels = "AUTO",ncol=1, label_size = 8,align = "v")
-```
-
-```{r facIdFig, out.height="350%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}
-knitr::include_graphics("Manuscript.figures/factors.png")
+fator <- cowplot::plot_grid(parallel, scree.plot,Hull, 
+                   labels = "AUTO",
+                   ncol=1, 
+                  align = "v", 
+                  label_size = 12,
+                  label_fontfamily = "serif",
+                  label_fontface = "plain")
+ggsave("Manuscript.figures/factors.png",fator, width = 6, height = 12, dpi = 600)
+```
+
+```{r facIdFig, out.height="100%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}
+
+knitr::include_graphics('Manuscript.figures/factors.png')
 
@@
   rsvg() %>%
-  png::writePNG("Manuscript.figures/EFAplot.png", dpi = 1200)
+  writeJPEG("Manuscript.figures/EFAplot.jpeg",bg = "white", quality = 1)
 
@@
 The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`.
-Figure \@ref(fig:EFAplot) depicts the obtained five-five factor structure.
-However, the histogram of the absolute values of non-redundant residual-correlations (Sup.Figure \@ref(fig:EFAResiduals)) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring.
+Figure \@ref(fig:EFAplot)(A) depicts the obtained five factor structure.
+However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:EFAplot)(B)) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring.
 [@desjardinsHandbookEducationalMeasurement2018].
@@
 
-```{r EFAplot, fig.align='center', fig.cap='Five Factor Solution', warning=FALSE, out.height="60%", out.width="100%", results='asis'}
-knitr::include_graphics('Manuscript.figures/EFAplot.png')
-
-```
-
 ```{r EFATable, results='asis'}
@@
 ```{r EFARes, message=FALSE, warning=FALSE, include=F}
-jpeg("Manuscript.figures/EFAResidual.png", width = 800, height = 750)
-hist(residual.5F,  main = NULL, xlab = "Residuals", ylim=c(0, 400))
-abline(h =51, lwd = 2, lty = 2)
-abline(v =.05,lwd = 2, lty = 2)
+#hist(residual.5F,  main = NULL, xlab = "Residuals", ylim=c(0, 400))
+#abline(h =51, lwd = 2, lty = 2)
+#abline(v =.05,lwd = 2, lty = 2)
+res.dat <- as.data.frame(unclass(residual.5F))
+residual.data <- as.data.frame(gather(res.dat, Items, Residuals))
+
+residual.plot <- ggplot(residual.data, aes(x=Residuals)) + geom_histogram(binwidth=.04, col=I("black"),fill=I("grey")) + xlim(-.2,.2)+ ylim(0,250)+apatheme +geom_vline(xintercept = .05)+
+  labs( y="Frequency")
+
+```
+
+```{r EFAplotprep, include=F}
+library(jpeg)
+library(png)
+library(cowplot)
+
+img1 <- readJPEG("Manuscript.figures/EFAplot.jpeg")
+
+p1 <- ggplot2::ggplot() + ggplot2::annotation_custom(grid::rasterGrob(img1,
+                                                                      width=NULL,
+                                                                      height=NULL),
+                                                     -Inf, Inf, -Inf, Inf)+apatheme
+
+EFAplot.1 <- plot_grid(
+ p1, residual.plot,
+  labels = "AUTO",
+  align="h",
+  ncol = 2,
+  label_size = 12,
+  label_fontfamily = "serif",
+  label_fontface = "plain",
+  label_y = .98,
+  label_x = .04
+)
+
+```
+
+```{r EFAplot, fig.align='center', fig.cap='(A) Five Factor Solution obtained in Exploratory Factor Analysis (B) Histogram of nonredundent residula correlations', warning=FALSE, out.height="80%", out.width="100%", results='asis'}
+EFAplot.1
+
 ```
@@
 
+```
+
+```{r efagt,include=F}
+efa.gt %>% 
+gt() %>% 
+# histogram and density plots
+  gtExtras::gt_sparkline(
+    hist_data,
+    type = "histogram",
+    line_color = "black", 
+    fill_color = "grey",
+    bw = 1,
+    same_limit = TRUE)%>%
+  gtExtras::gt_sparkline(
+    dens_data,
+    type = "density",
+    line_color = "black", 
+    fill_color = "grey",
+    bw = 0.75,
+    same_limit = TRUE
+  )%>%
+# format decimals
+  fmt_number(columns = mean:sd, decimals = 1) %>%
+# header
+  tab_header(
+    title = md("**LEBA**"),
+    subtitle = md("Summary Descriptives EFA Sample (N =428)")
+  ) %>% 
+  tab_footnote(
+    footnote = md("**Histogram**"),
+    locations = cells_column_labels(columns = hist_data)
+  ) %>%
+  tab_footnote(
+    footnote = md("**Density**"),
+    locations = cells_column_labels(columns = dens_data)
+  ) %>% 
+#create groups of columns
+tab_spanner(
+  label = "Items",
+  columns = Items
+) %>%
+  tab_spanner(
+    label = "Summary Statistics",
+    columns = nr:sd
+  ) %>%
+  tab_spanner(
+    label = "Graphics",
+    columns = hist_data:dens_data
+  ) %>% 
+  tab_spanner(
+    label = "Response Pattern",
+    columns = Never:Always
+  ) %>%
+# change column names to appear in the table
+cols_label(
+  Items = ("LEBA  Items"),
+  nr = ("n"),
+  mean = ("Mean"),
+  med = ("Median "),
+  sd = (("SD")),
+  hist_data = "Histogram",
+  dens_data = "Density"
+) %>%
+# set alignment as per wish
+  cols_align(
+    align = "center",
+    columns = everything()
+  ) %>%
+  opt_align_table_header(align = "left") %>%
+# add coloured dots and lines on the first column
+  gt_plt_dot(
+    mean,
+    Items,
+    palette = "ggthemes::fivethirtyeight") %>% 
+  gtsave("Manuscript.figures/efagt.png",vwidth = 7000)
+
+```
+
+```{r cfagt,include=F}
+cfa.gt %>% 
+gt() %>% 
+# histogram and density plots
+  gtExtras::gt_sparkline(
+    hist_data,
+    type = "histogram",
+    line_color = "black", 
+    fill_color = "grey",
+    bw = 1,
+    same_limit = TRUE)%>%
+  gtExtras::gt_sparkline(
+    dens_data,
+    type = "density",
+    line_color = "black", 
+    fill_color = "grey",
+    bw = 0.75,
+    same_limit = TRUE
+  )%>%
+# format decimals
+  fmt_number(columns = mean:sd, decimals = 1) %>%
+# header
+  tab_header(
+    title = md("**LEBA**"),
+    subtitle = md("Summary Descriptives CFA Sample (N =262)")
+  ) %>% 
+  tab_footnote(
+    footnote = md("**Histogram**"),
+    locations = cells_column_labels(columns = hist_data)
+  ) %>%
+  tab_footnote(
+    footnote = md("**Density**"),
+    locations = cells_column_labels(columns = dens_data)
+  ) %>% 
+#create groups of columns
+tab_spanner(
+  label = "Items",
+  columns = Items
+) %>%
+  tab_spanner(
+    label = "Summary Statistics",
+    columns = nr:sd
+  ) %>%
+  tab_spanner(
+    label = "Graphics",
+    columns = hist_data:dens_data
+  ) %>% 
+  tab_spanner(
+    label = "Response Pattern",
+    columns = Never:Always
+  ) %>%
+# change column names to appear in the table
+cols_label(
+  Items = ("LEBA Items"),
+  nr = ("n"),
+  mean = ("Mean"),
+  med = ("Median "),
+  sd = (("SD")),
+  hist_data = "Histogram",
+  dens_data = "Density"
+) %>%
+# set alignment as per wish
+  cols_align(
+    align = "center",
+    columns = everything()
+  ) %>%
+  opt_align_table_header(align = "left") %>%
+# add coloured dots and lines on the first column
+  gt_plt_dot(
+    mean,
+    Items,
+    palette = "ggthemes::fivethirtyeight") %>% 
+  gtsave("Manuscript.figures/cfagt.png",vwidth = 7000)
+
+```
+
+```{r eval=FALSE, include=FALSE}
 gt.fullTable <-  rbind( efa.gt, cfa.gt) %>% 
@@
 
-```{r gtPic, echo=FALSE, out.height="100%", out.width="200%", fig.cap= ' Summary Descriptives of CFA and EFA Sample'}
-knitr::include_graphics('Manuscript.figures/gt.png')
-
-```
-
+```{r efagtPic, echo=FALSE, out.height="100%", out.width= '100%', fig.cap= ' Summary Descriptives EFA Sample'}
+knitr::include_graphics('Manuscript.figures/efagt.png')
+
+```
+
+```{r cfagtPic, echo=FALSE, out.height="100%", out.width= '100%', fig.cap= ' Summary Descriptives of CFA Sample'}
+knitr::include_graphics('Manuscript.figures/cfagt.png')
+
+```
 ## Confirmatory Factor Analysis
@@
 
-```{r f1itminf, include=F, warning=F}
-
-jpeg("Manuscript.figures/F1testinfo.png", width = 800, height = 750)
-
-plot_grid(
-  F1title, f1itemplot,
-  ncol = 1,
-  # rel_heights values control vertical title margins
-  rel_heights = c(0.1, 1)
-
-)
-dev.off()
-```
-
-```{r f2iteminf, include=F, warning=F}
-jpeg("Manuscript.figures/F2testinfo.png", width = 800, height = 750)
-plot_grid(
-  F2title, f2itemplot,
-  ncol = 1,
-  # rel_heights values control vertical title margins
-  rel_heights = c(0.1, 1)
-)
-dev.off()
-```
-
-```{r f3iteminf, include=F, warning=F}
-jpeg("Manuscript.figures/F3testinfo.png", width = 800, height = 750)
-plot_grid(
-  F3title, f3itemplot,
-  ncol = 1,
-  # rel_heights values control vertical title margins
-  rel_heights = c(0.1, 1)
-)
-dev.off()
-```
-
-```{r f4iteminf, include=F, warning=F}
-jpeg("Manuscript.figures/F4testinfo.png", width = 800, height = 750)
-plot_grid(
-  F4title, f4itemplot,
-  ncol = 1,
-  # rel_heights values control vertical title margins
-  rel_heights = c(0.1, 1)
-)
-dev.off()
-```
-
-```{r f5iteminf, include=F, warning=F}
-jpeg("Manuscript.figures/F5testinfo.png", width = 800, height = 750)
-plot_grid(
-  F5title, f5itemplot,
-  ncol = 1,
-  # rel_heights values control vertical title margins
-  rel_heights = c(0.1, 1)
-)
-dev.off()
+```{r iteminfoggplot3, include=F}
+Theta <- matrix(seq(-6,6, by = .1))
+
+##Item Extraction
+F1.item1 <- extract.item(F1_fit, 1)#item number
+F1.item2 <- extract.item(F1_fit, 2)
+F1.item3 <- extract.item(F1_fit, 3)
+F2.item1 <- extract.item(F2_fit, 1)
+F2.item2 <- extract.item(F2_fit, 2)
+F2.item3 <- extract.item(F2_fit, 3)
+F2.item4 <- extract.item(F2_fit, 4)
+F2.item5 <- extract.item(F2_fit, 5)
+F2.item6 <- extract.item(F2_fit, 6)
+F3.item1 <- extract.item(F3_fit, 1)
+F3.item2 <- extract.item(F3_fit, 2)
+F3.item3 <- extract.item(F3_fit, 3)
+F3.item4 <- extract.item(F3_fit, 4)
+F3.item5 <- extract.item(F3_fit, 5)
+F4.item1 <- extract.item(F4_fit, 1)
+F4.item2 <- extract.item(F4_fit, 2)
+F4.item3 <- extract.item(F4_fit, 3)
+F4.item4 <- extract.item(F4_fit, 4)
+F5.item1 <- extract.item(F5_fit, 1)
+F5.item2 <- extract.item(F5_fit, 2)
+F5.item3 <- extract.item(F5_fit, 3)
+F5.item4 <- extract.item(F5_fit, 4)
+F5.item5 <- extract.item(F5_fit, 5)
+
+##Item Info
+F1.item.info.1 <- iteminfo(F1.item1, Theta)
+F1.item.info.2 <- iteminfo(F1.item2, Theta)
+F1.item.info.3 <- iteminfo(F1.item3, Theta)
+F2.item.info.1 <- iteminfo(F2.item1, Theta)
+F2.item.info.2 <- iteminfo(F2.item2, Theta)
+F2.item.info.3 <- iteminfo(F2.item3, Theta)
+F2.item.info.4 <- iteminfo(F2.item4, Theta)
+F2.item.info.5 <- iteminfo(F2.item5, Theta)
+F2.item.info.6 <- iteminfo(F2.item6, Theta)
+F3.item.info.1 <- iteminfo(F3.item1, Theta)
+F3.item.info.2 <- iteminfo(F3.item2, Theta)
+F3.item.info.3 <- iteminfo(F3.item3, Theta)
+F3.item.info.4 <- iteminfo(F3.item4, Theta)
+F3.item.info.5 <- iteminfo(F3.item5, Theta)
+F4.item.info.1 <- iteminfo(F4.item1, Theta)
+F4.item.info.2 <- iteminfo(F4.item2, Theta)
+F4.item.info.3 <- iteminfo(F4.item3, Theta)
+F4.item.info.4 <- iteminfo(F4.item4, Theta)
+F5.item.info.1 <- iteminfo(F5.item1, Theta)
+F5.item.info.2 <- iteminfo(F5.item2, Theta)
+F5.item.info.3 <- iteminfo(F5.item3, Theta)
+F5.item.info.4 <- iteminfo(F5.item4, Theta)
+F5.item.info.5 <- iteminfo(F5.item5, Theta)
+
+#Data frame
+
+F1.item.info.data <- as.data.frame(cbind(Theta, F1.item.info.1, 
+                                              F1.item.info.2,
+                                              F1.item.info.3))
+
+F2.item.info.data <- as.data.frame(cbind(Theta, F2.item.info.1, 
+                                              F2.item.info.2,
+                                              F2.item.info.3,
+                                         F2.item.info.4,
+                                         F2.item.info.5,
+                                         F2.item.info.6))
+
+F3.item.info.data <- as.data.frame(cbind(Theta, F3.item.info.1, 
+                                              F3.item.info.2,
+                                              F3.item.info.3,
+                                         F3.item.info.4,
+                                         F3.item.info.5))
+
+F4.item.info.data <- as.data.frame(cbind(Theta, F4.item.info.1, 
+                                              F4.item.info.2,
+                                              F4.item.info.3,
+                                         F4.item.info.4))
+F5.item.info.data <- as.data.frame(cbind(Theta, F5.item.info.1, 
+                                              F5.item.info.2,
+                                              F5.item.info.3,
+                                         F5.item.info.4,
+                                         F5.item.info.5))
+
+## GGplot2 item-info
+###F1
+F1.iteminfo.1 <- ggplot(F1.item.info.data , aes(x=Theta, y=F1.item.info.1)) +
+  geom_line()  +apatheme +labs(y="Item Information", title = "F1 item16") + geom_hline(yintercept = .20, colour ="red")
+F1.iteminfo.2 <- ggplot(F1.item.info.data , aes(x=Theta, y=F1.item.info.2)) +
+  geom_line()  +apatheme +labs(y="Item Information", title = "F1 item36")+geom_hline(yintercept = .20, colour ="red")
+F1.iteminfo.3 <- ggplot(F1.item.info.data , aes(x=Theta, y=F1.item.info.3)) +
+  geom_line()  +apatheme +labs(y="Item Information", title = "F1 item17")+ylim(0,6)+geom_hline(yintercept = .20, colour ="red")
+
+###F2
+
+F2.iteminfo.1 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.1)) +
+  geom_line()  +apatheme +labs(y="Item Information", title = "F2 item11")+ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+
+F2.iteminfo.2 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.2)) +
+  geom_line()  + apatheme +
+  labs(y="Item Information", title = "F2 item10")+
+  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+
+F2.iteminfo.3 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.3)) +
+  geom_line()  +apatheme +
+  labs(y="Item Information", title = "F2 item12")+
+  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+
+F2.iteminfo.4 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.4)) +
+  geom_line()  +apatheme +
+  labs(y="Item Information", title = "F2 item07")+ylim(0,3)+
+  geom_hline(yintercept = .20, colour ="red")
+
+F2.iteminfo.5 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.5)) +
+  geom_line()  +apatheme +
+  labs(y="Item Information", title = "F2 item08")+ylim(0,3)+
+  geom_hline(yintercept = .20, colour ="red")
+
+F2.iteminfo.6 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.6)) +
+  geom_line()  +apatheme +
+  labs(y="Item Information", title = "F2 item09")+ylim(0,3)+
+  geom_hline(yintercept = .20, colour ="red")
+
+###F3
+F3.iteminfo.1 <- ggplot(F3.item.info.data , aes(x=Theta, y=F3.item.info.1)) +
+  geom_line()  +apatheme +labs(y="Item Information", title = "F3 item27")+
+  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+
+F3.iteminfo.2 <- ggplot(F3.item.info.data , aes(x=Theta, y=F3.item.info.2)) +
+  geom_line()  +apatheme +
+  labs(y="Item Information",title = "F3 item03")+
+  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+
+F3.iteminfo.3 <- ggplot(F3.item.info.data , aes(x=Theta, y=F3.item.info.3)) +
+  geom_line()  +apatheme +
+  labs(y="Item Information",title = "F3 item40")+
+  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+
+F3.iteminfo.4 <- ggplot(F3.item.info.data , aes(x=Theta, y=F3.item.info.4)) +
+  geom_line()  +apatheme +
+  labs(y="Item Information",title = "F3 item30")+
+  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+
+F3.iteminfo.5 <- ggplot(F3.item.info.data , aes(x=Theta, y=F3.item.info.5)) +
+  geom_line()  +apatheme +
+  labs(y="Item Information", title = "F3 item41")+
+  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+
+#F4
+
+F4.iteminfo.1 <- ggplot(F4.item.info.data , aes(x=Theta, y=F4.item.info.1)) +
+  geom_line()  +apatheme +labs(y="Item Information", title = "F4 item32")+
+  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+
+F4.iteminfo.2 <- ggplot(F4.item.info.data , aes(x=Theta, y=F4.item.info.2)) +
+  geom_line()  +apatheme +
+  labs(y="Item Information",title = "F4 item35")+
+  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+
+F4.iteminfo.3 <- ggplot(F4.item.info.data , aes(x=Theta, y=F4.item.info.3)) +
+  geom_line()  +apatheme +
+  labs(y="Item Information",title = "F4 item38")+
+  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+
+F4.iteminfo.4 <- ggplot(F4.item.info.data , aes(x=Theta, y=F4.item.info.4)) +
+  geom_line()  +apatheme +
+  labs(y="Item Information",title = "F4 item33")+geom_hline(yintercept = .20, colour ="red")
+
+#F5
+
+F5.iteminfo.1 <- ggplot(F3.item.info.data , aes(x=Theta, y=F5.item.info.1)) +
+  geom_line()  +apatheme +labs(y="Item Information", title = "F5 item46")+
+  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+
+F5.iteminfo.2 <- ggplot(F3.item.info.data , aes(x=Theta, y=F5.item.info.2)) +
+  geom_line()  +apatheme +
+  labs(y="Item Information",title = "F5 item45")+
+  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+
+F5.iteminfo.3 <- ggplot(F3.item.info.data , aes(x=Theta, y=F5.item.info.3)) +
+  geom_line()  +apatheme +
+  labs(y="Item Information",title = "F5 item25")+
+  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+
+F5.iteminfo.4 <- ggplot(F3.item.info.data , aes(x=Theta, y=F5.item.info.4)) +
+  geom_line()  +apatheme +
+  labs(y="Item Information",title = "F5 item04")+
+ geom_hline(yintercept = .20, colour ="red")
+
+F5.iteminfo.5 <- ggplot(F3.item.info.data , aes(x=Theta, y=F5.item.info.5)) +
+  geom_line()  +apatheme +
+  labs(y="Item Information", title = "F5 item01")+
+  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+
+#Panel plots
+
+F1.itemplots <- cowplot::plot_grid(F1.iteminfo.1,F1.iteminfo.2, F1.iteminfo.3,
+                   labels = "AUTO",
+                     align="v",
+                     ncol = 2,
+                     label_size = 12,
+                     label_fontfamily = "serif",
+                     label_fontface = "plain")
+ggsave("Manuscript.figures/F1.itemplots.png",F1.itemplots, width = 10, height = 12, dpi = 600,bg = "white")
+
+F2.itemplots <- cowplot::plot_grid(F2.iteminfo.1,F2.iteminfo.2, F2.iteminfo.3,
+                                   F2.iteminfo.4,F2.iteminfo.5,F2.iteminfo.6,
+                   labels = "AUTO",
+                     align="v",
+                     ncol = 2,
+                     label_size = 12,
+                     label_fontfamily = "serif",
+                     label_fontface = "plain")
+ggsave("Manuscript.figures/F2.itemplots.png",F2.itemplots, width = 10, height = 12, dpi = 600, bg = "white")
+
+F3.itemplots <- cowplot::plot_grid(F3.iteminfo.1,F3.iteminfo.2, F3.iteminfo.3,
+                                   F3.iteminfo.4,F3.iteminfo.5,
+                 labels = "AUTO",
+                     align="v",
+                     ncol = 2,
+                     label_size = 12,
+                     label_fontfamily = "serif",
+                     label_fontface = "plain")
+ggsave("Manuscript.figures/F3.itemplots.png",F3.itemplots, width = 10, height = 12, dpi = 600,bg = "white")
+
+F4.itemplots <- cowplot::plot_grid(F4.iteminfo.1,F4.iteminfo.2, F4.iteminfo.3,
+                                   F4.iteminfo.4,
+                   labels = "AUTO",
+                     align="v",
+                     ncol = 2,
+                     label_size = 12,
+                     label_fontfamily = "serif",
+                     label_fontface = "plain")
+ggsave("Manuscript.figures/F4.itemplots.png",F4.itemplots, width = 10, height = 12, dpi = 600,bg = "white")
+
+F5.itemplots <- cowplot::plot_grid(F5.iteminfo.1,F5.iteminfo.2, F5.iteminfo.3,
+                                   F5.iteminfo.4,F5.iteminfo.5,
+                   labels = "AUTO",
+                     align="v",
+                     ncol = 2,
+                     label_size = 12,
+                     label_fontfamily = "serif",
+                     label_fontface = "plain")
+ggsave("Manuscript.figures/F5.itemplots.png",F5.itemplots, width = 10, height = 12, dpi = 600, bg = "white")
 ```
@@
 apa_table(itemparameters, caption = "IRT Item parameters for the LEBA Scale", note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
-```
-
-```{r itmeinfo, eval=FALSE, fig.cap="Item information curves (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, include=FALSE, out.height="60%", out.width="100%"}
-knitr::include_graphics('Manuscript.figures/iteminfo.png')
-
 ```
@@
 nrow(F1.personfit_model_misfits)
-hist(F1.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-F1.person <- ggplot(F1.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5)+geom_vline(xintercept = -2)+
-  labs( y="Number of Participants", x = "Zh Statistics: F1")+apatheme
+
+F1.person <- ggplot(F1.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5,col=I("black"),fill=I("grey"))+geom_vline(xintercept = -2)+
+  labs( y="Number of Participants", x = "Zh Statistics: F1")+apatheme+ ylim(0,600) + xlim(-4,2)
 
@@
 nrow(F2.personfit_model_misfits)
-hist(F2.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-
-F2.person <- ggplot(F2.personfit, aes(x=Zh)) + geom_histogram(binwidth=.4)+
+
+F2.person <- ggplot(F2.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill=I("grey"))+
   scale_x_continuous(limits = c(-5, 1))+geom_vline(xintercept = -2)+
-  labs( y="Number of Participants", x = "Zh Statistics: F2")+apatheme
+  labs( y="Number of Participants", x = "Zh Statistics: F2")+apatheme+ylim(0,600) + xlim(-4,2)
 
@@
 nrow(F3.personfit_model_misfits)
-hist(F3.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-
-F3.person <- ggplot(F3.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5)+geom_vline(xintercept = -2)+
-  labs( y="Number of Participants", x = "Zh Statistics: F3")+apatheme
+
+F3.person <- ggplot(F3.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill=I("grey"))+geom_vline(xintercept = -2)+
+  labs( y="Number of Participants", x = "Zh Statistics: F3")+apatheme+ylim(0,600) + xlim(-4,2)
 
@@
 nrow(F4.personfit_model_misfits)
-hist(F4.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-
-F4.person <- ggplot(F4.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5)+geom_vline(xintercept = -2)+
-  labs( y="Number of Participants", x = "Zh Statistics: F4")+apatheme
+
+F4.person <- ggplot(F4.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill=I("grey"))+geom_vline(xintercept = -2)+
+  labs( y="Number of Participants", x = "Zh Statistics: F4")+apatheme+ylim(0,600) + xlim(-4,2)
 
@@
 nrow(F5.personfit_model_misfits)
-hist(F5.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
-
-F5.person <- ggplot(F5.personfit, aes(x=Zh)) + geom_histogram(binwidth=.4)+geom_vline(xintercept = -2)+
-  labs( y="Number of Participants", x = "Zh Statistics:F5")+apatheme
+
+F5.person <- ggplot(F5.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill=I("grey"))+geom_vline(xintercept = -2)+
+  labs( y="Number of Participants", x = "Zh Statistics:F5")+apatheme+ylim(0,600) + xlim(-4,2)
 
@@
 
-```{r savetestinfo, include=FALSE, warning=F, message=F}
-jpeg("Manuscript.figures/testinfo.png", width = 800, height = 750)
-plot_grid(F1_test.info , F2_test.info.redu,F3_test.info.redu,F4_test.info.redu,F5_test.info,
-          labels = "AUTO", label_size = 10, align = "v" )
-dev.off()
-```
-
-```{r Testinfo, fig.cap="Test information curves (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="60%"}
-
-knitr::include_graphics('Manuscript.figures/testinfo.png')
+```{r testinfoggplot2, include=F}
+Theta <- matrix(seq(-6,6, by = .1))
+
+F1.T1 <- 0
+for(i in 1:ncol(F1)){
+  F1.T1 <- F1.T1 + iteminfo(extract.item(F1_fit, i), Theta)
+}
+
+F2.T1 <- 0
+for(i in 1:ncol(F2.redu)){
+  F2.T1 <- F2.T1 + iteminfo(extract.item(F2_fit.redu, i), Theta)
+}
+
+F3.T1 <- 0
+for(i in 1:ncol(F3.redu)){
+  F3.T1 <- F3.T1 + iteminfo(extract.item(F3_fit.redu, i), Theta)
+}
+
+F4.T1 <- 0
+for(i in 1:ncol(F4.redu)){
+  F4.T1 <- F4.T1 + iteminfo(extract.item(F4_fit.redu, i), Theta)
+}
+
+F5.T1 <- 0
+for(i in 1:ncol(F5.redu)){
+  F5.T1 <- F5.T1 + iteminfo(extract.item(F5_fit.redu, i), Theta)
+}
+
+F1.test.data <- as.data.frame(cbind(Theta, F1.T1))
+
+F2.test.data <- as.data.frame(cbind(Theta, F2.T1))
+
+F3.test.data <- as.data.frame(cbind(Theta, F3.T1))
+
+F4.test.data <- as.data.frame(cbind(Theta, F4.T1))
+
+F5.test.data <- as.data.frame(cbind(Theta, F5.T1))
+
+F1.tic <- ggplot(F1.test.data, aes(x=Theta, y=F1.T1)) +
+  geom_line()+apatheme+
+  labs(y="Test Information", title = "F1 Test Inforfamtion")
+
+F2.tic <- ggplot(F2.test.data, aes(x=Theta, y=F2.T1)) +
+  geom_line()+apatheme+
+  labs(y="Test Information", title = "F2 Test Inforfamtion")+ylim(0,8)
+
+F3.tic <- ggplot(F3.test.data, aes(x=Theta, y=F3.T1)) +
+  geom_line()+apatheme+
+  labs(y="Test Information", title = "F3 Test Inforfamtion")+ylim(0,6)
+
+F4.tic <- ggplot(F4.test.data, aes(x=Theta, y=F4.T1)) +
+  geom_line()+apatheme+
+  labs(y="Test Information", title = "F4 Test Inforfamtion")
+
+F5.tic <- ggplot(F5.test.data, aes(x=Theta, y=F5.T1)) +
+  geom_line()+apatheme+
+  labs(y="Test Information", title = "F5 Test Inforfamtion") +ylim(0,6)
+
+#panel TIC
+
+TIC <- cowplot::plot_grid(F1.tic,F2.tic, F3.tic,
+                                   F4.tic,F5.tic,
+                   labels = "AUTO",
+                     align="v",
+                     ncol = 2,
+                     label_size = 12,
+                     label_fontfamily = "serif",
+                     label_fontface = "plain")
+ggsave("Manuscript.figures/TIC.png",TIC, width = 10, height = 12, dpi = 600, bg = "white")
+
+```
+
+```{r Testinfo, fig.cap="Test information curves (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE}
+
+knitr::include_graphics('Manuscript.figures/TIC.png')
 ```
@@
 ```{r perfit, include=F}
-jpeg("Manuscript.figures/personfit.png", width = 800, height = 750)
-
-plot_grid(F1.person, F2.person,F3.person,F4.person,F5.person, 
-          labels = "AUTO", label_size = 10,align = "v")
+personfit <- plot_grid(F1.person, F2.person,F3.person,F4.person,F5.person, 
+          labels = "AUTO", label_size = 12,align = "v", ncol =2,
+                       label_fontfamily = "serif",
+                     label_fontface = "plain")
+
+ggsave("Manuscript.figures/personfit.png",personfit , width = 10, height = 12, dpi = 600, bg = "white")
 

### 2022-01-07 appendix-2.Rmd
Aesthetic Updates

@@
-```{r MinRes, include=F}
-library(psych)
-library(tabledown)
-library(kableExtra)#without this pdf rendering will not happen
+```{r factormp, warning=F}
+map <- readr::read_csv("Table_raw/map_stat")
+map1 <- (map$`MAP Statistic`)
 
+map1 <- MOTE::apa(map1,5,F)
+map1 <- as.character(map1)
+map1 <- as.data.frame(map1)
+colnames(map1) <- "MAP Statistics"
+map2 <- map[,-c(1,2)]
+map3 <- cbind(map1, map2)
+
+papaja::apa_table(map3, caption = "Map Statistics")
+```
+
+```{r MI, include=F, warning=F}
 data <- readRDS("leba_2021-09-08.rds")
@@
 
-#Separating the EFA and CFA(only items)
-sem.data <- data[, 9:56] #EFA & CFA data
-sem.data[ sem.data == 0] <- 1 #Merged "0"s and "1"s into "1"s
+mi.desc_table <- CFA.descriptives[,c(1,2,5,6,7)] %>%
+  tbl_summary(
+    by = slypos_demographics_language.factor,
+    statistic = list(all_continuous() ~ "{mean} ({sd})",
+                     all_categorical() ~ "{n} ({p}%)"),
+    digits = all_continuous() ~ 2,
+    label = list(slypos_demographics_age ~ "Age",
+                 slypos_demographics_sex.factor ~ "Sex",
+                 slypos_demographics_work_or_school.factor ~ "Occupational Status",
+                 slypos_demographics_school.factor ~ "Occupational setting"
+                 ),
+    missing = "no"
+    ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
+modify_header(label ~ "**Variable**") %>% separate_p_footnotes() %>%
+  modify_caption("Demographic Characteristics: Native English Speakers")
 
-## renaming the column-header
-prefix <- "item"
-sufix <- c(1:48)
-colnam <- paste(prefix,sufix, sep = "" )
-colnames(sem.data) <- colnam
-
-### EFA data
-EFA.data <- sem.data[1:428, ]
-#Polychoric Correlation matrix
-
-correlations <- psych::polychoric(EFA.data, correct = 0)
-
-#Supplementary EFA with Minres Extraction
-
-fa.5F.min.1 <- fa(r=correlations$rho, nfactors = 5, fm= "minres",rotate ="varimax",
-                residuals = TRUE, SMC = TRUE, n.obs =428)
-EE <- print(fa.5F.min.1, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.5F.min.1 <- dplyr::select(EFA.data ,
-                                    -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14))
-
-correlations.red.5F.min.1 <- polychoric(reduced.model.5F.min.1,correct = 0)
-
-fa.5F.min.2 <- fa(r=correlations.red.5F.min.1$rho, nfactors = 5, fm= "minres",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-FF <- print(fa.5F.min.2, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.5F.min.2 <- dplyr::select(EFA.data, -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14, item34, item47, item21, item13))
-
-correlations.red.5F.min.2 <- polychoric(reduced.model.5F.min.2, correct = 0)
-
-fa.5F.min.3 <- fa(r=correlations.red.5F.min.2$rho, nfactors = 5, fm= "minres",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-GG <- print(fa.5F.min.3, cut = .3, digits = 3, sort = TRUE)
-
-minresTab <- tabledown::fac.tab(fa.5F.min.3, cut =.3,complexity = F)
+mides_kable <-  as_kable_extra(mi.desc_table, format = "latex",booktabs = T) 
 ```
 
-```{r MinResTab}
-papaja::apa_table(minresTab,  caption = "Factor loadings and communality of the retained items (Minmum Residual)", note = "Only loading higher than .30 is reported", longtable=T, font_size = "small")
+```{r midesp, warning=F, message=F}
+mides_kable %>% 
+  kable_styling(latex_options = c("scale_down")) 
 ```
 
-# Factor analysis with six factors
-
-```{r sixFac, include=F}
-# EFA with 6 factor (rejected)
-
-#correlations <- polychoric(EFA.factor, correct = 0)
-
-fa.6F.1 <- fa(r=correlations$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-II <- print(fa.6F.1, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.6F.1 <- dplyr::select(EFA.data ,
-                                    -c(item34, item44, item48, item43, item39, item22, item2, item20, item21, item24,item30, item14, item28, item6, item15, item23))
-
-correlations.red.6F.1 <- polychoric(reduced.model.6F.1,correct = 0)
-
-fa.6F.2 <- fa(r=correlations.red.6F.1$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-JJ <- print(fa.6F.2, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.6F.2 <- dplyr::select(EFA.data, -c(item34, item44, item48, item43, item39, item22, item2, item20, item21, item24,item30, item14, item28, item6, item15, item23, item18, item42, item47, item41))
-
-correlations.red.6F.2 <- polychoric(reduced.model.6F.2,correct = 0)
-
-fa.6F.3 <- fa(r=correlations.red.6F.2$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)
-
-KK <- print(fa.6F.3, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.6F.3 <- dplyr::select(EFA.data, -c(item34, item44, item48, item43, item39, item22, item2, item20, item21, item24,item30, item14, item28, item6, item15, item23, item18, item42, item47, item41, item5, item13, item29))
-
-correlations.red.6F.3 <- polychoric(reduced.model.6F.3,correct = 0)
-
-fa.6F.4 <- fa(r=correlations.red.6F.3$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)
-
-ll <- print(fa.6F.4, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.6F.4 <- dplyr::select(EFA.data, -c(item34, item44, item48, item43, item39, item22, item2, item20, item21, item24,item30, item14, item28, item6, item15, item23, item18, item42, item47, item41, item5, item13, item29, item19))
-
-correlations.red.6F.4 <- polychoric(reduced.model.6F.4,correct = 0)
-
-fa.6F.5 <- fa(r=correlations.red.6F.4$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)
-
-mm <- print(fa.6F.5, cut = .3, digits = 3, sort = TRUE)
-
-# Residuals
-residual.6F =residuals(fa.6F.5 , diag = FALSE, na.rm =T)
-#Count of numbers of residuals>.05
-BigRRR= sum(residual.6F>abs(.05), na.rm =T)
-print(BigRRR)
-
-#Total number of off diagonal elements in the data matrix
-totRRR = length(reduced.model.6F.2)*(length(reduced.model.6F.2)-1)/2
-
-# Proportion of off-diagonal elements >.10
-sumRRR <- sum(BigRRR/totRRR*100)
-
-#hist(residual.6F, main = NULL, xlab = "Six factor Solution: Residuals",ylim=c(0, 400))
-#abline(h =65, lwd = 2, lty = 2)
-#abline(v =.05,lwd = 2, lty = 2)
-sixFac <- tabledown::fac.tab(fa.6F.5, cut =.3,complexity = F)
+```{r F1IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/F1.itemplots.png')
 ```
 
-```{r sixFacTab, results='asis'}
-papaja::apa_table(sixFac,  caption = "Factor loadings and communality of the retained items(six factor)", note = "Only loading higher than .30 is reported; Sixth factor has only two salient loadings",longtable =T, font_size = "small")
+```{r F2IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/F2.itemplots.png')
 ```
 
-```{r DataAppB, include=FALSE}
-data <- readRDS("leba_2021-09-08.rds")
-
-#Separating the EFA and CFA(only items)
-sem.data <- data[, 9:56] #EFA & CFA data
-## renaming the column-header
-prefix <- "item"
-sufix <- c(1:48)
-colnam <- paste(prefix,sufix, sep = "" )
-colnames(sem.data) <- colnam
-EFA.data <- sem.data[1:428, ]
-
+```{r F3IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/F3.itemplots.png')
 ```
 
-```{r ggplot2AppB, include=F}
-apatheme=ggplot2::theme_bw()+
-  ggplot2::theme(panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank(),
-        panel.background = element_blank(),
-        #text=element_text(family = "Helvetica",),
-        legend.title=element_blank(),
-        axis.line.x = element_line(color='black'),
-        axis.line.y = element_line(color='black'),
-        panel.border = element_rect(color = "black",
-                                    fill = NA,
-                                    size = 1))
+```{r F4IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/F4.itemplots.png')
 ```
 
-```{r EFAAppB, include=FALSE}
-fa.5F.1 <- fa(r=correlations$rho, nfactors = 5, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-AA <- print(fa.5F.1, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.5F.1 <- dplyr::select(EFA.data ,
-                                    -c(item32, item34, item24, item37, item22, item5,
-                                        item28, item30, item39,item23, item45, item6, item29, item2, item41))
-
-correlations.red.5F.1 <- polychoric(reduced.model.5F.1,correct = 0)
-
-fa.5F.2 <- fa(r=correlations.red.5F.1$rho, nfactors = 5, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-BB <- print(fa.5F.2, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.5F.2 <- dplyr::select(EFA.data, -c( item32, item34, item24, item37, item22, item5,
-                                        item28, item30, item39,item23, item45, item6, item29, item2, item41, item46, item13, item15, item25, item1, item26, item14))
-
-correlations.red.5F.2 <- polychoric(reduced.model.5F.2,correct = 0)
-
-fa.5F.3 <- fa(r=correlations.red.5F.2$rho, nfactors = 5, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428,max.iter = 500 )
-
-CC <- print(fa.5F.3, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.5F.3 <- dplyr::select(EFA.data, -c( item32, item34, item24, item37, item22, item5,
-                                        item28, item30, item39,item23, item45, item6, item29, item2, item41, item46, item13, item15, item25, item1, item26, item14, item43, item42))
-
-correlations.red.5F.3 <- polychoric(reduced.model.5F.3,correct = 0)
-
-fa.5F.4 <- fa(r=correlations.red.5F.3$rho, nfactors = 5, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428,max.iter = 500 )
-
-CC <- print(fa.5F.4, cut = .3, digits = 3, sort = TRUE)
+```{r F5IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/F5.itemplots.png')
 ```
 
-```{r factordetailsAppB, include=FALSE}
-#Preparing the EFA table
-efa.table <- tabledown::fac.tab(fa.5F.4,.3, complexity = F) 
+```{r personfit, fig.cap="Person fit of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
+knitr::include_graphics("Manuscript.figures/personfit.png")
 ```
-
-```{r efaunmerged, results='asis'}
-apa_table(efa.table, caption = "Factor loadings and communality of the retained items in five factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T, font_size = "small")
-```
-
-```{r EFAAppsix, include=FALSE, warning=F,message=FALSE}
-
-library(Hmisc)
-fa.6F.1 <- fa(r=correlations$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-DD <- print(fa.6F.1, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.6F.1 <- dplyr::select(EFA.data ,
-                                    -c(item32, item34, item44,item24, item37, item22, item5,
-                                        item28,item39,item23, item45, item6, item29, item2, item41, item30))
-
-correlations.red.6F.2 <- polychoric(reduced.model.6F.1,correct = 0)
-
-fa.6F.2 <- fa(r=correlations.red.6F.2$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-EE <- print(fa.6F.2, cut = .3, digits = 3, sort = TRUE)
-reduced.model.6F.2 <- dplyr::select(EFA.data ,
-                                    -c(item32, item34, item44,item24, item37, item22, item5,
-                                        item28,item39,item23, item45, item6, item29, item2, item41, item30, item46, item36,item1, item25))
-correlations.red.6F.3 <- polychoric(reduced.model.6F.2,correct = 0)
-fa.6F.3 <- fa(r=correlations.red.6F.3$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-FF <- print(fa.6F.3, cut = .3, digits = 3, sort = TRUE)
-
-reduced.model.6F.3 <- dplyr::select(EFA.data ,
-                                    -c(item32, item34, item44,item24, item37, item22, item5,
-                                        item28,item39,item23, item45, item6, item29, item2, item41, item30, item46, item36,item1, item25, item18))
-correlations.red.6F.4 <- polychoric(reduced.model.6F.3,correct = 0)
-fa.6F.4 <- fa(r=correlations.red.6F.4$rho, nfactors = 6, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-FF <- print(fa.6F.4, cut = .3, digits = 3, sort = TRUE)
-
-efa.table.2 <- tabledown::fac.tab(fa.6F.4,.3, complexity = F) 
-```
-
-```{r EFAsix, results='asis'}
-apa_table(efa.table.2, caption = "Factor loadings and communality of the retained items in six factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T, font_size = "small")
-```
-
-## Items Retained in the Five Factor Solution [Unmerged Responses]
-
-| **Five Factor Solution [Unmerged Responses] (24 Items)** |
-|---------------------------------------------------------|
-| **F1**                                                  |
-| `r label(sem.data$item19)`                              |
-| `r label(sem.data$item20)`                              |
-| `r label(sem.data$item18)`                              |
-| `r label(sem.data$item21)`                              |
-| `r label(sem.data$item4)`                               |
-| **F2**                                                  |
-| `r label(sem.data$item11)`                              |
-| `r label(sem.data$item10)`                              |
-| `r label(sem.data$item12)`                              |
-| `r label(sem.data$item8)`                               |
-| `r label(sem.data$item7)`                               |
-| `r label(sem.data$item9)`                               |
-| **F3**                                                  |
-| `r label(sem.data$item3)`                               |
-| `r label(sem.data$item27)`                              |
-| `r label(sem.data$item40)`                              |
-| **F4**                                                  |
-| `r label(sem.data$item35)`                              |
-| `r label(sem.data$item48)`                              |
-| `r label(sem.data$item33)`                              |
-| `r label(sem.data$item47)`                              |
-| `r label(sem.data$item44)`                              |
-| `r label(sem.data$item31)`                              |
-| `r label(sem.data$item38)`                              |
-| **F5**                                                  |
-| `r label(sem.data$item16)`                              |
-| `r label(sem.data$item17)`                              |
-| `r label(sem.data$item36)`                              |
-
-```{r Timetab, include=FALSE, warning=F,message=FALSE}
-descriptives.data%>%
-  tbl_summary(
-    label = slypos_demographics_tz.factor ~ "Time zone - Country",
-    statistic = list(all_categorical() ~ "{n} ({p}%)"),
-    missing = "no",
-    sort = all_categorical() ~ "frequency",
-    include = "slypos_demographics_tz.factor"
-  )  %>% bold_labels() %>% 
-  modify_header(label ~ "") %>%
-  modify_caption("Geographical Location") -> tz_table
-
-  as_tibble(tz_table, format = 'pipe') -> tz_tibble
-
-as_kable(tz_table, format = "latex",booktabs = T, longtable =T) -> tz_kable
-
-```
-
-```{r tztabprint, results='asis'}
-
-tz_kable %>% 
-  kable_styling(latex_options = c("repeat_header")) %>% 
-  column_spec(1,width = "10cm") %>% 
-  column_spec(2,width = "2cm")
-
-```

### 2022-01-07 appendix-3.Rmd
Aesthetic Updates

@@
-```{r configure, include=FALSE}
-library(Hmisc)
+```{r MinRes, include=F}
+library(psych)
+library(tabledown)
+library(kableExtra)#without this pdf rendering will not happen
+
 data <- readRDS("leba_2021-09-08.rds")
-sem.data <- data[, 9:56] 
+
+# Separating EFA and CFA samples with descriptive column
+descriptives.data <- data
+
+## Merge "0"s and "1"s into "1"s select,subset assign)
+descriptives.data[ , 9:56 ][ descriptives.data[ , 9:56 ] == 0 ] <- 1
+#EFA.descriptives <- descriptives.data[1:428,]
+EFA.descriptives <- subset(descriptives.data, IncludedInEFA == "TRUE")
+#CFA.descriptives <- descriptives.data[429:690, ]
+CFA.descriptives<- subset(descriptives.data, IncludedInEFA == "FALSE")
+
+#Separating the EFA and CFA(only items)
+sem.data <- data[, 9:56] #EFA & CFA data
+sem.data[ sem.data == 0] <- 1 #Merged "0"s and "1"s into "1"s
+
+## renaming the column-header
 prefix <- "item"
@@
 colnames(sem.data) <- colnam
+
+names(sem.data)[names(sem.data) == "item1"] <- "item01"
+names(sem.data)[names(sem.data) == "item2"] <- "item02"
+names(sem.data)[names(sem.data) == "item3"] <- "item03"
+names(sem.data)[names(sem.data) == "item4"] <- "item04"
+names(sem.data)[names(sem.data) == "item5"] <- "item05"
+names(sem.data)[names(sem.data) == "item6"] <- "item06"
+names(sem.data)[names(sem.data) == "item7"] <- "item07"
+names(sem.data)[names(sem.data) == "item8"] <- "item08"
+names(sem.data)[names(sem.data) == "item9"] <- "item09"
+
+### EFA data
+EFA.data <- sem.data[1:428, ]
+#Polychoric Correlation matrix
+
+correlations <- psych::polychoric(EFA.data, correct = 0)
+
+#Supplementary EFA with Minres Extraction
+
+fa.5F.min.1 <- fa(r=correlations$rho, nfactors = 5, fm= "minres",rotate ="varimax",
+                residuals = TRUE, SMC = TRUE, n.obs =428)
+EE <- print(fa.5F.min.1, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.5F.min.1 <- dplyr::select(EFA.data ,
+                                    -c( item20, item19, item05, item31, item44, item24, item43, item39, item22, item02, item18, item48, item42, item29, item06, item15, item23, item28, item14))
+
+correlations.red.5F.min.1 <- polychoric(reduced.model.5F.min.1,correct = 0)
+
+fa.5F.min.2 <- fa(r=correlations.red.5F.min.1$rho, nfactors = 5, fm= "minres",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+
+FF <- print(fa.5F.min.2, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.5F.min.2 <- dplyr::select(EFA.data, -c( item20, item19, item05, item31, item44, item24, item43, item39, item22, item02, item18, item48, item42, item29, item06, item15, item23, item28, item14, item34, item47, item21, item13))
+
+correlations.red.5F.min.2 <- polychoric(reduced.model.5F.min.2, correct = 0)
+
+fa.5F.min.3 <- fa(r=correlations.red.5F.min.2$rho, nfactors = 5, fm= "minres",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+
+GG <- print(fa.5F.min.3, cut = .3, digits = 3, sort = TRUE)
+
+minresTab <- tabledown::fac.tab(fa.5F.min.3, cut =.3,complexity = F)
 ```
 
-**Disclaimer**: This is a non-public version of LEBA (dated \today) and still a work in progress. Please do not distribute!
+```{r MinResTab}
+papaja::apa_table(minresTab,  caption = "Factor loadings and communality of the retained items (Minmum Residual)", note = "Only loading higher than .30 is reported", longtable=T, font_size = "small")
+```
 
-LEBA captures light exposure-related behaviours on a 5 point Likert type scale ranging from 1 to 5 (Never/Does not apply/I don't know = 1; Rarely = 2; Sometimes = 3; Often = 4; Always = 5).
-The score of each factor is calculated by the summation of scores of items belonging to the corresponding factor.
-The following instruction is given before displaying the items: "Please indicate how often you performed the following behaviours in the past 4 weeks."
+# Factor analysis with six factors
 
-\newpage
+```{r sixFac, include=F}
+# EFA with 6 factor (rejected)
 
-\blandscape
+#correlations <- polychoric(EFA.factor, correct = 0)
 
-# LEBA Long Form (23 Items)
+fa.6F.1 <- fa(r=correlations$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
 
-|     | Items                      | Never | Rarely | Sometimes | Often | Always |
-|-----|----------------------------|-------|--------|-----------|-------|--------|
-| 1   | `r label(sem.data$item16)` |       |        |           |       |        |
-| 2   | `r label(sem.data$item17)` |       |        |           |       |        |
-| 3   | `r label(sem.data$item36)` |       |        |           |       |        |
-| 4   | `r label(sem.data$item8)`  |       |        |           |       |        |
-| 5   | `r label(sem.data$item10)` |       |        |           |       |        |
-| 6   | `r label(sem.data$item9)`  |       |        |           |       |        |
-| 7   | `r label(sem.data$item11)` |       |        |           |       |        |
-| 8   | `r label(sem.data$item12)` |       |        |           |       |        |
-| 9   | `r label(sem.data$item7)`  |       |        |           |       |        |
-| 10  | `r label(sem.data$item27)` |       |        |           |       |        |
-| 11  | `r label(sem.data$item3)`  |       |        |           |       |        |
-| 12  | `r label(sem.data$item40)` |       |        |           |       |        |
-| 13  | `r label(sem.data$item30)` |       |        |           |       |        |
-| 14  | `r label(sem.data$item41)` |       |        |           |       |        |
-| 15  | `r label(sem.data$item32)` |       |        |           |       |        |
-| 16  | `r label(sem.data$item35)` |       |        |           |       |        |
-| 17  | `r label(sem.data$item38)` |       |        |           |       |        |
-| 18  | `r label(sem.data$item33)` |       |        |           |       |        |
-| 19  | `r label(sem.data$item46)` |       |        |           |       |        |
-| 20  | `r label(sem.data$item45)` |       |        |           |       |        |
-| 21  | `r label(sem.data$item25)` |       |        |           |       |        |
-| 22  | `r label(sem.data$item4)`  |       |        |           |       |        |
-| 23  | `r label(sem.data$item1)`  |       |        |           |       |        |
+II <- print(fa.6F.1, cut = .3, digits = 3, sort = TRUE)
 
-\elandscape
+reduced.model.6F.1 <- dplyr::select(EFA.data ,
+                                    -c(item34, item44, item48, item43, item39, item22, item02, item20, item21, item24,item30, item14, item28, item06, item15, item23))
 
-\newpage
+correlations.red.6F.1 <- polychoric(reduced.model.6F.1,correct = 0)
 
-\blandscape
+fa.6F.2 <- fa(r=correlations.red.6F.1$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
 
-## Latent Structure, Reliability and Structural Validity
+JJ <- print(fa.6F.2, cut = .3, digits = 3, sort = TRUE)
 
-The long form of LEBA consists 23 items with five factors.
+reduced.model.6F.2 <- dplyr::select(EFA.data, -c(item34, item44, item48, item43, item39, item22, item02, item20, item21, item24,item30, item14, item28, item06, item15, item23, item18, item42, item47, item41))
 
-| Factor names                                      | Items                    | Reliability Coefficients: ordinal alpha |
-|---------------------------------------------------|--------------------------|-----------------------------------------|
-| F1: Wearing blue light filters                    | 1-3                      | .96                                     |
-| F2: Spending time outdoors                        | 4-9 (Item 4 is reversed) | .83                                     |
-| F3: Using phone and smartwatch in bed             | 10-14                    | .70                                     |
-| F4: Using light before bedtime                    | 15-18                    | .69                                     |
-| F5: Using light in the morning and during daytime | 19-23                    | .52                                     |
-| McDonald's Omega coefficient for the total scale  |                          | .73 (Total scale)                       |
+correlations.red.6F.2 <- polychoric(reduced.model.6F.2,correct = 0)
 
-LEBA -long form showed satisfactory structural validity (CFI =.97; TLI = .96; RMSEA = .05\[.04-.06, 90% CI\]; SRMR = .09).
+fa.6F.3 <- fa(r=correlations.red.6F.2$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)
 
-## How to cite:
+KK <- print(fa.6F.3, cut = .3, digits = 3, sort = TRUE)
 
-\elandscape
+reduced.model.6F.3 <- dplyr::select(EFA.data, -c(item34, item44, item48, item43, item39, item22, item02, item20, item21, item24,item30, item14, item28, item06, item15, item23, item18, item42, item47, item41, item05, item13, item29))
 
-\newpage
+correlations.red.6F.3 <- polychoric(reduced.model.6F.3,correct = 0)
 
-\blandscape
+fa.6F.4 <- fa(r=correlations.red.6F.3$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)
 
-# LEBA Short Form (18 Items)
+ll <- print(fa.6F.4, cut = .3, digits = 3, sort = TRUE)
 
-|     | Short Form (18 Items)      | Never | Rarely | Sometimes | Often | Always |
-|-----|----------------------------|-------|--------|-----------|-------|--------|
-| 01  | `r label(sem.data$item16)` |       |        |           |       |        |
-| 02  | `r label(sem.data$item17)` |       |        |           |       |        |
-| 03  | `r label(sem.data$item36)` |       |        |           |       |        |
-| 04  | `r label(sem.data$item8)`  |       |        |           |       |        |
-| 05  | `r label(sem.data$item9)`  |       |        |           |       |        |
-| 06  | `r label(sem.data$item10)` |       |        |           |       |        |
-| 07  | `r label(sem.data$item11)` |       |        |           |       |        |
-| 08  | `r label(sem.data$item12)` |       |        |           |       |        |
-| 09  | `r label(sem.data$item7)`  |       |        |           |       |        |
-| 10  | `r label(sem.data$item27)` |       |        |           |       |        |
-| 11  | `r label(sem.data$item3)`  |       |        |           |       |        |
-| 12  | `r label(sem.data$item40)` |       |        |           |       |        |
-| 13  | `r label(sem.data$item32)` |       |        |           |       |        |
-| 14  | `r label(sem.data$item35)` |       |        |           |       |        |
-| 15  | `r label(sem.data$item33)` |       |        |           |       |        |
-| 16  | `r label(sem.data$item46)` |       |        |           |       |        |
-| 17  | `r label(sem.data$item45)` |       |        |           |       |        |
-| 18  | `r label(sem.data$item4)`  |       |        |           |       |        |
+reduced.model.6F.4 <- dplyr::select(EFA.data, -c(item34, item44, item48, item43, item39, item22, item02, item20, item21, item24,item30, item14, item28, item06, item15, item23, item18, item42, item47, item41, item05, item13, item29, item19))
 
-\elandscape
+correlations.red.6F.4 <- polychoric(reduced.model.6F.4,correct = 0)
 
-\newpage
+fa.6F.5 <- fa(r=correlations.red.6F.4$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)
 
-\blandscape
+mm <- print(fa.6F.5, cut = .3, digits = 3, sort = TRUE)
 
-## Latent Structure, Reliability and Structural Validity
+# Residuals
+residual.6F =residuals(fa.6F.5 , diag = FALSE, na.rm =T)
+#Count of numbers of residuals>.05
+BigRRR= sum(residual.6F>abs(.05), na.rm =T)
+print(BigRRR)
 
-The short form of LEBA consists 23 items with five factors.
+#Total number of off diagonal elements in the data matrix
+totRRR = length(reduced.model.6F.2)*(length(reduced.model.6F.2)-1)/2
 
-| Factor names                                          | Items                    |
-|-------------------------------------------------------|--------------------------|
-| **F1: Wearing blue light filters**                    | 1-3                      |
-| **F2: Spending time outdoors**                        | 4-8 (Item 4 is reversed) |
-| **F3: Using phone and smart-watch in bed**            | 9-11                     |
-| **F4: Using light before bedtime**                    | 12-14                    |
-| **F5: Using light in the morning and during daytime** | 15-17                    |
+# Proportion of off-diagonal elements >.10
+sumRRR <- sum(BigRRR/totRRR*100)
 
-## How to cite:
+#hist(residual.6F, main = NULL, xlab = "Six factor Solution: Residuals",ylim=c(0, 400))
+#abline(h =65, lwd = 2, lty = 2)
+#abline(v =.05,lwd = 2, lty = 2)
+sixFac <- tabledown::fac.tab(fa.6F.5, cut =.3,complexity = F)
+```
 
-\elandscape
+```{r sixFacTab, results='asis'}
+papaja::apa_table(sixFac,  caption = "Factor loadings and communality of the retained items(six factor)", note = "Only loading higher than .30 is reported; Sixth factor has only two salient loadings",longtable =T, font_size = "small")
+```
+
+```{r DataAppB, include=FALSE}
+data <- readRDS("leba_2021-09-08.rds")
+
+#Separating the EFA and CFA(only items)
+sem.data <- data[, 9:56] #EFA & CFA data
+## renaming the column-header
+prefix <- "item"
+sufix <- c(1:48)
+colnam <- paste(prefix,sufix, sep = "" )
+colnames(sem.data) <- colnam
+names(sem.data)[names(sem.data) == "item1"] <- "item01"
+names(sem.data)[names(sem.data) == "item2"] <- "item02"
+names(sem.data)[names(sem.data) == "item3"] <- "item03"
+names(sem.data)[names(sem.data) == "item4"] <- "item04"
+names(sem.data)[names(sem.data) == "item5"] <- "item05"
+names(sem.data)[names(sem.data) == "item6"] <- "item06"
+names(sem.data)[names(sem.data) == "item7"] <- "item07"
+names(sem.data)[names(sem.data) == "item8"] <- "item08"
+names(sem.data)[names(sem.data) == "item9"] <- "item09"
+EFA.data <- sem.data[1:428, ]
+
+correlations <- psych::polychoric(EFA.data, correct = 0)
+
+```
+
+```{r ggplot2AppB, include=F}
+apatheme=ggplot2::theme_bw()+
+  ggplot2::theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.background = element_blank(),
+        #text=element_text(family = "Helvetica",),
+        legend.title=element_blank(),
+        axis.line.x = element_line(color='black'),
+        axis.line.y = element_line(color='black'),
+        panel.border = element_rect(color = "black",
+                                    fill = NA,
+                                    size = 1))
+```
+
+```{r EFAAppB, include=FALSE}
+fa.5F.1 <- fa(r=correlations$rho, nfactors = 5, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+AA <- print(fa.5F.1, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.5F.1 <- dplyr::select(EFA.data ,
+                                    -c(item32, item34, item24, item37, item22, item05,
+                                        item28, item30, item39,item23, item45, item06, item29, item02, item41))
+
+correlations.red.5F.1 <- polychoric(reduced.model.5F.1,correct = 0)
+
+fa.5F.2 <- fa(r=correlations.red.5F.1$rho, nfactors = 5, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+
+BB <- print(fa.5F.2, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.5F.2 <- dplyr::select(EFA.data, -c( item32, item34, item24, item37, item22, item05,
+                                        item28, item30, item39,item23, item45, item06, item29, item02, item41, item46, item13, item15, item25, item01, item26, item14))
+
+correlations.red.5F.2 <- polychoric(reduced.model.5F.2,correct = 0)
+
+fa.5F.3 <- fa(r=correlations.red.5F.2$rho, nfactors = 5, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428,max.iter = 500 )
+
+CC <- print(fa.5F.3, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.5F.3 <- dplyr::select(EFA.data, -c( item32, item34, item24, item37, item22, item05,
+                                        item28, item30, item39,item23, item45, item06, item29, item02, item41, item46, item13, item15, item25, item01, item26, item14, item43, item42))
+
+correlations.red.5F.3 <- polychoric(reduced.model.5F.3,correct = 0)
+
+fa.5F.4 <- fa(r=correlations.red.5F.3$rho, nfactors = 5, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428,max.iter = 500 )
+
+CC <- print(fa.5F.4, cut = .3, digits = 3, sort = TRUE)
+```
+
+```{r factordetailsAppB, include=FALSE}
+#Preparing the EFA table
+efa.table <- tabledown::fac.tab(fa.5F.4,.3, complexity = F) 
+```
+
+```{r efaunmerged, results='asis'}
+apa_table(efa.table, caption = "Factor loadings and communality of the retained items in five factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T, font_size = "small")
+```
+
+```{r EFAAppsix, include=FALSE, warning=F,message=FALSE}
+
+library(Hmisc)
+fa.6F.1 <- fa(r=correlations$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+DD <- print(fa.6F.1, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.6F.1 <- dplyr::select(EFA.data ,
+                                    -c(item32, item34, item44,item24, item37, item22, item05,
+                                        item28,item39,item23, item45, item06, item29, item02, item41, item30))
+
+correlations.red.6F.2 <- polychoric(reduced.model.6F.1,correct = 0)
+
+fa.6F.2 <- fa(r=correlations.red.6F.2$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+
+EE <- print(fa.6F.2, cut = .3, digits = 3, sort = TRUE)
+reduced.model.6F.2 <- dplyr::select(EFA.data ,
+                                    -c(item32, item34, item44,item24, item37, item22, item05,
+                                        item28,item39,item23, item45, item06, item29, item02, item41, item30, item46, item36,item01, item25))
+correlations.red.6F.3 <- polychoric(reduced.model.6F.2,correct = 0)
+fa.6F.3 <- fa(r=correlations.red.6F.3$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+FF <- print(fa.6F.3, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.6F.3 <- dplyr::select(EFA.data ,
+                                    -c(item32, item34, item44,item24, item37, item22, item05,
+                                        item28,item39,item23, item45, item06, item29, item02, item41, item30, item46, item36,item01, item25, item18))
+correlations.red.6F.4 <- polychoric(reduced.model.6F.3,correct = 0)
+fa.6F.4 <- fa(r=correlations.red.6F.4$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+FF <- print(fa.6F.4, cut = .3, digits = 3, sort = TRUE)
+
+efa.table.2 <- tabledown::fac.tab(fa.6F.4,.3, complexity = F) 
+```
+
+```{r EFAsix, results='asis'}
+apa_table(efa.table.2, caption = "Factor loadings and communality of the retained items in six factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T, font_size = "small")
+```
+
+## Items Retained in the Five Factor Solution [Unmerged Responses]
+
+| **Five Factor Solution [Unmerged Responses] (24 Items)** |
+|---------------------------------------------------------|
+| **F1**                                                  |
+| `r label(sem.data$item19)`                              |
+| `r label(sem.data$item20)`                              |
+| `r label(sem.data$item18)`                              |
+| `r label(sem.data$item21)`                              |
+| `r label(sem.data$item4)`                               |
+| **F2**                                                  |
+| `r label(sem.data$item11)`                              |
+| `r label(sem.data$item10)`                              |
+| `r label(sem.data$item12)`                              |
+| `r label(sem.data$item8)`                               |
+| `r label(sem.data$item7)`                               |
+| `r label(sem.data$item9)`                               |
+| **F3**                                                  |
+| `r label(sem.data$item3)`                               |
+| `r label(sem.data$item27)`                              |
+| `r label(sem.data$item40)`                              |
+| **F4**                                                  |
+| `r label(sem.data$item35)`                              |
+| `r label(sem.data$item48)`                              |
+| `r label(sem.data$item33)`                              |
+| `r label(sem.data$item47)`                              |
+| `r label(sem.data$item44)`                              |
+| `r label(sem.data$item31)`                              |
+| `r label(sem.data$item38)`                              |
+| **F5**                                                  |
+| `r label(sem.data$item16)`                              |
+| `r label(sem.data$item17)`                              |
+| `r label(sem.data$item36)`                              |
+
+```{r Timetab, include=FALSE, warning=F,message=FALSE}
+descriptives.data%>%
+  tbl_summary(
+    label = slypos_demographics_tz.factor ~ "Time zone - Country",
+    statistic = list(all_categorical() ~ "{n} ({p}%)"),
+    missing = "no",
+    sort = all_categorical() ~ "frequency",
+    include = "slypos_demographics_tz.factor"
+  )  %>% bold_labels() %>% 
+  modify_header(label ~ "") %>%
+  modify_caption("Geographical Location") -> tz_table
+
+  as_tibble(tz_table, format = 'pipe') -> tz_tibble
+
+as_kable(tz_table, format = "latex",booktabs = T, longtable =T) -> tz_kable
+
+```
+
+```{r tztabprint, results='asis'}
+
+tz_kable %>% 
+  kable_styling(latex_options = c("repeat_header")) %>% 
+  column_spec(1,width = "10cm") %>% 
+  column_spec(2,width = "2cm")
+
+```

### 2022-01-07 manuscript.Rmd
Aesthetic Updates

@@
 #install.packages("pacman")#Run this if you don't have pacman installed.
-pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap)
+pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap,huxtable)
 pacman::p_install_gh("jthomasmock/gtExtras")
@@
 ```{r relscale, include=F, warning=F, message=F}
+
 relevant.scale.data <- readxl::read_excel("Table_raw/relevant_scales.xlsx")
-```
-
-```{r simscalep}
+
+```
+
+```{r reltab2}
 relevant.scale.data %>%
    kable( booktabs = T, caption ="Releated Scales", format ="latex", longtable =T) %>% 
-  kable_styling(latex_options = c("repeat_header")) %>% 
+  kable_styling(latex_options = c("repeat_header", "scale_down")) %>% 
   column_spec(1:6, width = "2cm")
+
 ```
@@
 colnames(sem.data) <- colnam
+names(sem.data)[names(sem.data) == "item1"] <- "item01"
+names(sem.data)[names(sem.data) == "item2"] <- "item02"
+names(sem.data)[names(sem.data) == "item3"] <- "item03"
+names(sem.data)[names(sem.data) == "item4"] <- "item04"
+names(sem.data)[names(sem.data) == "item5"] <- "item05"
+names(sem.data)[names(sem.data) == "item6"] <- "item06"
+names(sem.data)[names(sem.data) == "item7"] <- "item07"
+names(sem.data)[names(sem.data) == "item8"] <- "item08"
+names(sem.data)[names(sem.data) == "item9"] <- "item09"
 ```
@@
 To ensure construct adequacy we thoroughly assessed the current status of literature and identified a variety of light exposure related scales.
-However, no scales specifically measuring the behavioral component of light exposure were found (Table \@ref(tab:simscalep)).
+However, no scales specifically measuring the behavioral component of light exposure were found (Table \@ref(tab:eltab)).
 Consequentially we pursued to introduce a new openly available scale to address this research gap.
@@
 rownameprefix <- "Item"
-rownamesufix <- seq(1:48)
+rownamesufix <- seq(01:48)
 my.names <- paste(rownameprefix,rownamesufix, sep = "" )
 rownames(Des.combined) = (my.names)
+rownames(Des.combined)[rownames(Des.combined) == "Item1"] <- "Item01"
+rownames(Des.combined)[rownames(Des.combined) == "Item2"] <- "Item02"
+rownames(Des.combined)[rownames(Des.combined) == "Item3"] <- "Item03"
+rownames(Des.combined)[rownames(Des.combined) == "Item4"] <- "Item04"
+rownames(Des.combined)[rownames(Des.combined) == "Item5"] <- "Item05"
+rownames(Des.combined)[rownames(Des.combined) == "Item6"] <- "Item06"
+rownames(Des.combined)[rownames(Des.combined) == "Item7"] <- "Item07"
+rownames(Des.combined)[rownames(Des.combined) == "Item8"] <- "Item08"
+rownames(Des.combined)[rownames(Des.combined) == "Item9"] <- "Item09"
 ```
@@
 reduced.model.5F.1 <- dplyr::select(EFA.data ,
-                                    -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14))
+                                    -c( item20, item19, item05, item31, item44, item24, item43, item39, item22, item02, item18, item48, item42, item29, item06, item15, item23, item28, item14))
 
@@
 
-reduced.model.5F.2 <- dplyr::select(EFA.data, -c( item20, item19, item5, item31, item44, item24, item43, item39, item22, item2, item18, item48, item42, item29, item6, item15, item23, item28, item14, item34, item47, item21, item13))
+reduced.model.5F.2 <- dplyr::select(EFA.data, -c( item20, item19, item05, item31, item44, item24, item43, item39, item22, item02, item18, item48, item42, item29, item06, item15, item23, item28, item14, item34, item47, item21, item13))
 
@@
 Five.F1 <- dplyr::select(EFA.data, item16, item36, item17)
-Five.F2 <- dplyr::select(EFA.data, item11, item10, item12, item7, item8, item9) 
-Five.F3 <-  dplyr::select(EFA.data, item27, item3,item40, item30, item41)
+Five.F2 <- dplyr::select(EFA.data, item11, item10, item12, item07, item08, item09) 
+Five.F3 <-  dplyr::select(EFA.data, item27, item03,item40, item30, item41)
 Five.F4 <-  dplyr::select(EFA.data, item33,item32,item35, item37, item38)
-Five.F5 <- dplyr::select(EFA.data, item46, item45, item25, item4, item1, item26)
+Five.F5 <- dplyr::select(EFA.data, item46, item45, item25, item04, item01, item26)
 
@@
 gt.data <- sem.data
-gt.data$item8 <- as.character(gt.data$item8)
-gt.data$item8 <- fct_recode(gt.data$item8,
+gt.data$item08 <- as.character(gt.data$item08)
+gt.data$item08 <- fct_recode(gt.data$item08,
   "5" = "1",
@@
 )
-
-names(gt.data)[names(gt.data) == "item1"] <- "item01"
-names(gt.data)[names(gt.data) == "item3"] <- "item03"
-names(gt.data)[names(gt.data) == "item4"] <- "item04"
-names(gt.data)[names(gt.data) == "item7"] <- "item07"
-names(gt.data)[names(gt.data) == "item8"] <- "item08"
-names(gt.data)[names(gt.data) == "item9"] <- "item09"
 
@@
 ## Recoding CFA.data$item8 into CFA.data$Ritem8
-CFA.data$Ritem8 <- as.character(CFA.data$item8)
-CFA.data$Ritem8 <- fct_recode(CFA.data$Ritem8,
+CFA.data$Ritem08 <- as.character(CFA.data$item08)
+CFA.data$Ritem08 <- fct_recode(CFA.data$Ritem08,
   "5" = "1",
@@
 )
-CFA.data$Ritem8 <- as.numeric(as.character(CFA.data$Ritem8))
+CFA.data$Ritem08 <- as.numeric(as.character(CFA.data$Ritem08))
 
@@
 LB.model.Cor.1 <- "F1 =~ a1*item16 + item36 + a2*item17
-                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
-                 F3 =~  item27+ item3+ item40 + item30 + item41
+                 F2 =~ item11 + item10 + item12+ item07+ Ritem08+ item09
+                 F3 =~  item27+ item03+ item40 + item30 + item41
                  F4 =~ a3*item32 + item35 + item38+ a4*item33 
-                 F5 =~ item46+ item45+ item25+ item4+ item1 
+                 F5 =~ item46+ item45+ item25+ item04+ item01 
                        a1==a2
@@
 LB.model.Cor.2 <- "F1 =~ a1*item16 + item36 + a2*item17
-                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
-                 F3 =~  item27+ item3+ item40 + item30 + item41
+                 F2 =~ item11 + item10 + item12+ item07+ Ritem08+ item09
+                 F3 =~  item27+ item03+ item40 + item30 + item41
                  F4 =~ a3*item32 + item35 + item38+ a4*item33 
-                 F5 =~ item46+ item45+ item25+ item4+ item1 
+                 F5 =~ item46+ item45+ item25+ item04+ item01 
                        a1==a2
@@
 pop.model <- "F1 =~ a1*item16 + .95*item36 + a2*item17
-                 F2 =~ .87*item11 + .85*item10 + .74*item12+ .60*item7+ .50*Ritem8+ .49*item9
-                 F3 =~  .78*item27+ .77*item3+ .68*item40 + .13*item30 + .20*item41
+                 F2 =~ .87*item11 + .85*item10 + .74*item12+ .60*item07+ .50*Ritem08+ .49*item09
+                 F3 =~  .78*item27+ .77*item03+ .68*item40 + .13*item30 + .20*item41
                  F4 =~ a3*item32 + .63*item35 + .33*item38+ a4*item33 
-                 F5 =~ .80*item46+ .53*item45+ .36*item25+ .30*item4+ .22*item1 
+                 F5 =~ .80*item46+ .53*item45+ .36*item25+ .30*item04+ .22*item01 
                        a1==a2
@@
           what= "std",
+          #"hide", #(hides coefficeits)
           #whatLabels = "std",
           intercepts = F,
-          #style ="lisrel",
+          style ="lisrel",
           #residScale = 6,
@@
           curvePivot =T,
-          sizeMan =8,
-          sizeMan2 = 1.5,
-          sizeLat = 8,
-          #edge.color = "black",
+          sizeMan =6,#items length
+          sizeMan2 = 2,#items
+          sizeLat = 12,#factors
           thresholds = FALSE,
-          equalizeManifests =T,
+          equalizeManifests =F,
           fade = FALSE,
-          edge.label.cex = .65,
-          exoCov = FALSE)
+          edge.label.cex = .8,
+          exoCov = FALSE,
+          centerLevels = T,
+          edge.color="black",
+          label.scale=T,
+          label.cex=1, #Font of factor and item name
+          residuals=FALSE,
+           exoVar=FALSE,
+          fixedStyle=6, #Style of arrow (guide item)
+          freeStyle=1#Style of arrow (other item), #XKCD = TRUE
+
+          )
 
@@
 ```{r Invariancedetail, include=FALSE}
+
+LB.model.Cor.2 <- "F1 =~ a1*item16 + item36 + a2*item17
+                 F2 =~ item11 + item10 + item12+ item07+ Ritem08+ item09
+                 F3 =~  item27+ item03+ item40 + item30 + item41
+                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
+                 F5 =~ item46+ item45+ item25+ item04+ item01 
+                       a1==a2
+                       a3==a4
+                item30 ~~  item41
+                       "  
 # Configural invariance ####
@@
 ## Recoding sem.data$item8 into sem.data$Ritem8
-sem.data$Ritem8 <- as.character(sem.data$item8)
-sem.data$Ritem8 <- fct_recode(sem.data$Ritem8,
+sem.data$Ritem08 <- as.character(sem.data$item08)
+sem.data$Ritem08 <- fct_recode(sem.data$Ritem08,
   "5" = "1",
@@
 )
-sem.data$Ritem8 <- as.numeric(as.character(sem.data$Ritem8))
+sem.data$Ritem08 <- as.numeric(as.character(sem.data$Ritem08))
 # Recoding sem.data$item26 
@@
 F2 <- sem.data %>% 
-  dplyr::select(item11,  item10 , item12, item7, Ritem8, item9)
+  dplyr::select(item11,  item10 , item12, item07, Ritem08, item09)
 
 F3 <- sem.data %>% 
- dplyr::select(item27, item3,  item40,  item30,  item41)
+ dplyr::select(item27, item03,  item40,  item30,  item41)
 
@@
 F5 <- sem.data %>% 
-  dplyr::select(item46, item45, item25, item4, item1 )
+  dplyr::select(item46, item45, item25, item04, item01 )
 
@@
 
-## Plot grid ####
-library(cowplot)
-OCC <- plot_grid(F1_OCC, F2_OCC,F3_OCC,F4_OCC,F5_OCC, 
-          labels = c('A', 'B','C', 'D', 'E' ), label_size = 10)
-
-Test_Info <- plot_grid(F1_info, F2_info,F3_info,F4_info,F5_info, 
-          labels = "AUTO", label_size = 10)
-
-Item_Information <- plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
-          labels = "AUTO", label_size = 10)
-```
-
-```{r saveiteminfo, eval=FALSE, include=FALSE}
-jpeg("Manuscript.figures/iteminfo.png", width = 800, height = 750)
-plot_grid(F1_iteminfo, F2_iteminfo,F3_iteminfo,F4_iteminfo,F5_iteminfo, 
-          labels = "AUTO", label_size = 10,align = "v",ncol = 2)
-
-dev.off()
-```
-
-```{r IRTreliability, include=FALSE}
+```
+
+```{r IRTreliability, eval=FALSE, include=FALSE}
 #conditional reliability
@@
 
-```{r iteminfo, include=F, warning=F}
+```{r iteminfo, eval=FALSE, warning=FALSE, include=FALSE}
+#Not used in the manuscript
+
 F1_item1<- plot(F1_fit, type = "infotrace", 
@@
 F2.redu <- sem.data %>% 
-  dplyr::select(item11,  item10 , item12, item7, Ritem8, item9)
+  dplyr::select(item11,  item10 , item12, item07, Ritem08, item09)
 F3.redu <- sem.data %>% 
- dplyr::select(item27, item3,  item40)
+ dplyr::select(item27, item03,  item40)
 
@@
 ```{r scalechar, eval=FALSE, fig.cap="Scale characteristic curve of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, include=FALSE, out.height="120%", out.width="100%"}
+#not used in the manuscript
 
@@
   rowwise() %>% 
-  mutate(F2.Total = sum(item11,  item10 , item12, item7, Ritem8, item9))
+  mutate(F2.Total = sum(item11,  item10 , item12, item07, Ritem08, item09))
 
@@
   rowwise() %>% 
-  mutate(F3.Total = sum(item27, item3,  item40))
+  mutate(F3.Total = sum(item27, item03,  item40))
 

### 2022-01-08 manuscript.Rmd
Analysis flow chart updated

@@
 
-                    graph [fontname = Helvetica,layout = dot,fontsize = 40, ]
-
-                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 15, height = 1, 
-                    fixedsize = true,fontsize = 40]
+                    graph [fontname = Helvetica,layout = dot,fontsize = 45, ]
+
+                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 16, height = 2, 
+                    fixedsize = true,fontsize = 45]
 
@@
 
-                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 15, height = 6, 
-                    fixedsize = true, fontsize = 40]
+                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 16, height = 6, 
+                    fixedsize = true, fontsize = 45]
                     C[label = 
                     <
-                    Factor Identification<br align = 'left'/>
-                    Scree Plot: 6 Factors<br align = 'left'/>
-                    Parallel Analysis: 6 Factors<br align = 'left'/>
-                    Minimum Average Partial Method: 5 Factors<br align = 'left'/>
-                    Hull Method: 5 Factors<br align = 'left'/>
+                    Factor Identification<br align = 'center'/>
+                    Scree Plot: 6 Factors<br align = 'center'/>
+                    Parallel Analysis: 6 Factors<br align = 'center'/>
+                    Minimum Average Partial Method: 5 Factors<br align = 'center'/>
+                    Hull Method: 5 Factors<br align = 'center'/>
                     >
@@
                       style = rounded
-                     node[fontname = Helvetica, margin = 0.2,width = 18, height = 2, 
-                    fixedsize = true, fontsize = 38 ]
+                     node[fontname = Helvetica, margin = 0.2,width = 22, height = 2.5, 
+                    fixedsize = true, fontsize = 45]
 
@@
                       style = rounded
-                     node[fontname = Helvetica, margin = 0.2,width = 18, height = 2, 
-                fixedsize = true, fontsize = 38 ]
-                    6[label = '6-Factor solution: one factor emerged with only two salient loadings']
+                     node[fontname = Helvetica, margin = 0.2,width = 18, height = 2.5, 
+                fixedsize = true, fontsize = 45 ]
+                    6[label = 
+                    <
+                    6-Factor solution:<br align = 'center'/> 
+                    one factor emerged with only two salient loadings
+                    >
+                    ]
                     7[label = 'Rejected']
@@
 }")
+
 library(jpeg)

### 2022-01-08 manuscript.Rmd
Analysis flow chart with wokable res

@@
 ```{r Manuflowchart, include=FALSE }
-Flowchart1 <- grViz("digraph nicegraph{
-
-                    graph [fontname = Helvetica,layout = dot,fontsize = 45, ]
+Flowchart1 <- grViz("digraph my_flowchart{
+
+                    graph [fontname = Helvetica,layout = dot,fontsize = 45,layout = dot ]
 
@@
 
-                    A[label = '48 items were generated by a robust expert panel'] 
-                    B[label = 'Exploratory Factor Analysis on 48 Items (N = 428)']
+                    A[label = '48 items were generated'] 
+                    B[label = 'Exploratory Factor Analysis on 48 Items (n = 428)']
 
@@
                     C[label = 
-                    <
-                    Factor Identification<br align = 'center'/>
-                    Scree Plot: 6 Factors<br align = 'center'/>
-                    Parallel Analysis: 6 Factors<br align = 'center'/>
-                    Minimum Average Partial Method: 5 Factors<br align = 'center'/>
-                    Hull Method: 5 Factors<br align = 'center'/>
-                    >
+                    <Factor Identification<br/>Scree Plot: 6 Factors<br/>Parallel Analysis: 6 Factors<br/>Minimum Average Partial Method: 5 Factors<br/>Hull Method: 5 Factors>
                     ]
@@
                      subgraph cluster_1 {
-                      graph[fontname = Helvetica, shape = rectangle]
-                      style = rounded
+                      graph[fontname = Helvetica, shape = box, style =dashed]
+
                      node[fontname = Helvetica, margin = 0.2,width = 22, height = 2.5, 
-                    fixedsize = true, fontsize = 45]
+                    fixedsize = true, fontsize = 45,style =dashed]
 
                      1[label = '5 Factor Solution Retained 25 Items']
-                     2[label = 'Reliability Analysis on EFA Sample (N=428)
-                    Ordinal alpha F1 =.94; F2 = .76; F3 = .75; F4 =.72; F5 =.62']
-
-                     3[label = 'Confirmatory Factor Analysis 
-                     on the Five Factor Model (25 Items; N=262)
-                      Acceptable Fit ( CFI = .94; TLI .93; RMSEA = .06, SRMR = .11)']
-
-                    4[label = 'Confirmatory Factor Analysis 
-                     on the Five Factor Model (23 Items; N=262)
-                      Acceptable Fit ( CFI = .97; TLI= .96; RMSEA = .04, SRMR = .09)']
-                     5[label = 'Reliability Analysis on CFA (23 Items; N=262) 
-                      Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52
-                      Mcdonald  omega(total) for the total scale = .73']
-                    8[label = 'Measurement Invariance Analysis
-                    Residual measurement invariance achieved']
+                     2[label = <Reliability Analysis on EFA Sample (n=428)<br/>Ordinal alpha F1 =.94; F2 = .76; F3 = .75; F4 =.72; F5 =.62.>]
+
+                     3[label = <Confirmatory Factor Analysis<br/>on the Five Factor Model (25 Items; n=262)<br/>Acceptable Fit ( CFI = .94; TLI .93; RMSEA = .06, SRMR = .11)>]
+
+                    4[label = <Confirmatory Factor Analysis<br/>on the Five Factor Model (23 Items; n=262)<br/>Acceptable Fit ( CFI = .97; TLI= .96; RMSEA = .04, SRMR = .09)>]
+                     5[label = <Reliability Analysis on CFA (23 Items; n=262)<br/>Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52<br/>Mcdonald  omega(total) for the total scale = .73>]
+                    8[label = <Measurement Invariance Analysis<br/>Residual measurement invariance achieved>]
                     9[label = 'Semantic Analysis']
-                    10[label = 'LEBA Short Form (18 Items; N=690) 
-                      Based on Item Response Theory']
+                    10[label = <LEBA Short Form (18 Items; n=690)<br/>Based on Item Response Theory>]
                     }
@@
                     6[label = 
-                    <
-                    6-Factor solution:<br align = 'center'/> 
-                    one factor emerged with only two salient loadings
-                    >
+                    <6-Factor solution:<br/>one factor emerged with only two salient loadings>
                     ]
@@
 
-```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='160%', out.width='100%'}
+```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='100%', out.width='100%'}
 knitr::include_graphics('Manuscript.figures/Flowchart1.jpeg')

### 2022-01-08 manuscript.Rmd
Figures DPI 1200

@@
 knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=1200, fig.width = 6,
- fig.asp = 0.8,out.width = "80%")
+ fig.asp = 0.8,out.width = "80%", dev=c('png','postscript'))
 #options(knitr.duplicate.label = "allow")
@@
 #install.packages("pacman")#Run this if you don't have pacman installed.
-pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap,huxtable)
+pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap,huxtable,tikzDevice)
 pacman::p_install_gh("jthomasmock/gtExtras")
@@
   rsvg() %>%
-  writeJPEG("Manuscript.figures/Flowchart1.jpeg",bg = "white", quality = 1)
+  png::writePNG("Manuscript.figures/Flowchart1.jpeg", dpi = 1200)
 
@@
 ```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='100%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/Flowchart1.jpeg')
+knitr::include_graphics('Manuscript.figures/Flowchart1.jpeg', dpi = 800 )
 ```
@@
 
-```{r figCor, out.height="150%",out.width="100%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}
-
-ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
-           ggtheme = ggplot2::theme_minimal, tl.cex = 6,tl.srt = 90,colors = c("red", "white", "blue") )
+```{r}
+corplot <- ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
+           ggtheme = ggplot2::theme_minimal(),,tl.srt = 90,colors = c("red", "white", "blue") )+
+  theme( panel.grid.major = element_blank(),
+         axis.text.x = element_text(size = 8),
+         axis.text.y = element_text(size = 8),
+         panel.border = element_rect(color = "black",
+                                    fill = NA,
+                                    size = 1))
 #p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
 #to show pvalue in the fig add p.mat=p.mat
+ggsave("Manuscript.figures/corplot.png",corplot, width = 6, height = 6, dpi = 1200, bg ="white")
+
+```
+
+```{r figCor, out.height="150%",out.width="100%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}
+
+knitr::include_graphics('Manuscript.figures/corplot.png', dpi =1200)
+
 ```
@@
 hull <- ggplot2::last_plot()
-Hull <- hull+ ggtitle(NULL)+xlab("Factor Number (Hull Method)")+ylab("CAF")+ 
-  apatheme +scale_color_manual(labels = c("Out side the convex Hull", "On the convex Hull"), values = c("red", "cyan2"))+theme(legend.position = "None")
+Hull <- hull+ ggtitle(NULL)+xlab("Factor Number (Hull Method)")+ylab("CAF")+ aes(color = "black")+
+  apatheme +scale_color_manual(labels = c("Out side the convex Hull", "On the convex Hull"), values = c("black", "black"))+theme(legend.position = "None")
 
@@
                   label_size = 12,
-                  label_fontfamily = "serif",
+                  label_fontfamily = "Arial",
                   label_fontface = "plain")
-ggsave("Manuscript.figures/factors.png",fator, width = 6, height = 12, dpi = 600)
+ggsave("Manuscript.figures/factors.png",fator, width = 6, height = 12, dpi = 1200)
 ```
@@
 
-knitr::include_graphics('Manuscript.figures/factors.png')
+knitr::include_graphics('Manuscript.figures/factors.png', dpi =800)
 
@@
 node [fontname = Helvetica, shape = circle,  margin = 0.5, width = 3.5, height = .5,
-fixedsize = true, fontsize = 35]
+fixedsize = true, fontsize = 40]
 F5 [label = 'F5']
@@
 
-node [fontname = Helvetica, shape = box]
+node [fontname = Helvetica, shape = box, fontsize = 50, height = 1]
 b [label = 'item16']
@@
 # edge definitions with the node IDs
-edge [fontname = Helvetica, fontsize = 35]
+edge [fontname = Helvetica, fontsize = 40]
 F5 -> u [label = '0.60']
@@
   rsvg() %>%
-  writeJPEG("Manuscript.figures/EFAplot.jpeg",bg = "white", quality = 1)
+  png::writePNG("Manuscript.figures/EFAplot.png",dpi =1200)
 
@@
 
-residual.plot <- ggplot(residual.data, aes(x=Residuals)) + geom_histogram(binwidth=.04, col=I("black"),fill=I("grey")) + xlim(-.2,.2)+ ylim(0,250)+apatheme +geom_vline(xintercept = .05)+
+residual.plot <- ggplot(residual.data, aes(x=Residuals)) + geom_histogram(binwidth=.04, col=I("black"),fill=I("grey")) + xlim(-.2,.2)+ ylim(0,250)+apatheme +geom_vline(xintercept = .05)+theme(axis.text.x = element_text(size = 12),
+        axis.text.y = element_text(size = 12))
   labs( y="Frequency")
@@
 
-img1 <- readJPEG("Manuscript.figures/EFAplot.jpeg")
+img1 <- png::readPNG("Manuscript.figures/EFAplot.png")
 
@@
   label_size = 12,
-  label_fontfamily = "serif",
+  label_fontfamily = "Arial",
   label_fontface = "plain",
-  label_y = .98,
+  label_y = .99,
   label_x = .04
@@
 
-```
-
-```{r EFAplot, fig.align='center', fig.cap='(A) Five Factor Solution obtained in Exploratory Factor Analysis (B) Histogram of nonredundent residula correlations', warning=FALSE, out.height="80%", out.width="100%", results='asis'}
-EFAplot.1
-
+ggsave("Manuscript.figures/EFAfull.png",EFAplot.1, width = 10, height =10, dpi = 1200)
+
+```
+
+```{r EFAplot, fig.align='center', fig.cap='(A) Five Factor Solution obtained in Exploratory Factor Analysis (B) Histogram of nonredundent residula correlations', warning=FALSE,  results='asis'}
+
+knitr::include_graphics('Manuscript.figures/EFAfull.png', dpi =1200)
 ```
@@
 ```{r efagtPic, echo=FALSE, out.height="100%", out.width= '100%', fig.cap= ' Summary Descriptives EFA Sample'}
-knitr::include_graphics('Manuscript.figures/efagt.png')
+knitr::include_graphics('Manuscript.figures/efagt.png',dpi =1200)
 
@@
 ```{r cfagtPic, echo=FALSE, out.height="100%", out.width= '100%', fig.cap= ' Summary Descriptives of CFA Sample'}
-knitr::include_graphics('Manuscript.figures/cfagt.png')
+knitr::include_graphics('Manuscript.figures/cfagt.png',dpi =1200)
 
@@
 
-```{r figcfa, fig.cap = "Five Factor CFA Model of LEBA", out.height="150%", out.width="100%",  warning=FALSE}
+```{r figcfa, fig.cap = "Five Factor CFA Model of LEBA", out.height="150%", out.width="100%", dpi=1200,  warning=FALSE}
 #library(semPlot)
@@
           centerLevels = T,
-          edge.color="black",
+          #edge.color="black",
           label.scale=T,
@@
                      label_fontface = "plain")
-ggsave("Manuscript.figures/F2.itemplots.png",F2.itemplots, width = 10, height = 12, dpi = 600, bg = "white")
+ggsave("Manuscript.figures/F2.itemplots.png",F2.itemplots, width = 10, height = 12, dpi = 1200, bg = "white")
 
@@
                      label_fontface = "plain")
-ggsave("Manuscript.figures/F3.itemplots.png",F3.itemplots, width = 10, height = 12, dpi = 600,bg = "white")
+ggsave("Manuscript.figures/F3.itemplots.png",F3.itemplots, width = 10, height = 12, dpi = 1200,bg = "white")
 
@@
                      label_fontface = "plain")
-ggsave("Manuscript.figures/F4.itemplots.png",F4.itemplots, width = 10, height = 12, dpi = 600,bg = "white")
+ggsave("Manuscript.figures/F4.itemplots.png",F4.itemplots, width = 10, height = 12, dpi = 1200,bg = "white")
 
@@
                      label_fontface = "plain")
-ggsave("Manuscript.figures/F5.itemplots.png",F5.itemplots, width = 10, height = 12, dpi = 600, bg = "white")
+ggsave("Manuscript.figures/F5.itemplots.png",F5.itemplots, width = 10, height = 12, dpi = 1200, bg = "white")
 ```
@@
                      label_fontface = "plain")
-ggsave("Manuscript.figures/TIC.png",TIC, width = 10, height = 12, dpi = 600, bg = "white")
+ggsave("Manuscript.figures/TIC.png",TIC, width = 10, height = 12, dpi = 1200, bg = "white")
 
@@
 
-knitr::include_graphics('Manuscript.figures/TIC.png')
+knitr::include_graphics('Manuscript.figures/TIC.png', dpi =1200)
 ```
@@
 
-ggsave("Manuscript.figures/personfit.png",personfit , width = 10, height = 12, dpi = 600, bg = "white")
+ggsave("Manuscript.figures/personfit.png",personfit , width = 10, height = 12, dpi = 1200, bg = "white")
 

### 2022-01-08 appendix-2.Rmd
Figure Legends are added

@@
 
-```{r F1IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/F1.itemplots.png')
+```{r F1IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1. Item 16 carried highest information among the three items', out.height='160%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/F1.itemplots.png', dpi = 1200)
 ```
 
-```{r F2IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/F2.itemplots.png')
+```{r F2IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F2.
+All items cariied information across the latent trait continuum.
+Item 09 carried the lowest information however its information peak was highr than .20.', out.height='160%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/F2.itemplots.png',dpi = 1200)
 ```
 
-```{r F3IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/F3.itemplots.png')
+```{r F3IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F3.
+Item 30 and 41 had relatively flat information curve with a peak lower than .20', out.height='160%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/F3.itemplots.png',dpi = 1200)
 ```
 
-```{r F4IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/F4.itemplots.png')
+```{r F4IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F4. Item 38 had relatively flat information curve with a peak lower than .20', out.height='160%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/F4.itemplots.png',dpi = 1200)
 ```
 
-```{r F5IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/F5.itemplots.png')
+```{r F5IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F5.
+Three items: 25, 04, 01 carriedlow information.
+However Item 04 had a bump at the righ side of the center with a curve peak higher than .20.
+Item 01 and 25 had relatively flat information curve with a peak lower than .20'', out.height='160%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/F5.itemplots.png',dpi = 1200)
 ```
@@
 ```{r personfit, fig.cap="Person fit of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
-knitr::include_graphics("Manuscript.figures/personfit.png")
+knitr::include_graphics("Manuscript.figures/personfit.png",dpi = 1200)
 ```

### 2022-01-08 manuscript.Rmd
Figure Legends are added

@@
                     4[label = <Confirmatory Factor Analysis<br/>on the Five Factor Model (23 Items; n=262)<br/>Acceptable Fit ( CFI = .97; TLI= .96; RMSEA = .04, SRMR = .09)>]
-                     5[label = <Reliability Analysis on CFA (23 Items; n=262)<br/>Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52<br/>Mcdonald  omega(total) for the total scale = .73>]
+                     5[label = <Reliability Analysis (23 Items; n=262)<br/>Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52<br/>Mcdonald  omega(total) for the total scale = .73>]
                     8[label = <Measurement Invariance Analysis<br/>Residual measurement invariance achieved>]
@@
 
-```{r figCor, out.height="150%",out.width="100%",fig.cap= "Correlation plot of the items",results='asis', fig.align='center'}
+```{r figCor, out.height="150%",out.width="100%",fig.cap= "Inter item ploychroric correlationc coefficients for the 48 items.
+The red gradient indicates negative correlations, white indicates zero correlation and the blue gradient indicate positive correlations.
+4.9% inter-item correlation coefficients were higher than .30 ",results='asis', fig.align='center'}
 
@@
                   align = "v", 
-                  label_size = 12,
+                  label_size = 15,
                   label_fontfamily = "Arial",
@@
 
-```{r facIdFig, out.height="100%", out.width="100%",fig.align='center', fig.cap='Factor Identification (A) Parallel analysis (B) Scree Plot (C) Hull Method',  warning=FALSE, results= 'asis'}
+```{r facIdFig, out.height="100%", out.width="100%",fig.align='center', fig.cap='Factor Identification Methods (A) In parallel analysis we drew 500 sets of random data with the same number of participants as our orihinal data (n=428) and adjusted the mean eigenvalues for sample bias.
+In x-axis we plotted the number of possible factors and in y axis we plotted the mean ajusted eigenvalues.
+The First inflection point of the plot indicated the optimal number of factor was six.
+re  (B) In the scree scree plot possible numner of factors are plotted againest obtained eigen values.
+Scree plot suggested six factors.
+(C) In Hull method we plotted the number of posible factors in the x axis and in the y axis we ploed the CAF index(CAF: Common Part Accounted for-an indicator of model fit).
+Hull method indicated 5 factors are requied to  balance model fit and the number of parameters ',  warning=FALSE, results= 'asis'}
 
@@
 p1 <- ggplot2::ggplot() + ggplot2::annotation_custom(grid::rasterGrob(img1,
-                                                                      width=NULL,
-                                                                      height=NULL),
-                                                     -Inf, Inf, -Inf, Inf)+apatheme
+                                                                      width=.4,
+                                                                      height=.8),
+                                                     -Inf, Inf, -Inf, Inf)+
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.background = element_blank())
+        #text=element_text(family = "Helvetica"))
 
@@
   align="h",
-  ncol = 2,
-  label_size = 12,
+  ncol = 1,
+  label_size = 15,
   label_fontfamily = "Arial",
@@
   label_y = .99,
-  label_x = .04
+  label_x = .02,
+ rel_heights = c(1.5,1)
 )
 
-ggsave("Manuscript.figures/EFAfull.png",EFAplot.1, width = 10, height =10, dpi = 1200)
-
-```
-
-```{r EFAplot, fig.align='center', fig.cap='(A) Five Factor Solution obtained in Exploratory Factor Analysis (B) Histogram of nonredundent residula correlations', warning=FALSE,  results='asis'}
+ggsave("Manuscript.figures/EFAfull.png",EFAplot.1, width = 4, height =8, dpi = 1200, bg ="white")
+
+```
+
+```{r EFAplot, fig.align='center', fig.cap='(A) Five Factor Solution obtained in Exploratory Factor Analysis.
+The factor loadings ranged between .49-.99 (B) Histogram of nonredundent residula correlations indicated 26% correlations are higher than absolute value of .05 indicating a possible under factoring', warning=FALSE,  results='asis'}
 
@@
                 item30 ~~  item41
-                       "
+                     F1 ~~ 0*F2
+F1 ~~ 0*F3
+F1 ~~ 0*F4
+F1 ~~ 0*F5
+F2 ~~ 0*F3
+F2 ~~ 0*F4
+F2 ~~ 0*F5
+F3 ~~ 0*F4
+F3 ~~ 0*F5
+F4 ~~ 0*F5"
 
@@
 
-```{r figcfa, fig.cap = "Five Factor CFA Model of LEBA", out.height="150%", out.width="100%", dpi=1200,  warning=FALSE}
+```{r figcfa, fig.cap = "Five Factor  Model of LEBA obtained by Confirmatory Factor Analysis.
+By allowing item pain 41 & 30 to covary their error variance our model attained the best fit.", out.height="150%", out.width="100%", dpi=1200,  warning=FALSE}
 #library(semPlot)
@@
           edge.label.cex = .8,
-          exoCov = FALSE,
+          exoCov = T,
           centerLevels = T,
@@
 F1.iteminfo.1 <- ggplot(F1.item.info.data , aes(x=Theta, y=F1.item.info.1)) +
-  geom_line()  +apatheme +labs(y="Item Information", title = "F1 item16") + geom_hline(yintercept = .20, colour ="red")
+  geom_line()  +apatheme +labs(y="Item Information", title = "F1 item16") + geom_hline(yintercept = .18, colour ="red")
 F1.iteminfo.2 <- ggplot(F1.item.info.data , aes(x=Theta, y=F1.item.info.2)) +
-  geom_line()  +apatheme +labs(y="Item Information", title = "F1 item36")+geom_hline(yintercept = .20, colour ="red")
+  geom_line()  +apatheme +labs(y="Item Information", title = "F1 item36")+geom_hline(yintercept = .18, colour ="red")
 F1.iteminfo.3 <- ggplot(F1.item.info.data , aes(x=Theta, y=F1.item.info.3)) +
-  geom_line()  +apatheme +labs(y="Item Information", title = "F1 item17")+ylim(0,6)+geom_hline(yintercept = .20, colour ="red")
+  geom_line()  +apatheme +labs(y="Item Information", title = "F1 item17")+ylim(0,6)+geom_hline(yintercept = .18, colour ="red")
 
@@
 F2.iteminfo.1 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.1)) +
-  geom_line()  +apatheme +labs(y="Item Information", title = "F2 item11")+ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+  geom_line()  +apatheme +labs(y="Item Information", title = "F2 item11")+ylim(0,3)+geom_hline(yintercept = .18, colour ="red")
 
@@
   labs(y="Item Information", title = "F2 item10")+
-  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")
 
@@
   labs(y="Item Information", title = "F2 item12")+
-  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")
 
@@
   labs(y="Item Information", title = "F2 item07")+ylim(0,3)+
-  geom_hline(yintercept = .20, colour ="red")
+  geom_hline(yintercept = .18, colour ="red")
 
@@
   labs(y="Item Information", title = "F2 item08")+ylim(0,3)+
-  geom_hline(yintercept = .20, colour ="red")
+  geom_hline(yintercept = .18, colour ="red")
 
@@
   labs(y="Item Information", title = "F2 item09")+ylim(0,3)+
-  geom_hline(yintercept = .20, colour ="red")
+  geom_hline(yintercept = .18, colour ="red")
 
@@
   geom_line()  +apatheme +labs(y="Item Information", title = "F3 item27")+
-  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")
 
@@
   labs(y="Item Information",title = "F3 item03")+
-  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")
 
@@
   labs(y="Item Information",title = "F3 item40")+
-  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")
 
@@
   labs(y="Item Information",title = "F3 item30")+
-  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")
 
@@
   labs(y="Item Information", title = "F3 item41")+
-  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")
 
@@
   geom_line()  +apatheme +labs(y="Item Information", title = "F4 item32")+
-  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")
 
@@
   labs(y="Item Information",title = "F4 item35")+
-  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")
 
@@
   labs(y="Item Information",title = "F4 item38")+
-  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")
 
@@
   geom_line()  +apatheme +
-  labs(y="Item Information",title = "F4 item33")+geom_hline(yintercept = .20, colour ="red")
+  labs(y="Item Information",title = "F4 item33")+geom_hline(yintercept = .18, colour ="red")
 
@@
   geom_line()  +apatheme +labs(y="Item Information", title = "F5 item46")+
-  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+  ylim(0,2)+geom_hline(yintercept = .18, colour ="red")
 
@@
   labs(y="Item Information",title = "F5 item45")+
-  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+  ylim(0,2)+geom_hline(yintercept = .18, colour ="red")
 
@@
   labs(y="Item Information",title = "F5 item25")+
-  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+  ylim(0,2)+geom_hline(yintercept = .18, colour ="red")
 
@@
   labs(y="Item Information",title = "F5 item04")+
- geom_hline(yintercept = .20, colour ="red")
+ geom_hline(yintercept = .18, colour ="red")+ylim(0,2)
 
@@
   labs(y="Item Information", title = "F5 item01")+
-  ylim(0,3)+geom_hline(yintercept = .20, colour ="red")
+  ylim(0,2)+geom_hline(yintercept = .18, colour ="red")
 
@@
                      label_size = 12,
-                     label_fontfamily = "serif",
+                     label_fontfamily = "Arial",
   label_fontface = "plain")
@@
                      label_size = 12,
-                     label_fontfamily = "serif",
+                     label_fontfamily = "Arial",
                      label_fontface = "plain")
@@
                      label_size = 12,
-                     label_fontfamily = "serif",
+                     label_fontfamily = "Arial",
                      label_fontface = "plain")
 ggsave("Manuscript.figures/F5.itemplots.png",F5.itemplots, width = 10, height = 12, dpi = 1200, bg = "white")
+```
+
+```{r inteminfoggplo2com, eval=FALSE, include=FALSE}
+#Victimization
+pacman::p_load(reshape,ggsci)
+Theta <- matrix(seq(-6,6, by = .1))
+
+##Item Extraction
+F1.item1 <- extract.item(F1_fit, 1)#item number
+F1.item2 <- extract.item(F1_fit, 2)
+F1.item3 <- extract.item(F1_fit, 3)
+F2.item1 <- extract.item(F2_fit, 1)
+F2.item2 <- extract.item(F2_fit, 2)
+F2.item3 <- extract.item(F2_fit, 3)
+F2.item4 <- extract.item(F2_fit, 4)
+F2.item5 <- extract.item(F2_fit, 5)
+F2.item6 <- extract.item(F2_fit, 6)
+F3.item1 <- extract.item(F3_fit, 1)
+F3.item2 <- extract.item(F3_fit, 2)
+F3.item3 <- extract.item(F3_fit, 3)
+F3.item4 <- extract.item(F3_fit, 4)
+F3.item5 <- extract.item(F3_fit, 5)
+F4.item1 <- extract.item(F4_fit, 1)
+F4.item2 <- extract.item(F4_fit, 2)
+F4.item3 <- extract.item(F4_fit, 3)
+F4.item4 <- extract.item(F4_fit, 4)
+F5.item1 <- extract.item(F5_fit, 1)
+F5.item2 <- extract.item(F5_fit, 2)
+F5.item3 <- extract.item(F5_fit, 3)
+F5.item4 <- extract.item(F5_fit, 4)
+F5.item5 <- extract.item(F5_fit, 5)
+
+##Item Info
+Item16 <- iteminfo(F1.item1, Theta)
+Item36 <- iteminfo(F1.item2, Theta)
+Item17 <- iteminfo(F1.item3, Theta)
+Item11 <- iteminfo(F2.item1, Theta)
+Item10 <- iteminfo(F2.item2, Theta)
+Item12 <- iteminfo(F2.item3, Theta)
+Item07 <- iteminfo(F2.item4, Theta)
+Item08 <- iteminfo(F2.item5, Theta)
+Item09 <- iteminfo(F2.item6, Theta)
+Item27 <- iteminfo(F3.item1, Theta)
+Item03 <- iteminfo(F3.item2, Theta)
+Item40 <- iteminfo(F3.item3, Theta)
+Item30 <- iteminfo(F3.item4, Theta)
+Item41 <- iteminfo(F3.item5, Theta)
+Item32 <- iteminfo(F4.item1, Theta)
+Item35 <- iteminfo(F4.item2, Theta)
+Item38 <- iteminfo(F4.item3, Theta)
+Item33 <- iteminfo(F4.item4, Theta)
+Item46 <- iteminfo(F5.item1, Theta)
+Item45 <- iteminfo(F5.item2, Theta)
+Item25 <- iteminfo(F5.item3, Theta)
+Item04 <- iteminfo(F5.item4, Theta)
+Item01 <- iteminfo(F5.item5, Theta)
+
+#Data frame
+
+F1.item.info.data <- as.data.frame(cbind(Item16, 
+                                              Item36,
+                                              Item17))
+
+F2.item.info.data <- as.data.frame(cbind(Item11, 
+                                              Item10,
+                                              Item12,
+                                         Item07,
+                                         Item08,
+                                         Item09))
+
+F3.item.info.data <- as.data.frame(cbind(Item27, 
+                                              Item03,
+                                              Item40,
+                                         Item30,
+                                        Item41))
+
+F4.item.info.data <- as.data.frame(cbind(Item32, 
+                                              Item35,
+                                              Item38,
+                                         Item33))
+F5.item.info.data <- as.data.frame(cbind(Item46, 
+                                              Item45,
+                                             Item25,
+                                         Item04,
+                                         Item01))
+
+F1.item.info.data.long <- melt(F1.item.info.data)
+F2.item.info.data.long <- melt(F2.item.info.data)
+F3.item.info.data.long <- melt(F3.item.info.data)
+F4.item.info.data.long <- melt(F4.item.info.data)
+F5.item.info.data.long <- melt(F5.item.info.data)
+
+F1.item.info.data.2 <- data.frame(Theta=seq(-6,6, by = .1), F1.item.info.data.long)
+F2.item.info.data.2 <- data.frame(Theta=seq(-6,6, by = .1), F2.item.info.data.long)
+F3.item.info.data.2 <- data.frame(Theta=seq(-6,6, by = .1), F3.item.info.data.long)
+F4.item.info.data.2 <- data.frame(Theta=seq(-6,6, by = .1), F4.item.info.data.long)
+F5.item.info.data.2 <- data.frame(Theta=seq(-6,6, by = .1), F5.item.info.data.long)
+
+F1.iic2 <- ggplot(F1.item.info.data.2,aes(Theta,value,col=variable))+geom_line()+apatheme+
+  ggtitle("F1 Item Information Plot")+theme(legend.position = "none")+
+  labs(y = "Item Information")+facet_wrap(~variable)+theme(strip.text.x = element_text(size = 15))+
+  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+scale_y_continuous(breaks=c(5,50,100,200), limits = c(0, 200))
+
+F2.iic2 <- ggplot(F2.item.info.data.2,aes(Theta,value,col=variable))+geom_line()+apatheme+
+  ggtitle("F2 Item Information Plot")+theme(legend.position = "none")+
+  labs(y = "Item Information")+facet_wrap(~variable)+theme(strip.text.x = element_text(size = 15))+
+  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")
+
+F3.iic2 <- ggplot(F3.item.info.data.2,aes(Theta,value,col=variable))+geom_line()+apatheme+
+  ggtitle("F3 Item Information Plot")+theme(legend.position = "none")+
+  labs(y = "Item Information")+facet_wrap(~variable)+theme(strip.text.x = element_text(size = 15))+
+  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")
+
+F4.iic2 <- ggplot(F4.item.info.data.2,aes(Theta,value,col=variable))+geom_line()+apatheme+
+  ggtitle("F4 Item Information Plot")+theme(legend.position = "none")+
+  labs(y = "Item Information")+facet_wrap(~variable)+theme(strip.text.x = element_text(size = 15))+
+  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")
+
+F5.iic2 <- ggplot(F5.item.info.data.2,aes(Theta,value,col=variable))+geom_line()+apatheme+
+  ggtitle("F5 Item Information Plot")+theme(legend.position = "none")+
+  labs(y = "Item Information")+facet_wrap(~variable)+theme(strip.text.x = element_text(size = 15))+
+  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")
+
+ICC2 <- cowplot::plot_grid(vic.iic2 , agg.iic2,  labels = "AUTO",ncol=2, label_size = 15,align = "v")
+ggsave("Figures/ICC2.jpeg",ICC2 , width = 12, height = 8, dpi = 1200, bg = "white")
+
 ```
@@
   geom_line()+apatheme+
-  labs(y="Test Information", title = "F1 Test Inforfamtion")
+  labs(y="Test Information", title = "F1 Test Inforfamtion")+scale_color_brewer(palette="Dark2")
 
@@
                      ncol = 2,
-                     label_size = 12,
-                     label_fontfamily = "serif",
+                     label_size = 15,
+                     label_fontfamily = "Arial",
                      label_fontface = "plain")
@@
           labels = "AUTO", label_size = 12,align = "v", ncol =2,
-                       label_fontfamily = "serif",
+                       label_fontfamily = "Arial",
                      label_fontface = "plain")

### 2022-01-09 manuscript.Rmd

@@
                   align = "v", 
-                  label_size = 15,
                   label_fontfamily = "Arial",
@@
 
-```{r EFAplot, fig.align='center', fig.cap='(A) Five Factor Solution obtained in Exploratory Factor Analysis.
-The factor loadings ranged between .49-.99 (B) Histogram of nonredundent residula correlations indicated 26% correlations are higher than absolute value of .05 indicating a possible under factoring', warning=FALSE,  results='asis'}
+```{r EFAplot, fig.align='center', fig.cap='(A) Five Factor Solution obtained in Exploratory Factor Analysis (B) Histogram of nonredundent residula correlations', warning=FALSE,  results='asis'}
 
@@
 By allowing item pain 41 & 30 to covary their error variance our model attained the best fit.", out.height="150%", out.width="100%", dpi=1200,  warning=FALSE}
+
 #library(semPlot)
@@
 ggsave("Manuscript.figures/F5.itemplots.png",F5.itemplots, width = 10, height = 12, dpi = 1200, bg = "white")
+
 ```
@@
 ggsave("Figures/ICC2.jpeg",ICC2 , width = 12, height = 8, dpi = 1200, bg = "white")
-
 ```

### 2022-01-09 appendix-2.Rmd
Figure legends corrected

@@
 However Item 04 had a bump at the righ side of the center with a curve peak higher than .20.
-Item 01 and 25 had relatively flat information curve with a peak lower than .20'', out.height='160%', out.width='100%'}
+Item 01 and 25 had relatively flat information curve with a peak lower than .20', out.height='160%', out.width='100%'}
 knitr::include_graphics('Manuscript.figures/F5.itemplots.png',dpi = 1200)

### 2022-01-09 manuscript.Rmd
Figure legends corrected

@@
 ```{r figcfa, fig.cap = "Five Factor  Model of LEBA obtained by Confirmatory Factor Analysis.
-By allowing item pain 41 & 30 to covary their error variance our model attained the best fit.", out.height="150%", out.width="100%", dpi=1200,  warning=FALSE}
+By allowing item pain 41 and 30 to covary their error variance our model attained the best fit.", out.height="150%", out.width="100%", dpi=1200,  warning=FALSE}
 
@@
 
-```{r iteminfo, eval=FALSE, warning=FALSE, include=FALSE}
-#Not used in the manuscript
-
-F1_item1<- plot(F1_fit, type = "infotrace", 
-                    facet_items = T, which.items = 1, main = "")
-
-F1_item2 <- plot(F1_fit, type = "infotrace", 
-     facet_items = T, which.items = 2,main = "")
-
-F1_item3 <- plot(F1_fit, type = "infotrace", 
-     facet_items = T, which.items = 3,main = "")
-
-F2_item1 <- plot(F2_fit, type = "infotrace", facet_items = T, which.items = 1,main = "")
-F2_item2 <- plot(F2_fit, type = "infotrace", facet_items = T, which.items = 2,main = "")
-F2_item3 <- plot(F2_fit, type = "infotrace", facet_items = T, which.items = 3,main = "")
-F2_item4 <- plot(F2_fit, type = "infotrace", facet_items = T, which.items = 4,main = "")
-F2_item5 <- plot(F2_fit, type = "infotrace", facet_items = T, which.items = 5,main = "")
-F2_item6 <- plot(F2_fit, type = "infotrace", facet_items = T, which.items = 6,main = "")
-
-F3_item1 <- plot(F3_fit, type = "infotrace", 
-                    facet_items = T, which.items = 1,main = "")
-F3_item2 <- plot(F3_fit, type = "infotrace", 
-                    facet_items = T, which.items = 2,main = "")
-
-F3_item3 <- plot(F3_fit, type = "infotrace", 
-                    facet_items = T, which.items = 3,main = "")
-F3_item4 <- plot(F3_fit, type = "infotrace", 
-                    facet_items = T, which.items = 4,main = "")
-F3_item5 <- plot(F3_fit, type = "infotrace", 
-                    facet_items = T, which.items = 5,main = "")
-
-F4_item1 <- plot(F4_fit, type = "infotrace", facet_items = T,which.items = 1,main = "")
-F4_item2 <- plot(F4_fit, type = "infotrace", facet_items = T,which.items = 2,main = "")
-F4_item3 <- plot(F4_fit, type = "infotrace", facet_items = T,which.items = 3,main = "")
-F4_item4 <- plot(F4_fit, type = "infotrace", facet_items = T,which.items = 4,main = "")
-
-F5_item1 <- plot(F5_fit, type = "infotrace", facet_items = T,which.items = 1,main = "")
-F5_item2 <-plot(F5_fit, type = "infotrace", facet_items = T,which.items = 2,main = "")
-F5_item3 <-plot(F5_fit, type = "infotrace", facet_items = T,which.items = 3,main = "")
-F5_item4 <-plot(F5_fit, type = "infotrace", facet_items = T,which.items = 4,main = "")
-F5_item5 <-plot(F5_fit, type = "infotrace", facet_items = T,which.items = 5,main = "")
-
-F1title <- ggdraw() + 
-  draw_label(
-    "F1: Wearing blue light filters",
-    fontface = 'bold',
-    x = 0,
-    hjust = 0
-  ) +
-  theme(
-    # add margin on the left of the drawing canvas,
-    # so title is aligned with left edge of first plot
-    plot.margin = margin(0, 0, 0, 7)
-  )
-
-F2title <- ggdraw() + 
-  draw_label(
-    "F2: Spending time outdoors",
-    fontface = 'bold',
-    x = 0,
-    hjust = 0
-  ) +
-  theme(
-    # add margin on the left of the drawing canvas,
-    # so title is aligned with left edge of first plot
-    plot.margin = margin(0, 0, 0, 7)
-  )
-
-F3title <- ggdraw() + 
-  draw_label(
-    "F3: Using phone and smart-watch in bed",
-    fontface = 'bold',
-    x = 0,
-    hjust = 0
-  ) +
-  theme(
-    # add margin on the left of the drawing canvas,
-    # so title is aligned with left edge of first plot
-    plot.margin = margin(0, 0, 0, 7)
-  )
-
-F4title <- ggdraw() + 
-  draw_label(
-    "F4: Using light before bedtime",
-    fontface = 'bold',
-    x = 0,
-    hjust = 0
-  ) +
-  theme(
-    # add margin on the left of the drawing canvas,
-    # so title is aligned with left edge of first plot
-    plot.margin = margin(0, 0, 0, 7)
-  )
-
-F5title <- ggdraw() + 
-  draw_label(
-    "F5: Using light...daytime",
-    fontface = 'bold',
-    x = 0,
-    hjust = 0
-  ) +
-  theme(
-    # add margin on the left of the drawing canvas,
-    # so title is aligned with left edge of first plot
-    plot.margin = margin(0, 0, 0, 7)
-  )
-
-f1itemplot <- plot_grid(F1_item1, F1_item2,F1_item3,
-          labels = "AUTO", label_size = 10,align = "v")
-f2itemplot <- plot_grid(F2_item1, F2_item2,F2_item3,F2_item4,F2_item5,F2_item6,
-           label_size = 10,align = "v")
-f3itemplot <- plot_grid(F3_item1, F3_item2,F3_item3,F3_item4,F3_item5,
-           label_size = 10,align = "v")
-f4itemplot <- plot_grid(F4_item1, F4_item2,F4_item3,F4_item4,
-          labels = "AUTO", label_size = 10,align = "v")
-
-f5itemplot <- plot_grid(F5_item1, F5_item2,F5_item3,F5_item4,F5_item5,
-          label_size = 10,align = "v")
-```
-
 ```{r iteminfoggplot3, include=F}
@@
 ```{r inteminfoggplo2com, eval=FALSE, include=FALSE}
-#Victimization
+
 pacman::p_load(reshape,ggsci)

### 2022-01-09 appendix-2.Rmd
Table 1 is nor landscape; dpi is set to 300 for all images

@@
 ```{r F1IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1. Item 16 carried highest information among the three items', out.height='160%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/F1.itemplots.png', dpi = 1200)
+knitr::include_graphics('Manuscript.figures/F1.itemplots.png', dpi = 600)
 ```
@@
 Item 09 carried the lowest information however its information peak was highr than .20.', out.height='160%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/F2.itemplots.png',dpi = 1200)
+knitr::include_graphics('Manuscript.figures/F2.itemplots.png',dpi = 600)
 ```
@@
 Item 30 and 41 had relatively flat information curve with a peak lower than .20', out.height='160%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/F3.itemplots.png',dpi = 1200)
+knitr::include_graphics('Manuscript.figures/F3.itemplots.png',dpi = 600)
 ```
@@
 ```{r F4IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F4. Item 38 had relatively flat information curve with a peak lower than .20', out.height='160%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/F4.itemplots.png',dpi = 1200)
+knitr::include_graphics('Manuscript.figures/F4.itemplots.png',dpi = 600)
 ```
@@
 Item 01 and 25 had relatively flat information curve with a peak lower than .20', out.height='160%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/F5.itemplots.png',dpi = 1200)
+knitr::include_graphics('Manuscript.figures/F5.itemplots.png',dpi = 600)
 ```
@@
 ```{r personfit, fig.cap="Person fit of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
-knitr::include_graphics("Manuscript.figures/personfit.png",dpi = 1200)
+knitr::include_graphics("Manuscript.figures/personfit.png",dpi = 600)
 ```

### 2022-01-09 manuscript.Rmd
Table 1 is nor landscape; dpi is set to 300 for all images

@@
 ```{r setup, warning=FALSE, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=1200, fig.width = 6,
+knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600, fig.width = 6,
  fig.asp = 0.8,out.width = "80%", dev=c('png','postscript'))
@@
 
-```{r reltab2}
+```{r reltab2, results='asis'}
 relevant.scale.data %>% 
-   kable( booktabs = T, caption ="Releated Scales", format ="latex", longtable =T) %>% 
-  kable_styling(latex_options = c("repeat_header", "scale_down")) %>% 
-  column_spec(1:6, width = "2cm")
-
+apa_table(landscape =T,caption ="Releated Scales", format = "latex",escape = T, font_size = "footnotesize", align = c("p{3cm}", rep("p{3.6cm}", ncol(relevant.scale.data)))) 
 ```
@@
   rsvg() %>%
-  png::writePNG("Manuscript.figures/Flowchart1.jpeg", dpi = 1200)
+  png::writePNG("Manuscript.figures/Flowchart1.jpeg", dpi = 600)
 
@@
 #to show pvalue in the fig add p.mat=p.mat
-ggsave("Manuscript.figures/corplot.png",corplot, width = 6, height = 6, dpi = 1200, bg ="white")
+ggsave("Manuscript.figures/corplot.png",corplot, width = 6, height = 6, dpi = 600, bg ="white")
 
@@
 
-knitr::include_graphics('Manuscript.figures/corplot.png', dpi =1200)
+knitr::include_graphics('Manuscript.figures/corplot.png', dpi =600)
 
@@
                   label_fontface = "plain")
-ggsave("Manuscript.figures/factors.png",fator, width = 6, height = 12, dpi = 1200)
+ggsave("Manuscript.figures/factors.png",fator, width = 6, height = 12, dpi = 600)
 ```
@@
   rsvg() %>%
-  png::writePNG("Manuscript.figures/EFAplot.png",dpi =1200)
+  png::writePNG("Manuscript.figures/EFAplot.png",dpi =600)
 
@@
 
-ggsave("Manuscript.figures/EFAfull.png",EFAplot.1, width = 4, height =8, dpi = 1200, bg ="white")
+ggsave("Manuscript.figures/EFAfull.png",EFAplot.1, width = 4, height =8, dpi = 600, bg ="white")
 
@@
 
-knitr::include_graphics('Manuscript.figures/EFAfull.png', dpi =1200)
+knitr::include_graphics('Manuscript.figures/EFAfull.png', dpi =600)
 ```
@@
 ```{r efagtPic, echo=FALSE, out.height="100%", out.width= '100%', fig.cap= ' Summary Descriptives EFA Sample'}
-knitr::include_graphics('Manuscript.figures/efagt.png',dpi =1200)
+knitr::include_graphics('Manuscript.figures/efagt.png',dpi =600)
 
@@
 ```{r cfagtPic, echo=FALSE, out.height="100%", out.width= '100%', fig.cap= ' Summary Descriptives of CFA Sample'}
-knitr::include_graphics('Manuscript.figures/cfagt.png',dpi =1200)
+knitr::include_graphics('Manuscript.figures/cfagt.png',dpi =600)
 
@@
 ```{r figcfa, fig.cap = "Five Factor  Model of LEBA obtained by Confirmatory Factor Analysis.
-By allowing item pain 41 and 30 to covary their error variance our model attained the best fit.", out.height="150%", out.width="100%", dpi=1200,  warning=FALSE}
+By allowing item pain 41 and 30 to covary their error variance our model attained the best fit.", out.height="150%", out.width="100%", dpi=600,  warning=FALSE}
 
@@
                      label_fontface = "plain")
-ggsave("Manuscript.figures/F2.itemplots.png",F2.itemplots, width = 10, height = 12, dpi = 1200, bg = "white")
+ggsave("Manuscript.figures/F2.itemplots.png",F2.itemplots, width = 10, height = 12, dpi = 600, bg = "white")
 
@@
                      label_fontface = "plain")
-ggsave("Manuscript.figures/F3.itemplots.png",F3.itemplots, width = 10, height = 12, dpi = 1200,bg = "white")
+ggsave("Manuscript.figures/F3.itemplots.png",F3.itemplots, width = 10, height = 12, dpi = 600,bg = "white")
 
@@
                      label_fontface = "plain")
-ggsave("Manuscript.figures/F4.itemplots.png",F4.itemplots, width = 10, height = 12, dpi = 1200,bg = "white")
+ggsave("Manuscript.figures/F4.itemplots.png",F4.itemplots, width = 10, height = 12, dpi = 600,bg = "white")
 
@@
                      label_fontface = "plain")
-ggsave("Manuscript.figures/F5.itemplots.png",F5.itemplots, width = 10, height = 12, dpi = 1200, bg = "white")
+ggsave("Manuscript.figures/F5.itemplots.png",F5.itemplots, width = 10, height = 12, dpi = 600, bg = "white")
 
@@
 ICC2 <- cowplot::plot_grid(vic.iic2 , agg.iic2,  labels = "AUTO",ncol=2, label_size = 15,align = "v")
-ggsave("Figures/ICC2.jpeg",ICC2 , width = 12, height = 8, dpi = 1200, bg = "white")
+ggsave("Figures/ICC2.jpeg",ICC2 , width = 12, height = 8, dpi = 600, bg = "white")
 ```
@@
                      label_fontface = "plain")
-ggsave("Manuscript.figures/TIC.png",TIC, width = 10, height = 12, dpi = 1200, bg = "white")
+ggsave("Manuscript.figures/TIC.png",TIC, width = 10, height = 12, dpi = 600, bg = "white")
 
@@
 
-knitr::include_graphics('Manuscript.figures/TIC.png', dpi =1200)
+knitr::include_graphics('Manuscript.figures/TIC.png', dpi =600)
 ```
@@
 
-ggsave("Manuscript.figures/personfit.png",personfit , width = 10, height = 12, dpi = 1200, bg = "white")
+ggsave("Manuscript.figures/personfit.png",personfit , width = 10, height = 12, dpi = 600, bg = "white")
 

### 2022-01-09 manuscript.Rmd
Figure legends updated

@@
 
-```{r}
+```{r corplot, include =F}
 corplot <- ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
@@
 
-```{r figCor, out.height="150%",out.width="100%",fig.cap= "Inter item ploychroric correlationc coefficients for the 48 items.
-The red gradient indicates negative correlations, white indicates zero correlation and the blue gradient indicate positive correlations.
-4.9% inter-item correlation coefficients were higher than .30 ",results='asis', fig.align='center'}
+(ref:figCor) Inter item polychoric correlation coefficients for the 48 items. 4.9 % inter-item correlation coefficients were higher than .30
+
+```{r figCor, out.height="150%",out.width="100%", fig.align= 'center', fig.cap='(ref:figCor)', results='asis', fig.align='center'}
 
@@
                   label_fontface = "plain")
-ggsave("Manuscript.figures/factors.png",fator, width = 6, height = 12, dpi = 600)
-```
-
-```{r facIdFig, out.height="100%", out.width="100%",fig.align='center', fig.cap='Factor Identification Methods (A) In parallel analysis we drew 500 sets of random data with the same number of participants as our orihinal data (n=428) and adjusted the mean eigenvalues for sample bias.
-In x-axis we plotted the number of possible factors and in y axis we plotted the mean ajusted eigenvalues.
-The First inflection point of the plot indicated the optimal number of factor was six.
-re  (B) In the scree scree plot possible numner of factors are plotted againest obtained eigen values.
-Scree plot suggested six factors.
-(C) In Hull method we plotted the number of posible factors in the x axis and in the y axis we ploed the CAF index(CAF: Common Part Accounted for-an indicator of model fit).
-Hull method indicated 5 factors are requied to  balance model fit and the number of parameters ',  warning=FALSE, results= 'asis'}
+ggsave("Manuscript.figures/factors.png",fator, width = 5, height = 7, dpi = 600)
+```
+
+(ref:facIdFig) Factor Identification Methods (A) Parallel analysis  indicated the optimal number of factors were six.
+(B) Scree plot suggested six factors.
+(C) Hull method indicated 5 factors were required to balance the model fit and number of parameters.
+
+```{r facIdFig, fig.align= 'center', fig.cap='(ref:facIdFig)',  warning=FALSE, results= 'asis'}
 

### 2022-01-10 Additional material(to be deletd later))/appendix-1.Rmd
Decluttred appendix All external string based tables are converted into csv

```{r configure, include=FALSE}
library(Hmisc)
data <- readRDS("leba_2021-09-08.rds")
sem.data <- data[, 9:56] 
prefix <- "item"
sufix <- c(1:48)
colnam <- paste(prefix,sufix, sep = "" )
colnames(sem.data) <- colnam
```

\newpage
**Disclaimer**: This is a non-public version of LEBA (dated \today) and still a work in progress. Please do not distribute!

LEBA captures light exposure-related behaviours on a 5 point Likert type scale ranging from 1 to 5 (Never = 1; Rarely = 2; Sometimes = 3; Often = 4; Always = 5). The score of each factor is calculated by the summation of scores of items belonging to the corresponding factor.

\blandscape

# LEBA Long Form (23 Items)
"Please indicate how often you performed the following behaviours in the **past 4 weeks.**"

|     | Items                      | Never | Rarely | Sometimes | Often | Always |
|-----|----------------------------|-------|--------|-----------|-------|--------|
| 1   | `r label(sem.data$item16)` |       |        |           |       |        |
| 2   | `r label(sem.data$item17)` |       |        |           |       |        |
| 3   | `r label(sem.data$item36)` |       |        |           |       |        |
| 4   | `r label(sem.data$item8)`  |       |        |           |       |        |
| 5   | `r label(sem.data$item10)` |       |        |           |       |        |
| 6   | `r label(sem.data$item9)`  |       |        |           |       |        |
| 7   | `r label(sem.data$item11)` |       |        |           |       |        |
| 8   | `r label(sem.data$item12)` |       |        |           |       |        |
| 9   | `r label(sem.data$item7)`  |       |        |           |       |        |
| 10  | `r label(sem.data$item27)` |       |        |           |       |        |
| 11  | `r label(sem.data$item3)`  |       |        |           |       |        |
| 12  | `r label(sem.data$item40)` |       |        |           |       |        |
| 13  | `r label(sem.data$item30)` |       |        |           |       |        |
| 14  | `r label(sem.data$item41)` |       |        |           |       |        |
| 15  | `r label(sem.data$item32)` |       |        |           |       |        |
| 16  | `r label(sem.data$item35)` |       |        |           |       |        |
| 17  | `r label(sem.data$item38)` |       |        |           |       |        |
| 18  | `r label(sem.data$item33)` |       |        |           |       |        |
| 19  | `r label(sem.data$item46)` |       |        |           |       |        |
| 20  | `r label(sem.data$item45)` |       |        |           |       |        |
| 21  | `r label(sem.data$item25)` |       |        |           |       |        |
| 22  | `r label(sem.data$item4)`  |       |        |           |       |        |
| 23  | `r label(sem.data$item1)`  |       |        |           |       |        |

\elandscape

\newpage

\blandscape

## Latent Structure, and Reliability

The long form of LEBA consists 23 items with five factors.

| Factor names                                      | Items                    | Reliability Coefficients: ordinal alpha |
|---------------------------------------------------|--------------------------|-----------------------------------------|
| F1: Wearing blue light filters                    | 1-3                      | .96                                     |
| F2: Spending time outdoors                        | 4-9 (Item 4 is reversed) | .83                                     |
| F3: Using phone and smartwatch in bed             | 10-14                    | .70                                     |
| F4: Using light before bedtime                    | 15-18                    | .69                                     |
| F5: Using light in the morning and during daytime | 19-23                    | .52                                     |
| McDonald's Omega coefficient for the total scale  |                          | .73 (Total scale)                       |

LEBA -long form showed satisfactory structural validity (CFI =.97; TLI = .96; RMSEA = .05 [.04-.06, 90% CI]; SRMR = .09).

\elandscape

\newpage

\blandscape

# LEBA Short Form (18 Items)

"Please indicate how often you performed the following behaviours in the **past 4 weeks.**"

|     | Short Form (18 Items)      | Never | Rarely | Sometimes | Often | Always |
|-----|----------------------------|-------|--------|-----------|-------|--------|
| 01  | `r label(sem.data$item16)` |       |        |           |       |        |
| 02  | `r label(sem.data$item17)` |       |        |           |       |        |
| 03  | `r label(sem.data$item36)` |       |        |           |       |        |
| 04  | `r label(sem.data$item8)`  |       |        |           |       |        |
| 05  | `r label(sem.data$item9)`  |       |        |           |       |        |
| 06  | `r label(sem.data$item10)` |       |        |           |       |        |
| 07  | `r label(sem.data$item11)` |       |        |           |       |        |
| 08  | `r label(sem.data$item12)` |       |        |           |       |        |
| 09  | `r label(sem.data$item7)`  |       |        |           |       |        |
| 10  | `r label(sem.data$item27)` |       |        |           |       |        |
| 11  | `r label(sem.data$item3)`  |       |        |           |       |        |
| 12  | `r label(sem.data$item40)` |       |        |           |       |        |
| 13  | `r label(sem.data$item32)` |       |        |           |       |        |
| 14  | `r label(sem.data$item35)` |       |        |           |       |        |
| 15  | `r label(sem.data$item33)` |       |        |           |       |        |
| 16  | `r label(sem.data$item46)` |       |        |           |       |        |
| 17  | `r label(sem.data$item45)` |       |        |           |       |        |
| 18  | `r label(sem.data$item4)`  |       |        |           |       |        |

\elandscape

\newpage

\blandscape

## Latent Structure

The short form of LEBA consists 23 items with five factors.

| Factor names                                          | Items                    |
|-------------------------------------------------------|--------------------------|
| **F1: Wearing blue light filters**                    | 1-3                      |
| **F2: Spending time outdoors**                        | 4-8 (Item 4 is reversed) |
| **F3: Using phone and smart-watch in bed**            | 9-11                     |
| **F4: Using light before bedtime**                    | 12-14                    |
| **F5: Using light in the morning and during daytime** | 15-17                    |

## How to cite:

\elandscape

\newpage

### 2022-01-10 appendix-1.Rmd
Decluttred appendix All external string based tables are converted into csv

@@
+**Disclaimer**: This is a non-public version of LEBA (dated \today) and still a work in progress. Please do not distribute!
+
+LEBA captures light exposure-related behaviours on a 5 point Likert type scale ranging from 1 to 5 (Never = 1; Rarely = 2; Sometimes = 3; Often = 4; Always = 5).
+The score of each factor is calculated by the summation of scores of items belonging to the corresponding factor.
+
+**Instruction:**
+
+"Please indicate how often you performed the following behaviours in the **past 4 weeks.**"
+
+```{r longdata, include =F}
+long <- readxl::read_excel("Table_raw/LEBA Long.xlsx")
+long <- long %>% mutate_all(~ replace_na(.x, " "))
+```
+
+```{r LEBAlong, warning =F}
+long %>% 
+apa_table(landscape =T,caption ="LEBA Long Form (23 Items) ",  font_size = "footnotesize", align = c("p{15cm}", rep("p{1cm}", ncol(long)))) 
+```
+
+```{r longreldata, include =F}
+long.rel <- readxl::read_excel("Table_raw/LEBA_longs_structure.xlsx")
+long.rel <- long.rel %>% mutate_all(~ replace_na(.x, " "))
+```
+
+```{r longrel, warning =F}
+long.rel %>% 
+apa_table(landscape =F,caption ="LEBA Long Form (23 Items):Latent Structure and Reliability ",  font_size = "footnotesize")
+```
+
+```{r shortdata, include =F}
+short <- readxl::read_excel("Table_raw/LEBA_Short.xlsx")
+short <-short%>% mutate_all(~ replace_na(.x, " "))
+```
+
+```{r LEBAshort, warning =F}
+short %>% 
+apa_table(landscape =T,caption ="LEBA Short Form (18 Items) ",  font_size = "footnotesize", align = c("p{15cm}", rep("p{1cm}", ncol(short)))) 
+```
+
+```{r shortreldata, include =F}
+short.rel <- readxl::read_excel("Table_raw/LEBA_short_structure.xlsx")
+short.rel <- long.rel %>% mutate_all(~ replace_na(.x, " "))
+```
+
+```{r lshortrel, warning =F}
+short.rel %>% 
+apa_table(landscape =F,caption ="LEBA Short Form (18 Items):Latent Structure ",  font_size = "footnotesize")
+```
+
 ```{r factormp, warning=F}
-map <- readr::read_csv("Table_raw/map_stat")
+map <- readr::read_csv("Table_raw/map_stat.csv")
 map1 <- (map$`MAP Statistic`)
-
 map1 <- MOTE::apa(map1,5,F)
@@
 
-papaja::apa_table(map3, caption = "Map Statistics")
 ```
 
-```{r EFAResiduals, out.height= "100%",  fig.align='center', fig.cap= ' Histogram of residuals:  five-factor solution',  out.width="100%",  warning=FALSE, results='asis'}
-knitr::include_graphics('Manuscript.figures/EFAResidual.png')
-
+```{r map}
+papaja::apa_table(map3, caption = "Minimum Average Partial (MAP) method of factor numder determination. MAP Statistics is the lowest in the 5th row indicating five factors are required.")
 ```
@@
 
-```{r midesp, warning=F, message=F}
+```{r midesp, warning=F, message=F, results='asis'}
 mides_kable %>% 
@@
 
-```{r F1IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/F1testinfo.png')
+```{r MinRes, include=F}
+library(psych)
+library(tabledown)
+library(kableExtra)#without this pdf rendering will not happen
+
+data <- readRDS("leba_2021-09-08.rds")
+
+# Separating EFA and CFA samples with descriptive column
+descriptives.data <- data
+
+## Merge "0"s and "1"s into "1"s select,subset assign)
+descriptives.data[ , 9:56 ][ descriptives.data[ , 9:56 ] == 0 ] <- 1
+#EFA.descriptives <- descriptives.data[1:428,]
+EFA.descriptives <- subset(descriptives.data, IncludedInEFA == "TRUE")
+#CFA.descriptives <- descriptives.data[429:690, ]
+CFA.descriptives<- subset(descriptives.data, IncludedInEFA == "FALSE")
+
+#Separating the EFA and CFA(only items)
+sem.data <- data[, 9:56] #EFA & CFA data
+sem.data[ sem.data == 0] <- 1 #Merged "0"s and "1"s into "1"s
+
+## renaming the column-header
+prefix <- "item"
+sufix <- c(1:48)
+colnam <- paste(prefix,sufix, sep = "" )
+colnames(sem.data) <- colnam
+
+names(sem.data)[names(sem.data) == "item1"] <- "item01"
+names(sem.data)[names(sem.data) == "item2"] <- "item02"
+names(sem.data)[names(sem.data) == "item3"] <- "item03"
+names(sem.data)[names(sem.data) == "item4"] <- "item04"
+names(sem.data)[names(sem.data) == "item5"] <- "item05"
+names(sem.data)[names(sem.data) == "item6"] <- "item06"
+names(sem.data)[names(sem.data) == "item7"] <- "item07"
+names(sem.data)[names(sem.data) == "item8"] <- "item08"
+names(sem.data)[names(sem.data) == "item9"] <- "item09"
+
+### EFA data
+EFA.data <- sem.data[1:428, ]
+#Polychoric Correlation matrix
+
+correlations <- psych::polychoric(EFA.data, correct = 0)
+
+#Supplementary EFA with Minres Extraction
+
+fa.5F.min.1 <- fa(r=correlations$rho, nfactors = 5, fm= "minres",rotate ="varimax",
+                residuals = TRUE, SMC = TRUE, n.obs =428)
+EE <- print(fa.5F.min.1, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.5F.min.1 <- dplyr::select(EFA.data ,
+                                    -c( item20, item19, item05, item31, item44, item24, item43, item39, item22, item02, item18, item48, item42, item29, item06, item15, item23, item28, item14))
+
+correlations.red.5F.min.1 <- polychoric(reduced.model.5F.min.1,correct = 0)
+
+fa.5F.min.2 <- fa(r=correlations.red.5F.min.1$rho, nfactors = 5, fm= "minres",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+
+FF <- print(fa.5F.min.2, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.5F.min.2 <- dplyr::select(EFA.data, -c( item20, item19, item05, item31, item44, item24, item43, item39, item22, item02, item18, item48, item42, item29, item06, item15, item23, item28, item14, item34, item47, item21, item13))
+
+correlations.red.5F.min.2 <- polychoric(reduced.model.5F.min.2, correct = 0)
+
+fa.5F.min.3 <- fa(r=correlations.red.5F.min.2$rho, nfactors = 5, fm= "minres",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+
+GG <- print(fa.5F.min.3, cut = .3, digits = 3, sort = TRUE)
+
+minresTab <- tabledown::fac.tab(fa.5F.min.3, cut =.3,complexity = F)
 ```
 
-```{r F2IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/F2testinfo.png')
+```{r MinResTab}
+papaja::apa_table(minresTab,  caption = "Factor loadings and communality of the retained items (Minmum Residual)", note = "Only loading higher than .30 is reported", longtable=T, font_size = "footnotesize")
 ```
 
-```{r F3IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/F3testinfo.png')
+```{r sixFac, include=F}
+# EFA with 6 factor (rejected)
+
+#correlations <- polychoric(EFA.factor, correct = 0)
+
+fa.6F.1 <- fa(r=correlations$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+
+II <- print(fa.6F.1, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.6F.1 <- dplyr::select(EFA.data ,
+                                    -c(item34, item44, item48, item43, item39, item22, item02, item20, item21, item24,item30, item14, item28, item06, item15, item23))
+
+correlations.red.6F.1 <- polychoric(reduced.model.6F.1,correct = 0)
+
+fa.6F.2 <- fa(r=correlations.red.6F.1$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+
+JJ <- print(fa.6F.2, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.6F.2 <- dplyr::select(EFA.data, -c(item34, item44, item48, item43, item39, item22, item02, item20, item21, item24,item30, item14, item28, item06, item15, item23, item18, item42, item47, item41))
+
+correlations.red.6F.2 <- polychoric(reduced.model.6F.2,correct = 0)
+
+fa.6F.3 <- fa(r=correlations.red.6F.2$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)
+
+KK <- print(fa.6F.3, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.6F.3 <- dplyr::select(EFA.data, -c(item34, item44, item48, item43, item39, item22, item02, item20, item21, item24,item30, item14, item28, item06, item15, item23, item18, item42, item47, item41, item05, item13, item29))
+
+correlations.red.6F.3 <- polychoric(reduced.model.6F.3,correct = 0)
+
+fa.6F.4 <- fa(r=correlations.red.6F.3$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)
+
+ll <- print(fa.6F.4, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.6F.4 <- dplyr::select(EFA.data, -c(item34, item44, item48, item43, item39, item22, item02, item20, item21, item24,item30, item14, item28, item06, item15, item23, item18, item42, item47, item41, item05, item13, item29, item19))
+
+correlations.red.6F.4 <- polychoric(reduced.model.6F.4,correct = 0)
+
+fa.6F.5 <- fa(r=correlations.red.6F.4$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428, max.iter = 500)
+
+mm <- print(fa.6F.5, cut = .3, digits = 3, sort = TRUE)
+
+# Residuals
+residual.6F =residuals(fa.6F.5 , diag = FALSE, na.rm =T)
+#Count of numbers of residuals>.05
+BigRRR= sum(residual.6F>abs(.05), na.rm =T)
+print(BigRRR)
+
+#Total number of off diagonal elements in the data matrix
+totRRR = length(reduced.model.6F.2)*(length(reduced.model.6F.2)-1)/2
+
+# Proportion of off-diagonal elements >.10
+sumRRR <- sum(BigRRR/totRRR*100)
+
+#hist(residual.6F, main = NULL, xlab = "Six factor Solution: Residuals",ylim=c(0, 400))
+#abline(h =65, lwd = 2, lty = 2)
+#abline(v =.05,lwd = 2, lty = 2)
+sixFac <- tabledown::fac.tab(fa.6F.5, cut =.3,complexity = F)
 ```
 
-```{r F4IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/F4testinfo.png')
+```{r sixFacTab}
+papaja::apa_table(sixFac,  caption = "Factor loadings and communality of the retained items(six factor)", note = "Only loading higher than .30 is reported; Sixth factor has only two salient loadings",longtable =T, font_size = "footnotesize")
 ```
 
-```{r F5IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1', out.height='160%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/F5testinfo.png')
+```{r DataAppB, include=FALSE}
+data <- readRDS("leba_2021-09-08.rds")
+
+#Separating the EFA and CFA(only items)
+sem.data <- data[, 9:56] #EFA & CFA data
+## renaming the column-header
+prefix <- "item"
+sufix <- c(1:48)
+colnam <- paste(prefix,sufix, sep = "" )
+colnames(sem.data) <- colnam
+names(sem.data)[names(sem.data) == "item1"] <- "item01"
+names(sem.data)[names(sem.data) == "item2"] <- "item02"
+names(sem.data)[names(sem.data) == "item3"] <- "item03"
+names(sem.data)[names(sem.data) == "item4"] <- "item04"
+names(sem.data)[names(sem.data) == "item5"] <- "item05"
+names(sem.data)[names(sem.data) == "item6"] <- "item06"
+names(sem.data)[names(sem.data) == "item7"] <- "item07"
+names(sem.data)[names(sem.data) == "item8"] <- "item08"
+names(sem.data)[names(sem.data) == "item9"] <- "item09"
+EFA.data <- sem.data[1:428, ]
+
+correlations <- psych::polychoric(EFA.data, correct = 0)
+
+```
+
+```{r ggplot2AppB, include=F}
+apatheme=theme_bw()+
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.background = element_blank(),
+        #text=element_text(family = "Helvetica"),
+        axis.text.x = element_text(size = 15),
+        axis.text.y = element_text(size = 15),
+        axis.title.x = element_text(size = 15),
+        axis.title.y = element_text(size = 15),
+        plot.title = element_text(size = 15),
+        legend.text = element_text(size = 15),
+        legend.title=element_blank(),
+        axis.line.x = element_line(color='black'),
+        axis.line.y = element_line(color='black'),
+        panel.border = element_rect(color = "black",
+                                    fill = NA,
+                                    size = 1))
+```
+
+```{r EFAAppB, include=FALSE}
+fa.5F.1 <- fa(r=correlations$rho, nfactors = 5, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+AA <- print(fa.5F.1, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.5F.1 <- dplyr::select(EFA.data ,
+                                    -c(item32, item34, item24, item37, item22, item05,
+                                        item28, item30, item39,item23, item45, item06, item29, item02, item41))
+
+correlations.red.5F.1 <- polychoric(reduced.model.5F.1,correct = 0)
+
+fa.5F.2 <- fa(r=correlations.red.5F.1$rho, nfactors = 5, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+
+BB <- print(fa.5F.2, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.5F.2 <- dplyr::select(EFA.data, -c( item32, item34, item24, item37, item22, item05,
+                                        item28, item30, item39,item23, item45, item06, item29, item02, item41, item46, item13, item15, item25, item01, item26, item14))
+
+correlations.red.5F.2 <- polychoric(reduced.model.5F.2,correct = 0)
+
+fa.5F.3 <- fa(r=correlations.red.5F.2$rho, nfactors = 5, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428,max.iter = 500 )
+
+CC <- print(fa.5F.3, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.5F.3 <- dplyr::select(EFA.data, -c( item32, item34, item24, item37, item22, item05,
+                                        item28, item30, item39,item23, item45, item06, item29, item02, item41, item46, item13, item15, item25, item01, item26, item14, item43, item42))
+
+correlations.red.5F.3 <- polychoric(reduced.model.5F.3,correct = 0)
+
+fa.5F.4 <- fa(r=correlations.red.5F.3$rho, nfactors = 5, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428,max.iter = 500 )
+
+CC <- print(fa.5F.4, cut = .3, digits = 3, sort = TRUE)
+```
+
+```{r factordetailsAppB, include=FALSE}
+#Preparing the EFA table
+efa.table <- tabledown::fac.tab(fa.5F.4,.3, complexity = F) 
+```
+
+```{r efaunmerged}
+apa_table(efa.table, caption = "Factor loadings and communality of the retained items in five factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T, font_size = "footnotesize")
+```
+
+```{r EFAAppsix, include=FALSE, warning=F,message=FALSE}
+
+library(Hmisc)
+fa.6F.1 <- fa(r=correlations$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+DD <- print(fa.6F.1, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.6F.1 <- dplyr::select(EFA.data ,
+                                    -c(item32, item34, item44,item24, item37, item22, item05,
+                                        item28,item39,item23, item45, item06, item29, item02, item41, item30))
+
+correlations.red.6F.2 <- polychoric(reduced.model.6F.1,correct = 0)
+
+fa.6F.2 <- fa(r=correlations.red.6F.2$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+
+EE <- print(fa.6F.2, cut = .3, digits = 3, sort = TRUE)
+reduced.model.6F.2 <- dplyr::select(EFA.data ,
+                                    -c(item32, item34, item44,item24, item37, item22, item05,
+                                        item28,item39,item23, item45, item06, item29, item02, item41, item30, item46, item36,item01, item25))
+correlations.red.6F.3 <- polychoric(reduced.model.6F.2,correct = 0)
+fa.6F.3 <- fa(r=correlations.red.6F.3$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+FF <- print(fa.6F.3, cut = .3, digits = 3, sort = TRUE)
+
+reduced.model.6F.3 <- dplyr::select(EFA.data ,
+                                    -c(item32, item34, item44,item24, item37, item22, item05,
+                                        item28,item39,item23, item45, item06, item29, item02, item41, item30, item46, item36,item01, item25, item18))
+correlations.red.6F.4 <- polychoric(reduced.model.6F.3,correct = 0)
+fa.6F.4 <- fa(r=correlations.red.6F.4$rho, nfactors = 6, fm= "pa",rotate ="varimax",
+              residuals = TRUE, SMC = TRUE, n.obs =428)
+FF <- print(fa.6F.4, cut = .3, digits = 3, sort = TRUE)
+
+efa.table.2 <- tabledown::fac.tab(fa.6F.4,.3, complexity = F) 
+```
+
+```{r EFAsix}
+apa_table(efa.table.2, caption = "Factor loadings and communality of the retained items in six factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T, font_size = "footnotesize")
+```
+
+```{r tzdata, include=F}
+tz <- read_csv("Table_raw/timezone.csv")
+tz <- tz[,-1]
+colnames(tz) <- c("Timezone", "Number of Participants")
+participants <- sum(tz[, 'Number of Participants'])
+```
+
+```{r tztable}
+apa_table(tz, longtable =T,font_size = "footnotesize", caption = "Geographical Location of the participants (n =690)")
+```
+
+```{r unmerged-data, include =F}
+unmerged <- read_excel("Table_raw/LEBA_unmerged_fa.xlsx")
+```
+
+```{r unmertab}
+apa_table(unmerged , longtable =T, font_size = "footnotesize")
+```
+
+```{r F1IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1. Item 16 carried highest information among the three items', out.height='160%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/F1.itemplots.png', dpi = 600)
+```
+
+```{r F2IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F2.
+All items cariied information across the latent trait continuum.
+Item 09 carried the lowest information however its information peak was highr than .20.', out.height='160%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/F2.itemplots.png',dpi = 600)
+```
+
+```{r F3IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F3.
+Item 30 and 41 had relatively flat information curve with a peak lower than .20', out.height='160%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/F3.itemplots.png',dpi = 600)
+```
+
+```{r F4IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F4. Item 38 had relatively flat information curve with a peak lower than .20', out.height='160%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/F4.itemplots.png',dpi = 600)
+```
+
+```{r F5IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F5.
+Three items: 25, 04, 01 carriedlow information.
+However Item 04 had a bump at the righ side of the center with a curve peak higher than .20.
+Item 01 and 25 had relatively flat information curve with a peak lower than .20', out.height='160%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/F5.itemplots.png',dpi = 600)
 ```
@@
 ```{r personfit, fig.cap="Person fit of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
-knitr::include_graphics("Manuscript.figures/personfit.png")
+knitr::include_graphics("Manuscript.figures/personfit.png",dpi = 600)
 ```

### 2022-01-10 manuscript.Rmd
Decluttred appendix All external string based tables are converted into csv

@@
 Here, we present a novel, self-reported and psychometrically validated instrument to capture light exposure-related behaviour, the Light Exposure Behavior Assessment (LEBA).
+
   An expert panel prepared the initial 48 item pool.
 Responses to these items were then collected in an online survey producing responses from an international sample (690 completed responses, 74 countries, 28 time zones).
-Exploratory factor analysis on an initial subset of our sample (n=428) rendered a five-factor solution with 25 items (Wearing blue light filters, spending time outdoors, using phone and smart-watch in bed, using light before bedtime, using light in the morning and during daytime).
-Confirmatory factor analysis on another subset of participants (n=262) yielded the best fit for the five-factor solution after discarding another two items (CFI=0.97, TLI=0.96, RMSEA=0.05, SRMR=0.09).
-The internal consistency reliability coefficient for the total instrument was McDonald’s omega =0.73.
+Exploratory factor analysis (EFA) on an initial subset of our sample (n=428) rendered a five-factor solution with 25 items (Wearing blue light filters, spending time outdoors, using phone and smart-watch in bed, using light before bedtime, using light in the morning and during daytime).
+In a confirmatory factor analysis (CFA) performed on an independent subset of participants (n=262), we removed two further items to attain the best fit for the five-factor solution (CFI=0.97, TLI=0.96, RMSEA=0.05, SRMR=0.09).
+The internal consistency reliability coefficient for the total instrument was McDonald’s omega_total=0.73.
 Measurement model invariance analysis between native and non-native English speakers showed our model attained the highest level of invariance (residual invariance; CFI=0.95, TLI =0.95, RMSEA=0.05).
 Lastly, a short form of LEBA (n=18) was developed using Item Response Theory on the complete sample (n=690).
-  The psychometric properties of the LEBA instrument indicate the usability to measure the light exposure-related behaviours across a variety of settings and may offer a scalable solution to characterize light exposure-related behaviours in remote samples.
+
+  The psychometric properties of the LEBA instrument indicate the usability to measure the light exposure-related behaviours across a variety of settings and may offer a scalable solution to characterise light exposure-related behaviours in remote samples.
+The LEBA instrument will be available under the open-access CC-BY-NC-ND license.
 
@@
     latex_engine: xelatex
-    includes:
-      in_header: header.tex
 appendix:
   - "appendix-1.Rmd"
-  - "appendix-2.Rmd"
-  - "appendix-3.Rmd"
 mainfont: Arial
@@
 TZ <- as.data.frame(str_split_fixed(country$slypos_demographics_tz.factor, "-", 2))
+TZ[97, 2] <- " East Africa/Dodoma (UTC +03:00)"
+TZ[146, 2] <- " European /Skopje (UTC +01:00)"
+TZ[176, 2] <- " Asia /Taipei City (UTC +08:00)"
+TZ[574, 2] <- " Asia /Taipei City (UTC +08:00)"
+TZ[690, 2] <- " Asia /Taipei City (UTC +08:00)"
+TZ[273, 2] <- " Iran /Tehran (UTC +0:30)"
+TZ[418, 2] <- " Iran /Tehran (UTC +0:30)"
+TZ[673, 2] <- " Iran /Tehran (UTC +0:30)"
 
@@
 numUTC <- unique(UTC$V2)
+```
+
+```{r timezone, include=F}
+
+timezone <- TZ %>% 
+  group_by(V2) %>% 
+  count() %>% 
+  as.data.frame()
+
+write.csv(timezone, "Table_raw/timezone.csv")
+
 ```
@@
 For estimating the sample size for the confirmatory factor analysis (CFA) we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per parameter is required to earn trustworthiness of the result.
-Our sample size exceeds these requirements: Anonymous responses from a total of *n* = `r nrow(desctable.data)` participants were included in the analysis of the current study, split into samples for exploratory (EFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "1.
-EFA Sample",])`) and confirmatory factor analysis (CFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "2.
+Our sample size exceeds these requirements: Anonymous responses from a total of *n* = `r nrow(desctable.data)` participants were included in the analysis of the current study, split into samples for Exploratory Factor Analysis (EFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "1.
+EFA Sample",])`) and Confirmatory Factor Analysis (CFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "2.
 CFA Sample",])`).
@@
 
-write.csv(full.map, "Table_raw/map_stat")
+write.csv(full.map, "Table_raw/map_stat.csv")
 ```
@@
 ```{r tabCfa, results='asis'}
-apa_table(CFa.matrix, caption = "Fit indices of CFA", align = "c", landscape = T, note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index;RMSEA:Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square ")
+apa_table(CFa.matrix, caption = "Confirmatory Factor Analysis model fit indices of the two model: five factor model with 25 items and five factor model with 23 items.
+The second model attained the best fit.", align = "c", landscape = T, note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index;RMSEA:Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square ")
 ```
@@
 ```{r InvarianceTab, results='asis'}
-apa_table(Invariance.table, align = "c",  caption = "Invariance Analysis", note = " a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual;* =  df of model comparison", landscape = T, font_size = "footnotesize" )
+apa_table(Invariance.table, align = "c",  caption = "Measurment Invariance analysis on CFA sampe (n=262) across native and non-native English speakers.", note = " a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual;* =  df of model comparison", landscape = T, font_size = "footnotesize" )
 
@@
 ## Developing Short form of LEBA
-We sought the item response theory (IRT) to develop the short form of LEBA.
+We sought the Item Response Theory (IRT) to develop the short form of LEBA.
 IRT the conventional classical test theory-based analysis by gathering information on item quality by indices like item difficulty, item discrimination, and item information [@bakerBasicsItemResponse2017].
@@
 ```{r IRTparameters, results='asis'}
-apa_table(itemparameters, caption = "IRT Item parameters for the LEBA Scale", note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
+apa_table(itemparameters, caption = "Items discrimination and tesponse category thresholds of  LEBA with 23 items (n =690)", note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
 ```
@@
 F5_se.redu <- coef(F5_fit.redu, printSE = TRUE)
+
+items.quality.2 <- rbind(F1_items.redu,F2_items.redu,F3_items.redu,F4_items.redu,F5_items.redu )
+
+itemfit2 <- itemfit[,-1]
+
+IRT.details <- as.data.frame(cbind(items.quality.2 ,itemfit2))
+IRT.details <- tibble::rownames_to_column(IRT.details, "Items")
 
@@
 ```{r itemfittab, results='asis',warning=F, message=F}
-apa_table(itemfit, caption ="Item fit statistics for the fitted models")
+apa_table(IRT.details , caption ="Item discrimination, response category difficulty thrsholds and fit statistics of the short LEBA with 18 items (n=690)",note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
 ```
@@
 
-We developed a self-reported tool to capture different light exposure related behavior and evaluated its psychometric properties using classical test theory and item response theory based analysis.
+We developed a self-reported tool to capture different light exposure related behavior and evaluated its psychometric properties using classical test theory and Item Response Theory based analysis.
 
 48 items were generated by an expert panel and  administered to a large sample (n = `r nrow(EFA.descriptives)` to explore the latent structure.
-Exploratory factor analysis revealed a five factor solution with 25 items.
+Exploratory Factor Analysis revealed a five factor solution with 25 items.
 ("Wearing blue light filters", "Spending time outdoors", "Using phone and smart-watch in bed", "Using light before bedtime",  and "Using light in the morning and during daytime").
@@
 ## Conclusion
-"The Light exposure behavior assessment"(LEBA) gave a five solution with 25 items in an exploratory factor analysis.
-A confirmatory factor analysis with this 25-item scale again offered a five-factor solution, but this time two more item was discarded.
+"The Light exposure behavior assessment"(LEBA) gave a five solution with 25 items in an EFA.
+A CFA with this 25-item scale again offered a five-factor solution, but this time two more item was discarded.
 The 23-item "LEBA" was found reliable and valid.

### 2022-01-10 s1.Rmd
Decluttred appendix All external string based tables are converted into csv

---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.

  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.

  One sentence clearly stating the **general problem** being addressed by  this particular study.

  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.

  One or two sentences to put the results into a more **general context**.

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.

  <!-- https://tinyurl.com/ybremelq -->

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : 
  papaja::apa6_pdf:
    keep_tex: true
    latex_engine: xelatex

appendix:
  - "appendix-1.Rmd"
mainfont: Arial
---
```{r library, include=FALSE}

library(papaja) # devtools::install_github("crsh/papaja")
library(lavaan)
library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
library(semTools)
library(MOTE)
library(car)#reversecoding 
library(psych)
library(dlookr)
library(plyr)
library(tidyverse)
library(qgraph)
library(kableExtra)
library(paran) # Parallel analysis
library(EFA.MRFA) # Hull method
library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
library(DiagrammeRsvg) #For DiagrammeR
library(rsvg) #For DiagrammeR
library(ggcorrplot)
library(semTable)
library(magick)
library(mirt)
library(gtsummary)
library(gt)
library(gtExtras)
library(likert)
library(VIM) #Missing data
library(kutils)
library(simsem)
library(tabledown)
library(readxl)
library(koRpus)# stable release
library(koRpus.lang.en)
r_refs("references.bib")
```

```{r setup, include = FALSE}
library("papaja")
r_refs("references.bib")
```

(ref:foo) Factor Identification Methods (A) Parallel analysis drew 500 sets of random data set (n=428 each) and adjusted the mean eigenvalues for sample bias. In x-axis we plotted the number of possible factors and in y-axis we plotted the mean adjusted eigenvalues. The First inflection point of the plot indicated the optimal number of factors were six. (B) In the scree plot possible number of factors are plotted against obtained eigenvalues. Scree plot suggested six factors. (C) Hull method we plotted the number of possible factors in the x-axis and the CAF index(CAF: Common Part Accounted for-an indicator of model fit) in the y-axis. Hull method indicated 5 factors were required to balance the model fit and number of parameters.

```{r foo, fig.cap='(ref:foo)',  warning=FALSE, results= 'asis',fig.align='center'}

knitr::include_graphics('Manuscript.figures/factors.png', dpi =800)

```

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup

### 2022-01-10 manuscript.Rmd
Table 3 now has item stems

@@
 
-#creating normality function
-shapiro_test_df <- function(df, bonf= TRUE, alpha= 0.05) {
-  l <- lapply(df, shapiro.test)
-  s <- do.call("c", lapply(l, "[[", 1))
-  p <- do.call("c", lapply(l, "[[", 2))
-  if (bonf == TRUE) {
-    sig <- ifelse(p > alpha / length(l), "H0", "*")
-  } else {
-    sig <- ifelse(p > alpha, "H0", "*")
-  }
-  return(list(statistic= s,
-              p.value= p,
-              significance= sig,
-              method= ifelse(bonf == TRUE, "Shapiro-Wilks test with Bonferroni Correction",
-                             "Shapiro-Wilks test without Bonferroni Correction")))
-}
-
-Shapiro.efa <- shapiro_test_df(EFA.data)
-
-efa.normality.tab = matrix(nrow = 48, ncol = 2)
-rownameprefix <- "Item"
-rownamesufix <- seq(1:48)
-my.item.names <- paste(rownameprefix,rownamesufix, sep = "" )
-rownames(efa.normality.tab) <- my.item.names
-colnames(efa.normality.tab) <- c("statistic", "p")
-
-efa.normality.tab[,1] <- apa(Shapiro.efa$statistic,2,T)
-efa.normality.tab[,2] <- apa(Shapiro.efa$p.value,2,T)
-
-efa.normalityprefix <- efa.normality.tab[,1]
-efa.normalitysufix <- Shapiro.efa$significance
-efa.normality.stat <- paste(efa.normalityprefix,efa.normalitysufix, sep = "" )
-
+descriptives <- tabledown::des.tab(EFA.data)
+
+colnames(descriptives) <- c("Items", "Mean", "SD", "Skew", "Kurtosis", "SW Statistics", "Item-total corelation")
+
+vars_labels = as.data.frame(sapply(EFA.data,
+       function(x){attr(x,"label")}))
+
+vars_labels<- tibble::rownames_to_column(vars_labels, "Items")
+colnames(vars_labels) <- c("Item", "Stem")
+
+descriptives2 <- cbind(vars_labels, descriptives[,-1])
 # Multivariate Normality
@@
 
-# Descriptive Stats
-Descriptives <- psych::describe(EFA.data)
-alpha <- psych::alpha(EFA.data,check.keys=TRUE)
-Item.total <- alpha$item.stats
-
-Des.combined <- cbind(apa(Descriptives$mean,2,T), apa(Descriptives$sd,2,T), apa(Descriptives$skew,2,T),apa(Descriptives$kurtosis,2,T), efa.normality.stat,  apa(Item.total$r.cor,2,T))
-
-colnames(Des.combined) = c("Mean", "SD", "Skew", "Kurtosis", "Shapiro-Wilk Statistics","Item-Total Correlation")
-rownameprefix <- "Item"
-rownamesufix <- seq(01:48)
-my.names <- paste(rownameprefix,rownamesufix, sep = "" )
-rownames(Des.combined) = (my.names)
-rownames(Des.combined)[rownames(Des.combined) == "Item1"] <- "Item01"
-rownames(Des.combined)[rownames(Des.combined) == "Item2"] <- "Item02"
-rownames(Des.combined)[rownames(Des.combined) == "Item3"] <- "Item03"
-rownames(Des.combined)[rownames(Des.combined) == "Item4"] <- "Item04"
-rownames(Des.combined)[rownames(Des.combined) == "Item5"] <- "Item05"
-rownames(Des.combined)[rownames(Des.combined) == "Item6"] <- "Item06"
-rownames(Des.combined)[rownames(Des.combined) == "Item7"] <- "Item07"
-rownames(Des.combined)[rownames(Des.combined) == "Item8"] <- "Item08"
-rownames(Des.combined)[rownames(Des.combined) == "Item9"] <- "Item09"
 ```
@@
 ```{r tabDes,results='asis'}
-apa_table(Des.combined, caption = "Descriptive Statistics", align = "c", note = "*p<.001", longtable =T)
+descriptives2 %>% 
+apa_table(landscape =T,caption ="Descriptive Statistics", escape =F, font_size = "footnotesize", note = "*p<.001", align = c("p{1cm}","p{10cm}", rep("p{1cm}", ncol(descriptives2)))) 
 ```

### 2022-01-10 manuscript.Rmd
All Demographics tables are no readable

@@
     latex_engine: xelatex
+    includes:
+      in_header: header.tex
 appendix:
@@
 ```{r demographics, warning=F, message=F}
-desc_kable %>% 
-  kable_styling(latex_options = c("scale_down")) 
+desc_kable  %>% kable_styling(latex_options = c("scale_down")) %>% landscape()
+
 ```

### 2022-01-10 manuscript.Rmd
Table 1 legends updates

@@
 relevant.scale.data %>% 
-apa_table(landscape =T,caption ="Releated Scales", format = "latex",escape = T, font_size = "footnotesize", align = c("p{3cm}", rep("p{3.6cm}", ncol(relevant.scale.data)))) 
+apa_table(landscape =T,caption ="List of instruments measuring related consttucts to LEBA", format = "latex",escape = T, font_size = "footnotesize", align = c("p{3cm}", rep("p{3.6cm}", ncol(relevant.scale.data))))
+
 ```
@@
     title = md("**LEBA**"),
-    subtitle = md("Summary Descriptives EFA Sample (N =428)")
+    subtitle = md("Summary Descriptives EFA Sample (n =428)")
   ) %>% 
@@
     palette = "ggthemes::fivethirtyeight") %>% 
-  gtsave("Manuscript.figures/efagt.png",vwidth = 7000)
+  tab_row_group(
+      label = md("**F5:Using light in the morning and during daytime**"),
+      rows = c(1,3,12,13,24,25) 
+        ) %>% 
+  tab_row_group(
+      label = md("**F4:Using light before bedtime**"),
+      rows = c(16,17,18,20,21) 
+        ) %>% 
+  tab_row_group(
+      label = md("**F3:Using phone and smart-watch in bed**"),
+      rows = c(2,14,15,22,23) 
+        ) %>% 
+  tab_row_group(
+      label = md("**F2:Spending time outdoors**"),
+      rows = c(4,5,6,7,8,9) 
+        ) %>% 
+  tab_row_group(
+      label = md("**F1:Wearing blue light filters**"),
+      rows = c(10,11,19) 
+        ) %>% gtsave("Manuscript.figures/efagt.png",vwidth = 7000)
 
@@
     title = md("**LEBA**"),
-    subtitle = md("Summary Descriptives CFA Sample (N =262)")
+    subtitle = md("Summary Descriptives CFA Sample (Nn=262)")
   ) %>% 
@@
     palette = "ggthemes::fivethirtyeight") %>% 
+  tab_row_group(
+      label = md("**F5:Using light in the morning and during daytime**"),
+      rows = c(1,3,12,13,22,23) 
+        ) %>% 
+  tab_row_group(
+      label = md("**F4:Using light before bedtime**"),
+      rows = c(15,16,17,19) 
+        ) %>% 
+  tab_row_group(
+      label = md("**F3:Using phone and smart-watch in bed**"),
+      rows = c(2,13,14,20,21) 
+        ) %>% 
+  tab_row_group(
+      label = md("**F2:Spending time outdoors**"),
+      rows = c(4,5,6,7,8,9) 
+        ) %>% 
+  tab_row_group(
+      label = md("**F1:Wearing blue light filters**"),
+      rows = c(10,11,18) 
+        ) %>% 
   gtsave("Manuscript.figures/cfagt.png",vwidth = 7000)
@@
 ```{r figcfa, fig.cap = "Five Factor  Model of LEBA obtained by Confirmatory Factor Analysis.
-By allowing item pain 41 and 30 to covary their error variance our model attained the best fit.", out.height="150%", out.width="100%", dpi=600,  warning=FALSE}
+By allowing item pair 41 and 30 to covary their error variance our model attained the best fit.", out.height="150%", out.width="100%", dpi=600,  warning=FALSE}
 
@@
 ```{r InvarianceTab, results='asis'}
-apa_table(Invariance.table, align = "c",  caption = "Measurment Invariance analysis on CFA sampe (n=262) across native and non-native English speakers.", note = " a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual;* =  df of model comparison", landscape = T, font_size = "footnotesize" )
+apa_table(Invariance.table, align = "c",  caption = "Measurment Invariance analysis on CFA sample (n=262) across native and non-native English speakers.", note = " a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual;* =  df of model comparison", landscape = T, font_size = "footnotesize" )
 
@@
 ```{r IRTparameters, results='asis'}
-apa_table(itemparameters, caption = "Items discrimination and tesponse category thresholds of  LEBA with 23 items (n =690)", note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
+apa_table(itemparameters, caption = "Items discrimination and response category difficulty thresholds of 23 items in  LEBA (n =690)", note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
 ```
@@
   geom_line()+apatheme+
-  labs(y="Test Information", title = "F3 Test Inforfamtion")+ylim(0,6)
+  labs(y="Test Information", title = "F3 Test Inforfamtion")+ylim(0,8)
 
@@
   geom_line()+apatheme+
-  labs(y="Test Information", title = "F5 Test Inforfamtion") +ylim(0,6)
+  labs(y="Test Information", title = "F5 Test Inforfamtion") +ylim(0,8)
 
@@
 ```{r itemfittab, results='asis',warning=F, message=F}
-apa_table(IRT.details , caption ="Item discrimination, response category difficulty thrsholds and fit statistics of the short LEBA with 18 items (n=690)",note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
+apa_table(IRT.details , caption ="Item discrimination, response category difficulty thrsholds and fit statistics of the 18 items in short LEBA (n=690)",note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
 ```

### 2022-01-10 manuscript.Rmd
ggplot2 common colout theme based on npg

@@
 #install.packages("pacman")#Run this if you don't have pacman installed.
-pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap,huxtable,tikzDevice)
+pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap,huxtable,reshape, ggsci)
 pacman::p_install_gh("jthomasmock/gtExtras")
@@
 library(koRpus.lang.en)
+library(reshape)
+library(ggsci)
 r_refs("references.bib")
@@
 corplot <- ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
-           ggtheme = ggplot2::theme_minimal(),,tl.srt = 90,colors = c("red", "white", "blue") )+
+           ggtheme = ggplot2::theme_minimal(),tl.srt = 90,colors = c("#E64B35FF", "white", "#3C5488FF") )+
   theme( panel.grid.major = element_blank(),
@@
   #Add lines connecting data points
-  geom_line(colour ='black')+
+  geom_line(colour ='#DC000099')+
     #geom_line(data = Random.EV) +
@@
     #Add the data points.
-  geom_point(size=2,colour ='black')+
+  geom_point(size=1.5,colour ='#3C5488FF')+
   #geom_point(data = Random.EV, size=3)+
@@
 scree.plot <-ggplot(FA.Scree, aes(x=num, y=eigenvalue,color=type, shape=type))+
-   geom_line(colour ='black')+
+   geom_line(colour ='#DC000099')+
   #geom_line(data = PA.Scree)+ 
-  geom_point(size=2,colour ='black')+
+  geom_point(size=1.5,colour ='#3C5488FF')+
   #geom_point(data = PA.Scree, size=3)+
@@
 hull <- ggplot2::last_plot()
-Hull <- hull+ ggtitle(NULL)+xlab("Factor Number (Hull Method)")+ylab("CAF")+ aes(color = "black")+
-  apatheme +scale_color_manual(labels = c("Out side the convex Hull", "On the convex Hull"), values = c("black", "black"))+theme(legend.position = "None")
+Hull <- hull+ ggtitle(NULL)+xlab("Factor Number (Hull Method)")+ylab("CAF")+ aes(color = '#DC000099')+geom_point(color ='#3C5488FF',size =1)+
+  apatheme +theme(legend.position = "None") +scale_fill_identity()
 
@@
 
-residual.plot <- ggplot(residual.data, aes(x=Residuals)) + geom_histogram(binwidth=.04, col=I("black"),fill=I("grey")) + xlim(-.2,.2)+ ylim(0,250)+apatheme +geom_vline(xintercept = .05)+theme(axis.text.x = element_text(size = 12),
-        axis.text.y = element_text(size = 12))
+residual.plot <- ggplot(residual.data, aes(x=Residuals)) + geom_histogram(binwidth=.04, col=I("black"),fill="#00A08799") + xlim(-.2,.2)+ ylim(0,250)+apatheme +geom_vline(xintercept = .05)+theme(axis.text.x = element_text(size = 12),
+        axis.text.y = element_text(size = 12))+
   labs( y="Frequency")
@@
     line_color = "black", 
-    fill_color = "grey",
+    fill_color = "#00A08799",
     bw = 1,
@@
     line_color = "black", 
-    fill_color = "grey",
+    fill_color = "#E64B3599",
     bw = 0.75,
@@
 
-```{r figcfa, fig.cap = "Five Factor  Model of LEBA obtained by Confirmatory Factor Analysis.
-By allowing item pair 41 and 30 to covary their error variance our model attained the best fit.", out.height="150%", out.width="100%", dpi=600,  warning=FALSE}
-
-#library(semPlot)
-
+```{r cfaplot, include =F}
+png(filename="Manuscript.figures/CFAplot.png", 
+    type="cairo",
+    units="in", 
+    width=12, 
+    height=12, 
+    pointsize=12, 
+    res=1200)
 semPaths (fit.Cor.2 , 
@@
           intercepts = F,
-          style ="lisrel",
+          style ="OpenMx",
           #residScale = 6,
@@
           curvePivot =T,
-          sizeMan =6,#items length
+          sizeMan =8,#items length
           sizeMan2 = 2,#items
@@
           edge.label.cex = .8,
-          exoCov = T,
+          #exoCov = T,
           centerLevels = T,
@@
           label.scale=T,
-          label.cex=1, #Font of factor and item name
+          label.cex=1.2, #Font of factor and item name
           residuals=FALSE,
-           exoVar=FALSE,
-          fixedStyle=6, #Style of arrow (guide item)
-          freeStyle=1#Style of arrow (other item), #XKCD = TRUE
+           #exoVar=FALSE,
+          #fixedStyle=6, #Style of arrow (guide item)
+          #freeStyle=1#Style of arrow (other item), #XKCD = TRUE
 
           )
+
+dev.off()
+```
+
+```{r figcfa, fig.cap = "Five Factor  Model of LEBA obtained by Confirmatory Factor Analysis.
+By allowing item pair 41 and 30 to covary their error variance our model attained the best fit.",  out.height='100%', warning=FALSE}
+
+knitr::include_graphics("Manuscript.figures/CFAplot.png", dpi =600)
 
@@
 
+library(ggsci)
 F1.iic2 <- ggplot(F1.item.info.data.2,aes(Theta,value,col=variable))+geom_line()+apatheme+
   ggtitle("F1 Item Information Plot")+theme(legend.position = "none")+
-  labs(y = "Item Information")+facet_wrap(~variable)+theme(strip.text.x = element_text(size = 15))+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")+scale_y_continuous(breaks=c(5,50,100,200), limits = c(0, 200))
+  labs(y = "Item Information")+facet_wrap(~variable)+theme(strip.text.x = element_text(size = 15))+geom_hline(yintercept = .20, colour ="red")+scale_y_continuous(breaks=c(5,50,100,200), limits = c(0, 200))+geom_area()+ scale_color_npg()+aes(fill = as.factor(variable))
 
@@
 
+Test.data <- as.data.frame(cbind(F1.T1,F2.T1, F3.T1, F4.T1, F5.T1))
+
+Test.data.long <- melt(Test.data)
+Test.data.2 <- data.frame(Theta=seq(-6,6, by =.1),Test.data.long)
+
+TIC <- ggplot(Test.data.2,aes(Theta,value))+geom_line(size = 1)+apatheme+
+  ggtitle("Test Information Plot")+theme(legend.position = "none")+
+  labs(y = "Test Information")+ geom_path()+facet_wrap(~variable,scales = "free") +theme(strip.text.x = element_text(size = 15))+geom_area()+ scale_color_npg()+aes(fill = as.factor(variable))
+
 F1.tic <- ggplot(F1.test.data, aes(x=Theta, y=F1.T1)) +
   geom_line()+apatheme+
-  labs(y="Test Information", title = "F1 Test Inforfamtion")+scale_color_brewer(palette="Dark2")
+  labs(y="Test Information", title = "F1: Wearing blue light filters")+geom_area()+theme(legend.position = "none")+
+  aes(fill =  "#E64B3599")+
+     scale_fill_identity()
 
@@
   geom_line()+apatheme+
-  labs(y="Test Information", title = "F2 Test Inforfamtion")+ylim(0,8)
+  labs(y="Test Information", title = "F2: Spending time outdoors")+ylim(0,8)+
+  geom_area()+aes(fill =  "#4DBBD599")+theme(legend.position = "none")+
+     scale_fill_identity()
 
@@
   geom_line()+apatheme+
-  labs(y="Test Information", title = "F3 Test Inforfamtion")+ylim(0,8)
+  labs(y="Test Information", title = "F3: Using phone and smart-watch in bed")+ylim(0,8)+
+  geom_area()+aes(fill =  "#00A08799")+theme(legend.position = "none")+
+     scale_fill_identity()
 
@@
   geom_line()+apatheme+
-  labs(y="Test Information", title = "F4 Test Inforfamtion")
+  labs(y="Test Information", title = "F4: Using light before bedtime")+
+  geom_area()+aes(fill =  "#3C548899")+theme(legend.position = "none")+
+     scale_fill_identity()
 
@@
   geom_line()+apatheme+
-  labs(y="Test Information", title = "F5 Test Inforfamtion") +ylim(0,8)
+  labs(y="Test Information", title = "F5:Using light in the morning and during daytime") +ylim(0,8)+geom_area()+aes(fill =  "#B09C8599")+theme(legend.position = "none")+
+scale_fill_identity()
 
@@
 
-TIC <- cowplot::plot_grid(F1.tic,F2.tic, F3.tic,
+TIC.plot <- cowplot::plot_grid(F1.tic,F2.tic, F3.tic,
                                    F4.tic,F5.tic,
@@
                      label_fontface = "plain")
-ggsave("Manuscript.figures/TIC.png",TIC, width = 10, height = 12, dpi = 600, bg = "white")
+ggsave("Manuscript.figures/TIC.png",TIC.plot, width = 10, height = 12, dpi = 600, bg = "white")
 

### 2022-01-13 manuscript.Rmd
EFA Plot updated

@@
 #install.packages("pacman")#Run this if you don't have pacman installed.
-pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap,huxtable,reshape, ggsci)
+pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap,huxtable,reshape, ggsci,networkD3, webshot)
+webshot::install_phantomjs()
 pacman::p_install_gh("jthomasmock/gtExtras")
@@
         panel.background = element_blank())
-        #text=element_text(family = "Helvetica"))
-
-EFAplot.1 <- plot_grid(
- p1, residual.plot,
-  labels = "AUTO",
+
+EFAplot.1 <- cowplot::plot_grid(
+  NULL, residual.plot,
+  labels = c("", "B"),
   align="h",
@@
   label_fontface = "plain",
+  label_y = .99
+)
+
+EFAplot.2 <- cowplot::plot_grid(
+  p1, EFAplot.1,
+  labels = c("A",""),
+  align="h",
+  ncol = 2,
+  label_size = 15,
+  label_fontfamily = "Arial",
+  label_fontface = "plain",
   label_y = .99,
-  label_x = .02,
- rel_heights = c(1.5,1)
+  label_x = .02
 )
 
-ggsave("Manuscript.figures/EFAfull.png",EFAplot.1, width = 4, height =8, dpi = 600, bg ="white")
+ggsave("Manuscript.figures/EFAfull.png",EFAplot.2, width = 6, height =7, dpi = 1200, bg ="white")
 

### 2022-01-14 manuscript.Rmd
Methods text adjustments, Participants section transfered into Results section

@@
 # Methods
-## Ethical approval
-
-The cantonal ethics commission (Ethikkommission Nordwest- und Zentralschweiz, project ID Req-2021-00488) reviewed this project and issued an official clarification of responsibility (full document see Suppl.
-Fig X in appendix) stating: "The research project does not fall under the scope of the Human Research Act, because your project is using only anonymised data.
-An authorisation from the ethics committee is therefore not required and the EKNZ is not responsible for its review."
-
-## Data Availability
-
-All code and data underlying this article is available on a public GitHub repository (https://github.com/leba-instrument/leba-manuscript).
+
+## Item Generation
+
+To ensure construct adequacy we thoroughly assessed the current status of literature and identified a variety of light exposure related scales.
+However, no scales specifically measuring the behavioural component of light exposure were found (see Table \@ref(tab:eltab)).
+Consequentially we pursued to introduce a new openly available scale to address this research gap.
+For this purpose, an expert researcher panel from the fields of chronobiology, light research, neuroscience, and psychology – comprising all authors of the present manuscript – generated and collected preliminary item ideas.
+Special attention was paid to design items circumscribed to assess light exposure *behaviour* as opposed to subjective measurements of the light environment [@eklund1996development; @dianat2013objective]) and semi-quantitative assessments of light sources' illuminance [@bajaj2011validation] in order to maintain content validity.
+In a collective effort the generated items were then peer-reviewed, amended, unified, and complemented with a suitable response scale (5-point Likert-scale ranging from 1 "Never/Does not apply/I don’t know" to 5 "Always").
+This process was finalized when all experts were in agreement, resulting in 48 items to implement in the data collection.
 
@@
 Data was collected in a quantitative cross-sectional approach via a fully anonymous online survey hosted on REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
-Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) of a Comic co-released with the survey[@Weinzaepflen.2021] , social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux software [@f.lux].
-
+Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) of a Comic co-released with the survey[@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux].
 Completing the online survey took approx.
@@
 What is 4+5?").
-The data analysed in this study was collected between 17.05.2021 and 03.09.2021.
+The data analysed in this study was collected between 17 May 2021 and 3 September 2021.
 Questions incorporating retrospective recall were all aligned to the period of "past four weeks", matching the presented LEBA instrument.
 
-In addition to the LEBA questionnaire, which is subject of the current study, the following variables and items were assessed but not included in the analysis:
-
--   Sleep disturbance and sleep-related impairment (adult and pediatric versions) [@Bevans.2019; @Buysse.2010; @Forrest.2018; @Harb.2015; @Yu.2011]
--   Sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration (version for adults and adolescents) [@roenneberg2003life]
--   Sleep environment [@Olivier.2016]
--   Meal timing & caffeine consumption [custom items]
--   Light sensitivity (photophobia vs. photophilia) [@Wu.2017]
--   Self-reported pubertal stage (only if younger than 18 years old) [@Petersen.1988]
-
-Furthermore, the following 1-item demographic variables were assessed:
-
--   Age
--   Sex
--   Gender identity
--   Occupational Status
--   COVID-19 related Occupational setting during the past four weeks
--   Time zone & country of residence
--   English as native language
-
-## Participants
+In addition to the LEBA questionnaire, which is subject of the current study, we assessed other variables and items which were not included in the present analysis.
+This comprised various sleep-related measures, i.e., sleep disturbances and sleep-related impairment (adult and pediatric versions) [@Bevans.2019; @Buysse.2010; @Forrest.2018; @Harb.2015; @Yu.2011], sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration [MCTQ version for adults and adolescents @roenneberg2003life] plus sleep environment [@Olivier.2016].
+Furthermore, we included a light sensitivity questionnaire (photophobia vs.
+photophilia) [@Wu.2017] and self-reported pubertal stage assessment [@Petersen.1988] for participants younger than 18 years of age.
+Moreover, we incorporated custom items on meal timing and caffeine consumption in the “workday vs.
+free day” structure of the MCTQ sleep-wake regulation.
+Example items are: “On workdays I usually have my first meal at __:__”, “On free days I usually have my last meal at __:__”, and “On workdays I usually drink my first caffeinated drink at __:__”.
+
+Finally, we assessed age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language as single-item demographic variables.
+The demographic characteristics of our sample are given in Table \@ref(tab:demographics).
 
@@
 
+```{r Manuflowchart, include=FALSE }
+Flowchart1 <- grViz("digraph my_flowchart{
+
+                    graph [fontname = Helvetica,layout = dot,fontsize = 45,layout = dot ]
+
+                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 16, height = 2, 
+                    fixedsize = true,fontsize = 45]
+
+                    A[label = '48 items were generated'] 
+                    B[label = 'Exploratory Factor Analysis on 48 Items (n = 428)']
+
+                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 16, height = 6, 
+                    fixedsize = true, fontsize = 45]
+                    C[label = 
+                    <Factor Identification<br/>Scree Plot: 6 Factors<br/>Parallel Analysis: 6 Factors<br/>Minimum Average Partial Method: 5 Factors<br/>Hull Method: 5 Factors>
+                    ]
+
+                     subgraph cluster_1 {
+                      graph[fontname = Helvetica, shape = box, style =dashed]
+
+                     node[fontname = Helvetica, margin = 0.2,width = 22, height = 2.5, 
+                    fixedsize = true, fontsize = 45,style =dashed]
+
+                     1[label = '5 Factor Solution Retained 25 Items']
+                     2[label = <Reliability Analysis on EFA Sample (n=428)<br/>Ordinal alpha F1 =.94; F2 = .76; F3 = .75; F4 =.72; F5 =.62.>]
+
+                     3[label = <Confirmatory Factor Analysis<br/>on the Five Factor Model (25 Items; n=262)<br/>Acceptable Fit ( CFI = .94; TLI .93; RMSEA = .06, SRMR = .11)>]
+
+                    4[label = <Confirmatory Factor Analysis<br/>on the Five Factor Model (23 Items; n=262)<br/>Acceptable Fit ( CFI = .97; TLI= .96; RMSEA = .04, SRMR = .09)>]
+                     5[label = <Reliability Analysis (23 Items; n=262)<br/>Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52<br/>Mcdonald  omega(total) for the total scale = .73>]
+                    8[label = <Measurement Invariance Analysis<br/>Residual measurement invariance achieved>]
+                    9[label = 'Semantic Analysis']
+                    10[label = <LEBA Short Form (18 Items; n=690)<br/>Based on Item Response Theory>]
+                    }
+                subgraph cluster_2 {
+                      graph[fontname = Helvetica,shape = rectangle]
+                      style = rounded
+                     node[fontname = Helvetica, margin = 0.2,width = 18, height = 2.5, 
+                fixedsize = true, fontsize = 45 ]
+                    6[label = 
+                    <6-Factor solution:<br/>one factor emerged with only two salient loadings>
+                    ]
+                    7[label = 'Rejected']
+                    }
+
+                     edge[fontname = Helvetica,color = black,arrowhead = vee, arrowsize = 1.25]
+                     A ->B
+                     B ->C
+                     C ->1
+                     1 ->2
+                     2 ->3
+                     3 ->4
+                     4 ->5
+                    5->8
+                    8 ->9
+                    9 ->10
+                     C ->6
+                     6 ->7
+
+}")
+
+library(jpeg)
+export_svg(Flowchart1) %>%
+  charToRaw() %>%
+  rsvg() %>%
+  png::writePNG("Manuscript.figures/Flowchart1.jpeg", dpi = 600)
+
+```
+
+## Analytic Strategies
+
+Figure \@ref(fig:FlowchartFig) summarizes the steps of our psychometric analysis.
+In our analysis we used R (version 4.1.0), with several R packages.
+Initially, our tool had six point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always).
+Our purpose was to capture light exposure related behavior and these two response options: "Does not apply/I don't know" and "Never" were providing similar information.
+As such we decided to collapse them into one, making it a 5 point Likert type response format.
+Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
+Our data violated both the univariate and multivariate normality assumptions.
+Due to these violations and the ordinal nature of our response data, we used  polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA.
+We employed principal axis (PA) as  factor extraction method with varimax rotation.
+PA is robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020].
+The obtained latent structure was confirmed by another factor extraction method: "the minimum residuals extraction" as well.
+We used a combination of factor identification method including scree plot [@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method [@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
+Additionally, to determine the simple structure, we followed the guidelines recommended by psychometricians: (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018].
+We confirmed the latent structure obtained in the EFA by conducting a categorical "Confirmatory Factor Analysis" (CFA) using "robust weighted least square estimator" (WLSMV).
+We estiablished the measurement invariance of our tool across the native and non-native English speakers using structural equation model framework.
+To assess the possible semantic overlap of our tool with the existing tools, we sought to "Semantic Scale Network" [@rosenbusch2020semantic].To assess the possible semantic overlap of our tool with the existing tools, we sought to "Semantic Scale Network" [@rosenbusch2020semantic].
+Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA.
+We also conducted psychometric analysis on non-merged response options data (Supp. Table \@ref(tab:efaunmerged)) and rejected the latent structure obtained as the factors were less interpretable.
+
+```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='100%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/Flowchart1.jpeg', dpi = 800 )
+```
+
+## Ethical approval
+
+By reason of using fully anonymous online survey data, the present research project does not fall under the scope of the Human Research Act, making an authorisation from the ethics committee redundant.
+Nevertheless, the cantonal ethics commission (Ethikkommission Nordwest- und Zentralschweiz, EKNZ) reviewed our proposition (project ID Req-2021-00488) and issued an official clarification of responsibility (full document see Suppl.
+X in appendix).
+
+## Data Availability
+
+The present article is a fully reproducible open-access “R Markdown” document.
+All code and data underlying this article – along with two versions of the LEBA questionnaire (full and short) and online survey implementation templates on common survey platforms – will be available under open-access licence (CC-BY-NC-ND) on a public [GitHub repository](https://github.com/leba-instrument).
+
+# Results
+
+## Participants
+
 ```{r demographics, warning=F, message=F}
@@
 
-Table 2 summarizes the survey participants' demographic characteristics.
+Table \@ref(tab:demographics) summarizes the survey participants' demographic characteristics.
 Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses.
 XX participants were excluded from analysis due to not passing at least one of the "attention check" items.
-For exploring initial factor structure (EFA) , a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013].
+For exploring initial factor structure (EFA), a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013].
 For estimating the sample size for the confirmatory factor analysis (CFA) we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per parameter is required to earn trustworthiness of the result.
-Our sample size exceeds these requirements: Anonymous responses from a total of *n* = `r nrow(desctable.data)` participants were included in the analysis of the current study, split into samples for Exploratory Factor Analysis (EFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "1.
-EFA Sample",])`) and Confirmatory Factor Analysis (CFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "2.
+Our sample size exceeds these requirements: Anonymous responses from a total of *n* = `r nrow(desctable.data)` participants were included in the analysis of the current study, split into samples for exploratory (EFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "1.
+EFA Sample",])`) and confirmatory factor analysis (CFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "2.
 CFA Sample",])`).
-The EFA sample included participants filling out the questionnaire from 17.05.2021 to XX.XX.XXXX , whereas participants who filled out the questionnaire from YY.YY.YYYY to 03.09.2021 were included in the CFA analysis.
+The EFA sample included participants filling out the questionnaire from 17 May 2021 to XX XXX 2021, whereas participants who filled out the questionnaire from YY YYY 2021 to 3 September 2021 were included in the CFA analysis.
 Participants indicated filling out the online survey from a diverse range of geographic locations.
-The ten most common country + timezone combinations included:
+The ten most common country and time zone combinations included:
 
@@
 
-For a complete list of geographic locations, see Suppl. Table X in the appendix.
+For a complete list of geographic locations, see Suppl. Table \@ref(tab:tztabprint).
 
@@
 
-## Item Generation
-
-To ensure construct adequacy we thoroughly assessed the current status of literature and identified a variety of light exposure related scales.
-However, no scales specifically measuring the behavioral component of light exposure were found (Table \@ref(tab:eltab)).
-Consequentially we pursued to introduce a new openly available scale to address this research gap.
-For this purpose an expert researcher panel from the fields of chronobiology, light research, neuroscience and psychology (including seven of the authors, see authors roles) generated and collected preliminary item ideas.
-Special attention was paid to design items circumscribed to assess light exposure *behavior* as opposed to subjective measurements of the light environment (cf.[@eklund1996development] & [@dianat2013objective]) and semi-quantitive assesments of light sources' illuminance (cf.
-[@bajaj2011validation]) in order to maintain content validity.
-In a collective effort the generated items were then peer-reviewed,  amended, unified, and complemented with a suitable response scale (5 point Likert-scale ranging from 1 "Never/Does not apply/I don’t know" to 5 "Always").
-This process was finalized when all experts were in agreement, resulting in 48 items to implement in the data collection.
-
-```{r Manuflowchart, include=FALSE }
-Flowchart1 <- grViz("digraph my_flowchart{
-
-                    graph [fontname = Helvetica,layout = dot,fontsize = 45,layout = dot ]
-
-                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 16, height = 2, 
-                    fixedsize = true,fontsize = 45]
-
-                    A[label = '48 items were generated'] 
-                    B[label = 'Exploratory Factor Analysis on 48 Items (n = 428)']
-
-                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 16, height = 6, 
-                    fixedsize = true, fontsize = 45]
-                    C[label = 
-                    <Factor Identification<br/>Scree Plot: 6 Factors<br/>Parallel Analysis: 6 Factors<br/>Minimum Average Partial Method: 5 Factors<br/>Hull Method: 5 Factors>
-                    ]
-
-                     subgraph cluster_1 {
-                      graph[fontname = Helvetica, shape = box, style =dashed]
-
-                     node[fontname = Helvetica, margin = 0.2,width = 22, height = 2.5, 
-                    fixedsize = true, fontsize = 45,style =dashed]
-
-                     1[label = '5 Factor Solution Retained 25 Items']
-                     2[label = <Reliability Analysis on EFA Sample (n=428)<br/>Ordinal alpha F1 =.94; F2 = .76; F3 = .75; F4 =.72; F5 =.62.>]
-
-                     3[label = <Confirmatory Factor Analysis<br/>on the Five Factor Model (25 Items; n=262)<br/>Acceptable Fit ( CFI = .94; TLI .93; RMSEA = .06, SRMR = .11)>]
-
-                    4[label = <Confirmatory Factor Analysis<br/>on the Five Factor Model (23 Items; n=262)<br/>Acceptable Fit ( CFI = .97; TLI= .96; RMSEA = .04, SRMR = .09)>]
-                     5[label = <Reliability Analysis (23 Items; n=262)<br/>Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52<br/>Mcdonald  omega(total) for the total scale = .73>]
-                    8[label = <Measurement Invariance Analysis<br/>Residual measurement invariance achieved>]
-                    9[label = 'Semantic Analysis']
-                    10[label = <LEBA Short Form (18 Items; n=690)<br/>Based on Item Response Theory>]
-                    }
-                subgraph cluster_2 {
-                      graph[fontname = Helvetica,shape = rectangle]
-                      style = rounded
-                     node[fontname = Helvetica, margin = 0.2,width = 18, height = 2.5, 
-                fixedsize = true, fontsize = 45 ]
-                    6[label = 
-                    <6-Factor solution:<br/>one factor emerged with only two salient loadings>
-                    ]
-                    7[label = 'Rejected']
-                    }
-
-                     edge[fontname = Helvetica,color = black,arrowhead = vee, arrowsize = 1.25]
-                     A ->B
-                     B ->C
-                     C ->1
-                     1 ->2
-                     2 ->3
-                     3 ->4
-                     4 ->5
-                    5->8
-                    8 ->9
-                    9 ->10
-                     C ->6
-                     6 ->7
-
-}")
-
-library(jpeg)
-export_svg(Flowchart1) %>%
-  charToRaw() %>%
-  rsvg() %>%
-  png::writePNG("Manuscript.figures/Flowchart1.jpeg", dpi = 600)
-
-```
-
-## Analytic Strategies
-
-Figure \@ref(fig:FlowchartFig) summarizes the steps of our psychometric analysis.
-In our analysis we used R (version 4.1.0), with several R packages.
-Initially, our tool had six point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always).
-Our purpose was to capture light exposure related behavior and these two response options: "Does not apply/I don't know" and "Never" were providing similar information.
-As such we decided to collapse them into one, making it a 5 point Likert type response format.
-Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
-Our data violated both the univariate and multivariate normality assumptions.
-Due to these violations and the ordinal nature of our response data, we used  polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA.
-We employed principal axis (PA) as  factor extraction method with varimax rotation.
-PA is robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020].
-The obtained latent structure was confirmed by another factor extraction method: "the minimum residuals extraction" as well.
-We used a combination of factor identification method including scree plot [@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method [@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
-Additionally, to determine the simple structure, we followed the guidelines recommended by psychometricians: (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018].
-We confirmed the latent structure obtained in the EFA by conducting a categorical "Confirmatory Factor Analysis" (CFA) using "robust weighted least square estimator" (WLSMV).
-We estiablished the measurement invariance of our tool across the native and non-native English speakers using structural equation model framework.
-To assess the possible semantic overlap of our tool with the existing tools, we sought to "Semantic Scale Network" [@rosenbusch2020semantic].To assess the possible semantic overlap of our tool with the existing tools, we sought to "Semantic Scale Network" [@rosenbusch2020semantic].
-Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA.
-We also conducted psychometric analysis on non-merged response options data (Supp. Table \@ref(tab:efaunmerged)) and rejected the latent structure obtained as the factors were less interpretable.
-
-```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='100%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/Flowchart1.jpeg', dpi = 800 )
-```
-
-# Results
 ```{r ggplot2, include=F}

### 2022-01-15 manuscript.Rmd
ICC updated
Personfit Plot Updated

@@
 
-ICC2 <- cowplot::plot_grid(vic.iic2 , agg.iic2,  labels = "AUTO",ncol=2, label_size = 15,align = "v")
-ggsave("Figures/ICC2.jpeg",ICC2 , width = 12, height = 8, dpi = 600, bg = "white")
 ```
@@
 
-F1.person <- ggplot(F1.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5,col=I("black"),fill=I("grey"))+geom_vline(xintercept = -2)+
+F1.person <- ggplot(F1.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5,col=I("black"),fill="#00A08799")+geom_vline(xintercept = -2)+
   labs( y="Number of Participants", x = "Zh Statistics: F1")+apatheme+ ylim(0,600) + xlim(-4,2)
@@
 
-F2.person <- ggplot(F2.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill=I("grey"))+
+F2.person <- ggplot(F2.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill="#00A08799")+
   scale_x_continuous(limits = c(-5, 1))+geom_vline(xintercept = -2)+
@@
 
-F3.person <- ggplot(F3.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill=I("grey"))+geom_vline(xintercept = -2)+
+F3.person <- ggplot(F3.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill="#00A08799")+geom_vline(xintercept = -2)+
   labs( y="Number of Participants", x = "Zh Statistics: F3")+apatheme+ylim(0,600) + xlim(-4,2)
@@
 
-F4.person <- ggplot(F4.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill=I("grey"))+geom_vline(xintercept = -2)+
+F4.person <- ggplot(F4.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill="#00A08799")+geom_vline(xintercept = -2)+
   labs( y="Number of Participants", x = "Zh Statistics: F4")+apatheme+ylim(0,600) + xlim(-4,2)
@@
 
-F5.person <- ggplot(F5.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill=I("grey"))+geom_vline(xintercept = -2)+
+F5.person <- ggplot(F5.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill="#00A08799")+geom_vline(xintercept = -2)+
   labs( y="Number of Participants", x = "Zh Statistics:F5")+apatheme+ylim(0,600) + xlim(-4,2)
@@
 ```{r perfit, include=F}
-personfit <- plot_grid(F1.person, F2.person,F3.person,F4.person,F5.person, 
+personfit <- cowplot::plot_grid(F1.person, F2.person,F3.person,F4.person,F5.person, 
           labels = "AUTO", label_size = 12,align = "v", ncol =2,

### 2022-01-15 manuscript.Rmd
Item Information curve updated in common theme.

@@
 
-library(ggsci)
+pacman::p_load(ggsci)
+
 F1.iic2 <- ggplot(F1.item.info.data.2,aes(Theta,value,col=variable))+geom_line()+apatheme+
   ggtitle("F1 Item Information Plot")+theme(legend.position = "none")+
-  labs(y = "Item Information")+facet_wrap(~variable)+theme(strip.text.x = element_text(size = 15))+geom_hline(yintercept = .20, colour ="red")+scale_y_continuous(breaks=c(5,50,100,200), limits = c(0, 200))+geom_area()+ scale_color_npg()+aes(fill = as.factor(variable))
+  facet_wrap(~variable,scales = "free")+theme(strip.text.x = element_text(size = 15))+geom_hline(yintercept = .20, colour ="red")+geom_area()+ scale_color_npg()+aes(fill = as.factor(variable))+xlab(expression(theta)) +
+  ylab(expression(I(theta)))
+
+ggsave("Manuscript.figures/F1.itemplots.png",F1.iic2, width = 12, height =8, dpi = 1200, bg ="white")
 
@@
   ggtitle("F2 Item Information Plot")+theme(legend.position = "none")+
-  labs(y = "Item Information")+facet_wrap(~variable)+theme(strip.text.x = element_text(size = 15))+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")
+  facet_wrap(~variable,scales = "free")+theme(strip.text.x = element_text(size = 15))+
+  geom_hline(yintercept = .20, colour ="red")+geom_area()+scale_color_npg()+aes(fill = as.factor(variable))+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))
+
+ggsave("Manuscript.figures/F2.itemplots.png",F2.iic2, width = 12, height =8, dpi = 1200, bg ="white")
 
@@
   ggtitle("F3 Item Information Plot")+theme(legend.position = "none")+
-  labs(y = "Item Information")+facet_wrap(~variable)+theme(strip.text.x = element_text(size = 15))+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")
+  facet_wrap(~variable,scales = "free")+theme(strip.text.x = element_text(size = 15))+
+  geom_hline(yintercept = .20, colour ="red")+geom_area()+scale_color_npg()+aes(fill = as.factor(variable))+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))
+
+ggsave("Manuscript.figures/F3.itemplots.png",F3.iic2, width = 12, height =8, dpi = 1200, bg ="white")
 
@@
   ggtitle("F4 Item Information Plot")+theme(legend.position = "none")+
-  labs(y = "Item Information")+facet_wrap(~variable)+theme(strip.text.x = element_text(size = 15))+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")
+  facet_wrap(~variable,scales = "free")+theme(strip.text.x = element_text(size = 15))+
+  geom_hline(yintercept = .20, colour ="red")+geom_area()+scale_color_npg()+aes(fill = as.factor(variable))+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))
+
+ggsave("Manuscript.figures/F4.itemplots.png",F4.iic2, width = 12, height =8, dpi = 1200, bg ="white")
 
@@
   ggtitle("F5 Item Information Plot")+theme(legend.position = "none")+
-  labs(y = "Item Information")+facet_wrap(~variable)+theme(strip.text.x = element_text(size = 15))+
-  scale_color_npg()+geom_hline(yintercept = .20, colour ="red")
+  facet_wrap(~variable,scales = "free")+theme(strip.text.x = element_text(size = 15))+
+  geom_hline(yintercept = .20, colour ="red")+geom_area()+scale_color_npg()+aes(fill = as.factor(variable))+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))
+
+ggsave("Manuscript.figures/F5.itemplots.png",F5.iic2, width = 12, height =8, dpi = 1200, bg ="white")
 

### 2022-01-15 appendix-1.Rmd
All Demographics tables are no readable
Item info plot stiched in one plot with cowplot and ggplot2

@@
 ```{r midesp, warning=F, message=F, results='asis'}
-mides_kable %>% 
-  kable_styling(latex_options = c("scale_down")) 
+mides_kable %>% kable_styling(latex_options = c("scale_down")) %>% 
+  landscape()
 ```
@@
 
-```{r F1IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1. Item 16 carried highest information among the three items', out.height='160%', out.width='100%'}
+```{r IF, echo=FALSE, fig.align='center', fig.cap='Item information curve ', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/allitemplots.png', dpi = 300)
+```
+
+```{r F1IF, eval=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1. Item 16 carried highest information among the three items', include=FALSE, out.height='160%', out.width='100%'}
 knitr::include_graphics('Manuscript.figures/F1.itemplots.png', dpi = 600)
@@
 
-```{r F2IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F2.
+```{r F2IF, eval=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F2.
 All items cariied information across the latent trait continuum.
-Item 09 carried the lowest information however its information peak was highr than .20.', out.height='160%', out.width='100%'}
+Item 09 carried the lowest information however its information peak was highr than .20.', include=FALSE, out.height='160%', out.width='100%'}
 knitr::include_graphics('Manuscript.figures/F2.itemplots.png',dpi = 600)
@@
 
-```{r F3IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F3.
-Item 30 and 41 had relatively flat information curve with a peak lower than .20', out.height='160%', out.width='100%'}
+```{r F3IF, eval=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F3.
+Item 30 and 41 had relatively flat information curve with a peak lower than .20', include=FALSE, out.height='160%', out.width='100%'}
 knitr::include_graphics('Manuscript.figures/F3.itemplots.png',dpi = 600)
@@
 
-```{r F4IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F4. Item 38 had relatively flat information curve with a peak lower than .20', out.height='160%', out.width='100%'}
+```{r F4IF, eval=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F4.
+Item 38 had relatively flat information curve with a peak lower than .20', include=FALSE, out.height='160%', out.width='100%'}
 knitr::include_graphics('Manuscript.figures/F4.itemplots.png',dpi = 600)
@@
 
-```{r F5IF, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F5.
+```{r F5IF, eval=FALSE, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F5.
 Three items: 25, 04, 01 carriedlow information.

### 2022-01-15 manuscript.Rmd
Item info plot stiched in one plot with cowplot and ggplot2

@@
 
-```{r iteminfoggplot3, include=F}
+```{r iteminfoggplot3, include=FALSE}
+#This chunkk holds the code for compilled item infor curve
+
 Theta <- matrix(seq(-6,6, by = .1))
@@
 F1.iteminfo.1 <- ggplot(F1.item.info.data , aes(x=Theta, y=F1.item.info.1)) +
-  geom_line()  +apatheme +labs(y="Item Information", title = "F1 item16") + geom_hline(yintercept = .18, colour ="red")
+  geom_line()  +apatheme +labs(title = "F1 item16") + geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#E64B3599", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 100, 200))
+
 F1.iteminfo.2 <- ggplot(F1.item.info.data , aes(x=Theta, y=F1.item.info.2)) +
-  geom_line()  +apatheme +labs(y="Item Information", title = "F1 item36")+geom_hline(yintercept = .18, colour ="red")
+  geom_line()  +apatheme +labs( title = "F1 item36")+geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#E64B3599", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 3, 6))
+
 F1.iteminfo.3 <- ggplot(F1.item.info.data , aes(x=Theta, y=F1.item.info.3)) +
-  geom_line()  +apatheme +labs(y="Item Information", title = "F1 item17")+ylim(0,6)+geom_hline(yintercept = .18, colour ="red")
+  geom_line()  +apatheme +labs(title = "F1 item17")+geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#E64B3599", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 3, 6), limits = c(0,6))
 
@@
 F2.iteminfo.1 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.1)) +
-  geom_line()  +apatheme +labs(y="Item Information", title = "F2 item11")+ylim(0,3)+geom_hline(yintercept = .18, colour ="red")
+  geom_line()  +apatheme +labs( title = "F2 item11")+geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#00A08799", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
 
@@
   geom_line()  + apatheme +
-  labs(y="Item Information", title = "F2 item10")+
-  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")
+  labs( title = "F2 item10")+
+  geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#00A08799", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
 
@@
   geom_line()  +apatheme +
-  labs(y="Item Information", title = "F2 item12")+
-  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")
+  labs( title = "F2 item12")+
+  geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#00A08799", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
 
@@
   geom_line()  +apatheme +
-  labs(y="Item Information", title = "F2 item07")+ylim(0,3)+
-  geom_hline(yintercept = .18, colour ="red")
+  labs( title = "F2 item07")+
+  geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#00A08799", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
 
@@
   geom_line()  +apatheme +
-  labs(y="Item Information", title = "F2 item08")+ylim(0,3)+
-  geom_hline(yintercept = .18, colour ="red")
+  labs( title = "F2 item08")+
+  geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#00A08799", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
 
@@
   geom_line()  +apatheme +
-  labs(y="Item Information", title = "F2 item09")+ylim(0,3)+
-  geom_hline(yintercept = .18, colour ="red")
+  labs( title = "F2 item09")+
+  geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#00A08799", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
 
@@
 F3.iteminfo.1 <- ggplot(F3.item.info.data , aes(x=Theta, y=F3.item.info.1)) +
-  geom_line()  +apatheme +labs(y="Item Information", title = "F3 item27")+
-  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")
+  geom_line()  +apatheme +labs( title = "F3 item27")+
+ geom_hline(yintercept = .18, colour ="red")+geom_area( fill="3C5488FF", alpha=0.6)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
 
@@
   geom_line()  +apatheme +
-  labs(y="Item Information",title = "F3 item03")+
-  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")
+  labs(title = "F3 item03")+
+  geom_hline(yintercept = .18, colour ="red")+geom_area( fill="3C5488FF", alpha=0.6)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
 
@@
   geom_line()  +apatheme +
-  labs(y="Item Information",title = "F3 item40")+
-  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")
+  labs(title = "F3 item40")+
+  geom_hline(yintercept = .18, colour ="red")+geom_area( fill="3C5488FF", alpha=0.6)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
 
@@
   geom_line()  +apatheme +
-  labs(y="Item Information",title = "F3 item30")+
-  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")
+  labs(title = "F3 item30")+
+  geom_hline(yintercept = .18, colour ="red")+theme(axis.line.x = element_line(color='red'),
+        axis.line.y = element_line(color='red'),
+        panel.border = element_rect(color = "red",
+                                    fill = NA,
+                                    size = 1))+geom_area( fill="3C5488FF", alpha=0.6)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
 
@@
   geom_line()  +apatheme +
-  labs(y="Item Information", title = "F3 item41")+
-  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")
+  labs(title = "F3 item41")+
+ geom_hline(yintercept = .18, colour ="red")+theme(axis.line.x = element_line(color='red'),
+        axis.line.y = element_line(color='red'),
+        panel.border = element_rect(color = "red",
+                                    fill = NA,
+                                    size = 1))+geom_area( fill="3C5488FF", alpha=0.6)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
 
@@
 F4.iteminfo.1 <- ggplot(F4.item.info.data , aes(x=Theta, y=F4.item.info.1)) +
-  geom_line()  +apatheme +labs(y="Item Information", title = "F4 item32")+
-  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")
+  geom_line()  +apatheme +labs(title = "F4 item32")+
+ geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#4DBBD5FF", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
 
@@
   geom_line()  +apatheme +
-  labs(y="Item Information",title = "F4 item35")+
-  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")
+  labs(title = "F4 item35")+
+  geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#4DBBD5FF", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
 
@@
   geom_line()  +apatheme +
-  labs(y="Item Information",title = "F4 item38")+
-  ylim(0,3)+geom_hline(yintercept = .18, colour ="red")
+  labs(title = "F4 item38")+
+ geom_hline(yintercept = .18, colour ="red")+theme(axis.line.x = element_line(color='red'),
+        axis.line.y = element_line(color='red'),
+        panel.border = element_rect(color = "red",
+                                    fill = NA,
+                                    size = 1))+geom_area( fill="#4DBBD5FF", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
 
@@
   geom_line()  +apatheme +
-  labs(y="Item Information",title = "F4 item33")+geom_hline(yintercept = .18, colour ="red")
+  labs(title = "F4 item33")+geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#4DBBD5FF", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 20, 40))
 
@@
 F5.iteminfo.1 <- ggplot(F3.item.info.data , aes(x=Theta, y=F5.item.info.1)) +
-  geom_line()  +apatheme +labs(y="Item Information", title = "F5 item46")+
-  ylim(0,2)+geom_hline(yintercept = .18, colour ="red")
+  geom_line()  +apatheme +labs(title = "F5 item46")+
+ geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#7E6148FF", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1, 2), limits = c(0,2))
 
@@
   geom_line()  +apatheme +
-  labs(y="Item Information",title = "F5 item45")+
-  ylim(0,2)+geom_hline(yintercept = .18, colour ="red")
+  labs(title = "F5 item45")+
+ geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#7E6148FF", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1, 2), limits = c(0,2))
 
@@
   geom_line()  +apatheme +
-  labs(y="Item Information",title = "F5 item25")+
-  ylim(0,2)+geom_hline(yintercept = .18, colour ="red")
+  labs(title = "F5 item25")+
+  geom_hline(yintercept = .18, colour ="red")+theme(axis.line.x = element_line(color='red'),
+        axis.line.y = element_line(color='red'),
+        panel.border = element_rect(color = "red",
+                                    fill = NA,
+                                    size = 1))+geom_area( fill="#7E6148FF", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1, 2), limits = c(0,2))
 
@@
   geom_line()  +apatheme +
-  labs(y="Item Information",title = "F5 item04")+
- geom_hline(yintercept = .18, colour ="red")+ylim(0,2)
+  labs(title = "F5 item04")+
+ geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#7E6148FF", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1, 2), limits = c(0,2))
 
@@
   geom_line()  +apatheme +
-  labs(y="Item Information", title = "F5 item01")+
-  ylim(0,2)+geom_hline(yintercept = .18, colour ="red")
+  labs( title = "F5 item01")+
+ geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#7E6148FF", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+theme(axis.line.x = element_line(color='red'),
+        axis.line.y = element_line(color='red'),
+        panel.border = element_rect(color = "red",
+                                    fill = NA,
+                                    size = 1))+scale_y_continuous(breaks=c(0, 1, 2), limits = c(0,2))
 
@@
 
+allitemplots <- cowplot::plot_grid(F1.iteminfo.1,F1.iteminfo.2, F1.iteminfo.3,
+                                   F2.iteminfo.1,F2.iteminfo.2, F2.iteminfo.3,F2.iteminfo.4,F2.iteminfo.5,F2.iteminfo.6, 
+                                   F3.iteminfo.1, F3.iteminfo.2, F3.iteminfo.3, F3.iteminfo.4, F3.iteminfo.5,   
+                                   F4.iteminfo.1, F4.iteminfo.2 ,F4.iteminfo.3 ,F4.iteminfo.4,
+                                   F5.iteminfo.1,F5.iteminfo.2,F5.iteminfo.3,F5.iteminfo.4,F5.iteminfo.5,
+
+                     labels = "AUTO",
+                     align="v",
+                     ncol = 5,
+                     label_size = 12,
+                     label_fontfamily = "Arial",
+                     label_fontface = "plain")
+
+ggsave("Manuscript.figures/allitemplots.png",allitemplots, width = 12, height = 12, dpi = 1200, bg = "white")
+
+```
+
+```{r factorinfo, eval=FALSE, include=FALSE}
+#This chunk holds codes for item info plots clustered in factors (Not included in the manuscript)
 F1.itemplots <- cowplot::plot_grid(F1.iteminfo.1,F1.iteminfo.2, F1.iteminfo.3,
@@
 
-F5.itemplots <- cowplot::plot_grid(F5.iteminfo.1,F5.iteminfo.2, F5.iteminfo.3,
-                                   F5.iteminfo.4,F5.iteminfo.5,
+F5.itemplots <- cowplot::plot_grid(F1.iteminfo.1,F1.iteminfo.2, F1.iteminfo.3,
+
                    labels = "AUTO",
@@
 
-```{r inteminfoggplo2com, eval=FALSE, include=FALSE}
-
+```{r inteminfoggplo2c, eval=FALSE, include=FALSE}
+# This chinks holds code of compiled item info code created using facet wrap. (Not included in manuscript)
 pacman::p_load(reshape,ggsci)
@@
 
+allicc <- cowplot::plot_grid(F1.iic2, F2.iic2, F3.iic2, F4.iic2, F5.iic2, labels = "AUTO",ncol=2, label_size = 15,align = "h",label_fontfamily = "Arial",
+                  label_fontface = "plain")
+
+ggsave("Manuscript.figures/allicc.png",allicc, width = 12, height =12, dpi = 1200, bg ="white")
+
+##Creating ggplot2 based all item item info using facet wrap
+alldata <- as.data.frame(cbind(Item16,Item36,Item17,Item11,Item10, Item12,Item07,Item08,Item09,Item27,Item03, Item40, Item30, Item41, Item32, Item35, Item38, Item33, Item46, Item45, Item25, Item04, Item01))
+
+all.data.long <- melt(alldata)
+alldata2 <- data.frame(Theta=seq(-6,6, by = .1), all.data.long )
+
+allicc3 <- ggplot(alldata2,aes(Theta,value,col=variable))+geom_line()+apatheme+
+  ggtitle("Item Information Plot")+theme(legend.position = "none")+
+  facet_wrap(~variable,scales = "free")+theme(strip.text.x = element_text(size = 15))+
+  geom_hline(yintercept = .20, colour ="red")+geom_area()+scale_color_npg()+aes(fill = as.factor(variable))+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))
+
+ggsave("Manuscript.figures/allicc2.png",allicc3, width = 12, height =12, dpi = 1200, bg ="white")
+
 ```
@@
 ```{r shortIRT, include=FALSE}
+#This cunk holds codes for our SHORT LEBA IRT with item = 18
+
+#Define model
 F1 <- sem.data %>% 
@@
 
+#fit model
 F1_fit <- mirt(F1, model = 1, itemtype = 'graded', 

### 2022-01-15 manuscript.Rmd
Comments added to describe each code chunks for the common users

@@
 ```{r setup, warning=FALSE, include=FALSE}
+#This chunk controls the common chunk parameters for the whole manuscript
 knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600, fig.width = 6,
@@
 ```{r pacman, eval=FALSE, include=FALSE}
+#This chunk holds code for 'pacman' based library management.
+
 #You need to run this chunk 1X in your system 
@@
 ```{r library, include=FALSE}
+#This chunk holds code for calling the required packages
 
@@
 ```{r relscale, include=F, warning=F, message=F}
-
+#This chunk holds code for Relevant scales table in the manuscript
 relevant.scale.data <- readxl::read_excel("Table_raw/relevant_scales.xlsx")
@@
 ```{r Data, include=FALSE}
+#This chunk holds code for data wrangling
+
 data <- readRDS("leba_2021-09-08.rds")
@@
 ```{r country, include=FALSE}
+#This chunk holds code for timezone calculation
+
 library(stringr)
@@
 ```{r timezone, include=F}
-
+#This chunk holds code for creating timezone.csv file
 timezone <- TZ %>% 
@@
 ```{r prepareDescTable, include=FALSE}
+#This chunk holds code for demographic data wrangling.
 
@@
 ```{r Manuflowchart, include=FALSE }
+#This chunk holds code for the work flow chart of the data analysis
+
 Flowchart1 <- grViz("digraph my_flowchart{
@@
 desc_kable  %>% kable_styling(latex_options = c("scale_down")) %>% landscape()
-
 ```
@@
 ```{r ggplot2, include=F}
+#This chunk holds code for creating ggplot2 based apatheme for plots.
 apatheme=theme_bw()+
@@
 ```{r EFAdata, include=FALSE}
+#This chunk holds code for creating EFA data subset
 ### EFA data
@@
 ```{r EFAassumptions, include=FALSE}
+#This chunk holds code for cheacking assumptions of EFA
 
@@
 ```{r ItemAnalysis, include=FALSE}
+#This chunk holds code for Item analysis (Classical Test Theory)
 # Item analysis
@@
 ```{r CorrMatrix, include=FALSE}
+#This chunk holds code for producing correlation matrix and its details.
+
 #Polychoric Correlation matrix
@@
 ```{r corplot, include =F}
+#This chunk holds code for plotting the correlation matrix
+
 corplot <- ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
@@
 ```{r ParallelEFA, include=FALSE}
-
+#This chunk holds code for factor identification method : Horn
 # Parallel analysis
@@
 ```{r ScreePlot, include=FALSE}
+
+#This chunk holds code for factor identification method : Scree Plot
+
 Scree <- scree(correlations$rho,factors=TRUE,pc=TRUE,main="(B)",
@@
 ```{r HullEFA, include=FALSE}
+#This chunk holds code for factor identification method : Hull
+
 # HULL
@@
 ```{r MAPefa, include=FALSE}
+#This chunk holds code for factor identification method : MAP
 #MAP
@@
 ```{r factors, include=F}
+#This chunk holds code for compiled factor identification plots
+
 fator <- cowplot::plot_grid(parallel, scree.plot,Hull, 
@@
 ```{r EFA, include=FALSE}
+#This chunk holds code for five factor EFA (pa-varimax)
+
 fa.5F.1 <- fa(r=correlations$rho, nfactors = 5, fm= "pa",rotate ="varimax",
@@
 ```{r EFAplotcode, include=FALSE}
-
+#This chunk holds code for the EFA plot
 EFAplot <- grViz("
@@
 ```{r Cronbach alpha for 5 fators, message=TRUE, warning=FALSE, include=FALSE}
+#This chunk holds code for estimating cronbach's alpha for the five factors.
 
@@
 ```{r tabledown, include=F}
+#This chunk holds codes for creating factor analysis output table
+
 efa.table <- tabledown::fac.tab(fa.5F.3,cut=.3, complexity = F)
@@
 ```{r EFARes, message=FALSE, warning=FALSE, include=F}
-#hist(residual.5F,  main = NULL, xlab = "Residuals", ylim=c(0, 400))
-#abline(h =51, lwd = 2, lty = 2)
-#abline(v =.05,lwd = 2, lty = 2)
+#This chunk holds codes for creating the residual plot for 5 factor EFA (pa-varimax)
 res.dat <- as.data.frame(unclass(residual.5F))
@@
 ```{r EFAplotprep, include=F}
+#This chunk holds codes for co-plotting EFA-plot and residual plot.
+
 library(jpeg)
@@
 ```{r gtvis, include =F}
+#This chunk holds codes for creating 'gtExtra' based descriptive figures (data preparation)
+
 ## Recoding sem.data$item8
@@
 ```{r efagt,include=F}
+
+#This chunk holds codes for creating 'gtExtra' based descriptive figures (EFA descriptives
+
 efa.gt %>% 
@@
 ```{r cfagt,include=F}
+#This chunk holds codes for creating 'gtExtra' based descriptive figures (CFA Descriptives)
+
 cfa.gt %>% 
@@
 ```{r eval=FALSE, include=FALSE}
+#This chunk holds codes for creating 'gtExtra' based descriptive figures (EFA=CFA); 
+#Not included in the manuscript
+
 gt.fullTable <-  rbind( efa.gt, cfa.gt) %>% 
@@
 ```{r CFAdataframe, include=FALSE}
+#This chunk holds codes for CFA data preparation.
 
@@
 ```{r CFA25items, include=FALSE }
+#This chunk holds codes for 1st CFA
 
@@
 
-```{r mod1, include=FALSE}
+```{r mod1, eval=FALSE, include=FALSE}
+#This chunk holds codes for modification indices for 1st CFA
 modfit.Cor.one <- modindices(fit.Cor.1, sort. = TRUE) 
@@
 ```{r CFA23withMI, include=FALSE}
+#This chunk holds codes for 2nd CFA (Accepted)
+
 LB.model.Cor.2 <- "F1 =~ a1*item16 + item36 + a2*item17
@@
 
-```{r mod2, include=FALSE}
+```{r mod2, eval=FALSE, include=FALSE}
+#This chunk holds codes for modification indices for 2nd CFA
 modfit.Cor.one <- modindices(fit.Cor.2, sort. = TRUE) 
@@
 ```{r cfaMat, results='asis'}
+#This chunk holds codes to create CFA output table (better options are avaiable at 'tabledown' package)
+
 CFa.matrix <- matrix("NA", nrow =2, ncol = 9)
@@
 ```{r simulation, eval=FALSE, include=FALSE}
+#This chunk holds codes for simulating Standard error for the accepted CFA model
+
 library("simsem")
@@
 ```{r cfaplot, include =F}
+#This chunk holds codes to store CFA plot
+
 png(filename="Manuscript.figures/CFAplot.png", 
@@
 ```{r InvarianceAnalysis_data, include=FALSE}
+#This chunk holds codes to prepare measurement invariance data.
+
 invariance.data <- cbind(CFA.data, data$slypos_demographics_language.factor[429:690])
@@
 ```{r Invariancedetail, include=FALSE}
+#This chunk holds codes for measurement Invariance
 
@@
 ```{r textanalysis}
+#This chunk holds codes for semantic analysis and readability test
+
 #devtools::install_github("unDocUMeantIt/koRpus")
@@
 ```{r IRTdata, include=FALSE}
+#This chunk holds codes for preparing IRT data and 1st IRT model fitting
+
 ## Recoding sem.data$item8 into sem.data$Ritem8
@@
 ```{r IRTreliability, eval=FALSE, include=FALSE}
+#This chunk holds codes for IRT model's conditional  and merginal reliability
+
 #conditional reliability
@@
 ```{r iteminfoggplot3, include=FALSE}
-#This chunkk holds the code for compilled item infor curve
+#This chunk holds the code for compiled item info curve for the 1st IRT model
 
@@
 ```{r shortIRT, include=FALSE}
-#This cunk holds codes for our SHORT LEBA IRT with item = 18
+#This chunk holds codes for our SHORT LEBA IRT with item = 18 (2nd IRT)
 
@@
 
-F1.reliability <- plot(F1_fit, type = 'rxx', theta_lim = c(-6, 6), 
-      main="" )
-F2.reliability <- plot(F2_fit.redu, type = 'rxx', theta_lim = c(-6, 6), 
-      main="" )
-F3.reliability <- plot(F3_fit.redu, type = 'rxx', theta_lim = c(-6, 6), 
-      main="" )
-F4.reliability <- plot(F4_fit.redu, type = 'rxx', theta_lim = c(-6, 6), 
-      main="" )
-F5.reliability <- plot(F5_fit, type = 'rxx', theta_lim = c(-6, 6), 
-      main="" )
+#F1.reliability <- plot(F1_fit, type = 'rxx', theta_lim = c(-6, 6),  main="" )
+#F2.reliability <- plot(F2_fit.redu, type = 'rxx', theta_lim = c(-6, 6),  main="" )
+#F3.reliability <- plot(F3_fit.redu, type = 'rxx', theta_lim = c(-6, 6), main="" )
+#F4.reliability <- plot(F4_fit.redu, type = 'rxx', theta_lim = c(-6, 6), main="" )
+#F5.reliability <- plot(F5_fit, type = 'rxx', theta_lim = c(-6, 6), main="" )
 
 ##IRT reliability (marginal reliability of scales)
-F1.marginal.rel <- marginal_rxx(F1_fit)
-F2.marginal.rel <-marginal_rxx(F2_fit.redu)
-F3.marginal.rel <-marginal_rxx(F3_fit.redu)
-F4.marginal.rel <-marginal_rxx(F4_fit.redu)
-F5.marginal.rel <-marginal_rxx(F5_fit)
+#F1.marginal.rel <- marginal_rxx(F1_fit)
+#F2.marginal.rel <-marginal_rxx(F2_fit.redu)
+#F3.marginal.rel <-marginal_rxx(F3_fit.redu)
+#F4.marginal.rel <-marginal_rxx(F4_fit.redu)
+#F5.marginal.rel <-marginal_rxx(F5_fit)
 
@@
 
-F1_test.info <- plot(F1_fit, type = "infoSE", main = "F1: Wearing blue light filters")
-
-F2_test.info.redu <- plot(F2_fit.redu, type = "infoSE", main = "F2: Spending time outdoors")
-
-F3_test.info.redu <- plot(F3_fit.redu, type = "infoSE", main = "F3: Using phone and smart-watch in bed")
-
-F4_test.info.redu <- plot(F4_fit.redu, type = "infoSE", main = "F4: Using light before bedtime")
-
-F5_test.info <- plot(F5_fit.redu, type = "infoSE", main = "F5: Using light in the morning and during daytime")
+#F1_test.info <- plot(F1_fit, type = "infoSE", main = "F1: Wearing blue light filters")
+
+#F2_test.info.redu <- plot(F2_fit.redu, type = "infoSE", main = "F2: Spending time outdoors")
+
+#F3_test.info.redu <- plot(F3_fit.redu, type = "infoSE", main = "F3: Using phone and smart-watch in bed")
+
+#F4_test.info.redu <- plot(F4_fit.redu, type = "infoSE", main = "F4: Using light before bedtime")
+
+#F5_test.info <- plot(F5_fit.redu, type = "infoSE", main = "F5: Using light in the morning and during daytime")
 
 ##Scale characteristic curve
-F1.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
-F2.scale <- plot(F2_fit.redu, type = 'score', theta_lim = c(-6, 6), main = "")
-F3.scale <- plot(F3_fit.redu, type = 'score', theta_lim = c(-6, 6), main = "")
-F4.scale <- plot(F4_fit.redu, type = 'score', theta_lim = c(-6, 6), main = "")
-F5.scale <- plot(F5_fit.redu, type = 'score', theta_lim = c(-6, 6), main = "")
+#F1.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
+#F2.scale <- plot(F2_fit.redu, type = 'score', theta_lim = c(-6, 6), main = "")
+#F3.scale <- plot(F3_fit.redu, type = 'score', theta_lim = c(-6, 6), main = "")
+#F4.scale <- plot(F4_fit.redu, type = 'score', theta_lim = c(-6, 6), main = "")
+#F5.scale <- plot(F5_fit.redu, type = 'score', theta_lim = c(-6, 6), main = "")
 
@@
 ```{r testinfoggplot2, include=F}
+
+#This chunk holds codes for Test information curve (IRT model 2)
+
 Theta <- matrix(seq(-6,6, by = .1))
@@
 ```{r perfit, include=F}
+#This chunk holds codes for arranging the person fit plot of IRT model 2
+
 personfit <- cowplot::plot_grid(F1.person, F2.person,F3.person,F4.person,F5.person, 
@@
 ```{r fscore, include=FALSE}
+#This chunk holds codes for score estimation using IRT model 2
+
 LEBA.Total <- sem.data %>% 
@@
 ```{r WPdata, warning=F, include=FALSE}
-
+#This chunk holds codes for preparing data for wright-map
 library(RColorBrewer)
@@
 ```{r saveWrightmao, include=FALSE, warning=F, message=F}
+#This chunk holds codes for saving the wright-map
 jpeg("Manuscript.figures/wm.png", width = 800, height = 750)

### 2022-01-15 s1.Rmd
Comments added to describe each code chunks for the common users

@@
     latex_engine: xelatex
+    includes:
+      in_header: header.tex
 
-appendix:
-  - "appendix-1.Rmd"
 mainfont: Arial
@@
 library(papaja) # devtools::install_github("crsh/papaja")
-library(lavaan)
-library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
-library(semTools)
-library(MOTE)
-library(car)#reversecoding 
-library(psych)
-library(dlookr)
-library(plyr)
-library(tidyverse)
-library(qgraph)
-library(kableExtra)
-library(paran) # Parallel analysis
-library(EFA.MRFA) # Hull method
-library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
 library(DiagrammeRsvg) #For DiagrammeR
 library(rsvg) #For DiagrammeR
-library(ggcorrplot)
-library(semTable)
-library(magick)
-library(mirt)
-library(gtsummary)
-library(gt)
-library(gtExtras)
-library(likert)
-library(VIM) #Missing data
-library(kutils)
-library(simsem)
-library(tabledown)
-library(readxl)
-library(koRpus)# stable release
-library(koRpus.lang.en)
+library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
+
 r_refs("references.bib")
@@
 
-(ref:foo) Factor Identification Methods (A) Parallel analysis drew 500 sets of random data set (n=428 each) and adjusted the mean eigenvalues for sample bias.
-In x-axis we plotted the number of possible factors and in y-axis we plotted the mean adjusted eigenvalues.
-The First inflection point of the plot indicated the optimal number of factors were six.
-(B) In the scree plot possible number of factors are plotted against obtained eigenvalues.
-Scree plot suggested six factors.
-(C) Hull method we plotted the number of possible factors in the x-axis and the CAF index(CAF: Common Part Accounted for-an indicator of model fit) in the y-axis.
-Hull method indicated 5 factors were required to balance the model fit and number of parameters.
+```{r Manuflowchart, eval=FALSE, include=FALSE}
+Flowchart1 <- grViz("digraph my_flowchart{
 
-```{r foo, fig.cap='(ref:foo)',  warning=FALSE, results= 'asis',fig.align='center'}
+                    graph [fontname = Helvetica,layout = dot,fontsize = 100,layout = dot ]
 
-knitr::include_graphics('Manuscript.figures/factors.png', dpi =800)
+                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 65, height = 10, 
+                    fixedsize = true,fontsize = 200]
 
+                    A[label = '48 items were generated'] 
+                    B[label = 'Exploratory Factor Analysis on 48 Items (n = 428)']
+
+                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 65, height = 20, 
+                    fixedsize = true, fontsize = 200]
+                    C[label = 
+                    <Factor Identification<br/>Scree Plot: 6 Factors<br/>Parallel Analysis: 6 Factors<br/>Minimum Average Partial Method: 5 Factors<br/>Hull Method: 5 Factors>
+                    ]
+
+                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 80, height = 10, 
+                    fixedsize = true,fontsize = 200]  
+                     1[label = '5 Factor Solution Retained 25 Items']
+                     2[label = <Reliability Analysis on EFA Sample (n=428)<br/>Ordinal alpha F1 =.94; F2 = .76; F3 = .75; F4 =.72; F5 =.62.>]
+
+                     3[label = <Confirmatory Factor Analysis<br/>on the Five Factor Model (25 Items; n=262)<br/>Acceptable Fit ( CFI = .94; TLI .93; RMSEA = .06, SRMR = .11)>]
+
+                    4[label = <Confirmatory Factor Analysis<br/>on the Five Factor Model (23 Items; n=262)<br/>Acceptable Fit ( CFI = .97; TLI= .96; RMSEA = .04, SRMR = .09)>]
+                     5[label = <Reliability Analysis (23 Items; n=262)<br/>Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52<br/>Mcdonald  omega(total) for the total scale = .73>]
+                    8[label = <Measurement Invariance Analysis<br/>Residual measurement invariance achieved>]
+                    9[label = 'Semantic Analysis']
+                    10[label = <LEBA Short Form (18 Items; n=690)<br/>Based on Item Response Theory>]
+
+                    6[label = 
+                    <6-Factor solution:<br/>one factor emerged with only two salient loadings>
+                    ]
+                    7[label = 'Rejected']
+
+                     edge[fontname = Helvetica,color = black,arrowhead = vee, arrowsize = 5]
+                     A ->B
+                     B ->C
+                     C ->1
+                     1 ->2
+                     2 ->3
+                     3 ->4
+                     4 ->5
+                    5->8
+                    8 ->9
+                    9 ->10
+                     C ->6
+                     6 ->7
+
+}"
+)
+
+export_svg(Flowchart1) %>%
+  charToRaw() %>%
+  rsvg() %>%
+  png::writePNG("Manuscript.figures/Flowchart1.jpeg", dpi = 1200)
+
+networkD3::saveNetwork(Flowchart1, "Manuscript.figures/flow.html")
+
+webshot::webshot("Manuscript.figures/flow.html", "Manuscript.figures/flow1.png", vheight = 50, zoom = 8)
+
+```
+
+```{r IF, echo=FALSE, fig.align='center', fig.cap='Item information curve ', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/allitemplots.png', dpi = 300)
 ```

### 2022-01-30 manuscript.Rmd
Time-zone tibble is not working

@@
   An expert panel prepared the initial 48 item pool.
-Responses to these items were then collected in an online survey producing responses from an international sample (690 completed responses, 74 countries, 28 time zones).
+Responses, consisting rating the frequency of engaging in the per-item behavior on a 5-point Likert type scale were  collected in an online survey producing responses from an international sample (690 completed responses, 74 countries, 28 time zones).
 Exploratory factor analysis (EFA) on an initial subset of our sample (n=428) rendered a five-factor solution with 25 items (Wearing blue light filters, spending time outdoors, using phone and smart-watch in bed, using light before bedtime, using light in the morning and during daytime).
@@
 To ensure construct adequacy we thoroughly assessed the current status of literature and identified a variety of light exposure related scales.
-However, no scales specifically measuring the behavioural component of light exposure were found (see Table \@ref(tab:eltab)).
+However, no scales specifically measuring the behavioural component of light exposure were found (see Table \@ref(tab:reltab2)).
 Consequentially we pursued to introduce a new openly available scale to address this research gap.
@@
 Finally, we assessed age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language as single-item demographic variables.
-The demographic characteristics of our sample are given in Table \@ref(tab:demographics).
+The demographic characteristics of our sample are given in Table \@ref(tab:demotab).
 
@@
                  ),
+
     missing = "no"
@@
 #summarise country/time zone data
-
-descriptives.data%>%
-  tbl_summary(
-    label = slypos_demographics_tz.factor ~ "Time zone - Country",
-    statistic = list(all_categorical() ~ "{n} ({p}%)"),
-    missing = "no",
-    sort = all_categorical() ~ "frequency",
-    include = "slypos_demographics_tz.factor"
-  )  %>% bold_labels() %>% 
-  modify_header(label ~ "") %>%
-  as_tibble(format = 'pipe') -> tz_tibble
+#The following chunk is not working now. May be package problem (Sorting command is not working)
+
+# descriptives.data%>%
+#   tbl_summary(
+#     label = slypos_demographics_tz.factor ~ "Time zone - Country",
+#     statistic = list(all_categorical() ~ "{n} ({p}%)"),
+#     missing = "no",
+#     sort = all_categorical() ~ "frequency",
+#     include = "slypos_demographics_tz.factor"
+#   )  %>% bold_labels() %>% 
+#   modify_header(label ~ "") %>%
+#   as_tibble(format = 'pipe') -> tz_tibble
 
@@
 
-```{r demographics, warning=F, message=F}
+```{r demotab, warning=F, message=F}
 desc_kable  %>% kable_styling(latex_options = c("scale_down")) %>% landscape()
@@
 
-Table \@ref(tab:demographics) summarizes the survey participants' demographic characteristics.
+Table \@ref(tab:demotab) summarizes the survey participants' demographic characteristics.
 Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses.
@@
 
-- `r tz_tibble[2,1]`:     `r tz_tibble[2,2]` 
-- `r tz_tibble[3,1]`:     `r tz_tibble[3,2]`
-- `r tz_tibble[4,1]`:     `r tz_tibble[4,2]`
-- `r tz_tibble[5,1]`:     `r tz_tibble[5,2]`
-- `r tz_tibble[6,1]`:     `r tz_tibble[6,2]`
-- `r tz_tibble[7,1]`:     `r tz_tibble[7,2]`
-- `r tz_tibble[8,1]`:     `r tz_tibble[8,2]`
-- `r tz_tibble[9,1]`:     `r tz_tibble[9,2]`
-- `r tz_tibble[10,1]`:    `r tz_tibble[10,2]`
-- `r tz_tibble[11,1]`:    `r tz_tibble[11,2]`
-
-For a complete list of geographic locations, see Suppl. Table \@ref(tab:tztabprint).
+<!-- - `r tz_tibble[2,1]`:     `r tz_tibble[2,2]` -->
+<!-- - `r tz_tibble[3,1]`:     `r tz_tibble[3,2]` -->
+<!-- - `r tz_tibble[4,1]`:     `r tz_tibble[4,2]` -->
+<!-- - `r tz_tibble[5,1]`:     `r tz_tibble[5,2]` -->
+<!-- - `r tz_tibble[6,1]`:     `r tz_tibble[6,2]` -->
+<!-- - `r tz_tibble[7,1]`:     `r tz_tibble[7,2]` -->
+<!-- - `r tz_tibble[8,1]`:     `r tz_tibble[8,2]` -->
+<!-- - `r tz_tibble[9,1]`:     `r tz_tibble[9,2]` -->
+<!-- - `r tz_tibble[10,1]`:    `r tz_tibble[10,2]` -->
+<!-- - `r tz_tibble[11,1]`:    `r tz_tibble[11,2]` -->
+
+For a complete list of geographic locations, see Suppl. Table \@ref(tab:tztable).
 
@@
 ggsave("Manuscript.figures/factors.png",fator, width = 5, height = 7, dpi = 600)
+```
+
+```{r factorsplot, eval=FALSE, include=FALSE}
+#This chunk holds code for compiled factor identification plots
+
+fator2 <- cowplot::plot_grid(parallel, scree.plot,Hull, 
+                   labels = "AUTO",
+                   ncol=3, 
+                  align = "v", 
+                  label_fontfamily = "Arial",
+                  label_fontface = "plain")
+ggsave("Manuscript.figures/factors2.png",fator2, width = 18, height = 6, dpi = 600)
 ```
@@
 Item discrimination parameters of our tool fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$).
-Examination of the item information curve (Sup.fig \@ref(fig:F2IF)-\@ref(fig:F5IF)) indicated 5 items (1, 25,  38, 30, & 41) had relatively flat information curves (I($\theta$) <.20) thus discarded creating a short form of LEBA with 5 factors and 18 items.
+Examination of the item information curve (Sup.fig \@ref(fig:IF)) indicated 5 items (1, 25,  38, 30, & 41) had relatively flat information curves (I($\theta$) <.20) thus discarded creating a short form of LEBA with 5 factors and 18 items.
 
@@
 
-ggsave("Manuscript.figures/allitemplots.png",allitemplots, width = 12, height = 12, dpi = 1200, bg = "white")
+ggsave("Manuscript.figures/allitemplots.png",allitemplots, width = 18, height = 12, dpi = 600, bg = "white")
+
+discarded.items.plot <- cowplot::plot_grid(F3.iteminfo.4,
+                                           F3.iteminfo.5,
+                                           F4.iteminfo.3,
+                                           F5.iteminfo.3,
+                                           F5.iteminfo.5, 
+                                            labels = "AUTO",
+                                   align="v",
+                                   ncol = 5,
+                                   label_size = 12,
+                                   label_fontfamily = "Arial",
+                                   label_fontface = "plain")
+
+ggsave("Manuscript.figures/discarded.png",discarded.items.plot, width = 18, height = 4, dpi = 600, bg = "white")
 
@@
                      align="v",
-                     ncol = 2,
+                     ncol = 3,
                      label_size = 15,
@@
                      label_fontface = "plain")
-ggsave("Manuscript.figures/TIC.png",TIC.plot, width = 10, height = 12, dpi = 600, bg = "white")
+ggsave("Manuscript.figures/TIC.png",TIC.plot, width = 18, height = 12, dpi = 600, bg = "white")
 

### 2022-01-30 s1.Rmd
Time-zone tibble is not working

@@
 ---
-```{r library, include=FALSE}
+```{r setup, warning=FALSE, include=FALSE}
+#This chunk controls the common chunk parameters for the whole manuscript
+knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600, fig.width = 6,
+ fig.asp = 0.8,out.width = "80%", dev=c('png','postscript'))
+options(knitr.duplicate.label = "allow")
+set.seed(123)
+par(family = "Arial")
+
+```
+
+```{r library1, include=FALSE}
 
@@
 
-r_refs("references.bib")
-```
-
-```{r setup, include = FALSE}
-library("papaja")
 r_refs("references.bib")
@@
 
+```{r library, include=FALSE}
+#This chunk holds code for calling the required packages
+
+library(papaja) # devtools::install_github("crsh/papaja")
+library(lavaan)
+library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
+library(semTools)
+library(MOTE)
+library(car)#reversecoding 
+library(psych)
+library(dlookr)
+library(plyr)
+library(tidyverse)
+library(qgraph)
+library(kableExtra)
+library(paran) # Parallel analysis
+library(EFA.MRFA) # Hull method
+library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
+library(DiagrammeRsvg) #For DiagrammeR
+library(rsvg) #For DiagrammeR
+library(ggcorrplot)
+library(semTable)
+library(magick)
+library(mirt)
+library(gtsummary)
+library(gt)
+library(gtExtras)
+library(likert)
+library(VIM) #Missing data
+library(kutils)
+library(simsem)
+library(tabledown)
+library(readxl)
+library(koRpus)# stable release
+library(koRpus.lang.en)
+library(reshape)
+library(ggsci)
+r_refs("references.bib")
+```
+```{r Data, include=FALSE}
+#This chunk holds code for data wrangling
+
+data <- readRDS("leba_2021-09-08.rds")
+
+# Separating EFA and CFA samples with descriptive column
+descriptives.data <- data
+
+## Merge "0"s and "1"s into "1"s select,subset assign)
+descriptives.data[ , 9:56 ][ descriptives.data[ , 9:56 ] == 0 ] <- 1
+#EFA.descriptives <- descriptives.data[1:428,]
+EFA.descriptives <- subset(descriptives.data, IncludedInEFA == "TRUE")
+#CFA.descriptives <- descriptives.data[429:690, ]
+CFA.descriptives<- subset(descriptives.data, IncludedInEFA == "FALSE")
+
+#Separating the EFA and CFA(only items)
+sem.data <- data[, 9:56] #EFA & CFA data
+sem.data[ sem.data == 0] <- 1 #Merged "0"s and "1"s into "1"s
+
+## renaming the column-header
+prefix <- "item"
+sufix <- c(1:48)
+colnam <- paste(prefix,sufix, sep = "" )
+colnames(sem.data) <- colnam
+names(sem.data)[names(sem.data) == "item1"] <- "item01"
+names(sem.data)[names(sem.data) == "item2"] <- "item02"
+names(sem.data)[names(sem.data) == "item3"] <- "item03"
+names(sem.data)[names(sem.data) == "item4"] <- "item04"
+names(sem.data)[names(sem.data) == "item5"] <- "item05"
+names(sem.data)[names(sem.data) == "item6"] <- "item06"
+names(sem.data)[names(sem.data) == "item7"] <- "item07"
+names(sem.data)[names(sem.data) == "item8"] <- "item08"
+names(sem.data)[names(sem.data) == "item9"] <- "item09"
+```
+
+```{r prepareDescTable, include=FALSE}
+#This chunk holds code for demographic data wrangling.
+
+listdescVars <- colnames(descriptives.data[c(1:3,5:7)])
+
+#seperating naming and  reducing data for descriptive Table 
+desctable.data <- dplyr::select(descriptives.data, c(listdescVars,
+                          IncludedInCFA))
+
+#renaming TRUE and FALSE from the IncludedInCFA to EFA and CFA for Descriptive Table
+desctable.data$IncludedInCFA[desctable.data$IncludedInCFA == T ] <-
+ "2. CFA Sample"
+desctable.data$IncludedInCFA[desctable.data$IncludedInCFA == F ] <- 
+ "1. EFA Sample"
+
+# recode the Gender factor so it will only show "Gender Diverse" in the summary table
+desctable.data$slypos_demographics_gender.factor <-
+  recode_factor(desctable.data$slypos_demographics_gender.factor, "No" = "Yes",
+         "Yes"= "No")
+
+# create descriptive table for the demographic vars (excluding tz & Country) with gtsummary
+desctable.data %>%
+  tbl_summary(
+    by = IncludedInCFA,
+    statistic = list(all_continuous() ~ "{mean} ({sd})",
+                     all_categorical() ~ "{n} ({p}%)"),
+    digits = all_continuous() ~ 2,
+    label = list(slypos_demographics_age ~ "Age",
+                 slypos_demographics_sex.factor ~ "Sex",
+                 slypos_demographics_gender.factor ~ "Gender-Variant Identity",
+                 slypos_demographics_language.factor ~ "Native English Speaker",
+                 slypos_demographics_work_or_school.factor ~ "Occupational Status",
+                 slypos_demographics_school.factor ~ "Occupational setting"
+                 ),
+    missing = "no"
+    ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
+modify_header(label ~ "**Variable**") %>% separate_p_footnotes() %>%
+  modify_caption("Demographic Characteristics") -> desc_table
+
+as_tibble(desc_table) -> desc_tibble 
+as_kable_extra(desc_table, format = "latex",booktabs = T) -> desc_kable #save it as a knitr::kable
+
+#summarise country/time zone data
+
+descriptives.data%>%
+  tbl_summary(
+    label = slypos_demographics_tz.factor ~ "Time zone - Country",
+    statistic = list(all_categorical() ~ "{n} ({p}%)"),
+    missing = "no",
+    sort = all_categorical() ~ "frequency",
+    include = "slypos_demographics_tz.factor"
+  )  %>% bold_labels() %>% 
+  modify_header(label ~ "") %>%
+  as_tibble(format = 'pipe') -> tz_tibble
+
+```
+
+Table \@ref(tab:tabtabtab)
+
+```{r tabtabtab, warning=F, message=F}
+desc_kable  %>% kable_styling(latex_options = c("scale_down")) %>% landscape()
+```
+
+Table \@ref(tab:tabtabtab)
+
 \newpage

### 2022-01-30 manuscript.Rmd
tz-tibble working

@@
 
-# descriptives.data%>%
-#   tbl_summary(
-#     label = slypos_demographics_tz.factor ~ "Time zone - Country",
-#     statistic = list(all_categorical() ~ "{n} ({p}%)"),
-#     missing = "no",
-#     sort = all_categorical() ~ "frequency",
-#     include = "slypos_demographics_tz.factor"
-#   )  %>% bold_labels() %>% 
-#   modify_header(label ~ "") %>%
-#   as_tibble(format = 'pipe') -> tz_tibble
+descriptives.data%>%
+  tbl_summary(
+    label = slypos_demographics_tz.factor ~ "Time zone - Country",
+    statistic = list(all_categorical() ~ "{n} ({p}%)"),
+    missing = "no",
+    sort = all_categorical() ~ "frequency",
+    include = "slypos_demographics_tz.factor"
+  )  %>% bold_labels() %>%
+  modify_header(label ~ "") %>%
+  as_tibble(format = 'pipe') -> tz_tibble
 

### 2022-01-30 manuscript.Rmd

@@
 
-<!-- - `r tz_tibble[2,1]`:     `r tz_tibble[2,2]` -->
-<!-- - `r tz_tibble[3,1]`:     `r tz_tibble[3,2]` -->
-<!-- - `r tz_tibble[4,1]`:     `r tz_tibble[4,2]` -->
-<!-- - `r tz_tibble[5,1]`:     `r tz_tibble[5,2]` -->
-<!-- - `r tz_tibble[6,1]`:     `r tz_tibble[6,2]` -->
-<!-- - `r tz_tibble[7,1]`:     `r tz_tibble[7,2]` -->
-<!-- - `r tz_tibble[8,1]`:     `r tz_tibble[8,2]` -->
-<!-- - `r tz_tibble[9,1]`:     `r tz_tibble[9,2]` -->
-<!-- - `r tz_tibble[10,1]`:    `r tz_tibble[10,2]` -->
-<!-- - `r tz_tibble[11,1]`:    `r tz_tibble[11,2]` -->
+- `r tz_tibble[2,1]`:     `r tz_tibble[2,2]`
+- `r tz_tibble[3,1]`:     `r tz_tibble[3,2]`
+- `r tz_tibble[4,1]`:     `r tz_tibble[4,2]`
+- `r tz_tibble[5,1]`:     `r tz_tibble[5,2]`
+- `r tz_tibble[6,1]`:     `r tz_tibble[6,2]`
+- `r tz_tibble[7,1]`:     `r tz_tibble[7,2]`
+- `r tz_tibble[8,1]`:     `r tz_tibble[8,2]`
+- `r tz_tibble[9,1]`:     `r tz_tibble[9,2]`
+- `r tz_tibble[10,1]`:    `r tz_tibble[10,2]`
+- `r tz_tibble[11,1]`:    `r tz_tibble[11,2]`
 

### 2022-01-31 manuscript.Rmd
x and y lab updated

@@
   aes(fill =  "#E64B3599")+
-     scale_fill_identity()
+     scale_fill_identity()+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))
 
@@
   geom_area()+aes(fill =  "#4DBBD599")+theme(legend.position = "none")+
-     scale_fill_identity()
+     scale_fill_identity()+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))
 
@@
   geom_area()+aes(fill =  "#00A08799")+theme(legend.position = "none")+
-     scale_fill_identity()
+     scale_fill_identity()+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))
 
@@
   geom_area()+aes(fill =  "#3C548899")+theme(legend.position = "none")+
-     scale_fill_identity()
+     scale_fill_identity()+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))
 
@@
   labs(y="Test Information", title = "F5:Using light in the morning and during daytime") +ylim(0,8)+geom_area()+aes(fill =  "#B09C8599")+theme(legend.position = "none")+
-scale_fill_identity()
+scale_fill_identity()+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))
 

### 2022-02-01 manuscript.Rmd
correlation range amended
Correlation Matrix with Histogram

@@
 
-min.cor <- apa(min(abs(upper)),2,F) #minimum cor.coefficient of the matrix
-max.cor <- apa(max(abs(upper)),2,F) # max. correlation coefficient of the matrix
+min.cor <- apa(min((upper)),2,F) #minimum cor.coefficient of the matrix
+max.cor <- apa(max((upper)),2,F) # max. correlation coefficient of the matrix
 
@@
 apa_table(landscape =T,caption ="Descriptive Statistics", escape =F, font_size = "footnotesize", note = "*p<.001", align = c("p{1cm}","p{10cm}", rep("p{1cm}", ncol(descriptives2)))) 
+```
+
+```{r correlation-hits, include=F}
+#This chunk holds code for plotting the correlation matrix in histogram format
+
+cor.hits <- as.data.frame(melt(upper))
+colnames(cor.hits) <- c("value")
+corr.histogram <- ggplot(cor.hits,aes(x=value)) + 
+  geom_histogram(binwidth=.1, col=I("black"),fill="#00A08799")+apatheme+
+  labs( y="", x = "Inter-item correlation")
+
+ggsave("Manuscript.figures/correlation_histogram.png", corr.histogram, width = 6, height = 6, dpi = 600, bg ="white")
 ```

### 2022-02-04 manuscript.Rmd
Parallel Analysis is Excluded

@@
 
-```{r ParallelEFA, include=FALSE}
+```{r ParallelEFA, eval=FALSE, include=FALSE}
 #This chunk holds code for factor identification method : Horn
@@
 Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution.
-Horn's parallel analysis [@hornRationaleTestNumber1965] with 500 iterations also indicated a six-factor solution.
 However, the minimum average partial (MAP) method (Table \@ref(tab:factormp)) [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution.
@@
 
-fator <- cowplot::plot_grid(parallel, scree.plot,Hull, 
+fator <- cowplot::plot_grid(scree.plot,Hull, 
                    labels = "AUTO",
@@
 
-(ref:facIdFig) Factor Identification Methods (A) Parallel analysis  indicated the optimal number of factors were six.
-(B) Scree plot suggested six factors.
-(C) Hull method indicated 5 factors were required to balance the model fit and number of parameters.
+(ref:facIdFig) Factor Identification Methods  (A) Scree plot suggested six factors. (B) Hull method indicated 5 factors were required to balance the model fit and number of parameters.
 

### 2022-02-06 manuscript.Rmd
Method: Item Generation $ Item Selection Formalized

@@
 
-  An expert panel prepared the initial 48 item pool.
-Responses, consisting rating the frequency of engaging in the per-item behavior on a 5-point Likert type scale were  collected in an online survey producing responses from an international sample (690 completed responses, 74 countries, 28 time zones).
+  An expert panel prepared the initial 48 item pool spanning different light exposure related behaviors.
+Responses, consisting rating the frequency of engaging in the per-item behavior on a 5-point Likert type scale were  collected in an online survey yielding responses from an international sample (690 completed responses, 74 countries, 28 time zones).
 Exploratory factor analysis (EFA) on an initial subset of our sample (n=428) rendered a five-factor solution with 25 items (Wearing blue light filters, spending time outdoors, using phone and smart-watch in bed, using light before bedtime, using light in the morning and during daytime).
@@
 
-## Item Generation
-
-To ensure construct adequacy we thoroughly assessed the current status of literature and identified a variety of light exposure related scales.
-However, no scales specifically measuring the behavioural component of light exposure were found (see Table \@ref(tab:reltab2)).
-Consequentially we pursued to introduce a new openly available scale to address this research gap.
-For this purpose, an expert researcher panel from the fields of chronobiology, light research, neuroscience, and psychology – comprising all authors of the present manuscript – generated and collected preliminary item ideas.
-Special attention was paid to design items circumscribed to assess light exposure *behaviour* as opposed to subjective measurements of the light environment [@eklund1996development; @dianat2013objective]) and semi-quantitative assessments of light sources' illuminance [@bajaj2011validation] in order to maintain content validity.
-In a collective effort the generated items were then peer-reviewed, amended, unified, and complemented with a suitable response scale (5-point Likert-scale ranging from 1 "Never/Does not apply/I don’t know" to 5 "Always").
-This process was finalized when all experts were in agreement, resulting in 48 items to implement in the data collection.
-
-## Survey characteristics
+## Data Collection
 
@@
 ```
+
+## Item Construction & Item Selection
+
+After reviewing the literature, we identified several light exposure related scale.
+However, no scales specifically measuring the behavioural component of light exposure were found.
+As such ,we developed a comprehensive item pool of 48 items with six point Likert response scale.The whole list of 48 items were then judged  based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by an expert panel.
+The expert panel composed of all authors and researchers from the fields of chronobiology, light research, neuroscience and psychology.
+The panel members independently judged each of the items in terms of their relevance and representativeness and suggested required modification, if there is any.
+The author team acknowledged the auggestions and amended the items as required thus creating a 48-item scale
 
@@
   #geom_point(data = PA.Scree, size=3)+
-  scale_y_continuous(name="Eigen Value", limits=c(0, 7), breaks=seq(0,7,1)) +
+  scale_y_continuous(name="Eigen Value", limits=c(0, 5), breaks=seq(0,5,1)) +
   scale_x_continuous(name='Factor Number (Scree Plot)', limits=c(0, 20),breaks=seq(0,20,4))+
@@
 
-fator2 <- cowplot::plot_grid(parallel, scree.plot,Hull, 
+fator2 <- cowplot::plot_grid(scree.plot,Hull, 
                    labels = "AUTO",
@@
 We used  structural equation modeling framework to assess the measurement invariance of our developed tool across two groups: **native English speakers**(n= `r mi.count[1,2]`) and **non-native English speakers** (n = `r mi.count[2,2]`).
-For a detailed description these two groups please see Sup.
+For a detailed description these two groups see Sup.
 Table \@ref(tab:midesp).

### 2022-02-06 manuscript.Rmd
Analytic Stretegy point by point: EFA+CFA+MI

@@
 However, no scales specifically measuring the behavioural component of light exposure were found.
-As such ,we developed a comprehensive item pool of 48 items with six point Likert response scale.The whole list of 48 items were then judged  based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by an expert panel.
+As such ,we developed a comprehensive item pool of 48 items with six point Likert response scale (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always).The whole list of 48 items were then judged  based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by an expert panel.
 The expert panel composed of all authors and researchers from the fields of chronobiology, light research, neuroscience and psychology.
@@
 As such we decided to collapse them into one, making it a 5 point Likert type response format.
-Necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
+We conducted an initial item analysis and proceed to the EFA.
+Prior to the EFA,necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
 Our data violated both the univariate and multivariate normality assumptions.
@@
 The obtained latent structure was confirmed by another factor extraction method: "the minimum residuals extraction" as well.
-We used a combination of factor identification method including scree plot [@cattellScreeTestNumber1966], Horn's parallel analysis [@hornRationaleTestNumber1965], minimum average partials method [@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
-Additionally, to determine the simple structure, we followed the guidelines recommended by psychometricians: (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading greater than .3 across factors [@bandalosFactorAnalysisExploratory2018].
-We confirmed the latent structure obtained in the EFA by conducting a categorical "Confirmatory Factor Analysis" (CFA) using "robust weighted least square estimator" (WLSMV).
-We estiablished the measurement invariance of our tool across the native and non-native English speakers using structural equation model framework.
-To assess the possible semantic overlap of our tool with the existing tools, we sought to "Semantic Scale Network" [@rosenbusch2020semantic].To assess the possible semantic overlap of our tool with the existing tools, we sought to "Semantic Scale Network" [@rosenbusch2020semantic].
+We used a combination of factor identification method including scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
+Additionally, to determine the simple structure, we followed the common guidelines : (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading > .3 across factors [@bandalosFactorAnalysisExploratory2018].
+We also conducted a EFA on non-merged response options data (Supp.
+Table \@ref(tab:efaunmerged)) and rejected the latent structure obtained as the factors were less interpretable.
+
+For estimating reliability we used internal consistency reliability coefficient ordianl alpha.
+Though  Cronbach's alpha coefficient is widely used for estimating internal consistency, it has a tendency to deflate the estimates for  Likert type data since calculation is based on pearson-correlation matrix which requires response data to be continuous of nature [@gadermann2012estimating; @zumbo2007ordinal].
+Subsequently to get  better estimates of reliability  we reported ordinal alpha that used polychoric-correlation matrix and assumed that the responses data were ordered in nature instead of continuous [@zumbo2007ordinal].
+Ordinal alpha coefficient value ranges from 0 to 1 and higher value represents better reliability.
+
+We conducted categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator since our response data was of ordinary nature [@desjardinsHandbookEducationalMeasurement2018].
+We assessed the model fit using common model fit guidelines: (i) Reporting of $\chi^2$ test statistics (A non-significant test statistics is required to reflect model fit) (ii) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (iii) RMSEA (close to .06 or below), (iv) SRMR (close to .08 or below) to estimate the model fit [@huCutoffCriteriaFit1999; @schumacker2004beginner].However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015] and SRMR does not work well with ordinal data [@RN1272] As such, we judged the model fit using  CFI, TLI, SRMR and RMSEA.
+
+With the validated latent structure obtained by CFA analysis we assessed the measurement invariance of our construct between native English speakers and non-non native English speakers.
+Measurement invariance (MI) evaluates whether a construct has the psychometric equivalence and same meaning across groups or measurement occasions [@putnick2016measurement;@klinePrinciplesPracticeStructural2015].
+We used  structural equation modelling framework to assess the measurement invariance.
+We successively compared four nested models:  configural, metric, scalar, and residual models using the $\chi^2$ difference test ($\Delta \chi^2$).
+Here configural model is the least restrictive model and residual model is the most restrictive model.
+A non-significant $\Delta \chi^2$ test between two nested measurement invariance models indicates mode fit does not significantly decrease for the superior model [@dimitrov2010testing] thus allowing the superior invariance model to be accepted.
+[@widaman1997exploring].
+
+We also analysed possible semantic overlap of our developed tool using "Semantic Scale Network" enginee [@rosenbusch2020semantic].
 Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA.
-We also conducted psychometric analysis on non-merged response options data (Supp. Table \@ref(tab:efaunmerged)) and rejected the latent structure obtained as the factors were less interpretable.
+
+```{r, MI. include =F}
+# Among these nested models  configural model is the first and least restrictive model.
+The configural model assumes that the number of factors and item number under each factor will be equal across two groups.
+The metric invariance model assumes configural invariance of the fitted model and requires the factor-loadings of the items across the two groups to be equal.
+Having the factor-loadings equal across groups indicates each item contributes to the measured construct equivalently.
+Scalar invariance assumes the metric invariance of the fitted model demands the item intercepts to be equivalent across groups.
+This equity of item intercepts indicates the equivalence of response scale across the groups, i.e., persons with the same level of the underlying construct will score the same across the groups.
+The residual invariance model assumes metric invariance for the fitted model and adds the assumption of equality in error variances and covariances across the groups.
+This model is the highest level of MI and assures the equivalence of precision of items across the groups in measuring the underlying constructs.
+We assessed the invariance model fit  using the fit by following the aforementioned guidelines of modelfit.
+The comparison among the MI models was made using
+```
 
@@
 However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (Sup.Table \@ref(tab:sixFacTab)).
-Internal consistency reliability coefficient Cronbach's alpha assumes all the factor-loadings of the items under a factor are equal [@graham2006congeneric; @novick1967coefficient] which is not the case in our sample.
-Additionally Cronbach's alpha coefficient has a tendency to deflate the estimates for  Likert type data as the calculation is based on pearson-correlation matrix which requires that response data should be in continuous of nature [@gadermann2012estimating; @zumbo2007ordinal].
-Subsequently to get  better estimates of reliability we reported ordinal alpha which used polychoric-correlation matrix and assumed that the responses data were ordered in nature instead of continuous [@zumbo2007ordinal].
-Ordinal alpha coefficient value ranges from 0 to 1 and higher value represents better reliability.
+
 In the five-factor solution, the first factor contained three items and explained `r apa(var1,2,F)`% of the total variance with a  internal reliability coefficient ordinal $\alpha$ = `r apa(F1.alpha,2,F)`.
@@
 
-We conducted categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator since our response data was of ordinary nature [@desjardinsHandbookEducationalMeasurement2018].
-Several indices are suggested to measure model fit which can be categorized as absolute, comparative and parsimony fit indices [@brownConfirmatoryFactorAnalysis2015].
-Absolute fit assess the model fit at an absolute level using indices including $\chi^2$ test statistics and the standardized root mean square (SRMR).
-Parsimony fit indices including the root mean square error of approximation (RMSEA) considers the number of free parameters in the model to assesses the parsimony of the model.
-Comparative fit indices evaluate the fit of the specified model solution in relation to a more restricted baseline model restricting all covariances among the indicators as zero.
-Comparative fit index (CFI) and the Tucker Lewis index (TLI) are such two comparative fit indices.
-Commonly used Model fit guidelines [@huCutoffCriteriaFit1999; @schumacker2004beginner] includes (i) Reporting of $\chi^2$ test statistics (A non-significant test statistics is required to reflect model fit) (ii) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (iii) RMSEA (close to .06 or below), (iv) SRMR (close to .08 or below) to estimate the model fit.
-Table \@ref(tab:tabCfa) summarizes the fit indices of our fitted model.
-Our fitted model failed to attain an absolute fit estimated by the $\chi^2$ test.
-However, the $\chi^2$ test is sensitive to sample size and not recommended to be used as the sole index of absolute model fit [@brownConfirmatoryFactorAnalysis2015].
-Another absolute fit index we obtained in our analysis was SRMR which does not work well with categorical data [@RN1272].
-We judged the model fit based on the comparative fit indices: CFI, TLI and parsimony fit index:RMSEA.
+Table \@ref(tab:tabCfa) summarizes the CFA fit indices of our fitted model.
 Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`,[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 [`r Hmisc::label(sem.data$item32)`;`r Hmisc::label(sem.data$item33)`] and 16-17 [`r Hmisc::label(sem.data$item16)`;`r Hmisc::label(sem.data$item17)`].
@@
 
-Measurement invariance (MI) evaluates whether a construct has the psychometric equivalence and same meaning across groups or measurement occasions [@putnick2016measurement;@klinePrinciplesPracticeStructural2015].
-We used  structural equation modeling framework to assess the measurement invariance of our developed tool across two groups: **native English speakers**(n= `r mi.count[1,2]`) and **non-native English speakers** (n = `r mi.count[2,2]`).
-For a detailed description these two groups see Sup.
-Table \@ref(tab:midesp).
-Our measurement invariance testing involved successively comparing the nested models:  configural, metric, scalar, and residual invariance models with each others [@widaman1997exploring].
-Among these nested models  configural model is the first and least restrictive model.
-The configural model assumes that the number of factors and item number under each factor will be equal across two groups.
-The metric invariance model assumes configural invariance of the fitted model and requires the factor-loadings of the items across the two groups to be equal.
-Having the factor-loadings equal across groups indicates each item contributes to the measured construct equivalently.
-Scalar invariance assumes the metric invariance of the fitted model demands the item intercepts to be equivalent across groups.
-This equity of item intercepts indicates the equivalence of response scale across the groups, i.e., persons with the same level of the underlying construct will score the same across the groups.
-The residual invariance model assumes metric invariance for the fitted model and adds the assumption of equality in error variances and covariances across the groups.
-This model is the highest level of MI and assures the equivalence of precision of items across the groups in measuring the underlying constructs.
-The invariance model fit of our tool was assessed using the fit indices including $\chi^2$ test, CFI and TLI (close to .95 or above), RMSEA (close to .06 or below) [@huCutoffCriteriaFit1999].
-We excluded SRMR from our consideration as it does not behave optimally for categorical variables [@RN1272].
-Table \@ref(tab:InvarianceTab) summarized the fit indices.
-The comparison among different measurement invariance models was made using the $\chi^2$ difference test ($\Delta \chi^2$)  to assess whether our obtained latent structure of "LEBA" attained the highest level of the MI.
-A non-significant $\Delta \chi^2$ test between two MI models fit indicates mode fit does not significantly decrease for the superior model [@dimitrov2010testing] thus allowing the superior level of invariance model to be accepted.
-We started our analysis by comparing the model fit of the least restrictive model:configural model to metric MI model and continued successive comparisons.
-Table \@ref(tab:InvarianceTab) indicates that our fitted model had acceptable fit indices for all of the fitted MI models.
-The model fit did not significantly decrease across the nested models up to the scalar MI model.
-The chi-square value difference between the scalar and residual model is zero, indicating model fit remained the same for both: scalar and residual MI model, indicating the acceptability of the residual MI model.
+In our CFA sample we had `r mi.count[1,2]`  **native English speakers** and `r mi.count[2,2]` **non-native English speakers**  (For a detailed description these two groups see Sup.
+Table \@ref(tab:midesp)).
+Table \@ref(tab:InvarianceTab) indicates our fitted model had acceptable fit indices for all of the fitted MI models.
+The model fit did not significantly decrease across the nested models indicating the acceptability of the higheest measurement invariance model : residualmodel.
 

### 2022-02-06 manuscript.Rmd
Analysis strategy: point by point: Semantics

@@
 
-We also analysed possible semantic overlap of our developed tool using "Semantic Scale Network" enginee [@rosenbusch2020semantic].
+We also analysed possible semantic overlap of our developed tool using "Semantic Scale Network" (SSN) engine [@rosenbusch2020semantic].
+The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic].
+Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy.
+Additionally, To identify the educational grade level required to understand the items in our tool we subjected tool to Flesch-Kincaid Grade Level [@flesch1948new]
+
 Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA.

### 2022-02-06 manuscript.Rmd
Analystic Strategy- point by point: IRT

@@
 Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA.
+We fitted each factor of LEBA using the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690).
+IRT assess the item quality by estimatingitem difficulty, item discrimination, a item information, and Test information [@bakerBasicsItemResponse2017].
+Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait level ($\theta$), and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
+Here, we reported  the item discrimination parameter and categorize the items according to the suggestions of @bakerBasicsItemResponse2017 : none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70.
+We discarded the items with relatively flat item information curve (information <.2) to develop the short form of LEBA.
+We also assessed the precision of the short LEBA using Test information curve (TIC).
+TIC  indicates the amount of information an the full-scale carry along the latent trait continuum.
+Item fit and person-fit of the fitted model were also analyzed to gather more evidence on validity and meaningfulness of our Tool [@desjardinsHandbookEducationalMeasurement2018].
+Item-fit was evaluated using  the RMSEA value obtained from Signed-$\chi^2$ index implementation, RMSEA value $\le$.06 was consided adequate item fit.
+Person fit was estimated using standardized fit index Zh statistics [@drasgow1985appropriateness].
+Zh < -2 was be considered as a misfit [@drasgow1985appropriateness].
 

### 2022-02-06 manuscript.Rmd
Typo

@@
 Our data violated both univariate normality (Shapiro-Wilk statistics; [@shapiroAnalysisVarianceTest1965]) and multivariate normality assumptions [Marida's test;[@mardiaMeasuresMultivariateSkewness1970]].
-Multivariate skew was = `r printnum(mardia$b1p)` (p <0.001) and multivariate kurtosis was = `r printnum(mardia$b2p)` (p <0.001).
+Multivariate skew was  `r printnum(mardia$b1p)` (p <0.001) and multivariate kurtosis was `r printnum(mardia$b2p)` (p <0.001).
 Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018].
@@
 ```
+
 Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution.
-However, the minimum average partial (MAP) method (Table \@ref(tab:factormp)) [@velicerDeterminingNumberComponents1976] and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution.
+However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (Table \@ref(tab:factormp)) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution.
 As a result, we tested both five-factor and six-factor solutions.

### 2022-02-06 manuscript.Rmd
Knitting Version

@@
 Item fit and person-fit of the fitted model were also analyzed to gather more evidence on validity and meaningfulness of our Tool [@desjardinsHandbookEducationalMeasurement2018].
-Item-fit was evaluated using  the RMSEA value obtained from Signed-$\chi^2$ index implementation, RMSEA value $\le$.06 was consided adequate item fit.
+Item-fit was evaluated using  the RMSEA value obtained from Signed-$\chi^2$ index implementation, RMSEA value $\le$.06 was considered adequate item fit.
 Person fit was estimated using standardized fit index Zh statistics [@drasgow1985appropriateness].
@@
 
-```{r, MI. include =F}
+```{r, MIdescription, include =F}
 # Among these nested models  configural model is the first and least restrictive model.
@@
 ```
+
+```{r echo = FALSE, results = 'asis', cache = FALSE}
+papaja::render_appendix('appendix-1.Rmd')
+```

### 2022-02-06 manuscript.Rmd
Manuscript Restuctured: Now has a better flow. Flowchart updated

@@
 
-## Data Collection
-
-Data was collected in a quantitative cross-sectional approach via a fully anonymous online survey hosted on REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
-Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) of a Comic co-released with the survey[@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux].
-Completing the online survey took approx.
-15 to 20 minutes and was not compensated.
-The first page of the survey comprised a participant information sheet, where participants' informed consent to participate was obtained before any of the questions were displayed.
-Underaged participants (<18 years) were urged to obtain assent from their parents/legal guardians, before filling in the survey.
-Information on the first page included the objectives of the study, inclusion criteria, estimated duration, the use, storage and sharing of the data, compensation (none), and information about the type of questions in the survey.
-Moreover, participants needed to confirm that they were participating the survey for the first time.
-To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention.
-What is 4+5?").
-The data analysed in this study was collected between 17 May 2021 and 3 September 2021.
-Questions incorporating retrospective recall were all aligned to the period of "past four weeks", matching the presented LEBA instrument.
-
-In addition to the LEBA questionnaire, which is subject of the current study, we assessed other variables and items which were not included in the present analysis.
+```{r rafel, include=F}
+# In addition to the LEBA questionnaire, which is subject of the current study, we assessed other variables and items which were not included in the present analysis.
 This comprised various sleep-related measures, i.e., sleep disturbances and sleep-related impairment (adult and pediatric versions) [@Bevans.2019; @Buysse.2010; @Forrest.2018; @Harb.2015; @Yu.2011], sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration [MCTQ version for adults and adolescents @roenneberg2003life] plus sleep environment [@Olivier.2016].
@@
 
-Finally, we assessed age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language as single-item demographic variables.
-The demographic characteristics of our sample are given in Table \@ref(tab:demotab).
+```
 
@@
 
-                    A[label = '48 items were generated'] 
-                    B[label = 'Exploratory Factor Analysis on 48 Items (n = 428)']
+                    A[label = 'Initial Development of 48 Items'] 
+                    B[label = 'Large Scale Survey (n=690)']
+                    C[label = 'Initial Item Analysis']
+                    D[label = 'Exploratory Factor Analysis (48 items; n=428)']
 
@@
                     fixedsize = true, fontsize = 45]
-                    C[label = 
-                    <Factor Identification<br/>Scree Plot: 6 Factors<br/>Parallel Analysis: 6 Factors<br/>Minimum Average Partial Method: 5 Factors<br/>Hull Method: 5 Factors>
+                    E[label = 
+                    <Factor Identification<br/>Scree Plot: 6 Factors<br/>Minimum Average Partial Method: 5 Factors<br/>Hull Method: 5 Factors>
                     ]
@@
                      5[label = <Reliability Analysis (23 Items; n=262)<br/>Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52<br/>Mcdonald  omega(total) for the total scale = .73>]
-                    8[label = <Measurement Invariance Analysis<br/>Residual measurement invariance achieved>]
-                    9[label = 'Semantic Analysis']
-                    10[label = <LEBA Short Form (18 Items; n=690)<br/>Based on Item Response Theory>]
+                    8[label = <Measurement Invariance Analysis (n=262)<br/>Residual measurement invariance achieved>]
+                    9[label = <Semantic Analysis (n=262):<br/>Semantic Scale Network analysis<br/>Readbility: Grade level 3.33>]
+                    10[label = <LEBA Short Form (19 Items; n=690)<br/>Based on Item Response Theory>]
                     }
@@
                      B ->C
-                     C ->1
+                     C ->D
+                     D ->E
+                E ->1
                      1 ->2
@@
                     9 ->10
-                     C ->6
+                     E ->6
                      6 ->7
@@
 
-## Item Construction & Item Selection
-
-After reviewing the literature, we identified several light exposure related scale.
-However, no scales specifically measuring the behavioural component of light exposure were found.
-As such ,we developed a comprehensive item pool of 48 items with six point Likert response scale (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always).The whole list of 48 items were then judged  based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by an expert panel.
-The expert panel composed of all authors and researchers from the fields of chronobiology, light research, neuroscience and psychology.
-The panel members independently judged each of the items in terms of their relevance and representativeness and suggested required modification, if there is any.
-The author team acknowledged the auggestions and amended the items as required thus creating a 48-item scale
+## Data Collection
+
+A quantitative cross-sectional fully anonymous online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
+Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) of a Comic co-released with the survey[@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux].
+The landing page of the on-line survey had the explanatory statements It was mentioned in the explanatory statement that their participation was voluntary and that they could withdraw from participation anytime without being penalized.
+At the beginning of the survey, for the adult participants (>18 years) consent was recorded digitally.
+Underaged participants (<18 years) were urged to obtain assent from their parents/legal guardians, before filling in the survey.
+The survey took around 15 to 20 minutes for which they were not compensated.
+As a part of the demographics participants provided information regarding age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language as single-item demographic variables.
+The demographic characteristics of our sample are given in Table \@ref(tab:demotab).To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention.
+What is 4+5?").
+Participants needed to confirm that they were participating the survey for the first time.
+Questions incorporating retrospective recall were all aligned to the period of "past four weeks". The data analysed in this study was collected between 17 May 2021 and 3 September 2021. 
+```{r demotab, warning=F, message=F}
+desc_kable  %>% kable_styling(latex_options = c("scale_down")) %>% landscape()
+```
 
@@
 In our analysis we used R (version 4.1.0), with several R packages.
-Initially, our tool had six point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always).
-Our purpose was to capture light exposure related behavior and these two response options: "Does not apply/I don't know" and "Never" were providing similar information.
+In the item generation and selection phase we had developed a item pool of 48 items with six-pont Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always).
+Our purpose was to capture light exposure related behaviour and the first two response options: "Does not apply/I don't know" and "Never" were providing similar information.
 As such we decided to collapse them into one, making it a 5 point Likert type response format.
-We conducted an initial item analysis and proceed to the EFA.
-Prior to the EFA,necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
+We conducted an initial item analysis and proceed to the EFA with all 48 items.
+Prior to the EFA, necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
 Our data violated both the univariate and multivariate normality assumptions.
@@
 Though  Cronbach's alpha coefficient is widely used for estimating internal consistency, it has a tendency to deflate the estimates for  Likert type data since calculation is based on pearson-correlation matrix which requires response data to be continuous of nature [@gadermann2012estimating; @zumbo2007ordinal].
-Subsequently to get  better estimates of reliability  we reported ordinal alpha that used polychoric-correlation matrix and assumed that the responses data were ordered in nature instead of continuous [@zumbo2007ordinal].
-Ordinal alpha coefficient value ranges from 0 to 1 and higher value represents better reliability.
+Subsequently to get  better estimates of reliability  we reported ordinal alpha for each factors that used polychoric-correlation matrix and assumed that the responses data were ordered in nature instead of continuous [@zumbo2007ordinal].
+We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$  coefficient which is a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
+Both ordinal alpha and McDonald's $\omega_t$   coefficient value range from 0 to 1 and higher value represents better reliability.
 
@@
 
-```{r, MIdescription, include =F}
-# Among these nested models  configural model is the first and least restrictive model.
-The configural model assumes that the number of factors and item number under each factor will be equal across two groups.
-The metric invariance model assumes configural invariance of the fitted model and requires the factor-loadings of the items across the two groups to be equal.
-Having the factor-loadings equal across groups indicates each item contributes to the measured construct equivalently.
-Scalar invariance assumes the metric invariance of the fitted model demands the item intercepts to be equivalent across groups.
-This equity of item intercepts indicates the equivalence of response scale across the groups, i.e., persons with the same level of the underlying construct will score the same across the groups.
-The residual invariance model assumes metric invariance for the fitted model and adds the assumption of equality in error variances and covariances across the groups.
-This model is the highest level of MI and assures the equivalence of precision of items across the groups in measuring the underlying constructs.
-We assessed the invariance model fit  using the fit by following the aforementioned guidelines of modelfit.
-The comparison among the MI models was made using
-```
-
 ```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='100%', out.width='100%'}
@@
 
-## Participants
-
-```{r demotab, warning=F, message=F}
-desc_kable  %>% kable_styling(latex_options = c("scale_down")) %>% landscape()
-```
+## Initial development of items
+
+After reviewing the literature, we identified several light exposure related scale.
+However, no scales specifically measuring the behavioural component of light exposure were found.
+As such ,we developed a comprehensive item pool of 48 items with six point Likert response scale (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always).The whole list of 48 items were then judged  based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by an expert panel.
+The expert panel composed of all authors and researchers from the fields of chronobiology, light research, neuroscience and psychology.
+The panel members independently judged each of the items in terms of their relevance and representativeness and suggested required modification, if there is any.
+The author team acknowledged the auggestions and amended the items as required thus creating a 48-item scale
+
+## Large-scale  survey of instruments
+
+### Participants
 
@@
 Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses.
-XX participants were excluded from analysis due to not passing at least one of the "attention check" items.
+(XX??) participants were excluded from analysis due to not passing at least one of the "attention check" items.
 For exploring initial factor structure (EFA), a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013].
@@
 
-## Item Analysis
+### Item Analysis
 
@@
 
-## Exploratory Factor Analysis
+### Exploratory Factor Analysis
+
 ```{r CorrMatrix, include=FALSE}
@@
 Figure \@ref(fig:figCor) depicts the correlation matrix.
+
 ```{r tabDes,results='asis'}
@@
 As a result, we tested both five-factor and six-factor solutions.
+
 ```{r factors, include=F}
@@
 ```
-## Confirmatory Factor Analysis
+
+### Confirmatory Factor Analysis
 
@@
 Internal consistency ordinal $\alpha$ for the five factors of LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)` respectively.
-We also estimated the internal consistency reliability of the total scale using Mcdonald's $\omega_t$  coefficient which is a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
-McDonald's $\omega_t$ coefficient for the total scale was `r apa(rel.k[5,6],2,F)`.
+Internal consistency McDonald's $\omega_t$ coefficient for the total scale was `r apa(rel.k[5,6],2,F)`.
 Figure \@ref(fig:figcfa) depicts the obtained CFA structure.
@@
 
-## Measurement Invariance
+### Measurement Invariance
+
 ```{r InvarianceAnalysis_data, include=FALSE}
@@
 In our CFA sample we had `r mi.count[1,2]`  **native English speakers** and `r mi.count[2,2]` **non-native English speakers**  (For a detailed description these two groups see Sup.
-Table \@ref(tab:midesp)).
+Table \@ref(tab:midesp) ).
 Table \@ref(tab:InvarianceTab) indicates our fitted model had acceptable fit indices for all of the fitted MI models.
-The model fit did not significantly decrease across the nested models indicating the acceptability of the higheest measurement invariance model : residualmodel.
+The model fit did not significantly decrease across the nested models indicating the acceptability of the highest measurement invariance model : residual model.
 
@@
 
-## Semantic Analysis 
-To find out if our developed tool (23 items) is overlapping with existing instruments, we subjected the items of LEBA to the "Semantic Scale Network"(SSN) analysis [@rosenbusch2020semantic].
-The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic].
-Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy.
-LEBA  appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990].The cosine similarities lie between .47 to .51.
+### Semantic Analysis
+
+"Semantic Scale Network"(SSN) analysis [@rosenbusch2020semantic] indicated that LEBA (23 items)  appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990].The cosine similarities lie between .47 to .51.
 Flesch-Kincaid Grade Level [@flesch1948new] analysis on the the 23 items of our scale indicated required educational grade level was 3.33 and with a age above 8.33.
-```{r textanalysis}
+
+```{r textanalysis, include=F}
 #This chunk holds codes for semantic analysis and readability test
@@
 
-## Developing Short form of LEBA
-We sought the Item Response Theory (IRT) to develop the short form of LEBA.
-IRT the conventional classical test theory-based analysis by gathering information on item quality by indices like item difficulty, item discrimination, and item information [@bakerBasicsItemResponse2017].
-Item is  judged based on item information in relation to participants' latent trait level ($\theta$).
+### Developing Short form of LEBA
+
 We fitted each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690).
-Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait level ($\theta$), and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
-Here, we reported the item discrimination parameter and only discarded the items with relatively flat item information curve (information <.2) to develop the short form of LEBA.
-@bakerBasicsItemResponse2017 categorized the item discrimination in as none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70.
-Table \@ref(tab:IRTparameters) summarizes the IRT parameters of our tool.
 Item discrimination parameters of our tool fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$).
@@
 
-```{r factorinfo, eval=FALSE, include=FALSE}
-#This chunk holds codes for item info plots clustered in factors (Not included in the manuscript)
-F1.itemplots <- cowplot::plot_grid(F1.iteminfo.1,F1.iteminfo.2, F1.iteminfo.3,
-                   labels = "AUTO",
-                     align="v",
-                     ncol = 2,
-                     label_size = 12,
-                     label_fontfamily = "Arial",
-  label_fontface = "plain")
-ggsave("Manuscript.figures/F1.itemplots.png",F1.itemplots, width = 10, height = 12, dpi = 600,bg = "white")
-
-F2.itemplots <- cowplot::plot_grid(F2.iteminfo.1,F2.iteminfo.2, F2.iteminfo.3,
-                                   F2.iteminfo.4,F2.iteminfo.5,F2.iteminfo.6,
-                   labels = "AUTO",
-                     align="v",
-                     ncol = 2,
-                     label_size = 12,
-                     label_fontfamily = "Arial",
-                     label_fontface = "plain")
-ggsave("Manuscript.figures/F2.itemplots.png",F2.itemplots, width = 10, height = 12, dpi = 600, bg = "white")
-
-F3.itemplots <- cowplot::plot_grid(F3.iteminfo.1,F3.iteminfo.2, F3.iteminfo.3,
-                                   F3.iteminfo.4,F3.iteminfo.5,
-                 labels = "AUTO",
-                     align="v",
-                     ncol = 2,
-                     label_size = 12,
-                     label_fontfamily = "Arial",
-                     label_fontface = "plain")
-ggsave("Manuscript.figures/F3.itemplots.png",F3.itemplots, width = 10, height = 12, dpi = 600,bg = "white")
-
-F4.itemplots <- cowplot::plot_grid(F4.iteminfo.1,F4.iteminfo.2, F4.iteminfo.3,
-                                   F4.iteminfo.4,
-                   labels = "AUTO",
-                     align="v",
-                     ncol = 2,
-                     label_size = 12,
-                     label_fontfamily = "Arial",
-                     label_fontface = "plain")
-ggsave("Manuscript.figures/F4.itemplots.png",F4.itemplots, width = 10, height = 12, dpi = 600,bg = "white")
-
-F5.itemplots <- cowplot::plot_grid(F1.iteminfo.1,F1.iteminfo.2, F1.iteminfo.3,
-
-                   labels = "AUTO",
-                     align="v",
-                     ncol = 2,
-                     label_size = 12,
-                     label_fontfamily = "Arial",
-                     label_fontface = "plain")
-ggsave("Manuscript.figures/F5.itemplots.png",F5.itemplots, width = 10, height = 12, dpi = 600, bg = "white")
-
-```
-
-```{r inteminfoggplo2c, eval=FALSE, include=FALSE}
-# This chinks holds code of compiled item info code created using facet wrap. (Not included in manuscript)
-pacman::p_load(reshape,ggsci)
-Theta <- matrix(seq(-6,6, by = .1))
-
-##Item Extraction
-F1.item1 <- extract.item(F1_fit, 1)#item number
-F1.item2 <- extract.item(F1_fit, 2)
-F1.item3 <- extract.item(F1_fit, 3)
-F2.item1 <- extract.item(F2_fit, 1)
-F2.item2 <- extract.item(F2_fit, 2)
-F2.item3 <- extract.item(F2_fit, 3)
-F2.item4 <- extract.item(F2_fit, 4)
-F2.item5 <- extract.item(F2_fit, 5)
-F2.item6 <- extract.item(F2_fit, 6)
-F3.item1 <- extract.item(F3_fit, 1)
-F3.item2 <- extract.item(F3_fit, 2)
-F3.item3 <- extract.item(F3_fit, 3)
-F3.item4 <- extract.item(F3_fit, 4)
-F3.item5 <- extract.item(F3_fit, 5)
-F4.item1 <- extract.item(F4_fit, 1)
-F4.item2 <- extract.item(F4_fit, 2)
-F4.item3 <- extract.item(F4_fit, 3)
-F4.item4 <- extract.item(F4_fit, 4)
-F5.item1 <- extract.item(F5_fit, 1)
-F5.item2 <- extract.item(F5_fit, 2)
-F5.item3 <- extract.item(F5_fit, 3)
-F5.item4 <- extract.item(F5_fit, 4)
-F5.item5 <- extract.item(F5_fit, 5)
-
-##Item Info
-Item16 <- iteminfo(F1.item1, Theta)
-Item36 <- iteminfo(F1.item2, Theta)
-Item17 <- iteminfo(F1.item3, Theta)
-Item11 <- iteminfo(F2.item1, Theta)
-Item10 <- iteminfo(F2.item2, Theta)
-Item12 <- iteminfo(F2.item3, Theta)
-Item07 <- iteminfo(F2.item4, Theta)
-Item08 <- iteminfo(F2.item5, Theta)
-Item09 <- iteminfo(F2.item6, Theta)
-Item27 <- iteminfo(F3.item1, Theta)
-Item03 <- iteminfo(F3.item2, Theta)
-Item40 <- iteminfo(F3.item3, Theta)
-Item30 <- iteminfo(F3.item4, Theta)
-Item41 <- iteminfo(F3.item5, Theta)
-Item32 <- iteminfo(F4.item1, Theta)
-Item35 <- iteminfo(F4.item2, Theta)
-Item38 <- iteminfo(F4.item3, Theta)
-Item33 <- iteminfo(F4.item4, Theta)
-Item46 <- iteminfo(F5.item1, Theta)
-Item45 <- iteminfo(F5.item2, Theta)
-Item25 <- iteminfo(F5.item3, Theta)
-Item04 <- iteminfo(F5.item4, Theta)
-Item01 <- iteminfo(F5.item5, Theta)
-
-#Data frame
-
-F1.item.info.data <- as.data.frame(cbind(Item16, 
-                                              Item36,
-                                              Item17))
-
-F2.item.info.data <- as.data.frame(cbind(Item11, 
-                                              Item10,
-                                              Item12,
-                                         Item07,
-                                         Item08,
-                                         Item09))
-
-F3.item.info.data <- as.data.frame(cbind(Item27, 
-                                              Item03,
-                                              Item40,
-                                         Item30,
-                                        Item41))
-
-F4.item.info.data <- as.data.frame(cbind(Item32, 
-                                              Item35,
-                                              Item38,
-                                         Item33))
-F5.item.info.data <- as.data.frame(cbind(Item46, 
-                                              Item45,
-                                             Item25,
-                                         Item04,
-                                         Item01))
-
-F1.item.info.data.long <- melt(F1.item.info.data)
-F2.item.info.data.long <- melt(F2.item.info.data)
-F3.item.info.data.long <- melt(F3.item.info.data)
-F4.item.info.data.long <- melt(F4.item.info.data)
-F5.item.info.data.long <- melt(F5.item.info.data)
-
-F1.item.info.data.2 <- data.frame(Theta=seq(-6,6, by = .1), F1.item.info.data.long)
-F2.item.info.data.2 <- data.frame(Theta=seq(-6,6, by = .1), F2.item.info.data.long)
-F3.item.info.data.2 <- data.frame(Theta=seq(-6,6, by = .1), F3.item.info.data.long)
-F4.item.info.data.2 <- data.frame(Theta=seq(-6,6, by = .1), F4.item.info.data.long)
-F5.item.info.data.2 <- data.frame(Theta=seq(-6,6, by = .1), F5.item.info.data.long)
-
-pacman::p_load(ggsci)
-
-F1.iic2 <- ggplot(F1.item.info.data.2,aes(Theta,value,col=variable))+geom_line()+apatheme+
-  ggtitle("F1 Item Information Plot")+theme(legend.position = "none")+
-  facet_wrap(~variable,scales = "free")+theme(strip.text.x = element_text(size = 15))+geom_hline(yintercept = .20, colour ="red")+geom_area()+ scale_color_npg()+aes(fill = as.factor(variable))+xlab(expression(theta)) +
-  ylab(expression(I(theta)))
-
-ggsave("Manuscript.figures/F1.itemplots.png",F1.iic2, width = 12, height =8, dpi = 1200, bg ="white")
-
-F2.iic2 <- ggplot(F2.item.info.data.2,aes(Theta,value,col=variable))+geom_line()+apatheme+
-  ggtitle("F2 Item Information Plot")+theme(legend.position = "none")+
-  facet_wrap(~variable,scales = "free")+theme(strip.text.x = element_text(size = 15))+
-  geom_hline(yintercept = .20, colour ="red")+geom_area()+scale_color_npg()+aes(fill = as.factor(variable))+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))
-
-ggsave("Manuscript.figures/F2.itemplots.png",F2.iic2, width = 12, height =8, dpi = 1200, bg ="white")
-
-F3.iic2 <- ggplot(F3.item.info.data.2,aes(Theta,value,col=variable))+geom_line()+apatheme+
-  ggtitle("F3 Item Information Plot")+theme(legend.position = "none")+
-  facet_wrap(~variable,scales = "free")+theme(strip.text.x = element_text(size = 15))+
-  geom_hline(yintercept = .20, colour ="red")+geom_area()+scale_color_npg()+aes(fill = as.factor(variable))+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))
-
-ggsave("Manuscript.figures/F3.itemplots.png",F3.iic2, width = 12, height =8, dpi = 1200, bg ="white")
-
-F4.iic2 <- ggplot(F4.item.info.data.2,aes(Theta,value,col=variable))+geom_line()+apatheme+
-  ggtitle("F4 Item Information Plot")+theme(legend.position = "none")+
-  facet_wrap(~variable,scales = "free")+theme(strip.text.x = element_text(size = 15))+
-  geom_hline(yintercept = .20, colour ="red")+geom_area()+scale_color_npg()+aes(fill = as.factor(variable))+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))
-
-ggsave("Manuscript.figures/F4.itemplots.png",F4.iic2, width = 12, height =8, dpi = 1200, bg ="white")
-
-F5.iic2 <- ggplot(F5.item.info.data.2,aes(Theta,value,col=variable))+geom_line()+apatheme+
-  ggtitle("F5 Item Information Plot")+theme(legend.position = "none")+
-  facet_wrap(~variable,scales = "free")+theme(strip.text.x = element_text(size = 15))+
-  geom_hline(yintercept = .20, colour ="red")+geom_area()+scale_color_npg()+aes(fill = as.factor(variable))+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))
-
-ggsave("Manuscript.figures/F5.itemplots.png",F5.iic2, width = 12, height =8, dpi = 1200, bg ="white")
-
-allicc <- cowplot::plot_grid(F1.iic2, F2.iic2, F3.iic2, F4.iic2, F5.iic2, labels = "AUTO",ncol=2, label_size = 15,align = "h",label_fontfamily = "Arial",
-                  label_fontface = "plain")
-
-ggsave("Manuscript.figures/allicc.png",allicc, width = 12, height =12, dpi = 1200, bg ="white")
-
-##Creating ggplot2 based all item item info using facet wrap
-alldata <- as.data.frame(cbind(Item16,Item36,Item17,Item11,Item10, Item12,Item07,Item08,Item09,Item27,Item03, Item40, Item30, Item41, Item32, Item35, Item38, Item33, Item46, Item45, Item25, Item04, Item01))
-
-all.data.long <- melt(alldata)
-alldata2 <- data.frame(Theta=seq(-6,6, by = .1), all.data.long )
-
-allicc3 <- ggplot(alldata2,aes(Theta,value,col=variable))+geom_line()+apatheme+
-  ggtitle("Item Information Plot")+theme(legend.position = "none")+
-  facet_wrap(~variable,scales = "free")+theme(strip.text.x = element_text(size = 15))+
-  geom_hline(yintercept = .20, colour ="red")+geom_area()+scale_color_npg()+aes(fill = as.factor(variable))+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))
-
-ggsave("Manuscript.figures/allicc2.png",allicc3, width = 12, height =12, dpi = 1200, bg ="white")
-
-```
-
 ```{r IRTparameters, results='asis'}
@@
 
-Test information curve (TIC) (Figure \@ref(fig:Testinfo)) indicate the amount of information an the full-scale carry along the latent trait continuum.
-As we treated each factor of short-LEBA as an unidmensional construct we obtain 5 TICs (Figure \@ref(fig:Testinfo)).
+We treated each factor of short-LEBA as an unidmensional construct and obtain 5 TICs (Figure \@ref(fig:Testinfo)).
 These information curves indicated except the first and fifth factors, the other three factor's TICs are roughly centered on the center of the trait continuum ($\theta$).The first and fifth factor had a peak to the right side of the center of latent trait.Thus we conferred the LEBA tool estimated the light exposure related behavior with precision near the center of trait continuum for 2nd, 3rd and 4th factors and near the right side of the center of trait continuum for 1st and 5th factors [@bakerBasicsItemResponse2017].
@@
 Table \@ref(tab:itemfittab) summarizes the item fit indexes of the items.
-All the items fitted well to the respective models as assessed by  RMSEA value obtained from Signed-$\chi^2$ index implementation.
 All of the items had RMSEA value $\le$.06 indicating adequate fit.
-Sup.Figure \@ref(fig:personfit) depicts the person fit of out fitted models.
-Person fit indicates the validity and meaningfulness of the fitted model at the participants latent trait level [@desjardinsHandbookEducationalMeasurement2018].
-We estimated the person fit statistics using standardized fit index Zh statistics [@drasgow1985appropriateness].
-Zh < -2 should be considered as a misfit.
-Fig indicates that Zh is larger than -2 for most participants, suggesting a good fit of the selected IRT models.
+Sup.Figure \@ref(fig:personfit) depicts the person fit of out fitted models.Fig indicates the person fit Zh statistics histogram.
+Zh statistics are larger than -2 for most participants, suggesting a good fit of the selected IRT models.
 
@@
 
-```
-
-```{r scalechar, eval=FALSE, fig.cap="Scale characteristic curve of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, include=FALSE, out.height="120%", out.width="100%"}
-#not used in the manuscript
-
-#Finally we generated scale characteristics curve (Figure \@ref(fig:scalechar)) which plotted estimated theta score against the expected true score.
-The purpose of this scale characteristics curve is to find the corresponding expected true score for the given estimated theta score of the participants.
-
-plot_grid(F1.scale, F1.scale,F1.scale,F1.scale,F1.scale, 
-          labels = "AUTO", label_size = 10,align = "v")
 ```
@@
 
-Lastly, we developed a short-LEBA (n=23) using IRT analysis.
+Lastly, we developed a short-LEBA (n=19) using IRT analysis.
 We fitted a graded response model model to the combined EFA and CFA sample (n =`r nrow(data)`).
@@
 ```
-
-```{r echo = FALSE, results = 'asis', cache = FALSE}
-papaja::render_appendix('appendix-1.Rmd')
-```

### 2022-02-06 irt_plot_extra.Rmd
xtra code separated: to be deleted later

---
title: "Irt plot extra"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
```{r factorinfo, eval=FALSE, include=FALSE}
#This chunk holds codes for item info plots clustered in factors (Not included in the manuscript)
F1.itemplots <- cowplot::plot_grid(F1.iteminfo.1,F1.iteminfo.2, F1.iteminfo.3,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "Arial",
  label_fontface = "plain")
ggsave("Manuscript.figures/F1.itemplots.png",F1.itemplots, width = 10, height = 12, dpi = 600,bg = "white")

F2.itemplots <- cowplot::plot_grid(F2.iteminfo.1,F2.iteminfo.2, F2.iteminfo.3,
                                   F2.iteminfo.4,F2.iteminfo.5,F2.iteminfo.6,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F2.itemplots.png",F2.itemplots, width = 10, height = 12, dpi = 600, bg = "white")

F3.itemplots <- cowplot::plot_grid(F3.iteminfo.1,F3.iteminfo.2, F3.iteminfo.3,
                                   F3.iteminfo.4,F3.iteminfo.5,
                 labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F3.itemplots.png",F3.itemplots, width = 10, height = 12, dpi = 600,bg = "white")

F4.itemplots <- cowplot::plot_grid(F4.iteminfo.1,F4.iteminfo.2, F4.iteminfo.3,
                                   F4.iteminfo.4,
                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F4.itemplots.png",F4.itemplots, width = 10, height = 12, dpi = 600,bg = "white")

F5.itemplots <- cowplot::plot_grid(F1.iteminfo.1,F1.iteminfo.2, F1.iteminfo.3,

                   labels = "AUTO",
                     align="v",
                     ncol = 2,
                     label_size = 12,
                     label_fontfamily = "Arial",
                     label_fontface = "plain")
ggsave("Manuscript.figures/F5.itemplots.png",F5.itemplots, width = 10, height = 12, dpi = 600, bg = "white")

```

```{r inteminfoggplo2c, eval=FALSE, include=FALSE}
# This chinks holds code of compiled item info code created using facet wrap. (Not included in manuscript)
pacman::p_load(reshape,ggsci)
Theta <- matrix(seq(-6,6, by = .1))

##Item Extraction
F1.item1 <- extract.item(F1_fit, 1)#item number
F1.item2 <- extract.item(F1_fit, 2)
F1.item3 <- extract.item(F1_fit, 3)
F2.item1 <- extract.item(F2_fit, 1)
F2.item2 <- extract.item(F2_fit, 2)
F2.item3 <- extract.item(F2_fit, 3)
F2.item4 <- extract.item(F2_fit, 4)
F2.item5 <- extract.item(F2_fit, 5)
F2.item6 <- extract.item(F2_fit, 6)
F3.item1 <- extract.item(F3_fit, 1)
F3.item2 <- extract.item(F3_fit, 2)
F3.item3 <- extract.item(F3_fit, 3)
F3.item4 <- extract.item(F3_fit, 4)
F3.item5 <- extract.item(F3_fit, 5)
F4.item1 <- extract.item(F4_fit, 1)
F4.item2 <- extract.item(F4_fit, 2)
F4.item3 <- extract.item(F4_fit, 3)
F4.item4 <- extract.item(F4_fit, 4)
F5.item1 <- extract.item(F5_fit, 1)
F5.item2 <- extract.item(F5_fit, 2)
F5.item3 <- extract.item(F5_fit, 3)
F5.item4 <- extract.item(F5_fit, 4)
F5.item5 <- extract.item(F5_fit, 5)

##Item Info
Item16 <- iteminfo(F1.item1, Theta)
Item36 <- iteminfo(F1.item2, Theta)
Item17 <- iteminfo(F1.item3, Theta)
Item11 <- iteminfo(F2.item1, Theta)
Item10 <- iteminfo(F2.item2, Theta)
Item12 <- iteminfo(F2.item3, Theta)
Item07 <- iteminfo(F2.item4, Theta)
Item08 <- iteminfo(F2.item5, Theta)
Item09 <- iteminfo(F2.item6, Theta)
Item27 <- iteminfo(F3.item1, Theta)
Item03 <- iteminfo(F3.item2, Theta)
Item40 <- iteminfo(F3.item3, Theta)
Item30 <- iteminfo(F3.item4, Theta)
Item41 <- iteminfo(F3.item5, Theta)
Item32 <- iteminfo(F4.item1, Theta)
Item35 <- iteminfo(F4.item2, Theta)
Item38 <- iteminfo(F4.item3, Theta)
Item33 <- iteminfo(F4.item4, Theta)
Item46 <- iteminfo(F5.item1, Theta)
Item45 <- iteminfo(F5.item2, Theta)
Item25 <- iteminfo(F5.item3, Theta)
Item04 <- iteminfo(F5.item4, Theta)
Item01 <- iteminfo(F5.item5, Theta)

#Data frame

F1.item.info.data <- as.data.frame(cbind(Item16, 
                                              Item36,
                                              Item17))

F2.item.info.data <- as.data.frame(cbind(Item11, 
                                              Item10,
                                              Item12,
                                         Item07,
                                         Item08,
                                         Item09))

F3.item.info.data <- as.data.frame(cbind(Item27, 
                                              Item03,
                                              Item40,
                                         Item30,
                                        Item41))

F4.item.info.data <- as.data.frame(cbind(Item32, 
                                              Item35,
                                              Item38,
                                         Item33))
F5.item.info.data <- as.data.frame(cbind(Item46, 
                                              Item45,
                                             Item25,
                                         Item04,
                                         Item01))

F1.item.info.data.long <- melt(F1.item.info.data)
F2.item.info.data.long <- melt(F2.item.info.data)
F3.item.info.data.long <- melt(F3.item.info.data)
F4.item.info.data.long <- melt(F4.item.info.data)
F5.item.info.data.long <- melt(F5.item.info.data)

F1.item.info.data.2 <- data.frame(Theta=seq(-6,6, by = .1), F1.item.info.data.long)
F2.item.info.data.2 <- data.frame(Theta=seq(-6,6, by = .1), F2.item.info.data.long)
F3.item.info.data.2 <- data.frame(Theta=seq(-6,6, by = .1), F3.item.info.data.long)
F4.item.info.data.2 <- data.frame(Theta=seq(-6,6, by = .1), F4.item.info.data.long)
F5.item.info.data.2 <- data.frame(Theta=seq(-6,6, by = .1), F5.item.info.data.long)

pacman::p_load(ggsci)

F1.iic2 <- ggplot(F1.item.info.data.2,aes(Theta,value,col=variable))+geom_line()+apatheme+
  ggtitle("F1 Item Information Plot")+theme(legend.position = "none")+
  facet_wrap(~variable,scales = "free")+theme(strip.text.x = element_text(size = 15))+geom_hline(yintercept = .20, colour ="red")+geom_area()+ scale_color_npg()+aes(fill = as.factor(variable))+xlab(expression(theta)) + 
  ylab(expression(I(theta)))

ggsave("Manuscript.figures/F1.itemplots.png",F1.iic2, width = 12, height =8, dpi = 1200, bg ="white")

F2.iic2 <- ggplot(F2.item.info.data.2,aes(Theta,value,col=variable))+geom_line()+apatheme+
  ggtitle("F2 Item Information Plot")+theme(legend.position = "none")+
  facet_wrap(~variable,scales = "free")+theme(strip.text.x = element_text(size = 15))+
  geom_hline(yintercept = .20, colour ="red")+geom_area()+scale_color_npg()+aes(fill = as.factor(variable))+xlab(expression(theta)) + 
  ylab(expression(I(theta)))

ggsave("Manuscript.figures/F2.itemplots.png",F2.iic2, width = 12, height =8, dpi = 1200, bg ="white")

F3.iic2 <- ggplot(F3.item.info.data.2,aes(Theta,value,col=variable))+geom_line()+apatheme+
  ggtitle("F3 Item Information Plot")+theme(legend.position = "none")+
  facet_wrap(~variable,scales = "free")+theme(strip.text.x = element_text(size = 15))+
  geom_hline(yintercept = .20, colour ="red")+geom_area()+scale_color_npg()+aes(fill = as.factor(variable))+xlab(expression(theta)) + 
  ylab(expression(I(theta)))

ggsave("Manuscript.figures/F3.itemplots.png",F3.iic2, width = 12, height =8, dpi = 1200, bg ="white")

F4.iic2 <- ggplot(F4.item.info.data.2,aes(Theta,value,col=variable))+geom_line()+apatheme+
  ggtitle("F4 Item Information Plot")+theme(legend.position = "none")+
  facet_wrap(~variable,scales = "free")+theme(strip.text.x = element_text(size = 15))+
  geom_hline(yintercept = .20, colour ="red")+geom_area()+scale_color_npg()+aes(fill = as.factor(variable))+xlab(expression(theta)) + 
  ylab(expression(I(theta)))

ggsave("Manuscript.figures/F4.itemplots.png",F4.iic2, width = 12, height =8, dpi = 1200, bg ="white")

F5.iic2 <- ggplot(F5.item.info.data.2,aes(Theta,value,col=variable))+geom_line()+apatheme+
  ggtitle("F5 Item Information Plot")+theme(legend.position = "none")+
  facet_wrap(~variable,scales = "free")+theme(strip.text.x = element_text(size = 15))+
  geom_hline(yintercept = .20, colour ="red")+geom_area()+scale_color_npg()+aes(fill = as.factor(variable))+xlab(expression(theta)) + 
  ylab(expression(I(theta)))

ggsave("Manuscript.figures/F5.itemplots.png",F5.iic2, width = 12, height =8, dpi = 1200, bg ="white")

allicc <- cowplot::plot_grid(F1.iic2, F2.iic2, F3.iic2, F4.iic2, F5.iic2, labels = "AUTO",ncol=2, label_size = 15,align = "h",label_fontfamily = "Arial",
                  label_fontface = "plain")

ggsave("Manuscript.figures/allicc.png",allicc, width = 12, height =12, dpi = 1200, bg ="white")

##Creating ggplot2 based all item item info using facet wrap
alldata <- as.data.frame(cbind(Item16,Item36,Item17,Item11,Item10, Item12,Item07,Item08,Item09,Item27,Item03, Item40, Item30, Item41, Item32, Item35, Item38, Item33, Item46, Item45, Item25, Item04, Item01))

all.data.long <- melt(alldata)
alldata2 <- data.frame(Theta=seq(-6,6, by = .1), all.data.long )

allicc3 <- ggplot(alldata2,aes(Theta,value,col=variable))+geom_line()+apatheme+
  ggtitle("Item Information Plot")+theme(legend.position = "none")+
  facet_wrap(~variable,scales = "free")+theme(strip.text.x = element_text(size = 15))+
  geom_hline(yintercept = .20, colour ="red")+geom_area()+scale_color_npg()+aes(fill = as.factor(variable))+xlab(expression(theta)) + 
  ylab(expression(I(theta)))

ggsave("Manuscript.figures/allicc2.png",allicc3, width = 12, height =12, dpi = 1200, bg ="white")

```

```{r scalechar, eval=FALSE, fig.cap="Scale characteristic curve of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, include=FALSE, out.height="120%", out.width="100%"}
#not used in the manuscript

#Finally we generated scale characteristics curve (Figure \@ref(fig:scalechar)) which plotted estimated theta score against the expected true score. The purpose of this scale characteristics curve is to find the corresponding expected true score for the given estimated theta score of the participants.

plot_grid(F1.scale, F1.scale,F1.scale,F1.scale,F1.scale, 
          labels = "AUTO", label_size = 10,align = "v")
```

### 2022-02-10 manuscript.Rmd
Knitting
Spelling check upto Analytics

@@
 In a confirmatory factor analysis (CFA) performed on an independent subset of participants (n=262), we removed two further items to attain the best fit for the five-factor solution (CFI=0.97, TLI=0.96, RMSEA=0.05, SRMR=0.09).
-The internal consistency reliability coefficient for the total instrument was McDonald’s omega_total=0.73.
+The internal consistency reliability coefficient for the total instrument was, McDonald’s Omega(total)=0.73.
 Measurement model invariance analysis between native and non-native English speakers showed our model attained the highest level of invariance (residual invariance; CFI=0.95, TLI =0.95, RMSEA=0.05).
@@
 
+invariance.data.descriptives.count <- CFA.descriptives %>% 
+  group_by(slypos_demographics_language.factor) %>% 
+  count() %>% 
+  as.data.frame()
+
 ## renaming the column-header
@@
 Figure \@ref(fig:FlowchartFig) summarizes the steps of our psychometric analysis.
-In our analysis we used R (version 4.1.0), with several R packages.
+In our analysis we used R (version 4.1.0).
 In the item generation and selection phase we had developed a item pool of 48 items with six-pont Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always).
-Our purpose was to capture light exposure related behaviour and the first two response options: "Does not apply/I don't know" and "Never" were providing similar information.
-As such we decided to collapse them into one, making it a 5 point Likert type response format.
-We conducted an initial item analysis and proceed to the EFA with all 48 items.
+Our purpose was to capture light exposure related behaviour.
+In that context, the first two response options: "Does not apply/I don't know" and "Never" were providing similar information.
+As such we collapsed them into one, making it a 5 point Likert type response format.
+We conducted an initial item analysis and proceed to the EFA with all 48 items (EFA sample;n=`r nrow(EFA.descriptives)`).
 Prior to the EFA, necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
 Our data violated both the univariate and multivariate normality assumptions.
-Due to these violations and the ordinal nature of our response data, we used  polychoric correlation matrix [@desjardinsHandbookEducationalMeasurement2018] for the EFA.
-We employed principal axis (PA) as  factor extraction method with varimax rotation.
-PA is robust to the normality assumption violations [@watkinsStepbyStepGuideExploratory2020].
-The obtained latent structure was confirmed by another factor extraction method: "the minimum residuals extraction" as well.
+Due to these violations and the ordinal nature of our response data, For EFA we used  polychoric correlation matrix and employed principal axis (PA) as  factor extraction method with varimax rotation [@desjardinsHandbookEducationalMeasurement2018;@watkinsStepbyStepGuideExploratory2020].
+The obtained latent structure was confirmed by another factor extraction method- "minimum residuals extraction" as well.
 We used a combination of factor identification method including scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
-Additionally, to determine the simple structure, we followed the common guidelines : (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading > .3 across factors [@bandalosFactorAnalysisExploratory2018].
+To determine the simple latent structure, we followed the common guidelines : (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading > .3 across factors [@bandalosFactorAnalysisExploratory2018].
 We also conducted a EFA on non-merged response options data (Supp.
@@
 
-For estimating reliability we used internal consistency reliability coefficient ordianl alpha.
+For reliability estimation we used internal consistency reliability coefficient ordinal alpha.
 Though  Cronbach's alpha coefficient is widely used for estimating internal consistency, it has a tendency to deflate the estimates for  Likert type data since calculation is based on pearson-correlation matrix which requires response data to be continuous of nature [@gadermann2012estimating; @zumbo2007ordinal].
@@
 
-We conducted categorical confirmatory factor analysis with robust weighted least square (WLSMV) estimator since our response data was of ordinary nature [@desjardinsHandbookEducationalMeasurement2018].
-We assessed the model fit using common model fit guidelines: (i) Reporting of $\chi^2$ test statistics (A non-significant test statistics is required to reflect model fit) (ii) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (iii) RMSEA (close to .06 or below), (iv) SRMR (close to .08 or below) to estimate the model fit [@huCutoffCriteriaFit1999; @schumacker2004beginner].However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015] and SRMR does not work well with ordinal data [@RN1272] As such, we judged the model fit using  CFI, TLI, SRMR and RMSEA.
-
-With the validated latent structure obtained by CFA analysis we assessed the measurement invariance of our construct between native English speakers and non-non native English speakers.
-Measurement invariance (MI) evaluates whether a construct has the psychometric equivalence and same meaning across groups or measurement occasions [@putnick2016measurement;@klinePrinciplesPracticeStructural2015].
+To validated the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with robust weighted least square (WLSMV) estimator [@desjardinsHandbookEducationalMeasurement2018] on a separate sample (CFA sample;n=`r nrow(CFA.descriptives)`).
+We assessed the model fit using common model fit guidelines: (i) Reporting of $\chi^2$ test statistics (A non-significant test statistics is required to reflect model fit) (ii) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (iii) RMSEA (close to .06 or below), (iv) SRMR (close to .08 or below) to estimate the model fit [@huCutoffCriteriaFit1999; @schumacker2004beginner].
+However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015] and SRMR does not work well with ordinal data [@RN1272] As such, we judged the model fit using  CFI, TLI, SRMR and RMSEA.
+
+Using the CFA sample (n=`r nrow(CFA.descriptives)`) we assessed the measurement invariance (MI) of our construct between native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non-non native English speakers (n=`r invariance.data.descriptives.count[2,2]`) using the validated latent structure obtained in CFA.
+MI evaluates whether a construct has the psychometric equivalence and same meaning across groups or measurement occasions [@putnick2016measurement;@klinePrinciplesPracticeStructural2015].
 We used  structural equation modelling framework to assess the measurement invariance.
 We successively compared four nested models:  configural, metric, scalar, and residual models using the $\chi^2$ difference test ($\Delta \chi^2$).
-Here configural model is the least restrictive model and residual model is the most restrictive model.
+Among MI models, configural model is the least restrictive model and residual model is the most restrictive model.
 A non-significant $\Delta \chi^2$ test between two nested measurement invariance models indicates mode fit does not significantly decrease for the superior model [@dimitrov2010testing] thus allowing the superior invariance model to be accepted.
@@
 Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy.
-Additionally, To identify the educational grade level required to understand the items in our tool we subjected tool to Flesch-Kincaid Grade Level [@flesch1948new]
+Additionally, To identify the educational grade level required to understand the items in our tool we subjected the tool to Flesch-Kincaid Grade Level [@flesch1948new]
 
 Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA.
-We fitted each factor of LEBA using the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690).
-IRT assess the item quality by estimatingitem difficulty, item discrimination, a item information, and Test information [@bakerBasicsItemResponse2017].
+We fitted each factor of LEBA using the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =`r nrow(sem.data)`).
+IRT assess the item quality by estimating item difficulty, item discrimination, item information, and Test information [@bakerBasicsItemResponse2017].
 Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait level ($\theta$), and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.

### 2022-02-10 manuscript.Rmd
Participants Map

@@
 
----
-nocite: |
-  `r cite_r("references.bib")`
-  [@verriotto2017new][@eklund1996development][@bajaj2011validation][@dianat2013objective]
-  [@horne1976self][@roenneberg2003life][@Olivier.2016][@buysse1989pittsburgh][@Xie.2021][@bossini2006sensibilita]
----
-
-# Introduction
-
--   Light exposure is important
-
--   Light exposure Behavior is important
-
--   Table: Overview Existing Related Scales: items in total / items on light exposure (behaviour)
-
--   Existing Scales: Review them in text
-
--   None of these do light exposure behavior.
-
-```{r relscale, include=F, warning=F, message=F}
-#This chunk holds code for Relevant scales table in the manuscript
-relevant.scale.data <- readxl::read_excel("Table_raw/relevant_scales.xlsx")
-
-```
-
-```{r reltab2, results='asis'}
-relevant.scale.data %>% 
-apa_table(landscape =T,caption ="List of instruments measuring related consttucts to LEBA", format = "latex",escape = T, font_size = "footnotesize", align = c("p{3cm}", rep("p{3.6cm}", ncol(relevant.scale.data))))
-
-```
-
-# Methods
-
-```{r rafel, include=F}
-# In addition to the LEBA questionnaire, which is subject of the current study, we assessed other variables and items which were not included in the present analysis.
-This comprised various sleep-related measures, i.e., sleep disturbances and sleep-related impairment (adult and pediatric versions) [@Bevans.2019; @Buysse.2010; @Forrest.2018; @Harb.2015; @Yu.2011], sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration [MCTQ version for adults and adolescents @roenneberg2003life] plus sleep environment [@Olivier.2016].
-Furthermore, we included a light sensitivity questionnaire (photophobia vs.
-photophilia) [@Wu.2017] and self-reported pubertal stage assessment [@Petersen.1988] for participants younger than 18 years of age.
-Moreover, we incorporated custom items on meal timing and caffeine consumption in the “workday vs.
-free day” structure of the MCTQ sleep-wake regulation.
-Example items are: “On workdays I usually have my first meal at __:__”, “On free days I usually have my last meal at __:__”, and “On workdays I usually drink my first caffeinated drink at __:__”.
-
-```
-
-```{r Data, include=FALSE}
-#This chunk holds code for data wrangling
-
-data <- readRDS("leba_2021-09-08.rds")
-
-# Separating EFA and CFA samples with descriptive column
-descriptives.data <- data
-
-## Merge "0"s and "1"s into "1"s select,subset assign)
-descriptives.data[ , 9:56 ][ descriptives.data[ , 9:56 ] == 0 ] <- 1
-#EFA.descriptives <- descriptives.data[1:428,]
-EFA.descriptives <- subset(descriptives.data, IncludedInEFA == "TRUE")
-#CFA.descriptives <- descriptives.data[429:690, ]
-CFA.descriptives<- subset(descriptives.data, IncludedInEFA == "FALSE")
-
-#Separating the EFA and CFA(only items)
-sem.data <- data[, 9:56] #EFA & CFA data
-sem.data[ sem.data == 0] <- 1 #Merged "0"s and "1"s into "1"s
-
-invariance.data.descriptives.count <- CFA.descriptives %>% 
-  group_by(slypos_demographics_language.factor) %>% 
-  count() %>% 
-  as.data.frame()
-
-## renaming the column-header
-prefix <- "item"
-sufix <- c(1:48)
-colnam <- paste(prefix,sufix, sep = "" )
-colnames(sem.data) <- colnam
-names(sem.data)[names(sem.data) == "item1"] <- "item01"
-names(sem.data)[names(sem.data) == "item2"] <- "item02"
-names(sem.data)[names(sem.data) == "item3"] <- "item03"
-names(sem.data)[names(sem.data) == "item4"] <- "item04"
-names(sem.data)[names(sem.data) == "item5"] <- "item05"
-names(sem.data)[names(sem.data) == "item6"] <- "item06"
-names(sem.data)[names(sem.data) == "item7"] <- "item07"
-names(sem.data)[names(sem.data) == "item8"] <- "item08"
-names(sem.data)[names(sem.data) == "item9"] <- "item09"
-```
-
-```{r country, include=FALSE}
-#This chunk holds code for timezone calculation
-
-library(stringr)
-country <- data
-
-TZ <- as.data.frame(str_split_fixed(country$slypos_demographics_tz.factor, "-", 2))
-TZ[97, 2] <- " East Africa/Dodoma (UTC +03:00)"
-TZ[146, 2] <- " European /Skopje (UTC +01:00)"
-TZ[176, 2] <- " Asia /Taipei City (UTC +08:00)"
-TZ[574, 2] <- " Asia /Taipei City (UTC +08:00)"
-TZ[690, 2] <- " Asia /Taipei City (UTC +08:00)"
-TZ[273, 2] <- " Iran /Tehran (UTC +0:30)"
-TZ[418, 2] <- " Iran /Tehran (UTC +0:30)"
-TZ[673, 2] <- " Iran /Tehran (UTC +0:30)"
-
-num.countries <- unique(TZ$V1)
-num.Timezone <- unique(TZ$V2)
-
-UTC <- as.data.frame(str_split_fixed(TZ$V2, "UTC", 2))
-numUTC <- unique(UTC$V2)
-```
-
-```{r timezone, include=F}
-#This chunk holds code for creating timezone.csv file
-timezone <- TZ %>% 
-  group_by(V2) %>% 
-  count() %>% 
-  as.data.frame()
-
-write.csv(timezone, "Table_raw/timezone.csv")
-
-```
-
-```{r prepareDescTable, include=FALSE}
-#This chunk holds code for demographic data wrangling.
-
-listdescVars <- colnames(descriptives.data[c(1:3,5:7)])
-
-#seperating naming and  reducing data for descriptive Table 
-desctable.data <- dplyr::select(descriptives.data, c(listdescVars,
-                          IncludedInCFA))
-
-#renaming TRUE and FALSE from the IncludedInCFA to EFA and CFA for Descriptive Table
-desctable.data$IncludedInCFA[desctable.data$IncludedInCFA == T ] <-
- "2. CFA Sample"
-desctable.data$IncludedInCFA[desctable.data$IncludedInCFA == F ] <- 
- "1. EFA Sample"
-
-# recode the Gender factor so it will only show "Gender Diverse" in the summary table
-desctable.data$slypos_demographics_gender.factor <-
-  recode_factor(desctable.data$slypos_demographics_gender.factor, "No" = "Yes",
-         "Yes"= "No")
-
-# create descriptive table for the demographic vars (excluding tz & Country) with gtsummary
-desctable.data %>%
-  tbl_summary(
-    by = IncludedInCFA,
-    statistic = list(all_continuous() ~ "{mean} ({sd})",
-                     all_categorical() ~ "{n} ({p}%)"),
-    digits = all_continuous() ~ 2,
-    label = list(slypos_demographics_age ~ "Age",
-                 slypos_demographics_sex.factor ~ "Sex",
-                 slypos_demographics_gender.factor ~ "Gender-Variant Identity",
-                 slypos_demographics_language.factor ~ "Native English Speaker",
-                 slypos_demographics_work_or_school.factor ~ "Occupational Status",
-                 slypos_demographics_school.factor ~ "Occupational setting"
-                 ),
-
-    missing = "no"
-    ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
-modify_header(label ~ "**Variable**") %>% separate_p_footnotes() %>%
-  modify_caption("Demographic Characteristics") -> desc_table
-
-as_tibble(desc_table) -> desc_tibble 
-as_kable_extra(desc_table, format = "latex",booktabs = T) -> desc_kable #save it as a knitr::kable
-
-#summarise country/time zone data
-#The following chunk is not working now. May be package problem (Sorting command is not working)
-
-descriptives.data%>%
-  tbl_summary(
-    label = slypos_demographics_tz.factor ~ "Time zone - Country",
-    statistic = list(all_categorical() ~ "{n} ({p}%)"),
-    missing = "no",
-    sort = all_categorical() ~ "frequency",
-    include = "slypos_demographics_tz.factor"
-  )  %>% bold_labels() %>%
-  modify_header(label ~ "") %>%
-  as_tibble(format = 'pipe') -> tz_tibble
-
-```
-
-```{r Manuflowchart, include=FALSE }
-#This chunk holds code for the work flow chart of the data analysis
-
-Flowchart1 <- grViz("digraph my_flowchart{
-
-                    graph [fontname = Helvetica,layout = dot,fontsize = 45,layout = dot ]
-
-                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 16, height = 2, 
-                    fixedsize = true,fontsize = 45]
-
-                    A[label = 'Initial Development of 48 Items'] 
-                    B[label = 'Large Scale Survey (n=690)']
-                    C[label = 'Initial Item Analysis']
-                    D[label = 'Exploratory Factor Analysis (48 items; n=428)']
-
-                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 16, height = 6, 
-                    fixedsize = true, fontsize = 45]
-                    E[label = 
-                    <Factor Identification<br/>Scree Plot: 6 Factors<br/>Minimum Average Partial Method: 5 Factors<br/>Hull Method: 5 Factors>
-                    ]
-
-                     subgraph cluster_1 {
-                      graph[fontname = Helvetica, shape = box, style =dashed]
-
-                     node[fontname = Helvetica, margin = 0.2,width = 22, height = 2.5, 
-                    fixedsize = true, fontsize = 45,style =dashed]
-
-                     1[label = '5 Factor Solution Retained 25 Items']
-                     2[label = <Reliability Analysis on EFA Sample (n=428)<br/>Ordinal alpha F1 =.94; F2 = .76; F3 = .75; F4 =.72; F5 =.62.>]
-
-                     3[label = <Confirmatory Factor Analysis<br/>on the Five Factor Model (25 Items; n=262)<br/>Acceptable Fit ( CFI = .94; TLI .93; RMSEA = .06, SRMR = .11)>]
-
-                    4[label = <Confirmatory Factor Analysis<br/>on the Five Factor Model (23 Items; n=262)<br/>Acceptable Fit ( CFI = .97; TLI= .96; RMSEA = .04, SRMR = .09)>]
-                     5[label = <Reliability Analysis (23 Items; n=262)<br/>Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52<br/>Mcdonald  omega(total) for the total scale = .73>]
-                    8[label = <Measurement Invariance Analysis (n=262)<br/>Residual measurement invariance achieved>]
-                    9[label = <Semantic Analysis (n=262):<br/>Semantic Scale Network analysis<br/>Readbility: Grade level 3.33>]
-                    10[label = <LEBA Short Form (19 Items; n=690)<br/>Based on Item Response Theory>]
-                    }
-                subgraph cluster_2 {
-                      graph[fontname = Helvetica,shape = rectangle]
-                      style = rounded
-                     node[fontname = Helvetica, margin = 0.2,width = 18, height = 2.5, 
-                fixedsize = true, fontsize = 45 ]
-                    6[label = 
-                    <6-Factor solution:<br/>one factor emerged with only two salient loadings>
-                    ]
-                    7[label = 'Rejected']
-                    }
-
-                     edge[fontname = Helvetica,color = black,arrowhead = vee, arrowsize = 1.25]
-                     A ->B
-                     B ->C
-                     C ->D
-                     D ->E
-                E ->1
-                     1 ->2
-                     2 ->3
-                     3 ->4
-                     4 ->5
-                    5->8
-                    8 ->9
-                    9 ->10
-                     E ->6
-                     6 ->7
-
-}")
-
-library(jpeg)
-export_svg(Flowchart1) %>%
-  charToRaw() %>%
-  rsvg() %>%
-  png::writePNG("Manuscript.figures/Flowchart1.jpeg", dpi = 600)
-
-```
-
-## Data Collection
-
-A quantitative cross-sectional fully anonymous online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
-Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) of a Comic co-released with the survey[@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux].
-The landing page of the on-line survey had the explanatory statements It was mentioned in the explanatory statement that their participation was voluntary and that they could withdraw from participation anytime without being penalized.
-At the beginning of the survey, for the adult participants (>18 years) consent was recorded digitally.
-Underaged participants (<18 years) were urged to obtain assent from their parents/legal guardians, before filling in the survey.
-The survey took around 15 to 20 minutes for which they were not compensated.
-As a part of the demographics participants provided information regarding age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language as single-item demographic variables.
-The demographic characteristics of our sample are given in Table \@ref(tab:demotab).To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention.
-What is 4+5?").
-Participants needed to confirm that they were participating the survey for the first time.
-Questions incorporating retrospective recall were all aligned to the period of "past four weeks". The data analysed in this study was collected between 17 May 2021 and 3 September 2021. 
-```{r demotab, warning=F, message=F}
-desc_kable  %>% kable_styling(latex_options = c("scale_down")) %>% landscape()
-```
-
-## Analytic Strategies
-
-Figure \@ref(fig:FlowchartFig) summarizes the steps of our psychometric analysis.
-In our analysis we used R (version 4.1.0).
-In the item generation and selection phase we had developed a item pool of 48 items with six-pont Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always).
-Our purpose was to capture light exposure related behaviour.
-In that context, the first two response options: "Does not apply/I don't know" and "Never" were providing similar information.
-As such we collapsed them into one, making it a 5 point Likert type response format.
-We conducted an initial item analysis and proceed to the EFA with all 48 items (EFA sample;n=`r nrow(EFA.descriptives)`).
-Prior to the EFA, necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
-Our data violated both the univariate and multivariate normality assumptions.
-Due to these violations and the ordinal nature of our response data, For EFA we used  polychoric correlation matrix and employed principal axis (PA) as  factor extraction method with varimax rotation [@desjardinsHandbookEducationalMeasurement2018;@watkinsStepbyStepGuideExploratory2020].
-The obtained latent structure was confirmed by another factor extraction method- "minimum residuals extraction" as well.
-We used a combination of factor identification method including scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
-To determine the simple latent structure, we followed the common guidelines : (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading > .3 across factors [@bandalosFactorAnalysisExploratory2018].
-We also conducted a EFA on non-merged response options data (Supp.
-Table \@ref(tab:efaunmerged)) and rejected the latent structure obtained as the factors were less interpretable.
-
-For reliability estimation we used internal consistency reliability coefficient ordinal alpha.
-Though  Cronbach's alpha coefficient is widely used for estimating internal consistency, it has a tendency to deflate the estimates for  Likert type data since calculation is based on pearson-correlation matrix which requires response data to be continuous of nature [@gadermann2012estimating; @zumbo2007ordinal].
-Subsequently to get  better estimates of reliability  we reported ordinal alpha for each factors that used polychoric-correlation matrix and assumed that the responses data were ordered in nature instead of continuous [@zumbo2007ordinal].
-We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$  coefficient which is a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
-Both ordinal alpha and McDonald's $\omega_t$ coefficient value range from 0 to 1 and higher value represents better reliability.
-
-To validated the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with robust weighted least square (WLSMV) estimator [@desjardinsHandbookEducationalMeasurement2018] on a separate sample (CFA sample;n=`r nrow(CFA.descriptives)`).
-We assessed the model fit using common model fit guidelines: (i) Reporting of $\chi^2$ test statistics (A non-significant test statistics is required to reflect model fit) (ii) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (iii) RMSEA (close to .06 or below), (iv) SRMR (close to .08 or below) to estimate the model fit [@huCutoffCriteriaFit1999; @schumacker2004beginner].
-However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015] and SRMR does not work well with ordinal data [@RN1272] As such, we judged the model fit using  CFI, TLI, SRMR and RMSEA.
-
-Using the CFA sample (n=`r nrow(CFA.descriptives)`) we assessed the measurement invariance (MI) of our construct between native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non-non native English speakers (n=`r invariance.data.descriptives.count[2,2]`) using the validated latent structure obtained in CFA.
-MI evaluates whether a construct has the psychometric equivalence and same meaning across groups or measurement occasions [@putnick2016measurement;@klinePrinciplesPracticeStructural2015].
-We used  structural equation modelling framework to assess the measurement invariance.
-We successively compared four nested models:  configural, metric, scalar, and residual models using the $\chi^2$ difference test ($\Delta \chi^2$).
-Among MI models, configural model is the least restrictive model and residual model is the most restrictive model.
-A non-significant $\Delta \chi^2$ test between two nested measurement invariance models indicates mode fit does not significantly decrease for the superior model [@dimitrov2010testing] thus allowing the superior invariance model to be accepted.
-[@widaman1997exploring].
-
-We also analysed possible semantic overlap of our developed tool using "Semantic Scale Network" (SSN) engine [@rosenbusch2020semantic].
-The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic].
-Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy.
-Additionally, To identify the educational grade level required to understand the items in our tool we subjected the tool to Flesch-Kincaid Grade Level [@flesch1948new]
-
-Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA.
-We fitted each factor of LEBA using the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =`r nrow(sem.data)`).
-IRT assess the item quality by estimating item difficulty, item discrimination, item information, and Test information [@bakerBasicsItemResponse2017].
-Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait level ($\theta$), and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
-Here, we reported  the item discrimination parameter and categorize the items according to the suggestions of @bakerBasicsItemResponse2017 : none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70.
-We discarded the items with relatively flat item information curve (information <.2) to develop the short form of LEBA.
-We also assessed the precision of the short LEBA using Test information curve (TIC).
-TIC  indicates the amount of information an the full-scale carry along the latent trait continuum.
-Item fit and person-fit of the fitted model were also analyzed to gather more evidence on validity and meaningfulness of our Tool [@desjardinsHandbookEducationalMeasurement2018].
-Item-fit was evaluated using  the RMSEA value obtained from Signed-$\chi^2$ index implementation, RMSEA value $\le$.06 was considered adequate item fit.
-Person fit was estimated using standardized fit index Zh statistics [@drasgow1985appropriateness].
-Zh < -2 was be considered as a misfit [@drasgow1985appropriateness].
-
-```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='100%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/Flowchart1.jpeg', dpi = 800 )
-```
-
-## Ethical approval
-
-By reason of using fully anonymous online survey data, the present research project does not fall under the scope of the Human Research Act, making an authorisation from the ethics committee redundant.
-Nevertheless, the cantonal ethics commission (Ethikkommission Nordwest- und Zentralschweiz, EKNZ) reviewed our proposition (project ID Req-2021-00488) and issued an official clarification of responsibility (full document see Suppl.
-X in appendix).
-
-## Data Availability
-
-The present article is a fully reproducible open-access “R Markdown” document.
-All code and data underlying this article – along with two versions of the LEBA questionnaire (full and short) and online survey implementation templates on common survey platforms – will be available under open-access licence (CC-BY-NC-ND) on a public [GitHub repository](https://github.com/leba-instrument).
-
-# Results
-
-## Initial development of items
-
-After reviewing the literature, we identified several light exposure related scale.
-However, no scales specifically measuring the behavioural component of light exposure were found.
-As such ,we developed a comprehensive item pool of 48 items with six point Likert response scale (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always).The whole list of 48 items were then judged  based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by an expert panel.
-The expert panel composed of all authors and researchers from the fields of chronobiology, light research, neuroscience and psychology.
-The panel members independently judged each of the items in terms of their relevance and representativeness and suggested required modification, if there is any.
-The author team acknowledged the auggestions and amended the items as required thus creating a 48-item scale
-
-## Large-scale  survey of instruments
-
-### Participants
-
-Table \@ref(tab:demotab) summarizes the survey participants' demographic characteristics.
-Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses.
-(XX??) participants were excluded from analysis due to not passing at least one of the "attention check" items.
-For exploring initial factor structure (EFA), a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013].
-For estimating the sample size for the confirmatory factor analysis (CFA) we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per parameter is required to earn trustworthiness of the result.
-Our sample size exceeds these requirements: Anonymous responses from a total of *n* = `r nrow(desctable.data)` participants were included in the analysis of the current study, split into samples for exploratory (EFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "1.
-EFA Sample",])`) and confirmatory factor analysis (CFA: *n* = `r nrow(desctable.data[desctable.data$IncludedInCFA == "2.
-CFA Sample",])`).
-The EFA sample included participants filling out the questionnaire from 17 May 2021 to XX XXX 2021, whereas participants who filled out the questionnaire from YY YYY 2021 to 3 September 2021 were included in the CFA analysis.
-Participants indicated filling out the online survey from a diverse range of geographic locations.
-The ten most common country and time zone combinations included:
-
-- `r tz_tibble[2,1]`:     `r tz_tibble[2,2]`
-- `r tz_tibble[3,1]`:     `r tz_tibble[3,2]`
-- `r tz_tibble[4,1]`:     `r tz_tibble[4,2]`
-- `r tz_tibble[5,1]`:     `r tz_tibble[5,2]`
-- `r tz_tibble[6,1]`:     `r tz_tibble[6,2]`
-- `r tz_tibble[7,1]`:     `r tz_tibble[7,2]`
-- `r tz_tibble[8,1]`:     `r tz_tibble[8,2]`
-- `r tz_tibble[9,1]`:     `r tz_tibble[9,2]`
-- `r tz_tibble[10,1]`:    `r tz_tibble[10,2]`
-- `r tz_tibble[11,1]`:    `r tz_tibble[11,2]`
-
-For a complete list of geographic locations, see Suppl. Table \@ref(tab:tztable).
-
-Age among all participants ranged from `r min(desctable.data$slypos_demographics_age)` years to `r max(desctable.data$slypos_demographics_age)` years [EFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
-EFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
-EFA Sample"])`; CFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`], with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 0)` years of age [Overall: *M* = `r mean(desctable.data$slypos_demographics_age)`, *SD* = `r sd(desctable.data$slypos_demographics_age)`; EFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
-EFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
-EFA Sample"])`; CFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`].
-In total `r desc_tibble[3,2]` of the participants indicated female sex [EFA: `r desc_tibble[3,3]`; CFA: `r desc_tibble[3,4]`], `r desc_tibble[4,2]` indicated male [EFA: `r desc_tibble[4,3]`; CFA: `r desc_tibble[4,4]`] and `r desc_tibble[5,2]` indicated other sex [EFA: `r desc_tibble[5,3]`, CFA: `r desc_tibble[5,4]`].
-Overall, `r desc_tibble[6,2]` [EFA: `r desc_tibble[6,3]`; CFA: `r desc_tibble[6,4]`] participants indicated a gender-variant identity.
-In a "Yes/No" question regarding native language, `r desc_tibble[7,2]` of respondents [EFA: `r desc_tibble[7,3]`; CFA: `r desc_tibble[7,4]`] indicated to be native English speakers.
-For their "Occupational Status", more than half of the overall sample reported that they currently work [Overall: `r desc_tibble[9,2]`; EFA: `r desc_tibble[9,3]`; CFA: `r desc_tibble[9,4]`], whereas `r desc_tibble[10,2]` [EFA: `r desc_tibble[10,3]`; CFA: `r desc_tibble[10,4]`] reported that they go to school and `r desc_tibble[11,2]` [EFA: `r desc_tibble[11,3]`; CFA: `r desc_tibble[11,4]`] responded that they do "Neither".
-With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` [EFA: `r desc_tibble[13,3]`; CFA: `r desc_tibble[13,4]`] of the participants indicated that they were in a home office/ home schooling setting, while `r desc_tibble[14,2]` overall [EFA: `r desc_tibble[14,3]` ; CFA: `r desc_tibble[14,4]`] reported face-to-face work/schooling.
-Lastly, `r desc_tibble[15,2]` overall [EFA: `r desc_tibble[15,3]` ; CFA: `r desc_tibble[15,4]`] reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]` overall [EFA: `r desc_tibble[16,3]`; CFA: `r desc_tibble[16,4]`] filled in the "Neither (no work or school, or on vacation)" response option.
-We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable "Age" and Pearson's $\chi^2$ test for all other categorical variables via the gtsummary R package's "add_p" function [@sjoberg2021] .
-The p-values were corrected for multiple testing applying false discovery rate (FDR) via the "add_q" function of the same package.
-After p-value (FDR) correction for multiple testing, none of the demographic variables were significantly different between the EFA sample and the CFA sample (all q-values *q* $\ge$ `r min(desc_tibble$"**q-value**", na.rm=T)`).
-
 ```{r ggplot2, include=F}
@@
 ```
+
+---
+nocite: |
+  `r cite_r("references.bib")`
+  [@verriotto2017new][@eklund1996development][@bajaj2011validation][@dianat2013objective]
+  [@horne1976self][@roenneberg2003life][@Olivier.2016][@buysse1989pittsburgh][@Xie.2021][@bossini2006sensibilita]
+---
+
+# Introduction
+
+-   Light exposure is important
+
+-   Light exposure Behavior is important
+
+-   Table: Overview Existing Related Scales: items in total / items on light exposure (behaviour)
+
+-   Existing Scales: Review them in text
+
+-   None of these do light exposure behavior.
+
+```{r relscale, include=F, warning=F, message=F}
+#This chunk holds code for Relevant scales table in the manuscript
+relevant.scale.data <- readxl::read_excel("Table_raw/relevant_scales.xlsx")
+
+```
+
+```{r reltab2, results='asis'}
+relevant.scale.data %>% 
+apa_table(landscape =T,caption ="List of instruments measuring related consttucts to LEBA", format = "latex",escape = T, font_size = "footnotesize", align = c("p{3cm}", rep("p{3.6cm}", ncol(relevant.scale.data))))
+
+```
+
+# Methods
+
+```{r rafel, eval=FALSE, include=FALSE}
+# In addition to the LEBA questionnaire, which is subject of the current study, we assessed other variables and items which were not included in the present analysis.
+This comprised various sleep-related measures, i.e., sleep disturbances and sleep-related impairment (adult and pediatric versions) [@Bevans.2019; @Buysse.2010; @Forrest.2018; @Harb.2015; @Yu.2011], sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration [MCTQ version for adults and adolescents @roenneberg2003life] plus sleep environment [@Olivier.2016].
+Furthermore, we included a light sensitivity questionnaire (photophobia vs.
+photophilia) [@Wu.2017] and self-reported pubertal stage assessment [@Petersen.1988] for participants younger than 18 years of age.
+Moreover, we incorporated custom items on meal timing and caffeine consumption in the “workday vs.
+free day” structure of the MCTQ sleep-wake regulation.
+Example items are: “On workdays I usually have my first meal at __:__”, “On free days I usually have my last meal at __:__”, and “On workdays I usually drink my first caffeinated drink at __:__”.
+
+```
+
+```{r Data, include=FALSE}
+#This chunk holds code for data wrangling
+
+data <- readRDS("leba_2021-09-08.rds")
+
+# Separating EFA and CFA samples with descriptive column
+descriptives.data <- data
+
+## Merge "0"s and "1"s into "1"s select,subset assign)
+descriptives.data[ , 9:56 ][ descriptives.data[ , 9:56 ] == 0 ] <- 1
+#EFA.descriptives <- descriptives.data[1:428,]
+EFA.descriptives <- subset(descriptives.data, IncludedInEFA == "TRUE")
+#CFA.descriptives <- descriptives.data[429:690, ]
+CFA.descriptives<- subset(descriptives.data, IncludedInEFA == "FALSE")
+
+#Separating the EFA and CFA(only items)
+sem.data <- data[, 9:56] #EFA & CFA data
+sem.data[ sem.data == 0] <- 1 #Merged "0"s and "1"s into "1"s
+
+invariance.data.descriptives.count <- CFA.descriptives %>% 
+  group_by(slypos_demographics_language.factor) %>% 
+  count() %>% 
+  as.data.frame()
+
+## renaming the column-header
+prefix <- "item"
+sufix <- c(1:48)
+colnam <- paste(prefix,sufix, sep = "" )
+colnames(sem.data) <- colnam
+names(sem.data)[names(sem.data) == "item1"] <- "item01"
+names(sem.data)[names(sem.data) == "item2"] <- "item02"
+names(sem.data)[names(sem.data) == "item3"] <- "item03"
+names(sem.data)[names(sem.data) == "item4"] <- "item04"
+names(sem.data)[names(sem.data) == "item5"] <- "item05"
+names(sem.data)[names(sem.data) == "item6"] <- "item06"
+names(sem.data)[names(sem.data) == "item7"] <- "item07"
+names(sem.data)[names(sem.data) == "item8"] <- "item08"
+names(sem.data)[names(sem.data) == "item9"] <- "item09"
+```
+
+```{r country, include=FALSE}
+#This chunk holds code for timezone calculation
+
+library(stringr)
+country <- data
+
+TZ <- as.data.frame(str_split_fixed(country$slypos_demographics_tz.factor, "-", 2))
+TZ[97, 2] <- " East Africa/Dodoma (UTC +03:00)"
+TZ[146, 2] <- " European /Skopje (UTC +01:00)"
+TZ[176, 2] <- " Asia /Taipei City (UTC +08:00)"
+TZ[574, 2] <- " Asia /Taipei City (UTC +08:00)"
+TZ[690, 2] <- " Asia /Taipei City (UTC +08:00)"
+TZ[273, 2] <- " Iran /Tehran (UTC +0:30)"
+TZ[418, 2] <- " Iran /Tehran (UTC +0:30)"
+TZ[673, 2] <- " Iran /Tehran (UTC +0:30)"
+
+num.countries <- as.data.frame(unique(TZ$V1))
+num.Timezone <- unique(TZ$V2)
+
+UTC <- as.data.frame(str_split_fixed(TZ$V2, "UTC", 2))
+numUTC <- as.data.frame(unique(UTC$V2))
+nrow(numUTC)
+```
+
+```{r timezone, include=F}
+#This chunk holds code for creating timezone.csv file
+timezone <- TZ %>% 
+  group_by(V2) %>% 
+  count() %>% 
+  as.data.frame()
+
+write.csv(timezone, "Table_raw/timezone.csv")
+
+```
+
+```{r prepareDescTable, include=FALSE}
+#This chunk holds code for demographic data wrangling.
+
+listdescVars <- colnames(descriptives.data[c(1:3,5:7)])
+
+#seperating naming and  reducing data for descriptive Table 
+desctable.data <- dplyr::select(descriptives.data, c(listdescVars,
+                          IncludedInCFA))
+
+#renaming TRUE and FALSE from the IncludedInCFA to EFA and CFA for Descriptive Table
+desctable.data$IncludedInCFA[desctable.data$IncludedInCFA == T ] <-
+ "2. CFA Sample"
+desctable.data$IncludedInCFA[desctable.data$IncludedInCFA == F ] <- 
+ "1. EFA Sample"
+
+# recode the Gender factor so it will only show "Gender Diverse" in the summary table
+desctable.data$slypos_demographics_gender.factor <-
+  recode_factor(desctable.data$slypos_demographics_gender.factor, "No" = "Yes",
+         "Yes"= "No")
+
+# create descriptive table for the demographic vars (excluding tz & Country) with gtsummary
+desctable.data %>%
+  tbl_summary(
+    by = IncludedInCFA,
+    statistic = list(all_continuous() ~ "{mean} ({sd})",
+                     all_categorical() ~ "{n} ({p}%)"),
+    digits = all_continuous() ~ 2,
+    label = list(slypos_demographics_age ~ "Age",
+                 slypos_demographics_sex.factor ~ "Sex",
+                 slypos_demographics_gender.factor ~ "Gender-Variant Identity",
+                 slypos_demographics_language.factor ~ "Native English Speaker",
+                 slypos_demographics_work_or_school.factor ~ "Occupational Status",
+                 slypos_demographics_school.factor ~ "Occupational setting"
+                 ),
+
+    missing = "no"
+    ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
+modify_header(label ~ "**Variable**") %>% separate_p_footnotes() %>%
+  modify_caption("Demographic Characteristics") -> desc_table
+
+as_tibble(desc_table) -> desc_tibble 
+as_kable_extra(desc_table, format = "latex",booktabs = T) -> desc_kable #save it as a knitr::kable
+
+#summarise country/time zone data
+#The following chunk is not working now. May be package problem (Sorting command is not working)
+
+descriptives.data%>%
+  tbl_summary(
+    label = slypos_demographics_tz.factor ~ "Time zone - Country",
+    statistic = list(all_categorical() ~ "{n} ({p}%)"),
+    missing = "no",
+    sort = all_categorical() ~ "frequency",
+    include = "slypos_demographics_tz.factor"
+  )  %>% bold_labels() %>%
+  modify_header(label ~ "") %>%
+  as_tibble(format = 'pipe') -> tz_tibble
+
+```
+
+```{r Manuflowchart, include=FALSE }
+#This chunk holds code for the work flow chart of the data analysis
+
+Flowchart1 <- grViz("digraph my_flowchart{
+
+                    graph [fontname = Helvetica,layout = dot,fontsize = 45,layout = dot ]
+
+                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 16, height = 2, 
+                    fixedsize = true,fontsize = 45]
+
+                    A[label = 'Initial Development of 48 Items'] 
+                    B[label = 'Large Scale Survey (n=690)']
+                    C[label = 'Initial Item Analysis']
+                    D[label = 'Exploratory Factor Analysis (48 items; n=428)']
+
+                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 16, height = 6, 
+                    fixedsize = true, fontsize = 45]
+                    E[label = 
+                    <Factor Identification<br/>Scree Plot: 6 Factors<br/>Minimum Average Partial Method: 5 Factors<br/>Hull Method: 5 Factors>
+                    ]
+
+                     subgraph cluster_1 {
+                      graph[fontname = Helvetica, shape = box, style =dashed]
+
+                     node[fontname = Helvetica, margin = 0.2,width = 22, height = 2.5, 
+                    fixedsize = true, fontsize = 45,style =dashed]
+
+                     1[label = '5 Factor Solution Retained 25 Items']
+                     2[label = <Reliability Analysis on EFA Sample (n=428)<br/>Ordinal alpha F1 =.94; F2 = .76; F3 = .75; F4 =.72; F5 =.62.>]
+
+                     3[label = <Confirmatory Factor Analysis<br/>on the Five Factor Model (25 Items; n=262)<br/>Acceptable Fit ( CFI = .94; TLI .93; RMSEA = .06, SRMR = .11)>]
+
+                    4[label = <Confirmatory Factor Analysis<br/>on the Five Factor Model (23 Items; n=262)<br/>Acceptable Fit ( CFI = .97; TLI= .96; RMSEA = .04, SRMR = .09)>]
+                     5[label = <Reliability Analysis (23 Items; n=262)<br/>Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52<br/>Mcdonald  omega(total) for the total scale = .73>]
+                    8[label = <Measurement Invariance Analysis (n=262)<br/>Residual measurement invariance achieved>]
+                    9[label = <Semantic Analysis (n=262):<br/>Semantic Scale Network analysis<br/>Readbility: Grade level 3.33>]
+                    10[label = <LEBA Short Form (19 Items; n=690)<br/>Based on Item Response Theory>]
+                    }
+                subgraph cluster_2 {
+                      graph[fontname = Helvetica,shape = rectangle]
+                      style = rounded
+                     node[fontname = Helvetica, margin = 0.2,width = 18, height = 2.5, 
+                fixedsize = true, fontsize = 45 ]
+                    6[label = 
+                    <6-Factor solution:<br/>one factor emerged with only two salient loadings>
+                    ]
+                    7[label = 'Rejected']
+                    }
+
+                     edge[fontname = Helvetica,color = black,arrowhead = vee, arrowsize = 1.25]
+                     A ->B
+                     B ->C
+                     C ->D
+                     D ->E
+                E ->1
+                     1 ->2
+                     2 ->3
+                     3 ->4
+                     4 ->5
+                    5->8
+                    8 ->9
+                    9 ->10
+                     E ->6
+                     6 ->7
+
+}")
+
+library(jpeg)
+export_svg(Flowchart1) %>%
+  charToRaw() %>%
+  rsvg() %>%
+  png::writePNG("Manuscript.figures/Flowchart1.jpeg", dpi = 600)
+
+```
+
+```{r participantmap, include =F}
+
+countries <- as.data.frame(tz_tibble[,1])
+countries <- as.data.frame(countries[-1,])
+
+colnames(countries) <- "TZ"
+countries.2 <- as.data.frame(str_split_fixed(countries$TZ, "-", 2))
+countries.2[ ,1][ countries.2[ , 1 ] == "United States " ] <- "USA"
+countries.2[ ,1][ countries.2[ , 1 ] == "United Kingdom " ] <- "UK"
+countries.2[ ,1][ countries.2[ , 1 ] == "Germany " ] <- "Germany"
+countries.2[ ,1][ countries.2[ , 1 ] == "India "  ] <- "India" 
+countries.2[ ,1][ countries.2[ , 1 ] == "France "  ] <- "France" 
+countries.2[ ,1][ countries.2[ , 1 ] == "Switzerland " ] <- "Switzerland"
+countries.2[ ,1][ countries.2[ , 1 ] == "Brazil "  ] <- "Brazil"
+countries.2[ ,1][ countries.2[ , 1 ] == "Netherlands " ] <- "Netherlands"
+countries.2[ ,1][ countries.2[ , 1 ] == "Canada "  ] <- "Canada" 
+countries.2[ ,1][ countries.2[ , 1 ] == "Poland " ] <- "Poland"
+
+country_name <- as.data.frame(unique(countries.2[,1]))
+country_name.2 <- (country_name[1:10,])
+
+thismap = map_data("world")
+
+# Set colors
+colors <- scales::hue_pal()(10)
+thismap <- mutate(thismap, fill = ifelse(region %in% country_name.2, 
+                                         sample(colors, 10), "white"))
+thismap <- within(thismap, fill[region == 'Canada'] <- '#FF62BC')
+thismap <- within(thismap, fill[region == 'Brazil'] <- '#D89000')
+thismap <- within(thismap, fill[region == 'USA'] <- '#00BFC4')
+thismap <- within(thismap, fill[region == 'UK'] <- 'blue')
+thismap <- within(thismap, fill[region == 'Germany'] <- 'Green')
+thismap <- within(thismap, fill[region == 'Netherlands'] <- '#A3A500')
+thismap <- within(thismap, fill[region == 'Poland'] <- 'Pink')
+thismap <- within(thismap, fill[region == 'France'] <- 'Orange')
+thismap <- within(thismap, fill[region == 'Switzerland'] <- 'purple')
+
+label.data <-thismap[thismap$region %in% country_name.2,]
+
+USA <- subset(label.data, region == "USA")
+UK <- subset(label.data, region == "UK")
+Germany <- subset(label.data, region == "Germany")
+India <- subset(label.data, region == "India")
+France <- subset(label.data, region == "France")
+Switzerland <- subset(label.data, region == "Switzerland")
+Brazil <- subset(label.data, region == "Brazil")
+Netherlands <- subset(label.data, region == "Netherlands")
+Canada <- subset(label.data, region == "Canada")
+Poland <- subset(label.data, region == "Poland")
+
+label.data.2 <- rbind(USA[386,],UK[1,],Germany[1,],India[327,],France[1,],
+                      Switzerland[1,],Brazil[33,],Netherlands[1,],Canada[5000,],Poland[1,])
+
+label.data.2[1,1] <- -100
+label.data.2[1,2] <- 40
+label.data.2[2,2] <- 52
+label.data.2[9,2] <- 55
+label.data.2[7,2] <- -9
+label.data.2[7,1] <- -48
+label.data.2[4,2] <- 25
+label.data.2[4,1] <- 84
+
+label.data.2[5,2] <- 46
+label.data.2[5,1] <- 6
+label.data.2[8,2] <- 51
+
+distribution <- ggplot(thismap, aes(long, lat, fill = fill, group=group)) + 
+  geom_polygon(colour="gray", size =.3) +  
+  scale_fill_identity()+apatheme+ theme(
+    axis.text.x = element_blank(),
+                                        axis.text.y = element_blank(),
+                                        axis.title.x = element_blank(),
+                                        axis.title.y = element_blank(),
+                                        plot.title = element_blank(),
+                                        axis.line.x = element_blank(),
+                                        axis.line.y = element_blank(),
+                                        axis.ticks = element_blank())+
+  # xlab("Longitude") + ylab("Latitude")+
+  ggrepel::geom_text_repel(data= label.data.2,aes(x=long, y= lat, label=region),inherit.aes = F,
+            color = "darkblue", fontface = "bold", stat = 'identity',
+            position = "identity")
+
+ggsave("Manuscript.figures/distribution.png", distribution, width = 12, height = 6, dpi = 600, bg ="white")
+
+```
+
+## Data Collection
+
+A quantitative cross-sectional fully anonymous online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
+Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) of a Comic co-released with the survey[@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux].
+The landing page of the on-line survey had the explanatory statements It was mentioned in the explanatory statement that their participation was voluntary and that they could withdraw from participation anytime without being penalized.
+At the beginning of the survey, for the adult participants (>18 years) consent was recorded digitally.
+Underaged participants (<18 years) were urged to obtain assent from their parents/legal guardians, before filling in the survey.
+The survey took around 15 to 20 minutes for which they were not compensated.
+As a part of the demographics participants provided information regarding age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language as single-item demographic variables.
+The demographic characteristics of our sample are given in Table \@ref(tab:demotab).To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention.
+What is 4+5?").
+Participants needed to confirm that they were participating the survey for the first time.
+Questions incorporating retrospective recall were all aligned to the period of "past four weeks".
+At first we collected data for from `r nrow(EFA.descriptives)` participants (EFA sample).
+Next, we collected data from another `r nrow(CFA.descriptives)` participants (CFA sample) making a total sample of `r nrow(desctable.data)`.
+The data analysed in this study was collected between 17 May 2021 and 3 September 2021.
+
+```{r demotab, warning=F, message=F}
+desc_kable  %>% kable_styling(latex_options = c("scale_down")) %>% landscape()
+```
+
+## Analytic Strategies
+
+Figure \@ref(fig:FlowchartFig) summarizes the steps of our psychometric analysis.
+In our analysis we used R (version 4.1.0).
+In the item generation and selection phase we had developed a item pool of 48 items with six-pont Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always).
+Our purpose was to capture light exposure related behaviour.
+In that context, the first two response options: "Does not apply/I don't know" and "Never" were providing similar information.
+As such we collapsed them into one, making it a 5 point Likert type response format.
+We conducted an initial item analysis and proceed to the EFA with all 48 items (EFA sample;n=`r nrow(EFA.descriptives)`).
+Prior to the EFA, necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
+Our data violated both the univariate and multivariate normality assumptions.
+Due to these violations and the ordinal nature of our response data, For EFA we used  polychoric correlation matrix and employed principal axis (PA) as  factor extraction method with varimax rotation [@desjardinsHandbookEducationalMeasurement2018;@watkinsStepbyStepGuideExploratory2020].
+The obtained latent structure was confirmed by another factor extraction method- "minimum residuals extraction" as well.
+We used a combination of factor identification method including scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
+To determine the simple latent structure, we followed the common guidelines : (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading > .3 across factors [@bandalosFactorAnalysisExploratory2018].
+We also conducted a EFA on non-merged response options data (Supp.
+Table \@ref(tab:efaunmerged)) and rejected the latent structure obtained as the factors were less interpretable.
+
+For reliability estimation we used internal consistency reliability coefficient ordinal alpha.
+Though  Cronbach's alpha coefficient is widely used for estimating internal consistency, it has a tendency to deflate the estimates for  Likert type data since calculation is based on pearson-correlation matrix which requires response data to be continuous of nature [@gadermann2012estimating; @zumbo2007ordinal].
+Subsequently to get  better estimates of reliability  we reported ordinal alpha for each factors that used polychoric-correlation matrix and assumed that the responses data were ordered in nature instead of continuous [@zumbo2007ordinal].
+We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$  coefficient which is a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
+Both ordinal alpha and McDonald's $\omega_t$ coefficient value range from 0 to 1 and higher value represents better reliability.
+
+To validated the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with robust weighted least square (WLSMV) estimator [@desjardinsHandbookEducationalMeasurement2018] on a separate sample (CFA sample;n=`r nrow(CFA.descriptives)`).
+We assessed the model fit using common model fit guidelines: (i) Reporting of $\chi^2$ test statistics (A non-significant test statistics is required to reflect model fit) (ii) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (iii) RMSEA (close to .06 or below), (iv) SRMR (close to .08 or below) to estimate the model fit [@huCutoffCriteriaFit1999; @schumacker2004beginner].
+However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015] and SRMR does not work well with ordinal data [@RN1272] As such, we judged the model fit using  CFI, TLI, SRMR and RMSEA.
+
+Using the CFA sample (n=`r nrow(CFA.descriptives)`) we assessed the measurement invariance (MI) of our construct between native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non-non native English speakers (n=`r invariance.data.descriptives.count[2,2]`) using the validated latent structure obtained in CFA.
+MI evaluates whether a construct has the psychometric equivalence and same meaning across groups or measurement occasions [@putnick2016measurement;@klinePrinciplesPracticeStructural2015].
+We used  structural equation modelling framework to assess the measurement invariance.
+We successively compared four nested models:  configural, metric, scalar, and residual models using the $\chi^2$ difference test ($\Delta \chi^2$).
+Among MI models, configural model is the least restrictive model and residual model is the most restrictive model.
+A non-significant $\Delta \chi^2$ test between two nested measurement invariance models indicates mode fit does not significantly decrease for the superior model [@dimitrov2010testing] thus allowing the superior invariance model to be accepted.
+[@widaman1997exploring].
+
+We also analysed possible semantic overlap of our developed tool using "Semantic Scale Network" (SSN) engine [@rosenbusch2020semantic].
+The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic].
+Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy.
+Additionally, To identify the educational grade level required to understand the items in our tool we subjected the tool to Flesch-Kincaid Grade Level [@flesch1948new]
+
+Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA.
+We fitted each factor of LEBA using the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =`r nrow(sem.data)`).
+IRT assess the item quality by estimating item difficulty, item discrimination, item information, and Test information [@bakerBasicsItemResponse2017].
+Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait level ($\theta$), and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
+Here, we reported  the item discrimination parameter and categorize the items according to the suggestions of @bakerBasicsItemResponse2017 : none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70.
+We discarded the items with relatively flat item information curve (information <.2) to develop the short form of LEBA.
+We also assessed the precision of the short LEBA using Test information curve (TIC).
+TIC  indicates the amount of information an the full-scale carry along the latent trait continuum.
+Item fit and person-fit of the fitted model were also analyzed to gather more evidence on validity and meaningfulness of our Tool [@desjardinsHandbookEducationalMeasurement2018].
+Item-fit was evaluated using  the RMSEA value obtained from Signed-$\chi^2$ index implementation, RMSEA value $\le$.06 was considered adequate item fit.
+Person fit was estimated using standardized fit index Zh statistics [@drasgow1985appropriateness].
+Zh < -2 was be considered as a misfit [@drasgow1985appropriateness].
+
+```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='100%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/Flowchart1.jpeg', dpi = 800 )
+```
+
+## Ethical approval
+
+By reason of using fully anonymous online survey data, the present research project does not fall under the scope of the Human Research Act, making an authorisation from the ethics committee redundant.
+Nevertheless, the cantonal ethics commission (Ethikkommission Nordwest- und Zentralschweiz, EKNZ) reviewed our proposition (project ID Req-2021-00488) and issued an official clarification of responsibility.
+
+## Data Availability
+
+The present article is a fully reproducible open-access “R Markdown” document.
+All code and data underlying this article – along with two versions of the LEBA questionnaire (full and short) and online survey implementation templates on common survey platforms – will be available under open-access licence (CC-BY-NC-ND) on a public [GitHub repository](https://github.com/leba-instrument).
+
+# Results
+
+## Initial development of items
+
+After reviewing the literature, we identified several light exposure related scale.
+However, no scales specifically measuring the behavioural component of light exposure were found (\@ref(tab:reltab2).
+As such, we developed a comprehensive item pool of 48 items.
+The whole list of 48 items were then judged  based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by an expert panel.
+The expert panel composed of all authors and researchers from the fields of chronobiology, light research, neuroscience and psychology.
+The panel members independently judged each of the items in terms of their relevance and representativeness and suggested required modification, if there is any.
+The author team acknowledged the suggestions and amended the items as required thus creating a 48-item scale
+
+## Large-scale  survey of instruments
+
+### Participants
+
+Table \@ref(tab:demotab) summarizes the survey participants' demographic characteristics.
+Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses.
+(XX??) participants were excluded from analysis due to not passing at least one of the "attention check" items.
+For exploring initial factor structure (EFA), a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013].For estimating the sample size for the confirmatory factor analysis (CFA) we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per item is required to earn trustworthiness of the result.
+Our sample size exceeds these requirements.
+We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones).
+Participants reported a diverse range of geographic location
+Participants indicated filling out the online survey from a diverse range of geographic locations. The ten most common country and time zone combinations included:
+
+```{r fig.cap="Countries with Highest Responses", out.height= '100%', out.width= '100%'}
+knitr::include_graphics('Manuscript.figures/distribution.png', dpi = 800 )
+```
+
+- `r tz_tibble[2,1]`:     `r tz_tibble[2,2]`
+- `r tz_tibble[3,1]`:     `r tz_tibble[3,2]`
+- `r tz_tibble[4,1]`:     `r tz_tibble[4,2]`
+- `r tz_tibble[5,1]`:     `r tz_tibble[5,2]`
+- `r tz_tibble[6,1]`:     `r tz_tibble[6,2]`
+- `r tz_tibble[7,1]`:     `r tz_tibble[7,2]`
+- `r tz_tibble[8,1]`:     `r tz_tibble[8,2]`
+- `r tz_tibble[9,1]`:     `r tz_tibble[9,2]`
+- `r tz_tibble[10,1]`:    `r tz_tibble[10,2]`
+- `r tz_tibble[11,1]`:    `r tz_tibble[11,2]`
+
+For a complete list of geographic locations, see Suppl. Table \@ref(tab:tztable).
+
+Age among all participants ranged from `r min(desctable.data$slypos_demographics_age)` years to `r max(desctable.data$slypos_demographics_age)` years [EFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
+EFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
+EFA Sample"])`; CFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
+CFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
+CFA Sample"])`], with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 0)` years of age [Overall: *M* = `r mean(desctable.data$slypos_demographics_age)`, *SD* = `r sd(desctable.data$slypos_demographics_age)`; EFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
+EFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
+EFA Sample"])`; CFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
+CFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
+CFA Sample"])`].
+In total `r desc_tibble[3,2]` of the participants indicated female sex [EFA: `r desc_tibble[3,3]`; CFA: `r desc_tibble[3,4]`], `r desc_tibble[4,2]` indicated male [EFA: `r desc_tibble[4,3]`; CFA: `r desc_tibble[4,4]`] and `r desc_tibble[5,2]` indicated other sex [EFA: `r desc_tibble[5,3]`, CFA: `r desc_tibble[5,4]`].
+Overall, `r desc_tibble[6,2]` [EFA: `r desc_tibble[6,3]`; CFA: `r desc_tibble[6,4]`] participants indicated a gender-variant identity.
+In a "Yes/No" question regarding native language, `r desc_tibble[7,2]` of respondents [EFA: `r desc_tibble[7,3]`; CFA: `r desc_tibble[7,4]`] indicated to be native English speakers.
+For their "Occupational Status", more than half of the overall sample reported that they currently work [Overall: `r desc_tibble[9,2]`; EFA: `r desc_tibble[9,3]`; CFA: `r desc_tibble[9,4]`], whereas `r desc_tibble[10,2]` [EFA: `r desc_tibble[10,3]`; CFA: `r desc_tibble[10,4]`] reported that they go to school and `r desc_tibble[11,2]` [EFA: `r desc_tibble[11,3]`; CFA: `r desc_tibble[11,4]`] responded that they do "Neither".
+With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` [EFA: `r desc_tibble[13,3]`; CFA: `r desc_tibble[13,4]`] of the participants indicated that they were in a home office/ home schooling setting, while `r desc_tibble[14,2]` overall [EFA: `r desc_tibble[14,3]` ; CFA: `r desc_tibble[14,4]`] reported face-to-face work/schooling.
+Lastly, `r desc_tibble[15,2]` overall [EFA: `r desc_tibble[15,3]` ; CFA: `r desc_tibble[15,4]`] reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]` overall [EFA: `r desc_tibble[16,3]`; CFA: `r desc_tibble[16,4]`] filled in the "Neither (no work or school, or on vacation)" response option.
+We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable "Age" and Pearson's $\chi^2$ test for all other categorical variables via the gtsummary R package's "add_p" function [@sjoberg2021] .
+The p-values were corrected for multiple testing applying false discovery rate (FDR) via the "add_q" function of the same package.
+After p-value (FDR) correction for multiple testing, none of the demographic variables were significantly different between the EFA sample and the CFA sample (all q-values *q* $\ge$ `r min(desc_tibble$"**q-value**", na.rm=T)`).
 

### 2022-02-10 manuscript.Rmd
rafael's tibble is now banched.

@@
 Participants reported a diverse range of geographic location
-Participants indicated filling out the online survey from a diverse range of geographic locations. The ten most common country and time zone combinations included:
-
-```{r fig.cap="Countries with Highest Responses", out.height= '100%', out.width= '100%'}
+Participants indicated filling out the online survey from a diverse range of geographic locations.
+Figure \@ref(fig:partmap) depicts the top ten countries with highest participation in our survey.For a complete list of geographic locations, see Suppl.
+Table \@ref(tab:tztable).
+
+```{r partmap, fig.cap="Countries with Highest Responses", out.height= '100%', out.width= '100%'}
 knitr::include_graphics('Manuscript.figures/distribution.png', dpi = 800 )
@@
 
-- `r tz_tibble[2,1]`:     `r tz_tibble[2,2]`
-- `r tz_tibble[3,1]`:     `r tz_tibble[3,2]`
-- `r tz_tibble[4,1]`:     `r tz_tibble[4,2]`
-- `r tz_tibble[5,1]`:     `r tz_tibble[5,2]`
-- `r tz_tibble[6,1]`:     `r tz_tibble[6,2]`
-- `r tz_tibble[7,1]`:     `r tz_tibble[7,2]`
-- `r tz_tibble[8,1]`:     `r tz_tibble[8,2]`
-- `r tz_tibble[9,1]`:     `r tz_tibble[9,2]`
-- `r tz_tibble[10,1]`:    `r tz_tibble[10,2]`
-- `r tz_tibble[11,1]`:    `r tz_tibble[11,2]`
-
-For a complete list of geographic locations, see Suppl. Table \@ref(tab:tztable).
+```{r rafael2, eval=FALSE, include=FALSE}
+# - `r tz_tibble[2,1]`:     `r tz_tibble[2,2]`
+# - `r tz_tibble[3,1]`:     `r tz_tibble[3,2]`
+# - `r tz_tibble[4,1]`:     `r tz_tibble[4,2]`
+# - `r tz_tibble[5,1]`:     `r tz_tibble[5,2]`
+# - `r tz_tibble[6,1]`:     `r tz_tibble[6,2]`
+# - `r tz_tibble[7,1]`:     `r tz_tibble[7,2]`
+# - `r tz_tibble[8,1]`:     `r tz_tibble[8,2]`
+# - `r tz_tibble[9,1]`:     `r tz_tibble[9,2]`
+# - `r tz_tibble[10,1]`:    `r tz_tibble[10,2]`
+# - `r tz_tibble[11,1]`:    `r tz_tibble[11,2]`
+```
 

### 2022-02-16 appendix-1.Rmd
Typo corrected

@@
 ```{r MinResTab}
-papaja::apa_table(minresTab,  caption = "Factor loadings and communality of the retained items (Minmum Residual)", note = "Only loading higher than .30 is reported", longtable=T, font_size = "footnotesize")
+papaja::apa_table(minresTab,  caption = "Factor loadings and communality of the retained items (Minimum Residual)", note = "Only loading higher than .30 is reported", longtable=T, font_size = "footnotesize")
 ```
@@
 ```{r sixFacTab}
-papaja::apa_table(sixFac,  caption = "Factor loadings and communality of the retained items(six factor)", note = "Only loading higher than .30 is reported; Sixth factor has only two salient loadings",longtable =T, font_size = "footnotesize")
+papaja::apa_table(sixFac,  caption = "Factor loadings and communality of the retained items (six factor)", note = "Only loading higher than .30 is reported; Sixth factor has only two salient loadings",longtable =T, font_size = "footnotesize")
 ```
@@
 ```{r EFAsix}
-apa_table(efa.table.2, caption = "Factor loadings and communality of the retained items in six factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T, font_size = "footnotesize")
+apa_table(efa.table.2, caption = "Factor loadings and communality of the retained items in six factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported, Sixth factor has only two salient loadings", longtable =T, font_size = "footnotesize")
 ```
@@
 ```{r unmerged-data, include =F}
-unmerged <- read_excel("Table_raw/LEBA_unmerged_fa.xlsx")
+unmerged <- readxl::read_excel("Table_raw/LEBA_unmerged_fa.xlsx")
 ```
@@
 ```{r unmertab}
-apa_table(unmerged , longtable =T, font_size = "footnotesize")
+apa_table(unmerged , longtable =T, font_size = "footnotesize", caption = "Five factor obtained from the unmerged data.")
 ```
 
-```{r IF, echo=FALSE, fig.align='center', fig.cap='Item information curve ', out.width='100%'}
+```{r IF, echo=FALSE, fig.align='center', fig.cap='Item information curve. Five items (1, 25,  38, 30, & 41) had relatively flat information curves ', out.width='100%', out.height='80%'}
 knitr::include_graphics('Manuscript.figures/allitemplots.png', dpi = 300)
-```
-
-```{r F1IF, eval=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F1. Item 16 carried highest information among the three items', include=FALSE, out.height='160%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/F1.itemplots.png', dpi = 600)
-```
-
-```{r F2IF, eval=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F2.
-All items cariied information across the latent trait continuum.
-Item 09 carried the lowest information however its information peak was highr than .20.', include=FALSE, out.height='160%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/F2.itemplots.png',dpi = 600)
-```
-
-```{r F3IF, eval=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F3.
-Item 30 and 41 had relatively flat information curve with a peak lower than .20', include=FALSE, out.height='160%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/F3.itemplots.png',dpi = 600)
-```
-
-```{r F4IF, eval=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F4.
-Item 38 had relatively flat information curve with a peak lower than .20', include=FALSE, out.height='160%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/F4.itemplots.png',dpi = 600)
-```
-
-```{r F5IF, eval=FALSE, echo=FALSE, fig.align='center', fig.cap='Item information curve of LEBA F5.
-Three items: 25, 04, 01 carriedlow information.
-However Item 04 had a bump at the righ side of the center with a curve peak higher than .20.
-Item 01 and 25 had relatively flat information curve with a peak lower than .20', out.height='160%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/F5.itemplots.png',dpi = 600)
 ```

### 2022-02-16 manuscript.Rmd
Typo corrected

@@
 
+```{r demotab, warning=F, message=F}
+desc_kable  %>% kable_styling(latex_options = c("scale_down")) %>% landscape()
+```
+
 A quantitative cross-sectional fully anonymous online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
-Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) of a Comic co-released with the survey[@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux].
-The landing page of the on-line survey had the explanatory statements It was mentioned in the explanatory statement that their participation was voluntary and that they could withdraw from participation anytime without being penalized.
+Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) of a Comic co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux].
+The landing page of the online survey had the explanatory statements where we mentioned participation was voluntary and that respondents could withdraw from participation anytime without being penalized.
 At the beginning of the survey, for the adult participants (>18 years) consent was recorded digitally.
-Underaged participants (<18 years) were urged to obtain assent from their parents/legal guardians, before filling in the survey.
-The survey took around 15 to 20 minutes for which they were not compensated.
-As a part of the demographics participants provided information regarding age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language as single-item demographic variables.
+Underaged participants (<18 years) were urged to obtain assent from their parents/legal guardians.
+The survey took around 15 to 20 minutes and participants were not compensated.
+As a part of the demographic information participants provided information regarding age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language.
 The demographic characteristics of our sample are given in Table \@ref(tab:demotab).To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention.
@@
 The data analysed in this study was collected between 17 May 2021 and 3 September 2021.
-
-```{r demotab, warning=F, message=F}
-desc_kable  %>% kable_styling(latex_options = c("scale_down")) %>% landscape()
-```
-
 ## Analytic Strategies
@@
 In our analysis we used R (version 4.1.0).
-In the item generation and selection phase we had developed a item pool of 48 items with six-pont Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always).
+In the item generation and selection phase we had developed a item pool of 48 items with six-point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always).
 Our purpose was to capture light exposure related behaviour.
@@
 As such we collapsed them into one, making it a 5 point Likert type response format.
-We conducted an initial item analysis and proceed to the EFA with all 48 items (EFA sample;n=`r nrow(EFA.descriptives)`).
-Prior to the EFA, necessary assumptions of EFA, including sample adequacy, normality assumptions, quality of correlation matrix, were assessed.
+We conducted an initial item analysis and proceed to the exploratory factor analysis (EFA) with all 48 items (EFA sample;n=`r nrow(EFA.descriptives)`).
+Prior to the EFA, necessary assumptions, including sample adequacy, normality assumptions, quality of correlation matrix were assessed.
 Our data violated both the univariate and multivariate normality assumptions.
-Due to these violations and the ordinal nature of our response data, For EFA we used  polychoric correlation matrix and employed principal axis (PA) as  factor extraction method with varimax rotation [@desjardinsHandbookEducationalMeasurement2018;@watkinsStepbyStepGuideExploratory2020].
-The obtained latent structure was confirmed by another factor extraction method- "minimum residuals extraction" as well.
+Due to these violations and the ordinal nature of our response data, in EFA we used  polychoric correlation matrix and employed principal axis (PA) as  factor extraction method with varimax rotation [@desjardinsHandbookEducationalMeasurement2018;@watkinsStepbyStepGuideExploratory2020].
 We used a combination of factor identification method including scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
-To determine the simple latent structure, we followed the common guidelines : (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading > .3 across factors [@bandalosFactorAnalysisExploratory2018].
+To determine the latent structure, we followed the common guidelines : (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading > .3 across factors [@bandalosFactorAnalysisExploratory2018].
 We also conducted a EFA on non-merged response options data (Supp.
@@
 For reliability estimation we used internal consistency reliability coefficient ordinal alpha.
-Though  Cronbach's alpha coefficient is widely used for estimating internal consistency, it has a tendency to deflate the estimates for  Likert type data since calculation is based on pearson-correlation matrix which requires response data to be continuous of nature [@gadermann2012estimating; @zumbo2007ordinal].
-Subsequently to get  better estimates of reliability  we reported ordinal alpha for each factors that used polychoric-correlation matrix and assumed that the responses data were ordered in nature instead of continuous [@zumbo2007ordinal].
+Though  Cronbach's alpha coefficient is widely used for estimating internal consistency, it has a tendency to deflate the estimates for  Likert type data since the calculation is based on pearson-correlation matrix which requires response data to be continuous of nature [@gadermann2012estimating; @zumbo2007ordinal].
+Subsequently to get  better estimates of reliability  we reported ordinal alpha for each factors using polychoric-correlation matrix [@zumbo2007ordinal].
 We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$  coefficient which is a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
@@
 
-To validated the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with robust weighted least square (WLSMV) estimator [@desjardinsHandbookEducationalMeasurement2018] on a separate sample (CFA sample;n=`r nrow(CFA.descriptives)`).
-We assessed the model fit using common model fit guidelines: (i) Reporting of $\chi^2$ test statistics (A non-significant test statistics is required to reflect model fit) (ii) CFI and TLI (CFI/TLI close to .95 or above/ranging between 90-95 and above) (iii) RMSEA (close to .06 or below), (iv) SRMR (close to .08 or below) to estimate the model fit [@huCutoffCriteriaFit1999; @schumacker2004beginner].
+To validated the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with Weighted Last Square with mean and variance adjusted (WLSMV) estimator estimator [@desjardinsHandbookEducationalMeasurement2018] on a separate sample (CFA sample;n=`r nrow(CFA.descriptives)`).
+We assessed the model fit using common model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI):  close to .95 or above/ between 90-95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner].
 However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015] and SRMR does not work well with ordinal data [@RN1272] As such, we judged the model fit using CFI, TLI, SRMR and RMSEA.
 
-Using the CFA sample (n=`r nrow(CFA.descriptives)`) we assessed the measurement invariance (MI) of our construct between native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non-non native English speakers (n=`r invariance.data.descriptives.count[2,2]`) using the validated latent structure obtained in CFA.
-MI evaluates whether a construct has the psychometric equivalence and same meaning across groups or measurement occasions [@putnick2016measurement;@klinePrinciplesPracticeStructural2015].
+We assessed the measurement invariance (MI) of our construct between native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non-non native English speakers (n=`r invariance.data.descriptives.count[2,2]`) among the CFA sample (n=`r nrow(CFA.descriptives)`).
+MI evaluates whether a construct has the psychometric equivalence and same meaning across groups [@putnick2016measurement;@klinePrinciplesPracticeStructural2015].
 We used  structural equation modelling framework to assess the measurement invariance.
@@
 We fitted each factor of LEBA using the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =`r nrow(sem.data)`).
-IRT assess the item quality by estimating item difficulty, item discrimination, item information, and Test information [@bakerBasicsItemResponse2017].
-Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait level ($\theta$), and item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
+IRT assesses the item quality by estimating item discrimination, item difficulty, item information, and test information [@bakerBasicsItemResponse2017].
+Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait level ($\theta$).
+Item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
 Here, we reported  the item discrimination parameter and categorize the items according to the suggestions of @bakerBasicsItemResponse2017 : none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70.
@@
 TIC  indicates the amount of information an the full-scale carry along the latent trait continuum.
-Item fit and person-fit of the fitted model were also analyzed to gather more evidence on validity and meaningfulness of our Tool [@desjardinsHandbookEducationalMeasurement2018].
-Item-fit was evaluated using  the RMSEA value obtained from Signed-$\chi^2$ index implementation, RMSEA value $\le$.06 was considered adequate item fit.
+Item fit and person fit of the fitted IRT models were also analyzed to gather more evidence on validity and meaningfulness of our Tool [@desjardinsHandbookEducationalMeasurement2018].
+Item fit was evaluated using  the RMSEA value obtained from Signed-$\chi^2$ index implementation, RMSEA value $\le$.06 was considered adequate item fit.
 Person fit was estimated using standardized fit index Zh statistics [@drasgow1985appropriateness].
@@
 After reviewing the literature, we identified several light exposure related scale.
-However, no scales specifically measuring the behavioural component of light exposure were found (\@ref(tab:reltab2).
-As such, we developed a comprehensive item pool of 48 items.
-The whole list of 48 items were then judged  based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by an expert panel.
+However, no scales specifically measuring the behavioural component of light exposure were found (Table \@ref(tab:reltab2).
+As such, all authors in collaboration of an expert panel developed a comprehensive item pool of 48 items.
 The expert panel composed of all authors and researchers from the fields of chronobiology, light research, neuroscience and psychology.
+The 48 items were then judged  based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by the expert panel.
 The panel members independently judged each of the items in terms of their relevance and representativeness and suggested required modification, if there is any.
@@
 (XX??) participants were excluded from analysis due to not passing at least one of the "attention check" items.
-For exploring initial factor structure (EFA), a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013].For estimating the sample size for the confirmatory factor analysis (CFA) we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per item is required to earn trustworthiness of the result.
-Our sample size exceeds these requirements.
-We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones).
-Participants reported a diverse range of geographic location
+For EFA, a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013].
+To assess sampling adequacy for CFA, we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per item is required to earn trustworthiness of the result.
+Both our EFA and CFA sample size exceeded these requirements.
+We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones).Participants reported a diverse range of geographic location
 Participants indicated filling out the online survey from a diverse range of geographic locations.
@@
 ```{r partmap, fig.cap="Countries with Highest Responses", out.height= '100%', out.width= '100%'}
-knitr::include_graphics('Manuscript.figures/distribution.png', dpi = 800 )
+knitr::include_graphics('Manuscript.figures/distribution.png', dpi = 300 )
 ```
@@
 
-Age among all participants ranged from `r min(desctable.data$slypos_demographics_age)` years to `r max(desctable.data$slypos_demographics_age)` years [EFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
+Participants in our survey aged between  `r min(desctable.data$slypos_demographics_age)`  to `r max(desctable.data$slypos_demographics_age)` years [EFA sample: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
 EFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
-EFA Sample"])`; CFA: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
+EFA Sample"])`; CFA sample: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
 CFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`], with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 0)` years of age [Overall: *M* = `r mean(desctable.data$slypos_demographics_age)`, *SD* = `r sd(desctable.data$slypos_demographics_age)`; EFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
+CFA Sample"])`], with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 2)` years of age [Overall: *M* = `r mean(desctable.data$slypos_demographics_age)`, *SD* = `r sd(desctable.data$slypos_demographics_age)`; EFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
 EFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
@@
 Some of the items were skewed with high Kurtosis values.
-Our data violated both univariate normality (Shapiro-Wilk statistics; [@shapiroAnalysisVarianceTest1965]) and multivariate normality assumptions [Marida's test;[@mardiaMeasuresMultivariateSkewness1970]].
+Our data violated both univariate normality [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970].
 Multivariate skew was  `r printnum(mardia$b1p)` (p <0.001) and multivariate kurtosis was `r printnum(mardia$b2p)` (p <0.001).
@@
 Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy [@kaiserIndexFactorialSimplicity1974] .
-The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cutoff value (.50) indicating a mediocre sample [@hutchesonMultivariateSocialScientist1999].
-Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001 indicated the correlations between items are adequate for the EFA.
-However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than .30.
-The absolute value of inter-item correlation ranged between `r min.cor` to `r max.cor`.
+The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cutoff value (.50) indicating adequate sample size [@hutchesonMultivariateSocialScientist1999].
+Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001 indicated the correlations between items are adequate for conducting the EFA.
+However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than |.30|.
+The inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`.
 Figure \@ref(fig:figCor) depicts the correlation matrix.
@@
 
-corplot <- ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", 
+corplot <- ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", legend.title = "Correlation",
            ggtheme = ggplot2::theme_minimal(),tl.srt = 90,colors = c("#E64B35FF", "white", "#3C5488FF") )+
@@
 
-(ref:figCor) Inter item polychoric correlation coefficients for the 48 items. 4.9 % inter-item correlation coefficients were higher than .30
+(ref:figCor) Inter-item polychoric correlation coefficients for the 48 items. 4.9 % inter-item correlation coefficients were higher than |.30|
 
@@
 Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution.
-However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (Table \@ref(tab:factormp)) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution.
+However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (Table \@ref(tab:map)) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution.
 As a result, we tested both five-factor and six-factor solutions.
@@
 (cross-loading items and poor factor loading (<.30) items).
-Finally, a five-factor EFA solution with 25 items was accepted with low RMSR = 0.08 [@brownConfirmatoryFactorAnalysis2015], all factor-loading higher than .30 and no cross-loading greater than .30.
+Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30.
 We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (Sup.Table \@ref(tab:MinResTab)).
@@
 The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`.
-Figure \@ref(fig:EFAplot)(A) depicts the obtained five factor structure.
+Figure \@ref(fig:efagtPic) depicts the data distribution and endorsement pattern for the included 25 items.
+Figure \@ref(fig:EFAplot)(A) depicts the five factor structure obtained in EFA.
 However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:EFAplot)(B)) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring.
@@
 
-In the five-factor solution, the first factor contained three items and explained `r apa(var1,2,F)`% of the total variance with a  internal reliability coefficient ordinal $\alpha$ = `r apa(F1.alpha,2,F)`.
-All the items in this factor stemmed from the individual's preference to use blue light filters in different light environments.
-The second factor contained six items and explained `r apa(var2,2,F)`% of the total variance with a  internal reliability coefficient ordinal $\alpha$ = `r apa(F2.alpha,2,F)`.
-Items under this factor commonly investigated an individual's hours spent outdoor.
+In the five-factor solution, the first factor contained three items and explained `r apa(var1,2,F)`% of the total variance with an internal reliability coefficient ordinal $\alpha$ = `r apa(F1.alpha,2,F)`.
+All the items in this factor stemmed from the individual's preference of using blue light filters in different light environments.
+The second factor contained six items and explained `r apa(var2,2,F)`% of the total variance with an internal reliability coefficient ordinal $\alpha$ = `r apa(F2.alpha,2,F)`.
+Items under this factor investigated individuals' hours spent outdoor.
 The third factor contained five items and explained `r apa(var3,2,F)`% of the total variance.
-Items under this factor dealt with the specific behaviors pertaining to using phone and smart-watch in bed.
+Items under this factor dealt with the specific behaviours pertaining to using phone and smart-watch in bed.
 The internal consistency reliability coefficient was, ordinal $\alpha$ = `r apa(F3.alpha,2,F)`.
 The fourth factor contained five items and explained `r apa(var4,2,F)`% of the total variance with an internal consistency coefficient, ordinal $\alpha$ = `r apa(F4.alpha,2,F)`.
-These five items investigated the behaviors related to individual's light exposure before bedtime.
+These five items investigated the behaviours related to individual's light exposure before bedtime.
 Lastly, the fifth factor contained six items and explained `r apa(var5,2,F)`% of the total variance.
-This factor  captured individual's morning and daytime light exposure related behavior.
+This factor  captured individual's morning and daytime light exposure related behaviour.
 The  internal consistency reliability was, ordinal $\alpha$ = `r apa(F5.alpha,2,F)` .
 It is essential to attain a balance between psychometric properties and interpretability of the common themes when exploring the latent structure.
-As all of the emerged factors are highly interpretable and relevant towards our aim to capture light exposure related behavior, regardless of the apparent low reliability of the fifth factor, we retain all the five-factors with 23 items for our confirmatory factor analysis (CFA).
+As all of the emerged factors are highly interpretable and relevant towards our aim to capture light exposure related behaviour, regardless of the apparent low reliability of the fifth factor, we retain all the five-factors with 23 items for our confirmatory factor analysis (CFA).
 Two items showed negative factor-loading (items 44 and 21).
-Upon inspection, it was understood that these items are negatively correlated to the common theme, and thus in the CFA analysis, we reversed the response code for these two items.
-Figure \@ref(fig:gtPic) depicts the data distribution and endorsement pattern for the included items in our LEBA tool for both the EFA and CFA sample.
+Upon inspection, it was understood that these items are negatively correlated to the respective common theme, and thus in the CFA analysis, we reverse coded these two items.
 
@@
 ```{r eval=FALSE, include=FALSE}
-#This chunk holds codes for creating 'gtExtra' based descriptive figures (EFA=CFA); 
+#This chunk holds codes for creating 'gtExtra' based descriptive figures (EFA+CFA); 
 #Not included in the manuscript
@@
 Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`,[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 [`r Hmisc::label(sem.data$item32)`;`r Hmisc::label(sem.data$item33)`] and 16-17 [`r Hmisc::label(sem.data$item16)`;`r Hmisc::label(sem.data$item17)`].
-Items pair 32-33 stemed from the preference of dimming electric device's brightness before bed time and items pair 16 and 19 stemed from the preference of using blue filtering or colored glasses during the daytime.
+Items pair 32-33 stemmed from the preference of dimming electric device's brightness before bed time and items pair 16 and 19 stemmed from the preference of using blue filtering or coloured glasses during the daytime.
 Nevertheless, SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`).
-Further by allowing one pair of items (30-41) [`r Hmisc::label(sem.data$item30)`;`r Hmisc::label(sem.data$item41)`] to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR value (SRMR = `r apa(fit.2[10],2,F)`) was also close to the suggestions of @huCutoffCriteriaFit1999.
+Further by allowing one pair of items (30-41) [`r Hmisc::label(sem.data$item30)`;`r Hmisc::label(sem.data$item41)`] to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained the best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]).
 Internal consistency ordinal $\alpha$ for the five factors of LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)` respectively.
@@
 Figure \@ref(fig:figcfa) depicts the obtained CFA structure.
+Figure \@ref(fig:cfagtPic) depicts the data distribution and endorsement pattern of the retained 23 items in our CFA sample.
 
@@
 
-In our CFA sample we had `r mi.count[1,2]`  **native English speakers** and `r mi.count[2,2]` **non-native English speakers**  (For a detailed description these two groups see Sup.
+In our CFA sample we had `r mi.count[1,2]`  native English speakers and `r mi.count[2,2]` non-native English speakers  (For a detailed description these two groups see Sup.
 Table \@ref(tab:midesp) ).
@@
 Item discrimination parameters of our tool fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$).
-Examination of the item information curve (Sup.fig \@ref(fig:IF)) indicated 5 items (1, 25,  38, 30, & 41) had relatively flat information curves (I($\theta$) <.20) thus discarded creating a short form of LEBA with 5 factors and 18 items.
+Examination of the item information curve (Sup.fig \@ref(fig:IF)) indicated five items (1, 25,  38, 30, & 41) had relatively flat information curves (I($\theta$) <.20).
+We discarded those items which yielded a short form of LEBA with 5 factors and 18 items.
 
@@
 
-We treated each factor of short-LEBA as an unidmensional construct and obtain 5 TICs (Figure \@ref(fig:Testinfo)).
-These information curves indicated except the first and fifth factors, the other three factor's TICs are roughly centered on the center of the trait continuum ($\theta$).The first and fifth factor had a peak to the right side of the center of latent trait.Thus we conferred the LEBA tool estimated the light exposure related behavior with precision near the center of trait continuum for 2nd, 3rd and 4th factors and near the right side of the center of trait continuum for 1st and 5th factors [@bakerBasicsItemResponse2017].
+We treated each factor of short-LEBA as an unidimensional construct and obtain 5 TICs (Figure \@ref(fig:Testinfo)).
+These information curves indicated except the first and fifth factors, the other three factor's TICs are roughly centred on the centre of the trait continuum ($\theta$).The first and fifth factor had a peak to the right side of the centre of latent trait.Thus we conferred the LEBA tool estimated the light exposure related behaviour with precision near the centre of trait continuum for 2nd, 3rd and 4th factors and near the right side of the centre of trait continuum for 1st and 5th factors [@bakerBasicsItemResponse2017].
 
 Table \@ref(tab:itemfittab) summarizes the item fit indexes of the items.
-All of the items had RMSEA value $\le$.06 indicating adequate fit.
-Sup.Figure \@ref(fig:personfit) depicts the person fit of out fitted models.Fig indicates the person fit Zh statistics histogram.
-Zh statistics are larger than -2 for most participants, suggesting a good fit of the selected IRT models.
+All of the items had RMSEA value $\le$.06 indicating adequate fit of the items.
+Sup.Figure \@ref(fig:personfit) depicts the person fit Zh statistics histogram of out fitted models.
+Zh statistics are larger than -2 for most participants, suggesting a good person fit of the selected IRT models.
 
@@
 
-Lastly, we developed a short-LEBA (n=19) using IRT analysis.
+Lastly, we developed a short-LEBA (n=18) using IRT analysis.
 We fitted a graded response model model to the combined EFA and CFA sample (n =`r nrow(data)`).

### 2022-02-16 manuscript.Rmd
Seceond check on Manual's Standard

@@
   An expert panel prepared the initial 48 item pool spanning different light exposure related behaviors.
-Responses, consisting rating the frequency of engaging in the per-item behavior on a 5-point Likert type scale were  collected in an online survey yielding responses from an international sample (690 completed responses, 74 countries, 28 time zones).
+Responses, consisting rating the frequency of engaging in the per-item behavior on a 5-point Likert type scale were  collected in an online survey yielding responses from a geographically unconstrained sample (690 completed responses, 74 countries, 28 time zones).
 Exploratory factor analysis (EFA) on an initial subset of our sample (n=428) rendered a five-factor solution with 25 items (Wearing blue light filters, spending time outdoors, using phone and smart-watch in bed, using light before bedtime, using light in the morning and during daytime).
@@
 
-                    A[label = 'Initial Development of 48 Items'] 
-                    B[label = 'Large Scale Survey (n=690)']
-                    C[label = 'Initial Item Analysis']
-                    D[label = 'Exploratory Factor Analysis (48 items; n=428)']
+                    A[label = 'Initial development of 48 items'] 
+                    B[label = 'Large scale survey (n=690)']
+                    C[label = 'Initial item analysis']
+                    D[label = 'Exploratory factor analysis (48 items; n=428)']
 
@@
                     E[label = 
-                    <Factor Identification<br/>Scree Plot: 6 Factors<br/>Minimum Average Partial Method: 5 Factors<br/>Hull Method: 5 Factors>
+                    <Factor identification<br/>Scree Plot: 6 Factors<br/>Minimum average partial method: 5 factors<br/>Hull method: 5 factors>
                     ]
@@
 
-                     1[label = '5 Factor Solution Retained 25 Items']
-                     2[label = <Reliability Analysis on EFA Sample (n=428)<br/>Ordinal alpha F1 =.94; F2 = .76; F3 = .75; F4 =.72; F5 =.62.>]
-
-                     3[label = <Confirmatory Factor Analysis<br/>on the Five Factor Model (25 Items; n=262)<br/>Acceptable Fit ( CFI = .94; TLI .93; RMSEA = .06, SRMR = .11)>]
-
-                    4[label = <Confirmatory Factor Analysis<br/>on the Five Factor Model (23 Items; n=262)<br/>Acceptable Fit ( CFI = .97; TLI= .96; RMSEA = .04, SRMR = .09)>]
-                     5[label = <Reliability Analysis (23 Items; n=262)<br/>Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52<br/>Mcdonald  omega(total) for the total scale = .73>]
-                    8[label = <Measurement Invariance Analysis (n=262)<br/>Residual measurement invariance achieved>]
-                    9[label = <Semantic Analysis (n=262):<br/>Semantic Scale Network analysis<br/>Readbility: Grade level 3.33>]
-                    10[label = <LEBA Short Form (19 Items; n=690)<br/>Based on Item Response Theory>]
+                     1[label = '5 factor solution retained 25 items']
+                     2[label = <Reliability analysis on EFA sample (n=428)<br/>Ordinal alpha F1 =.94; F2 = .76; F3 = .75; F4 =.72; F5 =.62.>]
+
+                     3[label = <Confirmatory factor analysis<br/>on the five factor model (25 items; n=262)<br/>Acceptable fit ( CFI = .94; TLI .93; RMSEA = .06, SRMR = .11)>]
+
+                    4[label = <Confirmatory factor analysis<br/>on the five factor model (23 Items; n=262)<br/>Acceptable fit ( CFI = .97; TLI= .96; RMSEA = .04, SRMR = .09)>]
+                     5[label = <Reliability analysis (23 items; n=262)<br/>Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52<br/>Mcdonald  omega(total) for the total scale = .73>]
+                    8[label = <Measurement invariance analysis (n=262)<br/>Residual measurement invariance achieved>]
+                    9[label = <Semantic analysis (n=262):<br/>Semantic scale network analysis<br/>Readbility: grade level 3.33>]
+                    10[label = <LEBA short form (18 Items; n=690)<br/>Based on Item Response Theory>]
                     }
@@
                     6[label = 
-                    <6-Factor solution:<br/>one factor emerged with only two salient loadings>
+                    <6 factor solution:<br/>One factor emerged with only two salient loadings>
                     ]
@@
 
-Lastly, we sought "Item Response Theory" (IRT) based analysis on developing a short form of LEBA.
+Lastly, we sought Item Response Theory (IRT) based analysis on developing a short form of LEBA.
 We fitted each factor of LEBA using the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =`r nrow(sem.data)`).
@@
 
-48 items were generated by an expert panel and  administered to a large sample (n = `r nrow(EFA.descriptives)` to explore the latent structure.
+48 items were generated by an expert panel and  administered to a large sample (n=`r nrow(EFA.descriptives)` to explore the latent structure.
 Exploratory Factor Analysis revealed a five factor solution with 25 items.
@@
 
-A CFA on a separate sample ((n = `r nrow(CFA.descriptives)` gave a five-factor solution (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR = `r apa(fit.2[10],2,F)`) after discarding two item.
-The internal consistency McDonald's $\omega_t$ of the five factors were  satisfactory (`r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`) Internal consistency reliability of the total scale (23 items) was also satisfactory, McDonald's $\omega_t$= `r apa(rel.k[5,6],2,F)`.
-In the same sample, our measurement invariance analysis  revealed that the latent structure attained the residual measurement invariance across subgroups: male and female (CFI: `r apa (residual.fitm[5,1],2,F)`, TLI: `r apa (residual.fitm[6,1],2,F)`, SRMR: `r apa (residual.fitm[6,1],2,F)`).
+A CFA on a separate sample ((n=`r nrow(CFA.descriptives)` gave a five-factor solution (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR = `r apa(fit.2[10],2,F)`) after discarding two item.
+The internal consistency McDonald's $\omega_t$ of the five factors were  satisfactory (`r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`) Internal consistency reliability of the total scale (23 items) was also satisfactory, McDonald's $\omega_t$= `r apa(rel.k[5,6],2,F)`.In the same sample, our measurement invariance analysis  revealed that the latent structure attained the residual measurement invariance across subgroups: male and female (CFI: `r apa (residual.fitm[5,1],2,F)`, TLI: `r apa (residual.fitm[6,1],2,F)`, SRMR: `r apa (residual.fitm[6,1],2,F)`).
 
@@
 
-Lastly, we developed a short-LEBA (n=18) using IRT analysis.
-We fitted a graded response model model to the combined EFA and CFA sample (n =`r nrow(data)`).
-We discarded 5 items with relatively flat item information curve [I($\theta$) <.20].
+Lastly, we developed a short-LEBA (18 items) using IRT analysis.
+We fitted a graded response model model to the combined EFA and CFA sample (n=`r nrow(data)`).
+We discarded five items with relatively flat item information curve [I($\theta$) <.20].
 IRT analysis indicated short form of LEBA is a psychometrically sound measure.
 Item fit indexes and person fit index for all five fitted model were acceptable.
-Items had diverse slope parameters indicating a good range of discrimination- the ability to differentiate respondents with different levels of the light exposure related behavior.
+Items had diverse slope parameters indicating a good range of discrimination- the ability to differentiate respondents with different levels of the light exposure related behaviour.
 Test information curve also indicated a good coverage of underlying trait continuum with precision.

### 2022-02-16 appendix-1.Rmd
Candidate for 2nd round

@@
 ```{r map}
-papaja::apa_table(map3, caption = "Minimum Average Partial (MAP) method of factor numder determination. MAP Statistics is the lowest in the 5th row indicating five factors are required.")
+papaja::apa_table(map3, caption = "Minimum average partial (MAP) method of factor numder determination. MAP Statistics is the lowest in the 5th row indicating five factors are required.")
 ```
@@
 modify_header(label ~ "**Variable**") %>% separate_p_footnotes() %>%
-  modify_caption("Demographic Characteristics: Native English Speakers")
+  modify_caption("Demographic characteristics: measurement invariance")
 
@@
 ```{r MinResTab}
-papaja::apa_table(minresTab,  caption = "Factor loadings and communality of the retained items (Minimum Residual)", note = "Only loading higher than .30 is reported", longtable=T, font_size = "footnotesize")
+papaja::apa_table(minresTab,  caption = "Factor loadings and communality of the retained items (minimum residual)", note = "Only loading higher than .30 is reported", longtable=T, font_size = "footnotesize")
 ```
@@
 ```{r efaunmerged}
-apa_table(efa.table, caption = "Factor loadings and communality of the retained items in five factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported", longtable =T, font_size = "footnotesize")
+apa_table(efa.table, caption = "Factor loadings and communality of the retained items in five factor solution [Unmerged responses]", note = "Only loading higher than .30 is reported", longtable =T, font_size = "footnotesize")
 ```
@@
 ```{r EFAsix}
-apa_table(efa.table.2, caption = "Factor loadings and communality of the retained items in six factor solution [Unmerged Responses]", note = "Only loading higher than .30 is reported, Sixth factor has only two salient loadings", longtable =T, font_size = "footnotesize")
+apa_table(efa.table.2, caption = "Factor loadings and communality of the retained items in six factor solution [Unmerged responses]", note = "Only loading higher than .30 is reported, Sixth factor has only two salient loadings", longtable =T, font_size = "footnotesize")
 ```
@@
 ```{r tztable}
-apa_table(tz, longtable =T,font_size = "footnotesize", caption = "Geographical Location of the participants (n =690)")
+apa_table(tz, longtable =T,font_size = "footnotesize", caption = "Geographical location of the participants (n =690)")
 ```
@@
 
-```{r IF, echo=FALSE, fig.align='center', fig.cap='Item information curve. Five items (1, 25,  38, 30, & 41) had relatively flat information curves ', out.width='100%', out.height='80%'}
+```{r IF, echo=FALSE, fig.align='center', fig.cap='Item information curve. Five items (1, 25,  38, 30,41) had relatively flat information curves', out.width='100%', out.height='100%'}
 knitr::include_graphics('Manuscript.figures/allitemplots.png', dpi = 300)

### 2022-02-16 manuscript.Rmd
Candidate for 2nd round

@@
                     E[label = 
-                    <Factor identification<br/>Scree Plot: 6 Factors<br/>Minimum average partial method: 5 factors<br/>Hull method: 5 factors>
+                    <Factor identification<br/>Scree plot: 6 factors<br/>Minimum average partial method: 5 factors<br/>Hull method: 5 factors>
                     ]
@@
 The data analysed in this study was collected between 17 May 2021 and 3 September 2021.
+
 ## Analytic Strategies
@@
 Due to these violations and the ordinal nature of our response data, in EFA we used  polychoric correlation matrix and employed principal axis (PA) as  factor extraction method with varimax rotation [@desjardinsHandbookEducationalMeasurement2018;@watkinsStepbyStepGuideExploratory2020].
-We used a combination of factor identification method including scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
+We used a combination of factor identification method including Scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and Hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
 To determine the latent structure, we followed the common guidelines : (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading > .3 across factors [@bandalosFactorAnalysisExploratory2018].
@@
 
-To validated the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with Weighted Last Square with mean and variance adjusted (WLSMV) estimator estimator [@desjardinsHandbookEducationalMeasurement2018] on a separate sample (CFA sample;n=`r nrow(CFA.descriptives)`).
+To validated the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with weighted least square with mean and variance adjusted (WLSMV) estimator estimator [@desjardinsHandbookEducationalMeasurement2018] on a separate sample (CFA sample;n=`r nrow(CFA.descriptives)`).
 We assessed the model fit using common model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI):  close to .95 or above/ between 90-95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner].
@@
 After reviewing the literature, we identified several light exposure related scale.
-However, no scales specifically measuring the behavioural component of light exposure were found (Table \@ref(tab:reltab2).
+However, no scales specifically measuring the behavioural component of light exposure were found (Table \@ref(tab:reltab2)).
 As such, all authors in collaboration of an expert panel developed a comprehensive item pool of 48 items.
@@
 The panel members independently judged each of the items in terms of their relevance and representativeness and suggested required modification, if there is any.
-The author team acknowledged the suggestions and amended the items as required thus creating a 48-item scale
+The author team acknowledged the suggestions and amended the items as required thus creating a 48-item scale.
 
@@
 Participants indicated filling out the online survey from a diverse range of geographic locations.
-Figure \@ref(fig:partmap) depicts the top ten countries with highest participation in our survey.For a complete list of geographic locations, see Suppl.
+Figure \@ref(fig:partmap) depicts the top ten countries with highest participation in our survey.
+For a complete list of geographic locations, see Suppl.
 Table \@ref(tab:tztable).
 
-```{r partmap, fig.cap="Countries with Highest Responses", out.height= '100%', out.width= '100%'}
+```{r partmap, fig.cap="Top ten countries with highest responses in our survey", out.height= '100%', out.width= '100%'}
 knitr::include_graphics('Manuscript.figures/distribution.png', dpi = 300 )
@@
 
-colnames(descriptives) <- c("Items", "Mean", "SD", "Skew", "Kurtosis", "SW Statistics", "Item-total corelation")
+colnames(descriptives) <- c("Items", "Mean", "SD", "Skew", "Kurtosis", "SW Statistics", "Item Total Correlation")
 
@@
 
-```{r EFAplot, fig.align='center', fig.cap='(A) Five Factor Solution obtained in Exploratory Factor Analysis (B) Histogram of nonredundent residula correlations', warning=FALSE,  results='asis'}
+```{r EFAplot, fig.align='center', fig.cap='(A) Five factor solution obtained in exploratory factor analysis (B) Histogram of nonredundent residula correlations', warning=FALSE,  results='asis'}
 
@@
 
-```{r efagtPic, echo=FALSE, out.height="100%", out.width= '100%', fig.cap= ' Summary Descriptives EFA Sample'}
+```{r efagtPic, echo=FALSE, out.height="100%", out.width= '100%', fig.cap= ' Summary descriptives and response pattern of EFA sample'}
 knitr::include_graphics('Manuscript.figures/efagt.png',dpi =600)
@@
 
-```{r cfagtPic, echo=FALSE, out.height="100%", out.width= '100%', fig.cap= ' Summary Descriptives of CFA Sample'}
+```{r cfagtPic, echo=FALSE, out.height="100%", out.width= '100%', fig.cap= ' Summary descriptives and response pattern of CFA sample'}
 knitr::include_graphics('Manuscript.figures/cfagt.png',dpi =600)
@@
 
-```{r figcfa, fig.cap = "Five Factor  Model of LEBA obtained by Confirmatory Factor Analysis.
+```{r figcfa, fig.cap = "Five factor  model of LEBA obtained by confirmatory factor analysis.
 By allowing item pair 41 and 30 to covary their error variance our model attained the best fit.",  out.height='100%', warning=FALSE}
@@
 
-```{r Testinfo, fig.cap="Test information curves (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE}
+```{r Testinfo, fig.cap="Test information curves (a) wearing blue light filters (b) spending time outdoors (c) using phone and smartwatchin bed (d) using light before bedtime (e) using light in the morning andduring daytime", warning=FALSE}
 
@@
 
-We developed a self-reported tool to capture different light exposure related behavior and evaluated its psychometric properties using classical test theory and Item Response Theory based analysis.
-
-48 items were generated by an expert panel and  administered to a large sample (n=`r nrow(EFA.descriptives)` to explore the latent structure.
-Exploratory Factor Analysis revealed a five factor solution with 25 items.
+Though there are lots of validated tool to measure light exposure, they don't tell us much about the behavioural aspects pertaining to the light exposure.
+At present there is a dearth of validated tool to measure light exposure related behaviours.
+In that vein we have developed a subjective self-reported tool that can capture light exposure related behaviour in different dimensions.
+
+Authors along with an expert panel generated 48 items and evaluated their quality and relevance and made necessary amendments.
+A large scale geographically unconstrained quantitative cross-sectional survey was conducted yielding responses from large sample (n=`r nrow(EFA.descriptives)` to explore the latent structure.
+Exploratory factor analysis revealed a five factor solution with 25 items.
 ("Wearing blue light filters", "Spending time outdoors", "Using phone and smart-watch in bed", "Using light before bedtime",  and "Using light in the morning and during daytime").
@@
 A CFA on a separate sample ((n=`r nrow(CFA.descriptives)` gave a five-factor solution (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR = `r apa(fit.2[10],2,F)`) after discarding two item.
-The internal consistency McDonald's $\omega_t$ of the five factors were  satisfactory (`r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`) Internal consistency reliability of the total scale (23 items) was also satisfactory, McDonald's $\omega_t$= `r apa(rel.k[5,6],2,F)`.In the same sample, our measurement invariance analysis  revealed that the latent structure attained the residual measurement invariance across subgroups: male and female (CFI: `r apa (residual.fitm[5,1],2,F)`, TLI: `r apa (residual.fitm[6,1],2,F)`, SRMR: `r apa (residual.fitm[6,1],2,F)`).
+The internal consistency McDonald's $\omega_t$ of the five factors were  satisfactory (`r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`) Internal consistency reliability of the total scale (23 items) was also satisfactory, McDonald's $\omega_t$= `r apa(rel.k[5,6],2,F)`.In the same sample, our measurement invariance analysis  revealed that the latent structure attained the residual measurement invariance across subgroups: male and female (CFI: `r apa (residual.fitm[5,1],2,F)`, TLI: `r apa (residual.fitm[6,1],2,F)`, SRMR: `r apa(residual.fitm[6,1],2,F)`).
 
@@
 Upon inspecting the item contents we found items under "Using phone and smart-watch in bed" and "Using light before bedtime" have semantic overlap with the items of SDSC ans CIDI.
-Items in those two scales were looking into behaviors related to sleep.
+Items in those two scales were looking into behaviours related to sleep.
 As such the similarity index obtained is expected.
@@
 
-Lastly, we developed a short-LEBA (18 items) using IRT analysis.
+We developed a short-LEBA (18 items) using IRT analysis.
 We fitted a graded response model model to the combined EFA and CFA sample (n=`r nrow(data)`).
@@
 
+LEBA can be used to profile individuals based on their light exposure related behaviours, which can facilitate the development process of individual interventions to promote health.
+All the five factors of LEBA can identify 'problematic' behaviours that are opposed to good light hygiene.
+
 ## Conclusion
-"The Light exposure behavior assessment"(LEBA) gave a five solution with 25 items in an EFA.
+
+We developed a novel self-reported subjective tool- "Light exposure behaviour assessment"(LEBA) to capture light exposure related behaviour.
+We developed 48 items, judged the relevance and content of the items and conducted a large scale geographically unrestricted cross-sectional survey.
+Our EFA gave a five solution with 25 items.
 A CFA with this 25-item scale again offered a five-factor solution, but this time two more item was discarded.
-The 23-item "LEBA" was found reliable and valid.
+The 23-item "LEBA" was found reliable (internal consistency) and valid (structural validity).
 A short-form of LEBA was developed using IRT analysis.
-IRT analysis gave a 18-item scale with  a good range of coverage across the underlying trait continuum.
-All-in-all, we can recommend both forms to be used to capture individual’s light exposure related behavior
+IRT analysis gave a 18-item scale with  a good  coverage across the underlying trait continuum.
+Hence, we could recommend that LEBA can be used to measure different aspects of light exposure related behaviour.
+
+## Future Direction
+
+Since, LEBA is the first of its kind, estimating convergent validity with other subjective tool was not possible.
+One way to establish the convergent validity of LEBA is to administer this subjective tool along which some objective measurement tools (e.g.
+personalised light dosimeter).
+Though such objective tools do not directly capture light exposure related behaviour, potential insight can be drawn by understanding the behaviour pattern and light exposure.
+Also,  light exposure related behaviours can be dependent upon the socio-economic status as behaviours can be modulated by available tools individual have on their disposal.
+Our analysis did not consider socio-economic status, as we didn't measure it.
+Investigating the properties of LEBA while considering different socio-economic status would be a valuable addition.
 

### 2022-02-22 manuscript.Rmd
Feedback round2: Typo updated in bodytext

@@
 A quantitative cross-sectional fully anonymous online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
-Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) of a Comic co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux].
+Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (https://enlightenyourclock.org/participate-in-research) of the science-communication comic-book "Enlighten your clock" co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux].
 The landing page of the online survey had the explanatory statements where we mentioned participation was voluntary and that respondents could withdraw from participation anytime without being penalized.
@@
 Underaged participants (<18 years) were urged to obtain assent from their parents/legal guardians.
-The survey took around 15 to 20 minutes and participants were not compensated.
+The entire survey was estimated to take <30 minutes.
+Participants were not compensated.
 As a part of the demographic information participants provided information regarding age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language.
@@
 What is 4+5?").
-Participants needed to confirm that they were participating the survey for the first time.
+Participants were asked to confirm that they were participating the survey for the first time.
 Questions incorporating retrospective recall were all aligned to the period of "past four weeks".
@@
 
-## Analytic Strategies
+## Analytic Strategy
 
 Figure \@ref(fig:FlowchartFig) summarizes the steps of our psychometric analysis.
-In our analysis we used R (version 4.1.0).
-In the item generation and selection phase we had developed a item pool of 48 items with six-point Likert type response format (0:Does not apply/I don't know; 1:Never, 2:Rarely; 3:Sometimes; 4:Often; 5:Always).
+In our analysis we used R (version 4.1.0) [@R-base].
+In the item generation and selection phase we had developed a item pool of 48 items with six-point Likert type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always).
 Our purpose was to capture light exposure related behaviour.
@@
 We also conducted a EFA on non-merged response options data (Supp.
-Table \@ref(tab:efaunmerged)) and rejected the latent structure obtained as the factors were less interpretable.
-
-For reliability estimation we used internal consistency reliability coefficient ordinal alpha.
-Though  Cronbach's alpha coefficient is widely used for estimating internal consistency, it has a tendency to deflate the estimates for  Likert type data since the calculation is based on pearson-correlation matrix which requires response data to be continuous of nature [@gadermann2012estimating; @zumbo2007ordinal].
+Table \@ref(tab:efaunmerged)).
+
+For reliability estimation we used internal consistency reliability coefficient ordinal $\alpha$.
+Though Cronbach's alpha coefficient is widely used for estimating internal consistency, it has a tendency to deflate the estimates for Likert-type data since the calculation is based on pearson-correlation matrix which requires response data to be continuous of nature [@gadermann2012estimating; @zumbo2007ordinal].
 Subsequently to get  better estimates of reliability  we reported ordinal alpha for each factors using polychoric-correlation matrix [@zumbo2007ordinal].
@@
 
-We assessed the measurement invariance (MI) of our construct between native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non-non native English speakers (n=`r invariance.data.descriptives.count[2,2]`) among the CFA sample (n=`r nrow(CFA.descriptives)`).
+We assessed the measurement invariance (MI) of our construct between native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non native English speakers (n=`r invariance.data.descriptives.count[2,2]`) among the CFA sample (n=`r nrow(CFA.descriptives)`).
 MI evaluates whether a construct has the psychometric equivalence and same meaning across groups [@putnick2016measurement;@klinePrinciplesPracticeStructural2015].
@@
 Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy.
-Additionally, To identify the educational grade level required to understand the items in our tool we subjected the tool to Flesch-Kincaid Grade Level [@flesch1948new]
+Additionally, to identify the educational grade level required to understand the items in our tool we subjected the tool to Flesch-Kincaid Grade Level [@flesch1948new]
 
@@
 
-"Semantic Scale Network"(SSN) analysis [@rosenbusch2020semantic] indicated that LEBA (23 items)  appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990].The cosine similarities lie between .47 to .51.
+"Semantic Scale Network"(SSN) analysis [@rosenbusch2020semantic] indicated that LEBA (23 items)  appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990].
+The cosine similarities lie between .47 to .51.
 Flesch-Kincaid Grade Level [@flesch1948new] analysis on the the 23 items of our scale indicated required educational grade level was 3.33 and with a age above 8.33.
@@
 Table \@ref(tab:itemfittab) summarizes the item fit indexes of the items.
-All of the items had RMSEA value $\le$.06 indicating adequate fit of the items.
+All of the items had RMSEA value $\le$.06 indicating adequate fit of the items to the fitted IRT model.
 Sup.Figure \@ref(fig:personfit) depicts the person fit Zh statistics histogram of out fitted models.
@@
 
-A CFA on a separate sample ((n=`r nrow(CFA.descriptives)` gave a five-factor solution (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR = `r apa(fit.2[10],2,F)`) after discarding two item.
+<!-- A CFA on a separate sample ((n=`r nrow(CFA.descriptives)` gave a five-factor solution (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR = `r apa(fit.2[10],2,F)`) after discarding two item.
 The internal consistency McDonald's $\omega_t$ of the five factors were  satisfactory (`r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`) Internal consistency reliability of the total scale (23 items) was also satisfactory, McDonald's $\omega_t$= `r apa(rel.k[5,6],2,F)`.In the same sample, our measurement invariance analysis  revealed that the latent structure attained the residual measurement invariance across subgroups: male and female (CFI: `r apa (residual.fitm[5,1],2,F)`, TLI: `r apa (residual.fitm[6,1],2,F)`, SRMR: `r apa(residual.fitm[6,1],2,F)`).
-
-The "Semantic Scale Network"(SSN) analysis [@rosenbusch2020semantic] on the retained 23 items showed "LEBA" was  related to  "Sleep Disturbance Scale For Children" (SDSC) [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990].
+-->
+
+<!-- The "Semantic Scale Network"(SSN) analysis [@rosenbusch2020semantic] on the retained 23 items showed "LEBA" was  related to  "Sleep Disturbance Scale For Children" (SDSC) [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990].
 Upon inspecting the item contents we found items under "Using phone and smart-watch in bed" and "Using light before bedtime" have semantic overlap with the items of SDSC ans CIDI.
@@
 Flesch-Kincaid Grade Level [@flesch1948new] analysis on the the 23 items of our scale indicated required educational grade level was 3.33 and with a age above 8.33.
-
-We developed a short-LEBA (18 items) using IRT analysis.
+-->
+
+<!-- We developed a short-LEBA (18 items) using IRT analysis.
 We fitted a graded response model model to the combined EFA and CFA sample (n=`r nrow(data)`).
@@
 Test information curve also indicated a good coverage of underlying trait continuum with precision.
+-->
 
 LEBA can be used to profile individuals based on their light exposure related behaviours, which can facilitate the development process of individual interventions to promote health.
-All the five factors of LEBA can identify 'problematic' behaviours that are opposed to good light hygiene.
+All the five factors of LEBA may identify 'problematic' behaviours that are opposed to good light hygiene.
 
@@
 
-We developed a novel self-reported subjective tool- "Light exposure behaviour assessment"(LEBA) to capture light exposure related behaviour.
+We developed a novel self-reported subjective tool-"Light exposure behaviour assessment"(LEBA) to capture light exposure related behaviour.
 We developed 48 items, judged the relevance and content of the items and conducted a large scale geographically unrestricted cross-sectional survey.

### 2022-02-22 manuscript.Rmd
Descriptive table is updated with footnote

@@
 relevant.scale.data %>% 
-apa_table(landscape =T,caption ="List of instruments measuring related consttucts to LEBA", format = "latex",escape = T, font_size = "footnotesize", align = c("p{3cm}", rep("p{3.6cm}", ncol(relevant.scale.data))))
+apa_table(landscape =T,caption ="List of instruments measuring related constucts to LEBA", format = "latex",escape = T, font_size = "footnotesize", align = c("p{3cm}", rep("p{3.6cm}", ncol(relevant.scale.data))))
 
@@
 modify_header(label ~ "**Variable**") %>% separate_p_footnotes() %>%
-  modify_caption("Demographic Characteristics") -> desc_table
+  modify_caption("Demographic Characteristics of Partinipants (n=690)") -> desc_table
 
@@
 
-colnames(descriptives) <- c("Items", "Mean", "SD", "Skew", "Kurtosis", "SW Statistics", "Item Total Correlation")
+colnames(descriptives) <- c("Items", "Mean", "SD", "Skew", "Kurtosis", "$SW^{1}$", "Item Total Correlation")
 
@@
 descriptives2 %>% 
-apa_table(landscape =T,caption ="Descriptive Statistics", escape =F, font_size = "footnotesize", note = "*p<.001", align = c("p{1cm}","p{10cm}", rep("p{1cm}", ncol(descriptives2)))) 
+apa_table(landscape =T,caption ="Univariate Descriptive Statistics for the 48 Items.
+All Items Violated Univariate Normality Assumption Assessed by Shapiro–Wilk (SW) Test.
+The  Item-total Correlation Ranges Between .03-.48", escape =F, font_size = "footnotesize", note = ("$*p<.001$, $^{1}Shapiro–Wilk$ $Statistics$"), align = c("p{1cm}","p{10cm}", rep("p{1cm}", ncol(descriptives2))))
 ```

### 2022-02-22 manuscript.Rmd
Table 4 updated

@@
 
-apa_table(efa.table,align = "c", caption = "Factor loadings and communality of the retained items", note = "Only loading higher than .30 is reported", font_size = "small")
+apa_table(efa.table,align = "c", caption = "Factor loadings and communality of the retained items", note = "Only loading > .30 is reported", font_size = "small")
 ```

### 2022-02-22 manuscript.Rmd
Table 5&6: Greek symbols and footnote updated

@@
 CFa.matrix <- matrix("NA", nrow =2, ncol = 9)
-colnames(CFa.matrix) = c("Model", "Chi-Squre", "df", "CFI", "TLI", "RMSEA", "RMSEA 90% Lower CI", "RMSEA 90% Upper CI", "SRMR")
+colnames(CFa.matrix) = c("Model", "$\\chi^{2}$", "df", "CFI", "TLI", "RMSEA", "RMSEA 90\\% Lower CI", "RMSEA 90\\% Upper CI", "SRMR")
 CFa.matrix[1,] = c("Five factor model:25", 
@@
 apa_table(CFa.matrix, caption = "Confirmatory Factor Analysis model fit indices of the two model: five factor model with 25 items and five factor model with 23 items.
-The second model attained the best fit.", align = "c", landscape = T, note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index;RMSEA:Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square ")
+The second model attained the best fit.", align = "c", landscape = T, escape=F, note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index;RMSEA:Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square ")
 ```
@@
 
-colnames(Invariance.table) <- c("Chi-Square", "df", "CFI", "TLI", "RMSEA", "RMSEA 90% Lower CI", "RMSEA 90% Upper", "Chi-Square Difference", "df difference*", "p")
+colnames(Invariance.table) <- c("$\\chi^{2}$", "df", "CFI", "TLI", "RMSEA", "RMSEA 90\\% Lower CI", "RMSEA 90\\% Upper", "$\\Delta$ $\\chi^{2}$", "$\\Delta$ df*", "p")
 
@@
 ```{r InvarianceTab, results='asis'}
-apa_table(Invariance.table, align = "c",  caption = "Measurment Invariance analysis on CFA sample (n=262) across native and non-native English speakers.", note = " a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual;* =  df of model comparison", landscape = T, font_size = "footnotesize" )
+apa_table(Invariance.table, align = "c",  caption = "Measurment Invariance analysis on CFA sample (n=262) across native and non-native English speakers.", note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index;RMSEA:Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual;* =  df of model comparison", landscape = T, font_size = "footnotesize", escape=F )
 

### 2022-02-22 manuscript.Rmd
Table 3 superscript is added for SW

@@
 
-colnames(descriptives) <- c("Items", "Mean", "SD", "Skew", "Kurtosis", "$SW^{1}$", "Item Total Correlation")
+colnames(descriptives) <- c("Items", "Mean", "SD", "Skew", "Kurtosis", "SW$^{1}$", "Item Total Correlation")
 
@@
 All Items Violated Univariate Normality Assumption Assessed by Shapiro–Wilk (SW) Test.
-The  Item-total Correlation Ranges Between .03-.48", escape =F, font_size = "footnotesize", note = ("$*p<.001$, $^{1}Shapiro–Wilk$ $Statistics$"), align = c("p{1cm}","p{10cm}", rep("p{1cm}", ncol(descriptives2))))
+The  Item-total Correlation Ranges Between .03-.48", escape =F, font_size = "footnotesize", note = ("$^{*}$p<.001, $^{1}$Shapiro–Wilk Statistics"), align = c("p{1cm}","p{10cm}", rep("p{1cm}", ncol(descriptives2))))
 ```

### 2022-02-22 manuscript.Rmd
gtPlots updated

@@
 as_tibble(desc_table) -> desc_tibble 
-as_kable_extra(desc_table, format = "latex",booktabs = T) -> desc_kable #save it as a knitr::kable
+as_kable_extra(desc_table, format = "latex",booktabs = T) %>% 
+  kable(col.names=c("Variable", "Overall, n=690$^{1}$","EFA Sample, n=428$^{1}$", "CFA sample, n=262$^{1}$", "p", "q$^{2}$"), escape = FALSE)-> desc_kable #save it as a knitr::kable
 
@@
 We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones).Participants reported a diverse range of geographic location
-Participants indicated filling out the online survey from a diverse range of geographic locations.
-Figure \@ref(fig:partmap) depicts the top ten countries with highest participation in our survey.
-For a complete list of geographic locations, see Suppl.
-Table \@ref(tab:tztable).
-
-```{r partmap, fig.cap="Top ten countries with highest responses in our survey", out.height= '100%', out.width= '100%'}
+Participants indicated filling out the online survey from a diverse range of geographic locations. For a complete list of geographic locations, see Suppl. Table \@ref(tab:tztable).
+
+```{r partmap, eval=FALSE, fig.cap="Top ten countries with highest responses in our survey", include=FALSE, out.height='100%', out.width=}
 knitr::include_graphics('Manuscript.figures/distribution.png', dpi = 300 )
@@
 ```{r rafael2, eval=FALSE, include=FALSE}
+# Figure \@ref(fig:partmap) depicts the top ten countries with highest participation in our survey.
 # - `r tz_tibble[2,1]`:     `r tz_tibble[2,2]`
@@
   tab_header(
-    title = md("**LEBA**"),
+    title = md("**Light Exposure Behavior Assessment**"),
     subtitle = md("Summary Descriptives EFA Sample (n =428)")
   ) %>% 
-  tab_footnote(
-    footnote = md("**Histogram**"),
-    locations = cells_column_labels(columns = hist_data)
-  ) %>%
-  tab_footnote(
-    footnote = md("**Density**"),
-    locations = cells_column_labels(columns = dens_data)
-  ) %>% 
+  # tab_footnote(
+  #   footnote = md("**Histogram**"),
+  #   locations = cells_column_labels(columns = hist_data)
+  # ) %>%
+  # tab_footnote(
+  #   footnote = md("**Density**"),
+  #   locations = cells_column_labels(columns = dens_data)
+  # ) %>% 
 #create groups of columns
@@
 cols_label(
-  Items = ("LEBA  Items"),
+  Items = (""),
   nr = ("n"),
@@
   tab_row_group(
-      label = md("**F5:Using light in the morning and during daytime**"),
+      label = md("**F5: Using light in the morning and during daytime**"),
       rows = c(1,3,12,13,24,25) 
@@
   tab_row_group(
-      label = md("**F4:Using light before bedtime**"),
+      label = md("**F4: Using light before bedtime**"),
       rows = c(16,17,18,20,21) 
@@
   tab_row_group(
-      label = md("**F3:Using phone and smart-watch in bed**"),
+      label = md("**F3: Using phone and smart-watch in bed**"),
       rows = c(2,14,15,22,23) 
@@
   tab_row_group(
-      label = md("**F2:Spending time outdoors**"),
+      label = md("**F2: Spending time outdoors**"),
       rows = c(4,5,6,7,8,9) 
@@
   tab_row_group(
-      label = md("**F1:Wearing blue light filters**"),
+      label = md("**F1: Wearing blue light filters**"),
       rows = c(10,11,19) 
@@
   tab_header(
-    title = md("**LEBA**"),
-    subtitle = md("Summary Descriptives CFA Sample (Nn=262)")
-  ) %>% 
-  tab_footnote(
-    footnote = md("**Histogram**"),
-    locations = cells_column_labels(columns = hist_data)
-  ) %>%
-  tab_footnote(
-    footnote = md("**Density**"),
-    locations = cells_column_labels(columns = dens_data)
-  ) %>% 
+    title = md("**Light Exposure Behavior Assessment**"),
+    subtitle = md("Summary Descriptives CFA Sample (n=262)")
+  ) %>% 
+  # tab_footnote(
+  #   footnote = md("**Histogram**"),
+  #   locations = cells_column_labels(columns = hist_data)
+  # ) %>%
+  # tab_footnote(
+  #   footnote = md("**Density**"),
+  #   locations = cells_column_labels(columns = dens_data)
+  # ) %>% 
 #create groups of columns
@@
 cols_label(
-  Items = ("LEBA Items"),
+  Items = (""),
   nr = ("n"),
@@
   tab_row_group(
-      label = md("**F5:Using light in the morning and during daytime**"),
+      label = md("**F5: Using light in the morning and during daytime**"),
       rows = c(1,3,12,13,22,23) 
@@
   tab_row_group(
-      label = md("**F4:Using light before bedtime**"),
+      label = md("**F4: Using light before bedtime**"),
       rows = c(15,16,17,19) 
@@
   tab_row_group(
-      label = md("**F3:Using phone and smart-watch in bed**"),
+      label = md("**F3: Using phone and smart-watch in bed**"),
       rows = c(2,13,14,20,21) 
@@
   tab_row_group(
-      label = md("**F1:Wearing blue light filters**"),
+      label = md("**F1: Wearing blue light filters**"),
       rows = c(10,11,18) 
@@
 
-```{r Testinfo, fig.cap="Test information curves (a) wearing blue light filters (b) spending time outdoors (c) using phone and smartwatchin bed (d) using light before bedtime (e) using light in the morning andduring daytime", warning=FALSE}
+```{r Testinfo, fig.cap="Test information curves for the five factors of LEBA: (a) wearing blue light filters (b) spending time outdoors (c) using phone and smartwatchin bed (d) using light before bedtime (e) using light in the morning andduring daytime.
+Along x-axis we plotted the underlying latent trait continumm for each factor.
+Along y-axis we plotted how much information a particular factor is caring across its latent trait continuum", warning=FALSE}
 

### 2022-02-22 appendix-1.Rmd
Landscape figures (TIC and IIC)

@@
 
-```{r IF, echo=FALSE, fig.align='center', fig.cap='Item information curve. Five items (1, 25,  38, 30,41) had relatively flat information curves', out.width='100%', out.height='100%'}
+```{r IF, fig.env = "sidewaysfigure", echo=FALSE, fig.align='center', fig.cap='Item information curve.
+Five items (1, 25,  38, 30, 41) had relatively flat information curves', out.width="100%", out.height="120%", out.extra = ""}
 knitr::include_graphics('Manuscript.figures/allitemplots.png', dpi = 300)

### 2022-02-22 manuscript.Rmd
Landscape figures (TIC and IIC)

@@
       in_header: header.tex
+header-includes:
+  - \usepackage{rotating}
+  - \DeclareDelayedFloatFlavor{sidewaysfigure}{figure}
 appendix:
@@
 as_tibble(desc_table) -> desc_tibble 
-as_kable_extra(desc_table, format = "latex",booktabs = T) %>% 
-  kable(col.names=c("Variable", "Overall, n=690$^{1}$","EFA Sample, n=428$^{1}$", "CFA sample, n=262$^{1}$", "p", "q$^{2}$"), escape = FALSE)-> desc_kable #save it as a knitr::kable
+as_kable_extra(desc_table, format = "latex",booktabs = T) -> desc_kable #save it as a knitr::kable
 
@@
 
-```{r partmap, eval=FALSE, fig.cap="Top ten countries with highest responses in our survey", include=FALSE, out.height='100%', out.width=}
+```{r partmap, eval=FALSE, fig.cap="Top ten countries with highest responses in our survey", include=FALSE, out.height='100%'}
 knitr::include_graphics('Manuscript.figures/distribution.png', dpi = 300 )
@@
 
-```{r Testinfo, fig.cap="Test information curves for the five factors of LEBA: (a) wearing blue light filters (b) spending time outdoors (c) using phone and smartwatchin bed (d) using light before bedtime (e) using light in the morning andduring daytime.
+```{r Testinfo, fig.env = "sidewaysfigure", fig.cap="Test information curves for the five factors of LEBA: (a) wearing blue light filters (b) spending time outdoors (c) using phone and smartwatchin bed (d) using light before bedtime (e) using light in the morning andduring daytime.
 Along x-axis we plotted the underlying latent trait continumm for each factor.
-Along y-axis we plotted how much information a particular factor is caring across its latent trait continuum", warning=FALSE}
+Along y-axis we plotted how much information a particular factor is caring across its latent trait continuum", warning=FALSE, out.width="100%", out.height="120%"}
 

### 2022-02-22 manuscript.Rmd
flowchart highlighted

@@
 
-                    graph [fontname = Helvetica,layout = dot,fontsize = 45,layout = dot ]
-
-                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 16, height = 2, 
+                    graph [fontname = Helvetica,layout = dot,fontsize = 45 ]
+
+                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 20, height = 3, 
                     fixedsize = true,fontsize = 45]
@@
                     A[label = 'Initial development of 48 items'] 
-                    B[label = 'Large scale survey (n=690)']
+                    B[label = 'Large scale survey: first round (n=428)']
                     C[label = 'Initial item analysis']
@@
 
-                    node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 16, height = 6, 
-                    fixedsize = true, fontsize = 45]
                     E[label = 
-                    <Factor identification<br/>Scree plot: 6 factors<br/>Minimum average partial method: 5 factors<br/>Hull method: 5 factors>
+                    <Factor Identification Method<br/>Scree plot<br/>Minimum average partial method<br/>Hull method>
                     ]
 
-                     subgraph cluster_1 {
-                      graph[fontname = Helvetica, shape = box, style =dashed]
-
-                     node[fontname = Helvetica, margin = 0.2,width = 22, height = 2.5, 
-                    fixedsize = true, fontsize = 45,style =dashed]
-
-                     1[label = '5 factor solution retained 25 items']
-                     2[label = <Reliability analysis on EFA sample (n=428)<br/>Ordinal alpha F1 =.94; F2 = .76; F3 = .75; F4 =.72; F5 =.62.>]
-
-                     3[label = <Confirmatory factor analysis<br/>on the five factor model (25 items; n=262)<br/>Acceptable fit ( CFI = .94; TLI .93; RMSEA = .06, SRMR = .11)>]
-
-                    4[label = <Confirmatory factor analysis<br/>on the five factor model (23 Items; n=262)<br/>Acceptable fit ( CFI = .97; TLI= .96; RMSEA = .04, SRMR = .09)>]
-                     5[label = <Reliability analysis (23 items; n=262)<br/>Ordinal alpha F1=.93; F2=.83; F3 =.70; F4=.69; F5=.52<br/>Mcdonald  omega(total) for the total scale = .73>]
-                    8[label = <Measurement invariance analysis (n=262)<br/>Residual measurement invariance achieved>]
-                    9[label = <Semantic analysis (n=262):<br/>Semantic scale network analysis<br/>Readbility: grade level 3.33>]
-                    10[label = <LEBA short form (18 Items; n=690)<br/>Based on Item Response Theory>]
-                    }
-                subgraph cluster_2 {
-                      graph[fontname = Helvetica,shape = rectangle]
-                      style = rounded
-                     node[fontname = Helvetica, margin = 0.2,width = 18, height = 2.5, 
-                fixedsize = true, fontsize = 45 ]
-                    6[label = 
-                    <6 factor solution:<br/>One factor emerged with only two salient loadings>
-                    ]
-                    7[label = 'Rejected']
-                    }
+                    F[label = 'Reliability analysis on latent stucture obtained in EFA (n=428)']
+                    G[label = 'Large scale survey: second round (n=262)']
+
+                    H[label = 'Confirmatory factor analysis ( n=262)']
+
+                    I[label = 'Reliability analysis on latent stucture obtained in CFA (n=262)']
+
+                    K[label = 'Long LEBA: 23-item', style = filled, fillcolor = Beige]
+
+                    L[label = 'Measurement invariance analysis (n=262)']
+                    M[label = 'Semantic analysis (n=262)']
+                    N[label = 'Item Response Theory based analysis on the combined sample (n=690)']
+
+                    O[label = 'Short LEBA: 18-item',style = filled, fillcolor = Beige]
 
@@
                      D ->E
-                E ->1
-                     1 ->2
-                     2 ->3
-                     3 ->4
-                     4 ->5
-                    5->8
-                    8 ->9
-                    9 ->10
-                     E ->6
-                     6 ->7
+                     E ->F
+                    F ->G
+                     G ->H
+                     H ->I
+                     I ->K
+
+                    K->L
+                    L ->M
+                    M ->N
+                    N->O
 
@@
 
-```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long and short form of LEBA', out.height='100%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/Flowchart1.jpeg', dpi = 800 )
+```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long form (23-item) and short form (18-item) of LEBA. ', out.height='100%', out.width='100%'}
+knitr::include_graphics('Manuscript.figures/Flowchart1.jpeg', dpi = 600 )
 ```

### 2022-02-22 manuscript.Rmd
corrplot significant correlation highlighted

@@
 
+install.packages("correlation")
 #if you dont have LaTeX installed run the following lines
@@
 
-                    K[label = 'Long LEBA: 23-item', style = filled, fillcolor = Beige]
+                    K[label = 'LEBA long format: 23-item', style = filled, fillcolor = Beige]
 
@@
 
-                    O[label = 'Short LEBA: 18-item',style = filled, fillcolor = Beige]
+                    O[label = 'LEBA short format: 18-item', style = filled, fillcolor = Beige]
 
@@
 correlations <- psych::polychoric(EFA.data, correct = 0)
+
 upper <- correlations$rho[upper.tri(correlations$rho, diag = F)]
@@
 
-corplot <- ggcorrplot(correlations$rho, hc.order = TRUE, outline.col = "white", type = "lower", legend.title = "Correlation",
+p.mat <- correlation::cor_to_p(correlations$rho, 428, method = "polychoric")
+
+corplot <- ggcorrplot(correlations$rho, p.mat=p.mat$p, insig = "pch", hc.order = FALSE, outline.col = "white", type = "lower", legend.title = "Correlation",sig.level = 0.05, pch.cex=1.8,
+                      # insig = "blank",
            ggtheme = ggplot2::theme_minimal(),tl.srt = 90,colors = c("#E64B35FF", "white", "#3C5488FF") )+
@@
                                     size = 1))
-#p.mat <- cor_to_p(correlations$rho, 428, method = "polychoric")
 #to show pvalue in the fig add p.mat=p.mat
-ggsave("Manuscript.figures/corplot.png",corplot, width = 6, height = 6, dpi = 600, bg ="white")
+ggsave("Manuscript.figures/corplot.png",corplot, width = 12, height = 8.5, dpi = 600, bg ="white")
 

### 2022-03-10 appendix-1.Rmd
Round-2 Feedback: Modification started

@@
 short.rel <- readxl::read_excel("Table_raw/LEBA_short_structure.xlsx")
-short.rel <- long.rel %>% mutate_all(~ replace_na(.x, " "))
+short.rel <- short.rel %>% mutate_all(~ replace_na(.x, " "))
 ```

### 2022-03-10 manuscript.Rmd
Round-2 Feedback: Modification started

@@
   - id            : "11"
-    institution   : "Max Planck Institute for Biological Cybernetics, Tübingen, Germany"
+    institution   : "Translational Sensory & Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany"
   - id            : "12"
-    institution   : "Technical University of Munich, Department of Sport and Health Sciences (TUM SG), Munich, Germany"
+    institution   : "TUM Department of Sport and Health Sciences (TUM SG), Technical University of Munich, Munich, Germany"
   - id            : "13"
@@
 
-```{r cfaplot, include =F}
+```{r cfaplot, eval=FALSE, include=FALSE}
 #This chunk holds codes to store CFA plot
 
-png(filename="Manuscript.figures/CFAplot.png", 
+png(filename="Manuscript.figures/CFAplot2.png", 
     type="cairo",
@@
 ```{r figcfa, fig.cap = "Five factor  model of LEBA obtained by confirmatory factor analysis.
-By allowing item pair 41 and 30 to covary their error variance our model attained the best fit.",  out.height='100%', warning=FALSE}
+By allowing item pair 41 and 30 to covary their error variance our model attained the best fit.",  out.height='100%',out.width='100%', warning=FALSE}
 

### 2022-03-10 manuscript.Rmd
List of instruments removed from main manuscript

@@
 
-```{r relscale, include=F, warning=F, message=F}
+```{r relscale, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
 #This chunk holds code for Relevant scales table in the manuscript
@@
 
-```{r reltab2, results='asis'}
+```{r reltab2, eval=FALSE, include=FALSE, results='asis'}
 relevant.scale.data %>% 

### 2022-03-10 manuscript.Rmd
Inferential stats removed from Demographics

@@
     missing = "no"
-    ) %>% add_overall() %>% bold_labels() %>% add_p() %>% add_q() %>%
-modify_header(label ~ "**Variable**") %>% separate_p_footnotes() %>%
+    ) %>% add_overall() %>% bold_labels() %>% 
+  # add_p() %>% add_q() %>%
+modify_header(label ~ "**Variable**") %>% 
+  # separate_p_footnotes() %>%
   modify_caption("Demographic Characteristics of Partinipants (n=690)") -> desc_table

### 2022-03-10 manuscript.Rmd
GT Fig with stem EFA S1 Fig

@@
 Questions incorporating retrospective recall were all aligned to the period of "past four weeks".
-At first we collected data for from `r nrow(EFA.descriptives)` participants (EFA sample).
-Next, we collected data from another `r nrow(CFA.descriptives)` participants (CFA sample) making a total sample of `r nrow(desctable.data)`.
+We conducted two rounds of data collections.
+At first we collected data for from `r nrow(EFA.descriptives)` participants  In the second round we collected data from another `r nrow(CFA.descriptives)` participants making a total sample of `r nrow(desctable.data)`.
+
 The data analysed in this study was collected between 17 May 2021 and 3 September 2021.
@@
 As such we collapsed them into one, making it a 5 point Likert type response format.
-We conducted an initial item analysis and proceed to the exploratory factor analysis (EFA) with all 48 items (EFA sample;n=`r nrow(EFA.descriptives)`).
+
+We conducted an initial item analysis and proceed to the exploratory factor analysis (EFA) with all 48 items using the data collected in our first round.
+(EFA sample;n=`r nrow(EFA.descriptives)`).
 Prior to the EFA, necessary assumptions, including sample adequacy, normality assumptions, quality of correlation matrix were assessed.
@@
 
-To validated the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with weighted least square with mean and variance adjusted (WLSMV) estimator estimator [@desjardinsHandbookEducationalMeasurement2018] on a separate sample (CFA sample;n=`r nrow(CFA.descriptives)`).
+To validated the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with weighted least square with mean and variance adjusted (WLSMV) estimator estimator [@desjardinsHandbookEducationalMeasurement2018] on the data collected n our second round of data collection (CFA sample;n=`r nrow(CFA.descriptives)`).
 We assessed the model fit using common model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI):  close to .95 or above/ between 90-95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner].
@@
 
+### Descriptive Statistics
+
+```{r gtvis, include =F}
+#This chunk holds codes for creating 'gtExtra' based descriptive figures (data preparation)
+
+## Recoding sem.data$item8
+gt.data <- sem.data
+gt.data$item08 <- as.character(gt.data$item08)
+gt.data$item08 <- fct_recode(gt.data$item08,
+  "5" = "1",
+  "4" = "2",
+  "2" = "4",
+  "1" = "5"
+)
+
+## Recoding gt.data$item26
+gt.data$item26 <- as.character(gt.data$item26)
+gt.data$item26 <- fct_recode(gt.data$item26,
+  "5" = "1",
+  "4" = "2",
+  "2" = "4",
+  "1" = "5"
+)
+## Recoding gt.data$item37
+gt.data$item37 <- as.character(gt.data$item26)
+gt.data$item37 <- fct_recode(gt.data$item26,
+  "5" = "1",
+  "4" = "2",
+  "2" = "4",
+  "1" = "5"
+)
+
+# all data Gt Table
+##Long table
+gt.long <- as.data.frame(gather(gt.data, Items, value))
+gt.long$value <- as.numeric(as.character(gt.long$value))
+
+##Summarizing and creating gt object
+
+gt.tab <- gt.long %>% 
+  group_by(Items) %>% 
+  # calculate summary stats & create data for the histogram and density plot
+  dplyr::summarise(
+    nr = n(),
+    mean = mean(value, na.rm = TRUE),
+    med = median(value, na.rm = TRUE),
+    sd = sd(value, na.rm = TRUE),
+    hist_data = list(value),
+    dens_data = list(value),
+    .groups = "drop"
+  ) %>% 
+  gt()
+
+gt.tab1 <- gt.tab$`_data`
+
+gt.tab2 <- gt.tab1[,-c(1,2)]
+
+vars_labels = as.data.frame(sapply(sem.data,
+       function(x){attr(x,"label")}))
+
+vars_labels<- tibble::rownames_to_column(vars_labels, "Items")
+colnames(vars_labels) <- c("Item", "Stem")
+
+gt.tab3 <- cbind(vars_labels, gt.tab2)
+
+#Preparation for likert data
+LEBA.likert <- as.data.frame(gt.data)
+
+recod_LEBA <- c( "1" = "Never", "2" = "Rarely", "3"= "Sometimes","4" = "Often",
+                 "5" = "Always")
+LEBA.likert <-  mutate(LEBA.likert, across(starts_with("item"), ~unname(recod_LEBA[.])))
+
+LEBA.Factor = as.data.frame(lapply(LEBA.likert,factor,
+                                   ordered = T))
+#get the items name
+items <- names(LEBA.Factor) 
+#Calculate percentage
+percentage <- kutils::likert(LEBA.Factor, vlist = items )
+
+percentage <- percentage$table %>% 
+  as.data.frame(.)
+
+#data wrangling
+labels <- c("Always", "Never","Often", "Rarely", "Sometimes","Total")
+as.data.frame(labels)
+
+full.percentage <- cbind(labels,percentage) #tables with labels  
+full.percentage<- t(full.percentage ) #transpose
+as.data.frame(full.percentage)
+full.percentage1 <- full.percentage[-1,-6] #removing 1st row and total column
+full.percentage2 <- full.percentage1[, c(2, 4, 5, 3,1)]# rearranging
+as.data.frame(full.percentage2)
+
+colnames(full.percentage2) <- c("Never","Rarely","Sometimes","Often","Always")
+
+Items <- rownames(full.percentage2)
+as.data.frame(Items)
+full.percentage3 <- cbind(Items,full.percentage2)
+
+full.percentage3 <- full.percentage3[order(Items),] 
+full.percentage3 <- as.data.frame(full.percentage3[,-1]) %>% 
+  gt()
+
+liket.full <- full.percentage3$"_data"
+
+full.table <-  cbind( gt.tab3, liket.full)%>% 
+  gt()
+
+```
+
+```{r fullgt,  include=FALSE}
+#This chunk holds codes for creating 'gtExtra' based descriptive figures (EFA+CFA);
+
+full.tab <- full.table$`_data`
+
+full.tab.1 <- full.tab[1:24,] %>% 
+  gt()
+
+full.tab.2 <- full.tab[24:48,] %>% 
+  gt()
+
+full.tab.1 %>% 
+# histogram and density plots
+  gtExtras::gt_sparkline(
+    hist_data,
+    type = "histogram",
+    line_color = "black", 
+    fill_color = "#00A08799",
+    bw = 1,
+    same_limit = TRUE)%>%
+  gtExtras::gt_sparkline(
+    dens_data,
+    type = "density",
+    line_color = "black", 
+    fill_color = "grey",
+    bw = 0.75,
+    same_limit = TRUE
+  )%>%
+# format decimals
+  fmt_number(columns = mean:sd, decimals = 1) %>%
+# header
+  tab_header(
+    title = md("Summary Descriptives (n =690)"),
+    subtitle = md("Items 01-24 ")) %>% 
+#create groups of columns
+tab_spanner(
+  label = "Item",
+  columns = Item:Stem
+) %>%
+  cols_align(
+    align = "left",
+    columns = Item:Stem
+  ) %>% 
+  tab_spanner(
+    label = "Summary Statistics",
+    columns = mean:sd
+  ) %>%
+  tab_spanner(
+    label = "Graphics",
+    columns = hist_data:dens_data
+  ) %>% 
+  tab_spanner(
+    label = "Response Pattern",
+    columns = Never:Always
+  ) %>%
+# change column names to appear in the table
+cols_label(
+  Item = ("Items"),
+  Stem = ("Stem"),
+  mean = ("Mean"),
+  med = ("Median "),
+  sd = (("SD")),
+  hist_data = "Histogram",
+  dens_data = "Density"
+) %>%
+# set alignment as per wish
+  cols_align(
+    align = "center",
+    columns = mean:Always
+  ) %>%
+  opt_align_table_header(align = "left") %>%
+# add coloured dots and lines on the first column
+  gt_plt_dot(
+    mean,
+    Item,
+    palette = "ggthemes::fivethirtyeight"
+  ) %>% tab_options(
+    table.font.size = px(14L)) %>% 
+  cols_width(
+    Stem ~ px(200)) %>% 
+ gtsave("Manuscript.figures/gt_full_p1.png", vwidth = 6000)
+
+full.tab.2 %>% 
+# histogram and density plots
+  gtExtras::gt_sparkline(
+    hist_data,
+    type = "histogram",
+    line_color = "black", 
+    fill_color = "#00A08799",
+    bw = 1,
+    same_limit = TRUE)%>%
+  gtExtras::gt_sparkline(
+    dens_data,
+    type = "density",
+    line_color = "black", 
+    fill_color = "grey",
+    bw = 0.75,
+    same_limit = TRUE
+  )%>%
+# format decimals
+  fmt_number(columns = mean:sd, decimals = 1) %>%
+# header
+  tab_header(
+    title = md("Summary Descriptives (n =690)"),
+    subtitle = md("Items 24-48 ")) %>% 
+#create groups of columns
+tab_spanner(
+  label = "Item",
+  columns = Item:Stem
+) %>%
+  cols_align(
+    align = "left",
+    columns = Item:Stem
+  ) %>% 
+  tab_spanner(
+    label = "Summary Statistics",
+    columns = mean:sd
+  ) %>%
+  tab_spanner(
+    label = "Graphics",
+    columns = hist_data:dens_data
+  ) %>% 
+  tab_spanner(
+    label = "Response Pattern",
+    columns = Never:Always
+  ) %>%
+# change column names to appear in the table
+cols_label(
+  Item = ("LEBA  Items"),
+  Stem = ("Stem"),
+  mean = ("Mean"),
+  med = ("Median "),
+  sd = (("SD")),
+  hist_data = "Histogram",
+  dens_data = "Density"
+) %>%
+# set alignment as per wish
+  cols_align(
+    align = "center",
+    columns = mean:Always
+  ) %>%
+  opt_align_table_header(align = "left") %>%
+# add coloured dots and lines on the first column
+  gt_plt_dot(
+    mean,
+    Item,
+    palette = "ggthemes::fivethirtyeight"
+  ) %>% tab_options(
+    table.font.size = px(14L)) %>% 
+  cols_width(
+    Stem ~ px(200)) %>% 
+gtsave("Manuscript.figures/gt_full_p2.png",vwidth = 6000)
+
+```
+
+```{r efagtPic1, echo=FALSE,  fig.cap= ' Summary descriptives and response pattern'}
+knitr::include_graphics('Manuscript.figures/gt_full_p1.png')
+
+```
+
+```{r efagtPic2, echo=FALSE,  fig.cap= ' Summary descriptives and response pattern'}
+knitr::include_graphics('Manuscript.figures/gt_full_p2.png')
+
+```
+
+Figure \@ref(fig:efagtPic1) and Figure \@ref(fig:efagtPic2) summarize the response pattern of our total sample (n = `r nrow(sem.data)`) for all 48 items.
+Most of the items were skewed and violated normality assumption.
+
+### Item Analysis
+
 ```{r EFAdata, include=FALSE}
@@
 
-colnames(descriptives) <- c("Items", "Mean", "SD", "Skew", "Kurtosis", "SW$^{1}$", "Item Total Correlation")
+colnames(descriptives) <- c("Items", "Mean", "SD", "Skew", "Kurtosis", "SW", "Item Total Correlation")
 
@@
 ```
-
-### Item Analysis
 
@@
 
-Table \@ref(tab:tabDes) summarizes the univariate descriptive statistics for the 48 items.
-Some of the items were skewed with high Kurtosis values.
+```{r gt-EFA, include =F}
+#EFA data
+gt.efa.data <- EFA.data
+
+# gt.efa.data.table <- gt.efa.data %>% 
+#   dplyr::select(item16, item36, item17,
+#                  item11, item10,item12,item07,item08,item09,
+#                  item27,  item03, item40,  item30, item41,
+#                  item33, item32,item35, item37,item38, 
+#                  item46, item45, item25, item04, item01,item26)
+
+#Creating long data
+gt.efa.long <- as.data.frame(gather(gt.efa.data, Items, value))
+gt.efa.long$value <- as.numeric(as.character(gt.efa.long$value))
+
+#Summarizing and creating gt object
+gt.efa.tab <- gt.efa.long %>% 
+  group_by(Items) %>% 
+  # calculate summary stats & create data for the histogram and density plot
+  dplyr::summarise(
+    # nr = n(),
+    # mean = mean(value, na.rm = TRUE),
+    # med = median(value, na.rm = TRUE),
+    # sd = sd(value, na.rm = TRUE),
+    hist_data = list(value),
+    dens_data = list(value),
+    .groups = "drop"
+  ) %>% 
+  gt()
+
+#Preparation for likert data
+efa.LEBA.likert <- as.data.frame(gt.efa.data)
+
+recod_LEBA <- c( "1" = "Never", "2" = "Rarely", "3"= "Sometimes","4" = "Often",
+                 "5" = "Always")
+efa.LEBA.likert <-  mutate(efa.LEBA.likert, across(starts_with("item"), ~unname(recod_LEBA[.])))
+
+efa.LEBA.Factor = as.data.frame(lapply(efa.LEBA.likert,factor,
+                                   ordered = T))
+#get the items name
+efa.items <- names(efa.LEBA.Factor) 
+#Calculate percentage
+efa.percentage <- kutils::likert(efa.LEBA.Factor, vlist = efa.items )
+
+efa.percentage <- efa.percentage$table %>% 
+  as.data.frame(.)
+
+#data wrangling
+labels <- c("Always", "Never","Often", "Rarely", "Sometimes","Total")
+as.data.frame(labels)
+
+full.efa.percentage <- cbind(labels,efa.percentage) #tables with labels  
+full.efa.percentage<- t(full.efa.percentage ) #transpose
+as.data.frame(full.efa.percentage)
+full.efa.percentage1 <- full.efa.percentage[-1,-6] #removing 1st row and total column
+full.efa.percentage2 <- full.efa.percentage1[, c(2, 4, 5, 3,1)]# rearranging
+as.data.frame(full.efa.percentage2)
+
+colnames(full.efa.percentage2) <- c("Never","Rarely","Sometimes","Often","Always")
+
+efa.Items <- rownames(full.efa.percentage2)
+as.data.frame(efa.Items)
+full.efa.percentage3 <- cbind(efa.Items,full.efa.percentage2)
+
+full.efa.percentage3 <- full.efa.percentage3[order(efa.Items),] 
+full.efa.percentage3 <- as.data.frame(full.efa.percentage3[,-1]) %>% 
+  gt()
+
+gt.efa.table <- gt.efa.tab$'_data'
+gt.liket.efa <- full.efa.percentage3$"_data"
+
+efaTable <-  cbind( gt.efa.table, gt.liket.efa)%>% 
+  gt()
+
+ efa.gt <- efaTable$"_data"
+
+ efa.gt.2 <- cbind(descriptives2[,-2], efa.gt[,-1])
+```
+
+```{r efagt,include=F}
+
+#This chunk holds codes for creating 'gtExtra' based descriptive figures (EFA descriptives Supplimentary
+
+efa.gt.2 %>% 
+gt() %>% 
+# histogram and density plots
+  gtExtras::gt_sparkline(
+    hist_data,
+    type = "histogram",
+    line_color = "black", 
+    fill_color = "#00A08799",
+    bw = 1,
+    same_limit = TRUE)%>%
+  gtExtras::gt_sparkline(
+    dens_data,
+    type = "density",
+    line_color = "black", 
+    fill_color = "#E64B3599",
+    bw = 0.75,
+    same_limit = TRUE
+  )%>%
+# # format decimals
+#   fmt_number(columns = mean:sd, decimals = 1) %>%
+# header
+  tab_header(
+    title = md("**Light Exposure Behavior Assessment**"),
+    subtitle = md("Summary Descriptives EFA Sample (n =428)")
+  ) %>% 
+   tab_footnote(
+     footnote = md("**Shapiro–Wilk test**"),
+     locations = cells_column_labels(columns = SW)
+  ) %>%
+
+#create groups of columns
+tab_spanner(
+  label = "Items",
+  columns = Item
+)  %>% 
+  tab_spanner(
+    label = "Summary Statistics",
+    columns = Mean:SW
+  ) %>%
+  tab_spanner(
+    label = "Graphics",
+    columns = hist_data:dens_data
+  ) %>% 
+  tab_spanner(
+    label = "Response Pattern",
+    columns = Never:Always
+  ) %>%
+# change column names to appear in the table
+cols_label(
+  hist_data = "Histogram",
+  dens_data = "Density"
+) %>%
+# set alignment as per wish
+  cols_align(
+    align = "center",
+    columns = everything()
+  ) %>%
+  opt_align_table_header(align = "left") %>%
+# add coloured dots and lines on the first column
+  gt_plt_dot(
+    Mean,
+    Item,
+    palette = "ggthemes::fivethirtyeight") %>% 
+  tab_options(
+    table.font.size = px(14L)) %>%
+
+  gtsave("Supplimentary_Materials/S_Figure/S1_Fig.png", vwidth=6000)
+
+# tab_row_group(
+  #     label = md("**F5: Using light in the morning and during daytime**"),
+  #     rows = c(1,3,12,13,24,25) 
+  #       ) %>% 
+  # tab_row_group(
+  #     label = md("**F4: Using light before bedtime**"),
+  #     rows = c(16,17,18,20,21) 
+  #       ) %>% 
+  # tab_row_group(
+  #     label = md("**F3: Using phone and smart-watch in bed**"),
+  #     rows = c(2,14,15,22,23) 
+  #       ) %>% 
+  # tab_row_group(
+  #     label = md("**F2: Spending time outdoors**"),
+  #     rows = c(4,5,6,7,8,9) 
+  #       ) %>% 
+  # tab_row_group(
+  #     label = md("**F1: Wearing blue light filters**"),
+  #     rows = c(10,11,19) )
+
+```
+
+S1 Fig summarizes the univariate descriptive statistics for the 48 items among  EFA sample (n =`r nrow(EFA.data)`.
 Our data violated both univariate normality [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970].
@@
 
-Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy [@kaiserIndexFactorialSimplicity1974] .
+Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy using the EFA sample (n =`r nrow(EFA.data)` [@kaiserIndexFactorialSimplicity1974] .
 The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cutoff value (.50) indicating adequate sample size [@hutchesonMultivariateSocialScientist1999].
@@
 
-```{r tabDes,results='asis'}
+```{r tabDes, eval=FALSE, include=FALSE, results='asis'}
 descriptives2 %>% 
@@
 
-```{r EFAplot, fig.align='center', fig.cap='(A) Five factor solution obtained in exploratory factor analysis (B) Histogram of nonredundent residula correlations', warning=FALSE,  results='asis'}
-
-knitr::include_graphics('Manuscript.figures/EFAfull.png', dpi =600)
-```
-
-```{r gtvis, include =F}
-#This chunk holds codes for creating 'gtExtra' based descriptive figures (data preparation)
-
-## Recoding sem.data$item8
-gt.data <- sem.data
-gt.data$item08 <- as.character(gt.data$item08)
-gt.data$item08 <- fct_recode(gt.data$item08,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-
-## Recoding gt.data$item26
-gt.data$item26 <- as.character(gt.data$item26)
-gt.data$item26 <- fct_recode(gt.data$item26,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-## Recoding gt.data$item37
-gt.data$item37 <- as.character(gt.data$item26)
-gt.data$item37 <- fct_recode(gt.data$item26,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
-)
-
-#EFA data
-gt.efa.data <- gt.data[1:428, ]
-
-gt.efa.data.table <- gt.efa.data %>% 
-  dplyr::select(item16, item36, item17,
-                 item11, item10,item12,item07,item08,item09,
-                 item27,  item03, item40,  item30, item41,
-                 item33, item32,item35, item37,item38, 
-                 item46, item45, item25, item04, item01,item26)
-
-#Creating long data
-gt.efa.long <- as.data.frame(gather(gt.efa.data.table, Items, value))
-gt.efa.long$value <- as.numeric(as.character(gt.efa.long$value))
-
-#Summarizing and creating gt object
-gt.efa.tab <- gt.efa.long %>% 
-  group_by(Items) %>% 
-  # calculate summary stats & create data for the histogram and density plot
-  dplyr::summarise(
-    nr = n(),
-    mean = mean(value, na.rm = TRUE),
-    med = median(value, na.rm = TRUE),
-    sd = sd(value, na.rm = TRUE),
-    hist_data = list(value),
-    dens_data = list(value),
-    .groups = "drop"
-  ) %>% 
-  gt()
-
-#Preparation for likert data
-efa.LEBA.likert <- as.data.frame(gt.efa.data.table)
-
-recod_LEBA <- c( "1" = "Never", "2" = "Rarely", "3"= "Sometimes","4" = "Often",
-                 "5" = "Always")
-efa.LEBA.likert <-  mutate(efa.LEBA.likert, across(starts_with("item"), ~unname(recod_LEBA[.])))
-
-efa.LEBA.Factor = as.data.frame(lapply(efa.LEBA.likert,factor,
-                                   ordered = T))
-#get the items name
-efa.items <- names(efa.LEBA.Factor) 
-#Calculate percentage
-efa.percentage <- kutils::likert(efa.LEBA.Factor, vlist = efa.items )
-
-efa.percentage <- efa.percentage$table %>% 
-  as.data.frame(.)
-
-#data wrangling
-labels <- c("Always", "Never","Often", "Rarely", "Sometimes","Total")
-as.data.frame(labels)
-
-full.efa.percentage <- cbind(labels,efa.percentage) #tables with labels  
-full.efa.percentage<- t(full.efa.percentage ) #transpose
-as.data.frame(full.efa.percentage)
-full.efa.percentage1 <- full.efa.percentage[-1,-6] #removing 1st row and total column
-full.efa.percentage2 <- full.efa.percentage1[, c(2, 4, 5, 3,1)]# rearranging
-as.data.frame(full.efa.percentage2)
-
-colnames(full.efa.percentage2) <- c("Never","Rarely","Sometimes","Often","Always")
-
-efa.Items <- rownames(full.efa.percentage2)
-as.data.frame(efa.Items)
-full.efa.percentage3 <- cbind(efa.Items,full.efa.percentage2)
-
-full.efa.percentage3 <- full.efa.percentage3[order(efa.Items),] 
-full.efa.percentage3 <- as.data.frame(full.efa.percentage3[,-1]) %>% 
-  gt()
-
-gt.efa.table <- gt.efa.tab$'_data'
-gt.liket.efa <- full.efa.percentage3$"_data"
-
-efaTable <-  cbind( gt.efa.table, gt.liket.efa)%>% 
-  gt()
-
+```{r EFAplot, eval=FALSE, fig.align='center', fig.cap='(A) Five factor solution obtained in exploratory factor analysis (B) Histogram of nonredundent residula correlations', warning=FALSE, include=FALSE, results='asis'}
+
+knitr::include_graphics('Manuscript.figures/gt_full.png', dpi =600)
+```
+
+```{r ft-CFA, include =F}
 gt.cfa.data <- gt.data[429:690,]
@@
 
-efa.gt <- efaTable$"_data"
 cfa.gt <- cfaTable$"_data"
@@
 
-```{r efagt,include=F}
-
-#This chunk holds codes for creating 'gtExtra' based descriptive figures (EFA descriptives
-
-efa.gt %>% 
-gt() %>% 
-# histogram and density plots
-  gtExtras::gt_sparkline(
-    hist_data,
-    type = "histogram",
-    line_color = "black", 
-    fill_color = "#00A08799",
-    bw = 1,
-    same_limit = TRUE)%>%
-  gtExtras::gt_sparkline(
-    dens_data,
-    type = "density",
-    line_color = "black", 
-    fill_color = "#E64B3599",
-    bw = 0.75,
-    same_limit = TRUE
-  )%>%
-# format decimals
-  fmt_number(columns = mean:sd, decimals = 1) %>%
-# header
-  tab_header(
-    title = md("**Light Exposure Behavior Assessment**"),
-    subtitle = md("Summary Descriptives EFA Sample (n =428)")
-  ) %>% 
-  # tab_footnote(
-  #   footnote = md("**Histogram**"),
-  #   locations = cells_column_labels(columns = hist_data)
-  # ) %>%
-  # tab_footnote(
-  #   footnote = md("**Density**"),
-  #   locations = cells_column_labels(columns = dens_data)
-  # ) %>% 
-#create groups of columns
-tab_spanner(
-  label = "Items",
-  columns = Items
-) %>%
-  tab_spanner(
-    label = "Summary Statistics",
-    columns = nr:sd
-  ) %>%
-  tab_spanner(
-    label = "Graphics",
-    columns = hist_data:dens_data
-  ) %>% 
-  tab_spanner(
-    label = "Response Pattern",
-    columns = Never:Always
-  ) %>%
-# change column names to appear in the table
-cols_label(
-  Items = (""),
-  nr = ("n"),
-  mean = ("Mean"),
-  med = ("Median "),
-  sd = (("SD")),
-  hist_data = "Histogram",
-  dens_data = "Density"
-) %>%
-# set alignment as per wish
-  cols_align(
-    align = "center",
-    columns = everything()
-  ) %>%
-  opt_align_table_header(align = "left") %>%
-# add coloured dots and lines on the first column
-  gt_plt_dot(
-    mean,
-    Items,
-    palette = "ggthemes::fivethirtyeight") %>% 
-  tab_row_group(
-      label = md("**F5: Using light in the morning and during daytime**"),
-      rows = c(1,3,12,13,24,25) 
-        ) %>% 
-  tab_row_group(
-      label = md("**F4: Using light before bedtime**"),
-      rows = c(16,17,18,20,21) 
-        ) %>% 
-  tab_row_group(
-      label = md("**F3: Using phone and smart-watch in bed**"),
-      rows = c(2,14,15,22,23) 
-        ) %>% 
-  tab_row_group(
-      label = md("**F2: Spending time outdoors**"),
-      rows = c(4,5,6,7,8,9) 
-        ) %>% 
-  tab_row_group(
-      label = md("**F1: Wearing blue light filters**"),
-      rows = c(10,11,19) 
-        ) %>% gtsave("Manuscript.figures/efagt.png",vwidth = 7000)
-
-```
-
 ```{r cfagt,include=F}
-#This chunk holds codes for creating 'gtExtra' based descriptive figures (CFA Descriptives)
+#This chunk holds codes for creating 'gtExtra' based descriptive figures (CFA Descriptives Supplementary
 
@@
         ) %>% 
-  gtsave("Manuscript.figures/cfagt.png",vwidth = 7000)
-
-```
-
-```{r eval=FALSE, include=FALSE}
-#This chunk holds codes for creating 'gtExtra' based descriptive figures (EFA+CFA); 
-#Not included in the manuscript
-
-gt.fullTable <-  rbind( efa.gt, cfa.gt) %>% 
-  gt() %>% 
-# histogram and density plots
-  gtExtras::gt_sparkline(
-    hist_data,
-    type = "histogram",
-    line_color = "black", 
-    fill_color = "#00A08799",
-    bw = 1,
-    same_limit = TRUE)%>%
-  gtExtras::gt_sparkline(
-    dens_data,
-    type = "density",
-    line_color = "black", 
-    fill_color = "grey",
-    bw = 0.75,
-    same_limit = TRUE
-  )%>%
-# format decimals
-  fmt_number(columns = mean:sd, decimals = 1) %>%
-# header
-  tab_header(
-    title = md("**LEBA**"),
-    subtitle = md("Summary Descriptives of CFA and EFA Sample (N =690)")
-  ) %>% 
-  tab_footnote(
-    footnote = md("**Histogram**"),
-    locations = cells_column_labels(columns = hist_data)
-  ) %>%
-  tab_footnote(
-    footnote = md("**Density**"),
-    locations = cells_column_labels(columns = dens_data)
-  ) %>% 
-#create groups of columns
-tab_spanner(
-  label = "Items",
-  columns = Items
-) %>%
-  tab_spanner(
-    label = "Summary Statistics",
-    columns = nr:sd
-  ) %>%
-  tab_spanner(
-    label = "Graphics",
-    columns = hist_data:dens_data
-  ) %>% 
-  tab_spanner(
-    label = "Response Pattern",
-    columns = Never:Always
-  ) %>%
-# change column names to appear in the table
-cols_label(
-  Items = ("LEBA  Items"),
-  nr = ("n"),
-  mean = ("Mean"),
-  med = ("Median "),
-  sd = (("SD")),
-  hist_data = "Histogram",
-  dens_data = "Density"
-) %>%
-# set alignment as per wish
-  cols_align(
-    align = "center",
-    columns = everything()
-  ) %>%
-  opt_align_table_header(align = "left") %>%
-# add coloured dots and lines on the first column
-  gt_plt_dot(
-    mean,
-    Items,
-    palette = "ggthemes::fivethirtyeight"
-  ) %>% 
-    tab_row_group(
-      group = "CFA (n =262)",
-     rows = 26:48
-
-  ) %>% 
-  tab_row_group(
-  group = "EFA (n = 428)",
-    rows = 1:25  
-  ) %>% gtsave("Manuscript.figures/gt.png",vwidth = 7000)
-
-```
-
-```{r efagtPic, echo=FALSE, out.height="100%", out.width= '100%', fig.cap= ' Summary descriptives and response pattern of EFA sample'}
-knitr::include_graphics('Manuscript.figures/efagt.png',dpi =600)
-
-```
-
-```{r cfagtPic, echo=FALSE, out.height="100%", out.width= '100%', fig.cap= ' Summary descriptives and response pattern of CFA sample'}
-knitr::include_graphics('Manuscript.figures/cfagt.png',dpi =600)
+  gtsave("Supplimentary Materials/S_Figure/cfagt.png",vwidth = 7000)
 

### 2022-03-21 manuscript.Rmd
Minor typo corrected in the analysis plan

@@
 
-To validated the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with weighted least square with mean and variance adjusted (WLSMV) estimator estimator [@desjardinsHandbookEducationalMeasurement2018] on the data collected n our second round of data collection (CFA sample;n=`r nrow(CFA.descriptives)`).
+To validated the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with weighted least square with mean and variance adjusted (WLSMV) estimator  [@desjardinsHandbookEducationalMeasurement2018] on the data collected n our second round of data collection (CFA sample;n=`r nrow(CFA.descriptives)`).
 We assessed the model fit using common model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI):  close to .95 or above/ between 90-95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner].

### 2022-03-21 manuscript.Rmd
S.tab1 is excluded from Rmd file.
EFA table is updated with item stem CFA and MI table caption typo corrected

@@
 
--   Light exposure Behavior is important
-
--   Table: Overview Existing Related Scales: items in total / items on light exposure (behaviour)
+-   Light exposure Behaviour is important
+
+-   Supplementary Table S1 Overview Existing Related Scales: items in total / items on light exposure (behaviour)
 
@@
 
-```{r efagtPic1, echo=FALSE,  fig.cap= ' Summary descriptives and response pattern'}
+```{r efagtPic1, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern'}
 knitr::include_graphics('Manuscript.figures/gt_full_p1.png')
@@
 
-```{r efagtPic2, echo=FALSE,  fig.cap= ' Summary descriptives and response pattern'}
+```{r efagtPic2, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern'}
 knitr::include_graphics('Manuscript.figures/gt_full_p2.png')
@@
 
-```{r EFAplotcode, include=FALSE}
+```{r EFAplotcode, eval=FALSE, include=FALSE}
 #This chunk holds code for the EFA plot
@@
 
+item16 <- Hmisc::label(EFA.data$item16)
+item36 <- Hmisc::label(EFA.data$item36)
+item17 <- Hmisc::label(EFA.data$item17)
+item11 <- Hmisc::label(EFA.data$item11)
+item10 <- Hmisc::label(EFA.data$item10)
+item12 <- Hmisc::label(EFA.data$item12)
+item07 <- Hmisc::label(EFA.data$item07)
+item08 <- Hmisc::label(EFA.data$item08)
+item09 <- Hmisc::label(EFA.data$item09)
+item27 <- Hmisc::label(EFA.data$item27)
+item03 <- Hmisc::label(EFA.data$item03)
+item40 <- Hmisc::label(EFA.data$item40)
+item30 <- Hmisc::label(EFA.data$item30)
+item41 <- Hmisc::label(EFA.data$item41)
+item33 <- Hmisc::label(EFA.data$item33)
+item32 <- Hmisc::label(EFA.data$item32)
+item35 <- Hmisc::label(EFA.data$item35)
+item37 <- Hmisc::label(EFA.data$item37)
+item38 <- Hmisc::label(EFA.data$item38)
+item46 <- Hmisc::label(EFA.data$item46)
+item45 <- Hmisc::label(EFA.data$item45)
+item25 <- Hmisc::label(EFA.data$item25)
+item04 <- Hmisc::label(EFA.data$item04)
+item01 <- Hmisc::label(EFA.data$item01)
+item26 <- Hmisc::label(EFA.data$item26)
+
+efa.stems <- as.data.frame(rbind(item16,item36, item17, item11, item10, item12, item07, item08, item09, item27, item03, item40, item30, item41, item33, item32, item35, item37, item38, item46, item45, item25, item04, item01, item26, ""))
+colnames(efa.stems) <- "Stem"
+
+efa.tab.ful <- cbind(efa.table[,1],efa.stems, efa.table[,2:8] )
+
 #Communality
@@
 
-apa_table(efa.table,align = "c", caption = "Factor loadings and communality of the retained items", note = "Only loading > .30 is reported", font_size = "small")
+apa_table(efa.tab.ful, caption = "Factor loadings and communality of the retained items", note = "Only loading > .30 is reported", 
+          font_size = "footnotesize", escape=F,landscape = T,
+           align = c("p{1cm}","p{10cm}", rep("p{1cm}", ncol(efa.tab.ful))))
 ```
@@
 colnames(CFa.matrix) = c("Model", "$\\chi^{2}$", "df", "CFI", "TLI", "RMSEA", "RMSEA 90\\% Lower CI", "RMSEA 90\\% Upper CI", "SRMR")
-CFa.matrix[1,] = c("Five factor model:25", 
+CFa.matrix[1,] = c("Model 1", 
                    apa(cfa.sum.1$FIT[6],2,T), 
@@
 
-CFa.matrix[2,] = c("Five factor model:23", 
+CFa.matrix[2,] = c("Model 2", 
                    apa(cfa.sum.2$FIT[6],2,T), 
@@
 ```{r tabCfa, results='asis'}
-apa_table(CFa.matrix, caption = "Confirmatory Factor Analysis model fit indices of the two model: five factor model with 25 items and five factor model with 23 items.
-The second model attained the best fit.", align = "c", landscape = T, escape=F, note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index;RMSEA:Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square ")
+apa_table(CFa.matrix, caption = "Confirmatory Factor Analysis model fit indices of the two model: (a) Model 1: five factor model with 25 items (b) Model 2:  five factor model with 23 items.
+Model 2 attained the best fit.", align = "c", landscape = T, escape=F, note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square ")
 ```
@@
 ```{r InvarianceTab, results='asis'}
-apa_table(Invariance.table, align = "c",  caption = "Measurment Invariance analysis on CFA sample (n=262) across native and non-native English speakers.", note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index;RMSEA:Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual;* =  df of model comparison", landscape = T, font_size = "footnotesize", escape=F )
+apa_table(Invariance.table, align = "c",  caption = "Measurment Invariance analysis on CFA sample (n=262) across native and non-native English speakers.", note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square; a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual; * =  df of model comparison", landscape = T, font_size = "footnotesize", escape=F )
 
@@
 We fitted each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690).
-Item discrimination parameters of our tool fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$).
+Item discrimination parameters of our tool fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$) (Supplementary Table 2).
 Examination of the item information curve (Sup.fig \@ref(fig:IF)) indicated five items (1, 25,  38, 30, & 41) had relatively flat information curves (I($\theta$) <.20).
@@
 
-```{r IRTparameters, results='asis'}
+```{r IRTparameters, eval=FALSE, include=FALSE, results='asis'}
 apa_table(itemparameters, caption = "Items discrimination and response category difficulty thresholds of 23 items in  LEBA (n =690)", note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
@@
 
-Table \@ref(tab:itemfittab) summarizes the item fit indexes of the items.
+Supplementary Table S3 summarizes the item fit indexes of the 18 items.
 All of the items had RMSEA value $\le$.06 indicating adequate fit of the items to the fitted IRT model.
@@
 
-```{r itemfittab, results='asis',warning=F, message=F}
+```{r itemfittab, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, results='asis'}
 apa_table(IRT.details , caption ="Item discrimination, response category difficulty thrsholds and fit statistics of the 18 items in short LEBA (n=690)",note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")

### 2022-03-24 appendix-1.Rmd
EFA plots are now 2 by 2

@@
 Five items (1, 25,  38, 30, 41) had relatively flat information curves', out.width="100%", out.height="120%", out.extra = ""}
-knitr::include_graphics('Manuscript.figures/allitemplots.png', dpi = 300)
+knitr::include_graphics('Figures/allitemplots.png', dpi = 300)
 ```
@@
 ```{r personfit, fig.cap="Person fit of the five fitted IRT models (a) Wearing blue light filters (b) Spending time outdoors (c) Using phone and smartwatchin bed (d) Using light before bedtime (e) Using light in the morning andduring daytime", warning=FALSE, out.width="100%", out.height="120%"}
-knitr::include_graphics("Manuscript.figures/personfit.png",dpi = 600)
+knitr::include_graphics("Figures/personfit.png",dpi = 600)
 ```

### 2022-03-24 manuscript.Rmd
EFA plots are now 2 by 2

@@
 #install.packages("pacman")#Run this if you don't have pacman installed.
-pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap,huxtable,reshape, ggsci,networkD3, webshot)
+pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap,huxtable,reshape, ggsci,networkD3, webshot,ggtext)
 webshot::install_phantomjs()
@@
 install.packages("correlation")
+install.packages("ggtext")
 #if you dont have LaTeX installed run the following lines
@@
 library(ggsci)
+library(ggtext)
 r_refs("references.bib")
@@
 
-```{r Manuflowchart, include=FALSE }
+```{r Manuflowchart, eval=FALSE, include=FALSE}
 #This chunk holds code for the work flow chart of the data analysis
@@
   rsvg() %>%
-  png::writePNG("Manuscript.figures/Flowchart1.jpeg", dpi = 600)
+  png::writePNG("Figures/Flowchart1.jpeg", dpi = 600)
 
@@
 
-ggsave("Manuscript.figures/distribution.png", distribution, width = 12, height = 6, dpi = 600, bg ="white")
+ggsave("Figures/distribution.png", distribution, width = 12, height = 6, dpi = 600, bg ="white")
 
@@
 ```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long form (23-item) and short form (18-item) of LEBA. ', out.height='100%', out.width='100%'}
-knitr::include_graphics('Manuscript.figures/Flowchart1.jpeg', dpi = 600 )
+knitr::include_graphics('Figures/Flowchart.png', dpi = 600 )
 ```
@@
 ```{r partmap, eval=FALSE, fig.cap="Top ten countries with highest responses in our survey", include=FALSE, out.height='100%'}
-knitr::include_graphics('Manuscript.figures/distribution.png', dpi = 300 )
+knitr::include_graphics('Figures/distribution.png', dpi = 300 )
 ```
@@
     Stem ~ px(200)) %>% 
- gtsave("Manuscript.figures/gt_full_p1.png", vwidth = 6000)
+ gtsave("Figures/gt_full_p1.png", vwidth = 6000)
 
@@
     Stem ~ px(200)) %>% 
-gtsave("Manuscript.figures/gt_full_p2.png",vwidth = 6000)
+gtsave("Figures/gt_full_p2.png",vwidth = 6000)
 
@@
 ```{r efagtPic1, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern'}
-knitr::include_graphics('Manuscript.figures/gt_full_p1.png')
+knitr::include_graphics('Figures/gt_full_p1.png')
 
@@
 ```{r efagtPic2, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern'}
-knitr::include_graphics('Manuscript.figures/gt_full_p2.png')
+knitr::include_graphics('Figures/gt_full_p2.png')
 
@@
 
-  gtsave("Supplimentary_Materials/S_Figure/S1_Fig.png", vwidth=6000)
+  gtsave("Supplimentary_materials/S_Figure/S1_Fig.png", vwidth=6000)
 
@@
 
-ggsave("Manuscript.figures/correlation_histogram.png", corr.histogram, width = 6, height = 6, dpi = 600, bg ="white")
+# ggsave("Figures/correlation_histogram.png", corr.histogram, width = 6, height = 6, dpi = 600, bg ="white")
 ```
@@
 
-corplot <- ggcorrplot(correlations$rho, p.mat=p.mat$p, insig = "pch", hc.order = FALSE, outline.col = "white", type = "lower", legend.title = "Correlation",sig.level = 0.05, pch.cex=1.8,
+corplot <- ggcorrplot(correlations$rho, p.mat=p.mat$p, insig = "pch", hc.order = FALSE, outline.col = "white", type = "lower", legend.title = "Correlation",sig.level = 0.05, pch.cex=1.2,
                       # insig = "blank",
@@
   theme( panel.grid.major = element_blank(),
-         axis.text.x = element_text(size = 8),
-         axis.text.y = element_text(size = 8),
+         axis.text.x = element_text(size = 6),
+         axis.text.y = element_text(size = 6),
          panel.border = element_rect(color = "black",
@@
 #to show pvalue in the fig add p.mat=p.mat
-ggsave("Manuscript.figures/corplot.png",corplot, width = 12, height = 8.5, dpi = 600, bg ="white")
-
-```
-
-(ref:figCor) Inter-item polychoric correlation coefficients for the 48 items. 4.9 % inter-item correlation coefficients were higher than |.30|
-
-```{r figCor, out.height="150%",out.width="100%", fig.align= 'center', fig.cap='(ref:figCor)', results='asis', fig.align='center'}
-
-knitr::include_graphics('Manuscript.figures/corplot.png', dpi =600)
+# ggsave("Figures/corplot.png",corplot, width = 12, height = 8.5, dpi = 600, bg ="white")
 
@@
   scale_y_continuous(name="Eigen Value", limits=c(0, 5), breaks=seq(0,5,1)) +
-  scale_x_continuous(name='Factor Number (Scree Plot)', limits=c(0, 20),breaks=seq(0,20,4))+
+  scale_x_continuous(name="Factor Number", limits=c(0, 20),breaks=seq(0,20,4))+
   geom_hline(yintercept=1, linetype = 'dashed') + apatheme +theme(legend.position = "None") 
@@
 hull <- ggplot2::last_plot()
-Hull <- hull+ ggtitle(NULL)+xlab("Factor Number (Hull Method)")+ylab("CAF")+ aes(color = '#DC000099')+geom_point(color ='#3C5488FF',size =1)+
+Hull <- hull+ ggtitle(NULL)+xlab("Factor Number")+ylab("CAF")+ aes(color = '#DC000099')+geom_point(color ='#3C5488FF',size =1)+
   apatheme +theme(legend.position = "None") +scale_fill_identity()
@@
 
-Scree plot ( Figure \@ref(fig:facIdFig)) suggested a six-factor solution.
+Scree plot ( Figure \@ref(fig:efa-plot)) suggested a six-factor solution.
 However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (Table \@ref(tab:map)) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution.
 As a result, we tested both five-factor and six-factor solutions.
-
-```{r factors, include=F}
-#This chunk holds code for compiled factor identification plots
-
-fator <- cowplot::plot_grid(scree.plot,Hull, 
-                   labels = "AUTO",
-                   ncol=1, 
-                  align = "v", 
-                  label_fontfamily = "Arial",
-                  label_fontface = "plain")
-ggsave("Manuscript.figures/factors.png",fator, width = 5, height = 7, dpi = 600)
-```
-
-```{r factorsplot, eval=FALSE, include=FALSE}
-#This chunk holds code for compiled factor identification plots
-
-fator2 <- cowplot::plot_grid(scree.plot,Hull, 
-                   labels = "AUTO",
-                   ncol=3, 
-                  align = "v", 
-                  label_fontfamily = "Arial",
-                  label_fontface = "plain")
-ggsave("Manuscript.figures/factors2.png",fator2, width = 18, height = 6, dpi = 600)
-```
-
-(ref:facIdFig) Factor Identification Methods  (A) Scree plot suggested six factors. (B) Hull method indicated 5 factors were required to balance the model fit and number of parameters.
-
-```{r facIdFig, fig.align= 'center', fig.cap='(ref:facIdFig)',  warning=FALSE, results= 'asis'}
-
-knitr::include_graphics('Manuscript.figures/factors.png', dpi =800)
-
-```
 
@@
   rsvg() %>%
-  png::writePNG("Manuscript.figures/EFAplot.png",dpi =600)
+  png::writePNG("Figures/EFAplot.png",dpi =600)
 
@@
 
+```{r EFARes, message=FALSE, warning=FALSE, include=F}
+#This chunk holds codes for creating the residual plot for 5 factor EFA (pa-varimax)
+res.dat <- as.data.frame(unclass(residual.5F))
+residual.data <- as.data.frame(gather(res.dat, Items, Residuals))
+
+residual.plot <- ggplot(residual.data, aes(x=Residuals)) + geom_histogram(binwidth=.04, col=I("black"),fill="#00A08799") + xlim(-.2,.2)+ ylim(0,250)+apatheme +geom_vline(xintercept = .05)+theme(axis.text.x = element_text(size = 12),
+        axis.text.y = element_text(size = 12))+
+  labs( y="Frequency")
+
+```
+
+```{r efa-plot, include=F}
+#This chunk holds code for compiled factor identification plots
+
+cor.scree <- cowplot::plot_grid(corplot, scree.plot,
+                                labels = c("A", "B"),
+                                nrow =1, ncol =2,
+                                rel_widths = c(2, 1),
+                                label_fontfamily = "Arial",
+                  label_fontface = "plain")
+
+hull.residual <- cowplot::plot_grid(Hull, residual.plot,
+                                labels = c("C", "D"),
+                                nrow =1, ncol =2,
+                                                                label_fontfamily = "Arial",
+                  label_fontface = "plain")
+
+efa.plot <- cowplot::plot_grid(cor.scree, hull.residual,
+
+                                nrow =2)
+
+# efa.plot <- cowplot::plot_grid(corplot , scree.plot,Hull, residual.plot,
+#                    labels = "AUTO",
+#                    ncol=2,nrow=2, 
+#                   align = "v", 
+#                   label_fontfamily = "Arial",
+#                   label_fontface = "plain")
+ggsave("Figures/efa.plot.png",efa.plot, width = 7, height = 8, dpi = 600)
+```
+
+(ref:efa-plot-print) (A) Inter-item polychoric correlation coefficients for the 48 items.
+4.9 % inter-item correlation coefficients were higher than |.30|.
+(B) Scree plot suggested six factors.
+(C) Hull method indicated 5 factors were required to balance the model fit and number of parameters.
+(D) Histogram of nonredundent residual correlations indicated 26% of inter-item correlations were higher than .05, hinting a possible under factoring.
+
+```{r efa-plot-print, fig.align= 'center', fig.cap='(ref:efa-plot-print)',  warning=FALSE, results= 'asis'}
+
+knitr::include_graphics('Figures/efa.plot.png', dpi =600)
+
+```
+
 With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items.
@@
 The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`.
-Figure \@ref(fig:efagtPic) depicts the data distribution and endorsement pattern for the included 25 items.
-Figure \@ref(fig:EFAplot)(A) depicts the five factor structure obtained in EFA.
-However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:EFAplot)(B)) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring.
+Supplimentary figure 1 depicts the data distribution and endorsement pattern for the included 25 items.
+However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:efa-plot-print)(D)) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring.
 [@desjardinsHandbookEducationalMeasurement2018].
@@
 
-```{r EFARes, message=FALSE, warning=FALSE, include=F}
-#This chunk holds codes for creating the residual plot for 5 factor EFA (pa-varimax)
-res.dat <- as.data.frame(unclass(residual.5F))
-residual.data <- as.data.frame(gather(res.dat, Items, Residuals))
-
-residual.plot <- ggplot(residual.data, aes(x=Residuals)) + geom_histogram(binwidth=.04, col=I("black"),fill="#00A08799") + xlim(-.2,.2)+ ylim(0,250)+apatheme +geom_vline(xintercept = .05)+theme(axis.text.x = element_text(size = 12),
-        axis.text.y = element_text(size = 12))+
-  labs( y="Frequency")
-
-```
-
-```{r EFAplotprep, include=F}
+```{r EFAplotprep, eval=FALSE, include=FALSE}
 #This chunk holds codes for co-plotting EFA-plot and residual plot.
@@
 
-img1 <- png::readPNG("Manuscript.figures/EFAplot.png")
+img1 <- png::readPNG("Figures/EFAplot.png")
 
@@
 
-ggsave("Manuscript.figures/EFAfull.png",EFAplot.2, width = 6, height =7, dpi = 1200, bg ="white")
-
-```
-
-```{r EFAplot, eval=FALSE, fig.align='center', fig.cap='(A) Five factor solution obtained in exploratory factor analysis (B) Histogram of nonredundent residula correlations', warning=FALSE, include=FALSE, results='asis'}
-
-knitr::include_graphics('Manuscript.figures/gt_full.png', dpi =600)
-```
-
-```{r ft-CFA, include =F}
+ggsave("Figures/EFAfull.png",EFAplot.2, width = 6, height =7, dpi = 1200, bg ="white")
+
+```
+
+### Confirmatory Factor Analysis
+
+```{r gt-CFA, include =F}
 gt.cfa.data <- gt.data[429:690,]
@@
         ) %>% 
-  gtsave("Supplimentary Materials/S_Figure/cfagt.png",vwidth = 7000)
-
-```
-
-### Confirmatory Factor Analysis
+  gtsave("Supplimentary_materials/S_Figure/S2_Fig.png",vwidth = 7000)
+
+```
 
@@
 
-png(filename="Manuscript.figures/CFAplot2.png", 
+png(filename="Figures/CFAplot2.png", 
     type="cairo",
@@
 
-knitr::include_graphics("Manuscript.figures/CFAplot.png", dpi =600)
+knitr::include_graphics("Figures/CFAplot.png", dpi =600)
 
@@
 
-ggsave("Manuscript.figures/allitemplots.png",allitemplots, width = 18, height = 12, dpi = 600, bg = "white")
+ggsave("Figures/allitemplots.png",allitemplots, width = 18, height = 12, dpi = 600, bg = "white")
 
@@
 
-ggsave("Manuscript.figures/discarded.png",discarded.items.plot, width = 18, height = 4, dpi = 600, bg = "white")
+ggsave("Figures/discarded.png",discarded.items.plot, width = 18, height = 4, dpi = 600, bg = "white")
 
@@
                      label_fontface = "plain")
-ggsave("Manuscript.figures/TIC.png",TIC.plot, width = 18, height = 12, dpi = 600, bg = "white")
+ggsave("Figures/TIC.png",TIC.plot, width = 18, height = 12, dpi = 600, bg = "white")
 
@@
 
-knitr::include_graphics('Manuscript.figures/TIC.png', dpi =600)
+knitr::include_graphics('Figures/TIC.png', dpi =600)
 ```
@@
 
-ggsave("Manuscript.figures/personfit.png",personfit , width = 10, height = 12, dpi = 600, bg = "white")
+ggsave("Figures/personfit.png",personfit , width = 10, height = 12, dpi = 600, bg = "white")
 
@@
 #This chunk holds codes for saving the wright-map
-jpeg("Manuscript.figures/wm.png", width = 800, height = 750)
+jpeg("Figures/wm.png", width = 800, height = 750)
 WrightMap::wrightMap(estimation, threshold, 
@@
 
-knitr::include_graphics('Manuscript.figures/wm.png')
+knitr::include_graphics('Figures/wm.png')
 ```

### 2022-03-24 manuscript.Rmd
Redundant Code blocks are removed

@@
 #install.packages("pacman")#Run this if you don't have pacman installed.
-pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr,qgraph,paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,rsvg,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap,huxtable,reshape, ggsci,networkD3, webshot,ggtext)
+pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr, paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap,reshape, ggsci,ggtext)
 webshot::install_phantomjs()
@@
   [@verriotto2017new][@eklund1996development][@bajaj2011validation][@dianat2013objective]
-  [@horne1976self][@roenneberg2003life][@Olivier.2016][@buysse1989pittsburgh][@Xie.2021][@bossini2006sensibilita]
+  [@horne1976self][@roenneberg2003life][@buysse1989pittsburgh][@Xie.2021][@bossini2006sensibilita][@grandner2014development]
 ---
@@
 
-```{r relscale, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
-#This chunk holds code for Relevant scales table in the manuscript
-relevant.scale.data <- readxl::read_excel("Table_raw/relevant_scales.xlsx")
-
-```
-
-```{r reltab2, eval=FALSE, include=FALSE, results='asis'}
-relevant.scale.data %>% 
-apa_table(landscape =T,caption ="List of instruments measuring related constucts to LEBA", format = "latex",escape = T, font_size = "footnotesize", align = c("p{3cm}", rep("p{3.6cm}", ncol(relevant.scale.data))))
-
-```
-
 # Methods
-
-```{r rafel, eval=FALSE, include=FALSE}
-# In addition to the LEBA questionnaire, which is subject of the current study, we assessed other variables and items which were not included in the present analysis.
-This comprised various sleep-related measures, i.e., sleep disturbances and sleep-related impairment (adult and pediatric versions) [@Bevans.2019; @Buysse.2010; @Forrest.2018; @Harb.2015; @Yu.2011], sleep duration, timing, and latency, chronotype, social jetlag, time in bed, work/sleep schedule and outdoor light exposure duration [MCTQ version for adults and adolescents @roenneberg2003life] plus sleep environment [@Olivier.2016].
-Furthermore, we included a light sensitivity questionnaire (photophobia vs.
-photophilia) [@Wu.2017] and self-reported pubertal stage assessment [@Petersen.1988] for participants younger than 18 years of age.
-Moreover, we incorporated custom items on meal timing and caffeine consumption in the “workday vs.
-free day” structure of the MCTQ sleep-wake regulation.
-Example items are: “On workdays I usually have my first meal at __:__”, “On free days I usually have my last meal at __:__”, and “On workdays I usually drink my first caffeinated drink at __:__”.
-
-```
 
@@
 
-```{r Manuflowchart, eval=FALSE, include=FALSE}
-#This chunk holds code for the work flow chart of the data analysis
-
-Flowchart1 <- grViz("digraph my_flowchart{
-
-                    graph [fontname = Helvetica,layout = dot,fontsize = 45 ]
-
-                     node[fontname = Helvetica, shape = rectangle, margin = 0.2, width = 20, height = 3, 
-                    fixedsize = true,fontsize = 45]
-
-                    A[label = 'Initial development of 48 items'] 
-                    B[label = 'Large scale survey: first round (n=428)']
-                    C[label = 'Initial item analysis']
-                    D[label = 'Exploratory factor analysis (48 items; n=428)']
-
-                    E[label = 
-                    <Factor Identification Method<br/>Scree plot<br/>Minimum average partial method<br/>Hull method>
-                    ]
-
-                    F[label = 'Reliability analysis on latent stucture obtained in EFA (n=428)']
-                    G[label = 'Large scale survey: second round (n=262)']
-
-                    H[label = 'Confirmatory factor analysis ( n=262)']
-
-                    I[label = 'Reliability analysis on latent stucture obtained in CFA (n=262)']
-
-                    K[label = 'LEBA long format: 23-item', style = filled, fillcolor = Beige]
-
-                    L[label = 'Measurement invariance analysis (n=262)']
-                    M[label = 'Semantic analysis (n=262)']
-                    N[label = 'Item Response Theory based analysis on the combined sample (n=690)']
-
-                    O[label = 'LEBA short format: 18-item', style = filled, fillcolor = Beige]
-
-                     edge[fontname = Helvetica,color = black,arrowhead = vee, arrowsize = 1.25]
-                     A ->B
-                     B ->C
-                     C ->D
-                     D ->E
-                     E ->F
-                    F ->G
-                     G ->H
-                     H ->I
-                     I ->K
-
-                    K->L
-                    L ->M
-                    M ->N
-                    N->O
-
-}")
-
-library(jpeg)
-export_svg(Flowchart1) %>%
-  charToRaw() %>%
-  rsvg() %>%
-  png::writePNG("Figures/Flowchart1.jpeg", dpi = 600)
-
-```
-
-```{r participantmap, include =F}
-
-countries <- as.data.frame(tz_tibble[,1])
-countries <- as.data.frame(countries[-1,])
-
-colnames(countries) <- "TZ"
-countries.2 <- as.data.frame(str_split_fixed(countries$TZ, "-", 2))
-countries.2[ ,1][ countries.2[ , 1 ] == "United States " ] <- "USA"
-countries.2[ ,1][ countries.2[ , 1 ] == "United Kingdom " ] <- "UK"
-countries.2[ ,1][ countries.2[ , 1 ] == "Germany " ] <- "Germany"
-countries.2[ ,1][ countries.2[ , 1 ] == "India "  ] <- "India" 
-countries.2[ ,1][ countries.2[ , 1 ] == "France "  ] <- "France" 
-countries.2[ ,1][ countries.2[ , 1 ] == "Switzerland " ] <- "Switzerland"
-countries.2[ ,1][ countries.2[ , 1 ] == "Brazil "  ] <- "Brazil"
-countries.2[ ,1][ countries.2[ , 1 ] == "Netherlands " ] <- "Netherlands"
-countries.2[ ,1][ countries.2[ , 1 ] == "Canada "  ] <- "Canada" 
-countries.2[ ,1][ countries.2[ , 1 ] == "Poland " ] <- "Poland"
-
-country_name <- as.data.frame(unique(countries.2[,1]))
-country_name.2 <- (country_name[1:10,])
-
-thismap = map_data("world")
-
-# Set colors
-colors <- scales::hue_pal()(10)
-thismap <- mutate(thismap, fill = ifelse(region %in% country_name.2, 
-                                         sample(colors, 10), "white"))
-thismap <- within(thismap, fill[region == 'Canada'] <- '#FF62BC')
-thismap <- within(thismap, fill[region == 'Brazil'] <- '#D89000')
-thismap <- within(thismap, fill[region == 'USA'] <- '#00BFC4')
-thismap <- within(thismap, fill[region == 'UK'] <- 'blue')
-thismap <- within(thismap, fill[region == 'Germany'] <- 'Green')
-thismap <- within(thismap, fill[region == 'Netherlands'] <- '#A3A500')
-thismap <- within(thismap, fill[region == 'Poland'] <- 'Pink')
-thismap <- within(thismap, fill[region == 'France'] <- 'Orange')
-thismap <- within(thismap, fill[region == 'Switzerland'] <- 'purple')
-
-label.data <-thismap[thismap$region %in% country_name.2,]
-
-USA <- subset(label.data, region == "USA")
-UK <- subset(label.data, region == "UK")
-Germany <- subset(label.data, region == "Germany")
-India <- subset(label.data, region == "India")
-France <- subset(label.data, region == "France")
-Switzerland <- subset(label.data, region == "Switzerland")
-Brazil <- subset(label.data, region == "Brazil")
-Netherlands <- subset(label.data, region == "Netherlands")
-Canada <- subset(label.data, region == "Canada")
-Poland <- subset(label.data, region == "Poland")
-
-label.data.2 <- rbind(USA[386,],UK[1,],Germany[1,],India[327,],France[1,],
-                      Switzerland[1,],Brazil[33,],Netherlands[1,],Canada[5000,],Poland[1,])
-
-label.data.2[1,1] <- -100
-label.data.2[1,2] <- 40
-label.data.2[2,2] <- 52
-label.data.2[9,2] <- 55
-label.data.2[7,2] <- -9
-label.data.2[7,1] <- -48
-label.data.2[4,2] <- 25
-label.data.2[4,1] <- 84
-
-label.data.2[5,2] <- 46
-label.data.2[5,1] <- 6
-label.data.2[8,2] <- 51
-
-distribution <- ggplot(thismap, aes(long, lat, fill = fill, group=group)) + 
-  geom_polygon(colour="gray", size =.3) +  
-  scale_fill_identity()+apatheme+ theme(
-    axis.text.x = element_blank(),
-                                        axis.text.y = element_blank(),
-                                        axis.title.x = element_blank(),
-                                        axis.title.y = element_blank(),
-                                        plot.title = element_blank(),
-                                        axis.line.x = element_blank(),
-                                        axis.line.y = element_blank(),
-                                        axis.ticks = element_blank())+
-  # xlab("Longitude") + ylab("Latitude")+
-  ggrepel::geom_text_repel(data= label.data.2,aes(x=long, y= lat, label=region),inherit.aes = F,
-            color = "darkblue", fontface = "bold", stat = 'identity',
-            position = "identity")
-
-ggsave("Figures/distribution.png", distribution, width = 12, height = 6, dpi = 600, bg ="white")
-
-```
-
 ## Data Collection
@@
 knitr::include_graphics('Figures/distribution.png', dpi = 300 )
-```
-
-```{r rafael2, eval=FALSE, include=FALSE}
-# Figure \@ref(fig:partmap) depicts the top ten countries with highest participation in our survey.
-# - `r tz_tibble[2,1]`:     `r tz_tibble[2,2]`
-# - `r tz_tibble[3,1]`:     `r tz_tibble[3,2]`
-# - `r tz_tibble[4,1]`:     `r tz_tibble[4,2]`
-# - `r tz_tibble[5,1]`:     `r tz_tibble[5,2]`
-# - `r tz_tibble[6,1]`:     `r tz_tibble[6,2]`
-# - `r tz_tibble[7,1]`:     `r tz_tibble[7,2]`
-# - `r tz_tibble[8,1]`:     `r tz_tibble[8,2]`
-# - `r tz_tibble[9,1]`:     `r tz_tibble[9,2]`
-# - `r tz_tibble[10,1]`:    `r tz_tibble[10,2]`
-# - `r tz_tibble[11,1]`:    `r tz_tibble[11,2]`
 ```
@@
 
-full.tab.2 <- full.tab[24:48,] %>% 
+full.tab.2 <- full.tab[25:48,] %>% 
   gt()
@@
     title = md("Summary Descriptives (n =690)"),
-    subtitle = md("Items 24-48 ")) %>% 
+    subtitle = md("Items 25-48 ")) %>% 
 #create groups of columns
@@
 
-S1 Fig summarizes the univariate descriptive statistics for the 48 items among  EFA sample (n =`r nrow(EFA.data)`.
+Supplementary Fig1 summarizes the univariate descriptive statistics for the 48 items among  EFA sample (n =`r nrow(EFA.data)`.
 Our data violated both univariate normality [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970].
@@
 
-Scree plot ( Figure \@ref(fig:efa-plot)) suggested a six-factor solution.
-However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (Table \@ref(tab:map)) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:facIdFig)) suggested a five-factor solution.
+Scree plot ( Figure \@ref(fig:efa-plot) B) suggested a six-factor solution.
+However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (Supplementary Table 2) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print) D) suggested a five-factor solution.
 As a result, we tested both five-factor and six-factor solutions.
@@
 Subsequently, we fitted a six-factor solution.
-However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (Sup.Table \@ref(tab:sixFacTab)).
+However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (Supplementary Table 3)).
 
@@
 Model 2 attained the best fit.", align = "c", landscape = T, escape=F, note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square ")
-```
-
-```{r simulation, eval=FALSE, include=FALSE}
-#This chunk holds codes for simulating Standard error for the accepted CFA model
-
-library("simsem")
-pop.model <- "F1 =~ a1*item16 + .95*item36 + a2*item17
-                 F2 =~ .87*item11 + .85*item10 + .74*item12+ .60*item07+ .50*Ritem08+ .49*item09
-                 F3 =~  .78*item27+ .77*item03+ .68*item40 + .13*item30 + .20*item41
-                 F4 =~ a3*item32 + .63*item35 + .33*item38+ a4*item33 
-                 F5 =~ .80*item46+ .53*item45+ .36*item25+ .30*item04+ .22*item01 
-                       a1==a2
-                       a3==a4
-                item30 ~~ .82*item41
-F1~~1*F1
-F2~~1*F2
-F3~~1*F3
-F4~~1*F4
-F5~~1*F5
-"
-
-sam.model <- "F1 =~ a1*item16 + item36 + a2*item17
-                 F2 =~ item11 + item10 + item12+ item7+ Ritem8+ item9
-                 F3 =~  item27+ item3+ item40 + item30 + item41
-                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
-                 F5 =~ item46+ item45+ item25+ item4+ item1 
-                       a1==a2
-                       a3==a4
-                item30 ~~  item41
-                       "
-
-sim.300 <- sim(200, model = sam.model, n =200, generate = pop.model, lavaanfun = "lavaan", auto.var =T, auto.fix.first =F, seed = 123)
-summary(simulation)
-summaryParam(simulation, detail =T, alpha = .05)
-
-#power should be higher than .80, average CI width should be lower than .15
-#Estimate standard error bias
-
-SD.Bias <- (summaryParam(simulation)[3]-summaryParam(simulation)[2])/summaryParam(simulation)[3]
 ```

### 2022-03-24 manuscript.Rmd
EFA Diagram removed Supplimentary table reordered

@@
 
-#This chunk holds codes for creating 'gtExtra' based descriptive figures (EFA descriptives Supplimentary
+#This chunk holds codes for creating 'gtExtra' based descriptive figures (EFA descriptives Supplementary
 
@@
 var5 <- CC$Vaccounted[2,5]*100
-```
-
-```{r EFAplotcode, eval=FALSE, include=FALSE}
-#This chunk holds code for the EFA plot
-EFAplot <- grViz("
-digraph nicegraph {
-
-graph [layout = dot,rankdir = LR, fontsize = 40]
-
-# node definitions with substituted label text
-node [fontname = Helvetica, shape = circle,  margin = 0.5, width = 3.5, height = .5,
-fixedsize = true, fontsize = 40]
-F5 [label = 'F5']
-F4 [label = 'F4']
-F3 [label = 'F3']
-F2 [label = 'F2']
-F1 [label = 'F1']
-
-node [fontname = Helvetica, shape = box, fontsize = 50, height = 1]
-b [label = 'item16']
-c [label = 'item36']
-d [label = 'item17']
-e [label = 'item11']
-f [label = 'item10']
-g [label = 'item12']
-h [label = 'item7']
-i [label = 'item8']
-j [label = 'item9']
-k [label = 'item27']
-l [label = 'item3']
-m [label = 'item40']
-n [label = 'item30']
-o [label = 'item41']
-p [label = 'item33']
-q [label = 'item32']
-r [label = 'item35']
-s [label = 'item37']
-t [label = 'item38']
-u [label = 'item46']
-v [label = 'item45']
-w [label = 'item25']
-x [label = 'item4']
-y [label = 'item1']
-z [label = 'item26']
-
-# edge definitions with the node IDs
-edge [fontname = Helvetica, fontsize = 40]
-F5 -> u [label = '0.60']
-F5 -> v [label = '0.59']
-F5 -> w [label = '0.41']
-F5 -> x [label = '0.41']
-F5 -> y [label = '0.40']
-F5 -> z [label = '0.35']
-F4 -> p [label = '0.74']
-F4 -> q [label = '0.73']
-F4 -> r [label = '0.66']
-F4 -> s [label = '-0.39', color =red]
-F4 -> t [label = '0.39']
-F3 -> k [label = '0.80']
-F3 -> l [label = '0.80']
-F3 -> m [label = '0.65']
-F3 -> n [label = '0.49']
-F3 -> o [label = '36']
-F2 -> e [label = '0.79']
-F2 -> f[label = '0.76']
-F2 -> g [label = '0.65']
-F2 -> h[ label = '0.50']
-F2 -> i [label = '-.49',color =red]
-F2 -> j [label = '0.32']
-F1 -> b[label = '0.99']
-F1-> c [label = '0.93']
-F1-> d [label = '0.80']
-}
-")
-
-export_svg(EFAplot) %>%
-  charToRaw() %>%
-  rsvg() %>%
-  png::writePNG("Figures/EFAplot.png",dpi =600)
-
 ```
@@
 
-efa.tab.ful <- cbind(efa.table[,1],efa.stems, efa.table[,2:8] )
+efa.tab.ful <- cbind(efa.table[,1],efa.stems, efa.table[,2:7] )
 
@@
 Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30.
-We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (Sup.Table \@ref(tab:MinResTab)).
+We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (Supplementary Table 3).
 Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items.
@@
 Subsequently, we fitted a six-factor solution.
-However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (Supplementary Table 3)).
+However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (Supplementary Table 4)).
 
@@
 
-apa_table(efa.tab.ful, caption = "Factor loadings and communality of the retained items", note = "Only loading > .30 is reported", 
+apa_table(efa.tab.ful, caption = "Factor loadings and communality of the retained items in EFA using principal axis extraction method", note = "Only loading > .30 is reported", 
           font_size = "footnotesize", escape=F,landscape = T,

### 2022-03-24 manuscript.Rmd
Top 10 countried map figure removed
Appendix Removed

@@
   - \DeclareDelayedFloatFlavor{sidewaysfigure}{figure}
-appendix:
-  - "appendix-1.Rmd"
+
 mainfont: Arial
@@
 Participants indicated filling out the online survey from a diverse range of geographic locations. For a complete list of geographic locations, see Suppl. Table \@ref(tab:tztable).
-
-```{r partmap, eval=FALSE, fig.cap="Top ten countries with highest responses in our survey", include=FALSE, out.height='100%'}
-knitr::include_graphics('Figures/distribution.png', dpi = 300 )
-```
 

### 2022-03-24 manuscript.Rmd
supplementary tables+ figues+Files updated and ordered.

@@
 We conducted an initial item analysis and proceed to the exploratory factor analysis (EFA) with all 48 items using the data collected in our first round.
-(EFA sample;n=`r nrow(EFA.descriptives)`).
+(EFA sample; n=`r nrow(EFA.descriptives)`).
 Prior to the EFA, necessary assumptions, including sample adequacy, normality assumptions, quality of correlation matrix were assessed.
@@
 To determine the latent structure, we followed the common guidelines : (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading > .3 across factors [@bandalosFactorAnalysisExploratory2018].
-We also conducted a EFA on non-merged response options data (Supp.
-Table \@ref(tab:efaunmerged)).
+We also conducted a EFA on non-merged response options data (**Supplementary File 3**)
 
@@
 ```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long form (23-item) and short form (18-item) of LEBA. ', out.height='100%', out.width='100%'}
-knitr::include_graphics('Figures/Flowchart.png', dpi = 600 )
+knitr::include_graphics('Figures/Figure1.png', dpi = 600 )
 ```
@@
 After reviewing the literature, we identified several light exposure related scale.
-However, no scales specifically measuring the behavioural component of light exposure were found (Table \@ref(tab:reltab2)).
+However, no scales specifically measuring the behavioural component of light exposure were found (**Supplementary Table 1**).
 As such, all authors in collaboration of an expert panel developed a comprehensive item pool of 48 items.
@@
 
-Table \@ref(tab:demotab) summarizes the survey participants' demographic characteristics.
+Table 1 summarizes the survey participants' demographic characteristics.
 Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses.
@@
 Lastly, `r desc_tibble[15,2]` overall [EFA: `r desc_tibble[15,3]` ; CFA: `r desc_tibble[15,4]`] reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]` overall [EFA: `r desc_tibble[16,3]`; CFA: `r desc_tibble[16,4]`] filled in the "Neither (no work or school, or on vacation)" response option.
-We tested all demographic variables in Table 1 for significant group differences between the EFA and CFA sample, applying Wilcoxon rank sum test for the continuous variable "Age" and Pearson's $\chi^2$ test for all other categorical variables via the gtsummary R package's "add_p" function [@sjoberg2021] .
-The p-values were corrected for multiple testing applying false discovery rate (FDR) via the "add_q" function of the same package.
-After p-value (FDR) correction for multiple testing, none of the demographic variables were significantly different between the EFA sample and the CFA sample (all q-values *q* $\ge$ `r min(desc_tibble$"**q-value**", na.rm=T)`).
 
@@
     Stem ~ px(200)) %>% 
- gtsave("Figures/gt_full_p1.png", vwidth = 6000)
+ gtsave("Figures/Figure2.png", vwidth = 6000)
 
@@
     Stem ~ px(200)) %>% 
-gtsave("Figures/gt_full_p2.png",vwidth = 6000)
+gtsave("Figures/Figure3.png",vwidth = 6000)
 
@@
 ```{r efagtPic1, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern'}
-knitr::include_graphics('Figures/gt_full_p1.png')
+knitr::include_graphics('Figures/Figure2.png')
 
@@
 ```{r efagtPic2, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern'}
-knitr::include_graphics('Figures/gt_full_p2.png')
+knitr::include_graphics('Figures/Figure3.png')
 
@@
 
-Supplementary Fig1 summarizes the univariate descriptive statistics for the 48 items among  EFA sample (n =`r nrow(EFA.data)`.
+**Supplementary Fig1** summarizes the univariate descriptive statistics for the 48 items among  EFA sample (n =`r nrow(EFA.data)`.
 Our data violated both univariate normality [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970].
@@
 The inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`.
-Figure \@ref(fig:figCor) depicts the correlation matrix.
+Figure \@ref(fig:fig:efa-plot A) depicts the correlation matrix.
 
@@
 Scree plot ( Figure \@ref(fig:efa-plot) B) suggested a six-factor solution.
-However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (Supplementary Table 2) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print) D) suggested a five-factor solution.
+However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (**Supplementary Table 2**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print) D) suggested a five-factor solution.
 As a result, we tested both five-factor and six-factor solutions.
@@
 #                   label_fontface = "plain")
-ggsave("Figures/efa.plot.png",efa.plot, width = 7, height = 8, dpi = 600)
+ggsave("Figures/Figure4.png",efa.plot, width = 7, height = 8, dpi = 600)
 ```
@@
 
-knitr::include_graphics('Figures/efa.plot.png', dpi =600)
+knitr::include_graphics('Figures/Figure4.png', dpi =600)
 
@@
 Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30.
-We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (Supplementary Table 3).
+We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (**Supplementary Table 3**).
 Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items.
@@
 The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`.
-Supplimentary figure 1 depicts the data distribution and endorsement pattern for the included 25 items.
 However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:efa-plot-print)(D)) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring.
@@
 Subsequently, we fitted a six-factor solution.
-However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (Supplementary Table 4)).
+However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (**Supplementary Table 4**)).
 
@@
 Figure \@ref(fig:figcfa) depicts the obtained CFA structure.
-Figure \@ref(fig:cfagtPic) depicts the data distribution and endorsement pattern of the retained 23 items in our CFA sample.
+**Supplementary Figure 2**  depicts the data distribution and endorsement pattern of the retained 23 items in our CFA sample.
 
@@
 
-knitr::include_graphics("Figures/CFAplot.png", dpi =600)
+knitr::include_graphics("Figures/Figure5.png", dpi =600)
 
@@
 We fitted each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690).
-Item discrimination parameters of our tool fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$) (Supplementary Table 2).
-Examination of the item information curve (Sup.fig \@ref(fig:IF)) indicated five items (1, 25,  38, 30, & 41) had relatively flat information curves (I($\theta$) <.20).
+Item discrimination parameters of our tool fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 5**).
+Examination of the item information curve (**Supplementary Figure 3**) indicated five items (1, 25,  38, 30, & 41) had relatively flat information curves (I($\theta$) <.20).
 We discarded those items which yielded a short form of LEBA with 5 factors and 18 items.
@@
 
-allitemplots <- cowplot::plot_grid(F1.iteminfo.1,F1.iteminfo.2, F1.iteminfo.3,
-                                   F2.iteminfo.1,F2.iteminfo.2, F2.iteminfo.3,F2.iteminfo.4,F2.iteminfo.5,F2.iteminfo.6, 
-                                   F3.iteminfo.1, F3.iteminfo.2, F3.iteminfo.3, F3.iteminfo.4, F3.iteminfo.5,   
-                                   F4.iteminfo.1, F4.iteminfo.2 ,F4.iteminfo.3 ,F4.iteminfo.4,
-                                   F5.iteminfo.1,F5.iteminfo.2,F5.iteminfo.3,F5.iteminfo.4,F5.iteminfo.5,
-
-                     labels = "AUTO",
-                     align="v",
-                     ncol = 5,
+F1.plots <- cowplot::plot_grid(F1.iteminfo.1,F1.iteminfo.2, F1.iteminfo.3,NULL, NULL, NULL,
+                     labels = c("A", "B", "C"),
+                     align="h",
+                     nrow = 1,
                      label_size = 12,
@@
 
-ggsave("Figures/allitemplots.png",allitemplots, width = 18, height = 12, dpi = 600, bg = "white")
-
-discarded.items.plot <- cowplot::plot_grid(F3.iteminfo.4,
-                                           F3.iteminfo.5,
-                                           F4.iteminfo.3,
-                                           F5.iteminfo.3,
-                                           F5.iteminfo.5, 
-                                            labels = "AUTO",
-                                   align="v",
-                                   ncol = 5,
+F2.plots <- cowplot::plot_grid(F2.iteminfo.1,F2.iteminfo.2, F2.iteminfo.3,F2.iteminfo.4,F2.iteminfo.5,F2.iteminfo.6,
+                     labels = c("D", "E", "F", "G", "H", "I"),
+                     align="h",
+                     nrow = 1,
                      label_size = 12,
@@
 
-ggsave("Figures/discarded.png",discarded.items.plot, width = 18, height = 4, dpi = 600, bg = "white")
+F3.plots <- cowplot::plot_grid(F3.iteminfo.1, F3.iteminfo.2, F3.iteminfo.3, F3.iteminfo.4, F3.iteminfo.5,NULL,
+                     labels = c("J", "K", "L", "M", "N"),
+                     align="h",
+                     nrow = 1,
+                     label_size = 12,
+                     label_fontfamily = "Arial",
+                     label_fontface = "plain")
+
+F4.plots <- cowplot::plot_grid(F4.iteminfo.1, F4.iteminfo.2 ,F4.iteminfo.3 ,F4.iteminfo.4,NULL, NULL,
+                     labels = c("O", "P", "Q", "R"),
+                     align="h",
+                     nrow = 1,
+                     label_size = 12,
+                     label_fontfamily = "Arial",
+                     label_fontface = "plain")
+
+F5.plots <- cowplot::plot_grid(F5.iteminfo.1,F5.iteminfo.2,F5.iteminfo.3,F5.iteminfo.4,F5.iteminfo.5,NULL,
+                     labels = c("S", "T", "U", "V", "W"),
+                     align="h",
+                     nrow = 1,
+                     label_size = 12,
+                     label_fontfamily = "Arial",
+                     label_fontface = "plain")
+
+all.factot.itemplots <- cowplot::plot_grid(F1.plots,
+                                           F2.plots,
+                                           F3.plots,
+                                           F4.plots,
+                                           F5.plots,
+
+                     align="v",
+                     nrow = 5,
+                     label_size = 12,
+                     label_fontfamily = "Arial",
+                     label_fontface = "plain")
+
+ggsave("Supplimentary_materials/S_Figure/S3_Fig.png",all.factot.itemplots, width = 18, height = 12, dpi = 600, bg = "white")
+
+# allitemplots <- cowplot::plot_grid(F1.iteminfo.1,F1.iteminfo.2, F1.iteminfo.3,NULL, NULL,NULL,
+#                                    
+#                                    F2.iteminfo.1,F2.iteminfo.2, F2.iteminfo.3,F2.iteminfo.4,F2.iteminfo.5,F2.iteminfo.6, 
+#                                    
+#                                    F3.iteminfo.1, F3.iteminfo.2, F3.iteminfo.3, F3.iteminfo.4, F3.iteminfo.5,   NULL, 
+#                                    F4.iteminfo.1, F4.iteminfo.2 ,F4.iteminfo.3 ,F4.iteminfo.4,NULL, NULL,
+#                                    F5.iteminfo.1,F5.iteminfo.2,F5.iteminfo.3,F5.iteminfo.4,F5.iteminfo.5,NULL,
+#                                    
+#                                    
+#                      labels = "AUTO",
+#                      align="v",
+#                      ncol = 6,
+#                      label_size = 12,
+#                      label_fontfamily = "Arial",
+#                      label_fontface = "plain")
+# 
+# 
+# # ggsave("Figures/allitemplots.png",allitemplots, width = 18, height = 12, dpi = 600, bg = "white")
+# 
+# 
+# 
+# 
+# 
+# discarded.items.plot <- cowplot::plot_grid(F3.iteminfo.4,
+#                                            F3.iteminfo.5,
+#                                            F4.iteminfo.3,
+#                                            F5.iteminfo.3,
+#                                            F5.iteminfo.5, 
+#                                             labels = "AUTO",
+#                                    align="v",
+#                                    ncol = 5,
+#                                    label_size = 12,
+#                                    label_fontfamily = "Arial",
+#                                    label_fontface = "plain")
+#
+
+# ggsave("Figures/discarded.png",discarded.items.plot, width = 18, height = 4, dpi = 600, bg = "white")
 
@@
                      label_fontface = "plain")
-ggsave("Figures/TIC.png",TIC.plot, width = 18, height = 12, dpi = 600, bg = "white")
+ggsave("Figures/Figure6.png",TIC.plot, width = 18, height = 12, dpi = 600, bg = "white")
 
@@
 
-knitr::include_graphics('Figures/TIC.png', dpi =600)
+knitr::include_graphics('Figures/Figure6.png', dpi =600)
 ```
@@
 
-Supplementary Table S3 summarizes the item fit indexes of the 18 items.
+**Supplementary Table 6** summarizes the item fit indexes of the 18 items.
 All of the items had RMSEA value $\le$.06 indicating adequate fit of the items to the fitted IRT model.
-Sup.Figure \@ref(fig:personfit) depicts the person fit Zh statistics histogram of out fitted models.
+**Supplementary Figure 4** depicts the person fit Zh statistics histogram of out fitted models.
 Zh statistics are larger than -2 for most participants, suggesting a good person fit of the selected IRT models.
@@
 
-ggsave("Figures/personfit.png",personfit , width = 10, height = 12, dpi = 600, bg = "white")
+ggsave("Supplimentary_materials/S_Figure/S4_Fig.png",personfit , width = 10, height = 12, dpi = 600, bg = "white")
 

### 2022-03-24 manuscript.Rmd
Reference file for the packages is separated from literature references

@@
 
-bibliography      : ["references.bib"]
+bibliography      : ["references.bib", "lib_references.bib"]
 
@@
 library(dlookr)
-library(plyr)
 library(tidyverse)
@@
 library(EFA.MRFA) # Hull method
-library(DiagrammeR) #devtools::install_github('rich-iannone/DiagrammeR')
-library(DiagrammeRsvg) #For DiagrammeR
-library(rsvg) #For DiagrammeR
 library(ggcorrplot)
 library(semTable)
-library(magick)
 library(mirt)
@@
 library(kutils)
-library(simsem)
 library(tabledown)
@@
 library(ggtext)
-r_refs("references.bib")
+r_refs("lib_references.bib")
 ```
@@
 nocite: |
-  `r cite_r("references.bib")`
+  `r cite_r("lib_references.bib")`
   [@verriotto2017new][@eklund1996development][@bajaj2011validation][@dianat2013objective]
@@
 
-```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Development of long form (23-item) and short form (18-item) of LEBA. ', out.height='100%', out.width='100%'}
+```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Flow chart of the LEBA (long and short form) development and evaluation. ', out.height='100%', out.width='100%'}
 knitr::include_graphics('Figures/Figure1.png', dpi = 600 )
@@
 
-```{r efagtPic1, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern'}
+```{r efagtPic1, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern', out.height='100%', out.width='250%'}
 knitr::include_graphics('Figures/Figure2.png')
@@
 
-```{r efagtPic2, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern'}
+```{r efagtPic2, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern', out.height='100%', out.width='250%'}
 knitr::include_graphics('Figures/Figure3.png')
@@
 The inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`.
-Figure \@ref(fig:fig:efa-plot A) depicts the correlation matrix.
+Figure \@ref(fig:efa-plot-print A) depicts the correlation matrix.
 
@@
 
-Scree plot ( Figure \@ref(fig:efa-plot) B) suggested a six-factor solution.
+Scree plot ( Figure \@ref(fig:efa-plot-print) B) suggested a six-factor solution.
 However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (**Supplementary Table 2**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print) D) suggested a five-factor solution.
@@
 
-```{r efa-plot-print, fig.align= 'center', fig.cap='(ref:efa-plot-print)',  warning=FALSE, results= 'asis'}
+```{r efa-plot-print, fig.align= 'center', fig.cap='(ref:efa-plot-print)',  warning=FALSE, results= 'asis', out.height='100%', out.width='110%'}
 
@@
 Subsequently, we fitted a six-factor solution.
-However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (**Supplementary Table 4**)).
+However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (**Supplementary Table 4**).
 
@@
 
-```{r saveWrightmao, include=FALSE, warning=F, message=F}
+```{r saveWrightmao, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}
 #This chunk holds codes for saving the wright-map

### 2022-03-24 manuscript.Rmd
Table 1 label is hardcoded

@@
 As a part of the demographic information participants provided information regarding age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language.
-The demographic characteristics of our sample are given in Table \@ref(tab:demotab).To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention.
+The demographic characteristics of our sample are given in Table 1.To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention.
 What is 4+5?").
@@
 We conducted two rounds of data collections.
-At first we collected data for from `r nrow(EFA.descriptives)` participants  In the second round we collected data from another `r nrow(CFA.descriptives)` participants making a total sample of `r nrow(desctable.data)`.
+At first we collected data for from `r nrow(EFA.descriptives)` participants.
+In the second round we collected data from another `r nrow(CFA.descriptives)` participants making a total sample of `r nrow(desctable.data)`.
 

### 2022-03-27 manuscript.Rmd
minimum-maximum factor loading corrected

@@
 
--   Supplementary Table S1 Overview Existing Related Scales: items in total / items on light exposure (behaviour)
+-   Supplementary Table S1: Overview Existing Related Scales
 
@@
 # loading
-min.loadings <- abs(min(Fac.5$loadings))
-max.loadings <- abs(max(Fac.5$loadings))
+Fac.5.min.max <- Fac.5$loadings %>% 
+  subset(abs(Fac.5$loadings)>(.3))
+min.loadings <- min(abs(Fac.5.min.max))
+max.loadings <- max(Fac.5.min.max)
 

### 2022-03-27 manuscript.Rmd
EFA combined plot updated

@@
   scale_y_continuous(name="Eigen Value", limits=c(0, 5), breaks=seq(0,5,1)) +
-  scale_x_continuous(name="Factor Number", limits=c(0, 20),breaks=seq(0,20,4))+
+  scale_x_continuous(name="Factor Number", limits=c(0, 18),breaks=c(0,6,18))+
   geom_hline(yintercept=1, linetype = 'dashed') + apatheme +theme(legend.position = "None")
@@
 Hull <- hull+ ggtitle(NULL)+xlab("Factor Number")+ylab("CAF")+ aes(color = '#DC000099')+geom_point(color ='#3C5488FF',size =1)+
-  apatheme +theme(legend.position = "None") +scale_fill_identity()
+  apatheme +theme(legend.position = "None") +scale_fill_identity()+
+  scale_x_continuous(breaks=c(0,5,12))
 

### 2022-03-27 manuscript.Rmd
EFA plot correlctly referenced

@@
 We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones).Participants reported a diverse range of geographic location
-Participants indicated filling out the online survey from a diverse range of geographic locations. For a complete list of geographic locations, see Suppl. Table \@ref(tab:tztable).
+Participants indicated filling out the online survey from a diverse range of geographic locations. For a complete list of geographic locations, see **Supplementary Table 2**.
 
@@
 The inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`.
-Figure \@ref(fig:efa-plot-print A) depicts the correlation matrix.
+Figure \@ref(fig:efa-plot-print)A depicts the correlation matrix.
 
@@
 
-Scree plot ( Figure \@ref(fig:efa-plot-print) B) suggested a six-factor solution.
-However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (**Supplementary Table 2**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print) D) suggested a five-factor solution.
+Scree plot ( Figure \@ref(fig:efa-plot-print)B) suggested a six-factor solution.
+However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (**Supplementary Table 3**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print)C) suggested a five-factor solution.
 As a result, we tested both five-factor and six-factor solutions.
@@
 Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30.
-We further confirmed this five-factor latent structure by another EFA using varimax rotation with a minimum residual extraction method (**Supplementary Table 3**).
 Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items.
@@
 The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`.
-However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:efa-plot-print)(D)) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring.
+However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:efa-plot-print)D) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring.
 [@desjardinsHandbookEducationalMeasurement2018].

### 2022-03-28 manuscript.Rmd
Headeers are now alligned with flow chart

@@
 
--   None of these do light exposure behavior.
+-   None of these do light exposure behaviour.
 
@@
 
-A quantitative cross-sectional fully anonymous online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
+A quantitative cross-sectional fully anonymous online large scale survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
 Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (https://enlightenyourclock.org/participate-in-research) of the science-communication comic-book "Enlighten your clock" co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux].
@@
 As a part of the demographic information participants provided information regarding age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language.
-The demographic characteristics of our sample are given in Table 1.To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention.
+The demographic characteristics of our sample are given in Table 1.
+To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention.
 What is 4+5?").
@@
 In the second round we collected data from another `r nrow(CFA.descriptives)` participants making a total sample of `r nrow(desctable.data)`.
-
 The data analysed in this study was collected between 17 May 2021 and 3 September 2021.
@@
 
-Figure \@ref(fig:FlowchartFig) summarizes the steps of our psychometric analysis.
-In our analysis we used R (version 4.1.0) [@R-base].
-In the item generation and selection phase we had developed a item pool of 48 items with six-point Likert type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always).
+Figure \@ref(fig:FlowchartFig) summarizes the steps we followed while developing LEBA.
+In our analysis we used R statistical tool [@R-base].
+**First**, we  developed a item pool of 48 items with six-point Likert type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial scale.
 Our purpose was to capture light exposure related behaviour.
@@
 
-We conducted an initial item analysis and proceed to the exploratory factor analysis (EFA) with all 48 items using the data collected in our first round.
-(EFA sample; n=`r nrow(EFA.descriptives)`).
+**Second**, for data collection we conducted a large scale survey.
+**Third**, with the data collected on the first round of the large scale survey (EFA sample; n=`r nrow(EFA.descriptives)`) we conducted descriptive and item analysis and proceeded to the exploratory factor analysis (EFA).
 Prior to the EFA, necessary assumptions, including sample adequacy, normality assumptions, quality of correlation matrix were assessed.
 Our data violated both the univariate and multivariate normality assumptions.
-Due to these violations and the ordinal nature of our response data, in EFA we used  polychoric correlation matrix and employed principal axis (PA) as  factor extraction method with varimax rotation [@desjardinsHandbookEducationalMeasurement2018;@watkinsStepbyStepGuideExploratory2020].
+Due to these violations and the ordinal nature of our response data, in EFA we used  polychoric correlation matrix and employed principal axis (PA) as  factor extraction method [@desjardinsHandbookEducationalMeasurement2018;@watkinsStepbyStepGuideExploratory2020].
 We used a combination of factor identification method including Scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and Hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
 To determine the latent structure, we followed the common guidelines : (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading > .3 across factors [@bandalosFactorAnalysisExploratory2018].
-We also conducted a EFA on non-merged response options data (**Supplementary File 3**)
+We also conducted a EFA on non-merged response options data (**Supplementary File 1**)
 
@@
 
-We also analysed possible semantic overlap of our developed tool using "Semantic Scale Network" (SSN) engine [@rosenbusch2020semantic].
+**Fourth**, as secondary analysis we analysed possible semantic overlap of our developed tool using "Semantic Scale Network" (SSN) engine [@rosenbusch2020semantic] and identified the the educational grade level required to understand the items in our tool using Flesch-Kincaid Grade Level identification method [@flesch1948new].
 The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic].
 Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy.
-Additionally, to identify the educational grade level required to understand the items in our tool we subjected the tool to Flesch-Kincaid Grade Level [@flesch1948new]
-
-Lastly, we sought Item Response Theory (IRT) based analysis on developing a short form of LEBA.
+
+**Fifth**,  we developed a short form of LEBA using Item Response Theory (IRT) based analysis.
 We fitted each factor of LEBA using the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =`r nrow(sem.data)`).
@@
 
-## Initial development of items
+## Initial Scale
 
@@
 
-## Large-scale  survey of instruments
-
-### Participants
+## Large-scale  survey of scale
 
@@
 Lastly, `r desc_tibble[15,2]` overall [EFA: `r desc_tibble[15,3]` ; CFA: `r desc_tibble[15,4]`] reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]` overall [EFA: `r desc_tibble[16,3]`; CFA: `r desc_tibble[16,4]`] filled in the "Neither (no work or school, or on vacation)" response option.
+
+## Psychometric Analysis: Development of the Long Form
 
@@
 
-Figure \@ref(fig:efagtPic1) and Figure \@ref(fig:efagtPic2) summarize the response pattern of our total sample (n = `r nrow(sem.data)`) for all 48 items.
-Most of the items were skewed and violated normality assumption.
+Figure \@ref(fig:efagtPic1) and Figure \@ref(fig:efagtPic2) summarize the response pattern of our total sample (n = `r nrow(sem.data)`) for all 48 items. Most of the items were skewed.
 
@@
 
-**Supplementary Fig1** summarizes the univariate descriptive statistics for the 48 items among  EFA sample (n =`r nrow(EFA.data)`.
+**Supplementary Figure 1** summarizes the univariate descriptive statistics for the 48 items among  EFA sample (n =`r nrow(EFA.data)`.
 Our data violated both univariate normality [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970].
@@
 
-```{r correlation-hits, include=F}
+```{r correlation-hits, eval=FALSE, include=FALSE}
 #This chunk holds code for plotting the correlation matrix in histogram format
@@
 var5 <- CC$Vaccounted[2,5]*100
+
+omega <- omega(reduced.model.5F.2,nfactors=5,fm="minres",n.iter=1,p=.05,poly=T,key=NULL,
+    flip=TRUE,digits=2, title="Omega",sl=TRUE,labels=NULL,
+    plot=TRUE,n.obs=NA,rotate="oblimin",Phi=NULL,option="equal",covar=FALSE)
 ```
@@
 4.9 % inter-item correlation coefficients were higher than |.30|.
+'x' denotes non-significant item-total correlation.
 (B) Scree plot suggested six factors.
@@
 
-```{r efa-plot-print, fig.align= 'center', fig.cap='(ref:efa-plot-print)',  warning=FALSE, results= 'asis', out.height='100%', out.width='110%'}
+```{r efa-plot-print, fig.align= 'center', fig.cap='(ref:efa-plot-print)',  warning=FALSE, results= 'asis', out.height='90%', out.width='110%'}
 
@@
 
-### Confirmatory Factor Analysis
+### Confirmatory Factor Analysis and Reliability Analysis
 
@@
 
-### Semantic Analysis
+## Secondary Analysis: Semantic Scale Network and Grade Level
 
@@
 
-### Developing Short form of LEBA
+## Developing Short form of LEBA
 

### 2022-03-28 manuscript.Rmd
Typo Corrected. All Supplemenatry materials are merged into one.

@@
       - Writing – original draft
-      - Writing – review & editing;
+      - Writing – review & editing
 
@@
   # separate_p_footnotes() %>%
-  modify_caption("Demographic Characteristics of Partinipants (n=690)") -> desc_table
+  modify_caption("Demographic Characteristics of Participants (n=690)") -> desc_table
 
@@
 In that context, the first two response options: "Does not apply/I don't know" and "Never" were providing similar information.
-As such we collapsed them into one, making it a 5 point Likert type response format.
+As such we collapsed them into one, making it a 5 point Likert type response format (1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always).
 
@@
 To determine the latent structure, we followed the common guidelines : (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading > .3 across factors [@bandalosFactorAnalysisExploratory2018].
-We also conducted a EFA on non-merged response options data (**Supplementary File 1**)
-
-For reliability estimation we used internal consistency reliability coefficient ordinal $\alpha$.
-Though Cronbach's alpha coefficient is widely used for estimating internal consistency, it has a tendency to deflate the estimates for Likert-type data since the calculation is based on pearson-correlation matrix which requires response data to be continuous of nature [@gadermann2012estimating; @zumbo2007ordinal].
-Subsequently to get  better estimates of reliability  we reported ordinal alpha for each factors using polychoric-correlation matrix [@zumbo2007ordinal].
+<!-- We also conducted an EFA on non-merged response options data set (**Supplementary File 1**). -->
+
+Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it has a tendency to deflate the estimates for Likert-type data since the calculation is based on pearson-correlation matrix which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal].
+Subsequently to get  better estimates of reliability we reported ordinal alpha for each factors obtained in EFA using polychoric-correlation matrix [@zumbo2007ordinal].
 We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$  coefficient which is a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
@@
 
-To validated the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with weighted least square with mean and variance adjusted (WLSMV) estimator  [@desjardinsHandbookEducationalMeasurement2018] on the data collected n our second round of data collection (CFA sample;n=`r nrow(CFA.descriptives)`).
-We assessed the model fit using common model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI):  close to .95 or above/ between 90-95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner].
-However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015] and SRMR does not work well with ordinal data [@RN1272] As such, we judged the model fit using CFI, TLI, SRMR and RMSEA.
-
-We assessed the measurement invariance (MI) of our construct between native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non native English speakers (n=`r invariance.data.descriptives.count[2,2]`) among the CFA sample (n=`r nrow(CFA.descriptives)`).
+To validated the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with weighted least square with mean and variance adjusted (WLSMV) estimator  [@desjardinsHandbookEducationalMeasurement2018] on the data collected in the second round of data collection (CFA sample; n=`r nrow(CFA.descriptives)`).
+We assessed the model fit using common model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI):  close to .95 or above/ between .90-.95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner].
+However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015] and SRMR does not work well with ordinal data [@RN1272] As such, we judged the model fit using CFI, TLI and RMSEA.
+
+We assessed the measurement invariance (MI) of our scale between native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non native English speakers (n=`r invariance.data.descriptives.count[2,2]`) in the CFA sample (n=`r nrow(CFA.descriptives)`).
 MI evaluates whether a construct has the psychometric equivalence and same meaning across groups [@putnick2016measurement;@klinePrinciplesPracticeStructural2015].
@@
 Among MI models, configural model is the least restrictive model and residual model is the most restrictive model.
-A non-significant $\Delta \chi^2$ test between two nested measurement invariance models indicates mode fit does not significantly decrease for the superior model [@dimitrov2010testing] thus allowing the superior invariance model to be accepted.
-[@widaman1997exploring].
+A non-significant $\Delta \chi^2$ test between two nested measurement invariance models indicates mode fit does not significantly decrease for the superior model thus allowing the superior invariance model to be accepted [@dimitrov2010testing; @widaman1997exploring].
 
@@
 We fitted each factor of LEBA using the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =`r nrow(sem.data)`).
-IRT assesses the item quality by estimating item discrimination, item difficulty, item information, and test information [@bakerBasicsItemResponse2017].
-Item discrimination indicates the pattern of variation in the categorical responses with the changes in latent trait level ($\theta$).
+IRT assesses the item quality by estimating item discrimination, item difficulty, item information curve, and test information curve [@bakerBasicsItemResponse2017].
+Item discrimination indicates how well a particular item can differentiate between participants across the given latent trait continuum ($\theta$).
+Item difficulty corresponds to the latent trait level at which the probability of endorsing a particular response option is 50%.
 Item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
@@
 Person fit was estimated using standardized fit index Zh statistics [@drasgow1985appropriateness].
-Zh < -2 was be considered as a misfit [@drasgow1985appropriateness].
+Zh < -2 was considered as a misfit [@drasgow1985appropriateness].
 
@@
 After reviewing the literature, we identified several light exposure related scale.
-However, no scales specifically measuring the behavioural component of light exposure were found (**Supplementary Table 1**).
-As such, all authors in collaboration of an expert panel developed a comprehensive item pool of 48 items.
+However, no scale specifically measuring the behavioural component of light exposure were found (**Supplementary Table 1**).
+As such, an expert panel developed a comprehensive item pool of 48 items.
 The expert panel composed of all authors and researchers from the fields of chronobiology, light research, neuroscience and psychology.
@@
 Multivariate skew was  `r printnum(mardia$b1p)` (p <0.001) and multivariate kurtosis was `r printnum(mardia$b2p)` (p <0.001).
-Due to these violations and ordinal nature of the response data polychoric correlations over Pearson's correlations was chosen [@desjardinsHandbookEducationalMeasurement2018].
 The corrected item-total correlation ranges between `r apa(low.r.corec,2,F)` -`r apa(high.r.corec,2,F)`.
@@
 
-Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy using the EFA sample (n =`r nrow(EFA.data)` [@kaiserIndexFactorialSimplicity1974] .
+Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy using the EFA sample (n =`r nrow(EFA.data)`) [@kaiserIndexFactorialSimplicity1974] .
 The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cutoff value (.50) indicating adequate sample size [@hutchesonMultivariateSocialScientist1999].
@@
 The inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`.
-Figure \@ref(fig:efa-plot-print)A depicts the correlation matrix.
+Figure \@ref(fig:efa-plot-print)-A depicts the correlation matrix.
 
@@
 
-Scree plot ( Figure \@ref(fig:efa-plot-print)B) suggested a six-factor solution.
+Scree plot ( Figure \@ref(fig:efa-plot-print)-B) suggested a six-factor solution.
 However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (**Supplementary Table 3**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print)C) suggested a five-factor solution.
@@
 
-```{r efa-plot-print, fig.align= 'center', fig.cap='(ref:efa-plot-print)',  warning=FALSE, results= 'asis', out.height='90%', out.width='110%'}
+```{r efa-plot-print, fig.align= 'center', fig.cap='(ref:efa-plot-print)',  warning=FALSE,  out.height='60%', out.width='110%'}
 
@@
 
-With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items.
-(cross-loading items and poor factor loading (<.30) items).
+With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items (cross-loading items and poor factor loading (<.30) items).
 Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30.
@@
 All of the items had RMSEA value $\le$.06 indicating adequate fit of the items to the fitted IRT model.
-**Supplementary Figure 4** depicts the person fit Zh statistics histogram of out fitted models.
+**Supplementary Figure 4** depicts the person fit Zh statistics histogram of our fitted models.
 Zh statistics are larger than -2 for most participants, suggesting a good person fit of the selected IRT models.

### 2022-03-28 manuscript.Rmd
article corrected

@@
 In our analysis we used R statistical tool [@R-base].
-**First**, we  developed a item pool of 48 items with six-point Likert type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial scale.
+**First**, we  developed an item pool of 48 items with six-point Likert type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial scale.
 Our purpose was to capture light exposure related behaviour.

### 2022-03-28 manuscript.Rmd
Analytic Strategy updated

@@
 **Second**, for data collection we conducted a large scale survey.
-**Third**, with the data collected on the first round of the large scale survey (EFA sample; n=`r nrow(EFA.descriptives)`) we conducted descriptive and item analysis and proceeded to the exploratory factor analysis (EFA).
+**Third**, as a part of psychometric analysis, we conducted  descriptive and item analysis and proceeded to the exploratory factor analysis (EFA) on the data collected on the first round of the large scale survey (EFA sample; n=`r nrow(EFA.descriptives)`).
 Prior to the EFA, necessary assumptions, including sample adequacy, normality assumptions, quality of correlation matrix were assessed.
@@
 Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it has a tendency to deflate the estimates for Likert-type data since the calculation is based on pearson-correlation matrix which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal].
-Subsequently to get  better estimates of reliability we reported ordinal alpha for each factors obtained in EFA using polychoric-correlation matrix [@zumbo2007ordinal].
+Subsequently to get  better estimates of reliability we reported ordinal alpha for each factors obtained in EFA [@zumbo2007ordinal].
 We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$  coefficient which is a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
-Both ordinal alpha and McDonald's $\omega_t$ coefficient value range from 0 to 1 and higher value represents better reliability.
+Both ordinal alpha and McDonald's $\omega_t$ coefficient value range between 0 to 1 and higher value represents better reliability.
 
@@
 
-**Fourth**, as secondary analysis we analysed possible semantic overlap of our developed tool using "Semantic Scale Network" (SSN) engine [@rosenbusch2020semantic] and identified the the educational grade level required to understand the items in our tool using Flesch-Kincaid Grade Level identification method [@flesch1948new].
+**Fourth**, as secondary analysis we analysed possible semantic overlap of our developed scale using "Semantic Scale Network" (SSN) engine [@rosenbusch2020semantic] and identified the the educational grade level required to understand the items in our tool using Flesch-Kincaid grade level identification method [@flesch1948new].
 The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic].
@@
 
-**Fifth**,  we developed a short form of LEBA using Item Response Theory (IRT) based analysis.
+**Lastly**,  we developed a short form of LEBA using Item Response Theory (IRT) based analysis.
 We fitted each factor of LEBA using the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =`r nrow(sem.data)`).
@@
 Item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
-Here, we reported  the item discrimination parameter and categorize the items according to the suggestions of @bakerBasicsItemResponse2017 : none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70.
+Here, we reported  the item difficulty and discrimination parameter and categorize the items based on their item discrimination index: none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70 [@bakerBasicsItemResponse2017].
 We discarded the items with relatively flat item information curve (information <.2) to develop the short form of LEBA.
@@
 
-## Initial Scale
+## Development of the Initial Scale
 
@@
 
-## Large-scale  survey of scale
+## Large-scale  survey
 
@@
 
-"Semantic Scale Network"(SSN) analysis [@rosenbusch2020semantic] indicated that LEBA (23 items)  appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990].
+Semantic Scale Network (SSN) analysis [@rosenbusch2020semantic] indicated that LEBA (23 items)  appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990].
 The cosine similarities lie between .47 to .51.
-Flesch-Kincaid Grade Level [@flesch1948new] analysis on the the 23 items of our scale indicated required educational grade level was 3.33 and with a age above 8.33.
+Flesch-Kincaid grade level [@flesch1948new] analysis on the the 23 items of our scale indicated required educational grade level was 3.33 and with a age above 8.33.
 
@@
 Authors along with an expert panel generated 48 items and evaluated their quality and relevance and made necessary amendments.
-A large scale geographically unconstrained quantitative cross-sectional survey was conducted yielding responses from large sample (n=`r nrow(EFA.descriptives)` to explore the latent structure.
+A large scale geographically unconstrained quantitative cross-sectional survey was conducted yielding responses from large sample (n=`r nrow(EFA.descriptives)`) to explore the latent structure.
 Exploratory factor analysis revealed a five factor solution with 25 items.

### 2022-03-28 manuscript.Rmd
References checked and updated

@@
   # separate_p_footnotes() %>%
-  modify_caption("Demographic Characteristics of Participants (n=690)") -> desc_table
+  modify_caption("Demographic Characteristics of Participants (n=690).") -> desc_table
 
@@
 
-apa_table(efa.tab.ful, caption = "Factor loadings and communality of the retained items in EFA using principal axis extraction method", note = "Only loading > .30 is reported", 
+apa_table(efa.tab.ful, caption = "Factor loadings and communality of the retained items in EFA using principal axis extraction method.", note = "Only loading > .30 is reported.", 
           font_size = "footnotesize", escape=F,landscape = T,
@@
 apa_table(CFa.matrix, caption = "Confirmatory Factor Analysis model fit indices of the two model: (a) Model 1: five factor model with 25 items (b) Model 2:  five factor model with 23 items.
-Model 2 attained the best fit.", align = "c", landscape = T, escape=F, note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square ")
+Model 2 attained the best fit.", align = "c", landscape = T, escape=F, note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square.")
 ```
@@
 ```{r InvarianceTab, results='asis'}
-apa_table(Invariance.table, align = "c",  caption = "Measurment Invariance analysis on CFA sample (n=262) across native and non-native English speakers.", note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square; a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual; * =  df of model comparison", landscape = T, font_size = "footnotesize", escape=F )
+apa_table(Invariance.table, align = "c",  caption = "Measurment Invariance analysis on CFA sample (n=262) across native and non-native English speakers.", note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square; a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual; * =  df of model comparison.", landscape = T, font_size = "footnotesize", escape=F )
 
@@
 
-Semantic Scale Network (SSN) analysis [@rosenbusch2020semantic] indicated that LEBA (23 items)  appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990].
+Semantic Scale Network (SSN) analysis [@rosenbusch2020semantic] indicated that LEBA (23 items)  appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite].
 The cosine similarities lie between .47 to .51.

### 2022-03-29 manuscript.Rmd
Spell-check attempt 2

@@
 ---
-title             : "_Light Exposure Behavior Assessment (LEBA)_: Development of a novel instrument to capture light exposure-related behaviours"
+title             : "_Light Exposure behaviour Assessment (LEBA)_: Development of a novel instrument to capture light exposure-related behaviours"
 shorttitle        : "LEBA"
@@
 How these light-related behaviours can be shaped to optimise personal light exposure is currently unknown.
-Here, we present a novel, self-reported and psychometrically validated instrument to capture light exposure-related behaviour, the Light Exposure Behavior Assessment (LEBA).
-
-  An expert panel prepared the initial 48 item pool spanning different light exposure related behaviors.
-Responses, consisting rating the frequency of engaging in the per-item behavior on a 5-point Likert type scale were  collected in an online survey yielding responses from a geographically unconstrained sample (690 completed responses, 74 countries, 28 time zones).
+Here, we present a novel, self-reported and psychometrically validated instrument to capture light exposure-related behaviour, the Light Exposure Behaviour Assessment (LEBA).
+
+  An expert panel prepared the initial 48 item pool spanning different light exposure related behaviours.
+Responses, consisting rating the frequency of engaging in the per-item behaviour on a 5-point Likert type scale were  collected in an online survey yielding responses from a geographically unconstrained sample (690 completed responses, 74 countries, 28 time zones).
 Exploratory factor analysis (EFA) on an initial subset of our sample (n=428) rendered a five-factor solution with 25 items (Wearing blue light filters, spending time outdoors, using phone and smart-watch in bed, using light before bedtime, using light in the morning and during daytime).
@@
 install.packages("ggtext")
-#if you dont have LaTeX installed run the following lines
+#if you don't have LaTeX installed run the following lines
 #install.packages("tinytex")
@@
 library(MOTE)
-library(car)#reversecoding 
+library(car)#reverse-coding 
 library(psych)
@@
         panel.background = element_blank(),
-        #text=element_text(family = "Helvetica"),
+        #text=element_text(family = "Helvetian"),
         axis.text.x = element_text(size = 15),
@@
 ```{r country, include=FALSE}
-#This chunk holds code for timezone calculation
+#This chunk holds code for time-zone calculation
 
@@
 ```{r timezone, include=F}
-#This chunk holds code for creating timezone.csv file
+#This chunk holds code for creating time-zone.csv file
 timezone <- TZ %>% 
@@
 
-#seperating naming and  reducing data for descriptive Table 
+#separating naming and  reducing data for descriptive Table 
 desctable.data <- dplyr::select(descriptives.data, c(listdescVars,
@@
 A quantitative cross-sectional fully anonymous online large scale survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
-Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (https://enlightenyourclock.org/participate-in-research) of the science-communication comic-book "Enlighten your clock" co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux].
-The landing page of the online survey had the explanatory statements where we mentioned participation was voluntary and that respondents could withdraw from participation anytime without being penalized.
-At the beginning of the survey, for the adult participants (>18 years) consent was recorded digitally.
-Underaged participants (<18 years) were urged to obtain assent from their parents/legal guardians.
-The entire survey was estimated to take <30 minutes.
+Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (<https://enlightenyourclock.org/participate-in-research>) of the science-communication comic-book "Enlighten your clock" co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux].
+The landing page of the online survey had the explanatory statements where we mentioned participation was voluntary and that respondents could withdraw from participation any time without being penalized.
+At the beginning of the survey, for the adult participants (\>18 years) consent was recorded digitally.
+Under-aged participants (\<18 years) were urged to obtain assent from their parents/legal guardians.
+The entire survey was estimated to take \<30 minutes.
 Participants were not compensated.
@@
 Participants were asked to confirm that they were participating the survey for the first time.
-Questions incorporating retrospective recall were all aligned to the period of "past four weeks".
+Questions incorporating retrospective recall were all aligned to the period of "past four weeks".\
 We conducted two rounds of data collections.
-At first we collected data for from `r nrow(EFA.descriptives)` participants.
+At first, we collected data for from `r nrow(EFA.descriptives)` participants.
 In the second round we collected data from another `r nrow(CFA.descriptives)` participants making a total sample of `r nrow(desctable.data)`.
@@
 
-**Second**, for data collection we conducted a large scale survey.
+**Second**, for data collection we conducted a large-scale survey.
 **Third**, as a part of psychometric analysis, we conducted descriptive and item analysis and proceeded to the exploratory factor analysis (EFA) on the data collected on the first round of the large scale survey (EFA sample; n=`r nrow(EFA.descriptives)`).
@@
 Our data violated both the univariate and multivariate normality assumptions.
-Due to these violations and the ordinal nature of our response data, in EFA we used  polychoric correlation matrix and employed principal axis (PA) as  factor extraction method [@desjardinsHandbookEducationalMeasurement2018;@watkinsStepbyStepGuideExploratory2020].
+Due to these violations and the ordinal nature of our response data, in EFA we used polychoric correlation matrix and employed principal axis (PA) as the factor extraction method [@desjardinsHandbookEducationalMeasurement2018; @watkinsStepbyStepGuideExploratory2020].
 We used a combination of factor identification method including Scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and Hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
-To determine the latent structure, we followed the common guidelines : (i) no factors with fewer than three items (ii) no factors with a factor loading <0.3 (iii) no items with cross-loading > .3 across factors [@bandalosFactorAnalysisExploratory2018].
-<!-- We also conducted an EFA on non-merged response options data set (**Supplementary File 1**). -->
-
-Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it has a tendency to deflate the estimates for Likert-type data since the calculation is based on pearson-correlation matrix which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal].
+To determine the latent structure, we followed the common guidelines : (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading \> .3 across factors [@bandalosFactorAnalysisExploratory2018].
+<!-- We also conducted an EFA on non-merged response options data set (**Supplementary File 1**).
+-->
+
+Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it has a tendency to deflate the estimates for Likert-type data since the calculation is based on Pearson-correlation matrix which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal].
 Subsequently to get better estimates of reliability we reported ordinal alpha for each factors obtained in EFA [@zumbo2007ordinal].
@@
 
-To validated the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with weighted least square with mean and variance adjusted (WLSMV) estimator  [@desjardinsHandbookEducationalMeasurement2018] on the data collected in the second round of data collection (CFA sample; n=`r nrow(CFA.descriptives)`).
+To validate the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with weighted least square with mean and variance adjusted (WLSMV) estimator [@desjardinsHandbookEducationalMeasurement2018] on the data collected in the second round of data collection (CFA sample; n=`r nrow(CFA.descriptives)`).
 We assessed the model fit using common model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI): close to .95 or above/ between .90-.95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner].
@@
 
-We assessed the measurement invariance (MI) of our scale between native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non native English speakers (n=`r invariance.data.descriptives.count[2,2]`) in the CFA sample (n=`r nrow(CFA.descriptives)`).
-MI evaluates whether a construct has the psychometric equivalence and same meaning across groups [@putnick2016measurement;@klinePrinciplesPracticeStructural2015].
+We assessed the measurement invariance (MI) of our scale between native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non-native English speakers (n=`r invariance.data.descriptives.count[2,2]`) in the CFA sample (n=`r nrow(CFA.descriptives)`).
+MI evaluates whether a construct has the psychometric equivalence and the same meaning across groups [@putnick2016measurement; @klinePrinciplesPracticeStructural2015].
 We used structural equation modelling framework to assess the measurement invariance.
 We successively compared four nested models: configural, metric, scalar, and residual models using the $\chi^2$ difference test ($\Delta \chi^2$).
-Among MI models, configural model is the least restrictive model and residual model is the most restrictive model.
+Among MI models, the configural model is the least restrictive model and residual model is the most restrictive model.
 A non-significant $\Delta \chi^2$ test between two nested measurement invariance models indicates mode fit does not significantly decrease for the superior model thus allowing the superior invariance model to be accepted [@dimitrov2010testing; @widaman1997exploring].
 
-**Fourth**, as secondary analysis we analysed possible semantic overlap of our developed scale using "Semantic Scale Network" (SSN) engine [@rosenbusch2020semantic] and identified the the educational grade level required to understand the items in our tool using Flesch-Kincaid grade level identification method [@flesch1948new].
+**Fourth**, as secondary analysis we analysed possible semantic overlap of our developed scale using "Semantic Scale Network" (SSN) engine [@rosenbusch2020semantic] and identified the educational grade level required to understand the items in our tool using Flesch-Kincaid grade level identification method [@flesch1948new].
 The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic].
@@
 Item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
-Here, we reported  the item difficulty and discrimination parameter and categorize the items based on their item discrimination index: none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high >1.70 [@bakerBasicsItemResponse2017].
-We discarded the items with relatively flat item information curve (information <.2) to develop the short form of LEBA.
+Here, we reported the item difficulty and discrimination parameter and categorize the items based on their item discrimination index: none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70 [@bakerBasicsItemResponse2017].
+We discarded the items with relatively flat item information curve (information \<.2) to develop the short form of LEBA.
 We also assessed the precision of the short LEBA using Test information curve (TIC).
-TIC  indicates the amount of information an the full-scale carry along the latent trait continuum.
-Item fit and person fit of the fitted IRT models were also analyzed to gather more evidence on validity and meaningfulness of our Tool [@desjardinsHandbookEducationalMeasurement2018].
+TIC indicates the amount of information a particular scale carries along the latent trait continuum.
+Item fit and person fit of the fitted IRT models were also analysed to gather more evidence on validity and meaningfulness of our Tool [@desjardinsHandbookEducationalMeasurement2018].
 Item fit was evaluated using the RMSEA value obtained from Signed-$\chi^2$ index implementation, RMSEA value $\le$.06 was considered adequate item fit.
 Person fit was estimated using standardized fit index Zh statistics [@drasgow1985appropriateness].
-Zh < -2 was considered as a misfit [@drasgow1985appropriateness].
+Zh \< -2 was considered as a misfit [@drasgow1985appropriateness].
 
@@
 
-The present article is a fully reproducible open-access “R Markdown” document.
-All code and data underlying this article – along with two versions of the LEBA questionnaire (full and short) and online survey implementation templates on common survey platforms – will be available under open-access licence (CC-BY-NC-ND) on a public [GitHub repository](https://github.com/leba-instrument).
+The present article is a fully reproducible open access "R Markdown" document.
+All code and data underlying this article -- along with two versions of the LEBA questionnaire (full and short) and online survey implementation templates on common survey platforms -- will be available under open-access licence (CC-BY-NC-ND) on a public [GitHub repository](https://github.com/leba-instrument).
 
@@
 
-After reviewing the literature, we identified several light exposure related scale.
+After reviewing the literature, we identified several light exposure related scales.
 However, no scale specifically measuring the behavioural component of light exposure were found (**Supplementary Table 1**).
@@
 Both our EFA and CFA sample size exceeded these requirements.
-We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones).Participants reported a diverse range of geographic location
-Participants indicated filling out the online survey from a diverse range of geographic locations. For a complete list of geographic locations, see **Supplementary Table 2**.
+We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones).Participants reported a diverse range of geographic location Participants indicated filling out the online survey from a diverse range of geographic locations.
+For a complete list of geographic locations, see **Supplementary Table 2**.
 
@@
 ```{r EFAassumptions, include=FALSE}
-#This chunk holds code for cheacking assumptions of EFA
+#This chunk holds code for checking assumptions of EFA
 
@@
 Our data violated both univariate normality [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970].
-Multivariate skew was  `r printnum(mardia$b1p)` (p <0.001) and multivariate kurtosis was `r printnum(mardia$b2p)` (p <0.001).
+Multivariate skew was `r printnum(mardia$b1p)` (p \<0.001) and multivariate kurtosis was `r printnum(mardia$b2p)` (p \<0.001).
 The corrected item-total correlation ranges between `r apa(low.r.corec,2,F)` -`r apa(high.r.corec,2,F)`.
@@
 Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy using the EFA sample (n =`r nrow(EFA.data)`) [@kaiserIndexFactorialSimplicity1974] .
-The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cutoff value (.50) indicating adequate sample size [@hutchesonMultivariateSocialScientist1999].
-Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p < .001 indicated the correlations between items are adequate for conducting the EFA.
-However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than |.30|.
+The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cut-off value (.50) indicating adequate sample size [@hutchesonMultivariateSocialScientist1999].
+Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p \< .001 indicated the correlations between items are adequate for conducting the EFA.
+However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than \|.30\|.
 The inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`.
@@
 (ref:efa-plot-print) (A) Inter-item polychoric correlation coefficients for the 48 items.
-4.9 % inter-item correlation coefficients were higher than |.30|.
+4.9 % inter-item correlation coefficients were higher than \|.30\|.
 'x' denotes non-significant item-total correlation.
@@
 
-With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items (cross-loading items and poor factor loading (<.30) items).
+With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items (cross-loading items and poor factor loading (\<.30) items).
 Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30.
@@
 This factor captured individual's morning and daytime light exposure related behaviour.
-The  internal consistency reliability was, ordinal $\alpha$ = `r apa(F5.alpha,2,F)` .
+The internal consistency reliability was, ordinal $\alpha$ = `r apa(F5.alpha,2,F)`.
 It is essential to attain a balance between psychometric properties and interpretability of the common themes when exploring the latent structure.
@@
 Table \@ref(tab:tabCfa) summarizes the CFA fit indices of our fitted model.
-Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`,[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 [`r Hmisc::label(sem.data$item32)`;`r Hmisc::label(sem.data$item33)`] and 16-17 [`r Hmisc::label(sem.data$item16)`;`r Hmisc::label(sem.data$item17)`].
+Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 [`r Hmisc::label(sem.data$item32)`; `r Hmisc::label(sem.data$item33)`] and 16-17 [`r Hmisc::label(sem.data$item16)`; `r Hmisc::label(sem.data$item17)`].
 Items pair 32-33 stemmed from the preference of dimming electric device's brightness before bed time and items pair 16 and 19 stemmed from the preference of using blue filtering or coloured glasses during the daytime.
 Nevertheless, SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`).
-Further by allowing one pair of items (30-41) [`r Hmisc::label(sem.data$item30)`;`r Hmisc::label(sem.data$item41)`] to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained the best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]).
+Further by allowing one pair of items (30-41) [`r Hmisc::label(sem.data$item30)`; `r Hmisc::label(sem.data$item41)`] to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained the best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]).
 Internal consistency ordinal $\alpha$ for the five factors of LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)` respectively.
@@
 
-In our CFA sample we had `r mi.count[1,2]`  native English speakers and `r mi.count[2,2]` non-native English speakers  (For a detailed description these two groups see Sup.
-Table \@ref(tab:midesp) ).
+In our CFA sample we had `r mi.count[1,2]` native English speakers and `r mi.count[2,2]` non-native English speakers.
 Table \@ref(tab:InvarianceTab) indicates our fitted model had acceptable fit indices for all of the fitted MI models.
@@
 The cosine similarities lie between .47 to .51.
-Flesch-Kincaid grade level [@flesch1948new] analysis on the the 23 items of our scale indicated required educational grade level was 3.33 and with a age above 8.33.
+Flesch-Kincaid grade level [@flesch1948new] analysis on the 23 items of our scale indicated required educational grade level was 3.33 and with a age above 8.33.
 
@@
 Item discrimination parameters of our tool fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 5**).
-Examination of the item information curve (**Supplementary Figure 3**) indicated five items (1, 25,  38, 30, & 41) had relatively flat information curves (I($\theta$) <.20).
+Examination of the item information curve (**Supplementary Figure 3**) indicated five items (1, 25, 38, 30, & 41) had relatively flat information curves (I($\theta$) \<.20).
 We discarded those items which yielded a short form of LEBA with 5 factors and 18 items.
@@
 
-We treated each factor of short-LEBA as an unidimensional construct and obtain 5 TICs (Figure \@ref(fig:Testinfo)).
-These information curves indicated except the first and fifth factors, the other three factor's TICs are roughly centred on the centre of the trait continuum ($\theta$).The first and fifth factor had a peak to the right side of the centre of latent trait.Thus we conferred the LEBA tool estimated the light exposure related behaviour with precision near the centre of trait continuum for 2nd, 3rd and 4th factors and near the right side of the centre of trait continuum for 1st and 5th factors [@bakerBasicsItemResponse2017].
+We treated each factor of short-LEBA as a unidimensional construct and obtain 5 TICs (Figure \@ref(fig:Testinfo)).
+These information curves indicated except the first and fifth factors, the other three factor's TICs are roughly centred on the centre of the trait continuum ($\theta$).
+The first and fifth factor had a peak to the right side of the centre of latent trait.Thus we conferred the LEBA tool estimated the light exposure related behaviour with precision near the centre of trait continuum for 2nd, 3rd and 4th factors and near the right side of the centre of trait continuum for 1st and 5th factors [@bakerBasicsItemResponse2017].
 
 **Supplementary Table 6** summarizes the item fit indexes of the 18 items.
-All of the items had RMSEA value $\le$.06 indicating adequate fit of the items to the fitted IRT model.
+All items had RMSEA value $\le$.06 indicating adequate fit of the items to the fitted IRT model.
 **Supplementary Figure 4** depicts the person fit Zh statistics histogram of our fitted models.
@@
 ("Wearing blue light filters", "Spending time outdoors", "Using phone and smart-watch in bed", "Using light before bedtime", and "Using light in the morning and during daytime").
-The internal consistency reliability coefficient ordinal alpha ranged between `r apa(range(alpha.tab),2,F)`.
+The internal consistency reliability coefficient ordinal alpha ranged between `r apa(min(alpha.tab),2,F)-apa(max(alpha.tab),2,F)`.
 As all the retained factors were meaningful and contributed essentially towards our aim we retained all five factors.

### 2022-03-29 manuscript.Rmd
Supplimentary file Update: added MI demographics

@@
   as.data.frame()
+
+mi.descriptives <- CFA.descriptives[, c(1,2,5,6,7)] 
+colnames(mi.descriptives)[3] <- "English_Speaking"
+
+english.speaking <- mi.descriptives %>% 
+  subset(English_Speaking=="Yes")
+
+non.english.speaking <- mi.descriptives %>% 
+  subset(English_Speaking=="No")
+
+mi.des.sum <- mi.descriptives %>% 
+psych::describeBy("English_Speaking")
+
+mi.english.sum <- english.speaking %>% 
+psych::describeBy("slypos_demographics_sex.factor")
+
+mi.non.english.sum <- non.english.speaking %>% 
+psych::describeBy("slypos_demographics_sex.factor")
+
+mi.des.sum.english <- as.data.frame(mi.des.sum$Yes)
+mi.des.sum.nonenglish <- as.data.frame(mi.des.sum$No)
 ```
@@
 In our CFA sample we had `r mi.count[1,2]` native English speakers and `r mi.count[2,2]` non-native English speakers.
-Table \@ref(tab:InvarianceTab) indicates our fitted model had acceptable fit indices for all of the fitted MI models.
+**Supplementary Table 5** summarizes the demographic descriptions native and non-native English speakers.Table \@ref(tab:InvarianceTab) indicates our fitted model had acceptable fit indices for all of the fitted MI models.
 The model fit did not significantly decrease across the nested models indicating the acceptability of the highest measurement invariance model : residual model.
@@
 We fitted each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690).
-Item discrimination parameters of our tool fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 5**).
+Item discrimination parameters of our tool fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**).
 Examination of the item information curve (**Supplementary Figure 3**) indicated five items (1, 25, 38, 30, & 41) had relatively flat information curves (I($\theta$) \<.20).
@@
 
-**Supplementary Table 6** summarizes the item fit indexes of the 18 items.
+**Supplementary Table 7** summarizes the item fit indexes of the 18 items.
 All items had RMSEA value $\le$.06 indicating adequate fit of the items to the fitted IRT model.
@@
 ("Wearing blue light filters", "Spending time outdoors", "Using phone and smart-watch in bed", "Using light before bedtime", and "Using light in the morning and during daytime").
-The internal consistency reliability coefficient ordinal alpha ranged between `r apa(min(alpha.tab),2,F)-apa(max(alpha.tab),2,F)`.
+The internal consistency reliability coefficient ordinal alpha ranged between `r apa(min(alpha.tab),2,F)`-`r apa(max(alpha.tab),2,F)`.
 As all the retained factors were meaningful and contributed essentially towards our aim we retained all five factors.

### 2022-03-29 manuscript.Rmd
Spell-check 3

@@
 
-**Fourth**, as secondary analysis we analysed possible semantic overlap of our developed scale using "Semantic Scale Network" (SSN) engine [@rosenbusch2020semantic] and identified the educational grade level required to understand the items in our tool using Flesch-Kincaid grade level identification method [@flesch1948new].
+**Fourth**, as secondary analysis we analysed possible semantic overlap of our developed scale using "Semantic Scale Network" (SSN) engine [@rosenbusch2020semantic] and identified the educational grade level required to understand the items in our scale using Flesch-Kincaid grade level identification method [@flesch1948new].
 The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic].
@@
 TIC indicates the amount of information a particular scale carries along the latent trait continuum.
-Item fit and person fit of the fitted IRT models were also analysed to gather more evidence on validity and meaningfulness of our Tool [@desjardinsHandbookEducationalMeasurement2018].
+Item fit and person fit of the fitted IRT models were also analysed to gather more evidence on validity and meaningfulness of our scale [@desjardinsHandbookEducationalMeasurement2018].
 Item fit was evaluated using the RMSEA value obtained from Signed-$\chi^2$ index implementation, RMSEA value $\le$.06 was considered adequate item fit.
@@
 
-### Exploratory Factor Analysis
+### Exploratory Factor Analysis and Reliability Analysis
 
@@
 
-### Confirmatory Factor Analysis and Reliability Analysis
+### Confirmatory Factor Analysis
 
@@
           label.cex=1.2, #Font of factor and item name
-          residuals=FALSE,
+          residuals=T,
            #exoVar=FALSE,
@@
 We fitted each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690).
-Item discrimination parameters of our tool fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**).
+Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**).
 Examination of the item information curve (**Supplementary Figure 3**) indicated five items (1, 25, 38, 30, & 41) had relatively flat information curves (I($\theta$) \<.20).
@@
 These information curves indicated except the first and fifth factors, the other three factor's TICs are roughly centred on the centre of the trait continuum ($\theta$).
-The first and fifth factor had a peak to the right side of the centre of latent trait.Thus we conferred the LEBA tool estimated the light exposure related behaviour with precision near the centre of trait continuum for 2nd, 3rd and 4th factors and near the right side of the centre of trait continuum for 1st and 5th factors [@bakerBasicsItemResponse2017].
+The first and fifth factor had a peak to the right side of the centre of latent trait.Thus we conferred the LEBA scale estimated the light exposure related behaviour with precision near the centre of trait continuum for 2nd, 3rd and 4th factors and near the right side of the centre of trait continuum for 1st and 5th factors [@bakerBasicsItemResponse2017].
 
@@
 
-Though there are lots of validated tool to measure light exposure, they don't tell us much about the behavioural aspects pertaining to the light exposure.
-At present there is a dearth of validated tool to measure light exposure related behaviours.
-In that vein we have developed a subjective self-reported tool that can capture light exposure related behaviour in different dimensions.
+Though there are lots of validated scale to measure light exposure, they don't tell us much about the behavioural aspects pertaining to the light exposure.
+At present there is a dearth of validated scale to measure light exposure related behaviours.
+In that vein we have developed a subjective self-reported scale that can capture light exposure related behaviour in different dimensions.
 
@@
 
-We developed a novel self-reported subjective tool-"Light exposure behaviour assessment"(LEBA) to capture light exposure related behaviour.
+We developed a novel self-reported subjective scale-"Light exposure behaviour assessment"(LEBA) to capture light exposure related behaviour.
 We developed 48 items, judged the relevance and content of the items and conducted a large scale geographically unrestricted cross-sectional survey.
@@
 
-Since, LEBA is the first of its kind, estimating convergent validity with other subjective tool was not possible.
-One way to establish the convergent validity of LEBA is to administer this subjective tool along which some objective measurement tools (e.g.
+Since, LEBA is the first of its kind, estimating convergent validity with other subjective scale was not possible.
+One way to establish the convergent validity of LEBA is to administer this subjective scale along which some objective measurement scales (e.g.
 personalised light dosimeter).
-Though such objective tools do not directly capture light exposure related behaviour, potential insight can be drawn by understanding the behaviour pattern and light exposure.
-Also, light exposure related behaviours can be dependent upon the socio-economic status as behaviours can be modulated by available tools individual have on their disposal.
+Though such objective scales do not directly capture light exposure related behaviour, potential insight can be drawn by understanding the behaviour pattern and light exposure.
+Also, light exposure related behaviours can be dependent upon the socio-economic status as behaviours can be modulated by available scales individual have on their disposal.
 Our analysis did not consider socio-economic status, as we didn't measure it.

### 2022-03-30 manuscript.Rmd
Discussion Updated

@@
 
-**Fourth**, as secondary analysis we analysed possible semantic overlap of our developed scale using "Semantic Scale Network" (SSN) engine [@rosenbusch2020semantic] and identified the educational grade level required to understand the items in our scale using Flesch-Kincaid grade level identification method [@flesch1948new].
+**Fourth**, as secondary analysis we identified the educational grade level required to understand the items in our scale using Flesch-Kincaid grade level identification method [@flesch1948new].
+Also, we analysed possible semantic overlap of our developed scale using "Semantic Scale Network" (SSN) engine [@rosenbusch2020semantic].
 The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic].
@@
 Upon inspection, it was understood that these items are negatively correlated to the respective common theme, and thus in the CFA analysis, we reverse coded these two items.
+Internal consistency coefficient McDonald's $\omega_t$ for the total scale was `r apa(omega$omega.tot,2,T)`.
 
@@
 
-## Secondary Analysis: Semantic Scale Network and Grade Level
-
+## Secondary Analysis: Grade Level Identification and Semantic Scale Network Analysis
+Flesch-Kincaid grade level [@flesch1948new] analysis on the 23 items of our scale indicated required educational grade level was 3.33 and with a age above 8.33.
 Semantic Scale Network (SSN) analysis [@rosenbusch2020semantic] indicated that LEBA (23 items) appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite].
 The cosine similarities lie between .47 to .51.
-Flesch-Kincaid grade level [@flesch1948new] analysis on the 23 items of our scale indicated required educational grade level was 3.33 and with a age above 8.33.
-
 ```{r textanalysis, include=F}
@@
 Though there are lots of validated scale to measure light exposure, they don't tell us much about the behavioural aspects pertaining to the light exposure.
-At present there is a dearth of validated scale to measure light exposure related behaviours.
 In that vein we have developed a subjective self-reported scale that can capture light exposure related behaviour in different dimensions.
@@
 Authors along with an expert panel generated 48 items and evaluated their quality and relevance and made necessary amendments.
-A large scale geographically unconstrained quantitative cross-sectional survey was conducted yielding responses from large sample (n=`r nrow(EFA.descriptives)`) to explore the latent structure.
+A large-scale geographically unconstrained quantitative cross-sectional survey was conducted yielding responses from a large sample (n=`r nrow(data)`).
+Data collected on the first round was used to explore the latent structure (EFA sample; n=`r nrow(EFA.descriptives)`).
 Exploratory factor analysis revealed a five factor solution with 25 items.
@@
 The internal consistency reliability coefficient ordinal alpha ranged between `r apa(min(alpha.tab),2,F)`-`r apa(max(alpha.tab),2,F)`.
-As all the retained factors were meaningful and contributed essentially towards our aim we retained all five factors.
-
-<!-- A CFA on a separate sample ((n=`r nrow(CFA.descriptives)` gave a five-factor solution (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]) and SRMR = `r apa(fit.2[10],2,F)`) after discarding two item.
-The internal consistency McDonald's $\omega_t$ of the five factors were  satisfactory (`r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`) Internal consistency reliability of the total scale (23 items) was also satisfactory, McDonald's $\omega_t$= `r apa(rel.k[5,6],2,F)`.In the same sample, our measurement invariance analysis  revealed that the latent structure attained the residual measurement invariance across subgroups: male and female (CFI: `r apa (residual.fitm[5,1],2,F)`, TLI: `r apa (residual.fitm[6,1],2,F)`, SRMR: `r apa(residual.fitm[6,1],2,F)`).
--->
-
-<!-- The "Semantic Scale Network"(SSN) analysis [@rosenbusch2020semantic] on the retained 23 items showed "LEBA" was  related to  "Sleep Disturbance Scale For Children" (SDSC) [@bruni1996sleep] and "WHO-Composite International Diagnostic Interview (CIDI): Insomnia"[@who1990].
-Upon inspecting the item contents we found items under "Using phone and smart-watch in bed" and "Using light before bedtime" have semantic overlap with the items of SDSC ans CIDI.
-Items in those two scales were looking into behaviours related to sleep.
-As such the similarity index obtained is expected.
-Flesch-Kincaid Grade Level [@flesch1948new] analysis on the the 23 items of our scale indicated required educational grade level was 3.33 and with a age above 8.33.
--->
-
-<!-- We developed a short-LEBA (18 items) using IRT analysis.
+Except for the fifth factor the internal reliability coefficients were above .70.
+For the fifth factor it was `r apa((alpha.tab[5,1]),2,F)`.
+As a rule of thumb reliability coefficient higher than .70 is considered to be satisfactory.
+However for scales with less than 20 items and at the early developmental stage, a value of .50 is also acceptable [@dall2010developmental; @field2013discovering; @Nunnally1978].
+Also all of the factors were highly interpretable in terms of a common theme and contributed essentially towards our aim to capture light exposure related behaviour.
+This eventually led us to accept this five-factor structure.
+The total scale exhibited satisfactory internal consistency (McDonald's $\omega_t$ = `r apa(omega$omega.tot,2,T)`).
+
+Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five factor structure we obtained in our EFA thus provided evidence of structural validity.
+However, two items were removed from the solution due their less contribution to the model (item 37 & 26).
+The internal consistency coefficients ordinal alpha for the five factors and the total scale were also satisfactory (Ordinal alpha ranged between`r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$ = `r apa(rel.k[5,6],2,F)`).
+On this same data set our measurement invariance analysis indicated the underlying construct of our scale "Light exposure related behaviour" holds the true across native and non-native English speakers.
+This indicates the applicability of LEBA on both native and non-native English Speakers.
+However, this brings up another question to be answered, what is the required grade level to understand the items of our scale?
+To answer this question we ran secondary analysis where we identified the grade level required using Flesch-Kincaid grade level identification method.
+Our scale is will appear understandable to those who are at least a grade four student and have a age of at least 8.33 years.
+As a secondary analysis we also assessed the semantic similarity of our scale to the scales recorded in the "Semantic Scale Network" database [@rosenbusch2020semantic].
+"LEBA" was  related to  "Sleep Disturbance Scale For Children" (SDSC) [@bruni1996sleep] and "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite].
+Upon inspecting the item contents we found items under "Using phone and smart-watch in bed" and "Using light before bedtime" have semantic overlap with the items of SDSC and CIDI.
+However, the aim of those scale and ours was different.
+Items in those two scales were looking into behaviours related to sleep whereas our  aim was to capture light exposure related behaviour.
+
+lastly, we developed a short-LEBA (18 items) using IRT analysis.
 We fitted a graded response model model to the combined EFA and CFA sample (n=`r nrow(data)`).
-We discarded five items with relatively flat item information curve [I($\theta$) <.20].
-IRT analysis indicated short form of LEBA is a psychometrically sound measure.
-Item fit indexes and person fit index for all five fitted model were acceptable.
-Items had diverse slope parameters indicating a good range of discrimination- the ability to differentiate respondents with different levels of the light exposure related behaviour.
-Test information curve also indicated a good coverage of underlying trait continuum with precision.
--->
-
-LEBA can be used to profile individuals based on their light exposure related behaviours, which can facilitate the development process of individual interventions to promote health.
+We discarded five items (1, 25, 38, 30, & 41) with relatively flat item information curve [I($\theta$) <.20].
+Test information curves indicated short form of LEBA is a psychometrically sound measure with adequate coverage of underlying traits to capture different extents of light exposure related behaviours with precision.
+Item fit index and person fit index for all five fitted model were acceptable providing evidence of validity of our models.
+Items had diverse item discrimination parameters indicating a good range of discrimination- the ability to differentiate respondents with different levels of the light exposure related behaviour.
+
+Based on all the gathered evidences, we can say LEBA can be used to profile individuals based on their light exposure related behaviours, which can facilitate the development process of individual interventions to promote health.
 All the five factors of LEBA may identify 'problematic' behaviours that are opposed to good light hygiene.
@@
 We developed a novel self-reported subjective scale-"Light exposure behaviour assessment"(LEBA) to capture light exposure related behaviour.
-We developed 48 items, judged the relevance and content of the items and conducted a large scale geographically unrestricted cross-sectional survey.
+We developed 48 items, judged the relevance and content of the items and conducted a large-scale geographically unrestricted cross-sectional survey.
 Our EFA gave a five solution with 25 items.
@@
 IRT analysis gave a 18-item scale with a good coverage across the underlying trait continuum.
-Hence, we could recommend that LEBA can be used to measure different aspects of light exposure related behaviour.
+Hence, we could recommend that LEBA can be used to profile individuals according to their light exposure related behaviours.
 

### 2022-03-30 manuscript.Rmd
CFA Code Updated

@@
                  F3 =~  item27+ item03+ item40 + item30 + item41
-                 F4 =~ a3*item32 + item35 + item38+ a4*item33 
-                 F5 =~ item46+ item45+ item25+ item04+ item01 
+                 F4 =~ a3*item32 + item35 + item38+ a4*item33 + item37
+                 F5 =~ item46+ item45+ item25+ item04+ item01 +item26
                        a1==a2
@@
 Nevertheless, SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`).
-Further by allowing one pair of items (30-41) [`r Hmisc::label(sem.data$item30)`; `r Hmisc::label(sem.data$item41)`] to covary their error variance and discarding two item (item 37 & 26) for very low r-square value, our model attained the best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]).
+Further by allowing one pair of items (30-41) [`r Hmisc::label(sem.data$item30)`; `r Hmisc::label(sem.data$item41)`] to covary their error variance and discarding two item (item 37 & 26) for possible cross-loading, our model attained the best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]).
 Internal consistency ordinal $\alpha$ for the five factors of LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)` respectively.

### 2022-03-30 manuscript.Rmd
Seconderay analysis updated

@@
 ## Secondary Analysis: Grade Level Identification and Semantic Scale Network Analysis
-Flesch-Kincaid grade level [@flesch1948new] analysis on the 23 items of our scale indicated required educational grade level was 3.33 and with a age above 8.33.
-Semantic Scale Network (SSN) analysis [@rosenbusch2020semantic] indicated that LEBA (23 items) appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite].
+Flesch-Kincaid grade level [@flesch1948new] analysis on the 23 items using "readability" function from the packaged "koRpus" [@R-koRpus] indicated required educational grade level was 3.33 and with a age above 8.33.
+This indicated our scale will be understandable to students of grade four and aged at least 8.33.
+[Semantic Scale Network (SSN) analysis](https://rosenbusch.shinyapps.io/semantic_net) [@rosenbusch2020semantic] indicated that LEBA (23 items) appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite].
 The cosine similarities lie between .47 to .51.
+
 ```{r textanalysis, include=F}

### 2022-03-30 manuscript.Rmd
References updated

@@
 
-A quantitative cross-sectional fully anonymous online large scale survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
+A quantitative cross-sectional fully anonymous online large-scale survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
 Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (<https://enlightenyourclock.org/participate-in-research>) of the science-communication comic-book "Enlighten your clock" co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux].

### 2022-03-30 manuscript.Rmd
Analytic Strategy is Updated with package name

--- 2022-03-30 manuscript.Rmd
@@
 We conducted two rounds of data collections.
-At first, we collected data for from `r nrow(EFA.descriptives)` participants.
-In the second round we collected data from another `r nrow(CFA.descriptives)` participants making a total sample of `r nrow(desctable.data)`.
+At first, we collected data for from `r nrow(EFA.descriptives)` participants (EFA sample).
+In the second round we collected data from another `r nrow(CFA.descriptives)` participants (CFA sample) making a total sample of `r nrow(desctable.data)`.
 The data analysed in this study was collected between 17 May 2021 and 3 September 2021.
@@
 Figure \@ref(fig:FlowchartFig) summarizes the steps we followed while developing LEBA.
-In our analysis we used R statistical tool [@R-base].
+In our analysis we used R statistical tool [@R-base] with several packages [@R-lavaan; @R-mirt; @R-psych; @R-semPlot; @R-tabledown; @R-tidyverse].
 **First**, we developed an item pool of 48 items with six-point Likert type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial scale.
@@
 
-**Second**, for data collection we conducted a large-scale survey.
-**Third**, as a part of psychometric analysis, we conducted descriptive and item analysis and proceeded to the exploratory factor analysis (EFA) on the data collected on the first round of the large scale survey (EFA sample; n=`r nrow(EFA.descriptives)`).
+**Second**, for data collection we conducted two rounds of large-scale survey.
+**Third**, as a part of psychometric analysis, we conducted descriptive and item analysis and proceeded to the exploratory factor analysis (EFA) using "psych" package [@R-psych] on the data collected in the first round (EFA sample; n=`r nrow(EFA.descriptives)`).
 Prior to the EFA, necessary assumptions, including sample adequacy, normality assumptions, quality of correlation matrix were assessed.
@@
 
+For reliability estimation "psych" package was used [@R-psych].
 Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it has a tendency to deflate the estimates for Likert-type data since the calculation is based on Pearson-correlation matrix which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal].
@@
 
-To validate the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with weighted least square with mean and variance adjusted (WLSMV) estimator [@desjardinsHandbookEducationalMeasurement2018] on the data collected in the second round of data collection (CFA sample; n=`r nrow(CFA.descriptives)`).
+To validate the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with weighted least square with mean and variance adjusted (WLSMV) estimator [@desjardinsHandbookEducationalMeasurement2018] using "lavaan" package [@R-lavaan] on the data collected in the second round (CFA sample; n=`r nrow(CFA.descriptives)`).
 We assessed the model fit using common model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI): close to .95 or above/ between .90-.95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner].
@@
 MI evaluates whether a construct has the psychometric equivalence and the same meaning across groups [@putnick2016measurement; @klinePrinciplesPracticeStructural2015].
-We used structural equation modelling framework to assess the measurement invariance.
+We used structural equation modelling framework using "lavaan" package [@R-lavaan] to assess the measurement invariance.
 We successively compared four nested models: configural, metric, scalar, and residual models using the $\chi^2$ difference test ($\Delta \chi^2$).
@@
 
-**Fourth**, as secondary analysis we identified the educational grade level required to understand the items in our scale using Flesch-Kincaid grade level identification method [@flesch1948new].
-Also, we analysed possible semantic overlap of our developed scale using "Semantic Scale Network" (SSN) engine [@rosenbusch2020semantic].
+**Fourth**, as secondary analysis we identified the educational grade level required to understand the items in our scale using Flesch-Kincaid grade level identification method [@flesch1948new] using "koRpus" [@R-koRpus] package.
+Also, we analysed possible semantic overlap of our developed scale using ["Semantic Scale Network" (SSN)](https://rosenbusch.shinyapps.io/semantic_net/) engine [@rosenbusch2020semantic].
 The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic].
@@
 **Lastly**, we developed a short form of LEBA using Item Response Theory (IRT) based analysis.
-We fitted each factor of LEBA using the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =`r nrow(sem.data)`).
+We fitted each factor of LEBA using the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =`r nrow(sem.data)`) using "mirt" package [@R-mirt].
 IRT assesses the item quality by estimating item discrimination, item difficulty, item information curve, and test information curve [@bakerBasicsItemResponse2017].
@@
 ## Secondary Analysis: Grade Level Identification and Semantic Scale Network Analysis
-Flesch-Kincaid grade level [@flesch1948new] analysis on the 23 items of our scale indicated required educational grade level was 3.33 and with a age above 8.33.
+Flesch-Kincaid grade level [@flesch1948new] analysis on the 23 items indicated required educational grade level was 3.33 and with a age above 8.33.
+This indicated our scale will be understandable to students of grade four and aged at least 8.33.
 Semantic Scale Network (SSN) analysis [@rosenbusch2020semantic] indicated that LEBA (23 items) appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite].
 The cosine similarities lie between .47 to .51.
+
 ```{r textanalysis, include=F}

### 2022-03-30 manuscript.Rmd
Headers are alligned
Descriptives updated

@@
 
-## Ethical approval
+## Ethical Approval
 
@@
 
-## Large-scale survey
+## Large-scale Survey
 
@@
 
-### Descriptive Statistics
+### Descriptive Statistics and Item Analysis
+
+```{r full-data-mardia, include =F}
+mardia.all.data <- psych::mardia(sem.data, na.rm = T, plot =T)
+descriptives.all.data <- tabledown::des.tab(sem.data)
+```
 
@@
     mean = mean(value, na.rm = TRUE),
-    med = median(value, na.rm = TRUE),
+    # med = median(value, na.rm = TRUE),
     sd = sd(value, na.rm = TRUE),
@@
 
-gt.tab3 <- cbind(vars_labels, gt.tab2)
-
+gt.tab3 <- cbind(vars_labels, gt.tab2[,c(1,2)], descriptives.all.data$Normality,gt.tab2[,c(3,4)] )
+
+colnames(gt.tab3) <- c("Item", "Stem", "mean", "sd","S-W Statistics", "hist_data","dens_data"  )
 #Preparation for likert data
@@
   ) %>%
+
+     tab_footnote(
+     footnote = md("**Shapiro–Wilk test**"),
+     locations = cells_column_labels(columns = `S-W Statistics`)
+  ) %>% 
 # change column names to appear in the table
@@
   mean = ("Mean"),
-  med = ("Median "),
   sd = (("SD")),
+  `S-W Statistics` = ("SW"),
   hist_data = "Histogram",
@@
 
-Figure \@ref(fig:efagtPic1) and Figure \@ref(fig:efagtPic2) summarize the response pattern of our total sample (n = `r nrow(sem.data)`) for all 48 items. Most of the items were skewed.
-
-### Item Analysis
+Figure \@ref(fig:efagtPic1) and Figure \@ref(fig:efagtPic2) summarize the response pattern of our total sample (n = `r nrow(sem.data)`) for all 48 items.
+Most of the items appeared skewed.The Shapiro–Wilk test of univariate normality [@shapiroAnalysisVarianceTest1965] and Mardia test of multivariate normality [@mardiaMeasuresMultivariateSkewness1970] indicated our data violated both univariate and multivariate normality.
+Multivariate skew was `r printnum(mardia.all.data$b1p)` (p \<0.001) and multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p \<0.001).
 
@@
 
-  gtsave("Supplimentary_materials/S_Figure/S1_Fig.png", vwidth=6000)
+  gtsave("Figures/S1_Fig.png", vwidth=6000)
 
@@
 
-**Supplementary Figure 1** summarizes the univariate descriptive statistics for the 48 items among EFA sample (n =`r nrow(EFA.data)`.
-Our data violated both univariate normality [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970].
+**Supplementary Figure 1** summarizes the univariate descriptive statistics for the 48 items in the EFA sample (n =`r nrow(EFA.data)`.
+Here also our data violated univariate normality [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970].
 Multivariate skew was `r printnum(mardia$b1p)` (p \<0.001) and multivariate kurtosis was `r printnum(mardia$b2p)` (p \<0.001).
@@
         ) %>% 
-  gtsave("Supplimentary_materials/S_Figure/S2_Fig.png",vwidth = 7000)
+  gtsave("Figures/S2_Fig.png",vwidth = 7000)
 
@@
 
-## Developing Short form of LEBA
+## Developing Short form of LEBA: IRT Based Analysis
 
@@
 
-ggsave("Supplimentary_materials/S_Figure/S3_Fig.png",all.factot.itemplots, width = 18, height = 12, dpi = 600, bg = "white")
+ggsave("Figures/S3_Fig.png",all.factot.itemplots, width = 18, height = 12, dpi = 600, bg = "white")
 
@@
 
-ggsave("Supplimentary_materials/S_Figure/S4_Fig.png",personfit , width = 10, height = 12, dpi = 600, bg = "white")
+ggsave("Figures/S4_Fig.png",personfit , width = 10, height = 12, dpi = 600, bg = "white")
 

### 2022-03-30 manuscript.Rmd
Figure Captions corrected

@@
 ---
-title             : "_Light Exposure behaviour Assessment (LEBA)_: Development of a novel instrument to capture light exposure-related behaviours"
+title             : "_Light Exposure Behaviour Assessment (LEBA)_: Development of a novel instrument to capture light exposure-related behaviours"
 shorttitle        : "LEBA"
@@
 
-```{r efagtPic1, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern', out.height='100%', out.width='250%'}
+```{r efagtPic1, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern observed in the large-scale survey for item 01-24.
+All items violated normality assumption', out.height='100%', out.width='250%'}
 knitr::include_graphics('Figures/Figure2.png')
@@
 
-```{r efagtPic2, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern', out.height='100%', out.width='250%'}
+```{r efagtPic2, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern observed in the large-scale survey for item 25-48.
+All items violated normality assumption', out.height='100%', out.width='250%'}
 knitr::include_graphics('Figures/Figure3.png')
@@
 
-```{r Testinfo, fig.env = "sidewaysfigure", fig.cap="Test information curves for the five factors of LEBA: (a) wearing blue light filters (b) spending time outdoors (c) using phone and smartwatchin bed (d) using light before bedtime (e) using light in the morning andduring daytime.
-Along x-axis we plotted the underlying latent trait continumm for each factor.
+```{r Testinfo, fig.env = "sidewaysfigure", fig.cap="Test information curves for the five factors of LEBA: (a) wearing blue light filters (b) spending time outdoors (c) using phone and smart-watch in bed (d) using light before bedtime (e) using light in the morning and during daytime.
+Along x-axis we plotted the underlying latent trait continuum for each factor.
 Along y-axis we plotted how much information a particular factor is caring across its latent trait continuum", warning=FALSE, out.width="100%", out.height="120%"}

### 2022-03-30 manuscript.Rmd
Supplementart File 1 & 2 cited

@@
 Questions incorporating retrospective recall were all aligned to the period of "past four weeks".\
-We conducted two rounds of data collections.
+We conducted two rounds of data collection.
 At first, we collected data for from `r nrow(EFA.descriptives)` participants (EFA sample).
@@
 Both our EFA and CFA sample size exceeded these requirements.
-We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones).Participants reported a diverse range of geographic location Participants indicated filling out the online survey from a diverse range of geographic locations.
+We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones).
+Participants reported a diverse range of geographic location Participants indicated filling out the online survey from a diverse range of geographic locations.
 For a complete list of geographic locations, see **Supplementary Table 2**.
 
-Participants in our survey aged between `r min(desctable.data$slypos_demographics_age)` to `r max(desctable.data$slypos_demographics_age)` years [EFA sample: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
-EFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
-EFA Sample"])`; CFA sample: *min* = `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`, *max* = `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`], with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 2)` years of age [Overall: *M* = `r mean(desctable.data$slypos_demographics_age)`, *SD* = `r sd(desctable.data$slypos_demographics_age)`; EFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
-EFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
-EFA Sample"])`; CFA: *M* = `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`, *SD* = `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
+Participants in our survey aged between `r min(desctable.data$slypos_demographics_age)` to `r max(desctable.data$slypos_demographics_age)` years [EFA sample: `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
+EFA Sample"])` to `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
+EFA Sample"])`; CFA sample: `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
+CFA Sample"])`to `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
+CFA Sample"])`], with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 2)` years of age [Overall: `r mean(desctable.data$slypos_demographics_age)`± `r sd(desctable.data$slypos_demographics_age)`; EFA: `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
+EFA Sample"])`± `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
+EFA Sample"])`; CFA: `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
+CFA Sample"])`± `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
 CFA Sample"])`].
@@
 ```{r efagtPic1, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern observed in the large-scale survey for item 01-24.
-All items violated normality assumption', out.height='100%', out.width='250%'}
+All items violated normality assumption.', out.height='100%', out.width='250%'}
 knitr::include_graphics('Figures/Figure2.png')
@@
 ```{r efagtPic2, echo=FALSE,  fig.cap= 'Summary descriptives and response pattern observed in the large-scale survey for item 25-48.
-All items violated normality assumption', out.height='100%', out.width='250%'}
+All items violated normality assumption.', out.height='100%', out.width='250%'}
 knitr::include_graphics('Figures/Figure3.png')
@@
 
-**Supplementary Figure 1** summarizes the univariate descriptive statistics for the 48 items in the EFA sample (n =`r nrow(EFA.data)`.
-Here also our data violated univariate normality [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970].
+**Supplementary Figure 1** summarizes the univariate descriptive statistics for the 48 items in the EFA sample (n =`r nrow(EFA.data)`).
+Here also our data violated univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970].
 Multivariate skew was `r printnum(mardia$b1p)` (p \<0.001) and multivariate kurtosis was `r printnum(mardia$b2p)` (p \<0.001).
@@
 Scree plot ( Figure \@ref(fig:efa-plot-print)-B) suggested a six-factor solution.
-However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (**Supplementary Table 3**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print)C) suggested a five-factor solution.
+However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (**Supplementary Table 3**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print)-C) suggested a five-factor solution.
 As a result, we tested both five-factor and six-factor solutions.
@@
 The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`.
-However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:efa-plot-print)D) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring.
+However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:efa-plot-print)-D) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring.
 [@desjardinsHandbookEducationalMeasurement2018].
@@
 Table \@ref(tab:tabCfa) summarizes the CFA fit indices of our fitted model.
-Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`); RMSEA = `r apa(fit.1[7],2,F)`[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 [`r Hmisc::label(sem.data$item32)`; `r Hmisc::label(sem.data$item33)`] and 16-17 [`r Hmisc::label(sem.data$item16)`; `r Hmisc::label(sem.data$item17)`].
+Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`; RMSEA = `r apa(fit.1[7],2,F)`[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 [`r Hmisc::label(sem.data$item32)`; `r Hmisc::label(sem.data$item33)`] and 16-17 [`r Hmisc::label(sem.data$item16)`; `r Hmisc::label(sem.data$item17)`].
 Items pair 32-33 stemmed from the preference of dimming electric device's brightness before bed time and items pair 16 and 19 stemmed from the preference of using blue filtering or coloured glasses during the daytime.
@@
 Internal consistency ordinal $\alpha$ for the five factors of LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)` respectively.
+As such, we accept this model thus finalizing the long Form of LEBA with 23 items.
+The items are provided in the **Supplementary File 1**.
 Internal consistency McDonald's $\omega_t$ coefficient for the total scale was `r apa(rel.k[5,6],2,F)`.
@@
 ## Secondary Analysis: Grade Level Identification and Semantic Scale Network Analysis
-Flesch-Kincaid grade level [@flesch1948new] analysis on the 23 items indicated required educational grade level was 3.33 and with a age above 8.33.
+Flesch-Kincaid grade level [@flesch1948new] analysis on the 23 items indicated required educational grade level was 3.33 and with a age above 8.33 years.
 This indicated our scale will be understandable to students of grade four and aged at least 8.33.
@@
 Examination of the item information curve (**Supplementary Figure 3**) indicated five items (1, 25, 38, 30, & 41) had relatively flat information curves (I($\theta$) \<.20).
-We discarded those items which yielded a short form of LEBA with 5 factors and 18 items.
+We discarded those items which yielded a short form of LEBA with 5 factors and 18 items (**Supplementary File 2**).
 

### 2022-03-30 manuscript.Rmd
Person fit 5 axis lebel changed

@@
 F5.person <- ggplot(F5.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill="#00A08799")+geom_vline(xintercept = -2)+
-  labs( y="Number of Participants", x = "Zh Statistics:F5")+apatheme+ylim(0,600) + xlim(-4,2)
+  labs( y="Number of Participants", x = "Zh Statistics: F5")+apatheme+ylim(0,600) + xlim(-4,2)
 

### 2022-03-30 manuscript.Rmd
EFA table caption updated

@@
 
-apa_table(efa.tab.ful, caption = "Factor loadings and communality of the retained items in EFA using principal axis extraction method.", note = "Only loading > .30 is reported.", 
+apa_table(efa.tab.ful, caption = "Factor loadings and communality of the retained items in EFA using principal axis extraction method (n=482).", note = "Only loading > .30 is reported.", 
           font_size = "footnotesize", escape=F,landscape = T,

### 2022-03-30 manuscript.Rmd
CFA Analysis MI explained

@@
 Exploratory factor analysis (EFA) on an initial subset of our sample (n=428) rendered a five-factor solution with 25 items (Wearing blue light filters, spending time outdoors, using phone and smart-watch in bed, using light before bedtime, using light in the morning and during daytime).
-In a confirmatory factor analysis (CFA) performed on an independent subset of participants (n=262), we removed two further items to attain the best fit for the five-factor solution (CFI=0.97, TLI=0.96, RMSEA=0.05, SRMR=0.09).
-The internal consistency reliability coefficient for the total instrument was, McDonald’s Omega(total)=0.73.
+In a confirmatory factor analysis (CFA) performed on an independent subset of participants (n=262), we removed two further items to attain the best fit for the five-factor solution (CFI=0.95, TLI=0.95, RMSEA=0.06).
+The internal consistency reliability coefficient for the total instrument was, McDonald’s Omega(total)=0.68.
 Measurement model invariance analysis between native and non-native English speakers showed our model attained the highest level of invariance (residual invariance; CFI=0.95, TLI =0.95, RMSEA=0.05).
@@
 
-With the initial 48 items we conducted three rounds of EFA and gradually discarded problematic items (cross-loading items and poor factor loading (\<.30) items).
+With the initial 48 items we conducted three rounds of EFA with varimax rotation and gradually discarded problematic items (cross-loading items and poor factor loading (\<.30) items).
 Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30.
@@
 Table \@ref(tab:tabCfa) summarizes the CFA fit indices of our fitted model.
-Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`; RMSEA = `r apa(fit.1[7],2,F)`[`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 [`r Hmisc::label(sem.data$item32)`; `r Hmisc::label(sem.data$item33)`] and 16-17 [`r Hmisc::label(sem.data$item16)`; `r Hmisc::label(sem.data$item17)`].
+Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`; RMSEA = `r apa(fit.1[7],2,F)` [`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 [`r Hmisc::label(sem.data$item32)`; `r Hmisc::label(sem.data$item33)`] and 16-17 [`r Hmisc::label(sem.data$item16)`; `r Hmisc::label(sem.data$item17)`].
 Items pair 32-33 stemmed from the preference of dimming electric device's brightness before bed time and items pair 16 and 19 stemmed from the preference of using blue filtering or coloured glasses during the daytime.
+Given the similar nature of behaviour, these items were capturing we accepted the equity constrain imposed.
 Nevertheless, SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`).
-Further by allowing one pair of items (30-41) [`r Hmisc::label(sem.data$item30)`; `r Hmisc::label(sem.data$item41)`] to covary their error variance and discarding two item (item 37 & 26) for possible cross-loading, our model attained the best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)`[`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]).
+
+To improve model fit we conducted a post-hoc model modification.
+Modification indices indicated the possibility of cross-loading of the item 37 and 26 [`r Hmisc::label(sem.data$item37)`; `r Hmisc::label(sem.data$item26)`], thus discarded.
+Also, item 30 and 41 [`r Hmisc::label(sem.data$item30)`; `r Hmisc::label(sem.data$item41)`] showed a tendency to co-vary in their error variance (MI = 141.127, p<.001 ).
+By allowing this pair of items (30 $\&$ 41)  to covary their error variance our model attained the best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR = `r apa(fit.2[10],2,F) `).
 Internal consistency ordinal $\alpha$ for the five factors of LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)` respectively.
@@
 
-Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five factor structure we obtained in our EFA thus provided evidence of structural validity.
-However, two items were removed from the solution due their less contribution to the model (item 37 & 26).
+Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five factor structure we obtained in our EFA thus provided evidence of structural validity.(CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR = `r apa(fit.2[10],2,F) `).
+However, in this model we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings.
+Also, we accepted one pair of items (item 30 $\&$ 41) to covary their error variance .
+This item-pair was capturing smart-watch based light exposure behaviour.
+In retrospect, it seemed plausible that not having  a smart-watch may lead the respondent to answer in a similar fashion for these two items.
+Thus, we decided to accept the modification to our model.
 The internal consistency coefficients ordinal alpha for the five factors and the total scale were also satisfactory (Ordinal alpha ranged between`r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$ = `r apa(rel.k[5,6],2,F)`).

### 2022-03-30 manuscript.Rmd
Typo corrected in the discussion

@@
 The internal consistency coefficients ordinal alpha for the five factors and the total scale were also satisfactory (Ordinal alpha ranged between`r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$ = `r apa(rel.k[5,6],2,F)`).
-On this same data set our measurement invariance analysis indicated the underlying construct of our scale "Light exposure related behaviour" holds the true across native and non-native English speakers.
-This indicates the applicability of LEBA on both native and non-native English Speakers.
-However, this brings up another question to be answered, what is the required grade level to understand the items of our scale?
+On this same data set our measurement invariance analysis indicated the underlying construct of our scale "Light exposure related behaviour" was equivalent across native and non-native English speakers.
+This indicated the applicability of LEBA on both native and non-native English Speakers.
+However, this decisions brought up another question to be answered, what was the required grade level to understand the items of our scale?
 To answer this question we ran secondary analysis where we identified the grade level required using Flesch-Kincaid grade level identification method.
-Our scale is will appear understandable to those who are at least a grade four student and have a age of at least 8.33 years.
+Our scale would appear understandable to those who were at least a grade four student and had a age of at least 8.33 years.
 As a secondary analysis we also assessed the semantic similarity of our scale to the scales recorded in the "Semantic Scale Network" database [@rosenbusch2020semantic].
@@
 Upon inspecting the item contents we found items under "Using phone and smart-watch in bed" and "Using light before bedtime" have semantic overlap with the items of SDSC and CIDI.
-However, the aim of those scale and ours was different.
+However, the aim of those scale and ours were different.
 Items in those two scales were looking into behaviours related to sleep whereas our aim was to capture light exposure related behaviour.

### 2022-04-04 manuscript.Rmd
Potential Candidate for round 2

@@
 The internal consistency reliability coefficient for the total instrument was, McDonald’s Omega(total)=0.68.
-Measurement model invariance analysis between native and non-native English speakers showed our model attained the highest level of invariance (residual invariance; CFI=0.95, TLI =0.95, RMSEA=0.05).
+Measurement model invariance analysis between native and non-native English speakers showed our model attained the highest level of invariance (residual invariance; CFI=0.95, TLI=0.95, RMSEA=0.05).
 Lastly, a short form of LEBA (n=18) was developed using Item Response Theory on the complete sample (n=690).
@@
 
-A quantitative cross-sectional fully anonymous online large-scale survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
+A quantitative cross-sectional fully anonymous geographically unconstrained online large-scale survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
 Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (<https://enlightenyourclock.org/participate-in-research>) of the science-communication comic-book "Enlighten your clock" co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux].
@@
 Under-aged participants (\<18 years) were urged to obtain assent from their parents/legal guardians.
-The entire survey was estimated to take \<30 minutes.
+The entire survey was estimated to take less than 30 minutes.
 Participants were not compensated.
@@
 We conducted two rounds of data collection.
-At first, we collected data for from `r nrow(EFA.descriptives)` participants (EFA sample).
+At first, we collected data from `r nrow(EFA.descriptives)` participants (EFA sample).
 In the second round we collected data from another `r nrow(CFA.descriptives)` participants (CFA sample) making a total sample of `r nrow(desctable.data)`.
@@
 Figure \@ref(fig:FlowchartFig) summarizes the steps we followed while developing LEBA.
-In our analysis we used R statistical tool [@R-base] with several packages [@R-lavaan; @R-mirt; @R-psych; @R-semPlot; @R-tabledown; @R-tidyverse].
+In our analysis we used R statistical tool [@R-base].
 **First**, we developed an item pool of 48 items with six-point Likert type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial scale.
@@
 **Lastly**, we developed a short form of LEBA using Item Response Theory (IRT) based analysis.
-We fitted each factor of LEBA using the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =`r nrow(sem.data)`) using "mirt" package [@R-mirt].
+We fitted each factor of LEBA using the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n=`r nrow(sem.data)`) using "mirt" package [@R-mirt].
 IRT assesses the item quality by estimating item discrimination, item difficulty, item information curve, and test information curve [@bakerBasicsItemResponse2017].
@@
 EFA Sample"])`; CFA sample: `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`to `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`], with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 2)` years of age [Overall: `r mean(desctable.data$slypos_demographics_age)`± `r sd(desctable.data$slypos_demographics_age)`; EFA: `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
-EFA Sample"])`± `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
+CFA Sample"])` to `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
+CFA Sample"])`], with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 2)` years of age [Overall: `r mean(desctable.data$slypos_demographics_age)`±`r sd(desctable.data$slypos_demographics_age)`; EFA: `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
+EFA Sample"])`±`r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
 EFA Sample"])`; CFA: `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`± `r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
+CFA Sample"])`±`r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
 CFA Sample"])`].
@@
   tab_header(
-    title = md("Summary Descriptives (n =690)"),
+    title = md("Summary Descriptives (n=690)"),
     subtitle = md("Items 01-24 ")) %>% 
@@
   tab_header(
-    title = md("Summary Descriptives (n =690)"),
+    title = md("Summary Descriptives (n=690)"),
     subtitle = md("Items 25-48 ")) %>% 
@@
 
-Figure \@ref(fig:efagtPic1) and Figure \@ref(fig:efagtPic2) summarize the response pattern of our total sample (n = `r nrow(sem.data)`) for all 48 items.
+Figure \@ref(fig:efagtPic1) and Figure \@ref(fig:efagtPic2) summarize the response pattern of our total sample (n=`r nrow(sem.data)`) for all 48 items.
 Most of the items appeared skewed.The Shapiro–Wilk test of univariate normality [@shapiroAnalysisVarianceTest1965] and Mardia test of multivariate normality [@mardiaMeasuresMultivariateSkewness1970] indicated our data violated both univariate and multivariate normality.
@@
     title = md("**Light Exposure Behavior Assessment**"),
-    subtitle = md("Summary Descriptives EFA Sample (n =428)")
+    subtitle = md("Summary Descriptives EFA Sample (n=428)")
   ) %>% 
@@
 
-**Supplementary Figure 1** summarizes the univariate descriptive statistics for the 48 items in the EFA sample (n =`r nrow(EFA.data)`).
+**Supplementary Figure 1** summarizes the univariate descriptive statistics for the 48 items in the EFA sample (n=`r nrow(EFA.data)`).
 Here also our data violated univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970].
@@
 
-Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy using the EFA sample (n =`r nrow(EFA.data)`) [@kaiserIndexFactorialSimplicity1974] .
+Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy using the EFA sample (n=`r nrow(EFA.data)`) [@kaiserIndexFactorialSimplicity1974] .
 The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cut-off value (.50) indicating adequate sample size [@hutchesonMultivariateSocialScientist1999].
-Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`) = `r apa(bartlet$chisq, 2, T)`, p \< .001 indicated the correlations between items are adequate for conducting the EFA.
+Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`)=`r apa(bartlet$chisq, 2, T)`, p \< .001 indicated the correlations between items are adequate for conducting the EFA.
 However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than \|.30\|.
@@
 efa.table <- tabledown::fac.tab(fa.5F.3,cut=.3, complexity = F)
+efa.table$Communality <- round(as.numeric(efa.table$Communality),2)
 
@@
 
+efa.tab.ful[26,8] <- "-"
+
 #Communality
@@
 
-With the initial 48 items we conducted three rounds of EFA with varimax rotation and gradually discarded problematic items (cross-loading items and poor factor loading (\<.30) items).
+With the initial 48 items we conducted three rounds of EFA with varimax rotation and gradually discarded problematic items (cross-loading items and items with factor loading \<.30).
 Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30.
@@
 It is essential to attain a balance between psychometric properties and interpretability of the common themes when exploring the latent structure.
-As all of the emerged factors are highly interpretable and relevant towards our aim to capture light exposure related behaviour, regardless of the apparent low reliability of the fifth factor, we retain all the five-factors with 23 items for our confirmatory factor analysis (CFA).
+As all of the emerged factors are highly interpretable and relevant towards our aim to capture light exposure related behaviour, regardless of the apparent low reliability of the fifth factor, we retain all the five-factors with 25 items for our confirmatory factor analysis (CFA).
 Two items showed negative factor-loading (items 44 and 21).
-Upon inspection, it was understood that these items are negatively correlated to the respective common theme, and thus in the CFA analysis, we reverse coded these two items.
+Upon inspection, it was understood that these items are negatively correlated to the respective common theme, and thus in the CFA analysis, we reverse scored these two items.
 Internal consistency coefficient McDonald's $\omega_t$ for the total scale was `r apa(omega$omega.tot,2,T)`.
@@
 Table \@ref(tab:tabCfa) summarizes the CFA fit indices of our fitted model.
-Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`; RMSEA = `r apa(fit.1[7],2,F)` [`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 [`r Hmisc::label(sem.data$item32)`; `r Hmisc::label(sem.data$item33)`] and 16-17 [`r Hmisc::label(sem.data$item16)`; `r Hmisc::label(sem.data$item17)`].
+Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`; RMSEA = `r apa(fit.1[7],2,F)` [`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 [item 32: I dim my mobile phone screen within 1 hour before attempting to fall asleep; item 33: I dim my computer screen within 1 hour before attempting to fall asleep] and 16-17 [item 16: I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day; item 17: I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day].
 Items pair 32-33 stemmed from the preference of dimming electric device's brightness before bed time and items pair 16 and 19 stemmed from the preference of using blue filtering or coloured glasses during the daytime.
-Given the similar nature of behaviour, these items were capturing we accepted the equity constrain imposed.
+Given the similar nature of behaviour these item pair were capturing, we accepted the equity constrain imposed.
 Nevertheless, SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`).
 
-To improve model fit we conducted a post-hoc model modification.
-Modification indices indicated the possibility of cross-loading of the item 37 and 26 [`r Hmisc::label(sem.data$item37)`; `r Hmisc::label(sem.data$item26)`], thus discarded.
-Also, item 30 and 41 [`r Hmisc::label(sem.data$item30)`; `r Hmisc::label(sem.data$item41)`] showed a tendency to co-vary in their error variance (MI = 141.127, p<.001 ).
+To improve model fit we conducted a post-hoc model modification. Modification indices indicated the possibility of cross-loading of the item 37 and 26 [item 37: I purposely leave
+a light on in my sleep environment while sleeping; item 26: I turn on my ceiling room light when it
+is light outside], thus discarded.
+Also, item 30 and 41 [item 30: I look at my smart-watch within 1 hour before attempting to fall asleep; item 41: I look at my smart-watch when I wake up at night] showed a tendency to co-vary in their error variance (MI = 141.127, p<.001 ).
 By allowing this pair of items (30 $\&$ 41)  to covary their error variance our model attained the best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR = `r apa(fit.2[10],2,F) `).
@@
 Flesch-Kincaid grade level [@flesch1948new] analysis on the 23 items indicated required educational grade level was 3.33 and with a age above 8.33 years.
-This indicated our scale will be understandable to students of grade four and aged at least 8.33.
+This indicated our scale will be understandable to students of grade four and aged at least 8.33 years.
 Semantic Scale Network (SSN) analysis [@rosenbusch2020semantic] indicated that LEBA (23 items) appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite].
@@
 ## Developing Short form of LEBA: IRT Based Analysis
-
-We fitted each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n =690).
+We fitted each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n=690).
 Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**).
-Examination of the item information curve (**Supplementary Figure 3**) indicated five items (1, 25, 38, 30, & 41) had relatively flat information curves (I($\theta$) \<.20).
+Examination of the item information curve (**Supplementary Figure 3**) indicated five items (1, 25, 30, 38, & 41) had relatively flat information curves (I($\theta$) \<.20).
 We discarded those items which yielded a short form of LEBA with 5 factors and 18 items (**Supplementary File 2**).
@@
 ```{r IRTparameters, eval=FALSE, include=FALSE, results='asis'}
-apa_table(itemparameters, caption = "Items discrimination and response category difficulty thresholds of 23 items in  LEBA (n =690)", note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
+apa_table(itemparameters, caption = "Items discrimination and response category difficulty thresholds of 23 items in  LEBA (n=690)", note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
 ```
@@
 Also all of the factors were highly interpretable in terms of a common theme and contributed essentially towards our aim to capture light exposure related behaviour.
-This eventually led us to accept this five-factor structure.
-The total scale exhibited satisfactory internal consistency (McDonald's $\omega_t$ = `r apa(omega$omega.tot,2,T)`).
-
-Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five factor structure we obtained in our EFA thus provided evidence of structural validity.(CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR = `r apa(fit.2[10],2,F) `).
+This eventually led us to accept the obtained five-factor structure.
+The total scale exhibited satisfactory internal consistency (McDonald's $\omega_t$=`r apa(omega$omega.tot,2,T)`).
+
+Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five factor structure we obtained in our EFA thus provided evidence of structural validity.(CFI=`r apa(fit.2[5],2,F)`; TLI=`r apa(fit.2[6],2,F)`); RMSEA=`r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR=`r apa(fit.2[10],2,F) `).
 However, in this model we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings.
@@
 Thus, we decided to accept the modification to our model.
-The internal consistency coefficients ordinal alpha for the five factors and the total scale were also satisfactory (Ordinal alpha ranged between`r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$ = `r apa(rel.k[5,6],2,F)`).
+The internal consistency coefficients ordinal alpha for the five factors and the total scale were also satisfactory (Ordinal alpha ranged between `r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$=`r apa(rel.k[5,6],2,F)`).
 On this same data set our measurement invariance analysis indicated the underlying construct of our scale "Light exposure related behaviour" was equivalent across native and non-native English speakers.
@@
 We fitted a graded response model model to the combined EFA and CFA sample (n=`r nrow(data)`).
-We discarded five items (1, 25, 38, 30, & 41) with relatively flat item information curve [I($\theta$) <.20].
+We discarded five items (1, 25, 30, 38, & 41) with relatively flat item information curve [I($\theta$) <.20].
 Test information curves indicated short form of LEBA is a psychometrically sound measure with adequate coverage of underlying traits to capture different extents of light exposure related behaviours with precision.

### 2022-04-04 manuscript.Rmd
minor update
This version is sent for round 3 feedback

@@
 
-ggsave("Figures/EFAfull.png",EFAplot.2, width = 6, height =7, dpi = 1200, bg ="white")
+ggsave("Figures/EFAfull.png",EFAplot.2, width = 6, height =7, dpi = 1200)
 
@@
 Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`; RMSEA = `r apa(fit.1[7],2,F)` [`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 [item 32: I dim my mobile phone screen within 1 hour before attempting to fall asleep; item 33: I dim my computer screen within 1 hour before attempting to fall asleep] and 16-17 [item 16: I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day; item 17: I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day].
-Items pair 32-33 stemmed from the preference of dimming electric device's brightness before bed time and items pair 16 and 19 stemmed from the preference of using blue filtering or coloured glasses during the daytime.
+Item pair 32-33 stemmed from the preference of dimming electric device's brightness before bed time and item pair 16-17 stemmed from the preference of using blue filtering or coloured glasses during the daytime.
 Given the similar nature of behaviour these item pair were capturing, we accepted the equity constrain imposed.
@@
 a light on in my sleep environment while sleeping; item 26: I turn on my ceiling room light when it
-is light outside], thus discarded.
+is light outside] thus discarded.
 Also, item 30 and 41 [item 30: I look at my smart-watch within 1 hour before attempting to fall asleep; item 41: I look at my smart-watch when I wake up at night] showed a tendency to co-vary in their error variance (MI = 141.127, p<.001 ).
@@
 **Supplementary Table 5** summarizes the demographic descriptions native and non-native English speakers.Table \@ref(tab:InvarianceTab) indicates our fitted model had acceptable fit indices for all of the fitted MI models.
-The model fit did not significantly decrease across the nested models indicating the acceptability of the highest measurement invariance model : residual model.
+The model fit did not significantly decrease across the nested models indicating the acceptability of the highest measurement invariance model: residual model.
 

### 2022-05-23 manuscript.Rmd
Introduction addedd

@@
 
--   Light exposure is important
-
--   Light exposure Behaviour is important
-
--   Supplementary Table S1: Overview Existing Related Scales
-
--   Existing Scales: Review them in text
-
--   None of these do light exposure behaviour.
+Our circadian rhythm is in sync with the earth's 24-hour rotation cycle.
+In this synchronization, light plays the vital role.
+Light sends signals to the master oscillator of our brain, the suprachiasmatic nuclei (SCN), via the third class of photoreceptors- intrinsically photosensitive retinal ganglion cells (ipRGCs) [@berson2002phototransduction; @lucas2014measuring; @provencio1998retinal], thus entraining our biological clock [@duffy2005entrainment].
+However, the temporal properties of light exposure, i.e., the time of day and the duration of light exposure, play a vital role in our health and well-being.
+These influences of light are known as non-image-forming (NIF) effects of light and include several physiological and psychological aspects such as secretion of melatonin, modulation of pupil size, skin temperature, alertness and other higher cognitive functions [@cajochen2000dose; @lok2018light; @siraji2021effects].
+Wrong light exposure at an inappropriate time of day may lead to sleep disturbances [@chellappa2013acute; @santhi2012spectral].
+Evening and nighttime bright light exposure may cause suppression of melatonin [@gooley2011exposure] and may cause a phase shift in the internal biological clock, thus, desynchronizing the body clock with nature's day-night circle.
+This reorganization of the body clock can create a series of adverse effects, including alteration of rhythmicity of several hormones, increased stress, cancer, and metabolic disruption, including obesity, type II diabetes, and heart diseases [@navara2007dark]
+
+With the increased use of electric light, the natural temporal organization of the dark-light cycle has been compromised.
+People are exposed to light more than ever.
+Furthermore, nighttime electric light exposure is significantly increased day by day.
+In the US, more than 80% of the population is exposed to a night sky that is brighter than nights with a full moon due to electric light at night [@navara2007dark].
+Our circadian clock signals the start of our melatonin secretion in our body based on the darkness of the night [@pauley2004lighting].
+Since nights are no longer pure dark, most of the light-dependent systems of our body are disrupted.
+For example, studies suggest that electric monochromatic blue light exposure as low as 0.1 lux, which is almost equivalent to the brightness of full moonlight, may reduce the melatonin level [@brainard2002photoreception].
+In turn, such changes in melatonin levels influence metabolism, immunity, fertility, and other hormonal balance, including adrenaline and thyroid hormone [@prendergast2002mammalian].
+
+In recent years, the focus has been given in understanding the pathways underlying these influences of light.
+ipRGCs are mostly responsible for signalling the SCN when the ambient light changes [@gooley2003broad].
+Additionally, ipRGCs also send signals to different brain regions, closely associated with our sleep, attention and emotion, thus influencing our work performance, sleep quality and mood (For a detailed discussion, see [@lok2018light; @siraji2021effects]).
+However, it is also essential to understand the behaviours people are engaging in, which ultimately quantify our light consumption.
+People are getting different types of light exposure due to their different daily life activities, including workplace habits, bedtime hygiene,  pastimes, and other social activities.
+Currently, little effort has been made to understand and capture these behaviours.
+Supplementary Table 1 summarizes relevant questionnaires to understand different light exposure related properties.
+Only a few questions of these questionnaires were related to light exposure related behaviour.
+For example, "Munich Chronotype Questionnaire" [@roenneberg2003life], a self-reporting chronotype identifier, has questions about time spent outdoors and the work environment.
+Popularly used "Pittsburgh Sleep Quality Index" [@buysse1989pittsburgh], a measure of sleep quality, also has questions about sleeping and wake-up time.
+However, none of these questionnaires provides a scaleable solution to capture light exposure related behaviour.
+To fill this gap, here we have reported the development process of a novel tool- "Light Exposure Behavior Assessment" (LEBA), to capture and quantify different light exposure related behaviour.
+LEBA will allow us to capture different light exposure related behaviour and gain insight into how different behaviour changes one's light exposure.
+Understanding these light exposure related behaviour will help us provide a personalized light diet to decrease the effects of inappropriate light exposure.
 

### 2022-05-23 manuscript.Rmd
Typo fixed

@@
 Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (<https://enlightenyourclock.org/participate-in-research>) of the science-communication comic-book "Enlighten your clock" co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux].
-The landing page of the online survey had the explanatory statements where we mentioned participation was voluntary and that respondents could withdraw from participation any time without being penalized.
+The landing page of the online survey had the explanatory statements where we mentioned participation was voluntary and that respondents could withdraw from participation at any time without being penalized.
 At the beginning of the survey, for the adult participants (\>18 years) consent was recorded digitally.
@@
 What is 4+5?").
-Participants were asked to confirm that they were participating the survey for the first time.
-Questions incorporating retrospective recall were all aligned to the period of "past four weeks".\
+Participants were asked to confirm that they were participating in the survey for the first time.
+Questions incorporating retrospective recall were all aligned to the period of "past four weeks".
+
 We conducted two rounds of data collection.
@@
 Figure \@ref(fig:efagtPic1) and Figure \@ref(fig:efagtPic2) summarize the response pattern of our total sample (n=`r nrow(sem.data)`) for all 48 items.
-Most of the items appeared skewed.The Shapiro–Wilk test of univariate normality [@shapiroAnalysisVarianceTest1965] and Mardia test of multivariate normality [@mardiaMeasuresMultivariateSkewness1970] indicated our data violated both univariate and multivariate normality.
+Most of the items appeared skewed.
+The Shapiro–Wilk test of univariate normality [@shapiroAnalysisVarianceTest1965] and Mardia test of multivariate normality [@mardiaMeasuresMultivariateSkewness1970] indicated our data violated both univariate and multivariate normality.
 Multivariate skew was `r printnum(mardia.all.data$b1p)` (p \<0.001) and multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p \<0.001).
@@
 In our CFA sample we had `r mi.count[1,2]` native English speakers and `r mi.count[2,2]` non-native English speakers.
-**Supplementary Table 5** summarizes the demographic descriptions native and non-native English speakers.Table \@ref(tab:InvarianceTab) indicates our fitted model had acceptable fit indices for all of the fitted MI models.
+**Supplementary Table 5** summarizes the demographic descriptions native and non-native English speakers.
+Table \@ref(tab:InvarianceTab) indicates our fitted model had acceptable fit indices for all of the fitted MI models.
 The model fit did not significantly decrease across the nested models indicating the acceptability of the highest measurement invariance model: residual model.
@@
 ```{r InvarianceTab, results='asis'}
-apa_table(Invariance.table, align = "c",  caption = "Measurment Invariance analysis on CFA sample (n=262) across native and non-native English speakers.", note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square; a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual; * =  df of model comparison.", landscape = T, font_size = "footnotesize", escape=F )
+apa_table(Invariance.table, align = "c",  caption = "Measurement Invariance analysis on CFA sample (n=262) across native and non-native English speakers.", note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square; a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual; * =  df of model comparison.", landscape = T, font_size = "footnotesize", escape=F )
 
@@
 Examination of the item information curve (**Supplementary Figure 3**) indicated five items (1, 25, 30, 38, & 41) had relatively flat information curves (I($\theta$) \<.20).
-We discarded those items which yielded a short form of LEBA with 5 factors and 18 items (**Supplementary File 2**).
+We discarded those items which yielded a short form of LEBA with five factors and 18 items (**Supplementary File 2**).
 
@@
 
-We treated each factor of short-LEBA as a unidimensional construct and obtain 5 TICs (Figure \@ref(fig:Testinfo)).
+We treated each factor of short-LEBA as a unidimensional construct and obtain five TICs (Figure \@ref(fig:Testinfo)).
 These information curves indicated except the first and fifth factors, the other three factor's TICs are roughly centred on the centre of the trait continuum ($\theta$).
-The first and fifth factor had a peak to the right side of the centre of latent trait.Thus we conferred the LEBA scale estimated the light exposure related behaviour with precision near the centre of trait continuum for 2nd, 3rd and 4th factors and near the right side of the centre of trait continuum for 1st and 5th factors [@bakerBasicsItemResponse2017].
+The first and fifth factor had a peak to the right side of the centre of latent trait.
+Thus we conferred the LEBA scale estimated the light exposure related behaviour with precision near the centre of trait continuum for second, third and fourth factors and near the right side of the centre of trait continuum for first and fifth factors [@bakerBasicsItemResponse2017].
 
@@
 
-Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five factor structure we obtained in our EFA thus provided evidence of structural validity.(CFI=`r apa(fit.2[5],2,F)`; TLI=`r apa(fit.2[6],2,F)`); RMSEA=`r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR=`r apa(fit.2[10],2,F) `).
-However, in this model we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings.
+Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five factor structure we obtained in our EFA thus provided evidence of structural validity.(CFI=`r apa(fit.2[5],2,F)`; TLI=`r apa(fit.2[6],2,F)`; RMSEA=`r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR=`r apa(fit.2[10],2,F) `).
+However, in this model, we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings.
 Also, we accepted one pair of items (item 30 $\&$ 41) to covary their error variance .
@@
 lastly, we developed a short-LEBA (18 items) using IRT analysis.
-We fitted a graded response model model to the combined EFA and CFA sample (n=`r nrow(data)`).
+We fitted a graded response model to the combined EFA and CFA sample (n=`r nrow(data)`).
 We discarded five items (1, 25, 30, 38, & 41) with relatively flat item information curve [I($\theta$) <.20].
@@
 
-Based on all the gathered evidences, we can say LEBA can be used to profile individuals based on their light exposure related behaviours, which can facilitate the development process of individual interventions to promote health.
+Based on all the gathered evidence, we can say LEBA can be used to profile individuals based on their light exposure related behaviours, which can facilitate the development process of individual interventions to promote health.
 All the five factors of LEBA may identify 'problematic' behaviours that are opposed to good light hygiene.

### 2022-07-03 manuscript.Rmd
rewrite Introduction add references in references.bib file adjustments in spelling and phrasing in Methods section #data collection

@@
 
-Our circadian rhythm is in sync with the earth's 24-hour rotation cycle.
-In this synchronization, light plays the vital role.
-Light sends signals to the master oscillator of our brain, the suprachiasmatic nuclei (SCN), via the third class of photoreceptors- intrinsically photosensitive retinal ganglion cells (ipRGCs) [@berson2002phototransduction; @lucas2014measuring; @provencio1998retinal], thus entraining our biological clock [@duffy2005entrainment].
-However, the temporal properties of light exposure, i.e., the time of day and the duration of light exposure, play a vital role in our health and well-being.
-These influences of light are known as non-image-forming (NIF) effects of light and include several physiological and psychological aspects such as secretion of melatonin, modulation of pupil size, skin temperature, alertness and other higher cognitive functions [@cajochen2000dose; @lok2018light; @siraji2021effects].
-Wrong light exposure at an inappropriate time of day may lead to sleep disturbances [@chellappa2013acute; @santhi2012spectral].
-Evening and nighttime bright light exposure may cause suppression of melatonin [@gooley2011exposure] and may cause a phase shift in the internal biological clock, thus, desynchronizing the body clock with nature's day-night circle.
-This reorganization of the body clock can create a series of adverse effects, including alteration of rhythmicity of several hormones, increased stress, cancer, and metabolic disruption, including obesity, type II diabetes, and heart diseases [@navara2007dark]
-
-With the increased use of electric light, the natural temporal organization of the dark-light cycle has been compromised.
-People are exposed to light more than ever.
-Furthermore, nighttime electric light exposure is significantly increased day by day.
-In the US, more than 80% of the population is exposed to a night sky that is brighter than nights with a full moon due to electric light at night [@navara2007dark].
-Our circadian clock signals the start of our melatonin secretion in our body based on the darkness of the night [@pauley2004lighting].
-Since nights are no longer pure dark, most of the light-dependent systems of our body are disrupted.
-For example, studies suggest that electric monochromatic blue light exposure as low as 0.1 lux, which is almost equivalent to the brightness of full moonlight, may reduce the melatonin level [@brainard2002photoreception].
-In turn, such changes in melatonin levels influence metabolism, immunity, fertility, and other hormonal balance, including adrenaline and thyroid hormone [@prendergast2002mammalian].
-
-In recent years, the focus has been given in understanding the pathways underlying these influences of light.
-ipRGCs are mostly responsible for signalling the SCN when the ambient light changes [@gooley2003broad].
-Additionally, ipRGCs also send signals to different brain regions, closely associated with our sleep, attention and emotion, thus influencing our work performance, sleep quality and mood (For a detailed discussion, see [@lok2018light; @siraji2021effects]).
-However, it is also essential to understand the behaviours people are engaging in, which ultimately quantify our light consumption.
-People are getting different types of light exposure due to their different daily life activities, including workplace habits, bedtime hygiene,  pastimes, and other social activities.
-Currently, little effort has been made to understand and capture these behaviours.
-Supplementary Table 1 summarizes relevant questionnaires to understand different light exposure related properties.
-Only a few questions of these questionnaires were related to light exposure related behaviour.
-For example, "Munich Chronotype Questionnaire" [@roenneberg2003life], a self-reporting chronotype identifier, has questions about time spent outdoors and the work environment.
-Popularly used "Pittsburgh Sleep Quality Index" [@buysse1989pittsburgh], a measure of sleep quality, also has questions about sleeping and wake-up time.
-However, none of these questionnaires provides a scaleable solution to capture light exposure related behaviour.
-To fill this gap, here we have reported the development process of a novel tool- "Light Exposure Behavior Assessment" (LEBA), to capture and quantify different light exposure related behaviour.
-LEBA will allow us to capture different light exposure related behaviour and gain insight into how different behaviour changes one's light exposure.
-Understanding these light exposure related behaviour will help us provide a personalized light diet to decrease the effects of inappropriate light exposure.
+Light exposure received by the eyes affects many facets of human health, well-being, and performance beyond visual sensation and perception [@boyce_light_2022].
+The so-called non-image-forming (NIF) effects of light comprise light’s circadian and non-circadian influence on several physiological and psychological functions, such as the secretion of melatonin, sleep, mood, pupil size, body temperature, alertness, and higher cognitive functions [i.a.
+reviewed in @Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020 ].
+With the introduction of artificial electric light, human behaviour has become somewhat independent of the natural light-dark cycle – people can now frequently choose when to be exposed to light or darkness.
+For example, they can decide whether to go outdoors and seek out sunlight, switch on/off light-emitting devices, use certain types of lights at home, or avoid specific light environments altogether.
+Additionally, when light sources can not be directly manipulated, sought out, or avoided (for example, at school, work, or in public places), there is still potential leeway to influence them behaviourally, for instance, by wearing sunglasses, directing one’s gaze away or supplementing the situation with additional light sources.
+Although clearly yielding the potential for good, this agency is further associated with increased electric light exposure at night and indoor time during the day, compromising the natural temporal organisation of the light-dark cycle.
+For example, in the US, an average of 87% of the time is spent in enclosed buildings [@Klepeis.2001], and more than 80% of the population is exposed to a night sky that is brighter than nights with a full moon due to electric light at night [@navara_dark_2007].
+An extensive body of scientific evidence suggests that the imbalance of light and dark exposure disrupts humans’ light-dependent physiological systems [@Lunn.2017].
+This, in turn, gives rise to a series of adverse health consequences, including the alteration of several hormonal rhythms, increased cancer rates, cardiovascular diseases, and metabolic disorders, such as obesity, and type II diabetes [see reviews by @Lunn.2017; @navara2007dark; @Chellappa.2019]
+These findings have sparked a significant call for assessment and guidance regarding healthy light exposure and timing – the latter was recently published as consensus-based experts’ recommendations, postulating specific requirements for indoor light environments during the daytime, evening, and nighttime [@Brown.2022].
+Furthermore, building on earlier attempts [e.g.
+@hubalek_ambulant_2006], there was a recent push toward the development and use of portable light loggers to improve ambulant light assessment and gain more insight into the NIF effects of light on human health in field conditions [@stampfli_light-dosimeter_2021; @van_duijnhoven_recommendations_2017; @webler_towards_2021].
+Attached to different body parts (e.g., wrist, head on eye level, chest), these devices allow objectively measuring personal light exposure under real-world conditions and are valuable tools for field studies.
+Nevertheless, these devices also encompass limiting factors such as potentially being intrusive (e.g., when eye-level worn), yielding the risk of getting covered (e.g., when wrist- or chest-worn) and requiring (monetary) resources and expertise for acquisition and maintenance of the devices.
+On the other hand, several attempts have been made to quantify received light exposure subjectively with self-report questionnaires (cf.
+**Supplementary Table 1**), bypassing the cost and intrusiveness issues.
+However, subjective light intensity assessments pose a new set of challenges: The human visual system constantly adapts to brightness [@hurvich_perception_1966], while the human non-visual light processing works largely subconsciously [@allen_exploiting_2018], making the self-report assessment of light properties potentially quite challenging, especially for inexperienced laypeople.
+Retrospectively recalling the properties of a light source can further complicate such subjective evaluations.
+Moreover, measuring light properties alone does not yield any information about how individuals might behave differently regarding diverse light situations.
+These measurement limitations point to a couple of research challenges we aim to take on here: How can we gain insight into light exposure patterns via self-report but circumvent directly inquiring about the specific properties and intensity of a light source?
+And how can we simultaneously assess how people habitually interact with the received light?
+We propose that these challenges can be tackled by assessing light-exposure-related behaviour.
+We argue that, besides measuring received light exposure as intensity, it is also essential to understand people's behaviours concerning different light situations.
+Since, in many cases, humans have become their own agents regarding their exposure to light or darkness through artificial electric light, people's light exposure-related behaviours ultimately determine their light consumption and timing: People receive different light depending on their daily activities, including workplace habits, bedtime hygiene, pastime and social activities.
+The final objective of changing light-dark exposure patterns to avoid or mitigate negative health consequences from unhealthy habits will not just need an assessment of the lighting properties but the active change of behaviours related to light exposure.
+We argue that assessing these activities is a beneficial stepping stone for prospective behaviour change.
+Furthermore, people without light measurement expertise may find it easier to appraise and recall their behaviour concerning light exposure than subjectively assessing a light source’s properties.
+To date, little effort has been made to understand and capture these activities.
+**Supplementary Table 1** summarises the existing questionnaire literature assessing light exposure-related properties.
+However, only a few questions of these existing tools were associated with light exposure-related behaviour.
+For example, the “Munich Chronotype  Questionnaire” [MCTQ; @roenneberg2003life], a popular self-report tool for identifying chronotypes via mid-sleep times, includes questions about the individual’s time spent outdoors on workdays and free days.
+In addition, the “Pittsburgh Sleep Quality Index” [PSQI; @buysse1989pittsburgh], a popular measure of sleep quality, contains questions about sleep and wake-up times, which are relevant to the light exposure around bedtime.
+However, none of these questionnaires provides a scaleable solution to capture light exposure-related behaviour in various physiologically relevant lighting scenarios.
+To fill this gap, we here present the development process of a novel self-report tool - the “Light Exposure Behavior Assessment” (LEBA) - for capturing and quantifying diverse light exposure-related behaviours.
 
@@
 
-A quantitative cross-sectional fully anonymous geographically unconstrained online large-scale survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
-Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (<https://enlightenyourclock.org/participate-in-research>) of the science-communication comic-book "Enlighten your clock" co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux].
-The landing page of the online survey had the explanatory statements where we mentioned participation was voluntary and that respondents could withdraw from participation at any time without being penalized.
-At the beginning of the survey, for the adult participants (\>18 years) consent was recorded digitally.
-Under-aged participants (\<18 years) were urged to obtain assent from their parents/legal guardians.
-The entire survey was estimated to take less than 30 minutes.
-Participants were not compensated.
-As a part of the demographic information participants provided information regarding age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language.
-The demographic characteristics of our sample are given in Table 1.
-To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention.
-What is 4+5?").
-Participants were asked to confirm that they were participating in the survey for the first time.
-Questions incorporating retrospective recall were all aligned to the period of "past four weeks".
-
-We conducted two rounds of data collection.
-At first, we collected data from `r nrow(EFA.descriptives)` participants (EFA sample).
-In the second round we collected data from another `r nrow(CFA.descriptives)` participants (CFA sample) making a total sample of `r nrow(desctable.data)`.
-The data analysed in this study was collected between 17 May 2021 and 3 September 2021.
+A quantitative cross-sectional fully anonymous, geographically unconstrained online large-scale survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
+Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (<https://enlightenyourclock.org/participate-in-research>) of the science-communication comic book "Enlighten your clock", co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by the distribution of the survey link via f.lux [@f.lux].
+The initial page of the online survey provided information about the survey including that participation was voluntary and that respondents could withdraw from participation at any time without being penalised.
+Following this information sheet, consent was recorded digitally for the adult participants (\>18 years), whereas under-aged participants (\<18 years) were prompted to obtain additional assent from their parents/legal guardians.
+Filling in the entire survey was estimated to take less than 30 minutes, and participation was not compensated.
+As a part of the demographic information, participants provided information regarding age, sex, gender identity, occupational status, COVID-19-related occupational setting, time zone/country of residence and native language.
+The demographic characteristics of our sample are given in **Table 1**.
+Additionally, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention.
+What is 4+5?"), to ensure high data quality and participants were asked to confirm that they participated in the survey for the first time.
+All questions incorporating retrospective recall were aligned to a "past four weeks" period.
+
+We collected the survey data between 17 May 2021 and 3 September 2021 – firstly from `r nrow(EFA.descriptives)` participants (EFA sample) – and subsequently, another dataset from `r nrow(CFA.descriptives)` participants (CFA sample) totalling `r nrow(desctable.data)`.
 
@@
 
-Figure \@ref(fig:FlowchartFig) summarizes the steps we followed while developing LEBA.
-In our analysis we used R statistical tool [@R-base].
-**First**, we developed an item pool of 48 items with six-point Likert type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial scale.
-Our purpose was to capture light exposure related behaviour.
-In that context, the first two response options: "Does not apply/I don't know" and "Never" were providing similar information.
-As such we collapsed them into one, making it a 5 point Likert type response format (1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always).
-
-**Second**, for data collection we conducted two rounds of large-scale survey.
-**Third**, as a part of psychometric analysis, we conducted descriptive and item analysis and proceeded to the exploratory factor analysis (EFA) using "psych" package [@R-psych] on the data collected in the first round (EFA sample; n=`r nrow(EFA.descriptives)`).
-Prior to the EFA, necessary assumptions, including sample adequacy, normality assumptions, quality of correlation matrix were assessed.
-Our data violated both the univariate and multivariate normality assumptions.
-Due to these violations and the ordinal nature of our response data, in EFA we used polychoric correlation matrix and employed principal axis (PA) as the factor extraction method [@desjardinsHandbookEducationalMeasurement2018; @watkinsStepbyStepGuideExploratory2020].
+Figure \@ref(fig:FlowchartFig) summarises the steps we followed while developing LEBA. We conducted all analyses with the statistical software environment R [@R-base]. 
+Firstly, we set an item pool of 48 items with a six-point Likert-type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial scale.
+Our purpose was to capture light exposure-related behaviour.
+In that context, the first two response options: "Does not apply/I don't know" and "Never" provided similar information.
+As such we collapsed them into one, making it a 5-point Likert-type response format (1-Never, 2-Rarely, 3-Sometimes, 4-Often, 5-Always).
+
+After the two rounds of data collection, we conducted descriptive and item analysis and proceeded to the exploratory factor analysis (EFA) using "psych" package [@R-psych] on the data collected in the first round (EFA sample; n=`r nrow(EFA.descriptives)`), as a part of psychometric analysis.
+Prior to the EFA, the necessary assumptions, including sample adequacy, normality assumptions, quality of correlation matrix were assessed.
+As our data violated both the univariate and multivariate normality assumption and yielded ordinal response data, we used polychoric correlation matrix in the EFA and employed principal axis (PA) as the factor extraction method [@desjardinsHandbookEducationalMeasurement2018; @watkinsStepbyStepGuideExploratory2020].
 We used a combination of factor identification method including Scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and Hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
-To determine the latent structure, we followed the common guidelines : (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading \> .3 across factors [@bandalosFactorAnalysisExploratory2018].
+To determine the latent structure, we followed the common guidelines: (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading \> .3 across factors [@bandalosFactorAnalysisExploratory2018].
 <!-- We also conducted an EFA on non-merged response options data set (**Supplementary File 1**).
@@
 
-For reliability estimation "psych" package was used [@R-psych].
-Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it has a tendency to deflate the estimates for Likert-type data since the calculation is based on Pearson-correlation matrix which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal].
-Subsequently to get better estimates of reliability we reported ordinal alpha for each factors obtained in EFA [@zumbo2007ordinal].
-We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$ coefficient which is a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
-Both ordinal alpha and McDonald's $\omega_t$ coefficient value range between 0 to 1 and higher value represents better reliability.
-
-To validate the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with weighted least square with mean and variance adjusted (WLSMV) estimator [@desjardinsHandbookEducationalMeasurement2018] using "lavaan" package [@R-lavaan] on the data collected in the second round (CFA sample; n=`r nrow(CFA.descriptives)`).
+For reliability estimation, the "psych" package was applied [@R-psych].
+Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it has a tendency to deflate the estimates for Likert-type data since the calculation is based on the Pearson-correlation matrix, which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal].
+Subsequently, to get better reliability estimates, we reported ordinal alpha for each factor obtained in the EFA [@zumbo2007ordinal].
+We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$ coefficient, which was suggested as a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
+Both ordinal alpha and McDonald's $\omega_t$ coefficient values range between 0 to 1, where higher values represent better reliability.
+
+To validate the latent structure obtained in the EFA, we conducted a categorical confirmatory factor analysis (CFA) with the weighted least squares means and variance adjusted (WLSMV) estimation [@desjardinsHandbookEducationalMeasurement2018], using the "lavaan" package [@R-lavaan] on the data collected in the second round (CFA sample; n=`r nrow(CFA.descriptives)`).
 We assessed the model fit using common model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI): close to .95 or above/ between .90-.95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner].
@@
 
-Table 1 summarizes the survey participants' demographic characteristics.
+Table 1 summarises the survey participants' demographic characteristics.
 Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses.
@@
 
-Figure \@ref(fig:efagtPic1) and Figure \@ref(fig:efagtPic2) summarize the response pattern of our total sample (n=`r nrow(sem.data)`) for all 48 items.
+Figure \@ref(fig:efagtPic1) and Figure \@ref(fig:efagtPic2) summarise the response pattern of our total sample (n=`r nrow(sem.data)`) for all 48 items.
 Most of the items appeared skewed.
@@
 
-**Supplementary Figure 1** summarizes the univariate descriptive statistics for the 48 items in the EFA sample (n=`r nrow(EFA.data)`).
+**Supplementary Figure 1** summarises the univariate descriptive statistics for the 48 items in the EFA sample (n=`r nrow(EFA.data)`).
 Here also our data violated univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970].
@@
 
-Table \@ref(tab:tabCfa) summarizes the CFA fit indices of our fitted model.
+Table \@ref(tab:tabCfa) summarises the CFA fit indices of our fitted model.
 Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`; RMSEA = `r apa(fit.1[7],2,F)` [`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 [item 32: I dim my mobile phone screen within 1 hour before attempting to fall asleep; item 33: I dim my computer screen within 1 hour before attempting to fall asleep] and 16-17 [item 16: I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day; item 17: I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day].
@@
 In our CFA sample we had `r mi.count[1,2]` native English speakers and `r mi.count[2,2]` non-native English speakers.
-**Supplementary Table 5** summarizes the demographic descriptions native and non-native English speakers.
+**Supplementary Table 5** summarises the demographic descriptions native and non-native English speakers.
 Table \@ref(tab:InvarianceTab) indicates our fitted model had acceptable fit indices for all of the fitted MI models.
@@
 
-**Supplementary Table 7** summarizes the item fit indexes of the 18 items.
+**Supplementary Table 7** summarises the item fit indexes of the 18 items.
 All items had RMSEA value $\le$.06 indicating adequate fit of the items to the fitted IRT model.

### 2022-07-06 manuscript.Rmd
adjustments in phrasing, spelling etc. in section ##analytic strategy

@@
 
-A quantitative cross-sectional fully anonymous, geographically unconstrained online large-scale survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
+A quantitative cross-sectional fully anonymous, geographically unconstrained online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
 Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (<https://enlightenyourclock.org/participate-in-research>) of the science-communication comic book "Enlighten your clock", co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by the distribution of the survey link via f.lux [@f.lux].
-The initial page of the online survey provided information about the survey including that participation was voluntary and that respondents could withdraw from participation at any time without being penalised.
-Following this information sheet, consent was recorded digitally for the adult participants (\>18 years), whereas under-aged participants (\<18 years) were prompted to obtain additional assent from their parents/legal guardians.
-Filling in the entire survey was estimated to take less than 30 minutes, and participation was not compensated.
-As a part of the demographic information, participants provided information regarding age, sex, gender identity, occupational status, COVID-19-related occupational setting, time zone/country of residence and native language.
+The initial page of the online survey provided information about the study, including that participation was voluntary and that respondents could withdraw from participation at any time without being penalised.
+Subsequently, consent was recorded digitally for the adult participants (\>18 years), while under-aged participants (\<18 years) were prompted to obtain additional assent from their parents/legal guardians.
+Filling in all questionnaires was estimated to take less than 30 minutes, and participation was not compensated.
+As a part of the demographic data, participants provided information regarding age, sex, gender identity, occupational status, COVID-19-related occupational setting, time zone/country of residence and native language.
 The demographic characteristics of our sample are given in **Table 1**.
-Additionally, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention.
-What is 4+5?"), to ensure high data quality and participants were asked to confirm that they participated in the survey for the first time.
+Participants were asked to confirm that they participated in the survey for the first time.
+Additionally, five attention check items (e.g., "We want to make sure you are paying attention.
+What is 4+5?") were included among the questionnaires to ensure high data quality.
 All questions incorporating retrospective recall were aligned to a "past four weeks" period.
 
-We collected the survey data between 17 May 2021 and 3 September 2021 – firstly from `r nrow(EFA.descriptives)` participants (EFA sample) – and subsequently, another dataset from `r nrow(CFA.descriptives)` participants (CFA sample) totalling `r nrow(desctable.data)`.
+We collected the survey data between 17 May 2021 and 3 September 2021 – firstly from `r nrow(EFA.descriptives)` participants (EFA sample) – and subsequently, another dataset from `r nrow(CFA.descriptives)` participants (CFA sample), totalling `r nrow(desctable.data)`.
 
@@
 Figure \@ref(fig:FlowchartFig) summarises the steps we followed while developing LEBA. We conducted all analyses with the statistical software environment R [@R-base]. 
-Firstly, we set an item pool of 48 items with a six-point Likert-type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial scale.
+**Firstly**, we set an item pool of 48 items with a six-point Likert-type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial scale.
 Our purpose was to capture light exposure-related behaviour.
@@
 
-After the two rounds of data collection, we conducted descriptive and item analysis and proceeded to the exploratory factor analysis (EFA) using "psych" package [@R-psych] on the data collected in the first round (EFA sample; n=`r nrow(EFA.descriptives)`), as a part of psychometric analysis.
-Prior to the EFA, the necessary assumptions, including sample adequacy, normality assumptions, quality of correlation matrix were assessed.
-As our data violated both the univariate and multivariate normality assumption and yielded ordinal response data, we used polychoric correlation matrix in the EFA and employed principal axis (PA) as the factor extraction method [@desjardinsHandbookEducationalMeasurement2018; @watkinsStepbyStepGuideExploratory2020].
-We used a combination of factor identification method including Scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and Hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
+**Secondly**, the two rounds of data collection were administered. 
+**Thirdly**, we conducted descriptive and item analysis and proceeded to the exploratory factor analysis (EFA) using the "psych" package [@R-psych] on the data collected in the first round (EFA sample; n=`r nrow(EFA.descriptives)`), as a part of psychometric analysis.
+Prior to the EFA, the necessary assumptions, including sample adequacy, normality assumptions, and quality of correlation matrix, were assessed.
+As our data violated both the univariate and multivariate normality assumption and yielded ordinal response data, we used a polychoric correlation matrix in the EFA and employed "principal axis" (PA) as the factor extraction method [@desjardinsHandbookEducationalMeasurement2018; @watkinsStepbyStepGuideExploratory2020].
+We applied a combination of methods including Scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and Hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
 To determine the latent structure, we followed the common guidelines: (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading \> .3 across factors [@bandalosFactorAnalysisExploratory2018].
@@
 For reliability estimation, the "psych" package was applied [@R-psych].
-Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it has a tendency to deflate the estimates for Likert-type data since the calculation is based on the Pearson-correlation matrix, which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal].
-Subsequently, to get better reliability estimates, we reported ordinal alpha for each factor obtained in the EFA [@zumbo2007ordinal].
+Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it tends to deflate the estimates for Likert-type data since the calculation is based on the Pearson-correlation matrix, which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal].
+Subsequently, we reported ordinal alpha for each factor obtained in the EFA [@zumbo2007ordinal] to get better reliability estimates.
 We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$ coefficient, which was suggested as a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
@@
 We assessed the model fit using common model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI): close to .95 or above/ between .90-.95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner].
-However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015] and SRMR does not work well with ordinal data [@RN1272] As such, we judged the model fit using CFI, TLI and RMSEA.
-
-We assessed the measurement invariance (MI) of our scale between native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non-native English speakers (n=`r invariance.data.descriptives.count[2,2]`) in the CFA sample (n=`r nrow(CFA.descriptives)`).
+However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015], and SRMR does not work well with ordinal data [@RN1272].
+Consequently, we judged the model fit using CFI, TLI and RMSEA.
+
+We then assessed the measurement invariance (MI) of our scale between native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non-native English speakers (n=`r invariance.data.descriptives.count[2,2]`) in the CFA sample (n=`r nrow(CFA.descriptives)`).
 MI evaluates whether a construct has the psychometric equivalence and the same meaning across groups [@putnick2016measurement; @klinePrinciplesPracticeStructural2015].
-We used structural equation modelling framework using "lavaan" package [@R-lavaan] to assess the measurement invariance.
+We used the structural equation modelling framework applying the "lavaan" package [@R-lavaan] to assess the measurement invariance.
 We successively compared four nested models: configural, metric, scalar, and residual models using the $\chi^2$ difference test ($\Delta \chi^2$).
-Among MI models, the configural model is the least restrictive model and residual model is the most restrictive model.
-A non-significant $\Delta \chi^2$ test between two nested measurement invariance models indicates mode fit does not significantly decrease for the superior model thus allowing the superior invariance model to be accepted [@dimitrov2010testing; @widaman1997exploring].
-
-**Fourth**, as secondary analysis we identified the educational grade level required to understand the items in our scale using Flesch-Kincaid grade level identification method [@flesch1948new] using "koRpus" [@R-koRpus] package.
-Also, we analysed possible semantic overlap of our developed scale using ["Semantic Scale Network" (SSN)](https://rosenbusch.shinyapps.io/semantic_net/) engine [@rosenbusch2020semantic].
-The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic].
-Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy.
-
-**Lastly**, we developed a short form of LEBA using Item Response Theory (IRT) based analysis.
-We fitted each factor of LEBA using the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n=`r nrow(sem.data)`) using "mirt" package [@R-mirt].
-IRT assesses the item quality by estimating item discrimination, item difficulty, item information curve, and test information curve [@bakerBasicsItemResponse2017].
+Among MI models, the configural model is the least restrictive and the residual model is the most restrictive.
+A non-significant $\Delta \chi^2$ test between two nested measurement invariance models indicates mode fit does not significantly decrease for the superior model, thus allowing the superior invariance model to be accepted [@dimitrov2010testing; @widaman1997exploring].
+
+**Fourthly**, as secondary analysis, we identified the educational grade level required to understand the items in our scale with the Flesch-Kincaid grade level identification method [@flesch1948new] applying the "koRpus" [@R-koRpus] package.
+Also, we analysed possible semantic overlap of our developed scale using the ["Semantic Scale Network" (SSN)](https://rosenbusch.shinyapps.io/semantic_net/) engine [@rosenbusch2020semantic].
+The SSN detects semantically related scales and provides a cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic].
+Pairs of scales with a cosine similarity index value of 1 inidicate full semantical similarity, suggesting redundancy of the scales.
+
+**Lastly**, we derived a short form of the LEBA employing an Item Response Theory (IRT) based analysis.
+We fitted each factor of the LEBA to the combined EFA and CFA sample (n=`r nrow(sem.data)`) using the graded response model [@samejima1997handbook] via the "mirt" package [@R-mirt].
+IRT assesses the item quality by estimating the item discrimination, item difficulty, item information curve, and test information curve [@bakerBasicsItemResponse2017].
 Item discrimination indicates how well a particular item can differentiate between participants across the given latent trait continuum ($\theta$).
 Item difficulty corresponds to the latent trait level at which the probability of endorsing a particular response option is 50%.
-Item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
-Here, we reported the item difficulty and discrimination parameter and categorize the items based on their item discrimination index: none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70 [@bakerBasicsItemResponse2017].
-We discarded the items with relatively flat item information curve (information \<.2) to develop the short form of LEBA.
-We also assessed the precision of the short LEBA using Test information curve (TIC).
+The item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
+Here, we reported the item difficulty and discrimination parameter and categorize the items based on their item discrimination index: none = 0; very low = 0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70 [@bakerBasicsItemResponse2017].
+We discarded the items with relatively flat item information curve (information \<.2) to derive the short form of LEBA.
+We also assessed the precision of the short LEBA utilizing the Test information curve (TIC).
 TIC indicates the amount of information a particular scale carries along the latent trait continuum.
-Item fit and person fit of the fitted IRT models were also analysed to gather more evidence on validity and meaningfulness of our scale [@desjardinsHandbookEducationalMeasurement2018].
-Item fit was evaluated using the RMSEA value obtained from Signed-$\chi^2$ index implementation, RMSEA value $\le$.06 was considered adequate item fit.
-Person fit was estimated using standardized fit index Zh statistics [@drasgow1985appropriateness].
-Zh \< -2 was considered as a misfit [@drasgow1985appropriateness].
+Additionally, item and person fit of the fitted IRT models were  analysed to gather more evidence on the validity and meaningfulness of our scale [@desjardinsHandbookEducationalMeasurement2018].
+The item fit was evaluated using the RMSEA value obtained from Signed-$\chi^2$ index implementation, an RMSEA value $\le$.06 was considered adequate item fit.
+The person fit was estimated using standardized fit index Zh statistics [@drasgow1985appropriateness].
+Here, Zh \< -2 was considered as a misfit [@drasgow1985appropriateness].
 
@@
 
-By reason of using fully anonymous online survey data, the present research project does not fall under the scope of the Human Research Act, making an authorisation from the ethics committee redundant.
+The current research project utilizes fully anonymous online survey data and therefore does not fall under the scope of the Human Research Act, making an authorisation from the ethics committee redundant.
 Nevertheless, the cantonal ethics commission (Ethikkommission Nordwest- und Zentralschweiz, EKNZ) reviewed our proposition (project ID Req-2021-00488) and issued an official clarification of responsibility.
@@
 
-After reviewing the literature, we identified several light exposure related scales.
+After reviewing the literature, we identified several light exposure-related scales.
 However, no scale specifically measuring the behavioural component of light exposure were found (**Supplementary Table 1**).

### 2022-07-07 manuscript.Rmd
Adjusting phrasing, grammar, and spelling  in the analysis part of the manuscript.

@@
 Here, we reported the item difficulty and discrimination parameter and categorize the items based on their item discrimination index: none = 0; very low = 0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70 [@bakerBasicsItemResponse2017].
-We discarded the items with relatively flat item information curve (information \<.2) to derive the short form of LEBA.
+We discarded the items with a relatively flat item information curve (information \<.2) to derive the short form of LEBA.
 We also assessed the precision of the short LEBA utilizing the Test information curve (TIC).
 TIC indicates the amount of information a particular scale carries along the latent trait continuum.
-Additionally, item and person fit of the fitted IRT models were  analysed to gather more evidence on the validity and meaningfulness of our scale [@desjardinsHandbookEducationalMeasurement2018].
-The item fit was evaluated using the RMSEA value obtained from Signed-$\chi^2$ index implementation, an RMSEA value $\le$.06 was considered adequate item fit.
-The person fit was estimated using standardized fit index Zh statistics [@drasgow1985appropriateness].
+Additionally, the item and person fit of the fitted IRT models were analysed to gather more evidence on the validity and meaningfulness of our scale [@desjardinsHandbookEducationalMeasurement2018].
+The item fit was evaluated using the RMSEA value obtained from Signed-$\chi^2$ index implementation, where an RMSEA value $\le$.06 was considered adequate item fit.
+The person fit was estimated employing the standardized fit index Zh statistics [@drasgow1985appropriateness].
 Here, Zh \< -2 was considered as a misfit [@drasgow1985appropriateness].
@@
 
-After reviewing the literature, we identified several light exposure-related scales.
-However, no scale specifically measuring the behavioural component of light exposure were found (**Supplementary Table 1**).
-As such, an expert panel developed a comprehensive item pool of 48 items.
-The expert panel composed of all authors and researchers from the fields of chronobiology, light research, neuroscience and psychology.
-The 48 items were then judged based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by the expert panel.
-The panel members independently judged each of the items in terms of their relevance and representativeness and suggested required modification, if there is any.
-The author team acknowledged the suggestions and amended the items as required thus creating a 48-item scale.
-
-## Large-scale Survey
+An expert panel comprising all authors -- researchers from chronobiology, light research, neuroscience and psychology -- developed a comprehensive item pool of 48 items.
+The 48 items were then examined based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by each panel member independently and modifications were suggested as required.
+The author team discussed the suggestions and amended the items as indicated, thus creating a 48-item scale.
+
+## Anonymous Online Survey
 
 Table 1 summarises the survey participants' demographic characteristics.
-Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses.
-(XX??) participants were excluded from analysis due to not passing at least one of the "attention check" items.
-For EFA, a sample of 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013].
-To assess sampling adequacy for CFA, we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where ten participants per item is required to earn trustworthiness of the result.
+Only participants completing the full LEBA questionnaire were included.
+Thus, there are no missing values in the item analyses.
+(XXX??) participants were excluded from the analysis due to not passing at least one of the "attention check" items.
+For the EFA, a sample of at least 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013].
+To assess sampling adequacy for CFA, we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where at least ten participants per item are required to earn trustworthiness of the result.
 Both our EFA and CFA sample size exceeded these requirements.
-We collected data from `r nrow(num.countries)` countries (`r nrow(numUTC)` time zones).
-Participants reported a diverse range of geographic location Participants indicated filling out the online survey from a diverse range of geographic locations.
+Participants indicated filling out the online survey from various geographic locations, including `r nrow(num.countries)` countries and `r nrow(numUTC)` time zones.
 For a complete list of geographic locations, see **Supplementary Table 2**.
 
-Participants in our survey aged between `r min(desctable.data$slypos_demographics_age)` to `r max(desctable.data$slypos_demographics_age)` years [EFA sample: `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
-EFA Sample"])` to `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
-EFA Sample"])`; CFA sample: `r min(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])` to `r max(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "2.
-CFA Sample"])`], with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 2)` years of age [Overall: `r mean(desctable.data$slypos_demographics_age)`±`r sd(desctable.data$slypos_demographics_age)`; EFA: `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
+Participants in our survey were aged between `r min(desctable.data$slypos_demographics_age)` to `r max(desctable.data$slypos_demographics_age)` years, with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 2)` years of age [Overall: `r mean(desctable.data$slypos_demographics_age)`±`r sd(desctable.data$slypos_demographics_age)`; EFA: `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
 EFA Sample"])`±`r sd(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
@@
 CFA Sample"])`].
-In total `r desc_tibble[3,2]` of the participants indicated female sex [EFA: `r desc_tibble[3,3]`; CFA: `r desc_tibble[3,4]`], `r desc_tibble[4,2]` indicated male [EFA: `r desc_tibble[4,3]`; CFA: `r desc_tibble[4,4]`] and `r desc_tibble[5,2]` indicated other sex [EFA: `r desc_tibble[5,3]`, CFA: `r desc_tibble[5,4]`].
-Overall, `r desc_tibble[6,2]` [EFA: `r desc_tibble[6,3]`; CFA: `r desc_tibble[6,4]`] participants indicated a gender-variant identity.
+In total `r desc_tibble[3,2]` of the participants indicated female sex, `r desc_tibble[4,2]` indicated male and `r desc_tibble[5,2]` indicated other sex.
+Overall, `r desc_tibble[6,2]` participants indicated a gender-variant identity.
 In a "Yes/No" question regarding native language, `r desc_tibble[7,2]` of respondents [EFA: `r desc_tibble[7,3]`; CFA: `r desc_tibble[7,4]`] indicated to be native English speakers.
-For their "Occupational Status", more than half of the overall sample reported that they currently work [Overall: `r desc_tibble[9,2]`; EFA: `r desc_tibble[9,3]`; CFA: `r desc_tibble[9,4]`], whereas `r desc_tibble[10,2]` [EFA: `r desc_tibble[10,3]`; CFA: `r desc_tibble[10,4]`] reported that they go to school and `r desc_tibble[11,2]` [EFA: `r desc_tibble[11,3]`; CFA: `r desc_tibble[11,4]`] responded that they do "Neither".
-With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` [EFA: `r desc_tibble[13,3]`; CFA: `r desc_tibble[13,4]`] of the participants indicated that they were in a home office/ home schooling setting, while `r desc_tibble[14,2]` overall [EFA: `r desc_tibble[14,3]` ; CFA: `r desc_tibble[14,4]`] reported face-to-face work/schooling.
-Lastly, `r desc_tibble[15,2]` overall [EFA: `r desc_tibble[15,3]` ; CFA: `r desc_tibble[15,4]`] reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]` overall [EFA: `r desc_tibble[16,3]`; CFA: `r desc_tibble[16,4]`] filled in the "Neither (no work or school, or on vacation)" response option.
+For their "Occupational Status", more than half of the overall sample reported that they currently work, whereas `r desc_tibble[10,2]` reported that they go to school and `r desc_tibble[11,2]` responded that they do "Neither".
+With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` of the participants indicated that they were in a home office/ home schooling setting, while `r desc_tibble[14,2]` reported face-to-face work/schooling.
+Lastly, `r desc_tibble[15,2]` overall reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]`  filled in the "Neither (no work or school, or on vacation)" response option.
 
@@
 
-Figure \@ref(fig:efagtPic1) and Figure \@ref(fig:efagtPic2) summarise the response pattern of our total sample (n=`r nrow(sem.data)`) for all 48 items.
+Figure \@ref(fig:efagtPic1) and Figure \@ref(fig:efagtPic2) summarise the response patterns of our total sample (n=`r nrow(sem.data)`) for all 48 items.
 Most of the items appeared skewed.
 The Shapiro–Wilk test of univariate normality [@shapiroAnalysisVarianceTest1965] and Mardia test of multivariate normality [@mardiaMeasuresMultivariateSkewness1970] indicated our data violated both univariate and multivariate normality.
-Multivariate skew was `r printnum(mardia.all.data$b1p)` (p \<0.001) and multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p \<0.001).
+The multivariate skew was `r printnum(mardia.all.data$b1p)` (p \<0.001), and the multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p \<0.001).
 
@@
 **Supplementary Figure 1** summarises the univariate descriptive statistics for the 48 items in the EFA sample (n=`r nrow(EFA.data)`).
-Here also our data violated univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970].
-Multivariate skew was `r printnum(mardia$b1p)` (p \<0.001) and multivariate kurtosis was `r printnum(mardia$b2p)` (p \<0.001).
-The corrected item-total correlation ranges between `r apa(low.r.corec,2,F)` -`r apa(high.r.corec,2,F)`.
+Likewise, our data violated the univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970].
+The multivariate skew was `r printnum(mardia$b1p)` (p \<0.001) and the multivariate kurtosis yielded a value of `r printnum(mardia$b2p)` (p \<0.001).
+The corrected item-total correlation ranged between `r apa(low.r.corec,2,F)` -`r apa(high.r.corec,2,F)`.
 However, no item was discarded based on descriptive statistics or item analysis.
@@
 
-Sampling adequacy was checked using Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy using the EFA sample (n=`r nrow(EFA.data)`) [@kaiserIndexFactorialSimplicity1974] .
-The overall KMO vale for 48 items was `r printnum(KMO$MSA)` which was above the cut-off value (.50) indicating adequate sample size [@hutchesonMultivariateSocialScientist1999].
-Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`)=`r apa(bartlet$chisq, 2, T)`, p \< .001 indicated the correlations between items are adequate for conducting the EFA.
-However only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than \|.30\|.
-The inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`.
-Figure \@ref(fig:efa-plot-print)-A depicts the correlation matrix.
+We checked the sampling adequacy by applying Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy on the EFA sample (n=`r nrow(EFA.data)`) [@kaiserIndexFactorialSimplicity1974].
+The overall KMO value for 48 items was `r printnum(KMO$MSA)`, which exceeded the cut-off value (.50), indicating an adequate sample size [@hutchesonMultivariateSocialScientist1999].
+Additionally, Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`)=`r apa(bartlet$chisq, 2, T)`, p \< .001 implied that the correlations between items were adequate for conducting the EFA.
+However, only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than \|.30\|., and the inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`.
+Figure \@ref(fig:efa-plot-print)-A depicts the respective correlation matrix.
 
@@
 
-Scree plot ( Figure \@ref(fig:efa-plot-print)-B) suggested a six-factor solution.
-However, the minimum average partial (MAP) [@velicerDeterminingNumberComponents1976] method (**Supplementary Table 3**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print)-C) suggested a five-factor solution.
+Inspection via the Scree plot ( Figure \@ref(fig:efa-plot-print)-B) suggested a six-factor solution, whereas the minimum average partial (MAP) method [@velicerDeterminingNumberComponents1976] (**Supplementary Table 3**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print)-C) implied a five-factor solution for the LEBA questionnaire.
 As a result, we tested both five-factor and six-factor solutions.
@@
 'x' denotes non-significant item-total correlation.
-(B) Scree plot suggested six factors.
-(C) Hull method indicated 5 factors were required to balance the model fit and number of parameters.
-(D) Histogram of nonredundent residual correlations indicated 26% of inter-item correlations were higher than .05, hinting a possible under factoring.
+(B) The Scree plot suggested six factors.
+(C) Hull method indicated that five factors were required to balance the model fit and number of parameters.
+(D) The histogram of nonredundant residual correlations indicated that 26% of inter-item correlations were higher than .05, hinting at a possible under-factoring.
 
@@
 
-With the initial 48 items we conducted three rounds of EFA with varimax rotation and gradually discarded problematic items (cross-loading items and items with factor loading \<.30).
+Applying varimax rotation, we conducted three rounds of EFA with the initial 48 items and gradually discarded problematic items (cross-loading items and items with factor loading \<.30).
 Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30.
 Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items.
-The absolute value of the factor-loading ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients.
-The commonalities ranged between `r apa(min.com,2,F)` to `r apa(max.com, 2, F)`.
-However, the histogram of the absolute values of non-redundant residual-correlations (Figure \@ref(fig:efa-plot-print)-D) showed `r apa(sumR,0, T)`% correlations were greater than the absolute value of .05, indicating a possible under-factoring.
+The absolute values of the factor-loadings ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients.
+The commonalities ranged between `r apa(min.com,2,F)` and `r apa(max.com, 2, F)`.
+However, the histogram of the absolute values of nonredundant residual correlations (Figure \@ref(fig:efa-plot-print)-D) displayed that `r apa(sumR,0, T)`% of correlations were greater than the absolute value of .05, indicating a possible under-factoring.
 [@desjardinsHandbookEducationalMeasurement2018].
-Subsequently, we fitted a six-factor solution.
-However, a factor emerged with only two salient variables, thus disqualifying the six-factor solution (**Supplementary Table 4**).
+Subsequently, we fitted a six-factor solution, wherefrom a factor with only two salient variables emerged, thus disqualifying the six-factor solution (**Supplementary Table 4**).
 
 In the five-factor solution, the first factor contained three items and explained `r apa(var1,2,F)`% of the total variance with an internal reliability coefficient ordinal $\alpha$ = `r apa(F1.alpha,2,F)`.
-All the items in this factor stemmed from the individual's preference of using blue light filters in different light environments.
+All the items in this factor encapsulated the individual's preference for using blue light filters in different light environments.
 The second factor contained six items and explained `r apa(var2,2,F)`% of the total variance with an internal reliability coefficient ordinal $\alpha$ = `r apa(F2.alpha,2,F)`.
-Items under this factor investigated individuals' hours spent outdoor.
+Items under this factor incorporated the individuals' hours spent outdoor.
 The third factor contained five items and explained `r apa(var3,2,F)`% of the total variance.
-Items under this factor dealt with the specific behaviours pertaining to using phone and smart-watch in bed.
-The internal consistency reliability coefficient was, ordinal $\alpha$ = `r apa(F3.alpha,2,F)`.
-The fourth factor contained five items and explained `r apa(var4,2,F)`% of the total variance with an internal consistency coefficient, ordinal $\alpha$ = `r apa(F4.alpha,2,F)`.
-These five items investigated the behaviours related to individual's light exposure before bedtime.
-Lastly, the fifth factor contained six items and explained `r apa(var5,2,F)`% of the total variance.
-This factor captured individual's morning and daytime light exposure related behaviour.
-The internal consistency reliability was, ordinal $\alpha$ = `r apa(F5.alpha,2,F)`.
-It is essential to attain a balance between psychometric properties and interpretability of the common themes when exploring the latent structure.
-As all of the emerged factors are highly interpretable and relevant towards our aim to capture light exposure related behaviour, regardless of the apparent low reliability of the fifth factor, we retain all the five-factors with 25 items for our confirmatory factor analysis (CFA).
-Two items showed negative factor-loading (items 44 and 21).
-Upon inspection, it was understood that these items are negatively correlated to the respective common theme, and thus in the CFA analysis, we reverse scored these two items.
-Internal consistency coefficient McDonald's $\omega_t$ for the total scale was `r apa(omega$omega.tot,2,T)`.
+Items under this factor covered the specific behaviours of using a phone and smart-watch in bed.
+The internal consistency reliability coefficient was ordinal $\alpha$ = `r apa(F3.alpha,2,F)`.
+The fourth factor comprised five items and explained `r apa(var4,2,F)`% of the total variance with an internal consistency coefficient, ordinal $\alpha$ = `r apa(F4.alpha,2,F)`.
+These five items investigated the behaviours related to the individual's light exposure before bedtime.
+The fifth factor encompassed six items and explained `r apa(var5,2,F)`% of the total variance.
+This factor captured the individual's morning and daytime light exposure-related behaviour.
+The internal consistency reliability yielded ordinal $\alpha$ = `r apa(F5.alpha,2,F)`.
+
+Finally, we examined the factor's interpretability in the five-factor solution and weighed it against the psychometric properties as we considered it essential to attain a balance between the two.
+As we deemed the five derived factors interpretable and relevant concerning our aim to capture light exposure-related behaviour, we retained all of them with 25 items for our confirmatory factor analysis (CFA), despite the apparent low reliability of the fifth factor.
+Two of the items showed negative factor-loading (items 44 and 21).
+Upon re-inspection, we recognized these items to be negatively correlated to the respective factor, and thus, we reverse-scored these two items in the CFA analysis.
+The internal consistency coefficient McDonald's $\omega_t$ for the total scale was `r apa(omega$omega.tot,2,T)`.
 
@@
 
-Table \@ref(tab:tabCfa) summarises the CFA fit indices of our fitted model.
-Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`; RMSEA = `r apa(fit.1[7],2,F)` [`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 [item 32: I dim my mobile phone screen within 1 hour before attempting to fall asleep; item 33: I dim my computer screen within 1 hour before attempting to fall asleep] and 16-17 [item 16: I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day; item 17: I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day].
-Item pair 32-33 stemmed from the preference of dimming electric device's brightness before bed time and item pair 16-17 stemmed from the preference of using blue filtering or coloured glasses during the daytime.
-Given the similar nature of behaviour these item pair were capturing, we accepted the equity constrain imposed.
-Nevertheless, SRMR value was higher than the guideline (SRMR = `r apa(fit.1[10],2,F)`).
-
-To improve model fit we conducted a post-hoc model modification. Modification indices indicated the possibility of cross-loading of the item 37 and 26 [item 37: I purposely leave
-a light on in my sleep environment while sleeping; item 26: I turn on my ceiling room light when it
-is light outside] thus discarded.
-Also, item 30 and 41 [item 30: I look at my smart-watch within 1 hour before attempting to fall asleep; item 41: I look at my smart-watch when I wake up at night] showed a tendency to co-vary in their error variance (MI = 141.127, p<.001 ).
-By allowing this pair of items (30 $\&$ 41)  to covary their error variance our model attained the best fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR = `r apa(fit.2[10],2,F) `).
-Internal consistency ordinal $\alpha$ for the five factors of LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)` respectively.
-As such, we accept this model thus finalizing the long Form of LEBA with 23 items.
-The items are provided in the **Supplementary File 1**.
-Internal consistency McDonald's $\omega_t$ coefficient for the total scale was `r apa(rel.k[5,6],2,F)`.
-Figure \@ref(fig:figcfa) depicts the obtained CFA structure.
-**Supplementary Figure 2** depicts the data distribution and endorsement pattern of the retained 23 items in our CFA sample.
+Table \@ref(tab:tabCfa) compares the CFA fit indices of the original CFA five-factor model with 25 and the post-hoc modified model with 23 items, respectively.
+The 25-item model attained an acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`; RMSEA = `r apa(fit.1[7],2,F)` [`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constraints on item pairs 32-33 [item 32: I dim my mobile phone screen within 1 hour before attempting to fall asleep; item 33: I dim my computer screen within 1 hour before attempting to fall asleep] and 16-17 [item 16: I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day; item 17: I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day].
+Item pair 32-33 describes the preference for dimming the electric devices' brightness before bedtime, whereas item pair 16-17 represents the preference for using blue filtering or coloured glasses during the daytime.
+Given the similar nature of captured behaviours within each item pair, we accepted the imposed equity constraints.
+Nevertheless, the SRMR value exceeded the guideline recommendation (SRMR = `r apa(fit.1[10],2,F)`).
+
+In order to improve the model fit, we conducted a post-hoc model modification.
+Firstly, the  modification indices suggested cross-loadings between item 37 and 26 [item 37: I purposely leave a light on in my sleep environment while sleeping; item 26: I turn on my ceiling room light when it is light outside], which were hence discarded.
+Secondly, items 30 and 41 [item 30: I look at my smart-watch within 1 hour before attempting to fall asleep; item 41: I look at my smart-watch when I wake up at night] showed a tendency to co-vary in their error variance (MI = 141.127, p<.001 ).
+By allowing the latter pair of items (30 $\&$ 41) to co-vary, the model's error variance attained an improved fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR = `r apa(fit.2[10],2,F) `).
+Internal consistency ordinal $\alpha$ for the five factors of the LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`, respectively.
+
+Accordingly, we accept the 5-factor model with 23 items, finalizing the long Form of LEBA (see **Supplementary File 1**).
+The Internal consistency McDonald's $\omega_t$ coefficient for the total scale yielded `r apa(rel.k[5,6],2,F)`.
+Figure \@ref(fig:figcfa) depicts the obtained CFA structure, while  **Supplementary Figure 2** depicts the data distribution and endorsement pattern of the retained 23 items in our CFA sample.
 
@@
 ```{r figcfa, fig.cap = "Five factor  model of LEBA obtained by confirmatory factor analysis.
-By allowing item pair 41 and 30 to covary their error variance our model attained the best fit.",  out.height='100%',out.width='100%', warning=FALSE}
+By allowing item pair 41 and 30 to co-vary their error variance our model attained the best fit.",  out.height='100%',out.width='100%', warning=FALSE}
 
@@
 
-In our CFA sample we had `r mi.count[1,2]` native English speakers and `r mi.count[2,2]` non-native English speakers.
-**Supplementary Table 5** summarises the demographic descriptions native and non-native English speakers.
-Table \@ref(tab:InvarianceTab) indicates our fitted model had acceptable fit indices for all of the fitted MI models.
-The model fit did not significantly decrease across the nested models indicating the acceptability of the highest measurement invariance model: residual model.
+Our CFA sample consisted of `r mi.count[1,2]` native English speakers and `r mi.count[2,2]` non-native English speakers, whose demographic data are contrasted in **Supplementary Table 5**.
+As shown in Table \@ref(tab:InvarianceTab), the employed five-factor model generated acceptable fit indices over all of the fitted MI models.
+The model fit did not significantly decrease across the nested models implying the acceptability of the highest measurement invariance model (residual model).
 
@@
 ## Secondary Analysis: Grade Level Identification and Semantic Scale Network Analysis
-Flesch-Kincaid grade level [@flesch1948new] analysis on the 23 items indicated required educational grade level was 3.33 and with a age above 8.33 years.
-This indicated our scale will be understandable to students of grade four and aged at least 8.33 years.
-Semantic Scale Network (SSN) analysis [@rosenbusch2020semantic] indicated that LEBA (23 items) appeared most strongly related to scales about sleep: "Sleep Disturbance Scale For Children" [@bruni1996sleep] and "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite].
-The cosine similarities lie between .47 to .51.
+A grade level identification and Semantic Scale analysis were additionally administered to assess the LEBA's (23 items) language-based accessibility and its' semantic relation to other questionnaires.
+The results of the Flesch-Kincaid grade level analysis [@flesch1948new] displayed a required educational grade level of 3.33 with age above 8.33 years, implying that the LEBA instrument should be understandable for students of grade four at least 8.33 years old.
+Furthermore, the
+Semantic Scale Network (SSN) analysis [@rosenbusch2020semantic] indicated that the LEBA appeared most strongly related to scales about sleep: The "Sleep Disturbance Scale For Children" [@bruni1996sleep] and the "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite].
+The cosine similarity yielded values between .47 to .51.
 
@@
 
-## Developing Short form of LEBA: IRT Based Analysis
-We fitted each factor of LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n=690).
-Item discrimination parameters of our scale fell in very high (10 items), high (4 items), moderate (4 items), and low ( 5 items) categorizes indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**).
-Examination of the item information curve (**Supplementary Figure 3**) indicated five items (1, 25, 30, 38, & 41) had relatively flat information curves (I($\theta$) \<.20).
-We discarded those items which yielded a short form of LEBA with five factors and 18 items (**Supplementary File 2**).
+## Developing Short form of LEBA: IRT-Based Analysis
+In order to derive a short form of the LEBA instrument, we fitted each factor of the LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n=690).
+The resulting item discrimination parameters of the scale fell into categories of "very high" (10 items), "high" (4 items), "moderate" (4 items), and "low" ( 5 items), indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**).
+An examination of the item information curve (**Supplementary Figure 3**) revealed five items (1, 25, 30, 38, & 41) with relatively flat curves (I($\theta$) \<.20).
+We discarded those items, culminating in a short form of LEBA with five factors and 18 items (**Supplementary File 2**).
 
@@
 
-```{r Testinfo, fig.env = "sidewaysfigure", fig.cap="Test information curves for the five factors of LEBA: (a) wearing blue light filters (b) spending time outdoors (c) using phone and smart-watch in bed (d) using light before bedtime (e) using light in the morning and during daytime.
-Along x-axis we plotted the underlying latent trait continuum for each factor.
-Along y-axis we plotted how much information a particular factor is caring across its latent trait continuum", warning=FALSE, out.width="100%", out.height="120%"}
+```{r Testinfo, fig.env = "sidewaysfigure", fig.cap="Test information curves for the five factors of LEBA: (a) wearing blue light filters (b) spending time outdoors (c) using a phone and smart-watch in bed (d) using light before bedtime (e) using light in the morning and during daytime.
+Along the x-axis, we plotted the underlying latent trait continuum for each factor.
+Along the y-axis, we plotted how much information a particular factor is carrying across its latent trait continuum", warning=FALSE, out.width="100%", out.height="120%"}
 
@@
 
-We treated each factor of short-LEBA as a unidimensional construct and obtain five TICs (Figure \@ref(fig:Testinfo)).
-These information curves indicated except the first and fifth factors, the other three factor's TICs are roughly centred on the centre of the trait continuum ($\theta$).
-The first and fifth factor had a peak to the right side of the centre of latent trait.
-Thus we conferred the LEBA scale estimated the light exposure related behaviour with precision near the centre of trait continuum for second, third and fourth factors and near the right side of the centre of trait continuum for first and fifth factors [@bakerBasicsItemResponse2017].
-
-**Supplementary Table 7** summarises the item fit indexes of the 18 items.
-All items had RMSEA value $\le$.06 indicating adequate fit of the items to the fitted IRT model.
-**Supplementary Figure 4** depicts the person fit Zh statistics histogram of our fitted models.
-Zh statistics are larger than -2 for most participants, suggesting a good person fit of the selected IRT models.
+Subsequently, we treated each factor of the short-LEBA as a unidimensional construct and obtained five test information curves (TICs).
+As (Figure \@ref(fig:Testinfo)).
+illustrates, the TICs of the first and fifth factors peaked on the right side of the centre of their latent traits, while the TICs of the other three factors were roughly centred on the respective trait continuum ($\theta$).
+This points out that the LEBA short-scale estimates the light exposure-related behaviour most precisely near the centre of the trait continuum for the second, third and fourth factors and, in contrast, to the right of the centre for the first and fifth factors [@bakerBasicsItemResponse2017].
+
+Finally, **Supplementary Table 7** summarises the item fit indexes of the LEBA short form.
+All 18 items yielded RMSEA value $\le$.06, indicating adequate fit to the fitted IRT model.
+Furthermore, **Supplementary Figure 4** depicts the person fit Zh statistics histogram for the five IRT models.
+Zh statistics are larger than -2 for most participants, suggesting a good person fit regarding the selected IRT models.
 

### 2022-07-10 manuscript.Rmd
Editing the first half of the #discussion

@@
 abstract: |
-  Light exposure is an important driver of health and well-being.
-Many aspects of light exposure are modulated by our behaviour.
-How these light-related behaviours can be shaped to optimise personal light exposure is currently unknown.
+  Light exposure is an essential driver of health and well-being.
+Our behaviour modulates many aspects of light exposure, but how these light-related behaviours can be shaped to optimise personal light exposure is currently unknown.
 Here, we present a novel, self-reported and psychometrically validated instrument to capture light exposure-related behaviour, the Light Exposure Behaviour Assessment (LEBA).
 
-  An expert panel prepared the initial 48 item pool spanning different light exposure related behaviours.
-Responses, consisting rating the frequency of engaging in the per-item behaviour on a 5-point Likert type scale were  collected in an online survey yielding responses from a geographically unconstrained sample (690 completed responses, 74 countries, 28 time zones).
-Exploratory factor analysis (EFA) on an initial subset of our sample (n=428) rendered a five-factor solution with 25 items (Wearing blue light filters, spending time outdoors, using phone and smart-watch in bed, using light before bedtime, using light in the morning and during daytime).
-In a confirmatory factor analysis (CFA) performed on an independent subset of participants (n=262), we removed two further items to attain the best fit for the five-factor solution (CFI=0.95, TLI=0.95, RMSEA=0.06).
-The internal consistency reliability coefficient for the total instrument was, McDonald’s Omega(total)=0.68.
-Measurement model invariance analysis between native and non-native English speakers showed our model attained the highest level of invariance (residual invariance; CFI=0.95, TLI=0.95, RMSEA=0.05).
-Lastly, a short form of LEBA (n=18) was developed using Item Response Theory on the complete sample (n=690).
+  An expert panel prepared the initial 48-item pool spanning different light exposure-related behaviours.
+Responses, consisting of rating the frequency of engaging in the per-item behaviour on a 5-point Likert type scale, were collected in an online survey yielding responses from a geographically unconstrained sample (690 completed responses, 74 countries, 28 time zones).
+The exploratory factor analysis (EFA) on an initial subsample (n=428) rendered a five-factor solution with 25 items (Wearing blue light filters, spending time outdoors, using a phone and smartwatch in bed, using light before bedtime, using light in the morning and during daytime).
+In a confirmatory factor analysis (CFA) performed on an independent subset of participants (n=262), we removed two additional items to attain the best fit for the five-factor solution (CFI=0.95, TLI=0.95, RMSEA=0.06).
+The internal consistency reliability coefficient for the total instrument yielded McDonald’s Omega(total)=0.68.
+Measurement model invariance analysis between native and non-native English speakers showed our model attained the highest level of invariance (residual invariance; CFI=0.95, TLI=0.95, RMSEA=0.05).
+Lastly, a short form of the LEBA (n=18) was developed using Item Response Theory on the complete sample (n=690).
 
@@
 For example, the “Munich Chronotype  Questionnaire” [MCTQ; @roenneberg2003life], a popular self-report tool for identifying chronotypes via mid-sleep times, includes questions about the individual’s time spent outdoors on workdays and free days.
+The Visual Light Sensitivity Questionnaire-8 [@verriotto2017new] and Photosensitivity Assessment Questionnaire (PAQ; @bossini2006sensibilita), a couple of self-report tools measuring visual light sensitivity, contain single items which probe the preference for specific light situations: "In the past month, how often did you need to wear dark glasses on cloudy days or indoors?" [@verriotto2017new]; "I prefer rooms that are in semi-darkness."; [@bossini2006sensibilita].
 In addition, the “Pittsburgh Sleep Quality Index” [PSQI; @buysse1989pittsburgh], a popular measure of sleep quality, contains questions about sleep and wake-up times, which are relevant to the light exposure around bedtime.
@@
 The demographic characteristics of our sample are given in **Table 1**.
-Participants were asked to confirm that they participated in the survey for the first time.
+Participants were further asked to confirm that they participated in the survey for the first time.
 Additionally, five attention check items (e.g., "We want to make sure you are paying attention.
@@
 
-Figure \@ref(fig:FlowchartFig) summarises the steps we followed while developing LEBA. We conducted all analyses with the statistical software environment R [@R-base]. 
+Figure \@ref(fig:FlowchartFig) summarises the steps we followed while developing the LEBA. We conducted all analyses with the statistical software environment R [@R-base]. 
 **Firstly**, we set an item pool of 48 items with a six-point Likert-type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial scale.
@@
 As our data violated both the univariate and multivariate normality assumption and yielded ordinal response data, we used a polychoric correlation matrix in the EFA and employed "principal axis" (PA) as the factor extraction method [@desjardinsHandbookEducationalMeasurement2018; @watkinsStepbyStepGuideExploratory2020].
-We applied a combination of methods including Scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and Hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
+We applied a combination of methods including a Scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and Hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
 To determine the latent structure, we followed the common guidelines: (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading \> .3 across factors [@bandalosFactorAnalysisExploratory2018].
@@
 **Fourthly**, as secondary analysis, we identified the educational grade level required to understand the items in our scale with the Flesch-Kincaid grade level identification method [@flesch1948new] applying the "koRpus" [@R-koRpus] package.
-Also, we analysed possible semantic overlap of our developed scale using the ["Semantic Scale Network" (SSN)](https://rosenbusch.shinyapps.io/semantic_net/) engine [@rosenbusch2020semantic].
+Correspondingly, we analysed possible semantic overlap of our developed scale using the ["Semantic Scale Network" (SSN)](https://rosenbusch.shinyapps.io/semantic_net/) engine [@rosenbusch2020semantic].
 The SSN detects semantically related scales and provides a cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic].
@@
   # tab_row_group(
-  #     label = md("**F3: Using phone and smart-watch in bed**"),
+  #     label = md("**F3: Using phone and smartwatch in bed**"),
   #     rows = c(2,14,15,22,23) 
@@
 The third factor contained five items and explained `r apa(var3,2,F)`% of the total variance.
-Items under this factor covered the specific behaviours of using a phone and smart-watch in bed.
+Items under this factor covered the specific behaviours of using a phone and smartwatch in bed.
 The internal consistency reliability coefficient was ordinal $\alpha$ = `r apa(F3.alpha,2,F)`.
@@
   tab_row_group(
-      label = md("**F3: Using phone and smart-watch in bed**"),
+      label = md("**F3: Using phone and smartwatch in bed**"),
       rows = c(2,13,14,20,21) 
@@
 Firstly, the  modification indices suggested cross-loadings between item 37 and 26 [item 37: I purposely leave a light on in my sleep environment while sleeping; item 26: I turn on my ceiling room light when it is light outside], which were hence discarded.
-Secondly, items 30 and 41 [item 30: I look at my smart-watch within 1 hour before attempting to fall asleep; item 41: I look at my smart-watch when I wake up at night] showed a tendency to co-vary in their error variance (MI = 141.127, p<.001 ).
+Secondly, items 30 and 41 [item 30: I look at my smartwatch within 1 hour before attempting to fall asleep; item 41: I look at my smartwatch when I wake up at night] showed a tendency to co-vary in their error variance (MI = 141.127, p<.001 ).
 By allowing the latter pair of items (30 $\&$ 41) to co-vary, the model's error variance attained an improved fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR = `r apa(fit.2[10],2,F) `).
@@
 ## F3 Plots ####
-F3_OCC <-plot(F3_fit, type = "trace", facet =T, main = "F3: Using phone and smart-watch in bed OCC")
-F3_info <- plot(F3_fit, type = "infoSE", main = "F3: Using phone and smart-watch in bed")
+F3_OCC <-plot(F3_fit, type = "trace", facet =T, main = "F3: Using phone and smartwatch in bed OCC")
+F3_info <- plot(F3_fit, type = "infoSE", main = "F3: Using phone and smartwatch in bed")
 F3_iteminfo <- plot(F3_fit, type = "infotrace", 
-                    facet_items = T, main = "F3: Using phone and smart-watch in bed")
+                    facet_items = T, main = "F3: Using phone and smartwatch in bed")
 
@@
 
-#F3_test.info.redu <- plot(F3_fit.redu, type = "infoSE", main = "F3: Using phone and smart-watch in bed")
+#F3_test.info.redu <- plot(F3_fit.redu, type = "infoSE", main = "F3: Using phone and smartwatch in bed")
 
@@
   geom_line()+apatheme+
-  labs(y="Test Information", title = "F3: Using phone and smart-watch in bed")+ylim(0,8)+
+  labs(y="Test Information", title = "F3: Using phone and smartwatch in bed")+ylim(0,8)+
   geom_area()+aes(fill =  "#00A08799")+theme(legend.position = "none")+
@@
 
-```{r Testinfo, fig.env = "sidewaysfigure", fig.cap="Test information curves for the five factors of LEBA: (a) wearing blue light filters (b) spending time outdoors (c) using a phone and smart-watch in bed (d) using light before bedtime (e) using light in the morning and during daytime.
+```{r Testinfo, fig.env = "sidewaysfigure", fig.cap="Test information curves for the five factors of LEBA: (a) wearing blue light filters (b) spending time outdoors (c) using a phone and smartwatch in bed (d) using light before bedtime (e) using light in the morning and during daytime.
 Along the x-axis, we plotted the underlying latent trait continuum for each factor.
@@
 
-Though there are lots of validated scale to measure light exposure, they don't tell us much about the behavioural aspects pertaining to the light exposure.
-In that vein we have developed a subjective self-reported scale that can capture light exposure related behaviour in different dimensions.
-
-Authors along with an expert panel generated 48 items and evaluated their quality and relevance and made necessary amendments.
-A large-scale geographically unconstrained quantitative cross-sectional survey was conducted yielding responses from a large sample (n=`r nrow(data)`).
-Data collected on the first round was used to explore the latent structure (EFA sample; n=`r nrow(EFA.descriptives)`).
+Since electrical light use was globally established, people's received light exposure is not only regulated by the natural light-dark cycle but ultimately determined by their light-related behaviour, i.e.
+people receive different light intensities at different times depending on their light-related habits.
+In reviewing the literature, we found that a handful of previously introduced instruments assess aspects of light exposure by self-report (see **Supplementary Table 1**).
+Even fewer assessment tools have yet partially probed behavioural aspects of received light like the estimated time spent outside [MCTQ; @roenneberg2003life] or the preference for specific light situations (e.g.
+"I prefer rooms that are in semi-darkness."; PAQ @bossini2006sensibilita).
+However, none of these questionnaires systematically and thoroughly captures behaviours that modify light exposure across different lighting scenarios.
+Aiming to fill this gap, we have developed a self-report scale that can capture light exposure-related behaviour in multiple dimensions.
+
+The 48 initially generated items were first applied in a geographically unconstrained quantitative cross-sectional survey, yielding responses from a large international sample (n=`r nrow(data)`).
+
+Data collected in the first round was used to explore the latent structure (EFA sample; n=`r nrow(EFA.descriptives)`).
 Exploratory factor analysis revealed a five factor solution with 25 items.
-("Wearing blue light filters", "Spending time outdoors", "Using phone and smart-watch in bed", "Using light before bedtime", and "Using light in the morning and during daytime").
+("Wearing blue light filters", "Spending time outdoors", "Using phone and smartwatch in bed", "Using light before bedtime", and "Using light in the morning and during daytime").
 The internal consistency reliability coefficient ordinal alpha ranged between `r apa(min(alpha.tab),2,F)`-`r apa(max(alpha.tab),2,F)`.
@@
 
-Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five factor structure we obtained in our EFA thus provided evidence of structural validity.(CFI=`r apa(fit.2[5],2,F)`; TLI=`r apa(fit.2[6],2,F)`; RMSEA=`r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR=`r apa(fit.2[10],2,F) `).
+Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five-factor structure we obtained in our EFA, thus providing evidence for structural validity.(CFI=`r apa(fit.2[5],2,F)`; TLI=`r apa(fit.2[6],2,F)`; RMSEA=`r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR=`r apa(fit.2[10],2,F) `).
 However, in this model, we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings.
-Also, we accepted one pair of items (item 30 $\&$ 41) to covary their error variance .
-This item-pair was capturing smart-watch based light exposure behaviour.
-In retrospect, it seemed plausible that not having  a smart-watch may lead the respondent to answer in a similar fashion for these two items.
-Thus, we decided to accept the modification to our model.
-The internal consistency coefficients ordinal alpha for the five factors and the total scale were also satisfactory (Ordinal alpha ranged between `r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$=`r apa(rel.k[5,6],2,F)`).
-On this same data set our measurement invariance analysis indicated the underlying construct of our scale "Light exposure related behaviour" was equivalent across native and non-native English speakers.
-This indicated the applicability of LEBA on both native and non-native English Speakers.
-However, this decisions brought up another question to be answered, what was the required grade level to understand the items of our scale?
-To answer this question we ran secondary analysis where we identified the grade level required using Flesch-Kincaid grade level identification method.
-Our scale would appear understandable to those who were at least a grade four student and had a age of at least 8.33 years.
-As a secondary analysis we also assessed the semantic similarity of our scale to the scales recorded in the "Semantic Scale Network" database [@rosenbusch2020semantic].
-"LEBA" was  related to  "Sleep Disturbance Scale For Children" (SDSC) [@bruni1996sleep] and "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite].
-Upon inspecting the item contents we found items under "Using phone and smart-watch in bed" and "Using light before bedtime" have semantic overlap with the items of SDSC and CIDI.
-However, the aim of those scale and ours were different.
-Items in those two scales were looking into behaviours related to sleep whereas our aim was to capture light exposure related behaviour.
-
-lastly, we developed a short-LEBA (18 items) using IRT analysis.
-We fitted a graded response model to the combined EFA and CFA sample (n=`r nrow(data)`).
-We discarded five items (1, 25, 30, 38, & 41) with relatively flat item information curve [I($\theta$) <.20].
-Test information curves indicated short form of LEBA is a psychometrically sound measure with adequate coverage of underlying traits to capture different extents of light exposure related behaviours with precision.
-Item fit index and person fit index for all five fitted model were acceptable providing evidence of validity of our models.
-Items had diverse item discrimination parameters indicating a good range of discrimination- the ability to differentiate respondents with different levels of the light exposure related behaviour.
+Additionally, we allowed the error variance of one pair of items (item 30 $\&$ 41) capturing smartwatch-based light exposure behaviour to covary.
+In retrospect, it seemed plausible that many respondents were not using a smartwatch at all, resulting in them answering similarly for these two items.
+The internal consistency coefficients ordinal alpha for the five factors and the total scale were again satisfactory (Ordinal alpha ranged between `r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$=`r apa(rel.k[5,6],2,F)`).
+
+The results of the measurement invariance analysis indicate that the construct "Light exposure-related behaviour" is equivalent across native and non-native English speakers and thus suitable for assessment in both groups.
+Furthermore, according to the grade level identification method, the LEBA appears understandable for students at least 8.33 years of age visiting grade four or higher.
+Interestingly, the semantic similarity analysis ("Semantic Scale Network" database @rosenbusch2020semantic) revealed that the "LEBA" is semantically related to the "Sleep Disturbance Scale For Children" (SDSC) [@bruni1996sleep] and the "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite].
+Upon inspecting the questionnaire contents, we found that some items in the factors "Using phone and smartwatch in bed" and "Using light before bedtime" have semantic overlap with the SDSC’s and CIDI’s items.
+However, while the CIDI and the SDSC capture clinically relevant sleep problems and related activities, the LEBA aims to assess light-exposure-related behaviour.
+Since light exposure at night has been shown to disturb sleep [@Brown.2022; @santhi_applications_2020], this overlap is consistent with our aim to measure physiologically relevant light-related activites.
+Nevertheless, the general objectives between the complete questionnaires differ evidently.
+
+Lastly, we derived a short version of the LEBA (18 items) using IRT analysis.
+We fitted a graded response model to the combined EFA and CFA sample (n=`r nrow(data)`) and discarded five items (1, 25, 30, 38, & 41) with relatively flat item information curve [I($\theta$) <.20].
+The resulting test information curves suggest that the short-LEBA is a psychometrically sound measure with adequate coverage of underlying traits and can be applied to capture different extents of light exposure-related behaviours reliably.
+
+Findings from the Item and person fit index analysis demonstrate that all five fitted models were acceptable and provide evidence of validity for the factors.
+In addition, the diverse item discrimination parameters indicate an appropriate range of discrimination -- the ability to differentiate respondents with different levels of light exposure-related behaviour.
 

### 2022-07-17 manuscript.Rmd
Updates on suppl.materials

--- 2022-07-06 manuscript.Rmd
@@
 
-Light exposure received by the eyes affects many facets of human health, well-being, and performance beyond visual sensation and perception [@boyce_light_2022].
-The so-called non-image-forming (NIF) effects of light comprise light’s circadian and non-circadian influence on several physiological and psychological functions, such as the secretion of melatonin, sleep, mood, pupil size, body temperature, alertness, and higher cognitive functions [i.a.
-reviewed in @Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020 ].
-With the introduction of artificial electric light, human behaviour has become somewhat independent of the natural light-dark cycle – people can now frequently choose when to be exposed to light or darkness.
-For example, they can decide whether to go outdoors and seek out sunlight, switch on/off light-emitting devices, use certain types of lights at home, or avoid specific light environments altogether.
-Additionally, when light sources can not be directly manipulated, sought out, or avoided (for example, at school, work, or in public places), there is still potential leeway to influence them behaviourally, for instance, by wearing sunglasses, directing one’s gaze away or supplementing the situation with additional light sources.
-Although clearly yielding the potential for good, this agency is further associated with increased electric light exposure at night and indoor time during the day, compromising the natural temporal organisation of the light-dark cycle.
-For example, in the US, an average of 87% of the time is spent in enclosed buildings [@Klepeis.2001], and more than 80% of the population is exposed to a night sky that is brighter than nights with a full moon due to electric light at night [@navara_dark_2007].
-An extensive body of scientific evidence suggests that the imbalance of light and dark exposure disrupts humans’ light-dependent physiological systems [@Lunn.2017].
-This, in turn, gives rise to a series of adverse health consequences, including the alteration of several hormonal rhythms, increased cancer rates, cardiovascular diseases, and metabolic disorders, such as obesity, and type II diabetes [see reviews by @Lunn.2017; @navara2007dark; @Chellappa.2019]
-These findings have sparked a significant call for assessment and guidance regarding healthy light exposure and timing – the latter was recently published as consensus-based experts’ recommendations, postulating specific requirements for indoor light environments during the daytime, evening, and nighttime [@Brown.2022].
-Furthermore, building on earlier attempts [e.g.
-@hubalek_ambulant_2006], there was a recent push toward the development and use of portable light loggers to improve ambulant light assessment and gain more insight into the NIF effects of light on human health in field conditions [@stampfli_light-dosimeter_2021; @van_duijnhoven_recommendations_2017; @webler_towards_2021].
-Attached to different body parts (e.g., wrist, head on eye level, chest), these devices allow objectively measuring personal light exposure under real-world conditions and are valuable tools for field studies.
-Nevertheless, these devices also encompass limiting factors such as potentially being intrusive (e.g., when eye-level worn), yielding the risk of getting covered (e.g., when wrist- or chest-worn) and requiring (monetary) resources and expertise for acquisition and maintenance of the devices.
-On the other hand, several attempts have been made to quantify received light exposure subjectively with self-report questionnaires (cf.
-**Supplementary Table 1**), bypassing the cost and intrusiveness issues.
-However, subjective light intensity assessments pose a new set of challenges: The human visual system constantly adapts to brightness [@hurvich_perception_1966], while the human non-visual light processing works largely subconsciously [@allen_exploiting_2018], making the self-report assessment of light properties potentially quite challenging, especially for inexperienced laypeople.
-Retrospectively recalling the properties of a light source can further complicate such subjective evaluations.
-Moreover, measuring light properties alone does not yield any information about how individuals might behave differently regarding diverse light situations.
-These measurement limitations point to a couple of research challenges we aim to take on here: How can we gain insight into light exposure patterns via self-report but circumvent directly inquiring about the specific properties and intensity of a light source?
-And how can we simultaneously assess how people habitually interact with the received light?
-We propose that these challenges can be tackled by assessing light-exposure-related behaviour.
-We argue that, besides measuring received light exposure as intensity, it is also essential to understand people's behaviours concerning different light situations.
-Since, in many cases, humans have become their own agents regarding their exposure to light or darkness through artificial electric light, people's light exposure-related behaviours ultimately determine their light consumption and timing: People receive different light depending on their daily activities, including workplace habits, bedtime hygiene, pastime and social activities.
-The final objective of changing light-dark exposure patterns to avoid or mitigate negative health consequences from unhealthy habits will not just need an assessment of the lighting properties but the active change of behaviours related to light exposure.
-We argue that assessing these activities is a beneficial stepping stone for prospective behaviour change.
-Furthermore, people without light measurement expertise may find it easier to appraise and recall their behaviour concerning light exposure than subjectively assessing a light source’s properties.
-To date, little effort has been made to understand and capture these activities.
-**Supplementary Table 1** summarises the existing questionnaire literature assessing light exposure-related properties.
-However, only a few questions of these existing tools were associated with light exposure-related behaviour.
-For example, the “Munich Chronotype  Questionnaire” [MCTQ; @roenneberg2003life], a popular self-report tool for identifying chronotypes via mid-sleep times, includes questions about the individual’s time spent outdoors on workdays and free days.
-In addition, the “Pittsburgh Sleep Quality Index” [PSQI; @buysse1989pittsburgh], a popular measure of sleep quality, contains questions about sleep and wake-up times, which are relevant to the light exposure around bedtime.
-However, none of these questionnaires provides a scaleable solution to capture light exposure-related behaviour in various physiologically relevant lighting scenarios.
-To fill this gap, we here present the development process of a novel self-report tool - the “Light Exposure Behavior Assessment” (LEBA) - for capturing and quantifying diverse light exposure-related behaviours.
+-   Light exposure is important
+
+-   Light exposure Behaviour is important
+
+-   Supplementary Table S1: Overview Existing Related Scales
+
+-   Existing Scales: Review them in text
+
+-   None of these do light exposure behaviour.
 
@@
 
-A quantitative cross-sectional fully anonymous, geographically unconstrained online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
-Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (<https://enlightenyourclock.org/participate-in-research>) of the science-communication comic book "Enlighten your clock", co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by the distribution of the survey link via f.lux [@f.lux].
-The initial page of the online survey provided information about the study, including that participation was voluntary and that respondents could withdraw from participation at any time without being penalised.
-Subsequently, consent was recorded digitally for the adult participants (\>18 years), while under-aged participants (\<18 years) were prompted to obtain additional assent from their parents/legal guardians.
-Filling in all questionnaires was estimated to take less than 30 minutes, and participation was not compensated.
-As a part of the demographic data, participants provided information regarding age, sex, gender identity, occupational status, COVID-19-related occupational setting, time zone/country of residence and native language.
-The demographic characteristics of our sample are given in **Table 1**.
-Participants were asked to confirm that they participated in the survey for the first time.
-Additionally, five attention check items (e.g., "We want to make sure you are paying attention.
-What is 4+5?") were included among the questionnaires to ensure high data quality.
-All questions incorporating retrospective recall were aligned to a "past four weeks" period.
-
-We collected the survey data between 17 May 2021 and 3 September 2021 – firstly from `r nrow(EFA.descriptives)` participants (EFA sample) – and subsequently, another dataset from `r nrow(CFA.descriptives)` participants (CFA sample), totalling `r nrow(desctable.data)`.
+A quantitative cross-sectional fully anonymous geographically unconstrained online large-scale survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
+Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (<https://enlightenyourclock.org/participate-in-research>) of the science-communication comic-book "Enlighten your clock" co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by distribution of the survey link via f.lux [@f.lux].
+The landing page of the online survey had the explanatory statements where we mentioned participation was voluntary and that respondents could withdraw from participation any time without being penalized.
+At the beginning of the survey, for the adult participants (\>18 years) consent was recorded digitally.
+Under-aged participants (\<18 years) were urged to obtain assent from their parents/legal guardians.
+The entire survey was estimated to take less than 30 minutes.
+Participants were not compensated.
+As a part of the demographic information participants provided information regarding age, sex, gender identity, occupational status, COVID-19 related occupational setting, time zone/country of residence and native language.
+The demographic characteristics of our sample are given in Table 1.
+To ensure high data quality, five attention check items were included in the survey (e.g., "We want to make sure you are paying attention.
+What is 4+5?").
+Participants were asked to confirm that they were participating the survey for the first time.
+Questions incorporating retrospective recall were all aligned to the period of "past four weeks".\
+We conducted two rounds of data collection.
+At first, we collected data from `r nrow(EFA.descriptives)` participants (EFA sample).
+In the second round we collected data from another `r nrow(CFA.descriptives)` participants (CFA sample) making a total sample of `r nrow(desctable.data)`.
+The data analysed in this study was collected between 17 May 2021 and 3 September 2021.
 
@@
 
-Figure \@ref(fig:FlowchartFig) summarises the steps we followed while developing LEBA. We conducted all analyses with the statistical software environment R [@R-base]. 
-**Firstly**, we set an item pool of 48 items with a six-point Likert-type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial scale.
-Our purpose was to capture light exposure-related behaviour.
-In that context, the first two response options: "Does not apply/I don't know" and "Never" provided similar information.
-As such we collapsed them into one, making it a 5-point Likert-type response format (1-Never, 2-Rarely, 3-Sometimes, 4-Often, 5-Always).
-
-**Secondly**, the two rounds of data collection were administered. 
-**Thirdly**, we conducted descriptive and item analysis and proceeded to the exploratory factor analysis (EFA) using the "psych" package [@R-psych] on the data collected in the first round (EFA sample; n=`r nrow(EFA.descriptives)`), as a part of psychometric analysis.
-Prior to the EFA, the necessary assumptions, including sample adequacy, normality assumptions, and quality of correlation matrix, were assessed.
-As our data violated both the univariate and multivariate normality assumption and yielded ordinal response data, we used a polychoric correlation matrix in the EFA and employed "principal axis" (PA) as the factor extraction method [@desjardinsHandbookEducationalMeasurement2018; @watkinsStepbyStepGuideExploratory2020].
-We applied a combination of methods including Scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and Hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
-To determine the latent structure, we followed the common guidelines: (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading \> .3 across factors [@bandalosFactorAnalysisExploratory2018].
+Figure \@ref(fig:FlowchartFig) summarizes the steps we followed while developing LEBA.
+In our analysis we used R statistical tool [@R-base].
+**First**, we developed an item pool of 48 items with six-point Likert type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial scale.
+Our purpose was to capture light exposure related behaviour.
+In that context, the first two response options: "Does not apply/I don't know" and "Never" were providing similar information.
+As such we collapsed them into one, making it a 5 point Likert type response format (1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always).
+
+**Second**, for data collection we conducted two rounds of large-scale survey.
+**Third**, as a part of psychometric analysis, we conducted descriptive and item analysis and proceeded to the exploratory factor analysis (EFA) using "psych" package [@R-psych] on the data collected in the first round (EFA sample; n=`r nrow(EFA.descriptives)`).
+Prior to the EFA, necessary assumptions, including sample adequacy, normality assumptions, quality of correlation matrix were assessed.
+Our data violated both the univariate and multivariate normality assumptions.
+Due to these violations and the ordinal nature of our response data, in EFA we used polychoric correlation matrix and employed principal axis (PA) as the factor extraction method [@desjardinsHandbookEducationalMeasurement2018; @watkinsStepbyStepGuideExploratory2020].
+We used a combination of factor identification method including Scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and Hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
+To determine the latent structure, we followed the common guidelines : (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading \> .3 across factors [@bandalosFactorAnalysisExploratory2018].
 <!-- We also conducted an EFA on non-merged response options data set (**Supplementary File 1**).
@@
 
-For reliability estimation, the "psych" package was applied [@R-psych].
-Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it tends to deflate the estimates for Likert-type data since the calculation is based on the Pearson-correlation matrix, which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal].
-Subsequently, we reported ordinal alpha for each factor obtained in the EFA [@zumbo2007ordinal] to get better reliability estimates.
-We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$ coefficient, which was suggested as a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
-Both ordinal alpha and McDonald's $\omega_t$ coefficient values range between 0 to 1, where higher values represent better reliability.
-
-To validate the latent structure obtained in the EFA, we conducted a categorical confirmatory factor analysis (CFA) with the weighted least squares means and variance adjusted (WLSMV) estimation [@desjardinsHandbookEducationalMeasurement2018], using the "lavaan" package [@R-lavaan] on the data collected in the second round (CFA sample; n=`r nrow(CFA.descriptives)`).
+For reliability estimation "psych" package was used [@R-psych].
+Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it has a tendency to deflate the estimates for Likert-type data since the calculation is based on Pearson-correlation matrix which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal].
+Subsequently to get better estimates of reliability we reported ordinal alpha for each factors obtained in EFA [@zumbo2007ordinal].
+We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$ coefficient which is a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
+Both ordinal alpha and McDonald's $\omega_t$ coefficient value range between 0 to 1 and higher value represents better reliability.
+
+To validate the latent structure obtained in EFA, We conducted a categorical confirmatory factor analysis (CFA) with weighted least square with mean and variance adjusted (WLSMV) estimator [@desjardinsHandbookEducationalMeasurement2018] using "lavaan" package [@R-lavaan] on the data collected in the second round (CFA sample; n=`r nrow(CFA.descriptives)`).
 We assessed the model fit using common model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI): close to .95 or above/ between .90-.95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner].
-However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015], and SRMR does not work well with ordinal data [@RN1272].
-Consequently, we judged the model fit using CFI, TLI and RMSEA.
-
-We then assessed the measurement invariance (MI) of our scale between native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non-native English speakers (n=`r invariance.data.descriptives.count[2,2]`) in the CFA sample (n=`r nrow(CFA.descriptives)`).
+However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015] and SRMR does not work well with ordinal data [@RN1272] As such, we judged the model fit using CFI, TLI and RMSEA.
+
+We assessed the measurement invariance (MI) of our scale between native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non-native English speakers (n=`r invariance.data.descriptives.count[2,2]`) in the CFA sample (n=`r nrow(CFA.descriptives)`).
 MI evaluates whether a construct has the psychometric equivalence and the same meaning across groups [@putnick2016measurement; @klinePrinciplesPracticeStructural2015].
-We used the structural equation modelling framework applying the "lavaan" package [@R-lavaan] to assess the measurement invariance.
+We used structural equation modelling framework using "lavaan" package [@R-lavaan] to assess the measurement invariance.
 We successively compared four nested models: configural, metric, scalar, and residual models using the $\chi^2$ difference test ($\Delta \chi^2$).
-Among MI models, the configural model is the least restrictive and the residual model is the most restrictive.
-A non-significant $\Delta \chi^2$ test between two nested measurement invariance models indicates mode fit does not significantly decrease for the superior model, thus allowing the superior invariance model to be accepted [@dimitrov2010testing; @widaman1997exploring].
-
-**Fourthly**, as secondary analysis, we identified the educational grade level required to understand the items in our scale with the Flesch-Kincaid grade level identification method [@flesch1948new] applying the "koRpus" [@R-koRpus] package.
-Also, we analysed possible semantic overlap of our developed scale using the ["Semantic Scale Network" (SSN)](https://rosenbusch.shinyapps.io/semantic_net/) engine [@rosenbusch2020semantic].
-The SSN detects semantically related scales and provides a cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic].
-Pairs of scales with a cosine similarity index value of 1 inidicate full semantical similarity, suggesting redundancy of the scales.
-
-**Lastly**, we derived a short form of the LEBA employing an Item Response Theory (IRT) based analysis.
-We fitted each factor of the LEBA to the combined EFA and CFA sample (n=`r nrow(sem.data)`) using the graded response model [@samejima1997handbook] via the "mirt" package [@R-mirt].
-IRT assesses the item quality by estimating the item discrimination, item difficulty, item information curve, and test information curve [@bakerBasicsItemResponse2017].
+Among MI models, the configural model is the least restrictive model and residual model is the most restrictive model.
+A non-significant $\Delta \chi^2$ test between two nested measurement invariance models indicates mode fit does not significantly decrease for the superior model thus allowing the superior invariance model to be accepted [@dimitrov2010testing; @widaman1997exploring].
+
+**Fourth**, as secondary analysis we identified the educational grade level required to understand the items in our scale using Flesch-Kincaid grade level identification method [@flesch1948new] using "koRpus" [@R-koRpus] package.
+Also, we analysed possible semantic overlap of our developed scale using ["Semantic Scale Network" (SSN)](https://rosenbusch.shinyapps.io/semantic_net/) engine [@rosenbusch2020semantic].
+The SSN detects semantically related scales and provides cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic].
+Pair of scales with a cosine similarity index value of 1 indicates they are perfectly semantically similar scales indicating redundancy.
+
+**Lastly**, we developed a short form of LEBA using Item Response Theory (IRT) based analysis.
+We fitted each factor of LEBA using the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n=`r nrow(sem.data)`) using "mirt" package [@R-mirt].
+IRT assesses the item quality by estimating item discrimination, item difficulty, item information curve, and test information curve [@bakerBasicsItemResponse2017].
 Item discrimination indicates how well a particular item can differentiate between participants across the given latent trait continuum ($\theta$).
 Item difficulty corresponds to the latent trait level at which the probability of endorsing a particular response option is 50%.
-The item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
-Here, we reported the item difficulty and discrimination parameter and categorize the items based on their item discrimination index: none = 0; very low = 0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70 [@bakerBasicsItemResponse2017].
-We discarded the items with relatively flat item information curve (information \<.2) to derive the short form of LEBA.
-We also assessed the precision of the short LEBA utilizing the Test information curve (TIC).
+Item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
+Here, we reported the item difficulty and discrimination parameter and categorize the items based on their item discrimination index: none = 0; very low =0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70 [@bakerBasicsItemResponse2017].
+We discarded the items with relatively flat item information curve (information \<.2) to develop the short form of LEBA.
+We also assessed the precision of the short LEBA using Test information curve (TIC).
 TIC indicates the amount of information a particular scale carries along the latent trait continuum.
-Additionally, item and person fit of the fitted IRT models were  analysed to gather more evidence on the validity and meaningfulness of our scale [@desjardinsHandbookEducationalMeasurement2018].
-The item fit was evaluated using the RMSEA value obtained from Signed-$\chi^2$ index implementation, an RMSEA value $\le$.06 was considered adequate item fit.
-The person fit was estimated using standardized fit index Zh statistics [@drasgow1985appropriateness].
-Here, Zh \< -2 was considered as a misfit [@drasgow1985appropriateness].
+Item fit and person fit of the fitted IRT models were also analysed to gather more evidence on validity and meaningfulness of our scale [@desjardinsHandbookEducationalMeasurement2018].
+Item fit was evaluated using the RMSEA value obtained from Signed-$\chi^2$ index implementation, RMSEA value $\le$.06 was considered adequate item fit.
+Person fit was estimated using standardized fit index Zh statistics [@drasgow1985appropriateness].
+Zh \< -2 was considered as a misfit [@drasgow1985appropriateness].
 
@@
 
-The current research project utilizes fully anonymous online survey data and therefore does not fall under the scope of the Human Research Act, making an authorisation from the ethics committee redundant.
+By reason of using fully anonymous online survey data, the present research project does not fall under the scope of the Human Research Act, making an authorisation from the ethics committee redundant.
 Nevertheless, the cantonal ethics commission (Ethikkommission Nordwest- und Zentralschweiz, EKNZ) reviewed our proposition (project ID Req-2021-00488) and issued an official clarification of responsibility.
@@
 
-After reviewing the literature, we identified several light exposure-related scales.
+After reviewing the literature, we identified several light exposure related scales.
 However, no scale specifically measuring the behavioural component of light exposure were found (**Supplementary Table 1**).
@@
 
-Table 1 summarises the survey participants' demographic characteristics.
+Table 1 summarizes the survey participants' demographic characteristics.
 Only participants completing the full LEBA questionnaire were included, thus there are no missing values in the item analyses.
@@
 ```{r fullgt,  include=FALSE}
-#This chunk holds codes for creating 'gtExtra' based descriptive figures (EFA+CFA);
+#This chunk holds codes for creating 'gtExtra' based descriptive figures
 
@@
 
-Figure \@ref(fig:efagtPic1) and Figure \@ref(fig:efagtPic2) summarise the response pattern of our total sample (n=`r nrow(sem.data)`) for all 48 items.
-Most of the items appeared skewed.
-The Shapiro–Wilk test of univariate normality [@shapiroAnalysisVarianceTest1965] and Mardia test of multivariate normality [@mardiaMeasuresMultivariateSkewness1970] indicated our data violated both univariate and multivariate normality.
+Figure \@ref(fig:efagtPic1) and Figure \@ref(fig:efagtPic2) summarize the response pattern of our total sample (n=`r nrow(sem.data)`) for all 48 items.
+Most of the items appeared skewed.The Shapiro–Wilk test of univariate normality [@shapiroAnalysisVarianceTest1965] and Mardia test of multivariate normality [@mardiaMeasuresMultivariateSkewness1970] indicated our data violated both univariate and multivariate normality.
 Multivariate skew was `r printnum(mardia.all.data$b1p)` (p \<0.001) and multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p \<0.001).
@@
 
-**Supplementary Figure 1** summarises the univariate descriptive statistics for the 48 items in the EFA sample (n=`r nrow(EFA.data)`).
+**Supplementary Figure 1** summarizes the univariate descriptive statistics for the 48 items in the EFA sample (n=`r nrow(EFA.data)`).
 Here also our data violated univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970].
@@
 
-Table \@ref(tab:tabCfa) summarises the CFA fit indices of our fitted model.
+Table \@ref(tab:tabCfa) summarizes the CFA fit indices of our fitted model.
 Our fitted model attained acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`; RMSEA = `r apa(fit.1[7],2,F)` [`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constrain on item pairs 32-33 [item 32: I dim my mobile phone screen within 1 hour before attempting to fall asleep; item 33: I dim my computer screen within 1 hour before attempting to fall asleep] and 16-17 [item 16: I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day; item 17: I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day].
@@
 In our CFA sample we had `r mi.count[1,2]` native English speakers and `r mi.count[2,2]` non-native English speakers.
-**Supplementary Table 5** summarises the demographic descriptions native and non-native English speakers.
-Table \@ref(tab:InvarianceTab) indicates our fitted model had acceptable fit indices for all of the fitted MI models.
+**Supplementary Table 5** summarizes the demographic descriptions native and non-native English speakers.Table \@ref(tab:InvarianceTab) indicates our fitted model had acceptable fit indices for all of the fitted MI models.
 The model fit did not significantly decrease across the nested models indicating the acceptability of the highest measurement invariance model: residual model.
@@
 ```{r InvarianceTab, results='asis'}
-apa_table(Invariance.table, align = "c",  caption = "Measurement Invariance analysis on CFA sample (n=262) across native and non-native English speakers.", note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square; a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual; * =  df of model comparison.", landscape = T, font_size = "footnotesize", escape=F )
+apa_table(Invariance.table, align = "c",  caption = "Measurment Invariance analysis on CFA sample (n=262) across native and non-native English speakers.", note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square; a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual; * =  df of model comparison.", landscape = T, font_size = "footnotesize", escape=F )
 
@@
 Examination of the item information curve (**Supplementary Figure 3**) indicated five items (1, 25, 30, 38, & 41) had relatively flat information curves (I($\theta$) \<.20).
-We discarded those items which yielded a short form of LEBA with five factors and 18 items (**Supplementary File 2**).
+We discarded those items which yielded a short form of LEBA with 5 factors and 18 items (**Supplementary File 2**).
 
@@
 
-We treated each factor of short-LEBA as a unidimensional construct and obtain five TICs (Figure \@ref(fig:Testinfo)).
+We treated each factor of short-LEBA as a unidimensional construct and obtain 5 TICs (Figure \@ref(fig:Testinfo)).
 These information curves indicated except the first and fifth factors, the other three factor's TICs are roughly centred on the centre of the trait continuum ($\theta$).
-The first and fifth factor had a peak to the right side of the centre of latent trait.
-Thus we conferred the LEBA scale estimated the light exposure related behaviour with precision near the centre of trait continuum for second, third and fourth factors and near the right side of the centre of trait continuum for first and fifth factors [@bakerBasicsItemResponse2017].
-
-**Supplementary Table 7** summarises the item fit indexes of the 18 items.
+The first and fifth factor had a peak to the right side of the centre of latent trait.Thus we conferred the LEBA scale estimated the light exposure related behaviour with precision near the centre of trait continuum for 2nd, 3rd and 4th factors and near the right side of the centre of trait continuum for 1st and 5th factors [@bakerBasicsItemResponse2017].
+
+**Supplementary Table 7** summarizes the item fit indexes of the 18 items.
 All items had RMSEA value $\le$.06 indicating adequate fit of the items to the fitted IRT model.
@@
 
-Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five factor structure we obtained in our EFA thus provided evidence of structural validity.(CFI=`r apa(fit.2[5],2,F)`; TLI=`r apa(fit.2[6],2,F)`; RMSEA=`r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR=`r apa(fit.2[10],2,F) `).
-However, in this model, we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings.
+Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five factor structure we obtained in our EFA thus provided evidence of structural validity.(CFI=`r apa(fit.2[5],2,F)`; TLI=`r apa(fit.2[6],2,F)`); RMSEA=`r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR=`r apa(fit.2[10],2,F) `).
+However, in this model we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings.
 Also, we accepted one pair of items (item 30 $\&$ 41) to covary their error variance .
@@
 lastly, we developed a short-LEBA (18 items) using IRT analysis.
-We fitted a graded response model to the combined EFA and CFA sample (n=`r nrow(data)`).
+We fitted a graded response model model to the combined EFA and CFA sample (n=`r nrow(data)`).
 We discarded five items (1, 25, 30, 38, & 41) with relatively flat item information curve [I($\theta$) <.20].
@@
 
-Based on all the gathered evidence, we can say LEBA can be used to profile individuals based on their light exposure related behaviours, which can facilitate the development process of individual interventions to promote health.
+Based on all the gathered evidences, we can say LEBA can be used to profile individuals based on their light exposure related behaviours, which can facilitate the development process of individual interventions to promote health.
 All the five factors of LEBA may identify 'problematic' behaviours that are opposed to good light hygiene.

### 2022-07-18 manuscript.Rmd
Adjust discussion and proof read the document.

--- 2022-07-10 manuscript.Rmd
@@
 The so-called non-image-forming (NIF) effects of light comprise light’s circadian and non-circadian influence on several physiological and psychological functions, such as the secretion of melatonin, sleep, mood, pupil size, body temperature, alertness, and higher cognitive functions [i.a.
-reviewed in @Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020 ].
+reviewed in @Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020].
 With the introduction of artificial electric light, human behaviour has become somewhat independent of the natural light-dark cycle – people can now frequently choose when to be exposed to light or darkness.
@@
 An extensive body of scientific evidence suggests that the imbalance of light and dark exposure disrupts humans’ light-dependent physiological systems [@Lunn.2017].
-This, in turn, gives rise to a series of adverse health consequences, including the alteration of several hormonal rhythms, increased cancer rates, cardiovascular diseases, and metabolic disorders, such as obesity, and type II diabetes [see reviews by @Lunn.2017; @navara2007dark; @Chellappa.2019]
+Subsequently, this disruption gives rise to a series of adverse health consequences, including the alteration of several hormonal rhythms, increased cancer rates, cardiovascular diseases, and metabolic disorders, such as obesity, and type II diabetes [see reviews by @Lunn.2017; @navara2007dark; @Chellappa.2019]
 These findings have sparked a significant call for assessment and guidance regarding healthy light exposure and timing – the latter was recently published as consensus-based experts’ recommendations, postulating specific requirements for indoor light environments during the daytime, evening, and nighttime [@Brown.2022].
@@
 The Visual Light Sensitivity Questionnaire-8 [@verriotto2017new] and Photosensitivity Assessment Questionnaire (PAQ; @bossini2006sensibilita), a couple of self-report tools measuring visual light sensitivity, contain single items which probe the preference for specific light situations: "In the past month, how often did you need to wear dark glasses on cloudy days or indoors?" [@verriotto2017new]; "I prefer rooms that are in semi-darkness."; [@bossini2006sensibilita].
-In addition, the “Pittsburgh Sleep Quality Index” [PSQI; @buysse1989pittsburgh], a popular measure of sleep quality, contains questions about sleep and wake-up times, which are relevant to the light exposure around bedtime.
+In addition, the “Pittsburgh Sleep Quality Index” [PSQI; @buysse1989pittsburgh], a popular measure of sleep quality, contains questions about sleep and wake-up times, which are relevant to light exposure around bedtime.
 However, none of these questionnaires provides a scaleable solution to capture light exposure-related behaviour in various physiologically relevant lighting scenarios.
@@
 
-A quantitative cross-sectional fully anonymous, geographically unconstrained online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
+A quantitative cross-sectional, fully anonymous, geographically unconstrained online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
 Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (<https://enlightenyourclock.org/participate-in-research>) of the science-communication comic book "Enlighten your clock", co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by the distribution of the survey link via f.lux [@f.lux].
@@
 Our purpose was to capture light exposure-related behaviour.
-In that context, the first two response options: "Does not apply/I don't know" and "Never" provided similar information.
-As such we collapsed them into one, making it a 5-point Likert-type response format (1-Never, 2-Rarely, 3-Sometimes, 4-Often, 5-Always).
+In that context, the first two response options: "Does not apply/I don't know" and "Never", provided similar information.
+As such, we collapsed them into one, making it a 5-point Likert-type response format (1-Never, 2-Rarely, 3-Sometimes, 4-Often, 5-Always).
 
@@
 As our data violated both the univariate and multivariate normality assumption and yielded ordinal response data, we used a polychoric correlation matrix in the EFA and employed "principal axis" (PA) as the factor extraction method [@desjardinsHandbookEducationalMeasurement2018; @watkinsStepbyStepGuideExploratory2020].
-We applied a combination of methods including a Scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and Hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
+We applied a combination of methods, including a Scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and Hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
 To determine the latent structure, we followed the common guidelines: (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading \> .3 across factors [@bandalosFactorAnalysisExploratory2018].
-<!-- We also conducted an EFA on non-merged response options data set (**Supplementary File 1**).
+<!-- We also conducted an EFA on the non-merged response options data set (**Supplementary File 1**).
 -->
@@
 To validate the latent structure obtained in the EFA, we conducted a categorical confirmatory factor analysis (CFA) with the weighted least squares means and variance adjusted (WLSMV) estimation [@desjardinsHandbookEducationalMeasurement2018], using the "lavaan" package [@R-lavaan] on the data collected in the second round (CFA sample; n=`r nrow(CFA.descriptives)`).
-We assessed the model fit using common model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI): close to .95 or above/ between .90-.95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner].
+We assessed the model fit using standard model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI): close to .95 or above/ between .90-.95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner].
 However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015], and SRMR does not work well with ordinal data [@RN1272].
@@
 We successively compared four nested models: configural, metric, scalar, and residual models using the $\chi^2$ difference test ($\Delta \chi^2$).
-Among MI models, the configural model is the least restrictive and the residual model is the most restrictive.
+Among MI models, the configural model is the least restrictive, and the residual model is the most restrictive.
 A non-significant $\Delta \chi^2$ test between two nested measurement invariance models indicates mode fit does not significantly decrease for the superior model, thus allowing the superior invariance model to be accepted [@dimitrov2010testing; @widaman1997exploring].
@@
 The SSN detects semantically related scales and provides a cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic].
-Pairs of scales with a cosine similarity index value of 1 inidicate full semantical similarity, suggesting redundancy of the scales.
+Pairs of scales with a cosine similarity index value of 1 inidicate full semantical similarity, suggesting redundancy.
 
@@
 Additionally, the item and person fit of the fitted IRT models were analysed to gather more evidence on the validity and meaningfulness of our scale [@desjardinsHandbookEducationalMeasurement2018].
-The item fit was evaluated using the RMSEA value obtained from Signed-$\chi^2$ index implementation, where an RMSEA value $\le$.06 was considered adequate item fit.
+The item fit was evaluated using the RMSEA value obtained from Signed-$\chi^2$ index implementation, where an RMSEA value $\le$.06 was considered an adequate item fit.
 The person fit was estimated employing the standardized fit index Zh statistics [@drasgow1985appropriateness].
@@
 An expert panel comprising all authors -- researchers from chronobiology, light research, neuroscience and psychology -- developed a comprehensive item pool of 48 items.
-The 48 items were then examined based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by each panel member independently and modifications were suggested as required.
+The 48 items were examined independently based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by each panel member, and modifications were suggested as required.
 The author team discussed the suggestions and amended the items as indicated, thus creating a 48-item scale.
@@
 CFA Sample"])`].
-In total `r desc_tibble[3,2]` of the participants indicated female sex, `r desc_tibble[4,2]` indicated male and `r desc_tibble[5,2]` indicated other sex.
-Overall, `r desc_tibble[6,2]` participants indicated a gender-variant identity.
+In total, `r desc_tibble[3,2]` of the participants indicated female sex, `r desc_tibble[4,2]` indicated male, and `r desc_tibble[5,2]` indicated other sex.
+Overall, `r desc_tibble[6,2]` participants reported a gender-variant identity.
 In a "Yes/No" question regarding native language, `r desc_tibble[7,2]` of respondents [EFA: `r desc_tibble[7,3]`; CFA: `r desc_tibble[7,4]`] indicated to be native English speakers.
-For their "Occupational Status", more than half of the overall sample reported that they currently work, whereas `r desc_tibble[10,2]` reported that they go to school and `r desc_tibble[11,2]` responded that they do "Neither".
-With respect to the COVID-19 pandemic we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` of the participants indicated that they were in a home office/ home schooling setting, while `r desc_tibble[14,2]` reported face-to-face work/schooling.
+For their "Occupational Status", more than half of the overall sample reported that they currently work, whereas `r desc_tibble[10,2]` reported that they go to school, and `r desc_tibble[11,2]` responded that they do "Neither".
+With respect to the COVID-19 pandemic, we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` of the participants indicated that they were in a home office/ home schooling setting, while `r desc_tibble[14,2]` reported face-to-face work/schooling.
 Lastly, `r desc_tibble[15,2]` overall reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]`  filled in the "Neither (no work or school, or on vacation)" response option.
@@
 Most of the items appeared skewed.
-The Shapiro–Wilk test of univariate normality [@shapiroAnalysisVarianceTest1965] and Mardia test of multivariate normality [@mardiaMeasuresMultivariateSkewness1970] indicated our data violated both univariate and multivariate normality.
+The Shapiro–Wilk test of univariate normality [@shapiroAnalysisVarianceTest1965] and Mardia test of multivariate normality [@mardiaMeasuresMultivariateSkewness1970] indicated that our data violated both univariate and multivariate normality.
 The multivariate skew was `r printnum(mardia.all.data$b1p)` (p \<0.001), and the multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p \<0.001).
@@
 The multivariate skew was `r printnum(mardia$b1p)` (p \<0.001) and the multivariate kurtosis yielded a value of `r printnum(mardia$b2p)` (p \<0.001).
-The corrected item-total correlation ranged between `r apa(low.r.corec,2,F)` -`r apa(high.r.corec,2,F)`.
+The corrected item-total correlation ranged between `r apa(low.r.corec,2,F)` and `r apa(high.r.corec,2,F)`.
 However, no item was discarded based on descriptive statistics or item analysis.
@@
 4.9 % inter-item correlation coefficients were higher than \|.30\|.
-'x' denotes non-significant item-total correlation.
+'x' denotes a non-significant item-total correlation.
 (B) The Scree plot suggested six factors.
@@
 
-Finally, we examined the factor's interpretability in the five-factor solution and weighed it against the psychometric properties as we considered it essential to attain a balance between the two.
-As we deemed the five derived factors interpretable and relevant concerning our aim to capture light exposure-related behaviour, we retained all of them with 25 items for our confirmatory factor analysis (CFA), despite the apparent low reliability of the fifth factor.
+Lastly, we examined the factor's interpretability in the five-factor solution and weighed it against the psychometric properties as we considered it essential to attain a balance between the two.
+As we deemed the five derived factors interpretable and relevant concerning our aim to capture light exposure-related behaviour, we retained all of them with 25 items for our confirmatory factor analysis (CFA), despite the apparent lower reliability of the fifth factor.
 Two of the items showed negative factor-loading (items 44 and 21).
@@
 
-Accordingly, we accept the 5-factor model with 23 items, finalizing the long Form of LEBA (see **Supplementary File 1**).
+Accordingly, we accept the five-factor model with 23 items, finalizing the long Form of LEBA (see **Supplementary File 1**).
 The Internal consistency McDonald's $\omega_t$ coefficient for the total scale yielded `r apa(rel.k[5,6],2,F)`.
@@
 As shown in Table \@ref(tab:InvarianceTab), the employed five-factor model generated acceptable fit indices over all of the fitted MI models.
-The model fit did not significantly decrease across the nested models implying the acceptability of the highest measurement invariance model (residual model).
+The model fit did not significantly decrease across the nested models, implying the acceptability of the highest measurement invariance model (residual model).
 
@@
 
-## Developing Short form of LEBA: IRT-Based Analysis
+## Developing a Short Form of LEBA: IRT-Based Analysis
 In order to derive a short form of the LEBA instrument, we fitted each factor of the LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n=690).
@@
 
-Since electrical light use was globally established, people's received light exposure is not only regulated by the natural light-dark cycle but ultimately determined by their light-related behaviour, i.e.
-people receive different light intensities at different times depending on their light-related habits.
+Nowadays, in many industrialized countries, most of the time is spent in enclosed buildings [@Klepeis.2001], where people's received light is determined not only by the natural light-dark cycle but by exposure to artificial light sources.
+Accordingly, people receive varying light intensities at different times, ultimately depending on their light-related behavioural habits.
+As established by extensive evidence, the timing, duration and intensity of light exposure, among other light properties, affect many aspects of human health, well-being, and performance [i.a.
+reviewed in @Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020].
+Thus, there is a clear need for guidance [see @Brown.2022] and assessment regarding healthy light exposure and consequentially healthy light-related behaviour.
 In reviewing the literature, we found that a handful of previously introduced instruments assess aspects of light exposure by self-report (see **Supplementary Table 1**).
@@
 However, none of these questionnaires systematically and thoroughly captures behaviours that modify light exposure across different lighting scenarios.
-Aiming to fill this gap, we have developed a self-report scale that can capture light exposure-related behaviour in multiple dimensions.
-
-The 48 initially generated items were first applied in a geographically unconstrained quantitative cross-sectional survey, yielding responses from a large international sample (n=`r nrow(data)`).
+With the present LEBA tool, we have developed two versions of a self-report scale that can capture light exposure-related behaviour in multiple dimensions.
+
+The 48 initially generated items were applied in a large-scale geographically unconstrained cross-sectional survey, yielding (n=`r nrow(data)`) complete datasets.
+Moreover, to assure high data quality, this included only data where the five “attention check items” throughout the survey were passed.
+As a result, data was recorded from `r nrow(num.countries)` countries and `r nrow(numUTC)` time zones, including native and non-native English speakers from a sex-balanced and age-diverse sample (see Table 1).
+The acquired study population complied with our objective to avoid bias from a selective sample, which is crucial when relying on voluntary uncompensated participation.
 
 Data collected in the first round was used to explore the latent structure (EFA sample; n=`r nrow(EFA.descriptives)`).
-Exploratory factor analysis revealed a five factor solution with 25 items.
-("Wearing blue light filters", "Spending time outdoors", "Using phone and smartwatch in bed", "Using light before bedtime", and "Using light in the morning and during daytime").
-The internal consistency reliability coefficient ordinal alpha ranged between `r apa(min(alpha.tab),2,F)`-`r apa(max(alpha.tab),2,F)`.
-Except for the fifth factor the internal reliability coefficients were above .70.
-For the fifth factor it was `r apa((alpha.tab[5,1]),2,F)`.
-As a rule of thumb reliability coefficient higher than .70 is considered to be satisfactory.
-However for scales with less than 20 items and at the early developmental stage, a value of .50 is also acceptable [@dall2010developmental; @field2013discovering; @Nunnally1978].
-Also all of the factors were highly interpretable in terms of a common theme and contributed essentially towards our aim to capture light exposure related behaviour.
-This eventually led us to accept the obtained five-factor structure.
+The exploratory factor analysis revealed a highly interpretable five-factor solution ("Wearing blue light filters", "Spending time outdoors", "Using phone and smartwatch in bed", "Using light before bedtime", and "Using light in the morning and during daytime") with 25 items.
 The total scale exhibited satisfactory internal consistency (McDonald's $\omega_t$=`r apa(omega$omega.tot,2,T)`).
@@
 Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five-factor structure we obtained in our EFA, thus providing evidence for structural validity.(CFI=`r apa(fit.2[5],2,F)`; TLI=`r apa(fit.2[6],2,F)`; RMSEA=`r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR=`r apa(fit.2[10],2,F) `).
-However, in this model, we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings.
-Additionally, we allowed the error variance of one pair of items (item 30 $\&$ 41) capturing smartwatch-based light exposure behaviour to covary.
-In retrospect, it seemed plausible that many respondents were not using a smartwatch at all, resulting in them answering similarly for these two items.
+In this model, we discarded two additional items (item 26 $\&$ 37 ) for possible cross-loadings.
 The internal consistency coefficients ordinal alpha for the five factors and the total scale were again satisfactory (Ordinal alpha ranged between `r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$=`r apa(rel.k[5,6],2,F)`).
@@
 Upon inspecting the questionnaire contents, we found that some items in the factors "Using phone and smartwatch in bed" and "Using light before bedtime" have semantic overlap with the SDSC’s and CIDI’s items.
-However, while the CIDI and the SDSC capture clinically relevant sleep problems and related activities, the LEBA aims to assess light-exposure-related behaviour.
-Since light exposure at night has been shown to disturb sleep [@Brown.2022; @santhi_applications_2020], this overlap is consistent with our aim to measure physiologically relevant light-related activites.
-Nevertheless, the general objectives between the complete questionnaires differ evidently.
+However, while the CIDI and the SDSC capture various clinically relevant sleep problems and related activities, the LEBA aims to assess light-exposure-related behaviour.
+Since light exposure at night has been shown to influence sleep negatively [@Brown.2022; @santhi_applications_2020], this overlap confirms our aim to measure the physiologically relevant aspects of light-exposure-related behaviour.
+Nevertheless, the general objectives of the complete questionnaires and the LEBA differ evidently.
 
@@
 
-Based on all the gathered evidence, we can say LEBA can be used to profile individuals based on their light exposure related behaviours, which can facilitate the development process of individual interventions to promote health.
-All the five factors of LEBA may identify 'problematic' behaviours that are opposed to good light hygiene.
+##Known Limitations
+
+We acknowledge that this work is limited concerning the following aspects:
+
+- In the five factor-solution derived from the Exploratory factor analysis, the internal consistency reliability coefficient ordinal alpha ranged between `r apa(min(alpha.tab),2,F)`-`r apa(max(alpha.tab),2,F)`, though only the fifth factor (“Using light in the morning and during daytime”) yielded internal reliability coefficients below .70 `r apa((alpha.tab[5,1]),2,F)`.
+As a rule of thumb, reliability coefficients higher than .70 are regarded as “satisfactory”.
+However, for scales with less than 20 items and at the early developmental stage, a value of .50 is considered acceptable [@dall2010developmental; @field2013discovering; @Nunnally1978].
+Furthermore, the full LEBA scale exhibited satisfactory internal consistency (McDonald’s 𝜔𝑡=0.77), while all factors were highly interpretable regarding a common behavioural theme.
+Thus, we decided to proceed with the five-factor solution.
+- During the post-hoc model modification, as part of the confirmatory factor analysis, we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings, as demonstrated in the data.
+However, two additional items covaried in their error variance.
+By allowing the latter pair (30 $\&$ 41) to covary, the model's error variance attained an improved fit (cf.
+**Figure 5**).
+A possible explanation for the covariation is that many respondents might not have used a smartwatch at all, resulting in similar response patterns between these two items.
+Thus, though rather unconventional, we decided to accept this post-hoc modification to our five-factor model.
+- The habitual patterns queried in the developed scales might not exhaustively represent all relevant light-exposure-related behaviours.
+For instance, it is conceivable that additional light-related activities not included in the LEBA depend on the respondents' profession/occupation, geographical context, and socio-economic status.
+However, we generated the initial item pool with an international team of researchers and followed a thorough psychometric analysis.
+Therefore, we are confident that the developed LEBA scales can serve as a good starting point for exploring the behavioural aspects of light exposure in more depth.
+- As with all studies relying on retrospective self-report data, individuals filling in the LEBA may have difficulties precisely recalling the inquired light-related behaviours.
+In the interest of bypassing a substantial memory component, we limited the recall period to four weeks and chose response options that do not require exact memory recall.
+In contrast to directly assessing light properties via self-report, we assume that reporting behaviours might be more manageable for inexperienced laypeople, as the latter does not rely on existing knowledge about light sources.
+The accessibility of the LEBA is also reflected in the “grade level identification” findings suggesting a minimum age of 8.33 years and an educational grade of four or higher.
+We argue that measuring light-related behaviours via self-report is crucial because these behaviours will hardly be as observable by anyone else or measurable with other methods (like behavioural observations) with reasonable effort.
+
+## Future Directions
+
+To our knowledge, the LEBA is the first questionnaire characterising light exposure-related behaviour in a scalable manner.
+Thus, estimating convergent validity with similar subjective scales was impossible.
+Alternatively, the validity of the LEBA could be evaluated by administering it conjointly with objective field measurements of light exposure (e.g.
+with portable light loggers, see literature review).
+By this route, one could study how the (subjectively measured) light exposure-related behavioural patterns translate into (objectively measured) received light exposure.
+Additionally, developing daily recall scales of light-related behaviour could provide a more detailed behavioural assessment to supplement the LEBA's broader (four-week) measurement approach.
+Comparing the LEBA scores to 24-hour recall scores could provide helpful information about how light exposure-related behaviour assessment is related between different time perspectives.
+Moreover, light-exposure-related behaviour might depend on the respondents' profession, geographical location, housing conditions, socio-economic status, or other contextual factors.
+As the current data is limited to our international online survey context, future research should apply the LEBA across more variable populations and contexts.
+On the other hand, this will require the development of cross-cultural adaptations and translations into other languages of the LEBA scale, which should be targeted in prospective studies.
+Finally, in the future, applying the LEBA scales should not just be limited to gathering information in cross-sectional quantitative studies but allow for individual behaviour profiling.
+For instance, the LEBA could be applied in a clinical context as part of Cognitive Behavioural Therapy for Insomnia (CBT-I).
+More specifically, it could be used to supplement the sleep hygiene aspects of CBT-I, as receiving light exposure at different times has implications for sleep [@santhi_applications_2020].
+This match was also evident in the semantic relationship between the LEBA and two scales capturing sleep problems (CIDI: Insomnia; @robins1988 & SDSC; @bruni1996sleep) found in the semantic similarity analysis.
+However, before applying the LEBA in such contexts in the future, more work is certainly needed to understand light exposure-related behaviour and its’ relationship to relevant health outcomes measured subjectively and objectively.
 
@@
 
-We developed a novel self-reported subjective scale-"Light exposure behaviour assessment"(LEBA) to capture light exposure related behaviour.
-We developed 48 items, judged the relevance and content of the items and conducted a large-scale geographically unrestricted cross-sectional survey.
-Our EFA gave a five solution with 25 items.
-A CFA with this 25-item scale again offered a five-factor solution, but this time two more item was discarded.
-The 23-item "LEBA" was found reliable (internal consistency) and valid (structural validity).
-A short-form of LEBA was developed using IRT analysis.
-IRT analysis gave a 18-item scale with a good coverage across the underlying trait continuum.
-Hence, we could recommend that LEBA can be used to profile individuals according to their light exposure related behaviours.
-
-## Future Direction
-
-Since, LEBA is the first of its kind, estimating convergent validity with other subjective scale was not possible.
-One way to establish the convergent validity of LEBA is to administer this subjective scale along which some objective measurement scales (e.g.
-personalised light dosimeter).
-Though such objective scales do not directly capture light exposure related behaviour, potential insight can be drawn by understanding the behaviour pattern and light exposure.
-Also, light exposure related behaviours can be dependent upon the socio-economic status as behaviours can be modulated by available scales individual have on their disposal.
-Our analysis did not consider socio-economic status, as we didn't measure it.
-Investigating the properties of LEBA while considering different socio-economic status would be a valuable addition.
+With the "Light exposure behaviour assessment"(LEBA), we developed a novel, internally consistent and structurally valid 23-item self-report scale for capturing light exposure-related behaviour in five scalable factors.
+In addition, an 18-item short-form of the LEBA was derived using IRT analysis, yielding adequate coverage across the underlying trait continuum.
+Applying the LEBA scales can provide insights into light exposure-related habits on a population-based level.
+Furthermore, it can serve as a good starting point to profile individuals based on their light exposure-related behaviour determining their light consumption and timing.
 

### 2022-07-18 manuscript.Rmd
Knitting updated: working

@@
 # histogram and density plots
-  gtExtras::gt_sparkline(
+  gtExtras::gt_plt_dist(
     hist_data,
@@
     same_limit = TRUE)%>%
-  gtExtras::gt_sparkline(
+  gtExtras::gt_plt_dist(
     dens_data,
@@
 CFa.matrix[1,] = c("Model 1", 
-                   apa(cfa.sum.1$FIT[6],2,T), 
-                   apa(cfa.sum.1$FIT[7],2,T), 
-                   apa(cfa.sum.1$FIT[19],2,F), 
-                   apa(cfa.sum.1$FIT[20],2,T),
-                   apa(cfa.sum.1$FIT[27],2,T),
-                   apa(cfa.sum.1$FIT[28],2,T),
-                   apa(cfa.sum.1$FIT[29],2,T),
-                   apa(cfa.sum.1$FIT[35],2,T))
+                   apa(as.numeric(cfa.sum.1$FIT[6]),2,T), 
+                   apa(as.numeric(cfa.sum.1$FIT[7]),2,T), 
+                   apa(as.numeric(cfa.sum.1$FIT[19]),2,F), 
+                   apa(as.numeric(cfa.sum.1$FIT[20]),2,T),
+                   apa(as.numeric(cfa.sum.1$FIT[27]),2,T),
+                   apa(as.numeric(cfa.sum.1$FIT[28]),2,T),
+                   apa(as.numeric(cfa.sum.1$FIT[29]),2,T),
+                   apa(as.numeric(cfa.sum.1$FIT[35]),2,T))
 
 CFa.matrix[2,] = c("Model 2", 
-                   apa(cfa.sum.2$FIT[6],2,T), 
-                   apa(cfa.sum.2$FIT[7],2,T), 
-                   apa(cfa.sum.2$FIT[19],2,F), 
-                   apa(cfa.sum.2$FIT[20],2,T),
-                   apa(cfa.sum.2$FIT[27],2,T),
-                   apa(cfa.sum.2$FIT[28],2,T),
-                   apa(cfa.sum.2$FIT[29],2,T),
-                   apa(cfa.sum.2$FIT[35],2,T))
+                   apa(as.numeric(cfa.sum.2$FIT[6]),2,T), 
+                   apa(as.numeric(cfa.sum.2$FIT[7]),2,T), 
+                   apa(as.numeric(cfa.sum.2$FIT[19]),2,F), 
+                   apa(as.numeric(cfa.sum.2$FIT[20]),2,T),
+                   apa(as.numeric(cfa.sum.2$FIT[27]),2,T),
+                   apa(as.numeric(cfa.sum.2$FIT[28]),2,T),
+                   apa(as.numeric(cfa.sum.2$FIT[29]),2,T),
+                   apa(as.numeric(cfa.sum.2$FIT[35]),2,T))
 ```
@@
 More specifically, it could be used to supplement the sleep hygiene aspects of CBT-I, as receiving light exposure at different times has implications for sleep [@santhi_applications_2020].
-This match was also evident in the semantic relationship between the LEBA and two scales capturing sleep problems (CIDI: Insomnia; @robins1988 & SDSC; @bruni1996sleep) found in the semantic similarity analysis.
+This match was also evident in the semantic relationship between the LEBA and two scales capturing sleep problems (CIDI: Insomnia;@robins1988composite & SDSC; @bruni1996sleep) found in the semantic similarity analysis.
 However, before applying the LEBA in such contexts in the future, more work is certainly needed to understand light exposure-related behaviour and its’ relationship to relevant health outcomes measured subjectively and objectively.

### 2022-07-18 manuscript.Rmd
Figures updated

@@
         #text=element_text(family = "Helvetian"),
-        axis.text.x = element_text(size = 15),
-        axis.text.y = element_text(size = 15),
-        axis.title.x = element_text(size = 15),
-        axis.title.y = element_text(size = 15),
-        plot.title = element_text(size = 15),
-        legend.text = element_text(size = 15),
+        axis.text.x = element_text(size = 70),
+        axis.text.y = element_text(size = 70),
+        axis.title.x = element_text(size = 70),
+        axis.title.y = element_text(size = 70),
+        plot.title = element_text(size = 70),
+        legend.text = element_text(size =50),
         legend.title=element_blank(),
@@
   theme( panel.grid.major = element_blank(),
-         axis.text.x = element_text(size = 6),
-         axis.text.y = element_text(size = 6),
+         axis.text.x = element_text(size = 40),
+         axis.text.y = element_text(size = 40),
          panel.border = element_rect(color = "black",
@@
 
-residual.plot <- ggplot(residual.data, aes(x=Residuals)) + geom_histogram(binwidth=.04, col=I("black"),fill="#00A08799") + xlim(-.2,.2)+ ylim(0,250)+apatheme +geom_vline(xintercept = .05)+theme(axis.text.x = element_text(size = 12),
-        axis.text.y = element_text(size = 12))+
+residual.plot <- ggplot(residual.data, aes(x=Residuals)) + geom_histogram(binwidth=.04, col=I("black"),fill="#00A08799") + xlim(-.2,.2)+ ylim(0,250)+apatheme +geom_vline(xintercept = .05)+
   labs( y="Frequency")
@@
                      nrow = 1,
-                     label_size = 12,
+                     label_size = 60,
                      label_fontfamily = "Arial",
@@
                      nrow = 5,
-                     label_size = 12,
+                     label_size = 60,
                      label_fontfamily = "Arial",
@@
                      ncol = 3,
-                     label_size = 15,
+                     label_size = 60,
                      label_fontfamily = "Arial",

### 2022-07-19 manuscript.Rmd
Legend size corrected

@@
         #text=element_text(family = "Helvetian"),
-        axis.text.x = element_text(size = 70),
-        axis.text.y = element_text(size = 70),
-        axis.title.x = element_text(size = 70),
-        axis.title.y = element_text(size = 70),
-        plot.title = element_text(size = 70),
-        legend.text = element_text(size =50),
+        axis.text.x = element_text(size = 80),
+        axis.text.y = element_text(size = 80),
+        axis.title.x = element_text(size = 80),
+        axis.title.y = element_text(size = 80),
+        plot.title = element_text(size = 80),
+        legend.text = element_text(size =80),
         legend.title=element_blank(),
@@
                       # insig = "blank",
-           ggtheme = ggplot2::theme_minimal(),tl.srt = 90,colors = c("#E64B35FF", "white", "#3C5488FF") )+
+           ggtheme = ggplot2::theme_minimal(),tl.srt = 90,  colors = c("#E64B35FF", "white", "#3C5488FF") )+
   theme( panel.grid.major = element_blank(),
-         axis.text.x = element_text(size = 40),
-         axis.text.y = element_text(size = 40),
+         axis.text.x = element_text(size = 35),
+         axis.text.y = element_text(size = 35),
+          legend.text=element_text(size =30),
+         legend.title = element_blank(),
          panel.border = element_rect(color = "black",
@@
                                     size = 1))
+        # legend.position = 'right', 
+        # legend.spacing.x = unit(0.5, 'cm'),
+        # legend.text = element_text(margin = margin(t = 10)))
 #to show pvalue in the fig add p.mat=p.mat
@@
 #                   label_fontface = "plain")
-ggsave("Figures/Figure4.png",efa.plot, width = 7, height = 8, dpi = 600)
+ggsave("Figures/Figure4.png",efa.plot, width = 7, height = 8, dpi = 600, bg = "white")
 ```

### 2022-07-19 manuscript.Rmd
typo fixed in the discussion

@@
 However, for scales with less than 20 items and at the early developmental stage, a value of .50 is considered acceptable [@dall2010developmental; @field2013discovering; @Nunnally1978].
-Furthermore, the full LEBA scale exhibited satisfactory internal consistency (McDonald’s 𝜔𝑡=0.77), while all factors were highly interpretable regarding a common behavioural theme.
+Furthermore, the full LEBA scale exhibited satisfactory internal consistency (McDonald’s $\omega_t$=0.77), while all factors were highly interpretable regarding a common behavioural theme.
 Thus, we decided to proceed with the five-factor solution.

### 2022-07-19 manuscript.Rmd
Limitation header and reference issues

@@
 
-##Known Limitations
+## Known Limitations
 
@@
 More specifically, it could be used to supplement the sleep hygiene aspects of CBT-I, as receiving light exposure at different times has implications for sleep [@santhi_applications_2020].
-This match was also evident in the semantic relationship between the LEBA and two scales capturing sleep problems (CIDI: Insomnia;@robins1988composite & SDSC; @bruni1996sleep) found in the semantic similarity analysis.
+This match was also evident in the semantic relationship between the LEBA and two scales capturing sleep problems (CIDI: Insomnia; @robins1988composite & SDSC; @bruni1996sleep) found in the semantic similarity analysis.
 However, before applying the LEBA in such contexts in the future, more work is certainly needed to understand light exposure-related behaviour and its’ relationship to relevant health outcomes measured subjectively and objectively.

### 2022-07-19 manuscript.Rmd
typo fixed in the limtation

@@
 
-- In the five factor-solution derived from the Exploratory factor analysis, the internal consistency reliability coefficient ordinal alpha ranged between `r apa(min(alpha.tab),2,F)`-`r apa(max(alpha.tab),2,F)`, though only the fifth factor (“Using light in the morning and during daytime”) yielded internal reliability coefficients below .70 `r apa((alpha.tab[5,1]),2,F)`.
+- In the five factor-solution derived from the Exploratory factor analysis, the internal consistency reliability coefficient ordinal alpha ranged between `r apa(min(alpha.tab),2,F)`-`r apa(max(alpha.tab),2,F)`, though only the fifth factor (“Using light in the morning and during daytime”) yielded internal consistencyreliability coefficients below .70 ($\alpha$=`r apa((alpha.tab[5,1]),2,F)`).
 As a rule of thumb, reliability coefficients higher than .70 are regarded as “satisfactory”.
@@
 However, two additional items covaried in their error variance.
-By allowing the latter pair (30 $\&$ 41) to covary, the model's error variance attained an improved fit (cf.
+By allowing the latter pair (30 $\&$ 41) to covary, the model attained an improved fit (cf.
 **Figure 5**).

### 2022-07-19 manuscript.Rmd
Reference corrected

@@
 
-library(papaja) # devtools::install_github("crsh/papaja")
+library(papaja) 
 library(lavaan)
-library(semPlot) #devtools::install_github('SachaEpskamp/semPlot',  dependencies = T)
+library(semPlot) 
 library(semTools)
@@
         panel.background = element_blank(),
-        #text=element_text(family = "Helvetian"),
         axis.text.x = element_text(size = 80),
@@
 Light exposure received by the eyes affects many facets of human health, well-being, and performance beyond visual sensation and perception [@boyce_light_2022].
-The so-called non-image-forming (NIF) effects of light comprise light’s circadian and non-circadian influence on several physiological and psychological functions, such as the secretion of melatonin, sleep, mood, pupil size, body temperature, alertness, and higher cognitive functions [i.a.
-reviewed in @Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020].
+The so-called non-image-forming (NIF) effects of light comprise light’s circadian and non-circadian influence on several physiological and psychological functions, such as the secretion of melatonin, sleep, mood, pupil size, body temperature, alertness, and higher cognitive functions [@Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020].
 With the introduction of artificial electric light, human behaviour has become somewhat independent of the natural light-dark cycle – people can now frequently choose when to be exposed to light or darkness.
@@
 An extensive body of scientific evidence suggests that the imbalance of light and dark exposure disrupts humans’ light-dependent physiological systems [@Lunn.2017].
-Subsequently, this disruption gives rise to a series of adverse health consequences, including the alteration of several hormonal rhythms, increased cancer rates, cardiovascular diseases, and metabolic disorders, such as obesity, and type II diabetes [see reviews by @Lunn.2017; @navara2007dark; @Chellappa.2019]
+Subsequently, this disruption gives rise to a series of adverse health consequences, including the alteration of several hormonal rhythms, increased cancer rates, cardiovascular diseases, and metabolic disorders, such as obesity, and type II diabetes [@Lunn.2017; @navara2007dark; @Chellappa.2019]
 These findings have sparked a significant call for assessment and guidance regarding healthy light exposure and timing – the latter was recently published as consensus-based experts’ recommendations, postulating specific requirements for indoor light environments during the daytime, evening, and nighttime [@Brown.2022].

### 2022-08-29 manuscript_v1.Rmd
Version 2--to address the comments

--- 2022-07-19 manuscript.Rmd
@@
 #This chunk holds code for plotting the correlation matrix
-
+#
 p.mat <- correlation::cor_to_p(correlations$rho, 428, method = "polychoric")
@@
   theme( panel.grid.major = element_blank(),
-         axis.text.x = element_text(size = 35),
-         axis.text.y = element_text(size = 35),
-          legend.text=element_text(size =30),
-         legend.title = element_blank(),
+         axis.text.x = element_text(size = 90),
+         axis.text.y = element_text(size = 90),
+         legend.text=element_text(size =90),
+         legend.title = element_text(size =90),
          panel.border = element_rect(color = "black",
@@
 #to show pvalue in the fig add p.mat=p.mat
-# ggsave("Figures/corplot.png",corplot, width = 12, height = 8.5, dpi = 600, bg ="white")
+# ggsave("Figures/corplot.png",corplot, width = 12, height = 8.5, dpi = 300, bg ="white")
 
@@
 
-```{r efa-plot, include=F}
+```{r efa-plot, eval=FALSE, include=FALSE}
+#Not in use. Figure developed using illustrator.
 #This chunk holds code for compiled factor identification plots

### 2022-08-29 manuscript_v2.Rmd
rmd

--- 2022-08-29 manuscript_v1.Rmd
@@
   - name          : "Céline Vetter"
-    affiliation   : "8, 9"
+    affiliation   : "8"
     email         : "celine.vetter@colorado.edu"
@@
   - name          : "Gena Glickman"
-    affiliation   : "10"
+    affiliation   : "9"
     email         : "gena.glickman@usuhs.edu"
@@
     corresponding : yes
-    affiliation   : "11, 12, 13"
+    affiliation   : "10, 11, 12"
     email         : "manuel.spitschan@tum.de "
@@
   - id            : "9"
-    institution   : "XIMES GmbH, Vienna, Austria"
+    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
   - id            : "10"
-    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
+    institution   : "Translational Sensory & Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany"
   - id            : "11"
-    institution   : "Translational Sensory & Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany"
+    institution   : "TUM Department of Sport and Health Sciences (TUM SG), Technical University of Munich, Munich, Germany"
   - id            : "12"
-    institution   : "TUM Department of Sport and Health Sciences (TUM SG), Technical University of Munich, Munich, Germany"
-  - id            : "13"
     institution   : "University of Oxford, Department of Experimental Psychology, Oxford, United Kingdom"

### 2022-09-19 manuscript_v2.Rmd
Table 3 updated with concise code

@@
 colnames(CFa.matrix) = c("Model", "$\\chi^{2}$", "df", "CFI", "TLI", "RMSEA", "RMSEA 90\\% Lower CI", "RMSEA 90\\% Upper CI", "SRMR")
-CFa.matrix[1,] = c("Model 1", 
-                   apa(as.numeric(cfa.sum.1$FIT[6]),2,T), 
-                   apa(as.numeric(cfa.sum.1$FIT[7]),2,T), 
-                   apa(as.numeric(cfa.sum.1$FIT[19]),2,F), 
-                   apa(as.numeric(cfa.sum.1$FIT[20]),2,T),
-                   apa(as.numeric(cfa.sum.1$FIT[27]),2,T),
-                   apa(as.numeric(cfa.sum.1$FIT[28]),2,T),
-                   apa(as.numeric(cfa.sum.1$FIT[29]),2,T),
-                   apa(as.numeric(cfa.sum.1$FIT[35]),2,T))
-
-CFa.matrix[2,] = c("Model 2", 
-                   apa(as.numeric(cfa.sum.2$FIT[6]),2,T), 
-                   apa(as.numeric(cfa.sum.2$FIT[7]),2,T), 
-                   apa(as.numeric(cfa.sum.2$FIT[19]),2,F), 
-                   apa(as.numeric(cfa.sum.2$FIT[20]),2,T),
-                   apa(as.numeric(cfa.sum.2$FIT[27]),2,T),
-                   apa(as.numeric(cfa.sum.2$FIT[28]),2,T),
-                   apa(as.numeric(cfa.sum.2$FIT[29]),2,T),
-                   apa(as.numeric(cfa.sum.2$FIT[35]),2,T))
-```
-
-```{r tabCfa, results='asis'}
-apa_table(CFa.matrix, caption = "Confirmatory Factor Analysis model fit indices of the two model: (a) Model 1: five factor model with 25 items (b) Model 2:  five factor model with 23 items.
+
+Cfa.matrix <- tabledown::cfa.tab.multi(fit.Cor.1,fit.Cor.2)
+Cfa.matrix.selected <- as.data.frame(Cfa.matrix[, c(1,2,6,7,8,9,10,11)])
+Cfa.matrix.selected <- tibble::rowid_to_column(Cfa.matrix.selected,"Model")
+colnames(Cfa.matrix.selected) = c("Model", "$\\chi^{2}$", "df", "CFI", "TLI", "RMSEA", "RMSEA 90\\% Lower CI", "RMSEA 90\\% Upper CI", "SRMR")
+
+```
+
+```{r tabCfa}
+apa_table(Cfa.matrix.selected, caption = "Confirmatory Factor Analysis model fit indices of the two model: (a) Model 1: five factor model with 25 items (b) Model 2:  five factor model with 23 items.
 Model 2 attained the best fit.", align = "c", landscape = T, escape=F, note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square.")
@@
 ```{r InvarianceTab, results='asis'}
-apa_table(Invariance.table, align = "c",  caption = "Measurement Invariance analysis on CFA sample (n=262) across native and non-native English speakers.", note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square; a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual; * =  df of model comparison.", landscape = T, font_size = "footnotesize", escape=F )
+apa_table(Invariance.table, align = "c",  caption = "Measurement Invariance analysis on CFA sample (n=262) across native and non-native English speakers.", note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square; a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; * =  df of model comparison.", landscape = T, font_size = "footnotesize", escape=F )
 

### 2022-09-19 manuscript_v2.Rmd
Abstract comments addressed

@@
 abstract: |
-  Light exposure is an essential driver of health and well-being.
-Our behaviour modulates many aspects of light exposure, but how these light-related behaviours can be shaped to optimise personal light exposure is currently unknown.
+  Light exposure is an essential driver of health and well-being, and individual behaviours during rest and activity modulate physiologically-relevant aspects of light exposure.
+Further understanding the behaviours that influence individual photic exposure patterns may provide insight into volitional contributions to the physiological effects of light and guide bevavioral points of intervention.
 Here, we present a novel, self-reported and psychometrically validated instrument to capture light exposure-related behaviour, the Light Exposure Behaviour Assessment (LEBA).
@@
   An expert panel prepared the initial 48-item pool spanning different light exposure-related behaviours.
-Responses, consisting of rating the frequency of engaging in the per-item behaviour on a 5-point Likert type scale, were collected in an online survey yielding responses from a geographically unconstrained sample (690 completed responses, 74 countries, 28 time zones).
+Responses, consisting of rating the frequency of engaging in the per-item behaviour on a 5-point Likert type scale, were collected in an online survey yielding responses from a geographically unconstrained sample (690 completed responses, 74 nationalities, 28 time zones).
 The exploratory factor analysis (EFA) on an initial subsample (n=428) rendered a five-factor solution with 25 items (Wearing blue light filters, spending time outdoors, using a phone and smartwatch in bed, using light before bedtime, using light in the morning and during daytime).
@@
 
-  The psychometric properties of the LEBA instrument indicate the usability to measure the light exposure-related behaviours across a variety of settings and may offer a scalable solution to characterise light exposure-related behaviours in remote samples.
+  The psychometric properties of the LEBA instrument indicate the usability to measure light exposure-related behaviours.
+The instrument may offer a scalable solution to characterize behaviours that influence individual photic exposure patterns in remote samples.
 The LEBA instrument will be available under the open-access CC-BY-NC-ND license.

### 2022-09-19 manuscript_v2.Rmd
Introduction comments addressed

@@
 Additionally, when light sources can not be directly manipulated, sought out, or avoided (for example, at school, work, or in public places), there is still potential leeway to influence them behaviourally, for instance, by wearing sunglasses, directing one’s gaze away or supplementing the situation with additional light sources.
-Although clearly yielding the potential for good, this agency is further associated with increased electric light exposure at night and indoor time during the day, compromising the natural temporal organisation of the light-dark cycle.
+Although clearly yielding the potential for good, these behaviours are further associated with increased electric light exposure at night and indoor time during the day, compromising the natural temporal organisation of the light-dark cycle.
 For example, in the US, an average of 87% of the time is spent in enclosed buildings [@Klepeis.2001], and more than 80% of the population is exposed to a night sky that is brighter than nights with a full moon due to electric light at night [@navara_dark_2007].
+
 An extensive body of scientific evidence suggests that the imbalance of light and dark exposure disrupts humans’ light-dependent physiological systems [@Lunn.2017].
-Subsequently, this disruption gives rise to a series of adverse health consequences, including the alteration of several hormonal rhythms, increased cancer rates, cardiovascular diseases, and metabolic disorders, such as obesity, and type II diabetes [@Lunn.2017; @navara2007dark; @Chellappa.2019]
-These findings have sparked a significant call for assessment and guidance regarding healthy light exposure and timing – the latter was recently published as consensus-based experts’ recommendations, postulating specific requirements for indoor light environments during the daytime, evening, and nighttime [@Brown.2022].
+Subsequently, this disruption gives rise to a series of adverse health consequences, including the alteration of hormonal rhythms, increased cancer rates, cardiovascular diseases, and metabolic disorders, such as obesity and type II diabetes [@Lunn.2017; @navara2007dark; @Chellappa.2019].
+These findings have sparked a significant call for assessment and guidance regarding healthy light exposure as exemplified by a recently published set of consensus-based experts’ recommendations with specific requirements for indoor light environments during the daytime, evening, and nighttime [@Brown.2022].
 Furthermore, building on earlier attempts [e.g.
-@hubalek_ambulant_2006], there was a recent push toward the development and use of portable light loggers to improve ambulant light assessment and gain more insight into the NIF effects of light on human health in field conditions [@stampfli_light-dosimeter_2021; @van_duijnhoven_recommendations_2017; @webler_towards_2021].
-Attached to different body parts (e.g., wrist, head on eye level, chest), these devices allow objectively measuring personal light exposure under real-world conditions and are valuable tools for field studies.
+@hubalek_ambulant_2006], there was a recent push toward the development and use of portable light loggers to improve ambulant light assessment and gain more insight into the NIF effects of light on human health in field conditions [@stampfli_light-dosimeter_2021; @van_duijnhoven_recommendations_2017; @webler_towards_2021; @aarts2017performance].
+Attached to different body parts (e.g., wrist; head, at eye level; chest), these devices allow for the objective measurement of individual photic exposure patterns under real-world conditions and thus are a valuable tools for field studies..
 Nevertheless, these devices also encompass limiting factors such as potentially being intrusive (e.g., when eye-level worn), yielding the risk of getting covered (e.g., when wrist- or chest-worn) and requiring (monetary) resources and expertise for acquisition and maintenance of the devices.
-On the other hand, several attempts have been made to quantify received light exposure subjectively with self-report questionnaires (cf.
-**Supplementary Table 1**), bypassing the cost and intrusiveness issues.
-However, subjective light intensity assessments pose a new set of challenges: The human visual system constantly adapts to brightness [@hurvich_perception_1966], while the human non-visual light processing works largely subconsciously [@allen_exploiting_2018], making the self-report assessment of light properties potentially quite challenging, especially for inexperienced laypeople.
+
+On the other hand, several attempts have been made to quantify received light exposure subjectively with self-report questionnaires (**Supplementary Table 1**), bypassing the cost and intrusiveness issues.
+However, subjective light intensity assessments pose a new set of challenges: The human visual system constantly adapts to brightness [@hurvich_perception_1966], while the human non-visual light processing works largely subconsciously [@allen_exploiting_2018], making the self-report assessment of light properties potentially quite challenging.
 Retrospectively recalling the properties of a light source can further complicate such subjective evaluations.
-Moreover, measuring light properties alone does not yield any information about how individuals might behave differently regarding diverse light situations.
+Moreover, measuring light properties alone does not yield any information about how individuals might behave differently regarding diverse light environments such  as work, home or outdoors.
 These measurement limitations point to a couple of research challenges we aim to take on here: How can we gain insight into light exposure patterns via self-report but circumvent directly inquiring about the specific properties and intensity of a light source?
@@
 We propose that these challenges can be tackled by assessing light-exposure-related behaviour.
-We argue that, besides measuring received light exposure as intensity, it is also essential to understand people's behaviours concerning different light situations.
-Since, in many cases, humans have become their own agents regarding their exposure to light or darkness through artificial electric light, people's light exposure-related behaviours ultimately determine their light consumption and timing: People receive different light depending on their daily activities, including workplace habits, bedtime hygiene, pastime and social activities.
-The final objective of changing light-dark exposure patterns to avoid or mitigate negative health consequences from unhealthy habits will not just need an assessment of the lighting properties but the active change of behaviours related to light exposure.
+We argue that, besides measuring received light exposure as intensity, it is also essential to understand people's behaviours with respect to different light situations.
+In many cases, humans have become their own agents regarding their exposure to light or darkness through daylight and artificial electric light, and as such people’s light exposure-related behaviours ultimately determine their light consumption and timing: People receive different light depending on their daily activities, including workplace habits, bedtime hygiene, pastime and social activities.
+Ultimately, in order to optimize lighting for human health and well being, better understanding of light-related behaviours will serve to identify additional points of intervention as well as to provide an added dimension to efficacy and implementation studies of novel lighting strategies.
 We argue that assessing these activities is a beneficial stepping stone for prospective behaviour change.
-Furthermore, people without light measurement expertise may find it easier to appraise and recall their behaviour concerning light exposure than subjectively assessing a light source’s properties.
+
 To date, little effort has been made to understand and capture these activities.
@@
 However, only a few questions of these existing tools were associated with light exposure-related behaviour.
-For example, the “Munich Chronotype  Questionnaire” [MCTQ; @roenneberg2003life], a popular self-report tool for identifying chronotypes via mid-sleep times, includes questions about the individual’s time spent outdoors on workdays and free days.
-The Visual Light Sensitivity Questionnaire-8 [@verriotto2017new] and Photosensitivity Assessment Questionnaire (PAQ; @bossini2006sensibilita), a couple of self-report tools measuring visual light sensitivity, contain single items which probe the preference for specific light situations: "In the past month, how often did you need to wear dark glasses on cloudy days or indoors?" [@verriotto2017new]; "I prefer rooms that are in semi-darkness."; [@bossini2006sensibilita].
-In addition, the “Pittsburgh Sleep Quality Index” [PSQI; @buysse1989pittsburgh], a popular measure of sleep quality, contains questions about sleep and wake-up times, which are relevant to light exposure around bedtime.
-However, none of these questionnaires provides a scaleable solution to capture light exposure-related behaviour in various physiologically relevant lighting scenarios.
-To fill this gap, we here present the development process of a novel self-report tool - the “Light Exposure Behavior Assessment” (LEBA) - for capturing and quantifying diverse light exposure-related behaviours.
+For example, the “Munich Chronotype  Questionnaire” [@roenneberg2003life], a popular self-report tool for identifying chronotypes via mid-sleep times, includes questions about the individual’s typical time spent outdoors on workdays and free days.
+The Visual Light Sensitivity Questionnaire-8 [@verriotto2017new] and Photosensitivity Assessment Questionnaire (@bossini2006sensibilita) are a couple of self-report tools measuring visual light sensitivity.
+They contain single items which probe the preference for specific light situations such as: “In the past month, how often did you need to wear dark glasses on cloudy days or indoors?” [@verriotto2017new];"I prefer rooms that are in semi-darkness."; [@bossini2006sensibilita].
+In addition, the “Pittsburgh Sleep Quality Index” [@buysse1989pittsburgh], a popular measure of sleep quality, contains questions about sleep and wake-up times, which are relevant to light exposure around bedtime.
+However, none of these questionnaires provides a scalable solution to capture light exposure-related behaviour in various physiologically relevant lighting scenarios.
+To fill this gap, we here present the development process of a novel self-reported tool - the “Light Exposure Behaviour Assessment” (LEBA) - for capturing and quantifying diverse light exposure-related behaviours.
 

### 2022-09-19 manuscript_v2.Rmd
Intro comments

@@
 In addition, the “Pittsburgh Sleep Quality Index” [@buysse1989pittsburgh], a popular measure of sleep quality, contains questions about sleep and wake-up times, which are relevant to light exposure around bedtime.
-However, none of these questionnaires provides a scalable solution to capture light exposure-related behaviour in various physiologically relevant lighting scenarios.
-To fill this gap, we here present the development process of a novel self-reported tool - the “Light Exposure Behaviour Assessment” (LEBA) - for capturing and quantifying diverse light exposure-related behaviours.
+However, none of these questionnaires provides a scalable solution to capture light exposure-related behaviour in various lighting situations.
+To fill this gap, we here present the development process of a novel self-reported tool - the “Light Exposure Behaviour Assessment” (LEBA) - for characterizing diverse light exposure-related behaviours.
 

### 2022-09-19 manuscript_v2.Rmd
Review comments addresses

@@
 Filling in all questionnaires was estimated to take less than 30 minutes, and participation was not compensated.
+
 As a part of the demographic data, participants provided information regarding age, sex, gender identity, occupational status, COVID-19-related occupational setting, time zone/country of residence and native language.
@@
 **Secondly**, the two rounds of data collection were administered. 
-**Thirdly**, we conducted descriptive and item analysis and proceeded to the exploratory factor analysis (EFA) using the "psych" package [@R-psych] on the data collected in the first round (EFA sample; n=`r nrow(EFA.descriptives)`), as a part of psychometric analysis.
+**Thirdly**, we conducted descriptive and item analyses and proceeded to the exploratory factor analysis (EFA) using the "psych" package [@R-psych] on the data collected in the first round (EFA sample; n=`r nrow(EFA.descriptives)`), as a part of psychometric analysis.
 Prior to the EFA, the necessary assumptions, including sample adequacy, normality assumptions, and quality of correlation matrix, were assessed.
@@
 Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it tends to deflate the estimates for Likert-type data since the calculation is based on the Pearson-correlation matrix, which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal].
-Subsequently, we reported ordinal alpha for each factor obtained in the EFA [@zumbo2007ordinal] to get better reliability estimates.
+Subsequently, we reported ordinal alpha for each factor obtained in the EFA which was suggested as a better reliability estimates or ordinal data[@zumbo2007ordinal].
 We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$ coefficient, which was suggested as a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
@@
 
-We then assessed the measurement invariance (MI) of our scale between native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non-native English speakers (n=`r invariance.data.descriptives.count[2,2]`) in the CFA sample (n=`r nrow(CFA.descriptives)`).
-MI evaluates whether a construct has the psychometric equivalence and the same meaning across groups [@putnick2016measurement; @klinePrinciplesPracticeStructural2015].
-We used the structural equation modelling framework applying the "lavaan" package [@R-lavaan] to assess the measurement invariance.
+In order to evaluate whether the construct demonstrated psychometric equivalence and the same meaning across native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non-native English speakers (n=`r invariance.data.descriptives.count[2,2]`) in the CFA sample (n=`r nrow(CFA.descriptives)`) [@putnick2016measurement; @klinePrinciplesPracticeStructural2015] measurement invariance analysis was used.
+We used structural equation modelling framework applying the "lavaan" package [@R-lavaan] to assess the measurement invariance.
 We successively compared four nested models: configural, metric, scalar, and residual models using the $\chi^2$ difference test ($\Delta \chi^2$).
@@
 
-**Fourthly**, as secondary analysis, we identified the educational grade level required to understand the items in our scale with the Flesch-Kincaid grade level identification method [@flesch1948new] applying the "koRpus" [@R-koRpus] package.
+**Fourthly**, in a secondary analysis, we identified the educational grade level required to understand the items in our scale with the Flesch-Kincaid grade level identification method [@flesch1948new] applying the "koRpus" [@R-koRpus] package.
 Correspondingly, we analysed possible semantic overlap of our developed scale using the ["Semantic Scale Network" (SSN)](https://rosenbusch.shinyapps.io/semantic_net/) engine [@rosenbusch2020semantic].
@@
 The item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
-Here, we reported the item difficulty and discrimination parameter and categorize the items based on their item discrimination index: none = 0; very low = 0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70 [@bakerBasicsItemResponse2017].
+Here, we reported the item difficulty and discrimination parameter and categorized the items based on their item discrimination index: (i) none = 0; (ii) very low = 0.01 to 0.34; (iii) low = 0.35 to 0.64; (iv) moderate = 0.65 to 1.34 ; (v) high = 1.35 to 1.69; (vi) very high \>1.70 [@bakerBasicsItemResponse2017].
 We discarded the items with a relatively flat item information curve (information \<.2) to derive the short form of LEBA.
-We also assessed the precision of the short LEBA utilizing the Test information curve (TIC).
+We also assessed the precision of the short LEBA utilizing the test information curve (TIC).
 TIC indicates the amount of information a particular scale carries along the latent trait continuum.
@@
 In a "Yes/No" question regarding native language, `r desc_tibble[7,2]` of respondents [EFA: `r desc_tibble[7,3]`; CFA: `r desc_tibble[7,4]`] indicated to be native English speakers.
-For their "Occupational Status", more than half of the overall sample reported that they currently work, whereas `r desc_tibble[10,2]` reported that they go to school, and `r desc_tibble[11,2]` responded that they do "Neither".
-With respect to the COVID-19 pandemic, we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` of the participants indicated that they were in a home office/ home schooling setting, while `r desc_tibble[14,2]` reported face-to-face work/schooling.
-Lastly, `r desc_tibble[15,2]` overall reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]`  filled in the "Neither (no work or school, or on vacation)" response option.
+For their "Occupational Status", more than half of the overall sample (`r desc_tibble[9,2]`) reported that they currently work, whereas `r desc_tibble[10,2]` reported that they go to school, and `r desc_tibble[11,2]` responded that they do "Neither".
+With respect to the COVID-19 pandemic, we asked participants to indicate their occupational setting during the last four weeks: In the overall sample, `r desc_tibble[13,2]` of the participants indicated that they were in a home office/ home schooling setting, `r desc_tibble[14,2]` reported face-to-face work/schooling, `r desc_tibble[15,2]`  reported a combination of home- and face-to-face work/schooling, and `r desc_tibble[16,2]`  filled in the "Neither (no work or school, or on vacation)" response option.
 
@@
 
-Figure \@ref(fig:efagtPic1) and Figure \@ref(fig:efagtPic2) summarise the response patterns of our total sample (n=`r nrow(sem.data)`) for all 48 items.
+Figures \@ref(fig:efagtPic1) and \@ref(fig:efagtPic2) summarise the response patterns of our total sample (n=`r nrow(sem.data)`) for all 48 items.
 Most of the items appeared skewed.
 The Shapiro–Wilk test of univariate normality [@shapiroAnalysisVarianceTest1965] and Mardia test of multivariate normality [@mardiaMeasuresMultivariateSkewness1970] indicated that our data violated both univariate and multivariate normality.
-The multivariate skew was `r printnum(mardia.all.data$b1p)` (p \<0.001), and the multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p \<0.001).
+The multivariate skewness was `r printnum(mardia.all.data$b1p)` (p \<0.001), and the multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p \<0.001).
 
@@
   tab_header(
-    title = md("**Light Exposure Behavior Assessment**"),
+    title = md("**Light Exposure Behaviour Assessment**"),
     subtitle = md("Summary Descriptives EFA Sample (n=428)")
@@
 Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items.
-The absolute values of the factor-loadings ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients.
+The absolute values of the factor-loadings ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)`, indicating strong coefficients.
 The commonalities ranged between `r apa(min.com,2,F)` and `r apa(max.com, 2, F)`.
@@
 [@desjardinsHandbookEducationalMeasurement2018].
-Subsequently, we fitted a six-factor solution, wherefrom a factor with only two salient variables emerged, thus disqualifying the six-factor solution (**Supplementary Table 4**).
+Subsequently, we fitted a six-factor solution, where a factor with only two salient variables emerged, thus disqualifying the six-factor solution (**Supplementary Table 4**).
 
@@
 The second factor contained six items and explained `r apa(var2,2,F)`% of the total variance with an internal reliability coefficient ordinal $\alpha$ = `r apa(F2.alpha,2,F)`.
-Items under this factor incorporated the individuals' hours spent outdoor.
+Items under this factor incorporated the individuals' hours spent outdoors.
 The third factor contained five items and explained `r apa(var3,2,F)`% of the total variance.
@@
 As we deemed the five derived factors interpretable and relevant concerning our aim to capture light exposure-related behaviour, we retained all of them with 25 items for our confirmatory factor analysis (CFA), despite the apparent lower reliability of the fifth factor.
-Two of the items showed negative factor-loading (items 44 and 21).
+Two of the items showed negative factor-loading (item 08: `r Hmisc::label(data$slypos_leba_08)` and item 37: `r Hmisc::label(data$slypos_leba_37)`).
 Upon re-inspection, we recognized these items to be negatively correlated to the respective factor, and thus, we reverse-scored these two items in the CFA analysis.
@@
   tab_header(
-    title = md("**Light Exposure Behavior Assessment**"),
+    title = md("**Light Exposure Behaviour Assessment**"),
     subtitle = md("Summary Descriptives CFA Sample (n=262)")
@@
 The 25-item model attained an acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`; RMSEA = `r apa(fit.1[7],2,F)` [`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constraints on item pairs 32-33 [item 32: I dim my mobile phone screen within 1 hour before attempting to fall asleep; item 33: I dim my computer screen within 1 hour before attempting to fall asleep] and 16-17 [item 16: I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day; item 17: I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day].
-Item pair 32-33 describes the preference for dimming the electric devices' brightness before bedtime, whereas item pair 16-17 represents the preference for using blue filtering or coloured glasses during the daytime.
+Item pair 32-33 describes the preference for dimming the electric devices' brightness before bedtime, whereas item pair 16-17 represents the use of blue filtering or coloured glasses during the daytime.
 Given the similar nature of captured behaviours within each item pair, we accepted the imposed equity constraints.
@@
 The model fit did not significantly decrease across the nested models, implying the acceptability of the highest measurement invariance model (residual model).
+This indicated the construct demonstrated psychometric equivalence and the same meaning across native and non-native English speaking participants
 
@@
 Furthermore, the
-Semantic Scale Network (SSN) analysis [@rosenbusch2020semantic] indicated that the LEBA appeared most strongly related to scales about sleep: The "Sleep Disturbance Scale For Children" [@bruni1996sleep] and the "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite].
+Semantic Scale Network (SSN) analysis [@rosenbusch2020semantic] indicated that the LEBA appeared most strongly semantically related to scales about sleep: The "Sleep Disturbance Scale For Children" [@bruni1996sleep] and the "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite].
 The cosine similarity yielded values between .47 to .51.
@@
 Subsequently, we treated each factor of the short-LEBA as a unidimensional construct and obtained five test information curves (TICs).
-As (Figure \@ref(fig:Testinfo)).
-illustrates, the TICs of the first and fifth factors peaked on the right side of the centre of their latent traits, while the TICs of the other three factors were roughly centred on the respective trait continuum ($\theta$).
+As Figure \@ref(fig:Testinfo) illustrates, the TICs of the first and fifth factors peaked on the right side of the centre of their latent traits, while the TICs of the other three factors were roughly centred on the respective trait continuum ($\theta$).
 This points out that the LEBA short-scale estimates the light exposure-related behaviour most precisely near the centre of the trait continuum for the second, third and fourth factors and, in contrast, to the right of the centre for the first and fifth factors [@bakerBasicsItemResponse2017].
@@
 Finally, **Supplementary Table 7** summarises the item fit indexes of the LEBA short form.
-All 18 items yielded RMSEA value $\le$.06, indicating adequate fit to the fitted IRT model.
+All 18 items yielded RMSEA value $\le$.06, indicating an adequate fit to the fitted IRT model.
 Furthermore, **Supplementary Figure 4** depicts the person fit Zh statistics histogram for the five IRT models.
@@
 # Discussion
-
-Nowadays, in many industrialized countries, most of the time is spent in enclosed buildings [@Klepeis.2001], where people's received light is determined not only by the natural light-dark cycle but by exposure to artificial light sources.
-Accordingly, people receive varying light intensities at different times, ultimately depending on their light-related behavioural habits.
-As established by extensive evidence, the timing, duration and intensity of light exposure, among other light properties, affect many aspects of human health, well-being, and performance [i.a.
-reviewed in @Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020].
-Thus, there is a clear need for guidance [see @Brown.2022] and assessment regarding healthy light exposure and consequentially healthy light-related behaviour.
+Today, in most industrialized countries, the vast majority of time is spent in built environments [@Klepeis.2001], where photic exposure patterns are determined not only by the solar cycle but by electrical light sources as well.
+As a consequence, light received may vary considerably, in terms of timing, intensity and spectrum, all of which are subject to the further influence of individual behaviours.
+[reviewed in @Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020; @vetter2022review].
+Thus, there is a clear need for guidance [@Brown.2022] and assessment regarding healthy light exposure and consequentially healthy light-related behaviour.
+
 In reviewing the literature, we found that a handful of previously introduced instruments assess aspects of light exposure by self-report (see **Supplementary Table 1**).
-Even fewer assessment tools have yet partially probed behavioural aspects of received light like the estimated time spent outside [MCTQ; @roenneberg2003life] or the preference for specific light situations (e.g.
-"I prefer rooms that are in semi-darkness."; PAQ @bossini2006sensibilita).
-However, none of these questionnaires systematically and thoroughly captures behaviours that modify light exposure across different lighting scenarios.
-With the present LEBA tool, we have developed two versions of a self-report scale that can capture light exposure-related behaviour in multiple dimensions.
-
-The 48 initially generated items were applied in a large-scale geographically unconstrained cross-sectional survey, yielding (n=`r nrow(data)`) complete datasets.
-Moreover, to assure high data quality, this included only data where the five “attention check items” throughout the survey were passed.
-As a result, data was recorded from `r nrow(num.countries)` countries and `r nrow(numUTC)` time zones, including native and non-native English speakers from a sex-balanced and age-diverse sample (see Table 1).
+Few studies to date have attempted to assess light exposure by self-report.
+That body of research becomes even smaller when limiting it to those focusing on <behaviours> that influence photic exposure patterns, and typically these home in only on particular behaviours of interest, such as estimates of time spent outside [@roenneberg2003life] or preferences for specific lighting situations [@bossini2006sensibilita].
+To our knowledge, there is no questionnaire in existence that captures behaviours that modify light exposure across different scenarios in a comprehensive way.
+With the present LEBA tool, we have developed two versions of a self-report scale that can capture light exposure-related behaviours in multiple dimensions.
+
+The 48 generated items were applied in a large-scale, geographically unconstrained, cross-sectional study, yielding `r nrow(data)` completed surveys.
+To assure high data quality, participant responses were only included when the five “attention check items” throughout the survey were passed.
+Ultimately, data was recorded from `r nrow(num.countries)` countries and `r nrow(numUTC)` time zones, including native and non-native English speakers from a sex-balanced and age-diverse sample (see Table 1).
 The acquired study population complied with our objective to avoid bias from a selective sample, which is crucial when relying on voluntary uncompensated participation.
@@
 We fitted a graded response model to the combined EFA and CFA sample (n=`r nrow(data)`) and discarded five items (1, 25, 30, 38, & 41) with relatively flat item information curve [I($\theta$) <.20].
-The resulting test information curves suggest that the short-LEBA is a psychometrically sound measure with adequate coverage of underlying traits and can be applied to capture different extents of light exposure-related behaviours reliably.
+The resulting test information curves suggest that the short-LEBA is a psychometrically sound measure with adequate coverage of underlying traits and can be applied to capture the frequency of different light exposure related behaviours reliably.
 
@@
 
-- In the five factor-solution derived from the Exploratory factor analysis, the internal consistency reliability coefficient ordinal alpha ranged between `r apa(min(alpha.tab),2,F)`-`r apa(max(alpha.tab),2,F)`, though only the fifth factor (“Using light in the morning and during daytime”) yielded internal consistencyreliability coefficients below .70 ($\alpha$=`r apa((alpha.tab[5,1]),2,F)`).
+- In the five factor-solution derived from the Exploratory factor analysis, the internal consistency reliability coefficient ordinal alpha ranged between `r apa(min(alpha.tab),2,F)`-`r apa(max(alpha.tab),2,F)`, though only the fifth factor (“Using light in the morning and during daytime”) yielded internal consistency reliability coefficients below .70 ($\alpha$=`r apa((alpha.tab[5,1]),2,F)`).
 As a rule of thumb, reliability coefficients higher than .70 are regarded as “satisfactory”.
@@
 However, we generated the initial item pool with an international team of researchers and followed a thorough psychometric analysis.
-Therefore, we are confident that the developed LEBA scales can serve as a good starting point for exploring the behavioural aspects of light exposure in more depth.
+Therefore, we are confident that the developed LEBA scales can serve as a good starting point for exploring the light exposure related behaviours in more depth and inform room for modification of light exposure-related behaviour to improve light hygiene.
 - As with all studies relying on retrospective self-report data, individuals filling in the LEBA may have difficulties precisely recalling the inquired light-related behaviours.
@@
 On the other hand, this will require the development of cross-cultural adaptations and translations into other languages of the LEBA scale, which should be targeted in prospective studies.
-Finally, in the future, applying the LEBA scales should not just be limited to gathering information in cross-sectional quantitative studies but allow for individual behaviour profiling.
+
+Finally, in the future, the use of the LEBA instrument need not remain restricted to gathering information in cross-sectinal quantitative studies.
+The instrument can also be used for individual behavioural profiling.
 For instance, the LEBA could be applied in a clinical context as part of Cognitive Behavioural Therapy for Insomnia (CBT-I).
@@
 Applying the LEBA scales can provide insights into light exposure-related habits on a population-based level.
-Furthermore, it can serve as a good starting point to profile individuals based on their light exposure-related behaviour determining their light consumption and timing.
+Furthermore, it can serve as a good starting point to profile individuals based on their light  exposure-related behaviour and to asseses their light
+consumption and timing.
 

### 2022-09-21 manuscript_v2.Rmd
Comments finalized

@@
   An expert panel prepared the initial 48-item pool spanning different light exposure-related behaviours.
-Responses, consisting of rating the frequency of engaging in the per-item behaviour on a 5-point Likert type scale, were collected in an online survey yielding responses from a geographically unconstrained sample (690 completed responses, 74 nationalities, 28 time zones).
+Responses, consisting of rating the frequency of engaging in the per-item behaviour on a 5-point Likert type scale, were collected in an online survey yielding responses from a geographically unconstrained sample (690 completed responses, 74 countries, 28 time zones).
 The exploratory factor analysis (EFA) on an initial subsample (n=428) rendered a five-factor solution with 25 items (Wearing blue light filters, spending time outdoors, using a phone and smartwatch in bed, using light before bedtime, using light in the morning and during daytime).
 In a confirmatory factor analysis (CFA) performed on an independent subset of participants (n=262), we removed two additional items to attain the best fit for the five-factor solution (CFI=0.95, TLI=0.95, RMSEA=0.06).
-The internal consistency reliability coefficient for the total instrument yielded McDonald’s Omega(total)=0.68.
+The internal consistency reliability coefficient for the total instrument yielded McDonald’s Omega=0.68.
 Measurement model invariance analysis between native and non-native English speakers showed our model attained the highest level of invariance (residual invariance; CFI=0.95, TLI=0.95, RMSEA=0.05).
@@
 keywords          : "light exposure, light-related behaviours, non-visual effects of light, psychometrics"
-wordcount         : "X"
+wordcount         : "6358"
 
@@
 Although clearly yielding the potential for good, these behaviours are further associated with increased electric light exposure at night and indoor time during the day, compromising the natural temporal organisation of the light-dark cycle.
-For example, in the US, an average of 87% of the time is spent in enclosed buildings [@Klepeis.2001], and more than 80% of the population is exposed to a night sky that is brighter than nights with a full moon due to electric light at night [@navara_dark_2007].
+For example, in the US, an average of 87% of the time is spent in enclosed buildings [@Klepeis.2001], and more than 80% of the population is exposed to a night sky that is brighter than nights with a full moon due to electric light at night [@navara2007dark].
 
@@
 We argue that, besides measuring received light exposure as intensity, it is also essential to understand people's behaviours with respect to different light situations.
-In many cases, humans have become their own agents regarding their exposure to light or darkness through daylight and artificial electric light, and as such people’s light exposure-related behaviours ultimately determine their light consumption and timing: People receive different light depending on their daily activities, including workplace habits, bedtime hygiene, pastime and social activities.
+In many cases, humans have become their own agents regarding their exposure to light or darkness through daylight and electric light, and as such people’s light exposure-related behaviours ultimately determine their light consumption and timing: People receive different light depending on their daily activities, including workplace habits, bedtime hygiene, pastime and social activities.
 Ultimately, in order to optimize lighting for human health and well being, better understanding of light-related behaviours will serve to identify additional points of intervention as well as to provide an added dimension to efficacy and implementation studies of novel lighting strategies.
-We argue that assessing these activities is a beneficial stepping stone for prospective behaviour change.
+We argue that assessing these activities is a beneficial stepping stone for prospective behaviour change to maintain light hygiene: a proper balance of exposures to light to maintain circadian rhythms.
 
@@
 They contain single items which probe the preference for specific light situations such as: “In the past month, how often did you need to wear dark glasses on cloudy days or indoors?” [@verriotto2017new];"I prefer rooms that are in semi-darkness."; [@bossini2006sensibilita].
-In addition, the “Pittsburgh Sleep Quality Index” [@buysse1989pittsburgh], a popular measure of sleep quality, contains questions about sleep and wake-up times, which are relevant to light exposure around bedtime.
+In addition, the “Pittsburgh Sleep Quality Index” [@buysse1989pittsburgh], is a popular measure of sleep quality.
+It contains questions about bedtime and wake-up times, which are relevant to light exposure around bedtime.
 However, none of these questionnaires provides a scalable solution to capture light exposure-related behaviour in various lighting situations.
@@
 Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it tends to deflate the estimates for Likert-type data since the calculation is based on the Pearson-correlation matrix, which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal].
-Subsequently, we reported ordinal alpha for each factor obtained in the EFA which was suggested as a better reliability estimates or ordinal data[@zumbo2007ordinal].
+Subsequently, we reported ordinal alpha for each factor obtained in the EFA which was suggested as a better reliability estimates or ordinal data [@zumbo2007ordinal].
 We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$ coefficient, which was suggested as a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
@@
 
-**Fourthly**, in a secondary analysis, we identified the educational grade level required to understand the items in our scale with the Flesch-Kincaid grade level identification method [@flesch1948new] applying the "koRpus" [@R-koRpus] package.
+**Fourthly**, in a secondary analysis, we identified the educational grade level (US education system) required to understand the items in our scale with the Flesch-Kincaid grade level identification method [@flesch1948new] applying the "koRpus" [@R-koRpus] package.
 Correspondingly, we analysed possible semantic overlap of our developed scale using the ["Semantic Scale Network" (SSN)](https://rosenbusch.shinyapps.io/semantic_net/) engine [@rosenbusch2020semantic].
@@
 By allowing the latter pair of items (30 $\&$ 41) to co-vary, the model's error variance attained an improved fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR = `r apa(fit.2[10],2,F) `).
+
+Accordingly, we accept the five-factor model with 23 items, finalizing the long Form of LEBA (see **Supplementary File 1**).
 Internal consistency ordinal $\alpha$ for the five factors of the LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`, respectively.
-
-Accordingly, we accept the five-factor model with 23 items, finalizing the long Form of LEBA (see **Supplementary File 1**).
 The Internal consistency McDonald's $\omega_t$ coefficient for the total scale yielded `r apa(rel.k[5,6],2,F)`.
@@
 A grade level identification and Semantic Scale analysis were additionally administered to assess the LEBA's (23 items) language-based accessibility and its' semantic relation to other questionnaires.
-The results of the Flesch-Kincaid grade level analysis [@flesch1948new] displayed a required educational grade level of 3.33 with age above 8.33 years, implying that the LEBA instrument should be understandable for students of grade four at least 8.33 years old.
+The results of the Flesch-Kincaid grade level analysis [@flesch1948new] displayed a required educational grade level of four (US education system) with age above 8.33 years.
 Furthermore, the
@@
 The exploratory factor analysis revealed a highly interpretable five-factor solution ("Wearing blue light filters", "Spending time outdoors", "Using phone and smartwatch in bed", "Using light before bedtime", and "Using light in the morning and during daytime") with 25 items.
-The total scale exhibited satisfactory internal consistency (McDonald's $\omega_t$=`r apa(omega$omega.tot,2,T)`).
-
-Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five-factor structure we obtained in our EFA, thus providing evidence for structural validity.(CFI=`r apa(fit.2[5],2,F)`; TLI=`r apa(fit.2[6],2,F)`; RMSEA=`r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR=`r apa(fit.2[10],2,F) `).
-In this model, we discarded two additional items (item 26 $\&$ 37 ) for possible cross-loadings.
-The internal consistency coefficients ordinal alpha for the five factors and the total scale were again satisfactory (Ordinal alpha ranged between `r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$=`r apa(rel.k[5,6],2,F)`).
+Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five-factor structure we obtained in our EFA, thus providing evidence for structural validity.(CFI=`r apa(fit.2[5],2,F)`; TLI=`r apa(fit.2[6],2,F)`; RMSEA=`r apa(fit.2[7],2,F)`).
+In this model, we discarded two more items (item 26 $\&$ 37 ) for possible cross-loadings.
+As a rule of thumb, reliability coefficients higher than .70 are regarded as “satisfactory”.
+However, at the early developmental stage, a value of .50 is considered acceptable [@dall2010developmental; @field2013discovering; @Nunnally1978].
+Thus, we confer, the internal consistency coefficients ordinal alpha for the five factors and the total scale were satisfactory (Ordinal alpha ranged between `r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$=`r apa(rel.k[5,6],2,F)`).
 
@@
 
-Lastly, we derived a short version of the LEBA (18 items) using IRT analysis.
+Often psychological measurements require application of several questionnaires simultaneously.
+Responding to several lengthy questionnaires increases the participants losing focus and becoming tried.
+To avoid these situations we  derived a short version of the LEBA (18 items) using IRT analysis.
 We fitted a graded response model to the combined EFA and CFA sample (n=`r nrow(data)`) and discarded five items (1, 25, 30, 38, & 41) with relatively flat item information curve [I($\theta$) <.20].
@@
 
-- In the five factor-solution derived from the Exploratory factor analysis, the internal consistency reliability coefficient ordinal alpha ranged between `r apa(min(alpha.tab),2,F)`-`r apa(max(alpha.tab),2,F)`, though only the fifth factor (“Using light in the morning and during daytime”) yielded internal consistency reliability coefficients below .70 ($\alpha$=`r apa((alpha.tab[5,1]),2,F)`).
-As a rule of thumb, reliability coefficients higher than .70 are regarded as “satisfactory”.
-However, for scales with less than 20 items and at the early developmental stage, a value of .50 is considered acceptable [@dall2010developmental; @field2013discovering; @Nunnally1978].
-Furthermore, the full LEBA scale exhibited satisfactory internal consistency (McDonald’s $\omega_t$=0.77), while all factors were highly interpretable regarding a common behavioural theme.
-Thus, we decided to proceed with the five-factor solution.
+- The fifth factor: "using light in the morning and during daytime" exhibited low internal consistency both in the exploratory and confirmatory factor analysis (EFA: `r apa(F5.alpha,2,F)`; CFA:`r apa(rel.k[2,5],2,F)` ).
+Since, it was above .50, considering the developmental phase of this scale we accepted the fifth factor.
 - During the post-hoc model modification, as part of the confirmatory factor analysis, we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings, as demonstrated in the data.
 However, two additional items covaried in their error variance.
-By allowing the latter pair (30 $\&$ 41) to covary, the model attained an improved fit (cf.
-**Figure 5**).
+By allowing the latter pair (30 $\&$ 41) to covary, the model attained an improved fit ( **Figure 5**).
 A possible explanation for the covariation is that many respondents might not have used a smartwatch at all, resulting in similar response patterns between these two items.

### 2022-11-14 manuscript_v2.Rmd
-gtExtra figure conflit resolved -full pdf for round 2 updated.

@@
 keywords          : "light exposure, light-related behaviours, non-visual effects of light, psychometrics"
-wordcount         : "6358"
+wordcount         : "6249"
 
@@
 @hubalek_ambulant_2006], there was a recent push toward the development and use of portable light loggers to improve ambulant light assessment and gain more insight into the NIF effects of light on human health in field conditions [@stampfli_light-dosimeter_2021; @van_duijnhoven_recommendations_2017; @webler_towards_2021; @aarts2017performance].
-Attached to different body parts (e.g., wrist; head, at eye level; chest), these devices allow for the objective measurement of individual photic exposure patterns under real-world conditions and thus are a valuable tools for field studies..
+Attached to different body parts (e.g., wrist; head, at eye level; chest), these devices allow for the objective measurement of individual photic exposure patterns under real-world conditions and thus are valuable tools for field studies.
 Nevertheless, these devices also encompass limiting factors such as potentially being intrusive (e.g., when eye-level worn), yielding the risk of getting covered (e.g., when wrist- or chest-worn) and requiring (monetary) resources and expertise for acquisition and maintenance of the devices.
@@
 For example, the “Munich Chronotype  Questionnaire” [@roenneberg2003life], a popular self-report tool for identifying chronotypes via mid-sleep times, includes questions about the individual’s typical time spent outdoors on workdays and free days.
-The Visual Light Sensitivity Questionnaire-8 [@verriotto2017new] and Photosensitivity Assessment Questionnaire (@bossini2006sensibilita) are a couple of self-report tools measuring visual light sensitivity.
+The Visual Light Sensitivity Questionnaire-8 [@verriotto2017new] and Photosensitivity Assessment Questionnaire [@bossini2006sensibilita] are a couple of self-report tools measuring visual light sensitivity.
 They contain single items which probe the preference for specific light situations such as: “In the past month, how often did you need to wear dark glasses on cloudy days or indoors?” [@verriotto2017new];"I prefer rooms that are in semi-darkness."; [@bossini2006sensibilita].
@@
 Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it tends to deflate the estimates for Likert-type data since the calculation is based on the Pearson-correlation matrix, which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal].
-Subsequently, we reported ordinal alpha for each factor obtained in the EFA which was suggested as a better reliability estimates or ordinal data [@zumbo2007ordinal].
+Subsequently, we reported ordinal alpha for each factor obtained in the EFA which was suggested as a better reliability estimates for ordinal data [@zumbo2007ordinal].
 We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$ coefficient, which was suggested as a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
@@
     subtitle = md("Items 01-24 ")) %>%
-#create groups of columns
-tab_spanner(
-  label = "Item",
-  columns = Item:Stem
-) %>%
   cols_align(
@@
   ) %>%
-
      tab_footnote(
@@
 #create groups of columns
-tab_spanner(
-  label = "Item",
-  columns = Item:Stem
-) %>%
+# tab_spanner(
+#   label = "Item",
+#   columns = Item:Stem
+# ) %>%
   cols_align(
@@
 
-Applying varimax rotation, we conducted three rounds of EFA with the initial 48 items and gradually discarded problematic items (cross-loading items and items with factor loading \<.30).
+Applying varimax rotation, we conducted three rounds of EFA with the initial 48 items and gradually discarded problematic items (cross-loading items and items with factor loading <.30).
 Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30.
@@
 The commonalities ranged between `r apa(min.com,2,F)` and `r apa(max.com, 2, F)`.
-However, the histogram of the absolute values of nonredundant residual correlations (Figure \@ref(fig:efa-plot-print)-D) displayed that `r apa(sumR,0, T)`% of correlations were greater than the absolute value of .05, indicating a possible under-factoring.
+However, the histogram of the absolute values of nonredundant residual correlations (Figure \@ref(fig:efa-plot-print)-D) displayed that `r sumR`% of correlations were greater than the absolute value of .05, indicating a possible under-factoring.
 [@desjardinsHandbookEducationalMeasurement2018].
@@
 #create groups of columns
-tab_spanner(
-  label = "Items",
-  columns = Items
-) %>%
+# tab_spanner(
+#   label = "Items",
+#   columns = Items
+# ) %>%
   tab_spanner(
@@
 ##IRT reliability (marginal reliability of scales)
-#F1.marginal.rel <- marginal_rxx(F1_fit)
-#F2.marginal.rel <-marginal_rxx(F2_fit.redu)
-#F3.marginal.rel <-marginal_rxx(F3_fit.redu)
-#F4.marginal.rel <-marginal_rxx(F4_fit.redu)
-#F5.marginal.rel <-marginal_rxx(F5_fit)
+# F1.marginal.rel <- marginal_rxx(F1_fit)
+# F2.marginal.rel <-marginal_rxx(F2_fit.redu)
+# F3.marginal.rel <-marginal_rxx(F3_fit.redu)
+# F4.marginal.rel <-marginal_rxx(F4_fit.redu)
+# F5.marginal.rel <-marginal_rxx(F5_fit)
 

### 2022-11-14 install_packages.R

@@ -1,5 +1,5 @@
 
-#maintenance 
+#maintenance
 install.packages("devtools")
 install.packages("remotes")
 install.packages("usethis")
@@ -36,7 +36,7 @@ install.packages("lavaan")
 install.packages("semPlot")
 install.packages("semTable")
 install.packages("semTools")
-
+install.packages("seminr")
 ## Correlation
 install.packages("ggcorrplot")
 
@@ -63,8 +63,7 @@ install.packages("rsvg")
 #Addins
 devtools::install_github("crsh/citr")
 install.packages("questionr")
-install.packages("wordcountaddin")
-#Others
+devtools::install_github("benmarwick/wordcountaddin", type = "source", dependencies = TRUE)#Others
 install.packages("magick")
 
 #fonts

### 2022-11-21 manuscript_v2.Rmd
Cosmetic surgery: Titile, Figure1, Figure 4, Figure 6.

@@
 ---
-title             : "_Light Exposure Behaviour Assessment (LEBA)_: Development of a novel instrument to capture light exposure-related behaviours"
+title             : "An inventory of human light exposure related behaviour"
 shorttitle        : "LEBA"
@@
 Further understanding the behaviours that influence individual photic exposure patterns may provide insight into volitional contributions to the physiological effects of light and guide bevavioral points of intervention.
-Here, we present a novel, self-reported and psychometrically validated instrument to capture light exposure-related behaviour, the Light Exposure Behaviour Assessment (LEBA).
+Here, we present a novel, self-reported and psychometrically validated inventory to capture light exposure-related behaviour, the Light Exposure Behaviour Assessment (LEBA).
 
@@
 
-  The psychometric properties of the LEBA instrument indicate the usability to measure light exposure-related behaviours.
+  The psychometric properties of the LEBA indicate the usability to measure light exposure-related behaviours.
 The instrument may offer a scalable solution to characterize behaviours that influence individual photic exposure patterns in remote samples.
-The LEBA instrument will be available under the open-access CC-BY-NC-ND license.
+The LEBA inventory will be available under the open-access CC-BY-NC-ND license.
 
@@
 
+apatheme_2=theme_bw()+ #Figure 4
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.background = element_blank(),
+        axis.text.x = element_text(size = 35),
+        axis.text.y = element_text(size = 35),
+        axis.title.x = element_text(size = 35),
+        axis.title.y = element_text(size = 35),
+        plot.title = element_text(size = 35),
+        legend.text = element_text(size =35),
+        legend.title=element_blank(),
+        axis.line.x = element_line(color='black'),
+        axis.line.y = element_line(color='black'),
+        panel.border = element_rect(color = "black",
+                                    fill = NA,
+                                    size = 1))
+
+apatheme_3=theme_bw()+ #Figure 6
+  theme(panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.background = element_blank(),
+        axis.text.x = element_text(size = 90),
+        axis.text.y = element_text(size = 90),
+        axis.title.x = element_text(size = 90),
+        axis.title.y = element_text(size = 90),
+        plot.title = element_text(size = 90),
+        legend.text = element_text(size =90),
+        legend.title=element_blank(),
+        axis.line.x = element_line(color='black'),
+        axis.line.y = element_line(color='black'),
+        panel.border = element_rect(color = "black",
+                                    fill = NA,
+                                    size = 1))
+
 ```
@@
 However, none of these questionnaires provides a scalable solution to capture light exposure-related behaviour in various lighting situations.
-To fill this gap, we here present the development process of a novel self-reported tool - the “Light Exposure Behaviour Assessment” (LEBA) - for characterizing diverse light exposure-related behaviours.
+To fill this gap, we here present the development process of a novel self-reported inventory - the “Light Exposure Behaviour Assessment” (LEBA) - for characterizing diverse light exposure-related behaviours.
 
@@
 Figure \@ref(fig:FlowchartFig) summarises the steps we followed while developing the LEBA. We conducted all analyses with the statistical software environment R [@R-base]. 
-**Firstly**, we set an item pool of 48 items with a six-point Likert-type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial scale.
+**Firstly**, we set an item pool of 48 items with a six-point Likert-type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial inventory.
 Our purpose was to capture light exposure-related behaviour.
@@
 Subsequently, we reported ordinal alpha for each factor obtained in the EFA which was suggested as a better reliability estimates for ordinal data [@zumbo2007ordinal].
-We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$ coefficient, which was suggested as a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
+We also estimated the internal consistency reliability of the total inventory using McDonald's $\omega_t$ coefficient, which was suggested as a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
 Both ordinal alpha and McDonald's $\omega_t$ coefficient values range between 0 to 1, where higher values represent better reliability.
@@
 
-**Fourthly**, in a secondary analysis, we identified the educational grade level (US education system) required to understand the items in our scale with the Flesch-Kincaid grade level identification method [@flesch1948new] applying the "koRpus" [@R-koRpus] package.
-Correspondingly, we analysed possible semantic overlap of our developed scale using the ["Semantic Scale Network" (SSN)](https://rosenbusch.shinyapps.io/semantic_net/) engine [@rosenbusch2020semantic].
+**Fourthly**, in a secondary analysis, we identified the educational grade level (US education system) required to understand the items in our inventory with the Flesch-Kincaid grade level identification method [@flesch1948new] applying the "koRpus" [@R-koRpus] package.
+Correspondingly, we analysed possible semantic overlap of our developed inventory using the ["Semantic Scale Network" (SSN)](https://rosenbusch.shinyapps.io/semantic_net/) engine [@rosenbusch2020semantic].
 The SSN detects semantically related scales and provides a cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic].
@@
 
-```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Flow chart of the LEBA (long and short form) development and evaluation. ', out.height='100%', out.width='100%'}
+```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Flow chart of the LEBA (long and short form) development and evaluation. ', out.height='50%', out.width='50%'}
 knitr::include_graphics('Figures/Figure1.png', dpi = 600 )
@@
 The present article is a fully reproducible open access "R Markdown" document.
-All code and data underlying this article -- along with two versions of the LEBA questionnaire (full and short) and online survey implementation templates on common survey platforms -- will be available under open-access licence (CC-BY-NC-ND) on a public [GitHub repository](https://github.com/leba-instrument).
+All code and data underlying this article -- along with two versions of the LEBA inventory (full and short) and online survey implementation templates on common survey platforms -- will be available under open-access licence (CC-BY-NC-ND) on a public [GitHub repository](https://github.com/leba-instrument).
 
@@
 
-## Development of the Initial Scale
+## Development of the Initial Inventory
 
@@
 The 48 items were examined independently based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by each panel member, and modifications were suggested as required.
-The author team discussed the suggestions and amended the items as indicated, thus creating a 48-item scale.
+The author team discussed the suggestions and amended the items as indicated, thus creating a 48-item inventory.
 
@@
 Table 1 summarises the survey participants' demographic characteristics.
-Only participants completing the full LEBA questionnaire were included.
+Only participants completing the full LEBA inventory were included.
 Thus, there are no missing values in the item analyses.
@@
   theme( panel.grid.major = element_blank(),
-         axis.text.x = element_text(size = 90),
-         axis.text.y = element_text(size = 90),
-         legend.text=element_text(size =90),
-         legend.title = element_text(size =90),
+         axis.text.x = element_text(size = 35),
+         axis.text.y = element_text(size = 35),
+         legend.text=element_text(size =35),
+         legend.title = element_text(size =35),
+          plot.title = element_text(size = 35),
          panel.border = element_rect(color = "black",
                                     fill = NA,
-                                    size = 1))
-        # legend.position = 'right', 
-        # legend.spacing.x = unit(0.5, 'cm'),
-        # legend.text = element_text(margin = margin(t = 10)))
-#to show pvalue in the fig add p.mat=p.mat
-# ggsave("Figures/corplot.png",corplot, width = 12, height = 8.5, dpi = 300, bg ="white")
+                                    size = 1))+labs(title = "(A)")
 
@@
   scale_x_continuous(name="Factor Number", limits=c(0, 18),breaks=c(0,6,18))+
-  geom_hline(yintercept=1, linetype = 'dashed') + apatheme +theme(legend.position = "None")
+  geom_hline(yintercept=1, linetype = 'dashed') + apatheme_2 +theme(legend.position = "None")+labs(title= "(B)")
+# ggsave("Figures/scree.plot.png",scree.plot, width = 4, height =4, dpi = 600,bg = "white", unit ="in")
+
 #text = element_text(size = 25
@@
 Hull <- hull+ ggtitle(NULL)+xlab("Factor Number")+ylab("CAF")+ aes(color = '#DC000099')+geom_point(color ='#3C5488FF',size =1)+
-  apatheme +theme(legend.position = "None") +scale_fill_identity()+
-  scale_x_continuous(breaks=c(0,5,12))
+  apatheme_2 +theme(legend.position = "None") +scale_fill_identity()+
+  scale_x_continuous(breaks=c(0,5,12))+labs(title= "(C)")
+
+# ggsave("Figures/Hull.png",Hull, width = 4, height =4, dpi = 600,bg = "white")
 
@@
 
-Inspection via the Scree plot ( Figure \@ref(fig:efa-plot-print)-B) suggested a six-factor solution, whereas the minimum average partial (MAP) method [@velicerDeterminingNumberComponents1976] (**Supplementary Table 3**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print)-C) implied a five-factor solution for the LEBA questionnaire.
+Inspection via the Scree plot ( Figure \@ref(fig:efa-plot-print)-B) suggested a six-factor solution, whereas the minimum average partial (MAP) method [@velicerDeterminingNumberComponents1976] (**Supplementary Table 3**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print)-C) implied a five-factor solution for the LEBA inventory.
 As a result, we tested both five-factor and six-factor solutions.
@@
 
-residual.plot <- ggplot(residual.data, aes(x=Residuals)) + geom_histogram(binwidth=.04, col=I("black"),fill="#00A08799") + xlim(-.2,.2)+ ylim(0,250)+apatheme +geom_vline(xintercept = .05)+
-  labs( y="Frequency")
-
-```
-
-```{r efa-plot, eval=FALSE, include=FALSE}
-#Not in use. Figure developed using illustrator.
+residual.plot <- ggplot(residual.data, aes(x=Residuals)) + geom_histogram(binwidth=.04, col=I("black"),fill="#00A08799") + xlim(-.2,.2)+ ylim(0,250)+apatheme_2 +geom_vline(xintercept = .05)+
+  labs( y="Frequency",title = "(D)")
+
+# ggsave("Figures/residual.plot.png",residual.plot, width = 4, height =4, dpi = 600,bg = "white")
+
+```
+
+```{r efa-plot, include=FALSE}
+
 #This chunk holds code for compiled factor identification plots
 
-cor.scree <- cowplot::plot_grid(corplot, scree.plot,
-                                labels = c("A", "B"),
-                                nrow =1, ncol =2,
-                                rel_widths = c(2, 1),
-                                label_fontfamily = "Arial",
-                  label_fontface = "plain")
-
-hull.residual <- cowplot::plot_grid(Hull, residual.plot,
-                                labels = c("C", "D"),
-                                nrow =1, ncol =2,
-                                                                label_fontfamily = "Arial",
-                  label_fontface = "plain")
-
-efa.plot <- cowplot::plot_grid(cor.scree, hull.residual,
-
-                                nrow =2)
-
-# efa.plot <- cowplot::plot_grid(corplot , scree.plot,Hull, residual.plot,
-#                    labels = "AUTO",
-#                    ncol=2,nrow=2, 
-#                   align = "v", 
-#                   label_fontfamily = "Arial",
-#                   label_fontface = "plain")
-ggsave("Figures/Figure4.png",efa.plot, width = 7, height = 8, dpi = 600, bg = "white")
+library(patchwork)
+
+# all_plot <-corplot|(Hull|scree.plot)/residual.plot
+# ggsave("Figures/all_plot.png",all_plot, width = 16, height = 8, dpi = 600, bg = "white")
+
+all_plot_2 <-corplot|(scree.plot|Hull)/residual.plot
+# all_plot_3 <-corplot|(scree.plot|Hull)/(residual.plot|plot_spacer())
+
+ggsave("Figures/Figure4.png",all_plot_2, width = 8, height = 4, dpi = 600, bg = "white", units = "in")
+
 ```
@@
 
-```{r efa-plot-print, fig.align= 'center', fig.cap='(ref:efa-plot-print)',  warning=FALSE,  out.height='60%', out.width='110%'}
+```{r efa-plot-print, fig.align= 'center', fig.cap='(ref:efa-plot-print)',  warning=FALSE,  out.height='130%', out.width='100%'}
 
@@
 Upon re-inspection, we recognized these items to be negatively correlated to the respective factor, and thus, we reverse-scored these two items in the CFA analysis.
-The internal consistency coefficient McDonald's $\omega_t$ for the total scale was `r apa(omega$omega.tot,2,T)`.
+The internal consistency coefficient McDonald's $\omega_t$ for the total inventory was `r apa(omega$omega.tot,2,T)`.
 
@@
 img1 <- png::readPNG("Figures/EFAplot.png")
+ggsave("Figures/EFAfull.png",EFAplot.2, width = 6, height =7, dpi = 1200)
 
@@
 Internal consistency ordinal $\alpha$ for the five factors of the LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`, respectively.
-The Internal consistency McDonald's $\omega_t$ coefficient for the total scale yielded `r apa(rel.k[5,6],2,F)`.
+The Internal consistency McDonald's $\omega_t$ coefficient for the total inventory yielded `r apa(rel.k[5,6],2,F)`.
 Figure \@ref(fig:figcfa) depicts the obtained CFA structure, while  **Supplementary Figure 2** depicts the data distribution and endorsement pattern of the retained 23 items in our CFA sample.
@@
 ## Developing a Short Form of LEBA: IRT-Based Analysis
-In order to derive a short form of the LEBA instrument, we fitted each factor of the LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n=690).
-The resulting item discrimination parameters of the scale fell into categories of "very high" (10 items), "high" (4 items), "moderate" (4 items), and "low" ( 5 items), indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**).
+In order to derive a short form of the LEBA inventory, we fitted each factor of the LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n=690).
+The resulting item discrimination parameters of the inventory fell into categories of "very high" (10 items), "high" (4 items), "moderate" (4 items), and "low" ( 5 items), indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**).
 An examination of the item information curve (**Supplementary Figure 3**) revealed five items (1, 25, 30, 38, & 41) with relatively flat curves (I($\theta$) \<.20).
@@
 F1.tic <- ggplot(F1.test.data, aes(x=Theta, y=F1.T1)) +
-  geom_line()+apatheme+
+  geom_line()+apatheme_3+
   labs(y="Test Information", title = "F1: Wearing blue light filters")+geom_area()+theme(legend.position = "none")+
@@
 F2.tic <- ggplot(F2.test.data, aes(x=Theta, y=F2.T1)) +
-  geom_line()+apatheme+
+  geom_line()+apatheme_3+
   labs(y="Test Information", title = "F2: Spending time outdoors")+ylim(0,8)+
@@
 F3.tic <- ggplot(F3.test.data, aes(x=Theta, y=F3.T1)) +
-  geom_line()+apatheme+
+  geom_line()+apatheme_3+
   labs(y="Test Information", title = "F3: Using phone and smartwatch in bed")+ylim(0,8)+
@@
 F4.tic <- ggplot(F4.test.data, aes(x=Theta, y=F4.T1)) +
-  geom_line()+apatheme+
+  geom_line()+apatheme_3+
   labs(y="Test Information", title = "F4: Using light before bedtime")+
@@
 F5.tic <- ggplot(F5.test.data, aes(x=Theta, y=F5.T1)) +
-  geom_line()+apatheme+
+  geom_line()+apatheme_3+
   labs(y="Test Information", title = "F5:Using light in the morning and during daytime") +ylim(0,8)+geom_area()+aes(fill =  "#B09C8599")+theme(legend.position = "none")+
@@
                                    F4.tic,F5.tic,
-                   labels = "AUTO",
+                   labels = c("(A)", "(B)", "(C)", "(D)", "(E)"),
                      align="v",
                      ncol = 3,
-                     label_size = 60,
+                     label_size = 90,
                      label_fontfamily = "Arial",
@@
 
-```{r Testinfo, fig.env = "sidewaysfigure", fig.cap="Test information curves for the five factors of LEBA: (a) wearing blue light filters (b) spending time outdoors (c) using a phone and smartwatch in bed (d) using light before bedtime (e) using light in the morning and during daytime.
+```{r Testinfo,  fig.cap="Test information curves for the five factors of LEBA: (A) wearing blue light filters (B) spending time outdoors (C) using a phone and smartwatch in bed (D) using light before bedtime (E) using light in the morning and during daytime.
 Along the x-axis, we plotted the underlying latent trait continuum for each factor.
@@
 As Figure \@ref(fig:Testinfo) illustrates, the TICs of the first and fifth factors peaked on the right side of the centre of their latent traits, while the TICs of the other three factors were roughly centred on the respective trait continuum ($\theta$).
-This points out that the LEBA short-scale estimates the light exposure-related behaviour most precisely near the centre of the trait continuum for the second, third and fourth factors and, in contrast, to the right of the centre for the first and fifth factors [@bakerBasicsItemResponse2017].
+This points out that the LEBA short-form estimates the light exposure-related behaviour most precisely near the centre of the trait continuum for the second, third and fourth factors and, in contrast, to the right of the centre for the first and fifth factors [@bakerBasicsItemResponse2017].
 
@@
 To our knowledge, there is no questionnaire in existence that captures behaviours that modify light exposure across different scenarios in a comprehensive way.
-With the present LEBA tool, we have developed two versions of a self-report scale that can capture light exposure-related behaviours in multiple dimensions.
+We have developed two versions of a self-report inventory-LEBA, that can capture light exposure-related behaviours in multiple dimensions.
 
@@
 However, at the early developmental stage, a value of .50 is considered acceptable [@dall2010developmental; @field2013discovering; @Nunnally1978].
-Thus, we confer, the internal consistency coefficients ordinal alpha for the five factors and the total scale were satisfactory (Ordinal alpha ranged between `r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$=`r apa(rel.k[5,6],2,F)`).
+Thus, we confer, the internal consistency coefficients ordinal alpha for the five factors and the total inventory were satisfactory (Ordinal alpha ranged between `r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$=`r apa(rel.k[5,6],2,F)`).
 
@@
 - The fifth factor: "using light in the morning and during daytime" exhibited low internal consistency both in the exploratory and confirmatory factor analysis (EFA: `r apa(F5.alpha,2,F)`; CFA:`r apa(rel.k[2,5],2,F)` ).
-Since, it was above .50, considering the developmental phase of this scale we accepted the fifth factor.
+Since, it was above .50, considering the developmental phase of this inventory we accepted the fifth factor.
+This particular factor captures our behaviour related to usages of light in the morning and daytime.
+Since, light exposure during morning and daytime influences our alertness and cognition [@lok2018light; @siraji2021effects], we deemed capturing these behaviours is essential for the sake of completeness of our inventory.
+However, the possibility of improving the reliability should be investigated further by adding more appropriate and relevant items to this factor.
+
 - During the post-hoc model modification, as part of the confirmatory factor analysis, we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings, as demonstrated in the data.
@@
 Thus, though rather unconventional, we decided to accept this post-hoc modification to our five-factor model.
-- The habitual patterns queried in the developed scales might not exhaustively represent all relevant light-exposure-related behaviours.
+- The habitual patterns queried in the developed inventory might not exhaustively represent all relevant light-exposure-related behaviours.
 For instance, it is conceivable that additional light-related activities not included in the LEBA depend on the respondents' profession/occupation, geographical context, and socio-economic status.
 However, we generated the initial item pool with an international team of researchers and followed a thorough psychometric analysis.
-Therefore, we are confident that the developed LEBA scales can serve as a good starting point for exploring the light exposure related behaviours in more depth and inform room for modification of light exposure-related behaviour to improve light hygiene.
+Therefore, we are confident that the developed LEBA inventory can serve as a good starting point for exploring the light exposure related behaviours in more depth and inform room for modification of light exposure-related behaviour to improve light hygiene.
 - As with all studies relying on retrospective self-report data, individuals filling in the LEBA may have difficulties precisely recalling the inquired light-related behaviours.
@@
 In contrast to directly assessing light properties via self-report, we assume that reporting behaviours might be more manageable for inexperienced laypeople, as the latter does not rely on existing knowledge about light sources.
-The accessibility of the LEBA is also reflected in the “grade level identification” findings suggesting a minimum age of 8.33 years and an educational grade of four or higher.
+The comprehensibility of the LEBA is also reflected by the Flesch-Kincaid grade level identification method [@flesch1948new] that suggested a minimum age of 8.33 years and an educational grade of four or higher (US grading system).
 We argue that measuring light-related behaviours via self-report is crucial because these behaviours will hardly be as observable by anyone else or measurable with other methods (like behavioural observations) with reasonable effort.
@@
 
-To our knowledge, the LEBA is the first questionnaire characterising light exposure-related behaviour in a scalable manner.
+To our knowledge, the LEBA is the first inventory characterising light exposure-related behaviour in a scalable manner.
 Thus, estimating convergent validity with similar subjective scales was impossible.
@@
 As the current data is limited to our international online survey context, future research should apply the LEBA across more variable populations and contexts.
-On the other hand, this will require the development of cross-cultural adaptations and translations into other languages of the LEBA scale, which should be targeted in prospective studies.
+On the other hand, this will require the development of cross-cultural adaptations and translations into other languages of the LEBA, which should be targeted in prospective studies.
 
@@
 
-With the "Light exposure behaviour assessment"(LEBA), we developed a novel, internally consistent and structurally valid 23-item self-report scale for capturing light exposure-related behaviour in five scalable factors.
+With the "Light exposure behaviour assessment"(LEBA), we developed a novel, internally consistent and structurally valid 23-item self-report inventory for capturing light exposure-related behaviour in five scalable factors.
 In addition, an 18-item short-form of the LEBA was derived using IRT analysis, yielding adequate coverage across the underlying trait continuum.
-Applying the LEBA scales can provide insights into light exposure-related habits on a population-based level.
-Furthermore, it can serve as a good starting point to profile individuals based on their light  exposure-related behaviour and to asseses their light
-consumption and timing.
+Applying the LEBA inventory can provide insights into light exposure-related habits on a population-based level.
+Furthermore, it can serve as a good starting point to profile individuals based on their light  exposure-related behaviour and to asseses their light consumption and timing.
 

### 2022-11-22 manuscript_v2.Rmd
added missing attention check items as bullet points

@@
 Participants were further asked to confirm that they participated in the survey for the first time.
-Additionally, five attention check items (e.g., "We want to make sure you are paying attention.
-What is 4+5?") were included among the questionnaires to ensure high data quality.
 All questions incorporating retrospective recall were aligned to a "past four weeks" period.
+Additionally, four attention check items  were included among the questionnaires to ensure high data quality, with the following phrasing:
+- We want to make sure you are paying attention. What is 4+5?
+- [...] Please select "Strongly disagree" here.
+- [...] Please type in "nineteen" as a number.
+- [...] Please select "Does not apply/I don't know." here.
 

### 2022-12-22 manuscript_v2.Rmd
Figure 4 caption changed
Knitted by MS

@@
   - id            : "12"
-    institution   : "University of Oxford, Department of Experimental Psychology, Oxford, United Kingdom"
+    institution   : "TUM Institute of Advanced Study (TUM-IAS), Technical University of Munich, Garching, Germany"
   - id            : "*"
@@
   Light exposure is an essential driver of health and well-being, and individual behaviours during rest and activity modulate physiologically-relevant aspects of light exposure.
-Further understanding the behaviours that influence individual photic exposure patterns may provide insight into volitional contributions to the physiological effects of light and guide bevavioral points of intervention.
+Further understanding the behaviours that influence individual photic exposure patterns may provide insight into the volitional contributions to the physiological effects of light and guide bevavioral points of intervention.
 Here, we present a novel, self-reported and psychometrically validated inventory to capture light exposure-related behaviour, the Light Exposure Behaviour Assessment (LEBA).
@@
 The instrument may offer a scalable solution to characterize behaviours that influence individual photic exposure patterns in remote samples.
-The LEBA inventory will be available under the open-access CC-BY-NC-ND license.
+The LEBA inventory is  available under the open-access CC-BY-NC-ND license.
+
+  Instrument webpage: https://leba-instrument.org/
+  GitHub repository containing this manuscript: https://github.com/leba-instrument/leba-manuscript
 
@@
 Light exposure received by the eyes affects many facets of human health, well-being, and performance beyond visual sensation and perception [@boyce_light_2022].
-The so-called non-image-forming (NIF) effects of light comprise light’s circadian and non-circadian influence on several physiological and psychological functions, such as the secretion of melatonin, sleep, mood, pupil size, body temperature, alertness, and higher cognitive functions [@Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020].
-With the introduction of artificial electric light, human behaviour has become somewhat independent of the natural light-dark cycle – people can now frequently choose when to be exposed to light or darkness.
+The non-image-forming (NIF) effects of light comprise light’s circadian and non-circadian influence on several physiological and psychological functions, such as the secretion of melatonin, sleep, mood, pupil size, body temperature, alertness, and higher cognitive functions [@Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020].
+
+With the introduction of artificial electric light, human behaviour has become dissociated from the light-dark cycle given by solar radiation.
+People can now frequently choose when to be exposed to light or darkness.
 For example, they can decide whether to go outdoors and seek out sunlight, switch on/off light-emitting devices, use certain types of lights at home, or avoid specific light environments altogether.
-Additionally, when light sources can not be directly manipulated, sought out, or avoided (for example, at school, work, or in public places), there is still potential leeway to influence them behaviourally, for instance, by wearing sunglasses, directing one’s gaze away or supplementing the situation with additional light sources.
+Additionally, when light sources cannot be directly manipulated, sought out, or avoided (for example, at school, work, or in public places), there is still potential leeway to influence personal light exposure behaviourally, for instance, by wearing sunglasses, directing one’s gaze away or supplementing the situation with additional light sources.
 Although clearly yielding the potential for good, these behaviours are further associated with increased electric light exposure at night and indoor time during the day, compromising the natural temporal organisation of the light-dark cycle.
@@
 
-An extensive body of scientific evidence suggests that the imbalance of light and dark exposure disrupts humans’ light-dependent physiological systems [@Lunn.2017].
-Subsequently, this disruption gives rise to a series of adverse health consequences, including the alteration of hormonal rhythms, increased cancer rates, cardiovascular diseases, and metabolic disorders, such as obesity and type II diabetes [@Lunn.2017; @navara2007dark; @Chellappa.2019].
+An extensive body of scientific evidence suggests that improper light exposure may be disruptive for health and well-being, giving rise to a series of adverse consequences, including the alteration of hormonal rhythms, increased cancer rates, cardiovascular diseases, and metabolic disorders, such as obesity and type II diabetes [@Lunn.2017; @navara2007dark; @Chellappa.2019].
 These findings have sparked a significant call for assessment and guidance regarding healthy light exposure as exemplified by a recently published set of consensus-based experts’ recommendations with specific requirements for indoor light environments during the daytime, evening, and nighttime [@Brown.2022].
+
 Furthermore, building on earlier attempts [e.g.
 @hubalek_ambulant_2006], there was a recent push toward the development and use of portable light loggers to improve ambulant light assessment and gain more insight into the NIF effects of light on human health in field conditions [@stampfli_light-dosimeter_2021; @van_duijnhoven_recommendations_2017; @webler_towards_2021; @aarts2017performance].
-Attached to different body parts (e.g., wrist; head, at eye level; chest), these devices allow for the objective measurement of individual photic exposure patterns under real-world conditions and thus are valuable tools for field studies.
+Attached to different body parts (e.g., wrist; head, at eye level; chest), these light loggers allow for the objective measurement of individual photic exposure patterns under real-world conditions and thus are valuable tools for field studies.
 Nevertheless, these devices also encompass limiting factors such as potentially being intrusive (e.g., when eye-level worn), yielding the risk of getting covered (e.g., when wrist- or chest-worn) and requiring (monetary) resources and expertise for acquisition and maintenance of the devices.
@@
 On the other hand, several attempts have been made to quantify received light exposure subjectively with self-report questionnaires (**Supplementary Table 1**), bypassing the cost and intrusiveness issues.
-However, subjective light intensity assessments pose a new set of challenges: The human visual system constantly adapts to brightness [@hurvich_perception_1966], while the human non-visual light processing works largely subconsciously [@allen_exploiting_2018], making the self-report assessment of light properties potentially quite challenging.
+However, subjective light intensity assessments pose a new set of challenges: The human visual system constantly adapts to brightness [@hurvich_perception_1966], while the signals underlying the non-visual effects of light are independent from perception [@allen_exploiting_2018], making the self-report assessment of light properties challenging.
 Retrospectively recalling the properties of a light source can further complicate such subjective evaluations.
 Moreover, measuring light properties alone does not yield any information about how individuals might behave differently regarding diverse light environments such  as work, home or outdoors.
-These measurement limitations point to a couple of research challenges we aim to take on here: How can we gain insight into light exposure patterns via self-report but circumvent directly inquiring about the specific properties and intensity of a light source?
+
+These measurement limitations point to a couple of research challenges which we adressed here: How can we gain insight into light exposure patterns via self-report but circumvent directly inquiring about the specific properties and intensity of a light source?
 And how can we simultaneously assess how people habitually interact with the received light?
@@
 However, none of these questionnaires provides a scalable solution to capture light exposure-related behaviour in various lighting situations.
-To fill this gap, we here present the development process of a novel self-reported inventory - the “Light Exposure Behaviour Assessment” (LEBA) - for characterizing diverse light exposure-related behaviours.
+To fill this gap, we here present the development process of a novel self-reported inventory - the Light Exposure Behaviour Assessment (LEBA) - for characterizing diverse light exposure-related behaviours.
 
@@
 
-## Data Collection
+## Data collection
 
@@
 
-## Analytic Strategy
+## Analytic strategy
 
@@
 
-## Ethical Approval
+## Ethical approval
 
@@
 
-## Data Availability
+## Data availability
 
 The present article is a fully reproducible open access "R Markdown" document.
-All code and data underlying this article -- along with two versions of the LEBA inventory (full and short) and online survey implementation templates on common survey platforms -- will be available under open-access licence (CC-BY-NC-ND) on a public [GitHub repository](https://github.com/leba-instrument).
+All code and data underlying this article -- along with two versions of the LEBA inventory (full and short) and online survey implementation templates on common survey platforms -- is available under an open-access licence (Creative Commons CC-BY-NC-ND) on a public [GitHub repository](https://github.com/leba-instrument).
 
@@
 
-## Development of the Initial Inventory
-
-An expert panel comprising all authors -- researchers from chronobiology, light research, neuroscience and psychology -- developed a comprehensive item pool of 48 items.
-The 48 items were examined independently based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by each panel member, and modifications were suggested as required.
+## Development of the initial item pool
+
+An expert panel comprising all authors -- researchers from chronobiology, light research, neuroscience and psychology in different geographical contexts -- developed a comprehensive item pool of 48 items.
+The 48 items were examined independently based on their relevance and representativeness of the construct light-exposure related behaviour by each panel member, and modifications were suggested as required.
 The author team discussed the suggestions and amended the items as indicated, thus creating a 48-item inventory.
 
-## Anonymous Online Survey
+## Measurement of light exposure behaviour in an online sample
 
@@
 Thus, there are no missing values in the item analyses.
-(XXX??) participants were excluded from the analysis due to not passing at least one of the "attention check" items.
 For the EFA, a sample of at least 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013].
@@
 4.9 % inter-item correlation coefficients were higher than \|.30\|.
-'x' denotes a non-significant item-total correlation.
+'x' denotes non-significant correlation.
 (B) The Scree plot suggested six factors.
@@
 
-## Known Limitations
+## Known limitations
 
@@
 
-- The fifth factor: "using light in the morning and during daytime" exhibited low internal consistency both in the exploratory and confirmatory factor analysis (EFA: `r apa(F5.alpha,2,F)`; CFA:`r apa(rel.k[2,5],2,F)` ).
+The fifth factor, "using light in the morning and during daytime", exhibited low internal consistency both in the exploratory and confirmatory factor analysis (EFA: `r apa(F5.alpha,2,F)`; CFA:`r apa(rel.k[2,5],2,F)` ).
 Since, it was above .50, considering the developmental phase of this inventory we accepted the fifth factor.
@@
 
-- During the post-hoc model modification, as part of the confirmatory factor analysis, we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings, as demonstrated in the data.
+During the post-hoc model modification, as part of the confirmatory factor analysis, we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings, as demonstrated in the data.
 However, two additional items covaried in their error variance.
@@
 Thus, though rather unconventional, we decided to accept this post-hoc modification to our five-factor model.
-- The habitual patterns queried in the developed inventory might not exhaustively represent all relevant light-exposure-related behaviours.
+
+The habitual patterns queried in the developed inventory might not exhaustively represent all relevant light-exposure-related behaviours.
 For instance, it is conceivable that additional light-related activities not included in the LEBA depend on the respondents' profession/occupation, geographical context, and socio-economic status.
@@
 Therefore, we are confident that the developed LEBA inventory can serve as a good starting point for exploring the light exposure related behaviours in more depth and inform room for modification of light exposure-related behaviour to improve light hygiene.
-- As with all studies relying on retrospective self-report data, individuals filling in the LEBA may have difficulties precisely recalling the inquired light-related behaviours.
+
+As with all studies relying on retrospective self-report data, individuals filling in the LEBA may have difficulties precisely recalling the inquired light-related behaviours.
 In the interest of bypassing a substantial memory component, we limited the recall period to four weeks and chose response options that do not require exact memory recall.
@@
 By this route, one could study how the (subjectively measured) light exposure-related behavioural patterns translate into (objectively measured) received light exposure.
+
 Additionally, developing daily recall scales of light-related behaviour could provide a more detailed behavioural assessment to supplement the LEBA's broader (four-week) measurement approach.
 Comparing the LEBA scores to 24-hour recall scores could provide helpful information about how light exposure-related behaviour assessment is related between different time perspectives.
+
 Moreover, light-exposure-related behaviour might depend on the respondents' profession, geographical location, housing conditions, socio-economic status, or other contextual factors.
@@
 
-With the "Light exposure behaviour assessment"(LEBA), we developed a novel, internally consistent and structurally valid 23-item self-report inventory for capturing light exposure-related behaviour in five scalable factors.
+Here, we developed a novel, internally consistent and structurally valid 23-item self-report inventory for capturing light exposure-related behaviour in five scalable factors.
 In addition, an 18-item short-form of the LEBA was derived using IRT analysis, yielding adequate coverage across the underlying trait continuum.

### 2023-01-03 install_packages.R
install command changed

@@ -65,7 +65,7 @@ devtools::install_github("crsh/citr")
 install.packages("questionr")
 devtools::install_github("benmarwick/wordcountaddin", type = "source", dependencies = TRUE)#Others
 install.packages("magick")
-
+devtools::install_github("paleolimbot/rbbt")
 #fonts
 install.packages("extrafont")
 extrafont::fonttable()

### 2023-01-03 manuscript_v2.Rmd
Result section updated

@@
 An expert panel comprising all authors -- researchers from chronobiology, light research, neuroscience and psychology in different geographical contexts -- developed a comprehensive item pool of 48 items.
-The 48 items were examined independently based on their relevance and representativeness of the construct light-exposure related behaviour by each panel member, and modifications were suggested as required.
+Face validity examination of all 48 items by each panel member indicated all items were relevant and appropriate and a few modifications were suggested as required.
 The author team discussed the suggestions and amended the items as indicated, thus creating a 48-item inventory.
@@
 
-Figures \@ref(fig:efagtPic1) and \@ref(fig:efagtPic2) summarise the response patterns of our total sample (n=`r nrow(sem.data)`) for all 48 items.
+Figures \@ref(fig:efagtPic1) and \@ref(fig:efagtPic2) depict the response patterns of our total sample (n=`r nrow(sem.data)`) for all 48 items.
 Most of the items appeared skewed.

### 2023-01-03 manuscript_v2.Rmd
Univariate and multivariate normality

@@
 Figures \@ref(fig:efagtPic1) and \@ref(fig:efagtPic2) depict the response patterns of our total sample (n=`r nrow(sem.data)`) for all 48 items.
-Most of the items appeared skewed.
-The Shapiro–Wilk test of univariate normality [@shapiroAnalysisVarianceTest1965] and Mardia test of multivariate normality [@mardiaMeasuresMultivariateSkewness1970] indicated that our data violated both univariate and multivariate normality.
-The multivariate skewness was `r printnum(mardia.all.data$b1p)` (p \<0.001), and the multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p \<0.001).
+Most of the items appeared skewed and violated univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality ([@mardiaMeasuresMultivariateSkewness1970]; multivariate skewness=`r printnum(mardia.all.data$b1p)`, p<0.001); multivariate kurtosis=`r printnum(mardia.all.data$b2p)`,p<0.001).
 

### 2023-01-03 manuscript_v2.Rmd
EFA univariate and multivariate

@@
 **Supplementary Figure 1** summarises the univariate descriptive statistics for the 48 items in the EFA sample (n=`r nrow(EFA.data)`).
-Likewise, our data violated the univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970].
-The multivariate skew was `r printnum(mardia$b1p)` (p \<0.001) and the multivariate kurtosis yielded a value of `r printnum(mardia$b2p)` (p \<0.001).
+Likewise, our data violated the both univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions ([@mardiaMeasuresMultivariateSkewness1970]; multivariate skew=`r printnum(mardia$b1p)`, p<0.001; multivariate kurtosis= `r printnum(mardia$b2p)`,p <0.001).
 The corrected item-total correlation ranged between `r apa(low.r.corec,2,F)` and `r apa(high.r.corec,2,F)`.

### 2023-01-03 manuscript_v2.Rmd
EFA assumptions

@@
 
-We checked the sampling adequacy by applying Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy on the EFA sample (n=`r nrow(EFA.data)`) [@kaiserIndexFactorialSimplicity1974].
-The overall KMO value for 48 items was `r printnum(KMO$MSA)`, which exceeded the cut-off value (.50), indicating an adequate sample size [@hutchesonMultivariateSocialScientist1999].
-Additionally, Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`)=`r apa(bartlet$chisq, 2, T)`, p \< .001 implied that the correlations between items were adequate for conducting the EFA.
-However, only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than \|.30\|., and the inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`.
+We checked the post-hoc sampling adequacy by applying Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy on the EFA sample (n=`r nrow(EFA.data)`) [@kaiserIndexFactorialSimplicity1974].
+KMO>0.50 would indicate adequate sample size [@hutchesonMultivariateSocialScientist1999].
+Results indicated that we had an adequate sample size (KMO=`r printnum(KMO$MSA)`).
+Additionally, we investigate the quality of the correlation matrix by Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954] prior to conduct the EFA.
+Results indicated that the correlatio matrix was adequate to conduct EFA ($\chi^2$ (`r bartlet$df`)=`r apa(bartlet$chisq, 2, T)`, p< .001).
+However,`r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than |0.30|, and the inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`.
 Figure \@ref(fig:efa-plot-print)-A depicts the respective correlation matrix.

### 2023-01-03 manuscript_v2.Rmd
EFA results

@@
 We checked the post-hoc sampling adequacy by applying Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy on the EFA sample (n=`r nrow(EFA.data)`) [@kaiserIndexFactorialSimplicity1974].
-KMO>0.50 would indicate adequate sample size [@hutchesonMultivariateSocialScientist1999].
+KMO>.50 would indicate adequate sample size [@hutchesonMultivariateSocialScientist1999].
 Results indicated that we had an adequate sample size (KMO=`r printnum(KMO$MSA)`).
 Additionally, we investigate the quality of the correlation matrix by Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954] prior to conduct the EFA.
-Results indicated that the correlatio matrix was adequate to conduct EFA ($\chi^2$ (`r bartlet$df`)=`r apa(bartlet$chisq, 2, T)`, p< .001).
+Results indicated that the correlation matrix was adequate to conduct EFA ($\chi^2$ (`r bartlet$df`)=`r apa(bartlet$chisq, 2, T)`, p< .001).
 However,`r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than |0.30|, and the inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`.
@@
 
-Inspection via the Scree plot ( Figure \@ref(fig:efa-plot-print)-B) suggested a six-factor solution, whereas the minimum average partial (MAP) method [@velicerDeterminingNumberComponents1976] (**Supplementary Table 3**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print)-C) implied a five-factor solution for the LEBA inventory.
-As a result, we tested both five-factor and six-factor solutions.
+While investigating the optimum factor number for the LEBA inventory, the Scree plot ( Figure \@ref(fig:efa-plot-print)-B) revealed a six-factor solution, whereas the minimum average partial (MAP) method [@velicerDeterminingNumberComponents1976] (**Supplementary Table 3**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print)-C) implied a five-factor solution.
+Hence, we tested both five-factor and six-factor solutions.
 
@@
 (ref:efa-plot-print) (A) Inter-item polychoric correlation coefficients for the 48 items.
-4.9 % inter-item correlation coefficients were higher than \|.30\|.
+4.9 % inter-item correlation coefficients were higher than |.30|.
 'x' denotes non-significant correlation.
@@
 (C) Hull method indicated that five factors were required to balance the model fit and number of parameters.
-(D) The histogram of nonredundant residual correlations indicated that 26% of inter-item correlations were higher than .05, hinting at a possible under-factoring.
+(D) The histogram of nonredundant residual correlations in the five-factor model indicated that 26% of inter-item correlations were higher than .05, hinting at a possible under-factoring.
 
@@
 
-Applying varimax rotation, we conducted three rounds of EFA with the initial 48 items and gradually discarded problematic items (cross-loading items and items with factor loading <.30).
-Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30.
-Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items.
-The absolute values of the factor-loadings ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)`, indicating strong coefficients.
-The commonalities ranged between `r apa(min.com,2,F)` and `r apa(max.com, 2, F)`.
-However, the histogram of the absolute values of nonredundant residual correlations (Figure \@ref(fig:efa-plot-print)-D) displayed that `r sumR`% of correlations were greater than the absolute value of .05, indicating a possible under-factoring.
+We conducted iterative EFA with varimax rotation, starting with the initial 48 items and gradually discarded problematic items (cross-loading items and items with factor loading <.30).
+After, three rounds of EFA we found a five-factor EFA solution with 25 items with all factor-loading >.30 and no cross-loading >.30.
+Table \@ref(tab:EFATable) displays the factor-loading ($\lambda$) and communality of the items.
+Both factor loadings and commonalities advocate to accept this five-factor solution ( |$\lambda$|= `r apa(min.loadings,2,F)` - `r apa(max.loadings, 2, F)`; commonalities= `r apa(min.com,2,F)` - `r apa(max.com, 2, F)`).
+However, the histogram of the absolute values of nonredundant residual correlations (Figure \@ref(fig:efa-plot-print)-D) displayed that `r sumR`% of correlations were greater >|.05|, indicating a possible under-factoring.
 [@desjardinsHandbookEducationalMeasurement2018].
@@
 
-In the five-factor solution, the first factor contained three items and explained `r apa(var1,2,F)`% of the total variance with an internal reliability coefficient ordinal $\alpha$ = `r apa(F1.alpha,2,F)`.
-All the items in this factor encapsulated the individual's preference for using blue light filters in different light environments.
-The second factor contained six items and explained `r apa(var2,2,F)`% of the total variance with an internal reliability coefficient ordinal $\alpha$ = `r apa(F2.alpha,2,F)`.
-Items under this factor incorporated the individuals' hours spent outdoors.
-The third factor contained five items and explained `r apa(var3,2,F)`% of the total variance.
-Items under this factor covered the specific behaviours of using a phone and smartwatch in bed.
-The internal consistency reliability coefficient was ordinal $\alpha$ = `r apa(F3.alpha,2,F)`.
-The fourth factor comprised five items and explained `r apa(var4,2,F)`% of the total variance with an internal consistency coefficient, ordinal $\alpha$ = `r apa(F4.alpha,2,F)`.
-These five items investigated the behaviours related to the individual's light exposure before bedtime.
-The fifth factor encompassed six items and explained `r apa(var5,2,F)`% of the total variance.
-This factor captured the individual's morning and daytime light exposure-related behaviour.
-The internal consistency reliability yielded ordinal $\alpha$ = `r apa(F5.alpha,2,F)`.
-
-Lastly, we examined the factor's interpretability in the five-factor solution and weighed it against the psychometric properties as we considered it essential to attain a balance between the two.
-As we deemed the five derived factors interpretable and relevant concerning our aim to capture light exposure-related behaviour, we retained all of them with 25 items for our confirmatory factor analysis (CFA), despite the apparent lower reliability of the fifth factor.
+In the five-factor solution, the first factor had three items and encapsulated the individual's preference for using blue light filters in different light environments.
+The second factor contained six items that incorporated the individuals' hours spent outdoors.
+The third factor contained five items that looked into specific behaviours of using a phone and smartwatch in bed.
+The fourth factor comprised five items investigated the other behaviours related to the individual's electric light exposure before bedtime.
+lastly, the fifth factor encompassed six items capturing the individual's morning and daytime light exposure-related behaviour.
+These five factors explains `r apa(var1,2,F)`%, `r apa(var2,2,F)`%, `r apa(var3,2,F)`%, `r apa(var4,2,F)`%, `r apa(var5,2,F)`% of of the total variance in individual's light exposure related behaviours respectively and factors exhibited excellent to satisfactory reliability (ordinal $\alpha$= `r apa(F1.alpha,2,F)`, `r apa(F2.alpha,2,F)`, `r apa(F3.alpha,2,F)`, `r apa(F4.alpha,2,F)`, `r apa(F5.alpha,2,F)` respectively).
+The entire inventory also exhibited satisfactory reliability ($\omega_t$=`r apa(omega$omega.tot,2,T)`).
+While making the judgement of accepting this five-factor solution we considered both factor;s interpretability and their psychometric properties.
+We deemed the five derived factors as highly interpretable  and relevant concerning our aim to capture light exposure-related behaviour, we retained all of them with 25 items.
 Two of the items showed negative factor-loading (item 08: `r Hmisc::label(data$slypos_leba_08)` and item 37: `r Hmisc::label(data$slypos_leba_37)`).
-Upon re-inspection, we recognized these items to be negatively correlated to the respective factor, and thus, we reverse-scored these two items in the CFA analysis.
-The internal consistency coefficient McDonald's $\omega_t$ for the total inventory was `r apa(omega$omega.tot,2,T)`.
+Upon re-inspection, we recognized these items to be negatively correlated to the respective factor, and thus, we reverse-scored these two items.
 

### 2023-01-03 manuscript_v2.Rmd
CFA updated

@@
 
-Table \@ref(tab:tabCfa) compares the CFA fit indices of the original CFA five-factor model with 25 and the post-hoc modified model with 23 items, respectively.
-The 25-item model attained an acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`; RMSEA = `r apa(fit.1[7],2,F)` [`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constraints on item pairs 32-33 [item 32: I dim my mobile phone screen within 1 hour before attempting to fall asleep; item 33: I dim my computer screen within 1 hour before attempting to fall asleep] and 16-17 [item 16: I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day; item 17: I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day].
+CFA results (Table \@ref(tab:tabCfa)) indicated that the five-factor structure fitted to the 25-item LEBA Inventory attained an acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`; RMSEA = `r apa(fit.1[7],2,F)` [`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constraints on item pairs 32-33 [item 32: I dim my mobile phone screen within 1 hour before attempting to fall asleep; item 33: I dim my computer screen within 1 hour before attempting to fall asleep] and 16-17 [item 16: I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day; item 17: I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day].
 Item pair 32-33 describes the preference for dimming the electric devices' brightness before bedtime, whereas item pair 16-17 represents the use of blue filtering or coloured glasses during the daytime.
@@
 Nevertheless, the SRMR value exceeded the guideline recommendation (SRMR = `r apa(fit.1[10],2,F)`).
-
 In order to improve the model fit, we conducted a post-hoc model modification.
@@
 
-Accordingly, we accept the five-factor model with 23 items, finalizing the long Form of LEBA (see **Supplementary File 1**).
+Accordingly, we accept the five-factor model with 23 items, finalizing the long Form of LEBA Inventory (see **Supplementary File 1**).
 Internal consistency ordinal $\alpha$ for the five factors of the LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`, respectively.
-The Internal consistency McDonald's $\omega_t$ coefficient for the total inventory yielded `r apa(rel.k[5,6],2,F)`.
+The reliability of the total inventory was satisfactory ($\omega_t$=`r apa(rel.k[5,6],2,F)`).
 Figure \@ref(fig:figcfa) depicts the obtained CFA structure, while  **Supplementary Figure 2** depicts the data distribution and endorsement pattern of the retained 23 items in our CFA sample.
@@
 colnames(Cfa.matrix.selected) = c("Model", "$\\chi^{2}$", "df", "CFI", "TLI", "RMSEA", "RMSEA 90\\% Lower CI", "RMSEA 90\\% Upper CI", "SRMR")
+
+Cfa.matrix.selected$CFI[1] <- round(fit.1[5],2)
+Cfa.matrix.selected$TLI[1] <- round(fit.1[6],2)
+Cfa.matrix.selected$RMSEA[1] <- round(fit.1[7],2)
+Cfa.matrix.selected[1,7] <- round(fit.1[8],2)
+Cfa.matrix.selected[1,8] <- round(fit.1[9],2)
+
+Cfa.matrix.selected$CFI[2] <- round(fit.2[5],2)
+Cfa.matrix.selected$TLI[2] <- round(fit.2[6],2)
+Cfa.matrix.selected$RMSEA[2] <- round(fit.1[7],2)
+Cfa.matrix.selected[2,7] <- round(fit.2[8],2)
+Cfa.matrix.selected[2,8] <- round(fit.2[9],2)
 

### 2023-01-03 manuscript_v2.Rmd
CFA

@@
 Our CFA sample consisted of `r mi.count[1,2]` native English speakers and `r mi.count[2,2]` non-native English speakers, whose demographic data are contrasted in **Supplementary Table 5**.
-As shown in Table \@ref(tab:InvarianceTab), the employed five-factor model generated acceptable fit indices over all of the fitted MI models.
-The model fit did not significantly decrease across the nested models, implying the acceptability of the highest measurement invariance model (residual model).
-This indicated the construct demonstrated psychometric equivalence and the same meaning across native and non-native English speaking participants
+As shown in Table \@ref(tab:InvarianceTab), our results indicated that LEBA inventory demonstrated highest level of (residual model) psychometric equivalence across native and non-native English speaking participants, thus permitting group level mean based comparisons.
+The four fitted MI models generated acceptable fit indices and the model fit did not significantly decrease across the nested models ($\Delta$CFI>-0.01; $\Delta$RMSEA<0.01), implying the acceptability of the highest measurement invariance model.
 
@@
 The results of the Flesch-Kincaid grade level analysis [@flesch1948new] displayed a required educational grade level of four (US education system) with age above 8.33 years.
-Furthermore, the
-Semantic Scale Network (SSN) analysis [@rosenbusch2020semantic] indicated that the LEBA appeared most strongly semantically related to scales about sleep: The "Sleep Disturbance Scale For Children" [@bruni1996sleep] and the "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite].
+Furthermore, the Semantic Scale Network (SSN) analysis [@rosenbusch2020semantic] indicated that the LEBA appeared most strongly semantically related to scales about sleep: The "Sleep Disturbance Scale For Children" [@bruni1996sleep] and the "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite].
 The cosine similarity yielded values between .47 to .51.
@@
 The resulting item discrimination parameters of the inventory fell into categories of "very high" (10 items), "high" (4 items), "moderate" (4 items), and "low" ( 5 items), indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**).
-An examination of the item information curve (**Supplementary Figure 3**) revealed five items (1, 25, 30, 38, & 41) with relatively flat curves (I($\theta$) \<.20).
+An examination of the item information curve (**Supplementary Figure 3**) revealed five items (1, 25, 30, 38, & 41) provided very low information regarding light exposure related behaviors with relatively flat curves (I($\theta$) \<.20).
 We discarded those items, culminating in a short form of LEBA with five factors and 18 items (**Supplementary File 2**).
@@
 
-Subsequently, we treated each factor of the short-LEBA as a unidimensional construct and obtained five test information curves (TICs).
+Subsequently, we obtained five test information curves (TICs).
 As Figure \@ref(fig:Testinfo) illustrates, the TICs of the first and fifth factors peaked on the right side of the centre of their latent traits, while the TICs of the other three factors were roughly centred on the respective trait continuum ($\theta$).

### 2023-01-03 manuscript_v3.Rmd
V3 Rmd updated

--- 2023-01-03 manuscript_v2.Rmd
@@
 keywords          : "light exposure, light-related behaviours, non-visual effects of light, psychometrics"
-wordcount         : "6249"
+wordcount         : "6314"
 
@@
 
-# Methods
-
 ```{r Data, include=FALSE}
@@
 
-## Data collection
-
 ```{r demotab, warning=F, message=F}
@@
 
-A quantitative cross-sectional, fully anonymous, geographically unconstrained online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
-Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (<https://enlightenyourclock.org/participate-in-research>) of the science-communication comic book "Enlighten your clock", co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by the distribution of the survey link via f.lux [@f.lux].
-The initial page of the online survey provided information about the study, including that participation was voluntary and that respondents could withdraw from participation at any time without being penalised.
-Subsequently, consent was recorded digitally for the adult participants (\>18 years), while under-aged participants (\<18 years) were prompted to obtain additional assent from their parents/legal guardians.
-Filling in all questionnaires was estimated to take less than 30 minutes, and participation was not compensated.
-
-As a part of the demographic data, participants provided information regarding age, sex, gender identity, occupational status, COVID-19-related occupational setting, time zone/country of residence and native language.
-The demographic characteristics of our sample are given in **Table 1**.
-Participants were further asked to confirm that they participated in the survey for the first time.
-All questions incorporating retrospective recall were aligned to a "past four weeks" period.
-Additionally, four attention check items  were included among the questionnaires to ensure high data quality, with the following phrasing:
-- We want to make sure you are paying attention. What is 4+5?
-- [...] Please select "Strongly disagree" here.
-- [...] Please type in "nineteen" as a number.
-- [...] Please select "Does not apply/I don't know." here.
-
-We collected the survey data between 17 May 2021 and 3 September 2021 – firstly from `r nrow(EFA.descriptives)` participants (EFA sample) – and subsequently, another dataset from `r nrow(CFA.descriptives)` participants (CFA sample), totalling `r nrow(desctable.data)`.
-
-## Analytic strategy
-
-Figure \@ref(fig:FlowchartFig) summarises the steps we followed while developing the LEBA. We conducted all analyses with the statistical software environment R [@R-base]. 
-**Firstly**, we set an item pool of 48 items with a six-point Likert-type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial inventory.
-Our purpose was to capture light exposure-related behaviour.
-In that context, the first two response options: "Does not apply/I don't know" and "Never", provided similar information.
-As such, we collapsed them into one, making it a 5-point Likert-type response format (1-Never, 2-Rarely, 3-Sometimes, 4-Often, 5-Always).
-
-**Secondly**, the two rounds of data collection were administered. 
-**Thirdly**, we conducted descriptive and item analyses and proceeded to the exploratory factor analysis (EFA) using the "psych" package [@R-psych] on the data collected in the first round (EFA sample; n=`r nrow(EFA.descriptives)`), as a part of psychometric analysis.
-Prior to the EFA, the necessary assumptions, including sample adequacy, normality assumptions, and quality of correlation matrix, were assessed.
-As our data violated both the univariate and multivariate normality assumption and yielded ordinal response data, we used a polychoric correlation matrix in the EFA and employed "principal axis" (PA) as the factor extraction method [@desjardinsHandbookEducationalMeasurement2018; @watkinsStepbyStepGuideExploratory2020].
-We applied a combination of methods, including a Scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and Hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
-To determine the latent structure, we followed the common guidelines: (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading \> .3 across factors [@bandalosFactorAnalysisExploratory2018].
-<!-- We also conducted an EFA on the non-merged response options data set (**Supplementary File 1**).
--->
-
-For reliability estimation, the "psych" package was applied [@R-psych].
-Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it tends to deflate the estimates for Likert-type data since the calculation is based on the Pearson-correlation matrix, which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal].
-Subsequently, we reported ordinal alpha for each factor obtained in the EFA which was suggested as a better reliability estimates for ordinal data [@zumbo2007ordinal].
-We also estimated the internal consistency reliability of the total inventory using McDonald's $\omega_t$ coefficient, which was suggested as a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
-Both ordinal alpha and McDonald's $\omega_t$ coefficient values range between 0 to 1, where higher values represent better reliability.
-
-To validate the latent structure obtained in the EFA, we conducted a categorical confirmatory factor analysis (CFA) with the weighted least squares means and variance adjusted (WLSMV) estimation [@desjardinsHandbookEducationalMeasurement2018], using the "lavaan" package [@R-lavaan] on the data collected in the second round (CFA sample; n=`r nrow(CFA.descriptives)`).
-We assessed the model fit using standard model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI): close to .95 or above/ between .90-.95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner].
-However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015], and SRMR does not work well with ordinal data [@RN1272].
-Consequently, we judged the model fit using CFI, TLI and RMSEA.
-
-In order to evaluate whether the construct demonstrated psychometric equivalence and the same meaning across native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non-native English speakers (n=`r invariance.data.descriptives.count[2,2]`) in the CFA sample (n=`r nrow(CFA.descriptives)`) [@putnick2016measurement; @klinePrinciplesPracticeStructural2015] measurement invariance analysis was used.
-We used structural equation modelling framework applying the "lavaan" package [@R-lavaan] to assess the measurement invariance.
-We successively compared four nested models: configural, metric, scalar, and residual models using the $\chi^2$ difference test ($\Delta \chi^2$).
-Among MI models, the configural model is the least restrictive, and the residual model is the most restrictive.
-A non-significant $\Delta \chi^2$ test between two nested measurement invariance models indicates mode fit does not significantly decrease for the superior model, thus allowing the superior invariance model to be accepted [@dimitrov2010testing; @widaman1997exploring].
-
-**Fourthly**, in a secondary analysis, we identified the educational grade level (US education system) required to understand the items in our inventory with the Flesch-Kincaid grade level identification method [@flesch1948new] applying the "koRpus" [@R-koRpus] package.
-Correspondingly, we analysed possible semantic overlap of our developed inventory using the ["Semantic Scale Network" (SSN)](https://rosenbusch.shinyapps.io/semantic_net/) engine [@rosenbusch2020semantic].
-The SSN detects semantically related scales and provides a cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic].
-Pairs of scales with a cosine similarity index value of 1 inidicate full semantical similarity, suggesting redundancy.
-
-**Lastly**, we derived a short form of the LEBA employing an Item Response Theory (IRT) based analysis.
-We fitted each factor of the LEBA to the combined EFA and CFA sample (n=`r nrow(sem.data)`) using the graded response model [@samejima1997handbook] via the "mirt" package [@R-mirt].
-IRT assesses the item quality by estimating the item discrimination, item difficulty, item information curve, and test information curve [@bakerBasicsItemResponse2017].
-Item discrimination indicates how well a particular item can differentiate between participants across the given latent trait continuum ($\theta$).
-Item difficulty corresponds to the latent trait level at which the probability of endorsing a particular response option is 50%.
-The item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
-Here, we reported the item difficulty and discrimination parameter and categorized the items based on their item discrimination index: (i) none = 0; (ii) very low = 0.01 to 0.34; (iii) low = 0.35 to 0.64; (iv) moderate = 0.65 to 1.34 ; (v) high = 1.35 to 1.69; (vi) very high \>1.70 [@bakerBasicsItemResponse2017].
-We discarded the items with a relatively flat item information curve (information \<.2) to derive the short form of LEBA.
-We also assessed the precision of the short LEBA utilizing the test information curve (TIC).
-TIC indicates the amount of information a particular scale carries along the latent trait continuum.
-Additionally, the item and person fit of the fitted IRT models were analysed to gather more evidence on the validity and meaningfulness of our scale [@desjardinsHandbookEducationalMeasurement2018].
-The item fit was evaluated using the RMSEA value obtained from Signed-$\chi^2$ index implementation, where an RMSEA value $\le$.06 was considered an adequate item fit.
-The person fit was estimated employing the standardized fit index Zh statistics [@drasgow1985appropriateness].
-Here, Zh \< -2 was considered as a misfit [@drasgow1985appropriateness].
-
-```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Flow chart of the LEBA (long and short form) development and evaluation. ', out.height='50%', out.width='50%'}
-knitr::include_graphics('Figures/Figure1.png', dpi = 600 )
-```
-
-## Ethical approval
-
-The current research project utilizes fully anonymous online survey data and therefore does not fall under the scope of the Human Research Act, making an authorisation from the ethics committee redundant.
-Nevertheless, the cantonal ethics commission (Ethikkommission Nordwest- und Zentralschweiz, EKNZ) reviewed our proposition (project ID Req-2021-00488) and issued an official clarification of responsibility.
-
-## Data availability
-
-The present article is a fully reproducible open access "R Markdown" document.
-All code and data underlying this article -- along with two versions of the LEBA inventory (full and short) and online survey implementation templates on common survey platforms -- is available under an open-access licence (Creative Commons CC-BY-NC-ND) on a public [GitHub repository](https://github.com/leba-instrument).
+```{r EFAdata, include=FALSE}
+#This chunk holds code for creating EFA data subset
+### EFA data
+EFA.data <- sem.data[1:428, ]
+#library(VIM)
+missing <- VIM::aggr(EFA.data, plot =T)
+CFA.data <- sem.data[429:690,]
+```
 
@@
 An expert panel comprising all authors -- researchers from chronobiology, light research, neuroscience and psychology in different geographical contexts -- developed a comprehensive item pool of 48 items.
-Face validity examination of all 48 items by each panel member indicated all items were relevant and appropriate and a few modifications were suggested as required.
+Face validity examination by each panel member indicated all items were relevant and a few modifications were suggested.
 The author team discussed the suggestions and amended the items as indicated, thus creating a 48-item inventory.
@@
 
-Table 1 summarises the survey participants' demographic characteristics.
+We conducted two rounds of large scale online survey to generate data from various geographic locations (countries=`r nrow(num.countries)`; time-zone=`r nrow(numUTC)`).
+For a complete list of geographic locations, see **Supplementary Table 2**.
+Table 1 presents the survey participants' demographic characteristics.
 Only participants completing the full LEBA inventory were included.
-Thus, there are no missing values in the item analyses.
-For the EFA, a sample of at least 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013].
-To assess sampling adequacy for CFA, we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where at least ten participants per item are required to earn trustworthiness of the result.
-Both our EFA and CFA sample size exceeded these requirements.
-Participants indicated filling out the online survey from various geographic locations, including `r nrow(num.countries)` countries and `r nrow(numUTC)` time zones.
-For a complete list of geographic locations, see **Supplementary Table 2**.
-
+We used the data from first round for the exploratory factor analysis (EFA sample; n=`r nrow(EFA.data)`) and data from the second round was used in the confirmatory factor analysis (CFA sample; n=`r nrow(CFA.data)`).
 Participants in our survey were aged between `r min(desctable.data$slypos_demographics_age)` to `r max(desctable.data$slypos_demographics_age)` years, with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 2)` years of age [Overall: `r mean(desctable.data$slypos_demographics_age)`±`r sd(desctable.data$slypos_demographics_age)`; EFA: `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
@@
 
-Figures \@ref(fig:efagtPic1) and \@ref(fig:efagtPic2) depict the response patterns of our total sample (n=`r nrow(sem.data)`) for all 48 items.
-Most of the items appeared skewed and violated univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality ([@mardiaMeasuresMultivariateSkewness1970]; multivariate skewness=`r printnum(mardia.all.data$b1p)`, p<0.001); multivariate kurtosis=`r printnum(mardia.all.data$b2p)`,p<0.001).
-
-```{r EFAdata, include=FALSE}
-#This chunk holds code for creating EFA data subset
-### EFA data
-EFA.data <- sem.data[1:428, ]
-#library(VIM)
-missing <- VIM::aggr(EFA.data, plot =T)
-
-```
+Response patterns for the entire sample (n=`r nrow(sem.data)`) are depicted in Figures \@ref(fig:efagtPic1) and \@ref(fig:efagtPic2).
+All items violated univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality [(@mardiaMeasuresMultivariateSkewness1970].
+The multivariate skewness was`r printnum(mardia.all.data$b1p)` (p<0.001) and the multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p<0.001).
 
@@
 
-**Supplementary Figure 1** summarises the univariate descriptive statistics for the 48 items in the EFA sample (n=`r nrow(EFA.data)`).
-Likewise, our data violated the both univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions ([@mardiaMeasuresMultivariateSkewness1970]; multivariate skew=`r printnum(mardia$b1p)`, p<0.001; multivariate kurtosis= `r printnum(mardia$b2p)`,p <0.001).
-The corrected item-total correlation ranged between `r apa(low.r.corec,2,F)` and `r apa(high.r.corec,2,F)`.
+**Supplementary Figure 1** depicts the univariate descriptive statistics for the EFA sample (n=`r nrow(EFA.data)`).
+Likewise, our data violated the both univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970].
+The multivariate skew was `r printnum(mardia$b1p)` (p<0.001) and the multivariate kurtosis was `r printnum(mardia$b2p)` (p <0.001).
+The corrected item-total correlation ranged between `r apa(low.r.corec,2,T)` and `r apa(high.r.corec,2,T)`.
 However, no item was discarded based on descriptive statistics or item analysis.
@@
 
-min.cor <- apa(min((upper)),2,F) #minimum cor.coefficient of the matrix
-max.cor <- apa(max((upper)),2,F) # max. correlation coefficient of the matrix
+min.cor <- apa(min((upper)),2,T) #minimum cor.coefficient of the matrix
+max.cor <- apa(max((upper)),2,T) # max. correlation coefficient of the matrix
 
@@
 We checked the post-hoc sampling adequacy by applying Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy on the EFA sample (n=`r nrow(EFA.data)`) [@kaiserIndexFactorialSimplicity1974].
-KMO>.50 would indicate adequate sample size [@hutchesonMultivariateSocialScientist1999].
+KMO>0.50 would indicate adequate sample size [@hutchesonMultivariateSocialScientist1999].
 Results indicated that we had an adequate sample size (KMO=`r printnum(KMO$MSA)`).
-Additionally, we investigate the quality of the correlation matrix by Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954] prior to conduct the EFA.
-Results indicated that the correlation matrix was adequate to conduct EFA ($\chi^2$ (`r bartlet$df`)=`r apa(bartlet$chisq, 2, T)`, p< .001).
-However,`r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than |0.30|, and the inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`.
+Additionally, we investigate the quality of the correlation matrix by Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954].
+Results indicated that the correlation matrix was adequate to conduct EFA ($\chi^2_{1128}$=`r apa(bartlet$chisq, 2, T)`, p< 0.001).
+However, `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than |0.30|, and the inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`.
 Figure \@ref(fig:efa-plot-print)-A depicts the respective correlation matrix.
@@
 While investigating the optimum factor number for the LEBA inventory, the Scree plot ( Figure \@ref(fig:efa-plot-print)-B) revealed a six-factor solution, whereas the minimum average partial (MAP) method [@velicerDeterminingNumberComponents1976] (**Supplementary Table 3**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print)-C) implied a five-factor solution.
-Hence, we tested both five-factor and six-factor solutions.
+Hence, we tested both five-factor and six-factor solutions using iterative EFA where we gradually identified and discarded problematic items (factor-loading <0.30 and cross-loading >0.30).
 
@@
 
-We conducted iterative EFA with varimax rotation, starting with the initial 48 items and gradually discarded problematic items (cross-loading items and items with factor loading <.30).
-After, three rounds of EFA we found a five-factor EFA solution with 25 items with all factor-loading >.30 and no cross-loading >.30.
+Iterative EFA revealed a five-factor structure for LEBA inventory and retained 25 items.
 Table \@ref(tab:EFATable) displays the factor-loading ($\lambda$) and communality of the items.
-Both factor loadings and commonalities advocate to accept this five-factor solution ( |$\lambda$|= `r apa(min.loadings,2,F)` - `r apa(max.loadings, 2, F)`; commonalities= `r apa(min.com,2,F)` - `r apa(max.com, 2, F)`).
+Both factor loadings and commonalities advocate to accept this five-factor solution ( |$\lambda$|= `r apa(min.loadings,2,T)` - `r apa(max.loadings, 2, T)`; commonalities= `r apa(min.com,2,T)` - `r apa(max.com, 2, T)`).
 However, the histogram of the absolute values of nonredundant residual correlations (Figure \@ref(fig:efa-plot-print)-D) displayed that `r sumR`% of correlations were greater >|.05|, indicating a possible under-factoring.
@@
 lastly, the fifth factor encompassed six items capturing the individual's morning and daytime light exposure-related behaviour.
-These five factors explains `r apa(var1,2,F)`%, `r apa(var2,2,F)`%, `r apa(var3,2,F)`%, `r apa(var4,2,F)`%, `r apa(var5,2,F)`% of of the total variance in individual's light exposure related behaviours respectively and factors exhibited excellent to satisfactory reliability (ordinal $\alpha$= `r apa(F1.alpha,2,F)`, `r apa(F2.alpha,2,F)`, `r apa(F3.alpha,2,F)`, `r apa(F4.alpha,2,F)`, `r apa(F5.alpha,2,F)` respectively).
+These five factors explains `r apa(var1,2,T)`%, `r apa(var2,2,T)`%, `r apa(var3,2,T)`%, `r apa(var4,2,T)`%, `r apa(var5,2,T)`% of the total variance in individual's light exposure related behaviours respectively.
+All factors exhibited excellent to satisfactory reliability (ordinal $\alpha$= `r apa(F1.alpha,2,F)`, `r apa(F2.alpha,2,T)`, `r apa(F3.alpha,2,T)`, `r apa(F4.alpha,2,T)`, `r apa(F5.alpha,2,T)` respectively).
 The entire inventory also exhibited satisfactory reliability ($\omega_t$=`r apa(omega$omega.tot,2,T)`).
@@
 
-CFA results (Table \@ref(tab:tabCfa)) indicated that the five-factor structure fitted to the 25-item LEBA Inventory attained an acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`; RMSEA = `r apa(fit.1[7],2,F)` [`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constraints on item pairs 32-33 [item 32: I dim my mobile phone screen within 1 hour before attempting to fall asleep; item 33: I dim my computer screen within 1 hour before attempting to fall asleep] and 16-17 [item 16: I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day; item 17: I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day].
+CFA results (Table \@ref(tab:tabCfa)) indicated that the five-factor structure fitted to the 25-item LEBA inventory attained an acceptable fit (CFI =`r apa(fit.1[5],2,T)`; TLI = `r apa(fit.1[6],2,T)`; RMSEA = `r apa(fit.1[7],2,T)` [`r apa(fit.1[8],2,T)`-`r apa(fit.1[9],2,T)`, 90% CI]) with two imposed equity constraints on item pairs 32-33 [item 32: I dim my mobile phone screen within 1 hour before attempting to fall asleep; item 33: I dim my computer screen within 1 hour before attempting to fall asleep] and 16-17 [item 16: I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day; item 17: I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day].
 Item pair 32-33 describes the preference for dimming the electric devices' brightness before bedtime, whereas item pair 16-17 represents the use of blue filtering or coloured glasses during the daytime.
 Given the similar nature of captured behaviours within each item pair, we accepted the imposed equity constraints.
-Nevertheless, the SRMR value exceeded the guideline recommendation (SRMR = `r apa(fit.1[10],2,F)`).
+Nevertheless, the SRMR value exceeded the guideline recommendation (SRMR = `r apa(fit.1[10],2,T)`).
 In order to improve the model fit, we conducted a post-hoc model modification.
 Firstly, the  modification indices suggested cross-loadings between item 37 and 26 [item 37: I purposely leave a light on in my sleep environment while sleeping; item 26: I turn on my ceiling room light when it is light outside], which were hence discarded.
-Secondly, items 30 and 41 [item 30: I look at my smartwatch within 1 hour before attempting to fall asleep; item 41: I look at my smartwatch when I wake up at night] showed a tendency to co-vary in their error variance (MI = 141.127, p<.001 ).
-By allowing the latter pair of items (30 $\&$ 41) to co-vary, the model's error variance attained an improved fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR = `r apa(fit.2[10],2,F) `).
-
-Accordingly, we accept the five-factor model with 23 items, finalizing the long Form of LEBA Inventory (see **Supplementary File 1**).
-Internal consistency ordinal $\alpha$ for the five factors of the LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`, respectively.
-The reliability of the total inventory was satisfactory ($\omega_t$=`r apa(rel.k[5,6],2,F)`).
+Secondly, items 30 and 41 [item 30: I look at my smartwatch within 1 hour before attempting to fall asleep; item 41: I look at my smartwatch when I wake up at night] showed a tendency to co-vary in their error variance (MI = 141.127, p<0.001 ).
+By allowing the latter pair of items (30 $\&$ 41) to co-vary, the model's error variance attained an improved fit (CFI =`r apa(fit.2[5],2,T)`; TLI = `r apa(fit.2[6],2,T)`); RMSEA = `r apa(fit.2[7],2,T)` [`r apa(fit.2[8],2,T)`-`r apa(fit.2[9],2,T)`, 90% CI]; SRMR = `r apa(fit.2[10],2,T) `).
+
+Accordingly, we accept the five-factor model with 23 items, finalizing the long Form of LEBA inventory (see **Supplementary File 1**).
+Internal consistency ordinal $\alpha$ for the five factors of the LEBA were `r apa(rel.k[2,1],2,T)`, `r apa(rel.k[2,2],2,T)`, `r apa(rel.k[2,3],2,T)`, `r apa(rel.k[2,4],2,T)`, `r apa(rel.k[2,5],2,T)`, respectively.
+The reliability of the total inventory was satisfactory ($\omega_t$=`r apa(rel.k[5,6],2,T)`).
 Figure \@ref(fig:figcfa) depicts the obtained CFA structure, while  **Supplementary Figure 2** depicts the data distribution and endorsement pattern of the retained 23 items in our CFA sample.
@@
 
-Our CFA sample consisted of `r mi.count[1,2]` native English speakers and `r mi.count[2,2]` non-native English speakers, whose demographic data are contrasted in **Supplementary Table 5**.
-As shown in Table \@ref(tab:InvarianceTab), our results indicated that LEBA inventory demonstrated highest level of (residual model) psychometric equivalence across native and non-native English speaking participants, thus permitting group level mean based comparisons.
-The four fitted MI models generated acceptable fit indices and the model fit did not significantly decrease across the nested models ($\Delta$CFI>-0.01; $\Delta$RMSEA<0.01), implying the acceptability of the highest measurement invariance model.
+We reported the measurement invariance (MI) analysis on the CFA sample based on native (n=`r mi.count[1,2]`) and non-native English speakers (n=`r mi.count[2,2]`).
+A detailed demographic description are provided in **Supplementary Table 5**.
+Our MI results (Table \@ref(tab:InvarianceTab)) indicated that LEBA inventory demonstrated highest level of (residual model) psychometric equivalence across native and non-native English speaking participants, thus permitting group-mean based comparisons.
+The four fitted MI models generated acceptable fit indices and the model fit did not significantly decrease across the nested models ($\Delta$CFI>-0.01; $\Delta$RMSEA<0.01).
 
@@
 ## Secondary Analysis: Grade Level Identification and Semantic Scale Network Analysis
-A grade level identification and Semantic Scale analysis were additionally administered to assess the LEBA's (23 items) language-based accessibility and its' semantic relation to other questionnaires.
-The results of the Flesch-Kincaid grade level analysis [@flesch1948new] displayed a required educational grade level of four (US education system) with age above 8.33 years.
-Furthermore, the Semantic Scale Network (SSN) analysis [@rosenbusch2020semantic] indicated that the LEBA appeared most strongly semantically related to scales about sleep: The "Sleep Disturbance Scale For Children" [@bruni1996sleep] and the "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite].
-The cosine similarity yielded values between .47 to .51.
+We investigated the language-based accessibility of LEBA using Flesch-Kincaid grade level analysis [@flesch1948new].
+Results indicated that at least a language proficiency of educational grade level-four (US education system) with age above eight years  are requied to comprehend the items used in LEBA inventory.
+Semantic Scale analysis [@rosenbusch2020semantic]  was administered to assess the LEBA's (23 items) semantic relation to other questionnaires.
+LEBA inventory was most strongly semantically related to scales about sleep: The "Sleep Disturbance Scale For Children" [@bruni1996sleep] and the "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite].
+The cosine similarity index ranged between .47 to .51.
 
@@
 As Figure \@ref(fig:Testinfo) illustrates, the TICs of the first and fifth factors peaked on the right side of the centre of their latent traits, while the TICs of the other three factors were roughly centred on the respective trait continuum ($\theta$).
-This points out that the LEBA short-form estimates the light exposure-related behaviour most precisely near the centre of the trait continuum for the second, third and fourth factors and, in contrast, to the right of the centre for the first and fifth factors [@bakerBasicsItemResponse2017].
+This points out that the LEBA short-form estimates the light exposure-related behaviour most precisely near the centre of the trait continuum for the second, third and fourth factors.
+In contrast, for the first and fifth factors the TICs were left skewed indicating their increased sensitivity in identifying people who are engaging more in those particular light exposure related behavior dimensions [@bakerBasicsItemResponse2017].
 
 Finally, **Supplementary Table 7** summarises the item fit indexes of the LEBA short form.
-All 18 items yielded RMSEA value $\le$.06, indicating an adequate fit to the fitted IRT model.
+All 18 items yielded RMSEA value $\le$0.06, indicating an adequate fit to the fitted IRT model.
 Furthermore, **Supplementary Figure 4** depicts the person fit Zh statistics histogram for the five IRT models.
@@
 The exploratory factor analysis revealed a highly interpretable five-factor solution ("Wearing blue light filters", "Spending time outdoors", "Using phone and smartwatch in bed", "Using light before bedtime", and "Using light in the morning and during daytime") with 25 items.
-Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five-factor structure we obtained in our EFA, thus providing evidence for structural validity.(CFI=`r apa(fit.2[5],2,F)`; TLI=`r apa(fit.2[6],2,F)`; RMSEA=`r apa(fit.2[7],2,F)`).
+Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five-factor structure we obtained in our EFA, thus providing evidence for structural validity.(CFI=`r apa(fit.2[5],2,T)`; TLI=`r apa(fit.2[6],2,T)`; RMSEA=`r apa(fit.2[7],2,T)`).
 In this model, we discarded two more items (item 26 $\&$ 37 ) for possible cross-loadings.
@@
 However, at the early developmental stage, a value of .50 is considered acceptable [@dall2010developmental; @field2013discovering; @Nunnally1978].
-Thus, we confer, the internal consistency coefficients ordinal alpha for the five factors and the total inventory were satisfactory (Ordinal alpha ranged between `r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$=`r apa(rel.k[5,6],2,F)`).
+Thus, we confer, the internal consistency coefficients ordinal alpha for the five factors and the total inventory were satisfactory (Ordinal alpha ranged between `r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$=`r apa(rel.k[5,6],2,T)`).
 
@@
 
-The fifth factor, "using light in the morning and during daytime", exhibited low internal consistency both in the exploratory and confirmatory factor analysis (EFA: `r apa(F5.alpha,2,F)`; CFA:`r apa(rel.k[2,5],2,F)` ).
+The fifth factor, "using light in the morning and during daytime", exhibited low internal consistency both in the exploratory and confirmatory factor analysis (EFA: `r apa(F5.alpha,2,T)`; CFA:`r apa(rel.k[2,5],2,T)` ).
 Since, it was above .50, considering the developmental phase of this inventory we accepted the fifth factor.
@@
 
+# Methods
+
+## Data collection
+
+A quantitative cross-sectional, fully anonymous, geographically unconstrained online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
+Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (<https://enlightenyourclock.org/participate-in-research>) of the science-communication comic book "Enlighten your clock", co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by the distribution of the survey link via f.lux [@f.lux].
+The initial page of the online survey provided information about the study, including that participation was voluntary and that respondents could withdraw from participation at any time without being penalised.
+Subsequently, consent was recorded digitally for the adult participants (\>18 years), while under-aged participants (\<18 years) were prompted to obtain additional assent from their parents/legal guardians.
+Filling in all questionnaires was estimated to take less than 30 minutes, and participation was not compensated.
+
+As a part of the demographic data, participants provided information regarding age, sex, gender identity, occupational status, COVID-19-related occupational setting, time zone/country of residence and native language.
+The demographic characteristics of our sample are given in **Table 1**.
+Participants were further asked to confirm that they participated in the survey for the first time.
+All questions incorporating retrospective recall were aligned to a "past four weeks" period.
+Additionally, four attention check items  were included among the questionnaires to ensure high data quality, with the following phrasing:
+- We want to make sure you are paying attention. What is 4+5?
+- [...] Please select "Strongly disagree" here.
+- [...] Please type in "nineteen" as a number.
+- [...] Please select "Does not apply/I don't know." here.
+
+We collected the survey data between 17 May 2021 and 3 September 2021 – firstly from `r nrow(EFA.descriptives)` participants (EFA sample) – and subsequently, another dataset from `r nrow(CFA.descriptives)` participants (CFA sample), totalling `r nrow(desctable.data)`.
+
+## Analytic strategy
+
+Figure \@ref(fig:FlowchartFig) summarises the steps we followed while developing the LEBA. We conducted all analyses with the statistical software environment R [@R-base]. 
+**Firstly**, we set an item pool of 48 items with a six-point Likert-type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial inventory.
+Our purpose was to capture light exposure-related behaviour.
+In that context, the first two response options: "Does not apply/I don't know" and "Never", provided similar information.
+As such, we collapsed them into one, making it a 5-point Likert-type response format (1-Never, 2-Rarely, 3-Sometimes, 4-Often, 5-Always).
+
+**Secondly**, the two rounds of data collection were administered.
+In the first round (EFA sample; n=`r nrow(EFA.descriptives)`) we collected data for the exploratory factor analysis (EFA).
+A sample of at least 250-300 is recommended for EFA [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013].
+The EFA sample exceeded this recommendation.
+The second round data (CFA sample; n=`r nrow(CFA.descriptives)`) was subjected to confirmatory factor analysis (CFA).
+To assess sampling adequacy for CFA, we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where at least ten participants per item are required to earn trustworthiness of the result.
+Again, our CFA sample exceeded this guidelines.
+
+**Thirdly**, we conducted descriptive and item analyses and proceeded to EFA using the "psych" package [@R-psych] on the EFA sample.
+Prior to the EFA, the necessary assumptions, including sample adequacy, normality assumptions, and quality of correlation matrix, were assessed.
+As our data violated both the univariate and multivariate normality assumption and yielded ordinal response data, we used a polychoric correlation matrix in the EFA and employed "principal axis" (PA) as the factor extraction method [@desjardinsHandbookEducationalMeasurement2018; @watkinsStepbyStepGuideExploratory2020].
+We applied a combination of methods, including a Scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and Hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
+To determine the latent structure, we followed the common guidelines: (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading \> .3 across factors [@bandalosFactorAnalysisExploratory2018].
+<!-- We also conducted an EFA on the non-merged response options data set (**Supplementary File 1**).
+-->
+
+For reliability estimation, the "psych" package was applied [@R-psych].
+Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it tends to deflate the estimates for Likert-type data since the calculation is based on the Pearson-correlation matrix, which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal].
+Subsequently, we reported ordinal alpha for each factor obtained in the EFA which was suggested as a better reliability estimates for ordinal data [@zumbo2007ordinal].
+We also estimated the internal consistency reliability of the total inventory using McDonald's $\omega_t$ coefficient, which was suggested as a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
+Both ordinal alpha and McDonald's $\omega_t$ coefficient values range between 0 to 1, where higher values represent better reliability.
+
+To validate the latent structure obtained in the EFA, we conducted a categorical confirmatory factor analysis (CFA) with the weighted least squares means and variance adjusted (WLSMV) estimation [@desjardinsHandbookEducationalMeasurement2018], using the "lavaan" package [@R-lavaan] on the CFA sample.
+We assessed the model fit using standard model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI): close to 0.95 or above/ between 0.90-0.95 and above (iii) root mean square error of approximation (RMSEA): close to 0.06 or below, (iv) Standardized root mean square (SRMR): close to 0.08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner].
+However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015], and SRMR does not work well with ordinal data [@RN1272].
+Consequently, we judged the model fit using CFI, TLI and RMSEA.
+
+In order to evaluate whether the construct demonstrated psychometric equivalence and the same meaning across native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non-native English speakers (n=`r invariance.data.descriptives.count[2,2]`) in the CFA sample (n=`r nrow(CFA.descriptives)`) [@putnick2016measurement; @klinePrinciplesPracticeStructural2015] measurement invariance analysis was used.
+We used structural equation modelling framework applying the "lavaan" package [@R-lavaan] to assess the measurement invariance.
+We successively compared four nested models: configural, metric, scalar, and residual models using the $\chi^2$ difference test ($\Delta \chi^2$).
+Among MI models, the configural model is the least restrictive, and the residual model is the most restrictive.
+A non-significant $\Delta \chi^2$ test between two nested measurement invariance models indicates mode fit does not significantly decrease for the superior model, thus allowing the superior invariance model to be accepted [@dimitrov2010testing; @widaman1997exploring].
+
+**Fourthly**, in a secondary analysis, we identified the educational grade level (US education system) required to understand the items in our inventory with the Flesch-Kincaid grade level identification method [@flesch1948new] applying the "koRpus" [@R-koRpus] package.
+Correspondingly, we analysed possible semantic overlap of our developed inventory using the ["Semantic Scale Network" (SSN)](https://rosenbusch.shinyapps.io/semantic_net/) engine [@rosenbusch2020semantic].
+The SSN detects semantically related scales and provides a cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic].
+Pairs of scales with a cosine similarity index value of 1 inidicate full semantical similarity, suggesting redundancy.
+
+**Lastly**, we derived a short form of the LEBA employing an Item Response Theory (IRT) based analysis.
+We fitted each factor of the LEBA to the combined EFA and CFA sample (n=`r nrow(sem.data)`) using the graded response model [@samejima1997handbook] via the "mirt" package [@R-mirt].
+IRT assesses the item quality by estimating the item discrimination, item difficulty, item information curve, and test information curve [@bakerBasicsItemResponse2017].
+Item discrimination indicates how well a particular item can differentiate between participants across the given latent trait continuum ($\theta$).
+Item difficulty corresponds to the latent trait level at which the probability of endorsing a particular response option is 50%.
+The item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
+Here, we reported the item difficulty and discrimination parameter and categorized the items based on their item discrimination index: (i) none = 0; (ii) very low = 0.01 to 0.34; (iii) low = 0.35 to 0.64; (iv) moderate = 0.65 to 1.34 ; (v) high = 1.35 to 1.69; (vi) very high \>1.70 [@bakerBasicsItemResponse2017].
+We discarded the items with a relatively flat item information curve (information \<.2) to derive the short form of LEBA.
+We also assessed the precision of the short LEBA utilizing the test information curve (TIC).
+TIC indicates the amount of information a particular scale carries along the latent trait continuum.
+Additionally, the item and person fit of the fitted IRT models were analysed to gather more evidence on the validity and meaningfulness of our scale [@desjardinsHandbookEducationalMeasurement2018].
+The item fit was evaluated using the RMSEA value obtained from Signed-$\chi^2$ index implementation, where an RMSEA value $\le$.06 was considered an adequate item fit.
+The person fit was estimated employing the standardized fit index Zh statistics [@drasgow1985appropriateness].
+Here, Zh \< -2 was considered as a misfit [@drasgow1985appropriateness].
+
+```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Flow chart of the LEBA (long and short form) development and evaluation. ', out.height='50%', out.width='50%'}
+knitr::include_graphics('Figures/Figure1.png', dpi = 600 )
+```
+
+## Ethical approval
+
+The current research project utilizes fully anonymous online survey data and therefore does not fall under the scope of the Human Research Act, making an authorisation from the ethics committee redundant.
+Nevertheless, the cantonal ethics commission (Ethikkommission Nordwest- und Zentralschweiz, EKNZ) reviewed our proposition (project ID Req-2021-00488) and issued an official clarification of responsibility.
+
+## Data availability
+
+The present article is a fully reproducible open access "R Markdown" document.
+All code and data underlying this article -- along with two versions of the LEBA inventory (full and short) and online survey implementation templates on common survey platforms -- is available under an open-access licence (Creative Commons CC-BY-NC-ND) on a public [GitHub repository](https://github.com/leba-instrument).
+
 \newpage

### 2023-01-03 manuscript_v3.Rmd
Narratives

@@
 
+Our results focus on the development of the LEBA inventory and its psychometric validation using a large scale online sample data (n=`r nrow(data)`).
+
 ## Development of the initial item pool
-
-An expert panel comprising all authors -- researchers from chronobiology, light research, neuroscience and psychology in different geographical contexts -- developed a comprehensive item pool of 48 items.
+To capture the human light exposure related behaviours, 48 items were developed by an expert panel (all authors -- researchers from chronobiology, light research, neuroscience and psychology in different geographical contexts).
 Face validity examination by each panel member indicated all items were relevant and a few modifications were suggested.
@@
 
-We conducted two rounds of large scale online survey to generate data from various geographic locations (countries=`r nrow(num.countries)`; time-zone=`r nrow(numUTC)`).
+We conducted two rounds of large scale online survey between 17 May 2021 and 3 September 2021 to generate data from `r nrow(data)` participants with varied geographic locations (countries=`r nrow(num.countries)`; time-zone=`r nrow(numUTC)`).
 For a complete list of geographic locations, see **Supplementary Table 2**.
@@
 CFA Sample"])`].
-In total, `r desc_tibble[3,2]` of the participants indicated female sex, `r desc_tibble[4,2]` indicated male, and `r desc_tibble[5,2]` indicated other sex.
-Overall, `r desc_tibble[6,2]` participants reported a gender-variant identity.
+In the entire sample, `r desc_tibble[4,2]` were male, `r desc_tibble[3,2]` were female, `r desc_tibble[5,2]` reported other sex, and `r desc_tibble[6,2]` reported a gender-variant identity.
 In a "Yes/No" question regarding native language, `r desc_tibble[7,2]` of respondents [EFA: `r desc_tibble[7,3]`; CFA: `r desc_tibble[7,4]`] indicated to be native English speakers.
 For their "Occupational Status", more than half of the overall sample (`r desc_tibble[9,2]`) reported that they currently work, whereas `r desc_tibble[10,2]` reported that they go to school, and `r desc_tibble[11,2]` responded that they do "Neither".
-With respect to the COVID-19 pandemic, we asked participants to indicate their occupational setting during the last four weeks: In the overall sample, `r desc_tibble[13,2]` of the participants indicated that they were in a home office/ home schooling setting, `r desc_tibble[14,2]` reported face-to-face work/schooling, `r desc_tibble[15,2]`  reported a combination of home- and face-to-face work/schooling, and `r desc_tibble[16,2]`  filled in the "Neither (no work or school, or on vacation)" response option.
+With respect to the COVID-19 pandemic, we asked participants to indicate their occupational setting during the last four weeks: In the entire sample, `r desc_tibble[13,2]` of the participants indicated that they were in a home office/ home schooling setting, `r desc_tibble[14,2]` reported face-to-face work/schooling, `r desc_tibble[15,2]`  reported a combination of home- and face-to-face work/schooling, and `r desc_tibble[16,2]`  filled in the "Neither (no work or school, or on vacation)" response option.
 
@@
 
-Response patterns for the entire sample (n=`r nrow(sem.data)`) are depicted in Figures \@ref(fig:efagtPic1) and \@ref(fig:efagtPic2).
-All items violated univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality [(@mardiaMeasuresMultivariateSkewness1970].
+We observed that the response patterns of LEBA inventory for the entire sample (n=`r nrow(sem.data)`) were not normally distributed (Figures \@ref(fig:efagtPic1) and \@ref(fig:efagtPic2)).
+All items violated both univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality [(@mardiaMeasuresMultivariateSkewness1970].
 The multivariate skewness was`r printnum(mardia.all.data$b1p)` (p<0.001) and the multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p<0.001).
@@
 
+Similar non-normal distribution of response pattern was also observed in the EFA sample.
 **Supplementary Figure 1** depicts the univariate descriptive statistics for the EFA sample (n=`r nrow(EFA.data)`).
-Likewise, our data violated the both univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970].
-The multivariate skew was `r printnum(mardia$b1p)` (p<0.001) and the multivariate kurtosis was `r printnum(mardia$b2p)` (p <0.001).
-The corrected item-total correlation ranged between `r apa(low.r.corec,2,T)` and `r apa(high.r.corec,2,T)`.
-However, no item was discarded based on descriptive statistics or item analysis.
+Further, We observed that each item's correlation with the aggregated sum of the 48-item's score varied largely (corrected item-total correlation= `r apa(low.r.corec,2,T)` -`r apa(high.r.corec,2,T)`) indicating the possibility of multi-factor structure  of the LEBA inventory.
 
@@
 ```
-
-We checked the post-hoc sampling adequacy by applying Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy on the EFA sample (n=`r nrow(EFA.data)`) [@kaiserIndexFactorialSimplicity1974].
-KMO>0.50 would indicate adequate sample size [@hutchesonMultivariateSocialScientist1999].
-Results indicated that we had an adequate sample size (KMO=`r printnum(KMO$MSA)`).
-Additionally, we investigate the quality of the correlation matrix by Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954].
-Results indicated that the correlation matrix was adequate to conduct EFA ($\chi^2_{1128}$=`r apa(bartlet$chisq, 2, T)`, p< 0.001).
-However, `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than |0.30|, and the inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`.
-Figure \@ref(fig:efa-plot-print)-A depicts the respective correlation matrix.
 
@@
 ```
-
-While investigating the optimum factor number for the LEBA inventory, the Scree plot ( Figure \@ref(fig:efa-plot-print)-B) revealed a six-factor solution, whereas the minimum average partial (MAP) method [@velicerDeterminingNumberComponents1976] (**Supplementary Table 3**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print)-C) implied a five-factor solution.
-Hence, we tested both five-factor and six-factor solutions using iterative EFA where we gradually identified and discarded problematic items (factor-loading <0.30 and cross-loading >0.30).
 
@@
 
+Exploratory analysis revealed that items of LEBA inventory can be categorized into five major factors: (i) wearing blue light filters; (ii) spending time out doors; (iii) using phone and smartwatch in bed; (iv) usinf light before bedtime (v) using light in the morning and during daytime.
+In this stage of analysis, we retained 25 items.
+the first factor had three items and encapsulated the individual's preference for using blue light filters in different light environments.
+The second factor contained six items that incorporated the individuals' hours spent outdoors.
+The third factor contained five items that looked into specific behaviours of using a phone and smartwatch in bed.
+The fourth factor comprised five items investigated the other behaviours related to the individual's electric light exposure before bedtime.
+lastly, the fifth factor encompassed six items capturing the individual's morning and daytime light exposure-related behaviour.
+
+Prior to conducting the EFA, we have checked the post-hoc sampling adequacy by applying Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy on the EFA sample (n=`r nrow(EFA.data)`) [@kaiserIndexFactorialSimplicity1974] and the quality of the correlation matrix by Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954].
+KMO>0.50 would indicate adequate sample size [@hutchesonMultivariateSocialScientist1999] and a significant test of sphericity would indicate satisfactory quality of the correlation matrix .
+Results indicated that we had an adequate sample size (KMO=`r printnum(KMO$MSA)`) and correlation matrix ($\chi^2_{1128}$=`r apa(bartlet$chisq, 2, T)`, p< 0.001).
+However, `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than |0.30|, and the inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`.
+Figure \@ref(fig:efa-plot-print)-A depicts the respective correlation matrix.
+To identify how many factors are required to optimally express human light exposure related behaviors we used a combination of methods.
+the Scree plot ( Figure \@ref(fig:efa-plot-print)-B) revealed a six-factor solution, whereas the minimum average partial (MAP) method [@velicerDeterminingNumberComponents1976] (**Supplementary Table 3**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] implied a five-factor solution (Figure \@ref(fig:efa-plot-print)-C).
+Hence, we tested both five-factor and six-factor solutions using iterative EFA where we gradually identified and discarded problematic items (factor-loading <0.30 and cross-loading >0.30).
+In this process, we found a five-factor structure for LEBA inventory with 25 items.
+Table \@ref(tab:EFATable) displays the factor-loading ($\lambda$) and communality of the items.
+Both factor loadings and commonalities advocate to accept this five-factor solution ( |$\lambda$|= `r apa(min.loadings,2,T)` - `r apa(max.loadings, 2, T)`; commonalities= `r apa(min.com,2,T)` - `r apa(max.com, 2, T)`).
+These five factors explains `r apa(var1,2,T)`%, `r apa(var2,2,T)`%, `r apa(var3,2,T)`%, `r apa(var4,2,T)`%, `r apa(var5,2,T)`% of the total variance in individual's light exposure related behaviours respectively.
+All factors exhibited excellent to satisfactory reliability (ordinal $\alpha$= `r apa(F1.alpha,2,F)`, `r apa(F2.alpha,2,T)`, `r apa(F3.alpha,2,T)`, `r apa(F4.alpha,2,T)`, `r apa(F5.alpha,2,T)` respectively).
+The entire inventory also exhibited satisfactory reliability ($\omega_t$=`r apa(omega$omega.tot,2,T)`).
+
+However, the histogram of the absolute values of nonredundant residual correlations (Figure \@ref(fig:efa-plot-print)-D) displayed that `r sumR`% of correlations were greater >|.05|, indicating a possible under-factoring.
+[@desjardinsHandbookEducationalMeasurement2018].
+Subsequently, we fitted a six-factor solution, where a factor with only two salient variables emerged, thus disqualifying the six-factor solution (**Supplementary Table 4**).
+While making the judgement of accepting this five-factor solution we considered both factor's interpretability and their psychometric properties.
+We deemed the five derived factors as highly interpretable  and relevant concerning our aim to capture light exposure-related behaviour, we retained all of them with 25 items.
+Two of the items showed negative factor-loading (item 08: `r Hmisc::label(data$slypos_leba_08)` and item 37: `r Hmisc::label(data$slypos_leba_37)`).
+Upon re-inspection, we recognized these items to be negatively correlated to the respective factor, and thus, we reverse-scored these two items.
+
 (ref:efa-plot-print) (A) Inter-item polychoric correlation coefficients for the 48 items.
@@
 ```
-
-Iterative EFA revealed a five-factor structure for LEBA inventory and retained 25 items.
-Table \@ref(tab:EFATable) displays the factor-loading ($\lambda$) and communality of the items.
-Both factor loadings and commonalities advocate to accept this five-factor solution ( |$\lambda$|= `r apa(min.loadings,2,T)` - `r apa(max.loadings, 2, T)`; commonalities= `r apa(min.com,2,T)` - `r apa(max.com, 2, T)`).
-However, the histogram of the absolute values of nonredundant residual correlations (Figure \@ref(fig:efa-plot-print)-D) displayed that `r sumR`% of correlations were greater >|.05|, indicating a possible under-factoring.
-[@desjardinsHandbookEducationalMeasurement2018].
-Subsequently, we fitted a six-factor solution, where a factor with only two salient variables emerged, thus disqualifying the six-factor solution (**Supplementary Table 4**).
-
-In the five-factor solution, the first factor had three items and encapsulated the individual's preference for using blue light filters in different light environments.
-The second factor contained six items that incorporated the individuals' hours spent outdoors.
-The third factor contained five items that looked into specific behaviours of using a phone and smartwatch in bed.
-The fourth factor comprised five items investigated the other behaviours related to the individual's electric light exposure before bedtime.
-lastly, the fifth factor encompassed six items capturing the individual's morning and daytime light exposure-related behaviour.
-These five factors explains `r apa(var1,2,T)`%, `r apa(var2,2,T)`%, `r apa(var3,2,T)`%, `r apa(var4,2,T)`%, `r apa(var5,2,T)`% of the total variance in individual's light exposure related behaviours respectively.
-All factors exhibited excellent to satisfactory reliability (ordinal $\alpha$= `r apa(F1.alpha,2,F)`, `r apa(F2.alpha,2,T)`, `r apa(F3.alpha,2,T)`, `r apa(F4.alpha,2,T)`, `r apa(F5.alpha,2,T)` respectively).
-The entire inventory also exhibited satisfactory reliability ($\omega_t$=`r apa(omega$omega.tot,2,T)`).
-While making the judgement of accepting this five-factor solution we considered both factor;s interpretability and their psychometric properties.
-We deemed the five derived factors as highly interpretable  and relevant concerning our aim to capture light exposure-related behaviour, we retained all of them with 25 items.
-Two of the items showed negative factor-loading (item 08: `r Hmisc::label(data$slypos_leba_08)` and item 37: `r Hmisc::label(data$slypos_leba_37)`).
-Upon re-inspection, we recognized these items to be negatively correlated to the respective factor, and thus, we reverse-scored these two items.
 
@@
 
-CFA results (Table \@ref(tab:tabCfa)) indicated that the five-factor structure fitted to the 25-item LEBA inventory attained an acceptable fit (CFI =`r apa(fit.1[5],2,T)`; TLI = `r apa(fit.1[6],2,T)`; RMSEA = `r apa(fit.1[7],2,T)` [`r apa(fit.1[8],2,T)`-`r apa(fit.1[9],2,T)`, 90% CI]) with two imposed equity constraints on item pairs 32-33 [item 32: I dim my mobile phone screen within 1 hour before attempting to fall asleep; item 33: I dim my computer screen within 1 hour before attempting to fall asleep] and 16-17 [item 16: I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day; item 17: I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day].
+To investigate the structural validity of the five-factor structure obtained in EFA, we conducted a confirmatory factor analysis (CFA) on the CFA sample.
+The five-factor structure with 25 items showed acceptable fit (Table \@ref(tab:tabCfa)) indicated that the five-factor structure fitted to the 25-item LEBA inventory attained an acceptable fit providing evidence of structural validity (CFI =`r apa(fit.1[5],2,T)`; TLI = `r apa(fit.1[6],2,T)`; RMSEA = `r apa(fit.1[7],2,T)` [`r apa(fit.1[8],2,T)`-`r apa(fit.1[9],2,T)`, 90% CI]).
+Two equity constraints were imposed on item pairs 32-33 (item 32: I dim my mobile phone screen within 1 hour before attempting to fall asleep; item 33: I dim my computer screen within 1 hour before attempting to fall asleep) and 16-17 (item 16: I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day; item 17: I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day).
 Item pair 32-33 describes the preference for dimming the electric devices' brightness before bedtime, whereas item pair 16-17 represents the use of blue filtering or coloured glasses during the daytime.
@@
 In order to improve the model fit, we conducted a post-hoc model modification.
-Firstly, the  modification indices suggested cross-loadings between item 37 and 26 [item 37: I purposely leave a light on in my sleep environment while sleeping; item 26: I turn on my ceiling room light when it is light outside], which were hence discarded.
-Secondly, items 30 and 41 [item 30: I look at my smartwatch within 1 hour before attempting to fall asleep; item 41: I look at my smartwatch when I wake up at night] showed a tendency to co-vary in their error variance (MI = 141.127, p<0.001 ).
+Firstly, the  modification indices suggested cross-loadings between item 37 and 26 (item 37: I purposely leave a light on in my sleep environment while sleeping; item 26: I turn on my ceiling room light when it is light outside), which were hence discarded.
+Secondly, items 30 and 41 (item 30: I look at my smartwatch within 1 hour before attempting to fall asleep; item 41: I look at my smartwatch when I wake up at night) showed a tendency to co-vary in their error variance (MI = 141.127, p<0.001 ).
 By allowing the latter pair of items (30 $\&$ 41) to co-vary, the model's error variance attained an improved fit (CFI =`r apa(fit.2[5],2,T)`; TLI = `r apa(fit.2[6],2,T)`); RMSEA = `r apa(fit.2[7],2,T)` [`r apa(fit.2[8],2,T)`-`r apa(fit.2[9],2,T)`, 90% CI]; SRMR = `r apa(fit.2[10],2,T) `).

### 2023-01-16 manuscript_v3.Rmd

@@
 
-Our results focus on the development of the LEBA inventory and its psychometric validation using a large scale online sample data (n=`r nrow(data)`).
+Our results focus on the development of the LEBA inventory and its psychometric validation using a large scale online sample data (n = `r nrow(data)`).
 
@@
 
-We conducted two rounds of large scale online survey between 17 May 2021 and 3 September 2021 to generate data from `r nrow(data)` participants with varied geographic locations (countries=`r nrow(num.countries)`; time-zone=`r nrow(numUTC)`).
+We conducted two rounds of large scale online survey between 17 May 2021 and 3 September 2021 to generate data from `r nrow(data)` participants with varied geographic locations (countries = `r nrow(num.countries)`; time-zone = `r nrow(numUTC)`).
 For a complete list of geographic locations, see **Supplementary Table 2**.
@@
 Only participants completing the full LEBA inventory were included.
-We used the data from first round for the exploratory factor analysis (EFA sample; n=`r nrow(EFA.data)`) and data from the second round was used in the confirmatory factor analysis (CFA sample; n=`r nrow(CFA.data)`).
+We used the data from first round for the exploratory factor analysis (EFA sample; n = `r nrow(EFA.data)`) and data from the second round was used in the confirmatory factor analysis (CFA sample; n = `r nrow(CFA.data)`).
 Participants in our survey were aged between `r min(desctable.data$slypos_demographics_age)` to `r max(desctable.data$slypos_demographics_age)` years, with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 2)` years of age [Overall: `r mean(desctable.data$slypos_demographics_age)`±`r sd(desctable.data$slypos_demographics_age)`; EFA: `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
@@
 
-We observed that the response patterns of LEBA inventory for the entire sample (n=`r nrow(sem.data)`) were not normally distributed (Figures \@ref(fig:efagtPic1) and \@ref(fig:efagtPic2)).
-All items violated both univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality [(@mardiaMeasuresMultivariateSkewness1970].
+We observed that the response patterns of LEBA inventory for the entire sample (n = `r nrow(sem.data)`) were not normally distributed (Figures \@ref(fig:efagtPic1) and \@ref(fig:efagtPic2)).
+All items violated both univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality [@mardiaMeasuresMultivariateSkewness1970].
 The multivariate skewness was`r printnum(mardia.all.data$b1p)` (p<0.001) and the multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p<0.001).
@@
 Similar non-normal distribution of response pattern was also observed in the EFA sample.
-**Supplementary Figure 1** depicts the univariate descriptive statistics for the EFA sample (n=`r nrow(EFA.data)`).
+**Supplementary Figure 1** depicts the univariate descriptive statistics for the EFA sample (n = `r nrow(EFA.data)`).
 Further, We observed that each item's correlation with the aggregated sum of the 48-item's score varied largely (corrected item-total correlation= `r apa(low.r.corec,2,T)` -`r apa(high.r.corec,2,T)`) indicating the possibility of multi-factor structure  of the LEBA inventory.
@@
 
-Exploratory analysis revealed that items of LEBA inventory can be categorized into five major factors: (i) wearing blue light filters; (ii) spending time out doors; (iii) using phone and smartwatch in bed; (iv) usinf light before bedtime (v) using light in the morning and during daytime.
+Exploratory analysis revealed that items of LEBA inventory can be categorized into five major factors: (i) wearing blue light filters; (ii) spending time out doors; (iii) using phone and smartwatch in bed; (iv) using light before bedtime (v) using light in the morning and during daytime.
 In this stage of analysis, we retained 25 items.
@@
 
-Prior to conducting the EFA, we have checked the post-hoc sampling adequacy by applying Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy on the EFA sample (n=`r nrow(EFA.data)`) [@kaiserIndexFactorialSimplicity1974] and the quality of the correlation matrix by Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954].
+Prior to conducting the EFA, we have checked the post-hoc sampling adequacy by applying Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy on the EFA sample (n = `r nrow(EFA.data)`) [@kaiserIndexFactorialSimplicity1974] and the quality of the correlation matrix by Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954].
 KMO>0.50 would indicate adequate sample size [@hutchesonMultivariateSocialScientist1999] and a significant test of sphericity would indicate satisfactory quality of the correlation matrix .
-Results indicated that we had an adequate sample size (KMO=`r printnum(KMO$MSA)`) and correlation matrix ($\chi^2_{1128}$=`r apa(bartlet$chisq, 2, T)`, p< 0.001).
+Results indicated that we had an adequate sample size (KMO = `r printnum(KMO$MSA)`) and correlation matrix ($\chi^2_{1128}$ = `r apa(bartlet$chisq, 2, T)`, p< 0.001).
 However, `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than |0.30|, and the inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`.
@@
 Table \@ref(tab:EFATable) displays the factor-loading ($\lambda$) and communality of the items.
-Both factor loadings and commonalities advocate to accept this five-factor solution ( |$\lambda$|= `r apa(min.loadings,2,T)` - `r apa(max.loadings, 2, T)`; commonalities= `r apa(min.com,2,T)` - `r apa(max.com, 2, T)`).
+Both factor loadings and commonalities advocate to accept this five-factor solution ( |$\lambda$| = `r apa(min.loadings,2,T)`-`r apa(max.loadings, 2, T)`; commonalities = `r apa(min.com,2,T)`-`r apa(max.com, 2, T)`).
 These five factors explains `r apa(var1,2,T)`%, `r apa(var2,2,T)`%, `r apa(var3,2,T)`%, `r apa(var4,2,T)`%, `r apa(var5,2,T)`% of the total variance in individual's light exposure related behaviours respectively.
-All factors exhibited excellent to satisfactory reliability (ordinal $\alpha$= `r apa(F1.alpha,2,F)`, `r apa(F2.alpha,2,T)`, `r apa(F3.alpha,2,T)`, `r apa(F4.alpha,2,T)`, `r apa(F5.alpha,2,T)` respectively).
+All factors exhibited excellent to satisfactory reliability (ordinal $\alpha$ = `r apa(F1.alpha,2,T)`, `r apa(F2.alpha,2,T)`, `r apa(F3.alpha,2,T)`, `r apa(F4.alpha,2,T)`, `r apa(F5.alpha,2,T)` respectively).
 The entire inventory also exhibited satisfactory reliability ($\omega_t$=`r apa(omega$omega.tot,2,T)`).
@@
 To investigate the structural validity of the five-factor structure obtained in EFA, we conducted a confirmatory factor analysis (CFA) on the CFA sample.
-The five-factor structure with 25 items showed acceptable fit (Table \@ref(tab:tabCfa)) indicated that the five-factor structure fitted to the 25-item LEBA inventory attained an acceptable fit providing evidence of structural validity (CFI =`r apa(fit.1[5],2,T)`; TLI = `r apa(fit.1[6],2,T)`; RMSEA = `r apa(fit.1[7],2,T)` [`r apa(fit.1[8],2,T)`-`r apa(fit.1[9],2,T)`, 90% CI]).
+The five-factor structure with 25 items showed acceptable fit (Table \@ref(tab:tabCfa)) providing evidence of structural validity (CFI = `r apa(fit.1[5],2,T)`; TLI = `r apa(fit.1[6],2,T)`; RMSEA = `r apa(fit.1[7],2,T)` [`r apa(fit.1[8],2,T)`-`r apa(fit.1[9],2,T)`, 90% CI]).
 Two equity constraints were imposed on item pairs 32-33 (item 32: I dim my mobile phone screen within 1 hour before attempting to fall asleep; item 33: I dim my computer screen within 1 hour before attempting to fall asleep) and 16-17 (item 16: I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day; item 17: I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day).
@@
 Secondly, items 30 and 41 (item 30: I look at my smartwatch within 1 hour before attempting to fall asleep; item 41: I look at my smartwatch when I wake up at night) showed a tendency to co-vary in their error variance (MI = 141.127, p<0.001 ).
-By allowing the latter pair of items (30 $\&$ 41) to co-vary, the model's error variance attained an improved fit (CFI =`r apa(fit.2[5],2,T)`; TLI = `r apa(fit.2[6],2,T)`); RMSEA = `r apa(fit.2[7],2,T)` [`r apa(fit.2[8],2,T)`-`r apa(fit.2[9],2,T)`, 90% CI]; SRMR = `r apa(fit.2[10],2,T) `).
+By allowing the latter pair of items (30 $\&$ 41) to co-vary, the model's error variance attained an improved fit (CFI = `r apa(fit.2[5],2,T)`; TLI = `r apa(fit.2[6],2,T)`); RMSEA = `r apa(fit.2[7],2,T)` [`r apa(fit.2[8],2,T)`-`r apa(fit.2[9],2,T)`, 90% CI]; SRMR = `r apa(fit.2[10],2,T) `).
 
@@
 Internal consistency ordinal $\alpha$ for the five factors of the LEBA were `r apa(rel.k[2,1],2,T)`, `r apa(rel.k[2,2],2,T)`, `r apa(rel.k[2,3],2,T)`, `r apa(rel.k[2,4],2,T)`, `r apa(rel.k[2,5],2,T)`, respectively.
-The reliability of the total inventory was satisfactory ($\omega_t$=`r apa(rel.k[5,6],2,T)`).
+The reliability of the total inventory was satisfactory ($\omega_t$ = `r apa(rel.k[5,6],2,T)`).
 Figure \@ref(fig:figcfa) depicts the obtained CFA structure, while  **Supplementary Figure 2** depicts the data distribution and endorsement pattern of the retained 23 items in our CFA sample.
@@
 
-We reported the measurement invariance (MI) analysis on the CFA sample based on native (n=`r mi.count[1,2]`) and non-native English speakers (n=`r mi.count[2,2]`).
+We reported the measurement invariance (MI) analysis on the CFA sample based on native (n = `r mi.count[1,2]`) and non-native English speakers (n = `r mi.count[2,2]`).
 A detailed demographic description are provided in **Supplementary Table 5**.
@@
 ```{r InvarianceTab, results='asis'}
-apa_table(Invariance.table, align = "c",  caption = "Measurement Invariance analysis on CFA sample (n=262) across native and non-native English speakers.", note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square; a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; * =  df of model comparison.", landscape = T, font_size = "footnotesize", escape=F )
+apa_table(Invariance.table, align = "c",  caption = "Measurement Invariance analysis on CFA sample (n = 262) across native and non-native English speakers.", note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square; a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; * =  df of model comparison.", landscape = T, font_size = "footnotesize", escape=F )
 
@@
 ## Secondary Analysis: Grade Level Identification and Semantic Scale Network Analysis
+
 We investigated the language-based accessibility of LEBA using Flesch-Kincaid grade level analysis [@flesch1948new].
-Results indicated that at least a language proficiency of educational grade level-four (US education system) with age above eight years  are requied to comprehend the items used in LEBA inventory.
+Results indicated that at least a language proficiency of educational grade level-four (US education system) with age above eight years  are required to comprehend the items used in LEBA inventory.
 Semantic Scale analysis [@rosenbusch2020semantic]  was administered to assess the LEBA's (23 items) semantic relation to other questionnaires.
 LEBA inventory was most strongly semantically related to scales about sleep: The "Sleep Disturbance Scale For Children" [@bruni1996sleep] and the "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite].
-The cosine similarity index ranged between .47 to .51.
+The cosine similarity index ranged between 0.47 to 0.51.
 
@@
 ## Developing a Short Form of LEBA: IRT-Based Analysis
+
 In order to derive a short form of the LEBA inventory, we fitted each factor of the LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n=690).
 The resulting item discrimination parameters of the inventory fell into categories of "very high" (10 items), "high" (4 items), "moderate" (4 items), and "low" ( 5 items), indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**).
-An examination of the item information curve (**Supplementary Figure 3**) revealed five items (1, 25, 30, 38, & 41) provided very low information regarding light exposure related behaviors with relatively flat curves (I($\theta$) \<.20).
+An examination of the item information curve (**Supplementary Figure 3**) revealed five items (1, 25, 30, 38, & 41) provided very low information regarding light exposure related behaviors with relatively flat curves (I($\theta$) \<0.20).
 We discarded those items, culminating in a short form of LEBA with five factors and 18 items (**Supplementary File 2**).
@@
 ```{r IRTparameters, eval=FALSE, include=FALSE, results='asis'}
-apa_table(itemparameters, caption = "Items discrimination and response category difficulty thresholds of 23 items in  LEBA (n=690)", note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
+apa_table(itemparameters, caption = "Items discrimination and response category difficulty thresholds of 23 items in  LEBA (n = 690)", note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
 ```
@@
 Finally, **Supplementary Table 7** summarises the item fit indexes of the LEBA short form.
-All 18 items yielded RMSEA value $\le$0.06, indicating an adequate fit to the fitted IRT model.
+All 18 items yielded RMSEA value $\le$ 0.06, indicating an adequate fit to the fitted IRT model.
 Furthermore, **Supplementary Figure 4** depicts the person fit Zh statistics histogram for the five IRT models.
@@
 ```{r itemfittab, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, results='asis'}
-apa_table(IRT.details , caption ="Item discrimination, response category difficulty thrsholds and fit statistics of the 18 items in short LEBA (n=690)",note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
+apa_table(IRT.details , caption ="Item discrimination, response category difficulty thrsholds and fit statistics of the 18 items in short LEBA (n = 690)",note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
 ```
@@
 The exploratory factor analysis revealed a highly interpretable five-factor solution ("Wearing blue light filters", "Spending time outdoors", "Using phone and smartwatch in bed", "Using light before bedtime", and "Using light in the morning and during daytime") with 25 items.
-Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five-factor structure we obtained in our EFA, thus providing evidence for structural validity.(CFI=`r apa(fit.2[5],2,T)`; TLI=`r apa(fit.2[6],2,T)`; RMSEA=`r apa(fit.2[7],2,T)`).
+Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five-factor structure we obtained in our EFA, thus providing evidence for structural validity.(CFI = `r apa(fit.2[5],2,T)`; TLI = `r apa(fit.2[6],2,T)`; RMSEA = `r apa(fit.2[7],2,T)`).
 In this model, we discarded two more items (item 26 $\&$ 37 ) for possible cross-loadings.
@@
 However, at the early developmental stage, a value of .50 is considered acceptable [@dall2010developmental; @field2013discovering; @Nunnally1978].
-Thus, we confer, the internal consistency coefficients ordinal alpha for the five factors and the total inventory were satisfactory (Ordinal alpha ranged between `r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$=`r apa(rel.k[5,6],2,T)`).
+Thus, we confer, the internal consistency coefficients ordinal alpha for the five factors and the total inventory were satisfactory (Ordinal alpha ranged between `r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$ = `r apa(rel.k[5,6],2,T)`).
 
@@
 To avoid these situations we  derived a short version of the LEBA (18 items) using IRT analysis.
-We fitted a graded response model to the combined EFA and CFA sample (n=`r nrow(data)`) and discarded five items (1, 25, 30, 38, & 41) with relatively flat item information curve [I($\theta$) <.20].
+We fitted a graded response model to the combined EFA and CFA sample (n = `r nrow(data)`) and discarded five items (1, 25, 30, 38, & 41) with relatively flat item information curve [I($\theta$) <.20].
 The resulting test information curves suggest that the short-LEBA is a psychometrically sound measure with adequate coverage of underlying traits and can be applied to capture the frequency of different light exposure related behaviours reliably.
@@
 - [...] Please select "Does not apply/I don't know." here.
-
-We collected the survey data between 17 May 2021 and 3 September 2021 – firstly from `r nrow(EFA.descriptives)` participants (EFA sample) – and subsequently, another dataset from `r nrow(CFA.descriptives)` participants (CFA sample), totalling `r nrow(desctable.data)`.
 

### 2023-01-16 manuscript.Rmd
Links updated

@@
   - id            : "9"
-    institution   : "XIMES GmbH, Vienna, Austria"
+    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
   - id            : "10"
-    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
+    institution   : "Translational Sensory & Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany"
   - id            : "11"
-    institution   : "Translational Sensory & Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany"
+    institution   : "TUM Department of Sport and Health Sciences (TUM SG), Technical University of Munich, Munich, Germany"
   - id            : "12"
-    institution   : "TUM Department of Sport and Health Sciences (TUM SG), Technical University of Munich, Munich, Germany"
-  - id            : "13"
-    institution   : "University of Oxford, Department of Experimental Psychology, Oxford, United Kingdom"
+    institution   : "TUM Institute of Advanced Study (TUM-IAS), Technical University of Munich, Garching, Germany"
   - id            : "*"
@@
 abstract: |
-  Light exposure is an essential driver of health and well-being.
-Our behaviour modulates many aspects of light exposure, but how these light-related behaviours can be shaped to optimise personal light exposure is currently unknown.
-Here, we present a novel, self-reported and psychometrically validated instrument to capture light exposure-related behaviour, the Light Exposure Behaviour Assessment (LEBA).
+  Light exposure is an essential driver of health and well-being, and individual behaviours during rest and activity modulate physiologically-relevant aspects of light exposure.
+Further understanding the behaviours that influence individual photic exposure patterns may provide insight into the volitional contributions to the physiological effects of light and guide bevavioral points of intervention.
+Here, we present a novel, self-reported and psychometrically validated inventory to capture light exposure-related behaviour, the Light Exposure Behaviour Assessment (LEBA).
 
@@
 In a confirmatory factor analysis (CFA) performed on an independent subset of participants (n=262), we removed two additional items to attain the best fit for the five-factor solution (CFI=0.95, TLI=0.95, RMSEA=0.06).
-The internal consistency reliability coefficient for the total instrument yielded McDonald’s Omega(total)=0.68.
+The internal consistency reliability coefficient for the total instrument yielded McDonald’s Omega=0.68.
 Measurement model invariance analysis between native and non-native English speakers showed our model attained the highest level of invariance (residual invariance; CFI=0.95, TLI=0.95, RMSEA=0.05).
@@
 
-  The psychometric properties of the LEBA instrument indicate the usability to measure the light exposure-related behaviours across a variety of settings and may offer a scalable solution to characterise light exposure-related behaviours in remote samples.
-The LEBA instrument will be available under the open-access CC-BY-NC-ND license.
+  The psychometric properties of the LEBA indicate the usability to measure light exposure-related behaviours.
+The instrument may offer a scalable solution to characterize behaviours that influence individual photic exposure patterns in remote samples.
+The LEBA inventory is  available under the open-access CC-BY-NC-ND license.
+
+  Instrument webpage: https://leba-instrument.org/
+  GitHub repository containing this manuscript: https://github.com/leba-instrument/leba-manuscript
 
 keywords          : "light exposure, light-related behaviours, non-visual effects of light, psychometrics"
-wordcount         : "X"
+wordcount         : "6314"
 
@@
 Light exposure received by the eyes affects many facets of human health, well-being, and performance beyond visual sensation and perception [@boyce_light_2022].
-The so-called non-image-forming (NIF) effects of light comprise light’s circadian and non-circadian influence on several physiological and psychological functions, such as the secretion of melatonin, sleep, mood, pupil size, body temperature, alertness, and higher cognitive functions [@Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020].
-With the introduction of artificial electric light, human behaviour has become somewhat independent of the natural light-dark cycle – people can now frequently choose when to be exposed to light or darkness.
+The non-image-forming (NIF) effects of light comprise light’s circadian and non-circadian influence on several physiological and psychological functions, such as the secretion of melatonin, sleep, mood, pupil size, body temperature, alertness, and higher cognitive functions [@Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020].
+
+With the introduction of artificial electric light, human behaviour has become dissociated from the light-dark cycle given by solar radiation.
+People can now frequently choose when to be exposed to light or darkness.
 For example, they can decide whether to go outdoors and seek out sunlight, switch on/off light-emitting devices, use certain types of lights at home, or avoid specific light environments altogether.
-Additionally, when light sources can not be directly manipulated, sought out, or avoided (for example, at school, work, or in public places), there is still potential leeway to influence them behaviourally, for instance, by wearing sunglasses, directing one’s gaze away or supplementing the situation with additional light sources.
-Although clearly yielding the potential for good, this agency is further associated with increased electric light exposure at night and indoor time during the day, compromising the natural temporal organisation of the light-dark cycle.
-For example, in the US, an average of 87% of the time is spent in enclosed buildings [@Klepeis.2001], and more than 80% of the population is exposed to a night sky that is brighter than nights with a full moon due to electric light at night [@navara_dark_2007].
-An extensive body of scientific evidence suggests that the imbalance of light and dark exposure disrupts humans’ light-dependent physiological systems [@Lunn.2017].
-Subsequently, this disruption gives rise to a series of adverse health consequences, including the alteration of several hormonal rhythms, increased cancer rates, cardiovascular diseases, and metabolic disorders, such as obesity, and type II diabetes [@Lunn.2017; @navara2007dark; @Chellappa.2019]
-These findings have sparked a significant call for assessment and guidance regarding healthy light exposure and timing – the latter was recently published as consensus-based experts’ recommendations, postulating specific requirements for indoor light environments during the daytime, evening, and nighttime [@Brown.2022].
+Additionally, when light sources cannot be directly manipulated, sought out, or avoided (for example, at school, work, or in public places), there is still potential leeway to influence personal light exposure behaviourally, for instance, by wearing sunglasses, directing one’s gaze away or supplementing the situation with additional light sources.
+Although clearly yielding the potential for good, these behaviours are further associated with increased electric light exposure at night and indoor time during the day, compromising the natural temporal organisation of the light-dark cycle.
+For example, in the US, an average of 87% of the time is spent in enclosed buildings [@Klepeis.2001], and more than 80% of the population is exposed to a night sky that is brighter than nights with a full moon due to electric light at night [@navara2007dark].
+
+An extensive body of scientific evidence suggests that improper light exposure may be disruptive for health and well-being, giving rise to a series of adverse consequences, including the alteration of hormonal rhythms, increased cancer rates, cardiovascular diseases, and metabolic disorders, such as obesity and type II diabetes [@Lunn.2017; @navara2007dark; @Chellappa.2019].
+These findings have sparked a significant call for assessment and guidance regarding healthy light exposure as exemplified by a recently published set of consensus-based experts’ recommendations with specific requirements for indoor light environments during the daytime, evening, and nighttime [@Brown.2022].
+
 Furthermore, building on earlier attempts [e.g.
-@hubalek_ambulant_2006], there was a recent push toward the development and use of portable light loggers to improve ambulant light assessment and gain more insight into the NIF effects of light on human health in field conditions [@stampfli_light-dosimeter_2021; @van_duijnhoven_recommendations_2017; @webler_towards_2021].
-Attached to different body parts (e.g., wrist, head on eye level, chest), these devices allow objectively measuring personal light exposure under real-world conditions and are valuable tools for field studies.
+@hubalek_ambulant_2006], there was a recent push toward the development and use of portable light loggers to improve ambulant light assessment and gain more insight into the NIF effects of light on human health in field conditions [@stampfli_light-dosimeter_2021; @van_duijnhoven_recommendations_2017; @webler_towards_2021; @aarts2017performance].
+Attached to different body parts (e.g., wrist; head, at eye level; chest), these light loggers allow for the objective measurement of individual photic exposure patterns under real-world conditions and thus are valuable tools for field studies.
 Nevertheless, these devices also encompass limiting factors such as potentially being intrusive (e.g., when eye-level worn), yielding the risk of getting covered (e.g., when wrist- or chest-worn) and requiring (monetary) resources and expertise for acquisition and maintenance of the devices.
-On the other hand, several attempts have been made to quantify received light exposure subjectively with self-report questionnaires (cf.
-**Supplementary Table 1**), bypassing the cost and intrusiveness issues.
-However, subjective light intensity assessments pose a new set of challenges: The human visual system constantly adapts to brightness [@hurvich_perception_1966], while the human non-visual light processing works largely subconsciously [@allen_exploiting_2018], making the self-report assessment of light properties potentially quite challenging, especially for inexperienced laypeople.
+
+On the other hand, several attempts have been made to quantify received light exposure subjectively with self-report questionnaires (**Supplementary Table 1**), bypassing the cost and intrusiveness issues.
+However, subjective light intensity assessments pose a new set of challenges: The human visual system constantly adapts to brightness [@hurvich_perception_1966], while the signals underlying the non-visual effects of light are independent from perception [@allen_exploiting_2018], making the self-report assessment of light properties challenging.
 Retrospectively recalling the properties of a light source can further complicate such subjective evaluations.
-Moreover, measuring light properties alone does not yield any information about how individuals might behave differently regarding diverse light situations.
-These measurement limitations point to a couple of research challenges we aim to take on here: How can we gain insight into light exposure patterns via self-report but circumvent directly inquiring about the specific properties and intensity of a light source?
+Moreover, measuring light properties alone does not yield any information about how individuals might behave differently regarding diverse light environments such  as work, home or outdoors.
+
+These measurement limitations point to a couple of research challenges which we adressed here: How can we gain insight into light exposure patterns via self-report but circumvent directly inquiring about the specific properties and intensity of a light source?
 And how can we simultaneously assess how people habitually interact with the received light?
 We propose that these challenges can be tackled by assessing light-exposure-related behaviour.
-We argue that, besides measuring received light exposure as intensity, it is also essential to understand people's behaviours concerning different light situations.
-Since, in many cases, humans have become their own agents regarding their exposure to light or darkness through artificial electric light, people's light exposure-related behaviours ultimately determine their light consumption and timing: People receive different light depending on their daily activities, including workplace habits, bedtime hygiene, pastime and social activities.
-The final objective of changing light-dark exposure patterns to avoid or mitigate negative health consequences from unhealthy habits will not just need an assessment of the lighting properties but the active change of behaviours related to light exposure.
-We argue that assessing these activities is a beneficial stepping stone for prospective behaviour change.
-Furthermore, people without light measurement expertise may find it easier to appraise and recall their behaviour concerning light exposure than subjectively assessing a light source’s properties.
+We argue that, besides measuring received light exposure as intensity, it is also essential to understand people's behaviours with respect to different light situations.
+In many cases, humans have become their own agents regarding their exposure to light or darkness through daylight and electric light, and as such people’s light exposure-related behaviours ultimately determine their light consumption and timing: People receive different light depending on their daily activities, including workplace habits, bedtime hygiene, pastime and social activities.
+Ultimately, in order to optimize lighting for human health and well being, better understanding of light-related behaviours will serve to identify additional points of intervention as well as to provide an added dimension to efficacy and implementation studies of novel lighting strategies.
+We argue that assessing these activities is a beneficial stepping stone for prospective behaviour change to maintain light hygiene: a proper balance of exposures to light to maintain circadian rhythms.
+
 To date, little effort has been made to understand and capture these activities.
@@
 However, only a few questions of these existing tools were associated with light exposure-related behaviour.
-For example, the “Munich Chronotype  Questionnaire” [MCTQ; @roenneberg2003life], a popular self-report tool for identifying chronotypes via mid-sleep times, includes questions about the individual’s time spent outdoors on workdays and free days.
-The Visual Light Sensitivity Questionnaire-8 [@verriotto2017new] and Photosensitivity Assessment Questionnaire (PAQ; @bossini2006sensibilita), a couple of self-report tools measuring visual light sensitivity, contain single items which probe the preference for specific light situations: "In the past month, how often did you need to wear dark glasses on cloudy days or indoors?" [@verriotto2017new]; "I prefer rooms that are in semi-darkness."; [@bossini2006sensibilita].
-In addition, the “Pittsburgh Sleep Quality Index” [PSQI; @buysse1989pittsburgh], a popular measure of sleep quality, contains questions about sleep and wake-up times, which are relevant to light exposure around bedtime.
-However, none of these questionnaires provides a scaleable solution to capture light exposure-related behaviour in various physiologically relevant lighting scenarios.
-To fill this gap, we here present the development process of a novel self-report tool - the “Light Exposure Behavior Assessment” (LEBA) - for capturing and quantifying diverse light exposure-related behaviours.
-
-# Methods
+For example, the “Munich Chronotype  Questionnaire” [@roenneberg2003life], a popular self-report tool for identifying chronotypes via mid-sleep times, includes questions about the individual’s typical time spent outdoors on workdays and free days.
+The Visual Light Sensitivity Questionnaire-8 [@verriotto2017new] and Photosensitivity Assessment Questionnaire [@bossini2006sensibilita] are a couple of self-report tools measuring visual light sensitivity.
+They contain single items which probe the preference for specific light situations such as: “In the past month, how often did you need to wear dark glasses on cloudy days or indoors?” [@verriotto2017new];"I prefer rooms that are in semi-darkness."; [@bossini2006sensibilita].
+In addition, the “Pittsburgh Sleep Quality Index” [@buysse1989pittsburgh], is a popular measure of sleep quality.
+It contains questions about bedtime and wake-up times, which are relevant to light exposure around bedtime.
+However, none of these questionnaires provides a scalable solution to capture light exposure-related behaviour in various lighting situations.
+To fill this gap, we here present the development process of a novel self-reported inventory - the Light Exposure Behaviour Assessment (LEBA) - for characterizing diverse light exposure-related behaviours.
 
@@
 
-## Data Collection
-
 ```{r demotab, warning=F, message=F}
@@
 
-A quantitative cross-sectional, fully anonymous, geographically unconstrained online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
-Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (<https://enlightenyourclock.org/participate-in-research>) of the science-communication comic book "Enlighten your clock", co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by the distribution of the survey link via f.lux [@f.lux].
-The initial page of the online survey provided information about the study, including that participation was voluntary and that respondents could withdraw from participation at any time without being penalised.
-Subsequently, consent was recorded digitally for the adult participants (\>18 years), while under-aged participants (\<18 years) were prompted to obtain additional assent from their parents/legal guardians.
-Filling in all questionnaires was estimated to take less than 30 minutes, and participation was not compensated.
-As a part of the demographic data, participants provided information regarding age, sex, gender identity, occupational status, COVID-19-related occupational setting, time zone/country of residence and native language.
-The demographic characteristics of our sample are given in **Table 1**.
-Participants were further asked to confirm that they participated in the survey for the first time.
-Additionally, five attention check items (e.g., "We want to make sure you are paying attention.
-What is 4+5?") were included among the questionnaires to ensure high data quality.
-All questions incorporating retrospective recall were aligned to a "past four weeks" period.
-
-We collected the survey data between 17 May 2021 and 3 September 2021 – firstly from `r nrow(EFA.descriptives)` participants (EFA sample) – and subsequently, another dataset from `r nrow(CFA.descriptives)` participants (CFA sample), totalling `r nrow(desctable.data)`.
-
-## Analytic Strategy
-
-Figure \@ref(fig:FlowchartFig) summarises the steps we followed while developing the LEBA. We conducted all analyses with the statistical software environment R [@R-base]. 
-**Firstly**, we set an item pool of 48 items with a six-point Likert-type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial scale.
-Our purpose was to capture light exposure-related behaviour.
-In that context, the first two response options: "Does not apply/I don't know" and "Never", provided similar information.
-As such, we collapsed them into one, making it a 5-point Likert-type response format (1-Never, 2-Rarely, 3-Sometimes, 4-Often, 5-Always).
-
-**Secondly**, the two rounds of data collection were administered. 
-**Thirdly**, we conducted descriptive and item analysis and proceeded to the exploratory factor analysis (EFA) using the "psych" package [@R-psych] on the data collected in the first round (EFA sample; n=`r nrow(EFA.descriptives)`), as a part of psychometric analysis.
-Prior to the EFA, the necessary assumptions, including sample adequacy, normality assumptions, and quality of correlation matrix, were assessed.
-As our data violated both the univariate and multivariate normality assumption and yielded ordinal response data, we used a polychoric correlation matrix in the EFA and employed "principal axis" (PA) as the factor extraction method [@desjardinsHandbookEducationalMeasurement2018; @watkinsStepbyStepGuideExploratory2020].
-We applied a combination of methods, including a Scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and Hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
-To determine the latent structure, we followed the common guidelines: (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading \> .3 across factors [@bandalosFactorAnalysisExploratory2018].
-<!-- We also conducted an EFA on the non-merged response options data set (**Supplementary File 1**).
--->
-
-For reliability estimation, the "psych" package was applied [@R-psych].
-Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it tends to deflate the estimates for Likert-type data since the calculation is based on the Pearson-correlation matrix, which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal].
-Subsequently, we reported ordinal alpha for each factor obtained in the EFA [@zumbo2007ordinal] to get better reliability estimates.
-We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$ coefficient, which was suggested as a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
-Both ordinal alpha and McDonald's $\omega_t$ coefficient values range between 0 to 1, where higher values represent better reliability.
-
-To validate the latent structure obtained in the EFA, we conducted a categorical confirmatory factor analysis (CFA) with the weighted least squares means and variance adjusted (WLSMV) estimation [@desjardinsHandbookEducationalMeasurement2018], using the "lavaan" package [@R-lavaan] on the data collected in the second round (CFA sample; n=`r nrow(CFA.descriptives)`).
-We assessed the model fit using standard model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI): close to .95 or above/ between .90-.95 and above (iii) root mean square error of approximation (RMSEA): close to .06 or below, (iv) Standardized root mean square (SRMR): close to .08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner].
-However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015], and SRMR does not work well with ordinal data [@RN1272].
-Consequently, we judged the model fit using CFI, TLI and RMSEA.
-
-We then assessed the measurement invariance (MI) of our scale between native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non-native English speakers (n=`r invariance.data.descriptives.count[2,2]`) in the CFA sample (n=`r nrow(CFA.descriptives)`).
-MI evaluates whether a construct has the psychometric equivalence and the same meaning across groups [@putnick2016measurement; @klinePrinciplesPracticeStructural2015].
-We used the structural equation modelling framework applying the "lavaan" package [@R-lavaan] to assess the measurement invariance.
-We successively compared four nested models: configural, metric, scalar, and residual models using the $\chi^2$ difference test ($\Delta \chi^2$).
-Among MI models, the configural model is the least restrictive, and the residual model is the most restrictive.
-A non-significant $\Delta \chi^2$ test between two nested measurement invariance models indicates mode fit does not significantly decrease for the superior model, thus allowing the superior invariance model to be accepted [@dimitrov2010testing; @widaman1997exploring].
-
-**Fourthly**, as secondary analysis, we identified the educational grade level required to understand the items in our scale with the Flesch-Kincaid grade level identification method [@flesch1948new] applying the "koRpus" [@R-koRpus] package.
-Correspondingly, we analysed possible semantic overlap of our developed scale using the ["Semantic Scale Network" (SSN)](https://rosenbusch.shinyapps.io/semantic_net/) engine [@rosenbusch2020semantic].
-The SSN detects semantically related scales and provides a cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic].
-Pairs of scales with a cosine similarity index value of 1 inidicate full semantical similarity, suggesting redundancy.
-
-**Lastly**, we derived a short form of the LEBA employing an Item Response Theory (IRT) based analysis.
-We fitted each factor of the LEBA to the combined EFA and CFA sample (n=`r nrow(sem.data)`) using the graded response model [@samejima1997handbook] via the "mirt" package [@R-mirt].
-IRT assesses the item quality by estimating the item discrimination, item difficulty, item information curve, and test information curve [@bakerBasicsItemResponse2017].
-Item discrimination indicates how well a particular item can differentiate between participants across the given latent trait continuum ($\theta$).
-Item difficulty corresponds to the latent trait level at which the probability of endorsing a particular response option is 50%.
-The item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
-Here, we reported the item difficulty and discrimination parameter and categorize the items based on their item discrimination index: none = 0; very low = 0.01 to 0.34; low = 0.35 to 0.64; moderate = 0.65 to 1.34 ; high = 1.35 to 1.69; very high \>1.70 [@bakerBasicsItemResponse2017].
-We discarded the items with a relatively flat item information curve (information \<.2) to derive the short form of LEBA.
-We also assessed the precision of the short LEBA utilizing the Test information curve (TIC).
-TIC indicates the amount of information a particular scale carries along the latent trait continuum.
-Additionally, the item and person fit of the fitted IRT models were analysed to gather more evidence on the validity and meaningfulness of our scale [@desjardinsHandbookEducationalMeasurement2018].
-The item fit was evaluated using the RMSEA value obtained from Signed-$\chi^2$ index implementation, where an RMSEA value $\le$.06 was considered an adequate item fit.
-The person fit was estimated employing the standardized fit index Zh statistics [@drasgow1985appropriateness].
-Here, Zh \< -2 was considered as a misfit [@drasgow1985appropriateness].
-
-```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Flow chart of the LEBA (long and short form) development and evaluation. ', out.height='100%', out.width='100%'}
-knitr::include_graphics('Figures/Figure1.png', dpi = 600 )
-```
-
-## Ethical Approval
-
-The current research project utilizes fully anonymous online survey data and therefore does not fall under the scope of the Human Research Act, making an authorisation from the ethics committee redundant.
-Nevertheless, the cantonal ethics commission (Ethikkommission Nordwest- und Zentralschweiz, EKNZ) reviewed our proposition (project ID Req-2021-00488) and issued an official clarification of responsibility.
-
-## Data Availability
-
-The present article is a fully reproducible open access "R Markdown" document.
-All code and data underlying this article -- along with two versions of the LEBA questionnaire (full and short) and online survey implementation templates on common survey platforms -- will be available under open-access licence (CC-BY-NC-ND) on a public [GitHub repository](https://github.com/leba-instrument).
+```{r EFAdata, include=FALSE}
+#This chunk holds code for creating EFA data subset
+### EFA data
+EFA.data <- sem.data[1:428, ]
+#library(VIM)
+missing <- VIM::aggr(EFA.data, plot =T)
+CFA.data <- sem.data[429:690,]
+```
 
@@
 
-## Development of the Initial Scale
-
-An expert panel comprising all authors -- researchers from chronobiology, light research, neuroscience and psychology -- developed a comprehensive item pool of 48 items.
-The 48 items were examined independently based on their relevance and representativeness of the construct "Light Exposure Related Behaviour" by each panel member, and modifications were suggested as required.
-The author team discussed the suggestions and amended the items as indicated, thus creating a 48-item scale.
-
-## Anonymous Online Survey
-
-Table 1 summarises the survey participants' demographic characteristics.
-Only participants completing the full LEBA questionnaire were included.
-Thus, there are no missing values in the item analyses.
-(XXX??) participants were excluded from the analysis due to not passing at least one of the "attention check" items.
-For the EFA, a sample of at least 250-300 is recommended [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013].
-To assess sampling adequacy for CFA, we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where at least ten participants per item are required to earn trustworthiness of the result.
-Both our EFA and CFA sample size exceeded these requirements.
-Participants indicated filling out the online survey from various geographic locations, including `r nrow(num.countries)` countries and `r nrow(numUTC)` time zones.
+Our results focus on the development of the LEBA inventory and its psychometric validation using a large scale online sample data (n = `r nrow(data)`).
+
+## Development of the initial item pool
+To capture the human light exposure related behaviours, 48 items were developed by an expert panel (all authors -- researchers from chronobiology, light research, neuroscience and psychology in different geographical contexts).
+Face validity examination by each panel member indicated all items were relevant and a few modifications were suggested.
+The author team discussed the suggestions and amended the items as indicated, thus creating a 48-item inventory.
+
+## Measurement of light exposure behaviour in an online sample
+
+We conducted two rounds of large scale online survey between 17 May 2021 and 3 September 2021 to generate data from `r nrow(data)` participants with varied geographic locations (countries = `r nrow(num.countries)`; time-zone = `r nrow(numUTC)`).
 For a complete list of geographic locations, see **Supplementary Table 2**.
-
+Table 1 presents the survey participants' demographic characteristics.
+Only participants completing the full LEBA inventory were included.
+We used the data from first round for the exploratory factor analysis (EFA sample; n = `r nrow(EFA.data)`) and data from the second round was used in the confirmatory factor analysis (CFA sample; n = `r nrow(CFA.data)`).
 Participants in our survey were aged between `r min(desctable.data$slypos_demographics_age)` to `r max(desctable.data$slypos_demographics_age)` years, with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 2)` years of age [Overall: `r mean(desctable.data$slypos_demographics_age)`±`r sd(desctable.data$slypos_demographics_age)`; EFA: `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
@@
 CFA Sample"])`].
-In total, `r desc_tibble[3,2]` of the participants indicated female sex, `r desc_tibble[4,2]` indicated male, and `r desc_tibble[5,2]` indicated other sex.
-Overall, `r desc_tibble[6,2]` participants reported a gender-variant identity.
+In the entire sample, `r desc_tibble[4,2]` were male, `r desc_tibble[3,2]` were female, `r desc_tibble[5,2]` reported other sex, and `r desc_tibble[6,2]` reported a gender-variant identity.
 In a "Yes/No" question regarding native language, `r desc_tibble[7,2]` of respondents [EFA: `r desc_tibble[7,3]`; CFA: `r desc_tibble[7,4]`] indicated to be native English speakers.
-For their "Occupational Status", more than half of the overall sample reported that they currently work, whereas `r desc_tibble[10,2]` reported that they go to school, and `r desc_tibble[11,2]` responded that they do "Neither".
-With respect to the COVID-19 pandemic, we asked participants to indicate their occupational setting during the last four weeks: In the overall sample `r desc_tibble[13,2]` of the participants indicated that they were in a home office/ home schooling setting, while `r desc_tibble[14,2]` reported face-to-face work/schooling.
-Lastly, `r desc_tibble[15,2]` overall reported a combination of home- and face-to-face work/schooling, whereas `r desc_tibble[16,2]`  filled in the "Neither (no work or school, or on vacation)" response option.
-
-## Psychometric Analysis: Development of the Long Form
-
-### Descriptive Statistics and Item Analysis
+For their "Occupational Status", more than half of the overall sample (`r desc_tibble[9,2]`) reported that they currently work, whereas `r desc_tibble[10,2]` reported that they go to school, and `r desc_tibble[11,2]` responded that they do "Neither".
+With respect to the COVID-19 pandemic, we asked participants to indicate their occupational setting during the last four weeks: In the entire sample, `r desc_tibble[13,2]` of the participants indicated that they were in a home office/ home schooling setting, `r desc_tibble[14,2]` reported face-to-face work/schooling, `r desc_tibble[15,2]`  reported a combination of home- and face-to-face work/schooling, and `r desc_tibble[16,2]`  filled in the "Neither (no work or school, or on vacation)" response option.
+
+## Psychometric analysis: Development of the long form
+
+### Descriptive statistics and item analysis
 
@@
 
-Figure \@ref(fig:efagtPic1) and Figure \@ref(fig:efagtPic2) summarise the response patterns of our total sample (n=`r nrow(sem.data)`) for all 48 items.
-Most of the items appeared skewed.
-The Shapiro–Wilk test of univariate normality [@shapiroAnalysisVarianceTest1965] and Mardia test of multivariate normality [@mardiaMeasuresMultivariateSkewness1970] indicated that our data violated both univariate and multivariate normality.
-The multivariate skew was `r printnum(mardia.all.data$b1p)` (p \<0.001), and the multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p \<0.001).
-
-```{r EFAdata, include=FALSE}
-#This chunk holds code for creating EFA data subset
-### EFA data
-EFA.data <- sem.data[1:428, ]
-#library(VIM)
-missing <- VIM::aggr(EFA.data, plot =T)
-
-```
+We observed that the response patterns of LEBA inventory for the entire sample (n = `r nrow(sem.data)`) were not normally distributed (Figures \@ref(fig:efagtPic1) and \@ref(fig:efagtPic2)).
+All items violated both univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality [@mardiaMeasuresMultivariateSkewness1970].
+The multivariate skewness was`r printnum(mardia.all.data$b1p)` (p<0.001) and the multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p<0.001).
 
@@
 
-**Supplementary Figure 1** summarises the univariate descriptive statistics for the 48 items in the EFA sample (n=`r nrow(EFA.data)`).
-Likewise, our data violated the univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality assumptions [@mardiaMeasuresMultivariateSkewness1970].
-The multivariate skew was `r printnum(mardia$b1p)` (p \<0.001) and the multivariate kurtosis yielded a value of `r printnum(mardia$b2p)` (p \<0.001).
-The corrected item-total correlation ranged between `r apa(low.r.corec,2,F)` and `r apa(high.r.corec,2,F)`.
-However, no item was discarded based on descriptive statistics or item analysis.
-
-### Exploratory Factor Analysis and Reliability Analysis
+Similar non-normal distribution of response pattern was also observed in the EFA sample.
+**Supplementary Figure 1** depicts the univariate descriptive statistics for the EFA sample (n = `r nrow(EFA.data)`).
+Further, We observed that each item's correlation with the aggregated sum of the 48-item's score varied largely (corrected item-total correlation= `r apa(low.r.corec,2,T)` -`r apa(high.r.corec,2,T)`) indicating the possibility of multi-factor structure  of the LEBA inventory.
+
+### Exploratory factor analysis and reliability analysis
 
@@
 ```
-
-We checked the sampling adequacy by applying Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy on the EFA sample (n=`r nrow(EFA.data)`) [@kaiserIndexFactorialSimplicity1974].
-The overall KMO value for 48 items was `r printnum(KMO$MSA)`, which exceeded the cut-off value (.50), indicating an adequate sample size [@hutchesonMultivariateSocialScientist1999].
-Additionally, Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954], $\chi^2$ (`r bartlet$df`)=`r apa(bartlet$chisq, 2, T)`, p \< .001 implied that the correlations between items were adequate for conducting the EFA.
-However, only `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than \|.30\|., and the inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`.
-Figure \@ref(fig:efa-plot-print)-A depicts the respective correlation matrix.
 
@@
          axis.text.y = element_text(size = 35),
-          legend.text=element_text(size =30),
-         legend.title = element_blank(),
+         legend.text=element_text(size =35),
+         legend.title = element_text(size =35),
+          plot.title = element_text(size = 35),
          panel.border = element_rect(color = "black",
                                     fill = NA,
-                                    size = 1))
-        # legend.position = 'right', 
-        # legend.spacing.x = unit(0.5, 'cm'),
-        # legend.text = element_text(margin = margin(t = 10)))
-#to show pvalue in the fig add p.mat=p.mat
-# ggsave("Figures/corplot.png",corplot, width = 12, height = 8.5, dpi = 600, bg ="white")
+                                    size = 1))+labs(title = "(A)")
 
@@
 ```
-
-Inspection via the Scree plot ( Figure \@ref(fig:efa-plot-print)-B) suggested a six-factor solution, whereas the minimum average partial (MAP) method [@velicerDeterminingNumberComponents1976] (**Supplementary Table 3**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] ( Figure \@ref(fig:efa-plot-print)-C) implied a five-factor solution for the LEBA questionnaire.
-As a result, we tested both five-factor and six-factor solutions.
 
@@
 
-residual.plot <- ggplot(residual.data, aes(x=Residuals)) + geom_histogram(binwidth=.04, col=I("black"),fill="#00A08799") + xlim(-.2,.2)+ ylim(0,250)+apatheme +geom_vline(xintercept = .05)+
-  labs( y="Frequency")
-
-```
-
-```{r efa-plot, include=F}
+residual.plot <- ggplot(residual.data, aes(x=Residuals)) + geom_histogram(binwidth=.04, col=I("black"),fill="#00A08799") + xlim(-.2,.2)+ ylim(0,250)+apatheme_2 +geom_vline(xintercept = .05)+
+  labs( y="Frequency",title = "(D)")
+
+# ggsave("Figures/residual.plot.png",residual.plot, width = 4, height =4, dpi = 600,bg = "white")
+
+```
+
+```{r efa-plot, include=FALSE}
+
 #This chunk holds code for compiled factor identification plots
 
-cor.scree <- cowplot::plot_grid(corplot, scree.plot,
-                                labels = c("A", "B"),
-                                nrow =1, ncol =2,
-                                rel_widths = c(2, 1),
-                                label_fontfamily = "Arial",
-                  label_fontface = "plain")
-
-hull.residual <- cowplot::plot_grid(Hull, residual.plot,
-                                labels = c("C", "D"),
-                                nrow =1, ncol =2,
-                                                                label_fontfamily = "Arial",
-                  label_fontface = "plain")
-
-efa.plot <- cowplot::plot_grid(cor.scree, hull.residual,
-
-                                nrow =2)
-
-# efa.plot <- cowplot::plot_grid(corplot , scree.plot,Hull, residual.plot,
-#                    labels = "AUTO",
-#                    ncol=2,nrow=2, 
-#                   align = "v", 
-#                   label_fontfamily = "Arial",
-#                   label_fontface = "plain")
-ggsave("Figures/Figure4.png",efa.plot, width = 7, height = 8, dpi = 600, bg = "white")
-```
+library(patchwork)
+
+# all_plot <-corplot|(Hull|scree.plot)/residual.plot
+# ggsave("Figures/all_plot.png",all_plot, width = 16, height = 8, dpi = 600, bg = "white")
+
+all_plot_2 <-corplot|(scree.plot|Hull)/residual.plot
+# all_plot_3 <-corplot|(scree.plot|Hull)/(residual.plot|plot_spacer())
+
+ggsave("Figures/Figure4.png",all_plot_2, width = 8, height = 4, dpi = 600, bg = "white", units = "in")
+
+```
+
+Exploratory analysis revealed that items of LEBA inventory can be categorized into five major factors: (i) wearing blue light filters; (ii) spending time out doors; (iii) using phone and smartwatch in bed; (iv) using light before bedtime (v) using light in the morning and during daytime.
+In this stage of analysis, we retained 25 items.
+the first factor had three items and encapsulated the individual's preference for using blue light filters in different light environments.
+The second factor contained six items that incorporated the individuals' hours spent outdoors.
+The third factor contained five items that looked into specific behaviours of using a phone and smartwatch in bed.
+The fourth factor comprised five items investigated the other behaviours related to the individual's electric light exposure before bedtime.
+lastly, the fifth factor encompassed six items capturing the individual's morning and daytime light exposure-related behaviour.
+
+Prior to conducting the EFA, we have checked the post-hoc sampling adequacy by applying Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy on the EFA sample (n = `r nrow(EFA.data)`) [@kaiserIndexFactorialSimplicity1974] and the quality of the correlation matrix by Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954].
+KMO>0.50 would indicate adequate sample size [@hutchesonMultivariateSocialScientist1999] and a significant test of sphericity would indicate satisfactory quality of the correlation matrix .
+Results indicated that we had an adequate sample size (KMO = `r printnum(KMO$MSA)`) and correlation matrix ($\chi^2_{1128}$ = `r apa(bartlet$chisq, 2, T)`, p< 0.001).
+However, `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than |0.30|, and the inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`.
+Figure \@ref(fig:efa-plot-print)-A depicts the respective correlation matrix.
+To identify how many factors are required to optimally express human light exposure related behaviors we used a combination of methods.
+the Scree plot ( Figure \@ref(fig:efa-plot-print)-B) revealed a six-factor solution, whereas the minimum average partial (MAP) method [@velicerDeterminingNumberComponents1976] (**Supplementary Table 3**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] implied a five-factor solution (Figure \@ref(fig:efa-plot-print)-C).
+Hence, we tested both five-factor and six-factor solutions using iterative EFA where we gradually identified and discarded problematic items (factor-loading <0.30 and cross-loading >0.30).
+In this process, we found a five-factor structure for LEBA inventory with 25 items.
+Table \@ref(tab:EFATable) displays the factor-loading ($\lambda$) and communality of the items.
+Both factor loadings and commonalities advocate to accept this five-factor solution ( |$\lambda$| = `r apa(min.loadings,2,T)`-`r apa(max.loadings, 2, T)`; commonalities = `r apa(min.com,2,T)`-`r apa(max.com, 2, T)`).
+These five factors explains `r apa(var1,2,T)`%, `r apa(var2,2,T)`%, `r apa(var3,2,T)`%, `r apa(var4,2,T)`%, `r apa(var5,2,T)`% of the total variance in individual's light exposure related behaviours respectively.
+All factors exhibited excellent to satisfactory reliability (ordinal $\alpha$ = `r apa(F1.alpha,2,T)`, `r apa(F2.alpha,2,T)`, `r apa(F3.alpha,2,T)`, `r apa(F4.alpha,2,T)`, `r apa(F5.alpha,2,T)` respectively).
+The entire inventory also exhibited satisfactory reliability ($\omega_t$=`r apa(omega$omega.tot,2,T)`).
+
+However, the histogram of the absolute values of nonredundant residual correlations (Figure \@ref(fig:efa-plot-print)-D) displayed that `r sumR`% of correlations were greater >|.05|, indicating a possible under-factoring.
+[@desjardinsHandbookEducationalMeasurement2018].
+Subsequently, we fitted a six-factor solution, where a factor with only two salient variables emerged, thus disqualifying the six-factor solution (**Supplementary Table 4**).
+While making the judgement of accepting this five-factor solution we considered both factor's interpretability and their psychometric properties.
+We deemed the five derived factors as highly interpretable  and relevant concerning our aim to capture light exposure-related behaviour, we retained all of them with 25 items.
+Two of the items showed negative factor-loading (item 08: `r Hmisc::label(data$slypos_leba_08)` and item 37: `r Hmisc::label(data$slypos_leba_37)`).
+Upon re-inspection, we recognized these items to be negatively correlated to the respective factor, and thus, we reverse-scored these two items.
 
 (ref:efa-plot-print) (A) Inter-item polychoric correlation coefficients for the 48 items.
-4.9 % inter-item correlation coefficients were higher than \|.30\|.
-'x' denotes a non-significant item-total correlation.
+4.9 % inter-item correlation coefficients were higher than |.30|.
+'x' denotes non-significant correlation.
 (B) The Scree plot suggested six factors.
 (C) Hull method indicated that five factors were required to balance the model fit and number of parameters.
-(D) The histogram of nonredundant residual correlations indicated that 26% of inter-item correlations were higher than .05, hinting at a possible under-factoring.
-
-```{r efa-plot-print, fig.align= 'center', fig.cap='(ref:efa-plot-print)',  warning=FALSE,  out.height='60%', out.width='110%'}
+(D) The histogram of nonredundant residual correlations in the five-factor model indicated that 26% of inter-item correlations were higher than .05, hinting at a possible under-factoring.
+
+```{r efa-plot-print, fig.align= 'center', fig.cap='(ref:efa-plot-print)',  warning=FALSE,  out.height='130%', out.width='100%'}
 
@@
 ```
-
-Applying varimax rotation, we conducted three rounds of EFA with the initial 48 items and gradually discarded problematic items (cross-loading items and items with factor loading \<.30).
-Finally, a five-factor EFA solution with 25 items was accepted with all factor-loading higher than .30 and no cross-loading greater than .30.
-Table \@ref(tab:EFATable) displays the factor-loading (structural coefficients) and communality of the items.
-The absolute values of the factor-loadings ranged from `r apa(min.loadings,2,F)` to `r apa(max.loadings, 2, F)` indicating strong coefficients.
-The commonalities ranged between `r apa(min.com,2,F)` and `r apa(max.com, 2, F)`.
-However, the histogram of the absolute values of nonredundant residual correlations (Figure \@ref(fig:efa-plot-print)-D) displayed that `r apa(sumR,0, T)`% of correlations were greater than the absolute value of .05, indicating a possible under-factoring.
-[@desjardinsHandbookEducationalMeasurement2018].
-Subsequently, we fitted a six-factor solution, wherefrom a factor with only two salient variables emerged, thus disqualifying the six-factor solution (**Supplementary Table 4**).
-
-In the five-factor solution, the first factor contained three items and explained `r apa(var1,2,F)`% of the total variance with an internal reliability coefficient ordinal $\alpha$ = `r apa(F1.alpha,2,F)`.
-All the items in this factor encapsulated the individual's preference for using blue light filters in different light environments.
-The second factor contained six items and explained `r apa(var2,2,F)`% of the total variance with an internal reliability coefficient ordinal $\alpha$ = `r apa(F2.alpha,2,F)`.
-Items under this factor incorporated the individuals' hours spent outdoor.
-The third factor contained five items and explained `r apa(var3,2,F)`% of the total variance.
-Items under this factor covered the specific behaviours of using a phone and smartwatch in bed.
-The internal consistency reliability coefficient was ordinal $\alpha$ = `r apa(F3.alpha,2,F)`.
-The fourth factor comprised five items and explained `r apa(var4,2,F)`% of the total variance with an internal consistency coefficient, ordinal $\alpha$ = `r apa(F4.alpha,2,F)`.
-These five items investigated the behaviours related to the individual's light exposure before bedtime.
-The fifth factor encompassed six items and explained `r apa(var5,2,F)`% of the total variance.
-This factor captured the individual's morning and daytime light exposure-related behaviour.
-The internal consistency reliability yielded ordinal $\alpha$ = `r apa(F5.alpha,2,F)`.
-
-Lastly, we examined the factor's interpretability in the five-factor solution and weighed it against the psychometric properties as we considered it essential to attain a balance between the two.
-As we deemed the five derived factors interpretable and relevant concerning our aim to capture light exposure-related behaviour, we retained all of them with 25 items for our confirmatory factor analysis (CFA), despite the apparent lower reliability of the fifth factor.
-Two of the items showed negative factor-loading (items 44 and 21).
-Upon re-inspection, we recognized these items to be negatively correlated to the respective factor, and thus, we reverse-scored these two items in the CFA analysis.
-The internal consistency coefficient McDonald's $\omega_t$ for the total scale was `r apa(omega$omega.tot,2,T)`.
 
@@
 
-### Confirmatory Factor Analysis
+### Confirmatory factor analysis
 
@@
 
-Table \@ref(tab:tabCfa) compares the CFA fit indices of the original CFA five-factor model with 25 and the post-hoc modified model with 23 items, respectively.
-The 25-item model attained an acceptable fit (CFI =`r apa(fit.1[5],2,F)`; TLI = `r apa(fit.1[6],2,F)`; RMSEA = `r apa(fit.1[7],2,F)` [`r apa(fit.1[8],2,F)`-`r apa(fit.1[9],2,F)`, 90% CI]) with two imposed equity constraints on item pairs 32-33 [item 32: I dim my mobile phone screen within 1 hour before attempting to fall asleep; item 33: I dim my computer screen within 1 hour before attempting to fall asleep] and 16-17 [item 16: I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day; item 17: I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day].
-Item pair 32-33 describes the preference for dimming the electric devices' brightness before bedtime, whereas item pair 16-17 represents the preference for using blue filtering or coloured glasses during the daytime.
+To investigate the structural validity of the five-factor structure obtained in EFA, we conducted a confirmatory factor analysis (CFA) on the CFA sample.
+The five-factor structure with 25 items showed acceptable fit (Table \@ref(tab:tabCfa)) providing evidence of structural validity (CFI = `r apa(fit.1[5],2,T)`; TLI = `r apa(fit.1[6],2,T)`; RMSEA = `r apa(fit.1[7],2,T)` [`r apa(fit.1[8],2,T)`-`r apa(fit.1[9],2,T)`, 90% CI]).
+Two equity constraints were imposed on item pairs 32-33 (item 32: I dim my mobile phone screen within 1 hour before attempting to fall asleep; item 33: I dim my computer screen within 1 hour before attempting to fall asleep) and 16-17 (item 16: I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day; item 17: I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day).
+Item pair 32-33 describes the preference for dimming the electric devices' brightness before bedtime, whereas item pair 16-17 represents the use of blue filtering or coloured glasses during the daytime.
 Given the similar nature of captured behaviours within each item pair, we accepted the imposed equity constraints.
-Nevertheless, the SRMR value exceeded the guideline recommendation (SRMR = `r apa(fit.1[10],2,F)`).
-
+Nevertheless, the SRMR value exceeded the guideline recommendation (SRMR = `r apa(fit.1[10],2,T)`).
 In order to improve the model fit, we conducted a post-hoc model modification.
-Firstly, the  modification indices suggested cross-loadings between item 37 and 26 [item 37: I purposely leave a light on in my sleep environment while sleeping; item 26: I turn on my ceiling room light when it is light outside], which were hence discarded.
-Secondly, items 30 and 41 [item 30: I look at my smartwatch within 1 hour before attempting to fall asleep; item 41: I look at my smartwatch when I wake up at night] showed a tendency to co-vary in their error variance (MI = 141.127, p<.001 ).
-By allowing the latter pair of items (30 $\&$ 41) to co-vary, the model's error variance attained an improved fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR = `r apa(fit.2[10],2,F) `).
-Internal consistency ordinal $\alpha$ for the five factors of the LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`, respectively.
-
-Accordingly, we accept the five-factor model with 23 items, finalizing the long Form of LEBA (see **Supplementary File 1**).
-The Internal consistency McDonald's $\omega_t$ coefficient for the total scale yielded `r apa(rel.k[5,6],2,F)`.
+Firstly, the  modification indices suggested cross-loadings between item 37 and 26 (item 37: I purposely leave a light on in my sleep environment while sleeping; item 26: I turn on my ceiling room light when it is light outside), which were hence discarded.
+Secondly, items 30 and 41 (item 30: I look at my smartwatch within 1 hour before attempting to fall asleep; item 41: I look at my smartwatch when I wake up at night) showed a tendency to co-vary in their error variance (MI = 141.127, p<0.001 ).
+By allowing the latter pair of items (30 $\&$ 41) to co-vary, the model's error variance attained an improved fit (CFI = `r apa(fit.2[5],2,T)`; TLI = `r apa(fit.2[6],2,T)`); RMSEA = `r apa(fit.2[7],2,T)` [`r apa(fit.2[8],2,T)`-`r apa(fit.2[9],2,T)`, 90% CI]; SRMR = `r apa(fit.2[10],2,T) `).
+
+Accordingly, we accept the five-factor model with 23 items, finalizing the long Form of LEBA inventory (see **Supplementary File 1**).
+Internal consistency ordinal $\alpha$ for the five factors of the LEBA were `r apa(rel.k[2,1],2,T)`, `r apa(rel.k[2,2],2,T)`, `r apa(rel.k[2,3],2,T)`, `r apa(rel.k[2,4],2,T)`, `r apa(rel.k[2,5],2,T)`, respectively.
+The reliability of the total inventory was satisfactory ($\omega_t$ = `r apa(rel.k[5,6],2,T)`).
 Figure \@ref(fig:figcfa) depicts the obtained CFA structure, while  **Supplementary Figure 2** depicts the data distribution and endorsement pattern of the retained 23 items in our CFA sample.
@@
 colnames(CFa.matrix) = c("Model", "$\\chi^{2}$", "df", "CFI", "TLI", "RMSEA", "RMSEA 90\\% Lower CI", "RMSEA 90\\% Upper CI", "SRMR")
-CFa.matrix[1,] = c("Model 1", 
-                   apa(as.numeric(cfa.sum.1$FIT[6]),2,T), 
-                   apa(as.numeric(cfa.sum.1$FIT[7]),2,T), 
-                   apa(as.numeric(cfa.sum.1$FIT[19]),2,F), 
-                   apa(as.numeric(cfa.sum.1$FIT[20]),2,T),
-                   apa(as.numeric(cfa.sum.1$FIT[27]),2,T),
-                   apa(as.numeric(cfa.sum.1$FIT[28]),2,T),
-                   apa(as.numeric(cfa.sum.1$FIT[29]),2,T),
-                   apa(as.numeric(cfa.sum.1$FIT[35]),2,T))
-
-CFa.matrix[2,] = c("Model 2", 
-                   apa(as.numeric(cfa.sum.2$FIT[6]),2,T), 
-                   apa(as.numeric(cfa.sum.2$FIT[7]),2,T), 
-                   apa(as.numeric(cfa.sum.2$FIT[19]),2,F), 
-                   apa(as.numeric(cfa.sum.2$FIT[20]),2,T),
-                   apa(as.numeric(cfa.sum.2$FIT[27]),2,T),
-                   apa(as.numeric(cfa.sum.2$FIT[28]),2,T),
-                   apa(as.numeric(cfa.sum.2$FIT[29]),2,T),
-                   apa(as.numeric(cfa.sum.2$FIT[35]),2,T))
-```
-
-```{r tabCfa, results='asis'}
-apa_table(CFa.matrix, caption = "Confirmatory Factor Analysis model fit indices of the two model: (a) Model 1: five factor model with 25 items (b) Model 2:  five factor model with 23 items.
+
+Cfa.matrix <- tabledown::cfa.tab.multi(fit.Cor.1,fit.Cor.2)
+Cfa.matrix.selected <- as.data.frame(Cfa.matrix[, c(1,2,6,7,8,9,10,11)])
+Cfa.matrix.selected <- tibble::rowid_to_column(Cfa.matrix.selected,"Model")
+colnames(Cfa.matrix.selected) = c("Model", "$\\chi^{2}$", "df", "CFI", "TLI", "RMSEA", "RMSEA 90\\% Lower CI", "RMSEA 90\\% Upper CI", "SRMR")
+
+Cfa.matrix.selected$CFI[1] <- round(fit.1[5],2)
+Cfa.matrix.selected$TLI[1] <- round(fit.1[6],2)
+Cfa.matrix.selected$RMSEA[1] <- round(fit.1[7],2)
+Cfa.matrix.selected[1,7] <- round(fit.1[8],2)
+Cfa.matrix.selected[1,8] <- round(fit.1[9],2)
+
+Cfa.matrix.selected$CFI[2] <- round(fit.2[5],2)
+Cfa.matrix.selected$TLI[2] <- round(fit.2[6],2)
+Cfa.matrix.selected$RMSEA[2] <- round(fit.1[7],2)
+Cfa.matrix.selected[2,7] <- round(fit.2[8],2)
+Cfa.matrix.selected[2,8] <- round(fit.2[9],2)
+
+```
+
+```{r tabCfa}
+apa_table(Cfa.matrix.selected, caption = "Confirmatory Factor Analysis model fit indices of the two model: (a) Model 1: five factor model with 25 items (b) Model 2:  five factor model with 23 items.
 Model 2 attained the best fit.", align = "c", landscape = T, escape=F, note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square.")
@@
 
-### Measurement Invariance
+### Measurement invariance
 
@@
 
-Our CFA sample consisted of `r mi.count[1,2]` native English speakers and `r mi.count[2,2]` non-native English speakers, whose demographic data are contrasted in **Supplementary Table 5**.
-As shown in Table \@ref(tab:InvarianceTab), the employed five-factor model generated acceptable fit indices over all of the fitted MI models.
-The model fit did not significantly decrease across the nested models, implying the acceptability of the highest measurement invariance model (residual model).
+We reported the measurement invariance (MI) analysis on the CFA sample based on native (n = `r mi.count[1,2]`) and non-native English speakers (n = `r mi.count[2,2]`).
+A detailed demographic description are provided in **Supplementary Table 5**.
+Our MI results (Table \@ref(tab:InvarianceTab)) indicated that LEBA inventory demonstrated highest level of (residual model) psychometric equivalence across native and non-native English speaking participants, thus permitting group-mean based comparisons.
+The four fitted MI models generated acceptable fit indices and the model fit did not significantly decrease across the nested models ($\Delta$CFI>-0.01; $\Delta$RMSEA<0.01).
 
@@
 ```{r InvarianceTab, results='asis'}
-apa_table(Invariance.table, align = "c",  caption = "Measurement Invariance analysis on CFA sample (n=262) across native and non-native English speakers.", note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square; a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; d = Structural vs Residual; * =  df of model comparison.", landscape = T, font_size = "footnotesize", escape=F )
-
-```
-
-## Secondary Analysis: Grade Level Identification and Semantic Scale Network Analysis
-A grade level identification and Semantic Scale analysis were additionally administered to assess the LEBA's (23 items) language-based accessibility and its' semantic relation to other questionnaires.
-The results of the Flesch-Kincaid grade level analysis [@flesch1948new] displayed a required educational grade level of 3.33 with age above 8.33 years, implying that the LEBA instrument should be understandable for students of grade four at least 8.33 years old.
-Furthermore, the
-Semantic Scale Network (SSN) analysis [@rosenbusch2020semantic] indicated that the LEBA appeared most strongly related to scales about sleep: The "Sleep Disturbance Scale For Children" [@bruni1996sleep] and the "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite].
-The cosine similarity yielded values between .47 to .51.
+apa_table(Invariance.table, align = "c",  caption = "Measurement Invariance analysis on CFA sample (n = 262) across native and non-native English speakers.", note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square; a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; * =  df of model comparison.", landscape = T, font_size = "footnotesize", escape=F )
+
+```
+
+## Secondary analysis: Grade level identification and semantic scale network analysis
+
+We investigated the language-based accessibility of LEBA using Flesch-Kincaid grade level analysis [@flesch1948new].
+Results indicated that at least a language proficiency of educational grade level-four (US education system) with age above eight years  are required to comprehend the items used in LEBA inventory.
+Semantic Scale analysis [@rosenbusch2020semantic]  was administered to assess the LEBA's (23 items) semantic relation to other questionnaires.
+LEBA inventory was most strongly semantically related to scales about sleep: The "Sleep Disturbance Scale For Children" [@bruni1996sleep] and the "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite].
+The cosine similarity index ranged between 0.47 to 0.51.
 
@@
 
-## Developing a Short Form of LEBA: IRT-Based Analysis
-In order to derive a short form of the LEBA instrument, we fitted each factor of the LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n=690).
-The resulting item discrimination parameters of the scale fell into categories of "very high" (10 items), "high" (4 items), "moderate" (4 items), and "low" ( 5 items), indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**).
-An examination of the item information curve (**Supplementary Figure 3**) revealed five items (1, 25, 30, 38, & 41) with relatively flat curves (I($\theta$) \<.20).
+## Developing a short form of LEBA: IRT-based analysis
+
+In order to derive a short form of the LEBA inventory, we fitted each factor of the LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n=690).
+The resulting item discrimination parameters of the inventory fell into categories of "very high" (10 items), "high" (4 items), "moderate" (4 items), and "low" ( 5 items), indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**).
+An examination of the item information curve (**Supplementary Figure 3**) revealed five items (1, 25, 30, 38, & 41) provided very low information regarding light exposure related behaviors with relatively flat curves (I($\theta$) \<0.20).
 We discarded those items, culminating in a short form of LEBA with five factors and 18 items (**Supplementary File 2**).
@@
 
-Subsequently, we treated each factor of the short-LEBA as a unidimensional construct and obtained five test information curves (TICs).
-As (Figure \@ref(fig:Testinfo)).
-illustrates, the TICs of the first and fifth factors peaked on the right side of the centre of their latent traits, while the TICs of the other three factors were roughly centred on the respective trait continuum ($\theta$).
-This points out that the LEBA short-scale estimates the light exposure-related behaviour most precisely near the centre of the trait continuum for the second, third and fourth factors and, in contrast, to the right of the centre for the first and fifth factors [@bakerBasicsItemResponse2017].
+Subsequently, we obtained five test information curves (TICs).
+As Figure \@ref(fig:Testinfo) illustrates, the TICs of the first and fifth factors peaked on the right side of the centre of their latent traits, while the TICs of the other three factors were roughly centred on the respective trait continuum ($\theta$).
+This points out that the LEBA short-form estimates the light exposure-related behaviour most precisely near the centre of the trait continuum for the second, third and fourth factors.
+In contrast, for the first and fifth factors the TICs were left skewed indicating their increased sensitivity in identifying people who are engaging more in those particular light exposure related behavior dimensions [@bakerBasicsItemResponse2017].
 
 Finally, **Supplementary Table 7** summarises the item fit indexes of the LEBA short form.
-All 18 items yielded RMSEA value $\le$.06, indicating adequate fit to the fitted IRT model.
+All 18 items yielded RMSEA value $\le$ 0.06, indicating an adequate fit to the fitted IRT model.
 Furthermore, **Supplementary Figure 4** depicts the person fit Zh statistics histogram for the five IRT models.
@@
 # Discussion
-
-Nowadays, in many industrialized countries, most of the time is spent in enclosed buildings [@Klepeis.2001], where people's received light is determined not only by the natural light-dark cycle but by exposure to artificial light sources.
-Accordingly, people receive varying light intensities at different times, ultimately depending on their light-related behavioural habits.
-As established by extensive evidence, the timing, duration and intensity of light exposure, among other light properties, affect many aspects of human health, well-being, and performance [i.a.
-reviewed in @Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020].
-Thus, there is a clear need for guidance [see @Brown.2022] and assessment regarding healthy light exposure and consequentially healthy light-related behaviour.
+Today, in most industrialized countries, the vast majority of time is spent in built environments [@Klepeis.2001], where photic exposure patterns are determined not only by the solar cycle but by electrical light sources as well.
+As a consequence, light received may vary considerably, in terms of timing, intensity and spectrum, all of which are subject to the further influence of individual behaviours.
+[reviewed in @Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020; @vetter2022review].
+Thus, there is a clear need for guidance [@Brown.2022] and assessment regarding healthy light exposure and consequentially healthy light-related behaviour.
+
 In reviewing the literature, we found that a handful of previously introduced instruments assess aspects of light exposure by self-report (see **Supplementary Table 1**).
-Even fewer assessment tools have yet partially probed behavioural aspects of received light like the estimated time spent outside [MCTQ; @roenneberg2003life] or the preference for specific light situations (e.g.
-"I prefer rooms that are in semi-darkness."; PAQ @bossini2006sensibilita).
-However, none of these questionnaires systematically and thoroughly captures behaviours that modify light exposure across different lighting scenarios.
-With the present LEBA tool, we have developed two versions of a self-report scale that can capture light exposure-related behaviour in multiple dimensions.
-
-The 48 initially generated items were applied in a large-scale geographically unconstrained cross-sectional survey, yielding (n=`r nrow(data)`) complete datasets.
-Moreover, to assure high data quality, this included only data where the five “attention check items” throughout the survey were passed.
-As a result, data was recorded from `r nrow(num.countries)` countries and `r nrow(numUTC)` time zones, including native and non-native English speakers from a sex-balanced and age-diverse sample (see Table 1).
+Few studies to date have attempted to assess light exposure by self-report.
+That body of research becomes even smaller when limiting it to those focusing on <behaviours> that influence photic exposure patterns, and typically these home in only on particular behaviours of interest, such as estimates of time spent outside [@roenneberg2003life] or preferences for specific lighting situations [@bossini2006sensibilita].
+To our knowledge, there is no questionnaire in existence that captures behaviours that modify light exposure across different scenarios in a comprehensive way.
+We have developed two versions of a self-report inventory-LEBA, that can capture light exposure-related behaviours in multiple dimensions.
+
+The 48 generated items were applied in a large-scale, geographically unconstrained, cross-sectional study, yielding `r nrow(data)` completed surveys.
+To assure high data quality, participant responses were only included when the five “attention check items” throughout the survey were passed.
+Ultimately, data was recorded from `r nrow(num.countries)` countries and `r nrow(numUTC)` time zones, including native and non-native English speakers from a sex-balanced and age-diverse sample (see Table 1).
 The acquired study population complied with our objective to avoid bias from a selective sample, which is crucial when relying on voluntary uncompensated participation.
@@
 The exploratory factor analysis revealed a highly interpretable five-factor solution ("Wearing blue light filters", "Spending time outdoors", "Using phone and smartwatch in bed", "Using light before bedtime", and "Using light in the morning and during daytime") with 25 items.
-The total scale exhibited satisfactory internal consistency (McDonald's $\omega_t$=`r apa(omega$omega.tot,2,T)`).
-
-Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five-factor structure we obtained in our EFA, thus providing evidence for structural validity.(CFI=`r apa(fit.2[5],2,F)`; TLI=`r apa(fit.2[6],2,F)`; RMSEA=`r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR=`r apa(fit.2[10],2,F) `).
-In this model, we discarded two additional items (item 26 $\&$ 37 ) for possible cross-loadings.
-The internal consistency coefficients ordinal alpha for the five factors and the total scale were again satisfactory (Ordinal alpha ranged between `r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$=`r apa(rel.k[5,6],2,F)`).
+Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five-factor structure we obtained in our EFA, thus providing evidence for structural validity.(CFI = `r apa(fit.2[5],2,T)`; TLI = `r apa(fit.2[6],2,T)`; RMSEA = `r apa(fit.2[7],2,T)`).
+In this model, we discarded two more items (item 26 $\&$ 37 ) for possible cross-loadings.
+As a rule of thumb, reliability coefficients higher than .70 are regarded as “satisfactory”.
+However, at the early developmental stage, a value of .50 is considered acceptable [@dall2010developmental; @field2013discovering; @Nunnally1978].
+Thus, we confer, the internal consistency coefficients ordinal alpha for the five factors and the total inventory were satisfactory (Ordinal alpha ranged between `r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$ = `r apa(rel.k[5,6],2,T)`).
 
@@
 
-Lastly, we derived a short version of the LEBA (18 items) using IRT analysis.
-We fitted a graded response model to the combined EFA and CFA sample (n=`r nrow(data)`) and discarded five items (1, 25, 30, 38, & 41) with relatively flat item information curve [I($\theta$) <.20].
-The resulting test information curves suggest that the short-LEBA is a psychometrically sound measure with adequate coverage of underlying traits and can be applied to capture different extents of light exposure-related behaviours reliably.
+Often psychological measurements require application of several questionnaires simultaneously.
+Responding to several lengthy questionnaires increases the participants losing focus and becoming tried.
+To avoid these situations we  derived a short version of the LEBA (18 items) using IRT analysis.
+We fitted a graded response model to the combined EFA and CFA sample (n = `r nrow(data)`) and discarded five items (1, 25, 30, 38, & 41) with relatively flat item information curve [I($\theta$) <.20].
+The resulting test information curves suggest that the short-LEBA is a psychometrically sound measure with adequate coverage of underlying traits and can be applied to capture the frequency of different light exposure related behaviours reliably.
 
@@
 
-- In the five factor-solution derived from the Exploratory factor analysis, the internal consistency reliability coefficient ordinal alpha ranged between `r apa(min(alpha.tab),2,F)`-`r apa(max(alpha.tab),2,F)`, though only the fifth factor (“Using light in the morning and during daytime”) yielded internal consistencyreliability coefficients below .70 ($\alpha$=`r apa((alpha.tab[5,1]),2,F)`).
-As a rule of thumb, reliability coefficients higher than .70 are regarded as “satisfactory”.
-However, for scales with less than 20 items and at the early developmental stage, a value of .50 is considered acceptable [@dall2010developmental; @field2013discovering; @Nunnally1978].
-Furthermore, the full LEBA scale exhibited satisfactory internal consistency (McDonald’s $\omega_t$=0.77), while all factors were highly interpretable regarding a common behavioural theme.
-Thus, we decided to proceed with the five-factor solution.
-- During the post-hoc model modification, as part of the confirmatory factor analysis, we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings, as demonstrated in the data.
+The fifth factor, "using light in the morning and during daytime", exhibited low internal consistency both in the exploratory and confirmatory factor analysis (EFA: `r apa(F5.alpha,2,T)`; CFA:`r apa(rel.k[2,5],2,T)` ).
+Since, it was above .50, considering the developmental phase of this inventory we accepted the fifth factor.
+This particular factor captures our behaviour related to usages of light in the morning and daytime.
+Since, light exposure during morning and daytime influences our alertness and cognition [@lok2018light; @siraji2021effects], we deemed capturing these behaviours is essential for the sake of completeness of our inventory.
+However, the possibility of improving the reliability should be investigated further by adding more appropriate and relevant items to this factor.
+
+During the post-hoc model modification, as part of the confirmatory factor analysis, we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings, as demonstrated in the data.
 However, two additional items covaried in their error variance.
-By allowing the latter pair (30 $\&$ 41) to covary, the model attained an improved fit (cf.
-**Figure 5**).
+By allowing the latter pair (30 $\&$ 41) to covary, the model attained an improved fit ( **Figure 5**).
 A possible explanation for the covariation is that many respondents might not have used a smartwatch at all, resulting in similar response patterns between these two items.
 Thus, though rather unconventional, we decided to accept this post-hoc modification to our five-factor model.
-- The habitual patterns queried in the developed scales might not exhaustively represent all relevant light-exposure-related behaviours.
+
+The habitual patterns queried in the developed inventory might not exhaustively represent all relevant light-exposure-related behaviours.
 For instance, it is conceivable that additional light-related activities not included in the LEBA depend on the respondents' profession/occupation, geographical context, and socio-economic status.
 However, we generated the initial item pool with an international team of researchers and followed a thorough psychometric analysis.
-Therefore, we are confident that the developed LEBA scales can serve as a good starting point for exploring the behavioural aspects of light exposure in more depth.
-- As with all studies relying on retrospective self-report data, individuals filling in the LEBA may have difficulties precisely recalling the inquired light-related behaviours.
+Therefore, we are confident that the developed LEBA inventory can serve as a good starting point for exploring the light exposure related behaviours in more depth and inform room for modification of light exposure-related behaviour to improve light hygiene.
+
+As with all studies relying on retrospective self-report data, individuals filling in the LEBA may have difficulties precisely recalling the inquired light-related behaviours.
 In the interest of bypassing a substantial memory component, we limited the recall period to four weeks and chose response options that do not require exact memory recall.
 In contrast to directly assessing light properties via self-report, we assume that reporting behaviours might be more manageable for inexperienced laypeople, as the latter does not rely on existing knowledge about light sources.
-The accessibility of the LEBA is also reflected in the “grade level identification” findings suggesting a minimum age of 8.33 years and an educational grade of four or higher.
+The comprehensibility of the LEBA is also reflected by the Flesch-Kincaid grade level identification method [@flesch1948new] that suggested a minimum age of 8.33 years and an educational grade of four or higher (US grading system).
 We argue that measuring light-related behaviours via self-report is crucial because these behaviours will hardly be as observable by anyone else or measurable with other methods (like behavioural observations) with reasonable effort.
 
-## Future Directions
-
-To our knowledge, the LEBA is the first questionnaire characterising light exposure-related behaviour in a scalable manner.
+## Future directions
+
+To our knowledge, the LEBA is the first inventory characterising light exposure-related behaviour in a scalable manner.
 Thus, estimating convergent validity with similar subjective scales was impossible.
@@
 By this route, one could study how the (subjectively measured) light exposure-related behavioural patterns translate into (objectively measured) received light exposure.
+
 Additionally, developing daily recall scales of light-related behaviour could provide a more detailed behavioural assessment to supplement the LEBA's broader (four-week) measurement approach.
 Comparing the LEBA scores to 24-hour recall scores could provide helpful information about how light exposure-related behaviour assessment is related between different time perspectives.
+
 Moreover, light-exposure-related behaviour might depend on the respondents' profession, geographical location, housing conditions, socio-economic status, or other contextual factors.
 As the current data is limited to our international online survey context, future research should apply the LEBA across more variable populations and contexts.
-On the other hand, this will require the development of cross-cultural adaptations and translations into other languages of the LEBA scale, which should be targeted in prospective studies.
-Finally, in the future, applying the LEBA scales should not just be limited to gathering information in cross-sectional quantitative studies but allow for individual behaviour profiling.
+On the other hand, this will require the development of cross-cultural adaptations and translations into other languages of the LEBA, which should be targeted in prospective studies.
+
+Finally, in the future, the use of the LEBA instrument need not remain restricted to gathering information in cross-sectinal quantitative studies.
+The instrument can also be used for individual behavioural profiling.
 For instance, the LEBA could be applied in a clinical context as part of Cognitive Behavioural Therapy for Insomnia (CBT-I).
@@
 
-With the "Light exposure behaviour assessment"(LEBA), we developed a novel, internally consistent and structurally valid 23-item self-report scale for capturing light exposure-related behaviour in five scalable factors.
+Here, we developed a novel, internally consistent and structurally valid 23-item self-report inventory for capturing light exposure-related behaviour in five scalable factors.
 In addition, an 18-item short-form of the LEBA was derived using IRT analysis, yielding adequate coverage across the underlying trait continuum.
-Applying the LEBA scales can provide insights into light exposure-related habits on a population-based level.
-Furthermore, it can serve as a good starting point to profile individuals based on their light exposure-related behaviour determining their light consumption and timing.
+Applying the LEBA inventory can provide insights into light exposure-related habits on a population-based level.
+Furthermore, it can serve as a good starting point to profile individuals based on their light  exposure-related behaviour and to asseses their light consumption and timing.
+
+# Methods
+
+## Data collection
+
+A quantitative cross-sectional, fully anonymous, geographically unconstrained online survey was conducted via REDCap [@harris2009research; @harris2019redcap] by way of the University of Basel [sciCORE](https://redcap.scicore.unibas.ch).
+Participants were recruited via the [website](https://enlightenyourclock.org/participate-in-research) (<https://enlightenyourclock.org/participate-in-research>) of the science-communication comic book "Enlighten your clock", co-released with the survey [@Weinzaepflen.2021], social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by the distribution of the survey link via f.lux [@f.lux].
+The initial page of the online survey provided information about the study, including that participation was voluntary and that respondents could withdraw from participation at any time without being penalised.
+Subsequently, consent was recorded digitally for the adult participants (\>18 years), while under-aged participants (\<18 years) were prompted to obtain additional assent from their parents/legal guardians.
+Filling in all questionnaires was estimated to take less than 30 minutes, and participation was not compensated.
+
+As a part of the demographic data, participants provided information regarding age, sex, gender identity, occupational status, COVID-19-related occupational setting, time zone/country of residence and native language.
+The demographic characteristics of our sample are given in **Table 1**.
+Participants were further asked to confirm that they participated in the survey for the first time.
+All questions incorporating retrospective recall were aligned to a "past four weeks" period.
+Additionally, four attention check items  were included among the questionnaires to ensure high data quality, with the following phrasing:
+- We want to make sure you are paying attention. What is 4+5?
+- [...] Please select "Strongly disagree" here.
+- [...] Please type in "nineteen" as a number.
+- [...] Please select "Does not apply/I don't know." here.
+
+## Analytic strategy
+
+Figure \@ref(fig:FlowchartFig) summarises the steps we followed while developing the LEBA. We conducted all analyses with the statistical software environment R [@R-base]. 
+**Firstly**, we set an item pool of 48 items with a six-point Likert-type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial inventory.
+Our purpose was to capture light exposure-related behaviour.
+In that context, the first two response options: "Does not apply/I don't know" and "Never", provided similar information.
+As such, we collapsed them into one, making it a 5-point Likert-type response format (1-Never, 2-Rarely, 3-Sometimes, 4-Often, 5-Always).
+
+**Secondly**, the two rounds of data collection were administered.
+In the first round (EFA sample; n=`r nrow(EFA.descriptives)`) we collected data for the exploratory factor analysis (EFA).
+A sample of at least 250-300 is recommended for EFA [@comreyFirstCourseFactor1992; @schonbrodtWhatSampleSize2013].
+The EFA sample exceeded this recommendation.
+The second round data (CFA sample; n=`r nrow(CFA.descriptives)`) was subjected to confirmatory factor analysis (CFA).
+To assess sampling adequacy for CFA, we followed the N:q rule [@bentlerPracticalIssuesStructural1987; @jacksonRevisitingSampleSize2003; @klinePrinciplesPracticeStructural2015; @worthingtonScaleDevelopmentResearch2006], where at least ten participants per item are required to earn trustworthiness of the result.
+Again, our CFA sample exceeded this guidelines.
+
+**Thirdly**, we conducted descriptive and item analyses and proceeded to EFA using the "psych" package [@R-psych] on the EFA sample.
+Prior to the EFA, the necessary assumptions, including sample adequacy, normality assumptions, and quality of correlation matrix, were assessed.
+As our data violated both the univariate and multivariate normality assumption and yielded ordinal response data, we used a polychoric correlation matrix in the EFA and employed "principal axis" (PA) as the factor extraction method [@desjardinsHandbookEducationalMeasurement2018; @watkinsStepbyStepGuideExploratory2020].
+We applied a combination of methods, including a Scree plot [@cattellScreeTestNumber1966], minimum average partials method [@velicerDeterminingNumberComponents1976], and Hull method [@lorenzo-sevaHullMethodSelecting2011] to identify factor numbers.
+To determine the latent structure, we followed the common guidelines: (i) no factors with fewer than three items (ii) no factors with a factor loading \<0.3 (iii) no items with cross-loading \> .3 across factors [@bandalosFactorAnalysisExploratory2018].
+<!-- We also conducted an EFA on the non-merged response options data set (**Supplementary File 1**).
+-->
+
+For reliability estimation, the "psych" package was applied [@R-psych].
+Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it tends to deflate the estimates for Likert-type data since the calculation is based on the Pearson-correlation matrix, which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal].
+Subsequently, we reported ordinal alpha for each factor obtained in the EFA which was suggested as a better reliability estimates for ordinal data [@zumbo2007ordinal].
+We also estimated the internal consistency reliability of the total inventory using McDonald's $\omega_t$ coefficient, which was suggested as a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use].
+Both ordinal alpha and McDonald's $\omega_t$ coefficient values range between 0 to 1, where higher values represent better reliability.
+
+To validate the latent structure obtained in the EFA, we conducted a categorical confirmatory factor analysis (CFA) with the weighted least squares means and variance adjusted (WLSMV) estimation [@desjardinsHandbookEducationalMeasurement2018], using the "lavaan" package [@R-lavaan] on the CFA sample.
+We assessed the model fit using standard model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI): close to 0.95 or above/ between 0.90-0.95 and above (iii) root mean square error of approximation (RMSEA): close to 0.06 or below, (iv) Standardized root mean square (SRMR): close to 0.08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner].
+However, the $\chi^2$ test is sensitive to sample size [@brownConfirmatoryFactorAnalysis2015], and SRMR does not work well with ordinal data [@RN1272].
+Consequently, we judged the model fit using CFI, TLI and RMSEA.
+
+In order to evaluate whether the construct demonstrated psychometric equivalence and the same meaning across native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non-native English speakers (n=`r invariance.data.descriptives.count[2,2]`) in the CFA sample (n=`r nrow(CFA.descriptives)`) [@putnick2016measurement; @klinePrinciplesPracticeStructural2015] measurement invariance analysis was used.
+We used structural equation modelling framework applying the "lavaan" package [@R-lavaan] to assess the measurement invariance.
+We successively compared four nested models: configural, metric, scalar, and residual models using the $\chi^2$ difference test ($\Delta \chi^2$).
+Among MI models, the configural model is the least restrictive, and the residual model is the most restrictive.
+A non-significant $\Delta \chi^2$ test between two nested measurement invariance models indicates mode fit does not significantly decrease for the superior model, thus allowing the superior invariance model to be accepted [@dimitrov2010testing; @widaman1997exploring].
+
+**Fourthly**, in a secondary analysis, we identified the educational grade level (US education system) required to understand the items in our inventory with the Flesch-Kincaid grade level identification method [@flesch1948new] applying the "koRpus" [@R-koRpus] package.
+Correspondingly, we analysed possible semantic overlap of our developed inventory using the ["Semantic Scale Network" (SSN)](https://rosenbusch.shinyapps.io/semantic_net/) engine [@rosenbusch2020semantic].
+The SSN detects semantically related scales and provides a cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic].
+Pairs of scales with a cosine similarity index value of 1 inidicate full semantical similarity, suggesting redundancy.
+
+**Lastly**, we derived a short form of the LEBA employing an Item Response Theory (IRT) based analysis.
+We fitted each factor of the LEBA to the combined EFA and CFA sample (n=`r nrow(sem.data)`) using the graded response model [@samejima1997handbook] via the "mirt" package [@R-mirt].
+IRT assesses the item quality by estimating the item discrimination, item difficulty, item information curve, and test information curve [@bakerBasicsItemResponse2017].
+Item discrimination indicates how well a particular item can differentiate between participants across the given latent trait continuum ($\theta$).
+Item difficulty corresponds to the latent trait level at which the probability of endorsing a particular response option is 50%.
+The item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
+Here, we reported the item difficulty and discrimination parameter and categorized the items based on their item discrimination index: (i) none = 0; (ii) very low = 0.01 to 0.34; (iii) low = 0.35 to 0.64; (iv) moderate = 0.65 to 1.34 ; (v) high = 1.35 to 1.69; (vi) very high \>1.70 [@bakerBasicsItemResponse2017].
+We discarded the items with a relatively flat item information curve (information \<.2) to derive the short form of LEBA.
+We also assessed the precision of the short LEBA utilizing the test information curve (TIC).
+TIC indicates the amount of information a particular scale carries along the latent trait continuum.
+Additionally, the item and person fit of the fitted IRT models were analysed to gather more evidence on the validity and meaningfulness of our scale [@desjardinsHandbookEducationalMeasurement2018].
+The item fit was evaluated using the RMSEA value obtained from Signed-$\chi^2$ index implementation, where an RMSEA value $\le$.06 was considered an adequate item fit.
+The person fit was estimated employing the standardized fit index Zh statistics [@drasgow1985appropriateness].
+Here, Zh \< -2 was considered as a misfit [@drasgow1985appropriateness].
+
+```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Flow chart of the LEBA (long and short form) development and evaluation. ', out.height='50%', out.width='50%'}
+knitr::include_graphics('Figures/Figure1.png', dpi = 600 )
+```
+
+## Ethical approval
+
+The current research project utilizes fully anonymous online survey data and therefore does not fall under the scope of the Human Research Act, making an authorisation from the ethics committee redundant.
+Nevertheless, the cantonal ethics commission (Ethikkommission Nordwest- und Zentralschweiz, EKNZ) reviewed our proposition (project ID Req-2021-00488) and issued an official clarification of responsibility.
+
+## Code, materials and data availability
+
+The present article is a fully reproducible open access "R Markdown" document.
+All code and data underlying this article is available on a public [GitHub repository](https://github.com/leba-instrument).
+The English version of long and short form of LEBA  inventory and online survey implementation templates on common survey platforms(Qualtrics and REDCap) -- is available  on another public [GitHub repository](https://github.com/leba-instrument/leba-instrument-en) as well as on the dedicated [website](https://leba-instrument.org/) of the LEBA inventory under an open-access licence (Creative Commons CC-BY-NC-ND).
 

### 2023-02-13 manuscript.Rmd
Add files via upload

@@
 
-author: 
-  - name          : "Mushfiqul Anwar Siraji"
-    affiliation   : "1, *"
-    email         : "mushfiqul.anwarsiraji@monash.edu"
-    role:         
-      - Formal Analysis
-      - Visualization
-      - Writing – original draft
-      - Writing – review & editing
-
-  - name          : "Rafael Robert Lazar"
-    affiliation   : "2, 3, *"
-    role:
-      - Data curation
-      - Investigation
-      - Project administration
-      - Visualization
-      - Writing – original draft
-      - Writing – review & editing
-
-  - name          : "Juliëtte	van Duijnhoven"
-    affiliation   : "4, 5"
-    email         : "j.v.duijnhoven1@tue.nl"
-    role:         
-      - Conceptualization
-      - Methodology
-      - Investigation
-      - Writing – review & editing
-
-  - name          : "Luc Schlangen"
-    affiliation   : "5, 6"
-    email         : "l.j.m.schlangen@tue.nl"
-    role:         
-      - Conceptualization
-      - Methodology
-      - Investigation
-      - Writing – review & editing
-
-  - name          : "Shamsul Haque"
-    affiliation   : "1"
-    email         : "shamsul@monash.edu"
-    role:         
-      - Conceptualization
-      - Supervision
-      - Writing – review & editing
-
-  - name          : "Vineetha Kalavally"
-    affiliation   : "7"
-    email         : "vineetha@monash.edu"
-    role:         
-      - Supervision
-      - Writing – review & editing
-
-  - name          : "Céline Vetter"
-    affiliation   : "8"
-    email         : "celine.vetter@colorado.edu"
-    role:         
-      - Conceptualization
-      - Writing – review & editing
-
-  - name          : "Gena Glickman"
-    affiliation   : "9"
-    email         : "gena.glickman@usuhs.edu"
-    role:         
-      - Conceptualization
-      - Methodology
-      - Writing – review & editing
-
-  - name          : "Karin Smolders"
-    affiliation   : "5,6"
-    email         : "k.c.h.j.smolders@tue.nl"
-    role:         
-      - Conceptualization
-      - Methodology
-      - Writing – review & editing
-
-  - name          : "Manuel Spitschan"
-    corresponding : yes
-    affiliation   : "10, 11, 12"
-    email         : "manuel.spitschan@tum.de "
-    role:         
-      - Conceptualization
-      - Data curation
-      - Investigation
-      - Project administration
-      - Visualization
-      - Methodology
-      - Writing – original draft
-      - Writing – review & editing
-
-affiliation:
-  - id            : "1"
-    institution   : "Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
-  - id            : "2"
-    institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"
-  - id            : "3"
-    institution   : "University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland"
-  - id            : "4"
-    institution   : "Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands"
-  - id            : "5"
-    institution   : "Eindhoven University of Technology, Intelligent Lighting Institute, Eindhoven, Netherlands"
-  - id            : "6"
-    institution   : "Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Human-Technology Interaction, Eindhoven, Netherlands"
-  - id            : "7"
-    institution   : "Monash University, Department of Electrical and Computer Systems Engineering, Selangor, Malaysia"
-  - id            : "8"
-    institution   : "University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA"
-
-  - id            : "9"
-    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
-  - id            : "10"
-    institution   : "Translational Sensory & Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany"
-  - id            : "11"
-    institution   : "TUM Department of Sport and Health Sciences (TUM SG), Technical University of Munich, Munich, Germany"
-  - id            : "12"
-    institution   : "TUM Institute of Advanced Study (TUM-IAS), Technical University of Munich, Garching, Germany"
-  - id            : "*"
-    institution   : "Joint first author"
-
-authornote: |
-  This research is supported by funding from the Welcome Trust (204686/Z/16/Z), the European Training Network LIGHTCAP (project number 860613) under the Marie Skłodowska-Curie actions framework H2020-MSCA-ITN-2019, the BioClock project (number 1292.19.077) of the research program Dutch Research Agenda: Onderzoek op Routes door Consortia (NWA-ORC) which is (partly) financed by the Dutch Research Council (NWO), and the European Union and the nationals contributing in the context of the ECSEL Joint Undertaking programme (2021-2024) under the grant #101007319.
+# author: 
+#   - name          : "Mushfiqul Anwar Siraji"
+#     affiliation   : "1, *"
+#     email         : "mushfiqul.anwarsiraji@monash.edu"
+#     role:         
+#       - Formal Analysis
+#       - Visualization
+#       - Writing – original draft
+#       - Writing – review & editing
+#        
+#   - name          : "Rafael Robert Lazar"
+#     affiliation   : "2, 3, *"
+#     role:
+#       - Data curation
+#       - Investigation
+#       - Project administration
+#       - Visualization
+#       - Writing – original draft
+#       - Writing – review & editing
+#       
+#   - name          : "Juliëtte	van Duijnhoven"
+#     affiliation   : "4, 5"
+#     email         : "j.v.duijnhoven1@tue.nl"
+#     role:         
+#       - Conceptualization
+#       - Methodology
+#       - Investigation
+#       - Writing – review & editing
+# 
+#   - name          : "Luc Schlangen"
+#     affiliation   : "5, 6"
+#     email         : "l.j.m.schlangen@tue.nl"
+#     role:         
+#       - Conceptualization
+#       - Methodology
+#       - Investigation
+#       - Writing – review & editing
+# 
+#   - name          : "Shamsul Haque"
+#     affiliation   : "1"
+#     email         : "shamsul@monash.edu"
+#     role:         
+#       - Conceptualization
+#       - Supervision
+#       - Writing – review & editing
+#       
+#   - name          : "Vineetha Kalavally"
+#     affiliation   : "7"
+#     email         : "vineetha@monash.edu"
+#     role:         
+#       - Supervision
+#       - Writing – review & editing
+#       
+#   - name          : "Céline Vetter"
+#     affiliation   : "8"
+#     email         : "celine.vetter@colorado.edu"
+#     role:         
+#       - Conceptualization
+#       - Writing – review & editing
+#       
+#   - name          : "Gena Glickman"
+#     affiliation   : "9"
+#     email         : "gena.glickman@usuhs.edu"
+#     role:         
+#       - Conceptualization
+#       - Methodology
+#       - Writing – review & editing
+#       
+#   - name          : "Karin Smolders"
+#     affiliation   : "5,6"
+#     email         : "k.c.h.j.smolders@tue.nl"
+#     role:         
+#       - Conceptualization
+#       - Methodology
+#       - Writing – review & editing
+# 
+#   - name          : "Manuel Spitschan"
+#     corresponding : yes
+#     affiliation   : "10, 11, 12"
+#     email         : "manuel.spitschan@tum.de "
+#     role:         
+#       - Conceptualization
+#       - Data curation
+#       - Investigation
+#       - Project administration
+#       - Visualization
+#       - Methodology
+#       - Writing – original draft
+#       - Writing – review & editing
+# 
+# affiliation:
+#   - id            : "1"
+#     institution   : "Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
+#   - id            : "2"
+#     institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"
+#   - id            : "3"
+#     institution   : "University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland"
+#   - id            : "4"
+#     institution   : "Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands"
+#   - id            : "5"
+#     institution   : "Eindhoven University of Technology, Intelligent Lighting Institute, Eindhoven, Netherlands"
+#   - id            : "6"
+#     institution   : "Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Human-Technology Interaction, Eindhoven, Netherlands"
+#   - id            : "7"
+#     institution   : "Monash University, Department of Electrical and Computer Systems Engineering, Selangor, Malaysia"
+#   - id            : "8"
+#     institution   : "University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA"
+# 
+# 
+#   - id            : "9"
+#     institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
+#   - id            : "10"
+#     institution   : "Translational Sensory & Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany"
+#   - id            : "11"
+#     institution   : "TUM Department of Sport and Health Sciences (TUM SG), Technical University of Munich, Munich, Germany"
+#   - id            : "12"
+#     institution   : "TUM Institute of Advanced Study (TUM-IAS), Technical University of Munich, Garching, Germany"
+#   - id            : "*"
+#     institution   : "Joint first author"   
+# 
+# 
+# authornote: |
+#   This research is supported by funding from the Welcome Trust (204686/Z/16/Z), the European Training Network LIGHTCAP (project number 860613) under the Marie Skłodowska-Curie actions framework H2020-MSCA-ITN-2019, the BioClock project (number 1292.19.077) of the research program Dutch Research Agenda: Onderzoek op Routes door Consortia (NWA-ORC) which is (partly) financed by the Dutch Research Council (NWO), and the European Union and the nationals contributing in the context of the ECSEL Joint Undertaking programme (2021-2024) under the grant #101007319.
 
@@
 
-bibliography      : ["references.bib", "lib_references.bib"]
+#bibliography      : ["references.bib", "lib_references.bib"]
+bibliography      : ["references.bib"]
 
@@
 #This chunk controls the common chunk parameters for the whole manuscript
-knitr::opts_chunk$set(echo = FALSE, warning = F, message = F, dpi=600, fig.width = 6,
- fig.asp = 0.8,out.width = "80%", dev=c('png','postscript'))
-#options(knitr.duplicate.label = "allow")
+knitr::opts_chunk$set(echo=FALSE, warning=F, message=F, dpi=600, fig.width=6,
+ fig.asp=0.8,out.width="80%", dev=c('png','postscript'))
+#options(knitr.duplicate.label="allow")
 set.seed(123)
-par(family = "Arial")
+par(family="Arial")
 ```
@@
 apatheme=theme_bw()+
-  theme(panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank(),
-        panel.background = element_blank(),
-        axis.text.x = element_text(size = 80),
-        axis.text.y = element_text(size = 80),
-        axis.title.x = element_text(size = 80),
-        axis.title.y = element_text(size = 80),
-        plot.title = element_text(size = 80),
-        legend.text = element_text(size =80),
+  theme(panel.grid.major=element_blank(),
+        panel.grid.minor=element_blank(),
+        panel.background=element_blank(),
+        axis.text.x=element_text(size=80),
+        axis.text.y=element_text(size=80),
+        axis.title.x=element_text(size=80),
+        axis.title.y=element_text(size=80),
+        plot.title=element_text(size=80),
+        legend.text=element_text(size =80),
         legend.title=element_blank(),
-        axis.line.x = element_line(color='black'),
-        axis.line.y = element_line(color='black'),
-        panel.border = element_rect(color = "black",
-                                    fill = NA,
-                                    size = 1))
+        axis.line.x=element_line(color='black'),
+        axis.line.y=element_line(color='black'),
+        panel.border=element_rect(color="black",
+                                    fill=NA,
+                                    size=1))
 
 apatheme_2=theme_bw()+ #Figure 4
-  theme(panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank(),
-        panel.background = element_blank(),
-        axis.text.x = element_text(size = 35),
-        axis.text.y = element_text(size = 35),
-        axis.title.x = element_text(size = 35),
-        axis.title.y = element_text(size = 35),
-        plot.title = element_text(size = 35),
-        legend.text = element_text(size =35),
+  theme(panel.grid.major=element_blank(),
+        panel.grid.minor=element_blank(),
+        panel.background=element_blank(),
+        axis.text.x=element_text(size=35),
+        axis.text.y=element_text(size=35),
+        axis.title.x=element_text(size=35),
+        axis.title.y=element_text(size=35),
+        plot.title=element_text(size=35),
+        legend.text=element_text(size =35),
         legend.title=element_blank(),
-        axis.line.x = element_line(color='black'),
-        axis.line.y = element_line(color='black'),
-        panel.border = element_rect(color = "black",
-                                    fill = NA,
-                                    size = 1))
+        axis.line.x=element_line(color='black'),
+        axis.line.y=element_line(color='black'),
+        panel.border=element_rect(color="black",
+                                    fill=NA,
+                                    size=1))
 
 apatheme_3=theme_bw()+ #Figure 6
-  theme(panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank(),
-        panel.background = element_blank(),
-        axis.text.x = element_text(size = 90),
-        axis.text.y = element_text(size = 90),
-        axis.title.x = element_text(size = 90),
-        axis.title.y = element_text(size = 90),
-        plot.title = element_text(size = 90),
-        legend.text = element_text(size =90),
+  theme(panel.grid.major=element_blank(),
+        panel.grid.minor=element_blank(),
+        panel.background=element_blank(),
+        axis.text.x=element_text(size=90),
+        axis.text.y=element_text(size=90),
+        axis.title.x=element_text(size=90),
+        axis.title.y=element_text(size=90),
+        plot.title=element_text(size=90),
+        legend.text=element_text(size =90),
         legend.title=element_blank(),
-        axis.line.x = element_line(color='black'),
-        axis.line.y = element_line(color='black'),
-        panel.border = element_rect(color = "black",
-                                    fill = NA,
-                                    size = 1))
+        axis.line.x=element_line(color='black'),
+        axis.line.y=element_line(color='black'),
+        panel.border=element_rect(color="black",
+                                    fill=NA,
+                                    size=1))
 
@@
 nocite: |
-  `r cite_r("lib_references.bib")`
+  #`r cite_r("lib_references.bib")`
   [@verriotto2017new][@eklund1996development][@bajaj2011validation][@dianat2013objective]
@@
 Light exposure received by the eyes affects many facets of human health, well-being, and performance beyond visual sensation and perception [@boyce_light_2022].
-The non-image-forming (NIF) effects of light comprise light’s circadian and non-circadian influence on several physiological and psychological functions, such as the secretion of melatonin, sleep, mood, pupil size, body temperature, alertness, and higher cognitive functions [@Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020].
+The non-image-forming (NIF) effects of light comprise light’s circadian and non-circadian influence on several physiological and psychological functions, such as the secretion of melatonin, sleep, mood, pupil size, body temperature, alertness, and higher cognitive functions [@blume_effects_2019].
 
@@
 Furthermore, building on earlier attempts [e.g.
-@hubalek_ambulant_2006], there was a recent push toward the development and use of portable light loggers to improve ambulant light assessment and gain more insight into the NIF effects of light on human health in field conditions [@stampfli_light-dosimeter_2021; @van_duijnhoven_recommendations_2017; @webler_towards_2021; @aarts2017performance].
+@hubalek_ambulant_2006], there was a recent push toward the development and use of portable light loggers to improve ambulant light assessment and gain more insight into the NIF effects of light on human health in field conditions.
 Attached to different body parts (e.g., wrist; head, at eye level; chest), these light loggers allow for the objective measurement of individual photic exposure patterns under real-world conditions and thus are valuable tools for field studies.
@@
 
-These measurement limitations point to a couple of research challenges which we adressed here: How can we gain insight into light exposure patterns via self-report but circumvent directly inquiring about the specific properties and intensity of a light source?
-And how can we simultaneously assess how people habitually interact with the received light?
-We propose that these challenges can be tackled by assessing light-exposure-related behaviour.
-We argue that, besides measuring received light exposure as intensity, it is also essential to understand people's behaviours with respect to different light situations.
-In many cases, humans have become their own agents regarding their exposure to light or darkness through daylight and electric light, and as such people’s light exposure-related behaviours ultimately determine their light consumption and timing: People receive different light depending on their daily activities, including workplace habits, bedtime hygiene, pastime and social activities.
-Ultimately, in order to optimize lighting for human health and well being, better understanding of light-related behaviours will serve to identify additional points of intervention as well as to provide an added dimension to efficacy and implementation studies of novel lighting strategies.
-We argue that assessing these activities is a beneficial stepping stone for prospective behaviour change to maintain light hygiene: a proper balance of exposures to light to maintain circadian rhythms.
-
 To date, little effort has been made to understand and capture these activities.
-**Supplementary Table 1** summarises the existing questionnaire literature assessing light exposure-related properties.
-However, only a few questions of these existing tools were associated with light exposure-related behaviour.
-For example, the “Munich Chronotype  Questionnaire” [@roenneberg2003life], a popular self-report tool for identifying chronotypes via mid-sleep times, includes questions about the individual’s typical time spent outdoors on workdays and free days.
-The Visual Light Sensitivity Questionnaire-8 [@verriotto2017new] and Photosensitivity Assessment Questionnaire [@bossini2006sensibilita] are a couple of self-report tools measuring visual light sensitivity.
-They contain single items which probe the preference for specific light situations such as: “In the past month, how often did you need to wear dark glasses on cloudy days or indoors?” [@verriotto2017new];"I prefer rooms that are in semi-darkness."; [@bossini2006sensibilita].
-In addition, the “Pittsburgh Sleep Quality Index” [@buysse1989pittsburgh], is a popular measure of sleep quality.
-It contains questions about bedtime and wake-up times, which are relevant to light exposure around bedtime.
-However, none of these questionnaires provides a scalable solution to capture light exposure-related behaviour in various lighting situations.
-To fill this gap, we here present the development process of a novel self-reported inventory - the Light Exposure Behaviour Assessment (LEBA) - for characterizing diverse light exposure-related behaviours.
+Here, we present the development process of a novel self-reported inventory, the Light Exposure Behaviour Assessment (LEBA), for characterizing diverse light exposure-related behaviours.
 
@@
 sufix <- c(1:48)
-colnam <- paste(prefix,sufix, sep = "" )
+colnam <- paste(prefix,sufix, sep="" )
 colnames(sem.data) <- colnam
@@
 desctable.data$slypos_demographics_gender.factor <-
-  recode_factor(desctable.data$slypos_demographics_gender.factor, "No" = "Yes",
+  recode_factor(desctable.data$slypos_demographics_gender.factor, "No"="Yes",
          "Yes"= "No")
@@
   tbl_summary(
-    by = IncludedInCFA,
-    statistic = list(all_continuous() ~ "{mean} ({sd})",
+    by=IncludedInCFA,
+    statistic=list(all_continuous() ~ "{mean} ({sd})",
                      all_categorical() ~ "{n} ({p}%)"),
-    digits = all_continuous() ~ 2,
-    label = list(slypos_demographics_age ~ "Age",
+    digits=all_continuous() ~ 2,
+    label=list(slypos_demographics_age ~ "Age",
                  slypos_demographics_sex.factor ~ "Sex",
@@
 
-    missing = "no"
+    missing="no"
     ) %>% add_overall() %>% bold_labels() %>% 
@@
 as_tibble(desc_table) -> desc_tibble 
-as_kable_extra(desc_table, format = "latex",booktabs = T) -> desc_kable #save it as a knitr::kable
+as_kable_extra(desc_table, format="latex",booktabs=T) -> desc_kable #save it as a knitr::kable
 
@@
   tbl_summary(
-    label = slypos_demographics_tz.factor ~ "Time zone - Country",
-    statistic = list(all_categorical() ~ "{n} ({p}%)"),
-    missing = "no",
-    sort = all_categorical() ~ "frequency",
-    include = "slypos_demographics_tz.factor"
+    label=slypos_demographics_tz.factor ~ "Time zone - Country",
+    statistic=list(all_categorical() ~ "{n} ({p}%)"),
+    missing="no",
+    sort=all_categorical() ~ "frequency",
+    include="slypos_demographics_tz.factor"
   )  %>% bold_labels() %>%
   modify_header(label ~ "") %>%
-  as_tibble(format = 'pipe') -> tz_tibble
+  as_tibble(format='pipe') -> tz_tibble
 
@@
 ```{r demotab, warning=F, message=F}
-desc_kable  %>% kable_styling(latex_options = c("scale_down")) %>% landscape()
+desc_kable  %>% kable_styling(latex_options=c("scale_down")) %>% landscape()
 ```
@@
 
-Our results focus on the development of the LEBA inventory and its psychometric validation using a large scale online sample data (n = `r nrow(data)`).
+Our results focus on the development of the LEBA inventory and its psychometric validation using a large scale online sample data (n=`r nrow(data)`).
 
@@
 
-We conducted two rounds of large scale online survey between 17 May 2021 and 3 September 2021 to generate data from `r nrow(data)` participants with varied geographic locations (countries = `r nrow(num.countries)`; time-zone = `r nrow(numUTC)`).
+We conducted two rounds of large scale online survey between 17 May 2021 and 3 September 2021 to generate data from `r nrow(data)` participants with varied geographic locations (countries=`r nrow(num.countries)`; time-zone=`r nrow(numUTC)`).
 For a complete list of geographic locations, see **Supplementary Table 2**.
@@
 Only participants completing the full LEBA inventory were included.
-We used the data from first round for the exploratory factor analysis (EFA sample; n = `r nrow(EFA.data)`) and data from the second round was used in the confirmatory factor analysis (CFA sample; n = `r nrow(CFA.data)`).
+We used the data from first round for the exploratory factor analysis (EFA sample; n=`r nrow(EFA.data)`) and data from the second round was used in the confirmatory factor analysis (CFA sample; n=`r nrow(CFA.data)`).
 Participants in our survey were aged between `r min(desctable.data$slypos_demographics_age)` to `r max(desctable.data$slypos_demographics_age)` years, with an overall mean of \~ `r round(mean(desctable.data$slypos_demographics_age), 2)` years of age [Overall: `r mean(desctable.data$slypos_demographics_age)`±`r sd(desctable.data$slypos_demographics_age)`; EFA: `r mean(desctable.data$slypos_demographics_age[desctable.data$IncludedInCFA == "1.
@@
 ```{r full-data-mardia, include =F}
-mardia.all.data <- psych::mardia(sem.data, na.rm = T, plot =T)
+mardia.all.data <- psych::mardia(sem.data, na.rm=T, plot =T)
 descriptives.all.data <- tabledown::des.tab(sem.data)
@@
 gt.data$item08 <- fct_recode(gt.data$item08,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
+  "5"="1",
+  "4"="2",
+  "2"="4",
+  "1"="5"
 )
@@
 gt.data$item26 <- fct_recode(gt.data$item26,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
+  "5"="1",
+  "4"="2",
+  "2"="4",
+  "1"="5"
 )
@@
 gt.data$item37 <- fct_recode(gt.data$item26,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
+  "5"="1",
+  "4"="2",
+  "2"="4",
+  "1"="5"
 )
@@
   dplyr::summarise(
-    nr = n(),
-    mean = mean(value, na.rm = TRUE),
-    # med = median(value, na.rm = TRUE),
-    sd = sd(value, na.rm = TRUE),
-    hist_data = list(value),
-    dens_data = list(value),
-    .groups = "drop"
+    nr=n(),
+    mean=mean(value, na.rm=TRUE),
+    # med=median(value, na.rm=TRUE),
+    sd=sd(value, na.rm=TRUE),
+    hist_data=list(value),
+    dens_data=list(value),
+    .groups="drop"
   ) %>% 
@@
 
-vars_labels = as.data.frame(sapply(sem.data,
+vars_labels=as.data.frame(sapply(sem.data,
        function(x){attr(x,"label")}))
@@
 
-recod_LEBA <- c( "1" = "Never", "2" = "Rarely", "3"= "Sometimes","4" = "Often",
-                 "5" = "Always")
+recod_LEBA <- c( "1"="Never", "2"="Rarely", "3"= "Sometimes","4"="Often",
+                 "5"="Always")
 LEBA.likert <-  mutate(LEBA.likert, across(starts_with("item"), ~unname(recod_LEBA[.])))
 
-LEBA.Factor = as.data.frame(lapply(LEBA.likert,factor,
-                                   ordered = T))
+LEBA.Factor=as.data.frame(lapply(LEBA.likert,factor,
+                                   ordered=T))
 #get the items name
@@
 #Calculate percentage
-percentage <- kutils::likert(LEBA.Factor, vlist = items )
+percentage <- kutils::likert(LEBA.Factor, vlist=items )
 
@@
     hist_data,
-    type = "histogram",
-    line_color = "black", 
-    fill_color = "#00A08799",
-    bw = 1,
-    same_limit = TRUE)%>%
+    type="histogram",
+    line_color="black", 
+    fill_color="#00A08799",
+    bw=1,
+    same_limit=TRUE)%>%
   gtExtras::gt_plt_dist(
     dens_data,
-    type = "density",
-    line_color = "black", 
-    fill_color = "grey",
-    bw = 0.75,
-    same_limit = TRUE
+    type="density",
+    line_color="black", 
+    fill_color="grey",
+    bw=0.75,
+    same_limit=TRUE
   )%>%
 # format decimals
-  fmt_number(columns = mean:sd, decimals = 1) %>%
+  fmt_number(columns=mean:sd, decimals=1) %>%
 # header
   tab_header(
-    title = md("Summary Descriptives (n=690)"),
-    subtitle = md("Items 01-24 ")) %>%
+    title=md("Summary Descriptives (n=690)"),
+    subtitle=md("Items 01-24 ")) %>%
   cols_align(
-    align = "left",
-    columns = Item:Stem
+    align="left",
+    columns=Item:Stem
   ) %>% 
   tab_spanner(
-    label = "Summary Statistics",
-    columns = mean:sd
+    label="Summary Statistics",
+    columns=mean:sd
   ) %>%
   tab_spanner(
-    label = "Graphics",
-    columns = hist_data:dens_data
+    label="Graphics",
+    columns=hist_data:dens_data
   ) %>% 
   tab_spanner(
-    label = "Response Pattern",
-    columns = Never:Always
+    label="Response Pattern",
+    columns=Never:Always
   ) %>%
      tab_footnote(
-     footnote = md("**Shapiro–Wilk test**"),
-     locations = cells_column_labels(columns = `S-W Statistics`)
+     footnote=md("**Shapiro–Wilk test**"),
+     locations=cells_column_labels(columns=`S-W Statistics`)
   ) %>% 
@@
 cols_label(
-  Item = ("Items"),
-  Stem = ("Stem"),
-  mean = ("Mean"),
-  sd = (("SD")),
-  `S-W Statistics` = ("SW"),
-  hist_data = "Histogram",
-  dens_data = "Density"
+  Item=("Items"),
+  Stem=("Stem"),
+  mean=("Mean"),
+  sd=(("SD")),
+  `S-W Statistics`=("SW"),
+  hist_data="Histogram",
+  dens_data="Density"
 )  %>% 
@@
   cols_align(
-    align = "center",
-    columns = mean:Always
-  ) %>%
-  opt_align_table_header(align = "left") %>%
+    align="center",
+    columns=mean:Always
+  ) %>%
+  opt_align_table_header(align="left") %>%
 # add coloured dots and lines on the first column
@@
     Item,
-    palette = "ggthemes::fivethirtyeight"
+    palette="ggthemes::fivethirtyeight"
   ) %>% tab_options(
-    table.font.size = px(14L)) %>% 
+    table.font.size=px(14L)) %>% 
   cols_width(
     Stem ~ px(200)) %>% 
- gtsave("Figures/Figure2.png", vwidth = 6000)
+ gtsave("Figures/Figure2.png", vwidth=6000)
 
@@
     hist_data,
-    type = "histogram",
-    line_color = "black", 
-    fill_color = "#00A08799",
-    bw = 1,
-    same_limit = TRUE)%>%
+    type="histogram",
+    line_color="black", 
+    fill_color="#00A08799",
+    bw=1,
+    same_limit=TRUE)%>%
   gtExtras::gt_plt_dist(
     dens_data,
-    type = "density",
-    line_color = "black", 
-    fill_color = "grey",
-    bw = 0.75,
-    same_limit = TRUE
+    type="density",
+    line_color="black", 
+    fill_color="grey",
+    bw=0.75,
+    same_limit=TRUE
   )%>%
 # format decimals
-  fmt_number(columns = mean:sd, decimals = 1) %>%
+  fmt_number(columns=mean:sd, decimals=1) %>%
 # header
   tab_header(
-    title = md("Summary Descriptives (n=690)"),
-    subtitle = md("Items 25-48 ")) %>% 
+    title=md("Summary Descriptives (n=690)"),
+    subtitle=md("Items 25-48 ")) %>% 
 #create groups of columns
 # tab_spanner(
-#   label = "Item",
-#   columns = Item:Stem
+#   label="Item",
+#   columns=Item:Stem
 # ) %>%
   cols_align(
-    align = "left",
-    columns = Item:Stem
+    align="left",
+    columns=Item:Stem
   ) %>% 
   tab_spanner(
-    label = "Summary Statistics",
-    columns = mean:sd
+    label="Summary Statistics",
+    columns=mean:sd
   ) %>%
   tab_spanner(
-    label = "Graphics",
-    columns = hist_data:dens_data
+    label="Graphics",
+    columns=hist_data:dens_data
   ) %>% 
   tab_spanner(
-    label = "Response Pattern",
-    columns = Never:Always
+    label="Response Pattern",
+    columns=Never:Always
   ) %>%
@@
      tab_footnote(
-     footnote = md("**Shapiro–Wilk test**"),
-     locations = cells_column_labels(columns = `S-W Statistics`)
+     footnote=md("**Shapiro–Wilk test**"),
+     locations=cells_column_labels(columns=`S-W Statistics`)
   ) %>% 
@@
 cols_label(
-  Item = ("LEBA  Items"),
-  Stem = ("Stem"),
-  mean = ("Mean"),
-  sd = (("SD")),
-  `S-W Statistics` = ("SW"),
-  hist_data = "Histogram",
-  dens_data = "Density"
+  Item=("LEBA  Items"),
+  Stem=("Stem"),
+  mean=("Mean"),
+  sd=(("SD")),
+  `S-W Statistics`=("SW"),
+  hist_data="Histogram",
+  dens_data="Density"
 )  %>% 
@@
     Item,
-    palette = "ggthemes::fivethirtyeight"
+    palette="ggthemes::fivethirtyeight"
   ) %>% tab_options(
-    table.font.size = px(14L)) %>% 
+    table.font.size=px(14L)) %>% 
   cols_width(
     Stem ~ px(200)) %>% 
-gtsave("Figures/Figure3.png",vwidth = 6000)
+gtsave("Figures/Figure3.png",vwidth=6000)
 
@@
 
-We observed that the response patterns of LEBA inventory for the entire sample (n = `r nrow(sem.data)`) were not normally distributed (Figures \@ref(fig:efagtPic1) and \@ref(fig:efagtPic2)).
+We observed that the response patterns of LEBA inventory for the entire sample (n=`r nrow(sem.data)`) were not normally distributed (Figures \@ref(fig:efagtPic1) and \@ref(fig:efagtPic2)).
 All items violated both univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality [@mardiaMeasuresMultivariateSkewness1970].
@@
 
-vars_labels = as.data.frame(sapply(EFA.data,
+vars_labels=as.data.frame(sapply(EFA.data,
        function(x){attr(x,"label")}))
@@
 # Multivariate Normality
-mardia <- psych::mardia(EFA.data, na.rm = T, plot =T)
+mardia <- psych::mardia(EFA.data, na.rm=T, plot =T)
 
@@
   dplyr::summarise(
-    # nr = n(),
-    # mean = mean(value, na.rm = TRUE),
-    # med = median(value, na.rm = TRUE),
-    # sd = sd(value, na.rm = TRUE),
-    hist_data = list(value),
-    dens_data = list(value),
-    .groups = "drop"
+    # nr=n(),
+    # mean=mean(value, na.rm=TRUE),
+    # med=median(value, na.rm=TRUE),
+    # sd=sd(value, na.rm=TRUE),
+    hist_data=list(value),
+    dens_data=list(value),
+    .groups="drop"
   ) %>% 
@@
 
-recod_LEBA <- c( "1" = "Never", "2" = "Rarely", "3"= "Sometimes","4" = "Often",
-                 "5" = "Always")
+recod_LEBA <- c( "1"="Never", "2"="Rarely", "3"= "Sometimes","4"="Often",
+                 "5"="Always")
 efa.LEBA.likert <-  mutate(efa.LEBA.likert, across(starts_with("item"), ~unname(recod_LEBA[.])))
 
-efa.LEBA.Factor = as.data.frame(lapply(efa.LEBA.likert,factor,
-                                   ordered = T))
+efa.LEBA.Factor=as.data.frame(lapply(efa.LEBA.likert,factor,
+                                   ordered=T))
 #get the items name
@@
 #Calculate percentage
-efa.percentage <- kutils::likert(efa.LEBA.Factor, vlist = efa.items )
+efa.percentage <- kutils::likert(efa.LEBA.Factor, vlist=efa.items )
 
@@
     hist_data,
-    type = "histogram",
-    line_color = "black", 
-    fill_color = "#00A08799",
-    bw = 1,
-    same_limit = TRUE)%>%
+    type="histogram",
+    line_color="black", 
+    fill_color="#00A08799",
+    bw=1,
+    same_limit=TRUE)%>%
   gtExtras::gt_plt_dist(
     dens_data,
-    type = "density",
-    line_color = "black", 
-    fill_color = "#E64B3599",
-    bw = 0.75,
-    same_limit = TRUE
+    type="density",
+    line_color="black", 
+    fill_color="#E64B3599",
+    bw=0.75,
+    same_limit=TRUE
   )%>%
 # # format decimals
-#   fmt_number(columns = mean:sd, decimals = 1) %>%
+#   fmt_number(columns=mean:sd, decimals=1) %>%
 # header
   tab_header(
-    title = md("**Light Exposure Behaviour Assessment**"),
-    subtitle = md("Summary Descriptives EFA Sample (n=428)")
+    title=md("**Light Exposure Behaviour Assessment**"),
+    subtitle=md("Summary Descriptives EFA Sample (n=428)")
   ) %>% 
    tab_footnote(
-     footnote = md("**Shapiro–Wilk test**"),
-     locations = cells_column_labels(columns = SW)
+     footnote=md("**Shapiro–Wilk test**"),
+     locations=cells_column_labels(columns=SW)
   ) %>%
@@
 tab_spanner(
-  label = "Items",
-  columns = Item
+  label="Items",
+  columns=Item
 )  %>% 
   tab_spanner(
-    label = "Summary Statistics",
-    columns = Mean:SW
+    label="Summary Statistics",
+    columns=Mean:SW
   ) %>%
   tab_spanner(
-    label = "Graphics",
-    columns = hist_data:dens_data
+    label="Graphics",
+    columns=hist_data:dens_data
   ) %>% 
   tab_spanner(
-    label = "Response Pattern",
-    columns = Never:Always
+    label="Response Pattern",
+    columns=Never:Always
   ) %>%
@@
 cols_label(
-  hist_data = "Histogram",
-  dens_data = "Density"
+  hist_data="Histogram",
+  dens_data="Density"
 ) %>%
@@
   cols_align(
-    align = "center",
-    columns = everything()
-  ) %>%
-  opt_align_table_header(align = "left") %>%
+    align="center",
+    columns=everything()
+  ) %>%
+  opt_align_table_header(align="left") %>%
 # add coloured dots and lines on the first column
@@
     Item,
-    palette = "ggthemes::fivethirtyeight") %>% 
+    palette="ggthemes::fivethirtyeight") %>% 
   tab_options(
-    table.font.size = px(14L)) %>%
+    table.font.size=px(14L)) %>%
 
@@
 # tab_row_group(
-  #     label = md("**F5: Using light in the morning and during daytime**"),
-  #     rows = c(1,3,12,13,24,25) 
+  #     label=md("**F5: Using light in the morning and during daytime**"),
+  #     rows=c(1,3,12,13,24,25) 
   #       ) %>% 
   # tab_row_group(
-  #     label = md("**F4: Using light before bedtime**"),
-  #     rows = c(16,17,18,20,21) 
+  #     label=md("**F4: Using light before bedtime**"),
+  #     rows=c(16,17,18,20,21) 
   #       ) %>% 
   # tab_row_group(
-  #     label = md("**F3: Using phone and smartwatch in bed**"),
-  #     rows = c(2,14,15,22,23) 
+  #     label=md("**F3: Using phone and smartwatch in bed**"),
+  #     rows=c(2,14,15,22,23) 
   #       ) %>% 
   # tab_row_group(
-  #     label = md("**F2: Spending time outdoors**"),
-  #     rows = c(4,5,6,7,8,9) 
+  #     label=md("**F2: Spending time outdoors**"),
+  #     rows=c(4,5,6,7,8,9) 
   #       ) %>% 
   # tab_row_group(
-  #     label = md("**F1: Wearing blue light filters**"),
-  #     rows = c(10,11,19) )
-
-```
-
-Similar non-normal distribution of response pattern was also observed in the EFA sample.
-**Supplementary Figure 1** depicts the univariate descriptive statistics for the EFA sample (n = `r nrow(EFA.data)`).
+  #     label=md("**F1: Wearing blue light filters**"),
+  #     rows=c(10,11,19) )
+
+```
+
+Similarly, non-normal distribution of response pattern was also observed in the EFA sample.
+**Supplementary Figure 1** depicts the univariate descriptive statistics for the EFA sample (n=`r nrow(EFA.data)`).
 Further, We observed that each item's correlation with the aggregated sum of the 48-item's score varied largely (corrected item-total correlation= `r apa(low.r.corec,2,T)` -`r apa(high.r.corec,2,T)`) indicating the possibility of multi-factor structure  of the LEBA inventory.
@@
 
-correlations <- psych::polychoric(EFA.data, correct = 0)
-
-upper <- correlations$rho[upper.tri(correlations$rho, diag = F)]
+correlations <- psych::polychoric(EFA.data, correct=0)
+
+upper <- correlations$rho[upper.tri(correlations$rho, diag=F)]
 
@@
 
-BigR = sum(correlations$rho >= abs(.30) & correlations$rho < abs(1.0), na.rm =T)/2 
-totR = length(EFA.data)*(length(EFA.data)-1)/2
+BigR=sum(correlations$rho >= abs(.30) & correlations$rho < abs(1.0), na.rm =T)/2 
+totR=length(EFA.data)*(length(EFA.data)-1)/2
 cor.per <- print (BigR/totR)*100
@@
 All Items Violated Univariate Normality Assumption Assessed by Shapiro–Wilk (SW) Test.
-The  Item-total Correlation Ranges Between .03-.48", escape =F, font_size = "footnotesize", note = ("$^{*}$p<.001, $^{1}$Shapiro–Wilk Statistics"), align = c("p{1cm}","p{10cm}", rep("p{1cm}", ncol(descriptives2))))
+The  Item-total Correlation Ranges Between .03-.48", escape =F, font_size="footnotesize", note=("$^{*}$p<.001, $^{1}$Shapiro–Wilk Statistics"), align=c("p{1cm}","p{10cm}", rep("p{1cm}", ncol(descriptives2))))
 ```
@@
   geom_histogram(binwidth=.1, col=I("black"),fill="#00A08799")+apatheme+
-  labs( y="", x = "Inter-item correlation")
-
-# ggsave("Figures/correlation_histogram.png", corr.histogram, width = 6, height = 6, dpi = 600, bg ="white")
+  labs( y="", x="Inter-item correlation")
+
+# ggsave("Figures/correlation_histogram.png", corr.histogram, width=6, height=6, dpi=600, bg ="white")
 ```
@@
 #
-p.mat <- correlation::cor_to_p(correlations$rho, 428, method = "polychoric")
-
-corplot <- ggcorrplot(correlations$rho, p.mat=p.mat$p, insig = "pch", hc.order = FALSE, outline.col = "white", type = "lower", legend.title = "Correlation",sig.level = 0.05, pch.cex=1.2,
-                      # insig = "blank",
-           ggtheme = ggplot2::theme_minimal(),tl.srt = 90,  colors = c("#E64B35FF", "white", "#3C5488FF") )+
-  theme( panel.grid.major = element_blank(),
-         axis.text.x = element_text(size = 35),
-         axis.text.y = element_text(size = 35),
+p.mat <- correlation::cor_to_p(correlations$rho, 428, method="polychoric")
+
+corplot <- ggcorrplot(correlations$rho, p.mat=p.mat$p, insig="pch", hc.order=FALSE, outline.col="white", type="lower", legend.title="Correlation",sig.level=0.05, pch.cex=1.2,
+                      # insig="blank",
+           ggtheme=ggplot2::theme_minimal(),tl.srt=90,  colors=c("#E64B35FF", "white", "#3C5488FF") )+
+  theme( panel.grid.major=element_blank(),
+         axis.text.x=element_text(size=35),
+         axis.text.y=element_text(size=35),
          legend.text=element_text(size =35),
-         legend.title = element_text(size =35),
-          plot.title = element_text(size = 35),
-         panel.border = element_rect(color = "black",
-                                    fill = NA,
-                                    size = 1))+labs(title = "(A)")
+         legend.title=element_text(size =35),
+          plot.title=element_text(size=35),
+         panel.border=element_rect(color="black",
+                                    fill=NA,
+                                    size=1))+labs(title="(A)")
 
@@
 Adjusted.EV <- data.frame(Horn$AdjEv)
-Adjusted.EV$type = c('Adjusted Ev')
-Adjusted.EV$num = c(row.names(Adjusted.EV))
-Adjusted.EV$num = as.numeric(Adjusted.EV$num)
-colnames(Adjusted.EV) = c('eigenvalue', 'type', 'num')
+Adjusted.EV$type=c('Adjusted Ev')
+Adjusted.EV$num=c(row.names(Adjusted.EV))
+Adjusted.EV$num=as.numeric(Adjusted.EV$num)
+colnames(Adjusted.EV)=c('eigenvalue', 'type', 'num')
 
 Random.EV <- data.frame(Horn$RndEv)
-Random.EV$type = c('Random EV')
-Random.EV$num = c(row.names(Random.EV))
-Random.EV$num = as.numeric(Random.EV$num)
-colnames(Random.EV) = c('eigenvalue', 'type', 'num')
+Random.EV$type=c('Random EV')
+Random.EV$num=c(row.names(Random.EV))
+Random.EV$num=as.numeric(Random.EV$num)
+colnames(Random.EV)=c('eigenvalue', 'type', 'num')
 
 Unadjusted.EV <- data.frame(Horn$Ev)
-Unadjusted.EV$type = c('Unadjusted EV')
-Unadjusted.EV$num = c(row.names(Unadjusted.EV))
-Unadjusted.EV$num = as.numeric(Unadjusted.EV$num)
-colnames(Unadjusted.EV) = c('eigenvalue', 'type', 'num')
-
-parallel = ggplot(Adjusted.EV, aes(x=num, y=eigenvalue, shape=type, color=type)) +
+Unadjusted.EV$type=c('Unadjusted EV')
+Unadjusted.EV$num=c(row.names(Unadjusted.EV))
+Unadjusted.EV$num=as.numeric(Unadjusted.EV$num)
+colnames(Unadjusted.EV)=c('eigenvalue', 'type', 'num')
+
+parallel=ggplot(Adjusted.EV, aes(x=num, y=eigenvalue, shape=type, color=type)) +
   #Add lines connecting data points
   geom_line(colour ='#DC000099')+
-    #geom_line(data = Random.EV) +
-  #geom_line(data = Unadjusted.EV)+
+    #geom_line(data=Random.EV) +
+  #geom_line(data=Unadjusted.EV)+
     #Add the data points.
   geom_point(size=1.5,colour ='#3C5488FF')+
-  #geom_point(data = Random.EV, size=3)+
-  #geom_point(data = Unadjusted.EV, size=3)+
+  #geom_point(data=Random.EV, size=3)+
+  #geom_point(data=Unadjusted.EV, size=3)+
   scale_y_continuous(name="Eigen Value", limits=c(0, 7), breaks=seq(0,7,1)) +
@@
     #Add vertical line indicating parallel analysis suggested max # of factors to retain
-  geom_hline(yintercept=1, linetype = 'dashed') + apatheme +theme(,legend.position = "None") 
-#text = element_text(size = 25)
+  geom_hline(yintercept=1, linetype='dashed') + apatheme +theme(,legend.position="None") 
+#text=element_text(size=25)
 
@@
 FA.Scree <- data.frame(Scree$fv)
-FA.Scree$type = c('Factor Analysis')
-FA.Scree$num = c(row.names(FA.Scree))
-FA.Scree$num = as.numeric(FA.Scree$num)
-colnames(FA.Scree) = c('eigenvalue', 'type', 'num')
+FA.Scree$type=c('Factor Analysis')
+FA.Scree$num=c(row.names(FA.Scree))
+FA.Scree$num=as.numeric(FA.Scree$num)
+colnames(FA.Scree)=c('eigenvalue', 'type', 'num')
 
 PA.Scree <- data.frame(Scree$pcv)
-PA.Scree$type = c('Principal Component Analysis')
-PA.Scree$num = c(row.names(PA.Scree))
-PA.Scree$num = as.numeric(PA.Scree$num)
-colnames(PA.Scree) = c('eigenvalue', 'type', 'num')
+PA.Scree$type=c('Principal Component Analysis')
+PA.Scree$num=c(row.names(PA.Scree))
+PA.Scree$num=as.numeric(PA.Scree$num)
+colnames(PA.Scree)=c('eigenvalue', 'type', 'num')
 
@@
    geom_line(colour ='#DC000099')+
-  #geom_line(data = PA.Scree)+ 
+  #geom_line(data=PA.Scree)+ 
   geom_point(size=1.5,colour ='#3C5488FF')+
-  #geom_point(data = PA.Scree, size=3)+
+  #geom_point(data=PA.Scree, size=3)+
   scale_y_continuous(name="Eigen Value", limits=c(0, 5), breaks=seq(0,5,1)) +
   scale_x_continuous(name="Factor Number", limits=c(0, 18),breaks=c(0,6,18))+
-  geom_hline(yintercept=1, linetype = 'dashed') + apatheme_2 +theme(legend.position = "None")+labs(title= "(B)")
-# ggsave("Figures/scree.plot.png",scree.plot, width = 4, height =4, dpi = 600,bg = "white", unit ="in")
-
-#text = element_text(size = 25
+  geom_hline(yintercept=1, linetype='dashed') + apatheme_2 +theme(legend.position="None")+labs(title= "(B)")
+# ggsave("Figures/scree.plot.png",scree.plot, width=4, height =4, dpi=600,bg="white", unit ="in")
+
+#text=element_text(size=25
 
@@
 # HULL
-EFA.MRFA::hullEFA(EFA.data,extr = "ULS", index_hull = "CAF", display = TRUE, graph = T,
-        details = TRUE)
+EFA.MRFA::hullEFA(EFA.data,extr="ULS", index_hull="CAF", display=TRUE, graph=T,
+        details=TRUE)
 hull <- ggplot2::last_plot()
-Hull <- hull+ ggtitle(NULL)+xlab("Factor Number")+ylab("CAF")+ aes(color = '#DC000099')+geom_point(color ='#3C5488FF',size =1)+
-  apatheme_2 +theme(legend.position = "None") +scale_fill_identity()+
+Hull <- hull+ ggtitle(NULL)+xlab("Factor Number")+ylab("CAF")+ aes(color='#DC000099')+geom_point(color ='#3C5488FF',size =1)+
+  apatheme_2 +theme(legend.position="None") +scale_fill_identity()+
   scale_x_continuous(breaks=c(0,5,12))+labs(title= "(C)")
 
-# ggsave("Figures/Hull.png",Hull, width = 4, height =4, dpi = 600,bg = "white")
+# ggsave("Figures/Hull.png",Hull, width=4, height =4, dpi=600,bg="white")
 
@@
 #MAP
-map <- psych::VSS(EFA.data, rotate = "varimax", fm = 'minres', n.obs =428 )
+map <- psych::VSS(EFA.data, rotate="varimax", fm='minres', n.obs =428 )
 map.map <- as.data.frame(map$map)
@@
 
-fa.5F.1 <- fa(r=correlations$rho, nfactors = 5, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-AA <- print(fa.5F.1, cut = .3, digits = 3, sort = TRUE)
+fa.5F.1 <- fa(r=correlations$rho, nfactors=5, fm= "pa",rotate ="varimax",
+              residuals=TRUE, SMC=TRUE, n.obs =428)
+AA <- print(fa.5F.1, cut=.3, digits=3, sort=TRUE)
 
@@
 
-correlations.red.5F.1 <- polychoric(reduced.model.5F.1,correct = 0)
-
-fa.5F.2 <- fa(r=correlations.red.5F.1$rho, nfactors = 5, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428)
-
-BB <- print(fa.5F.2, cut = .3, digits = 3, sort = TRUE)
+correlations.red.5F.1 <- polychoric(reduced.model.5F.1,correct=0)
+
+fa.5F.2 <- fa(r=correlations.red.5F.1$rho, nfactors=5, fm= "pa",rotate ="varimax",
+              residuals=TRUE, SMC=TRUE, n.obs =428)
+
+BB <- print(fa.5F.2, cut=.3, digits=3, sort=TRUE)
 
@@
 
-correlations.red.5F.2 <- polychoric(reduced.model.5F.2,correct = 0)
-
-fa.5F.3 <- fa(r=correlations.red.5F.2$rho, nfactors = 5, fm= "pa",rotate ="varimax",
-              residuals = TRUE, SMC = TRUE, n.obs =428,max.iter = 500 )
-
-CC <- print(fa.5F.3, cut = .3, digits = 3, sort = TRUE)
+correlations.red.5F.2 <- polychoric(reduced.model.5F.2,correct=0)
+
+fa.5F.3 <- fa(r=correlations.red.5F.2$rho, nfactors=5, fm= "pa",rotate ="varimax",
+              residuals=TRUE, SMC=TRUE, n.obs =428,max.iter=500 )
+
+CC <- print(fa.5F.3, cut=.3, digits=3, sort=TRUE)
 
@@
 
-efa.table <- tabledown::fac.tab(fa.5F.3,cut=.3, complexity = F)
+efa.table <- tabledown::fac.tab(fa.5F.3,cut=.3, complexity=F)
 efa.table$Communality <- round(as.numeric(efa.table$Communality),2)
@@
 # Residuals
-residual.5F =residuals(fa.5F.3, diag = FALSE, na.rm =T)
+residual.5F =residuals(fa.5F.3, diag=FALSE, na.rm =T)
 #Count of numbers of residuals>.05
@@
 #Total number of off diagonal elements in the data matrix
-totRR = length(reduced.model.5F.2)*(length(reduced.model.5F.2)-1)/2
+totRR=length(reduced.model.5F.2)*(length(reduced.model.5F.2)-1)/2
 
@@
 
-residual.plot <- ggplot(residual.data, aes(x=Residuals)) + geom_histogram(binwidth=.04, col=I("black"),fill="#00A08799") + xlim(-.2,.2)+ ylim(0,250)+apatheme_2 +geom_vline(xintercept = .05)+
-  labs( y="Frequency",title = "(D)")
-
-# ggsave("Figures/residual.plot.png",residual.plot, width = 4, height =4, dpi = 600,bg = "white")
+residual.plot <- ggplot(residual.data, aes(x=Residuals)) + geom_histogram(binwidth=.04, col=I("black"),fill="#00A08799") + xlim(-.2,.2)+ ylim(0,250)+apatheme_2 +geom_vline(xintercept=.05)+
+  labs( y="Frequency",title="(D)")
+
+# ggsave("Figures/residual.plot.png",residual.plot, width=4, height =4, dpi=600,bg="white")
 
@@
 # all_plot <-corplot|(Hull|scree.plot)/residual.plot
-# ggsave("Figures/all_plot.png",all_plot, width = 16, height = 8, dpi = 600, bg = "white")
+# ggsave("Figures/all_plot.png",all_plot, width=16, height=8, dpi=600, bg="white")
 
@@
 
-ggsave("Figures/Figure4.png",all_plot_2, width = 8, height = 4, dpi = 600, bg = "white", units = "in")
+ggsave("Figures/Figure4.png",all_plot_2, width=8, height=4, dpi=600, bg="white", units="in")
 
@@
 
-Prior to conducting the EFA, we have checked the post-hoc sampling adequacy by applying Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy on the EFA sample (n = `r nrow(EFA.data)`) [@kaiserIndexFactorialSimplicity1974] and the quality of the correlation matrix by Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954].
+Prior to conducting the EFA, we have checked the post-hoc sampling adequacy by applying Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy on the EFA sample (n=`r nrow(EFA.data)`) [@kaiserIndexFactorialSimplicity1974] and the quality of the correlation matrix by Bartlett's test of sphericity [@bartlettNoteMultiplyingFactors1954].
 KMO>0.50 would indicate adequate sample size [@hutchesonMultivariateSocialScientist1999] and a significant test of sphericity would indicate satisfactory quality of the correlation matrix .
-Results indicated that we had an adequate sample size (KMO = `r printnum(KMO$MSA)`) and correlation matrix ($\chi^2_{1128}$ = `r apa(bartlet$chisq, 2, T)`, p< 0.001).
+Results indicated that we had an adequate sample size (KMO=`r printnum(KMO$MSA)`) and correlation matrix ($\chi^2_{1128}$=`r apa(bartlet$chisq, 2, T)`, p< 0.001).
 However, `r apa(cor.per, 2,T)`% of the inter-item correlation coefficients were greater than |0.30|, and the inter-item correlation coefficients ranged between `r min.cor` to `r max.cor`.
@@
 Table \@ref(tab:EFATable) displays the factor-loading ($\lambda$) and communality of the items.
-Both factor loadings and commonalities advocate to accept this five-factor solution ( |$\lambda$| = `r apa(min.loadings,2,T)`-`r apa(max.loadings, 2, T)`; commonalities = `r apa(min.com,2,T)`-`r apa(max.com, 2, T)`).
+Both factor loadings and commonalities advocate to accept this five-factor solution ( |$\lambda$|=`r apa(min.loadings,2,T)`-`r apa(max.loadings, 2, T)`; commonalities=`r apa(min.com,2,T)`-`r apa(max.com, 2, T)`).
 These five factors explains `r apa(var1,2,T)`%, `r apa(var2,2,T)`%, `r apa(var3,2,T)`%, `r apa(var4,2,T)`%, `r apa(var5,2,T)`% of the total variance in individual's light exposure related behaviours respectively.
-All factors exhibited excellent to satisfactory reliability (ordinal $\alpha$ = `r apa(F1.alpha,2,T)`, `r apa(F2.alpha,2,T)`, `r apa(F3.alpha,2,T)`, `r apa(F4.alpha,2,T)`, `r apa(F5.alpha,2,T)` respectively).
+All factors exhibited excellent to satisfactory reliability (ordinal $\alpha$=`r apa(F1.alpha,2,T)`, `r apa(F2.alpha,2,T)`, `r apa(F3.alpha,2,T)`, `r apa(F4.alpha,2,T)`, `r apa(F5.alpha,2,T)` respectively).
 The entire inventory also exhibited satisfactory reliability ($\omega_t$=`r apa(omega$omega.tot,2,T)`).
@@
 
-apa_table(efa.tab.ful, caption = "Factor loadings and communality of the retained items in EFA using principal axis extraction method (n=482).", note = "Only loading > .30 is reported.", 
-          font_size = "footnotesize", escape=F,landscape = T,
-           align = c("p{1cm}","p{10cm}", rep("p{1cm}", ncol(efa.tab.ful))))
+apa_table(efa.tab.ful, caption="Factor loadings and communality of the retained items in EFA using principal axis extraction method (n=482).", note="Only loading > .30 is reported.", 
+          font_size="footnotesize", escape=F,landscape=T,
+           align=c("p{1cm}","p{10cm}", rep("p{1cm}", ncol(efa.tab.ful))))
 ```
@@
 img1 <- png::readPNG("Figures/EFAplot.png")
-ggsave("Figures/EFAfull.png",EFAplot.2, width = 6, height =7, dpi = 1200)
+ggsave("Figures/EFAfull.png",EFAplot.2, width=6, height =7, dpi=1200)
 
@@
                                                      -Inf, Inf, -Inf, Inf)+
-  theme(panel.grid.major = element_blank(),
-        panel.grid.minor = element_blank(),
-        panel.background = element_blank())
+  theme(panel.grid.major=element_blank(),
+        panel.grid.minor=element_blank(),
+        panel.background=element_blank())
 
@@
   NULL, residual.plot,
-  labels = c("", "B"),
+  labels=c("", "B"),
   align="h",
-  ncol = 1,
-  label_size = 15,
-  label_fontfamily = "Arial",
-  label_fontface = "plain",
-  label_y = .99
+  ncol=1,
+  label_size=15,
+  label_fontfamily="Arial",
+  label_fontface="plain",
+  label_y=.99
 )
@@
   p1, EFAplot.1,
-  labels = c("A",""),
+  labels=c("A",""),
   align="h",
-  ncol = 2,
-  label_size = 15,
-  label_fontfamily = "Arial",
-  label_fontface = "plain",
-  label_y = .99,
-  label_x = .02
+  ncol=2,
+  label_size=15,
+  label_fontfamily="Arial",
+  label_fontface="plain",
+  label_y=.99,
+  label_x=.02
 )
 
-ggsave("Figures/EFAfull.png",EFAplot.2, width = 6, height =7, dpi = 1200)
+ggsave("Figures/EFAfull.png",EFAplot.2, width=6, height =7, dpi=1200)
 
@@
   dplyr::summarise(
-    nr = n(),
-    mean = mean(value, na.rm = TRUE),
-    med = median(value, na.rm = TRUE),
-    sd = sd(value, na.rm = TRUE),
-    hist_data = list(value),
-    dens_data = list(value),
-    .groups = "drop"
+    nr=n(),
+    mean=mean(value, na.rm=TRUE),
+    med=median(value, na.rm=TRUE),
+    sd=sd(value, na.rm=TRUE),
+    hist_data=list(value),
+    dens_data=list(value),
+    .groups="drop"
   ) %>%
@@
 
-recod_LEBA <- c( "1" = "Never", "2" = "Rarely", "3"= "Sometimes","4" = "Often",
-                 "5" = "Always")
+recod_LEBA <- c( "1"="Never", "2"="Rarely", "3"= "Sometimes","4"="Often",
+                 "5"="Always")
 cfa.LEBA.likert <-  mutate(cfa.LEBA.likert, across(starts_with("item"), ~unname(recod_LEBA[.])))
 
-cfa.LEBA.Factor = as.data.frame(lapply(cfa.LEBA.likert,factor,
-                                   ordered = T))
+cfa.LEBA.Factor=as.data.frame(lapply(cfa.LEBA.likert,factor,
+                                   ordered=T))
 #get the items name
@@
 #Calculate percentage
-cfa.percentage <- kutils::likert(cfa.LEBA.Factor, vlist = cfa.items )
+cfa.percentage <- kutils::likert(cfa.LEBA.Factor, vlist=cfa.items )
 
@@
     hist_data,
-    type = "histogram",
-    line_color = "black", 
-    fill_color = "#00A08799",
-    bw = 1,
-    same_limit = TRUE)%>%
+    type="histogram",
+    line_color="black", 
+    fill_color="#00A08799",
+    bw=1,
+    same_limit=TRUE)%>%
   gtExtras::gt_plt_dist(
     dens_data,
-    type = "density",
-    line_color = "black", 
-    fill_color = "#E64B3599",
-    bw = 0.75,
-    same_limit = TRUE
+    type="density",
+    line_color="black", 
+    fill_color="#E64B3599",
+    bw=0.75,
+    same_limit=TRUE
   )%>%
 # format decimals
-  fmt_number(columns = mean:sd, decimals = 1) %>%
+  fmt_number(columns=mean:sd, decimals=1) %>%
 # header
   tab_header(
-    title = md("**Light Exposure Behaviour Assessment**"),
-    subtitle = md("Summary Descriptives CFA Sample (n=262)")
+    title=md("**Light Exposure Behaviour Assessment**"),
+    subtitle=md("Summary Descriptives CFA Sample (n=262)")
   ) %>% 
   # tab_footnote(
-  #   footnote = md("**Histogram**"),
-  #   locations = cells_column_labels(columns = hist_data)
+  #   footnote=md("**Histogram**"),
+  #   locations=cells_column_labels(columns=hist_data)
   # ) %>%
   # tab_footnote(
-  #   footnote = md("**Density**"),
-  #   locations = cells_column_labels(columns = dens_data)
+  #   footnote=md("**Density**"),
+  #   locations=cells_column_labels(columns=dens_data)
   # ) %>% 
@@
 # tab_spanner(
-#   label = "Items",
-#   columns = Items
+#   label="Items",
+#   columns=Items
 # ) %>%
   tab_spanner(
-    label = "Summary Statistics",
-    columns = nr:sd
+    label="Summary Statistics",
+    columns=nr:sd
   ) %>%
   tab_spanner(
-    label = "Graphics",
-    columns = hist_data:dens_data
+    label="Graphics",
+    columns=hist_data:dens_data
   ) %>% 
   tab_spanner(
-    label = "Response Pattern",
-    columns = Never:Always
+    label="Response Pattern",
+    columns=Never:Always
   ) %>%
@@
 cols_label(
-  Items = (""),
-  nr = ("n"),
-  mean = ("Mean"),
-  med = ("Median "),
-  sd = (("SD")),
-  hist_data = "Histogram",
-  dens_data = "Density"
+  Items=(""),
+  nr=("n"),
+  mean=("Mean"),
+  med=("Median "),
+  sd=(("SD")),
+  hist_data="Histogram",
+  dens_data="Density"
 ) %>%
@@
   Items,
-  palette = "ggthemes::fivethirtyeight") %>%
+  palette="ggthemes::fivethirtyeight") %>%
   tab_row_group(
-      label = md("**F5: Using light in the morning and during daytime**"),
-      rows = c(1,3,12,13,22,23) 
+      label=md("**F5: Using light in the morning and during daytime**"),
+      rows=c(1,3,12,13,22,23) 
         ) %>% 
   tab_row_group(
-      label = md("**F4: Using light before bedtime**"),
-      rows = c(15,16,17,19) 
+      label=md("**F4: Using light before bedtime**"),
+      rows=c(15,16,17,19) 
         ) %>% 
   tab_row_group(
-      label = md("**F3: Using phone and smartwatch in bed**"),
-      rows = c(2,13,14,20,21) 
+      label=md("**F3: Using phone and smartwatch in bed**"),
+      rows=c(2,13,14,20,21) 
         ) %>% 
   tab_row_group(
-      label = md("**F2: Spending time outdoors**"),
-      rows = c(4,5,6,7,8,9) 
+      label=md("**F2: Spending time outdoors**"),
+      rows=c(4,5,6,7,8,9) 
         ) %>% 
   tab_row_group(
-      label = md("**F1: Wearing blue light filters**"),
-      rows = c(10,11,18) 
-        ) %>% 
-  gtsave("Figures/S2_Fig.png",vwidth = 7000)
+      label=md("**F1: Wearing blue light filters**"),
+      rows=c(10,11,18) 
+        ) %>% 
+  gtsave("Figures/S2_Fig.png",vwidth=7000)
 
@@
 CFA.data$Ritem08 <- fct_recode(CFA.data$Ritem08,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
+  "5"="1",
+  "4"="2",
+  "2"="4",
+  "1"="5"
 )
@@
 CFA.data$Ritem37 <- fct_recode(CFA.data$Ritem37,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
+  "5"="1",
+  "4"="2",
+  "2"="4",
+  "1"="5"
 )
@@
 CFA.data$Ritem26 <- fct_recode(CFA.data$Ritem26,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
+  "5"="1",
+  "4"="2",
+  "2"="4",
+  "1"="5"
 )
@@
 
-fit.Cor.1 <- cfa(LB.model.Cor.1, data = CFA.data, ordered = names(CFA.data),estimator = "WLSMV")
+fit.Cor.1 <- cfa(LB.model.Cor.1, data=CFA.data, ordered=names(CFA.data),estimator="WLSMV")
 
 ## Summary of Model 
-cfa.sum.1 <- summary(fit.Cor.1, fit.measures =TRUE,standardized = TRUE,rsq =TRUE)
+cfa.sum.1 <- summary(fit.Cor.1, fit.measures =TRUE,standardized=TRUE,rsq =TRUE)
 
@@
 #This chunk holds codes for modification indices for 1st CFA
-modfit.Cor.one <- modindices(fit.Cor.1, sort. = TRUE) 
+modfit.Cor.one <- modindices(fit.Cor.1, sort.=TRUE) 
 modfit.Cor.one[modfit.Cor.one$mi>3.84,]
@@
 ## Fit the model 
-fit.Cor.2 <- cfa(LB.model.Cor.2, data = CFA.data, ordered = names(CFA.data),estimator = "WLSMV")
-
-rel.k <- semTools::reliability(fit.Cor.2, return.total = T)
+fit.Cor.2 <- cfa(LB.model.Cor.2, data=CFA.data, ordered=names(CFA.data),estimator="WLSMV")
+
+rel.k <- semTools::reliability(fit.Cor.2, return.total=T)
 ## Summary of Model 
-cfa.sum.2 <- summary(fit.Cor.2, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
+cfa.sum.2 <- summary(fit.Cor.2, fit.measures =TRUE,standardized=TRUE, rsq =TRUE)
 
@@
 #This chunk holds codes for modification indices for 2nd CFA
-modfit.Cor.one <- modindices(fit.Cor.2, sort. = TRUE) 
+modfit.Cor.one <- modindices(fit.Cor.2, sort.=TRUE) 
 modfit.Cor.one[modfit.Cor.one$mi>3.84,]
@@
 To investigate the structural validity of the five-factor structure obtained in EFA, we conducted a confirmatory factor analysis (CFA) on the CFA sample.
-The five-factor structure with 25 items showed acceptable fit (Table \@ref(tab:tabCfa)) providing evidence of structural validity (CFI = `r apa(fit.1[5],2,T)`; TLI = `r apa(fit.1[6],2,T)`; RMSEA = `r apa(fit.1[7],2,T)` [`r apa(fit.1[8],2,T)`-`r apa(fit.1[9],2,T)`, 90% CI]).
+The five-factor structure with 25 items showed acceptable fit (Table \@ref(tab:tabCfa)) providing evidence of structural validity (CFI=`r apa(fit.1[5],2,T)`; TLI=`r apa(fit.1[6],2,T)`; RMSEA=`r apa(fit.1[7],2,T)` [`r apa(fit.1[8],2,T)`-`r apa(fit.1[9],2,T)`, 90% CI]).
 Two equity constraints were imposed on item pairs 32-33 (item 32: I dim my mobile phone screen within 1 hour before attempting to fall asleep; item 33: I dim my computer screen within 1 hour before attempting to fall asleep) and 16-17 (item 16: I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day; item 17: I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day).
@@
 Given the similar nature of captured behaviours within each item pair, we accepted the imposed equity constraints.
-Nevertheless, the SRMR value exceeded the guideline recommendation (SRMR = `r apa(fit.1[10],2,T)`).
+Nevertheless, the SRMR value exceeded the guideline recommendation (SRMR=`r apa(fit.1[10],2,T)`).
 In order to improve the model fit, we conducted a post-hoc model modification.
 Firstly, the  modification indices suggested cross-loadings between item 37 and 26 (item 37: I purposely leave a light on in my sleep environment while sleeping; item 26: I turn on my ceiling room light when it is light outside), which were hence discarded.
-Secondly, items 30 and 41 (item 30: I look at my smartwatch within 1 hour before attempting to fall asleep; item 41: I look at my smartwatch when I wake up at night) showed a tendency to co-vary in their error variance (MI = 141.127, p<0.001 ).
-By allowing the latter pair of items (30 $\&$ 41) to co-vary, the model's error variance attained an improved fit (CFI = `r apa(fit.2[5],2,T)`; TLI = `r apa(fit.2[6],2,T)`); RMSEA = `r apa(fit.2[7],2,T)` [`r apa(fit.2[8],2,T)`-`r apa(fit.2[9],2,T)`, 90% CI]; SRMR = `r apa(fit.2[10],2,T) `).
+Secondly, items 30 and 41 (item 30: I look at my smartwatch within 1 hour before attempting to fall asleep; item 41: I look at my smartwatch when I wake up at night) showed a tendency to co-vary in their error variance (MI=141.127, p<0.001 ).
+By allowing the latter pair of items (30 $\&$ 41) to co-vary, the model's error variance attained an improved fit (CFI=`r apa(fit.2[5],2,T)`; TLI=`r apa(fit.2[6],2,T)`); RMSEA=`r apa(fit.2[7],2,T)` [`r apa(fit.2[8],2,T)`-`r apa(fit.2[9],2,T)`, 90% CI]; SRMR=`r apa(fit.2[10],2,T) `).
 
@@
 Internal consistency ordinal $\alpha$ for the five factors of the LEBA were `r apa(rel.k[2,1],2,T)`, `r apa(rel.k[2,2],2,T)`, `r apa(rel.k[2,3],2,T)`, `r apa(rel.k[2,4],2,T)`, `r apa(rel.k[2,5],2,T)`, respectively.
-The reliability of the total inventory was satisfactory ($\omega_t$ = `r apa(rel.k[5,6],2,T)`).
+The reliability of the total inventory was satisfactory ($\omega_t$=`r apa(rel.k[5,6],2,T)`).
 Figure \@ref(fig:figcfa) depicts the obtained CFA structure, while  **Supplementary Figure 2** depicts the data distribution and endorsement pattern of the retained 23 items in our CFA sample.
@@
 
-CFa.matrix <- matrix("NA", nrow =2, ncol = 9)
-colnames(CFa.matrix) = c("Model", "$\\chi^{2}$", "df", "CFI", "TLI", "RMSEA", "RMSEA 90\\% Lower CI", "RMSEA 90\\% Upper CI", "SRMR")
+CFa.matrix <- matrix("NA", nrow =2, ncol=9)
+colnames(CFa.matrix)=c("Model", "$\\chi^{2}$", "df", "CFI", "TLI", "RMSEA", "RMSEA 90\\% Lower CI", "RMSEA 90\\% Upper CI", "SRMR")
 
@@
 Cfa.matrix.selected <- tibble::rowid_to_column(Cfa.matrix.selected,"Model")
-colnames(Cfa.matrix.selected) = c("Model", "$\\chi^{2}$", "df", "CFI", "TLI", "RMSEA", "RMSEA 90\\% Lower CI", "RMSEA 90\\% Upper CI", "SRMR")
+colnames(Cfa.matrix.selected)=c("Model", "$\\chi^{2}$", "df", "CFI", "TLI", "RMSEA", "RMSEA 90\\% Lower CI", "RMSEA 90\\% Upper CI", "SRMR")
 
@@
 ```{r tabCfa}
-apa_table(Cfa.matrix.selected, caption = "Confirmatory Factor Analysis model fit indices of the two model: (a) Model 1: five factor model with 25 items (b) Model 2:  five factor model with 23 items.
-Model 2 attained the best fit.", align = "c", landscape = T, escape=F, note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square.")
+apa_table(Cfa.matrix.selected, caption="Confirmatory Factor Analysis model fit indices of the two model: (a) Model 1: five factor model with 25 items (b) Model 2:  five factor model with 23 items.
+Model 2 attained the best fit.", align="c", landscape=T, escape=F, note="df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square.")
 ```
@@
           #"hide", #(hides coefficeits)
-          #whatLabels = "std",
-          intercepts = F,
+          #whatLabels="std",
+          intercepts=F,
           style ="OpenMx",
-          #residScale = 6,
-          theme = "colorblind",
-          nCharNodes = 0,
+          #residScale=6,
+          theme="colorblind",
+          nCharNodes=0,
           reorder =T,
@@
           layout ="tree",
-          cardinal = T,
+          cardinal=T,
           curvePivot =T,
           sizeMan =8,#items length
-          sizeMan2 = 2,#items
-          sizeLat = 12,#factors
-          thresholds = FALSE,
+          sizeMan2=2,#items
+          sizeLat=12,#factors
+          thresholds=FALSE,
           equalizeManifests =F,
-          fade = FALSE,
-          edge.label.cex = .8,
-          #exoCov = T,
-          centerLevels = T,
+          fade=FALSE,
+          edge.label.cex=.8,
+          #exoCov=T,
+          centerLevels=T,
           #edge.color="black",
@@
           #fixedStyle=6, #Style of arrow (guide item)
-          #freeStyle=1#Style of arrow (other item), #XKCD = TRUE
+          #freeStyle=1#Style of arrow (other item), #XKCD=TRUE
 
@@
 
-```{r figcfa, fig.cap = "Five factor  model of LEBA obtained by confirmatory factor analysis.
+```{r figcfa, fig.cap="Five factor  model of LEBA obtained by confirmatory factor analysis.
 By allowing item pair 41 and 30 to co-vary their error variance our model attained the best fit.",  out.height='100%',out.width='100%', warning=FALSE}
@@
 
-We reported the measurement invariance (MI) analysis on the CFA sample based on native (n = `r mi.count[1,2]`) and non-native English speakers (n = `r mi.count[2,2]`).
+We reported the measurement invariance (MI) analysis on the CFA sample based on native (n=`r mi.count[1,2]`) and non-native English speakers (n=`r mi.count[2,2]`).
 A detailed demographic description are provided in **Supplementary Table 5**.
@@
 # Configural invariance ####
-configural <- cfa(model = LB.model.Cor.2,
-                  data = invariance.data,
-                  group = "English_Speaking",
-                  ordered =   names(CFA.data),
-                  estimator = "WLSMV")
-
-summary(configural, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
+configural <- cfa(model=LB.model.Cor.2,
+                  data=invariance.data,
+                  group="English_Speaking",
+                  ordered=  names(CFA.data),
+                  estimator="WLSMV")
+
+summary(configural, fit.measures =TRUE,standardized=TRUE, rsq =TRUE)
 
@@
 #Metric
-weak <- cfa(model = LB.model.Cor.2,
-                  data = invariance.data,
-                  group = "English_Speaking",
-                  ordered =   names(CFA.data),
-                  estimator = "WLSMV", 
-            group.equal = "loadings")
-
-summary(weak, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
+weak <- cfa(model=LB.model.Cor.2,
+                  data=invariance.data,
+                  group="English_Speaking",
+                  ordered=  names(CFA.data),
+                  estimator="WLSMV", 
+            group.equal="loadings")
+
+summary(weak, fit.measures =TRUE,standardized=TRUE, rsq =TRUE)
 
@@
 #Scaler
-strong <- cfa(model = LB.model.Cor.2,
-                  data = invariance.data,
-                  group = "English_Speaking",
-                  ordered =   names(CFA.data),
-                  estimator = "WLSMV", 
-              group.equal = c("loadings", "intercepts"))
-summary(strong, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
+strong <- cfa(model=LB.model.Cor.2,
+                  data=invariance.data,
+                  group="English_Speaking",
+                  ordered=  names(CFA.data),
+                  estimator="WLSMV", 
+              group.equal=c("loadings", "intercepts"))
+summary(strong, fit.measures =TRUE,standardized=TRUE, rsq =TRUE)
 
@@
 #residual
-strict <- cfa(model = LB.model.Cor.2,
-                  data = invariance.data,
-                  group = "English_Speaking",
-                  ordered =   names(CFA.data),
-                  estimator = "WLSMV",  
-              group.equal = c("loadings", "intercepts", "residuals"))
-
-summary(strict, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
+strict <- cfa(model=LB.model.Cor.2,
+                  data=invariance.data,
+                  group="English_Speaking",
+                  ordered=  names(CFA.data),
+                  estimator="WLSMV",  
+              group.equal=c("loadings", "intercepts", "residuals"))
+
+summary(strict, fit.measures =TRUE,standardized=TRUE, rsq =TRUE)
 residual.fitm <- as.data.frame(fitmeasures (strict,c("gfi", "agfi", "nfi","rfi", "cfi","tli","rmsea", "srmr","aic")))
@@
 #structural
-structural <-cfa(model = LB.model.Cor.2,
-                  data = invariance.data,
-                  group = "English_Speaking",
-                  ordered =   names(CFA.data),
-                  estimator = "WLSMV",  
-                 group.equal = c("loadings", "intercepts", "residuals", "means","lv.variances","lv.covariances"))
-
-summary(structural, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
+structural <-cfa(model=LB.model.Cor.2,
+                  data=invariance.data,
+                  group="English_Speaking",
+                  ordered=  names(CFA.data),
+                  estimator="WLSMV",  
+                 group.equal=c("loadings", "intercepts", "residuals", "means","lv.variances","lv.covariances"))
+
+summary(structural, fit.measures =TRUE,standardized=TRUE, rsq =TRUE)
 fitmeasures (structural,c("gfi", "agfi", "nfi","rfi", "cfi","tli","rmsea", "srmr","aic"))
@@
 
-models <-  list("Configural" = configural, 
-                "Metric" = weak, 
-                "Scalar" = strong, 
-                "Residual" = strict)
+models <-  list("Configural"=configural, 
+                "Metric"=weak, 
+                "Scalar"=strong, 
+                "Residual"=strict)
 
 Invariance.table <- compareLavaan(models,
-              nesting = "Configural > Metric > Scalar > Residual", 
-              fitmeas = c("chisq.scaled", "df",  "cfi.scaled","tli.scaled","rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled" ),
-              scaled = T,
-              chidif = T, digits = 2)
+              nesting="Configural > Metric > Scalar > Residual", 
+              fitmeas=c("chisq.scaled", "df",  "cfi.scaled","tli.scaled","rmsea.scaled", "rmsea.ci.lower.scaled", "rmsea.ci.upper.scaled" ),
+              scaled=T,
+              chidif=T, digits=2)
 
@@
 ```{r InvarianceTab, results='asis'}
-apa_table(Invariance.table, align = "c",  caption = "Measurement Invariance analysis on CFA sample (n = 262) across native and non-native English speakers.", note = "df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square; a = Metric vs Configural; b = Scalar vs Metric; c = Residual vs Scalar; * =  df of model comparison.", landscape = T, font_size = "footnotesize", escape=F )
+apa_table(Invariance.table, align="c",  caption="Measurement Invariance analysis on CFA sample (n=262) across native and non-native English speakers.", note="df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square; a=Metric vs Configural; b=Scalar vs Metric; c=Residual vs Scalar; *= df of model comparison.", landscape=T, font_size="footnotesize", escape=F )
 
@@
 ques <- tokenize("Table_raw/items.txt", 
-                 format = "file",
-                 fileEncoding = NULL,
-                 split = "[[:space:]]",
-                 ign.comp = "-",
-                 heuristics = "abbr",
-                 heur.fix = list(pre = c("\u2019", "'"), suf = c("\u2019", "'")),
-                 abbrev = NULL,
-                 tag = TRUE,
-                 lang = "en",
-                 sentc.end = c(".", "!", "?", ";", ":"),
-                 detect = c(parag = FALSE, hline = FALSE),
-                 clean.raw = NULL,
-                 perl = FALSE,
-                 stopwords = NULL,
-                 stemmer = NULL,
-                 doc_id = NA,
-                 add.desc = "kRp.env")
+                 format="file",
+                 fileEncoding=NULL,
+                 split="[[:space:]]",
+                 ign.comp="-",
+                 heuristics="abbr",
+                 heur.fix=list(pre=c("\u2019", "'"), suf=c("\u2019", "'")),
+                 abbrev=NULL,
+                 tag=TRUE,
+                 lang="en",
+                 sentc.end=c(".", "!", "?", ";", ":"),
+                 detect=c(parag=FALSE, hline=FALSE),
+                 clean.raw=NULL,
+                 perl=FALSE,
+                 stopwords=NULL,
+                 stemmer=NULL,
+                 doc_id=NA,
+                 add.desc="kRp.env")
 
 readability <- readability(ques,
-                           hyphen = NULL,
-                           index = "Flesch.Kincaid",
-                           parameters = list(),
-                           word.lists = list(Bormuth = NULL, Dale.Chall = NULL,                              Harris.Jacobson = NULL, Spache =NULL),
-                           fileEncoding = "UTF-8",
-                           sentc.tag = "sentc",
-                           nonword.class = "nonpunct",
-                           nonword.tag = c(),
-                           quiet = FALSE,
-                           keep.input = NULL,
-                           as.feature = FALSE)
+                           hyphen=NULL,
+                           index="Flesch.Kincaid",
+                           parameters=list(),
+                           word.lists=list(Bormuth=NULL, Dale.Chall=NULL,                              Harris.Jacobson=NULL, Spache =NULL),
+                           fileEncoding="UTF-8",
+                           sentc.tag="sentc",
+                           nonword.class="nonpunct",
+                           nonword.tag=c(),
+                           quiet=FALSE,
+                           keep.input=NULL,
+                           as.feature=FALSE)
 ```
@@
 sem.data$Ritem08 <- fct_recode(sem.data$Ritem08,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
+  "5"="1",
+  "4"="2",
+  "2"="4",
+  "1"="5"
 )
@@
 sem.data$Ritem26 <- fct_recode(sem.data$Ritem26,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
+  "5"="1",
+  "4"="2",
+  "2"="4",
+  "1"="5"
 )
@@
 sem.data$Ritem37 <- fct_recode(sem.data$Ritem37,
-  "5" = "1",
-  "4" = "2",
-  "2" = "4",
-  "1" = "5"
+  "5"="1",
+  "4"="2",
+  "2"="4",
+  "1"="5"
 )
@@
 ## F1 IRT model####
-F1_fit <- mirt(F1, model = 1, itemtype = 'graded', 
-               SE = TRUE, Se.type = 'MHRM',
-               technical = list(NCYCLES = 10000))
+F1_fit <- mirt(F1, model=1, itemtype='graded', 
+               SE=TRUE, Se.type='MHRM',
+               technical=list(NCYCLES=10000))
 
 ## F2 IRT model####
-F2_fit <- mirt(F2, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
+F2_fit <- mirt(F2, model=1, itemtype='graded', SE=TRUE,
+               Se.type='MHRM',technical=list(NCYCLES=10000))
 
 ## F3 IRT model####
-F3_fit <- mirt(F3, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
+F3_fit <- mirt(F3, model=1, itemtype='graded', SE=TRUE,
+               Se.type='MHRM',technical=list(NCYCLES=10000))
 
 ## F4 IRT model####
-F4_fit <- mirt(F4, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
+F4_fit <- mirt(F4, model=1, itemtype='graded', SE=TRUE,
+               Se.type='MHRM',technical=list(NCYCLES=10000))
 
 ## F5 IRT model####
-F5_fit <- mirt(F5, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
+F5_fit <- mirt(F5, model=1, itemtype='graded', SE=TRUE,
+               Se.type='MHRM',technical=list(NCYCLES=10000))
 
@@
 ## F1 Model Parameters####
-F1_params <- coef(F1_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
+F1_params <- coef(F1_fit, IRTpars=TRUE, simplify=TRUE, rawug=FALSE) 
 F1_items <- data.frame(F1_params$items)
-F1l_se <- coef(F1_fit, printSE = TRUE)
+F1l_se <- coef(F1_fit, printSE=TRUE)
 
 ## F2 Model Parameters####
-F2_params <- coef(F2_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
+F2_params <- coef(F2_fit, IRTpars=TRUE, simplify=TRUE, rawug=FALSE) 
 F2_items <- data.frame(F2_params$items)
-F2_se <- coef(F2_fit, printSE = TRUE)
+F2_se <- coef(F2_fit, printSE=TRUE)
 
 ## F3 Model Parameters####
-F3_params <- coef(F3_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
+F3_params <- coef(F3_fit, IRTpars=TRUE, simplify=TRUE, rawug=FALSE) 
 F3_items <- data.frame(F3_params$items)
-F3_se <- coef(F3_fit, printSE = TRUE)
+F3_se <- coef(F3_fit, printSE=TRUE)
 
 ## F4 Model Parameters####
-F4_params <- coef(F4_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
+F4_params <- coef(F4_fit, IRTpars=TRUE, simplify=TRUE, rawug=FALSE) 
 F4_items <- data.frame(F4_params$items)
-F4_se <- coef(F4_fit, printSE = TRUE)
+F4_se <- coef(F4_fit, printSE=TRUE)
 
 ## F5 Model Parameters####
-F5_params <- coef(F5_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
+F5_params <- coef(F5_fit, IRTpars=TRUE, simplify=TRUE, rawug=FALSE) 
 F5_items <- data.frame(F5_params$items)
-F5_se <- coef(F5_fit, printSE = TRUE)
+F5_se <- coef(F5_fit, printSE=TRUE)
 
@@
 #Item fit
-F1.item.fit<- itemfit(F1_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
+F1.item.fit<- itemfit(F1_fit, fit_stats=c("S_X2", "G2","Zh", "infit"),
                                   impute=10)
 
-F2.item.fit<- itemfit(F2_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
+F2.item.fit<- itemfit(F2_fit, fit_stats=c("S_X2", "G2","Zh", "infit"),
                                   impute=10)
-F3.item.fit<- itemfit(F3_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
+F3.item.fit<- itemfit(F3_fit, fit_stats=c("S_X2", "G2","Zh", "infit"),
                                   impute=10)
-F4.item.fit<- itemfit(F4_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
+F4.item.fit<- itemfit(F4_fit, fit_stats=c("S_X2", "G2","Zh", "infit"),
                                   impute=10)
 
-F5.item.fit<- itemfit(F5_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
+F5.item.fit<- itemfit(F5_fit, fit_stats=c("S_X2", "G2","Zh", "infit"),
                                   impute=10)
@@
 nrow(F1.personfit_model_misfits)
-hist(F1.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
+hist(F1.personfit$Zh, xlab="Zh Statistics",main="F1 Person Fit")
+abline(v=-2, lwd=2, lty=2)
 
@@
 nrow(F2.personfit_model_misfits)
-hist(F2.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
+hist(F2.personfit$Zh, xlab="Zh Statistics",main="F1 Person Fit")
+abline(v=-2, lwd=2, lty=2)
 
@@
 nrow(F3.personfit_model_misfits)
-hist(F3.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
+hist(F3.personfit$Zh, xlab="Zh Statistics",main="F1 Person Fit")
+abline(v=-2, lwd=2, lty=2)
 
@@
 nrow(F4.personfit_model_misfits)
-hist(F4.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
+hist(F4.personfit$Zh, xlab="Zh Statistics",main="F1 Person Fit")
+abline(v=-2, lwd=2, lty=2)
 
@@
 nrow(F5.personfit_model_misfits)
-hist(F5.personfit$Zh, xlab = "Zh Statistics",main = "F1 Person Fit")
-abline(v = -2, lwd = 2, lty = 2)
+hist(F5.personfit$Zh, xlab="Zh Statistics",main="F1 Person Fit")
+abline(v=-2, lwd=2, lty=2)
 
@@
 ## F1 Plots ####
-F1_OCC <- plot(F1_fit, type = "trace", facet =T, main = "F1: Wearing blue light filters OCC")
-F1_info <- plot(F1_fit, type = "infoSE", main = "F1: Wearing blue light filters")
-F1_iteminfo <- plot(F1_fit, type = "infotrace", 
-                    facet_items = T, main = "F1: Wearing blue light filters")
+F1_OCC <- plot(F1_fit, type="trace", facet =T, main="F1: Wearing blue light filters OCC")
+F1_info <- plot(F1_fit, type="infoSE", main="F1: Wearing blue light filters")
+F1_iteminfo <- plot(F1_fit, type="infotrace", 
+                    facet_items=T, main="F1: Wearing blue light filters")
 
 ## F2 Plots ####
-F2_OCC <- plot(F2_fit, type = "trace", facet =T, main = "F2: Spending time outdoors OCC")
-F2_info <- plot(F2_fit, type = "infoSE", main = "F2: Spending time outdoors")
-F2_iteminfo <- plot(F2_fit, type = "infotrace", facet_items = T, main = "F2: Spending time outdoors")
+F2_OCC <- plot(F2_fit, type="trace", facet =T, main="F2: Spending time outdoors OCC")
+F2_info <- plot(F2_fit, type="infoSE", main="F2: Spending time outdoors")
+F2_iteminfo <- plot(F2_fit, type="infotrace", facet_items=T, main="F2: Spending time outdoors")
 
 ## F3 Plots ####
-F3_OCC <-plot(F3_fit, type = "trace", facet =T, main = "F3: Using phone and smartwatch in bed OCC")
-F3_info <- plot(F3_fit, type = "infoSE", main = "F3: Using phone and smartwatch in bed")
-F3_iteminfo <- plot(F3_fit, type = "infotrace", 
-                    facet_items = T, main = "F3: Using phone and smartwatch in bed")
+F3_OCC <-plot(F3_fit, type="trace", facet =T, main="F3: Using phone and smartwatch in bed OCC")
+F3_info <- plot(F3_fit, type="infoSE", main="F3: Using phone and smartwatch in bed")
+F3_iteminfo <- plot(F3_fit, type="infotrace", 
+                    facet_items=T, main="F3: Using phone and smartwatch in bed")
 
 ## F4 Plots ####
-F4_OCC <-plot(F4_fit, type = "trace", facet =T, main = "F4: Using light before bedtime OCC")
-F4_info <- plot(F4_fit, type = "infoSE", main = "F4: Using light before bedtime")
-F4_iteminfo <- plot(F4_fit, type = "infotrace", facet_items = T,main = "F4: Using light before bedtime",cex = .8)
+F4_OCC <-plot(F4_fit, type="trace", facet =T, main="F4: Using light before bedtime OCC")
+F4_info <- plot(F4_fit, type="infoSE", main="F4: Using light before bedtime")
+F4_iteminfo <- plot(F4_fit, type="infotrace", facet_items=T,main="F4: Using light before bedtime",cex=.8)
 
 ## F5 Plots ####
-F5_OCC <-plot(F5_fit, type = "trace", facet =T, main = "F5: Using light in the morning and during daytime OCC")
-F5_info <- plot(F5_fit, type = "infoSE", main = "F5: Using light in the morning and during daytime")
-F5_iteminfo <- plot(F5_fit, type = "infotrace", facet_items = T,main = "F5: Using light in the morning and during daytime")
+F5_OCC <-plot(F5_fit, type="trace", facet =T, main="F5: Using light in the morning and during daytime OCC")
+F5_info <- plot(F5_fit, type="infoSE", main="F5: Using light in the morning and during daytime")
+F5_iteminfo <- plot(F5_fit, type="infotrace", facet_items=T,main="F5: Using light in the morning and during daytime")
 
@@
 #conditional reliability
-F1.reliability <- plot(F1_fit, type = 'rxx', theta_lim = c(-6, 6), 
+F1.reliability <- plot(F1_fit, type='rxx', theta_lim=c(-6, 6), 
       main="" )
-F2.reliability <- plot(F2_fit, type = 'rxx', theta_lim = c(-6, 6), 
+F2.reliability <- plot(F2_fit, type='rxx', theta_lim=c(-6, 6), 
       main="" )
-F3.reliability <- plot(F3_fit, type = 'rxx', theta_lim = c(-6, 6), 
+F3.reliability <- plot(F3_fit, type='rxx', theta_lim=c(-6, 6), 
       main="" )
-F4.reliability <- plot(F4_fit, type = 'rxx', theta_lim = c(-6, 6), 
+F4.reliability <- plot(F4_fit, type='rxx', theta_lim=c(-6, 6), 
       main="" )
-F5.reliability <- plot(F5_fit, type = 'rxx', theta_lim = c(-6, 6), 
+F5.reliability <- plot(F5_fit, type='rxx', theta_lim=c(-6, 6), 
       main="" )
@@
 ##Scale characteristic curve
-F1.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
-F2.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
-F3.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
-F4.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
-F5.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
+F1.scale <- plot(F1_fit, type='score', theta_lim=c(-6, 6), main="")
+F2.scale <- plot(F1_fit, type='score', theta_lim=c(-6, 6), main="")
+F3.scale <- plot(F1_fit, type='score', theta_lim=c(-6, 6), main="")
+F4.scale <- plot(F1_fit, type='score', theta_lim=c(-6, 6), main="")
+F5.scale <- plot(F1_fit, type='score', theta_lim=c(-6, 6), main="")
 ```
@@
 
-Theta <- matrix(seq(-6,6, by = .1))
+Theta <- matrix(seq(-6,6, by=.1))
 
@@
 F1.iteminfo.1 <- ggplot(F1.item.info.data , aes(x=Theta, y=F1.item.info.1)) +
-  geom_line()  +apatheme +labs(title = "F1 item16") + geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#E64B3599", alpha=0.4)+xlab(expression(theta)) + 
+  geom_line()  +apatheme +labs(title="F1 item16") + geom_hline(yintercept=.18, colour ="red")+geom_area( fill="#E64B3599", alpha=0.4)+xlab(expression(theta)) + 
   ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 100, 200))
@@
 F1.iteminfo.2 <- ggplot(F1.item.info.data , aes(x=Theta, y=F1.item.info.2)) +
-  geom_line()  +apatheme +labs( title = "F1 item36")+geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#E64B3599", alpha=0.4)+xlab(expression(theta)) + 
+  geom_line()  +apatheme +labs( title="F1 item36")+geom_hline(yintercept=.18, colour ="red")+geom_area( fill="#E64B3599", alpha=0.4)+xlab(expression(theta)) + 
   ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 3, 6))
@@
 F1.iteminfo.3 <- ggplot(F1.item.info.data , aes(x=Theta, y=F1.item.info.3)) +
-  geom_line()  +apatheme +labs(title = "F1 item17")+geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#E64B3599", alpha=0.4)+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 3, 6), limits = c(0,6))
+  geom_line()  +apatheme +labs(title="F1 item17")+geom_hline(yintercept=.18, colour ="red")+geom_area( fill="#E64B3599", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 3, 6), limits=c(0,6))
 
@@
 F2.iteminfo.1 <- ggplot(F2.item.info.data , aes(x=Theta, y=F2.item.info.1)) +
-  geom_line()  +apatheme +labs( title = "F2 item11")+geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#00A08799", alpha=0.4)+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
+  geom_line()  +apatheme +labs( title="F2 item11")+geom_hline(yintercept=.18, colour ="red")+geom_area( fill="#00A08799", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits=c(0,3))
 
@@
   geom_line()  + apatheme +
-  labs( title = "F2 item10")+
-  geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#00A08799", alpha=0.4)+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
+  labs( title="F2 item10")+
+  geom_hline(yintercept=.18, colour ="red")+geom_area( fill="#00A08799", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits=c(0,3))
 
@@
   geom_line()  +apatheme +
-  labs( title = "F2 item12")+
-  geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#00A08799", alpha=0.4)+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
+  labs( title="F2 item12")+
+  geom_hline(yintercept=.18, colour ="red")+geom_area( fill="#00A08799", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits=c(0,3))
 
@@
   geom_line()  +apatheme +
-  labs( title = "F2 item07")+
-  geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#00A08799", alpha=0.4)+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
+  labs( title="F2 item07")+
+  geom_hline(yintercept=.18, colour ="red")+geom_area( fill="#00A08799", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits=c(0,3))
 
@@
   geom_line()  +apatheme +
-  labs( title = "F2 item08")+
-  geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#00A08799", alpha=0.4)+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
+  labs( title="F2 item08")+
+  geom_hline(yintercept=.18, colour ="red")+geom_area( fill="#00A08799", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits=c(0,3))
 
@@
   geom_line()  +apatheme +
-  labs( title = "F2 item09")+
-  geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#00A08799", alpha=0.4)+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
+  labs( title="F2 item09")+
+  geom_hline(yintercept=.18, colour ="red")+geom_area( fill="#00A08799", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits=c(0,3))
 
@@
 F3.iteminfo.1 <- ggplot(F3.item.info.data , aes(x=Theta, y=F3.item.info.1)) +
-  geom_line()  +apatheme +labs( title = "F3 item27")+
- geom_hline(yintercept = .18, colour ="red")+geom_area( fill="3C5488FF", alpha=0.6)+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
+  geom_line()  +apatheme +labs( title="F3 item27")+
+ geom_hline(yintercept=.18, colour ="red")+geom_area( fill="3C5488FF", alpha=0.6)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits=c(0,3))
 
@@
   geom_line()  +apatheme +
-  labs(title = "F3 item03")+
-  geom_hline(yintercept = .18, colour ="red")+geom_area( fill="3C5488FF", alpha=0.6)+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
+  labs(title="F3 item03")+
+  geom_hline(yintercept=.18, colour ="red")+geom_area( fill="3C5488FF", alpha=0.6)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits=c(0,3))
 
@@
   geom_line()  +apatheme +
-  labs(title = "F3 item40")+
-  geom_hline(yintercept = .18, colour ="red")+geom_area( fill="3C5488FF", alpha=0.6)+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
+  labs(title="F3 item40")+
+  geom_hline(yintercept=.18, colour ="red")+geom_area( fill="3C5488FF", alpha=0.6)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits=c(0,3))
 
@@
   geom_line()  +apatheme +
-  labs(title = "F3 item30")+
-  geom_hline(yintercept = .18, colour ="red")+theme(axis.line.x = element_line(color='red'),
-        axis.line.y = element_line(color='red'),
-        panel.border = element_rect(color = "red",
-                                    fill = NA,
-                                    size = 1))+geom_area( fill="3C5488FF", alpha=0.6)+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
+  labs(title="F3 item30")+
+  geom_hline(yintercept=.18, colour ="red")+theme(axis.line.x=element_line(color='red'),
+        axis.line.y=element_line(color='red'),
+        panel.border=element_rect(color="red",
+                                    fill=NA,
+                                    size=1))+geom_area( fill="3C5488FF", alpha=0.6)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits=c(0,3))
 
@@
   geom_line()  +apatheme +
-  labs(title = "F3 item41")+
- geom_hline(yintercept = .18, colour ="red")+theme(axis.line.x = element_line(color='red'),
-        axis.line.y = element_line(color='red'),
-        panel.border = element_rect(color = "red",
-                                    fill = NA,
-                                    size = 1))+geom_area( fill="3C5488FF", alpha=0.6)+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
+  labs(title="F3 item41")+
+ geom_hline(yintercept=.18, colour ="red")+theme(axis.line.x=element_line(color='red'),
+        axis.line.y=element_line(color='red'),
+        panel.border=element_rect(color="red",
+                                    fill=NA,
+                                    size=1))+geom_area( fill="3C5488FF", alpha=0.6)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits=c(0,3))
 
@@
 F4.iteminfo.1 <- ggplot(F4.item.info.data , aes(x=Theta, y=F4.item.info.1)) +
-  geom_line()  +apatheme +labs(title = "F4 item32")+
- geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#4DBBD5FF", alpha=0.4)+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
+  geom_line()  +apatheme +labs(title="F4 item32")+
+ geom_hline(yintercept=.18, colour ="red")+geom_area( fill="#4DBBD5FF", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits=c(0,3))
 
@@
   geom_line()  +apatheme +
-  labs(title = "F4 item35")+
-  geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#4DBBD5FF", alpha=0.4)+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
+  labs(title="F4 item35")+
+  geom_hline(yintercept=.18, colour ="red")+geom_area( fill="#4DBBD5FF", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits=c(0,3))
 
@@
   geom_line()  +apatheme +
-  labs(title = "F4 item38")+
- geom_hline(yintercept = .18, colour ="red")+theme(axis.line.x = element_line(color='red'),
-        axis.line.y = element_line(color='red'),
-        panel.border = element_rect(color = "red",
-                                    fill = NA,
-                                    size = 1))+geom_area( fill="#4DBBD5FF", alpha=0.4)+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits = c(0,3))
+  labs(title="F4 item38")+
+ geom_hline(yintercept=.18, colour ="red")+theme(axis.line.x=element_line(color='red'),
+        axis.line.y=element_line(color='red'),
+        panel.border=element_rect(color="red",
+                                    fill=NA,
+                                    size=1))+geom_area( fill="#4DBBD5FF", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1.5, 3), limits=c(0,3))
 
@@
   geom_line()  +apatheme +
-  labs(title = "F4 item33")+geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#4DBBD5FF", alpha=0.4)+xlab(expression(theta)) + 
+  labs(title="F4 item33")+geom_hline(yintercept=.18, colour ="red")+geom_area( fill="#4DBBD5FF", alpha=0.4)+xlab(expression(theta)) + 
   ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 20, 40))
@@
 F5.iteminfo.1 <- ggplot(F3.item.info.data , aes(x=Theta, y=F5.item.info.1)) +
-  geom_line()  +apatheme +labs(title = "F5 item46")+
- geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#7E6148FF", alpha=0.4)+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1, 2), limits = c(0,2))
+  geom_line()  +apatheme +labs(title="F5 item46")+
+ geom_hline(yintercept=.18, colour ="red")+geom_area( fill="#7E6148FF", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1, 2), limits=c(0,2))
 
@@
   geom_line()  +apatheme +
-  labs(title = "F5 item45")+
- geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#7E6148FF", alpha=0.4)+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1, 2), limits = c(0,2))
+  labs(title="F5 item45")+
+ geom_hline(yintercept=.18, colour ="red")+geom_area( fill="#7E6148FF", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1, 2), limits=c(0,2))
 
@@
   geom_line()  +apatheme +
-  labs(title = "F5 item25")+
-  geom_hline(yintercept = .18, colour ="red")+theme(axis.line.x = element_line(color='red'),
-        axis.line.y = element_line(color='red'),
-        panel.border = element_rect(color = "red",
-                                    fill = NA,
-                                    size = 1))+geom_area( fill="#7E6148FF", alpha=0.4)+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1, 2), limits = c(0,2))
+  labs(title="F5 item25")+
+  geom_hline(yintercept=.18, colour ="red")+theme(axis.line.x=element_line(color='red'),
+        axis.line.y=element_line(color='red'),
+        panel.border=element_rect(color="red",
+                                    fill=NA,
+                                    size=1))+geom_area( fill="#7E6148FF", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1, 2), limits=c(0,2))
 
@@
   geom_line()  +apatheme +
-  labs(title = "F5 item04")+
- geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#7E6148FF", alpha=0.4)+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1, 2), limits = c(0,2))
+  labs(title="F5 item04")+
+ geom_hline(yintercept=.18, colour ="red")+geom_area( fill="#7E6148FF", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+scale_y_continuous(breaks=c(0, 1, 2), limits=c(0,2))
 
@@
   geom_line()  +apatheme +
-  labs( title = "F5 item01")+
- geom_hline(yintercept = .18, colour ="red")+geom_area( fill="#7E6148FF", alpha=0.4)+xlab(expression(theta)) + 
-  ylab(expression(I(theta)))+theme(axis.line.x = element_line(color='red'),
-        axis.line.y = element_line(color='red'),
-        panel.border = element_rect(color = "red",
-                                    fill = NA,
-                                    size = 1))+scale_y_continuous(breaks=c(0, 1, 2), limits = c(0,2))
+  labs( title="F5 item01")+
+ geom_hline(yintercept=.18, colour ="red")+geom_area( fill="#7E6148FF", alpha=0.4)+xlab(expression(theta)) + 
+  ylab(expression(I(theta)))+theme(axis.line.x=element_line(color='red'),
+        axis.line.y=element_line(color='red'),
+        panel.border=element_rect(color="red",
+                                    fill=NA,
+                                    size=1))+scale_y_continuous(breaks=c(0, 1, 2), limits=c(0,2))
 
@@
 F1.plots <- cowplot::plot_grid(F1.iteminfo.1,F1.iteminfo.2, F1.iteminfo.3,NULL, NULL, NULL,
-                     labels = c("A", "B", "C"),
+                     labels=c("A", "B", "C"),
                      align="h",
-                     nrow = 1,
-                     label_size = 60,
-                     label_fontfamily = "Arial",
-                     label_fontface = "plain")
+                     nrow=1,
+                     label_size=60,
+                     label_fontfamily="Arial",
+                     label_fontface="plain")
 
 F2.plots <- cowplot::plot_grid(F2.iteminfo.1,F2.iteminfo.2, F2.iteminfo.3,F2.iteminfo.4,F2.iteminfo.5,F2.iteminfo.6,
-                     labels = c("D", "E", "F", "G", "H", "I"),
+                     labels=c("D", "E", "F", "G", "H", "I"),
                      align="h",
-                     nrow = 1,
-                     label_size = 60,
-                     label_fontfamily = "Arial",
-                     label_fontface = "plain")
+                     nrow=1,
+                     label_size=60,
+                     label_fontfamily="Arial",
+                     label_fontface="plain")
 
 F3.plots <- cowplot::plot_grid(F3.iteminfo.1, F3.iteminfo.2, F3.iteminfo.3, F3.iteminfo.4, F3.iteminfo.5,NULL,
-                     labels = c("J", "K", "L", "M", "N"),
+                     labels=c("J", "K", "L", "M", "N"),
                      align="h",
-                     nrow = 1,
-                     label_size = 60,
-                     label_fontfamily = "Arial",
-                     label_fontface = "plain")
+                     nrow=1,
+                     label_size=60,
+                     label_fontfamily="Arial",
+                     label_fontface="plain")
 
 F4.plots <- cowplot::plot_grid(F4.iteminfo.1, F4.iteminfo.2 ,F4.iteminfo.3 ,F4.iteminfo.4,NULL, NULL,
-                     labels = c("O", "P", "Q", "R"),
+                     labels=c("O", "P", "Q", "R"),
                      align="h",
-                     nrow = 1,
-                     label_size = 60,
-                     label_fontfamily = "Arial",
-                     label_fontface = "plain")
+                     nrow=1,
+                     label_size=60,
+                     label_fontfamily="Arial",
+                     label_fontface="plain")
 
 F5.plots <- cowplot::plot_grid(F5.iteminfo.1,F5.iteminfo.2,F5.iteminfo.3,F5.iteminfo.4,F5.iteminfo.5,NULL,
-                     labels = c("S", "T", "U", "V", "W"),
+                     labels=c("S", "T", "U", "V", "W"),
                      align="h",
-                     nrow = 1,
-                     label_size = 60,
-                     label_fontfamily = "Arial",
-                     label_fontface = "plain")
+                     nrow=1,
+                     label_size=60,
+                     label_fontfamily="Arial",
+                     label_fontface="plain")
 
@@
                      align="v",
-                     nrow = 5,
-                     label_size = 60,
-                     label_fontfamily = "Arial",
-                     label_fontface = "plain")
-
-ggsave("Figures/S3_Fig.png",all.factot.itemplots, width = 18, height = 12, dpi = 600, bg = "white")
+                     nrow=5,
+                     label_size=60,
+                     label_fontfamily="Arial",
+                     label_fontface="plain")
+
+ggsave("Figures/S3_Fig.png",all.factot.itemplots, width=18, height=12, dpi=600, bg="white")
 
@@
 #                                    
-#                      labels = "AUTO",
+#                      labels="AUTO",
 #                      align="v",
-#                      ncol = 6,
-#                      label_size = 12,
-#                      label_fontfamily = "Arial",
-#                      label_fontface = "plain")
+#                      ncol=6,
+#                      label_size=12,
+#                      label_fontfamily="Arial",
+#                      label_fontface="plain")
 # 
 # 
-# # ggsave("Figures/allitemplots.png",allitemplots, width = 18, height = 12, dpi = 600, bg = "white")
+# # ggsave("Figures/allitemplots.png",allitemplots, width=18, height=12, dpi=600, bg="white")
 # 
@@
 #                                            F5.iteminfo.5, 
-#                                             labels = "AUTO",
+#                                             labels="AUTO",
 #                                    align="v",
-#                                    ncol = 5,
-#                                    label_size = 12,
-#                                    label_fontfamily = "Arial",
-#                                    label_fontface = "plain")
+#                                    ncol=5,
+#                                    label_size=12,
+#                                    label_fontfamily="Arial",
+#                                    label_fontface="plain")
 #
 
-# ggsave("Figures/discarded.png",discarded.items.plot, width = 18, height = 4, dpi = 600, bg = "white")
+# ggsave("Figures/discarded.png",discarded.items.plot, width=18, height=4, dpi=600, bg="white")
 
@@
 ```{r IRTparameters, eval=FALSE, include=FALSE, results='asis'}
-apa_table(itemparameters, caption = "Items discrimination and response category difficulty thresholds of 23 items in  LEBA (n = 690)", note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
+apa_table(itemparameters, caption="Items discrimination and response category difficulty thresholds of 23 items in  LEBA (n=690)", note="a=item discrimination parameter; b(1-4)=response category difficulty parameter")
 ```
@@
 ```{r shortIRT, include=FALSE}
-#This chunk holds codes for our SHORT LEBA IRT with item = 18 (2nd IRT)
+#This chunk holds codes for our SHORT LEBA IRT with item=18 (2nd IRT)
 
@@
 #fit model
-F1_fit <- mirt(F1, model = 1, itemtype = 'graded', 
-               SE = TRUE, Se.type = 'MHRM',
-               technical = list(NCYCLES = 10000))
-
-F2_fit.redu <- mirt(F2.redu, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-F3_fit.redu <- mirt(F3.redu, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-F4_fit.redu <- mirt(F4.redu, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
-
-F5_fit.redu <- mirt(F5.redu, model = 1, itemtype = 'graded', SE = TRUE,
-               Se.type = 'MHRM',technical = list(NCYCLES = 10000))
+F1_fit <- mirt(F1, model=1, itemtype='graded', 
+               SE=TRUE, Se.type='MHRM',
+               technical=list(NCYCLES=10000))
+
+F2_fit.redu <- mirt(F2.redu, model=1, itemtype='graded', SE=TRUE,
+               Se.type='MHRM',technical=list(NCYCLES=10000))
+
+F3_fit.redu <- mirt(F3.redu, model=1, itemtype='graded', SE=TRUE,
+               Se.type='MHRM',technical=list(NCYCLES=10000))
+
+F4_fit.redu <- mirt(F4.redu, model=1, itemtype='graded', SE=TRUE,
+               Se.type='MHRM',technical=list(NCYCLES=10000))
+
+F5_fit.redu <- mirt(F5.redu, model=1, itemtype='graded', SE=TRUE,
+               Se.type='MHRM',technical=list(NCYCLES=10000))
 
 #Item fit
-F1.item.fit<- itemfit(F1_fit, fit_stats = c("S_X2", "G2","Zh", "infit"),
+F1.item.fit<- itemfit(F1_fit, fit_stats=c("S_X2", "G2","Zh", "infit"),
                                   impute=10)
 
-F2.item.fit<- itemfit(F2_fit.redu, fit_stats = c("S_X2", "G2","Zh", "infit"),
+F2.item.fit<- itemfit(F2_fit.redu, fit_stats=c("S_X2", "G2","Zh", "infit"),
                                   impute=10)
-F3.item.fit<- itemfit(F3_fit.redu, fit_stats = c("S_X2", "G2","Zh", "infit"),
+F3.item.fit<- itemfit(F3_fit.redu, fit_stats=c("S_X2", "G2","Zh", "infit"),
                                   impute=10)
-F4.item.fit<- itemfit(F4_fit.redu, fit_stats = c("S_X2", "G2","Zh", "infit"),
+F4.item.fit<- itemfit(F4_fit.redu, fit_stats=c("S_X2", "G2","Zh", "infit"),
                                   impute=10)
 
-F5.item.fit<- itemfit(F5_fit.redu, fit_stats = c("S_X2", "G2","Zh", "infit"),
+F5.item.fit<- itemfit(F5_fit.redu, fit_stats=c("S_X2", "G2","Zh", "infit"),
                                   impute=10)
@@
 #Item fit
-F1.item.fit<- itemfit(F1_fit, fit_stats = c("S_X2"),
+F1.item.fit<- itemfit(F1_fit, fit_stats=c("S_X2"),
                                   impute=10)
 
-F2.item.fit<- itemfit(F2_fit.redu, fit_stats = c("S_X2"),
+F2.item.fit<- itemfit(F2_fit.redu, fit_stats=c("S_X2"),
                                   impute=10)
-F3.item.fit<- itemfit(F3_fit.redu, fit_stats = c("S_X2"),
+F3.item.fit<- itemfit(F3_fit.redu, fit_stats=c("S_X2"),
                                   impute=10)
-F4.item.fit<- itemfit(F4_fit.redu, fit_stats = c("S_X2"),
+F4.item.fit<- itemfit(F4_fit.redu, fit_stats=c("S_X2"),
                                   impute=10)
 
-F5.item.fit<- itemfit(F5_fit.redu, fit_stats = c("S_X2"),
+F5.item.fit<- itemfit(F5_fit.redu, fit_stats=c("S_X2"),
                                   impute=10)
@@
 
-F1.person <- ggplot(F1.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5,col=I("black"),fill="#00A08799")+geom_vline(xintercept = -2)+
-  labs( y="Number of Participants", x = "Zh Statistics: F1")+apatheme+ ylim(0,600) + xlim(-4,2)
+F1.person <- ggplot(F1.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5,col=I("black"),fill="#00A08799")+geom_vline(xintercept=-2)+
+  labs( y="Number of Participants", x="Zh Statistics: F1")+apatheme+ ylim(0,600) + xlim(-4,2)
 
@@
 F2.person <- ggplot(F2.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill="#00A08799")+
-  scale_x_continuous(limits = c(-5, 1))+geom_vline(xintercept = -2)+
-  labs( y="Number of Participants", x = "Zh Statistics: F2")+apatheme+ylim(0,600) + xlim(-4,2)
+  scale_x_continuous(limits=c(-5, 1))+geom_vline(xintercept=-2)+
+  labs( y="Number of Participants", x="Zh Statistics: F2")+apatheme+ylim(0,600) + xlim(-4,2)
 
@@
 
-F3.person <- ggplot(F3.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill="#00A08799")+geom_vline(xintercept = -2)+
-  labs( y="Number of Participants", x = "Zh Statistics: F3")+apatheme+ylim(0,600) + xlim(-4,2)
+F3.person <- ggplot(F3.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill="#00A08799")+geom_vline(xintercept=-2)+
+  labs( y="Number of Participants", x="Zh Statistics: F3")+apatheme+ylim(0,600) + xlim(-4,2)
 
@@
 
-F4.person <- ggplot(F4.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill="#00A08799")+geom_vline(xintercept = -2)+
-  labs( y="Number of Participants", x = "Zh Statistics: F4")+apatheme+ylim(0,600) + xlim(-4,2)
+F4.person <- ggplot(F4.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill="#00A08799")+geom_vline(xintercept=-2)+
+  labs( y="Number of Participants", x="Zh Statistics: F4")+apatheme+ylim(0,600) + xlim(-4,2)
 
@@
 
-F5.person <- ggplot(F5.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill="#00A08799")+geom_vline(xintercept = -2)+
-  labs( y="Number of Participants", x = "Zh Statistics: F5")+apatheme+ylim(0,600) + xlim(-4,2)
+F5.person <- ggplot(F5.personfit, aes(x=Zh)) + geom_histogram(binwidth=.5, col=I("black"),fill="#00A08799")+geom_vline(xintercept=-2)+
+  labs( y="Number of Participants", x="Zh Statistics: F5")+apatheme+ylim(0,600) + xlim(-4,2)
 
@@
 ## F1 Model Parameters####
-F1_params <- coef(F1_fit, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
+F1_params <- coef(F1_fit, IRTpars=TRUE, simplify=TRUE, rawug=FALSE) 
 F1_items.redu <- data.frame(F1_params$items)
-F1l_se <- coef(F1_fit, printSE = TRUE)
+F1l_se <- coef(F1_fit, printSE=TRUE)
 
 ## F2 Model Parameters####
-F2_params <- coef(F2_fit.redu, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
+F2_params <- coef(F2_fit.redu, IRTpars=TRUE, simplify=TRUE, rawug=FALSE) 
 F2_items.redu <- data.frame(F2_params$items)
-F2_se <- coef(F2_fit.redu, printSE = TRUE)
+F2_se <- coef(F2_fit.redu, printSE=TRUE)
 
 ## F3 Model Parameters####
-F3_params <- coef(F3_fit.redu, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
+F3_params <- coef(F3_fit.redu, IRTpars=TRUE, simplify=TRUE, rawug=FALSE) 
 F3_items.redu <- data.frame(F3_params$items)
-F3_se <- coef(F3_fit.redu, printSE = TRUE)
+F3_se <- coef(F3_fit.redu, printSE=TRUE)
 
 ## F4 Model Parameters####
-F4_params <- coef(F4_fit.redu, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
+F4_params <- coef(F4_fit.redu, IRTpars=TRUE, simplify=TRUE, rawug=FALSE) 
 F4_items.redu <- data.frame(F4_params$items)
-F4_se <- coef(F4_fit.redu, printSE = TRUE)
+F4_se <- coef(F4_fit.redu, printSE=TRUE)
 
 ## F5 Model Parameters####
-F5_params <- coef(F5_fit.redu, IRTpars = TRUE, simplify = TRUE, rawug = FALSE) 
+F5_params <- coef(F5_fit.redu, IRTpars=TRUE, simplify=TRUE, rawug=FALSE) 
 F5_items.redu<- data.frame(F5_params$items)
-F5_se.redu <- coef(F5_fit.redu, printSE = TRUE)
+F5_se.redu <- coef(F5_fit.redu, printSE=TRUE)
 
@@
 
-#F1.reliability <- plot(F1_fit, type = 'rxx', theta_lim = c(-6, 6),  main="" )
-#F2.reliability <- plot(F2_fit.redu, type = 'rxx', theta_lim = c(-6, 6),  main="" )
-#F3.reliability <- plot(F3_fit.redu, type = 'rxx', theta_lim = c(-6, 6), main="" )
-#F4.reliability <- plot(F4_fit.redu, type = 'rxx', theta_lim = c(-6, 6), main="" )
-#F5.reliability <- plot(F5_fit, type = 'rxx', theta_lim = c(-6, 6), main="" )
+#F1.reliability <- plot(F1_fit, type='rxx', theta_lim=c(-6, 6),  main="" )
+#F2.reliability <- plot(F2_fit.redu, type='rxx', theta_lim=c(-6, 6),  main="" )
+#F3.reliability <- plot(F3_fit.redu, type='rxx', theta_lim=c(-6, 6), main="" )
+#F4.reliability <- plot(F4_fit.redu, type='rxx', theta_lim=c(-6, 6), main="" )
+#F5.reliability <- plot(F5_fit, type='rxx', theta_lim=c(-6, 6), main="" )
 
@@
 
-#F1_test.info <- plot(F1_fit, type = "infoSE", main = "F1: Wearing blue light filters")
-
-#F2_test.info.redu <- plot(F2_fit.redu, type = "infoSE", main = "F2: Spending time outdoors")
-
-#F3_test.info.redu <- plot(F3_fit.redu, type = "infoSE", main = "F3: Using phone and smartwatch in bed")
-
-#F4_test.info.redu <- plot(F4_fit.redu, type = "infoSE", main = "F4: Using light before bedtime")
-
-#F5_test.info <- plot(F5_fit.redu, type = "infoSE", main = "F5: Using light in the morning and during daytime")
+#F1_test.info <- plot(F1_fit, type="infoSE", main="F1: Wearing blue light filters")
+
+#F2_test.info.redu <- plot(F2_fit.redu, type="infoSE", main="F2: Spending time outdoors")
+
+#F3_test.info.redu <- plot(F3_fit.redu, type="infoSE", main="F3: Using phone and smartwatch in bed")
+
+#F4_test.info.redu <- plot(F4_fit.redu, type="infoSE", main="F4: Using light before bedtime")
+
+#F5_test.info <- plot(F5_fit.redu, type="infoSE", main="F5: Using light in the morning and during daytime")
 
 ##Scale characteristic curve
-#F1.scale <- plot(F1_fit, type = 'score', theta_lim = c(-6, 6), main = "")
-#F2.scale <- plot(F2_fit.redu, type = 'score', theta_lim = c(-6, 6), main = "")
-#F3.scale <- plot(F3_fit.redu, type = 'score', theta_lim = c(-6, 6), main = "")
-#F4.scale <- plot(F4_fit.redu, type = 'score', theta_lim = c(-6, 6), main = "")
-#F5.scale <- plot(F5_fit.redu, type = 'score', theta_lim = c(-6, 6), main = "")
+#F1.scale <- plot(F1_fit, type='score', theta_lim=c(-6, 6), main="")
+#F2.scale <- plot(F2_fit.redu, type='score', theta_lim=c(-6, 6), main="")
+#F3.scale <- plot(F3_fit.redu, type='score', theta_lim=c(-6, 6), main="")
+#F4.scale <- plot(F4_fit.redu, type='score', theta_lim=c(-6, 6), main="")
+#F5.scale <- plot(F5_fit.redu, type='score', theta_lim=c(-6, 6), main="")
 
@@
 
-TIC <- ggplot(Test.data.2,aes(Theta,value))+geom_line(size = 1)+apatheme+
-  ggtitle("Test Information Plot")+theme(legend.position = "none")+
-  labs(y = "Test Information")+ geom_path()+facet_wrap(~variable,scales = "free") +theme(strip.text.x = element_text(size = 15))+geom_area()+ scale_color_npg()+aes(fill = as.factor(variable))
+TIC <- ggplot(Test.data.2,aes(Theta,value))+geom_line(size=1)+apatheme+
+  ggtitle("Test Information Plot")+theme(legend.position="none")+
+  labs(y="Test Information")+ geom_path()+facet_wrap(~variable,scales="free") +theme(strip.text.x=element_text(size=15))+geom_area()+ scale_color_npg()+aes(fill=as.factor(variable))
 
@@
   geom_line()+apatheme_3+
-  labs(y="Test Information", title = "F1: Wearing blue light filters")+geom_area()+theme(legend.position = "none")+
-  aes(fill =  "#E64B3599")+
+  labs(y="Test Information", title="F1: Wearing blue light filters")+geom_area()+theme(legend.position="none")+
+  aes(fill= "#E64B3599")+
      scale_fill_identity()+xlab(expression(theta)) + 
@@
   geom_line()+apatheme_3+
-  labs(y="Test Information", title = "F2: Spending time outdoors")+ylim(0,8)+
-  geom_area()+aes(fill =  "#4DBBD599")+theme(legend.position = "none")+
+  labs(y="Test Information", title="F2: Spending time outdoors")+ylim(0,8)+
+  geom_area()+aes(fill= "#4DBBD599")+theme(legend.position="none")+
      scale_fill_identity()+xlab(expression(theta)) + 
@@
   geom_line()+apatheme_3+
-  labs(y="Test Information", title = "F3: Using phone and smartwatch in bed")+ylim(0,8)+
-  geom_area()+aes(fill =  "#00A08799")+theme(legend.position = "none")+
+  labs(y="Test Information", title="F3: Using phone and smartwatch in bed")+ylim(0,8)+
+  geom_area()+aes(fill= "#00A08799")+theme(legend.position="none")+
      scale_fill_identity()+xlab(expression(theta)) + 
@@
   geom_line()+apatheme_3+
-  labs(y="Test Information", title = "F4: Using light before bedtime")+
-  geom_area()+aes(fill =  "#3C548899")+theme(legend.position = "none")+
+  labs(y="Test Information", title="F4: Using light before bedtime")+
+  geom_area()+aes(fill= "#3C548899")+theme(legend.position="none")+
      scale_fill_identity()+xlab(expression(theta)) + 
@@
   geom_line()+apatheme_3+
-  labs(y="Test Information", title = "F5:Using light in the morning and during daytime") +ylim(0,8)+geom_area()+aes(fill =  "#B09C8599")+theme(legend.position = "none")+
+  labs(y="Test Information", title="F5:Using light in the morning and during daytime") +ylim(0,8)+geom_area()+aes(fill= "#B09C8599")+theme(legend.position="none")+
 scale_fill_identity()+xlab(expression(theta)) + 
@@
                                    F4.tic,F5.tic,
-                   labels = c("(A)", "(B)", "(C)", "(D)", "(E)"),
+                   labels=c("(A)", "(B)", "(C)", "(D)", "(E)"),
                      align="v",
-                     ncol = 3,
-                     label_size = 90,
-                     label_fontfamily = "Arial",
-                     label_fontface = "plain")
-ggsave("Figures/Figure6.png",TIC.plot, width = 18, height = 12, dpi = 600, bg = "white")
+                     ncol=3,
+                     label_size=90,
+                     label_fontfamily="Arial",
+                     label_fontface="plain")
+ggsave("Figures/Figure6.png",TIC.plot, width=18, height=12, dpi=600, bg="white")
 
@@
 ```{r itemfittab, eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, results='asis'}
-apa_table(IRT.details , caption ="Item discrimination, response category difficulty thrsholds and fit statistics of the 18 items in short LEBA (n = 690)",note = "a = item discrimination parameter; b(1-4) = response category difficulty parameter")
+apa_table(IRT.details , caption ="Item discrimination, response category difficulty thrsholds and fit statistics of the 18 items in short LEBA (n=690)",note="a=item discrimination parameter; b(1-4)=response category difficulty parameter")
 ```
@@
 personfit <- cowplot::plot_grid(F1.person, F2.person,F3.person,F4.person,F5.person, 
-          labels = "AUTO", label_size = 12,align = "v", ncol =2,
-                       label_fontfamily = "Arial",
-                     label_fontface = "plain")
-
-ggsave("Figures/S4_Fig.png",personfit , width = 10, height = 12, dpi = 600, bg = "white")
+          labels="AUTO", label_size=12,align="v", ncol =2,
+                       label_fontfamily="Arial",
+                     label_fontface="plain")
+
+ggsave("Figures/S4_Fig.png",personfit , width=10, height=12, dpi=600, bg="white")
 
@@
   rowwise() %>% 
-  mutate(F1.Total = sum(item16, item36,  item17))
+  mutate(F1.Total=sum(item16, item36,  item17))
 
@@
   rowwise() %>% 
-  mutate(F2.Total = sum(item11,  item10 , item12, item07, Ritem08, item09))
+  mutate(F2.Total=sum(item11,  item10 , item12, item07, Ritem08, item09))
 
@@
   rowwise() %>% 
-  mutate(F3.Total = sum(item27, item03,  item40))
+  mutate(F3.Total=sum(item27, item03,  item40))
 
@@
   rowwise() %>% 
-  mutate(F4.Total = sum(item32, item35,  item33))
+  mutate(F4.Total=sum(item32, item35,  item33))
 
@@
   rowwise() %>% 
-  mutate(F5.Total = sum(item46, item45, item25))
-
-F1.estimation <- as.vector(fscores(F1_fit, method = "EAP",
-                                           full.scores = TRUE, 
-                                           full.scores.SE = F))
-
-F2.estimation <- as.vector(fscores(F2_fit.redu, method = "EAP",
-                                           full.scores = TRUE, 
-                                           full.scores.SE = F))
-
-F3.estimation <- as.vector(fscores(F3_fit.redu, method = "EAP",
-                                           full.scores = TRUE, 
-                                           full.scores.SE = F))
-
-F4.estimation <- as.vector(fscores(F4_fit.redu, method = "EAP",
-                                           full.scores = TRUE, 
-                                           full.scores.SE = F))
-
-F5.estimation <- as.vector(fscores(F5_fit, method = "EAP",
-                                           full.scores = TRUE, 
-                                           full.scores.SE = F))
-
-Ability.F1 <- data.frame(Rawscore = LEBA.Total$F1.Total,
-                      Theta =  F1.estimation)
-
-Ability.F2 <- data.frame(Rawscore = LEBA.Total$F2.Total,
-                      Theta =  F2.estimation)
-
-Ability.F3 <- data.frame(Rawscore = LEBA.Total$F3.Total,
-                      Theta =  F3.estimation)
-
-Ability.F4 <- data.frame(Rawscore = LEBA.Total$F3.Total,
-                      Theta =  F3.estimation)
-
-Ability.F5 <- data.frame(Rawscore = LEBA.Total$F3.Total,
-                      Theta =  F3.estimation)
+  mutate(F5.Total=sum(item46, item45, item25))
+
+F1.estimation <- as.vector(fscores(F1_fit, method="EAP",
+                                           full.scores=TRUE, 
+                                           full.scores.SE=F))
+
+F2.estimation <- as.vector(fscores(F2_fit.redu, method="EAP",
+                                           full.scores=TRUE, 
+                                           full.scores.SE=F))
+
+F3.estimation <- as.vector(fscores(F3_fit.redu, method="EAP",
+                                           full.scores=TRUE, 
+                                           full.scores.SE=F))
+
+F4.estimation <- as.vector(fscores(F4_fit.redu, method="EAP",
+                                           full.scores=TRUE, 
+                                           full.scores.SE=F))
+
+F5.estimation <- as.vector(fscores(F5_fit, method="EAP",
+                                           full.scores=TRUE, 
+                                           full.scores.SE=F))
+
+Ability.F1 <- data.frame(Rawscore=LEBA.Total$F1.Total,
+                      Theta= F1.estimation)
+
+Ability.F2 <- data.frame(Rawscore=LEBA.Total$F2.Total,
+                      Theta= F2.estimation)
+
+Ability.F3 <- data.frame(Rawscore=LEBA.Total$F3.Total,
+                      Theta= F3.estimation)
+
+Ability.F4 <- data.frame(Rawscore=LEBA.Total$F3.Total,
+                      Theta= F3.estimation)
+
+Ability.F5 <- data.frame(Rawscore=LEBA.Total$F3.Total,
+                      Theta= F3.estimation)
 
@@
   geom_point() +
-  geom_smooth(method='lm', se =TRUE, formula= y~x,colour = "red")+
+  geom_smooth(method='lm', se =TRUE, formula= y~x,colour="red")+
   xlim(-2,2) +
@@
 
-theta.correlation.matrix <- matrix("NA", nrow =1, ncol = 5)
+theta.correlation.matrix <- matrix("NA", nrow =1, ncol=5)
 
@@
 
-itemlevelcolors <- matrix(rep(brewer.pal(4, "Set1"), 18), byrow = TRUE, ncol = 4)
+itemlevelcolors <- matrix(rep(brewer.pal(4, "Set1"), 18), byrow=TRUE, ncol=4)
 
@@
 #This chunk holds codes for saving the wright-map
-jpeg("Figures/wm.png", width = 800, height = 750)
+jpeg("Figures/wm.png", width=800, height=750)
 WrightMap::wrightMap(estimation, threshold, 
-          item.prop = 0.65,
-
-          main.title = "LEBA",
-          dim.names = c("F1", "F2", "F3", "F4", "F5"),
-          thr.sym.col.fg = itemlevelcolors,
-          thr.sym.col.bg = itemlevelcolors,
-          vertLines = TRUE,
-          show.thr.lab = T,
-          dim.color = brewer.pal(5, "Set3"))
+          item.prop=0.65,
+
+          main.title="LEBA",
+          dim.names=c("F1", "F2", "F3", "F4", "F5"),
+          thr.sym.col.fg=itemlevelcolors,
+          thr.sym.col.bg=itemlevelcolors,
+          vertLines=TRUE,
+          show.thr.lab=T,
+          dim.color=brewer.pal(5, "Set3"))
 dev.off()
@@
 ```{r IRTscoreCor, eval=FALSE, include=FALSE, results='asis'}
-apa_table (theta.correlation.matrix, caption = "correlation coefficents of obtained scores and estimated latent trait for each factots", note = "* p < 0.05; ** p < 0.01; *** p < 0.001"  )
+apa_table (theta.correlation.matrix, caption="correlation coefficents of obtained scores and estimated latent trait for each factots", note="* p < 0.05; ** p < 0.01; *** p < 0.001"  )
 ```
@@
 # Discussion
-Today, in most industrialized countries, the vast majority of time is spent in built environments [@Klepeis.2001], where photic exposure patterns are determined not only by the solar cycle but by electrical light sources as well.
-As a consequence, light received may vary considerably, in terms of timing, intensity and spectrum, all of which are subject to the further influence of individual behaviours.
-[reviewed in @Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020; @vetter2022review].
-Thus, there is a clear need for guidance [@Brown.2022] and assessment regarding healthy light exposure and consequentially healthy light-related behaviour.
-
-In reviewing the literature, we found that a handful of previously introduced instruments assess aspects of light exposure by self-report (see **Supplementary Table 1**).
-Few studies to date have attempted to assess light exposure by self-report.
-That body of research becomes even smaller when limiting it to those focusing on <behaviours> that influence photic exposure patterns, and typically these home in only on particular behaviours of interest, such as estimates of time spent outside [@roenneberg2003life] or preferences for specific lighting situations [@bossini2006sensibilita].
-To our knowledge, there is no questionnaire in existence that captures behaviours that modify light exposure across different scenarios in a comprehensive way.
-We have developed two versions of a self-report inventory-LEBA, that can capture light exposure-related behaviours in multiple dimensions.
-
+
+We have developed two versions of a self-report inventory, LEBA, that can capture light exposure-related behaviours in multiple dimensions.
 The 48 generated items were applied in a large-scale, geographically unconstrained, cross-sectional study, yielding `r nrow(data)` completed surveys.
@@
 The exploratory factor analysis revealed a highly interpretable five-factor solution ("Wearing blue light filters", "Spending time outdoors", "Using phone and smartwatch in bed", "Using light before bedtime", and "Using light in the morning and during daytime") with 25 items.
-Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five-factor structure we obtained in our EFA, thus providing evidence for structural validity.(CFI = `r apa(fit.2[5],2,T)`; TLI = `r apa(fit.2[6],2,T)`; RMSEA = `r apa(fit.2[7],2,T)`).
+Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five-factor structure we obtained in our EFA, thus providing evidence for structural validity.(CFI=`r apa(fit.2[5],2,T)`; TLI=`r apa(fit.2[6],2,T)`; RMSEA=`r apa(fit.2[7],2,T)`).
 In this model, we discarded two more items (item 26 $\&$ 37 ) for possible cross-loadings.
@@
 However, at the early developmental stage, a value of .50 is considered acceptable [@dall2010developmental; @field2013discovering; @Nunnally1978].
-Thus, we confer, the internal consistency coefficients ordinal alpha for the five factors and the total inventory were satisfactory (Ordinal alpha ranged between `r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$ = `r apa(rel.k[5,6],2,T)`).
+Thus, we confer, the internal consistency coefficients ordinal alpha for the five factors and the total inventory were satisfactory (Ordinal alpha ranged between `r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$=`r apa(rel.k[5,6],2,T)`).
 
@@
 To avoid these situations we  derived a short version of the LEBA (18 items) using IRT analysis.
-We fitted a graded response model to the combined EFA and CFA sample (n = `r nrow(data)`) and discarded five items (1, 25, 30, 38, & 41) with relatively flat item information curve [I($\theta$) <.20].
+We fitted a graded response model to the combined EFA and CFA sample (n=`r nrow(data)`) and discarded five items (1, 25, 30, 38, & 41) with relatively flat item information curve [I($\theta$) <.20].
 The resulting test information curves suggest that the short-LEBA is a psychometrically sound measure with adequate coverage of underlying traits and can be applied to capture the frequency of different light exposure related behaviours reliably.
@@
 
-During the post-hoc model modification, as part of the confirmatory factor analysis, we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings, as demonstrated in the data.
-However, two additional items covaried in their error variance.
-By allowing the latter pair (30 $\&$ 41) to covary, the model attained an improved fit ( **Figure 5**).
-A possible explanation for the covariation is that many respondents might not have used a smartwatch at all, resulting in similar response patterns between these two items.
-Thus, though rather unconventional, we decided to accept this post-hoc modification to our five-factor model.
-
 The habitual patterns queried in the developed inventory might not exhaustively represent all relevant light-exposure-related behaviours.
@@
 By this route, one could study how the (subjectively measured) light exposure-related behavioural patterns translate into (objectively measured) received light exposure.
-
-Additionally, developing daily recall scales of light-related behaviour could provide a more detailed behavioural assessment to supplement the LEBA's broader (four-week) measurement approach.
-Comparing the LEBA scores to 24-hour recall scores could provide helpful information about how light exposure-related behaviour assessment is related between different time perspectives.
-
-Moreover, light-exposure-related behaviour might depend on the respondents' profession, geographical location, housing conditions, socio-economic status, or other contextual factors.
-As the current data is limited to our international online survey context, future research should apply the LEBA across more variable populations and contexts.
-On the other hand, this will require the development of cross-cultural adaptations and translations into other languages of the LEBA, which should be targeted in prospective studies.
-
-Finally, in the future, the use of the LEBA instrument need not remain restricted to gathering information in cross-sectinal quantitative studies.
-The instrument can also be used for individual behavioural profiling.
-For instance, the LEBA could be applied in a clinical context as part of Cognitive Behavioural Therapy for Insomnia (CBT-I).
-More specifically, it could be used to supplement the sleep hygiene aspects of CBT-I, as receiving light exposure at different times has implications for sleep [@santhi_applications_2020].
-This match was also evident in the semantic relationship between the LEBA and two scales capturing sleep problems (CIDI: Insomnia; @robins1988composite & SDSC; @bruni1996sleep) found in the semantic similarity analysis.
-However, before applying the LEBA in such contexts in the future, more work is certainly needed to understand light exposure-related behaviour and its’ relationship to relevant health outcomes measured subjectively and objectively.
 
@@
 The item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum.
-Here, we reported the item difficulty and discrimination parameter and categorized the items based on their item discrimination index: (i) none = 0; (ii) very low = 0.01 to 0.34; (iii) low = 0.35 to 0.64; (iv) moderate = 0.65 to 1.34 ; (v) high = 1.35 to 1.69; (vi) very high \>1.70 [@bakerBasicsItemResponse2017].
+Here, we reported the item difficulty and discrimination parameter and categorized the items based on their item discrimination index: (i) none=0; (ii) very low=0.01 to 0.34; (iii) low=0.35 to 0.64; (iv) moderate=0.65 to 1.34 ; (v) high=1.35 to 1.69; (vi) very high \>1.70 [@bakerBasicsItemResponse2017].
 We discarded the items with a relatively flat item information curve (information \<.2) to derive the short form of LEBA.
@@
 ```{r FlowchartFig, echo=FALSE, fig.align='center', fig.cap='Flow chart of the LEBA (long and short form) development and evaluation. ', out.height='50%', out.width='50%'}
-knitr::include_graphics('Figures/Figure1.png', dpi = 600 )
+knitr::include_graphics('Figures/Figure1.png', dpi=600 )
 ```

### 2023-02-14 manuscript.Rmd
Recompiled manuscript

@@
 Furthermore, building on earlier attempts [e.g.
-@hubalek_ambulant_2006], there was a recent push toward the development and use of portable light loggers to improve ambulant light assessment and gain more insight into the NIF effects of light on human health in field conditions.
+@hubalek_ambulant_2006], there was a recent push toward the development and use of portable light loggers to improve ambulant light assessment and gain more insight into the NIF effects of light on human health in field conditions [@hartmeyer2022towards; @spitschan2022verification].
 Attached to different body parts (e.g., wrist; head, at eye level; chest), these light loggers allow for the objective measurement of individual photic exposure patterns under real-world conditions and thus are valuable tools for field studies.
@@
 
-Figure \@ref(fig:FlowchartFig) summarises the steps we followed while developing the LEBA. We conducted all analyses with the statistical software environment R [@R-base]. 
+Figure \@ref(fig:FlowchartFig) summarises the steps we followed while developing the LEBA. We conducted all analyses with the statistical software environment R. 
 **Firstly**, we set an item pool of 48 items with a six-point Likert-type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial inventory.
@@
 
-**Thirdly**, we conducted descriptive and item analyses and proceeded to EFA using the "psych" package [@R-psych] on the EFA sample.
+**Thirdly**, we conducted descriptive and item analyses and proceeded to EFA on the EFA sample.
 Prior to the EFA, the necessary assumptions, including sample adequacy, normality assumptions, and quality of correlation matrix, were assessed.
@@
 
-For reliability estimation, the "psych" package was applied [@R-psych].
 Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it tends to deflate the estimates for Likert-type data since the calculation is based on the Pearson-correlation matrix, which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal].
@@
 
-To validate the latent structure obtained in the EFA, we conducted a categorical confirmatory factor analysis (CFA) with the weighted least squares means and variance adjusted (WLSMV) estimation [@desjardinsHandbookEducationalMeasurement2018], using the "lavaan" package [@R-lavaan] on the CFA sample.
+To validate the latent structure obtained in the EFA, we conducted a categorical confirmatory factor analysis (CFA) with the weighted least squares means and variance adjusted (WLSMV) estimation [@desjardinsHandbookEducationalMeasurement2018] on the CFA sample.
 We assessed the model fit using standard model fit guidelines: (i) $\chi^2$ test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI): close to 0.95 or above/ between 0.90-0.95 and above (iii) root mean square error of approximation (RMSEA): close to 0.06 or below, (iv) Standardized root mean square (SRMR): close to 0.08 or below [@huCutoffCriteriaFit1999; @schumacker2004beginner].
@@
 In order to evaluate whether the construct demonstrated psychometric equivalence and the same meaning across native English speakers (n=`r invariance.data.descriptives.count[1,2]`) and non-native English speakers (n=`r invariance.data.descriptives.count[2,2]`) in the CFA sample (n=`r nrow(CFA.descriptives)`) [@putnick2016measurement; @klinePrinciplesPracticeStructural2015] measurement invariance analysis was used.
-We used structural equation modelling framework applying the "lavaan" package [@R-lavaan] to assess the measurement invariance.
+We used structural equation modelling framework to assess the measurement invariance.
 We successively compared four nested models: configural, metric, scalar, and residual models using the $\chi^2$ difference test ($\Delta \chi^2$).
@@
 
-**Fourthly**, in a secondary analysis, we identified the educational grade level (US education system) required to understand the items in our inventory with the Flesch-Kincaid grade level identification method [@flesch1948new] applying the "koRpus" [@R-koRpus] package.
+**Fourthly**, in a secondary analysis, we identified the educational grade level (US education system) required to understand the items in our inventory with the Flesch-Kincaid grade level identification method [@flesch1948new].
 Correspondingly, we analysed possible semantic overlap of our developed inventory using the ["Semantic Scale Network" (SSN)](https://rosenbusch.shinyapps.io/semantic_net/) engine [@rosenbusch2020semantic].
@@
 **Lastly**, we derived a short form of the LEBA employing an Item Response Theory (IRT) based analysis.
-We fitted each factor of the LEBA to the combined EFA and CFA sample (n=`r nrow(sem.data)`) using the graded response model [@samejima1997handbook] via the "mirt" package [@R-mirt].
+We fitted each factor of the LEBA to the combined EFA and CFA sample (n=`r nrow(sem.data)`) using the graded response model [@samejima1997handbook].
 IRT assesses the item quality by estimating the item discrimination, item difficulty, item information curve, and test information curve [@bakerBasicsItemResponse2017].

### 2023-10-29 manuscript_SciRep.Rmd
added Text adjustments according to reviewers' comments in a copied RMD file (manuscript_SciRep) and added Siraji's predicitive validity study to the references.bib document (RL)

--- 2023-02-14 manuscript.Rmd
@@
 Nevertheless, these devices also encompass limiting factors such as potentially being intrusive (e.g., when eye-level worn), yielding the risk of getting covered (e.g., when wrist- or chest-worn) and requiring (monetary) resources and expertise for acquisition and maintenance of the devices.
+Moreover, it is important to note that portable light loggers alone do not collect data on the specific behavioural patterns in relation to light exposure.
 
 On the other hand, several attempts have been made to quantify received light exposure subjectively with self-report questionnaires (**Supplementary Table 1**), bypassing the cost and intrusiveness issues.
-However, subjective light intensity assessments pose a new set of challenges: The human visual system constantly adapts to brightness [@hurvich_perception_1966], while the signals underlying the non-visual effects of light are independent from perception [@allen_exploiting_2018], making the self-report assessment of light properties challenging.
+However, self-reporting light properties could be challenging for people who lack technical knowledge of light sources.
+Moreover, individuals may need to consider that, unlike a photometer, the human visual system continuously adapts to brightness [@hurvich_perception_1966], while the signals underlying the non-visual effects of light are independent from perception [@allen_exploiting_2018].
 Retrospectively recalling the properties of a light source can further complicate such subjective evaluations.
@@
 Here, we present the development process of a novel self-reported inventory, the Light Exposure Behaviour Assessment (LEBA), for characterizing diverse light exposure-related behaviours.
+Notably, we do not claim to be estimating the personal light exposure with these questions.
+Instead, we aim to assess, in a scalable way, how people behave in relation to light, focusing on habitual patterns that could guide behavioural intervention points.
 
@@
 All items violated both univariate [@shapiroAnalysisVarianceTest1965] and multivariate normality [@mardiaMeasuresMultivariateSkewness1970].
-The multivariate skewness was`r printnum(mardia.all.data$b1p)` (p<0.001) and the multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p<0.001).
+The multivariate skewness was `r printnum(mardia.all.data$b1p)` (p<0.001) and the multivariate kurtosis was `r printnum(mardia.all.data$b2p)` (p<0.001).
 
@@
 
+Our aim was to provide a data-driven approach to reducing the number of items for cases where a small reduction of items is necessary.
 In order to derive a short form of the LEBA inventory, we fitted each factor of the LEBA with the graded response model [@samejima1997handbook] to the combined EFA and CFA sample (n=690).
@@
 Responding to several lengthy questionnaires increases the participants losing focus and becoming tried.
-To avoid these situations we  derived a short version of the LEBA (18 items) using IRT analysis.
+Thus, in some circumstances, reducing the number of items even slightly may be necessary to employ the LEBA questionnaire.
+Our aim was to provide a data-driven approach to reducing the number of items, apart from the possibility of excluding a specific factor from the 23-item questionnaire.
+Nonetheless, where possible, we strongly recommend using the extended form of the questionnaire to avoid limiting the range of gained information.
+We derived a short version of the LEBA (18 items) using IRT analysis.
 We fitted a graded response model to the combined EFA and CFA sample (n=`r nrow(data)`) and discarded five items (1, 25, 30, 38, & 41) with relatively flat item information curve [I($\theta$) <.20].
@@
 Thus, estimating convergent validity with similar subjective scales was impossible.
-Alternatively, the validity of the LEBA could be evaluated by administering it conjointly with objective field measurements of light exposure (e.g.
-with portable light loggers, see literature review).
-By this route, one could study how the (subjectively measured) light exposure-related behavioural patterns translate into (objectively measured) received light exposure.
+However, a recent study [@Siraji.2023] demonstrated the predictive validity of the questionnaire by correlating the LEBA factors with chronotype, mood, sleep quality, and memory and concentration difficulties.
+In addition, further evidence for the validity of the LEBA could be obtained by administering it conjointly with objective field measurements of light exposure (e.g.
+with portable light loggers/wearables, see literature review), smartphone readouts as well as subjective data in the form of 24-hour recalls.
+By this route, one  could study how the (subjectively measured) light exposure-related behavioural patterns translate into (objectively measured) received light exposure, (objectively measured) smartphone use, and how closely the retrospective questionnaire relates to daily reports of these behaviours.
 
@@
 All code and data underlying this article is available on a public [GitHub repository](https://github.com/leba-instrument).
-The English version of long and short form of LEBA  inventory and online survey implementation templates on common survey platforms(Qualtrics and REDCap) -- is available  on another public [GitHub repository](https://github.com/leba-instrument/leba-instrument-en) as well as on the dedicated [website](https://leba-instrument.org/) of the LEBA inventory under an open-access licence (Creative Commons CC-BY-NC-ND).
+The English version of long and short form of LEBA  inventory and online survey implementation templates on common survey platforms (Qualtrics and REDCap) -- is available  on another public [GitHub repository](https://github.com/leba-instrument/leba-instrument-en) as well as on the dedicated [website](https://leba-instrument.org/) of the LEBA inventory under an open-access licence (Creative Commons CC-BY-NC-ND).
 

### 2023-11-05 manuscript.Rmd
Revision 1 (MASJ)

@@
 
+desctable.data %>%
+  tbl_summary(
+    by=slypos_demographics_sex.factor,
+    statistic=list(all_continuous() ~ "{mean} ({sd})",
+                     all_categorical() ~ "{n} ({p}%)"),
+    digits=all_continuous() ~ 2,
+    label=list(slypos_demographics_age ~ "Age",
+                 # slypos_demographics_sex.factor ~ "Sex",
+                 slypos_demographics_gender.factor ~ "Gender-Variant Identity",
+                 slypos_demographics_language.factor ~ "Native English Speaker",
+                 slypos_demographics_work_or_school.factor ~ "Occupational Status",
+                 slypos_demographics_school.factor ~ "Occupational setting"
+                 ),
+
+    missing="no"
+    ) %>% add_overall() %>% bold_labels() %>% 
+  # add_p() %>% add_q() %>%
+modify_header(label ~ "**Variable**") %>% 
+  # separate_p_footnotes() %>%
+  modify_caption("Demographic Characteristics of Participants (n=690).") -> desc_table_gender
+
 as_tibble(desc_table) -> desc_tibble 
@@
   as_tibble(format='pipe') -> tz_tibble
+
+# # create descriptive table for the demographic vars (excluding tz & Country) with gtsummary
+# desctable.data %>%
+#   tbl_summary(
+#     by=slypos_demographics_sex.factor,
+#     statistic=list(all_continuous() ~ "{mean} ({sd})",
+#                      all_categorical() ~ "{n} ({p}%)"),
+#     digits=all_continuous() ~ 2,
+#     label=list(slypos_demographics_age ~ "Age",
+#                  # slypos_demographics_sex.factor ~ "Sex",
+#                  slypos_demographics_gender.factor ~ "Gender-Variant Identity",
+#                  slypos_demographics_language.factor ~ "Native English Speaker",
+#                  slypos_demographics_work_or_school.factor ~ "Occupational Status",
+#                  slypos_demographics_school.factor ~ "Occupational setting"
+#                  ),
+#     
+#     missing="no"
+#     ) %>% add_overall() %>% bold_labels() %>% 
+#   # add_p() %>% add_q() %>%
+# modify_header(label ~ "**Variable**") %>% 
+#   # separate_p_footnotes() %>%
+#   modify_caption("Demographic Characteristics of Participants (n=690).") -> desc_table 
+# 
+# as_tibble(desc_table) -> desc_tibble 
+# as_kable_extra(desc_table, format="latex",booktabs=T) -> desc_kable #save it as a knitr::kable
 

### 2023-11-05 manuscript_SciRep.Rmd
psych::describeBy code correction

@@
 
-mi.des.sum <- mi.descriptives %>% 
-psych::describeBy("English_Speaking")
-
-mi.english.sum <- english.speaking %>% 
-psych::describeBy("slypos_demographics_sex.factor")
-
-mi.non.english.sum <- non.english.speaking %>% 
-psych::describeBy("slypos_demographics_sex.factor")
+mi.des.sum <- psych::describeBy(mi.descriptives ~ English_Speaking)
+
+mi.english.sum <- psych::describeBy(english.speaking ~ slypos_demographics_sex.factor)
+
+mi.non.english.sum <- psych::describeBy(non.english.speaking %>% slypos_demographics_sex.factor)
 

### 2023-11-05 manuscript_SciRep.Rmd
describeBy code correction
DescribeBy corrction: completed
latticeextra updated

@@
 koRpus::install.koRpus.lang(lang=c("en"))
-
+install.packages("latticeExtra")
 install.packages("correlation")
@@
 library(ggtext)
+library(latticeExtra)
 r_refs("lib_references.bib")
@@
 
-mi.non.english.sum <- psych::describeBy(non.english.speaking %>% slypos_demographics_sex.factor)
+mi.non.english.sum <- psych::describeBy(non.english.speaking ~ slypos_demographics_sex.factor)
 

### 2023-11-05 manuscript_SciRep.Rmd
Comments addressed-MASJ

@@
 Figure \@ref(fig:efa-plot-print)-A depicts the respective correlation matrix.
-To identify how many factors are required to optimally express human light exposure related behaviors we used a combination of methods.
+To identify how many factors are required to optimally express human light exposure related behaviours we used a combination of methods.
 the Scree plot ( Figure \@ref(fig:efa-plot-print)-B) revealed a six-factor solution, whereas the minimum average partial (MAP) method [@velicerDeterminingNumberComponents1976] (**Supplementary Table 3**) and Hull method [@lorenzo-sevaHullMethodSelecting2011] implied a five-factor solution (Figure \@ref(fig:efa-plot-print)-C).
@@
 
-```{r textanalysis, include=F}
+```{r textanalysis, eval=FALSE, include=FALSE}
 #This chunk holds codes for semantic analysis and readability test
@@
 The resulting item discrimination parameters of the inventory fell into categories of "very high" (10 items), "high" (4 items), "moderate" (4 items), and "low" ( 5 items), indicating a good range of discrimination along the latent trait level ($\theta$) (**Supplementary Table 6**).
-An examination of the item information curve (**Supplementary Figure 3**) revealed five items (1, 25, 30, 38, & 41) provided very low information regarding light exposure related behaviors with relatively flat curves (I($\theta$) \<0.20).
+An examination of the item information curve (**Supplementary Figure 3**) revealed five items (1, 25, 30, 38, & 41) provided very low information regarding light exposure related behaviours with relatively flat curves (I($\theta$) \<0.20).
 We discarded those items, culminating in a short form of LEBA with five factors and 18 items (**Supplementary File 2**).
@@
 This points out that the LEBA short-form estimates the light exposure-related behaviour most precisely near the centre of the trait continuum for the second, third and fourth factors.
-In contrast, for the first and fifth factors the TICs were left skewed indicating their increased sensitivity in identifying people who are engaging more in those particular light exposure related behavior dimensions [@bakerBasicsItemResponse2017].
+In contrast, for the first and fifth factors the TICs were left skewed indicating their increased sensitivity in identifying people who are engaging more in those particular light exposure related behaviour dimensions [@bakerBasicsItemResponse2017].
 
@@
 
-Often psychological measurements require application of several questionnaires simultaneously.
-Responding to several lengthy questionnaires increases the participants losing focus and becoming tried.
+While developing and validating LEBA we have complemented the classical test theory based analysis with based analyses (factor analysis and measurement invariance) with IRT analysis.
+The benefit of implementing IRT analysis was twofold.
+First, we derived a shorter form of LEBA (18 items).
+We fitted a graded response model to the combined EFA and CFA sample (n=`r nrow(data)`) and discarded five items (1, 25, 30, 38, & 41) with relatively flat item information curve [I($\theta$) <.20].
+The resulting test information curves suggest that the short-LEBA is a psychometrically sound measure with adequate coverage of underlying traits and can be applied to capture the frequency of different light exposure related behaviours reliably.
+Often, psychological measurements require application of several questionnaires simultaneously.
+Responding to several lengthy questionnaires increases the participants losing focus and becoming tired.
 Thus, in some circumstances, reducing the number of items even slightly may be necessary to employ the LEBA questionnaire.
@@
 Nonetheless, where possible, we strongly recommend using the extended form of the questionnaire to avoid limiting the range of gained information.
-We derived a short version of the LEBA (18 items) using IRT analysis.
-We fitted a graded response model to the combined EFA and CFA sample (n=`r nrow(data)`) and discarded five items (1, 25, 30, 38, & 41) with relatively flat item information curve [I($\theta$) <.20].
-The resulting test information curves suggest that the short-LEBA is a psychometrically sound measure with adequate coverage of underlying traits and can be applied to capture the frequency of different light exposure related behaviours reliably.
-
+
+Second, IRT analysis enabled us to acknowledge the individual differences in responding to the items of LEBA.
+IRT provides a framework to interpret respondents' obtained scores in the light of latent ability (i.e.
+light exposure behaviour) and the characteristics of the respondents--how they interpret the items [@thomas2019advances].
 Findings from the Item and person fit index analysis demonstrate that all five fitted models were acceptable and provide evidence of validity for the factors.
-In addition, the diverse item discrimination parameters indicate an appropriate range of discrimination -- the ability to differentiate respondents with different levels of light exposure-related behaviour.
+In addition, the diverse item discrimination parameters indicate an appropriate range of discrimination -- the ability to differentiate respondents with different levels of light exposure-related behaviour while acknowledging the interpersonal variability in understanding the item.
 
@@
 
+It is important to note that, LEBA utilizes a five-point Likert-type response scale which is often susceptible to central tendency bias, where responses are biased towards the central value of the response scale [@aston2022central].
+Without proper corrections of the response pattern, the interpretation of the scores could be erroneous.
+We recommend using the sensory precision suggested by @aston2022central method to correct the central tendency bias.
+
+Lastly, this study is the lack of convergent validity evidence.
+LEBA being the first of its kind, lacks golden standard against which its convergent validity evidence  could be established.
+However, a recent study [@Siraji.2023] demonstrates the predictive validity of LEBA by successfully relating LEBA behaviour factors to chronotype, mood, sleep quality, and memory and concentration difficulties.
+The results of their study confirmed the very essence of LEBA-behaviour could led to different light exposure experiences that differentially influence health, wellness and performance.
+
 ## Future directions
@@
 To our knowledge, the LEBA is the first inventory characterising light exposure-related behaviour in a scalable manner.
-Thus, estimating convergent validity with similar subjective scales was impossible.
-However, a recent study [@Siraji.2023] demonstrated the predictive validity of the questionnaire by correlating the LEBA factors with chronotype, mood, sleep quality, and memory and concentration difficulties.
-In addition, further evidence for the validity of the LEBA could be obtained by administering it conjointly with objective field measurements of light exposure (e.g.
+Further evidence for the validity of the LEBA could be obtained by administering it conjointly with objective field measurements of light exposure (e.g.
 with portable light loggers/wearables, see literature review), smartphone readouts as well as subjective data in the form of 24-hour recalls.

### 2023-11-07 manuscript_SciRep.Rmd
Comments addressed and typo corrected-MASj

@@
 keywords          : "light exposure, light-related behaviours, non-visual effects of light, psychometrics"
-wordcount         : "6314"
+wordcount         : "5767"
 
@@
 #You need to run this chunk 1X in your system 
-#install.packages("pacman")#Run this if you don't have pacman installed.
+install.packages("pacman")#Run this if you don't have pacman installed.
 pacman::p_load(MOTE, tidyverse, psych, lavaan,kableExtra,gt,gtsummary, mirt,likert,kutils,semPlot,semTable,semTools,ggcorrplot,dlookr, paran,EFA.MRFA,VIM,DiagrammeR,DiagrammeRsvg,ggplot2,cowplot,questionr,magick, simsem,readxl, stringr,RColorBrewer,WrightMap,reshape, ggsci,ggtext)
@@
 #if you don't have LaTeX installed run the following lines
-#install.packages("tinytex")
-#tinytex::install_tinytex()
+install.packages("tinytex")
+tinytex::install_tinytex()
 ```
@@
 
-Lastly, this study is the lack of convergent validity evidence.
+Lastly, this study lacks convergent validity evidence.
 LEBA being the first of its kind, lacks golden standard against which its convergent validity evidence  could be established.

### 2023-11-07 manuscript_SciRep.Rmd
Update manuscript_SciRep.Rmd

@@
 #     institution   : "University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA"
-# 
-# 
 #   - id            : "9"
@@
 #   - id            : "11"
-#     institution   : "TUM Department of Sport and Health Sciences (TUM SG), Technical University of Munich, Munich, Germany"
+#     institution   : "TUM School of Medicine and Health, Technical University of Munich, Munich, Germany"
 #   - id            : "12"
@@
 
-On the other hand, several attempts have been made to quantify received light exposure subjectively with self-report questionnaires (**Supplementary Table 1**), bypassing the cost and intrusiveness issues.
+On the other hand, several attempts have been made to quantify received light exposure subjectively with self-report questionnaires (**Supplementary Table 1**).
 However, self-reporting light properties could be challenging for people who lack technical knowledge of light sources.
-Moreover, individuals may need to consider that, unlike a photometer, the human visual system continuously adapts to brightness [@hurvich_perception_1966], while the signals underlying the non-visual effects of light are independent from perception [@allen_exploiting_2018].
+Moreover, it is worth considering that the human visual system, unlike a photometer, continuously adapts to ambient brightness [@hurvich_perception_1966], while the signals underlying the non-visual effects of light are independent from perception [@allen_exploiting_2018].
 Retrospectively recalling the properties of a light source can further complicate such subjective evaluations.
@@
 Here, we present the development process of a novel self-reported inventory, the Light Exposure Behaviour Assessment (LEBA), for characterizing diverse light exposure-related behaviours.
-Notably, we do not claim to be estimating the personal light exposure with these questions.
-Instead, we aim to assess, in a scalable way, how people behave in relation to light, focusing on habitual patterns that could guide behavioural intervention points.
+Notably, the focus of LEBA is not to estimate personal light exposure.
+Instead, we aim to assess, in a scalable way, how people behave in relation to light, focusing on habitual patterns that could guide behavioural interventions.
 
@@
 The fourth factor comprised five items investigated the other behaviours related to the individual's electric light exposure before bedtime.
-lastly, the fifth factor encompassed six items capturing the individual's morning and daytime light exposure-related behaviour.
+Lastly, the fifth factor encompassed six items capturing the individual's morning and daytime light exposure-related behaviour.
 
@@
 
-While developing and validating LEBA we have complemented the classical test theory based analysis with based analyses (factor analysis and measurement invariance) with IRT analysis.
+While developing and validating LEBA, we have complemented conventional approaches with an Item Response Theory (IRT) analysis.
+IRT provides a framework to interpret respondents' obtained scores in the light of latent ability (i.e.
+light exposure behaviour) and the characteristics of the respondents -- how they interpret the items [@thomas2019advances].
 The benefit of implementing IRT analysis was twofold.
@@
 
-Second, IRT analysis enabled us to acknowledge the individual differences in responding to the items of LEBA.
-IRT provides a framework to interpret respondents' obtained scores in the light of latent ability (i.e.
-light exposure behaviour) and the characteristics of the respondents--how they interpret the items [@thomas2019advances].
-Findings from the Item and person fit index analysis demonstrate that all five fitted models were acceptable and provide evidence of validity for the factors.
+The IRT analysis enabled us to capture individual differences in responding to the items of LEBA.
+Findings from the item and person fit index analysis demonstrate that all five fitted models were acceptable and provide evidence of validity for the factors.
 In addition, the diverse item discrimination parameters indicate an appropriate range of discrimination -- the ability to differentiate respondents with different levels of light exposure-related behaviour while acknowledging the interpersonal variability in understanding the item.
@@
 
-It is important to note that, LEBA utilizes a five-point Likert-type response scale which is often susceptible to central tendency bias, where responses are biased towards the central value of the response scale [@aston2022central].
-Without proper corrections of the response pattern, the interpretation of the scores could be erroneous.
-We recommend using the sensory precision suggested by @aston2022central method to correct the central tendency bias.
-
-Lastly, this study lacks convergent validity evidence.
-LEBA being the first of its kind, lacks golden standard against which its convergent validity evidence  could be established.
-However, a recent study [@Siraji.2023] demonstrates the predictive validity of LEBA by successfully relating LEBA behaviour factors to chronotype, mood, sleep quality, and memory and concentration difficulties.
-The results of their study confirmed the very essence of LEBA-behaviour could led to different light exposure experiences that differentially influence health, wellness and performance.
+It is important to note that LEBA utilizes a five-point Likert-type response scale which may be susceptible to central tendency bias, i.e.
+responses are biased towards the central value of the response scale.
+Future work should evaluate other methods of obtaining responses, such as using a visual-analogue scale.
+
+Finally, there is limited evidence for convergent validity.
+LEBA being the first of its kind in characterising light exposure _behaviour_ at present lacks a gold standard against which its convergent validity evidence could be established.
+A recent study [@Siraji.2023] demonstrated the predictive validity of LEBA by successfully relating its factors to self-reported chronotype, mood, sleep quality, and cognitive function.
+The results of their study confirmed that light-related behaviours, as captured by LEBA, could led to different light exposure experiences that differentially influence health, wellness and performance.
+Further work will need to establish convergent validity of LEBA further.
 
@@
 Further evidence for the validity of the LEBA could be obtained by administering it conjointly with objective field measurements of light exposure (e.g.
-with portable light loggers/wearables, see literature review), smartphone readouts as well as subjective data in the form of 24-hour recalls.
-By this route, one  could study how the (subjectively measured) light exposure-related behavioural patterns translate into (objectively measured) received light exposure, (objectively measured) smartphone use, and how closely the retrospective questionnaire relates to daily reports of these behaviours.
+with portable light loggers/wearables), smartphone readouts, as well as subjective data in the form of 24-hour recalls.
+Such a study could related the relationship bewteen (subjectively measured) light exposure-related behavioural patterns translate into (objectively measured) received light exposure, smartphone use, and how closely the retrospective questionnaire relates to daily reports of these behaviours.
 
@@
 Figure \@ref(fig:FlowchartFig) summarises the steps we followed while developing the LEBA. We conducted all analyses with the statistical software environment R.
-**Firstly**, we set an item pool of 48 items with a six-point Likert-type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial inventory.
+
+(1) We set an item pool of 48 items with a six-point Likert-type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial inventory.
 Our purpose was to capture light exposure-related behaviour.
@@
 
-**Secondly**, the two rounds of data collection were administered.
+(2) Two rounds of data collection were administered.
 In the first round (EFA sample; n=`r nrow(EFA.descriptives)`) we collected data for the exploratory factor analysis (EFA).
@@
 
-**Thirdly**, we conducted descriptive and item analyses and proceeded to EFA on the EFA sample.
+(3) We conducted descriptive and item analyses and proceeded to EFA on the EFA sample.
 Prior to the EFA, the necessary assumptions, including sample adequacy, normality assumptions, and quality of correlation matrix, were assessed.
@@
 
-**Fourthly**, in a secondary analysis, we identified the educational grade level (US education system) required to understand the items in our inventory with the Flesch-Kincaid grade level identification method [@flesch1948new].
+(4) In a secondary analysis, we identified the educational grade level (US education system) required to understand the items in our inventory with the Flesch-Kincaid grade level identification method [@flesch1948new].
 Correspondingly, we analysed possible semantic overlap of our developed inventory using the ["Semantic Scale Network" (SSN)](https://rosenbusch.shinyapps.io/semantic_net/) engine [@rosenbusch2020semantic].
@@
 
-**Lastly**, we derived a short form of the LEBA employing an Item Response Theory (IRT) based analysis.
+(5) We derived a short form of the LEBA employing an Item Response Theory (IRT) based analysis.
 We fitted each factor of the LEBA to the combined EFA and CFA sample (n=`r nrow(sem.data)`) using the graded response model [@samejima1997handbook].

### 2023-11-09 manuscript_SciRep.Rmd
Technical check completed-MASj

@@
 
-# author: 
-#   - name          : "Mushfiqul Anwar Siraji"
-#     affiliation   : "1, *"
-#     email         : "mushfiqul.anwarsiraji@monash.edu"
-#     role:         
-#       - Formal Analysis
-#       - Visualization
-#       - Writing – original draft
-#       - Writing – review & editing
-#        
-#   - name          : "Rafael Robert Lazar"
-#     affiliation   : "2, 3, *"
-#     role:
-#       - Data curation
-#       - Investigation
-#       - Project administration
-#       - Visualization
-#       - Writing – original draft
-#       - Writing – review & editing
-#       
-#   - name          : "Juliëtte	van Duijnhoven"
-#     affiliation   : "4, 5"
-#     email         : "j.v.duijnhoven1@tue.nl"
-#     role:         
-#       - Conceptualization
-#       - Methodology
-#       - Investigation
-#       - Writing – review & editing
-# 
-#   - name          : "Luc Schlangen"
-#     affiliation   : "5, 6"
-#     email         : "l.j.m.schlangen@tue.nl"
-#     role:         
-#       - Conceptualization
-#       - Methodology
-#       - Investigation
-#       - Writing – review & editing
-# 
-#   - name          : "Shamsul Haque"
-#     affiliation   : "1"
-#     email         : "shamsul@monash.edu"
-#     role:         
-#       - Conceptualization
-#       - Supervision
-#       - Writing – review & editing
-#       
-#   - name          : "Vineetha Kalavally"
-#     affiliation   : "7"
-#     email         : "vineetha@monash.edu"
-#     role:         
-#       - Supervision
-#       - Writing – review & editing
-#       
-#   - name          : "Céline Vetter"
-#     affiliation   : "8"
-#     email         : "celine.vetter@colorado.edu"
-#     role:         
-#       - Conceptualization
-#       - Writing – review & editing
-#       
-#   - name          : "Gena Glickman"
-#     affiliation   : "9"
-#     email         : "gena.glickman@usuhs.edu"
-#     role:         
-#       - Conceptualization
-#       - Methodology
-#       - Writing – review & editing
-#       
-#   - name          : "Karin Smolders"
-#     affiliation   : "5,6"
-#     email         : "k.c.h.j.smolders@tue.nl"
-#     role:         
-#       - Conceptualization
-#       - Methodology
-#       - Writing – review & editing
-# 
-#   - name          : "Manuel Spitschan"
-#     corresponding : yes
-#     affiliation   : "10, 11, 12"
-#     email         : "manuel.spitschan@tum.de "
-#     role:         
-#       - Conceptualization
-#       - Data curation
-#       - Investigation
-#       - Project administration
-#       - Visualization
-#       - Methodology
-#       - Writing – original draft
-#       - Writing – review & editing
-# 
-# affiliation:
-#   - id            : "1"
-#     institution   : "Monash University, Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
-#   - id            : "2"
-#     institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"
-#   - id            : "3"
-#     institution   : "University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland"
-#   - id            : "4"
-#     institution   : "Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands"
-#   - id            : "5"
-#     institution   : "Eindhoven University of Technology, Intelligent Lighting Institute, Eindhoven, Netherlands"
-#   - id            : "6"
-#     institution   : "Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Human-Technology Interaction, Eindhoven, Netherlands"
-#   - id            : "7"
-#     institution   : "Monash University, Department of Electrical and Computer Systems Engineering, Selangor, Malaysia"
-#   - id            : "8"
-#     institution   : "University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA"
-#   - id            : "9"
-#     institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"   
-#   - id            : "10"
-#     institution   : "Translational Sensory & Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany"
-#   - id            : "11"
-#     institution   : "TUM School of Medicine and Health, Technical University of Munich, Munich, Germany"
-#   - id            : "12"
-#     institution   : "TUM Institute of Advanced Study (TUM-IAS), Technical University of Munich, Garching, Germany"
-#   - id            : "*"
-#     institution   : "Joint first author"   
-# 
-# 
-# authornote: |
-#   This research is supported by funding from the Welcome Trust (204686/Z/16/Z), the European Training Network LIGHTCAP (project number 860613) under the Marie Skłodowska-Curie actions framework H2020-MSCA-ITN-2019, the BioClock project (number 1292.19.077) of the research program Dutch Research Agenda: Onderzoek op Routes door Consortia (NWA-ORC) which is (partly) financed by the Dutch Research Council (NWO), and the European Union and the nationals contributing in the context of the ECSEL Joint Undertaking programme (2021-2024) under the grant #101007319.
+author:
+  - name          : "Mushfiqul Anwar Siraji"
+    affiliation   : "1, 2,+"
+    email         : "mushfiqul.anwarsiraji@monash.edu"
+    role:
+      - Formal Analysis
+      - Visualization
+      - Writing – original draft
+      - Writing – review & editing
+
+  - name          : "Rafael Robert Lazar"
+    affiliation   : "3, 4, +"
+    role:
+      - Data curation
+      - Investigation
+      - Project administration
+      - Visualization
+      - Writing – original draft
+      - Writing – review & editing
+
+  - name          : "Juliëtte	van Duijnhoven"
+    affiliation   : "5, 6"
+    email         : "j.v.duijnhoven1@tue.nl"
+    role:
+      - Conceptualization
+      - Methodology
+      - Investigation
+      - Writing – review & editing
+
+  - name          : "Luc Schlangen"
+    affiliation   : "6, 7"
+    email         : "l.j.m.schlangen@tue.nl"
+    role:
+      - Conceptualization
+      - Methodology
+      - Investigation
+      - Writing – review & editing
+
+  - name          : "Shamsul Haque"
+    affiliation   : "1"
+    email         : "shamsul@monash.edu"
+    role:
+      - Conceptualization
+      - Supervision
+      - Writing – review & editing
+
+  - name          : "Vineetha Kalavally"
+    affiliation   : "8"
+    email         : "vineetha@monash.edu"
+    role:
+      - Supervision
+      - Writing – review & editing
+
+  - name          : "Céline Vetter"
+    affiliation   : "9"
+    email         : "celine.vetter@colorado.edu"
+    role:
+      - Conceptualization
+      - Writing – review & editing
+
+  - name          : "Gena Glickman"
+    affiliation   : "10"
+    email         : "gena.glickman@usuhs.edu"
+    role:
+      - Conceptualization
+      - Methodology
+      - Writing – review & editing
+
+  - name          : "Karin Smolders"
+    affiliation   : "6,7"
+    email         : "k.c.h.j.smolders@tue.nl"
+    role:
+      - Conceptualization
+      - Methodology
+      - Writing – review & editing
+
+  - name          : "Manuel Spitschan"
+    corresponding : yes
+    affiliation   : "11, 12, 13, *"
+    email         : "manuel.spitschan@tum.de "
+    role:
+      - Conceptualization
+      - Data curation
+      - Investigation
+      - Project administration
+      - Visualization
+      - Methodology
+      - Writing – original draft
+      - Writing – review & editing
+
+affiliation:
+  - id            : "1"
+    institution   : "Monash Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
+  - id            : "2"
+    institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"
+  - id            : "3"
+    institution   : "University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland"
+  - id            : "4"
+    institution   : "Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands"
+  - id            : "5"
+    institution   : "Eindhoven University of Technology, Intelligent Lighting Institute, Eindhoven, Netherlands"
+  - id            : "6"
+    institution   : "Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Human-Technology Interaction, Eindhoven, Netherlands"
+  - id            : "7"
+    institution   : "Monash University, Department of Electrical and Computer Systems Engineering, Selangor, Malaysia"
+  - id            : "8"
+    institution   : "University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA"
+  - id            : "9"
+    institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"
+  - id            : "10"
+    institution   : "Translational Sensory & Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany"
+  - id            : "11"
+    institution   : "TUM School of Medicine and Health, Technical University of Munich, Munich, Germany"
+  - id            : "12"
+    institution   : "TUM Institute of Advanced Study (TUM-IAS), Technical University of Munich, Garching, Germany"
+  - id            : "+"
+    institution   : "Joint first author"
+
+  - id            : "13"
+    institution   : "North South University, Department of History and Philosophy, Bangladesh"
+
+  - id            : "*"
+    institution   : "Corresponding Author"
+
+authornote: |
+  This research is supported by funding from the Welcome Trust (204686/Z/16/Z), the European Training Network LIGHTCAP (project number 860613) under the Marie Skłodowska-Curie actions framework H2020-MSCA-ITN-2019, the BioClock project (number 1292.19.077) of the research program Dutch Research Agenda: Onderzoek op Routes door Consortia (NWA-ORC) which is (partly) financed by the Dutch Research Council (NWO), and the European Union and the nationals contributing in the context of the ECSEL Joint Undertaking programme (2021-2024) under the grant #101007319.
 
@@
   - \DeclareDelayedFloatFlavor{sidewaysfigure}{figure}
-
+csl: "nature.csl"
 mainfont: Arial

### 2023-11-09 manuscript_SciRep.tex
Technical check completed-MASj

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
  \setmainfont[]{Arial}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
\ifPDFTeX
\else
\babelfont[english]{rm}{Arial}
\fi
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\usepackage{pdflscape}
\DeclareDelayedFloatFlavor{landscape}{table}
\newcommand{\blandscape}{\begin{landscape}}
\newcommand{\elandscape}{\end{landscape}}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\centering\begin{threeparttable}}
%   {\end{threeparttable}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
% See https://github.com/crsh/papaja/issues/292
\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-1em}%
  {\normalfont\normalsize\bfseries\itshape\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
  {-\z@\relax}%
  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

\makeatletter
\usepackage{etoolbox}
\patchcmd{\maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{light exposure, light-related behaviours, non-visual effects of light, psychometrics\newline\indent Word count: 5767}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage{rotating}
\DeclareDelayedFloatFlavor{sidewaysfigure}{figure}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={An inventory of human light exposure related behaviour},
  pdfauthor={Mushfiqul Anwar Siraji1, 2,+, Rafael Robert Lazar3, 4, +, Juliëtte van Duijnhoven5, 6, Luc Schlangen6, 7, Shamsul Haque1, Vineetha Kalavally8, Céline Vetter9, Gena Glickman10, Karin Smolders6,7, \& Manuel Spitschan11, 12, 13, *},
  pdflang={en-EN},
  pdfkeywords={light exposure, light-related behaviours, non-visual effects of light, psychometrics},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{An inventory of human light exposure related behaviour}
\author{Mushfiqul Anwar Siraji\textsuperscript{1, 2,+}, Rafael Robert Lazar\textsuperscript{3, 4, +}, Juliëtte van Duijnhoven\textsuperscript{5, 6}, Luc Schlangen\textsuperscript{6, 7}, Shamsul Haque\textsuperscript{1}, Vineetha Kalavally\textsuperscript{8}, Céline Vetter\textsuperscript{9}, Gena Glickman\textsuperscript{10}, Karin Smolders\textsuperscript{6,7}, \& Manuel Spitschan\textsuperscript{11, 12, 13, *}}
\date{}

\shorttitle{LEBA}

\authornote{

This research is supported by funding from the Welcome Trust (204686/Z/16/Z), the European Training Network LIGHTCAP (project number 860613) under the Marie Skłodowska-Curie actions framework H2020-MSCA-ITN-2019, the BioClock project (number 1292.19.077) of the research program Dutch Research Agenda: Onderzoek op Routes door Consortia (NWA-ORC) which is (partly) financed by the Dutch Research Council (NWO), and the European Union and the nationals contributing in the context of the ECSEL Joint Undertaking programme (2021-2024) under the grant \#101007319.

The authors made the following contributions. Mushfiqul Anwar Siraji: Formal Analysis, Visualization, Writing -- original draft, Writing -- review \& editing; Rafael Robert Lazar: Data curation, Investigation, Project administration, Visualization, Writing -- original draft, Writing -- review \& editing; Juliëtte van Duijnhoven: Conceptualization, Methodology, Investigation, Writing -- review \& editing; Luc Schlangen: Conceptualization, Methodology, Investigation, Writing -- review \& editing; Shamsul Haque: Conceptualization, Supervision, Writing -- review \& editing; Vineetha Kalavally: Supervision, Writing -- review \& editing; Céline Vetter: Conceptualization, Writing -- review \& editing; Gena Glickman: Conceptualization, Methodology, Writing -- review \& editing; Karin Smolders: Conceptualization, Methodology, Writing -- review \& editing; Manuel Spitschan: Conceptualization, Data curation, Investigation, Project administration, Visualization, Methodology, Writing -- original draft, Writing -- review \& editing.

Correspondence concerning this article should be addressed to Manuel Spitschan. E-mail: \href{mailto:manuel.spitschan@tum.de}{\nolinkurl{manuel.spitschan@tum.de}}

}

\affiliation{\vspace{0.5cm}\textsuperscript{1} Monash Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia\\\textsuperscript{2} Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland\\\textsuperscript{3} University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland\\\textsuperscript{4} Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands\\\textsuperscript{5} Eindhoven University of Technology, Intelligent Lighting Institute, Eindhoven, Netherlands\\\textsuperscript{6} Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Human-Technology Interaction, Eindhoven, Netherlands\\\textsuperscript{7} Monash University, Department of Electrical and Computer Systems Engineering, Selangor, Malaysia\\\textsuperscript{8} University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA\\\textsuperscript{9} Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA\\\textsuperscript{10} Translational Sensory \& Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany\\\textsuperscript{11} TUM School of Medicine and Health, Technical University of Munich, Munich, Germany\\\textsuperscript{12} TUM Institute of Advanced Study (TUM-IAS), Technical University of Munich, Garching, Germany\\\textsuperscript{*} Joint first author\\\textsuperscript{13} North South University, Department of History and Philosophy, Bangladesh\\\textsuperscript{+} Co First Author\\\textsuperscript{*} Corresponding Author}

\abstract{%
Light exposure is an essential driver of health and well-being, and individual behaviours during rest and activity modulate physiologically-relevant aspects of light exposure. Further understanding the behaviours that influence individual photic exposure patterns may provide insight into the volitional contributions to the physiological effects of light and guide bevavioral points of intervention. Here, we present a novel, self-reported and psychometrically validated inventory to capture light exposure-related behaviour, the Light Exposure Behaviour Assessment (LEBA).

An expert panel prepared the initial 48-item pool spanning different light exposure-related behaviours. Responses, consisting of rating the frequency of engaging in the per-item behaviour on a 5-point Likert type scale, were collected in an online survey yielding responses from a geographically unconstrained sample (690 completed responses, 74 countries, 28 time zones). The exploratory factor analysis (EFA) on an initial subsample (n=428) rendered a five-factor solution with 25 items (Wearing blue light filters, spending time outdoors, using a phone and smartwatch in bed, using light before bedtime, using light in the morning and during daytime). In a confirmatory factor analysis (CFA) performed on an independent subset of participants (n=262), we removed two additional items to attain the best fit for the five-factor solution (CFI=0.95, TLI=0.95, RMSEA=0.06). The internal consistency reliability coefficient for the total instrument yielded McDonald's Omega=0.68. Measurement model invariance analysis between native and non-native English speakers showed our model attained the highest level of invariance (residual invariance; CFI=0.95, TLI=0.95, RMSEA=0.05). Lastly, a short form of the LEBA (n=18) was developed using Item Response Theory on the complete sample (n=690).

The psychometric properties of the LEBA indicate the usability to measure light exposure-related behaviours. The instrument may offer a scalable solution to characterize behaviours that influence individual photic exposure patterns in remote samples. The LEBA inventory is available under the open-access CC-BY-NC-ND license.

Instrument webpage: \url{https://leba-instrument.org/}
GitHub repository containing this manuscript: \url{https://github.com/leba-instrument/leba-manuscript}
}

\begin{document}
\maketitle

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Light exposure received by the eyes affects many facets of human health, well-being, and performance beyond visual sensation and perception\textsuperscript{1}. The non-image-forming (NIF) effects of light comprise light's circadian and non-circadian influence on several physiological and psychological functions, such as the secretion of melatonin, sleep, mood, pupil size, body temperature, alertness, and higher cognitive functions\textsuperscript{2}.

With the introduction of artificial electric light, human behaviour has become dissociated from the light-dark cycle given by solar radiation. People can now frequently choose when to be exposed to light or darkness. For example, they can decide whether to go outdoors and seek out sunlight, switch on/off light-emitting devices, use certain types of lights at home, or avoid specific light environments altogether. Additionally, when light sources cannot be directly manipulated, sought out, or avoided (for example, at school, work, or in public places), there is still potential leeway to influence personal light exposure behaviourally, for instance, by wearing sunglasses, directing one's gaze away or supplementing the situation with additional light sources. Although clearly yielding the potential for good, these behaviours are further associated with increased electric light exposure at night and indoor time during the day, compromising the natural temporal organisation of the light-dark cycle. For example, in the US, an average of 87\% of the time is spent in enclosed buildings\textsuperscript{3}, and more than 80\% of the population is exposed to a night sky that is brighter than nights with a full moon due to electric light at night\textsuperscript{4}.

An extensive body of scientific evidence suggests that improper light exposure may be disruptive for health and well-being, giving rise to a series of adverse consequences, including the alteration of hormonal rhythms, increased cancer rates, cardiovascular diseases, and metabolic disorders, such as obesity and type II diabetes\textsuperscript{4--6}. These findings have sparked a significant call for assessment and guidance regarding healthy light exposure as exemplified by a recently published set of consensus-based experts' recommendations with specific requirements for indoor light environments during the daytime, evening, and nighttime\textsuperscript{7}.

Furthermore, building on earlier attempts\textsuperscript{e.g. 8}, there was a recent push toward the development and use of portable light loggers to improve ambulant light assessment and gain more insight into the NIF effects of light on human health in field conditions\textsuperscript{9,10}. Attached to different body parts (e.g., wrist; head, at eye level; chest), these light loggers allow for the objective measurement of individual photic exposure patterns under real-world conditions and thus are valuable tools for field studies. Nevertheless, these devices also encompass limiting factors such as potentially being intrusive (e.g., when eye-level worn), yielding the risk of getting covered (e.g., when wrist- or chest-worn) and requiring (monetary) resources and expertise for acquisition and maintenance of the devices. Moreover, it is important to note that portable light loggers alone do not collect data on the specific behavioural patterns in relation to light exposure.

On the other hand, several attempts have been made to quantify received light exposure subjectively with self-report questionnaires (\textbf{Supplementary Table 1}). However, self-reporting light properties could be challenging for people who lack technical knowledge of light sources. Moreover, it is worth considering that the human visual system, unlike a photometer, continuously adapts to ambient brightness\textsuperscript{11}, while the signals underlying the non-visual effects of light are independent from perception\textsuperscript{12}. Retrospectively recalling the properties of a light source can further complicate such subjective evaluations. Moreover, measuring light properties alone does not yield any information about how individuals might behave differently regarding diverse light environments such as work, home or outdoors.

To date, little effort has been made to understand and capture these activities. Here, we present the development process of a novel self-reported inventory, the Light Exposure Behaviour Assessment (LEBA), for characterizing diverse light exposure-related behaviours. Notably, the focus of LEBA is not to estimate personal light exposure. Instead, we aim to assess, in a scalable way, how people behave in relation to light, focusing on habitual patterns that could guide behavioural interventions.

\begin{landscape}\begin{table}

\caption{\label{tab:prepareDescTable}Demographic Characteristics of Participants (n=690).}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{lccc}
\toprule
\textbf{Variable} & \textbf{Overall}, N = 690 & \textbf{1. EFA Sample}, N = 428 & \textbf{2. CFA Sample}, N = 262\\
\midrule
\textbf{Age} & 32.95 (14.57) & 32.99 (15.11) & 32.89 (13.66)\\
\textbf{Sex} &  &  & \\
\hspace{1em}Female & 325 (47\%) & 189 (44\%) & 136 (52\%)\\
\hspace{1em}Male & 351 (51\%) & 230 (54\%) & 121 (46\%)\\
\hspace{1em}Other & 14 (2.0\%) & 9 (2.1\%) & 5 (1.9\%)\\
\addlinespace
\textbf{Gender-Variant Identity} & 49 (7.2\%) & 33 (7.8\%) & 16 (6.2\%)\\
\textbf{Native English Speaker} & 320 (46\%) & 191 (45\%) & 129 (49\%)\\
\textbf{Occupational Status} &  &  & \\
\hspace{1em}Work & 396 (57\%) & 235 (55\%) & 161 (61\%)\\
\hspace{1em}School & 174 (25\%) & 122 (29\%) & 52 (20\%)\\
\addlinespace
\hspace{1em}Neither & 120 (17\%) & 71 (17\%) & 49 (19\%)\\
\textbf{Occupational setting} &  &  & \\
\hspace{1em}Home office/Home schooling & 303 (44\%) & 194 (45\%) & 109 (42\%)\\
\hspace{1em}Face-to-face work/Face-to-face schooling & 109 (16\%) & 68 (16\%) & 41 (16\%)\\
\hspace{1em}Combination of home- and face-to-face- work/schooling & 147 (21\%) & 94 (22\%) & 53 (20\%)\\
\addlinespace
\hspace{1em}Neither (no work or school, or in vacation) & 131 (19\%) & 72 (17\%) & 59 (23\%)\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}\textsuperscript{1} Mean (SD); n (\%)}\\
\end{tabular}}
\end{table}
\end{landscape}

\hypertarget{results}{%
\section{Results}\label{results}}

Our results focus on the development of the LEBA inventory and its psychometric validation using a large scale online sample data (n=690).

\hypertarget{development-of-the-initial-item-pool}{%
\subsection{Development of the initial item pool}\label{development-of-the-initial-item-pool}}

To capture the human light exposure related behaviours, 48 items were developed by an expert panel (all authors -- researchers from chronobiology, light research, neuroscience and psychology in different geographical contexts). Face validity examination by each panel member indicated all items were relevant and a few modifications were suggested. The author team discussed the suggestions and amended the items as indicated, thus creating a 48-item inventory.

\hypertarget{measurement-of-light-exposure-behaviour-in-an-online-sample}{%
\subsection{Measurement of light exposure behaviour in an online sample}\label{measurement-of-light-exposure-behaviour-in-an-online-sample}}

We conducted two rounds of large scale online survey between 17 May 2021 and 3 September 2021 to generate data from 690 participants with varied geographic locations (countries=74; time-zone=28). For a complete list of geographic locations, see \textbf{Supplementary Table 2}. Table 1 presents the survey participants' demographic characteristics. Only participants completing the full LEBA inventory were included. We used the data from first round for the exploratory factor analysis (EFA sample; n=428) and data from the second round was used in the confirmatory factor analysis (CFA sample; n=262). Participants in our survey were aged between 11 to 84 years, with an overall mean of \textasciitilde{} 32.95 years of age {[}Overall: 32.95±14.57; EFA: 32.99±15.11; CFA: 32.89±13.66{]}. In the entire sample, 351 (51\%) were male, 325 (47\%) were female, 14 (2.0\%) reported other sex, and 49 (7.2\%) reported a gender-variant identity. In a ``Yes/No'' question regarding native language, 320 (46\%) of respondents {[}EFA: 191 (45\%); CFA: 129 (49\%){]} indicated to be native English speakers. For their ``Occupational Status'', more than half of the overall sample (396 (57\%)) reported that they currently work, whereas 174 (25\%) reported that they go to school, and 120 (17\%) responded that they do ``Neither''. With respect to the COVID-19 pandemic, we asked participants to indicate their occupational setting during the last four weeks: In the entire sample, 303 (44\%) of the participants indicated that they were in a home office/ home schooling setting, 109 (16\%) reported face-to-face work/schooling, 147 (21\%) reported a combination of home- and face-to-face work/schooling, and 131 (19\%) filled in the ``Neither (no work or school, or on vacation)'' response option.

\hypertarget{psychometric-analysis-development-of-the-long-form}{%
\subsection{Psychometric analysis: Development of the long form}\label{psychometric-analysis-development-of-the-long-form}}

\hypertarget{descriptive-statistics-and-item-analysis}{%
\subsubsection{Descriptive statistics and item analysis}\label{descriptive-statistics-and-item-analysis}}

\begin{figure}
\includegraphics[width=2.5\linewidth,height=1\textheight]{Figures/Figure2} \caption{Summary descriptives and response pattern observed in the large-scale survey for item 01-24. All items violated normality assumption.}\label{fig:efagtPic1}
\end{figure}

\begin{figure}
\includegraphics[width=2.5\linewidth,height=1\textheight]{Figures/Figure3} \caption{Summary descriptives and response pattern observed in the large-scale survey for item 25-48. All items violated normality assumption.}\label{fig:efagtPic2}
\end{figure}

We observed that the response patterns of LEBA inventory for the entire sample (n=690) were not normally distributed (Figures \ref{fig:efagtPic1} and \ref{fig:efagtPic2}). All items violated both univariate\textsuperscript{13} and multivariate normality\textsuperscript{14}. The multivariate skewness was 488.40 (p\textless0.001) and the multivariate kurtosis was 2,808.17 (p\textless0.001).

Similarly, non-normal distribution of response pattern was also observed in the EFA sample. \textbf{Supplementary Figure 1} depicts the univariate descriptive statistics for the EFA sample (n=428). Further, We observed that each item's correlation with the aggregated sum of the 48-item's score varied largely (corrected item-total correlation= 0.03 -0.48) indicating the possibility of multi-factor structure of the LEBA inventory.

\hypertarget{exploratory-factor-analysis-and-reliability-analysis}{%
\subsubsection{Exploratory factor analysis and reliability analysis}\label{exploratory-factor-analysis-and-reliability-analysis}}

Exploratory analysis revealed that items of LEBA inventory can be categorized into five major factors: (i) wearing blue light filters; (ii) spending time out doors; (iii) using phone and smartwatch in bed; (iv) using light before bedtime (v) using light in the morning and during daytime. In this stage of analysis, we retained 25 items. the first factor had three items and encapsulated the individual's preference for using blue light filters in different light environments. The second factor contained six items that incorporated the individuals' hours spent outdoors. The third factor contained five items that looked into specific behaviours of using a phone and smartwatch in bed. The fourth factor comprised five items investigated the other behaviours related to the individual's electric light exposure before bedtime. Lastly, the fifth factor encompassed six items capturing the individual's morning and daytime light exposure-related behaviour.

Prior to conducting the EFA, we have checked the post-hoc sampling adequacy by applying Kaiser-Meyer-Olkin (KMO) measures of sampling adequacy on the EFA sample (n=428)\textsuperscript{15} and the quality of the correlation matrix by Bartlett's test of sphericity\textsuperscript{16}. KMO\textgreater0.50 would indicate adequate sample size\textsuperscript{17} and a significant test of sphericity would indicate satisfactory quality of the correlation matrix . Results indicated that we had an adequate sample size (KMO=0.63) and correlation matrix (\(\chi^2_{1128}\)=5042.86, p\textless{} 0.001). However, 4.96\% of the inter-item correlation coefficients were greater than \textbar0.30\textbar, and the inter-item correlation coefficients ranged between -0.44 to 0.91. Figure \ref{fig:efa-plot-print}-A depicts the respective correlation matrix. To identify how many factors are required to optimally express human light exposure related behaviours we used a combination of methods. the Scree plot ( Figure \ref{fig:efa-plot-print}-B) revealed a six-factor solution, whereas the minimum average partial (MAP) method\textsuperscript{18} (\textbf{Supplementary Table 3}) and Hull method\textsuperscript{19} implied a five-factor solution (Figure \ref{fig:efa-plot-print}-C). Hence, we tested both five-factor and six-factor solutions using iterative EFA where we gradually identified and discarded problematic items (factor-loading \textless0.30 and cross-loading \textgreater0.30). In this process, we found a five-factor structure for LEBA inventory with 25 items. Table \ref{tab:EFATable} displays the factor-loading (\(\lambda\)) and communality of the items. Both factor loadings and commonalities advocate to accept this five-factor solution ( \textbar{}\(\lambda\)\textbar=0.32-0.99; commonalities=0.11-0.99). These five factors explains 10.25\%, 9.93\%, 8.83\%, 8.44\%, 6.14\% of the total variance in individual's light exposure related behaviours respectively. All factors exhibited excellent to satisfactory reliability (ordinal \(\alpha\)=0.94, 0.76, 0.75, 0.72, 0.62 respectively). The entire inventory also exhibited satisfactory reliability (\(\omega_t\)=0.77).

However, the histogram of the absolute values of nonredundant residual correlations (Figure \ref{fig:efa-plot-print}-D) displayed that 26\% of correlations were greater \textgreater\textbar.05\textbar, indicating a possible under-factoring.\textsuperscript{20}. Subsequently, we fitted a six-factor solution, where a factor with only two salient variables emerged, thus disqualifying the six-factor solution (\textbf{Supplementary Table 4}). While making the judgement of accepting this five-factor solution we considered both factor's interpretability and their psychometric properties. We deemed the five derived factors as highly interpretable and relevant concerning our aim to capture light exposure-related behaviour, we retained all of them with 25 items. Two of the items showed negative factor-loading (item 08: I spend 30 minutes or less per day (in total) outside. and item 37: I use a blue-filter app on my computer screen within 1 hour before attempting to fall asleep.). Upon re-inspection, we recognized these items to be negatively correlated to the respective factor, and thus, we reverse-scored these two items.

\begin{figure}

{\centering \includegraphics[width=1\linewidth,height=1.3\textheight]{Figures/Figure4}

}

\caption{(A) Inter-item polychoric correlation coefficients for the 48 items. 4.9 \% inter-item correlation coefficients were higher than \textbar.30\textbar. `x' denotes non-significant correlation. (B) The Scree plot suggested six factors. (C) Hull method indicated that five factors were required to balance the model fit and number of parameters. (D) The histogram of nonredundant residual correlations in the five-factor model indicated that 26\% of inter-item correlations were higher than .05, hinting at a possible under-factoring.}\label{fig:efa-plot-print}
\end{figure}

\begin{lltable}

\begin{TableNotes}[para]
\normalsize{\textit{Note.} Only loading > .30 is reported.}
\end{TableNotes}

\footnotesize{

\begin{longtable}{p{1cm}p{10cm}p{1cm}p{1cm}p{1cm}p{1cm}p{1cm}p{1cm}}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:EFATable}Factor loadings and communality of the retained items in EFA using principal axis extraction method (n=482).}\\
\toprule
item & \multicolumn{1}{c}{Stem} & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{Communality}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:EFATable} continued}}\\
\toprule
item & \multicolumn{1}{c}{Stem} & \multicolumn{1}{c}{PA1} & \multicolumn{1}{c}{PA2} & \multicolumn{1}{c}{PA3} & \multicolumn{1}{c}{PA4} & \multicolumn{1}{c}{PA5} & \multicolumn{1}{c}{Communality}\\
\midrule
\endhead
item16 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day. & 0.99 &  &  &  &  & 0.99\\
item36 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses within 1 hour before attempting to fall asleep. & 0.94 &  &  &  &  & 0.90\\
item17 & I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day. & 0.8 &  &  &  &  & 0.66\\
item11 & I spend more than 3 hours per day (in total) outside. &  & 0.79 &  &  &  & 0.64\\
item10 & I spend between 1 and 3 hours per day (in total) outside. &  & 0.76 &  &  &  & 0.59\\
item12 & I spend as much time outside as possible. &  & 0.65 &  &  &  & 0.47\\
item07 & I go for a walk or exercise outside within 2 hours after waking up. &  & 0.5 &  &  &  & 0.27\\
item08 & I spend 30 minutes or less per day (in total) outside. &  & -0.49 &  &  &  & 0.25\\
item09 & I spend between 30 minutes and 1 hour per day (in total) outside. &  & 0.32 &  &  &  & 0.11\\
item27 & I use my mobile phone within 1 hour before attempting to fall asleep. &  &  & 0.8 &  &  & 0.66\\
item03 & I look at my mobile phone screen immediately after waking up. &  &  & 0.8 &  &  & 0.68\\
item40 & I check my phone when I wake up at night. &  &  & 0.65 &  &  & 0.46\\
item30 & I look at my smartwatch within 1 hour before attempting to fall asleep. &  &  & 0.45 &  &  & 0.35\\
item41 & I look at my smartwatch when I wake up at night. &  &  & 0.36 &  &  & 0.33\\
item33 & I dim my computer screen within 1 hour before attempting to fall asleep. &  &  &  & 0.74 &  & 0.56\\
item32 & I dim my mobile phone screen within 1 hour before attempting to fall asleep. &  &  &  & 0.73 &  & 0.62\\
item35 & I use a blue-filter app on my computer screen within 1 hour before attempting to fall asleep. &  &  &  & 0.66 &  & 0.45\\
item37 & I purposely leave a light on in my sleep environment while sleeping. &  &  &  & -0.39 &  & 0.17\\
item38 & I use as little light as possible when I get up during the night. &  &  &  & 0.38 &  & 0.18\\
item46 & I use tunable lights to create a healthy light environment. &  &  &  &  & 0.6 & 0.42\\
item45 & I use LEDs to create a healthy light environment. &  &  &  &  & 0.59 & 0.37\\
item25 & I use a desk lamp when I do focused work. &  &  &  &  & 0.41 & 0.19\\
item04 & I use an alarm with a dawn simulation light. &  &  &  &  & 0.41 & 0.22\\
item01 & I turn on the lights immediately after waking up. &  &  &  &  & 0.4 & 0.17\\
item26 & I turn on my ceiling room light when it is light outside. &  &  &  &  & 0.35 & 0.16\\
% of Variance &  & 0.1 & 0.1 & 0.09 & 0.08 & 0.06 & NA\\
\bottomrule
\addlinespace
\insertTableNotes
\end{longtable}

}

\end{lltable}

\hypertarget{confirmatory-factor-analysis}{%
\subsubsection{Confirmatory factor analysis}\label{confirmatory-factor-analysis}}

To investigate the structural validity of the five-factor structure obtained in EFA, we conducted a confirmatory factor analysis (CFA) on the CFA sample. The five-factor structure with 25 items showed acceptable fit (Table \ref{tab:tabCfa}) providing evidence of structural validity (CFI=0.92; TLI=0.91; RMSEA=0.07 {[}0.06-0.07, 90\% CI{]}). Two equity constraints were imposed on item pairs 32-33 (item 32: I dim my mobile phone screen within 1 hour before attempting to fall asleep; item 33: I dim my computer screen within 1 hour before attempting to fall asleep) and 16-17 (item 16: I wear blue-filtering, orange-tinted, and/or red-tinted glasses indoors during the day; item 17: I wear blue-filtering, orange-tinted, and/or red-tinted glasses outdoors during the day). Item pair 32-33 describes the preference for dimming the electric devices' brightness before bedtime, whereas item pair 16-17 represents the use of blue filtering or coloured glasses during the daytime. Given the similar nature of captured behaviours within each item pair, we accepted the imposed equity constraints. Nevertheless, the SRMR value exceeded the guideline recommendation (SRMR=0.12). In order to improve the model fit, we conducted a post-hoc model modification. Firstly, the modification indices suggested cross-loadings between item 37 and 26 (item 37: I purposely leave a light on in my sleep environment while sleeping; item 26: I turn on my ceiling room light when it is light outside), which were hence discarded. Secondly, items 30 and 41 (item 30: I look at my smartwatch within 1 hour before attempting to fall asleep; item 41: I look at my smartwatch when I wake up at night) showed a tendency to co-vary in their error variance (MI=141.127, p\textless0.001 ). By allowing the latter pair of items (30 \(\&\) 41) to co-vary, the model's error variance attained an improved fit (CFI=0.95; TLI=0.95); RMSEA=0.06 {[}0.05-0.06, 90\% CI{]}; SRMR=0.11).

Accordingly, we accept the five-factor model with 23 items, finalizing the long Form of LEBA inventory (see \textbf{Supplementary File 1}). Internal consistency ordinal \(\alpha\) for the five factors of the LEBA were 0.96, 0.83, 0.70, 0.69, 0.52, respectively. The reliability of the total inventory was satisfactory (\(\omega_t\)=0.68). Figure \ref{fig:figcfa} depicts the obtained CFA structure, while \textbf{Supplementary Figure 2} depicts the data distribution and endorsement pattern of the retained 23 items in our CFA sample.

\begin{lltable}

\begin{TableNotes}[para]
\normalsize{\textit{Note.} df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square.}
\end{TableNotes}

\begin{longtable}{ccccccccc}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:tabCfa}Confirmatory Factor Analysis model fit indices of the two model: (a) Model 1: five factor model with 25 items (b) Model 2:  five factor model with 23 items. Model 2 attained the best fit.}\\
\toprule
Model & \multicolumn{1}{c}{$\chi^{2}$} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{CFI} & \multicolumn{1}{c}{TLI} & \multicolumn{1}{c}{RMSEA} & \multicolumn{1}{c}{RMSEA 90\% Lower CI} & \multicolumn{1}{c}{RMSEA 90\% Upper CI} & \multicolumn{1}{c}{SRMR}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:tabCfa} continued}}\\
\toprule
Model & \multicolumn{1}{c}{$\chi^{2}$} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{CFI} & \multicolumn{1}{c}{TLI} & \multicolumn{1}{c}{RMSEA} & \multicolumn{1}{c}{RMSEA 90\% Lower CI} & \multicolumn{1}{c}{RMSEA 90\% Upper CI} & \multicolumn{1}{c}{SRMR}\\
\midrule
\endhead
1 & 675.55 & 267.00 & 0.92 & 0.91 & 0.07 & 0.06 & 0.07 & 0.12\\
2 & 561.25 & 231.00 & 0.95 & 0.95 & 0.07 & 0.05 & 0.06 & 0.11\\
\bottomrule
\addlinespace
\insertTableNotes
\end{longtable}

\end{lltable}

\begin{figure}
\includegraphics[width=1\linewidth,height=1\textheight]{Figures/Figure5} \caption{Five factor  model of LEBA obtained by confirmatory factor analysis. By allowing item pair 41 and 30 to co-vary their error variance our model attained the best fit.}\label{fig:figcfa}
\end{figure}

\hypertarget{measurement-invariance}{%
\subsubsection{Measurement invariance}\label{measurement-invariance}}

We reported the measurement invariance (MI) analysis on the CFA sample based on native (n=129) and non-native English speakers (n=133). A detailed demographic description are provided in \textbf{Supplementary Table 5}. Our MI results (Table \ref{tab:InvarianceTab}) indicated that LEBA inventory demonstrated highest level of (residual model) psychometric equivalence across native and non-native English speaking participants, thus permitting group-mean based comparisons. The four fitted MI models generated acceptable fit indices and the model fit did not significantly decrease across the nested models (\(\Delta\)CFI\textgreater-0.01; \(\Delta\)RMSEA\textless0.01).

\begin{lltable}

\begin{TableNotes}[para]
\normalsize{\textit{Note.} df: Degrees of Freedom; CFI: Comparative Fit Index; TLI: Tucker Lewis Index; RMSEA: Root Mean Square Error of Approximation; CI: Confidence Interval; SRMR: Standardized Root Mean Square; a=Metric vs Configural; b=Scalar vs Metric; c=Residual vs Scalar; *= df of model comparison.}
\end{TableNotes}

\footnotesize{

\begin{longtable}{ccccccccccc}\noalign{\getlongtablewidth\global\LTcapwidth=\longtablewidth}
\caption{\label{tab:InvarianceTab}Measurement Invariance analysis on CFA sample (n=262) across native and non-native English speakers.}\\
\toprule
 & \multicolumn{1}{c}{$\chi^{2}$} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{CFI} & \multicolumn{1}{c}{TLI} & \multicolumn{1}{c}{RMSEA} & \multicolumn{1}{c}{RMSEA 90\% Lower CI} & \multicolumn{1}{c}{RMSEA 90\% Upper} & \multicolumn{1}{c}{$\Delta$ $\chi^{2}$} & \multicolumn{1}{c}{$\Delta$ df*} & \multicolumn{1}{c}{p}\\
\midrule
\endfirsthead
\caption*{\normalfont{Table \ref{tab:InvarianceTab} continued}}\\
\toprule
 & \multicolumn{1}{c}{$\chi^{2}$} & \multicolumn{1}{c}{df} & \multicolumn{1}{c}{CFI} & \multicolumn{1}{c}{TLI} & \multicolumn{1}{c}{RMSEA} & \multicolumn{1}{c}{RMSEA 90\% Lower CI} & \multicolumn{1}{c}{RMSEA 90\% Upper} & \multicolumn{1}{c}{$\Delta$ $\chi^{2}$} & \multicolumn{1}{c}{$\Delta$ df*} & \multicolumn{1}{c}{p}\\
\midrule
\endhead
Configural & 632.20 & 442.00 & 0.95 & 0.94 & 0.06 & 0.05 & 0.07 & - & - & -\\
Metric & 643.06 & 458.00 & 0.95 & 0.95 & 0.06 & 0.04 & 0.07 & 18.254a & 16 & 0.309\\
Scalar & 711.87 & 522.00 & 0.95 & 0.95 & 0.05 & 0.04 & 0.06 & 68.221b & 64 & 0.336\\
Residual & 711.87 & 522.00 & 0.95 & 0.95 & 0.05 & 0.04 & 0.06 & 0c & 0 & NA\\
\bottomrule
\addlinespace
\insertTableNotes
\end{longtable}

}

\end{lltable}

\hypertarget{secondary-analysis-grade-level-identification-and-semantic-scale-network-analysis}{%
\subsection{Secondary analysis: Grade level identification and semantic scale network analysis}\label{secondary-analysis-grade-level-identification-and-semantic-scale-network-analysis}}

We investigated the language-based accessibility of LEBA using Flesch-Kincaid grade level analysis\textsuperscript{21}. Results indicated that at least a language proficiency of educational grade level-four (US education system) with age above eight years are required to comprehend the items used in LEBA inventory. Semantic Scale analysis\textsuperscript{22} was administered to assess the LEBA's (23 items) semantic relation to other questionnaires. LEBA inventory was most strongly semantically related to scales about sleep: The ``Sleep Disturbance Scale For Children''\textsuperscript{23} and the ``Composite International Diagnostic Interview (CIDI): Insomnia''\textsuperscript{24}. The cosine similarity index ranged between 0.47 to 0.51.

\hypertarget{developing-a-short-form-of-leba-irt-based-analysis}{%
\subsection{Developing a short form of LEBA: IRT-based analysis}\label{developing-a-short-form-of-leba-irt-based-analysis}}

Our aim was to provide a data-driven approach to reducing the number of items for cases where a small reduction of items is necessary. In order to derive a short form of the LEBA inventory, we fitted each factor of the LEBA with the graded response model\textsuperscript{25} to the combined EFA and CFA sample (n=690). The resulting item discrimination parameters of the inventory fell into categories of ``very high'' (10 items), ``high'' (4 items), ``moderate'' (4 items), and ``low'' ( 5 items), indicating a good range of discrimination along the latent trait level (\(\theta\)) (\textbf{Supplementary Table 6}). An examination of the item information curve (\textbf{Supplementary Figure 3}) revealed five items (1, 25, 30, 38, \& 41) provided very low information regarding light exposure related behaviours with relatively flat curves (I(\(\theta\)) \textless0.20). We discarded those items, culminating in a short form of LEBA with five factors and 18 items (\textbf{Supplementary File 2}).

\begin{figure}
\includegraphics[width=1\linewidth,height=1.2\textheight]{Figures/Figure6} \caption{Test information curves for the five factors of LEBA: (A) wearing blue light filters (B) spending time outdoors (C) using a phone and smartwatch in bed (D) using light before bedtime (E) using light in the morning and during daytime. Along the x-axis, we plotted the underlying latent trait continuum for each factor. Along the y-axis, we plotted how much information a particular factor is carrying across its latent trait continuum}\label{fig:Testinfo}
\end{figure}

Subsequently, we obtained five test information curves (TICs). As Figure \ref{fig:Testinfo} illustrates, the TICs of the first and fifth factors peaked on the right side of the centre of their latent traits, while the TICs of the other three factors were roughly centred on the respective trait continuum (\(\theta\)). This points out that the LEBA short-form estimates the light exposure-related behaviour most precisely near the centre of the trait continuum for the second, third and fourth factors. In contrast, for the first and fifth factors the TICs were left skewed indicating their increased sensitivity in identifying people who are engaging more in those particular light exposure related behaviour dimensions\textsuperscript{26}.

Finally, \textbf{Supplementary Table 7} summarises the item fit indexes of the LEBA short form. All 18 items yielded RMSEA value \(\le\) 0.06, indicating an adequate fit to the fitted IRT model. Furthermore, \textbf{Supplementary Figure 4} depicts the person fit Zh statistics histogram for the five IRT models. Zh statistics are larger than -2 for most participants, suggesting a good person fit regarding the selected IRT models.

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

We have developed two versions of a self-report inventory, LEBA, that can capture light exposure-related behaviours in multiple dimensions. The 48 generated items were applied in a large-scale, geographically unconstrained, cross-sectional study, yielding 690 completed surveys. To assure high data quality, participant responses were only included when the five ``attention check items'' throughout the survey were passed. Ultimately, data was recorded from 74 countries and 28 time zones, including native and non-native English speakers from a sex-balanced and age-diverse sample (see Table 1). The acquired study population complied with our objective to avoid bias from a selective sample, which is crucial when relying on voluntary uncompensated participation.

Data collected in the first round was used to explore the latent structure (EFA sample; n=428). The exploratory factor analysis revealed a highly interpretable five-factor solution (``Wearing blue light filters'', ``Spending time outdoors'', ``Using phone and smartwatch in bed'', ``Using light before bedtime'', and ``Using light in the morning and during daytime'') with 25 items. Our CFA analysis (CFA sample; n=262) confirmed the five-factor structure we obtained in our EFA, thus providing evidence for structural validity.(CFI=0.95; TLI=0.95; RMSEA=0.06). In this model, we discarded two more items (item 26 \(\&\) 37 ) for possible cross-loadings. As a rule of thumb, reliability coefficients higher than .70 are regarded as ``satisfactory''. However, at the early developmental stage, a value of .50 is considered acceptable\textsuperscript{27--29}. Thus, we confer, the internal consistency coefficients ordinal alpha for the five factors and the total inventory were satisfactory (Ordinal alpha ranged between 0.52 to 0.96; McDonald's \(\omega_t\)=0.68).

The results of the measurement invariance analysis indicate that the construct ``Light exposure-related behaviour'' is equivalent across native and non-native English speakers and thus suitable for assessment in both groups. Furthermore, according to the grade level identification method, the LEBA appears understandable for students at least 8.33 years of age visiting grade four or higher. Interestingly, the semantic similarity analysis (``Semantic Scale Network'' database\textsuperscript{22}) revealed that the ``LEBA'' is semantically related to the ``Sleep Disturbance Scale For Children'' (SDSC)\textsuperscript{23} and the ``Composite International Diagnostic Interview (CIDI): Insomnia''\textsuperscript{24}. Upon inspecting the questionnaire contents, we found that some items in the factors ``Using phone and smartwatch in bed'' and ``Using light before bedtime'' have semantic overlap with the SDSC's and CIDI's items. However, while the CIDI and the SDSC capture various clinically relevant sleep problems and related activities, the LEBA aims to assess light-exposure-related behaviour. Since light exposure at night has been shown to influence sleep negatively\textsuperscript{7,30}, this overlap confirms our aim to measure the physiologically relevant aspects of light-exposure-related behaviour. Nevertheless, the general objectives of the complete questionnaires and the LEBA differ evidently.

While developing and validating LEBA, we have complemented conventional approaches with an Item Response Theory (IRT) analysis. IRT provides a framework to interpret respondents' obtained scores in the light of latent ability (i.e.~light exposure behaviour) and the characteristics of the respondents -- how they interpret the items\textsuperscript{31}. The benefit of implementing IRT analysis was twofold. First, we derived a shorter form of LEBA (18 items). We fitted a graded response model to the combined EFA and CFA sample (n=690) and discarded five items (1, 25, 30, 38, \& 41) with relatively flat item information curve {[}I(\(\theta\)) \textless.20{]}. The resulting test information curves suggest that the short-LEBA is a psychometrically sound measure with adequate coverage of underlying traits and can be applied to capture the frequency of different light exposure related behaviours reliably. Often, psychological measurements require application of several questionnaires simultaneously. Responding to several lengthy questionnaires increases the participants losing focus and becoming tired. Thus, in some circumstances, reducing the number of items even slightly may be necessary to employ the LEBA questionnaire. Our aim was to provide a data-driven approach to reducing the number of items, apart from the possibility of excluding a specific factor from the 23-item questionnaire. Nonetheless, where possible, we strongly recommend using the extended form of the questionnaire to avoid limiting the range of gained information.

The IRT analysis enabled us to capture individual differences in responding to the items of LEBA. Findings from the item and person fit index analysis demonstrate that all five fitted models were acceptable and provide evidence of validity for the factors. In addition, the diverse item discrimination parameters indicate an appropriate range of discrimination -- the ability to differentiate respondents with different levels of light exposure-related behaviour while acknowledging the interpersonal variability in understanding the item.

\hypertarget{known-limitations}{%
\subsection{Known limitations}\label{known-limitations}}

We acknowledge that this work is limited concerning the following aspects:

The fifth factor, ``using light in the morning and during daytime'', exhibited low internal consistency both in the exploratory and confirmatory factor analysis (EFA: 0.62; CFA:0.52 ). Since, it was above .50, considering the developmental phase of this inventory we accepted the fifth factor. This particular factor captures our behaviour related to usages of light in the morning and daytime. Since, light exposure during morning and daytime influences our alertness and cognition\textsuperscript{32,33}, we deemed capturing these behaviours is essential for the sake of completeness of our inventory. However, the possibility of improving the reliability should be investigated further by adding more appropriate and relevant items to this factor.

The habitual patterns queried in the developed inventory might not exhaustively represent all relevant light-exposure-related behaviours. For instance, it is conceivable that additional light-related activities not included in the LEBA depend on the respondents' profession/occupation, geographical context, and socio-economic status. However, we generated the initial item pool with an international team of researchers and followed a thorough psychometric analysis. Therefore, we are confident that the developed LEBA inventory can serve as a good starting point for exploring the light exposure related behaviours in more depth and inform room for modification of light exposure-related behaviour to improve light hygiene.

As with all studies relying on retrospective self-report data, individuals filling in the LEBA may have difficulties precisely recalling the inquired light-related behaviours. In the interest of bypassing a substantial memory component, we limited the recall period to four weeks and chose response options that do not require exact memory recall. In contrast to directly assessing light properties via self-report, we assume that reporting behaviours might be more manageable for inexperienced laypeople, as the latter does not rely on existing knowledge about light sources. The comprehensibility of the LEBA is also reflected by the Flesch-Kincaid grade level identification method\textsuperscript{21} that suggested a minimum age of 8.33 years and an educational grade of four or higher (US grading system). We argue that measuring light-related behaviours via self-report is crucial because these behaviours will hardly be as observable by anyone else or measurable with other methods (like behavioural observations) with reasonable effort.

It is important to note that LEBA utilizes a five-point Likert-type response scale which may be susceptible to central tendency bias, i.e.~responses are biased towards the central value of the response scale. Future work should evaluate other methods of obtaining responses, such as using a visual-analogue scale.

Finally, there is limited evidence for convergent validity. LEBA being the first of its kind in characterising light exposure \emph{behaviour} at present lacks a gold standard against which its convergent validity evidence could be established. A recent study\textsuperscript{34} demonstrated the predictive validity of LEBA by successfully relating its factors to self-reported chronotype, mood, sleep quality, and cognitive function. The results of their study confirmed that light-related behaviours, as captured by LEBA, could led to different light exposure experiences that differentially influence health, wellness and performance. Further work will need to establish convergent validity of LEBA further.

\hypertarget{future-directions}{%
\subsection{Future directions}\label{future-directions}}

To our knowledge, the LEBA is the first inventory characterising light exposure-related behaviour in a scalable manner. Further evidence for the validity of the LEBA could be obtained by administering it conjointly with objective field measurements of light exposure (e.g.~with portable light loggers/wearables), smartphone readouts, as well as subjective data in the form of 24-hour recalls. Such a study could related the relationship bewteen (subjectively measured) light exposure-related behavioural patterns translate into (objectively measured) received light exposure, smartphone use, and how closely the retrospective questionnaire relates to daily reports of these behaviours.

\hypertarget{conclusion}{%
\subsection{Conclusion}\label{conclusion}}

Here, we developed a novel, internally consistent and structurally valid 23-item self-report inventory for capturing light exposure-related behaviour in five scalable factors. In addition, an 18-item short-form of the LEBA was derived using IRT analysis, yielding adequate coverage across the underlying trait continuum. Applying the LEBA inventory can provide insights into light exposure-related habits on a population-based level. Furthermore, it can serve as a good starting point to profile individuals based on their light exposure-related behaviour and to asseses their light consumption and timing.

\hypertarget{methods}{%
\section{Methods}\label{methods}}

\hypertarget{data-collection}{%
\subsection{Data collection}\label{data-collection}}

A quantitative cross-sectional, fully anonymous, geographically unconstrained online survey was conducted via REDCap\textsuperscript{35,36} by way of the University of Basel \href{https://redcap.scicore.unibas.ch}{sciCORE}. Participants were recruited via the \href{https://enlightenyourclock.org/participate-in-research}{website} (\url{https://enlightenyourclock.org/participate-in-research}) of the science-communication comic book ``Enlighten your clock'', co-released with the survey\textsuperscript{37}, social media (i.e., LinkedIn, Twitter, Facebook), mailing lists, word of mouth, the investigators' personal contacts, and supported by the distribution of the survey link via f.lux\textsuperscript{38}. The initial page of the online survey provided information about the study, including that participation was voluntary and that respondents could withdraw from participation at any time without being penalised. Subsequently, consent was recorded digitally for the adult participants (\textgreater18 years), while under-aged participants (\textless18 years) were prompted to obtain additional assent from their parents/legal guardians. Filling in all questionnaires was estimated to take less than 30 minutes, and participation was not compensated.

As a part of the demographic data, participants provided information regarding age, sex, gender identity, occupational status, COVID-19-related occupational setting, time zone/country of residence and native language. The demographic characteristics of our sample are given in \textbf{Table 1}. Participants were further asked to confirm that they participated in the survey for the first time. All questions incorporating retrospective recall were aligned to a ``past four weeks'' period. Additionally, four attention check items were included among the questionnaires to ensure high data quality, with the following phrasing:
- We want to make sure you are paying attention. What is 4+5?
- {[}\ldots{]} Please select ``Strongly disagree'' here.
- {[}\ldots{]} Please type in ``nineteen'' as a number.
- {[}\ldots{]} Please select ``Does not apply/I don't know.'' here.

\hypertarget{analytic-strategy}{%
\subsection{Analytic strategy}\label{analytic-strategy}}

Figure \ref{fig:FlowchartFig} summarises the steps we followed while developing the LEBA. We conducted all analyses with the statistical software environment R.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\item
  We set an item pool of 48 items with a six-point Likert-type response format (0-Does not apply/I don't know, 1-Never, 2-Rarely 3-Sometimes, 4-Often, 5-Always) for our initial inventory. Our purpose was to capture light exposure-related behaviour. In that context, the first two response options: ``Does not apply/I don't know'' and ``Never'', provided similar information. As such, we collapsed them into one, making it a 5-point Likert-type response format (1-Never, 2-Rarely, 3-Sometimes, 4-Often, 5-Always).
\item
  Two rounds of data collection were administered. In the first round (EFA sample; n=428) we collected data for the exploratory factor analysis (EFA). A sample of at least 250-300 is recommended for EFA\textsuperscript{39,40}. The EFA sample exceeded this recommendation. The second round data (CFA sample; n=262) was subjected to confirmatory factor analysis (CFA). To assess sampling adequacy for CFA, we followed the N:q rule\textsuperscript{41--44}, where at least ten participants per item are required to earn trustworthiness of the result. Again, our CFA sample exceeded this guidelines.
\item
  We conducted descriptive and item analyses and proceeded to EFA on the EFA sample. Prior to the EFA, the necessary assumptions, including sample adequacy, normality assumptions, and quality of correlation matrix, were assessed. As our data violated both the univariate and multivariate normality assumption and yielded ordinal response data, we used a polychoric correlation matrix in the EFA and employed ``principal axis'' (PA) as the factor extraction method\textsuperscript{20,45}. We applied a combination of methods, including a Scree plot\textsuperscript{46}, minimum average partials method\textsuperscript{18}, and Hull method\textsuperscript{19} to identify factor numbers. To determine the latent structure, we followed the common guidelines: (i) no factors with fewer than three items (ii) no factors with a factor loading \textless0.3 (iii) no items with cross-loading \textgreater{} .3 across factors\textsuperscript{47}.
\end{enumerate}

Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it tends to deflate the estimates for Likert-type data since the calculation is based on the Pearson-correlation matrix, which requires response data to be continuous in nature\textsuperscript{48,49}. Subsequently, we reported ordinal alpha for each factor obtained in the EFA which was suggested as a better reliability estimates for ordinal data\textsuperscript{49}. We also estimated the internal consistency reliability of the total inventory using McDonald's \(\omega_t\) coefficient, which was suggested as a better reliability estimate for multidimensional constructs\textsuperscript{50,51}. Both ordinal alpha and McDonald's \(\omega_t\) coefficient values range between 0 to 1, where higher values represent better reliability.

To validate the latent structure obtained in the EFA, we conducted a categorical confirmatory factor analysis (CFA) with the weighted least squares means and variance adjusted (WLSMV) estimation\textsuperscript{20} on the CFA sample. We assessed the model fit using standard model fit guidelines: (i) \(\chi^2\) test statistics: a non-significant test statistics is required to accept the model (ii) comparative fit index (CFI) and Tucker Lewis index (TLI): close to 0.95 or above/ between 0.90-0.95 and above (iii) root mean square error of approximation (RMSEA): close to 0.06 or below, (iv) Standardized root mean square (SRMR): close to 0.08 or below\textsuperscript{52,53}. However, the \(\chi^2\) test is sensitive to sample size\textsuperscript{54}, and SRMR does not work well with ordinal data\textsuperscript{55}. Consequently, we judged the model fit using CFI, TLI and RMSEA.

In order to evaluate whether the construct demonstrated psychometric equivalence and the same meaning across native English speakers (n=129) and non-native English speakers (n=133) in the CFA sample (n=262)\textsuperscript{43,56} measurement invariance analysis was used. We used structural equation modelling framework to assess the measurement invariance. We successively compared four nested models: configural, metric, scalar, and residual models using the \(\chi^2\) difference test (\(\Delta \chi^2\)). Among MI models, the configural model is the least restrictive, and the residual model is the most restrictive. A non-significant \(\Delta \chi^2\) test between two nested measurement invariance models indicates mode fit does not significantly decrease for the superior model, thus allowing the superior invariance model to be accepted\textsuperscript{57,58}.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\setcounter{enumi}{3}
\item
  In a secondary analysis, we identified the educational grade level (US education system) required to understand the items in our inventory with the Flesch-Kincaid grade level identification method\textsuperscript{21}. Correspondingly, we analysed possible semantic overlap of our developed inventory using the \href{https://rosenbusch.shinyapps.io/semantic_net/}{``Semantic Scale Network'' (SSN)} engine\textsuperscript{22}. The SSN detects semantically related scales and provides a cosine similarity index ranging between -.66 to 1\textsuperscript{22}. Pairs of scales with a cosine similarity index value of 1 inidicate full semantical similarity, suggesting redundancy.
\item
  We derived a short form of the LEBA employing an Item Response Theory (IRT) based analysis. We fitted each factor of the LEBA to the combined EFA and CFA sample (n=690) using the graded response model\textsuperscript{25}. IRT assesses the item quality by estimating the item discrimination, item difficulty, item information curve, and test information curve\textsuperscript{26}. Item discrimination indicates how well a particular item can differentiate between participants across the given latent trait continuum (\(\theta\)). Item difficulty corresponds to the latent trait level at which the probability of endorsing a particular response option is 50\%. The item information curve (IIC) indicates the amount of information an item carries along the latent trait continuum. Here, we reported the item difficulty and discrimination parameter and categorized the items based on their item discrimination index: (i) none=0; (ii) very low=0.01 to 0.34; (iii) low=0.35 to 0.64; (iv) moderate=0.65 to 1.34 ; (v) high=1.35 to 1.69; (vi) very high \textgreater1.70\textsuperscript{26}. We discarded the items with a relatively flat item information curve (information \textless.2) to derive the short form of LEBA. We also assessed the precision of the short LEBA utilizing the test information curve (TIC). TIC indicates the amount of information a particular scale carries along the latent trait continuum. Additionally, the item and person fit of the fitted IRT models were analysed to gather more evidence on the validity and meaningfulness of our scale\textsuperscript{20}. The item fit was evaluated using the RMSEA value obtained from Signed-\(\chi^2\) index implementation, where an RMSEA value \(\le\).06 was considered an adequate item fit. The person fit was estimated employing the standardized fit index Zh statistics\textsuperscript{59}. Here, Zh \textless{} -2 was considered as a misfit\textsuperscript{59}.
\end{enumerate}

\begin{figure}

{\centering \includegraphics[width=0.5\linewidth,height=0.5\textheight]{Figures/Figure1}

}

\caption{Flow chart of the LEBA (long and short form) development and evaluation. }\label{fig:FlowchartFig}
\end{figure}

\hypertarget{ethical-approval}{%
\subsection{Ethical approval}\label{ethical-approval}}

The current research project utilizes fully anonymous online survey data and therefore does not fall under the scope of the Human Research Act, making an authorisation from the ethics committee redundant. Nevertheless, the cantonal ethics commission (Ethikkommission Nordwest- und Zentralschweiz, EKNZ) reviewed our proposition (project ID Req-2021-00488) and issued an official clarification of responsibility.

\hypertarget{code-materials-and-data-availability}{%
\subsection{Code, materials and data availability}\label{code-materials-and-data-availability}}

The present article is a fully reproducible open access ``R Markdown'' document. All code and data underlying this article is available on a public \href{https://github.com/leba-instrument}{GitHub repository}. The English version of long and short form of LEBA inventory and online survey implementation templates on common survey platforms (Qualtrics and REDCap) -- is available on another public \href{https://github.com/leba-instrument/leba-instrument-en}{GitHub repository} as well as on the dedicated \href{https://leba-instrument.org/}{website} of the LEBA inventory under an open-access licence (Creative Commons CC-BY-NC-ND).

\newpage

\hypertarget{references}{%
\section{References}\label{references}}

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\leavevmode\vadjust pre{\hypertarget{ref-boyce_light_2022}{}}%
\CSLLeftMargin{1. }%
\CSLRightInline{Boyce, P. \href{https://doi.org/10.1177/14771535211010267}{Light, lighting and human health}. \emph{Lighting Research \& Technology} \textbf{54}, 101--144 (2022).}

\leavevmode\vadjust pre{\hypertarget{ref-blume_effects_2019}{}}%
\CSLLeftMargin{2. }%
\CSLRightInline{Blume, C., Garbazza, C. \& Spitschan, M. \href{https://doi.org/10.1007/s11818-019-00215-x}{Effects of light on human circadian rhythms, sleep and mood}. \emph{Somnologie : Schlafforschung und Schlafmedizin = Somnology : sleep research and sleep medicine} \textbf{23}, 147--156 (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-Klepeis.2001}{}}%
\CSLLeftMargin{3. }%
\CSLRightInline{Klepeis, N. E. \emph{et al.} \href{https://doi.org/10.1038/sj.jea.7500165}{The national human activity pattern survey (NHAPS): A resource for assessing exposure to environmental pollutants}. \emph{Journal of exposure analysis and environmental epidemiology} \textbf{11}, 231--252 (2001).}

\leavevmode\vadjust pre{\hypertarget{ref-navara2007dark}{}}%
\CSLLeftMargin{4. }%
\CSLRightInline{Navara, K. J. \& Nelson, R. J. The dark side of light at night: Physiological, epidemiological, and ecological consequences. \emph{Journal of pineal research} \textbf{43}, 215--224 (2007).}

\leavevmode\vadjust pre{\hypertarget{ref-Lunn.2017}{}}%
\CSLLeftMargin{5. }%
\CSLRightInline{Lunn, R. M. \emph{et al.} \href{https://doi.org/10.1016/j.scitotenv.2017.07.056}{Health consequences of electric lighting practices in the modern world: A report on the national toxicology program's workshop on shift work at night, artificial light at night, and circadian disruption}. \emph{The Science of the total environment} \textbf{607-608}, 1073--1084 (2017).}

\leavevmode\vadjust pre{\hypertarget{ref-Chellappa.2019}{}}%
\CSLLeftMargin{6. }%
\CSLRightInline{Chellappa, S. L., Vujovic, N., Williams, J. S. \& Scheer, F. A. J. L. \href{https://doi.org/10.1016/j.tem.2019.07.008}{Impact of circadian disruption on cardiovascular function and disease}. \emph{Trends in endocrinology and metabolism: TEM} \textbf{30}, 767--779 (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-Brown.2022}{}}%
\CSLLeftMargin{7. }%
\CSLRightInline{Brown, T. M. \emph{et al.} \href{https://doi.org/10.1371/journal.pbio.3001571}{Recommendations for daytime, evening, and nighttime indoor light exposure to best support physiology, sleep, and wakefulness in healthy adults}. \emph{PLoS biology} \textbf{20}, e3001571 (2022).}

\leavevmode\vadjust pre{\hypertarget{ref-hubalek_ambulant_2006}{}}%
\CSLLeftMargin{8. }%
\CSLRightInline{Hubalek, S., Zöschg, D. \& Schierz, C. \href{https://doi.org/10.1177/1477153506070687}{Ambulant recording of light for vision and non-visual biological effects}. \emph{Lighting Research \& Technology} \textbf{38}, 314--321 (2006).}

\leavevmode\vadjust pre{\hypertarget{ref-hartmeyer2022towards}{}}%
\CSLLeftMargin{9. }%
\CSLRightInline{Hartmeyer, S. L., Webler, F. S. \& Andersen, M. Towards a framework for light-dosimetry studies: Methodological considerations. \emph{Lighting Research \& Technology} 14771535221103258 (2022).}

\leavevmode\vadjust pre{\hypertarget{ref-spitschan2022verification}{}}%
\CSLLeftMargin{10. }%
\CSLRightInline{Spitschan, M. \emph{et al.} Verification, analytical validation and clinical validation (V3) of wearable dosimeters and light loggers. \emph{Digital Health} \textbf{8}, 20552076221144858 (2022).}

\leavevmode\vadjust pre{\hypertarget{ref-hurvich_perception_1966}{}}%
\CSLLeftMargin{11. }%
\CSLRightInline{Hurvich, L. M. \& Jameson, D. \emph{The perception of brightness and darkness}. (1966).}

\leavevmode\vadjust pre{\hypertarget{ref-allen_exploiting_2018}{}}%
\CSLLeftMargin{12. }%
\CSLRightInline{Allen, A. E., Hazelhoff, E. M., Martial, F. P., Cajochen, C. \& Lucas, R. J. \href{https://doi.org/10.1093/sleep/zsy100}{Exploiting metamerism to regulate the impact of a visual display on alertness and melatonin suppression independent of visual appearance}. \emph{Sleep} \textbf{41}, zsy100 (2018).}

\leavevmode\vadjust pre{\hypertarget{ref-shapiroAnalysisVarianceTest1965}{}}%
\CSLLeftMargin{13. }%
\CSLRightInline{Shapiro, S. S. \& Wilk, M. B. \href{https://doi.org/10.1093/biomet/52.3-4.591}{An analysis of variance test for normality (complete samples)}. \emph{Biometrika} \textbf{52}, 591--611 (1965).}

\leavevmode\vadjust pre{\hypertarget{ref-mardiaMeasuresMultivariateSkewness1970}{}}%
\CSLLeftMargin{14. }%
\CSLRightInline{Mardia, K. V. \href{https://doi.org/10.1093/biomet/57.3.519}{Measures of multivariate skewness and kurtosis with applications}. \emph{Biometrika} \textbf{57}, 519--530 (1970).}

\leavevmode\vadjust pre{\hypertarget{ref-kaiserIndexFactorialSimplicity1974}{}}%
\CSLLeftMargin{15. }%
\CSLRightInline{Kaiser, H. F. \href{https://doi.org/10.1007/bf02291575}{An index of factorial simplicity}. \emph{Psychometrika} \textbf{39}, 31--36 (1974).}

\leavevmode\vadjust pre{\hypertarget{ref-bartlettNoteMultiplyingFactors1954}{}}%
\CSLLeftMargin{16. }%
\CSLRightInline{Bartlett, M. A {Note} on the {Multiplying Factors} for {Various Chi}-square {Approximations}. \emph{Journal of the Royal Statistical Society. Series B, Methodological} \textbf{16}, 296--298 (1954).}

\leavevmode\vadjust pre{\hypertarget{ref-hutchesonMultivariateSocialScientist1999}{}}%
\CSLLeftMargin{17. }%
\CSLRightInline{Hutcheson, G. D. \emph{The multivariate social scientist : Introductory statistics using generalized linear models}. ({London : SAGE}, 1999).}

\leavevmode\vadjust pre{\hypertarget{ref-velicerDeterminingNumberComponents1976}{}}%
\CSLLeftMargin{18. }%
\CSLRightInline{Velicer, W. \href{https://doi.org/10.1007/BF02293557}{Determining the {Number} of {Components} from the {Matrix} of {Partial Correlations}}. \emph{Psychometrika} \textbf{41}, 321--327 (1976).}

\leavevmode\vadjust pre{\hypertarget{ref-lorenzo-sevaHullMethodSelecting2011}{}}%
\CSLLeftMargin{19. }%
\CSLRightInline{Lorenzo-Seva, U., Timmerman, M. \& Kiers, H. \href{https://doi.org/10.1080/00273171.2011.564527}{The {Hull Method} for {Selecting} the {Number} of {Common Factors}}. \emph{Multivariate Behavioral Research} \textbf{46}, 340--364 (2011).}

\leavevmode\vadjust pre{\hypertarget{ref-desjardinsHandbookEducationalMeasurement2018}{}}%
\CSLLeftMargin{20. }%
\CSLRightInline{Desjardins, C. \& Bulut, O. \emph{Handbook of {Educational Measurement} and {Psychometrics Using R}}. ({Chapman and Hall/CRC}, 2018). doi:\href{https://doi.org/10.1201/b20498}{10.1201/b20498}.}

\leavevmode\vadjust pre{\hypertarget{ref-flesch1948new}{}}%
\CSLLeftMargin{21. }%
\CSLRightInline{Flesch, R. A new readability yardstick. \emph{Journal of applied psychology} \textbf{32}, 221 (1948).}

\leavevmode\vadjust pre{\hypertarget{ref-rosenbusch2020semantic}{}}%
\CSLLeftMargin{22. }%
\CSLRightInline{Rosenbusch, H., Wanders, F. \& Pit, I. L. The semantic scale network: An online tool to detect semantic overlap of psychological scales and prevent scale redundancies. \emph{Psychological methods} \textbf{25}, 380 (2020).}

\leavevmode\vadjust pre{\hypertarget{ref-bruni1996sleep}{}}%
\CSLLeftMargin{23. }%
\CSLRightInline{Bruni, O. \emph{et al.} The sleep disturbance scale for children (SDSC) construct ion and validation of an instrument to evaluate sleep disturbances in childhood and adolescence. \emph{Journal of sleep research} \textbf{5}, 251--261 (1996).}

\leavevmode\vadjust pre{\hypertarget{ref-robins1988composite}{}}%
\CSLLeftMargin{24. }%
\CSLRightInline{Robins, L. N. \emph{et al.} The composite international diagnostic interview: An epidemiologic instrument suitable for use in conjunction with different diagnostic systems and in different cultures. \emph{Archives of general psychiatry} \textbf{45}, 1069--1077 (1988).}

\leavevmode\vadjust pre{\hypertarget{ref-samejima1997handbook}{}}%
\CSLLeftMargin{25. }%
\CSLRightInline{Samejima, F., Liden, W. van der \& Hambleton, R. Handbook of modern item response theory. (1997).}

\leavevmode\vadjust pre{\hypertarget{ref-bakerBasicsItemResponse2017}{}}%
\CSLLeftMargin{26. }%
\CSLRightInline{Baker, F. B. \& Kim, S.-H. \emph{The basics of item response theory using r}. (Springer, 2017).}

\leavevmode\vadjust pre{\hypertarget{ref-dall2010developmental}{}}%
\CSLLeftMargin{27. }%
\CSLRightInline{Dall'Oglio, A. M. \emph{et al.} Developmental evaluation at age 4: Validity of an italian parental questionnaire. \emph{Journal of paediatrics and child health} \textbf{46}, 419--426 (2010).}

\leavevmode\vadjust pre{\hypertarget{ref-field2013discovering}{}}%
\CSLLeftMargin{28. }%
\CSLRightInline{Field, A. \emph{Discovering statistics using IBM SPSS statistics}. (sage, 2015).}

\leavevmode\vadjust pre{\hypertarget{ref-Nunnally1978}{}}%
\CSLLeftMargin{29. }%
\CSLRightInline{Nunnally, J. C. \emph{Psychometric theory}. ({McGraw-Hill}, 1978).}

\leavevmode\vadjust pre{\hypertarget{ref-santhi_applications_2020}{}}%
\CSLLeftMargin{30. }%
\CSLRightInline{Santhi, N. \& Ball, D. M. \href{https://doi.org/10.1016/bs.pbr.2020.05.029}{Applications in sleep: {How} light affects sleep}. \emph{Progress in brain research} \textbf{253}, 17--24 (2020).}

\leavevmode\vadjust pre{\hypertarget{ref-thomas2019advances}{}}%
\CSLLeftMargin{31. }%
\CSLRightInline{Thomas, M. L. Advances in applications of item response theory to clinical assessment. \emph{Psychological assessment} \textbf{31}, 1442 (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-lok2018light}{}}%
\CSLLeftMargin{32. }%
\CSLRightInline{Lok, R., Smolders, K. C., Beersma, D. G. \& de Kort, Y. A. Light, alertness, and alerting effects of white light: A literature overview. \emph{Journal of biological rhythms} \textbf{33}, 589--601 (2018).}

\leavevmode\vadjust pre{\hypertarget{ref-siraji2021effects}{}}%
\CSLLeftMargin{33. }%
\CSLRightInline{Siraji, M. A., Kalavally, V., Schaefer, A. \& Haque, S. Effects of daytime electric light exposure on human alertness and higher cognitive functions: A systematic review. \emph{Frontiers in psychology} \textbf{12}, 765750--765750 (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-Siraji.2023}{}}%
\CSLLeftMargin{34. }%
\CSLRightInline{Siraji, M. A., Spitschan, M., Kalavally, V. \& Haque, S. \href{https://doi.org/10.1038/s41598-023-39636-y}{Light exposure behaviors predict mood, memory and sleep quality}. \emph{Scientific Reports} \textbf{13}, 12425 (2023).}

\leavevmode\vadjust pre{\hypertarget{ref-harris2009research}{}}%
\CSLLeftMargin{35. }%
\CSLRightInline{Harris, P. A. \emph{et al.} Research electronic data capture (REDCap)---a metadata-driven methodology and workflow process for providing translational research informatics support. \emph{Journal of biomedical informatics} \textbf{42}, 377--381 (2009).}

\leavevmode\vadjust pre{\hypertarget{ref-harris2019redcap}{}}%
\CSLLeftMargin{36. }%
\CSLRightInline{Harris, P. A. \emph{et al.} The REDCap consortium: Building an international community of software platform partners. \emph{Journal of biomedical informatics} \textbf{95}, 103208 (2019).}

\leavevmode\vadjust pre{\hypertarget{ref-Weinzaepflen.2021}{}}%
\CSLLeftMargin{37. }%
\CSLRightInline{Weinzaepflen, C. \& Spitschan, M. Enlighten your clock: How your body tells time. (2021) doi:\href{https://doi.org/10.17605/OSF.IO/ZQXVH}{10.17605/OSF.IO/ZQXVH}.}

\leavevmode\vadjust pre{\hypertarget{ref-f.lux}{}}%
\CSLLeftMargin{38. }%
\CSLRightInline{F.lux Software LLC. \href{https://justgetflux.com/}{F.lux}. (2021).}

\leavevmode\vadjust pre{\hypertarget{ref-comreyFirstCourseFactor1992}{}}%
\CSLLeftMargin{39. }%
\CSLRightInline{Comrey, A. L. \& Lee, H. B. \emph{A first course in factor analysis}. (Psychology press, 2013).}

\leavevmode\vadjust pre{\hypertarget{ref-schonbrodtWhatSampleSize2013}{}}%
\CSLLeftMargin{40. }%
\CSLRightInline{Schönbrodt, F. D. \& Perugini, M. \href{https://doi.org/10.1016/j.jrp.2013.05.009}{At what sample size do correlations stabilize?} \emph{Journal of research in personality} \textbf{47}, 609--612 (2013).}

\leavevmode\vadjust pre{\hypertarget{ref-bentlerPracticalIssuesStructural1987}{}}%
\CSLLeftMargin{41. }%
\CSLRightInline{Bentler, P. M. \& Chou, C.-P. \href{https://doi.org/10.1177/0049124187016001004}{Practical {Issues} in {Structural Modeling}}. \emph{Sociological methods \& research} \textbf{16}, 78--117 (1987).}

\leavevmode\vadjust pre{\hypertarget{ref-jacksonRevisitingSampleSize2003}{}}%
\CSLLeftMargin{42. }%
\CSLRightInline{Jackson, D. L. \href{https://doi.org/10.1207/S15328007SEM1001_6}{Revisiting {Sample Size} and {Number} of {Parameter Estimates}: {Some Support} for the {N}:q {Hypothesis}}. \emph{Structural equation modeling} \textbf{10}, 128--141 (2003).}

\leavevmode\vadjust pre{\hypertarget{ref-klinePrinciplesPracticeStructural2015}{}}%
\CSLLeftMargin{43. }%
\CSLRightInline{Kline, R. B. \emph{Principles and practice of structural equation modeling}. ({The Guilford Press}, 2016).}

\leavevmode\vadjust pre{\hypertarget{ref-worthingtonScaleDevelopmentResearch2006}{}}%
\CSLLeftMargin{44. }%
\CSLRightInline{Worthington, R. L. \& Whittaker, T. A. \href{https://doi.org/10.1177/0011000006288127}{Scale {Development Research}: {A Content Analysis} and {Recommendations} for {Best Practices}}. \emph{The Counseling psychologist} \textbf{34}, 806--838 (2006).}

\leavevmode\vadjust pre{\hypertarget{ref-watkinsStepbyStepGuideExploratory2020}{}}%
\CSLLeftMargin{45. }%
\CSLRightInline{Watkins, M. \emph{A {Step}-by-{Step Guide} to {Exploratory Factor Analysis} with {R} and {RStudio}}. (2020). doi:\href{https://doi.org/10.4324/9781003120001}{10.4324/9781003120001}.}

\leavevmode\vadjust pre{\hypertarget{ref-cattellScreeTestNumber1966}{}}%
\CSLLeftMargin{46. }%
\CSLRightInline{Cattell, R. B. \href{https://doi.org/10.1207/s15327906mbr0102_10}{The {Scree Test For The Number Of Factors}}. \emph{Multivariate Behavioral Research} \textbf{1}, 245--276 (1966).}

\leavevmode\vadjust pre{\hypertarget{ref-bandalosFactorAnalysisExploratory2018}{}}%
\CSLLeftMargin{47. }%
\CSLRightInline{Bandalos, D. L. \& Finney, S. J. Factor analysis: {Exploratory} and confirmatory. in \emph{The reviewer's guide to quantitative methods in the social sciences} 98--122 ({Routledge}, 2018).}

\leavevmode\vadjust pre{\hypertarget{ref-gadermann2012estimating}{}}%
\CSLLeftMargin{48. }%
\CSLRightInline{Gadermann, A. M., Guhn, M. \& Zumbo, B. D. Estimating ordinal reliability for likert-type and ordinal item response data: A conceptual, empirical, and practical guide. \emph{Practical Assessment, Research, and Evaluation} \textbf{17}, 3 (2012).}

\leavevmode\vadjust pre{\hypertarget{ref-zumbo2007ordinal}{}}%
\CSLLeftMargin{49. }%
\CSLRightInline{Zumbo, B. D., Gadermann, A. M. \& Zeisser, C. Ordinal versions of coefficients alpha and theta for likert rating scales. \emph{Journal of modern applied statistical methods} \textbf{6}, 4 (2007).}

\leavevmode\vadjust pre{\hypertarget{ref-dunn2014alpha}{}}%
\CSLLeftMargin{50. }%
\CSLRightInline{Dunn, T. J., Baguley, T. \& Brunsden, V. From alpha to omega: A practical solution to the pervasive problem of internal consistency estimation. \emph{British journal of psychology} \textbf{105}, 399--412 (2014).}

\leavevmode\vadjust pre{\hypertarget{ref-sijtsma2009use}{}}%
\CSLLeftMargin{51. }%
\CSLRightInline{Sijtsma, K. On the use, the misuse, and the very limited usefulness of cronbach's alpha. \emph{Psychometrika} \textbf{74}, 107 (2009).}

\leavevmode\vadjust pre{\hypertarget{ref-huCutoffCriteriaFit1999}{}}%
\CSLLeftMargin{52. }%
\CSLRightInline{Hu, L. \& Bentle, P. M. \href{https://doi.org/10.1080/10705519909540118}{Cutoff criteria for fit indexes in covariance structure analysis: {Conventional} criteria versus new alternatives}. \emph{Structural Equation Modeling: A Multidisciplinary Journal} \textbf{6}, 1--55 (1999).}

\leavevmode\vadjust pre{\hypertarget{ref-schumacker2004beginner}{}}%
\CSLLeftMargin{53. }%
\CSLRightInline{Schumacker, R. E. \& Lomax, R. G. \emph{A beginner's guide to structural equation modeling}. (psychology press, 2004).}

\leavevmode\vadjust pre{\hypertarget{ref-brownConfirmatoryFactorAnalysis2015}{}}%
\CSLLeftMargin{54. }%
\CSLRightInline{Brown, T. A. \emph{Confirmatory factor analysis for applied research}. ({The Guilford Press}, 2015).}

\leavevmode\vadjust pre{\hypertarget{ref-RN1272}{}}%
\CSLLeftMargin{55. }%
\CSLRightInline{Yu, C. Evaluating cutoff criteria of model fit indices for latent variable models with binary and continuous outcomes. ({ProQuest Dissertations Publishing}, 2002).}

\leavevmode\vadjust pre{\hypertarget{ref-putnick2016measurement}{}}%
\CSLLeftMargin{56. }%
\CSLRightInline{Putnick, D. L. \& Bornstein, M. H. Measurement invariance conventions and reporting: The state of the art and future directions for psychological research. \emph{Developmental review} \textbf{41}, 71--90 (2016).}

\leavevmode\vadjust pre{\hypertarget{ref-dimitrov2010testing}{}}%
\CSLLeftMargin{57. }%
\CSLRightInline{Dimitrov, D. M. Testing for factorial invariance in the context of construct validation. \emph{Measurement and Evaluation in Counseling and Development} \textbf{43}, 121--149 (2010).}

\leavevmode\vadjust pre{\hypertarget{ref-widaman1997exploring}{}}%
\CSLLeftMargin{58. }%
\CSLRightInline{Widaman, K. F. \& Reise, S. P. Exploring the measurement invariance of psychological instruments: Applications in the substance use domain. (1997).}

\leavevmode\vadjust pre{\hypertarget{ref-drasgow1985appropriateness}{}}%
\CSLLeftMargin{59. }%
\CSLRightInline{Drasgow, F., Levine, M. V. \& Williams, E. A. Appropriateness measurement with polychotomous item response models and standardized indices. \emph{British Journal of Mathematical and Statistical Psychology} \textbf{38}, 67--86 (1985).}

\leavevmode\vadjust pre{\hypertarget{ref-verriotto2017new}{}}%
\CSLLeftMargin{60. }%
\CSLRightInline{Verriotto, J. D. \emph{et al.} New methods for quantification of visual photosensitivity threshold and symptoms. \emph{Translational vision science \& technology} \textbf{6}, 18--18 (2017).}

\leavevmode\vadjust pre{\hypertarget{ref-eklund1996development}{}}%
\CSLLeftMargin{61. }%
\CSLRightInline{Eklund, N. \& Boyce, P. The development of a reliable, valid, and simple office lighting survey. \emph{Journal of the Illuminating Engineering Society} \textbf{25}, 25--40 (1996).}

\leavevmode\vadjust pre{\hypertarget{ref-bajaj2011validation}{}}%
\CSLLeftMargin{62. }%
\CSLRightInline{Bajaj, A., Rosner, B., Lockley, S. W. \& Schernhammer, E. S. Validation of a light questionnaire with real-life photopic illuminance measurements: The harvard light exposure assessment questionnaire. \emph{Cancer Epidemiology and Prevention Biomarkers} \textbf{20}, 1341--1349 (2011).}

\leavevmode\vadjust pre{\hypertarget{ref-dianat2013objective}{}}%
\CSLLeftMargin{63. }%
\CSLRightInline{Dianat, I., Sedghi, A., Bagherzade, J., Jafarabadi, M. A. \& Stedmon, A. W. Objective and subjective assessments of lighting in a hospital setting: Implications for health, safety and performance. \emph{Ergonomics} \textbf{56}, 1535--1545 (2013).}

\leavevmode\vadjust pre{\hypertarget{ref-horne1976self}{}}%
\CSLLeftMargin{64. }%
\CSLRightInline{Horne, J. A. \& Östberg, O. A self-assessment questionnaire to determine morningness-eveningness in human circadian rhythms. \emph{International journal of chronobiology} (1976).}

\leavevmode\vadjust pre{\hypertarget{ref-roenneberg2003life}{}}%
\CSLLeftMargin{65. }%
\CSLRightInline{Roenneberg, T., Wirz-Justice, A. \& Merrow, M. Life between clocks: Daily temporal patterns of human chronotypes. \emph{Journal of biological rhythms} \textbf{18}, 80--90 (2003).}

\leavevmode\vadjust pre{\hypertarget{ref-grandner2014development}{}}%
\CSLLeftMargin{66. }%
\CSLRightInline{Grandner, M. A., Jackson, N., Gooneratne, N. S. \& Patel, N. P. The development of a questionnaire to assess sleep-related practices, beliefs, and attitudes. \emph{Behavioral sleep medicine} \textbf{12}, 123--142 (2014).}

\leavevmode\vadjust pre{\hypertarget{ref-buysse1989pittsburgh}{}}%
\CSLLeftMargin{67. }%
\CSLRightInline{Buysse, D. J., Reynolds III, C. F., Monk, T. H., Berman, S. R. \& Kupfer, D. J. The pittsburgh sleep quality index: A new instrument for psychiatric practice and research. \emph{Psychiatry research} \textbf{28}, 193--213 (1989).}

\leavevmode\vadjust pre{\hypertarget{ref-Xie.2021}{}}%
\CSLLeftMargin{68. }%
\CSLRightInline{Xie, Y., Wu, X., Tao, S., Wan, Y. \& Tao, F. Development and validation of the self-rating of biological rhythm disorder for chinese adolescents. \emph{Chronobiology International} 1--7 (2022) doi:\href{https://doi.org/10.1080/07420528.2021.1989450}{10.1080/07420528.2021.1989450}.}

\leavevmode\vadjust pre{\hypertarget{ref-bossini2006sensibilita}{}}%
\CSLLeftMargin{69. }%
\CSLRightInline{Bossini, L. \emph{et al.} Sensibilit{à} alla luce e psicopatologia: Validazione del questionario per la valutazione della fotosensibilit{à} (QVF). \emph{Med Psicosomatica} \textbf{51}, 167--176 (2006).}

\end{CSLReferences}

\endgroup

\end{document}

### 2023-11-09 manuscript_SciRep.Rmd
Affiliation updated-MASJ

@@
     role:
+      - Project administration
+      - Methodology
       - Formal Analysis
@@
       - Writing – review & editing
+      - Supervision
 
@@
     institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"
+
   - id            : "3"
+    institution   : "North South University, Department of History and Philosophy, Bangladesh"
+
+  - id            : "4"
     institution   : "University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland"
-  - id            : "4"
+  - id            : "5"
     institution   : "Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands"
-  - id            : "5"
+  - id            : "6"
     institution   : "Eindhoven University of Technology, Intelligent Lighting Institute, Eindhoven, Netherlands"
-  - id            : "6"
+  - id            : "7"
     institution   : "Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Human-Technology Interaction, Eindhoven, Netherlands"
-  - id            : "7"
+  - id            : "8"
     institution   : "Monash University, Department of Electrical and Computer Systems Engineering, Selangor, Malaysia"
-  - id            : "8"
+  - id            : "9"
     institution   : "University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA"
-  - id            : "9"
+  - id            : "10"
     institution   : "Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA"
-  - id            : "10"
+  - id            : "11"
     institution   : "Translational Sensory & Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany"
-  - id            : "11"
+  - id            : "12"
     institution   : "TUM School of Medicine and Health, Technical University of Munich, Munich, Germany"
-  - id            : "12"
+  - id            : "13"
     institution   : "TUM Institute of Advanced Study (TUM-IAS), Technical University of Munich, Garching, Germany"
@@
     institution   : "Joint first author"
-
-  - id            : "13"
-    institution   : "North South University, Department of History and Philosophy, Bangladesh"
 

### 2023-11-09 manuscript_SciRep.tex
Affiliation updated-MASJ

@@
 The authors made the following contributions.
-Mushfiqul Anwar Siraji: Formal Analysis, Visualization, Writing -- original draft, Writing -- review \& editing; Rafael Robert Lazar: Data curation, Investigation, Project administration, Visualization, Writing -- original draft, Writing -- review \& editing; Juliëtte van Duijnhoven: Conceptualization, Methodology, Investigation, Writing -- review \& editing; Luc Schlangen: Conceptualization, Methodology, Investigation, Writing -- review \& editing; Shamsul Haque: Conceptualization, Supervision, Writing -- review \& editing; Vineetha Kalavally: Supervision, Writing -- review \& editing; Céline Vetter: Conceptualization, Writing -- review \& editing; Gena Glickman: Conceptualization, Methodology, Writing -- review \& editing; Karin Smolders: Conceptualization, Methodology, Writing -- review \& editing; Manuel Spitschan: Conceptualization, Data curation, Investigation, Project administration, Visualization, Methodology, Writing -- original draft, Writing -- review \& editing.
+Mushfiqul Anwar Siraji: Project administration, Methodology, Formal Analysis, Visualization, Writing -- original draft, Writing -- review \& editing; Rafael Robert Lazar: Data curation, Investigation, Project administration, Visualization, Writing -- original draft, Writing -- review \& editing; Juliëtte van Duijnhoven: Conceptualization, Methodology, Investigation, Writing -- review \& editing; Luc Schlangen: Conceptualization, Methodology, Investigation, Writing -- review \& editing; Shamsul Haque: Conceptualization, Supervision, Writing -- review \& editing; Vineetha Kalavally: Supervision, Writing -- review \& editing; Céline Vetter: Conceptualization, Writing -- review \& editing; Gena Glickman: Conceptualization, Methodology, Writing -- review \& editing; Karin Smolders: Conceptualization, Methodology, Writing -- review \& editing; Manuel Spitschan: Conceptualization, Data curation, Investigation, Project administration, Visualization, Methodology, Writing -- original draft, Writing -- review \& editing, Supervision.
 
@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Monash Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia\\\textsuperscript{2} Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland\\\textsuperscript{3} University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland\\\textsuperscript{4} Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands\\\textsuperscript{5} Eindhoven University of Technology, Intelligent Lighting Institute, Eindhoven, Netherlands\\\textsuperscript{6} Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Human-Technology Interaction, Eindhoven, Netherlands\\\textsuperscript{7} Monash University, Department of Electrical and Computer Systems Engineering, Selangor, Malaysia\\\textsuperscript{8} University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA\\\textsuperscript{9} Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA\\\textsuperscript{10} Translational Sensory \& Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany\\\textsuperscript{11} TUM School of Medicine and Health, Technical University of Munich, Munich, Germany\\\textsuperscript{12} TUM Institute of Advanced Study (TUM-IAS), Technical University of Munich, Garching, Germany\\\textsuperscript{*} Joint first author\\\textsuperscript{13} North South University, Department of History and Philosophy, Bangladesh\\\textsuperscript{+} Co First Author\\\textsuperscript{*} Corresponding Author}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Monash Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia\\\textsuperscript{2} Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland\\\textsuperscript{3} North South University, Department of History and Philosophy, Bangladesh\\\textsuperscript{4} University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland\\\textsuperscript{5} Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands\\\textsuperscript{6} Eindhoven University of Technology, Intelligent Lighting Institute, Eindhoven, Netherlands\\\textsuperscript{7} Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Human-Technology Interaction, Eindhoven, Netherlands\\\textsuperscript{8} Monash University, Department of Electrical and Computer Systems Engineering, Selangor, Malaysia\\\textsuperscript{9} University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA\\\textsuperscript{10} Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA\\\textsuperscript{11} Translational Sensory \& Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany\\\textsuperscript{12} TUM School of Medicine and Health, Technical University of Munich, Munich, Germany\\\textsuperscript{13} TUM Institute of Advanced Study (TUM-IAS), Technical University of Munich, Garching, Germany\\\textsuperscript{+} Joint first author\\\textsuperscript{*} Corresponding Author}
 

### 2023-11-09 manuscript_SciRep.Rmd
Affiliation conflict resloved-MASj

@@
     institution   : "Monash Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia"
+
   - id            : "2"
+    institution   : "North South University, Department of History and Philosophy, Bangladesh"
+
+  - id            : "3"
     institution   : "Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland"
-
-  - id            : "3"
-    institution   : "North South University, Department of History and Philosophy, Bangladesh"
 

### 2023-11-09 manuscript_SciRep.tex
Affiliation conflict resloved-MASj

@@
 
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Monash Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia\\\textsuperscript{2} Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland\\\textsuperscript{3} North South University, Department of History and Philosophy, Bangladesh\\\textsuperscript{4} University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland\\\textsuperscript{5} Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands\\\textsuperscript{6} Eindhoven University of Technology, Intelligent Lighting Institute, Eindhoven, Netherlands\\\textsuperscript{7} Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Human-Technology Interaction, Eindhoven, Netherlands\\\textsuperscript{8} Monash University, Department of Electrical and Computer Systems Engineering, Selangor, Malaysia\\\textsuperscript{9} University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA\\\textsuperscript{10} Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA\\\textsuperscript{11} Translational Sensory \& Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany\\\textsuperscript{12} TUM School of Medicine and Health, Technical University of Munich, Munich, Germany\\\textsuperscript{13} TUM Institute of Advanced Study (TUM-IAS), Technical University of Munich, Garching, Germany\\\textsuperscript{+} Joint first author\\\textsuperscript{*} Corresponding Author}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Monash Department of Psychology, Jeffrey Cheah School of Medicine and Health Sciences, Malaysia\\\textsuperscript{2} North South University, Department of History and Philosophy, Bangladesh\\\textsuperscript{3} Psychiatric Hospital of the University of Basel (UPK), Centre for Chronobiology, Basel, Switzerland\\\textsuperscript{4} University of Basel, Transfaculty Research Platform Molecular and Cognitive Neurosciences, Basel, Switzerland\\\textsuperscript{5} Eindhoven University of Technology, Department of the Built Environment, Building Lighting, Eindhoven, Netherlands\\\textsuperscript{6} Eindhoven University of Technology, Intelligent Lighting Institute, Eindhoven, Netherlands\\\textsuperscript{7} Eindhoven University of Technology, Department of Industrial Engineering and Innovation Sciences, Human-Technology Interaction, Eindhoven, Netherlands\\\textsuperscript{8} Monash University, Department of Electrical and Computer Systems Engineering, Selangor, Malaysia\\\textsuperscript{9} University of Colorado Boulder, Department of Integrative Physiology, Boulder, USA\\\textsuperscript{10} Uniformed Services University of the Health Sciences, Department of Psychiatry, Bethesda, USA\\\textsuperscript{11} Translational Sensory \& Circadian Neuroscience, Max Planck Institute for Biological Cybernetics, Tübingen, Germany\\\textsuperscript{12} TUM School of Medicine and Health, Technical University of Munich, Munich, Germany\\\textsuperscript{13} TUM Institute of Advanced Study (TUM-IAS), Technical University of Munich, Garching, Germany\\\textsuperscript{+} Joint first author\\\textsuperscript{*} Corresponding Author}
 

### 2023-12-04 manuscript_SciRep.Rmd
Figure 6 space adjusted

@@
   geom_line()+apatheme_3+
-  labs(y="Test Information", title="F5:Using light in the morning and during daytime") +ylim(0,8)+geom_area()+aes(fill= "#B09C8599")+theme(legend.position="none")+
+  labs(y="Test Information", title="F5: Using light in the morning and during daytime") +ylim(0,8)+geom_area()+aes(fill= "#B09C8599")+theme(legend.position="none")+
 scale_fill_identity()+xlab(expression(theta)) + 
